### 2022-02-24 R/exploratory/Notes.rmd
initialising refresh of repo to deal with large file problems from GIS. Also did some re-organising to keep things more focused

---
title: "How should we think about changes in the variance of physiological rates?"
output:
  html_document:
    code_folding: hide
    theme: united
    toc: yes
    toc_float: yes
author:  Daniel Noble, Fonti Kar, Frank Seebacher, Shinichi Nakagawa 
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: bib.bib
---

# Changes in Variance of Physiological rates

It it worth us thinking about what the change in variance of physiological rates, in response to acclimation, actually mean. There are a couple of ways we can pitch this. Frank, Shinichi and Dan thought about, and discussed briefly, the possibility of viewing this change as a change in the **Opportunity for Selection**. This makes intuitive sense given that natural selection is predicted to be limited by the total phenotypic variance of a trait. However, lets dissect this argument more.

First, it is a good idea to go and explore the original formulation of the **Opportunity for Selection** in more detail. The original idea was proposed by Crow [-@crow1958], discussing how to think about selection on human populations. Crow [-@crow1958] defines the *Total Selection Intensity* very clearly as:

> "...total amount of selection is best measured by the ratio of the variance in progeny number [reproductive success] to the square of the mean number. pg. 764"

This definition is as far as I can tell the exact formulation that is currently used in the evolutionary biology literature. This definition really means that, to make use of this term, we really need to know or have traits that are *reproductive success* or very closely related to reproductive success such as mating success, for example. This definition jives well with more recent papers that have discussed and used this term [@Krakauer2011; @janicke2016].

# Usefulness of *Opportunity for Selection* in our Context

We can dissect this even more by looking at the definition of responses to selection or adaptive evolutionary change from the breeders equation:

$$
\Delta{z} = h^2 \beta,
$$

where, $\Delta{z}$ is simply the change in trait from generation 1 to generation 2, $h^2$ is the heritability of the trait and $\beta$ is the selection gradient on the trait. It's worth parsing this equation down a bit further.

First, evolutionary biologists always use *relative reproductive success*, which is simply defined as $rw_{i} = w_{i} / \hat{w}$. Here, $w_{i}$ is individual *i*'s reproductive success and $\hat{w}$ is simply the population average reproductive success.

Additionally, they make use of standardsized traits. So, if trait *x* is of interest we can calculate a standardised trait $x_{std}$ as $x_{std} = x_{i} - \hat{x} / sd_{x}$, which is simply each individuals trait, subtracted from the population mean ($\hat{x}$) and divided by the population standard deviation ($sd_{x}$).

We also know that the heritability ($h^2$) is defined as $h^2 = V_{A} / V_{P}$, where $V_{A}$ is the additive genetic variance for a trait and $V_{P}$ is the total phenotypic variance.

The one last piece of information is dissecting down what $\beta$ actually is, now that we know we are working withe relative fitness ($rw_{i}$) and standardized traits ($x_{std}$).

$$
\beta = r_{rw,x_{std}} \frac{s_{rw}}{s_{x_{std}}}
$$

with $r_{rw,x_{std}}$ being the correlation between relative fitness and standardised trait. $s_{rw}/s_{x_{std}}$ is simply the ratio of standard deviations between the two variables. So, we can re-write our breeders equation as follows:

$$
\Delta{z} = \frac{V_{A}}{V_{P}} r_{rw,x_{std}} \frac{s_{rw}}{s_{x_{std}}},
$$

But, we can simplify this equation a few more ways. First, remember that $r_{rw,x_{std}}$ is defined as follows:

$$
r_{rw,x_{std}} = \frac{s_{rw,x_{std}}}{s_{rw}s_{x_{std}}}
$$

Where $s_{rw,x_{std}}$ is the covariance between relative fitness and trait. Also, remember that, because we have standardsied trait, the standard deviation is now equal to 1. So:

$$
\Delta{z} = \frac{V_{A}}{V_{P}} \frac{s_{rw,x_{std} }}{s_{rw}1} \frac{s_{rw}}{1}
$$

And, because $s_{rw}$ is both divided and multiplied, we can get rid of this term to simplify:
$$
\Delta{z} = \frac{V_{A}}{V_{P}} s_{rw,x_{std}}
$$

OK, so this is simple now. We can see the response to selection is dependent on the proportion of the phenotypic variation that is "heritable" in this case due to "genes", and the covariance between relative fitness and variance in a standardised trait.

From this equation, we can see that predicting the "evolutionary response" or the meaning of the **Opportunity for Selection** in this context is tricky. We can basically get any scenario we want.

#### Scenario 1: Increased evolutionary response!

We can only really be confident about a single parameter in this equation being changed and that's $V_{P}$ as this is all the information contained within our dataset. So, assume for a second that $V_{A}$ stays the same (pretty questionable, but maybe) and the covariance between fitness and trait also stays the same. If this is the case, because $V_{P}$ is inversely proportional to $\Delta{z}$ this means that decreased is $V_{P}$ actually increases responses to selection. This makes sense because if $V_{A}$ stays the same then when there is less noise (i.e., reduced $V_{P}$) the heritability increases, making responses faster!

In other words, in this scenario, because we observed a decreased variance (relative to the mean, anyway) in terrestrial systems we might expect, if the $V_{A}$ and $s_{rw,x_{std}}$ stays the same, that adaptive evolutionary responses would increase!

#### Scenario 2: No evolutionary response!

Under the assumption that both additive genetic and environmental (P) variance increase, which we actually have some data to support this [@RR2017], this would mean that heritability essentially stays the same, and assuming that selection stays the same it would mean that there would be no real change in the evolutionary response of the population because any increases in additive genetic variance are masked by increases in the non-genetic contributions. However, this is an unlikely scenario in our case because we know that $V_{P}$ is actually decreased.

#### Scenario 3: Slowed evolutionary response!

Given that we do not actually know what part of $V_{P}$ is decreasing it maybe that $V_{A}$ is actually decreasing at a faster rate as part of $V_{P}$, and as such, this would be expected to slow evolutionary responses if selection remains the same.

#### But, what about selection?

Up until now we have simply assumed that selection remains constant, but under more stressful conditions we would expect that selection would be stronger. However, things get hairy here because selection is always relative to the average within the population. So, it becomes incredibly hard to predict the strength of selection without also knowing fitness.

#### Overall Conclusions

I would say, given all of the above, it's a little unsettling to focus too heavily on the "evolutionary" implications because they are varied and we know little about key ingredients such as how traits are related to fitness and how selection operates on the traits. I suppose we could assume (had a nice conversation with Shinichi about this) that we can think of our result of $V_{P}$ as changes in the "capacity for selection on the trait" and also, if we assume a trait is not at all heritable, then a change in $V_{P}$ may still signify a lowered capacity of a population to cope with an changed environment and this make it more prone to population extinction. I would feel safe saying this, but we probably need to couch it better into theoretical terms. See section below. I guess one explanation for our patterns are simply that terrestrial systems physiological rates are reaching their limits, and thus, their overall variance within a population is simply getting squished. May just have consequences for populations and communities (see below). There is no question that terrestrial systems are completely screwed though (see below)!

# Thinking About Consequences of a Variance Change in Physiology **Rates**

One thing we haven't thought much about yet is the implications of the change in variance in **physiological rates**. I think it is really important that we recognize that all the variables we are dealing with are rates of change in physiological rates that have important consequences, not only for individuals, but also populations and communities in a ecological sense. The vast majority, as we know, are metabolic rates (e.g., vol O~2~ / hr). What we are showing is a decrease in variance of these rates with acclimation (controlling for the mean), and that we see a decreased variance in rates in terrestrial systems, a little in marine and nothing in freshwater. Is it worth thinking about what the consequences are of the changes in the variability of these rates within an individual and population? Can we make some sensible conclusions that are maybe more robust to the assumptions we would be making. It basically means that the population can only operate over a more limited range of environments? Would this be true? Maybe we should look a little more carefully at the eco-physiological literature that has really taken the 'functional trait' approach, often quite successfully – especially for plants. Here, we have all functional traits, we have them corrected for some environmental gradient (i.e., temperature) and these are all things that are strongly encouraged from the functional trait community perspective [@McGill2006; @Gomez2018; @Ghedini2018]. In other words, should we think about what a change in variance for physiological rates would mean for energy turnover? Population extinction (another explanation above)?

We could take a functional performance trait perspective. Assume that we have a population and individuals vary in their performance curves:

```{r eval=TRUE}
	sd_ind = 3
	 n_ind = 30
	 y0 = 10
	 Ek = 0.00006
	 k = 275:300
	 T = 34
	 To = 20

	 # Describe performance with the BA equation. Note that we have NO variation here. 
	 perf = y0* exp(-(Ek/k)*((1/T) - (1/To)))

```

# References

### 2022-02-24 R/exploratory/Overview_1.Rmd
initialising refresh of repo to deal with large file problems from GIS. Also did some re-organising to keep things more focused

---
title: "Acclimation Responses of Physiological Rates and Opprotunity for Selection"
output:
  html_document:
    code_folding: hide
    theme: united
    toc: yes
    toc_float: yes
author: Shinichi Nakagawa & Daniel Noble
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: bib.bib
---

```{r,echo=FALSE, cache=FALSE}
  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits
  options(digits = 2)
```

# Deriving New Temperature Corrected Effect Sizes for Mean and Variance

## *Q*~10~RR: Comparing mean physiological rates

  Inspired by Seebacher et al. [-@seebacher2015physiological] we derive a temperature corrected effect size to compare physiological rates, *Q*~10~RR, also known as, the temparature response ratio. We note that this is just a variant of the log response ratio (lnRR), which is one of the most popular effect size statistics [@hedges1999meta; @nakagawa2012methodological]. Given this, we can easily derive the sampling error variance for *Q*~10~RR (on the log scale), but surprsingly, it has not been done before in the literature. *Q*~10~RR is defined as:

  $$
  Q_{10}RR = \left( \frac{R_{2}}{R_{1}} \right)^{ \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) },
  $$
  where *R* is the rate and *T* is the temparature in Celsius (but can be kelvins). If we take the natural logarithm at the both sides:

  $$
  \ln{Q_{10}RR} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
  \left( \ln{R_2} -  \ln{R_1} \right).
  $$

  Therefore, the sampling variance of ln*Q*~10~RR (*V*~ln*Q*10~RR) is, following Hedges et al. [-@hedges1999meta]:
  $$
  V_{\ln{Q_{10}RR}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }^2
  \left[ \frac{(\text{SD}_{1})^2}{n_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{n_{2} ({R}_{2})^2} \right],
  $$
  where SD~1~ and SD~2~ are the sample standard deviation of *R*~1~ and *R*~2~ at two different temperatures (*T*~1~ and *T*~2~), respectively and *n* are sample size for estimating *R*.

  > [Wiki](https://en.wikipedia.org/wiki/Q10_(temperature_coefficient)) says "The *Q*~10~ temperature coefficient is a measure of the rate of change of a biological or chemical system as a consequence of increasing the temperature by 10&deg;C"

 #<!--- degree = &deg;C; check out https://gist.github.com/DeoluA/5a4e7dac54dbc3df19fe --->#

## *SQ*~10~: Comparing variances in physiological rates
  So *Q*~10~RR can be more accurately called 'the tempature coefficent of the rate of change'. Once one realizes that the rate, *R* has a SD, then, we can define what we call 'the tempature coefficent of change in the variation in the rates', which is inspired by Nakagawa et al. [-@nakagawa2015meta]. We denote this as *SQ*~10~, which can be written as:

  $$
  SQ_{10} = \left( \frac{\text{SD}_{2}}{\text{SD}_{1}} \right)^{ \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }.
  $$  
  Like *Q*~10~RR, we take the natural logarithm, then:
  $$
  \ln{SQ_{10}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
  \left( \ln{\text{SD}_2} -  \ln{\text{SD}_1} \right).
  $$
  The sampling variance for ln*S*~10~ (*V*~ln*S*10~) is, according to Nakagawa et al. [-@nakagawa2015meta]:
  $$
  V_{\ln{SQ_{10}}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }^2
  \left[ \frac{1}{2\left( n_{1}-1 \right)} + \frac{1}{2\left(n_{2} - 1\right)} \right]
  $$

  What does *SQ*~10~ tell us? And how is it different from *Q*~10~RR? *Q*~10~RR is also referred to as 'thermal sensitvity'. *SQ*~10~ represents a change of individual variation at two temparature. It is hard to come up with a nifty name but let's call it 'thermal individual-variation change' or 'thermal idiosyncrasy' is probably shorter and better? Actually Dan says "thermal stability" may capture the essence of *SQ*~10~.

## *CVQ*~10~: Comparing Coefficient of Variance in Physiological Rates

  We may want to derive *CVQ*~10~ (i.e., the coefficient of variance in Q10), which is the change in SD corrected for the mean (i.e., CV) given that we know there exsits the mean-variance relationship. NO idea how we call this but *CVQ*~10~ can be defiend as:

  $$
  CVQ_{10} = \left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right)^{ \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) },
  $$

  Like *SQ*~10~, we take the natural logarithm, then:

  $$
  \ln{CVQ_{10}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
  \left( \ln{\text{CV}_2} -  \ln{\text{CV}_1} \right).
  $$

  The sampling variance for ln*CV*~10~ (*V*~ln*CV*10~) is, follwoing Nakagawa et al. [-@nakagawa2015meta]:

  $$
  V_{\ln{CVQ}_{10}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }^2
  \left[ \frac{(\text{SD}_{1})^2}{n_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{n_{2} ({R}_{2})^2} + \frac{1}{2\left( n_{1}-1 \right)} + \frac{1}{2\left(n_{2} - 1\right)} \right]
  $$

  Note that we assume there is no correlaiton between the mean and variance at the level of the sampling error although Nakagawa et al. [-@nakagawa2015meta] did.

## Mathematical equivalence of Q~10~ effects sizes to LnRR?

  After some close inspection of things when interpreting, I (Dan) think we may not be getting at the question I (we) thought we are interested in. This only dawned on me when interpreting the effect size in detail.

  First, take a look back at Franks original paper. Basically, r1.1/2.1 to r1.2/r2.2 is really just discussing how the rate and variance change along the line of cold and warm acclimated. This is reflected strongly in the analyses presented throughout and the effect sizes we generate below. But, if we want to understand how exactly acclimation affects the mean and variance of physiological rates we need to compare to the post acclimation responses. However, contrary to what we have been thinking I do not think comparing r1.1 to r2.2 is relevant on its own (see the quite literal interpretations of this effect below). We certainly need to have an acute comparison otherwise post acclimation Q~10~ doesn't say much on it's own. There is no question that comparing r1.1 to r2.2 is relevant as a rate, but it's just that it needs to be relative to a non-acclimated response. The reason being is that the acclimation treatments are completely confounded with the measurement treatments. We already know from the Q~10~ analyses of acute responses below that, actually there are really strong effects on mean physiological rates in response to temperature, surprise, surprise. What is new, is that we show that this is a heteroscadastic! Which means that the variance around the population mean along these lines increases with temperature. This is totally new and unexplored.

  Nonetheless, this cool finding doesn't allow us to make conclusions about the extent to which 1) acclimation affects mean physiological rates and 2) how the variance of these physiological rates is impacted by acclimation. In other words, what we really need to do is contrast *Q*~10ac~RR (r1.1 to r1.2) with *Q*~10pa~RR (r1.1 to r2.2) effect sizes, or alternatively the slope of each acute response. Of course, comparing the slopes between cold acclimated response curves and warm acclimated response curves would limit the amount of data quite a bit as we would need to rely on fully factorial experiments. However, we can compare *Q*~10ac~RR (r1.1 to r1.2) with *Q*~10pa~RR (r1.1 to r2.2), as this is what was done in the original paper anyway and we can do this in an effect size framework as above:
  $$
  \ln{Q_{10}RR} = { \left(\ \frac{ { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
  \left( \ln{R_{1.2}} -  \ln{R_{1.1}} \right) }{ { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
  \left( \ln{R_{2.2}} -  \ln{R_{1.1}} \right)} \right) }
  $$

  But, this equation starts to look awfully familiar. We can easily see how this can be simplified. First, because we are taking a ratio the temperature correction factors completely cancel out. Second, we see that $\ln{R_{1.1}}$ is present in the denominator and numerator. So, this can go as well and our seemingly complex equation actually just simply condenses down mathematically to the good old fashioned log response ratio with the mean of the rates in the acclimation treatment 1 and acclimation 2 measured at the same temperature:

  $$
  \ln{RR} = {\ln \left( \frac{R_{1.2}}{R_{2.2}} \right)}
  $$

  Or, simply just:

  $$
  \ln{RR} = {\left( \ln{R_{1.2}} -  \ln{R_{2.2}} \right)}
  $$

  Mathematically, what this appears to mean (unless I made a mistake which of course is possible so check please), all we need to do to get at our question is simply just compare the mean physiological rates from the two acclimation treatments, measured at the same temperature.

  Actually, you will even notice that temperature is already corrected in these estimates, which means that we can actually compare across studies with wildly different temperatures anyway. Who the hell would have thought eh?

# Setting up R

```{r, include = FALSE}
  knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
```

```{r setup}
    # clearning up
    rm(list=ls())

    # loading packages
    devtools::install_github("haozhu233/kableExtra")
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets, metafor, stringr, formatR, rmarkdown, kableExtra)

    # loading functions
    source("../R/functions.R", chdir = TRUE)
```

## Loading and seeing data: R

  We can view the data

```{r data, message = FALSE}
    # getting data from Google Sheet 
    gs <- gs_title("q10_newdata")
    data <- as_tibble(gs_read(ss = gs))
    kable(data) %>%
    kable_styling(font_size = 10) %>% 
    	scroll_box(width = "100%", height = "200px")
```

# Getting *Q*~10~RR, *SQ*~10~ and *CVQ*~10~

### Taxonomy of *Q*~10~RR and *SQ*~10~

  We have 2 types but 3 kinds of *Q*~10~RR: acute termal sensitivity in the cold treatment (*Q*~10ac~RR), acute termal sensitivity in warm treatments (*Q*~10aw~RR) and post-acclimation thermal sensitivity (*Q*~10pa~RR). Likewise, we have 2 types but 3 kinds of *SQ*~10~: acute termal idiosyncrasy in the cold treatment (*SQ*~10ac~), acute termal idiosyncrasy in warm treatments (*SQ*~10aw~) and post-acclimation thermal idiosyncrasy (*SQ*~10pa~).

  But we probably should combined *Q*~10ac~RR and *Q*~10aw~RR (also for *S*~10ac~ and *S*~10aw~) as one effect size measure because "cold" in cold treatments is relative not absolute (think about how to do this effectively).

### Why do we need both *SQ*~10~ and *CVQ*~10~

  *SQ*~10~ tells us probably more about predictability of the trait at one temperature and also, statistically, heteroscedasticity along temperature needs to be modeled. In contrast, *CVQ*~10~ tells us more about evolutionary potential at a particular temperature and controls for the fact that the variance will be affected with any changes in the mean, and so, this needs to be controlled.

### Create Effect Sizes

```{r effect-size}
    # Adding 
    data$obs <- as.factor(1:dim(data)[1])

    # getting effect sizes
    data %<>% Q10S10(temp_1, temp_2, r1.1, r1.2, r2.1, r2.2, 
                     r1.1_se, r1.2_se, r2.1_se, r2.2_se,r1.1_N, r1.2_N, r2.1_N, r2.2_N)

    # adding species names
    data %<>% mutate(spp_names = str_c(genus, species, sep = "_"))

    kable(data) %>%
    kable_styling(font_size = 10) %>% 
      scroll_box(width = "100%", height = "200px")
```

# Data exploration (the mean-variance relationship)

```{r mv-relationship, warning=FALSE}

    p1 <-ggplot(data) +
      geom_point(aes(x = log(r1.1), y = log(r1.1_se*sqrt(r1.1_N)), color = habitat), size =1) +
      labs(x = "ln(mean)", y = "ln(SD)", title = "R1.1")

    p2 <-  ggplot(data) +
      geom_point(aes(x = log(r1.2), y = log(r1.2_se*sqrt(r1.2_N)), color = habitat), size =1) +
      labs(x = "ln(mean)", y = "ln(SD)", title = "R1.2")

    p3 <-ggplot(data) +
      geom_point(aes(x = log(r2.1), y = log(r2.1_se*sqrt(r2.1_N)), color = habitat), size =1) +
      labs(x = "ln(mean)", y = "ln(SD)", title = "R2.1")

    p4 <-  ggplot(data) +
      geom_point(aes(x = log(r2.2), y = log(r2.2_se*sqrt(r2.2_N)), color = habitat), size =1) +
      labs(x = "ln(mean)", y = "ln(SD)", title = "R2.2")

    grid.arrange(p1, p2, p3, p4, nrow = 2)
```

As we can see, there are very strong relationships between the mean and the variance (standard deviation), but we also see some outliers on the bottom of the figures - we need to check these points.

# Meta-analysis for *Q*~10~RR

### Meta-analysis for *Q*~10ac~RR

```{r ma-Q10ac, cache=TRUE}
    # data with sampling variance
    data %>% filter(!is.na(V_lnQ10ac), V_lnQ10ac > 0) -> data1

    m1 <- rma.mv(yi = lnQ10ac, V = V_lnQ10ac, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data1)
    summary(m1)
    # heterogeneity
    I2(m1)
```

So, just a note on **directionality**. We subtracted r1.2 from r1.1, which essentially means that when the rates of r1.2 are larger than the rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r1.2 has a ***higher*** rate than acclimation and measurement at r1.1 across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r1.2 has a ***lower*** rate than acclimation than acclimation and measurement at r1.1 across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm1 <- get_est(m1, "Intercept")
    exp(estm1$estimate)
```

**Interpretation**: In other words, on average cold acclimated populations have physiological rates at higher temperatures (r1.2) that are about `r (exp(estm1$estimate)-1)*100`% higher than physiological rates at lower temperatures (r1.1) over a 10&deg;C change in temperature.

### Meta-analysis for *Q*~10aw~RR

```{r, cache=TRUE}
    # data with sampling variance
    data %>% filter(!is.na(V_lnQ10aw), V_lnQ10aw > 0) -> data2

    m2 <- rma.mv(yi = lnQ10aw, V = V_lnQ10aw, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data2)
    summary(m2)
    # heterogeneity
    I2(m2)
```

So, just a note on **directionality**. We subtracted r2.2 from r2.1, which essentially means that when the rates of r2.2 are larger than the rates of r2.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** rate than acclimation and measurement at r2.1 across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** rate than acclimation than acclimation and measurement at r2.1 across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm2 <- get_est(m2, "Intercept")
    exp(estm2$estimate)
```

**Interpretation**: In other words, on average warm acclimated populations have physiological rates at higher temperatures (r2.2) that are about `r (exp(estm2$estimate)-1)*100`% higher than physiological rates at lower temperatures (r2.1) over a 10&deg;C change in temperature.

### Meta-analysis for *Q*~10pa~RR

```{r ma-Q10pa, cache=TRUE}
    # data with sampling variance
    data %>% filter(!is.na(V_lnQ10pa), V_lnQ10pa > 0) -> data3

    m3 <- rma.mv(yi = lnQ10pa, V = V_lnQ10pa, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data3)
    summary(m3)
    # heterogeneity
    I2(m3)
```

So, just a note on **directionality**. We subtracted r2.2 from r1.1, which essentially means that when the rates of r2.2 are larger than the rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm3 <- get_est(m3, "Intercept")
    exp(estm3$estimate)
```

**Interpretation**:In other words, on average, physiological rates of warm acclimated animals, measured at warm temperatures have physiological rates that are about `r (exp(estm3$estimate)-1)*100`% higher than physiological rates at lower acclimation and measurement temperatures (r1.1) over a 10&deg;C change in temperature.

# Meta-analysis for *SQ*~10~

### Meta-analysis for *SQ*~10ac~

```{r ma-S10ac, cache=TRUE}
  # data with sampling variance
  data %>% filter(!is.na(V_lnS10ac), lnS10ac != Inf,  lnS10ac != -Inf,  V_lnS10ac > 0) -> data4

  m4 <- rma.mv(yi = lnS10ac, V = V_lnS10ac, random = list(~ 1 | record_num, ~ 1 | spp_names,  ~ 1 | obs), data = data4)
  summary(m4)
  # heterogeneity
  I2(m4)
```

So, just a note on **directionality**. We subtracted r1.2 from r1.1, which essentially means that when the variance in rates of r1.2 are larger than the variance in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r1.2 has a ***higher*** variance than acclimation and measurement at r1.1 when comparing across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r1.2 has a ***lower*** variance in rates than acclimation and measurement at r1.1 when comparing across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm4 <- get_est(m4, "Intercept")
    exp(estm4$estimate)
```

**Interpretation**: In other words, on average cold acclimated populations have variance in physiological rates at higher temperatures (r1.2) that are about `r (exp(estm4$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r1.1) when comparing across a 10&deg;C change in temperature.

### Meta-analysis for *SQ*~10aw~

```{r ma-S10aw, cache=TRUE}
  # data with sampling variance
  # why do we get V_lnS10aw < 0??? - need to check data
  data %>% filter(!is.na(V_lnS10aw), lnS10aw != Inf,  lnS10aw != -Inf, V_lnS10aw > 0) -> data5

  m5 <- rma.mv(yi = lnS10aw, V = V_lnS10aw, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data5)
  summary(m5)
  # heterogeneity
  I2(m5)
```

So, just a note on **directionality**. We subtracted r2.2 from r2.1, which essentially means that when the variance in rates of r2.2 are larger than the variance in rates of r2.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance than acclimation and measurement at r2.1 when comparing across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in rates than acclimation  and measurement at r2.1 when comparing across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm5 <- get_est(m5, "Intercept")
    exp(estm5$estimate)
```

**Interpretation**: In other words, on average warm acclimated populations have variances in physiological rates at higher temperatures (r2.2) that are about `r (exp(estm5$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r2.1) when comparing across a 10&deg;C change in temperature.

### Meta-analysis for *SQ*~10pa~

```{r ma-S10pa, cache=TRUE}
    # data with sampling variance
    # why do we get V_lnS10aw < 0??? - need to check data
    data %>% filter(!is.na(V_lnS10pa), lnS10pa != Inf,  lnS10pa != -Inf, V_lnS10pa > 0) -> data6

    m6 <- rma.mv(yi = lnS10pa, V = V_lnS10pa, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data6)
    summary(m6)
    # heterogeneity
    I2(m6)
```

So, just a note on **directionality**. We subtracted r2.2 from r1.1, which essentially means that when the variation in rates of r2.2 are larger than the variance in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance in rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in physiological rates than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.

```{r, cache=TRUE}
    # data with sampling variance
    estm4 <- get_est(m6, "Intercept")
    exp(estm4$estimate)
```

**Interpretation**: In other words, on average, the variance in physiological rates of warm acclimated animals, measured at warm temperatures are about `r (exp(estm4$estimate)-1)*100`% higher than the variance in physiological rates at lower acclimation and measurement temperatures (r1.1) over a 10&deg;C change in temperature. However, this is just the variance and does not account for the fact that the mean physiological rate also changes, so this is why we also want to know whether this is a *real* change in variance or simply just a result of the change in mean we observed above.

# Meta-analysis for *CVQ*~10~

### Meta-analysis for *CVQ*~10ac~

```{r ma-SQ10ac, cache=TRUE}
  # data with sampling variance
  data %>% filter(!is.na(V_lnSQ10ac), lnSQ10ac != Inf,  lnSQ10ac != -Inf,  V_lnSQ10ac > 0) -> data7

  m7 <- rma.mv(yi = lnSQ10ac, V = V_lnSQ10ac, random = list(~ 1 | record_num, ~ 1 | spp_names,  ~ 1 | obs), data = data7)
  summary(m7)
  # heterogeneity
  I2(m7)
```

So, just a note on **directionality**. We subtracted r1.2 from r1.1, which essentially means that when the CV in rates of r1.2 are larger than the CV in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r1.2 has a ***higher*** coefficient of variation than acclimation and measurement at r1.1 when comparing across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r1.2 has a ***lower*** coefficient of variation in rates than acclimation and measurement at r1.1 when comparing across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm7 <- get_est(m7, "Intercept")
    exp(estm7$estimate)
```

**Interpretation**: In other words, on average cold acclimated populations have variance in physiological rates at higher temperatures (r1.2) that are about `r (exp(estm7$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r1.1) when comparing across a 10&deg;C change in temperature.

### Meta-analysis for *CVQ*~10aw~

```{r ma-SQ10aw, cache=TRUE}
  # data with sampling variance
  # why do we get V_lnS10aw < 0??? - need to check data
  data %>% filter(!is.na(V_lnSQ10aw), lnSQ10aw != Inf,  lnSQ10aw != -Inf, V_lnSQ10aw > 0) -> data8

  m8 <- rma.mv(yi = lnSQ10aw, V = V_lnSQ10aw, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data8)
  summary(m8)
  # heterogeneity
  I2(m8)
```

So, just a note on **directionality**. We subtracted r2.2 from r2.1, which essentially means that when the variance in rates of r2.2 are larger than the variance in rates of r2.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance than acclimation and measurement at r2.1 when comparing across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in rates than acclimation  and measurement at r2.1 when comparing across a 10&deg;C change.

We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.

```{r, cache=TRUE}
    # data with sampling variance
    estm8 <- get_est(m8, "Intercept")
    exp(estm8$estimate)
```

**Interpretation**: In other words, on average warm acclimated populations have variances in physiological rates at higher temperatures (r2.2) that are about `r (exp(estm8$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r2.1) when comparing across a 10&deg;C change in temperature.

### Meta-analysis for *CVQ*~10pa~

```{r ma-SQ10pa, cache=TRUE}
    # data with sampling variance
    # why do we get V_lnS10aw < 0??? - need to check data
    data %>% filter(!is.na(V_lnSQ10pa), lnSQ10pa != Inf,  lnSQ10pa != -Inf, V_lnSQ10pa > 0) -> data9

    m9 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9)
    summary(m9)
    # heterogeneity
    I2(m9)
```

So, just a note on **directionality**. We subtracted r2.2 from r1.1, which essentially means that when the coefficient of variation in rates of r2.2 are larger than the coefficient of variance in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance in rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change. In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in physiological rates than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.

```{r, cache=TRUE}
    # data with sampling variance
    estm5 <- get_est(m9, "Intercept")
    exp(estm5$estimate)
```

**Interpretation**: In other words, on average, the variance, controlling for changes in the mean, of physiological rates of warm acclimated animals, measured at warm temperatures are about `r (1-exp(estm5$estimate))*100`% **lower** than the variance in physiological rates at lower acclimation and measurement temperatures (r1.1) over a 10&deg;C change in temperature.

# Meta-regression for *Q*~10~RR: Habitat

### *Q*~10ac~RR: Habitat

```{r mr-Q10ac, cache=TRUE}

    m1.1 <- rma.mv(yi = lnQ10ac, V = V_lnQ10ac, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data1)
    summary(m1.1)

    # variance accounted for
      R2(m1.1)

    # get estimates
      res1.1 <- get_est(m1.1, mod = "habitat")

    # sample size
      data1 %>% group_by(habitat) %>% count() -> sample_size
      left_join(res1.1, sample_size, by =  c("name" = "habitat")) -> res1.1

```

**Interpretation**: Unsurprisingly, all mean physiological rates increase in the cold acclimated treatments. Freshwater physiological rates increase by `r (exp(res1.1$estimate[1])-1)*100`% at higher temperatures relative to colder temperatures, marine physiological rates increase by `r (exp(res1.1$estimate[2])-1)*100`% at higher temperatures relative to colder temperatures and terrestrial physiological rates increase by `r (exp(res1.1$estimate[3])-1)*100`% at higher temperatures relative to colder temperatures and significantly more than freshwater systems. In other words, for terrestrial species, physiological rates increase much more rapidly compared to marine and freshwater systems.

### *Q*~10aw~RR: Habitat

```{r mr-Q10aw, cache=TRUE}

    m2.1 <- rma.mv(yi = lnQ10aw, V = V_lnQ10aw, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data2)
    summary(m2.1)

    # variance accounted for
      R2(m2.1)

    # get estimates and plot
      res2.1 <- get_est(m2.1, mod = "habitat")

    # sample size
      data2 %>% group_by(habitat) %>% count() -> sample_size
      left_join(res2.1, sample_size, by =  c("name" = "habitat")) -> res2.1
```

**Interpretation**: Unsurprisingly, all mean physiological rates increase in the cold acclimated treatments. We largely see the same pattern at the higher acclimation temperature as we observe at the lower acclimation temperature. Freshwater physiological rates increase by `r (exp(res2.1$estimate[1])-1)*100`% at higher temperatures relative to colder temperatures, marine physiological rates increase by `r (exp(res2.1$estimate[2])-1)*100`% at higher temperatures relative to colder temperatures and terrestrial physiological rates increase by `r (exp(res2.1$estimate[3])-1)*100`% at higher temperatures relative to colder temperatures and significantly more than freshwater systems. Again, for terrestrial species, physiological rates increase much more rapidly compared to marine and freshwater systems.

### *Q*~10pa~RR: Habitat

```{r mr-Q10pa, cache=TRUE}

    m3.1 <- rma.mv(yi = lnQ10pa, V = V_lnQ10pa, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data3)
    summary(m3.1)
    # variance accounted for
    R2(m3.1)

    # get estimates and plot
    res3.1 <- get_est(m3.1, mod = "habitat")
    #s_plot(res3.1, title = "Q10pa - different habitats")

    # sample size
    data3 %>% group_by(habitat) %>% count() -> sample_size
    left_join(res3.1, sample_size, by =  c("name" = "habitat")) -> res3.1
```

**Interpretation**: Freshwater physiological rates increase by `r (exp(res3.1$estimate[1])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures, marine physiological rates increase by `r (exp(res3.1$estimate[2])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures. Terrestrial physiological rates increase by `r (exp(res3.1$estimate[3])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures. Again, for terrestrial species, post acclimation responses differ significantly from freshwater systems, but in all cases physiological rates are increased.

### A forest plot for *Q*~10~RR for 3 habitats

```{r Q-forest}

    # making a data frame for plotting
      resQ <- bind_rows(res1.1, res2.1, res3.1)

      lab <- c("FreshWater[acute1]", "Marin[acute1]", "Terrestrial[acute1]", "FreshWater[acute2]", "Marin[acute2]", "Terrestrial[acute2]", "FreshWater[acclim]", "Marin[acclim]", "Terrestrial[acclim]")
      reord <- c(1, 4, 7, 2, 5, 8, 3, 6, 9)

      resQ$lab <-lab
      resQ$reord <- reord

      resQ %<>% arrange(reord)

    # forest plot
      f_plot(resQ, title = "lnQ10[acute] vs. lnQ10[acclim] in 3 habitats")

```

# Meta-regression for *SQ*~10~: Habitat

### Meta-regression for *SQ*~10ac~: Habitat

```{r mr-S10ac, cache=TRUE}

    m4.1 <- rma.mv(yi = lnS10ac, V = V_lnS10ac, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data4)
    summary(m4.1)
    # variance accounted for
    R2(m4.1)

    # get estimates and plot
    res4.1 <- get_est(m4.1, mod = "habitat")

    # sample size
    data4 %>% group_by(habitat) %>% count() -> sample_size
    left_join(res4.1, sample_size, by =  c("name" = "habitat")) -> res4.1
```

**Interpretation**: Freshwater physiological rates increase by `r (exp(res3.1$estimate[1])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures, marine physiological rates increase by `r (exp(res3.1$estimate[2])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures. Terrestrial physiological rates increase by `r (exp(res3.1$estimate[3])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures. Again, for terrestrial species, post acclimation responses differ significantly from freshwater systems, but in all cases physiological rates are increased.

### Meta-regression for *SQ*~10aw~: Habitat

```{r mr-S10aw, cache=TRUE}

    m5.1 <- rma.mv(yi = lnS10aw, V = V_lnS10aw, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data5)
    summary(m5.1)
    # variance accounted for
    R2(m5.1)

    # get estimates and plot
    res5.1 <- get_est(m5.1, mod = "habitat")
    #s_plot(res5.1, title = "S10aw - different habitats")

    # sample size
    data5 %>% group_by(habitat) %>% count() -> sample_size
    left_join(res5.1, sample_size, by =  c("name" = "habitat")) -> res5.1
```

**Interpretation**: For populations acclimated to warm conditions, variance in freshwater physiological rates increase by `r (exp(res5.1$estimate[1])-1)*100`% when measured at higher temperatures relative to animals measured at colder temperatures, marine variance in physiological rates increase by `r (exp(res5.1$estimate[2])-1)*100`% when measured at higher temperatures relative to animals measured at colder temperatures. Variance in terrestrial physiological rates increase by `r (exp(res5.1$estimate[3])-1)*100`% when measured at higher temperatures relative to animals measured at colder temperatures. There doesn't appear to be any significant difference between organisms occupying major habitat types.

### Meta-regression for *SQ*~10pa~: Habitat

```{r mr-S10pa, cache=TRUE}

    m6.1 <- rma.mv(yi = lnS10pa, V = V_lnS10pa, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data6)
    summary(m6.1)
    # variance accounted for
    R2(m6.1)

    # get estimates and plot
    res6.1 <- get_est(m6.1, mod = "habitat")
    #s_plot(res6.1, title = "S10pa - different habitats")

    # sample size
    data6 %>% group_by(habitat) %>% count() -> sample_size
    left_join(res6.1, sample_size, by =  c("name" = "habitat")) -> res6.1
```

**Interpretation**: Variance in freshwater physiological rates increase by `r (exp(res5.1$estimate[1])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures, marine variance in physiological rates increase by `r (exp(res5.1$estimate[2])-1)*100`% when acclimated and measured at higher temperatures relative to animals measured and aclimated at colder temperatures. Variance in terrestrial physiological rates increase by `r (exp(res5.1$estimate[3])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures. Again, for terrestrial species, post acclimation responses differ significantly from freshwater systems, but in all cases physiological rates are increased.

### A forest plot for *SQ*~10~ for 3 habitats

```{r S-forest}

    # making a data frame for plotting
      resS <- bind_rows(res4.1, res5.1, res6.1)
      resS$lab <-lab
      resS$reord <- reord

      resS %<>% arrange(reord)

    # forest plot
      f_plot(resS, title = "lnS10[acute] vs. lnS10[acclim] in 3 habitats")

```

# Meta-regression for *CVQ*~10~: Habitat

### *CVQ*~10ac~: Habitat

```{r mr-SQ10ac, cache=TRUE}

    m7.1 <- rma.mv(yi = lnSQ10ac, V = V_lnSQ10ac, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data7)
    summary(m7.1)
    # variance accounted for
    R2(m7.1)

    # get estimates and plot
    res7.1 <- get_est(m7.1, mod = "habitat")
    #s_plot(res7.1, title = "SQ10ac - different habitats")

    # sample size
    data7 %>% group_by(habitat) %>% count() -> sample_size
    left_join(res7.1, sample_size, by =  c("name" = "habitat")) -> res7.1
```

### *CVQ*~10aw~: Habitat

```{r mr-SQ10aw, cache=TRUE}

    m8.1 <- rma.mv(yi = lnSQ10aw, V = V_lnSQ10aw, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data8)
    summary(m8.1)
    # variance accounted for
    R2(m8.1)

    # get estimates and plot
    res8.1 <- get_est(m8.1, mod = "habitat")
    #s_plot(res8.1, title = "SQ10aw - different habitats")

    # sample size
    data8 %>% group_by(habitat) %>% count() -> sample_size
    left_join(res8.1, sample_size, by =  c("name" = "habitat")) -> res8.1
```

### *CVQ*~10pa~: Habitat

```{r mr-SQ10pa, cache=TRUE}

    m9.1 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9)
    summary(m9.1)

    # m9.2 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, mod = ~ habitat , random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9)
    # summary(m9.2)

    # variance accounted for
      R2(m9.1)

    # get estimates and plot
      res9.1 <- get_est(m9.1, mod = "habitat")
      #s_plot(res9.1, title = "SQ10pa - different habitats")

    # sample size
      data %>% group_by(habitat) %>% count() -> sample_size
      left_join(res9.1, sample_size, by =  c("name" = "habitat")) -> res9.1
```

### A forest polot for *CVQ*~10~ for 3 habitats

```{r SQ-forest}

    # making a data frame for plotting
      resSQ <- bind_rows(res7.1, res8.1, res9.1)
      resSQ$lab <-lab
      resSQ$reord <- reord

      resSQ %<>% arrange(reord)

    # forest plot
      f_plot(resSQ, place = "negative", title = "lnSQ10[acute] vs. lnSQ10[acclim] in 3 habitats")

```

# Meta-regression for *Q*~10pa~RR: Traits in habitat

We can now have a look at the relationship between traits and habitat, but first we need to explore how much data we have in the relevant trait categories across the different habitat types. Here, we will only look at acclimation responses as this is what makes most sense.

```{r, cache=TRUE}
    table3 <- table(data3$trait_category, data3$habitat) 
    kable(table3)
```

So, we can see that we have quite a lot of traits not present in terrestrial systems. So, for simplicity, lets just exclude for this analysis any trait habitat combination with less than n = 5.

```{r, cache=TRUE}
    data3.2<- data3 %>% group_by(trait_category, habitat) %>% 
    filter(n() >= 5) 
```

OK, so now we are confident that we have removed levels with insufficient sample sizes. Now we can model the interaction, we'll simply create a variable for interacting trait and habitat to make the modeling a little easier as then we will have the mean estimate for each of the categories.

```{r, cache=TRUE}
    #Just to keep things easier for modelling just create a variable interacting trait and habitat
    data3.2$trait_habitat <- data3.2 %$% paste0(habitat, "_", trait_category)

    m10.1 <- rma.mv(yi = lnQ10pa, V = V_lnQ10pa, mod = ~ trait_habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data3.2)
    summary(m10.1)

    # variance accounted for
      R2(m10.1)

    # get estimates and plot
      res10.1 <- get_est(m10.1, mod = "trait_habitat")

    # sample size
      data3.2 %>% group_by(trait_habitat) %>% count() -> sample_size
      left_join(res10.1, sample_size, by =  c("name" = "trait_habitat")) -> res10.1
```

```{r, cache = TRUE}
    forest_plot <- function(est_table, col=colour, ylabel = "", xlabel = "lnQ10RR", xlimits = c(-0.5, 1.6), n_pos = -0.25){
      plot(1:nrow(est_table) ~ estimate, data = est_table, xlim = xlimits, ylab =ylabel, xlab = xlabel, col = colour, pch = 16, cex = 1.8, yaxt='n')
      arrows(x0= est_table$estimate, y0 = 1:nrow(est_table), y1 = 1:nrow(est_table), x1 = est_table$upperCL, length = 0, angle =90, col = colour)
      arrows(x0= est_table$estimate, y0 = 1:nrow(est_table), y1 = 1:nrow(est_table), x1 = est_table$lowerCL, length = 0, angle =90, col = colour)
      abline(v = 0, lty = 2)
      text(paste0("n = ", est_table$n), y = 1:nrow(est_table), x = n_pos, pos=2)
      axis(side = 2, at = 1:nrow(est_table), labels = est_table$name, las = 1)
    }

    # making a data frame for plotting
    # forest plot
      colour <- c(rep("orange", 10), rep("blue", 11), rep("forestgreen", 4), rep("blue", 11))

      par(mar = c(4,10,1,1))
      forest_plot(est_table=res10.1)
```

Here, we can basically see that the mean actually is affected pretty much across the board, but we see a more nuanced effect. For example, in freshwater systems basically acclimation changes the mean response for all traits, but we see that in marine systems performance based indices's are unaffected (sprint, endurance), whereas metabolic processes are. In contrast, we see performance and metabolism affected in terrestrial systems but this doesn't seem to be related to metabolic enzymes.

# Meta-regression for *SQ*~10pa~: Traits in habitat

We can now look at the variance change across each of the categories. First, set the data up as above.

```{r, cache=TRUE}
    data6.1 <- data6 %>% group_by(trait_category, habitat) %>% 
    filter(n() >= 5) 
    table6 <- table(data6.1$trait_category, data6.1$habitat) 
    kable(table6)
```

OK, so now that this is set up, lets model the variance

```{r, cache=TRUE}
    #Just to keep things easier for modelling just create a variable interacting trait and habitat
    data6.1$trait_habitat <- data6.1 %$% paste0(habitat, "_", trait_category)

    m11.1 <- rma.mv(yi = lnS10pa, V = V_lnS10pa, mod = ~ trait_habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data6.1)
    summary(m11.1)

    # variance accounted for
      R2(m11.1)

    # get estimates and plot
      res11.1 <- get_est(m11.1, mod = "trait_habitat")

    # sample size
      data6.1 %>% group_by(trait_habitat) %>% count() -> sample_size
      left_join(res11.1, sample_size, by =  c("name" = "trait_habitat")) -> res11.1
```

```{r, cache = TRUE}
      colour <- c(rep("orange", 10), rep("blue", 11), rep("forestgreen", 4), rep("blue", 11))
      par(mar = c(4,10,1,1))
      forest_plot(est_table=res11.1, xlimits = c(-1.5, 1.4), n_pos = -1.1, xlab = "lnSQ_10")
```

# Meta-regression for *CVQ*~10pa~: Traits in habitat

Of course, we may see changes in variance simply because we see a shit in the mean, which is potentially vary true because of the fact that we have strong mean-variance relationships in these data. So, better here to focus on changes in variance independent of the mean using *CVQ*~10pa~.

```{r, cache=TRUE}
    data9.1 <- data9 %>% group_by(trait_category, habitat) %>% 
    filter(n() >= 5) 
    table9 <- table(data9.1$trait_category, data9.1$habitat) 
    kable(table9)
```

OK, so now that this is set up, lets model the coefficient of variance.

```{r, cache=TRUE}
    #Just to keep things easier for modelling just create a variable interacting trait and habitat
    data9.1$trait_habitat <- data9.1 %$% paste0(habitat, "_", trait_category)

    m12.1 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, mod = ~ trait_habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9.1)
    summary(m12.1)

    # variance accounted for
      R2(m12.1)

    # get estimates and plot
      res12.1 <- get_est(m12.1, mod = "trait_habitat")

    # sample size
      data9.1 %>% group_by(trait_habitat) %>% count() -> sample_size
      left_join(res12.1, sample_size, by =  c("name" = "trait_habitat")) -> res12.1
```

```{r, cache = TRUE}
      colour <- c(rep("orange", 10), rep("blue", 11), rep("forestgreen", 4), rep("blue", 11))
      par(mar = c(4,10,1,1))
      forest_plot(est_table=res12.1, xlimits = c(-1.8, 0.8), n_pos = -1.5, xlab = "lnCVQ_10")
```

# Log response Ratio of the Acclimation treatments

As discussed above, these analyses seem not to get at exactly what we are after. We want to know how the Q~10~ changes as a function of acclimation, which essentially means comparing and contrasting Q~10aw~RR with Q~10pa~RR. Or, what appears to be an equivalent and more simple formulation, the log response ratio of the acclimation treatments at the same temperature. Now, whether we compare the cold versus the hot acclimation treatment direction or *vice versa* will likely be important. So, lets, for now just have a look at the habitat and trait models in the context of the log response ratio. Here is the equations that we will use:

$$
  \ln{RR} = {\ln \left( \frac{R_{1.2}}{R_{2.2}} \right)}
$$

and the the sampling variance for this is:

$$
  V_{\ln{RR}} = {\left( \frac{SD^2_{R_{1.2}}}{n_{R_{1.2}}M^2_{R_{1.2}}} \right)} + {\left( \frac{SD^2_{R_{2.2}} }{n_{R_{2.2}}M^2_{R_{2.2}}} \right)}
$$

First, we need a function for generating this new effect. I am going to just simply focus on the mean physiological rates for now given time constraints, but these will apply for variance too:

```{r}
      lnRR <- function(data, r1_2, r2_2, se1_2, se2_2, n1_2, n2_2){

            sd1_2 <- se1_2*sqrt(n1_2)
            sd2_2 <- se2_2*sqrt(n2_2)

           # log response ratio
           lnRR <- log(r1_2) - log(r2_2)

           # Sampling variance log RR
          VlnRR <- ( (sd1_2^2) / (n1_2*(r1_2^2)) ) + ( (sd2_2^2) / (n2_2*(r2_2^2)) )

          # Create the data table and add back into the data.
           lnRR <- tibble(lnRRac = lnRR, V_lnRRac = VlnRR)

           data <- bind_cols(data, lnRR)

        return(data)
      }
```

We can then add in this new effect size to the data.

```{r}
# getting effect sizes
    data %<>% lnRR(r1_2= data$r1.2, r2_2=data$r2.2, se1_2=data$r1.2_se, se2_2=data$r2.2_se, n1_2=data$r1.2_N, n2_2=data$r2.2_N)

```

Right, so now that we have all this we can do a meta-analysis of the **acclimation effects** on physiological rates and variance in physiological rates.

```{r}
  data %>% filter(!is.na(V_lnRRac), V_lnRRac > 0) -> data_acclim

  m_acclim <- rma.mv(yi = lnRRac, V = V_lnRRac, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data_acclim)
  summary(m_acclim)

  est_acclim <- get_est(m_acclim)

```

**Interpretation**: The above meta-analytic model suggests that across all organisms, traits and habitat types physiological rates of cold acclimated animals measured at higher temperatures are only `r (exp(est_acclim$estimate)-1)*100`% higher than animals acclimated at higher temperatures and measured at those temperatures. In other words, it doesn't look like acclimation, more generally, helps reduce the difference in physiological rates, but obviously there is a huge amount of variability among taxa and within these data that need to be explored.

We can explore this with respect to the original question of comparing Q10 acclimation across the major habitat types.

```{r}

  m_acclim_habitat <- rma.mv(yi = lnRRac, V = V_lnRRac, mod = ~ habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data_acclim)
  summary(m_acclim_habitat)

  est_acclim_habitat <- get_est(m_acclim_habitat, "habitat")

```

**Interpretation**: We can estimate the acclimation response at higher temperatures (note we lose power as we ignore the lower one, but for now this is ok) for organisms within each of the habitat types (freshwater, marine and terrestrial). So, cold acclimated freshwater species that are measured at higher temperatures have a `r (exp(est_acclim_habitat$estimate[1])-1)*100`% **higher** rate in physiological responses compared to warm acclimated freshwater species measured at the same *higher* temperature. Cold acclimated marine species that are measured at higher temperatures have a `r (exp(est_acclim_habitat$estimate[2])-1)*100`% **higher** rate in physiological responses compared to warm acclimated freshwater species measured at the same *higher* temperature. Lastly, cold acclimated terrestrial species have a `r (1-exp(est_acclim_habitat$estimate[3]))*100`% very slight, non-significant decrease in physiological rates at higher temperatures compared to warm acclimated terrestrial species measured at those same temperatures.

# Information for this session: R

```{r session, include = TRUE, echo = FALSE}
    sessionInfo()
```

# References

### 2022-02-24 R/tree_Q10.Rmd
initialising refresh of repo to deal with large file problems from GIS. Also did some re-organising to keep things more focused

---
title: "species_tree_Q10"
author: "ML"
date: "17/11/2019"
output: html_document
---

*NOTE:* not tested for knitting

```{r setup, cache = F, echo=FALSE, results = FALSE}
knitr::opts_chunk$set(error = TRUE) #allow some execution errors
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, warning = FALSE)
sessionInfo()
```

```{r prepare, message = FALSE, echo = TRUE, eval = FALSE, warning = FALSE}
install.packages("tidyverse")
install.packages("ape")
install.packages("curl")
install.packages("fulltext")
install.packages("treebase")
install.packages("devtools")
devtools::install_github("ropensci/rotl", dependencies = TRUE, build_vignette=TRUE)
install.packages("rotl")
install.packages("kutlis")
```

```{r load packages, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE}
library(tidyverse)
library(ape, curl)
library(rotl)
library(kutils) #https://rdrr.io/cran/kutils/man/mgsub.html
```

```{r load data, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE}
setwd("/Users/itchyshin/Dropbox/Losia-Shinichi/LAB/MA_general/trees_other/Shin_Q10")
dat <- read.csv("species_list_Q10.csv")
str(dat)
myspecies <- as.character(unique(dat$species_full)) #get list of species
str_sort(myspecies) #visual check
length(myspecies) #239 species
length(unique(myspecies)) #239 unique species names (does not account for synonyms)
```

## Using *rotl* package to retrieve synthetic species tree from Open Tree of Life

Rotl is an R package (https://peerj.com/preprints/1471/) allowing access to synthetic phylogenetic tree available at Open Tree of Life database (https://opentreeoflife.org/).

```{r rotl find species, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE, }
taxa <- tnrs_match_names(names = myspecies)
#Warning message: Enithares sp are not matched
dim(taxa) #239
table(taxa$approximate_match) #234 + 4 = 238, one row is NA, i.e. no match (Enithares sp)
#taxa[taxa$approximate_match==TRUE, ] #4 rows with approximate matches
```

Temporarily replace Enithares sp with Enithares ciliata

```{r rotl replace and find species, warning = FALSE, results=FALSE, eval = TRUE}
myspecies2 <- gsub("Enithares sp", "Enithares ciliata", myspecies)
taxa2 <- tnrs_match_names(names = myspecies2)
dim(taxa2) #239
table(taxa2$approximate_match) #235 + 4 = 239, all matched, but 4 are approximate
```

Get the initial tree.

```{r rotl species tree, warning = FALSE, results=FALSE}
tree <- tol_induced_subtree(ott_ids = taxa2[["ott_id"]], label_format = "name")  
#Error: HTTP failure: 400 [/v3/tree_of_life/induced_subtree] Error: node_id 'ott276728' was not found!list(ott276728 = "pruned_ott_id")
taxa2[taxa2$ott_id==276728, ] #Lithasia obovata - uncertain naming and position?
#OTOL explanation: This taxon is in our taxonomy but does not appear in the latest synthetic tree. This can happen for a variety of reasons, but the most probable is that is has a taxon flag (e.g. incertae sedis) that causes it to be pruned from the synthetic tree.
#https://tree.opentreeoflife.org/taxonomy/browse?id=231740
#https://tree.opentreeoflife.org/taxonomy/browse?id=670621
```

Temporarily replace Lithasia obovata with Aspella anceps (all genus Lithasia is hidden_inherited, same for all Pleuroceridae and a few levels up, Aspella is another snail from Neogastropoda). ALso fix Fundulus heteroclitus to match the name in OTOL database.

```{r rotl replace and find species again, warning = FALSE, results=FALSE, eval = TRUE}
myspecies2 <- gsub("Lithasia obovata", "Aspella anceps", myspecies2)
myspecies2[myspecies2=="Fundulus heteroclitus"] <-"Fundulus heteroclitus heteroclitus" #use subspecies name (diff syntax used due to double-matching)
```

```{r check for duplicated species - synonymous names, warning = FALSE, results=FALSE, eval = TRUE}
length(unique(taxa2[["ott_id"]])) #238
taxa2[duplicated(taxa2[["ott_id"]])==TRUE,] #check for non-unique ID's (some potential species synonyms)
taxa2[taxa2$ott_id == 829098,] #Chinemys reevesii = Mauremys reevesii

#change in the original species list to get rid of the synonyme! (IMPORTANT - CHANGE ALSO IN THE ORIGINAL DATASET)
myspecies2 <- gsub("Chinemys reevesii", "Mauremys reevesii", myspecies2)
length(unique(myspecies2)) #238
myspecies2 <- unique(myspecies2)
```

Get second tree for 238 unique species.

```{r rotl species tree2, warning = FALSE, results=FALSE}
taxa2 <- tnrs_match_names(names = myspecies2)
#taxa2
dim(taxa2) #238

tree2 <- tol_induced_subtree(ott_ids = taxa2[["ott_id"]], label_format = "name")  
#plot(tree2, cex=.6, label.offset =.1, no.margin = TRUE)
```

Check matching species and clean the tree

```{r re-check and reverse tree labels}
#make copies
tree3 <- tree2
taxa3 <- taxa2

#remove comments from taxa3$unique_name and tree3$tip.label
taxa3$unique_name <- gsub(" \\(.*", "", taxa3$unique_name) #remove comments
tree3$tip.label <- gsub(" \\(.*", "", tree3$tip.label) #remove comments
tree3$tip.label <- gsub("_"," ", tree3$tip.label) #get rid of the underscores

#check overlap and differences
intersect(tree3$tip.label, taxa3$unique_name) #237
setdiff(tree3$tip.label, taxa3$unique_name) #1 - Osmerus
setdiff(taxa3$unique_name, tree3$tip.label) #1 - Osmerus

#fix Osmerus on tree3$tip.label
tree3$tip.label <- gsub("Osmerus", "Osmerus mordax", tree3$tip.label)

#check overlap and differences
intersect(tree3$tip.label, taxa3$unique_name) #238
setdiff(tree3$tip.label, taxa3$unique_name) #0
setdiff(taxa3$unique_name, tree3$tip.label) #0
#now tip labels match exactly unique_name used by OTOL

#capitalise first letter in search string (names in the original dataset, except few changes we made to make the search work)
taxa3$search_string <- paste(toupper(substr(taxa3$search_string, 1, 1)), substr(taxa3$search_string, 2, nchar(taxa3$search_string)), sep="")

#check overlap and differences between tree tips labels names and search string names (names in the original dataset, except few changes we made to make the search work)
intersect(taxa3$search_string, tree3$tip.label) #208
setdiff(taxa3$search_string, tree3$tip.label) #30
setdiff(tree3$tip.label, taxa3$search_string) #30

#substitute names in tree tip labels to these from search string, based on unique name match
tree3$tip.label <- kutils::mgsub(taxa3$unique_name, taxa3$search_string, tree3$tip.label)

#re-check overlap and differences with search string
intersect(taxa3$search_string, tree3$tip.label) #2238
setdiff(taxa3$search_string, tree3$tip.label) #0
setdiff(tree3$tip.label, taxa3$search_string) #0

#check overlap and differences with myspecies list
intersect(myspecies, tree3$tip.label) #235
setdiff(myspecies, tree3$tip.label) #3
setdiff(tree3$tip.label, myspecies) #3

#make changes on tree3 to match exactly names in myspecies (except the sysnomym)
tree3$tip.label <- gsub("Fundulus heteroclitus heteroclitus", "Fundulus heteroclitus", tree3$tip.label)
tree3$tip.label <- gsub("Aspella anceps", "Lithasia obovata", tree3$tip.label)
tree3$tip.label <- gsub("Enithares ciliata", "Enithares sp", tree3$tip.label)

#re-check overlap and differences with myspecies list
intersect(myspecies, tree3$tip.label) #238
setdiff(myspecies, tree3$tip.label) #"Chinemys reevesii" - synonymous species name (not in the tree)
setdiff(tree3$tip.label, myspecies) #0
#tree labels are now mayching these in myspecies list, except "Chinemys reevesii"

#check if the tree is really binary 
is.binary.tree(tree3) #FALSE (i.e. there are polytomies) - a few small polytomies very close to the tree tips
#resolve polytomies randomly to make binary tree
tree_binary <- multi2di(tree3, random = TRUE)
is.binary.tree(tree_binary) #TRUE
# tree_binary$node.label <- NULL #you can delete internal node labels
# *NOTE:* no branch lengths are included, they can be created later via simulations.   
```

Save tree

```{r save final tree}
write.tree(tree_binary, file="tree_binary_SN_Q10.tre") #save the tree

# *NOTE:* underscores within species names on tree tip labals are added automatically
# tree <- read.tree(file="tree_binary_SN_Q10.tre") #if you need to read in the tree
# tree$tip.label <- gsub("_"," ", tree$tip.label) #get rid of the underscores
# tree$node.label <- NULL #you can delete internal node labels
```

Plot tree

```{r plot final binary tree, fig.width=10, fig.height=20, echo=TRUE, message=FALSE}
plot(tree_binary, cex=.6, label.offset =.1, no.margin = TRUE)

#or plot to pdf
pdf("plot_tree3_SN_Q10.pdf", width=8, heigh=30)
plot(tree_binary, cex=0.6, label.offset =.1, no.margin = TRUE)
dev.off()
```

*FINAL NOTE:*
"Chinemys reevesii" has to be replaced with "Mauremys reevesii" in the original data, as it is a synonym (only "Mauremys reevesii" appears on the tree). Also, "Lithasia obovata" was changed to "Aspella anceps", "Osmerus" to "Osmerus mordax", but should be on tree, but check anyway.

### 2022-02-24 supp/Supplemental Materials and Methods.Rmd
initialising refresh of repo to deal with large file problems from GIS. Also did some re-organising to keep things more focused

---
title: "Supplemental Materials, Methods and Results"
author: Daniel W.A. Noble, Fonti Kar, Frank Seebacher & Shinichi Nakagawa
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)
```

```{r packages_data, results='hide'}
##################################
# Clean workspace
##################################
    rm(list=ls())

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, microclima, NicheMapR, tmap, rgdal, MCMCglmm, brms, latex2exp)

#devtools::install_github(repo = "ErikKusch/KrigR")
## Function to produce colour palette
# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can greate a custom colour palelte function using colorRampPallette
colfunc <- colorRampPalette(rev(brewer.pal(10,"RdBu")))
#test colfunc(10) will generate the exact Hex codes for 10 different colours can 10 to 100 and you get 100 colour hex codes. Very useful webpage: https://pjbartlein.github.io/REarthSysSci/rasterVis01.html

    # loading functions
    source("../R/functions.R")

     #gs <- gs_title("q10_newdata")
    #data <- as_tibble(gs_read(ss = gs))

##################################
# Load Data & Manipulate
##################################

    #data <- read_sheet(ss = "q10_newdata")
    data <- read.csv("../../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
    data$lat <- as.numeric(data$lat)
    new_papers <- data[-grep("_o", data$record_num),]
    old_papers <- data[grep("_o", data$record_num),]

    # Add full species to data
      data <- data %>%
        mutate(species_full = paste0(genus, " ",species))

    # habitat
      spp_habitat <- data %>%
                      group_by(habitat) %>%
                      summarise(spp_n = length(unique(species_full)))

      # Note that some species need to be replaced
      data <- data %>%
              mutate(species_full = ifelse(species_full == "Chinemys reevesii", "Mauremys reevesii", species_full)) %>%
              mutate(species_full = ifelse(species_full == "Enithares sp", "Enithares ciliata", species_full))  %>%
              mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>% # Fix a few errors in habitat classificaton
              mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))

    # Convert se to SD so it can be used for effect sizes. Drop out the SE columns as these are no longer needed
      data <- data %>%
              mutate(r1.1_sd = se_to_sd(r1.1_se, r1.1_N),
                     r1.2_sd = se_to_sd(r1.2_se, r1.2_N),
                     r2.1_sd = se_to_sd(r2.1_se, r2.1_N),
                     r2.2_sd = se_to_sd(r2.2_se, r2.2_N)) %>%
              dplyr::select(-c(r1.1_se, r1.2_se, r2.1_se, r2.2_se,
                               r1.1_CV, r1.2_CV, r2.1_CV, r2.2_CV, 
                               r1.1_logCV, r1.2_logCV, r2.1_logCV, r2.2_logCV))
##################################
## Calculate effect sizes
##################################
    # Calculate Q10 effect sizes and sampling variances; filter out non-finate values and clean up dataframe a bit

      data <- data %>%
             mutate(lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnRR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    obs = 1:n()) %>%
            dplyr::select(-c(data_source, source_page,phylum, class, order, family, genus, species, geo_location, details, notes)) %>%
                  filter_if(~is.numeric(.), all_vars(!is.infinite(.)))

    # #******** Problem with effect size calculation. V_lnVR and V_lnCVR are negative for a couple studies, should not be! Hence warning messages NaN in plotting of precision; explored this probalem more. It's actually incorrect data in the old dataset from Frank. Fonti explored the extraction for p088_o and error bars not found, sample sizes not correct. For second study, the N value was incorrect, should have been N = 5 not 0.11. Will exclude p_088_o from the data. Fonti did a check and tried to re-extract but in the end missing error so excluded

      data <- data %>%
              filter(!record_num == "p088_o")

      #write.csv(data, file = "./output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################

      # We want to be able to reorganise the data longitudianlly based on the two acute and acclimation data. Extract the data in chunks

      data_t1 <- data                                                  %>%
                 dplyr::select(c(1:26, grep("acute_t1", colnames(.)))) %>%
                 filter_if(~is.numeric(.), all_vars(!is.na(.)))        %>% # Filter all the na effect sizes 
                 rename(lnRR_Q10    = lnRR_Q10_acute_t1,       # Rename columns
                        V_lnRR_Q10  = V_lnRR_Q10_acute_t1,
                        lnVR_Q10    = lnVR_Q10_acute_t1,
                        V_lnVR_Q10  = V_lnVR_Q10_acute_t1, 
                        lnCVR_Q10   = lnCVR_Q10_acute_t1,
                        V_lnCVR_Q10 = V_lnCVR_Q10_acute_t1,
                              paper = record_num)            %>%
                 mutate(type = "acute")

      dim(data_t1)

      # Do the same for hot acute
      data_t2 <- data                                                  %>%
                 dplyr::select(c(1:26, grep("acute_t2", colnames(.)))) %>%
                 filter_if(~is.numeric(.), all_vars(!is.na(.)))        %>%  # Filter all the na effect sizes 
                 rename(lnRR_Q10    = lnRR_Q10_acute_t2,
                        V_lnRR_Q10  = V_lnRR_Q10_acute_t2,
                        lnVR_Q10    = lnVR_Q10_acute_t2,
                        V_lnVR_Q10  = V_lnVR_Q10_acute_t2, 
                        lnCVR_Q10   = lnCVR_Q10_acute_t2,
                        V_lnCVR_Q10 = V_lnCVR_Q10_acute_t2,
                              paper = record_num)            %>%
                 mutate(type = "acute")
      dim(data_t2)

      # Now do for the acclimation
      data_acclim <- data                                            %>%
                 dplyr::select(c(1:26, grep("acclim", colnames(.)))) %>%
                 filter_if(~is.numeric(.), all_vars(!is.na(.)))      %>% # Filter all the na effect sizes 
                 rename(lnRR_Q10    = lnRR_Q10_acclim,
                        V_lnRR_Q10  = V_lnRR_Q10_acclim,
                        lnVR_Q10    = lnVR_Q10_acclim,
                        V_lnVR_Q10  = V_lnVR_Q10_acclim, 
                        lnCVR_Q10   = lnCVR_Q10_acclim,
                        V_lnCVR_Q10 = V_lnCVR_Q10_acclim,
                              paper = record_num)            %>%
                 mutate(type = "acclim")
      dim(data_acclim)

      # All these data frames are exactly the same excet that the effect sizes. We've removed NA, so lets bind together

      data_long <- bind_rows(data_t1, data_t2, data_acclim)

      # Checks:
      dim(data_long)
      with(data_long, table(type)) # Acute should be 2x larger
      with(data_long, table(type, trait_category))
      #write.csv(data_long, file = "./output/data/data_final_long.csv", row.names = FALSE)
```

## Materials and Methods
### *Literature collection*
We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures. We used data from a previous meta-analysis [@Seebacher2015] and updated Seebacher *et. al.* @Seebacher2015's data by extractng data from suitable studies from our own searches that followed the same search protocol. More specically, we performed a literature search on the 28th of June 2017 using the Web of Science database. We limited our search to articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et. al.* @Seebacher2015 searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*. We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.

Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016]. We also cross checked papers we found in our searches with a recent paper by Havird *et. al.* @Havird2020, which also updates Seebacher *et. al.* @Seebacher2015's dataset. We included any papers that were missed between our searches and those of Havird *et. al.* @Havird2020 from the dates 2013-2017. Havird *et. al.* @Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metbolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015]. Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et. al.* @Seebacher2015's dataset. More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et. al.* @Seebacher2015 dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles). Note that Seebacher *et. al.* @Seebacher2015 included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below). While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset. As such, our database represents the most up-to-date dataset used by Seebacher *et. al.* @Seebacher2015 to answer questions on acclimation across ectotherms.

We split the screening of titles and abstracts for the 1,321 papers found in our search among all authors evenly. To ensure consistency among authors in title and abstracts that should be included, prior to  screening all authors went through a randomly sleected set of papers together - agreeing on those that were relevant and those that were not based on our inclusion criteria (see below). Where any authors were uncertain about whether to include a paper in the sub-sample they screened, we conservatively included the paper for full text screening and dicussed uncertain papers among authors to come to a decison on whether to include the paper. After title and abstract screening, we were left with a total of 149 papers for full text screening. Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.

### *Data Compilation*

We extracted means, standard deviations and sample sizes for physiological rates at the two test tempetatures. If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatues experienced by the speceis in question. We extracted these data from text, tables or figures of a given paper. Data were extracted from figures using the R package *metaDigitise* [@pick2019]. We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied. For studies that did not provide latitude and longitude for the population, we searched for similar studies by the lab group to identify where the population was likely to have been sourced or derived from when needed. If the population was derived from the wild, we recorded the nearest latitude and longitude of the population to the field collection site. If the animals had been sourced from a commercial supplier, we took the latitude and longitude of the supplier that the paper identified the animals to have originated from. When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.

### *Calculating New $Q_{10}$ Based Effect Sizes and Sampling Variances*

To understand changes in physiological rates we often look to comparing $Q_{10}$ values, which describe the multiplicative change in physiological rates across a 10&deg;C temperature change. Higher $Q_{10}$ values indicate stronger changes in physiological rates, and it is expected that acclimation should reduce $Q_{10}$ values [@Seebacher2015]. Currently, however, we do not have effect sizes and associated sampling variances derived for $Q_{10}$ making it challenging to weight effect size estimates by sampling variance as is typical in meta-analysis. While the Delta method can be used to approximate the sampling variance (e.g., see Havird *et. al.* @Havird2020) this assumes  $Q_{10}$ is normally distributed and linear with respect to temperature. Unfortunately, this is not the case for $Q_{10}$, as such, the Delta method is likely a poor approximation to sampling variance. There are easier ways to derive effect sizes and associated samping variance for $Q_{10}$ given that $Q_{10}$ is simply a reformulation of a very commonly used effect size in the meta-analysis literature, the log response ratio (*lnRR*) [@hedges1999meta; @laj2011]. Recognition of the similarity between *lnRR* and $Q_{10}$ means we can derive $Q_{10}$ based effect sizes using the well known mathematical properties of *lnRR*, while also providing easy ways to extend this to effect sizes that compare variances in physiological rates [@nakagawa2015meta] and improve upon our ability to account for sources of non-independence that are typical in meta-analysis [@laj2011; @Noble2017]. As such, here we derive a series of $Q_{10}$ based effect sizes along with their associated sampling variances that allow one to compare both changes in mean and variance of physiological rates.

#### *Comparing changes in mean physiological rates*

Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*. The *lnRR* described by Hedges *et al.* @hedges1999meta and extended by Lajeunesse @laj2011 and can be calculated as follows:

$$
\begin{equation} 
  \begin{aligned}
  lnRR = ln\left ( \frac{X_{1}}{X_{2}}\right )
  \end{aligned}
  (\#eq:lnRR)
\end{equation} 
$$

$$
\begin{equation} 
  s_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
  (\#eq:slnRR)
\end{equation} 
$$
In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group). The mean of $X_{i}$ for group *i* can be any measurement type (e.g. a physiological rate, mass etc) so long as the measurement variable is ratio scale. Log transformation of this ratio makes the effect size normally distributed. Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.

The equations for *lnRR* and its sampling variance allow us to easily extend this to $Q_{10}$ based effect sizes. Recall that $Q_{10}$ is described as follows:

$$
\begin{equation} 
  Q_{10} = \left( \frac{R_{2}}{R_{1}} \right)^{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
  (\#eq:q10)
\end{equation} 
$$
Here, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured. Log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:

$$
\begin{equation} 
  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
(\#eq:lnq10)
\end{equation} 
$$
Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures. This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured. Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$. Recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:

$$
\begin{equation} 
  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
  (\#eq:Vlnq10)
\end{equation} 
$$

#### *Comparing changes in physiological rate variability*

Nakagawa *et al* @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*). Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variablity between two groups. We refer readers to Nakagawa *et al* @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling varaince) as follows:

$$
\begin{equation} 
lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
(\#eq:lnq10VR)
\end{equation} 
$$
$$
\begin{equation} 
s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
(\#eq:slnq10VR)
\end{equation} 
$$

Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)). While this is a useful metric, as discussed by Nakagawa *et al* @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance. As such, we can calculate the coefficient of variation, which standardises changes in variance for changes in means as follows:

$$
\begin{equation} 
lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
(\#eq:lnq10CVR)
\end{equation} 
$$
$$
\begin{equation} 
s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
(\#eq:slnq10CVR)
\end{equation} 
$$

where $CV$ is the coefficient of variation defined as $SD / R$.

#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
Using the mean, standard deviation and sample size for all acute and aclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates. For all effect sizes the higher acute or acclimation temperture was in the numerator and the lower of the two temperatures in the denominator. As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardised to 10&deg;C.

### *Moderator Variables*

We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates. These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exsposure occurs (longer exsposure = better acclimation response) and whether exsposure took place in the wild ("acclimitized") or lab ("acclimated") [@Seebacher2015]. We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "jeuvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et. al.* @Seebacher2015 show that these factors can impact $Q_{10}$ estimates. Physiological rates measures varied widely across the studies but could generally be groups into discrete trait categories @Seebacher2015. As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of

### *Meta-Analysis*
### *Sensitivity Analyses*
### *Publication Bias*

## Results

```{r datadescrp}
#####################################
# Data Descriptions and Exploration
#####################################

#spp <- data %>% dplyr::distinct(species_full, class, order, family) %>% arrange(species_full)

#####################################
# Climate data and Mapping
#####################################

## We can now bring in raster data from WorldClim, which contains a load of different environmental data that can be used, plus we can get very pretty world maps. The world climate datasets are called "bio" followed by a number. Details on what these datasets are exactly and how they can be obtaine can be found here: https://www.gis-blog.com/r-raster-data-acquisition/ & https://www.worldclim.org/data/index.html

####################################
# Terrestrial data from WorldClim
####################################

# Now, lets have a look at our data in relation to the climate layers @ 2.5 km resolution

worldclim <- getData("worldclim", var="tmax",res=2.5, path = "./gis_data/")

        coast <- read_sf("./gis_data/ne_110m_coastline/ne_110m_coastline.shp")
coast_outline <- as(st_geometry(coast), Class="Spatial")

# Grab the lat and long data from the studies in our data
coords <- data                     %>%
          dplyr::select(long, lat) %>%
          filter(!is.na(lat), !is.na(long))

# Lets have a look at a couple of the layers, seasonality, bio4 or tmax in each months

   seasonalityDec <- worldclim[["tmax12"]] #"bio4"
 seasonalityApril <- worldclim[["tmax4"]] #"bio4"
seasonalityAugust <- worldclim[["tmax8"]] #"bio4"

# Using our coordinates, extract the relevant environmental data from the worldclim laters. Remeber that the projections across layers need to match, so we will project worldclim crs
points <- SpatialPoints(coords, proj4string = worldclim@crs) 
values <- extract(worldclim, points)

# Create the dataframe 
env_data <- cbind.data.frame(coordinates(points), values)

####################################
## Sea surface data NOAA
####################################

# There are two files for sea and ice surface temperatures downloaded from NOAA (https://psl.noaa.gov/data/gridded/data.cobe2.html). These should contain monthly mean temperatures. What we want to do here is load these files, project them onto the worldclim temperature data, then, extract the relevant temperature data at the latitudes for the combined terrestrial and aquatic points. The grain of the aquatic data is much more coarse then the terrestrial data. There are a few reasons for this. First, it's hard to get really detailed SST data at fien scales. Second, it's probably not needed given that SST doesn't vary much over large areas. Useful ways to deal with files: https://cran.r-project.org/web/packages/futureheatwaves/vignettes/starting_from_netcdf.html & https://pjbartlein.github.io/REarthSysSci/netCDF.html#map-the-data

# Open the NetCDF data set, and print some basic information.
SSTdir  = "gis_data/"
ncname  = "HadISST_sst"
ncfname = paste0(SSTdir,ncname, ".nc", sep = "")
dname   = "sst"

# Open a NetCDF file
HAD.sst = nc_open(ncfname)
#print(HAD.sst)

# Get the longtiudes and latitudes as before, using now the ncvar_get() function in ncdf4.
lon     = ncvar_get(HAD.sst, "longitude")
lat     = ncvar_get(HAD.sst, "latitude", verbose = F)

# Get the time variable and its attributes using the ncvar_get() and ncatt_get() functions, and also get the number of times using the dim() function.
t       = ncvar_get(HAD.sst, "time")
tunits  = ncatt_get(HAD.sst, "time", "units")

# Get the variable and its attributes, and verify the size of the array.
sst.array = ncvar_get(HAD.sst, dname)
dlname    = ncatt_get(HAD.sst, dname, "long_name")
dunits    = ncatt_get(HAD.sst, dname, "units")
fillvalue = ncatt_get(HAD.sst, dname, "_FillValue")
dim(sst.array)

# Get the global attributes.
title       = ncatt_get(HAD.sst, 0, "Title")
description = ncatt_get(HAD.sst, 0, "description")
institution = ncatt_get(HAD.sst, 0, "institution")
datasource  = ncatt_get(HAD.sst, 0, "source")
references  = ncatt_get(HAD.sst, 0, "reference")
history     = ncatt_get(HAD.sst, 0, "history")
Conventions = ncatt_get(HAD.sst, 0, "Conventions")

# Close the NetCDF file using the nc_close() function.

nc_close(HAD.sst)

# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #

# The time variable, in "time-since" units can be converted into "real" (or more easily readable) 
# time values by splitting the time tunits$value string into its component parts, and then using 
# the chron() function to determine the absolute value of each time value from the time origin.

# Split the time units string into fields
tustr     = strsplit(tunits$value, " ")
tdstr     = strsplit(unlist(tustr)[3], "-")
tmonth    = as.integer(unlist(tdstr)[2])
tday      = as.integer(unlist(tdstr)[3])
tyear     = as.integer(unlist(tdstr)[1])

times     = chron(t, origin = c(tmonth, tday, tyear))
times     = as.POSIXct(times, "%d/%m/%y %H:%M:%S")

# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #

# In NetCDF file, values of a variable that are either missing or simply not available (i.e. ocean grid points in 
# a terrestrial data set) are flagged using specific "fill values" (_FillValue) or missing values (missing_value), 
# the values of which are set as attributes of a variable. In R, such unavailable data are indicated using the "NA"
# value. The following code fragment illustrates how to replace the NetCDF variable's fill values with R NA's .

sst.array[sst.array == fillvalue$value] = NA

# Also values of SST need to be divided by 100
sst.array = sst.array / 100

sst.slice <- sst.array[,,5]

grid   = expand.grid(lon = lon, lat = lat)
#cutpts = c(-5, -2, 0, 5, 10, 15, 20, 25, 30, 35)
levelplot(sst.slice ~ lon * lat, data = grid,  cuts = 11, pretty = TRUE, 
          col.regions = colfunc(50), ylab = "Latitude", xlab = "Longitude")  +# Have a quick look
          layer(sp.points(points, pch = 16, col = "black")) + 
          layer(sp.lines(coast_outline, col="black", lwd=0.5))

# Lets convert this to a dataframe so we can summarise data a bit easier. Remember, we have range of lat, long over a large period of time. So, we can expand upon the three variables.
#longlat <- as.matrix(expand.grid(lon, lat, time))

# Now we can simply convert to a vector and add to dataframe the raster / grid data
#sst_tmp <- as.vector(sst)

# Make final dataframe. Note that time is in Julian days or days since "1891-1-1 00:00:00"
#dat_SST <- data.frame(cbind(longlat, sst_tmp))
#colnames(dat_SST) <- c("lon", "lat", "time", "temp")
#dat_SST$date <- chron(dat_SST$time, origin=c(1, 1, 1891), format = c("d/m/y"))
#dat_SST$year <- year(dat_SST$date)
#dat_SST$month <- month(dat_SST$date)

# Apparently the ERA5 dataset is the top of the line climate data from Europe. It is also both land and SS based temperature data that can be calculated monthly from 1979-2020. It can be downlaoded by requesting access to various data metric here: https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-single-levels-monthly-means?tab=overview. 
####################################
## ERA5 Global Temperature data
####################################
        #coast <- read_sf("./gis_data/ne_110m_coastline/ne_110m_coastline.shp")
#coast_outline <- as(st_geometry(coast), Class="Spatial")

coast <- readOGR("./gis_data/ne_110m_coastline/ne_110m_coastline.shp")
coast_outline <- recenter(coast)

# Load the data
 ERA5_SST <- brick("./gis_data/SST_ERA.nc")
ERA5_land <- brick("./gis_data/2mTemp_ERA.nc")

#turn your file into a spatial points data frame
coords <- data                     %>%
          dplyr::select(long, lat) %>%
          filter(!is.na(lat), !is.na(long))
coords$long[coords$long<0] <- coords$long[coords$long<0] + 360 # Convert longitudes to eastings

    r <- SpatialPoints(coords, proj4string = coast_outline@proj4string)

# Extract to data frame
ext_SST <-  raster::extract(ERA5_SST, r, cellnumber = TRUE, df = TRUE)

# Try plotting with tmap package...seems great! https://mgimond.github.io/Spatial/mapping-data-in-r.html; https://confluence.ecmwf.int//display/CKB/ERA5%253A+What+is+the+spatial+reference
p1 <- tm_shape(subset(ERA5_SST, 1)-273.15) + 
  tm_raster(style = "quantile", n = 10, palette=colfunc(10), 
            title="1979 SST",
            legend.hist = TRUE, 
            showNA = TRUE, colorNA="grey") +
  tm_legend(outside = TRUE, hist.width = 2) +
  tm_shape(coast_outline) +
  tm_lines() +
  tm_shape(r) + tm_dots(size = 0.1, col = "black")

p1
```
The global distribution of studies / species in our data base was wide, with most research in North America, Europe and Asia (Figure \@ref(fig:FigS1)).

```{r FigS1,fig.height=10, fig.cap="Global distribution of species / studies for terrestrial, freshwater and marine ectotherm acclimation research. Latitudes and longitudes of studies are projected on a global map of maximum surface temperature in A) December, B) April and C) August for world and North America" }

 p1 <- levelplot(seasonalityDec/10, margin =FALSE, cuts=20, pretty=TRUE, main = "December", col.regions=colfunc(50)) +
        layer(sp.points(points, pch = 16, col = "black")) +
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better +
 p2 <- levelplot(seasonalityApril/10, margin =FALSE, main = "April", cuts=20, pretty=TRUE, col.regions=colfunc(50)) + 
        layer(sp.points(points, pch = 16, col = "black")) + 
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 p3 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=20, pretty=TRUE, col.regions=colfunc(50)) +
        layer(sp.points(points, pch = 16, col = "black")) + 
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 p4 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=50, pretty=TRUE, 
                 col.regions=colfunc(100), ylim = c(0,100), xlim = c(-130, -40)) + 
        layer(sp.points(points, pch = 16, col = "black")) + 
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better

 ggarrange(p1, p2, ggarrange(p3, p4, ncol=2, labels="C)"), labels = c("A)", "B)"), nrow = 3)

```

Overall, we have a total of `r sum(spp_habitat$spp_n)` species in the data. Phylogenetic relationships among taxa and the distribution of effect sizes across traits and taxa across habitats (Figure \@ref(fig:phylogeny))

```{r FigS2, fig.width=10, fig.height=10, results='hide', fig.cap="Phylogeny of taxa in the dataset"}

##################################
# Phylogenetic tree
##################################

    ## Tree data; also fix up some errors
    tree_data <-  data %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                  group_by(species_full)%>%
                  mutate(n = length(habitat)) %>%
                  dplyr::select(species_full,  habitat, n) %>% 
                  distinct(species_full, habitat, n)

      ## Load the phylogenetic tree
                tree <- read.tree("../tree/tree_binary_SN_Q10.tre")   
      tree$tip.label <- gsub("_", " ", tree$tip.label)
      tree$tip.label <- gsub("Enithares sp", "Enithares ciliata", tree$tip.label)

      ## Create nodes and add to data so detailed can be mapped
          tree_data$node <- NA
                 tipnode <- seq_along(tree$tip.label)
          names(tipnode) <- tree$tip.label
          tree_data$node <- tipnode[tree_data$species_full] ## convert the tip label to tip node number
                       i <- is.na(tree_data$node)
       tree_data$node[i] <- tree_data$species_full[i] ## fill in internal node number
          tree_data$node <- as.integer(tree_data$node)

      # Do a tree check with original data
          tree_checks(data, tree, dataCol = "species_full", type = "checks") # Great. Currently species in data and tree match

##################################
# Plotting tree data
##################################

      # Map data to tree. Just one variable for now
      d <- ggtree(tree, layout="circular") %<+% tree_data

      # Plot the tree
      scales1 <- c("#053061", "#D1E5F0", "#67001F")
      scales2 <- c("#053061", "#E7E0DB", "#67001F")
      p1 <- d + 
            #geom_tiplab(size=2, offset = 0.5) + 
            geom_tippoint(aes(color=habitat), size = 2) +
            labs(color = "Habitat") + 
            scale_colour_manual(values = scales1)

      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
      matrix_data <- as.data.frame(data %>%
                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
                  mutate(trait_category = ifelse(trait_category %in% 
                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
                  group_by(species_full, trait_category)   %>% 
                  summarise(n = n())                       %>% 
                  spread(trait_category, n, fill = 0))

      row.names(matrix_data) <- matrix_data$species_full
      matrix_data <- matrix_data[,c(2:8)]

      colnames(matrix_data)[c(1,3,6)] <- c("Antioxidants", "Metabolic Enzymes", "Other")

      # Plot a heatmap of N for each trait around the phylogeny.
      gheatmap(p1, data.matrix(matrix_data), offset = 1,  
               colnames_position="top", legend_title = "N", 
               colnames_angle=90, colnames_offset_y = 1, 
               hjust=0, font.size=2.5) + 
        scale_fill_viridis(alpha = 0.6)

##################################
# Tree checking and pruning
##################################
  # Have a look at species in data and tree. Note that the data2 object excluded all Inf values, which means that species may be lost in the process. So, tree would need to be pruned down
  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")

species_drop <- tree_checks(data, tree, dataCol = "species_full", type = "checks")$Species_InTree_But_NotData # Gra list of species in tree misisng from data for pruning

# Prune tree
tree2 <- drop.tip(tree, species_drop)

# Check that taxa dropped
tree_checks(data, tree2, dataCol = "species_full", type = "checks")

##################################
# Branch lengths and cor matrix
##################################
      # Now that we have the tree file, we need to use it to create a phylogenetic correlation matrix using Grafen's method. This assumes Brownian motion and is the best we can do without a molecular phylogeny. The topology of the tree should be fairly good. We will explore a few different options with p to determine the best power function

        tree_p1 <- compute.brlen(tree, method = "Grafen", power = 1)
      tree_p0.5 <- compute.brlen(tree, method = "Grafen", power = 0.5)

     # Create null nodes 
        tree_p1$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
      tree_p0.5$node.label <- NULL # We don't use nodes and will cause a warning so create null node names

     # Now lets create the phylogenetic matrices for analysis
      invA_1 <-       MCMCglmm::inverseA(tree_p1, nodes = "TIPS")$Ainv  # This in an inverse phylogenetic correlaton matrix, which is what MCMCglmm takes
         A_1 <- solve(MCMCglmm::inverseA(tree_p1, nodes = "TIPS")$Ainv) # This in a phylogenetic correlaton matrix, which is what brms takes
    rownames(A_1) <- rownames(invA_1)

    invA_0.5 <-       MCMCglmm::inverseA(tree_p0.5, nodes = "TIPS")$Ainv  # This in an inverse phylogenetic correlaton matrix, which is what MCMCglmm takes
       A_0.5 <- solve(MCMCglmm::inverseA(tree_p0.5, nodes = "TIPS")$Ainv) # This in a phylogenetic correlaton matrix, which is what brms takes
  rownames(A_0.5) <- colnames(A_0.5) <- rownames(invA_0.5)

```

```{r meta-analysis}

# There are a few ways to do this. We could re-organise the dataframe for all effect sizes and run "acute" and "acclim" effects. Alternatively, we can run a multivariate / multi-response model. Problem with this model is that there is quite a bit of missing data for each column of the data. I'm going to have a crack using brms first. Some important thing sto note. First, we don't really have any predcitions about acute hot or cold being different. As such, the acute responses could simply be condensed down. These are samples of independent indiviudals, not the same ones, so we could treat them as independent effect sizes. Acute and acclimation effects can come from the same paper, assuming those papers have done a fully factorial design. As such, we should account for the non-indpendence at the study/ paper level

data_long$obs <- 1:dim(data_long)[1]

rerun1 = FALSE
if(rerun1){
  lnRR_Q10_mod1 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.95), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
  saveRDS(lnRR_Q10_mod1, "../models/lnRR_Q10_mod1")
} else{
lnRR_Q10_mod1 <- readRDS("../models/lnRR_Q10_mod1")  }

# Checks
 summary(lnRR_Q10_mod1)     # Rhat all 1 = chain convergence
    plot(lnRR_Q10_mod1)     # Good mixing
   pairs(lnRR_Q10_mod1)
bayes_R2(lnRR_Q10_mod1)     # Variance explained by model

fixed_m1 <- posterior_samples(lnRR_Q10_mod1, "^b")
hyp_m1 <- hypothesis(lnRR_Q10_mod1, "typeacute = 0", class = "b", alpha = 0.05, scope = "standard")

# Build table results
# Acute mean esatimte and 95% CI
m1_results <- data.frame("Estimate" = c(mean(rowSums(fixed_m1)), mean(fixed_m1$b_Intercept)), 
                          "SE" = c(sd(rowSums(fixed_m1)), sd(fixed_m1$b_Intercept)),
                      "CI " = rbind(quantile(rowSums(fixed_m1), c(0.025, 0.975)), 
                                   quantile(fixed_m1$b_Intercept, c(0.025,0.975))), 
                      check.names = FALSE)

rerun2 = FALSE
if(rerun2){
  lnRR_Q10_mod2 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type*habitat + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.99), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
  saveRDS(lnRR_Q10_mod2, "../models/lnRR_Q10_mod2")
}else{
  lnRR_Q10_mod2 <- readRDS("../models/lnRR_Q10_mod2")
}
# Checks
 summary(lnRR_Q10_mod2) # Rhat all 1 = chain convergence
    plot(lnRR_Q10_mod2) # Good mixing
   pairs(lnRR_Q10_mod2) # Looks good
bayes_R2(lnRR_Q10_mod2) # Variance explained by model

fixed_m2 <- posterior_samples(lnRR_Q10_mod2, "^b")

```

### *Publication Bias*

```{r, FigS3, fig.width=10, fig.height=5, fig.cap="Funnel plots of precision and effect size for three effect size measures"}
      # Some plots
      par(mfrow=c(1,3), pch = 16, lty = 2, cex.lab = 2, las = 1, lwd = 1.5,mar = c(5,8,1,1))
      plot(1/sqrt(V_lnRR_Q10)  ~ lnRR_Q10, data = data_long, ylab = TeX('Precision  $\\left( \\frac{1}{se} \\right)$'), xlab = TeX('$lnRR_{Q_{10}}$'))
      abline(v = 0, col = "red")
      par(mar =c(5,3,1,1))
      plot(1/sqrt(V_lnVR_Q10)  ~ lnVR_Q10, data = data_long, ylab = "", xlab = TeX('$lnVR_{Q_{10}}$'))
      abline(v = 0, col = "red")
      plot(1/sqrt(V_lnCVR_Q10) ~ lnCVR_Q10, data = data_long, ylab = "", xlab = TeX('$lnCVR_{Q_{10}}$'))
      abline(v = 0, col = "red")

```
## References

### 2022-02-24 R/Surface_climate_timelines_RNCEP.R

@@ -1,0 +1,132 @@
+###################################################################################
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#                   NCEP REANLYSIS2 CLIMATE DATA DOWNLOAD
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+###################################################################################
+
+# NCEP Reanlysis
+# https://psl.noaa.gov/data/gridded/data.ncep.reanalysis.html
+
+
+rm(list=ls())
+
+library(raster)
+library(RNCEP)
+
+gbif = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+
+# Work through species
+for(spp in unique(gbif$Species)){
+  
+  if(file.exists(paste0("Output/RNCEP/",spp,"_clim_stats.RData"))){
+    load(paste0("Data/Land/",spp,"_clim_stats.RData"))
+    sites               = gbif_microclimate[[2]]
+    annual.thermal.data = gbif_microclimate[[3]]
+    s2                  = gbif_microclimate[[4]]
+    rm(gbif_microclimate)
+    
+  } else {
+    # Create matrix to hold thermal data for this species
+    annual.thermal.data = matrix(NA, ncol=30)
+    colnames(annual.thermal.data) = c("Fid","Latitude","Longitude","Year",
+                                      "Annual.mean",sprintf("Mean%02d",c(1:12)),
+                                      "Annual.sd",sprintf("SD%02d",c(1:12)) )
+    
+    # Choose  site at random, and then each next site as the furthest from those selected
+    sites.xy = gbif[which(gbif$Species==spp),c("longitude","latitude")]
+    plot(sites.xy, col="white", las=1)
+    sites    = which(gbif$Species==spp)
+    s1       = sample(sites, 1)
+    sites    = sites[!sites %in% s1]
+    for(i in 1:length(sites)){
+      if( length(s1)>250 ){    x1 = sample(s1,250) } else {   x1=s1 }
+      if( length(sites)>250 ){ x2 = sample(sites,250)} else { x2=sites }
+      x3    = pointDistance(sites.xy[s1,], sites.xy[x2,], lonlat = TRUE, allpairs=TRUE)/1000
+      if(length(x1)>1 & length(x2)>1){ if(dim(x3)[1]>1){ x3 = apply(x3,2,min) } }
[…]

### 2022-02-24 R/Surface_climate_timelines_hardcopy_ERA5.R

@@ -1,0 +1,156 @@
+###################################################################################
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#                       ERA5 Reanalysis 1 CLIMATE DATA
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+###################################################################################
+
+# This version doesn't actively download point estimates of temperature. 
+# Instead a NetCDF for ERA5 was downloaded for 1979-present.
+
+# See Word doc: Data/Downloading ERA5 historic climate data.docx
+
+# Note that the data is stored in Kelvin and transformed.
+# 2m surface temperature
+#     scale_factor: 0.00176319797961702
+#     add_offset: 257.703670097788
+# Sea Surface Temperature
+#     scale_factor: 0.00061697729459776
+#     add_offset: 289.46490147229
+
+# Time is recorded in hours since 1900-01-01 00:00:00.0
+
+rm(list=ls())
+library(ncdf4)
+#library(sf)
+#library(raster)
+
+if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
+  gbif     = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+  gbif$Fid = 1:nrow(gbif)
+  #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+  
+  gbif$ERA5col = gbif$longitude
+  gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
+  gbif$ERA5col = cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440))
+  
+  gbif$ERA5col = gbif$longitude
+  gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
+  gbif$ERA5col = as.numeric(cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440)))
+  
+  ncfname   = "E:/ERA5/ERA5_LST_and_SST_1979-present.nc"
+  ERA5.air  = nc_open(ncfname)
+  print(ERA5.air)
+  dname     = "t2m"
[…]

### 2022-02-24 R/Surface_climate_timelines_hardcopy_NCEP.R

@@ -1,0 +1,150 @@
+###################################################################################
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#                       NCEP Reanalysis 1 CLIMATE DATA
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+###################################################################################
+
+# This version doesn't actively download point estimates of temperature. 
+# Instead NCDFs for each year 1960-2000 were pre-downloaded and I extract what's available.
+
+rm(list=ls())
+library(ncdf4)
+#library(sf)
+#library(raster)
+
+if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")){
+  gbif     = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+  gbif$Fid = 1:nrow(gbif)
+  #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+  
+  gbif$NCEPcol = gbif$longitude
+  gbif$NCEPcol[gbif$NCEPcol<0] = (180-abs(gbif$NCEPcol[gbif$NCEPcol<0]))+180
+  gbif$NCEPcol = cut(gbif$longitude, seq(0,360,2.5), labels=c(1:144))
+  
+  gbif$NCEPcol = gbif$longitude
+  gbif$NCEPcol[gbif$NCEPcol<0] = (180-abs(gbif$NCEPcol[gbif$NCEPcol<0]))+180
+  gbif$NCEPcol = as.numeric(cut(gbif$longitude, seq(0,360,2.5), labels=c(1:144)))
+  
+  ncfname   = "E:/NCEP_Reanalysis 1/air.sig995.1960.nc"
+  NCEP.air  = nc_open(ncfname)
+  print(NCEP.air)
+  dname     = "air"
+  lon       = ncvar_get(NCEP.air, "lon")
+  head(lon)                                     # NCEP data is at 2.5' resolution
+  nlon      = length(lon) # number of columns
+  lat       = ncvar_get(NCEP.air, "lat", verbose = F)
+  head(lat)
+  nlat      = length(lat) # number of rows
+  t         = ncvar_get(NCEP.air, "time")
+  head(t)
+  nt        = dim(t) # 4 times for every day of the year
+  
[…]

### 2022-02-24 R/Surface_microclimate_timelines.R

@@ -1,0 +1,345 @@
+###################################################################################
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#               MICROCLIMATE OF TERRESTRIAL AND FRESHWATER TAXA
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+###################################################################################
+
+
+rm(list=ls())
+library(raster)
+
+spp.list = read.csv("q10_meta-master/data/species_list_Q10.csv")
+spp      = spp.list$species_full
+spp[71]  = "Enithares"                 # Switch 'Enithares sp' to whole genus
+spp[73]  = "Euchemotrema leaii"        # Synonym: Euchemotrema leai
+spp[133] = "Merlangius merlangus"      # Synonym: Merlanguis merlangus
+spp[175] = "Pinctada mazatlanica"      # Synonym: Pinctada mazatlantica
+spp[202] = "Hoplobatrachus tigerinus"  # Synonym: Rana tigrina
+spp[203] = "Lithobates virgatipes"     # Synonym: Rana vergatipes
+spp[239] = "Zoarces viviparus"         # Synonym: Zoarces viviparous
+
+widedat  = read.csv("q10_meta-master/data/CombinedData_wide.csv")
+widedat$spp_names = paste(widedat$genus,widedat$species)
+habitat  = widedat$habitat[match(spp.list$species_full, gsub("_"," ",widedat$spp_names))]
+
+# Change habitat of Shortnose Sturgeon (Acipenser brevirostrum) to freshwater
+habitat[4] = "f"
+widedat$habitat[match("Acipenser brevirostrum", widedat$spp_names)] = "f"
+
+
+#  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  #
+#     Coordinates of Q10 sites by habitat
+#  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  #
+
+# Try to fill some of the location rows missing data
+widedat[widedat$geo_location %in% "Coruna, Spain",         c("lat","long")] = c(43.425230, -8.414665)   # Marine sp. so placed point to north
+widedat[widedat$geo_location %in% "Newhay, Yorkshire UK",  c("lat","long")] = c(53.769377, -0.995573)
[…]

### 2022-02-24 R/exploratory/explore_climate_data.R

@@ -1,0 +1,321 @@
+###################################################################################
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#                       GLOBAL HISTORIC TEMPERATURE
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+###################################################################################
+
+rm(list=ls())
+pardefault = par()
+
+coords = read.csv("coord.csv")
+
+plot(coords[,2:3], xlim=c(-180,180), ylim=c(-70,70))
+abline(h=0, lty=2)
+
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+
+
+library(ncdf4)
+# Open the NetCDF data set, and print some basic information.
+SSTdir  = "gis_data/"
+ncname  = "HadISST_sst"
+ncfname = paste0(SSTdir,ncname, ".nc", sep = "")
+dname   = "sst" 
+
+# Open a NetCDF file
+HAD.sst = nc_open(ncfname)
+print(HAD.sst)
+
+# Get the longtiudes and latitudes as before, using now the ncvar_get() function in ncdf4.
+lon     = ncvar_get(HAD.sst, "longitude")
+nlon    = dim(lon)
+head(lon)
+
+lat     = ncvar_get(HAD.sst, "latitude", verbose = F)
+nlat    = dim(lat)
+head(lat)
+
+# Get the time variable and its attributes using the ncvar_get() and ncatt_get() functions, and also get the number of times using the dim() function.
+t       = ncvar_get(HAD.sst, "time")
+tunits  = ncatt_get(HAD.sst, "time", "units")
+nt      = dim(t)
+
+# Get the variable and its attributes, and verify the size of the array.
+sst.array = ncvar_get(HAD.sst, dname)
+dlname    = ncatt_get(HAD.sst, dname, "long_name")
+dunits    = ncatt_get(HAD.sst, dname, "units")
+fillvalue = ncatt_get(HAD.sst, dname, "_FillValue")
+dim(sst.array)
+
+# Get the global attributes.
+title       = ncatt_get(HAD.sst, 0, "Title")
+description = ncatt_get(HAD.sst, 0, "description")
+institution = ncatt_get(HAD.sst, 0, "institution")
+datasource  = ncatt_get(HAD.sst, 0, "source")
[…]

### 2022-02-24 R/exploratory/shiny_explore.R

@@ -1,0 +1,2 @@
+
+rmarkdown::run("./R/analysis.Rmd")

### 2022-02-24 R/functions.R

@@ -1,0 +1,670 @@
+#' @title lnRR_Q10
+#' @description Calculates the log Q10 response ratio.  Note that temperature 2 is placed in the numerator and temperature 1 is in the denominator
+#' @param t1  Lowest of the two treatment temperatures
+#' @param t2  Highest of the two treatment tempertures
+#' @param r1  Mean physiological rate for temperature 1
+#' @param r2  Mean physiolgical rate for temperature 2
+#' @param sd1 Standard deviation for physiological rates at temperature 1
+#' @param sd2 Standard deviation for physiological rates at temperature 2
+#' @param n1  Sample size at temperature 1
+#' @param n2  Sample size at temperature 2
+#' @param name Character string for column name
+#' @example
+#' lnRR_Q10(20, 30, 10, 5, 1, 1, 30, 30)
+#' lnRR_Q10(20, 30, 10, 5, 1, 1, 30, 30, name = "acclim")
+#' @export
+
+lnRR_Q10 <- function(t1, t2, r1, r2, sd1, sd2, n1, n2, name ="acute"){
+        
+    lnRR_Q10 <- (10 / (t2 - t1))   * log(r2 / r1)
+  V_lnRR_Q10 <- (10 / (t2 - t1))^2 * ((sd1^2 / (n1*r1^2)) + (sd2^2 / (n2*r2^2)))
+  
+              dat <- data.frame(lnRR_Q10, V_lnRR_Q10)
+    colnames(dat) <- c(paste0("lnRR_Q10", "_", name),  
+                       paste0("V_lnRR_Q10", "_", name))
+  return(dat)
+}
+
+#' @title lnVR_Q10
+#' @description Calculates the log Q10 variance ratio.  Note that temperature 2 is placed in the numerator and temperature 1 is in the denominator
+#' @param t1  Lowest of the two treatment temperatures
+#' @param t2  Highest of the two treatment tempertures
+#' @param r1  Mean physiological rate for temperature 1
+#' @param r2  Mean physiolgical rate for temperature 2
+#' @param sd1 Standard deviation for physiological rates at temperature 1
[…]

### 2022-02-24 R/performance.R

@@ -1,0 +1,70 @@
+library(rstan)
+library(brms)
+rstan::rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+
+# parameters for the metabolic rate model, natural log scale
+lnMetabolicRate  <-  function (lnB0 = -5, scalingExp = 0.75, lnMass = log(1:10)) {
+	lnB0 + scalingExp * lnMass
+}
+
+# parameters for the Boltzmann relationship, natural log scale
+lnBoltzmann  <-  function (lnBoTs = -5, Er = 0.6, invKT = 1 / 8.62e-5 * (1 / mean(274:310) - 1 / 274:310)) {
+	lnBoTs + Er * invKT
+}
+
+# complete Schoolfield-Sharpe equation
+lnSchoolfield  <-  function (lnBoTs = -5, Er = 0.6, Ei = 3, Topt = 303, tempKelvin = 274:310) {
+	boltz  <-  lnBoltzmann(lnBoTs, Er, 1 / 8.62e-5 * (1 / mean(tempKelvin) - 1 / tempKelvin))
+	boltz - log(1 + (Er / (Ei - Er)) * exp(Ei / 8.62e-5 * (1 / Topt - 1 / tempKelvin)))
+}
+
+boltzmannModelBrms  <-  function (data) {
+	# lnMass slope == scalingExp, invKT slope == Er
+
+	# FIXED EFFECTS ONLY
+	set.seed(1)
+	brms::brm(lnRateBoltz ~ lnMass + invKT, data = data, family = gaussian(), prior = c(brms::prior(normal(1, 2), 'b'), brms::prior(normal(3, 3), 'Intercept'), brms::prior(student_t(3, 0, 20), 'sigma')), sample_prior = TRUE, chains = 3, cores = 3, iter = 1e3)
+	
+	# OR ADD RANDOM EFFECTS like in lme4, where "ID" is your grouping variable
+	# brms::brm(lnRateBoltz ~ lnMass + invKT + (lnMass + invKT | ID), data = data, family = gaussian(), prior = c(brms::prior(normal(1, 2), 'b'), brms::prior(normal(3, 3), 'Intercept'), brms::prior(student_t(3, 0, 20), 'sd'), brms::prior(student_t(3, 0, 20), 'sigma')), sample_prior = TRUE, chains = 3, cores = 3, iter = 1e3)
+}
+
+schoolfieldModelBrms  <-  function (data) {
[…]

### 2022-02-24 R/tidy_wide2long_v2.R

@@ -1,0 +1,143 @@
+setwd("~/Dropbox/q10_meta/")
+
+rm(list = ls())
+
+library(googlesheets)
+library(tidyverse)
+library(magrittr)
+
+source("R/functions.R")
+
+gs <- gs_title("q10_newdata")
+data <- as_tibble(gs_read(ss = gs))
+
+head(data)
+
+
+#Creating ES
+
+data$obs <- as.factor(1:dim(data)[1])
+
+# getting effect sizes
+data %<>% Q10S10(temp_1, temp_2, r1.1, r1.2, r2.1, r2.2, r1.1_se, r1.2_se, r2.1_se, 
+                 r2.2_se, r1.1_N, r1.2_N, r2.1_N, r2.2_N)
+
+# adding species names
+data %<>% mutate(spp_names = str_c(genus, species, sep = "_"))
+
+data
+
+#Other raw data
+names(data)
+data[,1:45]
+
+#ES
+es <- c("RR", "SQ10", "CV")
+
+grep(es[1],colnames(data), perl = T)
+
+grep(es[2],colnames(data))
+
+grep(es[3],colnames(data))
+
+#treats
+
+treats <- c("ac", "aw", "pa")
+
+grep(treats[1],colnames(data))
+
+grep(treats[2],colnames(data))
+
+grep(treats[3],colnames(data))
+
+#Q10RR and Change Q10RR colnames
+Q10RRdat <- select(data, obs, grep(es[1],colnames(data), perl = T))
+
+Q10RRdat_ac <- select(Q10RRdat, obs, grep(treats[1], colnames(Q10RRdat)))
+colnames(Q10RRdat_ac) <- c("obs", "ES", "V_ES")
+Q10RRdat_ac$treat <- rep("ac", nrow(Q10RRdat_ac))
+
+
+Q10RRdat_aw <- select(Q10RRdat,  obs, grep(treats[2], colnames(Q10RRdat)))
+colnames(Q10RRdat_aw) <- c("obs", "ES", "V_ES")
+Q10RRdat_aw$treat <- rep("aw", nrow(Q10RRdat_aw))
+
+Q10RRdat_pa <- select(Q10RRdat,  obs, grep(treats[3], colnames(Q10RRdat)))
+colnames(Q10RRdat_pa) <- c("obs", "ES", "V_ES")
+Q10RRdat_pa$treat <- rep("pa", nrow(Q10RRdat_pa))
+
+
[…]

### 2022-02-24 supp/Supplemental Materials and Methods.Rmd
updating script to run wth new file structure. Need to export from levelplot from functions to avoid conflict iwth ggplot2

@@
 ##################################
-    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, microclima, NicheMapR, tmap, rgdal, MCMCglmm, brms, latex2exp)
+    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp)
 
@@
     #data <- read_sheet(ss = "q10_newdata")
-    data <- read.csv("../../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
+    data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
     data$lat <- as.numeric(data$lat)
@@
 
-      #write.csv(data, file = "./output/data/data_final_wide.csv", row.names = FALSE)
+      write.csv(data, file = "../output/data/data_final_wide.csv", row.names = FALSE)
 ##################################
@@
       with(data_long, table(type, trait_category))
-      #write.csv(data_long, file = "./output/data/data_final_long.csv", row.names = FALSE)
+      write.csv(data_long, file = "../output/data/data_final_long.csv", row.names = FALSE)
 ```
@@
           col.regions = colfunc(50), ylab = "Latitude", xlab = "Longitude")  +# Have a quick look
-          layer(sp.points(points, pch = 16, col = "black")) + 
-          layer(sp.lines(coast_outline, col="black", lwd=0.5))
+          latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
+          latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5))
 
@@
  p1 <- levelplot(seasonalityDec/10, margin =FALSE, cuts=20, pretty=TRUE, main = "December", col.regions=colfunc(50)) +
-        layer(sp.points(points, pch = 16, col = "black")) +
-        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better +
+        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) +
+        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better +
  p2 <- levelplot(seasonalityApril/10, margin =FALSE, main = "April", cuts=20, pretty=TRUE, col.regions=colfunc(50)) + 
-        layer(sp.points(points, pch = 16, col = "black")) + 
-        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
+        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
+        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
  p3 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=20, pretty=TRUE, col.regions=colfunc(50)) +
-        layer(sp.points(points, pch = 16, col = "black")) + 
-        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
+        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
+        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
  p4 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=50, pretty=TRUE, 
                  col.regions=colfunc(100), ylim = c(0,100), xlim = c(-130, -40)) + 
-        layer(sp.points(points, pch = 16, col = "black")) + 
-        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
+        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
+        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 
@@
   lnRR_Q10_mod1 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.95), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
-  saveRDS(lnRR_Q10_mod1, "../models/lnRR_Q10_mod1")
+  saveRDS(lnRR_Q10_mod1, "../output/models/lnRR_Q10_mod1")
 } else{
-lnRR_Q10_mod1 <- readRDS("../models/lnRR_Q10_mod1")  }
+lnRR_Q10_mod1 <- readRDS("../output/models/lnRR_Q10_mod1")  }
 
@@
   lnRR_Q10_mod2 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type*habitat + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.99), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
-  saveRDS(lnRR_Q10_mod2, "../models/lnRR_Q10_mod2")
+  saveRDS(lnRR_Q10_mod2, "../output/models/lnRR_Q10_mod2")
 }else{
-  lnRR_Q10_mod2 <- readRDS("../models/lnRR_Q10_mod2")
+  lnRR_Q10_mod2 <- readRDS("../output/models/lnRR_Q10_mod2")
 }

### 2022-02-24 supp/Supplemental Materials and Methods.Rmd
Cleaning up a bit of unecessary code

@@
 
-     #gs <- gs_title("q10_newdata")
-    #data <- as_tibble(gs_read(ss = gs))
-
 ##################################
@@
 
-    #data <- read_sheet(ss = "q10_newdata")
           data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)

### 2022-04-08 R/Surface_climate_timelines_hardcopy_ERA5.R
Adding path names

@@ -24,8 +24,8 @@ library(ncdf4)
 #library(sf)
 #library(raster)
 
-if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
-  gbif     = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+if(!file.exists("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
+  gbif     = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
   gbif$Fid = 1:nrow(gbif)
   #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
   
@@ -37,8 +37,8 @@ if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_ro
   gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
   gbif$ERA5col = as.numeric(cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440)))
   
-  ncfname   = "E:/ERA5/ERA5_LST_and_SST_1979-present.nc"
-  ERA5.air  = nc_open(ncfname)
+  ncfname   = "./data/climate_data/ERA5/ERA5_LST_and_SST_1979-present.nc"
+  ERA5.air  = nc_open(ncfname) ## Fails here, why?
   print(ERA5.air)
   dname     = "t2m"
   lon       = ncvar_get(ERA5.air, "longitude")
@@ -75,11 +75,11 @@ if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_ro
   
   rm(map, point.timeseries)
   
-  write.csv(gbif, "Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
+  write.csv(gbif, ".data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
   
 } else {
   
[…]

### 2022-04-09 R/Surface_climate_timelines_RNCEP.R
Updating path names and running script

@@ -13,13 +13,13 @@ rm(list=ls())
 library(raster)
 library(RNCEP)
 
-gbif = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+gbif = read.csv("data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
 
 # Work through species
 for(spp in unique(gbif$Species)){
   
-  if(file.exists(paste0("Output/RNCEP/",spp,"_clim_stats.RData"))){
-    load(paste0("Data/Land/",spp,"_clim_stats.RData"))
+  if(file.exists(paste0("output/climate_data/RNCEP/",spp,"_clim_stats.RData"))){
+    load(paste0("output/climate_data/RNCEP/land/",spp,"_clim_stats.RData")) 
     sites               = gbif_microclimate[[2]]
     annual.thermal.data = gbif_microclimate[[3]]
     s2                  = gbif_microclimate[[4]]
@@ -110,7 +110,7 @@ for(spp in unique(gbif$Species)){
     
     # Save
     gbif_microclimate = list("Species"=spp,"XY"=sites.xy, "Site_order"=sites,"Microclimate"=annual.thermal.data,"Time_taken"=s2)
-    save(gbif_microclimate, file=paste0("Data/Land/",spp,"_microclimate_stats.RData"))
+    save(gbif_microclimate, file=paste0("output/climate_data/RNCEP/land/",spp,"_microclimate_stats.RData"))
     
   } # Site loop
   

### 2022-04-09 R/Surface_climate_timelines_hardcopy_NCEP.R
Updating path names, but a few things are odd with this file because 1_ only 1960 data is locaded for initial load, what about all the other .nc files?; 2) path names don't seem to make much sense

@@ -12,8 +12,8 @@ library(ncdf4)
 #library(sf)
 #library(raster)
 
-if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")){
-  gbif     = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+if(!file.exists("./output/data/climate_data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")){
+  gbif     = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
   gbif$Fid = 1:nrow(gbif)
   #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
   
@@ -25,7 +25,7 @@ if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_ro
   gbif$NCEPcol[gbif$NCEPcol<0] = (180-abs(gbif$NCEPcol[gbif$NCEPcol<0]))+180
   gbif$NCEPcol = as.numeric(cut(gbif$longitude, seq(0,360,2.5), labels=c(1:144)))
   
-  ncfname   = "E:/NCEP_Reanalysis 1/air.sig995.1960.nc"
+  ncfname   = "./data/climate_data/NCEP_Reanalysis 1/air.sig995.1960.nc"
   NCEP.air  = nc_open(ncfname)
   print(NCEP.air)
   dname     = "air"
@@ -58,11 +58,11 @@ if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_ro
                                count= c(1,1,nt) )
   plot(point.timeseries ~c(1:nt), type="l")
   
-  write.csv(gbif, "Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")
+  write.csv(gbif, "data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")
   
 } else {
   
-  gbif = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")
[…]

### 2022-04-10 R/Surface_climate_timelines_hardcopy_NCEP.R
Still problems will Alex's script. L 73 fails because the col names NCE.. don't exist. There is no where these are specified.

@@ -62,7 +62,7 @@ if(!file.exists("./output/data/climate_data/GBIF/Terrestrial_GBIF_occurrences_pl
   
 } else {
   
-  gbif = read.csv("data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")
+  gbif = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
   
   spp  = unique(gbif$Species)
   
@@ -77,7 +77,7 @@ if(!file.exists("./output/data/climate_data/GBIF/Terrestrial_GBIF_occurrences_pl
       
       # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
       # Open NETCDF file
-      ncfname   = paste0("./data/climate_data/NCEP_Reanalysis 1/air.sig995.",j,".nc")
+      ncfname   = paste0("./data/climate_data/NCEP_Reanalysis_1/air.sig995.",j,".nc")
       NCEP.air  = nc_open(ncfname)
       dname     = "air"
       lon       = ncvar_get(NCEP.air, "lon")

### 2022-04-10 R/Surface_climate_timelines_RNCEP.R
Updating climate scripts. and removing RNCEP.R because it's not needed

@@ -1,132 +1,0 @@
-###################################################################################
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-#                   NCEP REANLYSIS2 CLIMATE DATA DOWNLOAD
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-###################################################################################
-
-# NCEP Reanlysis
-# https://psl.noaa.gov/data/gridded/data.ncep.reanalysis.html
-
-
-rm(list=ls())
-
-library(raster)
-library(RNCEP)
-
-gbif = read.csv("data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
-
-# Work through species
-for(spp in unique(gbif$Species)){
-  
-  if(file.exists(paste0("output/climate_data/RNCEP/",spp,"_clim_stats.RData"))){
-    load(paste0("output/climate_data/RNCEP/land/",spp,"_clim_stats.RData")) 
-    sites               = gbif_microclimate[[2]]
-    annual.thermal.data = gbif_microclimate[[3]]
-    s2                  = gbif_microclimate[[4]]
-    rm(gbif_microclimate)
-    
-  } else {
-    # Create matrix to hold thermal data for this species
-    annual.thermal.data = matrix(NA, ncol=30)
-    colnames(annual.thermal.data) = c("Fid","Latitude","Longitude","Year",
-                                      "Annual.mean",sprintf("Mean%02d",c(1:12)),
-                                      "Annual.sd",sprintf("SD%02d",c(1:12)) )
-    
-    # Choose  site at random, and then each next site as the furthest from those selected
-    sites.xy = gbif[which(gbif$Species==spp),c("longitude","latitude")]
-    plot(sites.xy, col="white", las=1)
-    sites    = which(gbif$Species==spp)
-    s1       = sample(sites, 1)
-    sites    = sites[!sites %in% s1]
-    for(i in 1:length(sites)){
-      if( length(s1)>250 ){    x1 = sample(s1,250) } else {   x1=s1 }
-      if( length(sites)>250 ){ x2 = sample(sites,250)} else { x2=sites }
-      x3    = pointDistance(sites.xy[s1,], sites.xy[x2,], lonlat = TRUE, allpairs=TRUE)/1000
[…]

### 2022-04-10 R/Surface_climate_timelines_hardcopy_NCEP.R

@@ -62,7 +62,7 @@ if(!file.exists("./output/data/climate_data/GBIF/Terrestrial_GBIF_occurrences_pl
   
 } else {
   
-  gbif = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
+  gbif = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")
   
   spp  = unique(gbif$Species)
   
@@ -123,7 +123,7 @@ if(!file.exists("./output/data/climate_data/GBIF/Terrestrial_GBIF_occurrences_pl
     
     # Save file of temperatures for each species
     rownames(Tdat) = sdat$Fid
-    write.csv(Tdat, paste0("./output/climate_data/ERA5/",sp,"_temperature_history.csv"))
+    write.csv(Tdat, paste0("./output/climate_data/NCEP/",sp,"_temperature_history.csv"))
     
   } #  End of species loop
   

### 2022-04-10 R/Surface_microclimate_timelines.R

@@ -158,7 +158,7 @@ apply(spp.lcm>0, 1, sum)
 
 write.csv(gbif_terr,  "Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv", row.names = F)
 
-
+###################### START CODE HERE FOR MICROCLIMATE PROJECTIONS###########
 ###################################################################################
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 #                         MICROCLIMATE CALCULATION

### 2022-04-10 R/GBIF_ocurrence_data.Rmd
Alex fixed the code. I nee dto fix path names

---
title: "GBIF occurrences"
author: "Alex Bush"
date: "17/05/2021"
output: html_document
---

# Species Data

```{r}
rm(list=ls())

spp.list = read.csv("../q10_meta-master/data/species_list_Q10.csv")
spp      = unique(spp.list$species_full)

spp[71]  = "Enithares"                 # Switch 'Enithares sp' to whole genus
spp[73]  = "Euchemotrema leaii"        # Synonym: Euchemotrema leai
spp[133] = "Merlangius merlangus"      # Synonym: Merlanguis merlangus
spp[175] = "Pinctada mazatlanica"      # Synonym: Pinctada mazatlantica
spp[202] = "Hoplobatrachus tigerinus"  # Synonym: Rana tigrina
spp[203] = "Lithobates virgatipes"     # Synonym: Rana vergatipes
spp[239] = "Zoarces viviparus"         # Synonym: Zoarces viviparous

# Note:
# > Halozetes fulvus is a species of mite endemic to Marion Island, hence no records in GBIF

```

# DOWNLOAD DATA FROM GBIF

```{r }
library(rgbif)
library(scrubr)
library(maps)

for(i in 1:length(spp)){
  if( !file.exists(paste0("../Data/GBIF/",gsub(" ","_",spp[i]),"_occurrences.RData")) ){
    # Download GBIF occurrence data for this taxon
    gbif_data = occ_data(scientificName = spp[i], hasCoordinate = TRUE, limit = 20000)
    # Save
    save(gbif_data, file=paste0("../Data/GBIF/",gsub(" ","_",spp[i]),"_occurrences.RData"))
    # No of records available:
    print(paste0(spp[i],": ",gbif_data$meta$count))
    # If "Records found" is larger than "Records returned", need to increase the 'limit' argument above
    # See help(occ_data) for options and limitations
    rm(gbif_data)
  }
}

# Quite a few have more than 20k records so need to update the download:
xspp = c("Alligator mississippiensis","Amphiura filiformis","Anolis carolinensis","Asterias rubens","Barbus barbus","Bithynia tentaculata","Boreogadus saida","Carassius auratus","Carassius carassius","Caretta caretta","Chrysemys picta","Crocodylus porosus","Cyprinus carpio","Gadus macrocephalus","Gadus morhua","Gambusia holbrooki","Gasterosteus aculeatus","Lepomis cyanellus","Lepomis macrochirus","Lepomis megalotis","Limax maximus","Limecola balthica","Limnodynastes peronii","Lithobates clamitans","Micropterus salmoides","Myoxocephalus scorpius","Mytilus edulis","Notophthalmus viridescens","Oncorhynchus mykiss","Oncorhynchus tshawytscha","Ophiothrix fragilis","Osmerus mordax","Perca flavescens","Perca fluviatilis","Pimephales promelas","Pomoxis nigromaculatus","Porcellio scaber","Pseudopleuronectes americanus","Pungitius pungitius","Rhinella marina","Rutilus rutilus","Salmo trutta","Salvelinus fontinalis","Salvelinus namaycush","Scomber japonicus","Trachemys scripta","Vipera berus","Zoarces viviparus")

for(i in match(xspp,spp)){
  # Download GBIF occurrence data for this taxon (hard limit is 100000)
  gbif_data = occ_data(scientificName = spp[i], hasCoordinate = TRUE, limit = 100000)
  # Save
  save(gbif_data, file=paste0("../Data/GBIF/",gsub(" ","_",spp[i]),"_occurrences.RData"))
  # No of records available:
  print(paste0(spp[i],": ",gbif_data$meta$count," == ",nrow(gbif_data$data)))
  # If "Records found" is larger than "Records returned", need to increase the 'limit' argument above
  # See help(occ_data) for options and limitations
  rm(gbif_data)
}

```

# CLEAN RECORDS

```{r }
doi.list = list()

for(i in 1:length(spp)){
  # Load GBI occurrence file
  load(paste0("../Data/GBIF/",gsub(" ","_",spp[i]),"_occurrences.RData"))

  # get the columns that matter for mapping and cleaning the occurrence data:
  xcols = c("decimalLongitude","decimalLatitude",
            "individualCount","occurrenceStatus",
            "coordinateUncertaintyInMeters",
            "institutionCode") #"references"
  coords = gbif_data$data[,names(gbif_data$data)%in%xcols] 
  coords = data.frame("Species" = spp[i], coords)
  #head(coords)

  # Map the occurrence data:
  map("world", 
      xlim = range(coords$decimalLongitude), 
      ylim = range(coords$decimalLatitude))  
  points(coords[ , c("decimalLongitude", "decimalLatitude")],pch=16, col="red", cex=0.5)

  # Remove records of absence or zero-abundance (if any)
  if( c("individualCount") %in% names(gbif_data$data)  ){
    #sort(unique(coords$individualCount))   # notice if some points correspond to zero abundance
    if( any(coords$individualCount==0 & !is.na(coords$individualCount)) ){
      coords = coords[!which(coords$individualCount==0 & !is.na(coords$individualCount)),]
    }
  }

  # Check for different indications of "absent", which could be in different languages! and remember that R is case-sensitive
  if( (c("individualCount") %in% names(gbif_data$data)) & c("occurrenceStatus") %in% names(gbif_data$data)  ){
    #sort(unique(coords$occurrenceStatus))
    absence_rows = which(coords$individualCount==0 | 
                           coords$occurrenceStatus %in% c("absent","Absent","ABSENT","ausente","Ausente","AUSENTE"))
    if(length(absence_rows) > 0){ coords = coords[-absence_rows, ] ; print(paste0("Removing ",length(absence_rows)," rows of 'absence' data.")) }
  }

  # Functions from the 'scrubr' package identify records with lat/long issues
  if( c("coordinateUncertaintyInMeters") %in% names(gbif_data$data)  ){
    #nrow(coords)
    coords      = coord_incomplete(coord_imprecise(coord_impossible(coord_unlikely(coords))))
    #nrow(coords)
  }

  # Eliminate presences with reported coordinate uncertainty (location error, 
  # spatial resolution) larger than 1 km (as this will be the grain of 
  # observation for the climate data later):
  if( c("coordinateUncertaintyInMeters") %in% names(gbif_data$data)  ){
    coords = coord_uncertain(coords, coorduncertainityLimit = 1000)
    #nrow(coords)
  }

  # Add DOIs to list for eventual citation for all species:
  doi.list = c(doi.list, gbif_citation(gbif_data))

  # Save
  save(gbif_data, file=paste0("../Data/GBIF/",gsub(" ","_",spp[i]),"_occurrences.RData"))

  rm(gbif_data)
  print(i)
}

# Keep only unique DOI's
doi.list = unique(doi.list)
# Save DOIs
save(doi.list, file="../Data/GBIF/List_of_GBIF_data_DOIs.RData")

```

****

```{r}
gbif = data.frame("Species"          = NA,
                  "decimalLongitude" = NA,
                  "decimalLatitude"  = NA)

for(i in c(1:length(spp))[-95] ){
  load(paste0("../Data/GBIF/",gsub(" ","_",spp[i]),"_occurrences.RData"))
  gbif = rbind(gbif, data.frame("Species"=spp[i],gbif_data$data[,c("decimalLongitude","decimalLatitude")]))
  print(paste0(spp[i],"   :::    ",nrow(gbif_data$data)))

}
gbif         = gbif[-1,]
gbif         = gbif[!duplicated(gbif),]
gbif$Species = gsub(" ","_",gbif$Species)

# Save
write.csv(gbif, paste0("../Data/GEE/All_GBIF_occurrences.csv"), row.names = F)

#map("world")
#points(gbif[ ,c("decimalLongitude","decimalLatitude")],pch=16, col="red", cex=0.5)

```

```{r}
rm(list=ls())

gbif = read.csv(paste0("../Data/GBIF/All_GBIF_occurrences.csv"))
names(gbif)[2:3] = c("longitude","latitude")

spp.list = read.csv("../q10_meta-master/data/species_list_Q10.csv")
spp      = spp.list$species_full
spp[71]  = "Enithares"                 # Switch 'Enithares sp' to whole genus
spp[73]  = "Euchemotrema leaii"        # Synonym: Euchemotrema leai
spp[133] = "Merlangius merlangus"      # Synonym: Merlanguis merlangus
spp[175] = "Pinctada mazatlanica"      # Synonym: Pinctada mazatlantica
spp[202] = "Hoplobatrachus tigerinus"  # Synonym: Rana tigrina
spp[203] = "Lithobates virgatipes"     # Synonym: Rana vergatipes
spp[239] = "Zoarces viviparus"         # Synonym: Zoarces viviparous

widedat  = read.csv("../q10_meta-master/data/CombinedData_wide.csv")
widedat$spp_names = paste(widedat$genus,widedat$species)
habitat  = widedat$habitat[match(spp.list$species_full, gsub("_"," ",widedat$spp_names))]
# Change habitat of Shortnose Sturgeon (Acipenser brevirostrum) to freshwater
habitat[4] = "f"

gbif             = read.csv(paste0("../Data/GEE/All_GBIF_occurrences.csv"))
names(gbif)[2:3] = c("longitude","latitude")
gbif$habitat     = habitat[match(gbif$Species, gsub(" ","_",spp))]

# Subsets
gbif_terr        = gbif[gbif$habitat=="t",1:3] # Take terrestrial subset for MODIS LCM extraction
gbif_fresh       = gbif[gbif$habitat=="f",1:3] # Take freshwater subset (also for MODIS LCM extraction)
gbif_mar         = gbif[gbif$habitat=="m",1:3] # Take marine subset to extract NOAA SST data

gbif_terr$Fid    = c(1:nrow(gbif_terr))
gbif_fresh$Fid   = c(1:nrow(gbif_fresh))
gbif_mar$Fid     = c(1:nrow(gbif_mar))

write.csv(gbif_terr,  paste0("../Data/GBIF/Terrestrial_GBIF_occurrences.csv"), row.names = F)
write.csv(gbif_fresh, paste0("../Data/GBIF/Freshwater_GBIF_occurrences.csv"), row.names = F)
write.csv(gbif_mar,   paste0("../Data/GBIF/Marine_GBIF_occurrences.csv"), row.names = F)

```

### 2022-04-10 R/Surface_climate_timelines_hardcopy_ERA5.R

@@ -24,8 +24,8 @@ library(ncdf4)
 #library(sf)
 #library(raster)
 
-if(!file.exists("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
-  gbif     = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
+  gbif     = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
   gbif$Fid = 1:nrow(gbif)
   #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
   
@@ -37,8 +37,8 @@ if(!file.exists("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_a
   gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
   gbif$ERA5col = as.numeric(cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440)))
   
-  ncfname   = "./data/climate_data/ERA5/ERA5_LST_and_SST_1979-present.nc"
-  ERA5.air  = nc_open(ncfname) ## Fails here, why?
+  ncfname   = "E:/ERA5/ERA5_LST_and_SST_1979-present.nc"
+  ERA5.air  = nc_open(ncfname)
   print(ERA5.air)
   dname     = "t2m"
   lon       = ncvar_get(ERA5.air, "longitude")
@@ -75,11 +75,11 @@ if(!file.exists("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_a
   
   rm(map, point.timeseries)
   
-  write.csv(gbif, ".data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
+  write.csv(gbif, "Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
   
 } else {
   
-  gbif = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
[…]

### 2022-04-10 R/Surface_climate_timelines_hardcopy_ERA5.R
Fixed up the path names for file. This still needs work in summarising climate data from ERA5

@@ -24,8 +24,8 @@ library(ncdf4)
 #library(sf)
 #library(raster)
 
-if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
-  gbif     = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat.csv")
+if(!file.exists("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
+  gbif     = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
   gbif$Fid = 1:nrow(gbif)
   #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
   
@@ -37,7 +37,7 @@ if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_ro
   gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
   gbif$ERA5col = as.numeric(cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440)))
   
-  ncfname   = "E:/ERA5/ERA5_LST_and_SST_1979-present.nc"
+  ncfname   = "./data/climate_data/ERA5/ERA5_LST_and_SST_1979-present.nc"
   ERA5.air  = nc_open(ncfname)
   print(ERA5.air)
   dname     = "t2m"
@@ -75,11 +75,11 @@ if(!file.exists("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_ro
   
   rm(map, point.timeseries)
   
-  write.csv(gbif, "Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
+  write.csv(gbif, "./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
   
 } else {
   
-  gbif = read.csv("Data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
+  gbif = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")
   
[…]

### 2022-04-12 supp/Supplemental Materials and Methods.Rmd
Code fixes
Added a few shortcuts. One, no need to rerun code to sort out data in long format. So, added two output data loads. Added a new code chunk to extract unique species names and lat, longs for those species that will be used to extract climate data. Exported as Species_LatLong_pluHabitat

@@
   options(digits = 2)
-```
 
-```{r packages_data, results='hide'}
 ##################################
@@
     source("../R/functions.R")
+```
 
+```{r packages_data, results='hide', eval = FALSE}
 ##################################
@@
       data <- data %>%
-              mutate(species_full = ifelse(species_full == "Chinemys reevesii", "Mauremys reevesii", species_full)) %>%
-              mutate(species_full = ifelse(species_full == "Enithares sp", "Enithares ciliata", species_full))  %>%
+              mutate(species_full = ifelse(species_full == "Chinemys reevesii", 
+                                           "Mauremys reevesii", species_full)) %>%
+              mutate(species_full = ifelse(species_full == "Enithares sp", 
+                                           "Enithares ciliata", species_full))  %>%
               mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>% # Fix a few errors in habitat classificaton
@@
 #####################################
+data_long <- read.csv("../output/data/data_final_long.csv")
+data_wide <- read.csv("../output/data/data_final_wide.csv")
 
@@
     ## Tree data; also fix up some errors
-    tree_data <-  data %>%
+    tree_data <-  data_long %>%
                   mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
@@
                   distinct(species_full, habitat, n)
+
+    # Get the unique species lat and long data which will be used to extract climate data for each ppulation / species for wild derived sources.
+    climate_data <-  data_long %>%
+                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
+                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
+                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
+                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
+                  group_by(species_full)%>%
+                  mutate(n = length(habitat)) %>%
+                  dplyr::select(species_full,  habitat, source, n, lat, long) %>% 
+                  distinct(species_full, habitat, n, source, lat, long) 
+      write.csv(climate_data, file = "../data/climate_data/Species_LatLong_plusHabitat.csv", row.names=FALSE)
 

### 2022-04-13 supp/Supplemental Materials and Methods.Rmd
replaced climae_data with data_wide as data_long seems to be missing quite a lot of data. Need to re-check the re-organisation of the data

@@
     # Get the unique species lat and long data which will be used to extract climate data for each ppulation / species for wild derived sources.
-    climate_data <-  data_long %>%
+    climate_data <-  data_wide %>%
                   mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
@@
                   mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
-                  group_by(species_full)%>%
-                  mutate(n = length(habitat)) %>%
-                  dplyr::select(species_full,  habitat, source, n, lat, long) %>% 
-                  distinct(species_full, habitat, n, source, lat, long) 
+                  dplyr::select(species_full,  habitat, source, lat, long) %>% 
+                  distinct(species_full, habitat, source, lat, long) 
       write.csv(climate_data, file = "../data/climate_data/Species_LatLong_plusHabitat.csv", row.names=FALSE)

### 2022-04-13 supp/Supplemental Materials and Methods.Rmd
Updated the code to use data_wide in the climate_data

@@
                   dplyr::select(species_full,  habitat, source, lat, long) %>% 
-                  distinct(species_full, habitat, source, lat, long) 
+                  distinct(species_full, habitat, source, lat, long) %>%
+                  arrange(species_full)
       write.csv(climate_data, file = "../data/climate_data/Species_LatLong_plusHabitat.csv", row.names=FALSE)

### 2022-04-14 supp/Supplemental Materials and Methods.Rmd
Added some code that pivots_wide longer to convert wide to long, and hopefully don't lose data anymore.

@@
 ##################################
+        ################ THIS SHOULD FIX THE DATA_LONG problems
+      data_long_t <- data_wide %>%
+                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% data.frame()
 

### 2022-04-14 supp/Supplemental Materials and Methods.Rmd
Adding in type, acclimation vs acute

--- 2022-04-13 supp/Supplemental Materials and Methods.Rmd
@@
 ##################################
+        ################ THIS SHOULD FIX THE DATA_LONG problems
+      data_long_t <- data_wide %>%
+                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
+                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
 

### 2022-04-15 ms/ms.rmd
Rejig MS

---
author: Daniel W.A. Noble, Fonti Kar, Frank Seebacher Alex Bush, & Shinichi Nakagawa
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits		  ## and rounded to 2 digits
  options(digits = 2)
```

### 2022-04-16 supp/Supplemental Materials and Methods.Rmd
changed data to data_wide through code. Makes it more clear

--- 2022-04-13 supp/Supplemental Materials and Methods.Rmd
@@
 
-          data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
-      data$lat <- as.numeric(data$lat)
-    new_papers <- data[-grep("_o", data$record_num),]
-    old_papers <- data[grep("_o", data$record_num),]
+          data_wide <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
+      data_wide$lat <- as.numeric(data_wide$lat)
+    new_papers <- data_wide[-grep("_o", data_wide$record_num),]
+    old_papers <- data_wide[grep("_o", data_wide$record_num),]
 
     # Add full species to data
-      data <- data %>%
+      data_wide <- data_wide %>%
               mutate(species_full = paste0(genus, " ",species))
@@
     # habitat
-      spp_habitat <- data %>%
+      spp_habitat <- data_wide %>%
                       group_by(habitat) %>%
@@
       # Note that some species need to be replaced
-      data <- data %>%
+      data_wide <- data_wide %>%
               mutate(species_full = ifelse(species_full == "Chinemys reevesii", 
@@
     # Convert se to SD so it can be used for effect sizes. Drop out the SE columns as these are no longer needed
-      data <- data %>%
+      data_wide <- data_wide %>%
               mutate(r1.1_sd = se_to_sd(r1.1_se, r1.1_N),
@@
 
-      data <- data %>%
+      data_wide <- data_wide %>%
              mutate(lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
@@
 
-      data <- data %>%
+      data_wide <- data_wide %>%
               filter(!record_num == "p088_o")
 
-      write.csv(data, file = "../output/data/data_final_wide.csv", row.names = FALSE)
+      write.csv(data_wide, file = "../output/data/data_final_wide.csv", row.names = FALSE)
 ##################################

### 2022-04-16 ms/ms.rmd
Seeting up MS. Need to think about how to best organise.

@@
   options(digits = 2)
+
+##################################
+# Clean workspace
+##################################
+    rm(list=ls())
+
+##################################
+# Loading packages & Functions
+##################################
+    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp)
+
+#devtools::install_github(repo = "ErikKusch/KrigR")
+## Function to produce colour palette
+# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can greate a custom colour palelte function using colorRampPallette
+colfunc <- colorRampPalette(rev(brewer.pal(10,"RdBu")))
+#test colfunc(10) will generate the exact Hex codes for 10 different colours can 10 to 100 and you get 100 colour hex codes.
+Very useful webpage: https://pjbartlein.github.io/REarthSysSci/rasterVis01.html
+
+    # loading functions
+    source("../R/functions.R")
+
 ```

### 2022-04-17 supp/Supplemental Materials and Methods.Rmd
fixing up data_long. Removing old code that wasn't working as expected.

@@
 ##################################
-        ################ THIS SHOULD FIX THE DATA_LONG problems
-      data_long_t <- data_wide %>%
-                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
-                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
 
@@
 
-      data_t1 <- data                                                  %>%
-                 dplyr::select(c(1:26, grep("acute_t1", colnames(.)))) %>%
-                 filter_if(~is.numeric(.), all_vars(!is.na(.)))        %>% # Filter all the na effect sizes 
-                 rename(lnRR_Q10    = lnRR_Q10_acute_t1,       # Rename columns
-                        V_lnRR_Q10  = V_lnRR_Q10_acute_t1,
-                        lnVR_Q10    = lnVR_Q10_acute_t1,
-                        V_lnVR_Q10  = V_lnVR_Q10_acute_t1, 
-                        lnCVR_Q10   = lnCVR_Q10_acute_t1,
-                        V_lnCVR_Q10 = V_lnCVR_Q10_acute_t1,
-                              paper = record_num)            %>%
-                 mutate(type = "acute")
-
-      dim(data_t1)
-
-      # Do the same for hot acute
-      data_t2 <- data                                                  %>%
-                 dplyr::select(c(1:26, grep("acute_t2", colnames(.)))) %>%
-                 filter_if(~is.numeric(.), all_vars(!is.na(.)))        %>%  # Filter all the na effect sizes 
-                 rename(lnRR_Q10    = lnRR_Q10_acute_t2,
-                        V_lnRR_Q10  = V_lnRR_Q10_acute_t2,
-                        lnVR_Q10    = lnVR_Q10_acute_t2,
-                        V_lnVR_Q10  = V_lnVR_Q10_acute_t2, 
-                        lnCVR_Q10   = lnCVR_Q10_acute_t2,
-                        V_lnCVR_Q10 = V_lnCVR_Q10_acute_t2,
-                              paper = record_num)            %>%
-                 mutate(type = "acute")
-      dim(data_t2)
-
-      # Now do for the acclimation
-      data_acclim <- data                                            %>%
-                 dplyr::select(c(1:26, grep("acclim", colnames(.)))) %>%
-                 filter_if(~is.numeric(.), all_vars(!is.na(.)))      %>% # Filter all the na effect sizes 
-                 rename(lnRR_Q10    = lnRR_Q10_acclim,
-                        V_lnRR_Q10  = V_lnRR_Q10_acclim,
-                        lnVR_Q10    = lnVR_Q10_acclim,
-                        V_lnVR_Q10  = V_lnVR_Q10_acclim, 
-                        lnCVR_Q10   = lnCVR_Q10_acclim,
-                        V_lnCVR_Q10 = V_lnCVR_Q10_acclim,
-                              paper = record_num)            %>%
-                 mutate(type = "acclim")
-      dim(data_acclim)
-
-      # All these data frames are exactly the same excet that the effect sizes. We've removed NA, so lets bind together
-
-      data_long <- bind_rows(data_t1, data_t2, data_acclim)
+        ################ THIS SHOULD FIX THE DATA_LONG problems
+      data_long <- data_wide %>%
+                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
+                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
 

### 2022-04-19 ms/ms.rmd
Adding code to new MS

@@
 ```
+
+```{r data_summary, echo = FALSE, results="hide"}
+
+##########################
+## Load processed datasets
+##########################
+data_wide <- read.csv("../output/data/data_final_wide.csv")
+data_long <- read.csv("../output/data/data_final_long.csv")
+
+##########################
+## Summarise data
+ data_wide$lat <- as.numeric(data_wide$lat)
+    new_papers <- data_wide[-grep("_o", data_wide$record_num),]
+    old_papers <- data_wide[grep("_o", data_wide$record_num),]
+
+    # habitat
+      spp_habitat <- data_wide %>%
+                      group_by(habitat) %>%
+                      summarise(spp_n = length(unique(species_full)))
+      tot_spp <- sum(spp_habitat[,2])
+
+```

### 2022-04-19 ms/ms.rmd
Adding text to materials nad methods

@@
 ```
+
+## Materials and Methods
+### *Literature collection*
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
+We used data from a previous meta-analysis [@Seebacher2015] and updated Seebacher *et.
+al.* @Seebacher2015's data by extractng data from suitable studies from our own searches that followed the same search protocol.
+More specically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
+We limited our search to articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et.
+al.* @Seebacher2015 searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
+
+Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016].
+We also cross checked papers we found in our searches with a recent paper by Havird *et.
+al.* @Havird2020, which also updates Seebacher *et.
+al.* @Seebacher2015's dataset.
+We included any papers that were missed between our searches and those of Havird *et.
+al.* @Havird2020 from the dates 2013-2017.
+Havird *et.
+al.* @Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metbolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et.
+al.* @Seebacher2015's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et.
+al.* @Seebacher2015 dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that Seebacher *et.
+al.* @Seebacher2015 included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
+While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
+As such, our database represents the most up-to-date dataset used by Seebacher *et.
+al.* @Seebacher2015 to answer questions on acclimation across ectotherms.
+
+We split the screening of titles and abstracts for the 1,321 papers found in our search among all authors evenly.
+To ensure consistency among authors in title and abstracts that should be included, prior to  screening all authors went through a randomly sleected set of papers together - agreeing on those that were relevant and those that were not based on our inclusion criteria (see below).
+Where any authors were uncertain about whether to include a paper in the sub-sample they screened, we conservatively included the paper for full text screening and dicussed uncertain papers among authors to come to a decison on whether to include the paper.
+After title and abstract screening, we were left with a total of 149 papers for full text screening.
+Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+
+### *Data Compilation*
+
+We extracted means, standard deviations and sample sizes for physiological rates at the two test tempetatures.
+If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatues experienced by the speceis in question.
+We extracted these data from text, tables or figures of a given paper.
+Data were extracted from figures using the R package *metaDigitise* [@pick2019].
+We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the lab group to identify where the population was likely to have been sourced or derived from when needed.
+If the population was derived from the wild, we recorded the nearest latitude and longitude of the population to the field collection site.
+If the animals had been sourced from a commercial supplier, we took the latitude and longitude of the supplier that the paper identified the animals to have originated from.
+When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
+
+### *Calculating New $Q_{10}$ Based Effect Sizes and Sampling Variances*
+
+To understand changes in physiological rates we often look to comparing $Q_{10}$ values, which describe the multiplicative change in physiological rates across a 10&deg;C temperature change.
+Higher $Q_{10}$ values indicate stronger changes in physiological rates, and it is expected that acclimation should reduce $Q_{10}$ values [@Seebacher2015].
+Currently, however, we do not have effect sizes and associated sampling variances derived for $Q_{10}$ making it challenging to weight effect size estimates by sampling variance as is typical in meta-analysis.
+While the Delta method can be used to approximate the sampling variance (e.g., see Havird *et.
+al.* @Havird2020) this assumes  $Q_{10}$ is normally distributed and linear with respect to temperature.
+Unfortunately, this is not the case for $Q_{10}$, as such, the Delta method is likely a poor approximation to sampling variance.
+There are easier ways to derive effect sizes and associated samping variance for $Q_{10}$ given that $Q_{10}$ is simply a reformulation of a very commonly used effect size in the meta-analysis literature, the log response ratio (*lnRR*) [@hedges1999meta; @laj2011].
+Recognition of the similarity between *lnRR* and $Q_{10}$ means we can derive $Q_{10}$ based effect sizes using the well known mathematical properties of *lnRR*, while also providing easy ways to extend this to effect sizes that compare variances in physiological rates [@nakagawa2015meta] and improve upon our ability to account for sources of non-independence that are typical in meta-analysis [@laj2011; @Noble2017].
+As such, here we derive a series of $Q_{10}$ based effect sizes along with their associated sampling variances that allow one to compare both changes in mean and variance of physiological rates.
+
+#### *Comparing changes in mean physiological rates*
+
+Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*.
+The *lnRR* described by Hedges *et al.* @hedges1999meta and extended by Lajeunesse @laj2011 and can be calculated as follows:
+
+$$
+\begin{equation} 
+  \begin{aligned}
+  lnRR = ln\left ( \frac{X_{1}}{X_{2}}\right )
+  \end{aligned}
+  (\#eq:lnRR)
+\end{equation} 
+$$
+
+$$
+\begin{equation} 
+  s_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
+  (\#eq:slnRR)
+\end{equation} 
+$$
+In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
+The mean of $X_{i}$ for group *i* can be any measurement type (e.g.
+a physiological rate, mass etc) so long as the measurement variable is ratio scale.
+Log transformation of this ratio makes the effect size normally distributed.
+Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
+
+The equations for *lnRR* and its sampling variance allow us to easily extend this to $Q_{10}$ based effect sizes. Recall that $Q_{10}$ is described as follows:
+
+$$
+\begin{equation} 
+  Q_{10} = \left( \frac{R_{2}}{R_{1}} \right)^{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+  (\#eq:q10)
+\end{equation} 
+$$
+Here, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured.
+Log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:
+
+$$
+\begin{equation} 
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10)
+\end{equation} 
+$$
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures.
+This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
+Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
+Recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
+
+$$
+\begin{equation} 
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+  (\#eq:Vlnq10)
+\end{equation} 
+$$
+
+#### *Comparing changes in physiological rate variability*
+
+Nakagawa *et al* @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variablity between two groups.
+We refer readers to Nakagawa *et al* @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling varaince) as follows:
+
+$$
+\begin{equation} 
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10VR)
+\end{equation} 
+$$
+$$
+\begin{equation} 
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+(\#eq:slnq10VR)
+\end{equation} 
+$$
+
+Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
+While this is a useful metric, as discussed by Nakagawa *et al* @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+As such, we can calculate the coefficient of variation, which standardises changes in variance for changes in means as follows:
+
+$$
+\begin{equation} 
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10CVR)
+\end{equation} 
+$$
+$$
+\begin{equation} 
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+(\#eq:slnq10CVR)
+\end{equation} 
+$$
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+
+#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
+Using the mean, standard deviation and sample size for all acute and aclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For all effect sizes the higher acute or acclimation temperture was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardised to 10&deg;C.
+
+### *Moderator Variables*
+
+We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exsposure occurs (longer exsposure = better acclimation response) and whether exsposure took place in the wild ("acclimitized") or lab ("acclimated") [@Seebacher2015].
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "jeuvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et.
+al.* @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
+Physiological rates measures varied widely across the studies but could generally be groups into discrete trait categories @Seebacher2015.
+As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of
+
+### *Meta-Analysis*
+### *Sensitivity Analyses*
+### *Publication Bias*
+
+## Results

### 2022-04-20 ms/ms.rmd
Adding in tree code

@@
 ---
-author: Daniel W.A. Noble, Fonti Kar, Frank Seebacher Alex Bush, & Shinichi Nakagawa
+author: Daniel W.A. Noble, Fonti Kar, Frank Seebacher, Alex Bush, & Shinichi Nakagawa
 date: "`r Sys.Date()`"
@@
 
-```{r data_summary, echo = FALSE, results="hide"}
+```{r data_setup, echo = FALSE, results="hide"}
 
@@
 ##########################
-## Summarise data
+## Summarize data
+##########################
+
  data_wide$lat <- as.numeric(data_wide$lat)
@@
       tot_spp <- sum(spp_habitat[,2])
+
+#########################
+## Phylogeny
+#########################
+ ## Tree data; also fix up some errors
+    tree_data <-  data_long %>%
+                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
+                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
+                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
+                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
+                  group_by(species_full)                                                 %>%
+                  mutate(n = length(habitat))                                            %>%
+                  dplyr::select(species_full,  habitat, n)                               %>% 
+                  distinct(species_full, habitat, n)
+
+ ## Load the phylogenetic tree
+                tree <- read.tree("../tree/tree_binary_SN_Q10.tre")   
+      tree$tip.label <- gsub("_", " ", tree$tip.label)
+      tree$tip.label <- gsub("Enithares sp", "Enithares ciliata", tree$tip.label)
+
+      ## Create nodes and add to data so detailed can be mapped
+          tree_data$node <- NA
+                 tipnode <- seq_along(tree$tip.label)
+          names(tipnode) <- tree$tip.label
+          tree_data$node <- tipnode[tree_data$species_full] ## convert the tip label to tip node number
+                       i <- is.na(tree_data$node)
+       tree_data$node[i] <- tree_data$species_full[i] ## fill in internal node number
+          tree_data$node <- as.integer(tree_data$node)
+
+      # Do a tree check with original data
+          tree_checks(data, tree, dataCol = "species_full", type = "checks") # Great. Currently species in data and tree match
 

### 2022-04-20 ms/ms.rmd
Adding tree checks for data_long. Still lose a lof of secies which is odd, so need to check what is happening with long format again

@@
 
-```{r data_setup, echo = FALSE, results="hide"}
+```{r data_setup_summary, echo = FALSE, results="hide"}
 
@@
       # Do a tree check with original data
-          tree_checks(data, tree, dataCol = "species_full", type = "checks") # Great. Currently species in data and tree match
+          tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
 
+##################################
+# Tree checking and pruning
+##################################
+  # Have a look at species in data and tree. Note that the data2 object excluded all Inf values, which means that species may be lost in the process. So, tree would need to be pruned down
+  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
+
+species_drop <- tree_checks(data_long, tree, dataCol = "species_full", type = "checks")$Species_InTree_But_NotData # Gra list of species in tree misisng from data for pruning
+
+# Prune tree
+tree2 <- drop.tip(tree, species_drop)
+
+# Check that taxa dropped
+tree_checks(data_long, tree2, dataCol = "species_full", type = "checks")
+
+##################################
+# Branch lengths and cor matrix
+##################################
+      # Now that we have the tree file, we need to use it to create a phylogenetic correlation matrix using Grafen's method.
+This assumes Brownian motion and is the best we can do without a molecular phylogeny.
+The topology of the tree should be fairly good.
+We will explore a few different options with p to determine the best power function
+
+        tree_p1 <- compute.brlen(tree2, method = "Grafen", power = 1)
+      tree_p0.5 <- compute.brlen(tree2, method = "Grafen", power = 0.5)
+
+     # Create null nodes 
+        tree_p1$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
+      tree_p0.5$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
 ```

### 2022-04-20 ms/ms.rmd
re-writing MS:

@@
 
-To understand changes in physiological rates we often look to comparing $Q_{10}$ values, which describe the multiplicative change in physiological rates across a 10&deg;C temperature change.
-Higher $Q_{10}$ values indicate stronger changes in physiological rates, and it is expected that acclimation should reduce $Q_{10}$ values [@Seebacher2015].
-Currently, however, we do not have effect sizes and associated sampling variances derived for $Q_{10}$ making it challenging to weight effect size estimates by sampling variance as is typical in meta-analysis.
-While the Delta method can be used to approximate the sampling variance (e.g., see Havird *et.
-al.* @Havird2020) this assumes  $Q_{10}$ is normally distributed and linear with respect to temperature.
-Unfortunately, this is not the case for $Q_{10}$, as such, the Delta method is likely a poor approximation to sampling variance.
-There are easier ways to derive effect sizes and associated samping variance for $Q_{10}$ given that $Q_{10}$ is simply a reformulation of a very commonly used effect size in the meta-analysis literature, the log response ratio (*lnRR*) [@hedges1999meta; @laj2011].
-Recognition of the similarity between *lnRR* and $Q_{10}$ means we can derive $Q_{10}$ based effect sizes using the well known mathematical properties of *lnRR*, while also providing easy ways to extend this to effect sizes that compare variances in physiological rates [@nakagawa2015meta] and improve upon our ability to account for sources of non-independence that are typical in meta-analysis [@laj2011; @Noble2017].
-As such, here we derive a series of $Q_{10}$ based effect sizes along with their associated sampling variances that allow one to compare both changes in mean and variance of physiological rates.
+Following @Noble2022 we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+These effect sizes are essentially similar to the traditional $Q_{10}$,
 

### 2022-04-21 R/1_data_process.R
Added mnew data process file to seperate out bits that are not essential for the actual MS rmd file

@@ -1,0 +1,86 @@
+##################################
+# Load Data & Manipulate
+##################################
+
+data_wide <- read.csv("./data/CombinedData_wide.csv", stringsAsFactors = FALSE)
+data_wide$lat <- as.numeric(data_wide$lat)
+new_papers <- data_wide[-grep("_o", data_wide$record_num),]
+old_papers <- data_wide[grep("_o", data_wide$record_num),]
+
+# Add full species to data
+data_wide <- data_wide %>%
+  mutate(species_full = paste0(genus, " ",species))
+
+# habitat
+spp_habitat <- data_wide %>%
+  group_by(habitat) %>%
+  summarise(spp_n = length(unique(species_full)))
+
+# Note that some species need to be replaced
+data_wide <- data_wide %>%
+  mutate(species_full = ifelse(species_full == "Chinemys reevesii", 
+                               "Mauremys reevesii", species_full)) %>%
+  mutate(species_full = ifelse(species_full == "Enithares sp", 
+                               "Enithares ciliata", species_full))  %>%
+  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>% # Fix a few errors in habitat classificaton
+  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat)) 
+
+# Convert se to SD so it can be used for effect sizes. Drop out the SE columns as these are no longer needed
+data_wide <- data_wide %>%
+  mutate(r1.1_sd = se_to_sd(r1.1_se, r1.1_N),
+         r1.2_sd = se_to_sd(r1.2_se, r1.2_N),
+         r2.1_sd = se_to_sd(r2.1_se, r2.1_N),
+         r2.2_sd = se_to_sd(r2.2_se, r2.2_N)) %>%
+  dplyr::select(-c(r1.1_se, r1.2_se, r2.1_se, r2.2_se,
+                   r1.1_CV, r1.2_CV, r2.1_CV, r2.2_CV, 
+                   r1.1_logCV, r1.2_logCV, r2.1_logCV, r2.2_logCV))
+##################################
+## Calculate effect sizes
+##################################
+# Calculate Q10 effect sizes and sampling variances; filter out non-finate values and clean up dataframe a bit
+
[…]

### 2022-04-21 supp/Supplemental Materials and Methods.Rmd
Changed name for pivot longer value

@@
       data_long <- data_wide %>%
-                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
+                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
                     mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()

### 2022-04-21 ms/ms.rmd
Realised that the dataset already had fixed names so removed redundant code here

@@
 #########################
- ## Tree data; also fix up some errors
+ ## Tree data
     tree_data <-  data_long %>%
-                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
-                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full)) %>%
-                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>%
-                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))  %>%
                   group_by(species_full)                                                 %>%

### 2022-04-21 supp/Supplemental Materials and Methods.Rmd
Realised that in long format we also need to make sure that V for each effect size is size by side in a single column. A few ways this can be done but probably most easily understood by ifelse

--- 2022-04-17 supp/Supplemental Materials and Methods.Rmd
@@
       data_long <- data_wide %>%
-                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
-                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
+                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
+                    mutate(V = ifelse(name == "lnRR_Q10_acute_t1", V_lnRR_Q10_acute_t1, 
+                                  ifelse(name == "lnRR_Q10_acute_t2", V_lnRR_Q10_acute_t2, 
+                                  ifelse(name == "lnRR_Q10_acclim", V_lnRR_Q10_acclim, 
+                                  ifelse(name == "lnVR_Q10_acute_t1", V_lnVR_Q10_acute_t1, 
+                                  ifelse(name == "lnVR_Q10_acute_t2", V_lnVR_Q10_acute_t1, 
+                                  ifelse(name == "lnVR_Q10_acclim", V_lnVR_Q10_acclim, 
+                                  ifelse(name == "lnCVR_Q10_acute_t1", V_lnCVR_Q10_acute_t1, 
+                                  ifelse(name == "lnCVR_Q10_acute_t2", V_lnCVR_Q10_acute_t2,V_lnCVR_Q10_acclim)))))))),
+                           type = ifelse(grepl("acute", name), "acute", "acclim"),
+                           obs = 1:n()) %>% dplyr::select(!grep("V_", colnames(.))) %>% data.frame()
 

### 2022-04-21 R/1_data_process.R

@@ -77,7 +77,16 @@ write.csv(data_wide, file = "./output/data/data_final_wide.csv", row.names = FAL
 ################ THIS SHOULD FIX THE DATA_LONG problems
 data_long <- data_wide %>%
   pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
-  mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
+  mutate(V = ifelse(name == "lnRR_Q10_acute_t1", V_lnRR_Q10_acute_t1, 
+                    ifelse(name == "lnRR_Q10_acute_t2", V_lnRR_Q10_acute_t2, 
+                           ifelse(name == "lnRR_Q10_acclim", V_lnRR_Q10_acclim, 
+                                  ifelse(name == "lnVR_Q10_acute_t1", V_lnVR_Q10_acute_t1, 
+                                         ifelse(name == "lnVR_Q10_acute_t2", V_lnVR_Q10_acute_t1, 
+                                                ifelse(name == "lnVR_Q10_acclim", V_lnVR_Q10_acclim, 
+                                                       ifelse(name == "lnCVR_Q10_acute_t1", V_lnCVR_Q10_acute_t1, 
+                                                              ifelse(name == "lnCVR_Q10_acute_t2", V_lnCVR_Q10_acute_t2,V_lnCVR_Q10_acclim)))))))),
+         type = ifelse(grepl("acute", name), "acute", "acclim"),
+         obs = 1:n()) %>% dplyr::select(!grep("V_", colnames(.))) %>% data.frame()
 
 # Checks:
 dim(data_long)

### 2022-04-21 ms/ms.rmd
MOre re-writing of methods now that Noble 2022 is published this can be simplified

@@
 
-### *Calculating New $Q_{10}$ Based Effect Sizes and Sampling Variances*
+### *$Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances*
 
 Following @Noble2022 we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
-These effect sizes are essentially similar to the traditional $Q_{10}$,
+These effect sizes are essentially similar to the traditional temperature coeffiecint ($Q_{10}$), but with formal analytical approximations for their sampling variances, allowing us to make use of powerful meta-analytic modelling approaches.
 
 #### *Comparing changes in mean physiological rates*
+
+To compare mean physiological rates we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022] as follows:
+
+$$
+\begin{equation} 
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+(\#eq:lnq10)
+\end{equation} 
+$$
+
+Where, $R_{1}$ is the mean physiological rate of group 1, often a control group, where as $R_{2}$ is the mean physiological rate of group 2 (e.g., a treatment group).
+Log transformation of this ratio makes the effect size normally distributed.
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@hedges1999meta; @laj2011] when the numerator and denomenator are measured at different temperatures.
+This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
+The sampling variance for equation \@ref(eq:lnq10) can be computed as follows (as described in @Noble2022):
+
+$$
+\begin{equation} 
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+  (\#eq:Vlnq10)
+\end{equation} 
+$$
+
+################ OLDER STUFF BELOW
 

### 2022-04-21 ms/ms.rmd
Adding in Ecology Letters csl which I think is a better spot for this paper

@@
 bibliography: refs.bib
-csl: science.csl
+csl: ecology-letters.csl
 output: 
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
 ## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,

### 2022-04-26 ms/ms.rmd
Fixed spelling

@@
 We used data from a previous meta-analysis [@Seebacher2015] and updated Seebacher *et.
-al.* @Seebacher2015's data by extractng data from suitable studies from our own searches that followed the same search protocol.
-More specically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
+al.* @Seebacher2015's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+More specifically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
 We limited our search to articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et.
@@
 Havird *et.
-al.* @Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metbolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
+al.* @Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
 Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et.
@@
 We split the screening of titles and abstracts for the 1,321 papers found in our search among all authors evenly.
-To ensure consistency among authors in title and abstracts that should be included, prior to  screening all authors went through a randomly sleected set of papers together - agreeing on those that were relevant and those that were not based on our inclusion criteria (see below).
-Where any authors were uncertain about whether to include a paper in the sub-sample they screened, we conservatively included the paper for full text screening and dicussed uncertain papers among authors to come to a decison on whether to include the paper.
+To ensure consistency among authors in title and abstracts that should be included, prior to  screening all authors went through a randomly selected set of papers together - agreeing on those that were relevant and those that were not based on our inclusion criteria (see below).
+Where any authors were uncertain about whether to include a paper in the sub-sample they screened, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision on whether to include the paper.
 After title and abstract screening, we were left with a total of 149 papers for full text screening.
@@
 
-We extracted means, standard deviations and sample sizes for physiological rates at the two test tempetatures.
-If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatues experienced by the speceis in question.
+We extracted means, standard deviations and sample sizes for physiological rates at the two test temperatures.
+If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
 We extracted these data from text, tables or figures of a given paper.
@@
 Following @Noble2022 we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
-These effect sizes are essentially similar to the traditional temperature coeffiecint ($Q_{10}$), but with formal analytical approximations for their sampling variances, allowing us to make use of powerful meta-analytic modelling approaches.
+These effect sizes are essentially similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations for their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
 
@@
 Log transformation of this ratio makes the effect size normally distributed.
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@hedges1999meta; @laj2011] when the numerator and denomenator are measured at different temperatures.
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@hedges1999meta; @laj2011] when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
@@
 $$
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denomenator are measured at different temperatures.
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
@@
 Nakagawa *et al* @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variablity between two groups.
-We refer readers to Nakagawa *et al* @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling varaince) as follows:
+Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to Nakagawa *et al* @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
 
@@
 While this is a useful metric, as discussed by Nakagawa *et al* @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
-As such, we can calculate the coefficient of variation, which standardises changes in variance for changes in means as follows:
+As such, we can calculate the coefficient of variation, which standardizes changes in variance for changes in means as follows:
 
@@
 Using the mean, standard deviation and sample size for all acute and aclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For all effect sizes the higher acute or acclimation temperture was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardised to 10&deg;C.
+For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.
 
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exsposure occurs (longer exsposure = better acclimation response) and whether exsposure took place in the wild ("acclimitized") or lab ("acclimated") [@Seebacher2015].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "jeuvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et.
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015].
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et.
 al.* @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.

### 2022-04-26 supp/Supplemental-Materials-and-Methods.Rmd
Update to supp

--- 2022-04-21 supp/Supplemental Materials and Methods.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+knitr::opts_chunk$set(echo = FALSE,  message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
 ## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,

### 2022-04-26 ms/ms.rmd
Remove number of sections. Remove unecessary citation formatting and also finished writing the effect size section

@@
 ---
+title: ""
 author: Daniel W.A. Noble, Fonti Kar, Frank Seebacher, Alex Bush, & Shinichi Nakagawa
@@
 output: 
+  bookdown::word_document2:
+    toc: no
+    toc_depth: 6
+    number_sections: false
+    reference_docx: template.docx
   bookdown::html_document2:
@@
     bibliography: refs.bib
-  bookdown::word_document2:
-    toc: no
-    toc_depth: 6
-    number_sections: true
-    reference_docx: template.docx
 editor_options: 
@@
 We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015] and updated Seebacher *et.
-al.* @Seebacher2015's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We used data from a previous meta-analysis [@Seebacher2015] and updated @Seebacher2015's data by extracting data from suitable studies from our own searches that followed the same search protocol.
 More specifically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
-We limited our search to articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et.
-al.* @Seebacher2015 searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We limited our search to articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015 searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
@@
 Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016].
-We also cross checked papers we found in our searches with a recent paper by Havird *et.
-al.* @Havird2020, which also updates Seebacher *et.
-al.* @Seebacher2015's dataset.
-We included any papers that were missed between our searches and those of Havird *et.
-al.* @Havird2020 from the dates 2013-2017.
-Havird *et.
-al.* @Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et.
-al.* @Seebacher2015's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et.
-al.* @Seebacher2015 dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that Seebacher *et.
-al.* @Seebacher2015 included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
+We also cross checked papers we found in our searches with a recent paper by @Havird2020, which also updates  @Seebacher2015's dataset.
+We included any papers that were missed between our searches and those of @Havird2020 from the dates 2013-2017.
+@Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015 dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that @Seebacher2015 included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by Seebacher *et.
-al.* @Seebacher2015 to answer questions on acclimation across ectotherms.
+As such, our database represents the most up-to-date dataset used by @Seebacher2015 to answer questions on acclimation across ectotherms.
 
@@
 
-Where, $R_{1}$ is the mean physiological rate of group 1, often a control group, where as $R_{2}$ is the mean physiological rate of group 2 (e.g., a treatment group).
+Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured.
 Log transformation of this ratio makes the effect size normally distributed.
@@
 
-################ OLDER STUFF BELOW
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations and $N_{1}$ and $N_{2}$ are the sample sizes in group 1 and 2, respectively.
 
-Prior to showing how the relevant $Q_{10}$ effect size can be calculated it can be helpful to understand its similarities to *lnRR*.
-The *lnRR* described by Hedges *et al.* @hedges1999meta and extended by Lajeunesse @laj2011 and can be calculated as follows:
-
-$$
-\begin{equation} 
-  \begin{aligned}
-  lnRR = ln\left ( \frac{X_{1}}{X_{2}}\right )
-  \end{aligned}
-  (\#eq:lnRR)
-\end{equation} 
-$$
-
-$$
-\begin{equation} 
-  s_{lnRR} = \left ( \frac{SD_{1}^2}{N_{1}X_{1}^2}\right ) + \left ( \frac{SD_{2}^2}{N_{2}X_{2}^2}\right )
-  (\#eq:slnRR)
-\end{equation} 
-$$
-In equation \@ref(eq:lnRR), $X_{1}$ is the mean of group 1, often a control group, where as $X_{2}$ is the mean of group 2 (e.g., a treatment group).
-The mean of $X_{i}$ for group *i* can be any measurement type (e.g.
-a physiological rate, mass etc) so long as the measurement variable is ratio scale.
-Log transformation of this ratio makes the effect size normally distributed.
-Equation \@ref(eq:slnRR) is the analytical solution for *lnRR*'s sampling variance where, $SD_{1}^2$ and $SD_{2}^2$ is the variance in group 1 and 2, respectively and $N_{1}$ and $N_{2}$ is the sample size in group 1 and 2.
-
-The equations for *lnRR* and its sampling variance allow us to easily extend this to $Q_{10}$ based effect sizes. Recall that $Q_{10}$ is described as follows:
-
-$$
-\begin{equation} 
-  Q_{10} = \left( \frac{R_{2}}{R_{1}} \right)^{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-  (\#eq:q10)
-\end{equation} 
-$$
-Here, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured.
-Log transformation of equation \@ref(eq:q10) leads to the following log transformed $Q_{10}$:
-
-$$
-\begin{equation} 
-  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-(\#eq:lnq10)
-\end{equation} 
-$$
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to lnRR when the numerator and denominator are measured at different temperatures.
-This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
-Here, we will refer to this as the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$.
-Recognition of this equivalence means that we can easily calculate the sampling variance for equation \@ref(eq:lnq10) as follows:
-
-$$
-\begin{equation} 
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-  (\#eq:Vlnq10)
-\end{equation} 
-$$
-
-#### *Comparing changes in physiological rate variability*
-
-Nakagawa *et al* @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-Like *lnRR*, *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to Nakagawa *et al* @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+#### *Comparing variance physiological rates*
+ @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
 
@@
 Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
-While this is a useful metric, as discussed by Nakagawa *et al* @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
-As such, we can calculate the coefficient of variation, which standardizes changes in variance for changes in means as follows:
+While this is a useful metric, as discussed by @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
 
@@
 These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et.
-al.* @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
-Physiological rates measures varied widely across the studies but could generally be groups into discrete trait categories @Seebacher2015.
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
+Physiological rates measures varied widely across the studies but could generally be groups into discrete trait categories [@Seebacher2015].
 As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of

### 2022-04-26 ms/ms.rmd
Add phylogenetic tree

@@
 ##################################
-  # Have a look at species in data and tree. Note that the data2 object excluded all Inf values, which means that species may be lost in the process. So, tree would need to be pruned down
-  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
-
-species_drop <- tree_checks(data_long, tree, dataCol = "species_full", type = "checks")$Species_InTree_But_NotData # Gra list of species in tree misisng from data for pruning
-
-# Prune tree
-tree2 <- drop.tip(tree, species_drop)
+  # Have a look at species in data and tree. 
+  tree <- tree_checks(data_long, tree, dataCol = "species_full", type = "prune")
 
 # Check that taxa dropped
-tree_checks(data_long, tree2, dataCol = "species_full", type = "checks")
+  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
 
@@
 
-        tree_p1 <- compute.brlen(tree2, method = "Grafen", power = 1)
-      tree_p0.5 <- compute.brlen(tree2, method = "Grafen", power = 0.5)
+        tree_p1 <- compute.brlen(tree, method = "Grafen", power = 1)
+      tree_p0.5 <- compute.brlen(tree, method = "Grafen", power = 0.5)
 
@@
 ## Results
+
+```{r phylogeny, fig.cap="Phylogenetic tree"}
+ # Map data to tree. Just one variable for now
+      d <- ggtree(tree, layout="circular") %<+% tree_data
+
+      # Plot the tree
+      scales1 <- c("#053061", "#D1E5F0", "#67001F")
+      scales2 <- c("#053061", "#E7E0DB", "#67001F")
+      p1 <- d + 
+            #geom_tiplab(size=2, offset = 0.5) + 
+            geom_tippoint(aes(color=habitat), size = 2) +
+            labs(color = "Habitat") + 
+            scale_colour_manual(values = scales1)
+
+      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
+      matrix_data <- as.data.frame(data_wide %>%
+                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
+                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
+                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
+                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
+                  mutate(trait_category = ifelse(trait_category %in% 
+                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
+                  group_by(species_full, trait_category)   %>% 
+                  summarise(n = n())                       %>% 
+                  spread(trait_category, n, fill = 0))
+
+      row.names(matrix_data) <- matrix_data$species_full
+      matrix_data <- matrix_data[,c(2:8)]
+
+      colnames(matrix_data)[c(1,3,6)] <- c("Antioxidants", "Metabolic Enzymes", "Other")
+
+      # Plot a heatmap of N for each trait around the phylogeny.
+      gheatmap(p1, data.matrix(matrix_data), offset = 1,  
+               colnames_position="top", legend_title = "N", 
+               colnames_angle=90, colnames_offset_y = 1, 
+               hjust=0, font.size=2.5) + 
+        scale_fill_viridis(alpha = 0.6) 
+```

### 2022-04-26 ms/ms.rmd
Modify Labels

@@
       gheatmap(p1, data.matrix(matrix_data), offset = 1,  
-               colnames_position="top", legend_title = "N", 
-               colnames_angle=90, colnames_offset_y = 1, 
-               hjust=0, font.size=2.5) + 
-        scale_fill_viridis(alpha = 0.6) 
+               colnames_position="bottom", legend_title = "N", 
+               colnames_angle=90, colnames_offset_y = 2, 
+               hjust=0, font.size=2.5, width = 0.25, colnames = FALSE) + 
+        scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
 ```

### 2022-04-26 ms/ms.rmd
Add rlang

@@
 ##################################
-    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp)
+    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp, rlang)
 

### 2022-04-27 ms/ms.rmd
refs
Switched data around phylogeny

@@
 
+      # Alternatively, summarise total effect sizes per species for acute and acclimation
+      matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
+                    mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
+                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
+                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
+                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
+                      group_by(species_full, type) %>% 
+                      summarise(n = n()) %>% 
+                      spread(type, n, fill = 0) %>% data.frame()
+                     # mutate(acclim = as.character(cut(acclim, breaks = c(0,15, 20, 25, 30, 40, 50))),
+                      #        acute = as.character(cut(acute, breaks = c(0,15, 20, 25, 30, 40, 50))))
+
+      row.names(matrix_data2) <- matrix_data2$species_full
+      matrix_data2 <- matrix_data2[,2:3]
+
       # Plot a heatmap of N for each trait around the phylogeny.
-      gheatmap(p1, data.matrix(matrix_data), offset = 1,  
+      gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
                colnames_position="bottom", legend_title = "N", 
-               colnames_angle=90, colnames_offset_y = 2, 
-               hjust=0, font.size=2.5, width = 0.25, colnames = FALSE) + 
+               colnames_angle=45, colnames_offset_y = 0, 
+               hjust=0, font.size=2.5, width = 0.35) + 
         scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
 ```
+
+## References

### 2022-04-27 ms/ms.rmd
Not sure why there are NA in habitat of phylogeny ployt when all habitat is filled our for each species. All dataframes match in size and species so this is ruled out

@@
       matrix_data <- as.data.frame(data_wide %>%
-                  mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
-                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
-                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
-                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
                   mutate(trait_category = ifelse(trait_category %in% 
@@
       # Plot a heatmap of N for each trait around the phylogeny.
-      gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
+   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
                colnames_position="bottom", legend_title = "N", 
-               colnames_angle=45, colnames_offset_y = 0, 
-               hjust=0, font.size=2.5, width = 0.35) + 
+               colnames_angle=-45, colnames_offset_y = 1,  colnames_offset_x = -0.5,
+               hjust=0, font.size=3, width = 0.35) + 
         scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
+   phylo
 ```

### 2022-04-27 ms/ms.rmd
Fixed habitat NA

@@
 ##################################
-    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp, rlang)
+    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp, rlang, ggnewscale)
 
@@
                   distinct(species_full, habitat, n)
+    #rownames(tree_data) <- tree_data$species_full
+    #tree_data <- tree_data[,2:3]
 
@@
 ### *Meta-Analysis*
+
+@Guangchuang2017
 ### *Sensitivity Analyses*
@@
       matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
-                    mutate(species_full = gsub("Chinemys reevesii", "Mauremys reevesii", species_full)) %>% 
-                  mutate(species_full = gsub("Enithares sp", "Enithares ciliata", species_full))      %>%
-                  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))       %>%
-                  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))               %>%
                       group_by(species_full, type) %>% 
@@
    phylo
+
 ```

### 2022-04-27 ms/ms.rmd
Deleting node code causing problems with not mapping habitate to phylogeny. This is not needed for proper mapping of data

@@
       tree$tip.label <- gsub("Enithares sp", "Enithares ciliata", tree$tip.label)
-
-      ## Create nodes and add to data so detailed can be mapped
-          tree_data$node <- NA
-                 tipnode <- seq_along(tree$tip.label)
-          names(tipnode) <- tree$tip.label
-          tree_data$node <- tipnode[tree_data$species_full] ## convert the tip label to tip node number
-                       i <- is.na(tree_data$node)
-       tree_data$node[i] <- tree_data$species_full[i] ## fill in internal node number
-          tree_data$node <- as.integer(tree_data$node)
 

### 2022-04-27 ms/ms.rmd
Adjustements to phylogeny

@@
       p1 <- d + 
-            #geom_tiplab(size=2, offset = 0.5) + 
+            geom_tiplab(size=2, offset = 10) + 
             geom_tippoint(aes(color=habitat), size = 2) +
@@
       # Plot a heatmap of N for each trait around the phylogeny.
-   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 1,  
+   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  
                colnames_position="bottom", legend_title = "N", 
-               colnames_angle=-45, colnames_offset_y = 1,  colnames_offset_x = -0.5,
+               colnames_angle=360, colnames_offset_y = 0, colnames_offset_x = -1.5, 
                hjust=0, font.size=3, width = 0.35) + 

### 2022-04-27 ms/ms.rmd
Fixed phylogeny and spit out the tree as png

@@
 @Guangchuang2017
+\
 ### *Sensitivity Analyses*
@@
 
-```{r phylogeny, fig.cap="Phylogenetic tree"}
+```{r phylogeny, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
  # Map data to tree. Just one variable for now
@@
                 scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
+
    phylo
-
+ggsave(filename = "fig1.png", path = "../output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
 ```

### 2022-04-29 R/1_data_process.R
Remove some unneeded annotaion

@@ -74,7 +74,6 @@ write.csv(data_wide, file = "./output/data/data_final_wide.csv", row.names = FAL
 
 # We want to be able to reorganise the data longitudianlly based on the two acute and acclimation data. Extract the data in chunks
 
-################ THIS SHOULD FIX THE DATA_LONG problems
 data_long <- data_wide %>%
   pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
   mutate(V = ifelse(name == "lnRR_Q10_acute_t1", V_lnRR_Q10_acute_t1, 

### 2022-04-29 R/2_climate_data.R

@@ -1,0 +1,73 @@
+###################################################################################
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#                       ERA5 Reanalysis 1 CLIMATE DATA
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+###################################################################################
+
+# This version doesn't actively download point estimates of temperature. 
+# Instead a NetCDF for ERA5 was downloaded for 1979-present.
+
+# See Word doc: Data/Downloading ERA5 historic climate data.docx
+
+# Note that the data is stored in Kelvin and transformed.
+# 2m surface temperature
+#     scale_factor: 0.00176319797961702
+#     add_offset: 257.703670097788
+# Sea Surface Temperature
+#     scale_factor: 0.00061697729459776
+#     add_offset: 289.46490147229
+
+# Time is recorded in hours since 1900-01-01 00:00:00.0
+
+rm(list=ls())
+library(ncdf4)
+
+geo_data = read.csv("./data/climate_data/Species_LatLong_plusHabitat.csv")
+
+spp  = unique(geo_data$species_full)
+
+for(i in 1:nrow(geo_data)){
+  
+  # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+  # Open NETCDF file
+  ncfname   = paste0("./data/climate_data/ERA5/ERA5_LST_and_SST_1979-present.nc")
+  ERA5      = nc_open(ncfname)
+  dname     = "t2m"
+  lon       = ncvar_get(ERA5, "longitude") # ncvar_get(ERA5.air, "lon")
+  nlon      = length(lon) # number of columns
+  lat       = ncvar_get(ERA5, "latitude") # ncvar_get(ERA5.air, "lat", verbose = F)
+  nlat      = length(lat) # number of rows
+  t         = ncvar_get(ERA5, "time")                 # units: hours since 1900-01-01 00:00:00.0
+  nt        = dim(t)                  # monthly averages
+  # Create a copy of the data as an array in R (which unlike the netcdf, makes
+  # it possible to index multiple locations at once)
[…]

### 2022-04-29 R/2_climate_data.R
climate data file

@@ -49,8 +49,8 @@ for(i in 1:nrow(geo_data)){
   
   # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
   
-  monthly.temp.data = matrix(NA, nrow=nt, ncol=nrow(spXY),
-                             dimnames=list(c(1:nt), sdat$Fid))
+  monthly.temp.data = matrix(NA, nrow=nt, ncol=nrow(geo_data),
+                             dimnames=list(c(1:nt)))
   for(j in 1:nt){ monthly.temp.data[j,] = X[,,j][spXY] }
   
   # Annual mean and SD

### 2022-04-29 R/2_climate_data.R
Trying to understand what this object actually is structured like. long, lat and then tempetrature but because lon/lat is so course matching with our coordinates seems not possible

@@ -51,6 +51,11 @@ for(i in 1:nrow(geo_data)){
   
   monthly.temp.data = matrix(NA, nrow=nt, ncol=nrow(geo_data),
                              dimnames=list(c(1:nt)))
+  # This is now an array that is formatted as: X[longitude, latitude, temp in Kelvin]
+  t <- with(na.omit(geo_data), X[long, lat, ])
+  
+  
+  
   for(j in 1:nt){ monthly.temp.data[j,] = X[,,j][spXY] }
   
   # Annual mean and SD

### 2022-04-30 R/2_climate_data.R
Given we are using the coordinates for teh specific location. I think it could be good to use microclima now to get data for the site....

@@ -53,26 +53,59 @@ for(i in 1:nrow(geo_data)){
                              dimnames=list(c(1:nt)))
   # This is now an array that is formatted as: X[longitude, latitude, temp in Kelvin]
   t <- with(na.omit(geo_data), X[long, lat, ])
+
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+#         Microclimate
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+
+# Microclimate paper:
+# Kearney et al. 2019 "A method for computing hourly, historical, terrain-corrected microclimate anywhere on earth"
+# https://doi.org/10.1111/2041-210X.13330
+
+  devtools::install_github("ilyamaclean/microclima")  
   
+# N.B. The function automatically assumes the raster should be 200 cells by 200 cells,
+#      so for a 30m resolution grid this is 6km across.
+#      I've reduced this to 50 cells across (1.5km x 1.5km) to make it faster
+
+# First remove missing lat and long
+  geo_data <- geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
   
+# Now we need the elevation at the point. Which we get using a loop because it can only take a single lat long coord at a time.
+  lat <- c()
+  for(i in 1:dim(geo_data)[1]){
+    elevation = microclima::get_dem(lat  = geo_data$lat[i], long = geo_data$long[i], resolution = 30, xdims = 50, ydims = 50)
+    lat <- c(elevation, lat)
+  }
   
-  for(j in 1:nt){ monthly.temp.data[j,] = X[,,j][spXY] }
+# plot(r)
+
+s1 = Sys.time()
+
+# And... we'll cycle through microclimate generation one year at a time between 1981 and 2020
+for(Y in c(1981:2020)){
   
-  # Annual mean and SD
-  annual.temp.means = aggregate(monthly.temp.data, by=list(format(t.Date,"%Y")),mean,na.rm=T)
-  annual.temp.sd    = aggregate(monthly.temp.data, by=list(format(t.Date,"%Y")),sd,na.rm=T)
+  temps = microclima::runauto(r, dstart = paste0("01/01/",Y,")"),  # start date
+                              dfinish   = paste0("31/12/",Y,")"),  # end date
[…]

### 2022-04-30 R/2_climate_data.R
change

@@ -83,9 +83,9 @@ for(i in 1:nrow(geo_data)){
 s1 = Sys.time()
 
 # And... we'll cycle through microclimate generation one year at a time between 1981 and 2020
-for(Y in c(1981:2020)){
+for(Y in c(1981:2022)){
   
-  temps = microclima::runauto(r, dstart = paste0("01/01/",Y,")"),  # start date
+  temps = microclima::runauto(lat, dstart = paste0("01/01/",Y,")"),  # start date
                               dfinish   = paste0("31/12/",Y,")"),  # end date
                               hgt = 0.1, l = NA, x = NA,
                               habitat = as.character(habitats$descriptor[gbif$Habitat[S]]),

### 2022-04-30 R/2_climate_data.R
Added elevation data and also rewrote code to bring in or rerun if needed as it takes too long to get elevation data for each lat long

@@ -72,12 +72,18 @@ for(i in 1:nrow(geo_data)){
   geo_data <- geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
   
 # Now we need the elevation at the point. Which we get using a loop because it can only take a single lat long coord at a time.
+run = FALSE
+if(run){
   lat <- c()
   for(i in 1:dim(geo_data)[1]){
     elevation = microclima::get_dem(lat  = geo_data$lat[i], long = geo_data$long[i], resolution = 30, xdims = 50, ydims = 50)
     lat <- c(elevation, lat)
   }
   
+saveRDS(lat, "./output/climate_data/elevation")
+} else{
+  elev <- readRDS("./output/climate_data/elevation")
+}
 # plot(r)
 
 s1 = Sys.time()
@@ -85,7 +91,7 @@ s1 = Sys.time()
 # And... we'll cycle through microclimate generation one year at a time between 1981 and 2020
 for(Y in c(1981:2022)){
   
-  temps = microclima::runauto(lat, dstart = paste0("01/01/",Y,")"),  # start date
+  temps = microclima::runauto(elev, dstart = paste0("01/01/",Y,")"),  # start date
                               dfinish   = paste0("31/12/",Y,")"),  # end date
                               hgt = 0.1, l = NA, x = NA,
                               habitat = as.character(habitats$descriptor[gbif$Habitat[S]]),

### 2022-07-12 ms/ms.rmd
Writing
Adding programmed version numbers and correct some errors

@@
 We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@pick2019].
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019].
 We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied.
@@
 #### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-Using the mean, standard deviation and sample size for all acute and aclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+Using the mean, standard deviation and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
 For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator.
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015].
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015].
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
-Physiological rates measures varied widely across the studies but could generally be groups into discrete trait categories [@Seebacher2015].
+Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015].
 As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of
@@
 ### *Meta-Analysis*
+We analysed our data using Bayesian multilevel meta-analytic and meta-regression models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
+`r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan].
+@Guangchuang2017
 
-@Guangchuang2017
-\
 ### *Sensitivity Analyses*

### 2022-07-13 ms/ms.rmd
Writing

@@
 Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015].
-As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of
+As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of 12 trait categories.
+These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
+Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('mito_leak') and oxidation ('mito_oxidation') as well as antioxidant enzymes ('antiox').
+All other traits not falling within these categories were placed into 'other'.
+
+### *Climate Data*
+
+To understand how climate impacts physiological acclimation abilities we used latitudes and longitudes reported in studies to extract temperature data from terrestrial and aquatic environments.
+Only studies on wild populations were used for climate analyses because temperature data at locations was likely reflective of past climate history.
+Temperature data was extracted using the ERA5 climate model.
+We extracted data over a 30 year period (1958-2022) for each population and species in the data.
 

### 2022-07-15 ms/ms.rmd
Priors
Adding some questions to guide us again

@@
 `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan].
+We included study, species and phylogeny as random effects to account for non-independence and also explore drivers of variation among $lnRR_{Q_{10}}$ estimates.
+
 @Guangchuang2017
@@
 
-## Results
+## *Results*
+
+### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
+### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
+### *Does between-individual variation in acclimation capacities differ across terrestrial and aquatic ectotherms?*
 

### 2022-07-18 ms/ms.rmd
update refs

@@
 Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016].
-We also cross checked papers we found in our searches with a recent paper by @Havird2020, which also updates  @Seebacher2015's dataset.
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020, which also updates  @Seebacher2015's dataset.
 We included any papers that were missed between our searches and those of @Havird2020 from the dates 2013-2017.
@@
 
-To understand how climate impacts physiological acclimation abilities we used latitudes and longitudes reported in studies to extract temperature data from terrestrial and aquatic environments.
+To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
 Only studies on wild populations were used for climate analyses because temperature data at locations was likely reflective of past climate history.
-Temperature data was extracted using the ERA5 climate model.
-We extracted data over a 30 year period (1958-2022) for each population and species in the data.
+Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
+For each population and species in the dataset we extracted a 30 year period (1958-2022) of either surface temperature at 2 meters for terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
 

### 2022-07-18 ms/ms.rmd
Adding summary of climate data

@@
 For each population and species in the dataset we extracted a 30 year period (1958-2022) of either surface temperature at 2 meters for terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
+We chose a 2 meters resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms.
+
+Using thermal time-series data for each location we summarised various metrics of thermal variability across months and years.
+We calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
 
 ### *Meta-Analysis*
-We analysed our data using Bayesian multilevel meta-analytic and meta-regression models in R (vers.
+We analysed our data using Bayesian multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
 `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.

### 2022-07-20 ms/ms.rmd
Change power for tree. ).5 is probably a little too low

@@
         tree_p1 <- compute.brlen(tree, method = "Grafen", power = 1)
-      tree_p0.5 <- compute.brlen(tree, method = "Grafen", power = 0.5)
+      tree_p0.7 <- compute.brlen(tree, method = "Grafen", power = 0.7) # Probably most sensible power
 
@@
         tree_p1$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
-      tree_p0.5$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
+      tree_p0.7$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
 ```

### 2022-11-20 ms/ms.rmd
spellig error fix

@@
 Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
-For each population and species in the dataset we extracted a 30 year period (1958-2022) of either surface temperature at 2 meters for terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
+For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
 We chose a 2 meters resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms.

### 2022-11-20 ms.rmd
Changed path names

--- 2022-11-20 ms/ms.rmd
@@
 date: "`r Sys.Date()`"
-bibliography: refs.bib
-csl: ecology-letters.csl
+bibliography: ./bib/refs.bib
+csl: ./bib/ecology-letters.csl
 output: 
@@
     number_sections: false
-    reference_docx: template.docx
+    reference_docx: ./bib/template.docx
   bookdown::html_document2:
@@
 ##################################
-    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp, rlang, ggnewscale)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp)
 
@@
     # loading functions
-    source("../R/functions.R")
+    source("./R/functions.R")
 
@@
 ##########################
-data_wide <- read.csv("../output/data/data_final_wide.csv")
-data_long <- read.csv("../output/data/data_final_long.csv")
+data_wide <- read.csv("./output/data/data_final_wide.csv")
+data_long <- read.csv("./output/data/data_final_long.csv")
 
@@
  ## Load the phylogenetic tree
-                tree <- read.tree("../tree/tree_binary_SN_Q10.tre")   
+                tree <- read.tree("./tree/tree_binary_SN_Q10.tre")   
       tree$tip.label <- gsub("_", " ", tree$tip.label)

### 2022-11-20 ms.rmd
Starting to add in the models. Going to use metafor so that I can make plots faster ;)

@@
 ### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
+
+```{r acclimation_cap}
+########################
+### Differences in acclimation capacity between terrestrial, aquatic and marine
+########################
+phylo_cor <- vcv(tree_p0.7, cor = TRUE)
+## lnRR first
+lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name)) %>% mutate(spp = species_full)
+
+model1.1 <- metafor::rma.mv(effect_size, V = V, 
+                            random = list(~1 + type | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
+
+```
+
 ### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*

### 2022-11-20 ms.rmd
Need tp exclude data where V = 0, and also NA because there are no data to calculate

@@
 phylo_cor <- vcv(tree_p0.7, cor = TRUE)
-## lnRR first
-lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name)) %>% mutate(spp = species_full)
 
-model1.1 <- metafor::rma.mv(effect_size, V = V, 
+#############
+## lnRRQ10
+#############
+
+# Subset the data
+lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% mutate(spp = species_full)
+
+# Intercept only model. 
+model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
                             random = list(~1 + type | record_num,

### 2022-11-20 ms.rmd
orchard

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd)
 
@@
                             R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
+model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
+orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, xlab = "lnRRQ10")
 

### 2022-11-20 ms.rmd
Code for models. Now controls for acclimation duration, centered. All models updated

@@
 # Subset the data
-lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% mutate(spp = species_full)
+lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+hist(lnRRQ10_data$V)
+
+# Studies with big V, why? Check N
+lnRRQ10_data %>% filter(V >= 2)
 
 # Intercept only model. 
-model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
+model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
                             random = list(~1 + type | record_num,
@@
 model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
-orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, xlab = "lnRRQ10")
+
+p1.1 <- orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, 
+                              xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45)
+
+# Save model1.1
+saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
+
+model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
+                            random = list(~1 + type | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
+model1.2_rob <- robust(model1.2, cluster = lnRRQ10_data$record_num)
+
+# Save model1.2
+saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
+
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical")
+
+p1.2 <- p1.2 + geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+                geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+               geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+                   annotate("text", x = 1, y = 2.50, 
+                            label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), " [", round(model1.2$ci.lb[3], 2)," - ", round(model1.2$ci.ub[3], 2), "] ", round((model1.2$b[3] / model1.2$b[1]*100), 2), "%")), hjust = 0)
 

### 2022-11-21 ms.rmd
Adding in some rerun false statements

--- 2022-11-20 ms.rmd
@@
 # Subset the data
-lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% mutate(spp = species_full)
+lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+hist(lnRRQ10_data$V)
+
+# Studies with big V, why? Check N
+lnRRQ10_data %>% filter(V >= 2)
 
 # Intercept only model. 
-model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
+rerun = FALSE
+if(rerun){
+  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
+                              random = list(~1 | record_num,
+                                              ~1 | species_full,
+                                              ~1 | spp,
+                                              ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+  # Save model1.1
+  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
+} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}
+
+# Robust variance estimation
+model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
+
+# OrchaRd plot of model 1.1
+p1.1 <- orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, 
+                              xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45)
+
+if(rerun){
+  # More realistic model with 
+  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                               random = list(~1 + type | record_num,
@@
                                               ~1 | obs),
-                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
-model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
-orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, xlab = "lnRRQ10")
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  # Save model1.2
+  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
+} else{
+  model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
+}
+
+# Robust variance
+model1.2_rob <- robust(model1.2, cluster = lnRRQ10_data$record_num)
+
+# Orchard plot
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical") + 
+  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+                geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+               geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+                   annotate("text", x = 1, y = 2.50, 
+                            label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), " [", round(model1.2$ci.lb[3], 2)," - ", round(model1.2$ci.ub[3], 2), "] ", round((model1.2$b[3] / model1.2$b[1]*100), 2), "%")), hjust = 0)
 

### 2022-11-21 R/1_data_process.R
Fixed path

@@ -91,4 +91,4 @@ data_long <- data_wide %>%
 dim(data_long)
 with(data_long, table(type)) # Acute should be 2x larger
 with(data_long, table(type, trait_category))
-write.csv(data_long, file = "../output/data/data_final_long.csv", row.names = FALSE)
+write.csv(data_long, file = "./output/data/data_final_long.csv", row.names = FALSE)

### 2022-11-21 ms.rmd
Update on rerun

@@
 # Intercept only model. 
-rerun = FALSE
+rerun = TRUE
 if(rerun){

### 2022-11-21 ms.rmd
Adding some Bayes models as I can't stand bloody contrasts

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp)
 
@@
 data_long <- read.csv("./output/data/data_final_long.csv")
+
+data_long2 <- data_long %>% mutate(type = factor(type, levels = c("acute", "acclim")))
 
@@
 phylo_cor <- vcv(tree_p0.7, cor = TRUE)
+A <- vcv(tree_p0.7, cor = FALSE) # For bayes
 
@@
 # Subset the data
-lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
@@
   model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 + type | record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,
@@
 
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.95), chains = 4, iter = 2000, warmup = 1000, cores = 5, data = lnRRQ10_data)
+
   # Save model1.2
   saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
+  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
+
   } else{
@@
 model1.2_rob <- robust(model1.2, cluster = lnRRQ10_data$record_num)
+
+summary(glht(model1.2, linfct=rbind(c(-1,0,1,0,0,0,0), c(1,0,1,-1,0,1,0)), test=adjusted("none")))
 
@@
                             arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-                   annotate("text", x = 1, y = 2.50, 
-                            label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), " [", round(model1.2$ci.lb[3], 2)," - ", round(model1.2$ci.ub[3], 2), "] ", round((model1.2$b[3] / model1.2$b[1]*100), 2), "%")), hjust = 0)
+                   annotate("text", x = 1, y = 2.10, 
+                            label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
+                   annotate("text", x = 1.01, y = 4.60, 
+                            label =paste0(round((model1.2$b[3] / model1.2$b[1]*100), 2), "%"), hjust = 0) + labs(shape = "Type") +
+   geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
+                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
+      annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)
 

### 2022-11-21 ms.rmd
Fixed up Baysian model so it performs better

@@
 
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.95), chains = 4, iter = 2000, warmup = 1000, cores = 5, data = lnRRQ10_data)
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
 

### 2022-11-21 ms.rmd
Ditch contrasts
extracting posteriors

@@
   model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
+  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
 }
@@
 
-summary(glht(model1.2, linfct=rbind(c(-1,0,1,0,0,0,0), c(1,0,1,-1,0,1,0)), test=adjusted("none")))
+## Contrasts
+posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
+f_acute  <- posteriors_1.2[,"b_Intercept"] 
+f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
 
 # Orchard plot
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") +
+  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") + 

### 2022-11-22 R/functions.R
added pmcmc function

@@ -94,7 +94,12 @@ se_to_sd <- function(se, n){
 }
 
 
-
+## pMCMC Function
+# Calculates the, p-value or pMCMC value for a posterior distribution
+# x The vector for the posterior distribution. Note that this will test the null hypothesis that the parameter of interest is significantly different from 0. 
+pmcmc <- function(x){
+  2*(1 - max(table(x<0) / length(x)))
+}
 
 
 #Tree checks function

### 2022-11-22 ms.rmd
Added new model that also deals with trait category

@@
 ########################
-phylo_cor <- vcv(tree_p0.7, cor = TRUE)
-A <- vcv(tree_p0.7, cor = FALSE) # For bayes
 
@@
 
+# Check and prune tree
+tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor <- vcv(tree_lnrr, cor = TRUE)
+        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
+
 # Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
@@
 # Intercept only model. 
-rerun = TRUE
+rerun = FALSE
 if(rerun){
@@
 f_acute  <- posteriors_1.2[,"b_Intercept"] 
+pmcmc(f_acute)
 f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
+m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
+m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
+t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
+t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
+
+# R2
+fix <- var(predict(model1.2_bayes)[,"Estimate"])
+r2_ml(model1.2)
 
 # Orchard plot
+results1.2 <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)
+
 p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") +
@@
   annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)
+
+ if(rerun){
+  # More realistic model with 
+  model1.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + habitat + type:habitat + trait_category:habitat:type + trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+   model1.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+
+  # Save model1.2
+  saveRDS(model1.3, file = "./output/models/lnRRQ10_1.3")
+  saveRDS(model1.3_bayes, file = "./output/models/lnRRQ10_1.3_bayes")
+
+  } else{
+  model1.3 <- readRDS("./output/models/lnRRQ10_1.3")
+  model1.3_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes")
+}
 

### 2022-11-23 ms.rmd
Add orchard plot
small update. orchard not working with complex model. grid issues so problems with emmeans

@@
 
+orchard_plot(model1.3, mod = "trait_category",  group = "record_num",  data = lnRRQ10_data)
+
+orchard_plot(model1.3, mod = "trait_category", at = list(type = c("acute", "acclim"), c_accl_time = 0, habitat = "m"), by = "type",  group = "record_num", weights = "prop", data = lnRRQ10_data, xlab = "lnRRQ10")
 ```

### 2022-11-23 ms.rmd
Running mod 1.3 Bayes

@@
 
-   model1.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+   model1.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + habitat + type:habitat + trait_category:habitat:type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
 

### 2022-11-25 ms.rmd
Adding some indicators for models to clean up

@@
 
+###################################
+# Organise the data and prune tree
+###################################
 # Subset the data
@@
 
+#############################
 # Intercept only model. 
+#############################
 rerun = FALSE
@@
                               xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45)
+
+#################################################
+# Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+#################################################
 
@@
 
+####################################################
+# Model 1.3's: Trait type varied by acclimation type
+# but data is seperated by habitat to simplify
+####################################################
  if(rerun){
+  # Filter to different habitats
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m")
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f")
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")
+
+   # Prune tree
+   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
    # More realistic model with 
-  model1.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + habitat + type:habitat + trait_category:habitat:type + trait_category, V = V, 
+  model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                               random = list(~1 | record_num,
@@
                               R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
+                              test = "t", data = lnRRQ10_data_m)
 
@@
 
-orchard_plot(model1.3, mod = "trait_category", at = list(type = c("acute", "acclim"), c_accl_time = 0, habitat = "m"), by = "type",  group = "record_num", weights = "prop", data = lnRRQ10_data, xlab = "lnRRQ10")
+orchard_plot(model1.3, mod = "trait_category", at = list(type = c("acute", "acclim"), habitat = c("m")),  group = "record_num", weights = "prop", data = lnRRQ10_data, xlab = "lnRRQ10")
+
+lnRRQ10_data %>% group_by(habitat, type, trait_category) %>% summarise(n = n()) %>% data.frame()
 ```

### 2022-11-25 ms.rmd
Separate out fig

@@
 #############################
-# Intercept only model. 
+# Model 1.1: Intercept only model. 
 #############################
@@
 #################################################
-# Model controlling for acclimation time, 
+# Model 1.2: Model controlling for acclimation time, 
 # type and habitat assuming type can vary by habitat
@@
 
-# Robust variance
-model1.2_rob <- robust(model1.2, cluster = lnRRQ10_data$record_num)
-
-## Contrasts
+#################################
+## Model 1.2: Bayesian Contrasts
+#################################
 posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
-f_acute  <- posteriors_1.2[,"b_Intercept"] 
-pmcmc(f_acute)
+f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
 f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
@@
 results1.2 <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)
-
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") +
-  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-  theme(legend.direction = "vertical") + 
-  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
-                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
-                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
-                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-annotate("text", x = 1, y = 2.10, 
-         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
-annotate("text", x = 1.01, y = 4.60, 
-         label =paste0(round((model1.2$b[3] / model1.2$b[1]*100), 2), "%"), hjust = 0) + labs(shape = "Type") +
-  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
-                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
-  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)
 
@@
 lnRRQ10_data %>% group_by(habitat, type, trait_category) %>% summarise(n = n()) %>% data.frame()
+```
+
+```{r, fig1, fig.align='center', fig.cap= "Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments"}
+
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") +
+  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical") + 
+  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
+                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
+annotate("text", x = 1, y = 2.10, 
+         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
+annotate("text", x = 1.01, y = 4.60, 
+         label =paste0(round((model1.2$b[3] / model1.2$b[1]*100), 2), "%"), hjust = 0) + labs(shape = "Type") +
+  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
+                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
+  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)
+  p1
 ```

### 2022-11-25 ms.rmd
Adding habitat models across traits

@@
 
-   # More realistic model with 
+   # cor matrices
+   m_phylo <- vcv(tree_m, corr = TRUE)
+       A_m <- vcv(tree_m, corr = FALSE)
+   f_phylo <- vcv(tree_f, corr = TRUE)
+       A_f <- vcv(tree_f, corr = FALSE)
+   t_phylo <- vcv(tree_t, corr = TRUE)
+       A_t <- vcv(tree_t, corr = FALSE)
+
+   # More realistic model with traits in marine species
   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              R = list(species_full = m_phylo), dfs = "contain", 
                               test = "t", data = lnRRQ10_data_m)
 
-   model1.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + habitat + type:habitat + trait_category:habitat:type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) + (1|obs), data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_m)
 
-  # Save model1.2
-  saveRDS(model1.3, file = "./output/models/lnRRQ10_1.3")
-  saveRDS(model1.3_bayes, file = "./output/models/lnRRQ10_1.3_bayes")
+    # More realistic model with traits in freshwater species
+  model1.3_f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full =f_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_f)
+
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|obs), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_f)
+
+    # More realistic model with traits in terrestrial species
+  model1.3_t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full =t_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_t)
+
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1|obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
+
+  # Save models
+  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
+  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
+  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
+  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
+  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
+  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")
 
   } else{
-  model1.3 <- readRDS("./output/models/lnRRQ10_1.3")
-  model1.3_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes")
+        model1.3_m <- readRDS("./output/models/lnRRQ10_1.3m")
+  model1.3_m_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_m")
+        model1.3_f <- readRDS("./output/models/lnRRQ10_1.3f")
+  model1.3_f_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_f")
+        model1.3_t <- readRDS("./output/models/lnRRQ10_1.3t")
+  model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
 }
@@
 
-orchard_plot(model1.3, mod = "trait_category", at = list(type = c("acute", "acclim"), habitat = c("m")),  group = "record_num", weights = "prop", data = lnRRQ10_data, xlab = "lnRRQ10")
+orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = "lnRRQ10", angle = 45)
 

### 2022-11-25 ms.rmd
code updates

@@
 
-orchard_plot(model1.3, mod = "trait_category",  group = "record_num",  data = lnRRQ10_data)
-
-orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = "lnRRQ10", angle = 45)
-
-lnRRQ10_data %>% group_by(habitat, type, trait_category) %>% summarise(n = n()) %>% data.frame()
 ```
@@
   p1
+```
+
+```{r, fig2, fig.align='center', fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
+
+orchard_plot(model1.3, mod = "trait_category",  group = "record_num",  data = lnRRQ10_data)
+
+orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = "lnRRQ10", angle = 45)
+
+lnRRQ10_data %>% group_by(habitat, type, trait_category) %>% summarise(n = n()) %>% data.frame()
+
 ```

### 2022-11-26 ms.rmd
clean

@@
 #############
-
 ###################################

### 2022-11-27 ms.rmd
Added in Bayesian calculatikons and added contrasts to plots. Finished p1.2

@@
 
+# % change in acclimation
+p_change_f <- ((f_acclim - f_acute) / f_acute); quantile(p_change_f, c(0.025, 0.975))
+p_change_m <- ((m_acclim - m_acute) / m_acute); quantile(p_change_m, c(0.025, 0.975))
+p_change_t <- ((t_acclim - t_acute) / t_acute); quantile(p_change_t, c(0.025, 0.975))
+
 # R2
@@
                             arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
-  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0)
-  p1
+  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0) +
+
+  annotate("text", x = 2, y = 2.10, 
+         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0) +
+annotate("text", x = 2.01, y = 4.60, 
+         label =paste0(round(mean(p_change_m)*100, 2), "%"), hjust = 0) + labs(shape = "Type") +
+  geom_segment(aes(x = 1.92, y = 5.6, xend = 2.07, yend = 5.6), 
+                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
+  annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0) +
+
+  annotate("text", x = 3, y = 2.10, 
+         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0) +
+annotate("text", x = 3.01, y = 4.60, 
+         label =paste0(round(mean(p_change_t)*100, 2), "%"), hjust = 0) + labs(shape = "Type") +
+  geom_segment(aes(x = 2.92, y = 5.6, xend = 3.07, yend = 5.6), 
+                            arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0)
+
+  p1.2
 ```

### 2022-11-27 ms.rmd
Adding in change on the converted q10 scale though

@@
 
+# But this is the % change on the log scale. We can also see what the Q10 change is..NEED TO BE CHECKED CAREFULLY
+f_q10 <-exp((f_acclim - f_acute)-1); mean(f_q10); quantile(f_q10, c(0.025, 0.975))
+m_q10 <-exp((m_acclim - m_acute)-1); mean(m_q10); quantile(m_q10, c(0.025, 0.975))
+t_q10 <-exp((t_acclim - t_acute)-1); mean(t_q10); quantile(t_q10, c(0.025, 0.975))
+
 # R2

### 2022-11-30 ms.rmd
Adding CVR models. Need to run VR too, but CVR for now

@@
 ```{r acclimation_cap}
-########################
-### Differences in acclimation capacity between terrestrial, aquatic and marine
-########################
-
 #############
@@
 
+```{r}
+#############
+## lnCVRQ10
+#############
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Check and prune tree
+  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
+          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
+
+# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+  hist(lnCVRQ10_data$V)
+
+# Studies with big V, why? Check N
+  lnCVRQ10_data %>% filter(V >= 2)
+
+##################################
+# Model 2.1: Intercept only model.
+# Used for heterogeneity analysis
+##################################
+rerun = TRUE
+if(rerun){
+  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data) 
+  # Save model1.1
+  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
+} else{ model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")}
+
+```
+
 ```{r, fig1, fig.align='center', fig.cap= "Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments"}

### 2022-12-01 ms.rmd
Organisaing better and adding in some more complete models

--- 2022-11-27 ms.rmd
@@
 ```{r acclimation_cap}
-########################
-### Differences in acclimation capacity between terrestrial, aquatic and marine
-########################
-
 #############
-## lnRRQ10
+## lnRRQ10 ##
 #############
-###################################
+##################################################
 # Organise the data and prune tree
-###################################
+##################################################
 # Subset the data
@@
 
-#############################
+##################################################
 # Model 1.1: Intercept only model. 
-#############################
-rerun = FALSE
+##################################################
+rerun = TRUE
 if(rerun){
-  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
+  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                               random = list(~1 | record_num,
@@
 
-# Robust variance estimation
-model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
-
-# OrchaRd plot of model 1.1
-p1.1 <- orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, 
-                              xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45)
-
-#################################################
+###################################################
 # Model 1.2: Model controlling for acclimation time, 
 # type and habitat assuming type can vary by habitat
-#################################################
+###################################################
 
@@
 
-#################################
+####################################################
 ## Model 1.2: Bayesian Contrasts
-#################################
+###################################################
 posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
@@
   model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
+}
+
+```
+
+```{r}
+#############
+## lnCVRQ10
+#############
+##################################################
+# Organise the data and prune tree
+#################################################
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Check and prune tree
+  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
+          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
+
+# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+  hist(lnCVRQ10_data$V)
+
+# Studies with big V, why? Check N
+  lnCVRQ10_data %>% filter(V >= 2)
+
+###################################################
+# Model 2.1: Intercept only model.
+# Used for heterogeneity analysis
+###################################################
+rerun = TRUE
+if(rerun){
+  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.1
+  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
+  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
+} else{ 
+        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
+  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
+  }
+
+###################################################
+# Model 2.2: Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
+  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
+
+  } else{
+        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
+  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
 }

### 2022-12-01 ms.rmd
Added Bayes model for intercept

@@
                               test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+
   # Save model1.1
   saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
-} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}
+  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
+} else{ 
+  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}
+model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
 
@@
 
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 

### 2022-12-01 ms.rmd
Adding trait random effect. I suspect it will explain a lot of variation.

--- 2022-12-01 ms.rmd
@@
                                             ~1 | species_full,
+                                            ~1 | trait,
                                             ~1 | spp,
@@
                               test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+
   # Save model1.1
   saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
-} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}
+  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
+} else{ 
+  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
+model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")}
 
@@
 
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
 
@@
 
-# R2
-fix <- var(predict(model1.2_bayes)[,"Estimate"])
-r2_ml(model1.2)
-
-# Orchard plot
-results1.2 <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)
-
 ####################################################
 # Model 1.3's: Trait type varied by acclimation type
-# but data is seperated by habitat to simplify
+# but data is separated by habitat to simplify
 ####################################################
@@
                                             ~1 | spp,
+                                            ~1 | trait,
                                             ~1 | obs),
@@
 
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) + (1|obs), data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_m)
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1|obs), data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_m)
 
@@
 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|obs), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_f)
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_f)
 
@@
 
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1|obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1|obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
 
@@
 
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 

### 2022-12-01 ms.rmd
Changed to FALSE so not rerun and moved out data from ifelse to make sure it gets run

@@
 
-```{r acclimation_cap}
+```{r lnrrq10}
 #############
@@
 ##################################################
-rerun = TRUE
+rerun = FALSE
 if(rerun){
@@
 ####################################################
- if(rerun){
 # Filter to different habitats
@@
 
+if(rerun){
    # More realistic model with traits in marine species
@@
 
-```{r}
+```{r, lncvrq10}
 #############
@@
 ###################################################
-rerun = TRUE
+rerun = FALSE
 if(rerun){

### 2022-12-02 ms.rmd
Added details in for back-transforming to Q10

@@
 
-# % change in acclimation
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10)
+  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10)
+   m_acute_Q10 <- exp(m_acute) ; mean(f_acute_Q10)
+  m_acclim_Q10 <- exp(m_acclim); mean(f_acclim_Q10)
+   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10)
+  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10)
+
+# % change in acclimation on log scale
   p_change_f <- ((f_acclim - f_acute) / f_acute); quantile(p_change_f, c(0.025, 0.975))
@@
 
-# But this is the % change on the log scale. We can also see what the Q10 change is..NEED TO BE CHECKED CAREFULLY
-f_q10 <-exp((f_acclim - f_acute)-1); mean(f_q10); quantile(f_q10, c(0.025, 0.975))
-m_q10 <-exp((m_acclim - m_acute)-1); mean(m_q10); quantile(m_q10, c(0.025, 0.975))
-t_q10 <-exp((t_acclim - t_acute)-1); mean(t_q10); quantile(t_q10, c(0.025, 0.975))
+# % change on Q10 scale
+  p_change_f_q10 <- exp(f_acclim - f_acute)-1; quantile(p_change_f_q10, c(0.025, 0.975))
+  p_change_m_q10 <- exp(m_acclim - m_acute)-1; quantile(p_change_m_q10, c(0.025, 0.975))
+  p_change_t_q10 <- exp(t_acclim - t_acute)-1; quantile(p_change_t_q10, c(0.025, 0.975))
 
@@
   p1.2
+  ggsave(p1.2, filename = "./output/figures/fig1.png", )
 ```
@@
 
-orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = "lnRRQ10", angle = 45)
+ptm <- orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS"))
+ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
 
@@
    phylo
-ggsave(filename = "fig1.png", path = "../output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
+ggsave(filename = "fig3.png", path = "./output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
 ```

### 2022-12-02 ms.rmd
Adding a table of the i2 stiuff to be plotted

@@
 
+# Heterogeneity analysis
+   w <- with(lnRRQ10_data, 1/V) # weights
+  sv <- sum(w*(length(lnRRQ10_data)-1)) / (sum(w)^2 + sum(w^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = "^sd")^2
+  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
+  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
+
+    res <- posteriors_1.1[,"obs"]
+   stdy <- posteriors_1.1[,"record_num"]
+  phylo <- posteriors_1.1[,"species_full"]
+    spp <- posteriors_1.1[,"spp"]
+  trait <- posteriors_1.1[,"trait"]
+  total <- phylo + spp + res + sv + stdy + trait
+
+  # Calculate I2
+     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
+   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
+     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
+    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
+   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
+     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
+
+  # Table
+     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
+                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
+
 ###################################################
@@
 # % change in acclimation on log scale
-  p_change_f <- ((f_acclim - f_acute) / f_acute); quantile(p_change_f, c(0.025, 0.975))
-  p_change_m <- ((m_acclim - m_acute) / m_acute); quantile(p_change_m, c(0.025, 0.975))
-  p_change_t <- ((t_acclim - t_acute) / t_acute); quantile(p_change_t, c(0.025, 0.975))
+  change_f <- abs(f_acclim - f_acute)*100; quantile(change_f, c(0.025, 0.975))
+  change_m <- abs(m_acclim - m_acute)*100; quantile(change_m, c(0.025, 0.975))
+  change_t <- abs(t_acclim - t_acute)*100; quantile(change_t, c(0.025, 0.975))
 
@@
 
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 annotate("text", x = 1.01, y = 4.60, 
-         label =paste0(round((model1.2$b[3] / model1.2$b[1]*100), 2), "%"), hjust = 0) + labs(shape = "Type") +
+         label =paste0(round(mean(change_f), 2), "%"), hjust = 0) + labs(shape = "Type") +
   geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
@@
 annotate("text", x = 2.01, y = 4.60, 
-         label =paste0(round(mean(p_change_m)*100, 2), "%"), hjust = 0) + labs(shape = "Type") +
+         label =paste0(round(mean(change_m), 2), "%"), hjust = 0) + labs(shape = "Type") +
   geom_segment(aes(x = 1.92, y = 5.6, xend = 2.07, yend = 5.6), 
@@
 annotate("text", x = 3.01, y = 4.60, 
-         label =paste0(round(mean(p_change_t)*100, 2), "%"), hjust = 0) + labs(shape = "Type") +
+         label =paste0(round(mean(change_t), 2), "%"), hjust = 0) + labs(shape = "Type") +
   geom_segment(aes(x = 2.92, y = 5.6, xend = 3.07, yend = 5.6), 
@@
   p1.2
-  ggsave(p1.2, filename = "./output/figures/fig1.png", )
+  ggsave(p1.2, filename = "./output/figures/fig1.png")
 ```

### 2022-12-02 ms.rmd
Adding new figure, marginalise acrodd acclimation type

@@
 
+```{r}
+
+# Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
+But, there is a clear reduction in between individual variance for terrestrial species.
+As temperature get hotter then the variance in physiological rates decreases.
+This is not true of aqautic systems.
+orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", 
+             weights = "prop", data = lnCVRQ10_data, angle = 45, legend.pos = "top.left") +
+            scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+            theme(legend.direction = "vertical")
+```
+
 ```{r, fig2, fig.align='center', fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}

### 2022-12-02 ms.rmd
Adding posteriors

--- 2022-12-02 ms.rmd
@@
 
+######################################################
+# Bayesian Contrasts
+######################################################
+
+  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
+  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute)
+  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
+  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
+  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
+  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
+  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
+
 ```
@@
 
+  annotate("text", x = 2, y = 2.10, 
+         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0) +
+annotate("text", x = 2.01, y = 4.60, 
+         label =paste0(round(mean(change_m), 2), "%"), hjust = 0) + labs(shape = "Type") +
+  geom_segment(aes(x = 1.92, y = 5.6, xend = 2.07, yend = 5.6), 
+                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
+  annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0) +
+
+  annotate("text", x = 3, y = 2.10, 
+         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0) +
+annotate("text", x = 3.01, y = 4.60, 
+         label =paste0(round(mean(change_t), 2), "%"), hjust = 0) + labs(shape = "Type") +
+  geom_segment(aes(x = 2.92, y = 5.6, xend = 3.07, yend = 5.6), 
+                            arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0)
+
+  p1.2
+  ggsave(p1.2, filename = "./output/figures/fig1.png")
+```
+
+```{r}
+
+# Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
+But, there is a clear reduction in between individual variance for terrestrial species.
+As temperature get hotter then the variance in physiological rates decreases.
+This is not true of aquatic systems.
+orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", 
+             weights = "prop", data = lnCVRQ10_data, angle = 45, legend.pos = "top.left") +
+            scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+            theme(legend.direction = "vertical") + #+ ylim(c(-1, 1)) 
  annotate("text", x = 2, y = 2.10, 

### 2022-12-02 ms.rmd
Added in the marginalised means

--- 2022-12-02 ms.rmd
@@
 
+######################################################
+# Bayesian Contrasts
+######################################################
+
+  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
+  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
+  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
+  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
+  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
+  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
+  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
+
+# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
+It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
+  # First get sample sizes
+    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_cvr_mean <- (f_acute_cvr*N[1,"n"][[1]] + f_acclim_cvr*N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
+    m_cvr_mean <- (m_acute_cvr*N[3,"n"][[1]] + m_acclim_cvr*N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
+    t_cvr_mean <- (t_acute_cvr*N[5,"n"][[1]] + t_acclim_cvr*N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+
 ```
@@
                             arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
-  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0)
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0) +
+    theme(axis.title  = element_text(size = 24),
+        axis.text = element_text(size = 15))
 
@@
 
-```{r, fig2, fig.align='center', fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
+```{r, fig2, fig.align='center', fig.cap= "lnCVR Q10 across marine, freshwater and terrestrial environments"}
+
+# Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
+But, there is a clear reduction in between individual variance for terrestrial species.
+As temperature get hotter then the variance in physiological rates decreases.
+This is not true of aquatic systems.
+p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", 
+             weights = "prop", data = lnCVRQ10_data, angle = 45) +
+            scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+annotate("text", x = 1.3, y = -5.2, 
+         label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 2), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0) + 
+annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0) + 
+annotate("text", x = 1.15, y = -5, 
+         label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0) +
+
+annotate("text", x = 2.3, y = -5.2, 
+         label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 2), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0) + 
+annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0) + 
+annotate("text", x = 2.15, y = -5, 
+         label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0) +
+
+annotate("text", x = 3.3, y = -5.2, 
+         label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 2), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0) + 
+annotate("text", x = 3.15, y = -5, 
+         label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0) + labs(shape = "Type") +
+  annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0) +
+  theme(axis.title  = element_text(size = 24),
+        axis.text = element_text(size = 15))
+  p2
+  ggsave(p2, filename = "./output/figures/fig2.png")
+```
+
+```{r, fig3, fig.align='center', fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
 
@@
 
-```{r phylogeny, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
+```{r figphylogeny, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
  # Map data to tree. Just one variable for now
@@
    phylo
-ggsave(filename = "fig3.png", path = "./output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
+ggsave(filename = "fig4.png", path = "./output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
 ```

### 2022-12-02 ms.rmd
New fig for variance explained

@@
 
-```{r lnrrq10}
+```{r lnrrq10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
 #############
@@
 
-```{r, lncvrq10}
+```{r, lncvrq10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
 #############
@@
 
+```{r, fig4, fig.align='center', fig.cap= "I2 estimates"}
+
+p4 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2)*100, 2), "%")), size = 12)
+
+p4
+ggsave(p4, filename = "./output/figures/fig4.png")
+
+```
+
 ### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*

### 2022-12-03 ms.rmd
Adding a Zoom in of the means and CIs
Trunks bigger in size

@@
 
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") +
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 4) +
   scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
@@
   p1.2
+  p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
   ggsave(p1.2, filename = "./output/figures/fig1.png")
+  ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
 ```

### 2022-12-03 ms.rmd
Added models that focus only on wild populations

@@
 
+```{r, wildlnRR10}
+#######################################
+## lnRRQ10 from Wild Populations ##
+#######################################
+##################################################
+# Organise the data and prune tree
+##################################################
+
+# Subset the data
+lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Check and prune tree
+tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
+        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
+
+###################################################
+# Model 3.2: Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model with 
+  model3.1          <- metafor::rma.mv(effect_size ~ 1, V = V,random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.2
+  saveRDS(model3.2, file = "./output/models/lnRRQ10_3.2")
+  saveRDS(model3.2_bayes, file = "./output/models/lnRRQ10_3.2_bayes")
+
+  } else{
+        model3.2 <- readRDS("./output/models/lnRRQ10_3.2")
+  model3.2_bayes <- readRDS("./output/models/lnRRQ10_3.2_bayes")
+}
+
+####################################################
+## Model 3.2: Bayesian Contrasts
+###################################################
+  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
+  f_acute_wild  <- posteriors_3.2[,"b_Intercept"]
+  f_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
+  m_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
+  m_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
+  t_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
+
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10_wild <- exp(f_acute_wild) ; mean(f_acute_Q10_wild)
+  f_acclim_Q10_wild <- exp(f_acclim_wild); mean(f_acclim_Q10_wild)
+   m_acute_Q10_wild <- exp(m_acute_wild) ; mean(f_acute_Q10_wild)
+  m_acclim_Q10_wild <- exp(m_acclim_wild); mean(f_acclim_Q10_wild)
+   t_acute_Q10_wild <- exp(t_acute_wild) ; mean(t_acute_Q10_wild)
+  t_acclim_Q10_wild <- exp(t_acclim_wild); mean(t_acclim_Q10_wild)
+
+# % change in acclimation on log scale
+  change_f_wild <- abs(f_acclim_wild - f_acute_wild)*100; quantile(change_f_wild, c(0.025, 0.975))
+  change_m_wild <- abs(m_acclim_wild - m_acute_wild)*100; quantile(change_m_wild, c(0.025, 0.975))
+  change_t_wild <- abs(t_acclim_wild - t_acute_wild)*100; quantile(change_t_wild, c(0.025, 0.975))
+
+# % change on Q10 scale
+  p_change_f_q10_wild <- exp(f_acclim_wild - f_acute_wild)-1; quantile(p_change_f_q10_wild, c(0.025, 0.975))
+  p_change_m_q10_wild <- exp(m_acclim_wild - m_acute_wild)-1; quantile(p_change_m_q10_wild, c(0.025, 0.975))
+  p_change_t_q10_wild <- exp(t_acclim_wild - t_acute_wild)-1; quantile(p_change_t_q10_wild, c(0.025, 0.975))
+
+```
+
 ```{r, fig1, fig.align='center', fig.cap= "Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments"}

### 2022-12-03 ms.rmd
Merge climate data with wild effect size data

@@
 
+# Bring in Climate data
+climate <- read.csv("./output/climate_data/temp_timeseries.csv")
+
+# Create a match column.
+climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
+
 # Subset the data
 lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnRRQ10_data_wild <- left_join(lnRRQ10_data_wild, climate2, by = "match")
 
@@
 ###################################################
-
+rerun = TRUE
 if(rerun){
   # More realistic model with 
-  model3.1          <- metafor::rma.mv(effect_size ~ 1, V = V,random = list(~1 | record_num,
+  model3.1          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+                                       random = list(~1 | record_num,
                                             ~1 | species_full,

### 2022-12-03 ms.rmd
Fixed name

@@
   # More realistic model with 
-  model3.1          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                                        random = list(~1 | record_num,

### 2022-12-03 ms.rmd
Adding first model that tests if plasticty is related to enviromental variability. We expect this to be true for acclimation but not acute so we have an interaction

@@
 # % change on Q10 scale
-  p_change_f_q10_wild <- exp(f_acclim_wild - f_acute_wild)-1; quantile(p_change_f_q10_wild, c(0.025, 0.975))
-  p_change_m_q10_wild <- exp(m_acclim_wild - m_acute_wild)-1; quantile(p_change_m_q10_wild, c(0.025, 0.975))
-  p_change_t_q10_wild <- exp(t_acclim_wild - t_acute_wild)-1; quantile(p_change_t_q10_wild, c(0.025, 0.975))
+  p_change_f_q10_wild <- (exp(f_acclim_wild - f_acute_wild)-1)*100; quantile(p_change_f_q10_wild, c(0.025, 0.975))
+  p_change_m_q10_wild <- (exp(m_acclim_wild - m_acute_wild)-1)*100; quantile(p_change_m_q10_wild, c(0.025, 0.975))
+  p_change_t_q10_wild <- (exp(t_acclim_wild - t_acute_wild)-1)*100; quantile(p_change_t_q10_wild, c(0.025, 0.975))
 
+####################################################
+# Model 3.3: Model environmental variability 
+####################################################
+  rerun = TRUE
+if(rerun){
+  # More realistic model with 
+  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv + type + type:cv, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv + type + type:cv + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.3, file = "./output/models/lnRRQ10_3.3")
+  saveRDS(model3.3_bayes, file = "./output/models/lnRRQ10_3.3_bayes")
+
+  } else{
+        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
+  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
+}
 ```

### 2022-12-04 ms.rmd
Added new models

--- 2022-12-03 ms.rmd
@@
 # % change on Q10 scale
-  p_change_f_q10_wild <- exp(f_acclim_wild - f_acute_wild)-1; quantile(p_change_f_q10_wild, c(0.025, 0.975))
-  p_change_m_q10_wild <- exp(m_acclim_wild - m_acute_wild)-1; quantile(p_change_m_q10_wild, c(0.025, 0.975))
-  p_change_t_q10_wild <- exp(t_acclim_wild - t_acute_wild)-1; quantile(p_change_t_q10_wild, c(0.025, 0.975))
+  p_change_f_q10_wild <- (exp(f_acclim_wild - f_acute_wild)-1)*100; quantile(p_change_f_q10_wild, c(0.025, 0.975))
+  p_change_m_q10_wild <- (exp(m_acclim_wild - m_acute_wild)-1)*100; quantile(p_change_m_q10_wild, c(0.025, 0.975))
+  p_change_t_q10_wild <- (exp(t_acclim_wild - t_acute_wild)-1)*100; quantile(p_change_t_q10_wild, c(0.025, 0.975))
 
+####################################################
+# Model 3.3: Model environmental variability 
+####################################################
+  rerun = TRUE
+if(rerun){
+  # More realistic model with 
+  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type + type:scale(cv), V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + type:scale(cv) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.3, file = "./output/models/lnRRQ10_3.3")
+  saveRDS(model3.3_bayes, file = "./output/models/lnRRQ10_3.3_bayes")
+
+  } else{
+        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
+  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
+  }
+
+  if(rerun){
+  # More realistic model with 
+  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type + type:scale(acf_all), V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + type:scale(acf_all) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.4, file = "./output/models/lnRRQ10_3.4")
+  saveRDS(model3.4_bayes, file = "./output/models/lnRRQ10_3.4_bayes")
+
+  } else{
+        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
+  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
+}
 ```

### 2022-12-04 ms.rmd
Added new models for assessing autocorrelations in climate and Q10

@@
   }
+
+if(rerun){
+  # More realistic model with 
+  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.5
+  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
+  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")
+
+  } else{
+        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
+  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
+  }
+
+  if(rerun){
+  # More realistic model with 
+  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.6
+  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
+  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")
+
+  } else{
+        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
+  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
+}
 ```

### 2022-12-04 ms.rmd
Adding in climate variability models

@@
   }
+
+  if(rerun){
+  # More realistic model with 
+  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + scale(cv) + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.7
+  saveRDS(model3.7, file = "./output/models/lnRRQ10_3.7")
+  saveRDS(model3.7_bayes, file = "./output/models/lnRRQ10_3.7_bayes")
+
+  } else{
+        model3.7 <- readRDS("./output/models/lnRRQ10_3.7")
+  model3.7_bayes <- readRDS("./output/models/lnRRQ10_3.7_bayes")
+}
+```
+
+```{r wildlncvr}
+#######################################
+## lnCVRQ10 from Wild Populations ##
+#######################################
+##################################################
+# Organise the data and prune tree
+##################################################
+
+# Bring in Climate data
+climate <- read.csv("./output/climate_data/temp_timeseries.csv")
+
+# Create a match column.
+climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
+
+# Subset the data
+lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
+                              mutate(spp = species_full, 
+                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
+                                     match = interaction(spp, lat, long))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
+
+# Check and prune tree
+tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
+        A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
+
+###################################################
+# Model 4.2: Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+###################################################
+rerun = TRUE
+if(rerun){
+  # More realistic model with 
+  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+
+  # Save model3.2
+  saveRDS(model4.2, file = "./output/models/lnCVRQ10_4.2")
+  saveRDS(model4.2_bayes, file = "./output/models/lnCVRQ10_4.2_bayes")
+
+  } else{
+        model4.2 <- readRDS("./output/models/lnCVRQ10_4.2")
+  model4.2_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
+}
+
+####################################################
+## Model 4.2: Bayesian Contrasts
+###################################################
+  posteriors_4.2 <- posterior_samples(model4.2_bayes, pars = "^b")
+  f_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"]
+  f_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_typeacclim"]
+  m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
+  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
+  t_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatt"]
+
+# CVRQ10 values for each category.
+   f_acute_Q10_wild_cvr <- exp(f_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
+  f_acclim_Q10_wild_cvr <- exp(f_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
+   m_acute_Q10_wild_cvr <- exp(m_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
+  m_acclim_Q10_wild_cvr <- exp(m_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
+   t_acute_Q10_wild_cvr <- exp(t_acute_wild_cvr) ; mean(t_acute_Q10_wild_cvr)
+  t_acclim_Q10_wild_cvr <- exp(t_acclim_wild_cvr); mean(t_acclim_Q10_wild_cvr)
+
+# % change in acclimation on log scale
+  change_f_wild_cvr <- abs(f_acclim_wild_cvr - f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
+  change_m_wild_cvr <- abs(m_acclim_wild_cvr - m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
+  change_t_wild_cvr <- abs(t_acclim_wild_cvr - t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
+
+# % change on Q10 scale
+  p_change_f_q10_wild_cvr <- (exp(f_acclim_wild_cvr - f_acute_wild_cvr)-1)*100; quantile(p_change_f_q10_wild_cvr, c(0.025, 0.975))
+  p_change_m_q10_wild_cvr <- (exp(m_acclim_wild_cvr - m_acute_wild_cvr)-1)*100; quantile(p_change_m_q10_wild_cvr, c(0.025, 0.975))
+  p_change_t_q10_wild_cvr <- (exp(t_acclim_wild_cvr - t_acute_wild_cvr)-1)*100; quantile(p_change_t_q10_wild_cvr, c(0.025, 0.975))
+
+####################################################
+# Model 4.3-4.7: Model environmental variability 
+####################################################
+  rerun = TRUE
+if(rerun){
+  # More realistic model with 
+  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type + type:scale(cv), V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + type:scale(cv) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+
+  # Save model4.3
+  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
+  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
+
+  } else{
+        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
+  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
+  }
+
+  if(rerun){
+  # More realistic model with 
+  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type + type:scale(acf_all), V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + type:scale(acf_all) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
+  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
+
+  } else{
+        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
+  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
+  }
+
+if(rerun){
+  # More realistic model with 
+  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+
+  # Save model4.5
+  saveRDS(model4.5, file = "./output/models/lnCVRQ10_4.5")
+  saveRDS(model4.5_bayes, file = "./output/models/lnCVRQ10_4.5_bayes")
+
+  } else{
+        model4.5 <- readRDS("./output/models/lnCVRQ10_4.5")
+  model4.5_bayes <- readRDS("./output/models/lnCVRQ10_4.5_bayes")
+  }
+
+  if(rerun){
+  # More realistic model with 
+  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+
+  # Save model4.6
+  saveRDS(model4.6, file = "./output/models/lnCVRQ10_4.6")
+  saveRDS(model4.6_bayes, file = "./output/models/lnCVRQ10_4.6_bayes")
+
+  } else{
+        model4.6 <- readRDS("./output/models/lnCVRQ10_4.6")
+  model4.6_bayes <- readRDS("./output/models/lnCVRQ10_4.6_bayes")
+  }
+
+ if(rerun){
+  # More realistic model with 
+  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + scale(cv) + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+
+  # Save model4.7
+  saveRDS(model4.7, file = "./output/models/lnCVRQ10_4.7")
+  saveRDS(model4.7_bayes, file = "./output/models/lnCVRQ10_4.7_bayes")
+
+  } else{
+        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")
+  model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
+}
 ```

### 2022-12-05 ms.rmd
Fixed SV calculation error. Added posterios for I2 for lnCVR. New fig5

@@
    w <- with(lnRRQ10_data, 1/V) # weights
-  sv <- sum(w*(length(lnRRQ10_data)-1)) / (sum(w)^2 + sum(w^2))
+  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
 
@@
 
+# Heterogeneity analysis
+   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
+  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = "^sd")^2
+  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
+  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
+
+    res_cvr <- posteriors_2.1[,"obs"]
+   stdy_cvr <- posteriors_2.1[,"record_num"]
+  phylo_cvr <- posteriors_2.1[,"species_full"]
+    spp_cvr <- posteriors_2.1[,"spp"]
+  trait_cvr <- posteriors_2.1[,"trait"]
+  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
+
+  # Calculate I2
+     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
+   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
+     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
+    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
+   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
+     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
+
+  # Table
+     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
+                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
+
 ###################################################
@@
 ####################################################
-# Model 3.3: Model environmental variability 
+  # Model 3.3: Model environmental variability by acute 
+  #  acclim 
 ####################################################
@@
 
+################################################################
+  # Model 3.7: Environmental autocorrelation model by acute/acclim
+################################################################
   if(rerun){
@@
 
+################################################################
+  # Model 3.5: Environmental variability  model
+################################################################
   if(rerun){
@@
 
+################################################################
+  # Model 3.6: Environmental autocorrelation model
+################################################################
   if(rerun){
@@
   }
+
+################################################################
+  # Model 3.7: Environmental variability and autocorrelation model
+################################################################
 
@@
 ####################################################
-# Model 4.3-4.7: Model environmental variability 
+  # Model 4.3: Model environmental variability by acute/acclim
 ####################################################
-  rerun = TRUE
+  rerun = FALSE
 if(rerun){
@@
 
+################################################################
+  # Model 4.4: Environmental autocorrelation model by acute/acclim
+################################################################
   if(rerun){
@@
 
+################################################################
+  # Model 4.5: Environmental variability
+################################################################
 if(rerun){
@@
 
+################################################################
+  # Model 4.6: Environmental autocorrelation model 
+################################################################
   if(rerun){
@@
 
+################################################################
+  # Model 4.7: Environmental autocorrelation and variability
+################################################################
  if(rerun){
@@
   p2
+   p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
   ggsave(p2, filename = "./output/figures/fig2.png")
+  ggsave(p2.2, filename = "./output/figures/fig2.2.png")
 ```
@@
 
-p4 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2)*100, 2), "%")), size = 12)
+p4 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2), 2), "%")), size = 12)
 
@@
 
+```
+
+```{r, fig5, fig.align='center', fig.cap= "I2 estimates lnCVR"}
+p5 <- ggplot(i2_lncvr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 12)
+
+p5
+ggsave(p5, filename = "./output/figures/fig5.png")
 ```

### 2022-12-05 ms.rmd
Added scale cv and acf to data and models

@@
 
+# Scale data
+        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
+                                                          acf_all_c = scale(acf_all))
 ###################################################
@@
   # More realistic model with 
-  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type + type:scale(cv), V = V,
+  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + type:scale(cv) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type + type:scale(acf_all), V = V,
+  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + type:scale(acf_all) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
+  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
 ################################################################
+
   if(rerun){
   # More realistic model with 
-  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
+  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + scale(cv) + type, V = V,
+  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
 
+# Scale environment variables
+    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
+                                                        acf_all_c = scale(acf_all))
 ###################################################
@@
   # More realistic model with 
-  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type + type:scale(cv), V = V,
+  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + type:scale(cv) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
 
@@
   # More realistic model with 
-  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type + type:scale(acf_all), V = V,
+  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + type:scale(acf_all) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
 
@@
   # More realistic model with 
-  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(cv) + type, V = V,
+  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
 
@@
   # More realistic model with 
-  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + type, V = V,
+  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
 
@@
   # More realistic model with 
-  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + scale(acf_all) + scale(cv) + type, V = V,
+  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + scale(acf_all) + scale(cv) + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
 
@@
 
+```{r, fig6, fig.align='center', fig.cap= "I2 estimates lnCVR"}
+p6 <- bubble_plot(model3.5, mod = "cv", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)")
+
+p7 <- bubble_plot(model3.6, mod = "acf_all", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank())
+
+p67 <- (p6 | p7) + plot_annotation(tag_levels = "A")
+
+ggsave(p67, filename = "./output/figures/fig6.png")
+```
+
 ### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*

### 2022-12-06 ms.rmd
Fixed a few errors and added some new modifications for figures

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm)
 
@@
   m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
-  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatm"]
   t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
@@
 ####################################################
-  rerun = FALSE
+  rerun = TRUE
 if(rerun){
@@
 
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 4) +
-  scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 5) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
 annotate("text", x = 1, y = 2.10, 
-         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0) + 
+         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0, size = 6) + 
 annotate("text", x = 1.01, y = 4.60, 
-         label =paste0(round(mean(change_f), 2), "%"), hjust = 0) + labs(shape = "Type") +
+         label =paste0(round(mean(change_f), 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
   geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
                             arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
-  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0) +
+  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0, size = 6) +
 
   annotate("text", x = 2, y = 2.10, 
-         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0) +
+         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
 annotate("text", x = 2.01, y = 4.60, 
-         label =paste0(round(mean(change_m), 2), "%"), hjust = 0) + labs(shape = "Type") +
+         label =paste0(round(mean(change_m), 2), "%"), hjust = 0, size = 6) +
   geom_segment(aes(x = 1.92, y = 5.6, xend = 2.07, yend = 5.6), 
                             arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
-  annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0) +
+  annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0, size = 6) +
 
   annotate("text", x = 3, y = 2.10, 
-         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0) +
+         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
 annotate("text", x = 3.01, y = 4.60, 
-         label =paste0(round(mean(change_t), 2), "%"), hjust = 0) + labs(shape = "Type") +
+         label =paste0(round(mean(change_t), 2), "%"), hjust = 0, size = 6) +
   geom_segment(aes(x = 2.92, y = 5.6, xend = 3.07, yend = 5.6), 
                             arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
-  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0) +
-    theme(axis.title  = element_text(size = 24),
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6, parse = TRUE)
+
+  p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
         axis.text = element_text(size = 15))
 
-  p1.2
+   res <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)
+
+    ggplot(lnRRQ10_data) + ggbeeswarm::geom_quasirandom(aes(y = effect_size, x = habitat, shape = type, colour = type, size = 1/sqrt(V)), alpha = 0.7)+ coord_flip() + theme_classic() + scale_x_discrete(labels = c("t" = "Terrestrial","m" = "Marine" ,"f" = "Freshwater")) + theme(axis.title.y = element_blank()) + labs(y = TeX("$lnRR_{Q_{10}}$"), size = "Precision (1/SE)",colour = "Type", shape = "Type")
+
+    geom_quasirandomgeom_point(position = position_beeswarm(dodge.width = 0.2, groupOnX = TRUE), alpha = 0.7)
+
   p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
@@
 
-```{r, fig6, fig.align='center', fig.cap= "I2 estimates lnCVR"}
-p6 <- bubble_plot(model3.5, mod = "cv", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)")
-
-p7 <- bubble_plot(model3.6, mod = "acf_all", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank())
+```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR"}
+p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), " P = ", round(model3.5$pval[3],3))))
+
+p7 <- bubble_plot(model3.6, mod = "acf_all_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = 3, label = TeX(paste0("$\\beta = $", round(model3.6$b[3], 3), ", 95%CI: ", round(model3.6$ci.lb[3],3), " to ", round(model3.6$ci.ub[3], 3), " P = ", round(model3.6$pval[3],3))))
 
@@
 
-ggsave(p67, filename = "./output/figures/fig6.png")
+ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 25, units = "cm")
+```
+
+```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR"}
+p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3))))
+
+p8 <- bubble_plot(model3.6, mod = "acf_all_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = 3, label = TeX(paste0("$\\beta = $", round(model4.6$b[3], 3), ", 95%CI: ", round(model4.6$ci.lb[3],3), " to ", round(model4.6$ci.ub[3], 3), " P = ", round(model4.6$pval[3],3))))
+
+p89 <- (p8 | p9) + plot_annotation(tag_levels = "A")
+
+ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 25, units = "cm")
 ```

### 2022-12-06 ms.rmd
Fixed error in posteriors

@@
 # Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10)
-  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10)
-   m_acute_Q10 <- exp(m_acute) ; mean(f_acute_Q10)
-  m_acclim_Q10 <- exp(m_acclim); mean(f_acclim_Q10)
-   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10)
-  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10)
+   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
+  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
+   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
+  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
+   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
+  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
 
@@
                             arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
-  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6, parse = TRUE)
-
-  p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6)
+
+  p1.2 <- p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
         axis.text = element_text(size = 15))
 
-   res <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)
-
-    ggplot(lnRRQ10_data) + ggbeeswarm::geom_quasirandom(aes(y = effect_size, x = habitat, shape = type, colour = type, size = 1/sqrt(V)), alpha = 0.7)+ coord_flip() + theme_classic() + scale_x_discrete(labels = c("t" = "Terrestrial","m" = "Marine" ,"f" = "Freshwater")) + theme(axis.title.y = element_blank()) + labs(y = TeX("$lnRR_{Q_{10}}$"), size = "Precision (1/SE)",colour = "Type", shape = "Type")
-
-    geom_quasirandomgeom_point(position = position_beeswarm(dodge.width = 0.2, groupOnX = TRUE), alpha = 0.7)
-
    p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
-  ggsave(p1.2, filename = "./output/figures/fig1.png")
+  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
   ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
@@
 This is not true of aquatic systems.
-p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", 
-             weights = "prop", data = lnCVRQ10_data, angle = 45) +
-            scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-
-annotate("text", x = 1.3, y = -5.2, 
-         label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 2), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0) + 
-annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0) + 
+p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", data = lnCVRQ10_data, angle = 45, trunk.size = 5) +
+            scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
+         label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 2), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
 annotate("text", x = 1.15, y = -5, 
-         label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0) +
-
+         label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
 annotate("text", x = 2.3, y = -5.2, 
-         label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 2), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0) + 
-annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0) + 
+         label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 2), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
 annotate("text", x = 2.15, y = -5, 
-         label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0) +
-
-annotate("text", x = 3.3, y = -5.2, 
-         label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 2), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0) + 
+         label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
+         label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 2), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
 annotate("text", x = 3.15, y = -5, 
-         label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0) + labs(shape = "Type") +
-  annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0) +
-  theme(axis.title  = element_text(size = 24),
+         label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
+  annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6)
+
+p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
         axis.text = element_text(size = 15))
-  p2
    p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
-  ggsave(p2, filename = "./output/figures/fig2.png")
+
+   ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
   ggsave(p2.2, filename = "./output/figures/fig2.2.png")

### 2022-12-06 ms.rmd
Adding  trait plots

@@
 
+ptf <- orchard_plot(model1.3_f, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS"))
+ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model1.3_t, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0)
+ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
 lnRRQ10_data %>% group_by(habitat, type, trait_category) %>% summarise(n = n()) %>% data.frame()

### 2022-12-06 ms.rmd
CVR figure

@@
 ```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR"}
-p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), " P = ", round(model3.5$pval[3],3))))
-
-p7 <- bubble_plot(model3.6, mod = "acf_all_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = 3, label = TeX(paste0("$\\beta = $", round(model3.6$b[3], 3), ", 95%CI: ", round(model3.6$ci.lb[3],3), " to ", round(model3.6$ci.ub[3], 3), " P = ", round(model3.6$pval[3],3))))
+p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), "; P = ", round(model3.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18))
+
+p7 <- bubble_plot(model3.6, mod = "acf_all_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability") + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = 3, label = TeX(paste0("$\\beta = $", round(model3.6$b[3], 3), ", 95%CI: ", round(model3.6$ci.lb[3],3), " to ", round(model3.6$ci.ub[3], 3), "; P = ", round(model3.6$pval[3],3)))) + theme_classic() + theme(axis.text = element_text(size = 12), axis.title = element_text(size = 18))
 
@@
 
-ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 25, units = "cm")
+ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 30, units = "cm")
 ```
@@
 ```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR"}
-p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3))))
-
-p8 <- bubble_plot(model3.6, mod = "acf_all_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Autocorrelation") + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = 3, label = TeX(paste0("$\\beta = $", round(model4.6$b[3], 3), ", 95%CI: ", round(model4.6$ci.lb[3],3), " to ", round(model4.6$ci.ub[3], 3), " P = ", round(model4.6$pval[3],3))))
+p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", k = FALSE) +annotate("text", x = 1, y = -5, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))
+
+p9 <- bubble_plot(model4.6, mod = "acf_all_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", k = FALSE) + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = -5, label = TeX(paste0("$\\beta = $", round(model4.6$b[3], 3), ", 95%CI: ", round(model4.6$ci.lb[3],3), " to ", round(model4.6$ci.ub[3], 3), " P = ", round(model4.6$pval[3],3)))) + theme_classic() + theme(axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))
 
@@
 
-ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 25, units = "cm")
+ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 30, units = "cm")
 ```

### 2022-12-07 ms.rmd
No real changes
Few new models given what Seebacher et al report

@@
   }
+
+############################################################################################
+# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
+# differently in each habitat
+############################################################################################  
+  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+  if(rerun){
+  # More realistic model with 
+  model3.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
+  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
+
+  } else{
+        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
+  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
+}
+
+############################################################################################
+# Model 3.9: Acclimatization lnRRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################
+
+if(rerun){
+  # More realistic model with 
+  model3.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.9, file = "./output/models/lnRRQ10_3.9")
+  saveRDS(model3.9_bayes, file = "./output/models/lnRRQ10_3.9_bayes")
+
+  } else{
+        model3.9 <- readRDS("./output/models/lnRRQ10_3.9")
+  model3.9_bayes <- readRDS("./output/models/lnRRQ10_3.9_bayes")
+}
+
 ```
@@
   }
+
+############################################################################################
+  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
+  # differently in each habitat
+############################################################################################  
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+  if(rerun){
+  # More realistic model with 
+  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model4.8
+  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
+  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
+
+  } else{
+        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
+  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
+}
+
+############################################################################################
+# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################
+
+if(rerun){
+  # More realistic model with 
+  model4.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model4.9, file = "./output/models/lnRRQ10_4.9")
+  saveRDS(model4.9_bayes, file = "./output/models/lnRRQ10_4.9_bayes")
+
+  } else{
+        model4.9 <- readRDS("./output/models/lnRRQ10_4.9")
+  model4.9_bayes <- readRDS("./output/models/lnRRQ10_4.9_bayes")
+}
+
 ```
@@
 
+```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations"}
+bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme(legend.position = "bottom")
+```
+
 ### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*

### 2022-12-07 ms.rmd
Colour updates to figs

@@
 ```{r, fig1, fig.align='center', fig.cap= "Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments"}
-
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
 p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 5) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
@@
                             arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
-  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6)
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6) + scale_fill_manual(values = c(col))
 
@@
          label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-  annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6)
+  annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
 
@@
 ```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations"}
-bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme(legend.position = "bottom")
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
+
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
+
+p8.1 / p8.2
+
 ```

### 2022-12-08 ms.rmd
Adding lnCVR plots for environment

@@
 
-```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR"}
+```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR wild populations"}
 p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), "; P = ", round(model3.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18))
@@
 
-```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR"}
+```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR wild populations"}
 p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", k = FALSE) +annotate("text", x = 1, y = -5, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))
@@
 
-```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations"}
+```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
 
@@
 
-p8.1 / p8.2
-
+p8.1.2 <- p8.1 / p8.2
+
+ggsave(p8.1.2, filename = "./output/figures/fig8.png")
+```
+
+```{r, fig9, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
+
+p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
+
+p91.2 <- p9.1 / p9.2
+
+ggsave(p91.2, filename = "./output/figures/fig9.png")
 ```

### 2022-12-09 ms.rmd
Adding in posterior calculations of slopes in each habitat and check if they are sig

@@
 
+#################################################
+### Bayesian Slopes from Model 3.8
+#################################################
+ posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
+
+    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
+    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
+    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
+
 ############################################################################################
@@
 }
+
+#################################################
+### Bayesian Slopes from Model 3.9
+#################################################
+ posteriors <- posterior_samples(model3.9_bayes, "^b")
+
+    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
+    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
+    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
 
@@
 }
+
+#################################################
+### Bayesian Slopes from Model 4.8
+#################################################
+ posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
+
+    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
+    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
+    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
 

### 2022-12-09 ms.rmd
Added posterios for last model to add to presentation

@@
 
+#################################################
+### Bayesian Slopes from Model 4.9
+#################################################
+ posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
+
+    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
+    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
+    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
 ```

### 2022-12-09 ms.rmd
Just checking consistency by running models foe each envirobment seperately. Same as the giant model, but need for greater clarity on variation explained because aggergate hides this a bit because of weighting of marine and freshwater systems which explain almost no variation.

@@
 
+##################################################
+    # Model 3.9, but terrestrial only
+##################################################
+    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+
+    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+
+    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+     model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+
+    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
 ```

### 2022-12-09 ms.rmd
Running model to test a new hypothesis in case I am missing an inetraction, which when thinking about it, is fairly justified.

--- 2022-12-09 ms.rmd
@@
 
+##################################################
+    # Model 3.9, but terrestrial only
+##################################################
+    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+
+    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+        # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+
+    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+       # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+     model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+
+    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+    # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+
 ```

### 2022-12-09 ms.rmd
More annottation

@@
 ##################################################
-    # Model 3.9, but terrestrial only
+    # Model 3.8, 3.9 and 3.10 - Habitat subset
 ##################################################
+    # Subset data to habitat
     lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
@@
 
+    # Terrestrial Models
     model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_t)
-
+    # Freshwater Models
     model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
@@
 
+    # Marine Models
       model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,

### 2022-12-10 ms.rmd
Nothing really

@@
 We want predictability AND variance
+
      model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
@@
 We want predictability AND variance
+
     model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,

### 2023-01-04 ms.rmd
UPdate to climate analysis

@@
 To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
-Only studies on wild populations were used for climate analyses because temperature data at locations was likely reflective of past climate history.
+Only studies on wild populations were used for climate analyses because temperature data at natural locations is likely to be reflective of past climate history.
 Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
-For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
-We chose a 2 meters resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms.
-
-Using thermal time-series data for each location we summarised various metrics of thermal variability across months and years.
-We calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
+For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
+We chose a 2 meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms.
+
+Using the thermal time-series data for each location we summarised various metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
+To estimate thermal variability we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
+To estimate thermal predictability we calculated the auto-regressive time lag across the entire dataset.
+Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticty evolution.
 

### 2023-01-04 ms.rmd
Writing of methods and switching Bayesian models to sigma = TRUE instead of an obs level random effect

@@
 To estimate thermal predictability we calculated the auto-regressive time lag across the entire dataset.
-Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticty evolution.
+Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticity evolution.
 
@@
 
-# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+# Found some other data entry problems from old dataset.
+Sample sizes are decimals.
+That's not correct.
+It has to be an integer.
+These are not the new data that we entered.
+Data now checked.
+Seemed to have resulted in a 'frame shift' in some data.
+Not sure how that happened, but it's now fixed.
 hist(lnRRQ10_data$V)
@@
 
-  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 
@@
 # extract posterior sds, but square them to turn to variance
-  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = "^sd")^2
+  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
   colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
@@
 
-    res <- posteriors_1.1[,"obs"]
+    res <- posteriors_1.1[,"sigma"]
    stdy <- posteriors_1.1[,"record_num"]
@@
 
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 

### 2023-01-05 ms.rmd
Testing out assumps for trait models, assuming het variance. Some issues with variables being dropped.

@@
 `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan].
-We included study, species and phylogeny as random effects to account for non-independence and also explore drivers of variation among $lnRR_{Q_{10}}$ estimates.
+We also refit the same models using *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010] to ensure that results were consistent, and to create orchard plots more easily [vers.
+2.0, @Nakagawa2021c].
+
+In all models, we included study, species and phylogeny as random effects to account for non-independence, and explore drivers of variation among $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+We ran 4 MCMC chains, each with a warm up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
+We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
+We checked that all MCMC chains were effectively mixing and had converged (i.e., $R_{hat} = 1$).
 
@@
 # Filter to different habitats
-   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m")
-   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f")
-   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m") %>% mutate(type = is.character(type))
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f") %>% mutate(type = is.character(type))
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t") %>% mutate(type = is.character(type))
 
@@
 if(rerun){
-   # More realistic model with traits in marine species
+   # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
@@
                               R = list(species_full = m_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_m)
-
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1|obs), data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_m)
+                              test = "t", data = lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size)))
+
+  model1.3_m_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = m_phylo), 
+                              str = "HCS", rho = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size)))
+
+  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = "plot", group = "spp", data = lnRRQ10_data_m, angle = 45)
+
+  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + type + trait_category + type:trait_category|gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
 
@@
 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_f)
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
 
@@
 
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 # extract posterior sds, but square them to turn to variance
-  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = "^sd")^2
+  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
   colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
@@
 
-    res_cvr <- posteriors_2.1[,"obs"]
+    res_cvr <- posteriors_2.1[,"sigma"]
    stdy_cvr <- posteriors_2.1[,"record_num"]
@@
 
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
 
-   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
 
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
 
-   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
 
-   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
 
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
 
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
 
@@
 
-   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
 
@@
 
-   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild)
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
 
@@
 
-   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
 

### 2023-01-05 ms.rmd
Some writing, and some attenps to render

@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015].
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015].
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
 Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015].
-As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of 12 trait categories.
+As such, using the detailed information on the trait type, and its associated units from a given study, we categorized each effect size into one of 12 trait categories.
 These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
@@
 ### *Meta-Analysis*
-We analysed our data using Bayesian multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
+We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
 `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan].
-We also refit the same models using *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010] to ensure that results were consistent, and to create orchard plots more easily [vers.
+`r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010].
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
 2.0, @Nakagawa2021c].
-
-In all models, we included study, species and phylogeny as random effects to account for non-independence, and explore drivers of variation among $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-We ran 4 MCMC chains, each with a warm up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
 We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were effectively mixing and had converged (i.e., $R_{hat} = 1$).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+
+#### *Multi-level Meta-analysis (MLMA) Models*
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species and phylogeny as random effects to account for non-independence.
+We also included trait as a random effect to account for trait variation within the data.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @NakaSantos2012; @Noble2022] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@NakaSantos2012].
+
+A phylogenetic tree was created using the Open Tree of Life (OTL) with the *rotl* package in R [vers. `r utils::packageVersion("rotl")`, ]. Branch lengths were computed using Gafen's method []
 
@@
 
+  # Check whether there is differences in variances for each habitat
+  model1.2_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 + type + habitat | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
    model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
@@
 # Filter to different habitats
-   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m") %>% mutate(type = is.character(type))
-   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f") %>% mutate(type = is.character(type))
-   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t") %>% mutate(type = is.character(type))
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m") 
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f") 
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")
 
@@
    # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
+  # Filter out antioxidant
+  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size))
+
   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
@@
                               R = list(species_full = m_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size)))
+                              test = "t", 
+                              data = lnRRQ10_data_m)
 
@@
                               str = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size)))
-
-  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = "plot", group = "spp", data = lnRRQ10_data_m, angle = 45)
+                              test = "t", data = lnRRQ10_data_m)
+
+  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", data = lnRRQ10_data_m, angle = 45)
 
@@
   saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
+  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
   saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
@@
 ####################################################
-  rerun = TRUE
+  rerun = FALSE
 if(rerun){
@@
 
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model4.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
         model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")
-  model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
+  #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
   }

### 2023-01-05 ms.rmd
New rendered MS

@@
 
+  p1.2
    p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
+
+   p1.2.2
   ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
@@
    p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
-
+  p2
+  p2.2
    ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
@@
 
-```{r, fig3, fig.align='center', fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
-
-orchard_plot(model1.3, mod = "trait_category",  group = "record_num",  data = lnRRQ10_data)
+```{r, fig3, fig.align='center', eval = FALSE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
 

### 2023-01-05 ms.rmd
JUst supressing some code and messages in code chunks for rendering

@@
 
-A phylogenetic tree was created using the Open Tree of Life (OTL) with the *rotl* package in R [vers. `r utils::packageVersion("rotl")`, ]. Branch lengths were computed using Gafen's method []
+A phylogenetic tree was created using the Open Tree of Life (OTL) with the *rotl* package in R [vers.
+`r utils::packageVersion("rotl")`, ].
+We resolved all polytomies in the tree and replaced any missing taxa with closely related species.
+Branch lengths were computed using Gafen's method []
 
@@
 
-```{r, wildlnRR10}
+```{r, wildlnRR10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
 #######################################
@@
 
-```{r wildlncvr}
+```{r wildlncvr, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
 #######################################

### 2023-01-06 ms.rmd
MS updates

@@
 ---
-title: ""
-author: Daniel W.A. Noble, Fonti Kar, Frank Seebacher, Alex Bush, & Shinichi Nakagawa
-date: "`r Sys.Date()`"
+title: "Reduced plasticity and opportunity for selection across terrestrial ectotherm populations"
 bibliography: ./bib/refs.bib
@@
 
-## Materials and Methods
+Daniel W.A. Noble^1, Fonti Kar^2, Frank Seebacher^3, Alex Bush^4, & Shinichi Nakagawa^2
+
+#### Affliations:
+$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
+$^2$ School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
+$^3$ SOLES, University of Sydney, Sydney, NSW, Australia
+$^4$ Department of Biology, Lancaster University, Liverpool, UK
+
+## **Abstract**
+
+## **Introduction**
+
+Variable thermal environments are expected to result in strong selection pressures that result in adaptation or the evolution of phenotypic plasticity.
+Plasticity and adaptation are considered critical for population resilience to human-induced climate change.
+
+Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) quantify the degree
+
+ectotherms are capable of physiological plasticity in rates: 1)
+
+## **Materials and Methods**
 ### *Literature collection*
@@
 
-We extracted means, standard deviations and sample sizes for physiological rates at the two test temperatures.
+We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
 If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
@@
 Following @Noble2022 we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
-These effect sizes are essentially similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations for their sampling variances.
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations for their sampling variances.
 Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
@@
 
-To compare mean physiological rates we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022] as follows:
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022] as follows:
 
@@
 #### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-Using the mean, standard deviation and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+Using the mean, standard deviation, and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
 For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator.
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015].
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015].
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
@@
 To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
-Only studies on wild populations were used for climate analyses because temperature data at natural locations is likely to be reflective of past climate history.
+It was unclear whether climate at the locations of captive reared organisms would be representative of a populations climate history - particularly for species reared under captive condition for many generations.
+Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations were used for climate analyses.
+
 Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
 For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
-We chose a 2 meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms.
+We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
 
 Using the thermal time-series data for each location we summarised various metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
-To estimate thermal variability we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
-To estimate thermal predictability we calculated the auto-regressive time lag across the entire dataset.
+To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
+To estimate thermal predictability, we calculated the auto-regressive time lag across the entire dataset.
 Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticity evolution.
@@
 2.0, @Nakagawa2021c].
-For our Bayesian models, we ran 4 MCMC chains, each with a warm up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
 We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
@@
 #### *Multi-level Meta-analysis (MLMA) Models*
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species and phylogeny as random effects to account for non-independence.
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, and phylogeny as random effects to account for non-independence.
 We also included trait as a random effect to account for trait variation within the data.
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @NakaSantos2012; @Noble2022] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@NakaSantos2012].
-
-A phylogenetic tree was created using the Open Tree of Life (OTL) with the *rotl* package in R [vers.
-`r utils::packageVersion("rotl")`, ].
-We resolved all polytomies in the tree and replaced any missing taxa with closely related species.
-Branch lengths were computed using Gafen's method []
-
-@Guangchuang2017
+This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @NakagawaSantos2012; @Noble2022] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@NakagawaSantos2012].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R [vers.
+`r utils::packageVersion("rotl")`, @rotl2016], and plotted using *ggtree* [vers.
+`r utils::packageVersion("ggtree")`, @Guangchuang2017].
+We resolved all polytomies in the tree.
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989].
+We used the R packages *ape* [vers.
+`r utils::packageVersion("ape")`, @ape] and *phytools* [vers.
+`r utils::packageVersion("phytools")`, @Revell2012] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+
+#### *Multi-level Meta-regression (MLMR) Models*
 
@@
 
-## *Results*
+## **Results**
 
@@
 Not sure how that happened, but it's now fixed.
-hist(lnRRQ10_data$V)
+#hist(lnRRQ10_data$V)
 
@@
 # Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
-  hist(lnCVRQ10_data$V)
+  #hist(lnCVRQ10_data$V)
 
@@
 ```{r, fig1, fig.align='center', fig.cap= "Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments"}
+
 col <- c("#0871B9", "#F3B40D", "#1BB908")
@@
 
-  p1.2
    p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
 
-   p1.2.2
-  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
-  ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
-```
-
-```{r, fig2, fig.align='center', fig.cap= "lnCVR Q10 across marine, freshwater and terrestrial environments"}
+  #ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
+  #ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
 
@@
    p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
-  p2
-  p2.2
-   ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
-  ggsave(p2.2, filename = "./output/figures/fig2.2.png")
+   #ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
+  #ggsave(p2.2, filename = "./output/figures/fig2.2.png")
+
+  phylo / (p1.2/p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
 ```
@@
 
+### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
+
 ### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
-### *Does between-individual variation in acclimation capacities differ across terrestrial and aquatic ectotherms?*
 
@@
       p1 <- d + 
-            geom_tiplab(size=2, offset = 10) + 
+            #geom_tiplab(size=2, offset = 10) + 
             geom_tippoint(aes(color=habitat), size = 2) +
@@
       # Plot a heatmap of N for each trait around the phylogeny.
-   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  
+   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  colnames = FALSE, 
                colnames_position="bottom", legend_title = "N", 
@@
 
-   phylo
-ggsave(filename = "fig4.png", path = "./output/figures/", phylo, device = "png", width = 10, height = 9, units = "in")
+ggsave(filename = "fig4.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in") 
 ```
 
+## **Discussion**
+
 ## References

### 2023-01-09 ms.rmd
Fig 1 complete

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage)
 
@@
 
-Daniel W.A. Noble^1, Fonti Kar^2, Frank Seebacher^3, Alex Bush^4, & Shinichi Nakagawa^2
+Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$
 
@@
 
-Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) quantify the degree
-
-ectotherms are capable of physiological plasticity in rates: 1)
+Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) quantify the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise and 3) test whether climate variability and predictability explain a populations capacity to respond plastically.
 
@@
 
-  #ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
-  #ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")
+  ggsave(p1.2, filename = "./output/figures/fig1.pdf", width = 11.5, height = 8)
+  ggsave(p1.2.2, filename = "./output/figures/fig1.1.pdf")
 
@@
    p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
-   #ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
-  #ggsave(p2.2, filename = "./output/figures/fig2.2.png")
-
-  phylo / (p1.2/p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-
+   ggsave(p2, filename = "./output/figures/fig2.pdf", width = 11.5, height = 8)
+  ggsave(p2.2, filename = "./output/figures/fig2.2.pdf")
+
+  #(phylo) / (p1.2 / p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+  fig1 <- image_read("./output/figures/fig1_final.png")
+  fig1
 ```
@@
 
-```{r figphylogeny, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
+```{r fig1a, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
  # Map data to tree. Just one variable for now
@@
 
-ggsave(filename = "fig4.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in") 
+ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in") 
 ```

### 2023-01-09 ms.rmd
Starting writing intro

@@
 
-Variable thermal environments are expected to result in strong selection pressures that result in adaptation or the evolution of phenotypic plasticity.
-Plasticity and adaptation are considered critical for population resilience to human-induced climate change.
+Variable thermal environments are expected to result in strong selection pressures that result in adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015].
+Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
+Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015;@Gunderson2015; @Pinsky2019].
+Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015], it is unclear if the magnitude of physiological adjustment is sufficient.
+In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems
+
+Theory suggests that phenotypic plasticity will evolve in variable, but predictable, habitats with empirical data supporting this prediction.
 
@@
 #### *Multi-level Meta-regression (MLMR) Models*
+We controlled for the duration of time organisms were given to acclimate by included scaled acclimation time (mean = 0, SD = 1) in all models.
 
@@
 
-```{r, fig1, fig.align='center', fig.cap= "Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments"}
-
+```{r, fig1, fig.align='center', fig.cap= "**Phylogeny and Q10 estimate for acute and acclimation type effects**.
+A) Phylogenetic distribution of taxa contained within the data.
+Total number of acute and acclimation type Q10 effect sizes are highlighted as well as if the taxa is marine, freshwater or terrestrial.
+Silouettes are representative taxa of major clades within the tree.
+B) Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments.
+C) lnCVR Q10 across traits for marine, freshwater and terrestrial systems.
+Note there were no differences between acute and acclimation Q10 types.
+k = total number of effect size estimates while numbers in brackets indicate the number of species."}
+
+# Load and plot Figure 1.
+Note that this figure was derived using 3 separate code chunks described below.
+Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
+  fig1 <- image_read("./output/figures/fig1_final.png")
+  fig1
+##################
+  # Figure 1a plot
+##################
+   # Map data to tree. Just one variable for now
+      d <- ggtree(tree, layout="circular") %<+% tree_data
+
+      # Plot the tree
+      scales1 <- c("#053061", "#D1E5F0", "#67001F")
+      scales2 <- c("#053061", "#E7E0DB", "#67001F")
+      p1 <- d + 
+            #geom_tiplab(size=2, offset = 10) + 
+            geom_tippoint(aes(color=habitat), size = 2) +
+            labs(color = "Habitat") + 
+            scale_colour_manual(values = scales1)
+
+      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
+      matrix_data <- as.data.frame(data_wide %>%
+                  mutate(trait_category = ifelse(trait_category %in% 
+                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
+                  group_by(species_full, trait_category)   %>% 
+                  summarise(n = n())                       %>% 
+                  spread(trait_category, n, fill = 0))
+
+      row.names(matrix_data) <- matrix_data$species_full
+      matrix_data <- matrix_data[,c(2:8)]
+
+      colnames(matrix_data)[c(1,3,6)] <- c("Antioxidants", "Metabolic Enzymes", "Other")
+
+      # Alternatively, summarise total effect sizes per species for acute and acclimation
+      matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
+                      group_by(species_full, type) %>% 
+                      summarise(n = n()) %>% 
+                      spread(type, n, fill = 0) %>% data.frame()
+                     # mutate(acclim = as.character(cut(acclim, breaks = c(0,15, 20, 25, 30, 40, 50))),
+                      #        acute = as.character(cut(acute, breaks = c(0,15, 20, 25, 30, 40, 50))))
+
+      row.names(matrix_data2) <- matrix_data2$species_full
+      matrix_data2 <- matrix_data2[,2:3]
+
+      # Plot a heatmap of N for each trait around the phylogeny.
+   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  colnames = FALSE, 
+               colnames_position="bottom", legend_title = "N", 
+               colnames_angle=360, colnames_offset_y = 0, colnames_offset_x = -1.5, 
+               hjust=0, font.size=3, width = 0.35) + 
+                scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
+
+ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
+##################
+  # Figure 1b plot
+##################
 col <- c("#0871B9", "#F3B40D", "#1BB908")
@@
 
+##################
+  # Figure 1c plot
+################## 
   # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
@@
 
-  fig1 <- image_read("./output/figures/fig1_final.png")
-  fig1
 ```
@@
 
+### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
+
+### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
+
+```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
+
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
+
+p8.1.2 <- p8.1 / p8.2
+
+ggsave(p8.1.2, filename = "./output/figures/fig8.png")
+```
+
+```{r, fig9, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
+
+p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
+
+p91.2 <- p9.1 / p9.2
+
+ggsave(p91.2, filename = "./output/figures/fig9.png")
+```
+
+## **Discussion**
+
+## References
+
+## Extra Figures
+
 ```{r, fig4, fig.align='center', fig.cap= "I2 estimates"}
@@
 ```
-
-```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
-
- col <- c("#0871B9", "#F3B40D", "#1BB908")
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
-
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
-
-p8.1.2 <- p8.1 / p8.2
-
-ggsave(p8.1.2, filename = "./output/figures/fig8.png")
-```
-
-```{r, fig9, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
-
- col <- c("#0871B9", "#F3B40D", "#1BB908")
-p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
-
-p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
-
-p91.2 <- p9.1 / p9.2
-
-ggsave(p91.2, filename = "./output/figures/fig9.png")
-```
-
-### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
-
-### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
-
-```{r fig1a, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
- # Map data to tree. Just one variable for now
-      d <- ggtree(tree, layout="circular") %<+% tree_data
-
-      # Plot the tree
-      scales1 <- c("#053061", "#D1E5F0", "#67001F")
-      scales2 <- c("#053061", "#E7E0DB", "#67001F")
-      p1 <- d + 
-            #geom_tiplab(size=2, offset = 10) + 
-            geom_tippoint(aes(color=habitat), size = 2) +
-            labs(color = "Habitat") + 
-            scale_colour_manual(values = scales1)
-
-      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
-      matrix_data <- as.data.frame(data_wide %>%
-                  mutate(trait_category = ifelse(trait_category %in% 
-                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
-                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
-                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
-                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
-                  group_by(species_full, trait_category)   %>% 
-                  summarise(n = n())                       %>% 
-                  spread(trait_category, n, fill = 0))
-
-      row.names(matrix_data) <- matrix_data$species_full
-      matrix_data <- matrix_data[,c(2:8)]
-
-      colnames(matrix_data)[c(1,3,6)] <- c("Antioxidants", "Metabolic Enzymes", "Other")
-
-      # Alternatively, summarise total effect sizes per species for acute and acclimation
-      matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
-                      group_by(species_full, type) %>% 
-                      summarise(n = n()) %>% 
-                      spread(type, n, fill = 0) %>% data.frame()
-                     # mutate(acclim = as.character(cut(acclim, breaks = c(0,15, 20, 25, 30, 40, 50))),
-                      #        acute = as.character(cut(acute, breaks = c(0,15, 20, 25, 30, 40, 50))))
-
-      row.names(matrix_data2) <- matrix_data2$species_full
-      matrix_data2 <- matrix_data2[,2:3]
-
-      # Plot a heatmap of N for each trait around the phylogeny.
-   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  colnames = FALSE, 
-               colnames_position="bottom", legend_title = "N", 
-               colnames_angle=360, colnames_offset_y = 0, colnames_offset_x = -1.5, 
-               hjust=0, font.size=3, width = 0.35) + 
-                scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
-
-ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in") 
-```
-
-## **Discussion**
-
-## References

### 2023-01-09 ms.rmd
Re-wording last paragraph of intro

@@
 
-Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) quantify the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise and 3) test whether climate variability and predictability explain a populations capacity to respond plastically.
+Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise, by applying new effect sizes that capture changes in physiological trait variance, and 3) test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
 

### 2023-01-10 R/1_data_process.R
Update so that orders and class in data again

@@ -59,7 +59,7 @@ data_wide <- data_wide %>%
          lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                    name = "acclim"),
          obs = 1:n()) %>%
-  dplyr::select(-c(data_source, source_page,phylum, class, order, family, genus, species, geo_location, details, notes)) %>%
+  dplyr::select(-c(data_source, source_page, genus, species, geo_location, details, notes)) %>%
   filter_if(~is.numeric(.), all_vars(!is.infinite(.)))
 
 # #******** Problem with effect size calculation. V_lnVR and V_lnCVR are negative for a couple studies, should not be! Hence warning messages NaN in plotting of precision; explored this probalem more. It's actually incorrect data in the old dataset from Frank. Fonti explored the extraction for p088_o and error bars not found, sample sizes not correct. For second study, the N value was incorrect, should have been N = 5 not 0.11. Will exclude p_088_o from the data. Fonti did a check and tried to re-extract but in the end missing error so excluded

### 2023-01-10 R/1_data_process.R
Fixed an error in data_long. Given we have 4 more columns selected we need to shift column selection of effect size when pivoting longer

@@ -75,7 +75,7 @@ write.csv(data_wide, file = "./output/data/data_final_wide.csv", row.names = FAL
 # We want to be able to reorganise the data longitudianlly based on the two acute and acclimation data. Extract the data in chunks
 
 data_long <- data_wide %>%
-  pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
+  pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)+4, values_to = "effect_size", values_drop_na = FALSE) %>% 
   mutate(V = ifelse(name == "lnRR_Q10_acute_t1", V_lnRR_Q10_acute_t1, 
                     ifelse(name == "lnRR_Q10_acute_t2", V_lnRR_Q10_acute_t2, 
                            ifelse(name == "lnRR_Q10_acclim", V_lnRR_Q10_acclim, 

### 2023-01-10 R/functions.R
Add function for plot theme

@@ -672,4 +672,41 @@ f_plot <- function(res, title = "", place = "positive") {
 #     legend.position="none")
 # }
 
+### Adding plotting theme function from Glenn Tattersall (Brock Uni). Probably won't use, but looks great!
 
+ggtheme <- function(base_size=12, base_line=0.3) {
+  theme(
+    
+    text =        element_text(size=base_size),
+    line =        element_line(size=base_line, linetype="solid"),
+    
+    axis.text.x = element_text(size=base_size*0.8, colour='black',  hjust=0.5, vjust=1, angle=0),
+    axis.text.y = element_text(size=base_size*0.8, colour='black', hjust=1, vjust=0.5, angle=0),
+    axis.line.x = element_line(size=base_line),
+    axis.line.y = element_line(size=base_line),
+    
+    axis.title.x =  element_text(size = base_size, vjust = 1, margin=unit(c(3,0,0,0),"mm")),
+    axis.title.y =  element_text(size = base_size, angle = 90, vjust = 0.5, margin=unit(c(0,3,0,0),"mm")),
+    axis.ticks = element_line(size=base_line),
+    axis.ticks.length = unit(0.3, "lines"),
+    
+    panel.background = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.border     = element_rect(fill=NA, colour=NA, size=base_line),
+    panel.spacing    = unit(1, "lines"),
+    
+    legend.background = element_rect(fill="transparent", colour="transparent"),
+    legend.key =       element_rect(fill="transparent", colour="transparent"),
+    legend.text=       element_text(size=base_size),
+    
+    strip.background =  element_blank(),
+    strip.text.x =      element_text(size = base_size * 0.8),
+    strip.text.y =      element_text(size = base_size * 0.8, angle = -90),
+    strip.switch.pad.grid = unit(0, "mm"),
+    strip.switch.pad.wrap = unit(0, "mm"),
+    
+    plot.margin =       unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
+    plot.title =        element_text(size = base_size * 1.2),
+    plot.background =   element_rect(colour = "transparent", fill="transparent", size=base_line)
+  )}

### 2023-01-10 ms.rmd
UPdated MS with summary of results

@@
 ---
-title: "Reduced plasticity and opportunity for selection across terrestrial ectotherm populations"
+title: "Double trouble: Terrestrial ectortherm populations have both reduced opportunity for selection and physiological plasticity"
 bibliography: ./bib/refs.bib
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = TRUE, warning = FALSE, tidy = TRUE, fig.width = 10)
 ## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
@@
       tot_spp <- sum(spp_habitat[,2])
+
+    # Taxa
+      taxa_sum <- data_wide %>%  
+              group_by(habitat, phylum, class) %>% 
+              summarise(spp = length(unique(species_full)), n = n()) %>%  
+              data.frame()
+
+      taxa_sum_long <- data_long2 %>% group_by(habitat, phylum, class) %>% 
+              summarise(spp = length(unique(species_full)), n = n()) %>%  
+              data.frame()
 
@@
 
-Variable thermal environments are expected to result in strong selection pressures that result in adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015].
+Variable thermal environments are expected to result in strong selection pressures that lead to adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015].
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable.
+Despite this theoretical expectation, empirical support for this prediction is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity).
+Reversible forms of phenotypic plasticity, such as acclimatization, may not be expected to adhere to such predictions.
+
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
@@
 In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems
-
-Theory suggests that phenotypic plasticity will evolve in variable, but predictable, habitats with empirical data supporting this prediction.
 
@@
 2.0, @Nakagawa2021c].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021; @Song2021].
 For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
@@
 This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @NakagawaSantos2012; @Noble2022] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@NakagawaSantos2012].
+We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021c; @Noble2022].
 
@@
 ## **Results**
+
+The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single species of Crustacean, Cnidarian), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
+\@ref(fig:fig1)A).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) (Fig.
+\@ref(fig:fig1)A).
 

### 2023-01-12 ms.rmd
Just adding details on traits

@@
 
+    # Traits 
+      traits_habitat <- data_long2 %>%
+                      group_by(habitat, trait_category) %>%
+                      summarise(spp_n = length(unique(species_full)), k = n())
+      traits_all <- data_long2 %>%
+                      group_by(trait_category) %>%
+                      summarise(spp_n = length(unique(species_full)), k = n())
 #########################
@@
 $^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
-$^2$ School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
+$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
 $^3$ SOLES, University of Sydney, Sydney, NSW, Australia
@@
 \@ref(fig:fig1)A).
+
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); me[,"spp_n"]`, $N_{effects}$ = `r me[,"k"]`) and whole-organism performance traits (i.e., sprint speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r sum(per[,"k"])`).
 

### 2023-01-12 ms.rmd
Update to function script. Removed unecessary code. Fixed a rendering bug for inline code

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = TRUE, warning = FALSE, tidy = TRUE, fig.width = 10)
+```{r setup, echo = FALSE, results="hide"}
+knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
 ## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
@@
               group_by(habitat, phylum, class) %>% 
-              summarise(spp = length(unique(species_full)), n = n()) %>%  
-              data.frame()
+              summarise(spp = length(unique(species_full)), n = n()) %>% data.frame()
 
       taxa_sum_long <- data_long2 %>% group_by(habitat, phylum, class) %>% 
-              summarise(spp = length(unique(species_full)), n = n()) %>%  
-              data.frame()
+              summarise(spp = length(unique(species_full)), n = n()) %>% data.frame()
 
@@
       # Do a tree check with original data
-          tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
+        #  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
 
@@
 # Check that taxa dropped
-  tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
+ # tree_checks(data_long, tree, dataCol = "species_full", type = "checks")
 
@@
 
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); me[,"spp_n"]`, $N_{effects}$ = `r me[,"k"]`) and whole-organism performance traits (i.e., sprint speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r sum(per[,"k"])`).
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
 

### 2023-01-12 R/functions.R

@@ -399,314 +399,3 @@ f_plot <- function(res, title = "", place = "positive") {
 
 
 
-
-# ###############
-
-# # I (Shinichi) is too lazy to fill in roxgen stuff - Fonti could you do this???
-
-# #' Title: calculate Q10 and S10 and their sampling variance
-# #'
-# #' @param data 
-# #' @param temp_1 
-# #' @param temp_2 
-# #' @param r1.1 
-# #' @param r1.2 
-# #' @param r2.1 
-# #' @param r2.2 
-# #' @param r1.1._se 
-# #' @param r1.2._se 
-# #' @param r2.1._se 
-# #' @param r2.2._se 
-# #' @param r1.1._N 
-# #' @param r1.2._N 
-# #' @param r2.1._N 
-# #' @param r2.2._N 
-# #'
-# #' @return
-# #' @export
-# #'
-# #' @examples
-# Q10S10 <- function(data, temp_1, temp_2, 
-#                    r1.1, r1.2, r2.1, r2.2, 
-#                    r1.1_se, r1.2_se, r2.1_se, r2.2_se,
-#                    r1.1_N, r1.2_N, r2.1_N, r2.2_N) {
-  
-#   temp_1 <- data[[deparse(substitute(temp_1))]]
-#   temp_2 <- data[[ deparse(substitute(temp_2))]]
-#   r1.1 <- data[[deparse(substitute(r1.1))]]
-#   r1.2 <- data[[deparse(substitute(r1.2))]]
-#   r2.1 <- data[[deparse(substitute(r2.1))]]
-#   r2.2 <- data[[deparse(substitute(r2.2))]]
-#   r1.1_se <- data[[ deparse(substitute(r1.1_se))]]
-#   r1.2_se <- data[[deparse(substitute(r1.2_se))]]
-#   r2.1_se <- data[[deparse(substitute(r2.1_se))]]
-#   r2.2_se <- data[[deparse(substitute(r2.2_se))]]
-#   r1.1_N <- data[[deparse(substitute(r1.1_N))]]
-#   r1.2_N <- data[[ deparse(substitute(r1.2_N))]]
-#   r2.1_N <- data[[deparse(substitute(r2.1_N))]]
-#   r2.2_N <- data[[deparse(substitute(r2.2_N))]]
-  
-#   # cover se to sd
[…]

### 2023-01-13 R/functions.R
Add a function for calculation of correction factor for AICc

@@ -397,5 +397,10 @@ f_plot <- function(res, title = "", place = "positive") {
     legend.position="none")
 }
 
-
+## Calculation a correction factor to apply to AIC to calculate AICc from metafor model objects
+AICc_correction <- function(model){
+  k = length(coef(model)) + length(model$sigma2) + length(model$gamma2) + length(model$tau2)
+  cor = (2*k^2 + 2*k) / model$k - k - 1
+  cor
+}
 

### 2023-01-13 ms.rmd
Clarifying acclimation time in methods

@@
 ---
-title: "Double trouble: Terrestrial ectortherm populations have both reduced opportunity for selection and physiological plasticity"
+title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
                       summarise(spp_n = length(unique(species_full)), k = n())
+    # Acclimation time vary across habitat?
+
+      acclim_time <- data_wide %>% 
+                      group_by(habitat) %>% 
+                      summarise(mean = mean(acclim_period, na.rm = TRUE),
+                                  sd = sd(acclim_period, na.rm = TRUE),
+                                  n = n())
+      test_m_t <- t.test(acclim_period ~ habitat, data = data_wide %>% filter(!habitat == "f"))
+      test_f_t <- t.test(acclim_period ~ habitat, data = data_wide %>% filter(!habitat == "m"))
+      test_f_m <- t.test(acclim_period ~ habitat, data = data_wide %>% filter(!habitat == "t"))
+
 #########################
@@
 
-#### *Comparing variance physiological rates*
+#### *Comparing variance in physiological rates*
  @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
@@
 To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
-It was unclear whether climate at the locations of captive reared organisms would be representative of a populations climate history - particularly for species reared under captive condition for many generations.
+It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
 Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations were used for climate analyses.
@@
 We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian).
+We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
+If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.
 
@@
 #### *Multi-level Meta-regression (MLMR) Models*
-We controlled for the duration of time organisms were given to acclimate by included scaled acclimation time (mean = 0, SD = 1) in all models.
+
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
+In all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`).
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
+Nonetheless, acclimation time was mean-centered (mean = 0) and controlled for in all our models.
+As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).
+
+We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems).
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
+Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020].
+In contrast, a difference in $lnCVR_{Q_{10}}_{acclimation}$ relative to $lnCVR_{Q_{10}}_{acute}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured.
+If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
+Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits.
+Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above).
+Variance in effects within trait categories appeared to vary depending on the trait type in question.
+Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = ,  and terrestrial = )
+
+Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type.
+We predicted that acclimation responses maybe more likely early in development compared to later in development, but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
 
@@
 
-The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single species of Crustacean, Cnidarian), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
+The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
 \@ref(fig:fig1)A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) (Fig.
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig.
 \@ref(fig:fig1)A).
@@
                                             ~1 | spp,
-                                            ~1 + type + habitat | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
+                                            ~1 + habitat | obs),
+                              R = list(species_full = phylo_cor), struct = "HCS", rho = 0, dfs = "contain", 
                               test = "t", data = lnRRQ10_data)
@@
 
+    # Filter out antioxidant
+  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
    # Prune tree
@@
    # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
-  # Filter out antioxidant
-  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size))
-
    model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
@@
                               R = list(species_full = m_phylo), 
-                              str = "HCS", rho = 0, dfs = "contain", 
+                              struct = "HCS", rho = 0, dfs = "contain", 
                               test = "t", data = lnRRQ10_data_m)
 
-  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", data = lnRRQ10_data_m, angle = 45)
+  # Check k is the same for both models (yes) and check which model is best supported
+    AICc1.3_m     <- AIC(model1.3_m) + AICc_correction(model1.3_m)
+    AICc1.3_m_het <- AIC(model1.3_m_het) + AICc_correction(model1.3_m_het)
+    # Clear support for this model. We'll go with this.
+    AICc1.3_m - AICc1.3_m_het
+
+  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", data = lnRRQ10_data_m, angle = 0)
 
   # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + type + trait_category + type:trait_category|gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
 
@@
 
+  # Heteroscedastic variance model for freshwater
+  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_f)
+
+  ## Check support for two models
+  AIC(model1.3_f_het, model1.3_f)
+
+  # Run the Bayesian equivalent of the top supported model. 
    model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
@@
                               R = list(species_full =t_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_t)
+
+  # Heteroscedastic variance model for terrestrial
+  model1.3_t_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full =t_phylo), struct = "HCS", rho = 0, dfs = "contain", 
                               test = "t", data = lnRRQ10_data_t)
@@
   saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
+
   saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
   saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
+
   saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
@@
 
-```{r, fig1, fig.align='center', fig.cap= "**Phylogeny and Q10 estimate for acute and acclimation type effects**.
-A) Phylogenetic distribution of taxa contained within the data.
-Total number of acute and acclimation type Q10 effect sizes are highlighted as well as if the taxa is marine, freshwater or terrestrial.
+```{r, fig1, fig.align='center', fig.cap= "**Taxonomic distribution of acute and acclimation Q10 estimates across major habitats**.
+**A)** Phylogenetic distribution of taxa contained within the data.
+The total number of acute and acclimation type Q10 effect sizes are highlighted as well as whether the taxa is marine, freshwater or terrestrial.
 Silouettes are representative taxa of major clades within the tree.
-B) Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments.
-C) lnCVR Q10 across traits for marine, freshwater and terrestrial systems.
+**B)** Acute and Acclimation lnRR Q10 across marine, freshwater, and terrestrial environments.
+**C)** lnCVR Q10 across traits for marine, freshwater and terrestrial systems.
 Note there were no differences between acute and acclimation Q10 types.
-k = total number of effect size estimates while numbers in brackets indicate the number of species."}
+k = total number of effect size estimates while the numbers in brackets indicate the number of species."}
 
@@
 
+One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats .
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023].
+However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10}}_{acclimation}$ compared to $lnRR_{Q_{10}}_{acute}$ when controlling for acclimation time.
+
 ## References
-
-## Extra Figures
+<br>
+<div id="refs"></div>
+<br>
+
+## Supplemental Results and Figures
 

### 2023-01-13 ms.rmd
tiny

@@
                       summarise(spp_n = length(unique(species_full)), k = n())
+
       # Acclimation time vary across habitat?
@@
 Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
-Nonetheless, acclimation time was mean-centered (mean = 0) and controlled for in all our models.
+To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
 As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).

### 2023-01-15 ms.rmd
Fix grammar error, and also removed some code and added het models for traits to do AIC comparison

@@
 Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`).
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
 To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
@@
 
-  # Check whether there is differences in variances for each habitat
-  model1.2_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 + habitat | obs),
-                              R = list(species_full = phylo_cor), struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
    model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
@@
 
-    # Filter out antioxidant
+    # Filter out antioxidant and NAs
   lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
   lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time))
+
   # Prune tree
@@
   saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
+   saveRDS(model1.3_f_het, file = "./output/models/lnRRQ10_1.3f_het")
   saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
@@
   saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
+   saveRDS(model1.3_t_het, file = "./output/models/lnRRQ10_1.3t_het")
   saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")

### 2023-01-15 ms.rmd
Fixed convergence issue for het freshwater model

@@
 Variance in effects within trait categories appeared to vary depending on the trait type in question.
-Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = ,  and terrestrial = )
+Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = )
 
@@
                               R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_f)
+                              test = "t", data = lnRRQ10_data_f, method = "REML", control=list(iter.max=1000, rel.tol=1e-8))
 
   ## Check support for two models
-  AIC(model1.3_f_het, model1.3_f)
+  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het). # Clearly better supported.
+      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
+  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het
 
   # Run the Bayesian equivalent of the top supported model. 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
 

### 2023-01-16 ms.rmd
Added dela and saved ehet models. ALl were better supported.

@@
 Variance in effects within trait categories appeared to vary depending on the trait type in question.
-Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = )
+Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 25)
 
@@
 
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1|obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
+  # Check which model is better
+    AICc_model1.3_t     <- AIC(model1.3_t) + AICc_correction(model1.3_t)
+    AICc_model1.3_t_het <- AIC(model1.3_t_het) + AICc_correction(model1.3_t_het)
+
+  #  Delta
+    AICc_model1.3_t - AICc_model1.3_t_het
+
+  # Bayesian model
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category |obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
 
@@
         model1.3_m <- readRDS("./output/models/lnRRQ10_1.3m")
+    model1.3_m_het <- readRDS("./output/models/lnRRQ10_1.3m_het")
   model1.3_m_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_m")
         model1.3_f <- readRDS("./output/models/lnRRQ10_1.3f")
+    model1.3_f_het <- readRDS("./output/models/lnRRQ10_1.3f_het")
   model1.3_f_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_f")
         model1.3_t <- readRDS("./output/models/lnRRQ10_1.3t")
+    model1.3_t_het <- readRDS("./output/models/lnRRQ10_1.3t_het")
   model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
@@
 
-ptm <- orchard_plot(model1.3_m, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
+ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
 
-ptf <- orchard_plot(model1.3_f, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
+ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
 
-ptt <- orchard_plot(model1.3_t, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0)
+ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0)
 ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

### 2023-01-16 ms.rmd
Adding climate data R versions

@@
 Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
-For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa.
+For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package (vers.
+`r utils::packageVersion("ncdf4")`).
 We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
@@
 Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type.
-We predicted that acclimation responses maybe more likely early in development compared to later in development, but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+We predicted that acclimation responses would be more likely early in development compared to later in development, but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
 
@@
   # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category |obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 20), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
 
@@
 
-```{r, fig3, fig.align='center', eval = FALSE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
+```{r, fig2, fig.align='center', eval = FALSE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
 

### 2023-01-17 ms.rmd
Trait plot
Removed un-needed code
decrease tree depth. Taking way too long

@@
   # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 20), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
 
@@
 
-lnRRQ10_data %>% group_by(habitat, type, trait_category) %>% summarise(n = n()) %>% data.frame()
+fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+fig2
 

### 2023-01-18 ms.rmd
Fixed terrestrial model. Converged but needed to exclude trait categories with too little data. Just need to be clear on that in methods

@@
 
-```{r setup, echo = FALSE, results="hide"}
+```{r knitrops, echo = FALSE, results="hide"}
 knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
@@
   options(digits = 2)
+
+```
+
+```{r setup, echo = FALSE, results="hide"}
 
@@
 
-    # Filter out antioxidant and NAs
+    # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
   lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
   lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR"))
 

### 2023-01-18 ms.rmd
Noted in stats methods

@@
 Variance in effects within trait categories appeared to vary depending on the trait type in question.
-Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 25)
+Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
+To ensure models converged we limited to trait categories for each habitat with six or more effect sizes.
 
@@
   lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR"))
+  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
 
@@
   # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
 

### 2023-01-19 ms.rmd
Updated MS. Knitted

@@
 ## Function to produce colour palette
-# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can greate a custom colour palelte function using colorRampPallette
+# Note that temp is stored as a factor of 10 C larger, so needs to be divided. Also, we can create a custom colour palette function using colorRampPallette
 colfunc <- colorRampPalette(rev(brewer.pal(10,"RdBu")))
@@
   ## Check support for two models
-  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het). # Clearly better supported.
+  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het) # Clearly better supported.
       AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
@@
 
-```{r, fig2, fig.align='center', eval = FALSE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
-
-ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
+```{r, fig2, fig.align='center', eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
+
+ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS"))
-ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0) +
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS"))
-ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0)
-ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
 
@@
 fig2
-
+ggsave(fig2, filename = "./output/figures/fig2_trait.pdf", height = 10, width = 40, device = "pdf", limitsize = FALSE, units = "cm")
 ```

### 2023-01-19 ms.rmd
Remoce fig alifgn which apparently isn't supported for docx

@@
 
-```{r, fig1, fig.align='center', fig.cap= "**Taxonomic distribution of acute and acclimation Q10 estimates across major habitats**.
+```{r, fig1,  fig.cap= "**Taxonomic distribution of acute and acclimation Q10 estimates across major habitats**.
 **A)** Phylogenetic distribution of taxa contained within the data.
@@
 
-```{r, fig2, fig.align='center', eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
+```{r, fig2,  eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
 

### 2023-01-20 ms.rmd
Some odd rendering behaviour with packages not being loaded. Sometimes works and others not. So, change to base pipe and explicit call to functions. Awkward for inline code, but works

@@
 
-The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
 \@ref(fig:fig1)A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig.
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig.
 \@ref(fig:fig1)A).
 
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
 

### 2023-01-22 ms.rmd
Added a sensitivity analysis that checked if t1 and t2 differed. They did, but not by much at all.

@@
 
-## **Results**
-
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
-\@ref(fig:fig1)A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig.
-\@ref(fig:fig1)A).
-
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
-
-### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
-
 ```{r lnrrq10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
@@
 
+####################################################
+# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
+####################################################
+ # Goal here is to test the assumption that acute Q10's are different or not
+ lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
+
+  model1.s1 <- metafor::rma.mv(effect_size ~  c_accl_time + name, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
 ```
+
+## **Results**
+
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
+\@ref(fig:fig1)A).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig.
+\@ref(fig:fig1)A).
+While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), they were in the same direction and only differed by ~10%.
+As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
+
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+
+### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
 

### 2023-01-23 ms.rmd
Sort of fixed image

@@
 ### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
+
+The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small ().
+Considering acute responses of acclimated animals at high temperatures are also expected to increase (see above), acclimatization is not likely going to provide adaptive benefits under climate change.
 
@@
 
-```{r, fig2,  eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
+```{r, fig2, out.width = "100%", eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
 
@@
 fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-fig2
 ggsave(fig2, filename = "./output/figures/fig2_trait.pdf", height = 10, width = 40, device = "pdf", limitsize = FALSE, units = "cm")
+
+img_fig2 <- magick::image_read("./output/figures/fig2_trait.pdf")
+img_fig2
 ```

### 2023-01-24 ms.rmd
Rewording sentence to be more clear

@@
 The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small ().
-Considering acute responses of acclimated animals at high temperatures are also expected to increase (see above), acclimatization is not likely going to provide adaptive benefits under climate change.
+Considering acute responses of animals acclimated to high temperatures is generally slightly elevated compared to cold acclimated animals ($\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change.
 

### 2023-01-25 ms.rmd
Small update on grammar

--- 2023-01-23 ms.rmd
@@
 The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small ().
-Considering acute responses of acclimated animals at high temperatures are also expected to increase (see above), acclimatization is not likely going to provide adaptive benefits under climate change.
+Considering acute responses of animals acclimated to high temperatures is generally slightly elevated compared to cold acclimated animals ($\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change, on average.
 

### 2023-01-25 ms.rmd
Added average across all habitats. Just arithmetic average at this point. And started writing a bit about Q10 results lnRR

@@
   change_t <- abs(t_acclim - t_acute)*100; quantile(change_t, c(0.025, 0.975))
+  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
 
@@
 
-The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small ().
+Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (Figure \@ref(fig:fig1)B) amounting to a `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) reduction in freshwater and a `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) reduction in marine environments.
 Considering acute responses of animals acclimated to high temperatures is generally slightly elevated compared to cold acclimated animals ($\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change, on average.

### 2023-01-26 ms.rmd
Completed first paragraph

@@
 Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (Figure \@ref(fig:fig1)B) amounting to a `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) reduction in freshwater and a `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) reduction in marine environments.
-Considering acute responses of animals acclimated to high temperatures is generally slightly elevated compared to cold acclimated animals ($\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change, on average.
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (Figure \@ref(fig:fig1)B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, Figure  \@ref(fig:fig1)B).
+Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change.
 

### 2023-02-10 ms.qmd
Kniting; need to fix figures renders, digits to

--- 2023-01-26 ms.rmd
@@
 csl: ./bib/ecology-letters.csl
-output: 
-  bookdown::word_document2:
-    toc: no
-    toc_depth: 6
-    number_sections: false
-    reference_docx: ./bib/template.docx
-  bookdown::html_document2:
-    code_folding: hide
-    number_sections: no
-    toc: yes
-    toc_depth: 6
-    toc_float: yes
-    bibliography: refs.bib
+format:
+  docx:
+    reference-doc: ./bib/template.docx
 editor_options: 
   chunk_output_type: console
+execute:
+  freeze: auto  # re-render only when source changes
+  cache: true
 ---
@@
 
-```{r, fig1,  fig.cap= "**Taxonomic distribution of acute and acclimation Q10 estimates across major habitats**.
+```{r}
+#| label: fig1
+#| fig-cap: Taxonomic distribution of acute and acclimation Q10 estimates across major habitats.
 **A)** Phylogenetic distribution of taxa contained within the data.
@@
 Note there were no differences between acute and acclimation Q10 types.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species."}
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+#| warning: false
 

### 2023-02-10 ms.qmd
Fixed figures, but need to format and digits

@@
   cache: true
+  echo: false
+  warning: false
+  error: false
+  include: true
+crossref:
+  fig-title: '**Fig**'
+  fig-labels: arabic
+  title-delim: "**.**"
 ---
 
-```{r knitrops, echo = FALSE, results="hide"}
+```{r, knitrops}
 knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
@@
 
-```{r setup, echo = FALSE, results="hide"}
+```{r setup}
 
@@
 
-```{r data_setup_summary, echo = FALSE, results="hide"}
+```{r data_setup_summary}
 
@@
 
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig.
-\@ref(fig:fig1)A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig.
-\@ref(fig:fig1)A).
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (@fig-1 A).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
 While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), they were in the same direction and only differed by ~10%.
@@
 Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (Figure \@ref(fig:fig1)B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, Figure  \@ref(fig:fig1)B).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, @fig-1 B).
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change.
@@
 ```{r}
-#| label: fig1
-#| fig-cap: Taxonomic distribution of acute and acclimation Q10 estimates across major habitats.
+#| label: fig-1
+#| fig-cap: "Taxonomic distribution of acute and acclimation Q10 estimates across major habitats.
 **A)** Phylogenetic distribution of taxa contained within the data.
@@
 Note there were no differences between acute and acclimation Q10 types.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species."
 #| warning: false

### 2023-02-11 ms.qmd
Testing cite. Use ctrl+space if does not show

@@
 title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
-bibliography: ./bib/refs.bib
+bibliography: [./bib/refs.bib]
 csl: ./bib/ecology-letters.csl
@@
 Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015], it is unclear if the magnitude of physiological adjustment is sufficient.
-In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems
+In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems.
 

### 2023-02-19 ms.rmd
Update refs because of integration with paperpile. So, cite keys have changed.

@@
 
-Variable thermal environments are expected to result in strong selection pressures that lead to adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015].
+Variable thermal environments are expected to result in strong selection pressures that lead to adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable.
@@
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
-Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015;@Gunderson2015; @Pinsky2019].
-Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015], it is unclear if the magnitude of physiological adjustment is sufficient.
+Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi;@Gunderson2015-hz; @Pinsky2019-fn].
+Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.
 In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems
@@
 We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015] and updated @Seebacher2015's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
 More specifically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
-We limited our search to articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015 searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We limited our search to articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015-wi searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
 
-Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016].
-We also cross-checked papers we found in our searches with a recent paper by @Havird2020, which also updates  @Seebacher2015's dataset.
-We included any papers that were missed between our searches and those of @Havird2020 from the dates 2013-2017.
-@Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015 dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that @Seebacher2015 included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
+Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016-ge].
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates  @Seebacher2015-wi's dataset.
+We included any papers that were missed between our searches and those of @Havird2020-mj from the dates 2013-2017.
+@Havird2020-mj added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by @Seebacher2015 to answer questions on acclimation across ectotherms.
+As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on acclimation across ectotherms.
 
@@
 We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@Pick2019].
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
 We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied.
@@
 
-Following @Noble2022 we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+Following @Noble2022-ty we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
 These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations for their sampling variances.
@@
 
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022] as follows:
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
 
@@
 Log transformation of this ratio makes the effect size normally distributed.
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@hedges1999meta; @laj2011] when the numerator and denominator are measured at different temperatures.
+Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
-The sampling variance for equation \@ref(eq:lnq10) can be computed as follows (as described in @Noble2022):
+The sampling variance for equation \@ref(eq:lnq10) can be computed as follows (as described in @Noble2022-ty):
 
@@
 #### *Comparing variance in physiological rates*
- @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+ @Nakagawa2015-fo recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
 *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
 
@@
 Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
-While this is a useful metric, as discussed by @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+While this is a useful metric, as discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
 As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015].
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-xj].
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-xj show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-xj].
 As such, using the detailed information on the trait type, and its associated units from a given study, we categorized each effect size into one of 12 trait categories.
@@
 
-Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
+Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
 For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package (vers.
@@
 `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010].
+`r utils::packageVersion("brms")` @Burkner2018-ur; @Burkner2017-wg; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
 We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021c].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021; @Song2021].
+2.0, @Nakagawa2021-ls].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba].
 For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
@@
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @NakagawaSantos2012; @Noble2022] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@NakagawaSantos2012].
-We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021c; @Noble2022].
+This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-su; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-su].
+We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
 
 A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R [vers.
-`r utils::packageVersion("rotl")`, @rotl2016], and plotted using *ggtree* [vers.
-`r utils::packageVersion("ggtree")`, @Guangchuang2017].
+`r utils::packageVersion("rotl")`, @Michonneau2016-if], and plotted using *ggtree* [vers.
+`r utils::packageVersion("ggtree")`, @Yu2017-wj].
 We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989].
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
 We used the R packages *ape* [vers.
-`r utils::packageVersion("ape")`, @ape] and *phytools* [vers.
-`r utils::packageVersion("phytools")`, @Revell2012] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+`r utils::packageVersion("ape")`, @Paradis2019-gx] and *phytools* [vers.
+`r utils::packageVersion("phytools")`, @Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
 
@@
 Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`).
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
 To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
@@
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
-Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020].
+Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj].
 In contrast, a difference in $lnCVR_{Q_{10}}_{acclimation}$ relative to $lnCVR_{Q_{10}}_{acute}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured.
@@
 One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats .
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023].
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
 However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10}}_{acclimation}$ compared to $lnRR_{Q_{10}}_{acute}$ when controlling for acclimation time.

### 2023-03-01 ms.qmd
Update to docs
tiny change
Update to quarto and refs, eqns working

@@
 title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
-bibliography: [./bib/refs.bib]
+bibliography: ./bib/refs.bib
 csl: ./bib/ecology-letters.csl
@@
   fig-labels: arabic
-  title-delim: "**.**"
+  title-delim: "**-**"
+  fig-prefix: "Figure"
+  tbl-labels: "**Table**"
 ---
 
-```{r, knitrops}
-knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
-## numbers >= 10^5 will be denoted in scientific notation,		  ## numbers >= 10^5 will be denoted in scientific notation,
-  ## and rounded to 2 digits		  ## and rounded to 2 digits
-  options(digits = 2)
-
-```
-
-```{r setup}
-
+```{r}
+#| label: setup
+#| echo: false
 ##################################
@@
 
+options(digits = 3, scipen = 3)
 ```
@@
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
-Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015;@Gunderson2015; @Pinsky2019].
-Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015], it is unclear if the magnitude of physiological adjustment is sufficient.
+Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis @Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn].
+Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.
 In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems.
@@
 We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015] and updated @Seebacher2015's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
 More specifically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
-We limited our search to articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015 searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We limited our search to articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015-wi searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
 
-Our search resulted in 1,321 papers for screening in Rayyan [@ouzzani2016].
-We also cross-checked papers we found in our searches with a recent paper by @Havird2020, which also updates  @Seebacher2015's dataset.
-We included any papers that were missed between our searches and those of @Havird2020 from the dates 2013-2017.
-@Havird2020 added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015 dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that @Seebacher2015 included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
+Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates  @Seebacher2015-wi's dataset.
+We included any papers that were missed between our searches and those of @Havird2020-mj from the dates 2013-2017.
+@Havird2020-mj added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by @Seebacher2015 to answer questions on acclimation across ectotherms.
+As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on acclimation across ectotherms.
 
@@
 
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022] as follows:
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
 
 $$
-\begin{equation} 
   lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-(\#eq:lnq10)
-\end{equation} 
-$$
+$$ {#eq-lnq10}
 
@@
 Log transformation of this ratio makes the effect size normally distributed.
-Equation \@ref(eq:lnq10) is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@hedges1999meta; @laj2011] when the numerator and denominator are measured at different temperatures.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
 This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
-The sampling variance for equation \@ref(eq:lnq10) can be computed as follows (as described in @Noble2022):
+The sampling variance for @eq-lnq10 can be computed as follows (as described in @Noble2022-ty):
 
 $$
-\begin{equation} 
   s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-  (\#eq:Vlnq10)
-\end{equation} 
+$$ {#eq-Vlnq10}
+
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations and $N_{1}$ and $N_{2}$ are the sample sizes in group 1 and 2, respectively.
+
+#### *Comparing variance in physiological rates*
+@Nakagawa2015-fo recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
 $$
-
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations and $N_{1}$ and $N_{2}$ are the sample sizes in group 1 and 2, respectively.
-
-#### *Comparing variance in physiological rates*
- @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
-
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$${#eq-lnq10VR}
 $$
-\begin{equation} 
-lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-(\#eq:lnq10VR)
-\end{equation} 
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slnq10VR}
+
+ @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10&deg;C temperature change along with its sampling variance (@eq-slnq10VR).
+While this is a useful metric, as discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
+
 $$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR}
 $$
-\begin{equation} 
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-(\#eq:slnq10VR)
-\end{equation} 
-$$
-
-Equations \@ref(eq:lnq10VR) and \@ref(eq:slnq10VR) describe the change in physiological rate variance (eqn \@ref(eq:lnq10VR)) across a 10&deg;C temperature change along with its sampling variance (eqn \@ref(eq:slnq10VR)).
-While this is a useful metric, as discussed by @nakagawa2015meta there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
-As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
-
-$$
-\begin{equation} 
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-(\#eq:lnq10CVR)
-\end{equation} 
-$$
-$$
-\begin{equation} 
 s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-(\#eq:slnq10CVR)
-\end{equation} 
-$$
+$$ {#eq-slncvr}
 
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015].
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
 As such, using the detailed information on the trait type, and its associated units from a given study, we categorized each effect size into one of 12 trait categories.
@@
 
-Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020].
-For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package (vers.
-`r utils::packageVersion("ncdf4")`).
+Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package [vers.
+`r utils::packageVersion("ncdf4")`, @Pierce2021].
 We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
@@
 `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010].
+`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
 We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021c].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021; @Song2021].
+2.0, @Nakagawa2021-ls].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba].
 For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
@@
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @NakagawaSantos2012; @Noble2022] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@NakagawaSantos2012].
-We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021c; @Noble2022].
+This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
 
 A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R [vers.
-`r utils::packageVersion("rotl")`, @rotl2016], and plotted using *ggtree* [vers.
-`r utils::packageVersion("ggtree")`, @Guangchuang2017].
+`r utils::packageVersion("rotl")`, @Michonneau2016-if], and plotted using *ggtree* [vers.
+`r utils::packageVersion("ggtree")`, @Yu2017-wj].
 We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989].
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
 We used the R packages *ape* [vers.
-`r utils::packageVersion("ape")`, @ape] and *phytools* [vers.
-`r utils::packageVersion("phytools")`, @Revell2012] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+`r utils::packageVersion("ape")`, @Paradis2019-gx] and *phytools* [vers.
+`r utils::packageVersion("phytools")`, @Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
 
@@
 
-```{r, fig2, out.width = "100%", eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}
-
+```{r}
+#| label: fig-2
+#| fig-cap: Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems
 ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +

### 2023-03-10 R/functions.R
New p-value function

@@ -404,3 +404,14 @@ AICc_correction <- function(model){
   cor
 }
 
+#' @title p_value
+#' @description Checks p-value and assigned to catagories unless non-significant then gives actual p
+#' @param x the value to check against
+#' 
+p_value <- function(x){
+  if(x <= 0.0001) {tmp = "< 0.0001"}
+  if(x <= 0.001 & x >= 0.0001) {tmp ="< 0.001"}
+  if(x <= 0.01 & x >= 0.001) {tmp ="< 0.01"}
+  if(x >= 0.01) {tmp = round(x, digits =2)}
+  return(tmp)
+}

### 2023-03-10 ms.qmd
Updated
Added p-value calcs

@@
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
-While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), they were in the same direction and only differed by ~10%.
+While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
 As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
@@
 In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, @fig-1 B).
-Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p < 0.001), acclimatization is not likely going to provide adaptive benefits under climate change.
-
-```{r, lncvrq10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
+Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
+
+```{r, lncvrq10}
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+
 #############
@@
 
-```
-
-```{r, wildlnRR10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
-#######################################
-  ## lnRRQ10 from Wild Populations ##
-#######################################
-##################################################
-  # Organise the data and prune tree
-##################################################
-
-# Bring in Climate data
-climate <- read.csv("./output/climate_data/temp_timeseries.csv")
-
-# Create a match column.
-climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
-
-# Subset the data
-lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
-
-# Now, join climate data to full data. This will give us all the climate variability data for each site across time
-lnRRQ10_data_wild <- left_join(lnRRQ10_data_wild, climate2, by = "match")
-
-# Check and prune tree
-tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
-        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
-
-# Scale data
-        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
-                                                          acf_all_c = scale(acf_all))
-###################################################
-  # Model 3.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.2
-  saveRDS(model3.2, file = "./output/models/lnRRQ10_3.2")
-  saveRDS(model3.2_bayes, file = "./output/models/lnRRQ10_3.2_bayes")
-
-  } else{
-        model3.2 <- readRDS("./output/models/lnRRQ10_3.2")
-  model3.2_bayes <- readRDS("./output/models/lnRRQ10_3.2_bayes")
-}
-
-####################################################
-  ## Model 3.2: Bayesian Contrasts
-###################################################
-  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
-  f_acute_wild  <- posteriors_3.2[,"b_Intercept"]
-  f_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
-  m_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
-  m_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
-  t_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
-  t_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
-
-# Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10_wild <- exp(f_acute_wild) ; mean(f_acute_Q10_wild)
-  f_acclim_Q10_wild <- exp(f_acclim_wild); mean(f_acclim_Q10_wild)
-   m_acute_Q10_wild <- exp(m_acute_wild) ; mean(f_acute_Q10_wild)
-  m_acclim_Q10_wild <- exp(m_acclim_wild); mean(f_acclim_Q10_wild)
-   t_acute_Q10_wild <- exp(t_acute_wild) ; mean(t_acute_Q10_wild)
-  t_acclim_Q10_wild <- exp(t_acclim_wild); mean(t_acclim_Q10_wild)
-
-# % change in acclimation on log scale
-  change_f_wild <- abs(f_acclim_wild - f_acute_wild)*100; quantile(change_f_wild, c(0.025, 0.975))
-  change_m_wild <- abs(m_acclim_wild - m_acute_wild)*100; quantile(change_m_wild, c(0.025, 0.975))
-  change_t_wild <- abs(t_acclim_wild - t_acute_wild)*100; quantile(change_t_wild, c(0.025, 0.975))
-
-# % change on Q10 scale
-  p_change_f_q10_wild <- (exp(f_acclim_wild - f_acute_wild)-1)*100; quantile(p_change_f_q10_wild, c(0.025, 0.975))
-  p_change_m_q10_wild <- (exp(m_acclim_wild - m_acute_wild)-1)*100; quantile(p_change_m_q10_wild, c(0.025, 0.975))
-  p_change_t_q10_wild <- (exp(t_acclim_wild - t_acute_wild)-1)*100; quantile(p_change_t_q10_wild, c(0.025, 0.975))
-
-####################################################
-  # Model 3.3: Model environmental variability by acute 
-  #  acclim 
-####################################################
-  rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model3.3, file = "./output/models/lnRRQ10_3.3")
-  saveRDS(model3.3_bayes, file = "./output/models/lnRRQ10_3.3_bayes")
-
-  } else{
-        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
-  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
-  }
-
-################################################################
-  # Model 3.7: Environmental autocorrelation model by acute/acclim
-################################################################
-  if(rerun){
-  # More realistic model with 
-  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model3.4, file = "./output/models/lnRRQ10_3.4")
-  saveRDS(model3.4_bayes, file = "./output/models/lnRRQ10_3.4_bayes")
-
-  } else{
-        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
-  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
-  }
-
-################################################################
-  # Model 3.5: Environmental variability  model
-################################################################
-  if(rerun){
-  # More realistic model with 
-  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.5
-  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
-  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")
-
-  } else{
-        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
-  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
-  }
-
-################################################################
-  # Model 3.6: Environmental autocorrelation model
-################################################################
-
-  if(rerun){
-  # More realistic model with 
-  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
-
-  # Save model3.6
-  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
-  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")
-
-  } else{
-        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
-  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
-  }
-
-################################################################
-  # Model 3.7: Environmental variability and autocorrelation model
-################################################################
-
-  if(rerun){
-  # More realistic model with 
-  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.7
-  saveRDS(model3.7, file = "./output/models/lnRRQ10_3.7")
-  saveRDS(model3.7_bayes, file = "./output/models/lnRRQ10_3.7_bayes")
-
-  } else{
-        model3.7 <- readRDS("./output/models/lnRRQ10_3.7")
-  model3.7_bayes <- readRDS("./output/models/lnRRQ10_3.7_bayes")
-  }
-
-############################################################################################
-# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
-# differently in each habitat
-############################################################################################  
-  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-  if(rerun){
-  # More realistic model with 
-  model3.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim)
-
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
-  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
-
-  } else{
-        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
-  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 3.8
-#################################################
- posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
-
-    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
-    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
-    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
-
-############################################################################################
-# Model 3.9: Acclimatization lnRRQ10 only. Test if environmental variance explains 
-# differently in each habitat
-############################################################################################
-
-if(rerun){
-  # More realistic model with 
-  model3.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim)
-
-   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model3.9, file = "./output/models/lnRRQ10_3.9")
-  saveRDS(model3.9_bayes, file = "./output/models/lnRRQ10_3.9_bayes")
-
-  } else{
-        model3.9 <- readRDS("./output/models/lnRRQ10_3.9")
-  model3.9_bayes <- readRDS("./output/models/lnRRQ10_3.9_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 3.9
-#################################################
- posteriors <- posterior_samples(model3.9_bayes, "^b")
-
-    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
-    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
-    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
-
-##################################################
-    # Model 3.8, 3.9 and 3.10 - Habitat subset
-##################################################
-    # Subset data to habitat
-    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
-    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
-    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
-
-    # Terrestrial Models
-    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-
-    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-        # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-    # Freshwater Models
-    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-
-    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-       # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-
-     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-
-    # Marine Models
-      model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-
-    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-    # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-
-    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-
-```
-
-```{r wildlncvr, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
-#######################################
-  ## lnCVRQ10 from Wild Populations ##
-#######################################
-##################################################
-  # Organise the data and prune tree
-##################################################
-
-# Bring in Climate data
-climate <- read.csv("./output/climate_data/temp_timeseries.csv")
-
-# Create a match column.
-climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
-
-# Subset the data
-lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
-                              mutate(spp = species_full, 
-                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
-                                     match = interaction(spp, lat, long))
-
-# Now, join climate data to full data. This will give us all the climate variability data for each site across time
-lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
-
-# Check and prune tree
-tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
-        A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
-
-# Scale environment variables
-    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
-                                                        acf_all_c = scale(acf_all))
-###################################################
-  # Model 4.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.2
-  saveRDS(model4.2, file = "./output/models/lnCVRQ10_4.2")
-  saveRDS(model4.2_bayes, file = "./output/models/lnCVRQ10_4.2_bayes")
-
-  } else{
-        model4.2 <- readRDS("./output/models/lnCVRQ10_4.2")
-  model4.2_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
-}
-
-####################################################
-  ## Model 4.2: Bayesian Contrasts
-###################################################
-  posteriors_4.2 <- posterior_samples(model4.2_bayes, pars = "^b")
-  f_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"]
-  f_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_typeacclim"]
-  m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
-  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatm"]
-  t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
-  t_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatt"]
-
-# CVRQ10 values for each category.
-   f_acute_Q10_wild_cvr <- exp(f_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
-  f_acclim_Q10_wild_cvr <- exp(f_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
-   m_acute_Q10_wild_cvr <- exp(m_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
-  m_acclim_Q10_wild_cvr <- exp(m_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
-   t_acute_Q10_wild_cvr <- exp(t_acute_wild_cvr) ; mean(t_acute_Q10_wild_cvr)
-  t_acclim_Q10_wild_cvr <- exp(t_acclim_wild_cvr); mean(t_acclim_Q10_wild_cvr)
-
-# % change in acclimation on log scale
-  change_f_wild_cvr <- abs(f_acclim_wild_cvr - f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
-  change_m_wild_cvr <- abs(m_acclim_wild_cvr - m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
-  change_t_wild_cvr <- abs(t_acclim_wild_cvr - t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
-
-# % change on Q10 scale
-  p_change_f_q10_wild_cvr <- (exp(f_acclim_wild_cvr - f_acute_wild_cvr)-1)*100; quantile(p_change_f_q10_wild_cvr, c(0.025, 0.975))
-  p_change_m_q10_wild_cvr <- (exp(m_acclim_wild_cvr - m_acute_wild_cvr)-1)*100; quantile(p_change_m_q10_wild_cvr, c(0.025, 0.975))
-  p_change_t_q10_wild_cvr <- (exp(t_acclim_wild_cvr - t_acute_wild_cvr)-1)*100; quantile(p_change_t_q10_wild_cvr, c(0.025, 0.975))
-
-####################################################
-  # Model 4.3: Model environmental variability by acute/acclim
-####################################################
-  rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.3
-  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
-  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
-
-  } else{
-        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
-  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
-  }
-
-################################################################
-  # Model 4.4: Environmental autocorrelation model by acute/acclim
-################################################################
-  if(rerun){
-  # More realistic model with 
-  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
-  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
-
-  } else{
-        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
-  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
-  }
-
-################################################################
-  # Model 4.5: Environmental variability
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.5
-  saveRDS(model4.5, file = "./output/models/lnCVRQ10_4.5")
-  saveRDS(model4.5_bayes, file = "./output/models/lnCVRQ10_4.5_bayes")
-
-  } else{
-        model4.5 <- readRDS("./output/models/lnCVRQ10_4.5")
-  model4.5_bayes <- readRDS("./output/models/lnCVRQ10_4.5_bayes")
-  }
-
-################################################################
-  # Model 4.6: Environmental autocorrelation model 
-################################################################
-  if(rerun){
-  # More realistic model with 
-  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.6
-  saveRDS(model4.6, file = "./output/models/lnCVRQ10_4.6")
-  saveRDS(model4.6_bayes, file = "./output/models/lnCVRQ10_4.6_bayes")
-
-  } else{
-        model4.6 <- readRDS("./output/models/lnCVRQ10_4.6")
-  model4.6_bayes <- readRDS("./output/models/lnCVRQ10_4.6_bayes")
-  }
-
-################################################################
-  # Model 4.7: Environmental autocorrelation and variability
-################################################################
- if(rerun){
-  # More realistic model with 
-  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.7
-  saveRDS(model4.7, file = "./output/models/lnCVRQ10_4.7")
-  saveRDS(model4.7_bayes, file = "./output/models/lnCVRQ10_4.7_bayes")
-
-  } else{
-        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")
-  #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
-  }
-
-############################################################################################
-  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
-  # differently in each habitat
-############################################################################################  
-  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-  if(rerun){
-  # More realistic model with 
-  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model4.8
-  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
-  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
-
-  } else{
-        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
-  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.8
-#################################################
- posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
-
-    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
-    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
-    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
-
-############################################################################################
-# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
-# differently in each habitat
-############################################################################################
-
-if(rerun){
-  # More realistic model with 
-  model4.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model4.9, file = "./output/models/lnRRQ10_4.9")
-  saveRDS(model4.9_bayes, file = "./output/models/lnRRQ10_4.9_bayes")
-
-  } else{
-        model4.9 <- readRDS("./output/models/lnRRQ10_4.9")
-  model4.9_bayes <- readRDS("./output/models/lnRRQ10_4.9_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.9
-#################################################
- posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
-
-    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
-    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
-    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
 ```
@@
 #| warning: false
+#| echo: false
 
@@
 #| fig-cap: Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems
+#| echo: false
+
 ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
@@
 ### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
+```{r, wildlnRR10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
+#######################################
+  ## lnRRQ10 from Wild Populations ##
+#######################################
+##################################################
+  # Organise the data and prune tree
+##################################################
+
+# Bring in Climate data
+climate <- read.csv("./output/climate_data/temp_timeseries.csv")
+
+# Create a match column.
+climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
+
+# Subset the data
+lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnRRQ10_data_wild <- left_join(lnRRQ10_data_wild, climate2, by = "match")
+
+# Check and prune tree
+tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
+        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale data
+        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
+                                                          acf_all_c = scale(acf_all))
+###################################################
+  # Model 3.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.2
+  saveRDS(model3.2, file = "./output/models/lnRRQ10_3.2")
+  saveRDS(model3.2_bayes, file = "./output/models/lnRRQ10_3.2_bayes")
+
+  } else{
+        model3.2 <- readRDS("./output/models/lnRRQ10_3.2")
+  model3.2_bayes <- readRDS("./output/models/lnRRQ10_3.2_bayes")
+}
+
+####################################################
+  ## Model 3.2: Bayesian Contrasts
+###################################################
+  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
+  f_acute_wild  <- posteriors_3.2[,"b_Intercept"]
+  f_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
+  m_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
+  m_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
+  t_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
+
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10_wild <- exp(f_acute_wild) ; mean(f_acute_Q10_wild)
+  f_acclim_Q10_wild <- exp(f_acclim_wild); mean(f_acclim_Q10_wild)
+   m_acute_Q10_wild <- exp(m_acute_wild) ; mean(f_acute_Q10_wild)
+  m_acclim_Q10_wild <- exp(m_acclim_wild); mean(f_acclim_Q10_wild)
+   t_acute_Q10_wild <- exp(t_acute_wild) ; mean(t_acute_Q10_wild)
+  t_acclim_Q10_wild <- exp(t_acclim_wild); mean(t_acclim_Q10_wild)
+
+# % change in acclimation on log scale
+  change_f_wild <- abs(f_acclim_wild - f_acute_wild)*100; quantile(change_f_wild, c(0.025, 0.975))
+  change_m_wild <- abs(m_acclim_wild - m_acute_wild)*100; quantile(change_m_wild, c(0.025, 0.975))
+  change_t_wild <- abs(t_acclim_wild - t_acute_wild)*100; quantile(change_t_wild, c(0.025, 0.975))
+
+# % change on Q10 scale
+  p_change_f_q10_wild <- (exp(f_acclim_wild - f_acute_wild)-1)*100; quantile(p_change_f_q10_wild, c(0.025, 0.975))
+  p_change_m_q10_wild <- (exp(m_acclim_wild - m_acute_wild)-1)*100; quantile(p_change_m_q10_wild, c(0.025, 0.975))
+  p_change_t_q10_wild <- (exp(t_acclim_wild - t_acute_wild)-1)*100; quantile(p_change_t_q10_wild, c(0.025, 0.975))
+
+####################################################
+  # Model 3.3: Model environmental variability by acute 
+  #  acclim 
+####################################################
+  rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.3, file = "./output/models/lnRRQ10_3.3")
+  saveRDS(model3.3_bayes, file = "./output/models/lnRRQ10_3.3_bayes")
+
+  } else{
+        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
+  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
+  }
+
+################################################################
+  # Model 3.7: Environmental autocorrelation model by acute/acclim
+################################################################
+  if(rerun){
+  # More realistic model with 
+  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.4, file = "./output/models/lnRRQ10_3.4")
+  saveRDS(model3.4_bayes, file = "./output/models/lnRRQ10_3.4_bayes")
+
+  } else{
+        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
+  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
+  }
+
+################################################################
+  # Model 3.5: Environmental variability  model
+################################################################
+  if(rerun){
+  # More realistic model with 
+  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.5
+  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
+  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")
+
+  } else{
+        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
+  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
+  }
+
+################################################################
+  # Model 3.6: Environmental autocorrelation model
+################################################################
+  if(rerun){
+  # More realistic model with 
+  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.6
+  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
+  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")
+
+  } else{
+        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
+  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
+  }
+
+################################################################
+  # Model 3.7: Environmental variability and autocorrelation model
+################################################################
+
+  if(rerun){
+  # More realistic model with 
+  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.7
+  saveRDS(model3.7, file = "./output/models/lnRRQ10_3.7")
+  saveRDS(model3.7_bayes, file = "./output/models/lnRRQ10_3.7_bayes")
+
+  } else{
+        model3.7 <- readRDS("./output/models/lnRRQ10_3.7")
+  model3.7_bayes <- readRDS("./output/models/lnRRQ10_3.7_bayes")
+  }
+
+############################################################################################
+# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
+# differently in each habitat
+############################################################################################  
+  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+  if(rerun){
+  # More realistic model with 
+  model3.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
+  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
+
+  } else{
+        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
+  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 3.8
+#################################################
+ posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
+
+    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
+    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
+    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
+
+############################################################################################
+# Model 3.9: Acclimatization lnRRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################
+
+if(rerun){
+  # More realistic model with 
+  model3.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.9, file = "./output/models/lnRRQ10_3.9")
+  saveRDS(model3.9_bayes, file = "./output/models/lnRRQ10_3.9_bayes")
+
+  } else{
+        model3.9 <- readRDS("./output/models/lnRRQ10_3.9")
+  model3.9_bayes <- readRDS("./output/models/lnRRQ10_3.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 3.9
+#################################################
+ posteriors <- posterior_samples(model3.9_bayes, "^b")
+
+    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
+    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
+    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
+
+##################################################
+    # Model 3.8, 3.9 and 3.10 - Habitat subset
+##################################################
+    # Subset data to habitat
+    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+    # Terrestrial Models
+    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+
+    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+        # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+    # Freshwater Models
+    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+       # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+
+     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+    # Marine Models
+      model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+
+    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+    # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+
+    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+
+```
+
+```{r wildlncvr, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
+#######################################
+  ## lnCVRQ10 from Wild Populations ##
+#######################################
+##################################################
+  # Organise the data and prune tree
+##################################################
+
+# Bring in Climate data
+climate <- read.csv("./output/climate_data/temp_timeseries.csv")
+
+# Create a match column.
+climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
+
+# Subset the data
+lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
+                              mutate(spp = species_full, 
+                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
+                                     match = interaction(spp, lat, long))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
+
+# Check and prune tree
+tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
+        A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale environment variables
+    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
+                                                        acf_all_c = scale(acf_all))
+###################################################
+  # Model 4.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model3.2
+  saveRDS(model4.2, file = "./output/models/lnCVRQ10_4.2")
+  saveRDS(model4.2_bayes, file = "./output/models/lnCVRQ10_4.2_bayes")
+
+  } else{
+        model4.2 <- readRDS("./output/models/lnCVRQ10_4.2")
+  model4.2_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
+}
+
+####################################################
+  ## Model 4.2: Bayesian Contrasts
+###################################################
+  posteriors_4.2 <- posterior_samples(model4.2_bayes, pars = "^b")
+  f_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"]
+  f_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_typeacclim"]
+  m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
+  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatm"]
+  t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
+  t_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatt"]
+
+# CVRQ10 values for each category.
+   f_acute_Q10_wild_cvr <- exp(f_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
+  f_acclim_Q10_wild_cvr <- exp(f_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
+   m_acute_Q10_wild_cvr <- exp(m_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
+  m_acclim_Q10_wild_cvr <- exp(m_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
+   t_acute_Q10_wild_cvr <- exp(t_acute_wild_cvr) ; mean(t_acute_Q10_wild_cvr)
+  t_acclim_Q10_wild_cvr <- exp(t_acclim_wild_cvr); mean(t_acclim_Q10_wild_cvr)
+
+# % change in acclimation on log scale
+  change_f_wild_cvr <- abs(f_acclim_wild_cvr - f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
+  change_m_wild_cvr <- abs(m_acclim_wild_cvr - m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
+  change_t_wild_cvr <- abs(t_acclim_wild_cvr - t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
+
+# % change on Q10 scale
+  p_change_f_q10_wild_cvr <- (exp(f_acclim_wild_cvr - f_acute_wild_cvr)-1)*100; quantile(p_change_f_q10_wild_cvr, c(0.025, 0.975))
+  p_change_m_q10_wild_cvr <- (exp(m_acclim_wild_cvr - m_acute_wild_cvr)-1)*100; quantile(p_change_m_q10_wild_cvr, c(0.025, 0.975))
+  p_change_t_q10_wild_cvr <- (exp(t_acclim_wild_cvr - t_acute_wild_cvr)-1)*100; quantile(p_change_t_q10_wild_cvr, c(0.025, 0.975))
+
+####################################################
+  # Model 4.3: Model environmental variability by acute/acclim
+####################################################
+  rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.3
+  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
+  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
+
+  } else{
+        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
+  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
+  }
+
+################################################################
+  # Model 4.4: Environmental autocorrelation model by acute/acclim
+################################################################
+  if(rerun){
+  # More realistic model with 
+  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
+  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
+
+  } else{
+        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
+  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
+  }
+
+################################################################
+  # Model 4.5: Environmental variability
+################################################################
+if(rerun){
+  # More realistic model with 
+  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.5
+  saveRDS(model4.5, file = "./output/models/lnCVRQ10_4.5")
+  saveRDS(model4.5_bayes, file = "./output/models/lnCVRQ10_4.5_bayes")
+
+  } else{
+        model4.5 <- readRDS("./output/models/lnCVRQ10_4.5")
+  model4.5_bayes <- readRDS("./output/models/lnCVRQ10_4.5_bayes")
+  }
+
+################################################################
+  # Model 4.6: Environmental autocorrelation model 
+################################################################
+  if(rerun){
+  # More realistic model with 
+  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.6
+  saveRDS(model4.6, file = "./output/models/lnCVRQ10_4.6")
+  saveRDS(model4.6_bayes, file = "./output/models/lnCVRQ10_4.6_bayes")
+
+  } else{
+        model4.6 <- readRDS("./output/models/lnCVRQ10_4.6")
+  model4.6_bayes <- readRDS("./output/models/lnCVRQ10_4.6_bayes")
+  }
+
+################################################################
+  # Model 4.7: Environmental autocorrelation and variability
+################################################################
+ if(rerun){
+  # More realistic model with 
+  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.7
+  saveRDS(model4.7, file = "./output/models/lnCVRQ10_4.7")
+  saveRDS(model4.7_bayes, file = "./output/models/lnCVRQ10_4.7_bayes")
+
+  } else{
+        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")
+  #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
+  }
+
+############################################################################################
+  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
+  # differently in each habitat
+############################################################################################  
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+  if(rerun){
+  # More realistic model with 
+  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model4.8
+  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
+  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
+
+  } else{
+        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
+  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.8
+#################################################
+ posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
+
+    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
+    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
+    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
+
+############################################################################################
+# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################
+
+if(rerun){
+  # More realistic model with 
+  model4.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model4.9, file = "./output/models/lnRRQ10_4.9")
+  saveRDS(model4.9_bayes, file = "./output/models/lnRRQ10_4.9_bayes")
+
+  } else{
+        model4.9 <- readRDS("./output/models/lnRRQ10_4.9")
+  model4.9_bayes <- readRDS("./output/models/lnRRQ10_4.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.9
+#################################################
+ posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
+
+    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
+    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
+    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
+```
 
@@
 
-```{r, fig4, fig.align='center', fig.cap= "I2 estimates"}
+```{r}
+#| label: fig-fig4
+#| fig-cap: I2 estimates
+#| fig-align: center
 
@@
 
-```{r, fig5, fig.align='center', fig.cap= "I2 estimates lnCVR"}
+```{r}
+#| label: fig-fig5
+#| fig-cap: I2 estimates lnCVR
+#| fig-align: center
+#| 
 p5 <- ggplot(i2_lncvr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 12)
@@
 
-```{r, fig6, fig.align='center', fig.cap= "Bubble plot environment lnRR wild populations"}
+```{r}
+#| label: fig-fig6
+#| fig-cap: Bubble plot environment lnRR wild populations
+#| fig-align: center
 p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), "; P = ", round(model3.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18))
@@
 
-```{r, fig7, fig.align='center', fig.cap= "Bubble plot environment lnCVR wild populations"}
+```{r}
+#| label: fig-fig7
+#| fig-cap: Bubble plot environment lnCVR wild populations
+#| fig-align: center
 p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", k = FALSE) +annotate("text", x = 1, y = -5, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))

### 2023-03-10 ms.qmd
Updated with bubble plots needs some adjustments

@@
 
-options(digits = 3, scipen = 3)
+  options(digits = 2, scipen = 3)
 ```
@@
 
-Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$
+<p style="text-align: center;">Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$</p>
 
@@
 
-```{r, fig8, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
-
+```{r}
+#| label: fig-fig8
+#| fig-align: center
+#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
  col <- c("#0871B9", "#F3B40D", "#1BB908")
@@
 p8.1.2 <- p8.1 / p8.2
-
+p8.1.2
 ggsave(p8.1.2, filename = "./output/figures/fig8.png")
@@
 
-```{r, fig9, fig.align='center', fig.cap= "Bubble plot environment lnRR for wild populations by habitat"}
-
+```{r}
+#| label: fig-fig9
+#| fig-align: center
+#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
  col <- c("#0871B9", "#F3B40D", "#1BB908")
@@
 p91.2 <- p9.1 / p9.2
-
+p91.2
 ggsave(p91.2, filename = "./output/figures/fig9.png")
@@
 p67 <- (p6 | p7) + plot_annotation(tag_levels = "A")
-
+p67
 ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 30, units = "cm")
@@
 p89 <- (p8 | p9) + plot_annotation(tag_levels = "A")
-
+p89
 ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 30, units = "cm")

### 2023-03-11 ms.qmd
Need to add slopes to figs

@@
 #| fig-cap: Bubble plot environment lnRR for wild populations by habitat
+
+    # Add slopes and 95% CI to each panel
+    # CV
+    slope_f <-  posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
+    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
+    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
+
+    # ACF
+    posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
+
+    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
+    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
+    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
+
  col <- c("#0871B9", "#F3B40D", "#1BB908")

### 2023-03-14 R/functions.R
New text function

@@ -415,3 +415,11 @@ p_value <- function(x){
   if(x >= 0.01) {tmp = round(x, digits =2)}
   return(tmp)
 }
+
+#' @title text
+#' @description Converts posterior distribution into a text statement for plotting
+#' @param post the posterior distribution as a vector
+#' 
+ text <- function(post){
+      paste0("B = ", round(mean(post), 2), ", 95% CI: ", round(quantile(post, c(0.025, 0.975)[1]), 2), " to ", round(quantile(post, c(0.025, 0.975)[2]), 2))
+  }

### 2023-03-14 ms.qmd
Added to figure and wrote in hetereogeniety

@@
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
+Effect heterogeneity was nontheless high (only `r mean(tot_i2)`% of the variance was the resulting of sampling varianbility, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary and species specific ecoloogy explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%)
 
@@
 
+dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
+                      condition = c("f", "m", "t"),
+                      x = rep(1.2, 3),
+                      y = rep(-1.2, 3))
+
  col <- c("#0871B9", "#F3B40D", "#1BB908")
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
-
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col)) + geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7)
+
+dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
+                      condition = c("f", "m", "t"),
+                      x = rep(1.2, 3),
+                      y = rep(-1.2, 3))
+
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col)) geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7)
 

### 2023-03-14 R/functions.R
UPdated functions

@@ -420,6 +420,14 @@ p_value <- function(x){
 #' @description Converts posterior distribution into a text statement for plotting
 #' @param post the posterior distribution as a vector
 #' 
- text <- function(post){
-      paste0("B = ", round(mean(post), 2), ", 95% CI: ", round(quantile(post, c(0.025, 0.975)[1]), 2), " to ", round(quantile(post, c(0.025, 0.975)[2]), 2))
+ text <- function(post, b = TRUE){
+      if(b){
+        paste0("B = ", round(mean(post), 2))
+      } else {
+        paste0("95% CI: ", round(quantile(post, c(0.025, 0.975)[1]), 2), " to ", round(quantile(post, c(0.025, 0.975)[2]), 2))
+      }
   }
+
+p_text <- function(post){
+   paste0("p = ", round(pmcmc(post), 2))
+}

### 2023-03-14 ms.qmd
Fixed figures

@@
   freeze: auto  # re-render only when source changes
-  cache: true
+  cache: false
   echo: false
@@
 
-    # Add slopes and 95% CI to each panel
+size_axis = 18
 # CV
-    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
-    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
-    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
-
-    # ACF
-    posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
-
-    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
-    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
-    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
-
 dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
+                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
+                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
+                      title = c("Freshwater", "Marine", "Terrestrial"), 
                       condition = c("f", "m", "t"),
@@
  col <- c("#0871B9", "#F3B40D", "#1BB908")
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col)) + geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7)
-
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) +
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7) + 
+geom_text(data = dat_text, aes(x = x, y = y-0.2, label = label2), size = 7) +
+geom_text(data = dat_text, aes(x = x, y = y-0.4, label = p), size = 7) +
+geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 7) + 
+theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
+
+  # ACF
 dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
+                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
+                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
                       condition = c("f", "m", "t"),
-                      x = rep(1.2, 3),
+                      x = rep(-2.8, 3),
                       y = rep(-1.2, 3))
 
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1) + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col)) geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7)
-
-p8.1.2 <- p8.1 / p8.2
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) +
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7) + 
+geom_text(data = dat_text2, aes(x = x, y = y-0.2, label = label2), size = 7) +
+geom_text(data = dat_text2, aes(x = x, y = y-0.4, label = p), size = 7) +
+theme(legend.position = "bottom", 
+      strip.background = element_blank(), 
+      strip.text = element_blank(), 
+      axis.text = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      legend.text = element_text(size = 16),
+      legend.title = element_text(size = 16))
+
+p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+ggsave(p8.1.2, width = 13, height = 12.5, filename = "./output/figures/fig8.png")
+
+  p8.1.2 <- image_read("./output/figures/fig8.png")
 p8.1.2
-ggsave(p8.1.2, filename = "./output/figures/fig8.png")
 ```

### 2023-03-14 ms.qmd
Figures sort of sorted for lnRRq10

@@
 
-```{r lnrrq10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
+```{r lnrrq10}
+#| echo: false
+#| cache: true
+#| message: false
+#| warning: false
+#| include: false
+
 #############
@@
 #| include: false
+#| cache: true
 
@@
 ### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
-```{r, wildlnRR10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
+```{r, wildlnRR10}
+#| cache: true
+#| include: false
+#| echo: false
+#| warning: false
+#| 
 #######################################
@@
 
-```{r wildlncvr, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
+```{r wildlncvr}
+#| cache: true
+#| include: false
+#| echo: false
+#| warning: false
+#| 
 #######################################

### 2023-03-14 ms.qmd
Wrote opportunity for sleection paragraph

@@
   # Calculated weighted mean by sample size. 
-    f_cvr_mean <- (f_acute_cvr*N[1,"n"][[1]] + f_acclim_cvr*N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
-    m_cvr_mean <- (m_acute_cvr*N[3,"n"][[1]] + m_acclim_cvr*N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
-    t_cvr_mean <- (t_acute_cvr*N[5,"n"][[1]] + t_acclim_cvr*N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
+    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
+    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+
+  # Lets now convert these to a %
+  f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
+  m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
+  t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
 
@@
 ### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
+
+The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$\deg$C.
+In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(f_cvr_mean)`).
+
 ```{r, wildlnRR10}

### 2023-03-15 ms.qmd
Updated section on CV. Probably should add VR to supplement
Added in VR models as a sensitivity anlaysis

@@
 crossref:
-  fig-title: '**Fig**'
+  fig-title: 'Figure'
   fig-labels: arabic
-  title-delim: "**-**"
+  title-delim: "-"
   fig-prefix: "Figure"
-  tbl-labels: "**Table**"
+  tbl-labels: "Table"
 ---
@@
 
+```{r, lnvrq10}
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+#| cache: true
+
+#############
+  ## lnVRQ10
+#############
+##################################################
+  # Organise the data and prune tree
+#################################################
+  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Check and prune tree
+  tree_lnVR <- tree_checks(data = lnVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnVRQ10_data, tree = tree_lnVR, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_VR <- vcv(tree_lnVR, cor = TRUE)
+          A_VR <- vcv(tree_lnVR, cor = FALSE) # For bayes, need cov matrix
+
+# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+  #hist(lnVRQ10_data$V)
+
+# Studies with big V, why? Check N
+  lnVRQ10_data %>% filter(V >= 2)
+
+###################################################
+  # Model 3.1: Intercept only model.
+  # Used for heterogeneity analysis
+###################################################
+rerun = TRUE
+if(rerun){
+  model3.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+  model3.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+
+  # Save model1.1
+  saveRDS(model3.1, file = "./output/models/lnVRQ10_3.1")
+  saveRDS(model3.1_bayes, file = "./output/models/lnVRQ10_3.1_bayes")
+} else{ 
+        model3.1 <- readRDS("./output/models/lnVRQ10_3.1")
+  model3.1_bayes <- readRDS("./output/models/lnVRQ10_3.1_bayes")
+  }
+
+# Heterogeneity analysis
+   w_VR <- with(lnVRQ10_data, 1/V) # weights
+  sv_VR <- sum(w_VR*(dim(lnVRQ10_data)[1]-1)) / (sum(w_VR)^2 + sum(w_VR^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_3.1 <- posterior_samples(model3.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_3.1) <- gsub("__Intercept", "", colnames(posteriors_3.1))
+  colnames(posteriors_3.1) <- gsub("sd_", "", colnames(posteriors_3.1))
+
+    res_VR <- posteriors_3.1[,"sigma"]
+   stdy_VR <- posteriors_3.1[,"record_num"]
+  phylo_VR <- posteriors_3.1[,"species_full"]
+    spp_VR <- posteriors_3.1[,"spp"]
+  trait_VR <- posteriors_3.1[,"trait"]
+  total_VR <- phylo_VR + spp_VR + res_VR + sv_VR + stdy_VR + trait_VR
+
+  # Calculate I2
+     tot_i2_VR <- (sv_VR / total_VR)*100    ; mean(tot_i2_VR)  ; quantile(tot_i2_VR, c(0.025, 0.975))
+   phylo_i2_VR <- (phylo_VR / total_VR)*100 ; mean(phylo_i2_VR); quantile(phylo_i2_VR, c(0.025, 0.975))
+     spp_i2_VR <- (spp_VR / total_VR)*100   ; mean(spp_i2_VR)  ; quantile(spp_i2_VR, c(0.025, 0.975))
+    stdy_i2_VR <- (stdy_VR / total_VR)*100  ; mean(stdy_i2_VR) ; quantile(stdy_i2_VR, c(0.025, 0.975))
+   trait_i2_VR <- (trait_VR / total_VR)*100 ; mean(trait_i2_VR); quantile(trait_i2_VR, c(0.025, 0.975))
+     res_i2_VR <- (res_VR / total_VR)*100   ; mean(res_i2_VR)  ; quantile(res_i2_VR, c(0.025, 0.975))
+
+  # Table
+     i2_lnVR <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_VR),mean(spp_i2_VR), mean(stdy_i2_VR), mean(trait_i2_VR)),
+                           lci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[1], quantile(spp_i2_VR, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_VR, c(0.025, 0.975))[1], quantile(trait_i2_VR, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[2], quantile(spp_i2_VR, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_VR, c(0.025, 0.975))[2], quantile(trait_i2_VR, c(0.025, 0.975))[2]))
+
+###################################################
+  # Model 3.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model3.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
+  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")
+
+  } else{
+        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
+  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
+}
+
+######################################################
+  # Bayesian Contrasts
+######################################################
+
+  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
+  f_acute_VR  <- posteriors_3.2[,"b_Intercept"]; pmcmc(f_acute_VR)
+  f_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
+  m_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
+  m_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
+  t_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
+
+# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
+It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
+  # First get sample sizes
+    N <- lnVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_VR_mean <- (f_acute_VR * N[1,"n"][[1]] + f_acclim_VR * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_VR_mean)
+    m_VR_mean <- (m_acute_VR * N[3,"n"][[1]] + m_acclim_VR * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_VR_mean)
+    t_VR_mean <- (t_acute_VR * N[5,"n"][[1]] + t_acclim_VR * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_VR_mean)
+
+  # Lets now convert these to a %
+    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) # ~8.4% reduction
+    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) # ~15% reduction
+    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100) # ~30% reduction
+
+```
+
 ```{r}

### 2023-03-15 ms.qmd
Added lnVR

@@
 
+Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-lnvr).
+
+```{r}
+#| label: fig-lnvr
+#| fig-align: center
+#| fig-cap: lnVR
+
+##################
+  # Figure S1
+################## 
+  # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
+  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", data = lnVRQ10_data, angle = 45, trunk.size = 5) +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
+           label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_VR_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = 1.15, y = -5, 
+           label =paste0(round(mean(exp(f_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
+  annotate("text", x = 2.3, y = -5.2, 
+           label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_VR_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = 2.15, y = -5, 
+           label =paste0(round(mean(exp(m_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
+           label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 3.15, y = -5, 
+           label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
+    annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_VR_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
+
+  p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
+          axis.text = element_text(size = 15))
+  p3
+     ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
+```
+
 ```{r}

### 2023-03-16 ms.qmd
Fixed figure to look better

@@
 scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 7) + 
-geom_text(data = dat_text, aes(x = x, y = y-0.2, label = label2), size = 7) +
-geom_text(data = dat_text, aes(x = x, y = y-0.4, label = p), size = 7) +
-geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 7) + 
+geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
 theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
@@
 scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 7) + 
-geom_text(data = dat_text2, aes(x = x, y = y-0.2, label = label2), size = 7) +
-geom_text(data = dat_text2, aes(x = x, y = y-0.4, label = p), size = 7) +
+geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text2, aes(x = x, y = y-0.3, label = label2), size = 5) +
+geom_text(data = dat_text2, aes(x = x, y = y-0.65, label = p), size = 5) +
 theme(legend.position = "bottom", 
@@
 
-p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-
-ggsave(p8.1.2, width = 13, height = 12.5, filename = "./output/figures/fig8.png")
+p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+
+ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
 

### 2023-03-16 ms.qmd
model update. Fixed up VR figure

@@
   # Lets now convert these to a %
-    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) # ~8.4% reduction
-    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) # ~15% reduction
-    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100) # ~30% reduction
+    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) 
+    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) 
+    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100)
 
@@
            label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_VR_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = 1.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
   annotate("text", x = 1.15, y = -5, 
@@
            label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_VR_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = 2.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
   annotate("text", x = 2.15, y = -5, 
@@
            label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_VR_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
+    annotate("text", x = 3.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(t_VR_mean), digit = 3)))), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
 
   p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
-          axis.text = element_text(size = 15))
-  p3
-     ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
+          axis.text = element_text(size = 15), legend.text = element_text(size = 15),
+          legend.title = element_text(size = 15))
+
+  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 10, height = 8)
+
+  figs1 <- image_read("./output/figures/figS1.pdf")
+  figs1
 ```

### 2023-03-17 ms.qmd
Added some jazz about PB, fixed figure in supp.

@@
 
-### *Sensitivity Analyses*
 ### *Publication Bias*
+
+We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling varinace and publication year [@Nakagawa2021-uf].
+Funnel plot asymetry may suggest a 'file-drawer' form of publication bias whereby low-powered studies are less likely to be published.
+However, asymetry can also result form high hetereogenity.
+As such, testing (and correcting) for publication bias using a meta-regression approach can attempt to counteract bias that maybe driven by high hetereogneity.
+In addition, time-lag bias is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2022-qw].
 
@@
 
-  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 10, height = 8)
+  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
 

### 2023-03-17 ms.qmd
Fixed lnCVR figure

--- 2023-03-16 ms.qmd
@@
 
-### *Sensitivity Analyses*
 ### *Publication Bias*
+
+We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) and publication year [@Nakagawa2021-gy].
+Funnel plot asymetry may suggest a form of publication called a 'file-drawer' effect whereby low-powered studies are less likely to be published.
+However, asymetry can also result form high hetereogenity.
+As such, testing (and correcting) for publication bias using a meta-regression approach can attempt to counteract bias that maybe driven by high effect hetereogneity.
+In addition, a second form of publication bias, time-lag bias, is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2022-qw].
 
@@
 #| fig-align: center
-#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
+#| fig-cap: Bubble plot environment $lnRR_{Q_{10}}$ for wild populations by habitat.
 
@@
  col <- c("#0871B9", "#F3B40D", "#1BB908")
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1) +
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) +
 theme_classic() + 
@@
 #| fig-align: center
-#| fig-cap: Bubble plot environment lnRR for wild populations by habitat
+#| fig-cap: Bubble plot environment $lnCVR_{Q_{10}}$ for wild populations by habitat.
+
+size_axis = 18
+# CV
+dat_text <- data.frame(label = c(text(slope_f_4.9), text(slope_m_4.9), text(slope_t_4.9)),
+                      label2 = c(text(slope_f_4.9, b = FALSE), text(slope_m_4.9,b = FALSE), text(slope_t_4.9,b = FALSE)),
+                      p = c(p_text(slope_f_4.9), p_text(slope_m_4.9), p_text(slope_t_4.9)),
+                      title = c("Freshwater", "Marine", "Terrestrial"), 
+                      condition = c("f", "m", "t"),
+                      x = rep(1.2, 3),
+                      y = rep(-4, 3))
+
  col <- c("#0871B9", "#F3B40D", "#1BB908")
-p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "none", strip.background = element_blank())  + scale_fill_manual(values = c(col))
-
-p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k.pos = "bottom.left") + theme_classic() + theme(legend.position = "bottom", strip.background = element_blank(), strip.text = element_blank())+ scale_fill_manual(values = c(col))
-
-p91.2 <- p9.1 / p9.2
-p91.2
-ggsave(p91.2, filename = "./output/figures/fig9.png")
+p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnCVRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) +
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text, aes(x = x, y = y-1, label = label2), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y-2, label = p), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y+10, label = title, size = 5)) + 
+theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
+
+  # ACF
+dat_text2 <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
+                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
+                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
+                      condition = c("f", "m", "t"),
+                      x = rep(-2.8, 3),
+                      y = rep(-4, 3))
+
+p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnCVRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) +
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text2, aes(x = x, y = y-0.6, label = label2), size = 5) +
+geom_text(data = dat_text2, aes(x = x, y = y-1.2, label = p), size = 5) +
+theme(legend.position = "bottom", 
+      strip.background = element_blank(), 
+      strip.text = element_blank(), 
+      axis.text = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      legend.text = element_text(size = 16),
+      legend.title = element_text(size = 16))
+
+p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+
+ggsave(p9.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig9.png")
+
+  p9.1.2 <- image_read("./output/figures/fig8.png")
+  p9.1.2 
 ```

### 2023-03-21 ms.qmd
small changes
change
Funnel plots

@@
 ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
+
 ##################
@@
                                                           acf_all_c = scale(acf_all))
+
 ###################################################
@@
                                                         acf_all_c = scale(acf_all))
+
 ###################################################
@@
 
+#### Comparing raw variance changes using $lnVR_{Q_{10}}$
 ```{r, lnvrq10}
@@
 
+#### Publicaton Bias Analysis
+
+We compared
+
+```{r}
+#| label: fig-figs2
+#| fig-cap: Funnel plots of sampling error variance agaist effect size for a) $lnRR_{Q_{10}}$, b) $lnCVR_{Q_{10}}$ and c) $lnVR_{Q_{10}}$.
+cols <- c("#2ECC71", "#FFC300")
+ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none")
+
+ps2_2 <- ggplot(lnCVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnCVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none", axis.title.y = element_blank())
+
+ps2_3 <- ggplot(lnVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15),  axis.title.y = element_blank())
+
+(ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+```
+
 ```{r}

### 2023-03-22 ms.qmd
Fixed plot S2

@@
 
-We compared
+Funnel plots did not show any noticable deviation from the typical funnel shape for any of the effect size estimates (@fig-figs2).
 
@@
 #| label: fig-figs2
-#| fig-cap: Funnel plots of sampling error variance agaist effect size for a) $lnRR_{Q_{10}}$, b) $lnCVR_{Q_{10}}$ and c) $lnVR_{Q_{10}}$.
+#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
+Both acute ('green') and acclimation ('orange') effect sizes are plotted.
 cols <- c("#2ECC71", "#FFC300")
-ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none")
-
-ps2_2 <- ggplot(lnCVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnCVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none", axis.title.y = element_blank())
-
-ps2_3 <- ggplot(lnVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15),  axis.title.y = element_blank())
-
-(ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-
+ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)
+
+ps2_2 <- ggplot(lnCVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnCVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none", axis.title.y = element_blank())+ scale_color_manual(name = "Type", values = cols)
+
+ps2_3 <- ggplot(lnVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15),  axis.title.y = element_blank())+ scale_color_manual(name = "Type", values = cols)
+
+figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS2.png")
+
+figs2 <- image_read("./output/figures/figS2.png")
+figs2
 ```

### 2023-03-22 ms.qmd
Fix refs for pub bias

@@
 
-We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) and publication year [@Nakagawa2021-gy].
+We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) and publication year [@Nakagawa2022-gy].
 Funnel plot asymetry may suggest a form of publication called a 'file-drawer' effect whereby low-powered studies are less likely to be published.
@@
 As such, testing (and correcting) for publication bias using a meta-regression approach can attempt to counteract bias that maybe driven by high effect hetereogneity.
-In addition, a second form of publication bias, time-lag bias, is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2022-qw].
+In addition, a second form of publication bias, time-lag bias, is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2023-qw].
 

### 2023-03-22 ms.qmd
Fixed up I2 plot

@@
 
-# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
-  #hist(lnVRQ10_data$V)
-
-# Studies with big V, why? Check N
-  lnVRQ10_data %>% filter(V >= 2)
-
 ###################################################
@@
 
-Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-lnvr).
+Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-figs1).
 
 ```{r}
-#| label: fig-lnvr
+#| label: fig-figs1
 #| fig-align: center
@@
 
+#### Plots of $I^2$ for multi-level models
+```{r}
+#| label: fig-figs3
+#| fig-cap: I2 estimates
+#| fig-align: center
+
+ps3_1 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2), 2), "%")), size = 10)
+
+ps3_2 <- ggplot(i2_lncvr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_blank(), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 10)
+
+ps3_3 <- ggplot(i2_lnVR, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_blank(), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 10)
+
+figs3 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figs3.png")
+
+figs3 <- image_read("./output/figures/figs3.png")
+figs3
+```
+
 #### Publicaton Bias Analysis
@@
 ```
-
-```{r}
-#| label: fig-fig4
-#| fig-cap: I2 estimates
-#| fig-align: center
-
-p4 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2), 2), "%")), size = 12)
-
-p4
-ggsave(p4, filename = "./output/figures/fig4.png")
-
-```
-
-```{r}
-#| label: fig-fig5
-#| fig-cap: I2 estimates lnCVR
-#| fig-align: center
-#| 
-p5 <- ggplot(i2_lncvr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 12)
-
-p5
-ggsave(p5, filename = "./output/figures/fig5.png")
-```
-
-```{r}
-#| label: fig-fig6
-#| fig-cap: Bubble plot environment lnRR wild populations
-#| fig-align: center
-p6 <- bubble_plot(model3.5, mod = "cv_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)") +annotate("text", x = 1, y = 3, label = TeX(paste0("$\\beta = $", round(model3.5$b[3], 3), ", 95%CI: ", round(model3.5$ci.lb[3],3), " to ", round(model3.5$ci.ub[3], 3), "; P = ", round(model3.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18))
-
-p7 <- bubble_plot(model3.6, mod = "acf_all_c", group  = "record_num", data = lnRRQ10_data_wild, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability") + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = 3, label = TeX(paste0("$\\beta = $", round(model3.6$b[3], 3), ", 95%CI: ", round(model3.6$ci.lb[3],3), " to ", round(model3.6$ci.ub[3], 3), "; P = ", round(model3.6$pval[3],3)))) + theme_classic() + theme(axis.text = element_text(size = 12), axis.title = element_text(size = 18))
-
-p67 <- (p6 | p7) + plot_annotation(tag_levels = "A")
-p67
-ggsave(p67, filename = "./output/figures/fig6.png", height = 10, width = 30, units = "cm")
-```
-
-```{r}
-#| label: fig-fig7
-#| fig-cap: Bubble plot environment lnCVR wild populations
-#| fig-align: center
-p8 <- bubble_plot(model4.5, mod = "cv_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", k = FALSE) +annotate("text", x = 1, y = -5, label = TeX(paste0("$\\beta = $", round(model4.5$b[3], 3), ", 95%CI: ", round(model4.5$ci.lb[3],3), " to ", round(model4.5$ci.ub[3], 3), " P = ", round(model4.5$pval[3],3)))) + theme_classic() + theme(legend.position = "none", axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))
-
-p9 <- bubble_plot(model4.6, mod = "acf_all_c", group  = "record_num", data = lnCVRQ10_data_wild, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", k = FALSE) + theme(axis.title.y = element_blank()) +annotate("text", x = -3, y = -5, label = TeX(paste0("$\\beta = $", round(model4.6$b[3], 3), ", 95%CI: ", round(model4.6$ci.lb[3],3), " to ", round(model4.6$ci.ub[3], 3), " P = ", round(model4.6$pval[3],3)))) + theme_classic() + theme(axis.text = element_text(size = 12), axis.title = element_text(size = 18)) + ylim(c(-6, 3))
-
-p89 <- (p8 | p9) + plot_annotation(tag_levels = "A")
-p89
-ggsave(p89, filename = "./output/figures/fig7.png", height = 10, width = 30, units = "cm")
-```

### 2023-03-23 ms.qmd
Adding VR table with some formatting

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt)
 
@@
    model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
-
+      summary(model3.2_bayes)                            
   # Save model1.2
@@
 
+```{r}
+#| label: tbl-tabs1
+#| tbl-cap: Model estimates, standard error, and 95% credible intervals
+
+ # Extract the fixed / population-level effect summaries of the posterior
+    fixed <- summary(model3.2_bayes)$fixed[,1:4]
+    fixed <- cbind(Parameter = rownames(fixed), fixed)
+  rownames(fixed) <- NULL
+
+ # Extract the random effect summaries of the posteriors (SDs)
+  random <- plyr::ldply(summary(model3.2_bayes)$random)[,1:5]
+  colnames(random)[1] <- "Parameter"
+
+# Headers for the table to indicate fixed and random effects
+  fixed_head <- c("Fixed Effects", rep(" ", 4))
+  random_head <- c("Random Effects", rep(" ", 4))
+
+# Create the table
+  tabs1 <- rbind(fixed, random)
+  gt(tabs1) %>%  fmt_number(
+    columns = 2:5,
+    decimals = 2
+  ) %>% tab_row_group(label = "Fixed Effects", rows = 1:7) %>% tab_row_group(label = "Random Effects", rows = 8:11)
+```
+
 #### Plots of $I^2$ for multi-level models

### 2023-03-23 ms.qmd
Added bold format

@@
   tabs1 <- rbind(fixed, random)
-  gt(tabs1) %>%  fmt_number(
-    columns = 2:5,
-    decimals = 2
-  ) %>% tab_row_group(label = "Fixed Effects", rows = 1:7) %>% tab_row_group(label = "Random Effects", rows = 8:11)
+  gt(tabs1) %>%  
+  fmt_number(columns = 2:5, decimals = 2) %>% 
+  tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
+  tab_row_group(label = "Random Effects", rows = 8:11) %>%  
+  tab_style(style = list(cell_text(weight = "bold")),
+        locations = list(cells_column_labels(), cells_row_groups()))
 ```

### 2023-03-23 ms.qmd
Fixed borders

--- 2023-03-23 ms.qmd
@@
   tabs1 <- rbind(fixed, random)
-  gt(tabs1) %>%  fmt_number(
-    columns = 2:5,
-    decimals = 2
-  ) %>% tab_row_group(label = "Fixed Effects", rows = 1:7) %>% tab_row_group(label = "Random Effects", rows = 8:11)
+  gt(tabs1) %>%  
+  fmt_number(columns = 2:5, decimals = 2) %>% 
+  tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
+  tab_row_group(label = "Random Effects", rows = 8:11) %>%  
+  tab_style(style = list(cell_text(weight = "bold")),
+        locations = list(cells_column_labels(), cells_row_groups())) %>% 
+  opt_table_lines(extent = "none")  %>% 
+  tab_style(style = cell_borders(sides = c("top", "bottom")),
+        locations = list(cells_column_labels()))  %>% 
+tab_style(style = cell_borders(sides = "bottom", weight = px(2)),
+        locations =  cells_body(rows = 7))
+
 ```

### 2023-03-24 ms.qmd
Update to table

@@
   freeze: auto  # re-render only when source changes
-  cache: false
+  cache: true
   echo: false
@@
 }
-
+str(summary(model3.2_bayes)
+)
 ######################################################
@@
 Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-figs1).
+@tbl-tabs1
 
@@
 #| label: tbl-tabs1
-#| tbl-cap: Model estimates, standard error, and 95% credible intervals
+#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
+Models estimates are based off `r summary(model3.2_bayes)$nobs` effect sizes from `r summary(model3.2_bayes)$ngrps$record_num` studies.
 
@@
     colnames(random)[1] <- "Parameter"
-
-# Headers for the table to indicate fixed and random effects
-  fixed_head <- c("Fixed Effects", rep(" ", 4))
-  random_head <- c("Random Effects", rep(" ", 4))
 

### 2023-03-24 ms.qmd
Fixed table issues. Was a yaml problem

@@
   fig-prefix: "Figure"
-  tbl-labels: "Table"
+  tbl-prefix: "Table"
 ---

### 2023-03-24 ms.qmd
echo false for table, need to fix legending fomratting

@@
 #| label: tbl-tabs1
+#| echo: false
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
@@
     tabs1 <- rbind(fixed, random)
-    gt(tabs1) %>%  
+   tabs1_2 <-  gt(tabs1) %>%  
     fmt_number(columns = 2:5, decimals = 2) %>% 
@@
           locations =  cells_body(rows = 7))
-
+    tabs1_2
 ```

### 2023-03-28 ms.qmd
Update to ref
Re-render and starting to write last section
Fixed colour scheme pub bias.

@@
 For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package [vers.
-`r utils::packageVersion("ncdf4")`, @Pierce2021].
+`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
 We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
@@
 
-    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
+    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); mean(slope_f); quantile(slope_f, c(0.025, 0.975))
     slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_t)
+
+       r2_t <- r2_ml(model3.9_t)[1]                       
         # Model just quickly tests if we are missing an important interaction.
@@
 ### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
+
+Thermal variability (i.e., $CV$) explained acclimation capacity among terrestrial ectotherms, but explained little variability in acclimation responses among marine or freshwater populations (@fig-fig8).
+Wild populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
+In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-fig8).
 
@@
 Both acute ('green') and acclimation ('orange') effect sizes are plotted.
-cols <- c("#2ECC71", "#FFC300")
+cols <- c("#303234", "#D3D3D3")
 ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)

### 2023-03-29 ms.qmd
Added pub bias model, started model with habitat

@@
 
-We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) and publication year [@Nakagawa2022-gy].
-Funnel plot asymetry may suggest a form of publication called a 'file-drawer' effect whereby low-powered studies are less likely to be published.
-However, asymetry can also result form high hetereogenity.
-As such, testing (and correcting) for publication bias using a meta-regression approach can attempt to counteract bias that maybe driven by high effect hetereogneity.
-In addition, a second form of publication bias, time-lag bias, is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2023-qw].
+We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) [@Nakagawa2022-gy].
+Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published.
+To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that acounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
 
 ```{r lnrrq10}
+#| label: lnrrq10
 #| echo: false
@@
 lnRRQ10_data %>% filter(V >= 2)
+
+# have a quick look on habitat, development and type. Mostly looks sensibel but there is not too much data in terrestrial realm.
+sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
 
@@
 
+###########################################################
+## Model 1.4 - whether chance between q10 depends on life stage and habita
+###########################################################
+if(rerun){
+  # More realistic model with 
+  model1.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.4
+  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
+  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
+
+  } else{
+        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
+  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
+}
+
 ####################################################
@@
 ```{r, lncvrq10}
+#| label: lncvrq10
 #| echo: false
@@
 ```{r, wildlnRR10}
+#| label: wildlnRR10
 #| cache: true
@@
 ```{r wildlncvr}
+#| label: wildlncvr
 #| cache: true
@@
 
-Thermal variability (i.e., $CV$) explained acclimation capacity among terrestrial ectotherms, but explained little variability in acclimation responses among marine or freshwater populations (@fig-fig8).
-Wild populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
+Thermal variability (i.e., $CV$) explained variation in acclimation capacity among terrestrial ectotherms, but not for marine or freshwater populations (@fig-fig8).
+Terrestrial ectotherm populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
 In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-fig8).
+
+In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability (@fig-fig9).
 
@@
 ```{r, lnvrq10}
+#| label: lnvrq10
 #| echo: false
@@
 
+```{r, pubias}
+#| label: pubias
+#| echo: false
+
+model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat + life.hist + type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+```
+
 ```{r}

### 2023-03-29 ms.qmd
Add figure for life stage

@@
 ###########################################################
+rerun = FALSE
 if(rerun){
@@
 
+```{r}
+#| label: fig-fig3
+#| fig-cap: Predicted mean acclimation and acute "$lnRR_{Q_{10}}$" for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
+
+p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))
+
+p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())
+
+p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())
+
+fig3 <- (p1 | p2 | p3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig3, filename = "./output/figures/fig3_lh.pdf", width = 8, height = 4.5)
+
+fig3 <- magick::image_read("./output/figures/fig3_lh.pdf")
+fig3
+
+```
 ### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
@@
 
-model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat + life.hist + type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
+if(rerun){
+  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+
+  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+
+  saveRDS(model_full_lnrr_pb, file = "./output/models/lnRRQ10_pubbias")
+  saveRDS(model_full_lncvr_pb, file = "./output/models/lnCVRQ10_pubbias")
+  saveRDS(model_full_lnvr_pb, file = "./output/models/lnVRQ10_pubbias")
+} else {
+   model_full_lnrr_pb <- readRDS(file = "./output/models/lnRRQ10_pubbias")
+  model_full_lncvr_pb <- readRDS(file = "./output/models/lnCVRQ10_pubbias")
+  model_full_lnvr_pb <- readRDS(file = "./output/models/lnVRQ10_pubbias")
+}
+
+summary(model_full_lnrr_pb)
 ```

### 2023-03-29 ms.qmd
Landscape fig2

@@
 
+\newpage
+\begin{landscape}
 ```{r}
@@
 ```
+
+\end{landscape}
 

### 2023-03-29 ms.qmd
landscape. Trying this out

@@
 \end{landscape}
-
+\newpage
 ```{r}

### 2023-03-30 ms.qmd
New doc, trying flextable which does formatting well, but still cross ref problems

--- 2023-03-29 ms.qmd
@@
 
-### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
+### *Terrestrial and aquatic ectotherms differ in their capacity to acclimate but acclimation does not depend on life-history stage*
 
@@
 ```
-### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
+### *The opportunity for selection is reduced in terrestrial ectotherms*
 
@@
     slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
+
 ```
 
-### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
+### *Climate variability predicts acclimation capacity for terrestrial ectotherms*
 
@@
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
-Models estimates are based off `r summary(model3.2_bayes)$nobs` effect sizes from `r summary(model3.2_bayes)$ngrps$record_num` studies.
+Models estimates are based off 1253 effect sizes from 139 studies.
 
@@
           locations =  cells_body(rows = 7))
-    tabs1_2
+    #tabs1_2
+
+    flextable(tabs1)  %>%  autofit()
 ```
@@
 #| echo: false
+#| include: false
 

### 2023-03-30 ms.qmd
Add in flextable

@@
     tabs1 <- rbind(fixed, random)
-   tabs1_2 <-  gt(tabs1) %>%  
-    fmt_number(columns = 2:5, decimals = 2) %>% 
-    tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
-    tab_row_group(label = "Random Effects", rows = 8:11) %>%  
-    tab_style(style = list(cell_text(weight = "bold")),
-          locations = list(cells_column_labels(), cells_row_groups())) %>% 
-    opt_table_lines(extent = "none")  %>% 
-    tab_style(style = cell_borders(sides = c("top", "bottom")),
-          locations = list(cells_column_labels()))  %>% 
-    tab_style(style = cell_borders(sides = "bottom", weight = px(2)),
-          locations =  cells_body(rows = 7))
-    #tabs1_2
-
-    flextable(tabs1)  %>%  autofit()
+
+    flextable(tabs1)  %>%  add_body_row()  %>% autofit()
 ```

### 2023-03-31 ms.qmd
Keep flextable simple
Fixed flextable so it's formatted right

@@
   model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
-model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")}
+model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
+}
 
@@
 
+ if(rerun){ 
     model1.s1 <- metafor::rma.mv(effect_size ~  c_accl_time + name, V = V, 
@@
                               test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1, file = "./output/models/model1.s1")
+} else{
+      model1.s1 <-  readRDS(file = "./output/models/model1.s1")
+}
+
 ```
@@
 fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig2, filename = "./output/figures/fig2_trait.pdf", height = 10, width = 40, device = "pdf", limitsize = FALSE, units = "cm")
-
-img_fig2 <- magick::image_read("./output/figures/fig2_trait.pdf")
+ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 8.5, width = 26)
+
+img_fig2 <- magick::image_read("./output/figures/fig2_trait.png")
 img_fig2
@@
 fig3 <- (p1 | p2 | p3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig3, filename = "./output/figures/fig3_lh.pdf", width = 8, height = 4.5)
-
-fig3 <- magick::image_read("./output/figures/fig3_lh.pdf")
+ggsave(fig3, filename = "./output/figures/fig3_lh.png", width = 14, height = 4.5)
+
+fig3 <- magick::image_read("./output/figures/fig3_lh.png")
 fig3
@@
 
+if(rerun){
     # Terrestrial Models
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_t)
+    saveRDS(model3.8_t, "./output/models/model3.8_t")
 
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_t)
-
+    saveRDS(model3.9_t, "./output/models/model3.9_t")
        r2_t <- r2_ml(model3.9_t)[1]                       
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_t)
+     saveRDS(model3.10_t, "./output/models/model3.10_t")
     # Freshwater Models
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_f)
+    saveRDS(model3.8_f, "./output/models/model3.8_f")
 
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+    saveRDS(model3.9_f, "./output/models/model3.9_f")
+
        # Model just quickly tests if we are missing an important interaction.
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_f)
-
+      saveRDS(model3.10_f, "./output/models/model3.10_f")
     # Marine Models
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_m)
+        saveRDS(model3.8_m, "./output/models/model3.8_m")
 
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_m)
+    saveRDS(model3.9_m, "./output/models/model3.9_m")
     # Model just quickly tests if we are missing an important interaction.
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_m)
-
+    saveRDS(model3.10_m, "./output/models/model3.10_m")
+  } else {
+     model3.8_t <- readRDS("./output/models/model3.8_t")
+     model3.9_t <- readRDS("./output/models/model3.9_t")
+    model3.10_t <- readRDS("./output/models/model3.10_t")
+     model3.8_f <- readRDS("./output/models/model3.8_f")
+     model3.9_f <- readRDS("./output/models/model3.9_f")
+    model3.10_f <- readRDS("./output/models/model3.10_f")
+     model3.9_m <- readRDS("./output/models/model3.9_m")
+    model3.10_m <- readRDS("./output/models/model3.10_m")
+     model3.8_m <- readRDS("./output/models/model3.8_m")
+}
 ```
@@
 }
-str(summary(model3.2_bayes)
-)
+
 ######################################################
@@
 #| label: tbl-tabs1
-#| echo: false
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
@@
     tabs1 <- rbind(fixed, random)
-
-    flextable(tabs1)  %>%  add_body_row()  %>% autofit()
+   tabs1$Parameter <- c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial", "Study", "Phylogeny", "Species", "Trait")
+
+    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
 ```

### 2023-03-31 ms.qmd
Contrasts for q10 jeuvenile stages

@@
 ---
-title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
+title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations"
 bibliography: ./bib/refs.bib
@@
 
+#######################################################################
+# Bayesian posteriors from model 1.4
+#######################################################################
+ # Create the data we want to make predcitions for. Just more intuitive
+  newdata <- data.frame( c_accl_time = 0, 
+                                type = as.factor(rep(c("acute", "acclim"))), 
+                             habitat = as.factor(rep(c("m", "f", "t"), each = 4)), 
+                           life.hist = as.factor(c("j", "a", "a", "j")))
+  newdata$type  <- relevel(newdata$type, ref = "acute")
+
+# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
+  X <- model.matrix(~c_accl_time + type*habitat*life.hist, data = newdata)
+
+# Extract posteriors
+  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
+
+# Now we can do all the calculations in one shot.
+         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
+     sum_pred <- apply(pred, 1, function(x) mean(x))
+  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
+  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
+
+# Create a summary dataset. 
+  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95)
+
+# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
+    # Marine 
+        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
+        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
+    # Freshwater
+        f_ad <- 4
+        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
+        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
+    # terrestrial
+        t_ad <- 8
+        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
+        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species
+
+# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
+    # Marine 
+         m_acute <-  pred[1,] - pred[3,] 
+        m_acclim <-  pred[4,] - pred[2,] 
+    # Freshwater
+            f_ad <- 4
+        f_acute <- pred[1+f_ad,] - pred[3+f_ad,] 
+        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] 
+    # terrestrial
+        t_ad <- 8
+        t_acute <- pred[1+t_ad,] - pred[3+t_ad,] 
+        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]
+
+# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong
+#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
+#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")
+
 ####################################################
@@
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, @fig-1 B).
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
+While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
+Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3).
+
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
-Effect heterogeneity was nontheless high (only `r mean(tot_i2)`% of the variance was the resulting of sampling varianbility, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary and species specific ecoloogy explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%)
+Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the resulting of sampling varianbility, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary and species specific ecoloogy explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
 
@@
 
-```{r}
+```{r, fig-1}
 #| label: fig-1
@@
 
-```{r}
+```{r, fig-2}
 #| label: fig-2
@@
 
-```{r}
-#| label: fig-fig3
+```{r, fig-3}
+#| label: fig-3
 #| fig-cap: Predicted mean acclimation and acute "$lnRR_{Q_{10}}$" for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
@@
 ```
+
 ### *The opportunity for selection is reduced in terrestrial ectotherms*
@@
     saveRDS(model3.9_t, "./output/models/model3.9_t")
-       r2_t <- r2_ml(model3.9_t)[1]                       
+
         # Model just quickly tests if we are missing an important interaction.
@@
 }
+
+       r2_t <- r2_ml(model3.9_t)[1]    
 ```
@@
 
-Thermal variability (i.e., $CV$) explained variation in acclimation capacity among terrestrial ectotherms, but not for marine or freshwater populations (@fig-fig8).
+Thermal variability (i.e., $CV$) explained variation in acclimation capacity among terrestrial ectotherms, but not for marine or freshwater populations (@fig-4).
 Terrestrial ectotherm populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
-In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-fig8).
-
-In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability (@fig-fig9).
-
-```{r}
-#| label: fig-fig8
+In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-4).
+
+In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability (@fig-5).
+
+```{r, fig-4}
+#| label: fig-4
 #| fig-align: center
@@
 
-```{r}
-#| label: fig-fig9
+```{r, fig-5}
+#| label: fig-5
 #| fig-align: center
@@
 
-Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-figs1).
-@tbl-tabs1
-
-```{r}
-#| label: fig-figs1
+Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-s1). @tbl-s1
+
+```{r, fig-s1}
+#| label: fig-s1
 #| fig-align: center
@@
 
-```{r}
-#| label: tbl-tabs1
+```{r, tbl-s1}
+#| label: tbl-s1
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
@@
 #### Plots of $I^2$ for multi-level models
-```{r}
-#| label: fig-figs3
+```{r, fig-s3}
+#| label: fig-s3
 #| fig-cap: I2 estimates
@@
 
-Funnel plots did not show any noticable deviation from the typical funnel shape for any of the effect size estimates (@fig-figs2).
+Funnel plots did not show any noticable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
 
@@
 
-summary(model_full_lnrr_pb)
 ```
 
-```{r}
-#| label: fig-figs2
+```{r, fig-s2}
+#| label: fig-s2
 #| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).

### 2023-03-31 ms.qmd
Added stats for adult / jeuvenile comparison

@@
         f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
-    # terrestrial
+    # Terrestrial
         t_ad <- 8
@@
     # Marine 
-         m_acute <-  pred[1,] - pred[3,] 
-        m_acclim <-  pred[4,] - pred[2,] 
+         m_acute <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
+        m_acclim <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
     # Freshwater
             f_ad <- 4
-        f_acute <- pred[1+f_ad,] - pred[3+f_ad,] 
-        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] 
-    # terrestrial
+        f_acute <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
+        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
+    # Terrestrial
         t_ad <- 8
-        t_acute <- pred[1+t_ad,] - pred[3+t_ad,] 
-        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]
-
-# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong
+        t_acute <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
+        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species
+
+  # Acute differences between a and j across all habitats
+    acute_all <- c(m_acute, f_acute, t_acute); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
+    acclim_all <- c(m_acclim, f_acclim, t_acclim)
+
+# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong. These two lines of code should roughly match
 #  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
@@
 While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
-Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3).
+Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
 

### 2023-04-01 ms.qmd
small adjustments

@@
 ```
-
+install.packages("flextable")
 #### Plots of $I^2$ for multi-level models

### 2023-04-01 ms.qmd
trying some fixes

--- 2023-03-31 ms.qmd
@@
 
-Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}_{acute}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
@@
 #| label: tbl-s1
+#| echo: false
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
@@
 
-    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
+    flextable(tabs1) %>% flextable::bold(part = "header") %>% flextable::autofit() %>% flextable::add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% flextable::compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
 ```
-
+install.packages("flextable")
 #### Plots of $I^2$ for multi-level models

### 2023-04-01 ms.qmd
remove lone code

@@
 ```
-install.packages("flextable")
+
 #### Plots of $I^2$ for multi-level models

### 2023-04-01 R/functions.R
Added a new function to manually summarise posterior draws

@@ -431,3 +431,16 @@ p_value <- function(x){
 p_text <- function(post){
    paste0("p = ", round(pmcmc(post), 2))
 }
+
+
+post_summary <- function(x){
+         Est <- mean(x)
+         se <- sd(x)
+         l95 <- quantile(x, 0.025)[1]
+         u95 <- quantile(x, 0.975)[1]
+
+         return(data.frame(Estimate = Est,
+                    Est.Error = se,
+                    `l-95% CI` = l95,
+                    `u-95% CI` = u95, check.names = FALSE, row.names = NULL))
+}

### 2023-04-01 ms.qmd
Fixed table because theer was some very weird stuff going on with brms model...

@@
    model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
-      summary(model3.2_bayes)                            
+
   # Save model1.2
@@
  # Extract the fixed / population-level effect summaries of the posterior
-    fixed <- summary(model3.2_bayes)$fixed[,1:4]
-    fixed <- cbind(Parameter = rownames(fixed), fixed)
+    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
+    fixed <- cbind(Parameter = c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
     rownames(fixed) <- NULL
@@
  # Extract the random effect summaries of the posteriors (SDs)
-    random <- plyr::ldply(summary(model3.2_bayes)$random)[,1:5]
-    colnames(random)[1] <- "Parameter"
+    random <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x)))
+    random <- cbind(Parameter = c( "Study", "Phylogeny", "Species", "Trait"), random)
+    rownames(random) <- NULL
 
@@
     tabs1 <- rbind(fixed, random)
-   tabs1$Parameter <- c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial", "Study", "Phylogeny", "Species", "Trait")
-
-    flextable(tabs1) %>% flextable::bold(part = "header") %>% flextable::autofit() %>% flextable::add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% flextable::compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
+
+    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
 ```

### 2023-04-01 ms.qmd
Did not fix the in line eqn

@@
 
-Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}_{acute}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.

### 2023-04-01 ms.qmd
Fix fig B

@@
 Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
 In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).

### 2023-04-01 ms.qmd
We fixed the notation across word and html

--- 2023-04-01 ms.qmd
@@
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
-Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj].
-In contrast, a difference in $lnCVR_{Q_{10}}_{acclimation}$ relative to $lnCVR_{Q_{10}}_{acute}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured.
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj].
+In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured.
 If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
@@
 
-Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
+Overall, $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
 While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
-Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
 
@@
 Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
-However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10}}_{acclimation}$ compared to $lnRR_{Q_{10}}_{acute}$ when controlling for acclimation time.
+However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10}}_{acute}$ when controlling for acclimation time.
 

### 2023-04-01 ms.qmd
Fix

@@
 While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
-Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
 

### 2023-04-01 ms.qmd
Last fix on latex

@@
 Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
-However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10}}_{acute}$ when controlling for acclimation time.
+However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
 

### 2023-04-02 ms.qmd
Fixed fig legend names for effects

@@
 #| echo: false
+#| include: false
 ##################################
@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, update = TRUE)
 
@@
 #| label: fig-1
-#| fig-cap: "Taxonomic distribution of acute and acclimation Q10 estimates across major habitats.
+#| fig-cap: "Taxonomic distribution of acute and acclimation $Q_{10}$ estimates across major habitats.
 **A)** Phylogenetic distribution of taxa contained within the data.
@@
 Silouettes are representative taxa of major clades within the tree.
-**B)** Acute and Acclimation lnRR Q10 across marine, freshwater, and terrestrial environments.
-**C)** lnCVR Q10 across traits for marine, freshwater and terrestrial systems.
-Note there were no differences between acute and acclimation Q10 types.
+**B)** Acute and Acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial environments.
+**C)** $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
+Note there were no differences between acute and acclimation $Q_{10}$ types.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species."

### 2023-04-03 ms.qmd
writing

@@
 
-In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability (@fig-5).
+In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability across any of the habitats (@fig-5).
 

### 2023-04-05 ms.qmd
Adding in some notes about how to approach the problem/predcition of Q10 in future climate scenerios.

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, update = TRUE)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt)
 
@@
 
+### Global change in opportunity for selection
+
+```{r, global}
+#| label: global
+#| echo: false
+
+# Here, we want to make global predcitions, at the lat/long in the data for how the opportunity of selection is expected to change with climate change.
+How can we do this?
+Q10 effects already have temperature controls within the effect size.
+So, what we want is to be able to understand how Q10 changes with latitude and longitude.
+Once we know that, we an extarct how temperature is expected to change from our current levels to future levels.
+This will be in degrees C.
+Then, assuming no plasticty and evolution (big assumption) we can get a baseline change in variance for each site.
+We first need to adjust the predcited Q10 value so that it's at 1C temperaure, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
+This will adjust the predcited Q10 value to the change in 1 degree C.
+We can then multiply this by the temperature change expected at that location to get the % change in variance or acure/acclim response.
+We can then plot these globally.
+
+#############################
+rerun = FALSE
+if(rerun){
+
+  # Model lat and long....
+
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat +s(lat.y, long.x) + s(lat.y, long.x, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  saveRDS(model5_bayes, file = "./output/models/lnCVRQ10_5_bayes")
+
+  } else{
+          model5_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
+}
+
+lnCVRQ10_data_wild
+```
+
 ## **Discussion**

### 2023-04-06 ms.qmd
running model with splines.

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance)
 
@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat +s(lat.y, long.x) + s(lat.y, long.x, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + habitat + type + type:habitat + s(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
   } else{
-          model5_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
-}
-
-lnCVRQ10_data_wild
+  model5_bayes <- readRDS("./output/models/lnCVRQ10_5_bayes")
+}
+
+# Lets now make some predictions
+
+pred <- posterior_epred(model5_bayes, re_formula = 'NA')
+
 ```

### 2023-04-11 ms.qmd
re-render

@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + habitat + type + type:habitat + s(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + s(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 # Lets now make some predictions 
-
-pred <- posterior_epred(model5_bayes, re_formula = 'NA')
+#conditional_effects(model5_bayes)
+
+#pred <- posterior_epred(model5_bayes, re_formula = 'NA')
 

### 2023-04-12 ms.qmd
writs some methods about GAMMs

@@
 
+#### Modelling how climate change will impact on opportunity for selection
+
+To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiogical traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude.
+We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
+We used cubic splines for latitude and longitude (and their interaction) as any response could be complicated by local factors.
+Our model included random effects of species, trait, phylogeny and study.
+We predcited the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
+
 ### *Publication Bias*
@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + s(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + t2(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-#pred <- posterior_epred(model5_bayes, re_formula = 'NA')
-
+pred <- conditional_smooths(model5_bayes)
+pp_check(model5_bayes)
 ```

### 2023-04-12 ms.qmd
Not comfrotable with smoothers and don't seem to work with many brms functions to check. Simplifying model to linear and interaction between lata nd long separetd by habitat

@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + t2(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-pred <- conditional_smooths(model5_bayes)
+pred <- conditional_effects(model5_bayes)
 pp_check(model5_bayes)

### 2023-04-12 ms.qmd
Model not conveging for lat and long interacting with habitat. Simplified

@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 

### 2023-04-13 ms.qmd
Still not converging. Going to try spline of lat and long instead

@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + s(long.x) + s(lat.y) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 

### 2023-04-13 ms.qmd
Poor mixing still even with simplified model. Trying simplier splines now

--- 2023-04-12 ms.qmd
@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + s(long.x) + s(lat.y) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
 
@@
 pp_check(model5_bayes)
+
+predictions <- cbind(lnCVRQ10_data_wild, predict(model5_bayes))
 ```

### 2023-04-13 ms.qmd
tensor update

--- 2023-04-12 ms.qmd
@@
 
-  # Model lat and long....
-
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+  # Model lat and long. Need to exclude missing acclimdation data. That will make it easier to create predcitions and explore the model fit.
+
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(long.x, lat.y) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
 
@@
 
-# Lets now make some predictions 
-#conditional_effects(model5_bayes)
-
-pred <- conditional_effects(model5_bayes)
-pp_check(model5_bayes)
+# Lets explore the model and how it's predciting the real data
+  data_w_pred <- cbind(lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),], predict(model5_bayes))
+  head(data_w_pred)
+
+# Fitted vs actual data
+  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Predicted Effect Size", y = "Observed Effect Size") + theme_classic() + 
+  geom_abline(intercept = 0, slope = 1)
+
+# Fitted by Lat/long
+  ggplot(data = data_w_pred, aes(y = Estimate, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = Estimate, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+
+# Observed by Lat/long
+  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+
 ```

### 2023-04-13 ms.qmd
Added R2 in...

@@
 # Observed by Lat/long
-  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
+
+# How much variation does this model explain.
+Need to do this manually because function doesn't seme to work on the model object.
+We need to remember that predcit will include random effect variances so we may need to exclude this
+  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
+  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x))
+
+# Extract the random effect variances
+  v_trait <- re_post$sd_trait__Intercept^2
+    v_spp <- re_post$sd_spp__Intercept^2
+    v_phy <- re_post$sd_species_full__Intercept^2
+    v_std <- re_post$sd_record_num__Intercept^2
+      v_r <- re_post$sd_obs__Intercept^2
+
+# Lets get the total variance for the random effects only
+  tot_re <- v_trait + v_spp + v_phy + v_std + v_r
+
+# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
+  r2 <- (v_fix - tot_re) / (v_fix)
+
+  mean(r2) # Seems a bit high 
+  quantile(r2, probs = c(0.025, 0.975))
 

### 2023-04-14 ms.qmd
Checked R2, I think we are explaining about 50%, which is good

@@
   re_post <- posterior_samples(model5_bayes, pars = "^sd_")
-  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x))
+  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)
+
+# sigma2_v = typical sampling error variance**NEW STEP**
+sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
+              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))
+
+# Now check that var fix from raw data and remove sampling variance. **NEW STEP**
+  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
 
@@
 # Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
-  r2 <- (v_fix - tot_re) / (v_fix)
-
-  mean(r2) # Seems a bit high 
-  quantile(r2, probs = c(0.025, 0.975))
+    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too
+
+    mean(r2) # Seems a bit high 0.5
+  quantile(r2, probs = c(0.025, 0.975)); #0.27-0.69
+
+# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
+  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2
+
+  mean(r2_2) #  0.48
+  quantile(r2_2, probs = c(0.025, 0.975)); #0.31-0.60
 

### 2023-04-15 ms.qmd
Adding in start to making predcitions. Each habitat will need it's own so will subset data. Then, need to ake sure unique . distinct lata nd longs are in new data.

@@
 
+# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
+  terrest_data <- sub_data  %>% filter(habitat == "t")
+    new_data_t <- data.frame(
+      spp = terrest_data$spp,
+      trait = terrest_data$trait,
+      habitat = terrest_data$habitat,
+      c_accl_time = 0,
+      V = 0,
+      effect_size = 0,
+      lat = terrest_data$lat.y,
+      long = terrest_data$long.x
+    )
+
+terre_pred <- predict(model5_bayes, newdata = new_data_t, summary = FALSE)
+
 ```

### 2023-04-15 ms.qmd
Adding in all habitat types. Prepred for monday

--- 2023-04-14 ms.qmd
@@
 
+######################################################################
+# Model predcitions for terrestrial, marine and freshwater ectotherms
+######################################################################
+# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
+
+## Terrestrial Ectotherms
+  terrest_data <- sub_data  %>% filter(habitat == "t")
+    new_data_t <- data.frame(
+      spp = terrest_data$spp,
+      trait = terrest_data$trait,
+      habitat = terrest_data$habitat,
+      c_accl_time = 0,
+      V = 0,
+      lat = terrest_data$lat.y,
+      long = terrest_data$long.x
+    )
+
+terre_pred <- predict(model5_bayes, newdata = new_data_t, summary = FALSE)
+
+## Marine ectotherms  
+  marine_data <- sub_data  %>% filter(habitat == "m")
+    new_data_m <- data.frame(
+      spp = marine_data$spp,
+      trait = marine_data$trait,
+      habitat = marine_data$habitat,
+      c_accl_time = 0,
+      V = 0,
+      lat = marine_data$lat.y,
+      long = marine_data$long.x
+    )
+
+marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = FALSE)
+
+## Freshwater ectotherms
+  fresh_data <- sub_data  %>% filter(habitat == "f")
+    new_data_f <- data.frame(
+      spp = fresh_data$spp,
+      trait = fresh_data$trait,
+      habitat = fresh_data$habitat,
+      c_accl_time = 0,
+      V = 0,
+      lat = fresh_data$lat.y,
+      long = fresh_data$long.x
+    )
+
+fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = FALSE)
+
 ```

### 2023-04-16 ms.qmd
Need to think about how to deal with RE in predictions. They explain a lot of variation, do we integrate the unique data such that they go across all random effects?

@@
 # Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
+test <- sub_data  %>% filter(habitat == "t") %>% distinct(spp, lat.y, long.x)
+length(unique(test$spp))
 
 ## Terrestrial Ectotherms
-  terrest_data <- sub_data  %>% filter(habitat == "t")
+  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, habitat, lat.y, long.x)
   new_data_t <- data.frame(
-      spp = terrest_data$spp,
-      trait = terrest_data$trait,
-      habitat = terrest_data$habitat,
       c_accl_time = 0,
       V = 0,
-      lat = terrest_data$lat.y,
-      long = terrest_data$long.x
+      trait = 0,
+      obs = 0, 
+      type = "acute",
+      record_num = 0,
+      species_full = terrest_data$spp
     )
 
-terre_pred <- predict(model5_bayes, newdata = new_data_t, summary = FALSE)
+  # Create new dataframe with only unique values for predcition.
+  new_data_t2  <- cbind(terrest_data, new_data_t)
+
+  # We'll now make the predcitions from the model object using the new dataframe
+  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, robust = FALSE)
+
+  # Test manual calculations.
+We can also set summary = FALSE and then do the calculations ourselves.
+Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE
+  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, robust = FALSE)
+  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
 

### 2023-04-16 ms.qmd
I think we make predcitions using 'uncertainty' from sample_new_levels argument.

@@
   # We'll now make the predcitions from the model object using the new dataframe
-  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, robust = FALSE)
+  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
 
@@
 Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE
-  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, robust = FALSE)
+  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
   plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))

### 2023-04-17 R/2_climate_data.R
No mirioclcimate - ditching

@@ -104,63 +104,3 @@ write.csv(clim_data_matrix, "./output/climate_data/temp_timeseries.csv")
 r1 <- acf(as.numeric(clim_data_matrix[1,4:522]), lag.max = 522 - 4, plot = FALSE, na.action = na.pass)$acf[-1]
 lag <- c(1:518)
 plot(r1 ~ lag)
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-#         Microclimate
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-
-# Microclimate paper:
-# Kearney et al. 2019 "A method for computing hourly, historical, terrain-corrected microclimate anywhere on earth"
-# https://doi.org/10.1111/2041-210X.13330
-
-  devtools::install_github("ilyamaclean/microclima")  
-  
-# N.B. The function automatically assumes the raster should be 200 cells by 200 cells,
-#      so for a 30m resolution grid this is 6km across.
-#      I've reduced this to 50 cells across (1.5km x 1.5km) to make it faster
-
-
-  
-# Now we need the elevation at the point. Which we get using a loop because it can only take a single lat long coord at a time.
-run = FALSE
-if(run){
-  lat <- c()
-  for(i in 1:dim(geo_data)[1]){
-    elevation = microclima::get_dem(lat  = geo_data$lat[i], long = geo_data$long[i], resolution = 30, xdims = 50, ydims = 50)
-    lat <- c(elevation, lat)
-  }
-  names(lat) <- paste0(1:nrow(geo_data), "_", geo_data$species_full)
-saveRDS(lat, "./output/climate_data/elevation")
-} else{
-  elev <- readRDS("./output/climate_data/elevation")
-}
-# plot(r)
-
-s1 = Sys.time()
-
-# And... we'll cycle through microclimate generation one year at a time between 1981 and 2020
-for(Y in c(1981:2022)){
-  
-  temps = microclima::runauto(elev, dstart = paste0("01/01/",Y,")"),  # start date
-                              dfinish   = paste0("31/12/",Y,")"),  # end date
-                              hgt = 0.1, l = NA, x = NA,
-                              habitat = as.character(habitats$descriptor[gbif$Habitat[S]]),
-                              plot.progress = FALSE)
-  
[…]

### 2023-04-17 ms.qmd
Checking sign change predcitions. Nothing obviously wrong for subset of data checked. 4 studies

@@
   data_w_pred <- cbind(lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),], predict(model5_bayes))
-  head(data_w_pred)
 
@@
   geom_abline(intercept = 0, slope = 1)
+
+# Seems to be OK, but over and under-predciting at times.
+Lets explore the data for odd ball predictions to see if there are any obvious reasons why.
+T here are very few for the most part but lets see why sign changes occur which are most stricking differences.
+Sign changes indicate the observed data is completely opposite in sign to the predcited data
+
+#  Spot check of a bunch of studies doesn't show any obvious issues with the data.
+Note that data is repeated because acute and acclimated rates are calculated.
+We expect the rows of raw data for acute and acclim to be repeated even though these data are NOT all used to make the calculation.
+  sign_change_dat <- data_w_pred  %>% filter(sign(Estimate) != sign(effect_size))
+  #View(sign_change_dat)
 
@@
 # Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
-test <- sub_data  %>% filter(habitat == "t") %>% distinct(spp, lat.y, long.x)
-length(unique(test$spp))
-
+
+#############################
 ## Terrestrial Ectotherms
-  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, habitat, lat.y, long.x)
+#############################
+
+  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, lat.y, long.x)
   new_data_t <- data.frame(
@@
       obs = 0, 
-      type = "acute",
-      record_num = 0,
-      species_full = terrest_data$spp
+      record_num = 0
     )
@@
 We can also set summary = FALSE and then do the calculations ourselves.
-Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE
+Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE .
+These are extremely close.
+Maybe just a rounding isuse or a slight change in what summary stat is used...not clear if I supressed robust or not.
   terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
@@
 
+#############################
 ## Marine ectotherms  
+#############################
   marine_data <- sub_data  %>% filter(habitat == "m")
@@
 
+#############################
 ## Freshwater ectotherms
+#############################
   fresh_data <- sub_data  %>% filter(habitat == "f")

### 2023-04-17 ms.qmd
Fixed up predcition code

@@
 ######################################################################
-# Model predcitions for terrestrial, marine and freshwater ectotherms
+# Model predictions for terrestrial, marine and freshwater ectotherms
 ######################################################################
@@
 #############################
-  marine_data <- sub_data  %>% filter(habitat == "m")
+  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, lat.y, long.x)
+
   new_data_m <- data.frame(
-      spp = marine_data$spp,
-      trait = marine_data$trait,
-      habitat = marine_data$habitat,
       c_accl_time = 0,
       V = 0,
-      lat = marine_data$lat.y,
-      long = marine_data$long.x
+      trait = 0,
+      obs = 0, 
+      record_num = 0
     )
 
-marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = FALSE)
+  # Create new dataframe with only unique values for predcition.
+  new_data_m  <- cbind(marine_data, new_data_m)
+
+  # We'll now make the predcitions from the model object using the new dataframe
+  marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
 
@@
 #############################
-  fresh_data <- sub_data  %>% filter(habitat == "f")
+  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, lat.y, long.x)
+
   new_data_f <- data.frame(
-      spp = fresh_data$spp,
-      trait = fresh_data$trait,
-      habitat = fresh_data$habitat,
       c_accl_time = 0,
       V = 0,
-      lat = fresh_data$lat.y,
-      long = fresh_data$long.x
+      trait = 0,
+      obs = 0, 
+      record_num = 0
     )
 
-fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = FALSE)
+  # Create new dataframe with only unique values for predcition.
+  new_data_f  <- cbind(fresh_data, new_data_f)
+
+  # We'll now make the predcitions from the model object using the new dataframe
+  fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
 

### 2023-04-17 ms.qmd
Getting world maps started

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance, ggthemes)
 
@@
 
+  # Lets merge predictions with the original data
+  terrest_data <- cbind(terrest_data, terre_pred)
+
   # Test manual calculations.
@@
 Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE .
-These are extremely close.
-Maybe just a rounding isuse or a slight change in what summary stat is used...not clear if I supressed robust or not.
+These are extremely close, and I suspect are only different because sample_new_levels is sampling differently each time predict is run, so will be slightly different from run-to-run
   terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
@@
 
+  # Lets merge predictions with the original data
+  marine_data <- cbind(marine_data, marine_pred)
+
 #############################
@@
   fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # Lets merge predictions with the original data
+  fresh_data <- cbind(fresh_data, fresh_pred)
+
+# Now that we have all the predictions we can merge the data together.
+Note that species itself is not really that useful because each prediction at each latitude and longitude should incoperate the species effect.
+So we'll remove it.
+While I retain spp, it's still not totally specific to the species, but left it there so it's clear how these data match with the wild data.
+Note there are only 134 species because this is subset of the wild data.
+  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)
+
+```
+
+```{r}
+#| label: fig-preds
+#| fig-cap: Predictions
+
+world_map = map_data("world")
+
+ggplot() +
+  geom_map(
+    data = world_map, map = world_map,
+    aes(long, lat, map_id = region),
+    color = "black", fill = "lightgray") +
+  geom_point(
+    data = all_pred,
+    aes(long.x, lat.y, color = Estimate),
+    alpha = 0.7
+  ) +
+  theme_void() +
+  theme(legend.position = "none")
 

### 2023-04-18 ms.qmd
Map working

@@
     aes(long.x, lat.y, color = Estimate),
-    alpha = 0.7
-  ) +
-  theme_void() +
-  theme(legend.position = "none")
+    alpha = 0.7, size = 6
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"))
 

### 2023-04-18 ms.qmd
Adjustments to map to make it look a little prettier

--- 2023-04-17 ms.qmd
@@
 
-world_map = map_data("world")
+world_map = map_data("world") %>% 
+  filter(! long > 180)
 
@@
     color = "black", fill = "lightgray") +
+  expand_limits(x = world_map$long, y = world_map$lat) +
+  coord_map("moll") +
   geom_point(
@@
     aes(long.x, lat.y, color = Estimate),
-    alpha = 0.7
-  ) +
-  theme_void() +
-  theme(legend.position = "none")
+    alpha = 0.7, size = 6
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) +
+   theme_map()
 

### 2023-04-18 ms.qmd
Map current

--- 2023-04-17 ms.qmd
@@
 
-world_map = map_data("world")
-
-ggplot() +
+world_map = map_data("world") %>% 
+  filter(! long > 180)
+
+map1_current <- ggplot() +
   geom_map(
@@
     aes(long.x, lat.y, color = Estimate),
-    alpha = 0.7
-  ) +
-  theme_void() +
-  theme(legend.position = "none")
+    alpha = 0.7, size = 6
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) +
+   theme_map()
+map1_current
 

### 2023-04-18 ms.qmd
New colour scale to viridis

--- 2023-04-18 ms.qmd
@@
     aes(long.x, lat.y, color = Estimate),
-    alpha = 0.7, size = 6
-  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"))
+    alpha = 0.7, size = 5
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) + scale_color_viridis() +
+   theme_map()
+map1_current
 

### 2023-04-18 ms.qmd
Starting more detailed map

@@
 
+zoom_areas <- data.frame(
+     x = c(-130,  -10, 130),
+     y = c(  25, 30, -25),
+  xend = c( -50, 45, 170),
+  yend = c(  55,  70, -5),
+  label = c("North America", "Europe", "Asia")
+)
+
+zoom_plots <- lapply(1:nrow(zoom_areas), function(i) {
+  map1_current +
+    geom_polygon(fill = "gray80", color = "black") +
+    coord_cartesian(xlim = c(zoom_areas[i, "x"], zoom_areas[i, "xend"]), 
+                    ylim = c(zoom_areas[i, "y"], zoom_areas[i, "yend"])) +
+                    theme(legend.position = "none")
+})
+
+p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])
+
 ```

### 2023-04-18 ms.qmd
Adding some ployt layout features. I think the insets work better

@@
 
-p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])
+# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
+
+p <- (zoom_plots[[1]] | zoom_plots[[2]]) /map1_current / (zoom_plots[[3]]) + plot_layout(
+  nrow = 3, # 3 rows of plots,
+  ncol = 3, # 3 columns of plots,
+  heights = c(1, 2, 1), # The first plot is half the size of the second and thrid plot
+  widths = c(1, 1, 1) # all plots have equal width
+)
+
+map1_current + inset_element(zoom_plots[[1]], left = 0, bottom = 0.95, right = 0.4, top = 1.4, align_to = 'full') + inset_element(zoom_plots[[2]], left = 0.7, bottom =0.95, right = 1, top = 1.4, align_to = 'full') + plot_annotation(tag_levels = "A", tag_suffix = ")")
 

### 2023-04-19 ms.qmd
Ditched insets. to hard to control labelling

--- 2023-04-18 ms.qmd
@@
 
-p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])
+# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
+
+p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  / (plot_spacer() | plot_spacer() |zoom_plots[[3]]) + plot_layout(heights  = c(1, 2.5, 1)) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+p
 

### 2023-04-19 ms.qmd
Going to ditch Southern hemisphere as there isn't too much data there anyway

--- 2023-04-18 ms.qmd
@@
 zoom_areas <- data.frame(
-     x = c(-130,  -10, 130),
-     y = c(  25, 30, -25),
-  xend = c( -50, 45, 170),
-  yend = c(  55,  70, -5),
-  label = c("North America", "Europe", "Asia")
+     x = c(-130, -10, -60, 145),
+  xend = c( -50, 48, -35, 155),
+     y = c(  25, 30, 0, -45),
+  yend = c(  55,  70, -60, -10),
+  label = c("North America", "Europe", "South America", "Australia")
 )
@@
 
-p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])
+# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
+
+p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2.5)) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+p
 

### 2023-04-19 ms.qmd
Fixed base_size for legend key text size

@@
   all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)
-
+  spp_wild  <- length(unique(sub_data$spp))
 ```
+
+Measurements of acute and acclimation responses for wild ectotherms was much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`).
+Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).
+Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
 
@@
     alpha = 0.7, size = 5
-  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) + scale_color_viridis() +
-   theme_map()
-map1_current
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) + scale_color_viridis() + theme_map(base_size = 22)
 
@@
 
-# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
-
-p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2.5)) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-
-p
-
+# Make a multipanel plot. Make the world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
+
+p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2.5)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"))
+
+ggsave(p, filename = "./output/figures/fig-preds.png", width = 9.1, height = 7.2)
+
+image_read("./output/figures/fig-preds.png")
+```
 ```

### 2023-04-20 ms.qmd
Rerendered. Fixed up some text on climate modelling and filtered global data to only acclimation

@@
 ---
-title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations"
+title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
 It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
-Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations were used for climate analyses.
-
-Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package [vers.
+Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
+
+ Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface temperature at 2 meters (0.01 resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25 resolution) using the *ncdf4* R package [vers.
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
@@
 
-#### Modelling how climate change will impact on opportunity for selection
+#### *Modelling how climate change will impact on opportunity for selection*
 
@@
 
-Measurements of acute and acclimation responses for wild ectotherms was much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`).
+Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`).
 Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).
@@
 #| label: fig-preds
-#| fig-cap: Predictions
+#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
 
@@
   geom_point(
-    data = all_pred,
+    data = all_pred  %>% filter(type == "acclim"),
     aes(long.x, lat.y, color = Estimate),
@@
 zoom_areas <- data.frame(
-     x = c(-130, -10, -60, 145),
+     x = c(-130, -15, -60, 145),
   xend = c( -50, 48, -35, 155),
-     y = c(  25, 30, 0, -45),
-  yend = c(  55,  70, -60, -10),
+     y = c(  25, 34, 0, -45),
+  yend = c(  55,  69.8, -60, -10),
   label = c("North America", "Europe", "South America", "Australia")
@@
 
-p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2.5)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"))
+p <- (zoom_plots[[1]] | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"), plot.margin = unit(c(0, 0, 0, 0), "cm"))
 
@@
 image_read("./output/figures/fig-preds.png")
-```
 ```
@@
 ## References
+
 <br>

### 2023-04-28 R/2_climate_data.R
NOte for Alex on how to proceed

@@ -252,6 +252,7 @@ for(i in 1:nrow(geo_data)){
 
 # Read NetCDF
 
+########################### **ALEX. BELOW IS THE CODE WE USED TO EXTRACT THE CLIMATE DATA AND CALCULATE the 1) variance and autocorrelation from past to current and then 2) get the future climate projections. ** I guess you just need to modify below. The path name to the data on GitHub is: "data/climate_data/ERA5_LAND/" which is the folder where all teh files you shared live. 
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # Previous Projections

### 2023-04-29 R/Surface_climate_timelines_hardcopy_ERA5.R
Cleaning. Removing old files from Alex and others

@@ -1,156 +1,0 @@
-###################################################################################
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-#                       ERA5 Reanalysis 1 CLIMATE DATA
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-###################################################################################
-
-# This version doesn't actively download point estimates of temperature. 
-# Instead a NetCDF for ERA5 was downloaded for 1979-present.
-
-# See Word doc: Data/Downloading ERA5 historic climate data.docx
-
-# Note that the data is stored in Kelvin and transformed.
-# 2m surface temperature
-#     scale_factor: 0.00176319797961702
-#     add_offset: 257.703670097788
-# Sea Surface Temperature
-#     scale_factor: 0.00061697729459776
-#     add_offset: 289.46490147229
-
-# Time is recorded in hours since 1900-01-01 00:00:00.0
-
-rm(list=ls())
-library(ncdf4)
-#library(sf)
-#library(raster)
-
-if(!file.exists("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat_and_ERA5_rowcol.csv")){
-  gbif     = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
-  gbif$Fid = 1:nrow(gbif)
-  #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
-  
-  gbif$ERA5col = gbif$longitude
-  gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
-  gbif$ERA5col = cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440))
-  
-  gbif$ERA5col = gbif$longitude
-  gbif$ERA5col[gbif$ERA5col<0] = (180-abs(gbif$ERA5col[gbif$ERA5col<0]))+180
-  gbif$ERA5col = as.numeric(cut(gbif$longitude, seq(0,360,0.25), labels=c(1:1440)))
-  
-  ncfname   = "./data/climate_data/ERA5/ERA5_LST_and_SST_1979-present.nc"
-  ERA5.air  = nc_open(ncfname)
-  print(ERA5.air)
-  dname     = "t2m"
[…]

### 2023-04-29 R/Surface_climate_timelines_hardcopy_NCEP.R

@@ -1,150 +1,0 @@
-###################################################################################
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-#                       NCEP Reanalysis 1 CLIMATE DATA
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-###################################################################################
-
-# This version doesn't actively download point estimates of temperature. 
-# Instead NCDFs for each year 1960-2000 were pre-downloaded and I extract what's available.
-
-rm(list=ls())
-library(ncdf4)
-#library(sf)
-#library(raster)
-
-if(!file.exists("./output/data/climate_data/GBIF/Terrestrial_GBIF_occurrences_plus_habitat_and_NCEP_rowcol.csv")){
-  gbif     = read.csv("./data/climate_data/Terrestrial_GBIF_occurrences_plus_habitat.csv")
-  gbif$Fid = 1:nrow(gbif)
-  #gbif_shp = st_as_sf(gbif, coords = c("longitude", "latitude"), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
-  
-  gbif$NCEPcol = gbif$longitude
-  gbif$NCEPcol[gbif$NCEPcol<0] = (180-abs(gbif$NCEPcol[gbif$NCEPcol<0]))+180
-  gbif$NCEPcol = cut(gbif$longitude, seq(0,360,2.5), labels=c(1:144))
-  
-  gbif$NCEPcol = gbif$longitude
-  gbif$NCEPcol[gbif$NCEPcol<0] = (180-abs(gbif$NCEPcol[gbif$NCEPcol<0]))+180
-  gbif$NCEPcol = as.numeric(cut(gbif$longitude, seq(0,360,2.5), labels=c(1:144)))
-  
-  ncfname   = "./data/climate_data/NCEP_Reanalysis 1/air.sig995.1960.nc"
-  NCEP.air  = nc_open(ncfname)
-  print(NCEP.air)
-  dname     = "air"
-  lon       = ncvar_get(NCEP.air, "lon")
-  head(lon)                                     # NCEP data is at 2.5' resolution
-  nlon      = length(lon) # number of columns
-  lat       = ncvar_get(NCEP.air, "lat", verbose = F)
-  head(lat)
-  nlat      = length(lat) # number of rows
-  t         = ncvar_get(NCEP.air, "time")
-  head(t)
[…]

### 2023-04-29 R/Surface_microclimate_timelines.R

@@ -1,345 +1,0 @@
-###################################################################################
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-#               MICROCLIMATE OF TERRESTRIAL AND FRESHWATER TAXA
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-###################################################################################
-
-
-rm(list=ls())
-library(raster)
-
-spp.list = read.csv("q10_meta-master/data/species_list_Q10.csv")
-spp      = spp.list$species_full
-spp[71]  = "Enithares"                 # Switch 'Enithares sp' to whole genus
-spp[73]  = "Euchemotrema leaii"        # Synonym: Euchemotrema leai
-spp[133] = "Merlangius merlangus"      # Synonym: Merlanguis merlangus
-spp[175] = "Pinctada mazatlanica"      # Synonym: Pinctada mazatlantica
-spp[202] = "Hoplobatrachus tigerinus"  # Synonym: Rana tigrina
-spp[203] = "Lithobates virgatipes"     # Synonym: Rana vergatipes
-spp[239] = "Zoarces viviparus"         # Synonym: Zoarces viviparous
-
-widedat  = read.csv("q10_meta-master/data/CombinedData_wide.csv")
-widedat$spp_names = paste(widedat$genus,widedat$species)
-habitat  = widedat$habitat[match(spp.list$species_full, gsub("_"," ",widedat$spp_names))]
-
-# Change habitat of Shortnose Sturgeon (Acipenser brevirostrum) to freshwater
-habitat[4] = "f"
-widedat$habitat[match("Acipenser brevirostrum", widedat$spp_names)] = "f"
-
-
-#  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  #
-#     Coordinates of Q10 sites by habitat
-#  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  #
-
-# Try to fill some of the location rows missing data
-widedat[widedat$geo_location %in% "Coruna, Spain",         c("lat","long")] = c(43.425230, -8.414665)   # Marine sp. so placed point to north
-widedat[widedat$geo_location %in% "Newhay, Yorkshire UK",  c("lat","long")] = c(53.769377, -0.995573)
[…]

### 2023-04-29 R/performance.R

@@ -1,70 +1,0 @@
-library(rstan)
-library(brms)
-rstan::rstan_options(auto_write = TRUE)
-options(mc.cores = parallel::detectCores())
-
-# parameters for the metabolic rate model, natural log scale
-lnMetabolicRate  <-  function (lnB0 = -5, scalingExp = 0.75, lnMass = log(1:10)) {
-	lnB0 + scalingExp * lnMass
-}
-
-# parameters for the Boltzmann relationship, natural log scale
-lnBoltzmann  <-  function (lnBoTs = -5, Er = 0.6, invKT = 1 / 8.62e-5 * (1 / mean(274:310) - 1 / 274:310)) {
-	lnBoTs + Er * invKT
-}
-
-# complete Schoolfield-Sharpe equation
-lnSchoolfield  <-  function (lnBoTs = -5, Er = 0.6, Ei = 3, Topt = 303, tempKelvin = 274:310) {
-	boltz  <-  lnBoltzmann(lnBoTs, Er, 1 / 8.62e-5 * (1 / mean(tempKelvin) - 1 / tempKelvin))
-	boltz - log(1 + (Er / (Ei - Er)) * exp(Ei / 8.62e-5 * (1 / Topt - 1 / tempKelvin)))
-}
-
-boltzmannModelBrms  <-  function (data) {
-	# lnMass slope == scalingExp, invKT slope == Er
-
-	# FIXED EFFECTS ONLY
-	set.seed(1)
-	brms::brm(lnRateBoltz ~ lnMass + invKT, data = data, family = gaussian(), prior = c(brms::prior(normal(1, 2), 'b'), brms::prior(normal(3, 3), 'Intercept'), brms::prior(student_t(3, 0, 20), 'sigma')), sample_prior = TRUE, chains = 3, cores = 3, iter = 1e3)
-	
-	# OR ADD RANDOM EFFECTS like in lme4, where "ID" is your grouping variable
-	# brms::brm(lnRateBoltz ~ lnMass + invKT + (lnMass + invKT | ID), data = data, family = gaussian(), prior = c(brms::prior(normal(1, 2), 'b'), brms::prior(normal(3, 3), 'Intercept'), brms::prior(student_t(3, 0, 20), 'sd'), brms::prior(student_t(3, 0, 20), 'sigma')), sample_prior = TRUE, chains = 3, cores = 3, iter = 1e3)
-}
-
-schoolfieldModelBrms  <-  function (data) {
[…]

### 2023-04-29 R/exploratory/analysis.Rmd
Moved Shiny app for exploration into exploreatory folder

---
title: "Q10 Exploratory Analysis"
output: html_document
#df_print: paged
#toc: yes
date: "`r format(Sys.time(), '%d %B, %Y')`"
runtime: shiny
---

## Install packages
You will need to install a couple packages for loading data:

```{r, echo = TRUE, eval = FALSE, message = FALSE}
	install.packages("googlesheets")
	install.packages("rmarkdown")
	install.packages("phytools")
	install.packages("ape")
	install.packages("rotl")
	install.packages("tidyverse")
```

```{r, echo = TRUE, eval = TRUE, message = FALSE}
	library("googlesheets")
	library("rmarkdown")
	library("phytools")
	library("ape")
	library("rotl")
	library("tidyverse")
```

## Load the google spreadsheet
We can load the dataset using the google sheets

```{r, echo = TRUE, eval = TRUE, message = FALSE, error = FALSE}
	  gs <- gs_title("q10_newdata")
	data <- as.data.frame(gs_read(ss = gs))

```

## Explore the data

The data consists of a total of **`r length(unique(data$record_num))`** studies, including a total of **`r length(unique(data[-grep("_o", data$record_num), "record_num"]))`** new studies that we extracted over the last few months. This is already a fairly large increase in the total number of studies, and represents a fairly significant update to the previous dataset.

###Plots of various variables in the data

```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE}
	 data2 <- dplyr::select_if(data, is.numeric)
	 ui1 <-  fluidPage(
		  sidebarLayout(
		  	sidebarPanel(selectInput("variable1", "Variable on Y-axis for plotting", names(data2)),
		  selectInput("variable2", "Variable on X-axis for plotting", names(data2)),
		  selectInput("transformY", "Transformation of Y", c("none", "log")), 
		  selectInput("transformX", "Transformation of X", c("none", "log"))),
		  mainPanel(plotOutput("plot",  height = "400px", width = "400px"))
	 	 )
		)
	  server1 <-function(input,output){
		  output$plot <- renderPlot({
		  	if(input$transformY == "log" & input$transformX == "none"){
				var1 <- log(data[,input$variable1])
		  		var2 <- data[,input$variable2]		  		
		  	}

		  	if(input$transformX == "log" & input$transformY == "none"){
				var1 <- data[,input$variable1]
		  		var2 <- log(data[,input$variable2])		  		
		  	}

		  	if(input$transformX == "log" & input$transformY == "log"){
				var1 <- log(data[,input$variable1])
		  		var2 <- log(data[,input$variable2])		  		
		  	}

			if(input$transformX == "none" & input$transformY == "none"){
				var1 <- data[,input$variable1]
		  		var2 <- data[,input$variable2]		  		
		  	}
		  	par(mar=c(4,4,1,1))
		  	plot(var1 ~ var2, pch = 16, cex = 1.5, ylab = input$variable1, xlab = input$variable2)	
		  })
		}

	  shinyApp(ui1, server1)
```

### Categorical variables and amount of data in levels

This section is really for checking the categorical variables. Mainly for making sure the levels in the variables are correct, and for us to make note of some of the problems that might arise if we modeled with these as categorical variables.

```{r, echo = FALSE, eval = TRUE}

	data6 <- dplyr::select_if(data, is.character)

	ui6 <- fluidPage(
		sidebarLayout(
			sidebarPanel(
				selectInput("var1", "Variable", names(data6))) ,
		mainPanel(tableOutput("table_sum"))
		))

	server6 <- function(input, output){

		output$table_sum <- renderTable({
			table( Variable = data6[,input$var1])
		})

	}

	shinyApp(ui6, server6)
```

###Plot of SE and N

Check that the standard error (SE) for a set of variables correlates with sample size, and look for outliers in SE.

```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE}
	ui2<- fluidPage(
	 	sidebarLayout(
	 		sidebarPanel(selectInput("se", "Standard Error Variable", c("r1.1_CV", "r1.1_logCV", "r1.2_CV", "r1.2_logCV", "r2.1_CV", "r2.1_logCV", "r2.2_CV", "r2.2_logCV")),
	  		selectInput("N", "Sample size", c("r1.1_N", "r1.2_N", "r2.1_N", "r2.2_N"))),
	  		mainPanel(plotOutput("plot2", height = "400px", width = "400px"))
	  		)
		)
	server2 <- function(input, output){
	  output$plot2 <- renderPlot({
	  	selectedData <- reactive({data[,c(input$se, input$N)]})
	  	par(mar = c(4.1,4.1,1,1))
	  	plot(selectedData(), pch = 16, cex = 1.5)	
	  })
	  }

	shinyApp(ui2, server2)  
```

### Rows with large SE

So, there are clearly some problems with the data still. These SE's are way to large for many rows. Probably these were mistakenly entered as SD, so we will check these:

```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE}
	data2 <- as.data.frame(data)

	ui3 <- fluidPage(
		selectInput("se", "Standard Error Variable", c("r1.1_CV", "r1.1_logCV", "r1.2_CV", "r1.2_logCV", "r2.1_CV", "r2.1_logCV", "r2.2_CV", "r2.2_logCV")),
		numericInput("val", "Cutoff of SE", 30),
		tableOutput("table2")
		)

	server3 <- function(input, output){

		output$table2 <- renderTable({	
		cols <-  c(1:3, 18, 21)
		colInput <- which(names(data2) == input$se, TRUE)
		rows <-  which((data2[, input$se]*-1) >= input$val, TRUE)
		data2[rows, c(cols, colInput)]
		})
	}

	shinyApp(ui3, server3)

```

## Species in the dataset

```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE}
	data$binom_species <- paste0(data$genus, "_", data$species) 	
```
We have a total of **`r length(unique(data$binom_species))`** unique species in the data set. We can get a sense of the phylogenetic relationships between species using time tree. To do this we can export the unique species names from [Time Tree](http://www.timetree.org/). First we can load a txt file of the list of species and then upload them to time tree to generate a nexus file that we can use to bring in the phylogenetic relationships among the species.

Looking at many of these we can see that they are subspecies that need to be resolved. This shouldn't take too much work to sort. The question then becomes what is the best way to deal with uncertain taxonomic positions of existing taxa?

Here is the tree with the phylogenetic relationships of the taxa identified in time tree:

```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 8}
	# First bring in the newick file
		tree <- read.tree(file = "./phylogeny/species.nwk")

	# We can then plot the tree to have a look
		par(mar = c(1,1,1,1))
		plot(tree, type = "fan", cex = 0.65)
```
```{r, echo = FALSE, eval = TRUE, message = FALSE, error = FALSE}

	ui7<- fluidPage(
	 	sidebarLayout(
	 		sidebarPanel(selectInput("order1", "Choose Order:", unique(data$order))),
	  		mainPanel(plotOutput("plot_phylo", height = "400px", width = "400px"))
		))

	server7 <- function(input, output){
	  output$plot_phylo <- renderPlot({
	  	species <- as.character(unique(data[grep(input$order1, data$order), "binom_species"]))
	  	pruned.tree<-drop.tip(tree, tree$tip.label[!tree$tip.label %in% species])
		plot(pruned.tree, type = "phylogram", show.tip.label = TRUE, cex = 0.6, main = input$order1)	
	  })
	}

	shinyApp(ui7, server7)  
```

The tree currently contains `r length(tree$tip.label)` taxa, all identified in time tree, which doesn't match the current list of species in the dataset given that 83 were identified as "unresolved" so there are other synonymous names we need to look at, probably best to use with rotl.

Often when we do this there are quite a few taxonomic uncertainties we need to deal with. In our data specifically, we have a total of 83 unresolved tips. The list of taxa we should have a look for to resolve uncertainty are as follows, along with the corresponding rows in the data that match these species:

```{r, echo = FALSE, eval = TRUE}

data_species <- read.csv("./phylogeny/species_notFound.csv")
data_species$binomial <- paste0(data_species$genus, "_", data_species$species)
data_species <- dplyr::arrange(data_species, binomial) 
data_species$letter <- substr(data_species$binomial, 1, 1)

	ui5 <- fluidPage(
		sidebarLayout(
			sidebarPanel(
				selectInput("Genus", "Alphabetical Order", unique(data_species$letter)),
				tableOutput("tablespp")),
		mainPanel(tableOutput("table_rows"))
		))

	server5 <- function(input, output){

		output$tablespp <- renderTable({	
			data_species[data_species$letter == input$Genus,"binomial"]
		})

		output$table_rows <- renderTable({	
			cols <-  c(1:3,  36)
			rows <-  which(data$binom_species %in% data_species[data_species$letter == input$Genus,"binomial"], TRUE)
			data[rows, cols]
			})
	}

	shinyApp(ui5, server5)
```

We can also see if we can improve on the matching using rotl, but we could also use to identify synonyms and sort out relationships where taxa don't match

```{r, echo = TRUE, eval = FALSE, message = FALSE, error = FALSE}

	# Unfortunately, we have to do this in 2 steps as it can only search 250 taxa at once, and we have 252
		chunk2 <- function(x,n) split(x, cut(seq_along(x), n, labels = FALSE))
	      size <- 1:length(unique(data$binom_species))
	      vecs <- chunk2(size,7)

	   tree_rotl_names <- data.frame()

	for(i in 1:7){
		tree_rotl_tmp <- tnrs_match_names(names = unique(data$binom_species)[vecs[[i]]])
		    tree_rotl_names <- rbind(tree_rotl_names, tree_rotl_tmp)
	}

	# Grab the tree, where phylogeny is informed 
	tree_rotln <- tol_induced_subtree(ott_ids=na.omit(tree_rotl$ott_id))

	# Omit any unknown taxa
	taxonomy_taxon(na.omit(tree_rotl$ott_id))

	# Write the tree
	write.tree(file = paste0("output/data/tree_rotl.", date(), ".txt"), tree_rotl)

```

```{r, echo = FALSE, eval = FALSE, message = FALSE, error = FALSE}
	data2 <- as.data.frame(data)#

	ui3 <- fluidPage(
		selectInput("se", "Standard Error Variable", c("r1.1_se", "r1.2_se", "r2.1_se", "r2.2_se")),
		numericInput("val", "Cutoff of SE", 30),
		verbatimTextOutput("table")
		)

	server3 <- function(input, output){

		output$table <- renderPrint({	
		cols <-  c(1:3, 20, 21)
		colInput <- which(names(data2) == input$se, TRUE)
		rows <-  which(data2[, input$se] >= input$val, TRUE)
		data2[rows, c(cols, colInput)]
		})
	}

	shinyApp(ui3, server3)
```

### 2023-04-30 R/2_climate_data.R
Updated path so Alex's script works here

@@ -52,7 +52,7 @@ wf_set_key(user="89307", key="e661d59a-c4f0-4e9e-9da4-476fa0a9536e", service='cd
 
 for(i in which(geo_data$source=="w") ){  #nrow(geo_data)){
   
-  filelist = unlist(lapply(list.files("./Data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
+  filelist = unlist(lapply(list.files("./data/climate_data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
   filelist = as.numeric(gsub("\\.nc","",filelist))
   
   if( !i %in% filelist ){
@@ -130,7 +130,7 @@ for(i in which(geo_data$source=="w") ){  #nrow(geo_data)){
       user     = "89307",
       request  = request,   
       transfer = TRUE,  
-      path     = "./Data/ERA5_LAND",
+      path     = "./data/climate_data/ERA5_LAND",
       verbose  = FALSE
     )
     
@@ -170,7 +170,7 @@ for(i in which(geo_data$source=="w") ){  #nrow(geo_data)){
 
 for(i in 1:nrow(geo_data)){
   
-  filelist = unlist(lapply(dir("./Data/ERA5_LAND/",pattern="proj"),FUN=function(x) strsplit(x,"proj")[[1]][2]))
+  filelist = unlist(lapply(dir("./data/climate_data/ERA5_LAND/",pattern="proj"),FUN=function(x) strsplit(x,"proj")[[1]][2]))
   filelist = as.numeric(gsub("\\.zip","",filelist))
   
   if( !i %in% filelist ){
@@ -221,7 +221,7 @@ for(i in 1:nrow(geo_data)){
       user     = "89307",
       request  = request,   
       transfer = TRUE,  
-      path     = "./Data/ERA5_LAND",
+      path     = "./data/climate_data/ERA5_LAND",
       verbose  = FALSE
     )
     

### 2023-05-01 R/2_climate_data.R
Added to climate script to clean up time series files from Alex

@@ -337,3 +337,22 @@ write.csv(clim_data_matrix, "./output/climate_data/temp_timeseries.csv")
 r1 <- acf(as.numeric(clim_data_matrix[1,4:522]), lag.max = 522 - 4, plot = FALSE, na.action = na.pass)$acf[-1]
 lag <- c(1:518)
 plot(r1 ~ lag)
+
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+# Merge together SST and Land projections as loop separated them out
+# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+
+# Read in the updated time series data
+   sst <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+  land <- read.csv("./output/climate_data/ERA5_landsurface_timeseries.csv")
+
+# Clear missing data from each sheet, merge sheets together and then re-arrange
+
+ sst <- sst %>% filter(!is.na(mean))
+land <- land %>% filter(!is.na(mean))
+
+# Rbind
+    clim_data_matrix <- rbind(sst, land)  %>% arrange(Species)
+
+# Write out
+write.csv(clim_data_matrix, "./output/climate_data/temp_timeseries.csv", row.names = FALSE)

### 2023-05-02 R/2_climate_data.R
Still not sure what happened with species/pop numbers after Alex ran the data. Clarifying some more

@@ -339,20 +339,17 @@ lag <- c(1:518)
 plot(r1 ~ lag)
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-# Merge together SST and Land projections as loop separated them out
+# New Climate Projections - Cleanup and export
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 
 # Read in the updated time series data
-   sst <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
-  land <- read.csv("./output/climate_data/ERA5_landsurface_timeseries.csv")
+   sst <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv") # Climate data includes SST and air temperature for terrestrial
+  land <- read.csv("./output/climate_data/ERA5_landsurface_timeseries.csv") # Climate data includes SST and soil temperature for terrestrial
 
 # Clear missing data from each sheet, merge sheets together and then re-arrange
 
  sst <- sst %>% filter(!is.na(mean))
 land <- land %>% filter(!is.na(mean))
-
-# Rbind
-    clim_data_matrix <- rbind(sst, land)  %>% arrange(Species)
 
 # Write out
 write.csv(clim_data_matrix, "./output/climate_data/temp_timeseries.csv", row.names = FALSE)

### 2023-05-03 ms.qmd
Added a ggmagnify code
Climate methods

@@
 Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface temperature at 2 meters (0.01 resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25 resolution) using the *ncdf4* R package [vers.
+For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface air temperature at 2 meters (0.01 resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25 resolution) using the *ncdf4* R package [vers.
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
 We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+For terrestrial species we also collected soil temperature as for many species this maybe more representative of microhabitat choice compared to air temperature.
+We fit models using both air and soil temperature and found that the results were qualitatively similar.
+As such, we only present results for air temperature (See Supplementary Materials).
 
@@
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
+climate2 <- climate %>% mutate(match = interaction(Species, Longitude, Latitude)) %>% dplyr::select(-c(5:523))
 
@@
 Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
+
+devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
 

### 2023-05-03 ms.qmd
Writing some methods about climate modelling

@@
 We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used cubic splines for latitude and longitude (and their interaction) as any response could be complicated by local factors.
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors.
 Our model included random effects of species, trait, phylogeny and study.
-We predcited the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
+We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
+To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1$^{\circ}$C change as opoosed to 10$^{\circ}$C as follows:
+
+$$
+lnCVR_{Q_{1}} = \frac{lnCVR_{Q_{10}}}{10}
+$$ {#eq-lCVRpred}
+
+@eq-lCVRpred turned the expected change across 10$^{\circ}$C to 1$^{\circ}$C.
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenerios in 2080.
 

### 2023-05-08 R/2_climate_data.R
Code from Alex

@@ -1,3 +1,4 @@
+
 rm(list=ls())
 library(tidyr)
 library(ecmwfr)
@@ -8,11 +9,10 @@ library(maps)
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # SURVEY LOCATIONS
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
+geo_data = read.csv("Data/Species_LatLong_plusHabitat.csv")  # ./data/climate_data/Species_LatLong_plusHabitat.csv
+# Remove missing lat and long
+geo_data = geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
 
-geo_data = read.csv("./data/climate_data/Species_LatLong_plusHabitat.csv")
-
-# First remove missing lat and long
-geo_data <- geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # SETUP API
@@ -28,6 +28,7 @@ wf_set_key(user="89307", key="e661d59a-c4f0-4e9e-9da4-476fa0a9536e", service='cd
 # paste the API code from the CDS website, and then use an RStudio plugin to 
 # convert the text to an R-relevant command!
 #   https://cran.r-project.org/web/packages/ecmwfr/vignettes/cds_vignette.html
+
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # HISTORIC CLIMATIC DATA
@@ -52,7 +53,7 @@ wf_set_key(user="89307", key="e661d59a-c4f0-4e9e-9da4-476fa0a9536e", service='cd
 
 for(i in which(geo_data$source=="w") ){  #nrow(geo_data)){
   
-  filelist = unlist(lapply(list.files("./data/climate_data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
+  filelist = unlist(lapply(list.files("./Data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
   filelist = as.numeric(gsub("\\.nc","",filelist))
   
   if( !i %in% filelist ){
@@ -66,7 +67,11 @@ for(i in which(geo_data$source=="w") ){  #nrow(geo_data)){
[…]

### 2023-05-09 ms.qmd
Minor change
Updates to lnRR on new files from Alex

@@
 We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used non-linear tensors for latitude and longitude as any response could be complicated by local factors.
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
 Our model included random effects of species, trait, phylogeny and study.
@@
 # Bring in Climate data
-climate <- read.csv("./output/climate_data/temp_timeseries.csv")
+climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
 
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(species, lat, long)) %>% dplyr::select(-c(5:523))
+climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
 

### 2023-05-10 ms.qmd
Found out the match problem Climate data reversed Lat and long. Checking with Alex about if this affects the data or just a quick renaming

@@
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+climate2 <- climate %>% mutate(match = interaction(Species, Longitude, Latitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
 

### 2023-05-11 ms.qmd
Fixed lat long order

--- 2023-05-09 ms.qmd
@@
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
-Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis @Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn].
+Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn].
 Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.

### 2023-05-12 ms.qmd
Fixing code error for loading fig 9, change lat and long stuff

@@
 ###################################################
-rerun = FALSE
+rerun = TRUE
 if(rerun){
@@
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Longitude, Latitude)) %>% dplyr::select(-c(5:523))
+climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(-c(5:523))
 
@@
 
-  p9.1.2 <- image_read("./output/figures/fig8.png")
+  p9.1.2 <- image_read("./output/figures/fig9.png")
   p9.1.2 

### 2023-05-12 ms.qmd
Update ignore and fixing orchard plots as data argument now dropped

--- 2023-05-11 ms.qmd
@@
 
-  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", data = lnRRQ10_data_m, angle = 0)
+  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 0)
 
@@
 col <- c("#0871B9", "#F3B40D", "#1BB908")
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 5) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 5) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
 This is not true of aquatic systems.
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", data = lnCVRQ10_data, angle = 45, trunk.size = 5) +
+  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 5) +
               scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
@@
 
-ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_m, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
 
-ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_f, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
 
-ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", data = lnRRQ10_data_t, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
@@
 
-p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))
-
-p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())
-
-p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", data = lnRRQ10_data, g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())
+p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))
+
+p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())
+
+p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())
 
@@
 ################################################################
-  # Model 3.7: Environmental autocorrelation model by acute/acclim
+  # Model 3.4: Environmental autocorrelation model by acute/acclim
 ################################################################
@@
 # Bring in Climate data
-climate <- read.csv("./output/climate_data/temp_timeseries.csv")
+climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
 
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Longitude, Latitude)) %>% dplyr::select(-c(5:523))
+climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
 
@@
   } else{
-        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")
+        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")   ### DIFFERENT 
   #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
@@
   col <- c("#0871B9", "#F3B40D", "#1BB908")
-  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", data = lnVRQ10_data, angle = 45, trunk.size = 5) +
+  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 5) +
               scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 

### 2023-05-12 ms.qmd
Excluding missing data in acclimation response as its still tricky with orchard even though dropping data should have solved this problem

@@
 # Subset the data
-lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

### 2023-05-13 ms.qmd
Turns out metafor data slot retains missing data, so that needs fixing in orchaRd

@@
 ##################################################
-rerun = FALSE
+rerun = TRUE
 if(rerun){
@@
 ###########################################################
-rerun = FALSE
+rerun = TRUE
 if(rerun){
@@
 #################################################
-  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
@@
 # Subset the data
-lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
+lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
@@
 # Subset the data
-lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & source == "w") %>% 
+lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
                               mutate(spp = species_full, 
@@
 ####################################################
-rerun = FALSE
+rerun = TRUE
 if(rerun){
@@
 #############################
-rerun = FALSE
+rerun = TRUE
 if(rerun){

### 2023-05-13 R/2_climate_data.R
Updated script from Alex

@@ -3,57 +3,37 @@ rm(list=ls())
 library(tidyr)
 library(ecmwfr)
 library(terra)
-#library(ncdf4)
 library(maps)
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # SURVEY LOCATIONS
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-geo_data = read.csv("Data/Species_LatLong_plusHabitat.csv")  # ./data/climate_data/Species_LatLong_plusHabitat.csv
+
+geo_data = read.csv("./data/climate_data/Species_LatLong_plusHabitat.csv") 
 # Remove missing lat and long
 geo_data = geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
-
+# Remove records for captive individuals
+geo_data = geo_data[geo_data$source=="w",]
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # SETUP API
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 
-### SET KEYRING USER DETAILS TO CONNECT TO CLIMATE DATA STORE ACCOUNT
-### Note: this is my personal CDS account so if you have your own
-### its possible to change the details, but mine should work for you too.
-wf_set_key(user="89307", key="e661d59a-c4f0-4e9e-9da4-476fa0a9536e", service='cds')
-#wf_user_info("89307")
-
-# This page had a really helpful instructions. In particular, you can copy and
-# paste the API code from the CDS website, and then use an RStudio plugin to 
-# convert the text to an R-relevant command!
-#   https://cran.r-project.org/web/packages/ecmwfr/vignettes/cds_vignette.html
+### Set keyring and user details to connect to the Climate Data Store account.
+### Note: the details below are illustrative and will not work. You need to 
+### register for CDS account and enter your own details.
+wf_set_key(user    = "89303", 
+           key     = "e661d57a-c4f0-4e9e-9da4-477fa0a9537e", 
+           service = 'cds')
 
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # HISTORIC CLIMATIC DATA
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 
[…]

### 2023-05-14 ms.qmd
Fixed orchard plot - removed ata argument. Models mostly all rerun

--- 2023-05-12 ms.qmd
@@
 
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) +
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
 theme_classic() + 

### 2023-05-14 ms.qmd
re-rendered MS with updated climate results

@@
  col <- c("#0871B9", "#F3B40D", "#1BB908")
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) +
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
 theme_classic() + 
@@
  col <- c("#0871B9", "#F3B40D", "#1BB908")
-p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat", data = lnCVRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) +
+p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
 theme_classic() + 
@@
 
-p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnCVRQ10_data_wild_acclim, ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) +
+p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
 theme_classic() + 
@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(long.x, lat.y) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(Longitude, Latitude) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
 
@@
 
-# Fitted by Lat/long
-  ggplot(data = data_w_pred, aes(y = Estimate, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = Estimate, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+# Fitted by Lat/long Longitude, Latitude
+  ggplot(data = data_w_pred, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
 
 # Observed by Lat/long
-  ggplot(data = data_w_pred, aes(y = effect_size, x = lat.y)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = effect_size, x = long.x)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
+  ggplot(data = data_w_pred, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
 
@@
 
-  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, lat.y, long.x)
+  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
   new_data_t <- data.frame(
@@
 #############################
-  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, lat.y, long.x)
+  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
 
@@
 #############################
-  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, lat.y, long.x)
+  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
 
@@
     data = all_pred  %>% filter(type == "acclim"),
-    aes(long.x, lat.y, color = Estimate),
+    aes(Longitude, Latitude, color = Estimate),
     alpha = 0.7, size = 5
@@
 #################################################
-  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
+  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

### 2023-05-14 ms.qmd
Fixed degree symbol

@@
 The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$\deg$C.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C.
 In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(f_cvr_mean)`).

### 2023-05-15 ms.qmd
Need to add in populations

@@
 
-Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`).
+Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`, from XX populations).
 Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).

### 2023-05-17 ms.qmd
Fixes

--- 2023-05-14 ms.qmd
@@
 
+# Populations and species?
+pop_spp_w <- climate2[complete.cases(climate2),]
+
 # Subset the data
@@
 # Lets explore the model and how it's predciting the real data
-  data_w_pred <- cbind(lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),], predict(model5_bayes))
+  data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+
+# combine with predictions
+  data_w_pred <- cbind(data_w, predict(model5_bayes))
 
@@
 
-Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`).
+Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(pop_spp_w$Species))`, from `r dim(pop_spp_w)[1]` populations).
 Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).
@@
 #| include: false
-
+rerun = FALSE
 if(rerun){

### 2023-05-17 ms.qmd
Supress messages

@@
 #| label: fig-preds
+#| echo: false
+#| warning: false
+#| message: false
 #| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.

### 2023-05-22 ms.qmd
Code mostly together but I need to do some careful checks as a few things are not quite making sense

@@
 
-# sigma2_v = typical sampling error variance**NEW STEP**
+# sigma2_v = typical sampling error variance
 sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
@@
 
-# Now check that var fix from raw data and remove sampling variance. **NEW STEP**
+# Now check that var fix from raw data and remove sampling variance. 
   v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
@@
 
+Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showed an increase (@fig-future).
+Overall, there was a net decrease in the opportunity for selection across the globe ()
+
 ```{r}
@@
 
-devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
+#devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
 
@@
 
+```{r}
+#| label: future_clim
+#| echo: false
+#| warning: false
+
+# Now we want to take the predictions from `global` and use this for future climate sceneios.
+We have the future temperatures expected for each location.
+We can then use the predicted Q10 values to calculate the expected change in variance.
+We can then plot these globally.
+
+# First, lets get the current and future temperature data for 2081-2085. We'll use the mean. 
+  future_temp <- read.csv("./output/climate_data/gfdl2081-2085_air_and_SST_timeseries.csv")
+
+# Lets clean this data up. We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins
+  future_temp  <- future_temp  %>% 
+                  dplyr::select(Species, Latitude, Longitude, mean)  %>% 
+                  mutate(Celc_future = mean - 273.15,
+                          match = interaction(Species, Latitude, Longitude))
+
+# Current climate data
+  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+# Clean up and create a match column. We need to get the last 5 years current to average temp and then convert this to Celcius
+  climate2_future <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(match, Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(climate)))  %>% mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15) %>% dplyr::select(-grep("X2018|X2019|X2020|X2021|X2022", colnames(.)))
+
+# Now we can merge teh climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
+
+  climate_data <- left_join(climate2_future, future_temp, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
+
+# Lets look at future and current. Most, I would expect, should be above the line indicating higher future temperatures.
+  ggplot(data = climate_data, aes(x = Celc_curr, y = Celc_future)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Current Temperature (C)", y = "Future Temperature (C)") + theme_classic() + geom_abline(intercept = 0, slope = 1)
+
+# Lets have a global plot of temperature changes to see it sptially 
+  map2_temp_proj <- ggplot() +
+    geom_map(
+      data = world_map, map = world_map,
+      aes(long, lat, map_id = region),
+      color = "black", fill = "lightgray") +
+    expand_limits(x = world_map$long, y = world_map$lat) +
+    coord_map("moll") +
+    geom_point(
+      data = climate_data[complete.cases(climate_data$T_change),],
+      aes(Longitude, Latitude, color = T_change),
+      alpha = 0.7, size = 5
+    ) + labs(x = "Longitude", y = "Latitude", color = TeX("$\\Delta$ Temp.
+($^\\circ$C)"), title = "Current (2018-2022) vs Future (2080-2085)") + scale_colour_gradient2(trans = "reverse") + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+
+# Now lets merge all_pred with the climate projections
+  # Simplify columns 
+  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude, -Species)
+
+  # Mereg with model predcitions.
+This is the predcited lnCVRq10 for 10C change AT the specific latitude and longitude.
+We must assume that there is no plasticty or adaptation at each site to make projections
+  all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
+              left_join(., climate_data_new, by = "match")  %>% 
+              mutate(lnCVR_future = (Estimate / 10) * T_change,
+                      lnCVR_F_l95 = (Q2.5 / 10) * T_change,
+                      lnCVR_F_u95 = (Q97.5 / 10) * T_change, 
+                      per_change = (exp(lnCVR_future) - 1) * 100,
+                      per_change_l95 = (exp(lnCVR_F_l95) - 1) * 100,
+                      per_change_u95 = (exp(lnCVR_F_u95) - 1) * 100)
+
+# Need to take a step back
+  # 1. Why do we have NA in this data set? 
+  # 2. Why are l95 and u95 for marine not working
+  # 3. Apply to the posteriors, rather than summary.
+
+tables_future <- all_pred2 %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
+                                                                l95 = mean(per_change_l95, na.rm = TRUE), 
+                                                                u95 = mean(per_change_u95, na.rm = TRUE))
+
+```
+
+```{r}
+#| label: fig-future
+#| echo: false
+#| warning: false
+
+map2_future <- ggplot() +
+    geom_map(
+      data = world_map, map = world_map,
+      aes(long, lat, map_id = region),
+      color = "black", fill = "lightgray") +
+    expand_limits(x = world_map$long, y = world_map$lat) +
+    coord_map("moll") +
+    geom_point(
+      data = all_pred2[complete.cases(all_pred2$per_change),],
+      aes(Longitude, Latitude, color = per_change),
+      alpha = 0.7, size = 5
+    ) + labs(x = "Longitude", y = "Latitude", color = TeX("% $\\Delta$"), title = "Future (2080-2085)") + scale_colour_viridis() + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+```
 ## **Discussion**

### 2023-05-22 ms.qmd
Rerender. Fixed plottting of unecessary figure. Need to fix up word map

@@
 
-Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showed an increase (@fig-future).
+Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-preds D).
 Overall, there was a net decrease in the opportunity for selection across the globe ()
-
-```{r}
-#| label: fig-preds
-#| echo: false
-#| warning: false
-#| message: false
-#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
-Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
-
-#devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
-
-world_map = map_data("world") %>% 
-  filter(! long > 180)
-
-map1_current <- ggplot() +
-  geom_map(
-    data = world_map, map = world_map,
-    aes(long, lat, map_id = region),
-    color = "black", fill = "lightgray") +
-  expand_limits(x = world_map$long, y = world_map$lat) +
-  coord_map("moll") +
-  geom_point(
-    data = all_pred  %>% filter(type == "acclim"),
-    aes(Longitude, Latitude, color = Estimate),
-    alpha = 0.7, size = 5
-  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) + scale_color_viridis() + theme_map(base_size = 22)
-
-zoom_areas <- data.frame(
-     x = c(-130, -15, -60, 145),
-  xend = c( -50, 48, -35, 155),
-     y = c(  25, 34, 0, -45),
-  yend = c(  55,  69.8, -60, -10),
-  label = c("North America", "Europe", "South America", "Australia")
-)
-
-zoom_plots <- lapply(1:nrow(zoom_areas), function(i) {
-  map1_current +
-    geom_polygon(fill = "gray80", color = "black") +
-    coord_cartesian(xlim = c(zoom_areas[i, "x"], zoom_areas[i, "xend"]), 
-                    ylim = c(zoom_areas[i, "y"], zoom_areas[i, "yend"])) +
-                    theme(legend.position = "none")
-})
-
-# Make a multipanel plot. Make the world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
-
-p <- (zoom_plots[[1]] | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"), plot.margin = unit(c(0, 0, 0, 0), "cm"))
-
-ggsave(p, filename = "./output/figures/fig-preds.png", width = 9.1, height = 7.2)
-
-image_read("./output/figures/fig-preds.png")
-```
 
@@
 #| warning: false
+#| include: false
 
@@
 # Clean up and create a match column. We need to get the last 5 years current to average temp and then convert this to Celcius
-  climate2_future <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(match, Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(climate)))  %>% mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15) %>% dplyr::select(-grep("X2018|X2019|X2020|X2021|X2022", colnames(.)))
+  climate2_future <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% 
+                                dplyr::select(match, Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(climate)))  %>% 
+                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15) %>% 
+                                dplyr::select(-grep("X2018|X2019|X2020|X2021|X2022", colnames(.)))
 
@@
 # Lets have a global plot of temperature changes to see it sptially
+
+world_map = map_data("world") %>% 
+  filter(! long > 180)
+
   map2_temp_proj <- ggplot() +
@@
 ```{r}
-#| label: fig-future
+#| label: fig-preds
 #| echo: false
 #| warning: false
+#| message: false
+#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
+
+#devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
+
+world_map = map_data("world") %>% 
+  filter(! long > 180)
+
+map1_current <- ggplot() +
+  geom_map(
+    data = world_map, map = world_map,
+    aes(long, lat, map_id = region),
+    color = "black", fill = "lightgray") +
+  expand_limits(x = world_map$long, y = world_map$lat) +
+  coord_map("moll") +
+  geom_point(
+    data = all_pred  %>% filter(type == "acclim"),
+    aes(Longitude, Latitude, color = Estimate),
+    alpha = 0.7, size = 5
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"), title = "Current (2018-2022)") + scale_color_viridis() + theme_map(base_size = 22) +  theme(plot.title = element_text(hjust = 0.5))
+
+zoom_areas <- data.frame(
+     x = c(-130, -15, -60, 145),
+  xend = c( -50, 48, -35, 155),
+     y = c(  25, 34, 0, -45),
+  yend = c(  55,  69.8, -60, -10),
+  label = c("North America", "Europe", "South America", "Australia")
+)
+
+zoom_plots <- lapply(1:nrow(zoom_areas), function(i) {
+  map1_current +
+    geom_polygon(fill = "gray80", color = "black") +
+    coord_cartesian(xlim = c(zoom_areas[i, "x"], zoom_areas[i, "xend"]), 
+                    ylim = c(zoom_areas[i, "y"], zoom_areas[i, "yend"])) +
+                    theme(legend.position = "none",
+                        plot.title = element_blank())
+})
 
@@
     ) + labs(x = "Longitude", y = "Latitude", color = TeX("% $\\Delta$"), title = "Future (2080-2085)") + scale_colour_viridis() + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+
+# Make a multipanel plot. Make the world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
+
+p <- (((zoom_plots[[1]] | zoom_plots[[2]]) / map1_current) + map2_future) + plot_layout(heights  = c(1, 2, 2)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"), plot.margin = unit(c(0, 0, 0, 0), "cm"))
+
+ggsave(p, filename = "./output/figures/fig-preds.png", width = 9.1, height = 7.2)
+
+image_read("./output/figures/fig-preds.png")
 ```
+
 ## **Discussion**

### 2023-05-22 ms.qmd
Added some code to avoid summary of predcitions. This way I have the whole PD to work with in the global future climate predcitions

@@
 
+  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
   # Lets merge predictions with the original data
@@
 
+  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
   # Lets merge predictions with the original data
@@
 
+  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
   # Lets merge predictions with the original data
@@
   all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)
+  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% dplyr::select(-species_full)
   spp_wild  <- length(unique(sub_data$spp))

### 2023-05-22 ms.qmd
Fixed global predcitions figure. Added in new predcitions without posteriprs. NEed to figure out why exactly NA's still excist as they shouldn't

@@
 
-# Now we can merge teh climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
+# Now we can merge the climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
 
@@
   # Simplify columns 
-  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude, -Species)
+  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude)
 
@@
                       per_change_u95 = (exp(lnCVR_F_u95) - 1) * 100)
+
+  all_pred2_no_sum <-  all_pred_no_sum %>% mutate(match = interaction(spp, Latitude, Longitude))  %>% left_join(., climate_data_new, by = "match")
 
@@
 
-ggsave(p, filename = "./output/figures/fig-preds.png", width = 9.1, height = 7.2)
+ggsave(p, filename = "./output/figures/fig-preds.png", width = 7.8, height = 10.1)
 

### 2023-05-22 ms.qmd
Small changes

@@
 Note there are only 134 species because this is subset of the wild data.
-  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)
+  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)  %>% mutate(uniques = interaction(spp, Latitude, Longitude))
   all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% dplyr::select(-species_full)
@@
 ```
-
-Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(pop_spp_w$Species))`, from `r dim(pop_spp_w)[1]` populations).
-Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).
-Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-
-Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-preds D).
-Overall, there was a net decrease in the opportunity for selection across the globe ()
 
@@
 
+# Check on how many to decrease
+  all_pred2 %>% filter(type == "acclim") %>% mutate(d = if_else(per_change < 0, 1, 0 ))
+
 ```
+
+Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
+Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).
+Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
+
+Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-preds D).
+Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r `
 

### 2023-05-23 R/functions.R
Added new function for converting lncvr10 to lncvr1

@@ -444,3 +444,9 @@ post_summary <- function(x){
                     `l-95% CI` = l95,
                     `u-95% CI` = u95, check.names = FALSE, row.names = NULL))
 }
+
+#' @title lncvr_1c
+#' @description Converts a single estimate of lnCVR10 into a 1 degree Celsius estimate
+ lncvr_1c <-  function(x){
+        return(x/10)
+    }

### 2023-05-23 R/functions.R
Added a new kncvr_1c function and I also did teh calculations for future change in variance on the entire posterior distribution

@@ -449,4 +449,4 @@ post_summary <- function(x){
 #' @description Converts a single estimate of lnCVR10 into a 1 degree Celsius estimate
  lncvr_1c <-  function(x){
         return(x/10)
-    }
+  }

### 2023-05-23 ms.qmd
See previous comment message

@@
 
-```{r}
+```{r, future_clim}
 #| label: future_clim
@@
 
-  all_pred2_no_sum <-  all_pred_no_sum %>% mutate(match = interaction(spp, Latitude, Longitude))  %>% left_join(., climate_data_new, by = "match")
+  # Lets now use the whole posterior distribtion instead. This is a little hacky because the object is complicated
+
+  # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
+    cols_select <- colnames(all_pred2_no_sum) %in% c(1:3200)
+
+    all_pred2_no_sum <-  all_pred_no_sum %>% 
+                        mutate(match = interaction(spp, Latitude, Longitude))  %>% 
+                        left_join(., climate_data_new, by = "match")
+
+  # Second, lets convert each estimate to lncvr 1 degree C insteda of 10
+   all_pred2_no_sum2 <- all_pred2_no_sum %>%  
+                        mutate_if(cols_select, lncvr_1c)
+
+  # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
+    all_pred2_no_sum2[,cols_select]  <- all_pred2_no_sum2[,cols_select] * all_pred2_no_sum2$T_change
 
 # Need to take a step back
-  # 1. Why do we have NA in this data set? 
-  # 2. Why are l95 and u95 for marine not working
-  # 3. Apply to the posteriors, rather than summary.
+  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
+  # 2. Why are l95 and u95 for marine not working...no idea
+  # 3. Apply to the posteriors, rather than summary. Working on this....
 
@@
 Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
-Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds).
+Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6).
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
 
-Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-preds D).
+Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D).
 Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r `
 
-```{r}
-#| label: fig-preds
+```{r, fig-fig6}
+#| label: fig-fig6
 #| echo: false

### 2023-05-23 ms.qmd
95% CI and mean for mean overall percentage changes

@@
 
+  # Fourth, we can calculate the percentage change on the posterior
+    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,cols_select]) - 1)*100
+
+  # Now we can summarise each.
+Here, what we are doing is taking the mean for each column.
+Effectively pooling across all the iterations for each dataset.
+This gives us an estimation of the mean change in variance across all locations/species., but it gives us 3200 point estimates of this mean.
+We can then use this to calculate the 95% CI's.
+    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 2, mean, na.rm = TRUE)
+    mean(mean_perc)
+    quantile(mean_perc, 0.025)
+    quantile(mean_perc, 0.975)
+    hist(mean_perc)
+
+  # We can summarise this across the habitat types
+    all_pred2_no_sum2  %>% group_by(habitat) %>% summarise(mean = mean(est_per, na.rm = TRUE), 
+                                                            l95 = mean(est_perl95, na.rm = TRUE), 
+                                                            u95 = mean(est_peru95, na.rm = TRUE))
+
 # Need to take a step back
@@
 # Check on how many to decrease
-  all_pred2 %>% filter(type == "acclim") %>% mutate(d = if_else(per_change < 0, 1, 0 ))
+  decreases <- all_pred2 %>% group_by(match)  %>% summarise(n = if_else(any(per_change < 0), 1, 0))
 
@@
 Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
-Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6).
+Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6 A-C).
+Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D).
+Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-
-Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D).
-Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r `
 

### 2023-05-23 ms.qmd
Getting summaries f the posterior distrvution. Probably good to turn into a function or two

@@
 
+  # Now, lets do this but for each habitat, the good old fashioned way
+  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 2, mean, na.rm = TRUE))
+  lapply(mean_perc_habitat, mean)
+  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
+  #lapply(mean_perc_habitat, hist)
+
   # We can summarise this across the habitat types

### 2023-05-23 ms.qmd
Note

--- 2023-05-23 ms.qmd
@@
 
+  # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
+  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 2, mean, na.rm = TRUE))
+  lapply(mean_perc_habitat, mean)
+  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
+  #lapply(mean_perc_habitat, hist)
+
   # We can summarise this across the habitat types

### 2023-05-25 ms.qmd
Delete some code

@@
 
-  # We can summarise this across the habitat types
-    all_pred2_no_sum2  %>% group_by(habitat) %>% summarise(mean = mean(est_per, na.rm = TRUE), 
-                                                            l95 = mean(est_perl95, na.rm = TRUE), 
-                                                            u95 = mean(est_peru95, na.rm = TRUE))
-
 # Need to take a step back
   # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
-  # 2. Why are l95 and u95 for marine not working...no idea
-  # 3. Apply to the posteriors, rather than summary. Working on this....
+  # 2. Why are l95 and u95 for marine not working...Fixed
+  # 3. Apply to the posteriors, rather than summary. Done
 

### 2023-06-04 ms.qmd
Updated the code to reflect Alex's new climate model projections. Temps needed to be re-summarised based on new 5 year interval as this models goes to 2100

@@
 
-Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+Monthly average temperature data were extracted from the CanESM2 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
 For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface air temperature at 2 meters (0.01 resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25 resolution) using the *ncdf4* R package [vers.
@@
 # First, lets get the current and future temperature data for 2081-2085. We'll use the mean. 
-  future_temp <- read.csv("./output/climate_data/gfdl2081-2085_air_and_SST_timeseries.csv")
-
-# Lets clean this data up. We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins
-  future_temp  <- future_temp  %>% 
-                  dplyr::select(Species, Latitude, Longitude, mean)  %>% 
-                  mutate(Celc_future = mean - 273.15,
-                          match = interaction(Species, Latitude, Longitude))
-
-# Current climate data
-  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
-
-# Clean up and create a match column. We need to get the last 5 years current to average temp and then convert this to Celcius
-  climate2_future <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% 
-                                dplyr::select(match, Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(climate)))  %>% 
-                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15) %>% 
-                                dplyr::select(-grep("X2018|X2019|X2020|X2021|X2022", colnames(.)))
+  future_temp <- read.csv("./output/climate_data/CanESM2_air_and_SST_timeseries.csv")
+
+# Now, lets summarise the mean for the current temps (i.e., 2018-2022)
+current_temps <-   future_temp  %>% 
+                   dplyr::select(Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(future_temp)))  %>% 
+                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15, match = interaction(Species, Latitude, Longitude))
+
+# Lets clean this data up.
+We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins.
+We'll now take the last 5 years of the future temperature 2096-2100
+  future_temps  <- future_temp  %>% 
+                  dplyr::select(Species, Latitude, Longitude,  grep("X2096|X2097|X2098|X2099|X2100", colnames(future_temp)))  %>% 
+                  mutate(mean = apply(.[, grep("X2096|X2097|X2098|X2099|X2100", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_future = mean - 273.15,  match = interaction(Species, Latitude, Longitude))
 
@@
 
-  climate_data <- left_join(climate2_future, future_temp, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
+  climate_data <- left_join(current_temps, future_temps, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
 
@@
     ) + labs(x = "Longitude", y = "Latitude", color = TeX("$\\Delta$ Temp.
-($^\\circ$C)"), title = "Current (2018-2022) vs Future (2080-2085)") + scale_colour_gradient2(trans = "reverse") + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+($^\\circ$C)"), title = "Current (2018-2022) vs Future (2096-2100)") + scale_colour_gradient2(trans = "reverse") + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
 

### 2023-06-05 ms.qmd
Fixed an error in calculations. It was applying mean across columns, not rows! Now the values make more sense. Figured something was up.

@@
 
-# Bring in Climate data
+# Bring in  historial climate data
 climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
@@
 
-  # Mereg with model predcitions.
+  # Merge with model predcitions.
 This is the predcited lnCVRq10 for 10C change AT the specific latitude and longitude.
@@
 
+######## *** THE CODE BELOW NEEDS SOME NEW CHECKING AS ABOVE WAS MODIFIED! ****
+
   # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
-    cols_select <- colnames(all_pred2_no_sum) %in% c(1:3200)
 
@@
 
-  # Second, lets convert each estimate to lncvr 1 degree C insteda of 10
+  # Second, lets convert each estimate to lncvr 1 degree C instead of 10...
    all_pred2_no_sum2 <- all_pred2_no_sum %>%  
-                        mutate_if(cols_select, lncvr_1c)
+                        mutate_if(colnames(.) %in% c(1:3200), lncvr_1c)
 
   # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
-    all_pred2_no_sum2[,cols_select]  <- all_pred2_no_sum2[,cols_select] * all_pred2_no_sum2$T_change
+    all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]  <- all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)] * all_pred2_no_sum2$T_change
 
   # Fourth, we can calculate the percentage change on the posterior
-    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,cols_select]) - 1)*100
+    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]) - 1)*100
 
@@
 We can then use this to calculate the 95% CI's.
-    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 2, mean, na.rm = TRUE)
+    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) # Fixed an error here. It was applying the mean across columns, not rows!
     mean(mean_perc)
@@
   # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
-  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 2, mean, na.rm = TRUE))
+  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE))
   lapply(mean_perc_habitat, mean)

### 2023-06-06 ms.qmd
Added in details on future climate reductions in variance

@@
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
+Across habitat types climate change is predicted to result in a only a `r lapply(mean_perc_habitat, mean)$f`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%) under a RCP8.5 climate scenerio.
 

### 2023-06-07 ms.qmd
fixed pmcmc and also fig6

--- 2023-06-05 ms.qmd
@@
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
+Across habitat types climate change is predicted to result in a only a `r lapply(mean_perc_habitat, mean)$f`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$t)`) under a RCP8.5 climate scenerio.
 
@@
       alpha = 0.7, size = 5
-    ) + labs(x = "Longitude", y = "Latitude", color = TeX("% $\\Delta$"), title = "Future (2080-2085)") + scale_colour_viridis() + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+    ) + labs(x = "Longitude", y = "Latitude", color = TeX("% $\\Delta$"), title = "Future (2096-2100)") + scale_colour_viridis() + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
 

### 2023-06-07 R/2_climate_data.R
Updated code from Alex, but also need to fix paths because he's not working from repo

@@ -3,17 +3,16 @@ rm(list=ls())
 library(tidyr)
 library(ecmwfr)
 library(terra)
+library(ncdf4)
 library(maps)
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # SURVEY LOCATIONS
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-
-geo_data = read.csv("./data/climate_data/Species_LatLong_plusHabitat.csv") 
+geo_data = read.csv("Data/Species_LatLong_plusHabitat.csv")  # ./data/climate_data/Species_LatLong_plusHabitat.csv
 # Remove missing lat and long
 geo_data = geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
-# Remove records for captive individuals
-geo_data = geo_data[geo_data$source=="w",]
+
 
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # SETUP API
@@ -26,14 +25,13 @@ wf_set_key(user    = "89303",
            key     = "e661d57a-c4f0-4e9e-9da4-477fa0a9537e", 
            service = 'cds')
 
-
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 # HISTORIC CLIMATIC DATA
 # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
 
 for(i in 1:nrow(geo_data) ){
   
-  filelist = unlist(lapply(list.files("./data/climate_data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
+  filelist = unlist(lapply(list.files("./Data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
   filelist = as.numeric(gsub("\\.nc","",filelist))
   
   if( !i %in% filelist ){
@@ -90,7 +88,7 @@ for(i in 1:nrow(geo_data) ){
       user     = "89303",
       request  = request,   
       transfer = TRUE,  
-      path     = "./data/climate_data/ERA5_LAND",
+      path     = "./Data/ERA5_LAND",
       verbose  = FALSE
     )
     
@@ -102,11 +100,6 @@ for(i in 1:nrow(geo_data) ){
[…]

### 2023-06-07 ms.qmd
Fixed p-value

@@
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Across habitat types climate change is predicted to result in a only a `r lapply(mean_perc_habitat, mean)$f`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$t)`) under a RCP8.5 climate scenerio.
+Across habitat types climate change is predicted to result in a only a `r lapply(mean_perc_habitat, mean)$f`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
 

### 2023-06-07 ms.qmd
Fixed p-value notation

@@
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
-While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
+While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
 As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
@@
 While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
-Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
 The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(f_cvr_mean)`).
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C.
+In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
 
@@
 Thermal variability (i.e., $CV$) explained variation in acclimation capacity among terrestrial ectotherms, but not for marine or freshwater populations (@fig-4).
-Terrestrial ectotherm populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
+Terrestrial ectotherm populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
 In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-4).

### 2023-06-08 ms.qmd
Updated climate methods

@@
 
-Monthly average temperature data were extracted from the CanESM2 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
 For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface air temperature at 2 meters (0.01 resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25 resolution) using the *ncdf4* R package [vers.
@@
 Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticity evolution.
+
+We also extracted climate projections into the future to understand the effects of climate warming will have on opportunity for selection.
+We used the CanESM2 climate model (2096-2100) under a high emissions scenerio (RCP8.5).
 

### 2023-06-10 ms.qmd
Small update
Re-render

@@
 ##################################
-    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance, ggthemes)
+    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance, ggthemes, mapproj)
 
@@
 We also extracted climate projections into the future to understand the effects of climate warming will have on opportunity for selection.
-We used the CanESM2 climate model (2096-2100) under a high emissions scenerio (RCP8.5).
+We used the CanESM2 climate model (2005-2100) under a high emissions scenerio (RCP8.5).
 

### 2023-12-01 ms.qmd
Notes to prep intro

@@
 
+1. Phenotypic plasticity and evolutionary adatation to novel environments
+2. Capacity for plasticity and adaptation differ between aqautic and terrestrial ectotherms
+3. Climate change is expected to impact on the capacity for plasticity and adaptation
+4. We test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
+
 Variable thermal environments are expected to result in strong selection pressures that lead to adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi].

### 2023-12-04 ms.qmd
Writing intro

@@
 
-Variable thermal environments are expected to result in strong selection pressures that lead to adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi].
+Climate change is expected to result in warmer and more variable thermal environments for many organisms globally [@Suarez2023].
+Greater thermal variability is expected to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi].
+Nonetheless, the extent to which plasticity versus genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established.
+Without adaptive genetic or plastic responses high rates of extinction are predicted [@Cahill2012].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable.
@@
 
-Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise, by applying new effect sizes that capture changes in physiological trait variance, and 3) test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
+Reversibly plastic responses, such as acclimitisation, are expected to provide organisms with resilience to climate change by allowing them to adjust their physiology to match the thermal environment they are exposed to [@Seebacher2015-wi].
+
+Here, we apply new effect sizes to: 1) re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise and 3) test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
 

### 2023-12-04 ms.qmd
Update intro

@@
 
+<!-- 
 1. Phenotypic plasticity and evolutionary adatation to novel environments
@@
 4. We test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
-
-Climate change is expected to result in warmer and more variable thermal environments for many organisms globally [@Suarez2023].
-Greater thermal variability is expected to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi].
-Nonetheless, the extent to which plasticity versus genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established.
-Without adaptive genetic or plastic responses high rates of extinction are predicted [@Cahill2012].
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable.
+-->
+
+Climate change is expected to result in warmer and more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
+Greater thermal variability is expected to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014].
+Nonetheless, the extent to which adaptive plasticity versus genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
+Without adaptive genetic or plastic responses high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Chevin2017].
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable [@Chevin2017].
 Despite this theoretical expectation, empirical support for this prediction is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity).
@@
 
-Reversibly plastic responses, such as acclimitisation, are expected to provide organisms with resilience to climate change by allowing them to adjust their physiology to match the thermal environment they are exposed to [@Seebacher2015-wi].
+Studies investigating reversibly plastic responses, such as acclimitisation, have primarily been focused on mean physiological responses, paying little attention to changes in physiological variability under more extreme thermal conditions [@Seebacher2015-wi; @Havird2020-mj].
+Understanding how variability in physiological rates is affected by climate change has important implications for understanding a populations capacity for physiological traits to evolve because lack of physiological variation is expected to limit responses to selection (i.e., the opportunity for selection) [@Sanderson2023].
+Change is physiological variability can also inform on the extent to which populations are able to buffer against environmental change [@Sanderson2023].
+For example, if populations are able to buffer against environmental change by increasing physiological variability, this may be a mechanism that allows populations to persist in the face of climate change.
 

### 2023-12-04 ms.qmd
Updated intro

--- 2023-12-01 ms.qmd
@@
 
+<!-- 
   1. Phenotypic plasticity and evolutionary adatation to novel environments
@@
   4. We test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
-
-Variable thermal environments are expected to result in strong selection pressures that lead to adaptation or the evolution of phenotypic plasticity -- both of which are considered critical for population resilience to human-induced climate change [@Seebacher2015-wi].
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable.
-Despite this theoretical expectation, empirical support for this prediction is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity).
+-->
+
+Climate change is expected to result in warmer and more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
+Greater thermal variability in the past is expected to have resulted in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
+The extent to which adaptive plasticity and genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
+Without such responses high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
+Phenotypic plasticity is expected to the the 'first line of defence' against changing climates by buyding time for genetic adaptation to take place (i.e., the 'plasticty first hypothesis' - ).
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016].
+Despite this theoretical expectation, empirical support is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity).
 Reversible forms of phenotypic plasticity, such as acclimatization, may not be expected to adhere to such predictions.
+
+Arguably, reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are likely to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Scheiner2020].
+Such responses are driven by changes in underlying physiology that can respond rapidly to the environment.
+However, studies have primarily been focused on mean physiological responses, paying little attention to changes in physiological variability [@Seebacher2015-wi; @Havird2020-mj].
+For example, most work has focused on the degree to which mean thermal tolerances or acclimation abilities are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022], neglecting how intrapopulation variability might also be impacted.
+Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
+Change in physiological variability can also inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010].
+Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance depedning on the trait [@Scheiner2020].
+Changes in phenotypic variability can also result in 'phenotypic drift' that may result in the loss of important variation relevant for adaptation.
 
@@
 Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.
-In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems.
-
-Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise, by applying new effect sizes that capture changes in physiological trait variance, and 3) test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
+In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits is expected to be a stronger constraint on physiological processes in terrestrial ectotherms.
+
+Here, we use meta-analysis and new effect sizes to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
+We then expand these effect sizes to allow for comparisons of variance in physiological rates to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?; 2) Are temperture effects on plastic adjustments in physiolgical rates larger than changes in variance across aquatic and terrestrial ectotherms?; 3) Are changes in plasticity or variance in physiological rates impacted by a population's past climate history?
+and 4) How are means and variances in physiological rates expected to change under climate change?
 

### 2023-12-04 ms.qmd
Updated MS

@@
 Climate change is expected to result in warmer and more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability in the past is expected to have resulted in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
+Greater thermal variability in the past is expected to have resulted in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
 The extent to which adaptive plasticity and genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
-Without such responses high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to the the 'first line of defence' against changing climates by buyding time for genetic adaptation to take place (i.e., the 'plasticty first hypothesis' - ).
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016].
+Without such responses, high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
+Phenotypic plasticity is expected to the the 'first line of defence' against changing climates by buying time for genetic adaptation to take place (i.e., the 'plasticty first hypothesis' - ).
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016].
 Despite this theoretical expectation, empirical support is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity).
@@
 Change in physiological variability can also inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010].
-Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance depedning on the trait [@Scheiner2020].
-Changes in phenotypic variability can also result in 'phenotypic drift' that may result in the loss of important variation relevant for adaptation.
+Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance depending on the trait [@Scheiner2020].
+The implications of changes in variance could therefore have wide-reaching implications for understanding the capacity for populations to adapt to novel environments [@Scheiner2020].
 
@@
 Here, we use meta-analysis and new effect sizes to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We then expand these effect sizes to allow for comparisons of variance in physiological rates to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?; 2) Are temperture effects on plastic adjustments in physiolgical rates larger than changes in variance across aquatic and terrestrial ectotherms?; 3) Are changes in plasticity or variance in physiological rates impacted by a population's past climate history?
+We then expand these effect sizes to allow for comparisons of variance in physiological rates to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
+2) Are temperture effects on plastic adjustments in physiolgical rates larger than changes in variance across aquatic and terrestrial ectotherms?
+3) Are changes in plasticity or variance in physiological rates impacted by a population's past climate history?
 and 4) How are means and variances in physiological rates expected to change under climate change?

### 2023-12-04 ms.qmd
Added new refs

@@
 #### Affliations:
-$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
-$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
-$^3$ SOLES, University of Sydney, Sydney, NSW, Australia
+$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia \n
+$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia \n
+$^3$ SOLES, University of Sydney, Sydney, NSW, Australia \n
 $^4$ Department of Biology, Lancaster University, Liverpool, UK
@@
 Without such responses, high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to the the 'first line of defence' against changing climates by buying time for genetic adaptation to take place (i.e., the 'plasticty first hypothesis' - ).
+Phenotypic plasticity is expected to the the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003, see also @Lande2009].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016].

### 2023-12-04 ms.qmd
update to me spelling errors

--- 2023-12-04 ms.qmd
@@
 #### Affliations:
-$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
-$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
-$^3$ SOLES, University of Sydney, Sydney, NSW, Australia
+$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia <br />
+$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia <br />
+$^3$ SOLES, University of Sydney, Sydney, NSW, Australia <br />
 $^4$ Department of Biology, Lancaster University, Liverpool, UK
@@
 Without such responses, high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to the the 'first line of defence' against changing climates by buying time for genetic adaptation to take place (i.e., the 'plasticty first hypothesis' - ).
+Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003, see also @Lande2009].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016].
@@
 Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the resulting of sampling varianbility, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary and species specific ecoloogy explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
 
@@
 
-The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms.
+The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
 Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
+In contrast, freshwater ectotherms exhibited a much smaller reduction in physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
 
@@
 Terrestrial ectotherm populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
-In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-4).
+In contrast, thermal predictability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-4).
 
@@
 Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
+
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

### 2023-12-04 ms.qmd
Newline

@@
 #### Affliations:
-$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia <br />
-$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia <br />
-$^3$ SOLES, University of Sydney, Sydney, NSW, Australia <br />
+$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
+$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
+$^3$ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
 $^4$ Department of Biology, Lancaster University, Liverpool, UK

### 2023-12-05 ms.qmd
Updaed MS with some more writing

@@
 Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Change in physiological variability can also inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010].
+Higher physiological variability may imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zhang2023].
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance depending on the trait [@Scheiner2020].

### 2023-12-05 ms.qmd
Some more writing

--- 2023-12-04 ms.qmd
@@
 However, studies have primarily been focused on mean physiological responses, paying little attention to changes in physiological variability [@Seebacher2015-wi; @Havird2020-mj].
-For example, most work has focused on the degree to which mean thermal tolerances or acclimation abilities are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022], neglecting how intrapopulation variability might also be impacted.
+For example, most work has focused on the degree to which mean thermal tolerances or acclimation abilities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022], neglecting how intrapopulation variability might also be impacted.
 Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Change in physiological variability can also inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010].
-Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance depending on the trait [@Scheiner2020].
+Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zhang2023].
+Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020].
 The implications of changes in variance could therefore have wide-reaching implications for understanding the capacity for populations to adapt to novel environments [@Scheiner2020].
@@
 Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.
-In addition, low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits is expected to be a stronger constraint on physiological processes in terrestrial ectotherms.
+Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits is expected to be a stronger constraint on physiological processes in terrestrial ectotherms.
+Given that terrestrial ectotherms are expected to be closer to their thermal limits increases in temperature may have a stronger impact on variation in physiological rates within populations compared to aqautic ectotherms.
+Reduced variability may result from variances being eroded by strong selection, an inability to adjust physiological rates, or a combination of both.
 

### 2023-12-06 ms.qmd
Fixed a few ref problems

@@
 Without such responses, high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003, see also @Lande2009].
+Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003; see also @Lande2009].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016].
@@
 
-Arguably, reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are likely to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Scheiner2020].
+Reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Scheiner2020].
 Such responses are driven by changes in underlying physiology that can respond rapidly to the environment.
@@
 Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zhang2023].
+Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zheng2023].
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020].

### 2023-12-07 ms.qmd
Fleshing out the discussion a bit

@@
 
+Understanding how the opportunity for selection will change and the capcity of populations to acclimate with climate change is critical for predicting how populations will respond to future environmental change.
+Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change.
+This is because the acute and acclimation responses of wild ectotherms are expected to be lower in warmer environments.
+
+### **Acute and acclimation responses of wild ectotherms are lower in warmer environments**
 One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats .
@@
 However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
+
+### **The opportunity for selection is expected to decrease for wild ectotherms under climate change**
+
+### **Limitations and future directions**
 

### 2023-12-08 ms.qmd
Discussion

@@
 
-Understanding how the opportunity for selection will change and the capcity of populations to acclimate with climate change is critical for predicting how populations will respond to future environmental change.
+Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change.
 Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change.

### 2023-12-10 ms.qmd
Clarity on writing

@@
 Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change.
-Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change.
-This is because the acute and acclimation responses of wild ectotherms are expected to be lower in warmer environments.
+Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change, but particularly so for terrestrial ectotherms.
+Decreases in variance are larger than the expected benefits from acclimation.
 

### 2023-12-10 ms.qmd
summary

--- 2023-12-08 ms.qmd
@@
 
-Reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Scheiner2020].
+Reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Scheiner2020; @Dewitt1998].
 Such responses are driven by changes in underlying physiology that can respond rapidly to the environment.
@@
 
-Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change.
-Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change.
-This is because the acute and acclimation responses of wild ectotherms are expected to be lower in warmer environments.
+Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change [@Chevin2017; @Chevin2010].
+Here, we show that the opportunity for selection is expected to decrease for wild ectotherms, but particularly so for terrestrial ectotherms (~28%).
+Decreases in variance in physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (marine: 9% acclimation vs.
+15% reduction in variance; terrestrial: no acclimation vs 28% reduction in variance).
+Such effects are expected to result in a decrease in the opportunity for selection for marine and terrestrial ectotherms under climate change (between 4-13% reduction in total variance).
 

### 2023-12-11 ms.qmd
Updated MS

@@
 Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003; see also @Lande2009].
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016].
-Despite this theoretical expectation, empirical support is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity).
-Reversible forms of phenotypic plasticity, such as acclimatization, may not be expected to adhere to such predictions.
-
-Reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Scheiner2020; @Dewitt1998].
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998].
+Despite this theoretical expectation, empirical support is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
+
+Reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Dewitt1998; @Scheiner2020].
 Such responses are driven by changes in underlying physiology that can respond rapidly to the environment.
@@
 Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zheng2023].
-Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020].
+Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zheng2023; @Slatyer2013].
+Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
 The implications of changes in variance could therefore have wide-reaching implications for understanding the capacity for populations to adapt to novel environments [@Scheiner2020].
@@
 Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.
-Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits is expected to be a stronger constraint on physiological processes in terrestrial ectotherms.
+Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
 Given that terrestrial ectotherms are expected to be closer to their thermal limits increases in temperature may have a stronger impact on variation in physiological rates within populations compared to aqautic ectotherms.
@@
 While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
-Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-3) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
 
-### *Climate variability predicts acclimation capacity for terrestrial ectotherms*
-
-Thermal variability (i.e., $CV$) explained variation in acclimation capacity among terrestrial ectotherms, but not for marine or freshwater populations (@fig-4).
-Terrestrial ectotherm populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%).
-In contrast, thermal predictability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-4).
-
-In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability across any of the habitats (@fig-5).
+### *Past climate variability does not influence acclimation capacity or expected change in variance*
+
+Thermal variability (i.e., $CV$) and predictability a population experienced in its past did not explain acclimation capacity or changes in opportunity for selection (i.e., the change in physiological variability) among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
 
@@
 
-Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change [@Chevin2017; @Chevin2010].
+Understanding acclimation capacity and how the opportunity for selection will change across populations and species is important for predicting the impacts of climate change [@Chevin2017; @Chevin2010].
 Here, we show that the opportunity for selection is expected to decrease for wild ectotherms, but particularly so for terrestrial ectotherms (~28%).
@@
 15% reduction in variance; terrestrial: no acclimation vs 28% reduction in variance).
-Such effects are expected to result in a decrease in the opportunity for selection for marine and terrestrial ectotherms under climate change (between 4-13% reduction in total variance).
+Such effects are expected to result in a decrease in the opportunity for selection for marine and terrestrial ectotherms (between 4-13% reduction in total variance) under climate change assuming a fraction of this variation is heritable and/or it weakens selection.
 

### 2023-12-11 ms.qmd
more writing

@@
 Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003; see also @Lande2009].
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998].
-Despite this theoretical expectation, empirical support is scant [], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
 
@@
 
-Here, we use meta-analysis and new effect sizes to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
+Here, we use new effect sizes and meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
 We then expand these effect sizes to allow for comparisons of variance in physiological rates to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
@@
 
-### *Past climate variability does not influence acclimation capacity or expected change in variance*
+### *Past climate does not influence acclimation capacity or expected change in variance*
 
@@
 Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Across habitat types climate change is predicted to result in a only a `r lapply(mean_perc_habitat, mean)$f`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
+Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
 
@@
 Such effects are expected to result in a decrease in the opportunity for selection for marine and terrestrial ectotherms (between 4-13% reduction in total variance) under climate change assuming a fraction of this variation is heritable and/or it weakens selection.
+
+### **Acclimation capacity is limited in ectotherms**
 

### 2023-12-11 ms.qmd
Adding trait and life-history models for lnCVR

@@
 
+###################################################
+  # Model 2.3: Model controlling for acclimation time, 
+  # type and trait category assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
+  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
+
+  } else{
+        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
+  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
+}
+
+###################################################
+  # Model 2.4: Model controlling for acclimation time, 
+  # type and life history stage assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model
+  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
+  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
+
+  } else{
+        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
+  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
+}
+
 ```
@@
 
-### **Acclimation capacity is limited in ectotherms**
+### **Acclimation capacity and opportunity for selection is limited in response to climate change**
+One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats.
+However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
+Faster rates of acclimation would therefore result in the opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
+
+### **No signature of past climate on capacity for acclimation or opportunity for selection**
+
+### ***Ecological consequences of reduced variation in physiological Rates***
+- need analysis of traits for lnCVR.
 
 ### **Acute and acclimation responses of wild ectotherms are lower in warmer environments**
-One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats .
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
-However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
 

### 2023-12-11 ms.qmd
some more writing

@@
 Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Schindler2010; @Zheng2023; @Slatyer2013].
+Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Bolnick2011 and @Schindler2010; @Zheng2023; @Slatyer2013].
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
-The implications of changes in variance could therefore have wide-reaching implications for understanding the capacity for populations to adapt to novel environments [@Scheiner2020].
+Such changes in physiological trait variation can may also have important ecological consequences by promotong population productivity and stability [@Agashe2009], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011].
+The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to adapt to novel environments [@Scheiner2020].
 
@@
 
+Traits did not differ in whether they exhibited a reduction in variation in physiological rates at high temperatures.
+Each life-history stage also exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
+
+```{r, fig-cvrlh}
+#| label: fig-cvrlh
+#| fig-cap: "Predicted mean $lnCVR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms."
+#| echo: false
+#| warning: false
+
+p1 <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))
+
+p2 <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())
+
+p3 <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())
+
+fig4 <- (p1 | p2 | p3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig4, filename = "./output/figures/fig4_lh.png", width = 14, height = 4.5)
+
+fig4 <- magick::image_read("./output/figures/fig4_lh.png")
+fig4
+```
+
 ```{r, wildlnRR10}
@@
 
-Understanding acclimation capacity and how the opportunity for selection will change across populations and species is important for predicting the impacts of climate change [@Chevin2017; @Chevin2010].
-Here, we show that the opportunity for selection is expected to decrease for wild ectotherms, but particularly so for terrestrial ectotherms (~28%).
+Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the impacts ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
+Here we show that the opportunity for selection is expected to decrease for ectotherms, but particularly so for terrestrial ectotherms (~28%).
 Decreases in variance in physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (marine: 9% acclimation vs.
 15% reduction in variance; terrestrial: no acclimation vs 28% reduction in variance).
-Such effects are expected to result in a decrease in the opportunity for selection for marine and terrestrial ectotherms (between 4-13% reduction in total variance) under climate change assuming a fraction of this variation is heritable and/or it weakens selection.
+Such effects are expected to result in a decrease in the variability in physiologcial rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
 
@@
 Faster rates of acclimation would therefore result in the opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
+assuming a fraction of this variation is heritable and/or it weakens selection
 
@@
 
+Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability, particularly if oscillations are predictable over time [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016].
+Empirical evidence properly testing these predictions, however, is scant.
+@Leung2020 recently showed that greater plasticty in morphological traits did evolve in experimental algae populations, however, work in seed beetles.
+Our results suggest that such theretical explanations may not be general but rather specific to the population, context and trait in question.
+
 ### ***Ecological consequences of reduced variation in physiological Rates***
-- need analysis of traits for lnCVR.
+The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remains unclear.
+The dearth of empirical data demonstrating changes in variance paired with a lack of theoretical models
+- buckley 2014, - Lawton 1991, - Nisbet
 

### 2023-12-11 ms.qmd
Cool ref and some more notes for writing

@@
 - buckley 2014, - Lawton 1991, - Nisbet 
+especailly see @kooijman1989population given that they "introduce some small spread" and it results in oscillatinos dapeming..
 

### 2023-12-11 ms.qmd
updates

@@
 @Leung2020 recently showed that greater plasticty in morphological traits did evolve in experimental algae populations, however, work in seed beetles.
-Our results suggest that such theretical explanations may not be general but rather specific to the population, context and trait in question.
+Our results suggest that such theoretical explanations may not be general but rather specific to the population, context and trait in question; a point emphaised by others.
 
 ### ***Ecological consequences of reduced variation in physiological Rates***
+Variance in physiological rates decreases substantially at high temperatures with effects being especially pronouced in terrestrial ecosystems.
 The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remains unclear.

### 2023-12-12 ms.qmd
Updated MS

--- 2023-12-11 ms.qmd
@@
 Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Bolnick2011 and @Schindler2010; @Zheng2023; @Slatyer2013].
+Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
-Such changes in physiological trait variation can may also have important ecological consequences by promotong population productivity and stability [@Agashe2009], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011].
-The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to adapt to novel environments [@Scheiner2020].
+Such changes in physiological trait variation may also have important ecological consequences by promotong population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011].
+The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to persist in and adapt to novel environments [@Scheiner2020].
 
@@
 In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
-While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2).
-Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-3) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
-
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
+
 Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the resulting of sampling varianbility, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
 Evolutionary relationships among taxa and species ecology explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+
+Different trait categories showed different accclimation responses across habitat types, however, they mirrored patterns seen overall (@fig-2).
+Acclimation capacity also did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-3) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
 
+  # We can also run subsets for each habitat
+   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
+       A_m_cvr <- vcv(tree_m_cvr, corr = FALSE)
+   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
+       A_f_cvr <- vcv(tree_f_cvr, corr = FALSE)
+   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
+       A_t_cvr <- vcv(tree_t_cvr, corr = FALSE)
+
+  model2.3f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "f"))
+
+  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
+
+  model2.3m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "m"))
+  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
+
+  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
+  model2.3t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "t"))
+  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
+
   } else{
         model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
+        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
+        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
+        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
   model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
@@
 
-Traits did not differ in whether they exhibited a reduction in variation in physiological rates at high temperatures.
-Each life-history stage also exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
+The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between study and trait differences (See supplemental @fig-s3).
+Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
+While traits did differ in whether they exhibited a reduction in variation in physiological rates at high temperatures reduced variance was prominant for resting metabolic rates and sprint speed (@fig-cvrtrait).
 
@@
 fig4
+```
+
+```{r, fig-cvrtrait}
+#| label: fig-cvrtrait
+#| fig-cap: Acute and Acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems
+#| echo: false
+
+ptm <- orchard_plot(model2.3m, mod = "trait_category", group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() 
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf <- orchard_plot(model2.3f, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model2.3t, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate")) + theme_classic() + labs(legend = "Type")
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+figcvrtrait <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 8.5, width = 26)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figcvrtrait.png")
+img_figcvrtrait
 ```
@@
 
+# Look at the environment details across different habitats. Seems very similar. *** Check with ALEX ***
+  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(cv), mean(acf_all))
+
 # Check and prune tree
@@
 Such effects are expected to result in a decrease in the variability in physiologcial rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
+Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further attention.
 
@@
 
-Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability, particularly if oscillations are predictable over time [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016].
+Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key].
+Higher spatial heterogenetiy in terrestrial ectotherms suggests that plasticity should be more likely evolve, however, we did not find evidence to this effect; possibly because of the lower predictability of thermal environments over time making cues unreliable [@hendry2016key].
 Empirical evidence properly testing these predictions, however, is scant.
 @Leung2020 recently showed that greater plasticty in morphological traits did evolve in experimental algae populations, however, work in seed beetles.
-Our results suggest that such theretical explanations may not be general but rather specific to the population, context and trait in question.
+Our results suggest that such theoretical explanations may not be general but rather specific to the population, context and trait in question; a point emphaised by others.
 
 ### ***Ecological consequences of reduced variation in physiological Rates***
-The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remains unclear.
+Variance in physiological rates decreases substantially at high temperatures with effects being especially pronouced in terrestrial ecosystems and for key traits such as metabolism and performance.
+Changes in variability in physiological rates, particularly energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems that can have important consequences for population dynamics [@hendry2016key].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increasdd growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key].
+For examaple, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+They showed that greater between-individual variation in DEB parameters led to less extreme population occilations compared to scenerios with no variation [@kooijman1989population].
+The differences in variance change across major habitat types suggest that terrestrial ecotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extintion and reduced productivity – predictions already reinforced by a number of authorities .
+To date, however, an appreciation for the wide-reaching impacts changes in variance may have on populations and communities remains limited.
+Indeed, the ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remain unclear.
+Such insight will require the development of theoretical models that better integrate intrapopulation variation into mechanistic physiological models or ones that better capture stochasticity such as individual based models.
+
 The dearth of empirical data demonstrating changes in variance paired with a lack of theoretical models 
@@
 ### **Limitations and future directions**
+
+An enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may increase our ability to make more informed predcitions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
 
@@
 #| label: fig-s3
-#| fig-cap: I2 estimates
+#| fig-cap: "$I^2$ estimates. A) $lnRR_{Q_{10}}$ B) $lnCVR_{Q_{10}}$ and C) $lnVR_{Q_{10}}$." 
 #| fig-align: center

### 2023-12-13 ms.qmd
Updated MS. Intro roughly finished

@@
 ---
-title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
+title: "Reduced plasticity and variance in physiological rates for terrestrial ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
 
-<p style="text-align: center;">Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$</p>
+<p style="text-align: center;">Daniel W.A. Noble^1^, Fonti Kar^2^, Frank Seebacher^3^, Alex Bush^4^, & Shinichi Nakagawa^2^</p>
 
 #### Affliations:
-$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
-$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
-$^3$ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
-$^4$ Department of Biology, Lancaster University, Liverpool, UK
+^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
+^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
+^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
+^4^ Department of Biology, Lancaster University, Liverpool, UK
 
@@
 Such changes in physiological trait variation may also have important ecological consequences by promotong population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011].
-The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to persist in and adapt to novel environments [@Scheiner2020].
+The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
 
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
-Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn].
-Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., see @Seebacher2015-wi], it is unclear if the magnitude of physiological adjustment is sufficient.
+Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn; @hoffmann2013upper].
+Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient.
 Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
@@
 Reduced variability may result from variances being eroded by strong selection, an inability to adjust physiological rates, or a combination of both.
+Changes in physiological rate variance may therefore have important cascading effects on energy transfer and productivity for populations across these different ecosystems that are as of yet poorly measured and modelled.
 
@@
 
-Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the impacts ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
-Here we show that the opportunity for selection is expected to decrease for ectotherms, but particularly so for terrestrial ectotherms (~28%).
-Decreases in variance in physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (marine: 9% acclimation vs.
+Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
+Here we show that variance in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
+Decreases in variance of physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (marine: 9% acclimation vs.
 15% reduction in variance; terrestrial: no acclimation vs 28% reduction in variance).
 Such effects are expected to result in a decrease in the variability in physiologcial rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further attention.
+Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention.
 
@@
 Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key].
-Higher spatial heterogenetiy in terrestrial ectotherms suggests that plasticity should be more likely evolve, however, we did not find evidence to this effect; possibly because of the lower predictability of thermal environments over time making cues unreliable [@hendry2016key].
-Empirical evidence properly testing these predictions, however, is scant.
+Higher spatial and temporal heterogenetiy in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely evolve, however, we did not find evidence to this effect; possibly because of the lower predictability of thermal environments over time making cues unreliable [@hendry2016key].
+Empirical evidence properly testing these predictions is also scant.
 @Leung2020 recently showed that greater plasticty in morphological traits did evolve in experimental algae populations, however, work in seed beetles.
@@
 Changes in variability in physiological rates, particularly energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems that can have important consequences for population dynamics [@hendry2016key].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increasdd growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key].
 For examaple, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.

### 2023-12-13 ms.qmd
More discussion writing

@@
 
-### **Acclimation capacity and opportunity for selection is limited in response to climate change**
+### ***Acclimation capacity and opportunity for selection across ectotherms in response to climate change***
+
+There is a general interest in understanding the interplay between plasticity and genetic adaptation to a populations capacity to mitigate climate change effects [].
+We show that plastic adjustments to physiological rates are rather small (if they exist at all) compared to the general reduction variance in physiological rates.
+While it is unclear the extent to which such changes in variance are heritable we expect changes in variance of this magnitude to have an impact on the opportunity for selection by reducing the strength of selection or underlying genetic variance.
+Both are predcited to reduce the capacity of populations to evolve under climate change.
 One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats.
@@
 
-### **No signature of past climate on capacity for acclimation or opportunity for selection**
-
-Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key].
-Higher spatial and temporal heterogenetiy in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely evolve, however, we did not find evidence to this effect; possibly because of the lower predictability of thermal environments over time making cues unreliable [@hendry2016key].
-Empirical evidence properly testing these predictions is also scant.
-@Leung2020 recently showed that greater plasticty in morphological traits did evolve in experimental algae populations, however, work in seed beetles.
-Our results suggest that such theoretical explanations may not be general but rather specific to the population, context and trait in question; a point emphaised by others.
+### ***No signature of past climate on capacity for acclimation***
+
+Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Higher spatial and temporal heterogenetiy in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely evolve in terrestrial environments, however, we did not find evidence to this effect.
+The lack of relationship between acclimation responses and environmental variability and predictability could be due to the challenges in estimating realistic microthermal enviroments experienced by taxa or because lower predictability of thermal environments over time make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
+Randomly flutuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
+For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly flutuating thermal conditions did not lead to the expected increase in plasticity, but reduced plasticity.
+@Leung2020 also showed reduced plasticity in morphological traits when environments experienced were less predictable by experimentally evolving algae populations (*Dunaliella salina*) [see also @leung2023phenotypic].
+The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predcitability, which is likely generally higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
 
 ### ***Ecological consequences of reduced variation in physiological Rates***
-Variance in physiological rates decreases substantially at high temperatures with effects being especially pronouced in terrestrial ecosystems and for key traits such as metabolism and performance.
-Changes in variability in physiological rates, particularly energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems that can have important consequences for population dynamics [@hendry2016key].
+While we found that variance in physiological rates decreases substantially at high temperatures, especially pronouced in terrestrial ecosystems, variance reductions in metabolism and performance were key traits most strongly impacted.
+Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems [@hendry2016key].
 More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key].
-For examaple, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+Maintaining intrapopulaton variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
+Nonetheless, few studies have explored the consequences that variation in physiological traits have for population dynamics.
+Those studies that have have shown that such variation can have important implications.
+For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
 They showed that greater between-individual variation in DEB parameters led to less extreme population occilations compared to scenerios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ecotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extintion and reduced productivity – predictions already reinforced by a number of authorities .
-To date, however, an appreciation for the wide-reaching impacts changes in variance may have on populations and communities remains limited.
-Indeed, the ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remain unclear.
-Such insight will require the development of theoretical models that better integrate intrapopulation variation into mechanistic physiological models or ones that better capture stochasticity such as individual based models.
-
-The dearth of empirical data demonstrating changes in variance paired with a lack of theoretical models 
-- buckley 2014, - Lawton 1991, - Nisbet
-
-### **Acute and acclimation responses of wild ectotherms are lower in warmer environments**
-
-### **The opportunity for selection is expected to decrease for wild ectotherms under climate change**
-
-### **Limitations and future directions**
-
-An enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may increase our ability to make more informed predcitions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
+The differences in variance change across major habitat types suggest that terrestrial ecotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extintion and reduced productivity – predictions already reinforced by a number of studies [@hoffmann2013upper; @Gunderson2015; @Pottier2022].
+To date, however, an appreciation for the wide-reaching impacts that changes in variance may have on populations and communities remains limited.
+The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remain unclear.
+What we desperately need now are the development of theoretical models that better integrate intrapopulation variation into mechanistic physiological models or ones that better capture stochasticity such as individual based models.
+Our meta-analytic findings can help us better position ourselves to now start asking questions about the ecological and evolutionary consequences of changes in variance in physiological rates.
+
+### ***Limitations and future directions***
+
+An enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may increase our ability to make more informed predictions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
+Variance in physiological rates could be better incoperated in physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
+Our meta-analysis mean that such models can be that are better aligned with empirical findings.
+Nonethless, many fascinating questions remain unanswered that will require greater focus on the consequences of change sin variance (rather than just the mean): How does a reduction in physiological rate varaince change the flow of energy across tropic levels within communities?
+What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?
+What fraction of the change in variance is environmental versus genetic?
 

### 2023-12-14 ms.qmd
Think I have a rough first draft done

@@
 ## **Abstract**
+ will write this later...should take me 20 minutes
 
 ## **Introduction**
-
-<!-- 
-  1. Phenotypic plasticity and evolutionary adatation to novel environments
-  2. Capacity for plasticity and adaptation differ between aqautic and terrestrial ectotherms
-  3. Climate change is expected to impact on the capacity for plasticity and adaptation
-  4. We test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
--->
 
@@
 Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn; @hoffmann2013upper].
-Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient.
+Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient, particularly in combination with potential changes other factors such as genetic and phenotypic variability.
 Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
@@
 We fit models using both air and soil temperature and found that the results were qualitatively similar.
-As such, we only present results for air temperature (See Supplementary Materials).
+As such, we only present results for air temperature.
 
@@
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
 We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
@@
 
-### *The opportunity for selection is reduced in terrestrial ectotherms*
-
-The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
+### *Reduced variation in physiological rates in terrestrial ectotherms*
+
+Variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
 Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C.
@@
 
-Thermal variability (i.e., $CV$) and predictability a population experienced in its past did not explain acclimation capacity or changes in opportunity for selection (i.e., the change in physiological variability) among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
+Thermal variability (i.e., $CV$) and predictability a population experienced in its past did not explain acclimation capacity or changes in the change in physiological variability among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
 
@@
 
-### Global change in opportunity for selection
+### Changes in physiological rate variance under climate change
 
@@
 Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6 A-C).
-Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D).
-Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
-
-Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
+Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
+However, out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
+
+Predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
 Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
@@
 Here we show that variance in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
-Decreases in variance of physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (marine: 9% acclimation vs.
-15% reduction in variance; terrestrial: no acclimation vs 28% reduction in variance).
+Decreases in variance of physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 9% acclimation vs.
+15% reduction in variance; *terrestrial*: no acclimation vs 28% reduction in variance).
 Such effects are expected to result in a decrease in the variability in physiologcial rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
 Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention.
-
-### ***Acclimation capacity and opportunity for selection across ectotherms in response to climate change***
-
-There is a general interest in understanding the interplay between plasticity and genetic adaptation to a populations capacity to mitigate climate change effects [].
-We show that plastic adjustments to physiological rates are rather small (if they exist at all) compared to the general reduction variance in physiological rates.
-While it is unclear the extent to which such changes in variance are heritable we expect changes in variance of this magnitude to have an impact on the opportunity for selection by reducing the strength of selection or underlying genetic variance.
-Both are predcited to reduce the capacity of populations to evolve under climate change.
+We discuss our findings in the context of the current literature and highlight key areas for future research.
+
+### ***Potential evolutionary consequences for reduced plasticity and variance in physiologcial rates across ectotherms***
+
+There is a general interest in understanding the interplay and relative importance of plasticity and genetic adaptation to a population's capacity to mitigate climate change effects [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate].
+Phenotypic plasticty is expected to allow populations to persist in the face of climate extremes by better allowing phenotypes to match fitness optima, however, maladaptive responses can occur [@noble2019plastic; @radersma2020plasticity] and there may be limits / costs to plasticty that may prevent it from evolving [@Dewitt1998; but see @Murren2015].
+While there is substantial variation in effects across species, we show that plastic adjustments to physiological rates are, on average, rather small compared to the general reduction variance in physiological rates.
+Variance reductions are particularly pronouced for terrestrial ectotherms and there were no major differences between life-stages.
+While it is unclear the extent to which such changes in variance are heritable, we expect changes in variance of this magnitude to have an impact on the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
+Both are predicted to impact the capacity of populations to evolve under climate change [@hoffmann2011climate; @urban2023and].
+
 One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats.
 However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
-Faster rates of acclimation would therefore result in the opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
-assuming a fraction of this variation is heritable and/or it weakens selection
+Faster rates of acclimation would therefore result in the opposite patterns to those that we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
+The weak acclimation responses of terrestrial ectotherms suggests that evolving plasticty in physiological rates may be hard, possibly because terrestrial ectotherms are more likely to experience more variable and unpredictable thermal environments compared to aquatic ectotherms (see below).
+Reductions in physiological rate variance for terrestrial ectotherms may be because of selective mortality at higher temperatures reducing intrapopulation variability or populations being pushed closer to their thermal maxima (or a combination of both).
+Disentangling these hypotheses will require empirical studies to connect measures of survival at different temperatures with thermal physiology across indiviudals (e.g., $CT_{max}$).
+
+### ***Plasticity and variance in physiologcial rates do not differ between life-stages***
+Greater plasticity for early life-stages in development may be particularly important for dealing with the effects of climate change because early life-stages are usually particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+Evidence across the literature conflicts in terms of the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
+For example, @moghadam2019heat showed that larvae *Drosophila* were more plastic in their heat hardening responses compared to adults.
+In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
+Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticty.
+Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
+However, very few studies measured multiple life-history stages within the same population.
+As such, we need more studies that explicitly compare, within populations, differences in plasticity among life stages across multiple traits.
+A better understanding of the microthermal enviroments experienced by different life-stages will also be important in understanding why plasticty (or lack thereof) may differ among life-stages.
 
@@
 Randomly flutuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
-For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly flutuating thermal conditions did not lead to the expected increase in plasticity, but reduced plasticity.
+For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly flutuating thermal conditions did not lead to the expected increase in plasticity, but rather reduced plasticity.
 @Leung2020 also showed reduced plasticity in morphological traits when environments experienced were less predictable by experimentally evolving algae populations (*Dunaliella salina*) [see also @leung2023phenotypic].
-The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predcitability, which is likely generally higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-
-### ***Ecological consequences of reduced variation in physiological Rates***
-While we found that variance in physiological rates decreases substantially at high temperatures, especially pronouced in terrestrial ecosystems, variance reductions in metabolism and performance were key traits most strongly impacted.
+The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
+However, disentangling the relative importance of environmental variability and predictability will require better distinguishing between active and passive plasticty, as the latter is expected to more likely be adaptive (@Havird2020-mj).
+
+### ***Ecological consequences of reduced variation in physiological rates***
+While we found that variance in physiological rates decreases substantially at high temperatures, being especially pronouced in terrestrial ectotherms, variance reductions in metabolism and performance were key traits most strongly impacted.
 Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems [@hendry2016key].
@@
 Nonetheless, few studies have explored the consequences that variation in physiological traits have for population dynamics.
-Those studies that have have shown that such variation can have important implications.
+Those studies that have, have shown that such variation can have important implications.
 For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
 They showed that greater between-individual variation in DEB parameters led to less extreme population occilations compared to scenerios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ecotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extintion and reduced productivity – predictions already reinforced by a number of studies [@hoffmann2013upper; @Gunderson2015; @Pottier2022].
+The differences in variance change across major habitat types suggest that terrestrial ecotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extintion and reduced productivity – predictions reinforced by a number of studies [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022].
 To date, however, an appreciation for the wide-reaching impacts that changes in variance may have on populations and communities remains limited.
@@
 
-### ***Limitations and future directions***
+### ***Conclusions and future directions***
 
 An enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may increase our ability to make more informed predictions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
-Variance in physiological rates could be better incoperated in physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
-Our meta-analysis mean that such models can be that are better aligned with empirical findings.
-Nonethless, many fascinating questions remain unanswered that will require greater focus on the consequences of change sin variance (rather than just the mean): How does a reduction in physiological rate varaince change the flow of energy across tropic levels within communities?
+Variance in physiological rates could be better incorperated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
+While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predcitions.
+Our meta-analysis allows for realistic models to be parameterised and ensure they are better aligned with empirical findings.
+Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
+Particularly interesting questions include: How does a reduction in physiological rate varaince change the flow of energy across tropic levels within communities?
 What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?
-What fraction of the change in variance is environmental versus genetic?
+Are reductions in variance in one trait associated with reductions in correlated traits or do some traits increase while others decrease?
+How much of the reduction in variance driven by lower levels of genetic variance?
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation.
 

### 2023-12-14 ms.qmd
Rendered with new ref

@@
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
-Such changes in physiological trait variation may also have important ecological consequences by promotong population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011].
+Such changes in physiological trait variation may also have important ecological consequences by promotong population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
 The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
@@
 Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems [@hendry2016key].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
 Maintaining intrapopulaton variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.

### 2023-12-15 ms.qmd
Updates to legends

@@
 
-        tree_p1 <- compute.brlen(tree, method = "Grafen", power = 1)
       tree_p0.7 <- compute.brlen(tree, method = "Grafen", power = 0.7) # Probably most sensible power
@@
      # Create null nodes 
-        tree_p1$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
       tree_p0.7$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
@@
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on acclimation across ectotherms.
+As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
 
@@
 #### *Comparing variance in physiological rates*
-@Nakagawa2015-fo recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
 *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
@@
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
-We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+We chose a 2-meter resolution because we believed that it more likely reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
 For terrestrial species we also collected soil temperature as for many species this maybe more representative of microhabitat choice compared to air temperature.
@@
 
-We also extracted climate projections into the future to understand the effects of climate warming will have on opportunity for selection.
+We also extracted climate projections into the future to understand the effects that climate warming will have on physiological rate variance.
 We used the CanESM2 climate model (2005-2100) under a high emissions scenerio (RCP8.5).
@@
 
-# have a quick look on habitat, development and type. Mostly looks sensibel but there is not too much data in terrestrial realm.
+# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
 sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
@@
 
-Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the resulting of sampling varianbility, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
 Evolutionary relationships among taxa and species ecology explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
@@
 #| label: fig-2
-#| fig-cap: Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems
+#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
 #| echo: false
@@
 #| label: fig-3
-#| fig-cap: Predicted mean acclimation and acute "$lnRR_{Q_{10}}$" for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
+#| fig-cap: "Predicted mean acclimation and acute $lnRR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.""
 
@@
 #| label: fig-cvrlh
-#| fig-cap: "Predicted mean $lnCVR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms."
+#| fig-cap: "Predicted mean $lnCVR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.""
 #| echo: false
@@
 #| label: fig-cvrtrait
-#| fig-cap: Acute and Acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems
+#| fig-cap: "Acute and Acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.""
 #| echo: false
@@
 
-Thermal variability (i.e., $CV$) and predictability a population experienced in its past did not explain acclimation capacity or changes in the change in physiological variability among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
+Thermal variability (i.e., $CV$) and predictability a population experienced in its past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
 
@@
 #| fig-align: center
-#| fig-cap: Bubble plot environment $lnRR_{Q_{10}}$ for wild populations by habitat.
+#| fig-cap: "Predcited mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations by habitat.
+Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Model slope ($\beta$) and p-value are shown for each habitat along with the 95% CI and $p_{MCMC} value."
 
@@
 #| fig-align: center
-#| fig-cap: Bubble plot environment $lnCVR_{Q_{10}}$ for wild populations by habitat.
+#| fig-cap: "Predcited mean (thick black line) $lnCVR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations by habitat.
+Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Model slope ($\beta$) and p-value are shown for each habitat along with the 95% CI and $p_{MCMC} value."
 
@@
 Reductions in physiological rate variance for terrestrial ectotherms may be because of selective mortality at higher temperatures reducing intrapopulation variability or populations being pushed closer to their thermal maxima (or a combination of both).
-Disentangling these hypotheses will require empirical studies to connect measures of survival at different temperatures with thermal physiology across indiviudals (e.g., $CT_{max}$).
+Disentangling these hypotheses will require empirical studies to connect measures of survival at different temperatures with thermal physiology across individuals (e.g., $CT_{max}$).
 
 ### ***Plasticity and variance in physiologcial rates do not differ between life-stages***
-Greater plasticity for early life-stages in development may be particularly important for dealing with the effects of climate change because early life-stages are usually particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+Greater plasticity for early life-stages in development may be important for dealing with the effects of climate change because early life-stages are usually particularly vulnerable periods in development [@martin2015age; @stearns1976life].
 Evidence across the literature conflicts in terms of the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
@@
 
-### ***No signature of past climate on capacity for acclimation***
-
-Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+### ***No signature of past climate on capacity for physiological plasticity***
+
+Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
 Higher spatial and temporal heterogenetiy in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely evolve in terrestrial environments, however, we did not find evidence to this effect.
-The lack of relationship between acclimation responses and environmental variability and predictability could be due to the challenges in estimating realistic microthermal enviroments experienced by taxa or because lower predictability of thermal environments over time make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
+The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal enviroments experienced by taxa or because lower predictability of thermal environments over time make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
 Randomly flutuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
@@
 @Leung2020 also showed reduced plasticity in morphological traits when environments experienced were less predictable by experimentally evolving algae populations (*Dunaliella salina*) [see also @leung2023phenotypic].
+These findings, in combination with our results, suggests that there are costs to being plastic when environments are not predictable (either intrinsic physiological costs, fitness costs or both).
 The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-However, disentangling the relative importance of environmental variability and predictability will require better distinguishing between active and passive plasticty, as the latter is expected to more likely be adaptive (@Havird2020-mj).
+However, disentangling the relative importance of environmental variability and predictability will require better distinguishing between active and passive plasticty, as the latter is expected to more likely be adaptive (@Havird2020-mj), and better a understanding the fitness consequences of exhibiting plastic versus canalised phenotypes.
 
 ### ***Ecological consequences of reduced variation in physiological rates***
-While we found that variance in physiological rates decreases substantially at high temperatures, being especially pronouced in terrestrial ectotherms, variance reductions in metabolism and performance were key traits most strongly impacted.
+While we found that variance in physiological rates decreases at high temperatures, being especially pronouced in terrestrial ectotherms, variance reductions in metabolism and performance were key traits most strongly impacted.
 Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems [@hendry2016key].
@@
 
-An enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may increase our ability to make more informed predictions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
+An enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
 Variance in physiological rates could be better incorperated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
@@
 Are reductions in variance in one trait associated with reductions in correlated traits or do some traits increase while others decrease?
-How much of the reduction in variance driven by lower levels of genetic variance?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation.
+How much of the reduction in variance is driven by lower levels of genetic variance?
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation, but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
 

### 2023-12-15 ms.qmd
Most recent paper. First draft

@@
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.""
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
 
@@
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.""
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
 #| echo: false

### 2024-01-03 ms.qmd
comment fixes

@@
 
-<p style="text-align: center;">Daniel W.A. Noble^1^, Fonti Kar^2^, Frank Seebacher^3^, Alex Bush^4^, & Shinichi Nakagawa^2^</p>
+<p style="text-align: center;">Daniel W.A. Noble^1^, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^, & Shinichi Nakagawa^2^</p>
 
@@
 ^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
-^4^ Department of Biology, Lancaster University, Liverpool, UK
+^4^ Department of Biology, Lancaster University, Liverpool, UK &NewLine;
+^*^ Shared senior authorship &NewLine;
+^**^ corresponding author, daniel.noble@anu.edu.au &NewLine;
 

### 2024-01-04 ms.qmd
Fixing symbols

--- 2023-12-15 ms.qmd
@@
 
-<p style="text-align: center;">Daniel W.A. Noble^1^, Fonti Kar^2^, Frank Seebacher^3^, Alex Bush^4^, & Shinichi Nakagawa^2^</p>
+<p style="text-align: center;">Daniel W.A. Noble^1^ $\dagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
 
@@
 ^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
-^4^ Department of Biology, Lancaster University, Liverpool, UK
+^4^ Department of Biology, Lancaster University, Liverpool, UK &NewLine;
+^$\dagger$^ Shared senior authorship &NewLine;
+^$\ddagger$^ corresponding author, daniel.noble@anu.edu.au &NewLine;
 

### 2024-01-04 ms.qmd
Comments to Resuts section dealt with aside from prisma

--- 2023-12-15 ms.qmd
@@
 
-<p style="text-align: center;">Daniel W.A. Noble^1^, Fonti Kar^2^, Frank Seebacher^3^, Alex Bush^4^, & Shinichi Nakagawa^2^</p>
+<p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
 
@@
 ^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
-^4^ Department of Biology, Lancaster University, Liverpool, UK
+^4^ Department of Biology, Lancaster University, Liverpool, UK &NewLine;  
+$\dagger$ contributed equally &NewLine;  
+$\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
 
@@
 The extent to which adaptive plasticity and genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
-Without such responses, high rates of extinction are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticty first hypothesis' - @WestEberhard2003; see also @Lande2009].
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity is low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Without such responses, high extinction rates are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
+Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticity first hypothesis' - @WestEberhard2003; see also @Lande2009].
+Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
 Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
 
-Reversible forms of phenotypic plasticty, such as acclimitisation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticty are low – @Dewitt1998; @Scheiner2020].
+Reversible forms of phenotypic plasticity, such as acclimatization  and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
 Such responses are driven by changes in underlying physiology that can respond rapidly to the environment.
-However, studies have primarily been focused on mean physiological responses, paying little attention to changes in physiological variability [@Seebacher2015-wi; @Havird2020-mj].
+However, studies have primarily been focused on mean physiological responses, paying little attention to changes in physiological variability in a population [@Seebacher2015-wi; @Havird2020-mj].
 For example, most work has focused on the degree to which mean thermal tolerances or acclimation abilities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022], neglecting how intrapopulation variability might also be impacted.
-Understanding how variability in physiological rates -- traits thought to be closely closely linked to fitness -- are affected by climate change has important implications for understanding a populations capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variability may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
+Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change has important implications for understanding a population's capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
+Higher physiological variability in a population may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
 Such changes in physiological trait variation may also have important ecological consequences by promotong population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
-The implications of changes in variance could therefore have wide-reaching consequences for understanding the capacity for populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
+The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
 
@@
 Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn; @hoffmann2013upper].
-Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient, particularly in combination with potential changes other factors such as genetic and phenotypic variability.
+Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient, particularly in combination with potential changes in other factors, such as genetic and phenotypic variability.
 Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
-Given that terrestrial ectotherms are expected to be closer to their thermal limits increases in temperature may have a stronger impact on variation in physiological rates within populations compared to aqautic ectotherms.
+Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms.
 Reduced variability may result from variances being eroded by strong selection, an inability to adjust physiological rates, or a combination of both.
-Changes in physiological rate variance may therefore have important cascading effects on energy transfer and productivity for populations across these different ecosystems that are as of yet poorly measured and modelled.
+Changes in physiological rate variance may therefore have important cascading effects on energy transfer and productivity for populations across these different ecosystems that are, as of yet, poorly measured and modelled.
 
@@
 3) Are changes in plasticity or variance in physiological rates impacted by a population's past climate history?
-and 4) How are means and variances in physiological rates expected to change under climate change?
+4) How are means and variances in physiological rates expected to change under climate change?
 
@@
 Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
-We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates  @Seebacher2015-wi's dataset.
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
 We included any papers that were missed between our searches and those of @Havird2020-mj from the dates 2013-2017.
@@
 We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
-If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
+If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
 We extracted these data from text, tables or figures of a given paper.
@@
 
-Following @Noble2022-ty we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
 These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations for their sampling variances.
@@
 We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021-ls].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba].
+2.0, @Nakagawa2021-ls; @nakagawaorchard].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
 For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
@@
 #### *Multi-level Meta-analysis (MLMA) Models*
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, and phylogeny as random effects to account for non-independence.
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, and phylogeny as random effects to account for non-independence.
 We also included trait as a random effect to account for trait variation within the data.
@@
 This will be in degrees C.
-Then, assuming no plasticty and evolution (big assumption) we can get a baseline change in variance for each site.
+Then, assuming no plasticity and evolution (big assumption) we can get a baseline change in variance for each site.
 We first need to adjust the predcited Q10 value so that it's at 1C temperaure, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
@@
 This is the predcited lnCVRq10 for 10C change AT the specific latitude and longitude.
-We must assume that there is no plasticty or adaptation at each site to make projections
+We must assume that there is no plasticity or adaptation at each site to make projections
   all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
@@
 There is a general interest in understanding the interplay and relative importance of plasticity and genetic adaptation to a population's capacity to mitigate climate change effects [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate].
-Phenotypic plasticty is expected to allow populations to persist in the face of climate extremes by better allowing phenotypes to match fitness optima, however, maladaptive responses can occur [@noble2019plastic; @radersma2020plasticity] and there may be limits / costs to plasticty that may prevent it from evolving [@Dewitt1998; but see @Murren2015].
+Phenotypic plasticity is expected to allow populations to persist in the face of climate extremes by better allowing phenotypes to match fitness optima, however, maladaptive responses can occur [@noble2019plastic; @radersma2020plasticity] and there may be limits / costs to plasticity that may prevent it from evolving [@Dewitt1998; but see @Murren2015].
 While there is substantial variation in effects across species, we show that plastic adjustments to physiological rates are, on average, rather small compared to the general reduction variance in physiological rates.
@@
 Faster rates of acclimation would therefore result in the opposite patterns to those that we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
-The weak acclimation responses of terrestrial ectotherms suggests that evolving plasticty in physiological rates may be hard, possibly because terrestrial ectotherms are more likely to experience more variable and unpredictable thermal environments compared to aquatic ectotherms (see below).
+The weak acclimation responses of terrestrial ectotherms suggests that evolving plasticity in physiological rates may be hard, possibly because terrestrial ectotherms are more likely to experience more variable and unpredictable thermal environments compared to aquatic ectotherms (see below).
 Reductions in physiological rate variance for terrestrial ectotherms may be because of selective mortality at higher temperatures reducing intrapopulation variability or populations being pushed closer to their thermal maxima (or a combination of both).
@@
 In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
-Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticty.
+Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticity.
 Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
@@
 As such, we need more studies that explicitly compare, within populations, differences in plasticity among life stages across multiple traits.
-A better understanding of the microthermal enviroments experienced by different life-stages will also be important in understanding why plasticty (or lack thereof) may differ among life-stages.
+A better understanding of the microthermal enviroments experienced by different life-stages will also be important in understanding why plasticity (or lack thereof) may differ among life-stages.
 
@@
 The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-However, disentangling the relative importance of environmental variability and predictability will require better distinguishing between active and passive plasticty, as the latter is expected to more likely be adaptive (@Havird2020-mj), and better a understanding the fitness consequences of exhibiting plastic versus canalised phenotypes.
+However, disentangling the relative importance of environmental variability and predictability will require better distinguishing between active and passive plasticity, as the latter is expected to more likely be adaptive (@Havird2020-mj), and better a understanding the fitness consequences of exhibiting plastic versus canalised phenotypes.
 

### 2024-01-05 ms.qmd
Writing abstract

@@
 ## **Abstract**
- will write this later...should take me 20 minutes
+
+Climate change is expected to result in warmer and more variable thermal environments globally.
+Greater thermal variability is expeced to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
+However, such responses depend on the extent of genetic and phenotypic variability, yet most work has focused on mean responses to climate warming ignoring how temperature changes variability.
+Here, we collect data on marine, freshwater and terrestrial ectotherms to quantify their capacity for acclimation and the extent to which variance in physiological rates change in response to higher temperatures.
+We use new effect size measures and meta-analysis to understand
 

### 2024-01-06 ms.qmd
Fix trait fig to remove extra legends.

@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() 
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
 #ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
 #ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

### 2024-01-07 R/functions.R
New function for plots

@@ -416,6 +416,17 @@ p_value <- function(x){
   return(tmp)
 }
 
+#' @title manual_extract
+#' @description Extracts the k and number of groups manually from a model object using mod_results
+#' @param model The model of interest
+#' @param mod The moderator of interest
+#' @param group The grouping variable
+#' @param exclude The moderator level to exclude (optional)
+#' 
+manual_extract  <- function(model, mod = "trait_category", group = "record_num", exclude = NULL){
+  orchaRd::mod_results(model, mod = mod, group = group)$data  %>% group_by(moderator) %>% summarise(k = n(), sdy = length(unique(stdy)))  %>% filter(!moderator == exclude)
+}
+
 #' @title text
 #' @description Converts posterior distribution into a text statement for plotting
 #' @param post the posterior distribution as a vector

### 2024-01-07 ms.qmd
Fixing trait plots to make them look cleaner and easier to see

@@
 #| echo: false
+k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
 
@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none",
+                              axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
+                            annotate("text", label= paste0(k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4)
 #ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

### 2024-01-07 R/exploratory/Overview_1.Rmd
Not clear why these files have changed as they havent

@@
----
-title: "Acclimation Responses of Physiological Rates and Opprotunity for Selection"
-output:
-  html_document:
-    code_folding: hide
-    theme: united
-    toc: yes
-    toc_float: yes
-author: Shinichi Nakagawa & Daniel Noble
-date: "`r format(Sys.time(), '%d %B, %Y')`"
-bibliography: bib.bib
----
-
-```{r,echo=FALSE, cache=FALSE}
-  ## numbers >= 10^5 will be denoted in scientific notation,
-  ## and rounded to 2 digits
-  options(digits = 2)
-```
-
-# Deriving New Temperature Corrected Effect Sizes for Mean and Variance
-
-## *Q*~10~RR: Comparing mean physiological rates
-
-  Inspired by Seebacher et al.
-[-@seebacher2015physiological] we derive a temperature corrected effect size to compare physiological rates, *Q*~10~RR, also known as, the temparature response ratio.
-We note that this is just a variant of the log response ratio (lnRR), which is one of the most popular effect size statistics [@hedges1999meta; @nakagawa2012methodological].
-Given this, we can easily derive the sampling error variance for *Q*~10~RR (on the log scale), but surprsingly, it has not been done before in the literature.
-*Q*~10~RR is defined as:
-
-  $$
-  Q_{10}RR = \left( \frac{R_{2}}{R_{1}} \right)^{ \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) },
-  $$
-  where *R* is the rate and *T* is the temparature in Celsius (but can be kelvins). If we take the natural logarithm at the both sides:
-
-  $$
-  \ln{Q_{10}RR} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
-  \left( \ln{R_2} -  \ln{R_1} \right).
-  $$
-
-  Therefore, the sampling variance of ln*Q*~10~RR (*V*~ln*Q*10~RR) is, following Hedges et al. [-@hedges1999meta]:
-  $$
-  V_{\ln{Q_{10}RR}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }^2
-  \left[ \frac{(\text{SD}_{1})^2}{n_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{n_{2} ({R}_{2})^2} \right],
-  $$
-  where SD~1~ and SD~2~ are the sample standard deviation of *R*~1~ and *R*~2~ at two different temperatures (*T*~1~ and *T*~2~), respectively and *n* are sample size for estimating *R*.
-
-  > [Wiki](https://en.wikipedia.org/wiki/Q10_(temperature_coefficient)) says "The *Q*~10~ temperature coefficient is a measure of the rate of change of a biological or chemical system as a consequence of increasing the temperature by 10&deg;C"
-
- #<!--- degree = &deg;C; check out https://gist.github.com/DeoluA/5a4e7dac54dbc3df19fe --->#
-
-## *SQ*~10~: Comparing variances in physiological rates
-  So *Q*~10~RR can be more accurately called 'the tempature coefficent of the rate of change'.
-Once one realizes that the rate, *R* has a SD, then, we can define what we call 'the tempature coefficent of change in the variation in the rates', which is inspired by Nakagawa et al.
-[-@nakagawa2015meta].
-We denote this as *SQ*~10~, which can be written as:
-
-  $$
-  SQ_{10} = \left( \frac{\text{SD}_{2}}{\text{SD}_{1}} \right)^{ \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }.
-  $$  
-  Like *Q*~10~RR, we take the natural logarithm, then:
-  $$
-  \ln{SQ_{10}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
-  \left( \ln{\text{SD}_2} -  \ln{\text{SD}_1} \right).
-  $$
-  The sampling variance for ln*S*~10~ (*V*~ln*S*10~) is, according to Nakagawa et al. [-@nakagawa2015meta]:
-  $$
-  V_{\ln{SQ_{10}}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }^2
-  \left[ \frac{1}{2\left( n_{1}-1 \right)} + \frac{1}{2\left(n_{2} - 1\right)} \right]
-  $$
-
-  What does *SQ*~10~ tell us?
-And how is it different from *Q*~10~RR?
-*Q*~10~RR is also referred to as 'thermal sensitvity'.
-*SQ*~10~ represents a change of individual variation at two temparature.
-It is hard to come up with a nifty name but let's call it 'thermal individual-variation change' or 'thermal idiosyncrasy' is probably shorter and better?
-Actually Dan says "thermal stability" may capture the essence of *SQ*~10~.
-
-## *CVQ*~10~: Comparing Coefficient of Variance in Physiological Rates
-
-  We may want to derive *CVQ*~10~ (i.e., the coefficient of variance in Q10), which is the change in SD corrected for the mean (i.e., CV) given that we know there exsits the mean-variance relationship.
-NO idea how we call this but *CVQ*~10~ can be defiend as:
-
-  $$
-  CVQ_{10} = \left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right)^{ \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) },
-  $$
-
-  Like *SQ*~10~, we take the natural logarithm, then:
-
-  $$
-  \ln{CVQ_{10}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
-  \left( \ln{\text{CV}_2} -  \ln{\text{CV}_1} \right).
-  $$
-
-  The sampling variance for ln*CV*~10~ (*V*~ln*CV*10~) is, follwoing Nakagawa et al. [-@nakagawa2015meta]:
-
-  $$
-  V_{\ln{CVQ}_{10}} = { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }^2
-  \left[ \frac{(\text{SD}_{1})^2}{n_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{n_{2} ({R}_{2})^2} + \frac{1}{2\left( n_{1}-1 \right)} + \frac{1}{2\left(n_{2} - 1\right)} \right]
-  $$
-
-  Note that we assume there is no correlaiton between the mean and variance at the level of the sampling error although Nakagawa et al. [-@nakagawa2015meta] did.
-
-## Mathematical equivalence of Q~10~ effects sizes to LnRR?
-
-  After some close inspection of things when interpreting, I (Dan) think we may not be getting at the question I (we) thought we are interested in.
-This only dawned on me when interpreting the effect size in detail.
-
-  First, take a look back at Franks original paper.
-Basically, r1.1/2.1 to r1.2/r2.2 is really just discussing how the rate and variance change along the line of cold and warm acclimated.
-This is reflected strongly in the analyses presented throughout and the effect sizes we generate below.
-But, if we want to understand how exactly acclimation affects the mean and variance of physiological rates we need to compare to the post acclimation responses.
-However, contrary to what we have been thinking I do not think comparing r1.1 to r2.2 is relevant on its own (see the quite literal interpretations of this effect below).
-We certainly need to have an acute comparison otherwise post acclimation Q~10~ doesn't say much on it's own.
-There is no question that comparing r1.1 to r2.2 is relevant as a rate, but it's just that it needs to be relative to a non-acclimated response.
-The reason being is that the acclimation treatments are completely confounded with the measurement treatments.
-We already know from the Q~10~ analyses of acute responses below that, actually there are really strong effects on mean physiological rates in response to temperature, surprise, surprise.
-What is new, is that we show that this is a heteroscadastic!
-Which means that the variance around the population mean along these lines increases with temperature.
-This is totally new and unexplored.
-
-  Nonetheless, this cool finding doesn't allow us to make conclusions about the extent to which 1) acclimation affects mean physiological rates and 2) how the variance of these physiological rates is impacted by acclimation.
-In other words, what we really need to do is contrast *Q*~10ac~RR (r1.1 to r1.2) with *Q*~10pa~RR (r1.1 to r2.2) effect sizes, or alternatively the slope of each acute response.
-Of course, comparing the slopes between cold acclimated response curves and warm acclimated response curves would limit the amount of data quite a bit as we would need to rely on fully factorial experiments.
-However, we can compare *Q*~10ac~RR (r1.1 to r1.2) with *Q*~10pa~RR (r1.1 to r2.2), as this is what was done in the original paper anyway and we can do this in an effect size framework as above:
-  $$
-  \ln{Q_{10}RR} = { \left(\ \frac{ { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
-  \left( \ln{R_{1.2}} -  \ln{R_{1.1}} \right) }{ { \left(\ \frac{10^{\circ}}{T_{2}-T_{1}} \right) }
-  \left( \ln{R_{2.2}} -  \ln{R_{1.1}} \right)} \right) }
-  $$
-
-  But, this equation starts to look awfully familiar.
-We can easily see how this can be simplified.
-First, because we are taking a ratio the temperature correction factors completely cancel out.
-Second, we see that $\ln{R_{1.1}}$ is present in the denominator and numerator.
-So, this can go as well and our seemingly complex equation actually just simply condenses down mathematically to the good old fashioned log response ratio with the mean of the rates in the acclimation treatment 1 and acclimation 2 measured at the same temperature:
-
-  $$
-  \ln{RR} = {\ln \left( \frac{R_{1.2}}{R_{2.2}} \right)}
-  $$
-
-  Or, simply just:
-
-  $$
-  \ln{RR} = {\left( \ln{R_{1.2}} -  \ln{R_{2.2}} \right)}
-  $$
-
-  Mathematically, what this appears to mean (unless I made a mistake which of course is possible so check please), all we need to do to get at our question is simply just compare the mean physiological rates from the two acclimation treatments, measured at the same temperature.
-
-  Actually, you will even notice that temperature is already corrected in these estimates, which means that we can actually compare across studies with wildly different temperatures anyway.
-Who the hell would have thought eh?
-
-# Setting up R
-
-```{r, include = FALSE}
-  knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
-```
-
-```{r setup}
-    # clearning up
-    rm(list=ls())
-
-    # loading packages
-    devtools::install_github("haozhu233/kableExtra")
-    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets, metafor, stringr, formatR, rmarkdown, kableExtra)
-
-    # loading functions
-    source("../R/functions.R", chdir = TRUE)
-```
-
-## Loading and seeing data: R
-
-  We can view the data
-
-```{r data, message = FALSE}
-    # getting data from Google Sheet 
-    gs <- gs_title("q10_newdata")
-    data <- as_tibble(gs_read(ss = gs))
-    kable(data) %>%
-    kable_styling(font_size = 10) %>% 
-    	scroll_box(width = "100%", height = "200px")
-```
-
-# Getting *Q*~10~RR, *SQ*~10~ and *CVQ*~10~
-
-### Taxonomy of *Q*~10~RR and *SQ*~10~
-
-  We have 2 types but 3 kinds of *Q*~10~RR: acute termal sensitivity in the cold treatment (*Q*~10ac~RR), acute termal sensitivity in warm treatments (*Q*~10aw~RR) and post-acclimation thermal sensitivity (*Q*~10pa~RR).
-Likewise, we have 2 types but 3 kinds of *SQ*~10~: acute termal idiosyncrasy in the cold treatment (*SQ*~10ac~), acute termal idiosyncrasy in warm treatments (*SQ*~10aw~) and post-acclimation thermal idiosyncrasy (*SQ*~10pa~).
-
-  But we probably should combined *Q*~10ac~RR and *Q*~10aw~RR (also for *S*~10ac~ and *S*~10aw~) as one effect size measure because "cold" in cold treatments is relative not absolute (think about how to do this effectively).
-
-### Why do we need both *SQ*~10~ and *CVQ*~10~
-
-  *SQ*~10~ tells us probably more about predictability of the trait at one temperature and also, statistically, heteroscedasticity along temperature needs to be modeled.
-In contrast, *CVQ*~10~ tells us more about evolutionary potential at a particular temperature and controls for the fact that the variance will be affected with any changes in the mean, and so, this needs to be controlled.
-
-### Create Effect Sizes
-
-```{r effect-size}
-    # Adding 
-    data$obs <- as.factor(1:dim(data)[1])
-
-    # getting effect sizes
-    data %<>% Q10S10(temp_1, temp_2, r1.1, r1.2, r2.1, r2.2, 
-                     r1.1_se, r1.2_se, r2.1_se, r2.2_se,r1.1_N, r1.2_N, r2.1_N, r2.2_N)
-
-    # adding species names
-    data %<>% mutate(spp_names = str_c(genus, species, sep = "_"))
-
-    kable(data) %>%
-    kable_styling(font_size = 10) %>% 
-      scroll_box(width = "100%", height = "200px")
-```
-
-# Data exploration (the mean-variance relationship)
-
-```{r mv-relationship, warning=FALSE}
-
-    p1 <-ggplot(data) +
-      geom_point(aes(x = log(r1.1), y = log(r1.1_se*sqrt(r1.1_N)), color = habitat), size =1) +
-      labs(x = "ln(mean)", y = "ln(SD)", title = "R1.1")
-
-    p2 <-  ggplot(data) +
-      geom_point(aes(x = log(r1.2), y = log(r1.2_se*sqrt(r1.2_N)), color = habitat), size =1) +
-      labs(x = "ln(mean)", y = "ln(SD)", title = "R1.2")
-
-    p3 <-ggplot(data) +
-      geom_point(aes(x = log(r2.1), y = log(r2.1_se*sqrt(r2.1_N)), color = habitat), size =1) +
-      labs(x = "ln(mean)", y = "ln(SD)", title = "R2.1")
-
-    p4 <-  ggplot(data) +
-      geom_point(aes(x = log(r2.2), y = log(r2.2_se*sqrt(r2.2_N)), color = habitat), size =1) +
-      labs(x = "ln(mean)", y = "ln(SD)", title = "R2.2")
-
-    grid.arrange(p1, p2, p3, p4, nrow = 2)
-```
-
-As we can see, there are very strong relationships between the mean and the variance (standard deviation), but we also see some outliers on the bottom of the figures - we need to check these points.
-
-# Meta-analysis for *Q*~10~RR
-
-### Meta-analysis for *Q*~10ac~RR
-
-```{r ma-Q10ac, cache=TRUE}
-    # data with sampling variance
-    data %>% filter(!is.na(V_lnQ10ac), V_lnQ10ac > 0) -> data1
-
-    m1 <- rma.mv(yi = lnQ10ac, V = V_lnQ10ac, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data1)
-    summary(m1)
-    # heterogeneity
-    I2(m1)
-```
-
-So, just a note on **directionality**.
-We subtracted r1.2 from r1.1, which essentially means that when the rates of r1.2 are larger than the rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r1.2 has a ***higher*** rate than acclimation and measurement at r1.1 across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r1.2 has a ***lower*** rate than acclimation than acclimation and measurement at r1.1 across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm1 <- get_est(m1, "Intercept")
-    exp(estm1$estimate)
-```
-
-**Interpretation**: In other words, on average cold acclimated populations have physiological rates at higher temperatures (r1.2) that are about `r (exp(estm1$estimate)-1)*100`% higher than physiological rates at lower temperatures (r1.1) over a 10&deg;C change in temperature.
-
-### Meta-analysis for *Q*~10aw~RR
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    data %>% filter(!is.na(V_lnQ10aw), V_lnQ10aw > 0) -> data2
-
-    m2 <- rma.mv(yi = lnQ10aw, V = V_lnQ10aw, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data2)
-    summary(m2)
-    # heterogeneity
-    I2(m2)
-```
-
-So, just a note on **directionality**.
-We subtracted r2.2 from r2.1, which essentially means that when the rates of r2.2 are larger than the rates of r2.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** rate than acclimation and measurement at r2.1 across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** rate than acclimation than acclimation and measurement at r2.1 across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm2 <- get_est(m2, "Intercept")
-    exp(estm2$estimate)
-```
-
-**Interpretation**: In other words, on average warm acclimated populations have physiological rates at higher temperatures (r2.2) that are about `r (exp(estm2$estimate)-1)*100`% higher than physiological rates at lower temperatures (r2.1) over a 10&deg;C change in temperature.
-
-### Meta-analysis for *Q*~10pa~RR
-
-```{r ma-Q10pa, cache=TRUE}
-    # data with sampling variance
-    data %>% filter(!is.na(V_lnQ10pa), V_lnQ10pa > 0) -> data3
-
-    m3 <- rma.mv(yi = lnQ10pa, V = V_lnQ10pa, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data3)
-    summary(m3)
-    # heterogeneity
-    I2(m3)
-```
-
-So, just a note on **directionality**.
-We subtracted r2.2 from r1.1, which essentially means that when the rates of r2.2 are larger than the rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm3 <- get_est(m3, "Intercept")
-    exp(estm3$estimate)
-```
-
-**Interpretation**:In other words, on average, physiological rates of warm acclimated animals, measured at warm temperatures have physiological rates that are about `r (exp(estm3$estimate)-1)*100`% higher than physiological rates at lower acclimation and measurement temperatures (r1.1) over a 10&deg;C change in temperature.
-
-# Meta-analysis for *SQ*~10~
-
-### Meta-analysis for *SQ*~10ac~
-
-```{r ma-S10ac, cache=TRUE}
-  # data with sampling variance
-  data %>% filter(!is.na(V_lnS10ac), lnS10ac != Inf,  lnS10ac != -Inf,  V_lnS10ac > 0) -> data4
-
-  m4 <- rma.mv(yi = lnS10ac, V = V_lnS10ac, random = list(~ 1 | record_num, ~ 1 | spp_names,  ~ 1 | obs), data = data4)
-  summary(m4)
-  # heterogeneity
-  I2(m4)
-```
-
-So, just a note on **directionality**.
-We subtracted r1.2 from r1.1, which essentially means that when the variance in rates of r1.2 are larger than the variance in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r1.2 has a ***higher*** variance than acclimation and measurement at r1.1 when comparing across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r1.2 has a ***lower*** variance in rates than acclimation and measurement at r1.1 when comparing across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm4 <- get_est(m4, "Intercept")
-    exp(estm4$estimate)
-```
-
-**Interpretation**: In other words, on average cold acclimated populations have variance in physiological rates at higher temperatures (r1.2) that are about `r (exp(estm4$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r1.1) when comparing across a 10&deg;C change in temperature.
-
-### Meta-analysis for *SQ*~10aw~
-
-```{r ma-S10aw, cache=TRUE}
-  # data with sampling variance
-  # why do we get V_lnS10aw < 0??? - need to check data
-  data %>% filter(!is.na(V_lnS10aw), lnS10aw != Inf,  lnS10aw != -Inf, V_lnS10aw > 0) -> data5
-
-  m5 <- rma.mv(yi = lnS10aw, V = V_lnS10aw, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data5)
-  summary(m5)
-  # heterogeneity
-  I2(m5)
-```
-
-So, just a note on **directionality**.
-We subtracted r2.2 from r2.1, which essentially means that when the variance in rates of r2.2 are larger than the variance in rates of r2.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance than acclimation and measurement at r2.1 when comparing across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in rates than acclimation  and measurement at r2.1 when comparing across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm5 <- get_est(m5, "Intercept")
-    exp(estm5$estimate)
-```
-
-**Interpretation**: In other words, on average warm acclimated populations have variances in physiological rates at higher temperatures (r2.2) that are about `r (exp(estm5$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r2.1) when comparing across a 10&deg;C change in temperature.
-
-### Meta-analysis for *SQ*~10pa~
-
-```{r ma-S10pa, cache=TRUE}
-    # data with sampling variance
-    # why do we get V_lnS10aw < 0??? - need to check data
-    data %>% filter(!is.na(V_lnS10pa), lnS10pa != Inf,  lnS10pa != -Inf, V_lnS10pa > 0) -> data6
-
-    m6 <- rma.mv(yi = lnS10pa, V = V_lnS10pa, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data6)
-    summary(m6)
-    # heterogeneity
-    I2(m6)
-```
-
-So, just a note on **directionality**.
-We subtracted r2.2 from r1.1, which essentially means that when the variation in rates of r2.2 are larger than the variance in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance in rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in physiological rates than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm4 <- get_est(m6, "Intercept")
-    exp(estm4$estimate)
-```
-
-**Interpretation**: In other words, on average, the variance in physiological rates of warm acclimated animals, measured at warm temperatures are about `r (exp(estm4$estimate)-1)*100`% higher than the variance in physiological rates at lower acclimation and measurement temperatures (r1.1) over a 10&deg;C change in temperature.
-However, this is just the variance and does not account for the fact that the mean physiological rate also changes, so this is why we also want to know whether this is a *real* change in variance or simply just a result of the change in mean we observed above.
-
-# Meta-analysis for *CVQ*~10~
-
-### Meta-analysis for *CVQ*~10ac~
-
-```{r ma-SQ10ac, cache=TRUE}
-  # data with sampling variance
-  data %>% filter(!is.na(V_lnSQ10ac), lnSQ10ac != Inf,  lnSQ10ac != -Inf,  V_lnSQ10ac > 0) -> data7
-
-  m7 <- rma.mv(yi = lnSQ10ac, V = V_lnSQ10ac, random = list(~ 1 | record_num, ~ 1 | spp_names,  ~ 1 | obs), data = data7)
-  summary(m7)
-  # heterogeneity
-  I2(m7)
-```
-
-So, just a note on **directionality**.
-We subtracted r1.2 from r1.1, which essentially means that when the CV in rates of r1.2 are larger than the CV in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r1.2 has a ***higher*** coefficient of variation than acclimation and measurement at r1.1 when comparing across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r1.2 has a ***lower*** coefficient of variation in rates than acclimation and measurement at r1.1 when comparing across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm7 <- get_est(m7, "Intercept")
-    exp(estm7$estimate)
-```
-
-**Interpretation**: In other words, on average cold acclimated populations have variance in physiological rates at higher temperatures (r1.2) that are about `r (exp(estm7$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r1.1) when comparing across a 10&deg;C change in temperature.
-
-### Meta-analysis for *CVQ*~10aw~
-
-```{r ma-SQ10aw, cache=TRUE}
-  # data with sampling variance
-  # why do we get V_lnS10aw < 0??? - need to check data
-  data %>% filter(!is.na(V_lnSQ10aw), lnSQ10aw != Inf,  lnSQ10aw != -Inf, V_lnSQ10aw > 0) -> data8
-
-  m8 <- rma.mv(yi = lnSQ10aw, V = V_lnSQ10aw, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data8)
-  summary(m8)
-  # heterogeneity
-  I2(m8)
-```
-
-So, just a note on **directionality**.
-We subtracted r2.2 from r2.1, which essentially means that when the variance in rates of r2.2 are larger than the variance in rates of r2.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance than acclimation and measurement at r2.1 when comparing across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in rates than acclimation  and measurement at r2.1 when comparing across a 10&deg;C change.
-
-We can also convert this into a more understandable measure by exp the log ratio. It's not going to be perfectly accurate, but close enough for our purposes.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm8 <- get_est(m8, "Intercept")
-    exp(estm8$estimate)
-```
-
-**Interpretation**: In other words, on average warm acclimated populations have variances in physiological rates at higher temperatures (r2.2) that are about `r (exp(estm8$estimate)-1)*100`% higher than the variance in physiological rates at lower temperatures (r2.1) when comparing across a 10&deg;C change in temperature.
-
-### Meta-analysis for *CVQ*~10pa~
-
-```{r ma-SQ10pa, cache=TRUE}
-    # data with sampling variance
-    # why do we get V_lnS10aw < 0??? - need to check data
-    data %>% filter(!is.na(V_lnSQ10pa), lnSQ10pa != Inf,  lnSQ10pa != -Inf, V_lnSQ10pa > 0) -> data9
-
-    m9 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9)
-    summary(m9)
-    # heterogeneity
-    I2(m9)
-```
-
-So, just a note on **directionality**.
-We subtracted r2.2 from r1.1, which essentially means that when the coefficient of variation in rates of r2.2 are larger than the coefficient of variance in rates of r1.1 the effect size is **positive** and this essentially means that acclimation and measurement at r2.2 has a ***higher*** variance in rate than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.
-In contrast, when the effect size is **negative** this essentially means that acclimation and measurement at r2.2 has a ***lower*** variance in physiological rates than acclimation at temp 1 and measurement at temp 1 (r1.1) across a 10&deg;C change.
-
-```{r, cache=TRUE}
-    # data with sampling variance
-    estm5 <- get_est(m9, "Intercept")
-    exp(estm5$estimate)
-```
-
-**Interpretation**: In other words, on average, the variance, controlling for changes in the mean, of physiological rates of warm acclimated animals, measured at warm temperatures are about `r (1-exp(estm5$estimate))*100`% **lower** than the variance in physiological rates at lower acclimation and measurement temperatures (r1.1) over a 10&deg;C change in temperature.
-
-# Meta-regression for *Q*~10~RR: Habitat
-
-### *Q*~10ac~RR: Habitat
-
-```{r mr-Q10ac, cache=TRUE}
-
-    m1.1 <- rma.mv(yi = lnQ10ac, V = V_lnQ10ac, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data1)
-    summary(m1.1)
-
-    # variance accounted for
-      R2(m1.1)
-
-    # get estimates
-      res1.1 <- get_est(m1.1, mod = "habitat")
-
-    # sample size
-      data1 %>% group_by(habitat) %>% count() -> sample_size
-      left_join(res1.1, sample_size, by =  c("name" = "habitat")) -> res1.1
-
-```
-
-**Interpretation**: Unsurprisingly, all mean physiological rates increase in the cold acclimated treatments.
-Freshwater physiological rates increase by `r (exp(res1.1$estimate[1])-1)*100`% at higher temperatures relative to colder temperatures, marine physiological rates increase by `r (exp(res1.1$estimate[2])-1)*100`% at higher temperatures relative to colder temperatures and terrestrial physiological rates increase by `r (exp(res1.1$estimate[3])-1)*100`% at higher temperatures relative to colder temperatures and significantly more than freshwater systems.
-In other words, for terrestrial species, physiological rates increase much more rapidly compared to marine and freshwater systems.
-
-### *Q*~10aw~RR: Habitat
-
-```{r mr-Q10aw, cache=TRUE}
-
-    m2.1 <- rma.mv(yi = lnQ10aw, V = V_lnQ10aw, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data2)
-    summary(m2.1)
-
-    # variance accounted for
-      R2(m2.1)
-
-    # get estimates and plot
-      res2.1 <- get_est(m2.1, mod = "habitat")
-
-    # sample size
-      data2 %>% group_by(habitat) %>% count() -> sample_size
-      left_join(res2.1, sample_size, by =  c("name" = "habitat")) -> res2.1
-```
-
-**Interpretation**: Unsurprisingly, all mean physiological rates increase in the cold acclimated treatments.
-We largely see the same pattern at the higher acclimation temperature as we observe at the lower acclimation temperature.
-Freshwater physiological rates increase by `r (exp(res2.1$estimate[1])-1)*100`% at higher temperatures relative to colder temperatures, marine physiological rates increase by `r (exp(res2.1$estimate[2])-1)*100`% at higher temperatures relative to colder temperatures and terrestrial physiological rates increase by `r (exp(res2.1$estimate[3])-1)*100`% at higher temperatures relative to colder temperatures and significantly more than freshwater systems.
-Again, for terrestrial species, physiological rates increase much more rapidly compared to marine and freshwater systems.
-
-### *Q*~10pa~RR: Habitat
-
-```{r mr-Q10pa, cache=TRUE}
-
-    m3.1 <- rma.mv(yi = lnQ10pa, V = V_lnQ10pa, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data3)
-    summary(m3.1)
-    # variance accounted for
-    R2(m3.1)
-
-    # get estimates and plot
-    res3.1 <- get_est(m3.1, mod = "habitat")
-    #s_plot(res3.1, title = "Q10pa - different habitats")
-
-    # sample size
-    data3 %>% group_by(habitat) %>% count() -> sample_size
-    left_join(res3.1, sample_size, by =  c("name" = "habitat")) -> res3.1
-```
-
-**Interpretation**: Freshwater physiological rates increase by `r (exp(res3.1$estimate[1])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures, marine physiological rates increase by `r (exp(res3.1$estimate[2])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures.
-Terrestrial physiological rates increase by `r (exp(res3.1$estimate[3])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures.
-Again, for terrestrial species, post acclimation responses differ significantly from freshwater systems, but in all cases physiological rates are increased.
-
-### A forest plot for *Q*~10~RR for 3 habitats
-
-```{r Q-forest}
-
-    # making a data frame for plotting
-      resQ <- bind_rows(res1.1, res2.1, res3.1)
-
-      lab <- c("FreshWater[acute1]", "Marin[acute1]", "Terrestrial[acute1]", "FreshWater[acute2]", "Marin[acute2]", "Terrestrial[acute2]", "FreshWater[acclim]", "Marin[acclim]", "Terrestrial[acclim]")
-      reord <- c(1, 4, 7, 2, 5, 8, 3, 6, 9)
-
-      resQ$lab <-lab
-      resQ$reord <- reord
-
-      resQ %<>% arrange(reord)
-
-    # forest plot
-      f_plot(resQ, title = "lnQ10[acute] vs. lnQ10[acclim] in 3 habitats")
-
-```
-
-# Meta-regression for *SQ*~10~: Habitat
-
-### Meta-regression for *SQ*~10ac~: Habitat
-
-```{r mr-S10ac, cache=TRUE}
-
-    m4.1 <- rma.mv(yi = lnS10ac, V = V_lnS10ac, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data4)
-    summary(m4.1)
-    # variance accounted for
-    R2(m4.1)
-
-    # get estimates and plot
-    res4.1 <- get_est(m4.1, mod = "habitat")
-
-    # sample size
-    data4 %>% group_by(habitat) %>% count() -> sample_size
-    left_join(res4.1, sample_size, by =  c("name" = "habitat")) -> res4.1
-```
-
-**Interpretation**: Freshwater physiological rates increase by `r (exp(res3.1$estimate[1])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures, marine physiological rates increase by `r (exp(res3.1$estimate[2])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures.
-Terrestrial physiological rates increase by `r (exp(res3.1$estimate[3])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures.
-Again, for terrestrial species, post acclimation responses differ significantly from freshwater systems, but in all cases physiological rates are increased.
-
-### Meta-regression for *SQ*~10aw~: Habitat
-
-```{r mr-S10aw, cache=TRUE}
-
-    m5.1 <- rma.mv(yi = lnS10aw, V = V_lnS10aw, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data5)
-    summary(m5.1)
-    # variance accounted for
-    R2(m5.1)
-
-    # get estimates and plot
-    res5.1 <- get_est(m5.1, mod = "habitat")
-    #s_plot(res5.1, title = "S10aw - different habitats")
-
-    # sample size
-    data5 %>% group_by(habitat) %>% count() -> sample_size
-    left_join(res5.1, sample_size, by =  c("name" = "habitat")) -> res5.1
-```
-
-**Interpretation**: For populations acclimated to warm conditions, variance in freshwater physiological rates increase by `r (exp(res5.1$estimate[1])-1)*100`% when measured at higher temperatures relative to animals measured at colder temperatures, marine variance in physiological rates increase by `r (exp(res5.1$estimate[2])-1)*100`% when measured at higher temperatures relative to animals measured at colder temperatures.
-Variance in terrestrial physiological rates increase by `r (exp(res5.1$estimate[3])-1)*100`% when measured at higher temperatures relative to animals measured at colder temperatures.
-There doesn't appear to be any significant difference between organisms occupying major habitat types.
-
-### Meta-regression for *SQ*~10pa~: Habitat
-
-```{r mr-S10pa, cache=TRUE}
-
-    m6.1 <- rma.mv(yi = lnS10pa, V = V_lnS10pa, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data6)
-    summary(m6.1)
-    # variance accounted for
-    R2(m6.1)
-
-    # get estimates and plot
-    res6.1 <- get_est(m6.1, mod = "habitat")
-    #s_plot(res6.1, title = "S10pa - different habitats")
-
-    # sample size
-    data6 %>% group_by(habitat) %>% count() -> sample_size
-    left_join(res6.1, sample_size, by =  c("name" = "habitat")) -> res6.1
-```
-
-**Interpretation**: Variance in freshwater physiological rates increase by `r (exp(res5.1$estimate[1])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures, marine variance in physiological rates increase by `r (exp(res5.1$estimate[2])-1)*100`% when acclimated and measured at higher temperatures relative to animals measured and aclimated at colder temperatures.
-Variance in terrestrial physiological rates increase by `r (exp(res5.1$estimate[3])-1)*100`% when acclimated and measured at higher temperatures relative to animals acclimated and measured at colder temperatures.
-Again, for terrestrial species, post acclimation responses differ significantly from freshwater systems, but in all cases physiological rates are increased.
-
-### A forest plot for *SQ*~10~ for 3 habitats
-
-```{r S-forest}
-
-    # making a data frame for plotting
-      resS <- bind_rows(res4.1, res5.1, res6.1)
-      resS$lab <-lab
-      resS$reord <- reord
-
-      resS %<>% arrange(reord)
-
-    # forest plot
-      f_plot(resS, title = "lnS10[acute] vs. lnS10[acclim] in 3 habitats")
-
-```
-
-# Meta-regression for *CVQ*~10~: Habitat
-
-### *CVQ*~10ac~: Habitat
-
-```{r mr-SQ10ac, cache=TRUE}
-
-    m7.1 <- rma.mv(yi = lnSQ10ac, V = V_lnSQ10ac, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data7)
-    summary(m7.1)
-    # variance accounted for
-    R2(m7.1)
-
-    # get estimates and plot
-    res7.1 <- get_est(m7.1, mod = "habitat")
-    #s_plot(res7.1, title = "SQ10ac - different habitats")
-
-    # sample size
-    data7 %>% group_by(habitat) %>% count() -> sample_size
-    left_join(res7.1, sample_size, by =  c("name" = "habitat")) -> res7.1
-```
-
-### *CVQ*~10aw~: Habitat
-
-```{r mr-SQ10aw, cache=TRUE}
-
-    m8.1 <- rma.mv(yi = lnSQ10aw, V = V_lnSQ10aw, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data8)
-    summary(m8.1)
-    # variance accounted for
-    R2(m8.1)
-
-    # get estimates and plot
-    res8.1 <- get_est(m8.1, mod = "habitat")
-    #s_plot(res8.1, title = "SQ10aw - different habitats")
-
-    # sample size
-    data8 %>% group_by(habitat) %>% count() -> sample_size
-    left_join(res8.1, sample_size, by =  c("name" = "habitat")) -> res8.1
-```
-
-### *CVQ*~10pa~: Habitat
-
-```{r mr-SQ10pa, cache=TRUE}
-
-    m9.1 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, mod = ~ habitat - 1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9)
-    summary(m9.1)
-
-    # m9.2 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, mod = ~ habitat , random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9)
-    # summary(m9.2)
-
-    # variance accounted for
-      R2(m9.1)
-
-    # get estimates and plot
-      res9.1 <- get_est(m9.1, mod = "habitat")
-      #s_plot(res9.1, title = "SQ10pa - different habitats")
-
-    # sample size
-      data %>% group_by(habitat) %>% count() -> sample_size
-      left_join(res9.1, sample_size, by =  c("name" = "habitat")) -> res9.1
-```
-
-### A forest polot for *CVQ*~10~ for 3 habitats
-
-```{r SQ-forest}
-
-    # making a data frame for plotting
-      resSQ <- bind_rows(res7.1, res8.1, res9.1)
-      resSQ$lab <-lab
-      resSQ$reord <- reord
-
-      resSQ %<>% arrange(reord)
-
-    # forest plot
-      f_plot(resSQ, place = "negative", title = "lnSQ10[acute] vs. lnSQ10[acclim] in 3 habitats")
-
-```
-
-# Meta-regression for *Q*~10pa~RR: Traits in habitat
-
-We can now have a look at the relationship between traits and habitat, but first we need to explore how much data we have in the relevant trait categories across the different habitat types.
-Here, we will only look at acclimation responses as this is what makes most sense.
-
-```{r, cache=TRUE}
-    table3 <- table(data3$trait_category, data3$habitat) 
-    kable(table3)
-```
-
-So, we can see that we have quite a lot of traits not present in terrestrial systems. So, for simplicity, lets just exclude for this analysis any trait habitat combination with less than n = 5.
-
-```{r, cache=TRUE}
-    data3.2<- data3 %>% group_by(trait_category, habitat) %>% 
-    filter(n() >= 5) 
-```
-
-OK, so now we are confident that we have removed levels with insufficient sample sizes.
-Now we can model the interaction, we'll simply create a variable for interacting trait and habitat to make the modeling a little easier as then we will have the mean estimate for each of the categories.
-
-```{r, cache=TRUE}
-    #Just to keep things easier for modelling just create a variable interacting trait and habitat
-    data3.2$trait_habitat <- data3.2 %$% paste0(habitat, "_", trait_category)
-
-    m10.1 <- rma.mv(yi = lnQ10pa, V = V_lnQ10pa, mod = ~ trait_habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data3.2)
-    summary(m10.1)
-
-    # variance accounted for
-      R2(m10.1)
-
-    # get estimates and plot
-      res10.1 <- get_est(m10.1, mod = "trait_habitat")
-
-    # sample size
-      data3.2 %>% group_by(trait_habitat) %>% count() -> sample_size
-      left_join(res10.1, sample_size, by =  c("name" = "trait_habitat")) -> res10.1
-```
-
-```{r, cache = TRUE}
-    forest_plot <- function(est_table, col=colour, ylabel = "", xlabel = "lnQ10RR", xlimits = c(-0.5, 1.6), n_pos = -0.25){
-      plot(1:nrow(est_table) ~ estimate, data = est_table, xlim = xlimits, ylab =ylabel, xlab = xlabel, col = colour, pch = 16, cex = 1.8, yaxt='n')
-      arrows(x0= est_table$estimate, y0 = 1:nrow(est_table), y1 = 1:nrow(est_table), x1 = est_table$upperCL, length = 0, angle =90, col = colour)
-      arrows(x0= est_table$estimate, y0 = 1:nrow(est_table), y1 = 1:nrow(est_table), x1 = est_table$lowerCL, length = 0, angle =90, col = colour)
-      abline(v = 0, lty = 2)
-      text(paste0("n = ", est_table$n), y = 1:nrow(est_table), x = n_pos, pos=2)
-      axis(side = 2, at = 1:nrow(est_table), labels = est_table$name, las = 1)
-    }
-
-    # making a data frame for plotting
-    # forest plot
-      colour <- c(rep("orange", 10), rep("blue", 11), rep("forestgreen", 4), rep("blue", 11))
-
-      par(mar = c(4,10,1,1))
-      forest_plot(est_table=res10.1)
-```
-
-Here, we can basically see that the mean actually is affected pretty much across the board, but we see a more nuanced effect.
-For example, in freshwater systems basically acclimation changes the mean response for all traits, but we see that in marine systems performance based indices's are unaffected (sprint, endurance), whereas metabolic processes are.
-In contrast, we see performance and metabolism affected in terrestrial systems but this doesn't seem to be related to metabolic enzymes.
-
-# Meta-regression for *SQ*~10pa~: Traits in habitat
-
-We can now look at the variance change across each of the categories. First, set the data up as above.
-
-```{r, cache=TRUE}
-    data6.1 <- data6 %>% group_by(trait_category, habitat) %>% 
-    filter(n() >= 5) 
-    table6 <- table(data6.1$trait_category, data6.1$habitat) 
-    kable(table6)
-```
-
-OK, so now that this is set up, lets model the variance
-
-```{r, cache=TRUE}
-    #Just to keep things easier for modelling just create a variable interacting trait and habitat
-    data6.1$trait_habitat <- data6.1 %$% paste0(habitat, "_", trait_category)
-
-    m11.1 <- rma.mv(yi = lnS10pa, V = V_lnS10pa, mod = ~ trait_habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data6.1)
-    summary(m11.1)
-
-    # variance accounted for
-      R2(m11.1)
-
-    # get estimates and plot
-      res11.1 <- get_est(m11.1, mod = "trait_habitat")
-
-    # sample size
-      data6.1 %>% group_by(trait_habitat) %>% count() -> sample_size
-      left_join(res11.1, sample_size, by =  c("name" = "trait_habitat")) -> res11.1
-```
-
-```{r, cache = TRUE}
-      colour <- c(rep("orange", 10), rep("blue", 11), rep("forestgreen", 4), rep("blue", 11))
-      par(mar = c(4,10,1,1))
-      forest_plot(est_table=res11.1, xlimits = c(-1.5, 1.4), n_pos = -1.1, xlab = "lnSQ_10")
-```
-
-# Meta-regression for *CVQ*~10pa~: Traits in habitat
-
-Of course, we may see changes in variance simply because we see a shit in the mean, which is potentially vary true because of the fact that we have strong mean-variance relationships in these data.
-So, better here to focus on changes in variance independent of the mean using *CVQ*~10pa~.
-
-```{r, cache=TRUE}
-    data9.1 <- data9 %>% group_by(trait_category, habitat) %>% 
-    filter(n() >= 5) 
-    table9 <- table(data9.1$trait_category, data9.1$habitat) 
-    kable(table9)
-```
-
-OK, so now that this is set up, lets model the coefficient of variance.
-
-```{r, cache=TRUE}
-    #Just to keep things easier for modelling just create a variable interacting trait and habitat
-    data9.1$trait_habitat <- data9.1 %$% paste0(habitat, "_", trait_category)
-
-    m12.1 <- rma.mv(yi = lnSQ10pa, V = V_lnSQ10pa, mod = ~ trait_habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data9.1)
-    summary(m12.1)
-
-    # variance accounted for
-      R2(m12.1)
-
-    # get estimates and plot
-      res12.1 <- get_est(m12.1, mod = "trait_habitat")
-
-    # sample size
-      data9.1 %>% group_by(trait_habitat) %>% count() -> sample_size
-      left_join(res12.1, sample_size, by =  c("name" = "trait_habitat")) -> res12.1
-```
-
-```{r, cache = TRUE}
-      colour <- c(rep("orange", 10), rep("blue", 11), rep("forestgreen", 4), rep("blue", 11))
-      par(mar = c(4,10,1,1))
-      forest_plot(est_table=res12.1, xlimits = c(-1.8, 0.8), n_pos = -1.5, xlab = "lnCVQ_10")
-```
-
-# Log response Ratio of the Acclimation treatments
-
-As discussed above, these analyses seem not to get at exactly what we are after.
-We want to know how the Q~10~ changes as a function of acclimation, which essentially means comparing and contrasting Q~10aw~RR with Q~10pa~RR.
-Or, what appears to be an equivalent and more simple formulation, the log response ratio of the acclimation treatments at the same temperature.
-Now, whether we compare the cold versus the hot acclimation treatment direction or *vice versa* will likely be important.
-So, lets, for now just have a look at the habitat and trait models in the context of the log response ratio.
-Here is the equations that we will use:
-
-$$
-  \ln{RR} = {\ln \left( \frac{R_{1.2}}{R_{2.2}} \right)}
-$$
-
-and the the sampling variance for this is:
-
-$$
-  V_{\ln{RR}} = {\left( \frac{SD^2_{R_{1.2}}}{n_{R_{1.2}}M^2_{R_{1.2}}} \right)} + {\left( \frac{SD^2_{R_{2.2}} }{n_{R_{2.2}}M^2_{R_{2.2}}} \right)}
-$$
-
-First, we need a function for generating this new effect. I am going to just simply focus on the mean physiological rates for now given time constraints, but these will apply for variance too:
-
-```{r}
-      lnRR <- function(data, r1_2, r2_2, se1_2, se2_2, n1_2, n2_2){
-
-            sd1_2 <- se1_2*sqrt(n1_2)
-            sd2_2 <- se2_2*sqrt(n2_2)
-
-           # log response ratio
-           lnRR <- log(r1_2) - log(r2_2)
-
-           # Sampling variance log RR
-          VlnRR <- ( (sd1_2^2) / (n1_2*(r1_2^2)) ) + ( (sd2_2^2) / (n2_2*(r2_2^2)) )
-
-          # Create the data table and add back into the data.
-           lnRR <- tibble(lnRRac = lnRR, V_lnRRac = VlnRR)
-
-           data <- bind_cols(data, lnRR)
-
-        return(data)
-      }
-```
-
-We can then add in this new effect size to the data.
-
-```{r}
-# getting effect sizes
-    data %<>% lnRR(r1_2= data$r1.2, r2_2=data$r2.2, se1_2=data$r1.2_se, se2_2=data$r2.2_se, n1_2=data$r1.2_N, n2_2=data$r2.2_N)
-
-```
-
-Right, so now that we have all this we can do a meta-analysis of the **acclimation effects** on physiological rates and variance in physiological rates.
-
-```{r}
-  data %>% filter(!is.na(V_lnRRac), V_lnRRac > 0) -> data_acclim
-
-  m_acclim <- rma.mv(yi = lnRRac, V = V_lnRRac, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data_acclim)
-  summary(m_acclim)
-
-  est_acclim <- get_est(m_acclim)
-
-```
-
-**Interpretation**: The above meta-analytic model suggests that across all organisms, traits and habitat types physiological rates of cold acclimated animals measured at higher temperatures are only `r (exp(est_acclim$estimate)-1)*100`% higher than animals acclimated at higher temperatures and measured at those temperatures.
-In other words, it doesn't look like acclimation, more generally, helps reduce the difference in physiological rates, but obviously there is a huge amount of variability among taxa and within these data that need to be explored.
-
-We can explore this with respect to the original question of comparing Q10 acclimation across the major habitat types.
-
-```{r}
-
-  m_acclim_habitat <- rma.mv(yi = lnRRac, V = V_lnRRac, mod = ~ habitat-1, random = list(~ 1 | record_num, ~ 1 | spp_names, ~ 1 | obs), data = data_acclim)
-  summary(m_acclim_habitat)
-
-  est_acclim_habitat <- get_est(m_acclim_habitat, "habitat")
-
-```
-
-**Interpretation**: We can estimate the acclimation response at higher temperatures (note we lose power as we ignore the lower one, but for now this is ok) for organisms within each of the habitat types (freshwater, marine and terrestrial).
-So, cold acclimated freshwater species that are measured at higher temperatures have a `r (exp(est_acclim_habitat$estimate[1])-1)*100`% **higher** rate in physiological responses compared to warm acclimated freshwater species measured at the same *higher* temperature.
-Cold acclimated marine species that are measured at higher temperatures have a `r (exp(est_acclim_habitat$estimate[2])-1)*100`% **higher** rate in physiological responses compared to warm acclimated freshwater species measured at the same *higher* temperature.
-Lastly, cold acclimated terrestrial species have a `r (1-exp(est_acclim_habitat$estimate[3]))*100`% very slight, non-significant decrease in physiological rates at higher temperatures compared to warm acclimated terrestrial species measured at those same temperatures.
-
-# Information for this session: R
-
-```{r session, include = TRUE, echo = FALSE}
-    sessionInfo()
-```
-
-# References
+version https://git-lfs.github.com/spec/v1
+oid sha256:efc3bdbca77108986e7d2e1d6d19eb773ca7a537388148fc6ab073efffb76aff
+size 48426

### 2024-01-07 R/1_data_process.R

@@ -1,94 +1,3 @@
-##################################
-# Load Data & Manipulate
-##################################
-
-data_wide <- read.csv("./data/CombinedData_wide.csv", stringsAsFactors = FALSE)
-data_wide$lat <- as.numeric(data_wide$lat)
-new_papers <- data_wide[-grep("_o", data_wide$record_num),]
-old_papers <- data_wide[grep("_o", data_wide$record_num),]
-
-# Add full species to data
-data_wide <- data_wide %>%
-  mutate(species_full = paste0(genus, " ",species))
-
-# habitat
-spp_habitat <- data_wide %>%
-  group_by(habitat) %>%
-  summarise(spp_n = length(unique(species_full)))
-
-# Note that some species need to be replaced
-data_wide <- data_wide %>%
-  mutate(species_full = ifelse(species_full == "Chinemys reevesii", 
-                               "Mauremys reevesii", species_full)) %>%
-  mutate(species_full = ifelse(species_full == "Enithares sp", 
-                               "Enithares ciliata", species_full))  %>%
-  mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>% # Fix a few errors in habitat classificaton
-  mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat)) 
-
-# Convert se to SD so it can be used for effect sizes. Drop out the SE columns as these are no longer needed
-data_wide <- data_wide %>%
-  mutate(r1.1_sd = se_to_sd(r1.1_se, r1.1_N),
-         r1.2_sd = se_to_sd(r1.2_se, r1.2_N),
-         r2.1_sd = se_to_sd(r2.1_se, r2.1_N),
-         r2.2_sd = se_to_sd(r2.2_se, r2.2_N)) %>%
-  dplyr::select(-c(r1.1_se, r1.2_se, r2.1_se, r2.2_se,
-                   r1.1_CV, r1.2_CV, r2.1_CV, r2.2_CV, 
-                   r1.1_logCV, r1.2_logCV, r2.1_logCV, r2.2_logCV))
-##################################
-## Calculate effect sizes
-##################################
-# Calculate Q10 effect sizes and sampling variances; filter out non-finate values and clean up dataframe a bit
-
[…]

### 2024-01-07 R/2_climate_data.R

@@ -1,489 +1,3 @@
-
-rm(list=ls())
-library(tidyr)
-library(ecmwfr)
-library(terra)
-library(ncdf4)
-library(maps)
-
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-# SURVEY LOCATIONS
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-geo_data = read.csv("Data/Species_LatLong_plusHabitat.csv")  # ./data/climate_data/Species_LatLong_plusHabitat.csv
-# Remove missing lat and long
-geo_data = geo_data %>% dplyr::filter(!is.na(lat) & !is.na(long))
-
-
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-# SETUP API
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-
-### Set keyring and user details to connect to the Climate Data Store account.
-### Note: the details below are illustrative and will not work. You need to 
-### register for CDS account and enter your own details.
-wf_set_key(user    = "89303", 
-           key     = "e661d57a-c4f0-4e9e-9da4-477fa0a9537e", 
-           service = 'cds')
-
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-# HISTORIC CLIMATIC DATA
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-
-for(i in 1:nrow(geo_data) ){
-  
-  filelist = unlist(lapply(list.files("./Data/ERA5_LAND/",pattern="point"),FUN=function(x) strsplit(x,"point")[[1]][2]))
-  filelist = as.numeric(gsub("\\.nc","",filelist))
-  
-  if( !i %in% filelist ){
-    
-    Habitat= geo_data$habitat[i] %in% c("t","f")
-    
-    if(Habitat){
-      # If the species is Terrestrial or Freshwater we refer our request to the ERA5-LAND dataset
-      
-      # Maintain a tightly focused spatial extent
-      Xlim   = round(round(geo_data$long[i],2) + c(-0.01,0.01),2)
-      Ylim   = round(round(geo_data$lat[i],2) + c(-0.01,0.01),2)
-      
-      # ERA5-Land monthly averaged data from 1950 to present
[…]

### 2024-01-07 R/exploratory/explore_climate_data.R

@@ -1,321 +1,3 @@
-###################################################################################
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-#                       GLOBAL HISTORIC TEMPERATURE
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-###################################################################################
-
-rm(list=ls())
-pardefault = par()
-
-coords = read.csv("coord.csv")
-
-plot(coords[,2:3], xlim=c(-180,180), ylim=c(-70,70))
-abline(h=0, lty=2)
-
-# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
-
-
-library(ncdf4)
-# Open the NetCDF data set, and print some basic information.
-SSTdir  = "gis_data/"
-ncname  = "HadISST_sst"
-ncfname = paste0(SSTdir,ncname, ".nc", sep = "")
-dname   = "sst" 
-
-# Open a NetCDF file
-HAD.sst = nc_open(ncfname)
-print(HAD.sst)
-
-# Get the longtiudes and latitudes as before, using now the ncvar_get() function in ncdf4.
-lon     = ncvar_get(HAD.sst, "longitude")
-nlon    = dim(lon)
-head(lon)
-
-lat     = ncvar_get(HAD.sst, "latitude", verbose = F)
-nlat    = dim(lat)
-head(lat)
-
-# Get the time variable and its attributes using the ncvar_get() and ncatt_get() functions, and also get the number of times using the dim() function.
-t       = ncvar_get(HAD.sst, "time")
-tunits  = ncatt_get(HAD.sst, "time", "units")
-nt      = dim(t)
-
-# Get the variable and its attributes, and verify the size of the array.
-sst.array = ncvar_get(HAD.sst, dname)
-dlname    = ncatt_get(HAD.sst, dname, "long_name")
-dunits    = ncatt_get(HAD.sst, dname, "units")
-fillvalue = ncatt_get(HAD.sst, dname, "_FillValue")
-dim(sst.array)
-
-# Get the global attributes.
-title       = ncatt_get(HAD.sst, 0, "Title")
-description = ncatt_get(HAD.sst, 0, "description")
-institution = ncatt_get(HAD.sst, 0, "institution")
-datasource  = ncatt_get(HAD.sst, 0, "source")
[…]

### 2024-01-07 R/exploratory/shiny_explore.R

@@ -1,2 +1,3 @@
-
-rmarkdown::run("./R/analysis.Rmd")
+version https://git-lfs.github.com/spec/v1
+oid sha256:03a5160a06b806cbe8450feadf7863bc0424b3a993558751ce55ed265d57d762
+size 36

### 2024-01-07 R/tidy_wide2long_v2.R

@@ -1,143 +1,3 @@
-setwd("~/Dropbox/q10_meta/")
-
-rm(list = ls())
-
-library(googlesheets)
-library(tidyverse)
-library(magrittr)
-
-source("R/functions.R")
-
-gs <- gs_title("q10_newdata")
-data <- as_tibble(gs_read(ss = gs))
-
-head(data)
-
-
-#Creating ES
-
-data$obs <- as.factor(1:dim(data)[1])
-
-# getting effect sizes
-data %<>% Q10S10(temp_1, temp_2, r1.1, r1.2, r2.1, r2.2, r1.1_se, r1.2_se, r2.1_se, 
-                 r2.2_se, r1.1_N, r1.2_N, r2.1_N, r2.2_N)
-
-# adding species names
-data %<>% mutate(spp_names = str_c(genus, species, sep = "_"))
-
-data
-
-#Other raw data
-names(data)
-data[,1:45]
-
-#ES
-es <- c("RR", "SQ10", "CV")
-
-grep(es[1],colnames(data), perl = T)
-
-grep(es[2],colnames(data))
-
-grep(es[3],colnames(data))
-
-#treats
-
-treats <- c("ac", "aw", "pa")
-
-grep(treats[1],colnames(data))
-
-grep(treats[2],colnames(data))
-
-grep(treats[3],colnames(data))
-
-#Q10RR and Change Q10RR colnames
-Q10RRdat <- select(data, obs, grep(es[1],colnames(data), perl = T))
-
-Q10RRdat_ac <- select(Q10RRdat, obs, grep(treats[1], colnames(Q10RRdat)))
-colnames(Q10RRdat_ac) <- c("obs", "ES", "V_ES")
-Q10RRdat_ac$treat <- rep("ac", nrow(Q10RRdat_ac))
-
-
-Q10RRdat_aw <- select(Q10RRdat,  obs, grep(treats[2], colnames(Q10RRdat)))
-colnames(Q10RRdat_aw) <- c("obs", "ES", "V_ES")
-Q10RRdat_aw$treat <- rep("aw", nrow(Q10RRdat_aw))
-
-Q10RRdat_pa <- select(Q10RRdat,  obs, grep(treats[3], colnames(Q10RRdat)))
-colnames(Q10RRdat_pa) <- c("obs", "ES", "V_ES")
-Q10RRdat_pa$treat <- rep("pa", nrow(Q10RRdat_pa))
-
-
[…]

### 2024-01-08 R/functions.R
function to deal with NULL for plotting

@@ -424,7 +424,13 @@ p_value <- function(x){
 #' @param exclude The moderator level to exclude (optional)
 #' 
 manual_extract  <- function(model, mod = "trait_category", group = "record_num", exclude = NULL){
-  orchaRd::mod_results(model, mod = mod, group = group)$data  %>% group_by(moderator) %>% summarise(k = n(), sdy = length(unique(stdy)))  %>% filter(!moderator == exclude)
+  
+  if(is.null(exclude)){
+    orchaRd::mod_results(model, mod = mod, group = group)$data  %>% group_by(moderator) %>% summarise(k = n(), sdy = length(unique(stdy)))
+  } else{
+    orchaRd::mod_results(model, mod = mod, group = group)$data  %>% group_by(moderator) %>% summarise(k = n(), sdy = length(unique(stdy)))  %>% filter(!moderator == exclude)
+  }
+  
 }
 
 #' @title text

### 2024-01-08 ms.qmd
Clean up fig 1 a bit and increase width of CI

@@
 col <- c("#0871B9", "#F3B40D", "#1BB908")
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 5) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+  k_lnrr <- manual_extract(model1.2, mod = "habitat", group = "record_num", exclude = NULL)
+
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 8, branch.size = 2) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
          label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0, size = 6) + 
-annotate("text", x = 1.01, y = 4.60, 
+annotate("text", x = 1.01, y = 4.0, 
          label =paste0(round(mean(change_f), 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-  geom_segment(aes(x = 0.92, y = 5.6, xend = 1.07, yend = 5.6), 
+  geom_segment(aes(x = 0.92, y = 3.9, xend = 1.07, yend = 3.9), 
                             arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
   annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0, size = 6) + 
-
   annotate("text", x = 2, y = 2.10, 
          label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-annotate("text", x = 2.01, y = 4.60, 
+annotate("text", x = 2.01, y = 4.0, 
          label =paste0(round(mean(change_m), 2), "%"), hjust = 0, size = 6) +
-  geom_segment(aes(x = 1.92, y = 5.6, xend = 2.07, yend = 5.6), 
+  geom_segment(aes(x = 1.92, y = 3.9, xend = 2.07, yend = 3.9), 
                             arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
   annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0, size = 6) +
-
   annotate("text", x = 3, y = 2.10, 
          label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-annotate("text", x = 3.01, y = 4.60, 
+annotate("text", x = 3.01, y = 4.0, 
          label =paste0(round(mean(change_t), 2), "%"), hjust = 0, size = 6) +
-  geom_segment(aes(x = 2.92, y = 5.6, xend = 3.07, yend = 5.6), 
+  geom_segment(aes(x = 2.92, y = 3.9, xend = 3.07, yend = 3.9), 
                             arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
-  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6) + scale_fill_manual(values = c(col))
+  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-0.8, 5.05) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = k_lnrr$moderator, y = 5)
 
@@
 
-   p1.2.2 <- p1.2 + ylim(c(0,1)) + theme(legend.position = 'none')
-
-  ggsave(p1.2, filename = "./output/figures/fig1.pdf", width = 11.5, height = 8)
-  ggsave(p1.2.2, filename = "./output/figures/fig1.1.pdf")
+  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 12, height = 9.6)
 
@@
 This is not true of aquatic systems.
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 5) +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
+
+  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
+
+  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 8, branch.size = 2) +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -1.8, 
            label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 2), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -5, 
+  annotate("text", x = 1.15, y = -1.5, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = 1.15, y = 1, 
            label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
-  annotate("text", x = 2.3, y = -5.2, 
+  annotate("text", x = 2.3, y = -1.8, 
            label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 2), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -5, 
-           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
+  annotate("text", x = 2.15, y = -1.5, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = 2.15, y = 1, 
+           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.4, y = -1.8, 
            label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 2), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 3.15, y = -5, 
+  annotate("text", x = 3.25, y = 1, 
            label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
+    annotate("text", x = 3.25, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 1.8) + 
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = k_cvr$moderator, y = 2.4)
 
@@
           axis.text = element_text(size = 15))
-     p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
-     ggsave(p2, filename = "./output/figures/fig2.pdf", width = 11.5, height = 8)
-    ggsave(p2.2, filename = "./output/figures/fig2.2.pdf")
+
+     ggsave(p2, filename = "./output/figures/fig2.png", width = 10, height = 9.5)
 

### 2024-01-08 ms.qmd
Just fixing figures so that they are using negative and ditching arrows. Need to also fix up the posteriors so they are not using absolute. We can take absolute later

@@
 # % change in acclimation on log scale
-  change_f <- abs(f_acclim - f_acute)*100; quantile(change_f, c(0.025, 0.975))
-  change_m <- abs(m_acclim - m_acute)*100; quantile(change_m, c(0.025, 0.975))
-  change_t <- abs(t_acclim - t_acute)*100; quantile(change_t, c(0.025, 0.975))
+  change_f <- (f_acclim - f_acute)*100; quantile(change_f, c(0.025, 0.975))
+  change_m <- (m_acclim - m_acute)*100; quantile(change_m, c(0.025, 0.975))
+  change_t <- (t_acclim - t_acute)*100; quantile(change_t, c(0.025, 0.975))
   avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
@@
 Overall, $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r mean(abs(change_f))`% (95% CI: `r quantile(abs(change_f), c(0.025, 0.975))[1]` to `r quantile(abs(change_f), c(0.025, 0.975))[2]`) in freshwater and `r mean(abs(change_m))`% (95% CI: `r quantile(mean(abs(change_m), c(0.025, 0.975))[1]` to `r quantile(mean(abs(change_m), c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(abs(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(abs(change_t), c(0.025, 0.975))[1]` to `r quantile(abs(change_t), c(0.025, 0.975))[2]`, [@fig-1]B).
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
@@
          label =paste0(round(mean(change_f), 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-  geom_segment(aes(x = 0.92, y = 3.9, xend = 1.07, yend = 3.9), 
-                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
   annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0, size = 6) + 
@@
          label =paste0(round(mean(change_m), 2), "%"), hjust = 0, size = 6) +
-  geom_segment(aes(x = 1.92, y = 3.9, xend = 2.07, yend = 3.9), 
-                            arrow = arrow(angle = 45, ends = "first", length = unit(0.01, "npc"))) +
   annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0, size = 6) +
@@
          label =paste0(round(mean(change_t), 2), "%"), hjust = 0, size = 6) +
-  geom_segment(aes(x = 2.92, y = 3.9, xend = 3.07, yend = 3.9), 
-                            arrow = arrow(angle = 45, ends = "last", length = unit(0.01, "npc"))) +
   annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-0.8, 5.05) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = k_lnrr$moderator, y = 5)
@@
            label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = 3.25, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 1.8) + 
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = k_cvr$moderator, y = 2.4)
+    annotate("text", x = 3.25, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 2) + 
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(1.15, 2.15, 3.25), y = 1.8)
 
   p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
-          axis.text = element_text(size = 15))
+                                       axis.text = element_text(size = 15),
+                                       legend.title = element_text(size = 15),
+                                        legend.text = element_text(size = 15),)
 
      ggsave(p2, filename = "./output/figures/fig2.png", width = 10, height = 9.5)
-
-  #(phylo) / (p1.2 / p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
 

### 2024-01-08 ms.qmd
Correcting a few coding issues. Needs checking on % differences. May need to have a look at the discusison some more on this

@@
 
-# % change in acclimation on log scale
-  change_f <- (f_acclim - f_acute)*100; quantile(change_f, c(0.025, 0.975))
-  change_m <- (m_acclim - m_acute)*100; quantile(change_m, c(0.025, 0.975))
-  change_t <- (t_acclim - t_acute)*100; quantile(change_t, c(0.025, 0.975))
+# % change in mean acclimation relative to acute
+  change_f <- (exp(f_acclim - f_acute)-1)*100; quantile(change_f, c(0.025, 0.975)) 
+  change_m <- (exp(m_acclim - m_acute)-1)*100; quantile(change_m, c(0.025, 0.975))
+  change_t <- (exp(t_acclim - t_acute)-1)*100; quantile(change_t, c(0.025, 0.975))
   avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
-
+  (f_acclim - f_acute) / mean(c(f_acclim, f_acute))
 # % change on Q10 scale
@@
 
-Overall, $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Overall, $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ differed by only `r mean(abs(avg_change))`% across all habitats (95%CI: `r quantile(abs(avg_change), c(0.025, 0.975))[1]` to `r quantile(abs(avg_change), c(0.025, 0.975))[2]`%).
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r mean(abs(change_f))`% (95% CI: `r quantile(abs(change_f), c(0.025, 0.975))[1]` to `r quantile(abs(change_f), c(0.025, 0.975))[2]`) in freshwater and `r mean(abs(change_m))`% (95% CI: `r quantile(mean(abs(change_m), c(0.025, 0.975))[1]` to `r quantile(mean(abs(change_m), c(0.025, 0.975))[2]`) in marine environments.

### 2024-01-09 ms.qmd
Rerender with updated changes. Most small stuff  finished but just need to work on figures a bit more

--- 2024-01-08 ms.qmd
@@
 
-# % change in acclimation on log scale
-  change_f <- (f_acclim - f_acute)*100; quantile(change_f, c(0.025, 0.975))
-  change_m <- (m_acclim - m_acute)*100; quantile(change_m, c(0.025, 0.975))
-  change_t <- (t_acclim - t_acute)*100; quantile(change_t, c(0.025, 0.975))
+# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
+  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
+  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
+  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
+  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
   avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
-
-# % change on Q10 scale
-  p_change_f_q10 <- exp(f_acclim - f_acute)-1; quantile(p_change_f_q10, c(0.025, 0.975))
-  p_change_m_q10 <- exp(m_acclim - m_acute)-1; quantile(p_change_m_q10, c(0.025, 0.975))
-  p_change_t_q10 <- exp(t_acclim - t_acute)-1; quantile(p_change_t_q10, c(0.025, 0.975))
 
@@
 Overall, $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r mean(abs(change_f))`% (95% CI: `r quantile(abs(change_f), c(0.025, 0.975))[1]` to `r quantile(abs(change_f), c(0.025, 0.975))[2]`) in freshwater and `r mean(abs(change_m))`% (95% CI: `r quantile(mean(abs(change_m), c(0.025, 0.975))[1]` to `r quantile(mean(abs(change_m), c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(abs(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(abs(change_t), c(0.025, 0.975))[1]` to `r quantile(abs(change_t), c(0.025, 0.975))[2]`, [@fig-1]B).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
@@
 
-Different trait categories showed different accclimation responses across habitat types, however, they mirrored patterns seen overall (@fig-2).
+Different trait categories showed different accclimation responses across habitat types, however, they mirrored patterns seen overall (see Supplement; @fig-2).
 Acclimation capacity also did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-3) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
@@
 
-  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 12, height = 9.6)
+  pdf("./output/figures/fig1.pdf", useDingbats=FALSE, width = 12, height = 9.6)
+    p1.2
+  dev.off()
+  ggsave(p1.2, filename = "./output/figures/fig1.pdf", width = 12, height = 9.6, device = "pdf")
 
@@
                                        legend.title = element_text(size = 15),
-                                        legend.text = element_text(size = 15),)
+                                        legend.text = element_text(size = 15))
 
@@
 
-```{r, fig-2}
-#| label: fig-2
-#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+```{r, fig-3}
+#| label: fig-3
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
-#| echo: false
-k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
-
-ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none",
-                              axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
-                            annotate("text", label= paste0(k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4)
-#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
-#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")
-#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 8.5, width = 26)
-
-img_fig2 <- magick::image_read("./output/figures/fig2_trait.png")
-img_fig2
-```
-
-```{r, fig-3}
-#| label: fig-3
-#| fig-cap: "Predicted mean acclimation and acute $lnRR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
 
@@
 
-Variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a much smaller reduction in physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
-
-The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between study and trait differences (See supplemental @fig-s3).
+Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increase by 10$^\circ$C.
+In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
+
+The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between study and trait differences (see Supplement;  @fig-s3).
 Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
@@
 #| label: fig-cvrlh
-#| fig-cap: "Predicted mean $lnCVR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
+#| fig-cap: "Estimated mean $lnCVR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 
-# % change in acclimation on log scale
-  change_f_wild <- abs(f_acclim_wild - f_acute_wild)*100; quantile(change_f_wild, c(0.025, 0.975))
-  change_m_wild <- abs(m_acclim_wild - m_acute_wild)*100; quantile(change_m_wild, c(0.025, 0.975))
-  change_t_wild <- abs(t_acclim_wild - t_acute_wild)*100; quantile(change_t_wild, c(0.025, 0.975))
-
-# % change on Q10 scale
-  p_change_f_q10_wild <- (exp(f_acclim_wild - f_acute_wild)-1)*100; quantile(p_change_f_q10_wild, c(0.025, 0.975))
-  p_change_m_q10_wild <- (exp(m_acclim_wild - m_acute_wild)-1)*100; quantile(p_change_m_q10_wild, c(0.025, 0.975))
-  p_change_t_q10_wild <- (exp(t_acclim_wild - t_acute_wild)-1)*100; quantile(p_change_t_q10_wild, c(0.025, 0.975))
+# % change in acclimation on log scale; relative to the acute measurements
+  change_f_wild <- ((f_acclim_wild - f_acute_wild) / f_acute_wild) *100; quantile(change_f_wild, c(0.025, 0.975))
+  change_m_wild <- ((m_acclim_wild - m_acute_wild) / m_acute_wild) *100; quantile(change_m_wild, c(0.025, 0.975))
+  change_t_wild <- ((t_acclim_wild - t_acute_wild) / t_acute_wild) *100; quantile(change_t_wild, c(0.025, 0.975))
 
@@
 # % change in acclimation on log scale
-  change_f_wild_cvr <- abs(f_acclim_wild_cvr - f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
-  change_m_wild_cvr <- abs(m_acclim_wild_cvr - m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
-  change_t_wild_cvr <- abs(t_acclim_wild_cvr - t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
-
-# % change on Q10 scale
-  p_change_f_q10_wild_cvr <- (exp(f_acclim_wild_cvr - f_acute_wild_cvr)-1)*100; quantile(p_change_f_q10_wild_cvr, c(0.025, 0.975))
-  p_change_m_q10_wild_cvr <- (exp(m_acclim_wild_cvr - m_acute_wild_cvr)-1)*100; quantile(p_change_m_q10_wild_cvr, c(0.025, 0.975))
-  p_change_t_q10_wild_cvr <- (exp(t_acclim_wild_cvr - t_acute_wild_cvr)-1)*100; quantile(p_change_t_q10_wild_cvr, c(0.025, 0.975))
+  change_f_wild_cvr <- ((f_acclim_wild_cvr - f_acute_wild_cvr) / f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
+  change_m_wild_cvr <- ((m_acclim_wild_cvr - m_acute_wild_cvr) /m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
+  change_t_wild_cvr <- ((t_acclim_wild_cvr - t_acute_wild_cvr)/t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
 
@@
 #| fig-align: center
-#| fig-cap: "Predcited mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations by habitat.
+#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\beta$) and p-value are shown for each habitat along with the 95% CI and $p_{MCMC} value."
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value are shown for each habitat."
 
@@
 #| fig-align: center
-#| fig-cap: "Predcited mean (thick black line) $lnCVR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations by habitat.
+#| fig-cap: "Predicted mean (thick black line) $lnCVR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\beta$) and p-value are shown for each habitat along with the 95% CI and $p_{MCMC} value."
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value are shown for each habitat."
 
@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
-Here we show that variance in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
-Decreases in variance of physiological rates is larger than the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 9% acclimation vs.
+Here, we show that the relative variance in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
+Decreases in the relative variance of physiological rates are larger than the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 9% acclimation vs.
 15% reduction in variance; *terrestrial*: no acclimation vs 28% reduction in variance).
-Such effects are expected to result in a decrease in the variability in physiologcial rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
+Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
 Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention.
@@
 While there is substantial variation in effects across species, we show that plastic adjustments to physiological rates are, on average, rather small compared to the general reduction variance in physiological rates.
-Variance reductions are particularly pronouced for terrestrial ectotherms and there were no major differences between life-stages.
-While it is unclear the extent to which such changes in variance are heritable, we expect changes in variance of this magnitude to have an impact on the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
+Variance reductions are particularly pronounced  for terrestrial ectotherms and there were no major differences between life-stages.
+While it is unclear the extent to which such changes in variance are heritable, we expect changes in variance of this magnitude to impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
 Both are predicted to impact the capacity of populations to evolve under climate change [@hoffmann2011climate; @urban2023and].
 
-One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats.
+One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms were, on average, acclimated for significantly less time than ectotherms from aquatic habitats.
 However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
 Faster rates of acclimation would therefore result in the opposite patterns to those that we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
-The weak acclimation responses of terrestrial ectotherms suggests that evolving plasticity in physiological rates may be hard, possibly because terrestrial ectotherms are more likely to experience more variable and unpredictable thermal environments compared to aquatic ectotherms (see below).
+The weak acclimation responses of terrestrial ectotherms suggest that evolving plasticity  in physiological rates may be hard, possibly because terrestrial ectotherms are more likely to experience more variable and unpredictable thermal environments than aquatic ectotherms (see below).
 Reductions in physiological rate variance for terrestrial ectotherms may be because of selective mortality at higher temperatures reducing intrapopulation variability or populations being pushed closer to their thermal maxima (or a combination of both).
-Disentangling these hypotheses will require empirical studies to connect measures of survival at different temperatures with thermal physiology across individuals (e.g., $CT_{max}$).
+Disentangling these hypotheses will require empirical studies to connect survival measures at different temperatures with thermal physiology across individuals (e.g., $CT_{max}$).
 
@@
 Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogenetiy in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely evolve in terrestrial environments, however, we did not find evidence to this effect.
+Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
+However, we did not find evidence to this effect.
 The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal enviroments experienced by taxa or because lower predictability of thermal environments over time make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
@@
 For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
-They showed that greater between-individual variation in DEB parameters led to less extreme population occilations compared to scenerios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ecotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extintion and reduced productivity – predictions reinforced by a number of studies [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022].
+They showed that greater between-individual variation in DEB parameters led to less extreme population oscillations compared to scenarios with no variation [@kooijman1989population].
+The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extinction and reduced productivity – predictions reinforced by several studies [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022].
 To date, however, an appreciation for the wide-reaching impacts that changes in variance may have on populations and communities remains limited.
@@
 What we desperately need now are the development of theoretical models that better integrate intrapopulation variation into mechanistic physiological models or ones that better capture stochasticity such as individual based models.
-Our meta-analytic findings can help us better position ourselves to now start asking questions about the ecological and evolutionary consequences of changes in variance in physiological rates.
+Our meta-analytic findings can help us better position ourselves to start asking questions about the ecological and evolutionary consequences of changes in variance in physiological rates.
 
@@
 
-An enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about ecological and evolutonary dynamics of natural populations [@forsman2015rethinking].
-Variance in physiological rates could be better incorperated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
-While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predcitions.
+Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking].
+Changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced and possibly more realistic predictions about the impacts of climate change on natural populations.
+While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predictions.
 Our meta-analysis allows for realistic models to be parameterised and ensure they are better aligned with empirical findings.
 Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
-Particularly interesting questions include: How does a reduction in physiological rate varaince change the flow of energy across tropic levels within communities?
+Particularly interesting questions include: How does a reduction in physiological rate varaince change energy flow across tropic levels within communities?
 What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?
-Are reductions in variance in one trait associated with reductions in correlated traits or do some traits increase while others decrease?
+Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?
 How much of the reduction in variance is driven by lower levels of genetic variance?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation, but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
 
@@
 ## Supplemental Results and Figures
+
+#### Acute and acclimation $lnRR_{Q_{10}}$ for different trait categories across marine, freshwater and terrestrial taxa
+
+```{r, fig-2}
+#| label: fig-2
+#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
+#| echo: false
+k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
+
+ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none",
+                              axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
+                            annotate("text", label= paste0(k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4)
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 8.5, width = 26)
+
+img_fig2 <- magick::image_read("./output/figures/fig2_trait.png")
+img_fig2
+```
 

### 2024-01-10 ms.qmd
MS updated with Shinichi's comments

@@
 Greater thermal variability is expeced to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-However, such responses depend on the extent of genetic and phenotypic variability, yet most work has focused on mean responses to climate warming ignoring how temperature changes variability.
-Here, we collect data on marine, freshwater and terrestrial ectotherms to quantify their capacity for acclimation and the extent to which variance in physiological rates change in response to higher temperatures.
-We use new effect size measures and meta-analysis to understand
+However, such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean responses to climate warming ignoring how temperature changes variability.
+Here, using a large database of physiological rate data on marine, freshwater and terrestrial ectotherms we quantify the capacity for acclimation and the extent to which relative variance in physiological rates change in response to higher temperatures.
+Using new effect size measures and meta-analysis we show that physiological acclimation and changes in relative variance do not depend on past temperature variability and predictability experienced by a population or differ between life stages.
+Across habitats there was a general tendency for relative variation in physiological rates to decrease at higher temperatures.
+Freshwater ectotherms are capable of acclimating and such responses will likely be beneficial considering that these effects are larger than reductions in relative variance in physiological rates.
+In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not be as beneficial as previously thought.
+Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a general inability to acclimate highlighting the vulnerability of terrestrial ectotherms to climate change.
+Our results highlight the importance of considering changes in variance in physiological rates when predicting the capacity of populations to persist in and adapt to novel environments.
 
@@
 
-where $CV$ is the coefficient of variation defined as $SD / R$.
+where $CV$ is the coefficient of variation defined as $SD / R$. We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
 
@@
 
-Overall, $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Overall, $lnRR_{Q_{10_{acclimation}}}$ decreased from $lnRR_{Q_{10_{acute}}}$ by only `r abs(mean(avg_change))`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
@@
 Different trait categories showed different accclimation responses across habitat types, however, they mirrored patterns seen overall (see Supplement; @fig-2).
-Acclimation capacity also did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-3) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity also did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
   theme(legend.direction = "vertical") +
-  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
-                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-  geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
-                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-  geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
-                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
-annotate("text", x = 1, y = 2.10, 
+
+  annotate("text", x = 1.5, y = 0, 
          label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0, size = 6) + 
-annotate("text", x = 1.01, y = 4.0, 
-         label =paste0(round(mean(change_f), 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-  annotate("text", x = 0.85, y = 3, label = "P < 0.001", hjust = 0, size = 6) + 
-  annotate("text", x = 2, y = 2.10, 
+  annotate("text", x = 1.20, y = 1.4, 
+         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
+  annotate("text", x = 1.20, y = -0.8, label = "P < 0.001", hjust = 0, size = 6) +
+
+  annotate("text", x = 2.5, y = 0, 
          label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-annotate("text", x = 2.01, y = 4.0, 
-         label =paste0(round(mean(change_m), 2), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 1.85, y = 3, label = "P = 0.01", hjust = 0, size = 6) +
-  annotate("text", x = 3, y = 2.10, 
+  annotate("text", x = 2.20, y = 1.4, 
+         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 6) +
+  annotate("text", x = 2.20, y = -0.8, label = "P = 0.01", hjust = 0, size = 6) +
+
+  annotate("text", x = 3.5, y = 0, 
          label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-annotate("text", x = 3.01, y = 4.0, 
-         label =paste0(round(mean(change_t), 2), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 2.85, y = 3, label = "P = 0.36", hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-0.8, 5.05) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = k_lnrr$moderator, y = 5)
+  annotate("text", x = 3.20, y = 1.4, 
+         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 6) +
+  annotate("text", x = 3.20, y = -0.8, label = "P = 0.36", hjust = 0, size = 6) +
+
+  scale_fill_manual(values = c(col)) + ylim(-0.8, 2) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.7, size = 5)
 
   p1.2 <- p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
-        axis.text = element_text(size = 15))
-
-  pdf("./output/figures/fig1.pdf", useDingbats=FALSE, width = 12, height = 9.6)
-    p1.2
-  dev.off()
-  ggsave(p1.2, filename = "./output/figures/fig1.pdf", width = 12, height = 9.6, device = "pdf")
+        axis.text = element_text(size = 15), legend.title = element_text(size = 15),
+                               legend.text = element_text(size = 15),
+                               title = element_text(size = 24))
+
+  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 9.1, height = 9.2, device = "png")
 
@@
 
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 8, branch.size = 2) +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -1.8, 
-           label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 2), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -1.5, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = 1, 
+  x1 = 1.4
+  x2 = 2.4
+  x3 = 3.4
+
+  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 8, branch.size = 2, k.pos = "none") +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+  annotate("text", x = x1, y = -2, 
+           label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = x1-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = x1-0.15, y = 1, 
            label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 2.3, y = -1.8, 
-           label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 2), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -1.5, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) +
-  annotate("text", x = 2.15, y = 1, 
-           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.4, y = -1.8, 
-           label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 2), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 3.25, y = 1, 
+
+  annotate("text", x = x2, y = -2, 
+           label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = x2-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) +
+  annotate("text", x = x2-0.15, y = 1, 
+           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
+
+  annotate("text", x = x3, y = -2, 
+           label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = x3-0.15, y = 1, 
            label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = 3.25, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 2) + 
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(1.15, 2.15, 3.25), y = 1.8)
+    annotate("text", x = x3-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 2) + 
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5)
 
@@
                                        legend.title = element_text(size = 15),
-                                        legend.text = element_text(size = 15))
-
-     ggsave(p2, filename = "./output/figures/fig2.png", width = 10, height = 9.5)
-
-```
-
-```{r, fig-3}
-#| label: fig-3
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
-
-p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))
-
-p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())
-
-p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())
-
-fig3 <- (p1 | p2 | p3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig3, filename = "./output/figures/fig3_lh.png", width = 14, height = 4.5)
-
-fig3 <- magick::image_read("./output/figures/fig3_lh.png")
-fig3
+                               legend.text = element_text(size = 15),
+                               title = element_text(size = 24))
+
+  ggsave(p2, filename = "./output/figures/fig2.png", width = 9.3, height = 8.8)
 
@@
 #| label: fig-cvrlh
-#| fig-cap: "Estimated mean $lnCVR_{Q_{10}}$ for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult and juevenile life-history stages for Marine (A & D), Freshwater (B & E) and Terrestrial (C & F) ectotherms.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 
-p1 <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45) + labs(title = "Marine") + ylim(c(-2, 2.2))
-
-p2 <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Freshwater") + theme(legend.position = "none", axis.text.y = element_blank())
-
-p3 <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE)+ labs(title = "Terrestrial")+ theme(legend.position = "none", axis.text.y = element_blank())
-
-fig4 <- (p1 | p2 | p3) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig4, filename = "./output/figures/fig4_lh.png", width = 14, height = 4.5)
-
-fig4 <- magick::image_read("./output/figures/fig4_lh.png")
+add_theme  <- function(){theme(axis.title  = element_text(size = 24),
+                               axis.text.y = element_text(size = 15),
+                               axis.text.x = element_text(size = 15),
+                              legend.title = element_text(size = 15),
+                               legend.text = element_text(size = 15),
+                               title = element_text(size = 24))}
+branch.size = 2
+trunk.size = 5
+
+p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1, 1.8)
+
+p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45,)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1, 1.8)
+
+p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) +  ylim(-1, 1.8)
+
+p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-2.5, 2.5)
+
+p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
+
+p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
+
+fig4 <-(p1 | p2 | p3) / (p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig4, filename = "./output/figures/fig4_lh.pdf", width = 19, height = 12, device = "pdf")
+
+fig4 <- magick::image_read("./output/figures/fig4_lh.pdf")
 fig4
-```
-
-```{r, fig-cvrtrait}
-#| label: fig-cvrtrait
-#| fig-cap: "Acute and Acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
-#| echo: false
-
-ptm <- orchard_plot(model2.3m, mod = "trait_category", group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() 
-#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptf <- orchard_plot(model2.3f, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
-#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptt <- orchard_plot(model2.3t, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate")) + theme_classic() + labs(legend = "Type")
-#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-figcvrtrait <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 8.5, width = 26)
-
-img_figcvrtrait <- magick::image_read("./output/figures/figcvrtrait.png")
-img_figcvrtrait
 ```
@@
 scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
-geom_text(data = dat_text2, aes(x = x, y = y-0.3, label = label2), size = 5) +
-geom_text(data = dat_text2, aes(x = x, y = y-0.65, label = p), size = 5) +
+geom_text(data = dat_text2, aes(x = x+1, y = y, label =label), size = 5) + 
+geom_text(data = dat_text2, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
+geom_text(data = dat_text2, aes(x = x+1, y = y-0.65, label = p), size = 5) +
 theme(legend.position = "bottom", 
@@
 scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
-geom_text(data = dat_text2, aes(x = x, y = y-0.6, label = label2), size = 5) +
-geom_text(data = dat_text2, aes(x = x, y = y-1.2, label = p), size = 5) +
+geom_text(data = dat_text2, aes(x = x+1, y = y, label = label), size = 5) + 
+geom_text(data = dat_text2, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
+geom_text(data = dat_text2, aes(x = x+1, y = y-1.2, label = p), size = 5) +
 theme(legend.position = "bottom", 
@@
 Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
+Predicted change in physiological rate variance (relative variance) for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
+Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenerio relative to current climate conditions (% change).
 
@@
 Here, we show that the relative variance in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
-Decreases in the relative variance of physiological rates are larger than the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 9% acclimation vs.
-15% reduction in variance; *terrestrial*: no acclimation vs 28% reduction in variance).
+Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
+15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1).
 Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
@@
 Phenotypic plasticity is expected to allow populations to persist in the face of climate extremes by better allowing phenotypes to match fitness optima, however, maladaptive responses can occur [@noble2019plastic; @radersma2020plasticity] and there may be limits / costs to plasticity that may prevent it from evolving [@Dewitt1998; but see @Murren2015].
-While there is substantial variation in effects across species, we show that plastic adjustments to physiological rates are, on average, rather small compared to the general reduction variance in physiological rates.
-Variance reductions are particularly pronounced  for terrestrial ectotherms and there were no major differences between life-stages.
+We show that plastic adjustments in physiological rates and changes in their relative variance differs across habitats.
+In freshwater habitats, acclimation responses will likely be beneficial considering that these effects are larger than reductions in relative variance in physiological rates.
+In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not be as beneficial.
+Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a general inability to acclimate highlighting the vulnerability of terrestrial ectotherms to climate change.
 While it is unclear the extent to which such changes in variance are heritable, we expect changes in variance of this magnitude to impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
@@
 ### ***Plasticity and variance in physiologcial rates do not differ between life-stages***
-Greater plasticity for early life-stages in development may be important for dealing with the effects of climate change because early life-stages are usually particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+Interestingly, there were no major differences in acclimation or reductions in physiological variance between life-stages across habitat types.
+Greater plasticity for early life-stages of development is expected to be important for dealing with the effects of climate change because early life-stages are usually particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+However, our results highlight that early life stages are not likely to be protected from the impacts of climate change.
 Evidence across the literature conflicts in terms of the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
@@
 
+### ***Limitations***
+A number of limitations need to be recognised to better contextualise our results.
+First, and as mentioned above, the evolutionary implications of changes in relative variances in physiological rates is still unclear because we lack a full understanding of how much variation is genetic versus environmental, or how traits are related to fitness.
+Second, while we found no relationships between historical climate variability / predictability and capacity for plasticity this does not necessarily mean they are not important.
+There are major challenges to estimating realistic microthermal environments experienced by taxa; it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
+Third, while we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
+Substantial variation in acclimation responses and changes in variance exist among populations as evidenced by wide prediction intervals.
+As such, finer scale analyses that look at acclimation responses *and* changes in relative variance will be beneficial for developing a better understanding of their interplay when considering how populations will be impacted by climate change.
+
 ### ***Conclusions and future directions***
@@
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+The x-axis is truncated for ease of visualisation."
 #| echo: false
 k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
-
-ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+k_fresh=manual_extract(model1.3_f_het, mod = "trait_category", group = "record_num")
+k_terrs=manual_extract(model1.3_t_het, mod = "trait_category", group = "record_num")
+
+ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none",
-                              axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
-                            annotate("text", label= paste0(k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4)
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
+                            annotate("text", label= paste0("k = ", k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4) + add_theme()
 #ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
 
-ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
@@
                               "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme() + 
+                              annotate("text", label= paste0("k = ", k_fresh$k, " (", k_fresh$sdy, ")"), x = k_fresh$moderator, y = 2.4) + add_theme()
 #ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
 
-ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
   scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")
+                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")+ annotate("text", label= paste0("k = ", k_terrs$k, " (", k_terrs$sdy, ")"), x = k_terrs$moderator, y = 2.4) + add_theme() + ylim(-1,3)
 #ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
 
-fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 8.5, width = 26)
+fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 14, width = 10)
 
@@
 img_fig2
+```
+
+```{r, fig-cvrtrait}
+#| label: fig-cvrtrait
+#| fig-cap: "Acute and Acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+The x-axis is truncated for ease of visualisation."
+#| echo: false
+
+k_marinecv=manual_extract(model2.3m, mod = "trait_category", group = "record_num", exclude = "Antiox")
+k_freshcv=manual_extract(model2.3f, mod = "trait_category", group = "record_num")
+k_terrscv=manual_extract(model2.3t, mod = "trait_category", group = "record_num")
+
+ptm <- orchard_plot(model2.3m, mod = "trait_category", group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, k.pos = "none", condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + add_theme() + annotate("text", label= paste0("k = ", k_marinecv$k, " (", k_marinecv$sdy, ")"), x = k_marinecv$moderator, y = 2.4) + ylim(-2, 2.6)
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf <- orchard_plot(model2.3f, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type",  k.pos = "none") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic()+ add_theme() + annotate("text", label= paste0("k = ", k_freshcv$k, " (", k_freshcv$sdy, ")"), x = k_freshcv$moderator, y = 2.4) + ylim(-2.5, 2.65)
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model2.3t, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0,  k.pos = "none", condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate")) + theme_classic() +  annotate("text", label= paste0("k = ", k_terrscv$k, " (", k_terrscv$sdy, ")"), x = k_terrscv$moderator, y = 2.4) + labs(legend = "Type")+ add_theme() + ylim(-2, 2.65)
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 14, width = 10)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figcvrtrait.png")
+img_figcvrtrait
 ```
@@
 #| fig-align: center
-#| fig-cap: lnVR
+#| fig-cap: "Estimated mean $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial systems.
+Note there were no differences between acute and acclimation $Q_{10}$ types so they were averaged.
+Thick black bars are 95% confidence intervals (CI's) and thin bars 95% prediction intervals (PI's).
+The percentage change in variance is also back calculated.
+Note that these are raw variances and do not account for changes in mean physiological rates.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species."
 
@@
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
-Models estimates are based off 1253 effect sizes from 139 studies.
+Models estimates are based off 1,253 effect sizes from 139 studies.
 

### 2024-01-11 ms.qmd
Edited wording in results

@@
 Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increase by 10$^\circ$C.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiologcial rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increase by 10$^\circ$C.
 In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).

### 2024-01-14 ms.qmd
Results and discussions comments changed

@@
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj].
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
 In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured.
@@
 
-### *Reduced variation in physiological rates in terrestrial ectotherms*
+### *Reduced variation in physiological rates in terrestrial and marine ectotherms*
 
@@
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals."
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Raw data for both adult and jeunvile life-history stages also presented but point are not separated by type for ease of presentation."
 #| echo: false
@@
 Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
-Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6 A-C).
+Globally, there was a clear bias towards species in the Northern Hemiphere (@fig-fig6 A-C).
 Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
-Here, we show that the relative variance in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
-Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
+Here, we show that the relative variance $lnCVR_{Q_{10}}$ in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
+Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation (i.e., $lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
 15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1).
@@
 However, we did not find evidence to this effect.
-The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal enviroments experienced by taxa or because lower predictability of thermal environments over time make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
+The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments experienced by taxa.
+Alternatively, lower predictability of thermal environments over time may make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
 Randomly flutuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
@@
 Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
-Particularly interesting questions include: How does a reduction in physiological rate varaince change energy flow across tropic levels within communities?
+Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across tropic levels within communities?
 What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?

### 2024-01-14 ms.qmd
Fonti's suggested changes incorperated

@@
 Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
-Such changes in physiological trait variation may also have important ecological consequences by promotong population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
+Such changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
 The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
@@
 More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive $Q_{10}$ effect sizes and associated sampling variances (see below).
+Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
@@
 Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type.
-We predicted that acclimation responses would be more likely early in development compared to later in development, but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g., @moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
 

### 2024-01-15 ms.qmd
Adding PRISMA

@@
 Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+We provide a PRISMA flow diagram of our extraction process in the *Supplement* (see @fig-prisma).
 
@@
 ## Supplemental Results and Figures
+
+### PRISMA Flow Diagram
+
+```{r, fig-prisma}
+#| label: fig-prisma
+#| fig-cap: "PRISMA flow diagram of the literature search and screening process."
+#| echo: false
+
+prisma <- magick::image_read("./output/figures/PRISMA.png")
+prisma
+```
 

### 2024-01-17 ms.qmd
Figures and updated MS
Absract and start of intro

@@
 Climate change is expected to result in warmer and more variable thermal environments globally.
-Greater thermal variability is expeced to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-However, such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean responses to climate warming ignoring how temperature changes variability.
+Greater thermal variability is expected to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
+Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean responses to climate warming ignoring how temperature changes variability.
 Here, using a large database of physiological rate data on marine, freshwater and terrestrial ectotherms we quantify the capacity for acclimation and the extent to which relative variance in physiological rates change in response to higher temperatures.
-Using new effect size measures and meta-analysis we show that physiological acclimation and changes in relative variance do not depend on past temperature variability and predictability experienced by a population or differ between life stages.
+Using new effect size measures and meta-analysis we show that physiological acclimation and changes in relative variance do not depend on past temperature variability and predictability experienced by a population, or differ between life stages.
 Across habitats there was a general tendency for relative variation in physiological rates to decrease at higher temperatures.
@@
 
-Climate change is expected to result in warmer and more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
+Climate change is expected to result in warmer but also more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
 Greater thermal variability in the past is expected to have resulted in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
@@
 
-### PRISMA Flow Diagram
+#### PRISMA Flow Diagram
 

### 2024-01-18 ms.qmd
reword

@@
 We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-More specifically, we performed a literature search on the 28th of June 2017 using the Web of Science database.
-We limited our search to articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015-wi searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015-wi searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.

### 2024-01-19 ms.qmd
Changing up wording in methods

@@
 We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
-We included any papers that were missed between our searches and those of @Havird2020-mj from the dates 2013-2017.
-@Havird2020-mj added 7 new studies between 2013-2017 (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+We included any papers that were missed between our searches and those of @Havird2020-mj.
+@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
 Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects) that were published between 2013 - 2017 (a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
 Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).

### 2024-01-22 ms.qmd
Fxing up Alex's comments

@@
 Greater thermal variability in the past is expected to have resulted in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
-The extent to which adaptive plasticity and genetic adaptation will allow organisms to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
+The extent to which adaptive plasticity and genetic adaptation will each contribute to a populations capacity to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
 Without such responses, high extinction rates are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
@@
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], and/or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
+Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
 
@@
 
-Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to debates over which ecosystems will be most vulnerable to contemporary climate change.
-Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @Pinsky2019-fn; @hoffmann2013upper].
+Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to uncertainty over which ecosystems will be most vulnerable to contemporary climate change.
+Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper], whereas greater proximity to upper thermal limits in marine systems have questioned such conclusions [@Pinsky2019-fn].
 Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient, particularly in combination with potential changes in other factors, such as genetic and phenotypic variability.

### 2024-01-22 ms.qmd
All Alex's comments dealt with

@@
 Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface air temperature at 2 meters (0.01 resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25 resolution) using the *ncdf4* R package [vers.
+For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution) using the *ncdf4* R package [vers.
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
-We chose a 2-meter resolution because we believed that it more likely reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
-For terrestrial species we also collected soil temperature as for many species this maybe more representative of microhabitat choice compared to air temperature.
+We chose surface temperature because we believed that it was more likely reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+For terrestrial species we estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
 We fit models using both air and soil temperature and found that the results were qualitatively similar.
@@
 
-Using the thermal time-series data for each location we summarised various metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
+Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
 To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
@@
 
-We also extracted climate projections into the future to understand the effects that climate warming will have on physiological rate variance.
+Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability and predictability for the future.
 We used the CanESM2 climate model (2005-2100) under a high emissions scenerio (RCP8.5).
@@
 Silouettes are representative taxa of major clades within the tree.
-**B)** Acute and Acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial environments.
+**B)** Acute and Acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
 **C)** $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
@@
 
-Thermal variability (i.e., $CV$) and predictability a population experienced in its past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
+Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
 

### 2024-02-01 ms.qmd
Adding sentence to a new paper which is good
Revised abstract

@@
 Greater thermal variability is expected to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean responses to climate warming ignoring how temperature changes variability.
-Here, using a large database of physiological rate data on marine, freshwater and terrestrial ectotherms we quantify the capacity for acclimation and the extent to which relative variance in physiological rates change in response to higher temperatures.
-Using new effect size measures and meta-analysis we show that physiological acclimation and changes in relative variance do not depend on past temperature variability and predictability experienced by a population, or differ between life stages.
-Across habitats there was a general tendency for relative variation in physiological rates to decrease at higher temperatures.
-Freshwater ectotherms are capable of acclimating and such responses will likely be beneficial considering that these effects are larger than reductions in relative variance in physiological rates.
+Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean phenotypic responses to climate warming ignoring how temperature changes phenotypic variability.
+Here, using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (changes in variance after accounting for changes in the mean) in physiological rates changes in response to increasing temperatures.
+Using new effect size estimates and meta-analysis we show that acclimation of physiological rates and changes in their relative variance do not depend on past temperature variability and predictability experienced by a population at its geographical location; neither do these responses differ between life stages.
+Across habitats relative variance in physiological rates decreased at higher temperatures.
+Freshwater ectotherms are capable of acclimating which is likely to be beneficial considering that reductions in relative variance in physiological rates at high temperatures is lower for freshwater species.
 In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not be as beneficial as previously thought.
 Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a general inability to acclimate highlighting the vulnerability of terrestrial ectotherms to climate change.
-Our results highlight the importance of considering changes in variance in physiological rates when predicting the capacity of populations to persist in and adapt to novel environments.
+Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance, challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
+Reductions in physiological rate variance at high temperatures may further have important ecological implications that impact population and community productivity that can have cascading effects on population and ecosystem processes.
 
@@
 However, we did not find evidence to this effect.
+This finding is consistent with other meta-analyses [e.g., @barley2021limited; @Gunderson2015-hz] with thermal tolerance.
 The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments experienced by taxa.

### 2024-02-01 ms.qmd
Changed the wroding of ending sentence of abstract

@@
 Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance, challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
-Reductions in physiological rate variance at high temperatures may further have important ecological implications that impact population and community productivity that can have cascading effects on population and ecosystem processes.
+Reductions in physiological rate variance at high temperatures may further have important ecological ramifications that impact population and ecosystem processes that cascade to affect population and community productivity.
 

### 2024-02-01 ms.qmd
Missed a few text changes

@@
 Greater thermal variability is expected to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean phenotypic responses to climate warming ignoring how temperature changes phenotypic variability.
+Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean phenotypic responses to climate warming ignore how temperature may change phenotypic variability.
 Here, using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (changes in variance after accounting for changes in the mean) in physiological rates changes in response to increasing temperatures.
@@
 Freshwater ectotherms are capable of acclimating which is likely to be beneficial considering that reductions in relative variance in physiological rates at high temperatures is lower for freshwater species.
-In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not be as beneficial as previously thought.
-Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a general inability to acclimate highlighting the vulnerability of terrestrial ectotherms to climate change.
+In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not necssarily be beneficial.
+Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a lack of capacity for acclimation, which highlights the vulnerability of terrestrial ectotherms to climate change.
 Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance, challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.

### 2024-02-02 ms.qmd
INtroduction

@@
 Climate change is expected to result in warmer but also more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability in the past is expected to have resulted in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
-The extent to which adaptive plasticity and genetic adaptation will each contribute to a populations capacity to adapt to new environmental conditions is not yet clearly established [@Chevin2017].
-Without such responses, high extinction rates are predicted if organisms cannot track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to be the 'first line of defence' against changing climates by buying time for genetic adaptation to take place [i.e., the 'plasticity first hypothesis' - @WestEberhard2003; see also @Lande2009].
+Evolutionary theory predicts that greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
+Without plasticity or adaptation, high extinction rates are predicted unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
+Phenotypic plasticity is expected to be the 'first line of defence' against changing climates, thereby buying time for genetic adaptation to take place [i.e., the 'plasticity first hypothesis' - @WestEberhard2003; see also @Lande2009].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], or the prediction is likely only supported for specific plastic responses (i.e., active and developmental plasticity) or life-history stages.
-
-Reversible forms of phenotypic plasticity, such as acclimatization  and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses can be fine-tuned to environments [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
-Such responses are driven by changes in underlying physiology that can respond rapidly to the environment.
-However, studies have primarily been focused on mean physiological responses, paying little attention to changes in physiological variability in a population [@Seebacher2015-wi; @Havird2020-mj].
-For example, most work has focused on the degree to which mean thermal tolerances or acclimation abilities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022], neglecting how intrapopulation variability might also be impacted.
-Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change has important implications for understanding a population's capacity for physiological trait evolution because lack of physiological variation is expected to play a role in limiting responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variability in a population may also imply greater niche breadth and inform on the extent to which populations are able to buffer against environmental change [for example, through 'portfolio effects' see @Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
-Decreases in phenotypic variance may also suggest strong stabilising selection or constraints on performance, depending on the trait [@Scheiner2020; @Dewitt1998].
-Such changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
+Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], or the prediction is only supported for specific life-history stages.
+
+Reversible phenotypic plasticity, such as acclimation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
+Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to faciliate a rapid response to the environment.
+However, the focus up to now has been primarily on mean physiological responses.
+For example, mean thermal tolerances or acclimation abilities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022].
+However, it is possible that intrapopulation variability might also be impacted in addition to the mean.
+Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
+Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
+Decreases in phenotypic variance also suggests strong stabilising selection or reflect constraints on performance [@Scheiner2020; @Dewitt1998].
+Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
 The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
 
-Periods of past climatic change have had disproportionate impacts on some ecosystems over others leading to uncertainty over which ecosystems will be most vulnerable to contemporary climate change.
-Studies have highlighted species occupying terrestrial ecosystems as being particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper], whereas greater proximity to upper thermal limits in marine systems have questioned such conclusions [@Pinsky2019-fn].
-Despite marine and freshwater ecosystems appearing to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], it is unclear if the magnitude of physiological adjustment is sufficient, particularly in combination with potential changes in other factors, such as genetic and phenotypic variability.
-Low oxygen availability has been suggested as a major factor influencing the vulnerability of aquatic ecosystems whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
+Periods of past climatic change have had disproportionate impacts on some ecosystems over others raising the question of which ecosystems will be most vulnerable to contemporary climate change.
+Species occupying terrestrial ecosystems are particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper], whereas greater proximity to upper thermal limits in marine systems have questioned such conclusions [@Pinsky2019-fn].
+Marine and freshwater ecosystems appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
+However, it is unclear if the magnitude of physiological adjustment is sufficient to compensate for potentially negative environmental effects, particularly when temperature interacts with other abiotic changes.
+Low oxygen availability may be a major factor influencing the vulnerability of aquatic ecosystems, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
 Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms.
@@
 We then expand these effect sizes to allow for comparisons of variance in physiological rates to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
-2) Are temperture effects on plastic adjustments in physiolgical rates larger than changes in variance across aquatic and terrestrial ectotherms?
-3) Are changes in plasticity or variance in physiological rates impacted by a population's past climate history?
+2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
+3) Are changes in plasticity or variance in physiological rates impacted by past climate history?
 4) How are means and variances in physiological rates expected to change under climate change?

### 2024-02-02 ms.qmd
Fist section of methods fixed. Up to Data Compilation

@@
 
-Reversible phenotypic plasticity, such as acclimation and behavioural plasticity, are expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
-Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to faciliate a rapid response to the environment.
+Reversible phenotypic plasticity, such as acclimation, is expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
+Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to faciliate a rapid response to the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
 However, the focus up to now has been primarily on mean physiological responses.
@@
 Low oxygen availability may be a major factor influencing the vulnerability of aquatic ecosystems, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
-Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms.
-Reduced variability may result from variances being eroded by strong selection, an inability to adjust physiological rates, or a combination of both.
-Changes in physiological rate variance may therefore have important cascading effects on energy transfer and productivity for populations across these different ecosystems that are, as of yet, poorly measured and modelled.
+Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms which may have important cascading effects on energy transfer and productivity across different ecosystems.
 
@@
 
-We split the screening of titles and abstracts for the 1,321 papers found in our search among all authors evenly.
-To ensure consistency among authors in title and abstracts that should be included, prior to  screening all authors went through a randomly selected set of papers together - agreeing on those that were relevant and those that were not based on our inclusion criteria (see below).
-Where any authors were uncertain about whether to include a paper in the sub-sample they screened, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision on whether to include the paper.
-After title and abstract screening, we were left with a total of 149 papers for full text screening.
+We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
+To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
+In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
+After title and abstract screening, there was a total of 149 papers for full text screening.
 Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.

### 2024-02-02 ms.qmd
Methods fixed. On to results

@@
 Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
-We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied.
-For studies that did not provide latitude and longitude for the population, we searched for similar studies by the lab group to identify where the population was likely to have been sourced or derived from when needed.
-If the population was derived from the wild, we recorded the nearest latitude and longitude of the population to the field collection site.
-If the animals had been sourced from a commercial supplier, we took the latitude and longitude of the supplier that the paper identified the animals to have originated from.
+We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
+If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
+If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
 When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
@@
 Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations for their sampling variances.
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
 Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
@@
 
-Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures that these rates are measured.
+Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures at which these rates are measured.
 Log transformation of this ratio makes the effect size normally distributed.
 @eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows one to compare the mean of two temperature treatments directly regardless of the temperatures that these groups have been measured.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
 The sampling variance for @eq-lnq10 can be computed as follows (as described in @Noble2022-ty):
@@
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
-We chose surface temperature because we believed that it was more likely reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
 For terrestrial species we estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
 We fit models using both air and soil temperature and found that the results were qualitatively similar.
-As such, we only present results for air temperature.
+We therefore only present results for air temperature.
 
@@
 
-To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiogical traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude.
+To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiological traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude.
 We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
@@
 Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published.
-To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that acounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that accounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
 

### 2024-02-02 ms.qmd
Results done. Discussion left to do and a few things to chat to Frank about next week

@@
 
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (@fig-1 A).
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-1 A).
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
-While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (Acute responses were higher for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
+While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
 As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
@@
 
-Overall, $lnRR_{Q_{10_{acclimation}}}$ decreased from $lnRR_{Q_{10_{acute}}}$ by only `r abs(mean(avg_change))`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
 In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
-Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely going to provide adaptive benefits under climate change.
-
-Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), with most variance being explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
-
-Different trait categories showed different accclimation responses across habitat types, however, they mirrored patterns seen overall (see Supplement; @fig-2).
-Acclimation capacity also did not vary by life-stage given that there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+
+Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+
+Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
+Acclimation capacity also did not vary by life-history stage given and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
 The total number of acute and acclimation type Q10 effect sizes are highlighted as well as whether the taxa is marine, freshwater or terrestrial.
-Silouettes are representative taxa of major clades within the tree.
+Silhouettes are representative taxa of major clades within the tree.
 **B)** Acute and Acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
@@
 Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiologcial rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increase by 10$^\circ$C.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiologcial rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
 In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
@@
 Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
-While traits did differ in whether they exhibited a reduction in variation in physiological rates at high temperatures reduced variance was prominant for resting metabolic rates and sprint speed (@fig-cvrtrait).
+Reduced relative variance was particularly prominant for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
 
@@
 
-Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
-Globally, there was a clear bias towards species in the Northern Hemiphere (@fig-fig6 A-C).
+Acute and acclimation responses for wild ectotherms were much less common than studies on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
+Globally, there was a clear bias towards species in the Northern Hemisphere (@fig-fig6 A-C).
 Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
@@
 Predicted change in physiological rate variance (relative variance) for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
-Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenerio relative to current climate conditions (% change).
+Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change).
 
@@
 Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a general inability to acclimate highlighting the vulnerability of terrestrial ectotherms to climate change.
+Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely to provide adaptive benefits under climate change.
 While it is unclear the extent to which such changes in variance are heritable, we expect changes in variance of this magnitude to impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.

### 2024-02-03 ms.qmd
First paragraph of discussion

@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
-Here, we show that the relative variance $lnCVR_{Q_{10}}$ in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%).
-Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation (i.e., $lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms is expected to decrease for ectotherms as temperatures increase, and this decrease is particularly pronouced in terrestrial ectotherms (~28%).
+Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation ($lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
 15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1).
 Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention.
+Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention.
 We discuss our findings in the context of the current literature and highlight key areas for future research.

### 2024-02-03 ms.qmd
First paragraph of Potential... finished. Start at second paragraph

@@
 
-### ***Potential evolutionary consequences for reduced plasticity and variance in physiologcial rates across ectotherms***
-
-There is a general interest in understanding the interplay and relative importance of plasticity and genetic adaptation to a population's capacity to mitigate climate change effects [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate].
-Phenotypic plasticity is expected to allow populations to persist in the face of climate extremes by better allowing phenotypes to match fitness optima, however, maladaptive responses can occur [@noble2019plastic; @radersma2020plasticity] and there may be limits / costs to plasticity that may prevent it from evolving [@Dewitt1998; but see @Murren2015].
+### ***Potential evolutionary consequences of reduced plasticity and variance in physiologcial rates across ectotherms***
+
+Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate].
+Phenotypic plasticity can allow populations to persist in the face of climate extremes by matching phenotypes to fitness optima, although this is not always the case [@noble2019plastic; @radersma2020plasticity] and there may be limits and costs to plasticity that constrain its expression [@Dewitt1998; but see @Murren2015].
 We show that plastic adjustments in physiological rates and changes in their relative variance differs across habitats.
@@
 In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not be as beneficial.
-Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a general inability to acclimate highlighting the vulnerability of terrestrial ectotherms to climate change.
+Relative variance reductions are particularly pronounced in terrestrial ectotherms and this coincides with a general inability to acclimate.
 Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely to provide adaptive benefits under climate change.
-While it is unclear the extent to which such changes in variance are heritable, we expect changes in variance of this magnitude to impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
+Together, these findings highlight the vulnerability of terrestrial ectotherms to climate change.
+It may be expected that reductions in variance of this magnitude impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
 Both are predicted to impact the capacity of populations to evolve under climate change [@hoffmann2011climate; @urban2023and].

### 2024-02-05 ms.qmd
Ok, simplified section and now on to "signature of past climate"

@@
 
-One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms were, on average, acclimated for significantly less time than ectotherms from aquatic habitats.
-However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023-lz].
-Faster rates of acclimation would therefore result in the opposite patterns to those that we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ when controlling for acclimation time.
-The weak acclimation responses of terrestrial ectotherms suggest that evolving plasticity  in physiological rates may be hard, possibly because terrestrial ectotherms are more likely to experience more variable and unpredictable thermal environments than aquatic ectotherms (see below).
-Reductions in physiological rate variance for terrestrial ectotherms may be because of selective mortality at higher temperatures reducing intrapopulation variability or populations being pushed closer to their thermal maxima (or a combination of both).
-Disentangling these hypotheses will require empirical studies to connect survival measures at different temperatures with thermal physiology across individuals (e.g., $CT_{max}$).
-
-### ***Plasticity and variance in physiologcial rates do not differ between life-stages***
+### ***Plasticity and variance in physiological rates do not differ between life-stages***
 Interestingly, there were no major differences in acclimation or reductions in physiological variance between life-stages across habitat types.
-Greater plasticity for early life-stages of development is expected to be important for dealing with the effects of climate change because early life-stages are usually particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
 However, our results highlight that early life stages are not likely to be protected from the impacts of climate change.
-Evidence across the literature conflicts in terms of the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
-For example, @moghadam2019heat showed that larvae *Drosophila* were more plastic in their heat hardening responses compared to adults.
+Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
 In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
@@
 However, very few studies measured multiple life-history stages within the same population.
-As such, we need more studies that explicitly compare, within populations, differences in plasticity among life stages across multiple traits.
-A better understanding of the microthermal enviroments experienced by different life-stages will also be important in understanding why plasticity (or lack thereof) may differ among life-stages.
+In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same populations.
+A better understanding of the microthermal environments experienced by different life-stages will also be important in understanding why plasticity may or may not differ among life-stages.
 

### 2024-02-05 ms.qmd
Franks comments addressed. Now need to deal with the few bigger points.

@@
 This finding is consistent with other meta-analyses [e.g., @barley2021limited; @Gunderson2015-hz] with thermal tolerance.
-The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments experienced by taxa.
+The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal enviroments many taxa actually experience in nature.
 Alternatively, lower predictability of thermal environments over time may make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
 Randomly flutuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
-For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly flutuating thermal conditions did not lead to the expected increase in plasticity, but rather reduced plasticity.
-@Leung2020 also showed reduced plasticity in morphological traits when environments experienced were less predictable by experimentally evolving algae populations (*Dunaliella salina*) [see also @leung2023phenotypic].
-These findings, in combination with our results, suggests that there are costs to being plastic when environments are not predictable (either intrinsic physiological costs, fitness costs or both).
+For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
+@Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
+These findings, in combination with our results, suggests that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticty when environments are not predictable (either intrinsic physiological costs, fitness costs or both).
 The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-However, disentangling the relative importance of environmental variability and predictability will require better distinguishing between active and passive plasticity, as the latter is expected to more likely be adaptive (@Havird2020-mj), and better a understanding the fitness consequences of exhibiting plastic versus canalised phenotypes.
 
 ### ***Ecological consequences of reduced variation in physiological rates***
-While we found that variance in physiological rates decreases at high temperatures, being especially pronouced in terrestrial ectotherms, variance reductions in metabolism and performance were key traits most strongly impacted.
+Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
 Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems [@hendry2016key].
@@
 Maintaining intrapopulaton variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-Nonetheless, few studies have explored the consequences that variation in physiological traits have for population dynamics.
-Those studies that have, have shown that such variation can have important implications.
 For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
-They showed that greater between-individual variation in DEB parameters led to less extreme population oscillations compared to scenarios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face an onslaught of ecological and evolutionary challenges which will mean greater rates of extinction and reduced productivity – predictions reinforced by several studies [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022].
-To date, however, an appreciation for the wide-reaching impacts that changes in variance may have on populations and communities remains limited.
-The ecological consequences of changes in physiological rate variance across aquatic and terrestrial ecosystems remain unclear.
-What we desperately need now are the development of theoretical models that better integrate intrapopulation variation into mechanistic physiological models or ones that better capture stochasticity such as individual based models.
-Our meta-analytic findings can help us better position ourselves to start asking questions about the ecological and evolutionary consequences of changes in variance in physiological rates.
+They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
+The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity.
+However, data testing the impacts of changes in variance on populations are limited to very few taxa.
+We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
+Our meta-analytic findings can be integrated into theoretical models by permitting model paramaters to capture biologically relevant variation.
+Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
 

### 2024-02-06 ms.qmd
Fixed Shin's comments and a few more of Franks. Checked with Shinichi about comparison of acclimation and relative variance.

@@
 Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean phenotypic responses to climate warming ignore how temperature may change phenotypic variability.
-Here, using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (changes in variance after accounting for changes in the mean) in physiological rates changes in response to increasing temperatures.
+Here, using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (changes in variance after accounting for changes in the mean, or coefficient of variation) in physiological rates changes in response to increasing temperatures.
 Using new effect size estimates and meta-analysis we show that acclimation of physiological rates and changes in their relative variance do not depend on past temperature variability and predictability experienced by a population at its geographical location; neither do these responses differ between life stages.
@@
 Freshwater ectotherms are capable of acclimating which is likely to be beneficial considering that reductions in relative variance in physiological rates at high temperatures is lower for freshwater species.
-In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not necssarily be beneficial.
+In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiological rates, suggesting acclimation may not necessarily be beneficial.
 Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a lack of capacity for acclimation, which highlights the vulnerability of terrestrial ectotherms to climate change.
@@
 Reversible phenotypic plasticity, such as acclimation, is expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
-Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to faciliate a rapid response to the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
+Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to facilitate a rapid response to the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
 However, the focus up to now has been primarily on mean physiological responses.
@@
 Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation repsonses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
 
@@
 Silhouettes are representative taxa of major clades within the tree.
-**B)** Acute and Acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
-**C)** $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
+**B)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
+**C)** Mean $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
 Note there were no differences between acute and acclimation $Q_{10}$ types.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species."
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI)."
 #| warning: false
@@
 Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
-Reduced relative variance was particularly prominant for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
+Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
 
@@
 #| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult and juevenile life-history stages for Marine (A & D), Freshwater (B & E) and Terrestrial (C & F) ectotherms.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult and juvenile life-history stages for Marine (A & D), Freshwater (B & E) and Terrestrial (C & F) ectotherms.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-Raw data for both adult and jeunvile life-history stages also presented but point are not separated by type for ease of presentation."
+Raw data for both adult and juvenile life-history stages also presented but point are not separated by type for ease of presentation."
 #| echo: false
@@
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value are shown for each habitat."
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
 
@@
 Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
-However, out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
+However, out of the `r length(unique(all_pred2$match))` populations, relative variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
 
 Predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
+Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
 
@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms is expected to decrease for ectotherms as temperatures increase, and this decrease is particularly pronouced in terrestrial ectotherms (~28%).
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease as temperatures increase, and this decrease is particularly pronouced in terrestrial ectotherms (~28%).
 Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation ($lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
@@
 
-### ***Potential evolutionary consequences of reduced plasticity and variance in physiologcial rates across ectotherms***
+### ***Potential evolutionary consequences of reduced plasticity and variance in physiological rates across ectotherms***
 
@@
 In freshwater habitats, acclimation responses will likely be beneficial considering that these effects are larger than reductions in relative variance in physiological rates.
-In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiolgical rates, suggesting acclimation may not be as beneficial.
-Relative variance reductions are particularly pronounced in terrestrial ectotherms and this coincides with a general inability to acclimate.
-Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely to provide adaptive benefits under climate change.
+In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiological rates, suggesting acclimation may not be as beneficial.
+Relative variance reductions are particularly pronounced in terrestrial ectotherms, and this coincides with a general inability to acclimate.
+Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold-acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely to provide adaptive benefits under climate change.
 Together, these findings highlight the vulnerability of terrestrial ectotherms to climate change.
+Theoretical models that capture the percentage changes in relative variances and acclimation responses we observe here are needed fully appreciate the biological consequences such changes have on ecological and evolutionary dynamics.
 It may be expected that reductions in variance of this magnitude impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
@@
 
-Theoretical models predict that plasticity should evolve in populatons experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time, making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
 Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
@@
 The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal enviroments many taxa actually experience in nature.
-Alternatively, lower predictability of thermal environments over time may make cues unreliable preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
-Randomly flutuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
+Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
+Alternatively, lower predictability of thermal environments over time may make cues unreliable, preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
+Randomly fluctuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
 For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
 @Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
-These findings, in combination with our results, suggests that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticty when environments are not predictable (either intrinsic physiological costs, fitness costs or both).
-The fact that aquatic ectotherms did show a capacity to acclimate suggest that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
+These findings, in combination with our results, suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable.
+The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
 
@@
 Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
-Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities and ecosystems [@hendry2016key].
+Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key].
 More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-Maintaining intrapopulaton variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
+Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
 For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
@@
 We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
-Our meta-analytic findings can be integrated into theoretical models by permitting model paramaters to capture biologically relevant variation.
+Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant variation.
 Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
 
-### ***Limitations***
-A number of limitations need to be recognised to better contextualise our results.
-First, and as mentioned above, the evolutionary implications of changes in relative variances in physiological rates is still unclear because we lack a full understanding of how much variation is genetic versus environmental, or how traits are related to fitness.
-Second, while we found no relationships between historical climate variability / predictability and capacity for plasticity this does not necessarily mean they are not important.
-There are major challenges to estimating realistic microthermal environments experienced by taxa; it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
-Third, while we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
+### ***Conclusions and future directions***
+
+Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking].
+While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
 Substantial variation in acclimation responses and changes in variance exist among populations as evidenced by wide prediction intervals.
-As such, finer scale analyses that look at acclimation responses *and* changes in relative variance will be beneficial for developing a better understanding of their interplay when considering how populations will be impacted by climate change.
-
-### ***Conclusions and future directions***
-
-Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking].
-Changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced and possibly more realistic predictions about the impacts of climate change on natural populations.
+Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced and possibly more realistic predictions about the impacts of climate change on natural populations.
 While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predictions.

### 2024-02-06 ms.qmd
Clean up of discussion

@@
 Phenotypic plasticity can allow populations to persist in the face of climate extremes by matching phenotypes to fitness optima, although this is not always the case [@noble2019plastic; @radersma2020plasticity] and there may be limits and costs to plasticity that constrain its expression [@Dewitt1998; but see @Murren2015].
-We show that plastic adjustments in physiological rates and changes in their relative variance differs across habitats.
+We show that plastic adjustments in physiological rates and changes in their relative variance differ across habitats.
 In freshwater habitats, acclimation responses will likely be beneficial considering that these effects are larger than reductions in relative variance in physiological rates.
@@
 ### ***Plasticity and variance in physiological rates do not differ between life-stages***
-Interestingly, there were no major differences in acclimation or reductions in physiological variance between life-stages across habitat types.
+Interestingly, there were no differences in acclimation or reductions in physiological variance between life-stages across habitat types.
 Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
@@
 Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
-However, very few studies measured multiple life-history stages within the same population.
-In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same populations.
-A better understanding of the microthermal environments experienced by different life-stages will also be important in understanding why plasticity may or may not differ among life-stages.
+However, very few studies measure multiple life-history stages within the same population.
+In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
 
@@
 They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity.
+The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
 However, data testing the impacts of changes in variance on populations are limited to very few taxa.
 We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
-Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant variation.
+Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant changes in variation.
 Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.

### 2024-02-06 ms.qmd
Need to rim down abstract so doing that

@@
 Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean phenotypic responses to climate warming ignore how temperature may change phenotypic variability.
-Here, using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (changes in variance after accounting for changes in the mean, or coefficient of variation) in physiological rates changes in response to increasing temperatures.
-Using new effect size estimates and meta-analysis we show that acclimation of physiological rates and changes in their relative variance do not depend on past temperature variability and predictability experienced by a population at its geographical location; neither do these responses differ between life stages.
-Across habitats relative variance in physiological rates decreased at higher temperatures.
-Freshwater ectotherms are capable of acclimating which is likely to be beneficial considering that reductions in relative variance in physiological rates at high temperatures is lower for freshwater species.
-In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiological rates, suggesting acclimation may not necessarily be beneficial.
-Relative variance reductions are particularly pronounced for terrestrial ectotherms and this coincides with a lack of capacity for acclimation, which highlights the vulnerability of terrestrial ectotherms to climate change.
-Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance, challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
-Reductions in physiological rate variance at high temperatures may further have important ecological ramifications that impact population and ecosystem processes that cascade to affect population and community productivity.
+Using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (i.e., coefficient of variation) in physiological rates change at high temperatures.
+Using new effect size estimates and meta-analysis, we show that across habitats relative variance in physiological rates decreased at higher temperatures.
+Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
+In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiological rates.
+Relative variance reductions are particularly pronounced for terrestrial ectotherms, and this coincides with a lack of capacity for acclimation highlighting the vulnerability of terrestrial ectotherms to climate change.
+Neither life-history stage nor past climate explained effect variability.
+Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance that may have important evolutionary and ecological ramifications, challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
 

### 2024-02-06 ms.qmd
Small update

@@
 Neither life-history stage nor past climate explained effect variability.
-Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance that may have important evolutionary and ecological ramifications, challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
+Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance that may have important evolutionary and ecological ramifications challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
 

### 2024-02-07 ms.qmd
Abstarct reworked

@@
 Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
-In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiological rates.
-Relative variance reductions are particularly pronounced for terrestrial ectotherms, and this coincides with a lack of capacity for acclimation highlighting the vulnerability of terrestrial ectotherms to climate change.
+Marine organisms also showed a capacity to acclimate to higher temperatures but they coincide with a reduction in relative variance in physiological rates.
+Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincides with a lack of capacity for acclimation highlighting the vulnerability of terrestrial ectotherms to climate change.
 Neither life-history stage nor past climate explained effect variability.
-Our results emphasise how beneficial acclimation responses may be offset by reductions in physiological rate variance that may have important evolutionary and ecological ramifications challenging the notion that plasticity will be sufficient to counteract climate change effects on populations.
+Our results emphasise how beneficial acclimation responses may trade-off with reductions in physiological rate variance that could have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations in the future.
 

### 2024-02-07 ms.qmd
Re-order paragraphs

@@
 Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease as temperatures increase, and this decrease is particularly pronouced in terrestrial ectotherms (~28%).
-Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation ($lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
-15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1).
+Decreases in the relative variance of physiological rates trade-off with the expected benefits from acclimation in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
+15% reduction in relative variance at high temperatures; *terrestrial*: no acclimation vs 28% reduction in relative variance at high temperatures; @fig-1).
 Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
@@
 Both are predicted to impact the capacity of populations to evolve under climate change [@hoffmann2011climate; @urban2023and].
-
-### ***Plasticity and variance in physiological rates do not differ between life-stages***
-Interestingly, there were no differences in acclimation or reductions in physiological variance between life-stages across habitat types.
-Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
-However, our results highlight that early life stages are not likely to be protected from the impacts of climate change.
-Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
-Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticity.
-Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
-However, very few studies measure multiple life-history stages within the same population.
-In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
 
@@
 
+### ***Plasticity and variance in physiological rates do not differ between life-stages***
+Interestingly, there were no differences in acclimation or reductions in physiological variance between life-stages across habitat types.
+Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+However, our results highlight that early life stages are not likely to be protected from the impacts of climate change.
+Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
+In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
+Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticity.
+Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
+However, very few studies measure multiple life-history stages within the same population.
+In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
+
 ### ***Ecological consequences of reduced variation in physiological rates***
 Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
-Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key].
+Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can].
 More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].

### 2024-02-07 ms.qmd
Rejig the first section of discussion to incoperate mroe species distributoon modelling

--- 2024-02-07 ms.qmd
@@
 
-Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease as temperatures increase, and this decrease is particularly pronouced in terrestrial ectotherms (~28%).
-Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation ($lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs.
-15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1).
+Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can].
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease to varying extents across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
 Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention.
+Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations that require further empirical and theoretical attention.
 We discuss our findings in the context of the current literature and highlight key areas for future research.
 
-### ***Potential evolutionary consequences of reduced plasticity and variance in physiological rates across ectotherms***
-
-Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate].
-Phenotypic plasticity can allow populations to persist in the face of climate extremes by matching phenotypes to fitness optima, although this is not always the case [@noble2019plastic; @radersma2020plasticity] and there may be limits and costs to plasticity that constrain its expression [@Dewitt1998; but see @Murren2015].
+### ***Potential consequences of reduced plasticity and variance in physiological rates across ectotherms***
+
+Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can].
+For example, incorperating phenotypic plasticity and adaptation into species distribution models has been shown to dampen the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
+It addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, impacting a population's capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
+
 We show that plastic adjustments in physiological rates and changes in their relative variance differ across habitats.
-In freshwater habitats, acclimation responses will likely be beneficial considering that these effects are larger than reductions in relative variance in physiological rates.
-In contrast, acclimation responses of marine organisms coincide with a nearly equal reduction in relative variance in physiological rates, suggesting acclimation may not be as beneficial.
-Relative variance reductions are particularly pronounced in terrestrial ectotherms, and this coincides with a general inability to acclimate.
-Considering acute responses of animals acclimated to high temperatures are generally slightly elevated compared to cold-acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization is not likely to provide adaptive benefits under climate change.
-Together, these findings highlight the vulnerability of terrestrial ectotherms to climate change.
-Theoretical models that capture the percentage changes in relative variances and acclimation responses we observe here are needed fully appreciate the biological consequences such changes have on ecological and evolutionary dynamics.
-It may be expected that reductions in variance of this magnitude impact the 'opportunity for selection' by reducing the strength of selection and/or impacting underlying genetic variance exposed to selection.
-Both are predicted to impact the capacity of populations to evolve under climate change [@hoffmann2011climate; @urban2023and].
+In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance in physiological rates providing more raw material for selection to operate.
+In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance in physiological rates, which may trade-off with the beneficial effects that acclimation provides at high temperatures.
+In terrestrial ectotherms, relative variance reductions are particularly pronounced and this coincides with a general inability to acclimate.
+Considering acute physiological rates of animals acclimated to high temperatures are generally elevated compared to cold-acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization may not always provide adaptive benefits under climate change, particularly when considering changes in relative variance.
+
+Our findings highlight the potential vulnerability of terrestrial and marine ectotherms to climate change.
+Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warnming.
+Our results also define the range of responses observed across diverse taxa (e.g., through prediction intervals) that also provide opportunities to incorperate realistic biological variation into the modelling process.
+Incorperating relavant variation in such change are needed fully appreciate the biological consequences such changes have on ecological and evolutionary dynamics (@bush2016incorporating).
 
@@
 In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
+
+### ***Ecological consequences of reduced variation in physiological rates***
+Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
+Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
+For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
+The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
+However, data testing the impacts of changes in variance on populations are limited to very few taxa.
+We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
+Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant changes in variation.
+Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
 
@@
 The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-
-### ***Ecological consequences of reduced variation in physiological rates***
-Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
-Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
-They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
-However, data testing the impacts of changes in variance on populations are limited to very few taxa.
-We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
-Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant changes in variation.
-Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
 

### 2024-02-08 ms.qmd
Re-organisation for NEE

@@
 
-## **Introduction**
+## **Main**
 
 Climate change is expected to result in warmer but also more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Evolutionary theory predicts that greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016].
+Evolutionary theory predicts that greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
 Without plasticity or adaptation, high extinction rates are predicted unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
@@
 Low oxygen availability may be a major factor influencing the vulnerability of aquatic ecosystems, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
-Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms which may have important cascading effects on energy transfer and productivity across different ecosystems.
+Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms which may have important cascading effects on energy transfer and productivity across different ecosystems [@seebacher2023can; @barneche2021warming].
 
@@
 4) How are means and variances in physiological rates expected to change under climate change?
+
+```{r lnrrq10}
+#| label: lnrrq10
+#| echo: false
+#| cache: true
+#| message: false
+#| warning: false
+#| include: false
+
+#############
+## lnRRQ10 ##
+#############
+##################################################
+# Organise the data and prune tree
+##################################################
+# Subset the data
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Check and prune tree
+tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor <- vcv(tree_lnrr, cor = TRUE)
+        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
+
+# Found some other data entry problems from old dataset.
+Sample sizes are decimals.
+That's not correct.
+It has to be an integer.
+These are not the new data that we entered.
+Data now checked.
+Seemed to have resulted in a 'frame shift' in some data.
+Not sure how that happened, but it's now fixed.
+#hist(lnRRQ10_data$V)
+
+# Studies with big V, why? Check N
+lnRRQ10_data %>% filter(V >= 2)
+
+# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
+sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
+
+##################################################
+# Model 1.1: Intercept only model. 
+##################################################
+rerun = FALSE
+if(rerun){
+  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.1
+  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
+  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
+} else{ 
+  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
+model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
+}
+
+# Heterogeneity analysis
+   w <- with(lnRRQ10_data, 1/V) # weights
+  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
+  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
+
+    res <- posteriors_1.1[,"sigma"]
+   stdy <- posteriors_1.1[,"record_num"]
+  phylo <- posteriors_1.1[,"species_full"]
+    spp <- posteriors_1.1[,"spp"]
+  trait <- posteriors_1.1[,"trait"]
+  total <- phylo + spp + res + sv + stdy + trait
+
+  # Calculate I2
+     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
+   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
+     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
+    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
+   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
+     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
+
+  # Table
+     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
+                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
+
+###################################################
+# Model 1.2: Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model with 
+  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.2
+  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
+  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
+
+  } else{
+        model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
+  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
+}
+
+####################################################
+## Model 1.2: Bayesian Contrasts
+###################################################
+  posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
+  f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
+  f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
+  m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
+  m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
+  t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
+  t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
+
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
+  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
+   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
+  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
+   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
+  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
+
+# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
+  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
+  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
+  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
+  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
+  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
+
+####################################################
+# Model 1.3's: Trait type varied by acclimation type
+# but data is separated by habitat to simplify
+####################################################
+# Filter to different habitats
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m") 
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f") 
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")
+
+    # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
+  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
+
+  # Prune tree
+   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo <- vcv(tree_m, corr = TRUE)
+       A_m <- vcv(tree_m, corr = FALSE)
+   f_phylo <- vcv(tree_f, corr = TRUE)
+       A_f <- vcv(tree_f, corr = FALSE)
+   t_phylo <- vcv(tree_t, corr = TRUE)
+       A_t <- vcv(tree_t, corr = FALSE)
+
+if(rerun){
+   # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
+   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = m_phylo), dfs = "contain", 
+                              test = "t", 
+                              data = lnRRQ10_data_m)
+
+  model1.3_m_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = m_phylo), 
+                              struct = "HCS", rho = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_m)
+
+  # Check k is the same for both models (yes) and check which model is best supported
+    AICc1.3_m     <- AIC(model1.3_m) + AICc_correction(model1.3_m)
+    AICc1.3_m_het <- AIC(model1.3_m_het) + AICc_correction(model1.3_m_het)
+    # Clear support for this model. We'll go with this.
+    AICc1.3_m - AICc1.3_m_het
+
+  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 0)
+
+  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
+
+    # More realistic model with traits in freshwater species
+  model1.3_f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full =f_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_f)
+
+  # Heteroscedastic variance model for freshwater
+  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_f, method = "REML", control=list(iter.max=1000, rel.tol=1e-8))
+
+  ## Check support for two models
+  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het) # Clearly better supported.
+      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
+  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het
+
+  # Run the Bayesian equivalent of the top supported model. 
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
+
+    # More realistic model with traits in terrestrial species
+  model1.3_t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full =t_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_t)
+
+  # Heteroscedastic variance model for terrestrial
+  model1.3_t_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full =t_phylo), struct = "HCS", rho = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_t)
+
+  # Check which model is better
+    AICc_model1.3_t     <- AIC(model1.3_t) + AICc_correction(model1.3_t)
+    AICc_model1.3_t_het <- AIC(model1.3_t_het) + AICc_correction(model1.3_t_het)
+
+  #  Delta
+    AICc_model1.3_t - AICc_model1.3_t_het
+
+  # Bayesian model
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
+
+    # Save models
+  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
+  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
+  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
+
+  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
+  saveRDS(model1.3_f_het, file = "./output/models/lnRRQ10_1.3f_het")
+  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
+
+  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
+  saveRDS(model1.3_t_het, file = "./output/models/lnRRQ10_1.3t_het")
+  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")
+
+  } else{
+        model1.3_m <- readRDS("./output/models/lnRRQ10_1.3m")
+    model1.3_m_het <- readRDS("./output/models/lnRRQ10_1.3m_het")
+  model1.3_m_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_m")
+        model1.3_f <- readRDS("./output/models/lnRRQ10_1.3f")
+    model1.3_f_het <- readRDS("./output/models/lnRRQ10_1.3f_het")
+  model1.3_f_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_f")
+        model1.3_t <- readRDS("./output/models/lnRRQ10_1.3t")
+    model1.3_t_het <- readRDS("./output/models/lnRRQ10_1.3t_het")
+  model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
+}
+
+###########################################################
+## Model 1.4 - whether chance between q10 depends on life stage and habita
+###########################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model1.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.4
+  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
+  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
+
+  } else{
+        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
+  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
+}
+
+#######################################################################
+# Bayesian posteriors from model 1.4
+#######################################################################
+ # Create the data we want to make predcitions for. Just more intuitive
+  newdata <- data.frame( c_accl_time = 0, 
+                                type = as.factor(rep(c("acute", "acclim"))), 
+                             habitat = as.factor(rep(c("m", "f", "t"), each = 4)), 
+                           life.hist = as.factor(c("j", "a", "a", "j")))
+  newdata$type  <- relevel(newdata$type, ref = "acute")
+
+# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
+  X <- model.matrix(~c_accl_time + type*habitat*life.hist, data = newdata)
+
+# Extract posteriors
+  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
+
+# Now we can do all the calculations in one shot.
+         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
+     sum_pred <- apply(pred, 1, function(x) mean(x))
+  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
+  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
+
+# Create a summary dataset. 
+  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95)
+
+# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
+    # Marine 
+        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
+        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
+    # Freshwater
+        f_ad <- 4
+        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
+        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
+    # Terrestrial
+        t_ad <- 8
+        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
+        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species
+
+# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
+    # Marine 
+         m_acute <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
+        m_acclim <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
+    # Freshwater
+            f_ad <- 4
+         f_acute <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
+        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
+    # Terrestrial
+            t_ad <- 8
+         t_acute <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
+        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species
+
+  # Acute differences between a and j across all habitats
+     acute_all <- c(m_acute, f_acute, t_acute); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
+    acclim_all <- c(m_acclim, f_acclim, t_acclim)
+
+# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong. These two lines of code should roughly match
+#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
+#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")
+
+####################################################
+# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
+####################################################
+ # Goal here is to test the assumption that acute Q10's are different or not
+ lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
+
+ if(rerun){ 
+    model1.s1 <- metafor::rma.mv(effect_size ~  c_accl_time + name, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1, file = "./output/models/model1.s1")
+} else{
+      model1.s1 <-  readRDS(file = "./output/models/model1.s1")
+}
+
+```
+
+## **Results**
+
+Using a large database on physiolgical rates (@Seebacher2015-wi) for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10$^{\circ}$C temperature difference.
+These standardised effects sizes can be converted to percentage differences allowing us to compare the relative magnitude of rate changes resulting from acclimation and relative variance change at high temperatures.
+Acclimation responses could be measured by comparing acclimation $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acclimation}}}$) to acute $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acute}}}$) from experimental ectotherms acclimated to different temperatures.
+The difference in $lnRR_{Q_{10_{acclimation}}}$ compared to  $lnRR_{Q_{10_{acute}}}$ measures the extent of acclimation (i.e., plasticity).
+
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-1 A).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
+While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
+As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
+
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+
+### *Terrestrial and aquatic ectotherms differ in their capacity to acclimate but acclimation does not depend on life-history stage*
+
+Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
+
+Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+
+Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
+Acclimation capacity also did not vary by life-history stage given and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+
+```{r, lncvrq10}
+#| label: lncvrq10
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+#| cache: true
+
+#############
+  ## lnCVRQ10
+#############
+##################################################
+  # Organise the data and prune tree
+#################################################
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# Check and prune tree
+  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
+          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
+
+# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
+  #hist(lnCVRQ10_data$V)
+
+# Studies with big V, why? Check N
+  lnCVRQ10_data %>% filter(V >= 2)
+
+###################################################
+  # Model 2.1: Intercept only model.
+  # Used for heterogeneity analysis
+###################################################
+rerun = FALSE
+if(rerun){
+  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.1
+  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
+  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
+} else{ 
+        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
+  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
+}
+
+# Heterogeneity analysis
+   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
+  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
+  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
+
+    res_cvr <- posteriors_2.1[,"sigma"]
+   stdy_cvr <- posteriors_2.1[,"record_num"]
+  phylo_cvr <- posteriors_2.1[,"species_full"]
+    spp_cvr <- posteriors_2.1[,"spp"]
+  trait_cvr <- posteriors_2.1[,"trait"]
+  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
+
+  # Calculate I2
+     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
+   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
+     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
+    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
+   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
+     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
+
+  # Table
+     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
+                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
+
+###################################################
+  # Model 2.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
+  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
+
+  } else{
+        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
+  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
+}
+
+######################################################
+  # Bayesian Contrasts
+######################################################
+
+  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
+  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
+  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
+  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
+  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
+  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
+  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
+
+# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
+It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
+  # First get sample sizes
+    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
+    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
+    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+
+  # Lets now convert these to a %
+    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
+    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
+    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
+
+###################################################
+  # Model 2.3: Model controlling for acclimation time, 
+  # type and trait category assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
+  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
+
+  # We can also run subsets for each habitat
+   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
+       A_m_cvr <- vcv(tree_m_cvr, corr = FALSE)
+   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
+       A_f_cvr <- vcv(tree_f_cvr, corr = FALSE)
+   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
+       A_t_cvr <- vcv(tree_t_cvr, corr = FALSE)
+
+  model2.3f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "f"))
+
+  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
+
+  model2.3m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "m"))
+  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
+
+  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
+  model2.3t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "t"))
+  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
+
+  } else{
+        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
+        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
+        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
+        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
+  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
+}
+
+###################################################
+  # Model 2.4: Model controlling for acclimation time, 
+  # type and life history stage assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model
+  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
+  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
+
+  } else{
+        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
+  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
+}
+
+```
+
+```{r, fig-1}
+#| label: fig-1
+#| fig-cap: "Taxonomic distribution of acute and acclimation $Q_{10}$ estimates across major habitats.
+**A)** Phylogenetic distribution of taxa contained within the data.
+The total number of acute and acclimation type Q10 effect sizes are highlighted as well as whether the taxa is marine, freshwater or terrestrial.
+Silhouettes are representative taxa of major clades within the tree.
+**B)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
+**C)** Mean $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
+Note there were no differences between acute and acclimation $Q_{10}$ types.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI)."
+#| warning: false
+#| echo: false
+
+# Load and plot Figure 1.
+Note that this figure was derived using 3 separate code chunks described below.
+Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
+  fig1 <- image_read("./output/figures/fig1_final.png")
+  fig1
+##################
+  # Figure 1a plot
+##################
+   # Map data to tree. Just one variable for now
+      d <- ggtree(tree, layout="circular") %<+% tree_data
+
+      # Plot the tree
+      scales1 <- c("#053061", "#D1E5F0", "#67001F")
+      scales2 <- c("#053061", "#E7E0DB", "#67001F")
+      p1 <- d + 
+            #geom_tiplab(size=2, offset = 10) + 
+            geom_tippoint(aes(color=habitat), size = 2) +
+            labs(color = "Habitat") + 
+            scale_colour_manual(values = scales1)
+
+      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
+      matrix_data <- as.data.frame(data_wide %>%
+                  mutate(trait_category = ifelse(trait_category %in% 
+                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
+                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
+                  group_by(species_full, trait_category)   %>% 
+                  summarise(n = n())                       %>% 
+                  spread(trait_category, n, fill = 0))
+
+      row.names(matrix_data) <- matrix_data$species_full
+      matrix_data <- matrix_data[,c(2:8)]
+
+      colnames(matrix_data)[c(1,3,6)] <- c("Antioxidants", "Metabolic Enzymes", "Other")
+
+      # Alternatively, summarise total effect sizes per species for acute and acclimation
+      matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
+                      group_by(species_full, type) %>% 
+                      summarise(n = n()) %>% 
+                      spread(type, n, fill = 0) %>% data.frame()
+                     # mutate(acclim = as.character(cut(acclim, breaks = c(0,15, 20, 25, 30, 40, 50))),
+                      #        acute = as.character(cut(acute, breaks = c(0,15, 20, 25, 30, 40, 50))))
+
+      row.names(matrix_data2) <- matrix_data2$species_full
+      matrix_data2 <- matrix_data2[,2:3]
+
+      # Plot a heatmap of N for each trait around the phylogeny.
+   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  colnames = FALSE, 
+               colnames_position="bottom", legend_title = "N", 
+               colnames_angle=360, colnames_offset_y = 0, colnames_offset_x = -1.5, 
+               hjust=0, font.size=3, width = 0.35) + 
+                scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
+
+ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
+
+##################
+  # Figure 1b plot
+##################
+col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+  k_lnrr <- manual_extract(model1.2, mod = "habitat", group = "record_num", exclude = NULL)
+
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 8, branch.size = 2) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical") +
+
+  annotate("text", x = 1.5, y = 0, 
+         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 1.20, y = 1.4, 
+         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
+  annotate("text", x = 1.20, y = -0.8, label = "P < 0.001", hjust = 0, size = 6) +
+
+  annotate("text", x = 2.5, y = 0, 
+         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
+  annotate("text", x = 2.20, y = 1.4, 
+         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 6) +
+  annotate("text", x = 2.20, y = -0.8, label = "P = 0.01", hjust = 0, size = 6) +
+
+  annotate("text", x = 3.5, y = 0, 
+         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
+  annotate("text", x = 3.20, y = 1.4, 
+         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 6) +
+  annotate("text", x = 3.20, y = -0.8, label = "P = 0.36", hjust = 0, size = 6) +
+
+  scale_fill_manual(values = c(col)) + ylim(-0.8, 2) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.7, size = 5)
+
+  p1.2 <- p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
+        axis.text = element_text(size = 15), legend.title = element_text(size = 15),
+                               legend.text = element_text(size = 15),
+                               title = element_text(size = 24))
+
+  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 9.1, height = 9.2, device = "png")
+
+##################
+  # Figure 1c plot
+################## 
+  # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
+But, there is a clear reduction in between individual variance for terrestrial species.
+As temperature get hotter then the variance in physiological rates decreases.
+This is not true of aquatic systems.
+
+  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
+
+  x1 = 1.4
+  x2 = 2.4
+  x3 = 3.4
+
+  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 8, branch.size = 2, k.pos = "none") +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+  annotate("text", x = x1, y = -2, 
+           label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = x1-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = x1-0.15, y = 1, 
+           label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
+
+  annotate("text", x = x2, y = -2, 
+           label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = x2-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) +
+  annotate("text", x = x2-0.15, y = 1, 
+           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
+
+  annotate("text", x = x3, y = -2, 
+           label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = x3-0.15, y = 1, 
+           label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
+    annotate("text", x = x3-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 2) + 
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5)
+
+  p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 15),
+                                       legend.title = element_text(size = 15),
+                               legend.text = element_text(size = 15),
+                               title = element_text(size = 24))
+
+  ggsave(p2, filename = "./output/figures/fig2.png", width = 9.3, height = 8.8)
+
+```
+
+### *Reduced variation in physiological rates in terrestrial and marine ectotherms*
+
+Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiologcial rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
+In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
+
+The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between study and trait differences (see Supplement;  @fig-s3).
+Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
+Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
+
+```{r, fig-cvrlh}
+#| label: fig-cvrlh
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult and juvenile life-history stages for Marine (A & D), Freshwater (B & E) and Terrestrial (C & F) ectotherms.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Raw data for both adult and juvenile life-history stages also presented but point are not separated by type for ease of presentation."
+#| echo: false
+#| warning: false
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 24),
+                               axis.text.y = element_text(size = 15),
+                               axis.text.x = element_text(size = 15),
+                              legend.title = element_text(size = 15),
+                               legend.text = element_text(size = 15),
+                               title = element_text(size = 24))}
+branch.size = 2
+trunk.size = 5
+
+p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1, 1.8)
+
+p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45,)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1, 1.8)
+
+p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) +  ylim(-1, 1.8)
+
+p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-2.5, 2.5)
+
+p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
+
+p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
+
+fig4 <-(p1 | p2 | p3) / (p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig4, filename = "./output/figures/fig4_lh.pdf", width = 19, height = 12, device = "pdf")
+
+fig4 <- magick::image_read("./output/figures/fig4_lh.pdf")
+fig4
+```
+
+```{r, wildlnRR10}
+#| label: wildlnRR10
+#| cache: true
+#| include: false
+#| echo: false
+#| warning: false
+#| 
+#######################################
+  ## lnRRQ10 from Wild Populations ##
+#######################################
+##################################################
+  # Organise the data and prune tree
+##################################################
+
+# Bring in Climate data
+climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+# Create a match column.
+climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+
+# Subset the data
+lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnRRQ10_data_wild <- left_join(lnRRQ10_data_wild, climate2, by = "match")
+
+# Check and prune tree
+tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
+        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale data
+        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
+                                                          acf_all_c = scale(acf_all))
+
+###################################################
+  # Model 3.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.2
+  saveRDS(model3.2, file = "./output/models/lnRRQ10_3.2")
+  saveRDS(model3.2_bayes, file = "./output/models/lnRRQ10_3.2_bayes")
+
+  } else{
+        model3.2 <- readRDS("./output/models/lnRRQ10_3.2")
+  model3.2_bayes <- readRDS("./output/models/lnRRQ10_3.2_bayes")
+}
+
+####################################################
+  ## Model 3.2: Bayesian Contrasts
+###################################################
+  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
+  f_acute_wild  <- posteriors_3.2[,"b_Intercept"]
+  f_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
+  m_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
+  m_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
+  t_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
+
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10_wild <- exp(f_acute_wild) ; mean(f_acute_Q10_wild)
+  f_acclim_Q10_wild <- exp(f_acclim_wild); mean(f_acclim_Q10_wild)
+   m_acute_Q10_wild <- exp(m_acute_wild) ; mean(f_acute_Q10_wild)
+  m_acclim_Q10_wild <- exp(m_acclim_wild); mean(f_acclim_Q10_wild)
+   t_acute_Q10_wild <- exp(t_acute_wild) ; mean(t_acute_Q10_wild)
+  t_acclim_Q10_wild <- exp(t_acclim_wild); mean(t_acclim_Q10_wild)
+
+# % change in acclimation on log scale; relative to the acute measurements
+  change_f_wild <- ((f_acclim_wild - f_acute_wild) / f_acute_wild) *100; quantile(change_f_wild, c(0.025, 0.975))
+  change_m_wild <- ((m_acclim_wild - m_acute_wild) / m_acute_wild) *100; quantile(change_m_wild, c(0.025, 0.975))
+  change_t_wild <- ((t_acclim_wild - t_acute_wild) / t_acute_wild) *100; quantile(change_t_wild, c(0.025, 0.975))
+
+####################################################
+  # Model 3.3: Model environmental variability by acute 
+  #  acclim 
+####################################################
+  rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.3, file = "./output/models/lnRRQ10_3.3")
+  saveRDS(model3.3_bayes, file = "./output/models/lnRRQ10_3.3_bayes")
+
+  } else{
+        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
+  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
+}
+
+################################################################
+  # Model 3.4: Environmental autocorrelation model by acute/acclim
+################################################################
+if(rerun){
+  # More realistic model with 
+  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model3.4, file = "./output/models/lnRRQ10_3.4")
+  saveRDS(model3.4_bayes, file = "./output/models/lnRRQ10_3.4_bayes")
+
+  } else{
+        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
+  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
+}
+
+################################################################
+  # Model 3.5: Environmental variability  model
+################################################################
+if(rerun){
+  # More realistic model with 
+  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.5
+  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
+  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")
+
+  } else{
+        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
+  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
+}
+
+################################################################
+  # Model 3.6: Environmental autocorrelation model
+################################################################
+if(rerun){
+  # More realistic model with 
+  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  # Save model3.6
+  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
+  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")
+
+  } else{
+        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
+  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
+}
+
+################################################################
+  # Model 3.7: Environmental variability and autocorrelation model
+################################################################
+
+if(rerun){
+  # More realistic model with 
+  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild)
+
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+
+  # Save model3.7
+  saveRDS(model3.7, file = "./output/models/lnRRQ10_3.7")
+  saveRDS(model3.7_bayes, file = "./output/models/lnRRQ10_3.7_bayes")
+
+  } else{
+        model3.7 <- readRDS("./output/models/lnRRQ10_3.7")
+  model3.7_bayes <- readRDS("./output/models/lnRRQ10_3.7_bayes")
+}
+
+############################################################################################
+# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
+# differently in each habitat
+############################################################################################  
+  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+if(rerun){
+  # More realistic model with 
+  model3.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
+  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
+
+  } else{
+        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
+  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 3.8
+#################################################
+ posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
+
+    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
+    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
+    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
+
+############################################################################################
+# Model 3.9: Acclimatization lnRRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################
+
+if(rerun){
+  # More realistic model with 
+  model3.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.9, file = "./output/models/lnRRQ10_3.9")
+  saveRDS(model3.9_bayes, file = "./output/models/lnRRQ10_3.9_bayes")
+
+  } else{
+        model3.9 <- readRDS("./output/models/lnRRQ10_3.9")
+  model3.9_bayes <- readRDS("./output/models/lnRRQ10_3.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 3.9
+#################################################
+ posteriors <- posterior_samples(model3.9_bayes, "^b")
+
+    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); mean(slope_f); quantile(slope_f, c(0.025, 0.975))
+    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
+    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
+
+##################################################
+    # Model 3.8, 3.9 and 3.10 - Habitat subset
+##################################################
+    # Subset data to habitat
+    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+if(rerun){
+    # Terrestrial Models
+    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+    saveRDS(model3.8_t, "./output/models/model3.8_t")
+
+    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+    saveRDS(model3.9_t, "./output/models/model3.9_t")
+
+        # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+     saveRDS(model3.10_t, "./output/models/model3.10_t")
+    # Freshwater Models
+    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+    saveRDS(model3.8_f, "./output/models/model3.8_f")
+
+    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+
+    saveRDS(model3.9_f, "./output/models/model3.9_f")
+
+       # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+
+     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+      saveRDS(model3.10_f, "./output/models/model3.10_f")
+    # Marine Models
+      model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+        saveRDS(model3.8_m, "./output/models/model3.8_m")
+
+    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+    saveRDS(model3.9_m, "./output/models/model3.9_m")
+    # Model just quickly tests if we are missing an important interaction.
+It may not necessarily be just about the variability.
+We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
+We want predictability AND variance
+
+    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+    saveRDS(model3.10_m, "./output/models/model3.10_m")
+  } else {
+     model3.8_t <- readRDS("./output/models/model3.8_t")
+     model3.9_t <- readRDS("./output/models/model3.9_t")
+    model3.10_t <- readRDS("./output/models/model3.10_t")
+     model3.8_f <- readRDS("./output/models/model3.8_f")
+     model3.9_f <- readRDS("./output/models/model3.9_f")
+    model3.10_f <- readRDS("./output/models/model3.10_f")
+     model3.9_m <- readRDS("./output/models/model3.9_m")
+    model3.10_m <- readRDS("./output/models/model3.10_m")
+     model3.8_m <- readRDS("./output/models/model3.8_m")
+}
+
+       r2_t <- r2_ml(model3.9_t)[1]    
+```
+
+```{r wildlncvr}
+#| label: wildlncvr
+#| cache: true
+#| include: false
+#| echo: false
+#| warning: false
+#| 
+#######################################
+  ## lnCVRQ10 from Wild Populations ##
+#######################################
+##################################################
+  # Organise the data and prune tree
+##################################################
+
+# Bring in  historial climate data
+climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+# Create a match column.
+climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+
+# Populations and species?
+pop_spp_w <- climate2[complete.cases(climate2),]
+
+# Subset the data
+lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+                              mutate(spp = species_full, 
+                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
+                                     match = interaction(spp, lat, long))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
+
+# Look at the environment details across different habitats. Seems very similar. *** Check with ALEX ***
+  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(cv), mean(acf_all))
+
+# Check and prune tree
+tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
+        A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale environment variables
+    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
+                                                        acf_all_c = scale(acf_all))
+
+###################################################
+  # Model 4.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model3.2
+  saveRDS(model4.2, file = "./output/models/lnCVRQ10_4.2")
+  saveRDS(model4.2_bayes, file = "./output/models/lnCVRQ10_4.2_bayes")
+
+  } else{
+        model4.2 <- readRDS("./output/models/lnCVRQ10_4.2")
+  model4.2_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
+}
+
+####################################################
+  ## Model 4.2: Bayesian Contrasts
+###################################################
+  posteriors_4.2 <- posterior_samples(model4.2_bayes, pars = "^b")
+  f_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"]
+  f_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_typeacclim"]
+  m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
+  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatm"]
+  t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
+  t_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatt"]
+
+# CVRQ10 values for each category.
+   f_acute_Q10_wild_cvr <- exp(f_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
+  f_acclim_Q10_wild_cvr <- exp(f_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
+   m_acute_Q10_wild_cvr <- exp(m_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
+  m_acclim_Q10_wild_cvr <- exp(m_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
+   t_acute_Q10_wild_cvr <- exp(t_acute_wild_cvr) ; mean(t_acute_Q10_wild_cvr)
+  t_acclim_Q10_wild_cvr <- exp(t_acclim_wild_cvr); mean(t_acclim_Q10_wild_cvr)
+
+# % change in acclimation on log scale
+  change_f_wild_cvr <- ((f_acclim_wild_cvr - f_acute_wild_cvr) / f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
+  change_m_wild_cvr <- ((m_acclim_wild_cvr - m_acute_wild_cvr) /m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
+  change_t_wild_cvr <- ((t_acclim_wild_cvr - t_acute_wild_cvr)/t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
+
+####################################################
+  # Model 4.3: Model environmental variability by acute/acclim
+####################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.3
+  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
+  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
+
+  } else{
+        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
+  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
+}
+
+################################################################
+  # Model 4.4: Environmental autocorrelation model by acute/acclim
+################################################################
+if(rerun){
+  # More realistic model with 
+  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
+  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
+
+  } else{
+        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
+  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
+}
+
+################################################################
+  # Model 4.5: Environmental variability
+################################################################
+if(rerun){
+  # More realistic model with 
+  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.5
+  saveRDS(model4.5, file = "./output/models/lnCVRQ10_4.5")
+  saveRDS(model4.5_bayes, file = "./output/models/lnCVRQ10_4.5_bayes")
+
+  } else{
+        model4.5 <- readRDS("./output/models/lnCVRQ10_4.5")
+  model4.5_bayes <- readRDS("./output/models/lnCVRQ10_4.5_bayes")
+}
+
+################################################################
+  # Model 4.6: Environmental autocorrelation model 
+################################################################
+if(rerun){
+  # More realistic model with 
+  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.6
+  saveRDS(model4.6, file = "./output/models/lnCVRQ10_4.6")
+  saveRDS(model4.6_bayes, file = "./output/models/lnCVRQ10_4.6_bayes")
+
+  } else{
+        model4.6 <- readRDS("./output/models/lnCVRQ10_4.6")
+  model4.6_bayes <- readRDS("./output/models/lnCVRQ10_4.6_bayes")
+}
+
+################################################################
+  # Model 4.7: Environmental autocorrelation and variability
+################################################################
+if(rerun){
+  # More realistic model with 
+  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.7
+  saveRDS(model4.7, file = "./output/models/lnCVRQ10_4.7")
+  saveRDS(model4.7_bayes, file = "./output/models/lnCVRQ10_4.7_bayes")
+
+  } else{
+        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")   ### DIFFERENT 
+  #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
+}
+
+############################################################################################
+  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
+  # differently in each habitat
+############################################################################################  
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+if(rerun){
+  # More realistic model with 
+  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model4.8
+  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
+  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
+
+  } else{
+        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
+  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.8
+#################################################
+ posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
+
+    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
+    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
+    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
+
+############################################################################################
+# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################
+
+if(rerun){
+  # More realistic model with 
+  model4.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model4.9, file = "./output/models/lnRRQ10_4.9")
+  saveRDS(model4.9_bayes, file = "./output/models/lnRRQ10_4.9_bayes")
+
+  } else{
+        model4.9 <- readRDS("./output/models/lnRRQ10_4.9")
+  model4.9_bayes <- readRDS("./output/models/lnRRQ10_4.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.9
+#################################################
+ posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
+
+    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
+    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
+    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
+
+```
+
+### *Past climate does not influence acclimation capacity or expected change in variance*
+
+Using the ERA5 climate model, we extracted a 30-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution).
+We used the historical temperature data for each geographical location to calculate a measure of thermal variability and predcitability (see *Methods*).
+Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
+
+```{r, fig-4}
+#| label: fig-4
+#| fig-align: center
+#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
+Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
+
+size_axis = 18
+# CV
+dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
+                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
+                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
+                      title = c("Freshwater", "Marine", "Terrestrial"), 
+                      condition = c("f", "m", "t"),
+                      x = rep(1.2, 3),
+                      y = rep(-1.2, 3))
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
+theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
+
+  # ACF
+dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
+                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
+                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
+                      condition = c("f", "m", "t"),
+                      x = rep(-2.8, 3),
+                      y = rep(-1.2, 3))
+
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text2, aes(x = x+1, y = y, label =label), size = 5) + 
+geom_text(data = dat_text2, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
+geom_text(data = dat_text2, aes(x = x+1, y = y-0.65, label = p), size = 5) +
+theme(legend.position = "bottom", 
+      strip.background = element_blank(), 
+      strip.text = element_blank(), 
+      axis.text = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      legend.text = element_text(size = 16),
+      legend.title = element_text(size = 16))
+
+p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+
+ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
+
+  p8.1.2 <- image_read("./output/figures/fig8.png")
+  p8.1.2 
+```
+
+```{r, fig-5}
+#| label: fig-5
+#| fig-align: center
+#| fig-cap: "Predicted mean (thick black line) $lnCVR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
+Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
+
+size_axis = 18
+# CV
+dat_text <- data.frame(label = c(text(slope_f_4.9), text(slope_m_4.9), text(slope_t_4.9)),
+                      label2 = c(text(slope_f_4.9, b = FALSE), text(slope_m_4.9,b = FALSE), text(slope_t_4.9,b = FALSE)),
+                      p = c(p_text(slope_f_4.9), p_text(slope_m_4.9), p_text(slope_t_4.9)),
+                      title = c("Freshwater", "Marine", "Terrestrial"), 
+                      condition = c("f", "m", "t"),
+                      x = rep(1.2, 3),
+                      y = rep(-4, 3))
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text, aes(x = x, y = y-1, label = label2), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y-2, label = p), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y+10, label = title, size = 5)) + 
+theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
+
+  # ACF
+dat_text2 <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
+                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
+                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
+                      condition = c("f", "m", "t"),
+                      x = rep(-2.8, 3),
+                      y = rep(-4, 3))
+
+p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text2, aes(x = x+1, y = y, label = label), size = 5) + 
+geom_text(data = dat_text2, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
+geom_text(data = dat_text2, aes(x = x+1, y = y-1.2, label = p), size = 5) +
+theme(legend.position = "bottom", 
+      strip.background = element_blank(), 
+      strip.text = element_blank(), 
+      axis.text = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      legend.text = element_text(size = 16),
+      legend.title = element_text(size = 16))
+
+p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+
+ggsave(p9.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig9.png")
+
+  p9.1.2 <- image_read("./output/figures/fig9.png")
+  p9.1.2 
+```
+
+### Changes in physiological rate variance under climate change
+
+```{r, global}
+#| label: global
+#| echo: false
+#| include: false
+
+# Here, we want to make global predcitions, at the lat/long in the data for how the opportunity of selection is expected to change with climate change.
+How can we do this?
+Q10 effects already have temperature controls within the effect size.
+So, what we want is to be able to understand how Q10 changes with latitude and longitude.
+Once we know that, we an extarct how temperature is expected to change from our current levels to future levels.
+This will be in degrees C.
+Then, assuming no plasticity and evolution (big assumption) we can get a baseline change in variance for each site.
+We first need to adjust the predcited Q10 value so that it's at 1C temperaure, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
+This will adjust the predcited Q10 value to the change in 1 degree C.
+We can then multiply this by the temperature change expected at that location to get the % change in variance or acure/acclim response.
+We can then plot these globally.
+
+#############################
+rerun = FALSE
+if(rerun){
+
+  # Model lat and long. Need to exclude missing acclimdation data. That will make it easier to create predcitions and explore the model fit.
+
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(Longitude, Latitude) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
+
+  saveRDS(model5_bayes, file = "./output/models/lnCVRQ10_5_bayes")
+
+  } else{
+  model5_bayes <- readRDS("./output/models/lnCVRQ10_5_bayes")
+}
+
+# Lets explore the model and how it's predciting the real data
+  data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+
+# combine with predictions
+  data_w_pred <- cbind(data_w, predict(model5_bayes))
+
+# Fitted vs actual data
+  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Predicted Effect Size", y = "Observed Effect Size") + theme_classic() + 
+  geom_abline(intercept = 0, slope = 1)
+
+# Seems to be OK, but over and under-predciting at times.
+Lets explore the data for odd ball predictions to see if there are any obvious reasons why.
+T here are very few for the most part but lets see why sign changes occur which are most stricking differences.
+Sign changes indicate the observed data is completely opposite in sign to the predcited data
+
+#  Spot check of a bunch of studies doesn't show any obvious issues with the data.
+Note that data is repeated because acute and acclimated rates are calculated.
+We expect the rows of raw data for acute and acclim to be repeated even though these data are NOT all used to make the calculation.
+  sign_change_dat <- data_w_pred  %>% filter(sign(Estimate) != sign(effect_size))
+  #View(sign_change_dat)
+
+# Fitted by Lat/long Longitude, Latitude
+  ggplot(data = data_w_pred, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+
+# Observed by Lat/long
+  ggplot(data = data_w_pred, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
+
+# How much variation does this model explain.
+Need to do this manually because function doesn't seme to work on the model object.
+We need to remember that predcit will include random effect variances so we may need to exclude this
+  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
+  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)
+
+# sigma2_v = typical sampling error variance
+sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
+              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))
+
+# Now check that var fix from raw data and remove sampling variance. 
+  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
+
+# Extract the random effect variances
+  v_trait <- re_post$sd_trait__Intercept^2
+    v_spp <- re_post$sd_spp__Intercept^2
+    v_phy <- re_post$sd_species_full__Intercept^2
+    v_std <- re_post$sd_record_num__Intercept^2
+      v_r <- re_post$sd_obs__Intercept^2
+
+# Lets get the total variance for the random effects only
+  tot_re <- v_trait + v_spp + v_phy + v_std + v_r
+
+# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
+    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too
+
+    mean(r2) # Seems a bit high 0.5
+  quantile(r2, probs = c(0.025, 0.975)); #0.27-0.69
+
+# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
+  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2
+
+  mean(r2_2) #  0.48
+  quantile(r2_2, probs = c(0.025, 0.975)); #0.31-0.60
+
+######################################################################
+# Model predictions for terrestrial, marine and freshwater ectotherms
+######################################################################
+# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
+
+#############################
+## Terrestrial Ectotherms
+#############################
+
+  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+  new_data_t <- data.frame(
+      c_accl_time = 0,
+      V = 0,
+      trait = 0,
+      obs = 0, 
+      record_num = 0
+    )
+
+  # Create new dataframe with only unique values for predcition.
+  new_data_t2  <- cbind(terrest_data, new_data_t)
+
+  # We'll now make the predcitions from the model object using the new dataframe
+  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
+  # Lets merge predictions with the original data
+  terrest_data <- cbind(terrest_data, terre_pred)
+
+  # Test manual calculations.
+We can also set summary = FALSE and then do the calculations ourselves.
+Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE .
+These are extremely close, and I suspect are only different because sample_new_levels is sampling differently each time predict is run, so will be slightly different from run-to-run
+  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
+  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
+
+#############################
+## Marine ectotherms  
+#############################
+  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+
+  new_data_m <- data.frame(
+      c_accl_time = 0,
+      V = 0,
+      trait = 0,
+      obs = 0, 
+      record_num = 0
+    )
+
+  # Create new dataframe with only unique values for predcition.
+  new_data_m  <- cbind(marine_data, new_data_m)
+
+  # We'll now make the predcitions from the model object using the new dataframe
+  marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
+  # Lets merge predictions with the original data
+  marine_data <- cbind(marine_data, marine_pred)
+
+#############################
+## Freshwater ectotherms
+#############################
+  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+
+  new_data_f <- data.frame(
+      c_accl_time = 0,
+      V = 0,
+      trait = 0,
+      obs = 0, 
+      record_num = 0
+    )
+
+  # Create new dataframe with only unique values for predcition.
+  new_data_f  <- cbind(fresh_data, new_data_f)
+
+  # We'll now make the predcitions from the model object using the new dataframe
+  fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
+  # Lets merge predictions with the original data
+  fresh_data <- cbind(fresh_data, fresh_pred)
+
+# Now that we have all the predictions we can merge the data together.
+Note that species itself is not really that useful because each prediction at each latitude and longitude should incoperate the species effect.
+So we'll remove it.
+While I retain spp, it's still not totally specific to the species, but left it there so it's clear how these data match with the wild data.
+Note there are only 134 species because this is subset of the wild data.
+  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)  %>% mutate(uniques = interaction(spp, Latitude, Longitude))
+  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% dplyr::select(-species_full)
+  spp_wild  <- length(unique(sub_data$spp))
+```
+
+```{r, future_clim}
+#| label: future_clim
+#| echo: false
+#| warning: false
+#| include: false
+
+# Now we want to take the predictions from `global` and use this for future climate sceneios.
+We have the future temperatures expected for each location.
+We can then use the predicted Q10 values to calculate the expected change in variance.
+We can then plot these globally.
+
+# First, lets get the current and future temperature data for 2081-2085. We'll use the mean. 
+  future_temp <- read.csv("./output/climate_data/CanESM2_air_and_SST_timeseries.csv")
+
+# Now, lets summarise the mean for the current temps (i.e., 2018-2022)
+current_temps <-   future_temp  %>% 
+                   dplyr::select(Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(future_temp)))  %>% 
+                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15, match = interaction(Species, Latitude, Longitude))
+
+# Lets clean this data up.
+We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins.
+We'll now take the last 5 years of the future temperature 2096-2100
+  future_temps  <- future_temp  %>% 
+                  dplyr::select(Species, Latitude, Longitude,  grep("X2096|X2097|X2098|X2099|X2100", colnames(future_temp)))  %>% 
+                  mutate(mean = apply(.[, grep("X2096|X2097|X2098|X2099|X2100", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_future = mean - 273.15,  match = interaction(Species, Latitude, Longitude))
+
+# Now we can merge the climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
+
+  climate_data <- left_join(current_temps, future_temps, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
+
+# Lets look at future and current. Most, I would expect, should be above the line indicating higher future temperatures.
+  ggplot(data = climate_data, aes(x = Celc_curr, y = Celc_future)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Current Temperature (C)", y = "Future Temperature (C)") + theme_classic() + geom_abline(intercept = 0, slope = 1)
+
+# Lets have a global plot of temperature changes to see it sptially
+
+world_map = map_data("world") %>% 
+  filter(! long > 180)
+
+  map2_temp_proj <- ggplot() +
+    geom_map(
+      data = world_map, map = world_map,
+      aes(long, lat, map_id = region),
+      color = "black", fill = "lightgray") +
+    expand_limits(x = world_map$long, y = world_map$lat) +
+    coord_map("moll") +
+    geom_point(
+      data = climate_data[complete.cases(climate_data$T_change),],
+      aes(Longitude, Latitude, color = T_change),
+      alpha = 0.7, size = 5
+    ) + labs(x = "Longitude", y = "Latitude", color = TeX("$\\Delta$ Temp.
+($^\\circ$C)"), title = "Current (2018-2022) vs Future (2096-2100)") + scale_colour_gradient2(trans = "reverse") + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+
+# Now lets merge all_pred with the climate projections
+  # Simplify columns 
+  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude)
+
+  # Merge with model predcitions.
+This is the predcited lnCVRq10 for 10C change AT the specific latitude and longitude.
+We must assume that there is no plasticity or adaptation at each site to make projections
+  all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
+              left_join(., climate_data_new, by = "match")  %>% 
+              mutate(lnCVR_future = (Estimate / 10) * T_change,
+                      lnCVR_F_l95 = (Q2.5 / 10) * T_change,
+                      lnCVR_F_u95 = (Q97.5 / 10) * T_change, 
+                      per_change = (exp(lnCVR_future) - 1) * 100,
+                      per_change_l95 = (exp(lnCVR_F_l95) - 1) * 100,
+                      per_change_u95 = (exp(lnCVR_F_u95) - 1) * 100)
+
+  # Lets now use the whole posterior distribtion instead. This is a little hacky because the object is complicated
+
+######## *** THE CODE BELOW NEEDS SOME NEW CHECKING AS ABOVE WAS MODIFIED! ****
+
+  # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
+
+    all_pred2_no_sum <-  all_pred_no_sum %>% 
+                        mutate(match = interaction(spp, Latitude, Longitude))  %>% 
+                        left_join(., climate_data_new, by = "match")
+
+  # Second, lets convert each estimate to lncvr 1 degree C instead of 10...
+   all_pred2_no_sum2 <- all_pred2_no_sum %>%  
+                        mutate_if(colnames(.) %in% c(1:3200), lncvr_1c)
+
+  # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
+    all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]  <- all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)] * all_pred2_no_sum2$T_change
+
+  # Fourth, we can calculate the percentage change on the posterior
+    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]) - 1)*100
+
+  # Now we can summarise each.
+Here, what we are doing is taking the mean for each column.
+Effectively pooling across all the iterations for each dataset.
+This gives us an estimation of the mean change in variance across all locations/species., but it gives us 3200 point estimates of this mean.
+We can then use this to calculate the 95% CI's.
+    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) # Fixed an error here. It was applying the mean across columns, not rows!
+    mean(mean_perc)
+    quantile(mean_perc, 0.025)
+    quantile(mean_perc, 0.975)
+    hist(mean_perc)
+
+  # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
+  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE))
+  lapply(mean_perc_habitat, mean)
+  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
+  #lapply(mean_perc_habitat, hist)
+
+# Need to take a step back
+  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
+  # 2. Why are l95 and u95 for marine not working...Fixed
+  # 3. Apply to the posteriors, rather than summary. Done
+
+tables_future <- all_pred2 %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
+                                                                l95 = mean(per_change_l95, na.rm = TRUE), 
+                                                                u95 = mean(per_change_u95, na.rm = TRUE))
+
+# Check on how many to decrease
+  decreases <- all_pred2 %>% group_by(match)  %>% summarise(n = if_else(any(per_change < 0), 1, 0))
+
+```
+
+Acute and acclimation responses for wild ectotherms were much less common than studies on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
+Globally, there was a clear bias towards species in the Northern Hemisphere (@fig-fig6 A-C).
+Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
+However, out of the `r length(unique(all_pred2$match))` populations, relative variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
+
+Predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
+Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
+
+```{r, fig-fig6}
+#| label: fig-fig6
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
+Predicted change in physiological rate variance (relative variance) for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
+Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change).
+
+#devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
+
+world_map = map_data("world") %>% 
+  filter(! long > 180)
+
+map1_current <- ggplot() +
+  geom_map(
+    data = world_map, map = world_map,
+    aes(long, lat, map_id = region),
+    color = "black", fill = "lightgray") +
+  expand_limits(x = world_map$long, y = world_map$lat) +
+  coord_map("moll") +
+  geom_point(
+    data = all_pred  %>% filter(type == "acclim"),
+    aes(Longitude, Latitude, color = Estimate),
+    alpha = 0.7, size = 5
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"), title = "Current (2018-2022)") + scale_color_viridis() + theme_map(base_size = 22) +  theme(plot.title = element_text(hjust = 0.5))
+
+zoom_areas <- data.frame(
+     x = c(-130, -15, -60, 145),
+  xend = c( -50, 48, -35, 155),
+     y = c(  25, 34, 0, -45),
+  yend = c(  55,  69.8, -60, -10),
+  label = c("North America", "Europe", "South America", "Australia")
+)
+
+zoom_plots <- lapply(1:nrow(zoom_areas), function(i) {
+  map1_current +
+    geom_polygon(fill = "gray80", color = "black") +
+    coord_cartesian(xlim = c(zoom_areas[i, "x"], zoom_areas[i, "xend"]), 
+                    ylim = c(zoom_areas[i, "y"], zoom_areas[i, "yend"])) +
+                    theme(legend.position = "none",
+                        plot.title = element_blank())
+})
+
+map2_future <- ggplot() +
+    geom_map(
+      data = world_map, map = world_map,
+      aes(long, lat, map_id = region),
+      color = "black", fill = "lightgray") +
+    expand_limits(x = world_map$long, y = world_map$lat) +
+    coord_map("moll") +
+    geom_point(
+      data = all_pred2[complete.cases(all_pred2$per_change),],
+      aes(Longitude, Latitude, color = per_change),
+      alpha = 0.7, size = 5
+    ) + labs(x = "Longitude", y = "Latitude", color = TeX("% $\\Delta$"), title = "Future (2096-2100)") + scale_colour_viridis() + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+
+# Make a multipanel plot. Make the world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
+
+p <- (((zoom_plots[[1]] | zoom_plots[[2]]) / map1_current) + map2_future) + plot_layout(heights  = c(1, 2, 2)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"), plot.margin = unit(c(0, 0, 0, 0), "cm"))
+
+ggsave(p, filename = "./output/figures/fig-preds.png", width = 7.8, height = 10.1)
+
+image_read("./output/figures/fig-preds.png")
+```
+
+## **Discussion**
+
+Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can].
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease to varying extents across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
+Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
+Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations that require further empirical and theoretical attention.
+We discuss our findings in the context of the current literature and highlight key areas for future research.
+
+### ***Potential consequences of reduced plasticity and variance in physiological rates across ectotherms***
+
+Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can; @cooke2021one].
+For example, incorperating phenotypic plasticity and adaptation into species distribution models has been shown to dampen the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
+In addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, impacting a population's capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
+Quntifying the degree of plasticity and genetic/phenotypic variation in key physiolgical responses is therefore recognised as being critical to informing projections for organisms threatened by climate change [@cooke2021one].
+
+We show that plastic adjustments in physiological rates and changes in their relative variance differ across habitats.
+In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance in physiological rates providing more raw material for selection to operate.
+In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance in physiological rates, which may trade-off with the beneficial effects that acclimation provides at high temperatures.
+In terrestrial ectotherms, relative variance reductions are particularly pronounced and this coincides with a general inability to acclimate.
+Considering acute physiological rates of animals acclimated to high temperatures are generally still elevated compared to cold-acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization may not always provide adaptive benefits under climate change, particularly when considering changes in relative variance.
+
+Our findings highlight the potential vulnerability of terrestrial and marine ectotherms to climate change.
+Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warnming.
+Our results also define the range of biological responses observed across diverse taxa (e.g., through prediction intervals) providing opportunities to incorperate realistic biological variation into the modelling process.
+Incorperating relavant variation in models is needed fully appreciate the biological consequences such changes in variation and plasticity have on ecological and evolutionary dynamics [@bush2016incorporating; @demarche2019incorporating], that have not yet been explored.
+
+### ***Plasticity and variance in physiological rates do not differ between life-stages***
+Life-history stages often occupy different ecological niches and exhibit different physiological responses, levels of plasticity, and patterns of mortality in response to temperature.
+As such, it is becoming increasingly important to understand how climate change will impact different life-history stages so that more realistic predictive models can be developed [@levy2015resolving; @petitgas2013impacts].
+Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticity.
+Our results highlight that early life stages are not likely to be protected from the impacts of climate change.
+Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
+In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
+Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
+However, very few studies measure multiple life-history stages within the same population.
+In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
+
+### ***Ecological consequences of reduced variation in physiological rates***
+Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
+Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
+For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
+The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
+However, data testing the impacts of changes in variance on populations are limited to very few taxa.
+We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
+Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant changes in variation.
+Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
+
+### ***No signature of past climate on capacity for physiological plasticity***
+
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time, making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
+However, we did not find evidence to this effect.
+This finding is consistent with other meta-analyses [e.g., @barley2021limited; @Gunderson2015-hz] with thermal tolerance.
+The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal enviroments many taxa actually experience in nature.
+Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
+Alternatively, lower predictability of thermal environments over time may make cues unreliable, preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
+Randomly fluctuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
+For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
+@Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
+These findings, in combination with our results, suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable.
+The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
+
+### ***Conclusions and future directions***
+
+Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one].
+While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
+Substantial variation in acclimation responses and changes in variance exist among populations as evidenced by wide prediction intervals.
+Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced and possibly more realistic predictions about the impacts of climate change on natural populations.
+While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predictions.
+Our meta-analysis allows for realistic models to be parameterised and ensure they are better aligned with empirical findings.
+Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
+Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across tropic levels within communities?
+What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?
+Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?
+How much of the reduction in variance is driven by lower levels of genetic variance?
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
 
@@
 
-```{r lnrrq10}
-#| label: lnrrq10
-#| echo: false
-#| cache: true
-#| message: false
-#| warning: false
-#| include: false
-
-#############
-## lnRRQ10 ##
-#############
-##################################################
-# Organise the data and prune tree
-##################################################
-# Subset the data
-lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
-
-# Check and prune tree
-tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor <- vcv(tree_lnrr, cor = TRUE)
-        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
-
-# Found some other data entry problems from old dataset.
-Sample sizes are decimals.
-That's not correct.
-It has to be an integer.
-These are not the new data that we entered.
-Data now checked.
-Seemed to have resulted in a 'frame shift' in some data.
-Not sure how that happened, but it's now fixed.
-#hist(lnRRQ10_data$V)
-
-# Studies with big V, why? Check N
-lnRRQ10_data %>% filter(V >= 2)
-
-# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
-sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
-
-##################################################
-# Model 1.1: Intercept only model. 
-##################################################
-rerun = FALSE
-if(rerun){
-  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.1
-  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
-  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
-} else{ 
-  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
-model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
-}
-
-# Heterogeneity analysis
-   w <- with(lnRRQ10_data, 1/V) # weights
-  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
-  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
-
-    res <- posteriors_1.1[,"sigma"]
-   stdy <- posteriors_1.1[,"record_num"]
-  phylo <- posteriors_1.1[,"species_full"]
-    spp <- posteriors_1.1[,"spp"]
-  trait <- posteriors_1.1[,"trait"]
-  total <- phylo + spp + res + sv + stdy + trait
-
-  # Calculate I2
-     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
-   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
-     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
-    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
-   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
-     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
-
-  # Table
-     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
-                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
-
-###################################################
-# Model 1.2: Model controlling for acclimation time, 
-# type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model with 
-  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.2
-  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
-  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
-
-  } else{
-        model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
-  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
-}
-
-####################################################
-## Model 1.2: Bayesian Contrasts
-###################################################
-  posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
-  f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
-  f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
-  m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
-  m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
-  t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
-  t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
-
-# Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
-  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
-   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
-  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
-   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
-  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
-
-# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
-  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
-  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
-  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
-  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
-  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
-
-####################################################
-# Model 1.3's: Trait type varied by acclimation type
-# but data is separated by habitat to simplify
-####################################################
-# Filter to different habitats
-   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m") 
-   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f") 
-   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")
-
-    # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
-  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
-
-  # Prune tree
-   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-
-   # cor matrices
-   m_phylo <- vcv(tree_m, corr = TRUE)
-       A_m <- vcv(tree_m, corr = FALSE)
-   f_phylo <- vcv(tree_f, corr = TRUE)
-       A_f <- vcv(tree_f, corr = FALSE)
-   t_phylo <- vcv(tree_t, corr = TRUE)
-       A_t <- vcv(tree_t, corr = FALSE)
-
-if(rerun){
-   # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
-   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = m_phylo), dfs = "contain", 
-                              test = "t", 
-                              data = lnRRQ10_data_m)
-
-  model1.3_m_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 + trait_category | obs),
-                              R = list(species_full = m_phylo), 
-                              struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_m)
-
-  # Check k is the same for both models (yes) and check which model is best supported
-    AICc1.3_m     <- AIC(model1.3_m) + AICc_correction(model1.3_m)
-    AICc1.3_m_het <- AIC(model1.3_m_het) + AICc_correction(model1.3_m_het)
-    # Clear support for this model. We'll go with this.
-    AICc1.3_m - AICc1.3_m_het
-
-  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 0)
-
-  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
-
-    # More realistic model with traits in freshwater species
-  model1.3_f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full =f_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_f)
-
-  # Heteroscedastic variance model for freshwater
-  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 + trait_category | obs),
-                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_f, method = "REML", control=list(iter.max=1000, rel.tol=1e-8))
-
-  ## Check support for two models
-  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het) # Clearly better supported.
-      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
-  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het
-
-  # Run the Bayesian equivalent of the top supported model. 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
-
-    # More realistic model with traits in terrestrial species
-  model1.3_t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full =t_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_t)
-
-  # Heteroscedastic variance model for terrestrial
-  model1.3_t_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 + trait_category | obs),
-                              R = list(species_full =t_phylo), struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_t)
-
-  # Check which model is better
-    AICc_model1.3_t     <- AIC(model1.3_t) + AICc_correction(model1.3_t)
-    AICc_model1.3_t_het <- AIC(model1.3_t_het) + AICc_correction(model1.3_t_het)
-
-  #  Delta
-    AICc_model1.3_t - AICc_model1.3_t_het
-
-  # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
-
-    # Save models
-  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
-  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
-  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
-
-  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
-  saveRDS(model1.3_f_het, file = "./output/models/lnRRQ10_1.3f_het")
-  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
-
-  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
-  saveRDS(model1.3_t_het, file = "./output/models/lnRRQ10_1.3t_het")
-  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")
-
-  } else{
-        model1.3_m <- readRDS("./output/models/lnRRQ10_1.3m")
-    model1.3_m_het <- readRDS("./output/models/lnRRQ10_1.3m_het")
-  model1.3_m_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_m")
-        model1.3_f <- readRDS("./output/models/lnRRQ10_1.3f")
-    model1.3_f_het <- readRDS("./output/models/lnRRQ10_1.3f_het")
-  model1.3_f_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_f")
-        model1.3_t <- readRDS("./output/models/lnRRQ10_1.3t")
-    model1.3_t_het <- readRDS("./output/models/lnRRQ10_1.3t_het")
-  model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
-}
-
-###########################################################
-## Model 1.4 - whether chance between q10 depends on life stage and habita
-###########################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model1.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.4
-  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
-  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
-
-  } else{
-        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
-  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
-}
-
-#######################################################################
-# Bayesian posteriors from model 1.4
-#######################################################################
- # Create the data we want to make predcitions for. Just more intuitive
-  newdata <- data.frame( c_accl_time = 0, 
-                                type = as.factor(rep(c("acute", "acclim"))), 
-                             habitat = as.factor(rep(c("m", "f", "t"), each = 4)), 
-                           life.hist = as.factor(c("j", "a", "a", "j")))
-  newdata$type  <- relevel(newdata$type, ref = "acute")
-
-# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
-  X <- model.matrix(~c_accl_time + type*habitat*life.hist, data = newdata)
-
-# Extract posteriors
-  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
-
-# Now we can do all the calculations in one shot.
-         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
-     sum_pred <- apply(pred, 1, function(x) mean(x))
-  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
-  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
-
-# Create a summary dataset. 
-  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95)
-
-# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-    # Marine 
-        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
-        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
-    # Freshwater
-        f_ad <- 4
-        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
-        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
-    # Terrestrial
-        t_ad <- 8
-        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
-        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species
-
-# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-    # Marine 
-         m_acute <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
-        m_acclim <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
-    # Freshwater
-            f_ad <- 4
-         f_acute <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
-        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
-    # Terrestrial
-            t_ad <- 8
-         t_acute <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
-        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species
-
-  # Acute differences between a and j across all habitats
-     acute_all <- c(m_acute, f_acute, t_acute); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
-    acclim_all <- c(m_acclim, f_acclim, t_acclim)
-
-# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong. These two lines of code should roughly match
-#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
-#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")
-
-####################################################
-# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
-####################################################
- # Goal here is to test the assumption that acute Q10's are different or not
- lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
-
- if(rerun){ 
-    model1.s1 <- metafor::rma.mv(effect_size ~  c_accl_time + name, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
-    saveRDS(model1.s1, file = "./output/models/model1.s1")
-} else{
-      model1.s1 <-  readRDS(file = "./output/models/model1.s1")
-}
-
-```
-
-## **Results**
-
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-1 A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
-While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
-As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
-
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
-
-### *Terrestrial and aquatic ectotherms differ in their capacity to acclimate but acclimation does not depend on life-history stage*
-
-Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
-
-Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
-
-Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
-Acclimation capacity also did not vary by life-history stage given and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
-
-```{r, lncvrq10}
-#| label: lncvrq10
-#| echo: false
-#| warning: false
-#| error: false
-#| include: false
-#| cache: true
-
-#############
-  ## lnCVRQ10
-#############
-##################################################
-  # Organise the data and prune tree
-#################################################
-  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
-
-# Check and prune tree
-  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
-          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
-
-# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
-  #hist(lnCVRQ10_data$V)
-
-# Studies with big V, why? Check N
-  lnCVRQ10_data %>% filter(V >= 2)
-
-###################################################
-  # Model 2.1: Intercept only model.
-  # Used for heterogeneity analysis
-###################################################
-rerun = FALSE
-if(rerun){
-  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.1
-  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
-  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
-} else{ 
-        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
-  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
-}
-
-# Heterogeneity analysis
-   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
-  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
-  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
-
-    res_cvr <- posteriors_2.1[,"sigma"]
-   stdy_cvr <- posteriors_2.1[,"record_num"]
-  phylo_cvr <- posteriors_2.1[,"species_full"]
-    spp_cvr <- posteriors_2.1[,"spp"]
-  trait_cvr <- posteriors_2.1[,"trait"]
-  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
-
-  # Calculate I2
-     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
-   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
-     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
-    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
-   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
-     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
-
-  # Table
-     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
-                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
-
-###################################################
-  # Model 2.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
-  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
-
-  } else{
-        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
-  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
-}
-
-######################################################
-  # Bayesian Contrasts
-######################################################
-
-  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
-  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
-  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
-  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
-  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
-  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
-  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
-
-# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
-It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
-  # First get sample sizes
-    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
-
-  # Calculated weighted mean by sample size. 
-    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
-    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
-    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
-
-  # Lets now convert these to a %
-    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
-    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
-    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
-
-###################################################
-  # Model 2.3: Model controlling for acclimation time, 
-  # type and trait category assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
-  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
-
-  # We can also run subsets for each habitat
-   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-
-   # cor matrices
-   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
-       A_m_cvr <- vcv(tree_m_cvr, corr = FALSE)
-   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
-       A_f_cvr <- vcv(tree_f_cvr, corr = FALSE)
-   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
-       A_t_cvr <- vcv(tree_t_cvr, corr = FALSE)
-
-  model2.3f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "f"))
-
-  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
-
-  model2.3m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "m"))
-  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
-
-  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
-  model2.3t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "t"))
-  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
-
-  } else{
-        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
-        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
-        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
-        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
-  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
-}
-
-###################################################
-  # Model 2.4: Model controlling for acclimation time, 
-  # type and life history stage assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model
-  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
-  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
-
-  } else{
-        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
-  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
-}
-
-```
-
-```{r, fig-1}
-#| label: fig-1
-#| fig-cap: "Taxonomic distribution of acute and acclimation $Q_{10}$ estimates across major habitats.
-**A)** Phylogenetic distribution of taxa contained within the data.
-The total number of acute and acclimation type Q10 effect sizes are highlighted as well as whether the taxa is marine, freshwater or terrestrial.
-Silhouettes are representative taxa of major clades within the tree.
-**B)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
-**C)** Mean $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
-Note there were no differences between acute and acclimation $Q_{10}$ types.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI)."
-#| warning: false
-#| echo: false
-
-# Load and plot Figure 1.
-Note that this figure was derived using 3 separate code chunks described below.
-Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
-  fig1 <- image_read("./output/figures/fig1_final.png")
-  fig1
-##################
-  # Figure 1a plot
-##################
-   # Map data to tree. Just one variable for now
-      d <- ggtree(tree, layout="circular") %<+% tree_data
-
-      # Plot the tree
-      scales1 <- c("#053061", "#D1E5F0", "#67001F")
-      scales2 <- c("#053061", "#E7E0DB", "#67001F")
-      p1 <- d + 
-            #geom_tiplab(size=2, offset = 10) + 
-            geom_tippoint(aes(color=habitat), size = 2) +
-            labs(color = "Habitat") + 
-            scale_colour_manual(values = scales1)
-
-      # Create the data matrix that can be used to plot data as a heatmap around the phylogeny
-      matrix_data <- as.data.frame(data_wide %>%
-                  mutate(trait_category = ifelse(trait_category %in% 
-                                                   c("ATPase", "mito_leak", "mito_oxidation"), "Mito. Function", trait_category)) %>%
-                  mutate(trait_category = ifelse(trait_category %in% c("endurance", "sprint"), "Performance", trait_category))    %>%
-                  mutate(trait_category = ifelse(trait_category %in% c("muscle", "cardiac"), "Muscle Function", trait_category))  %>%
-                  mutate(trait_category = ifelse(trait_category %in% c("rest_MR", "max_MR"), "Metabolic Rate", trait_category))   %>%
-                  group_by(species_full, trait_category)   %>% 
-                  summarise(n = n())                       %>% 
-                  spread(trait_category, n, fill = 0))
-
-      row.names(matrix_data) <- matrix_data$species_full
-      matrix_data <- matrix_data[,c(2:8)]
-
-      colnames(matrix_data)[c(1,3,6)] <- c("Antioxidants", "Metabolic Enzymes", "Other")
-
-      # Alternatively, summarise total effect sizes per species for acute and acclimation
-      matrix_data2 <- data_long %>% filter(grepl("lnRR_Q10", name)) %>% 
-                      group_by(species_full, type) %>% 
-                      summarise(n = n()) %>% 
-                      spread(type, n, fill = 0) %>% data.frame()
-                     # mutate(acclim = as.character(cut(acclim, breaks = c(0,15, 20, 25, 30, 40, 50))),
-                      #        acute = as.character(cut(acute, breaks = c(0,15, 20, 25, 30, 40, 50))))
-
-      row.names(matrix_data2) <- matrix_data2$species_full
-      matrix_data2 <- matrix_data2[,2:3]
-
-      # Plot a heatmap of N for each trait around the phylogeny.
-   phylo <-   gheatmap(p1, data.matrix(matrix_data2), offset = 0,  colnames = FALSE, 
-               colnames_position="bottom", legend_title = "N", 
-               colnames_angle=360, colnames_offset_y = 0, colnames_offset_x = -1.5, 
-               hjust=0, font.size=3, width = 0.35) + 
-                scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
-
-ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
-
-##################
-  # Figure 1b plot
-##################
-col <- c("#0871B9", "#F3B40D", "#1BB908")
-
-  k_lnrr <- manual_extract(model1.2, mod = "habitat", group = "record_num", exclude = NULL)
-
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 8, branch.size = 2) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-  theme(legend.direction = "vertical") +
-
-  annotate("text", x = 1.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.20, y = 1.4, 
-         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-  annotate("text", x = 1.20, y = -0.8, label = "P < 0.001", hjust = 0, size = 6) +
-
-  annotate("text", x = 2.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-  annotate("text", x = 2.20, y = 1.4, 
-         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 2.20, y = -0.8, label = "P = 0.01", hjust = 0, size = 6) +
-
-  annotate("text", x = 3.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-  annotate("text", x = 3.20, y = 1.4, 
-         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 3.20, y = -0.8, label = "P = 0.36", hjust = 0, size = 6) +
-
-  scale_fill_manual(values = c(col)) + ylim(-0.8, 2) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.7, size = 5)
-
-  p1.2 <- p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
-        axis.text = element_text(size = 15), legend.title = element_text(size = 15),
-                               legend.text = element_text(size = 15),
-                               title = element_text(size = 24))
-
-  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 9.1, height = 9.2, device = "png")
-
-##################
-  # Figure 1c plot
-################## 
-  # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
-But, there is a clear reduction in between individual variance for terrestrial species.
-As temperature get hotter then the variance in physiological rates decreases.
-This is not true of aquatic systems.
-
-  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
-
-  x1 = 1.4
-  x2 = 2.4
-  x3 = 3.4
-
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 8, branch.size = 2, k.pos = "none") +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-
-  annotate("text", x = x1, y = -2, 
-           label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x1-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
-  annotate("text", x = x1-0.15, y = 1, 
-           label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
-
-  annotate("text", x = x2, y = -2, 
-           label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x2-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) +
-  annotate("text", x = x2-0.15, y = 1, 
-           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
-
-  annotate("text", x = x3, y = -2, 
-           label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x3-0.15, y = 1, 
-           label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = x3-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 2) + 
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5)
-
-  p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 15),
-                                       legend.title = element_text(size = 15),
-                               legend.text = element_text(size = 15),
-                               title = element_text(size = 24))
-
-  ggsave(p2, filename = "./output/figures/fig2.png", width = 9.3, height = 8.8)
-
-```
-
-### *Reduced variation in physiological rates in terrestrial and marine ectotherms*
-
-Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiologcial rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
-
-The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between study and trait differences (see Supplement;  @fig-s3).
-Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
-Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
-
-```{r, fig-cvrlh}
-#| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult and juvenile life-history stages for Marine (A & D), Freshwater (B & E) and Terrestrial (C & F) ectotherms.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-Raw data for both adult and juvenile life-history stages also presented but point are not separated by type for ease of presentation."
-#| echo: false
-#| warning: false
-
-add_theme  <- function(){theme(axis.title  = element_text(size = 24),
-                               axis.text.y = element_text(size = 15),
-                               axis.text.x = element_text(size = 15),
-                              legend.title = element_text(size = 15),
-                               legend.text = element_text(size = 15),
-                               title = element_text(size = 24))}
-branch.size = 2
-trunk.size = 5
-
-p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1, 1.8)
-
-p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45,)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1, 1.8)
-
-p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) +  ylim(-1, 1.8)
-
-p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-2.5, 2.5)
-
-p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
-
-p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
-
-fig4 <-(p1 | p2 | p3) / (p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig4, filename = "./output/figures/fig4_lh.pdf", width = 19, height = 12, device = "pdf")
-
-fig4 <- magick::image_read("./output/figures/fig4_lh.pdf")
-fig4
-```
-
-```{r, wildlnRR10}
-#| label: wildlnRR10
-#| cache: true
-#| include: false
-#| echo: false
-#| warning: false
-#| 
-#######################################
-  ## lnRRQ10 from Wild Populations ##
-#######################################
-##################################################
-  # Organise the data and prune tree
-##################################################
-
-# Bring in Climate data
-climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
-
-# Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
-
-# Subset the data
-lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
-
-# Now, join climate data to full data. This will give us all the climate variability data for each site across time
-lnRRQ10_data_wild <- left_join(lnRRQ10_data_wild, climate2, by = "match")
-
-# Check and prune tree
-tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
-        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
-
-# Scale data
-        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
-                                                          acf_all_c = scale(acf_all))
-
-###################################################
-  # Model 3.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.2
-  saveRDS(model3.2, file = "./output/models/lnRRQ10_3.2")
-  saveRDS(model3.2_bayes, file = "./output/models/lnRRQ10_3.2_bayes")
-
-  } else{
-        model3.2 <- readRDS("./output/models/lnRRQ10_3.2")
-  model3.2_bayes <- readRDS("./output/models/lnRRQ10_3.2_bayes")
-}
-
-####################################################
-  ## Model 3.2: Bayesian Contrasts
-###################################################
-  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
-  f_acute_wild  <- posteriors_3.2[,"b_Intercept"]
-  f_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
-  m_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
-  m_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
-  t_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
-  t_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
-
-# Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10_wild <- exp(f_acute_wild) ; mean(f_acute_Q10_wild)
-  f_acclim_Q10_wild <- exp(f_acclim_wild); mean(f_acclim_Q10_wild)
-   m_acute_Q10_wild <- exp(m_acute_wild) ; mean(f_acute_Q10_wild)
-  m_acclim_Q10_wild <- exp(m_acclim_wild); mean(f_acclim_Q10_wild)
-   t_acute_Q10_wild <- exp(t_acute_wild) ; mean(t_acute_Q10_wild)
-  t_acclim_Q10_wild <- exp(t_acclim_wild); mean(t_acclim_Q10_wild)
-
-# % change in acclimation on log scale; relative to the acute measurements
-  change_f_wild <- ((f_acclim_wild - f_acute_wild) / f_acute_wild) *100; quantile(change_f_wild, c(0.025, 0.975))
-  change_m_wild <- ((m_acclim_wild - m_acute_wild) / m_acute_wild) *100; quantile(change_m_wild, c(0.025, 0.975))
-  change_t_wild <- ((t_acclim_wild - t_acute_wild) / t_acute_wild) *100; quantile(change_t_wild, c(0.025, 0.975))
-
-####################################################
-  # Model 3.3: Model environmental variability by acute 
-  #  acclim 
-####################################################
-  rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model3.3, file = "./output/models/lnRRQ10_3.3")
-  saveRDS(model3.3_bayes, file = "./output/models/lnRRQ10_3.3_bayes")
-
-  } else{
-        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
-  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
-}
-
-################################################################
-  # Model 3.4: Environmental autocorrelation model by acute/acclim
-################################################################
-if(rerun){
-  # More realistic model with 
-  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model3.4, file = "./output/models/lnRRQ10_3.4")
-  saveRDS(model3.4_bayes, file = "./output/models/lnRRQ10_3.4_bayes")
-
-  } else{
-        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
-  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
-}
-
-################################################################
-  # Model 3.5: Environmental variability  model
-################################################################
-if(rerun){
-  # More realistic model with 
-  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.5
-  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
-  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")
-
-  } else{
-        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
-  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
-}
-
-################################################################
-  # Model 3.6: Environmental autocorrelation model
-################################################################
-if(rerun){
-  # More realistic model with 
-  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
-
-  # Save model3.6
-  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
-  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")
-
-  } else{
-        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
-  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
-}
-
-################################################################
-  # Model 3.7: Environmental variability and autocorrelation model
-################################################################
-
-if(rerun){
-  # More realistic model with 
-  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.7
-  saveRDS(model3.7, file = "./output/models/lnRRQ10_3.7")
-  saveRDS(model3.7_bayes, file = "./output/models/lnRRQ10_3.7_bayes")
-
-  } else{
-        model3.7 <- readRDS("./output/models/lnRRQ10_3.7")
-  model3.7_bayes <- readRDS("./output/models/lnRRQ10_3.7_bayes")
-}
-
-############################################################################################
-# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
-# differently in each habitat
-############################################################################################  
-  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-if(rerun){
-  # More realistic model with 
-  model3.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim)
-
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
-  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
-
-  } else{
-        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
-  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 3.8
-#################################################
- posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
-
-    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
-    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
-    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
-
-############################################################################################
-# Model 3.9: Acclimatization lnRRQ10 only. Test if environmental variance explains 
-# differently in each habitat
-############################################################################################
-
-if(rerun){
-  # More realistic model with 
-  model3.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim)
-
-   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model3.9, file = "./output/models/lnRRQ10_3.9")
-  saveRDS(model3.9_bayes, file = "./output/models/lnRRQ10_3.9_bayes")
-
-  } else{
-        model3.9 <- readRDS("./output/models/lnRRQ10_3.9")
-  model3.9_bayes <- readRDS("./output/models/lnRRQ10_3.9_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 3.9
-#################################################
- posteriors <- posterior_samples(model3.9_bayes, "^b")
-
-    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); mean(slope_f); quantile(slope_f, c(0.025, 0.975))
-    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
-    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))
-
-##################################################
-    # Model 3.8, 3.9 and 3.10 - Habitat subset
-##################################################
-    # Subset data to habitat
-    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
-    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
-    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
-
-if(rerun){
-    # Terrestrial Models
-    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-    saveRDS(model3.8_t, "./output/models/model3.8_t")
-
-    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-    saveRDS(model3.9_t, "./output/models/model3.9_t")
-
-        # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-     saveRDS(model3.10_t, "./output/models/model3.10_t")
-    # Freshwater Models
-    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-    saveRDS(model3.8_f, "./output/models/model3.8_f")
-
-    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-
-    saveRDS(model3.9_f, "./output/models/model3.9_f")
-
-       # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-
-     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-      saveRDS(model3.10_f, "./output/models/model3.10_f")
-    # Marine Models
-      model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-        saveRDS(model3.8_m, "./output/models/model3.8_m")
-
-    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-    saveRDS(model3.9_m, "./output/models/model3.9_m")
-    # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-
-    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-    saveRDS(model3.10_m, "./output/models/model3.10_m")
-  } else {
-     model3.8_t <- readRDS("./output/models/model3.8_t")
-     model3.9_t <- readRDS("./output/models/model3.9_t")
-    model3.10_t <- readRDS("./output/models/model3.10_t")
-     model3.8_f <- readRDS("./output/models/model3.8_f")
-     model3.9_f <- readRDS("./output/models/model3.9_f")
-    model3.10_f <- readRDS("./output/models/model3.10_f")
-     model3.9_m <- readRDS("./output/models/model3.9_m")
-    model3.10_m <- readRDS("./output/models/model3.10_m")
-     model3.8_m <- readRDS("./output/models/model3.8_m")
-}
-
-       r2_t <- r2_ml(model3.9_t)[1]    
-```
-
-```{r wildlncvr}
-#| label: wildlncvr
-#| cache: true
-#| include: false
-#| echo: false
-#| warning: false
-#| 
-#######################################
-  ## lnCVRQ10 from Wild Populations ##
-#######################################
-##################################################
-  # Organise the data and prune tree
-##################################################
-
-# Bring in  historial climate data
-climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
-
-# Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
-
-# Populations and species?
-pop_spp_w <- climate2[complete.cases(climate2),]
-
-# Subset the data
-lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
-                              mutate(spp = species_full, 
-                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
-                                     match = interaction(spp, lat, long))
-
-# Now, join climate data to full data. This will give us all the climate variability data for each site across time
-lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
-
-# Look at the environment details across different habitats. Seems very similar. *** Check with ALEX ***
-  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(cv), mean(acf_all))
-
-# Check and prune tree
-tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
-        A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
-
-# Scale environment variables
-    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
-                                                        acf_all_c = scale(acf_all))
-
-###################################################
-  # Model 4.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.2
-  saveRDS(model4.2, file = "./output/models/lnCVRQ10_4.2")
-  saveRDS(model4.2_bayes, file = "./output/models/lnCVRQ10_4.2_bayes")
-
-  } else{
-        model4.2 <- readRDS("./output/models/lnCVRQ10_4.2")
-  model4.2_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
-}
-
-####################################################
-  ## Model 4.2: Bayesian Contrasts
-###################################################
-  posteriors_4.2 <- posterior_samples(model4.2_bayes, pars = "^b")
-  f_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"]
-  f_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_typeacclim"]
-  m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
-  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatm"]
-  t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
-  t_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatt"]
-
-# CVRQ10 values for each category.
-   f_acute_Q10_wild_cvr <- exp(f_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
-  f_acclim_Q10_wild_cvr <- exp(f_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
-   m_acute_Q10_wild_cvr <- exp(m_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
-  m_acclim_Q10_wild_cvr <- exp(m_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
-   t_acute_Q10_wild_cvr <- exp(t_acute_wild_cvr) ; mean(t_acute_Q10_wild_cvr)
-  t_acclim_Q10_wild_cvr <- exp(t_acclim_wild_cvr); mean(t_acclim_Q10_wild_cvr)
-
-# % change in acclimation on log scale
-  change_f_wild_cvr <- ((f_acclim_wild_cvr - f_acute_wild_cvr) / f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
-  change_m_wild_cvr <- ((m_acclim_wild_cvr - m_acute_wild_cvr) /m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
-  change_t_wild_cvr <- ((t_acclim_wild_cvr - t_acute_wild_cvr)/t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
-
-####################################################
-  # Model 4.3: Model environmental variability by acute/acclim
-####################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.3
-  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
-  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
-
-  } else{
-        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
-  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
-}
-
-################################################################
-  # Model 4.4: Environmental autocorrelation model by acute/acclim
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
-  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
-
-  } else{
-        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
-  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
-}
-
-################################################################
-  # Model 4.5: Environmental variability
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.5
-  saveRDS(model4.5, file = "./output/models/lnCVRQ10_4.5")
-  saveRDS(model4.5_bayes, file = "./output/models/lnCVRQ10_4.5_bayes")
-
-  } else{
-        model4.5 <- readRDS("./output/models/lnCVRQ10_4.5")
-  model4.5_bayes <- readRDS("./output/models/lnCVRQ10_4.5_bayes")
-}
-
-################################################################
-  # Model 4.6: Environmental autocorrelation model 
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.6
-  saveRDS(model4.6, file = "./output/models/lnCVRQ10_4.6")
-  saveRDS(model4.6_bayes, file = "./output/models/lnCVRQ10_4.6_bayes")
-
-  } else{
-        model4.6 <- readRDS("./output/models/lnCVRQ10_4.6")
-  model4.6_bayes <- readRDS("./output/models/lnCVRQ10_4.6_bayes")
-}
-
-################################################################
-  # Model 4.7: Environmental autocorrelation and variability
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.7
-  saveRDS(model4.7, file = "./output/models/lnCVRQ10_4.7")
-  saveRDS(model4.7_bayes, file = "./output/models/lnCVRQ10_4.7_bayes")
-
-  } else{
-        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")   ### DIFFERENT 
-  #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
-}
-
-############################################################################################
-  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
-  # differently in each habitat
-############################################################################################  
-  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-if(rerun){
-  # More realistic model with 
-  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model4.8
-  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
-  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
-
-  } else{
-        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
-  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.8
-#################################################
- posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
-
-    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
-    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
-    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
-
-############################################################################################
-# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
-# differently in each habitat
-############################################################################################
-
-if(rerun){
-  # More realistic model with 
-  model4.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model4.9, file = "./output/models/lnRRQ10_4.9")
-  saveRDS(model4.9_bayes, file = "./output/models/lnRRQ10_4.9_bayes")
-
-  } else{
-        model4.9 <- readRDS("./output/models/lnRRQ10_4.9")
-  model4.9_bayes <- readRDS("./output/models/lnRRQ10_4.9_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.9
-#################################################
- posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
-
-    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
-    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
-    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
-
-```
-
-### *Past climate does not influence acclimation capacity or expected change in variance*
-
-Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
-
-```{r, fig-4}
-#| label: fig-4
-#| fig-align: center
-#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
-Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
-
-size_axis = 18
-# CV
-dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
-                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
-                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
-                      title = c("Freshwater", "Marine", "Terrestrial"), 
-                      condition = c("f", "m", "t"),
-                      x = rep(1.2, 3),
-                      y = rep(-1.2, 3))
-
- col <- c("#0871B9", "#F3B40D", "#1BB908")
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
-geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
-theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
-
-  # ACF
-dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
-                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
-                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
-                      condition = c("f", "m", "t"),
-                      x = rep(-2.8, 3),
-                      y = rep(-1.2, 3))
-
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y, label =label), size = 5) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
-geom_text(data = dat_text2, aes(x = x+1, y = y-0.65, label = p), size = 5) +
-theme(legend.position = "bottom", 
-      strip.background = element_blank(), 
-      strip.text = element_blank(), 
-      axis.text = element_text(size = size_axis), 
-      axis.title = element_text(size = size_axis),
-      legend.text = element_text(size = 16),
-      legend.title = element_text(size = 16))
-
-p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-
-ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
-
-  p8.1.2 <- image_read("./output/figures/fig8.png")
-  p8.1.2 
-```
-
-```{r, fig-5}
-#| label: fig-5
-#| fig-align: center
-#| fig-cap: "Predicted mean (thick black line) $lnCVR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
-Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
-
-size_axis = 18
-# CV
-dat_text <- data.frame(label = c(text(slope_f_4.9), text(slope_m_4.9), text(slope_t_4.9)),
-                      label2 = c(text(slope_f_4.9, b = FALSE), text(slope_m_4.9,b = FALSE), text(slope_t_4.9,b = FALSE)),
-                      p = c(p_text(slope_f_4.9), p_text(slope_m_4.9), p_text(slope_t_4.9)),
-                      title = c("Freshwater", "Marine", "Terrestrial"), 
-                      condition = c("f", "m", "t"),
-                      x = rep(1.2, 3),
-                      y = rep(-4, 3))
-
- col <- c("#0871B9", "#F3B40D", "#1BB908")
-p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
-geom_text(data = dat_text, aes(x = x, y = y-1, label = label2), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y-2, label = p), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y+10, label = title, size = 5)) + 
-theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
-
-  # ACF
-dat_text2 <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
-                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
-                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
-                      condition = c("f", "m", "t"),
-                      x = rep(-2.8, 3),
-                      y = rep(-4, 3))
-
-p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y, label = label), size = 5) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
-geom_text(data = dat_text2, aes(x = x+1, y = y-1.2, label = p), size = 5) +
-theme(legend.position = "bottom", 
-      strip.background = element_blank(), 
-      strip.text = element_blank(), 
-      axis.text = element_text(size = size_axis), 
-      axis.title = element_text(size = size_axis),
-      legend.text = element_text(size = 16),
-      legend.title = element_text(size = 16))
-
-p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-
-ggsave(p9.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig9.png")
-
-  p9.1.2 <- image_read("./output/figures/fig9.png")
-  p9.1.2 
-```
-
-### Changes in physiological rate variance under climate change
-
-```{r, global}
-#| label: global
-#| echo: false
-#| include: false
-
-# Here, we want to make global predcitions, at the lat/long in the data for how the opportunity of selection is expected to change with climate change.
-How can we do this?
-Q10 effects already have temperature controls within the effect size.
-So, what we want is to be able to understand how Q10 changes with latitude and longitude.
-Once we know that, we an extarct how temperature is expected to change from our current levels to future levels.
-This will be in degrees C.
-Then, assuming no plasticity and evolution (big assumption) we can get a baseline change in variance for each site.
-We first need to adjust the predcited Q10 value so that it's at 1C temperaure, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
-This will adjust the predcited Q10 value to the change in 1 degree C.
-We can then multiply this by the temperature change expected at that location to get the % change in variance or acure/acclim response.
-We can then plot these globally.
-
-#############################
-rerun = FALSE
-if(rerun){
-
-  # Model lat and long. Need to exclude missing acclimdation data. That will make it easier to create predcitions and explore the model fit.
-
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(Longitude, Latitude) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
-
-  saveRDS(model5_bayes, file = "./output/models/lnCVRQ10_5_bayes")
-
-  } else{
-  model5_bayes <- readRDS("./output/models/lnCVRQ10_5_bayes")
-}
-
-# Lets explore the model and how it's predciting the real data
-  data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
-
-# combine with predictions
-  data_w_pred <- cbind(data_w, predict(model5_bayes))
-
-# Fitted vs actual data
-  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Predicted Effect Size", y = "Observed Effect Size") + theme_classic() + 
-  geom_abline(intercept = 0, slope = 1)
-
-# Seems to be OK, but over and under-predciting at times.
-Lets explore the data for odd ball predictions to see if there are any obvious reasons why.
-T here are very few for the most part but lets see why sign changes occur which are most stricking differences.
-Sign changes indicate the observed data is completely opposite in sign to the predcited data
-
-#  Spot check of a bunch of studies doesn't show any obvious issues with the data.
-Note that data is repeated because acute and acclimated rates are calculated.
-We expect the rows of raw data for acute and acclim to be repeated even though these data are NOT all used to make the calculation.
-  sign_change_dat <- data_w_pred  %>% filter(sign(Estimate) != sign(effect_size))
-  #View(sign_change_dat)
-
-# Fitted by Lat/long Longitude, Latitude
-  ggplot(data = data_w_pred, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
-
-# Observed by Lat/long
-  ggplot(data = data_w_pred, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
-
-# How much variation does this model explain.
-Need to do this manually because function doesn't seme to work on the model object.
-We need to remember that predcit will include random effect variances so we may need to exclude this
-  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
-  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)
-
-# sigma2_v = typical sampling error variance
-sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
-  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
-              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))
-
-# Now check that var fix from raw data and remove sampling variance. 
-  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
-
-# Extract the random effect variances
-  v_trait <- re_post$sd_trait__Intercept^2
-    v_spp <- re_post$sd_spp__Intercept^2
-    v_phy <- re_post$sd_species_full__Intercept^2
-    v_std <- re_post$sd_record_num__Intercept^2
-      v_r <- re_post$sd_obs__Intercept^2
-
-# Lets get the total variance for the random effects only
-  tot_re <- v_trait + v_spp + v_phy + v_std + v_r
-
-# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
-    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too
-
-    mean(r2) # Seems a bit high 0.5
-  quantile(r2, probs = c(0.025, 0.975)); #0.27-0.69
-
-# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
-  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2
-
-  mean(r2_2) #  0.48
-  quantile(r2_2, probs = c(0.025, 0.975)); #0.31-0.60
-
-######################################################################
-# Model predictions for terrestrial, marine and freshwater ectotherms
-######################################################################
-# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
-
-#############################
-## Terrestrial Ectotherms
-#############################
-
-  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
-  new_data_t <- data.frame(
-      c_accl_time = 0,
-      V = 0,
-      trait = 0,
-      obs = 0, 
-      record_num = 0
-    )
-
-  # Create new dataframe with only unique values for predcition.
-  new_data_t2  <- cbind(terrest_data, new_data_t)
-
-  # We'll now make the predcitions from the model object using the new dataframe
-  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
-
-  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
-  terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
-
-  # Lets merge predictions with the original data
-  terrest_data <- cbind(terrest_data, terre_pred)
-
-  # Test manual calculations.
-We can also set summary = FALSE and then do the calculations ourselves.
-Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE .
-These are extremely close, and I suspect are only different because sample_new_levels is sampling differently each time predict is run, so will be slightly different from run-to-run
-  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
-  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
-
-#############################
-## Marine ectotherms  
-#############################
-  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
-
-  new_data_m <- data.frame(
-      c_accl_time = 0,
-      V = 0,
-      trait = 0,
-      obs = 0, 
-      record_num = 0
-    )
-
-  # Create new dataframe with only unique values for predcition.
-  new_data_m  <- cbind(marine_data, new_data_m)
-
-  # We'll now make the predcitions from the model object using the new dataframe
-  marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
-
-  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
-  marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
-
-  # Lets merge predictions with the original data
-  marine_data <- cbind(marine_data, marine_pred)
-
-#############################
-## Freshwater ectotherms
-#############################
-  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
-
-  new_data_f <- data.frame(
-      c_accl_time = 0,
-      V = 0,
-      trait = 0,
-      obs = 0, 
-      record_num = 0
-    )
-
-  # Create new dataframe with only unique values for predcition.
-  new_data_f  <- cbind(fresh_data, new_data_f)
-
-  # We'll now make the predcitions from the model object using the new dataframe
-  fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
-
-  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
-  fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
-
-  # Lets merge predictions with the original data
-  fresh_data <- cbind(fresh_data, fresh_pred)
-
-# Now that we have all the predictions we can merge the data together.
-Note that species itself is not really that useful because each prediction at each latitude and longitude should incoperate the species effect.
-So we'll remove it.
-While I retain spp, it's still not totally specific to the species, but left it there so it's clear how these data match with the wild data.
-Note there are only 134 species because this is subset of the wild data.
-  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)  %>% mutate(uniques = interaction(spp, Latitude, Longitude))
-  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% dplyr::select(-species_full)
-  spp_wild  <- length(unique(sub_data$spp))
-```
-
-```{r, future_clim}
-#| label: future_clim
-#| echo: false
-#| warning: false
-#| include: false
-
-# Now we want to take the predictions from `global` and use this for future climate sceneios.
-We have the future temperatures expected for each location.
-We can then use the predicted Q10 values to calculate the expected change in variance.
-We can then plot these globally.
-
-# First, lets get the current and future temperature data for 2081-2085. We'll use the mean. 
-  future_temp <- read.csv("./output/climate_data/CanESM2_air_and_SST_timeseries.csv")
-
-# Now, lets summarise the mean for the current temps (i.e., 2018-2022)
-current_temps <-   future_temp  %>% 
-                   dplyr::select(Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(future_temp)))  %>% 
-                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15, match = interaction(Species, Latitude, Longitude))
-
-# Lets clean this data up.
-We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins.
-We'll now take the last 5 years of the future temperature 2096-2100
-  future_temps  <- future_temp  %>% 
-                  dplyr::select(Species, Latitude, Longitude,  grep("X2096|X2097|X2098|X2099|X2100", colnames(future_temp)))  %>% 
-                  mutate(mean = apply(.[, grep("X2096|X2097|X2098|X2099|X2100", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_future = mean - 273.15,  match = interaction(Species, Latitude, Longitude))
-
-# Now we can merge the climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
-
-  climate_data <- left_join(current_temps, future_temps, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
-
-# Lets look at future and current. Most, I would expect, should be above the line indicating higher future temperatures.
-  ggplot(data = climate_data, aes(x = Celc_curr, y = Celc_future)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Current Temperature (C)", y = "Future Temperature (C)") + theme_classic() + geom_abline(intercept = 0, slope = 1)
-
-# Lets have a global plot of temperature changes to see it sptially
-
-world_map = map_data("world") %>% 
-  filter(! long > 180)
-
-  map2_temp_proj <- ggplot() +
-    geom_map(
-      data = world_map, map = world_map,
-      aes(long, lat, map_id = region),
-      color = "black", fill = "lightgray") +
-    expand_limits(x = world_map$long, y = world_map$lat) +
-    coord_map("moll") +
-    geom_point(
-      data = climate_data[complete.cases(climate_data$T_change),],
-      aes(Longitude, Latitude, color = T_change),
-      alpha = 0.7, size = 5
-    ) + labs(x = "Longitude", y = "Latitude", color = TeX("$\\Delta$ Temp.
-($^\\circ$C)"), title = "Current (2018-2022) vs Future (2096-2100)") + scale_colour_gradient2(trans = "reverse") + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
-
-# Now lets merge all_pred with the climate projections
-  # Simplify columns 
-  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude)
-
-  # Merge with model predcitions.
-This is the predcited lnCVRq10 for 10C change AT the specific latitude and longitude.
-We must assume that there is no plasticity or adaptation at each site to make projections
-  all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
-              left_join(., climate_data_new, by = "match")  %>% 
-              mutate(lnCVR_future = (Estimate / 10) * T_change,
-                      lnCVR_F_l95 = (Q2.5 / 10) * T_change,
-                      lnCVR_F_u95 = (Q97.5 / 10) * T_change, 
-                      per_change = (exp(lnCVR_future) - 1) * 100,
-                      per_change_l95 = (exp(lnCVR_F_l95) - 1) * 100,
-                      per_change_u95 = (exp(lnCVR_F_u95) - 1) * 100)
-
-  # Lets now use the whole posterior distribtion instead. This is a little hacky because the object is complicated
-
-######## *** THE CODE BELOW NEEDS SOME NEW CHECKING AS ABOVE WAS MODIFIED! ****
-
-  # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
-
-    all_pred2_no_sum <-  all_pred_no_sum %>% 
-                        mutate(match = interaction(spp, Latitude, Longitude))  %>% 
-                        left_join(., climate_data_new, by = "match")
-
-  # Second, lets convert each estimate to lncvr 1 degree C instead of 10...
-   all_pred2_no_sum2 <- all_pred2_no_sum %>%  
-                        mutate_if(colnames(.) %in% c(1:3200), lncvr_1c)
-
-  # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
-    all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]  <- all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)] * all_pred2_no_sum2$T_change
-
-  # Fourth, we can calculate the percentage change on the posterior
-    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]) - 1)*100
-
-  # Now we can summarise each.
-Here, what we are doing is taking the mean for each column.
-Effectively pooling across all the iterations for each dataset.
-This gives us an estimation of the mean change in variance across all locations/species., but it gives us 3200 point estimates of this mean.
-We can then use this to calculate the 95% CI's.
-    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) # Fixed an error here. It was applying the mean across columns, not rows!
-    mean(mean_perc)
-    quantile(mean_perc, 0.025)
-    quantile(mean_perc, 0.975)
-    hist(mean_perc)
-
-  # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
-  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE))
-  lapply(mean_perc_habitat, mean)
-  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
-  #lapply(mean_perc_habitat, hist)
-
-# Need to take a step back
-  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
-  # 2. Why are l95 and u95 for marine not working...Fixed
-  # 3. Apply to the posteriors, rather than summary. Done
-
-tables_future <- all_pred2 %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
-                                                                l95 = mean(per_change_l95, na.rm = TRUE), 
-                                                                u95 = mean(per_change_u95, na.rm = TRUE))
-
-# Check on how many to decrease
-  decreases <- all_pred2 %>% group_by(match)  %>% summarise(n = if_else(any(per_change < 0), 1, 0))
-
-```
-
-Acute and acclimation responses for wild ectotherms were much less common than studies on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
-Globally, there was a clear bias towards species in the Northern Hemisphere (@fig-fig6 A-C).
-Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
-However, out of the `r length(unique(all_pred2$match))` populations, relative variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
-
-Predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
-
-```{r, fig-fig6}
-#| label: fig-fig6
-#| echo: false
-#| warning: false
-#| message: false
-#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
-Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
-Predicted change in physiological rate variance (relative variance) for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
-Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change).
-
-#devtools::install_github("hughjonesd/ggmagnify") #https://github.com/hughjonesd/ggmagnify
-
-world_map = map_data("world") %>% 
-  filter(! long > 180)
-
-map1_current <- ggplot() +
-  geom_map(
-    data = world_map, map = world_map,
-    aes(long, lat, map_id = region),
-    color = "black", fill = "lightgray") +
-  expand_limits(x = world_map$long, y = world_map$lat) +
-  coord_map("moll") +
-  geom_point(
-    data = all_pred  %>% filter(type == "acclim"),
-    aes(Longitude, Latitude, color = Estimate),
-    alpha = 0.7, size = 5
-  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"), title = "Current (2018-2022)") + scale_color_viridis() + theme_map(base_size = 22) +  theme(plot.title = element_text(hjust = 0.5))
-
-zoom_areas <- data.frame(
-     x = c(-130, -15, -60, 145),
-  xend = c( -50, 48, -35, 155),
-     y = c(  25, 34, 0, -45),
-  yend = c(  55,  69.8, -60, -10),
-  label = c("North America", "Europe", "South America", "Australia")
-)
-
-zoom_plots <- lapply(1:nrow(zoom_areas), function(i) {
-  map1_current +
-    geom_polygon(fill = "gray80", color = "black") +
-    coord_cartesian(xlim = c(zoom_areas[i, "x"], zoom_areas[i, "xend"]), 
-                    ylim = c(zoom_areas[i, "y"], zoom_areas[i, "yend"])) +
-                    theme(legend.position = "none",
-                        plot.title = element_blank())
-})
-
-map2_future <- ggplot() +
-    geom_map(
-      data = world_map, map = world_map,
-      aes(long, lat, map_id = region),
-      color = "black", fill = "lightgray") +
-    expand_limits(x = world_map$long, y = world_map$lat) +
-    coord_map("moll") +
-    geom_point(
-      data = all_pred2[complete.cases(all_pred2$per_change),],
-      aes(Longitude, Latitude, color = per_change),
-      alpha = 0.7, size = 5
-    ) + labs(x = "Longitude", y = "Latitude", color = TeX("% $\\Delta$"), title = "Future (2096-2100)") + scale_colour_viridis() + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
-
-# Make a multipanel plot. Make the world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork
-
-p <- (((zoom_plots[[1]] | zoom_plots[[2]]) / map1_current) + map2_future) + plot_layout(heights  = c(1, 2, 2)) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20, face = "bold"), plot.margin = unit(c(0, 0, 0, 0), "cm"))
-
-ggsave(p, filename = "./output/figures/fig-preds.png", width = 7.8, height = 10.1)
-
-image_read("./output/figures/fig-preds.png")
-```
-
-## **Discussion**
-
-Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease to varying extents across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
-Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations that require further empirical and theoretical attention.
-We discuss our findings in the context of the current literature and highlight key areas for future research.
-
-### ***Potential consequences of reduced plasticity and variance in physiological rates across ectotherms***
-
-Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can].
-For example, incorperating phenotypic plasticity and adaptation into species distribution models has been shown to dampen the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
-It addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, impacting a population's capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
-
-We show that plastic adjustments in physiological rates and changes in their relative variance differ across habitats.
-In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance in physiological rates providing more raw material for selection to operate.
-In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance in physiological rates, which may trade-off with the beneficial effects that acclimation provides at high temperatures.
-In terrestrial ectotherms, relative variance reductions are particularly pronounced and this coincides with a general inability to acclimate.
-Considering acute physiological rates of animals acclimated to high temperatures are generally elevated compared to cold-acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization may not always provide adaptive benefits under climate change, particularly when considering changes in relative variance.
-
-Our findings highlight the potential vulnerability of terrestrial and marine ectotherms to climate change.
-Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warnming.
-Our results also define the range of responses observed across diverse taxa (e.g., through prediction intervals) that also provide opportunities to incorperate realistic biological variation into the modelling process.
-Incorperating relavant variation in such change are needed fully appreciate the biological consequences such changes have on ecological and evolutionary dynamics (@bush2016incorporating).
-
-### ***Plasticity and variance in physiological rates do not differ between life-stages***
-Interestingly, there were no differences in acclimation or reductions in physiological variance between life-stages across habitat types.
-Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
-However, our results highlight that early life stages are not likely to be protected from the impacts of climate change.
-Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
-Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticity.
-Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
-However, very few studies measure multiple life-history stages within the same population.
-In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
-
-### ***Ecological consequences of reduced variation in physiological rates***
-Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
-Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
-They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
-However, data testing the impacts of changes in variance on populations are limited to very few taxa.
-We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
-Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant changes in variation.
-Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
-
-### ***No signature of past climate on capacity for physiological plasticity***
-
-Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time, making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
-However, we did not find evidence to this effect.
-This finding is consistent with other meta-analyses [e.g., @barley2021limited; @Gunderson2015-hz] with thermal tolerance.
-The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal enviroments many taxa actually experience in nature.
-Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
-Alternatively, lower predictability of thermal environments over time may make cues unreliable, preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
-Randomly fluctuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
-For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
-@Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
-These findings, in combination with our results, suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable.
-The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-
-### ***Conclusions and future directions***
-
-Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking].
-While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations as evidenced by wide prediction intervals.
-Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced and possibly more realistic predictions about the impacts of climate change on natural populations.
-While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predictions.
-Our meta-analysis allows for realistic models to be parameterised and ensure they are better aligned with empirical findings.
-Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
-Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across tropic levels within communities?
-What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?
-Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?
-How much of the reduction in variance is driven by lower levels of genetic variance?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
+## Funding
+This work was partially supported by an Australian Research Council (ARC) Discovery Early Career Research Award (DE150101774) and ARC Future Fellowship (FT220100276) to DWAN.
 

### 2024-02-08 ms.qmd
Updted MS and a re-read and slight organsational change for NEE. Methods at end and moved up some context in the results section

@@
 ---
-title: "Reduced plasticity and variance in physiological rates for terrestrial ectotherm populations under climate change"
+title: "Reduced plasticity and variance in physiological rates for ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
-csl: ./bib/ecology-letters.csl
+csl: ./bib/nature.csl
 format:
@@
 Climate change is expected to result in warmer but also more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Evolutionary theory predicts that greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
 Without plasticity or adaptation, high extinction rates are predicted unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to be the 'first line of defence' against changing climates, thereby buying time for genetic adaptation to take place [i.e., the 'plasticity first hypothesis' - @WestEberhard2003; see also @Lande2009].
+Phenotypic plasticity is expected to be the 'first line of defence' against changing climates, thereby buying time for genetic adaptation to take place (i.e., the 'plasticity first hypothesis')[@WestEberhard2003; @Lande2009].
 Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Despite this theoretical expectation, empirical support is scant [but see @Leung2020], likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], or the prediction is only supported for specific life-history stages.
-
-Reversible phenotypic plasticity, such as acclimation, is expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions [assuming the costs of plasticity are low – @Dewitt1998; @Scheiner2020].
+Despite this theoretical expectation, empirical support is scant (but see [@Leung2020]), likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], or the prediction is only supported for specific life-history stages.
+
+Reversible phenotypic plasticity, such as acclimation, is expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions (assuming the costs of plasticity are low) [@Dewitt1998; @Scheiner2020].
 Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to facilitate a rapid response to the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
@@
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others raising the question of which ecosystems will be most vulnerable to contemporary climate change.
-Species occupying terrestrial ecosystems are particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper], whereas greater proximity to upper thermal limits in marine systems have questioned such conclusions [@Pinsky2019-fn].
+Species occupying terrestrial ecosystems are are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper], whereas greater proximity to upper thermal limits in marine systems have questioned such conclusions [@Pinsky2019-fn].
 Marine and freshwater ecosystems appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
@@
 
-Using a large database on physiolgical rates (@Seebacher2015-wi) for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10$^{\circ}$C temperature difference.
+Using a large database on physiolgical rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10$^{\circ}$C temperature difference.
 These standardised effects sizes can be converted to percentage differences allowing us to compare the relative magnitude of rate changes resulting from acclimation and relative variance change at high temperatures.
-Acclimation responses could be measured by comparing acclimation $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acclimation}}}$) to acute $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acute}}}$) from experimental ectotherms acclimated to different temperatures.
+Acclimation responses can be measured by comparing acclimation $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acclimation}}}$) to acute $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acute}}}$) from ectotherms acclimated to different temperatures.
 The difference in $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ measures the extent of acclimation (i.e., plasticity).
@@
 
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzyme rates ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
 
@@
 Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
-Acclimation capacity also did not vary by life-history stage given and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity also did not vary by life-history stage given there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
 Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiologcial rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
+Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
 In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
@@
 
-Predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
+Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
 Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
@@
 In terrestrial ectotherms, relative variance reductions are particularly pronounced and this coincides with a general inability to acclimate.
-Considering acute physiological rates of animals acclimated to high temperatures are generally still elevated compared to cold-acclimated animals (~7%; $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, p `r p_value(model1.s1$pval[3])`), acclimatization may not always provide adaptive benefits under climate change, particularly when considering changes in relative variance.
+Considering acute physiological rates of animals acclimated to high temperatures are generally still elevated compared to cold-acclimated animals (~7% increase), acclimatization may not always provide adaptive benefits under climate change, particularly when considering changes in relative variance.
 
 Our findings highlight the potential vulnerability of terrestrial and marine ectotherms to climate change.
-Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warnming.
+Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warming.
 Our results also define the range of biological responses observed across diverse taxa (e.g., through prediction intervals) providing opportunities to incorperate realistic biological variation into the modelling process.
-Incorperating relavant variation in models is needed fully appreciate the biological consequences such changes in variation and plasticity have on ecological and evolutionary dynamics [@bush2016incorporating; @demarche2019incorporating], that have not yet been explored.
+Incorperating relavant variation in models is needed fully appreciate the biological consequences such changes in variation and plasticity have on ecological and evolutionary dynamics [@bush2016incorporating; @demarche2019incorporating] and are yet to be explored.
 
@@
 Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
+For example, Moghadam *et al.* @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
+In contrast, Carter *et al.* @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
 Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
@@
 Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+For example, Kooijman *et al.* @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
 They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
@@
 
-Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time, making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Theoretical evolutionary models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time, making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
 Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
 However, we did not find evidence to this effect.
-This finding is consistent with other meta-analyses [e.g., @barley2021limited; @Gunderson2015-hz] with thermal tolerance.
+This finding is consistent with other meta-analyses [@barley2021limited; @Gunderson2015-hz] with thermal tolerance.
 The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal enviroments many taxa actually experience in nature.
 Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
-Alternatively, lower predictability of thermal environments over time may make cues unreliable, preventing plastic responses from evolving easily [@Leung2020; @hendry2016key].
 Randomly fluctuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
-For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
-@Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
-These findings, in combination with our results, suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable.
+For example, using seed beetles (*Callosobruchus maculatus*), Hallsson *et al.* @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
+Leung *et al.* @Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
+These findings, in combination with our results, suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@Leung2020; @hendry2016key].
 The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.

### 2024-02-09 ms.qmd
Fixed a bunch of spelling mistakes in new section.

@@
 Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can; @cooke2021one].
-For example, incorperating phenotypic plasticity and adaptation into species distribution models has been shown to dampen the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
+For example, incorporating phenotypic plasticity and adaptation into species distribution models has been shown to dampen the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
 In addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, impacting a population's capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
-Quntifying the degree of plasticity and genetic/phenotypic variation in key physiolgical responses is therefore recognised as being critical to informing projections for organisms threatened by climate change [@cooke2021one].
+Quantifying the degree of plasticity and genetic/phenotypic variation in key physiological responses is therefore recognised as being critical to informing projections for organisms threatened by climate change [@cooke2021one].
 
@@
 Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warming.
-Our results also define the range of biological responses observed across diverse taxa (e.g., through prediction intervals) providing opportunities to incorperate realistic biological variation into the modelling process.
-Incorperating relavant variation in models is needed fully appreciate the biological consequences such changes in variation and plasticity have on ecological and evolutionary dynamics [@bush2016incorporating; @demarche2019incorporating] and are yet to be explored.
+Our results also define the range of biological responses observed across diverse taxa (e.g., through prediction intervals) providing opportunities to incorporate realistic biological variation into the modelling process.
+Incorporating relevant variation in models is needed fully appreciate the biological consequences such changes in variation and plasticity have on ecological and evolutionary dynamics [@bush2016incorporating; @demarche2019incorporating] and are yet to be explored.
 
@@
 This finding is consistent with other meta-analyses [@barley2021limited; @Gunderson2015-hz] with thermal tolerance.
-The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal enviroments many taxa actually experience in nature.
+The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal environments many taxa actually experience in nature.
 Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.

### 2024-02-10 ms.qmd
Added funding

@@
 ## Funding
-This work was partially supported by an Australian Research Council (ARC) Discovery Early Career Research Award (DE150101774) and ARC Future Fellowship (FT220100276) to DWAN.
+DWAN is supported by an Australian Research Council (ARC) Future Fellowship (FT220100276) and ARC Discovery Project (DP210101152).
+SN is supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
 

### 2024-02-14 ms.qmd
Abstarct and afflication fixed

@@
 ---
-title: "Reduced plasticity and variance in physiological rates for ectotherm populations under climate change"
+title: "Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
 ^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
-^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
+^3^ School of Life and Environmental Sciences, University of Sydney, Sydney, NSW 2006, Australia  &NewLine;  
 ^4^ Department of Biology, Lancaster University, Liverpool, UK &NewLine;  
@@
 Greater thermal variability is expected to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-Such responses depend on genetic and phenotypic variability, yet most work has focused on plastic changes in mean phenotypic responses to climate warming ignore how temperature may change phenotypic variability.
-Using a large database of physiological rate data from marine, freshwater and terrestrial ectotherms we quantify the capacity for temperature acclimation and the extent to which relative variance (i.e., coefficient of variation) in physiological rates change at high temperatures.
-Using new effect size estimates and meta-analysis, we show that across habitats relative variance in physiological rates decreased at higher temperatures.
+Such responses depend on genetic and phenotypic variability.
+However, most work has focused on changes in mean phenotypic responses to climate warming ignoring how temperature may also change phenotypic variability.
+Phenotypic variability may be particularly important at extreme, high temperatures, which would facilitate selection of resistant individuals or promote plasticity (acclimation) and thereby increase resilience to heat waves.
+Using newly developed effect size estimates and meta-analysis (>1900 effects from 226 species), we show that across habitats relative variance in physiological rates decreased at higher temperatures.
 Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
-Marine organisms also showed a capacity to acclimate to higher temperatures but they coincide with a reduction in relative variance in physiological rates.
-Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincides with a lack of capacity for acclimation highlighting the vulnerability of terrestrial ectotherms to climate change.
+Marine organisms also showed a capacity to acclimate to higher temperatures, but capacity for plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
+Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
 Neither life-history stage nor past climate explained effect variability.
-Our results emphasise how beneficial acclimation responses may trade-off with reductions in physiological rate variance that could have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations in the future.
+Our results show that beneficial acclimation responses may trade-off with reductions in physiological rate variance.
+This trade-off could constrain evolutionary responses to climate change and reduce the potential benefits of portfolio effects.
+These findings have important evolutionary and ecological ramifications that affect our understanding of how climate change will impacts populations now and in the future.
 

### 2024-02-14 ms.qmd
Franks comments incorperated up to Potential consequences section in discussion

@@
 
-Climate change is expected to result in warmer but also more variable thermal environments for many organisms globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
+Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
 Greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
@@
 However, the focus up to now has been primarily on mean physiological responses.
-For example, mean thermal tolerances or acclimation abilities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022].
+For example, mean thermal tolerances or acclimation capacities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022].
 However, it is possible that intrapopulation variability might also be impacted in addition to the mean.
 Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
-Decreases in phenotypic variance also suggests strong stabilising selection or reflect constraints on performance [@Scheiner2020; @Dewitt1998].
+Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change (i.e., the portfolio effect) [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
+Decreases in phenotypic variance also suggests strong stabilising selection or reflects constraints on performance [@Scheiner2020; @Dewitt1998].
 Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
-The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date have been largely ignored [@Scheiner2020].
+The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date there are few data testing the importance of variances in this context [@Scheiner2020].
 
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others raising the question of which ecosystems will be most vulnerable to contemporary climate change.
-Species occupying terrestrial ecosystems are are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper], whereas greater proximity to upper thermal limits in marine systems have questioned such conclusions [@Pinsky2019-fn].
+Species occupying terrestrial ecosystems are are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
+However, this conclusion has been questioned given that marine ectotherms have recently been shown to be closer to their upper thermal limits compared to terrestrial species [@Pinsky2019-fn].
 Marine and freshwater ecosystems appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
@@
 
-Here, we use new effect sizes and meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We then expand these effect sizes to allow for comparisons of variance in physiological rates to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
+Here, we use meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
+We then developed new effect sizes effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
 2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
@@
 Using a large database on physiolgical rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10$^{\circ}$C temperature difference.
-These standardised effects sizes can be converted to percentage differences allowing us to compare the relative magnitude of rate changes resulting from acclimation and relative variance change at high temperatures.
-Acclimation responses can be measured by comparing acclimation $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acclimation}}}$) to acute $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acute}}}$) from ectotherms acclimated to different temperatures.
+These standardised effects sizes can be converted to percentage differences to permit comparisons between the relative magnitudes of rate changes resulting from acclimation and relative variance changes at high temperatures.
+Acclimation responses can be determined by comparing acclimation $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acclimation}}}$) to acute $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acute}}}$) from ectotherms acclimated to different temperatures.
 The difference in $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ measures the extent of acclimation (i.e., plasticity).
@@
 The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-1 A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (@fig-1).
-While the two acute $lnRR_{Q_{10}}$ effect sizes did differ significantly from each other, on average (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), they were in the same direction and only differed by ~10%.
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-1).
+The two acute $lnRR_{Q_{10}}$ effect sizes differed significantly from each other (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), but on average they were in the same direction and only differed by ~10%.
 As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
@@
 Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
-Acclimation capacity also did not vary by life-history stage given there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
 
@@
 **A)** Phylogenetic distribution of taxa contained within the data.
-The total number of acute and acclimation type Q10 effect sizes are highlighted as well as whether the taxa is marine, freshwater or terrestrial.
+The total number of acute and acclimation Q10 effect sizes are highlighted as well as whether the taxa are marine, freshwater or terrestrial.
 Silhouettes are representative taxa of major clades within the tree.
@@
 
-Relative variance in physiological rates, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but was especially pronouced in terrestrial and marine ectotherms.
+Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a decrease with increasing temperature across all habitat types, which was especially pronounced in terrestrial and marine ectotherms.
 Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a much smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
-
-The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between study and trait differences (see Supplement;  @fig-s3).
+In contrast, freshwater ectotherms exhibited a smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
+
+The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between-study and trait differences (see Supplement;  @fig-s3).
 Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
@@
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-Raw data for both adult and juvenile life-history stages also presented but point are not separated by type for ease of presentation."
+Raw data for both adult and juvenile life-history stages also presented but points are not distinguished by different symbols for ease of presentation."
 #| echo: false
@@
 
-Using the ERA5 climate model, we extracted a 30-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution).
+Using the ERA5 climate model, we extracted a 72-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution).
 We used the historical temperature data for each geographical location to calculate a measure of thermal variability and predcitability (see *Methods*).
@@
 
-Acute and acclimation responses for wild ectotherms were much less common than studies on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations).
+Measurements of acute and acclimation responses from wild ectotherms were much less common than from captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` wild populations).
 Globally, there was a clear bias towards species in the Northern Hemisphere (@fig-fig6 A-C).
@@
 Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Across habitat types climate change is predicted to result in a only a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
+Across habitat types climate change is predicted to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in relative variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
 
@@
 
-Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates for ectotherms is expected to decrease to varying extents across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
-Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations that require further empirical and theoretical attention.
-We discuss our findings in the context of the current literature and highlight key areas for future research.
+Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can].
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
+These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
+Our results uncover an hitherto unrecognised dynamic where the benefits of acclimation may be counteracted by a decrease in trait variance.
 
@@
 Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 30-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution) using the *ncdf4* R package [vers.
+For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution) using the *ncdf4* R package [vers.
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].

### 2024-02-15 ms.qmd
Franks comments includes now

@@
 
-Understanding the interplay between plasticity and genetic adaptation has important implications for predicting a populations resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can; @cooke2021one].
-For example, incorporating phenotypic plasticity and adaptation into species distribution models has been shown to dampen the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
-In addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, impacting a population's capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
+Understanding the interplay between plasticity and genetic adaptation has important implications for predicting population resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can; @cooke2021one].
+For example, incorporating phenotypic plasticity and adaptation into species distribution models dampens the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
+In addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, thereby reducing the capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
 Quantifying the degree of plasticity and genetic/phenotypic variation in key physiological responses is therefore recognised as being critical to informing projections for organisms threatened by climate change [@cooke2021one].
 
-We show that plastic adjustments in physiological rates and changes in their relative variance differ across habitats.
-In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance in physiological rates providing more raw material for selection to operate.
-In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance in physiological rates, which may trade-off with the beneficial effects that acclimation provides at high temperatures.
-In terrestrial ectotherms, relative variance reductions are particularly pronounced and this coincides with a general inability to acclimate.
-Considering acute physiological rates of animals acclimated to high temperatures are generally still elevated compared to cold-acclimated animals (~7% increase), acclimatization may not always provide adaptive benefits under climate change, particularly when considering changes in relative variance.
+We show that acclimation of physiological rates and changes relative variance differ across habitats.
+In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance thereby maintaining the raw material for selection to operate.
+In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance so that the beneficial effects of acclimation trade-off against reduced potential for selection at high temperatures.
+In terrestrial ectotherms, relative variance reductions are particularly pronounced, and this coincides with a general inability to acclimate.
+Terrestrial ectotherms are therefore most vulnerable to climate because both compensations for potentially negative effect of temperature via acclimation, and adaptation to novel conditions are relatively ineffective.
+However, terrestrial species have greater opportunity for behavioural microhabitat selection which will decrease the impacts of climate change at least in complex, thermally heterogeneous environments [@huey2012predicting].
 
 Our findings highlight the potential vulnerability of terrestrial and marine ectotherms to climate change.
-Our meta-analytic results provide opportunities to parameterise predictive models in ways that capture the percentage changes in relative variances and acclimation responses when predicting species distributions or modelling population resilience in the face of climate warming.
+Our meta-analytic results provide percentage changes of relative variances and acclimation responses that can be used to parameterise models (e.g., species distribution models) [@bush2016incorporating; @demarche2019incorporating] to predict species distributions or assess population resilience in the face of climate warming.
 Our results also define the range of biological responses observed across diverse taxa (e.g., through prediction intervals) providing opportunities to incorporate realistic biological variation into the modelling process.
-Incorporating relevant variation in models is needed fully appreciate the biological consequences such changes in variation and plasticity have on ecological and evolutionary dynamics [@bush2016incorporating; @demarche2019incorporating] and are yet to be explored.
 
@@
 Life-history stages often occupy different ecological niches and exhibit different physiological responses, levels of plasticity, and patterns of mortality in response to temperature.
-As such, it is becoming increasingly important to understand how climate change will impact different life-history stages so that more realistic predictive models can be developed [@levy2015resolving; @petitgas2013impacts].
-Greater plasticity for early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
-Across a diversity of taxa, we show that there were generally similar patterns between early and late life stages -- both in terms of variance changes and the capacity for plasticity.
-Our results highlight that early life stages are not likely to be protected from the impacts of climate change.
-Evidence across the literature is equivocal with respect to the extent to which one life-stage is more or less plastic than another [@carter2020life; @moghadam2019heat].
+As such, it is becoming increasingly important to understand how climate change will impact different life-history stages [@levy2015resolving; @petitgas2013impacts].
+Greater plasticity in early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+We show that there were generally similar patterns between early and late life stages across a diversity of taxa, both in terms of variance changes and the capacity for plasticity.
+On average, our results show that early life stages are not more vulnerable to the impacts of climate change.
+However, our general meta-analytic findings do not imply that early life stages are not always less plastic, but that such responses are likely context or trait depedent [@carter2020life; @moghadam2019heat].
 For example, Moghadam *et al.* @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
 In contrast, Carter *et al.* @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
-Unsurprisingly, there is much variation in the literature and our findings suggest that patterns will depend on the species and traits in question.
-However, very few studies measure multiple life-history stages within the same population.
+Despite variation in the literature, very few studies measure multiple life-history stages within the same population.
 In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
@@
 ### ***Ecological consequences of reduced variation in physiological rates***
-Variance reductions in metabolism and performance (e.g., sprint speed) were key traits most strongly impacted by increased temperature.
-Changes in variability in physiological rates, particularly traits governing energy demand, could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming].
+Variance reductions in metabolism and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
+Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming].
 More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
@@
 They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-The differences in variance change across major habitat types suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
+Our results suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
 However, data testing the impacts of changes in variance on populations are limited to very few taxa.
-We need creative experimentation across broader taxa that manipulate levels of variance to understand their ecological outcomes.
-Our meta-analytic findings can be integrated into theoretical models by permitting model parameters to capture biologically relevant changes in variation.
-Such predictive models can then be integrated with experimental approaches to better understand the consequences of changes in variation on ecological dynamics.
+Future experimentation across a broader range of taxa should manipulate levels of variance to understand its ecological outcomes.
 
@@
 
-Theoretical evolutionary models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly if oscillations are predictable over time, making environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Theoretical evolutionary models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
 Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
 However, we did not find evidence to this effect.
-This finding is consistent with other meta-analyses [@barley2021limited; @Gunderson2015-hz] with thermal tolerance.
-The lack of relationship between physiological plasticity and environmental variability and predictability could be due to the challenges in estimating realistic microthermal environments given that air temperatures may not represent thermal environments many taxa actually experience in nature.
+Our finding is consistent with other meta-analyses [@barley2021limited; @Gunderson2015-hz] with thermal tolerance (which we did not consider here).
+Modelling correct microenvironments for over 200 species across such diverse habitats is challenging.
+The lack of a relationship between physiological plasticity and environmental variability and predictability could be due the fact that ectotherms simply seek out microhabitats that make their environment quite stable [@huey2012predicting].
 Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
@@
 Leung *et al.* @Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
-These findings, in combination with our results, suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@Leung2020; @hendry2016key].
+While it is unclear how these findings relate directly to acclimation because they integrate multiple forms of plasticity, they do suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@Leung2020; @hendry2016key].
 The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
@@
 
-Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may increase our ability to make more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one].
+Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one].
 While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
@@
 While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predictions.
-Our meta-analysis allows for realistic models to be parameterised and ensure they are better aligned with empirical findings.
+Our meta-analysis now provides the opportunity to parameterise models and ensure they are better aligned with empirical findings.
 Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
 Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across tropic levels within communities?
-What are the biochemical, cellular and physiological mechanisms that underly reduced variance in physiological rates?
+What are the biochemical, cellular, and physiological mechanisms that underly reduced variance in physiological rates?
 Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?

### 2024-02-15 ms.qmd
Fixing a few formatting issues, symbols and also referencing. Also found that one of the data frames was using all lnVR, lnCVR and lnRR to calculate and summaruse total effects so fixed that so it only uses one

@@
     # Traits 
-      traits_habitat <- data_long2 %>%
+      traits_habitat <- data_long2 %>% filter(grepl("lnRR_Q10",name))  %>% 
                       group_by(habitat, trait_category) %>%
                       summarise(spp_n = length(unique(species_full)), k = n())
-      traits_all <- data_long2 %>%
+      traits_all <- data_long2 %>% filter(grepl("lnRR_Q10",name)) %>% 
                       group_by(trait_category) %>%   
@@
 
-Using a large database on physiolgical rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10$^{\circ}$C temperature difference.
+Using a large database on physiolgical rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10&deg;C temperature difference.
 These standardised effects sizes can be converted to percentage differences to permit comparisons between the relative magnitudes of rate changes resulting from acclimation and relative variance changes at high temperatures.
@@
 
-Using the ERA5 climate model, we extracted a 72-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution).
+Using the ERA5 climate model, we extracted a 72-year period (1950-2022) of either surface air temperature (0.01&deg; resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25&deg; resolution).
 We used the historical temperature data for each geographical location to calculate a measure of thermal variability and predcitability (see *Methods*).
@@
 Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01$^{\circ}$ resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25$^{\circ}$ resolution) using the *ncdf4* R package [vers.
+For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01&deg; resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25&deg; resolution) using the *ncdf4* R package [vers.
 `r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
@@
 
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R [vers.
-`r utils::packageVersion("rotl")`, @Michonneau2016-if], and plotted using *ggtree* [vers.
-`r utils::packageVersion("ggtree")`, @Yu2017-wj].
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
+`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
 We resolved all polytomies in the tree.
 Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-We used the R packages *ape* [vers.
-`r utils::packageVersion("ape")`, @Paradis2019-gx] and *phytools* [vers.
-`r utils::packageVersion("phytools")`, @Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
 
@@
 Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured.
+In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10&deg;C differ depending on whether acute or acclimation responses are measured.
 If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
@@
 We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
-To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1$^{\circ}$C change as opoosed to 10$^{\circ}$C as follows:
+To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1&deg;C change as opoosed to 10&deg;C as follows:
 
@@
 
-@eq-lCVRpred turned the expected change across 10$^{\circ}$C to 1$^{\circ}$C.
+@eq-lCVRpred turned the expected change across 10&deg;C to 1&deg;C.
 We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenerios in 2080.

### 2024-02-16 ms.qmd
Fixing some stuff and rerender so this is dealt with for sureure drafts

@@
 We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 [the date after @Seebacher2015-wi searches were conducted] using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.

### 2024-02-16 ms.qmd
Fix some spelling errors and formatting Supp

@@
 
-#### Affliations:
+#### Affiliations:
 ^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
@@
 This trade-off could constrain evolutionary responses to climate change and reduce the potential benefits of portfolio effects.
-These findings have important evolutionary and ecological ramifications that affect our understanding of how climate change will impacts populations now and in the future.
+These findings have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
 
@@
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others raising the question of which ecosystems will be most vulnerable to contemporary climate change.
-Species occupying terrestrial ecosystems are are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
+Species occupying terrestrial ecosystems are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
 However, this conclusion has been questioned given that marine ectotherms have recently been shown to be closer to their upper thermal limits compared to terrestrial species [@Pinsky2019-fn].
@@
 
-Using a large database on physiolgical rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10&deg;C temperature difference.
+Using a large database on physiological rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10&deg;C temperature difference.
 These standardised effects sizes can be converted to percentage differences to permit comparisons between the relative magnitudes of rate changes resulting from acclimation and relative variance changes at high temperatures.
@@
 
-## **Materials and Methods**
+## **Methods & Protocols**
 ### *Literature collection*
@@
 Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability and predictability for the future.
-We used the CanESM2 climate model (2005-2100) under a high emissions scenerio (RCP8.5).
+We used the CanESM2 climate model (2005-2100) under a high emissions scenario (RCP8.5).
 
@@
 SN is supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
+
+## Data Availability 
+All data and code used to reproduce all analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis.
 
@@
 #| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
-Models estimates are based off 1,253 effect sizes from 139 studies.
+Model estimates are based off 1,253 effect sizes from 139 studies.
 
@@
 
-#### Publicaton Bias Analysis
-
-Funnel plots did not show any noticable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
+#### Publication Bias Analysis
+
+Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
 

### 2024-03-11 ms.qmd
Update to qmd

@@
 bibliography: ./bib/refs.bib
-csl: ./bib/nature.csl
+csl: ./bib/science-advances.csl
 format:
@@
 
+## **Short Title**: Reduced physiological rate variation in ectotherms
+
 <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
@@
 $\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
+
+## **Teasor**
+
+Climate change reduces physiological rate variation in ectotherms to impact ecological and evolutionary processes.
 

### 2024-03-12 ms.qmd
rerender doc for Sci Advances

@@
 ---
-title: "Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
+title: "Title: Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
 
-<p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
-
-#### Affiliations:
+## Authors: <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
+
+## Affiliations:
 ^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
@@
 
-## **Main**
+## **Introduction**
 
@@
 We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated Seebacher *et al.* @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et al.* [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
@@
 Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
-We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
-We included any papers that were missed between our searches and those of @Havird2020-mj.
-@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
+We also cross-checked papers we found in our searches with a recent paper by Havird *et al.* @Havird2020-mj, which also updates the dataset of Seebacher *et al.* @Seebacher2015-wi's.
+We included any papers that were missed between our searches and those of Havird *et al.* @Havird2020-mj.
+Havird *et al.* @Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et al.* @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et al.* @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that Seebacher *et al.* @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+As such, our database represents the most up-to-date dataset used by Seebacher *et al.* @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
 
@@
 
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+Following Noble *et al.* @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
 These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
@@
 #### *Comparing variance in physiological rates*
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+Nakagawa *et al.* @Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
 *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+We refer readers to Nakagawa *et al.* @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
 
@@
  @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10&deg;C temperature change along with its sampling variance (@eq-slnq10VR).
-While this is a useful metric, as discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+While this is a useful metric, as discussed by Nakagawa *et al.* @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
 As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
@@
 These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et al.* @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
 Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
@@
 ## Data Availability 
-All data and code used to reproduce all analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis.
+All data and code used to reproduce analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis.
 

### 2024-03-12 ms.qmd
MS updated. Need to format for Sci Advances now
Updating formatting for figs so they are bold and Fig.

@@
 crossref:
-  fig-title: 'Figure'
+  fig-title: '**Fig.**'
   fig-labels: arabic
   title-delim: "-"
-  fig-prefix: "Figure"
+  fig-prefix: "**Fig.**"
   tbl-prefix: "Table"
@@
 
-## Authors: <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
+## Authors:
+
+ <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
 
@@
 $\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
-
-## **Teasor**
-
-Climate change reduces physiological rate variation in ectotherms to impact ecological and evolutionary processes.
 
@@
 These findings have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+
+## **Teasor**
+
+Climate change reduces physiological rate variation in ectotherms to impact ecological and evolutionary processes.
 

### 2024-03-12 ms.qmd
Updating MS to Sci Adva formatting

@@
   fig-prefix: "**Fig.**"
-  tbl-prefix: "Table"
+  tbl-prefix: "**Table**"
 ---
@@
 
-Climate change is expected to result in warmer and more variable thermal environments globally.
-Greater thermal variability is expected to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-Such responses depend on genetic and phenotypic variability.
-However, most work has focused on changes in mean phenotypic responses to climate warming ignoring how temperature may also change phenotypic variability.
-Phenotypic variability may be particularly important at extreme, high temperatures, which would facilitate selection of resistant individuals or promote plasticity (acclimation) and thereby increase resilience to heat waves.
-Using newly developed effect size estimates and meta-analysis (>1900 effects from 226 species), we show that across habitats relative variance in physiological rates decreased at higher temperatures.
-Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
-Marine organisms also showed a capacity to acclimate to higher temperatures, but capacity for plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
-Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
-Neither life-history stage nor past climate explained effect variability.
-Our results show that beneficial acclimation responses may trade-off with reductions in physiological rate variance.
-This trade-off could constrain evolutionary responses to climate change and reduce the potential benefits of portfolio effects.
-These findings have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
-
-## **Teasor**
+Maintaining phenotypic variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
+Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
+Using newly developed effect size estimates and meta-analysis (>1900 effects from 226 species), we show that across habitats (marine, freshwater and terrestrial) relative variance in physiological rates decreased at higher temperatures.
+Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for plasticity (acclimation), highlighting the vulnerability of terrestrial ectotherms to climate change.
+Our results show that beneficial acclimation responses in some ecosystems (marine and freshwater) may trade-off with reductions in physiological rate variance that can have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+
+## **Teaser**
 

### 2024-03-13 ms.qmd
Re-organise and format for GCB/Ecol Letters

--- 2024-03-12 ms.qmd
@@
 ---
-title: "Title: Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
+title: "Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
-csl: ./bib/science-advances.csl
+csl: ./bib/ecology-letters.csl
 format:
@@
 crossref:
-  fig-title: '**Fig.**'
+  fig-title: 'Figure'
   fig-labels: arabic
   title-delim: "-"
-  fig-prefix: "**Fig.**"
+  fig-prefix: "Figure"
   tbl-prefix: "Table"
@@
 
-## **Short Title**: Reduced physiological rate variation in ectotherms
-
-## Authors:
-
 <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
@@
 $\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
+
+**Running head**: Reduced physiological rate variation in ectotherms
 
@@
 
-## **Teasor**
-
-Climate change reduces physiological rate variation in ectotherms to impact ecological and evolutionary processes.
-
 ## **Introduction**
@@
 4) How are means and variances in physiological rates expected to change under climate change?
+
+## **Materials and Methods**
+### *Literature collection*
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated Seebacher *et al.* @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et al.* [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
+
+Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
+We also cross-checked papers we found in our searches with a recent paper by Havird *et al.* @Havird2020-mj, which also updates the dataset of Seebacher *et al.* @Seebacher2015-wi's.
+We included any papers that were missed between our searches and those of Havird *et al.* @Havird2020-mj.
+Havird *et al.* @Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et al.* @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et al.* @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that Seebacher *et al.* @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
+While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
+As such, our database represents the most up-to-date dataset used by Seebacher *et al.* @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+
+We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
+To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
+In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
+After title and abstract screening, there was a total of 149 papers for full text screening.
+Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+We provide a PRISMA flow diagram of our extraction process in the *Supplement* (see @fig-prisma).
+
+### *Data Compilation*
+
+We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
+If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
+We extracted these data from text, tables or figures of a given paper.
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
+We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
+If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
+If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
+When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
+
+### *$Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances*
+
+Following Noble *et al.* @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+
+#### *Comparing changes in mean physiological rates*
+
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+
+$$
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10}
+
+Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures at which these rates are measured.
+Log transformation of this ratio makes the effect size normally distributed.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
+The sampling variance for @eq-lnq10 can be computed as follows (as described in @Noble2022-ty):
+
+$$
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-Vlnq10}
+
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations and $N_{1}$ and $N_{2}$ are the sample sizes in group 1 and 2, respectively.
+
+#### *Comparing variance in physiological rates*
+Nakagawa *et al.* @Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to Nakagawa *et al.* @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
+$$
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$${#eq-lnq10VR}
+$$
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slnq10VR}
+
+ @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10&deg;C temperature change along with its sampling variance (@eq-slnq10VR).
+While this is a useful metric, as discussed by Nakagawa *et al.* @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR}
+$$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$. We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+
+#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
+Using the mean, standard deviation, and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.
+
+### *Moderator Variables*
+
+We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
+These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et al.* @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
+As such, using the detailed information on the trait type, and its associated units from a given study, we categorized each effect size into one of 12 trait categories.
+These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
+Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('mito_leak') and oxidation ('mito_oxidation') as well as antioxidant enzymes ('antiox').
+All other traits not falling within these categories were placed into 'other'.
+
+### *Climate Data*
+
+To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
+It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
+Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
+
+Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01&deg; resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25&deg; resolution) using the *ncdf4* R package [vers.
+`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
+We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+For terrestrial species we estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
+We fit models using both air and soil temperature and found that the results were qualitatively similar.
+We therefore only present results for air temperature.
+
+Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
+To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
+To estimate thermal predictability, we calculated the auto-regressive time lag across the entire dataset.
+Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticity evolution.
+
+Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability and predictability for the future.
+We used the CanESM2 climate model (2005-2100) under a high emissions scenario (RCP8.5).
+
+### *Meta-Analysis*
+We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
+`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
+2.0, @Nakagawa2021-ls; @nakagawaorchard].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
+We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian).
+We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
+If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.
+
+#### *Multi-level Meta-analysis (MLMA) Models*
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, and phylogeny as random effects to account for non-independence.
+We also included trait as a random effect to account for trait variation within the data.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
+`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
+We resolved all polytomies in the tree.
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
+We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+
+#### *Multi-level Meta-regression (MLMR) Models*
+
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
+In all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`).
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
+To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
+As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).
+
+We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems).
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
+In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10&deg;C differ depending on whether acute or acclimation responses are measured.
+If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
+Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits.
+Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above).
+Variance in effects within trait categories appeared to vary depending on the trait type in question.
+Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
+To ensure models converged we limited to trait categories for each habitat with six or more effect sizes.
+
+Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type.
+We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g., @moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+
+#### *Modelling how climate change will impact on opportunity for selection*
+
+To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiological traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude.
+We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
+Our model included random effects of species, trait, phylogeny and study.
+We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
+To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1&deg;C change as opoosed to 10&deg;C as follows:
+
+$$
+lnCVR_{Q_{1}} = \frac{lnCVR_{Q_{10}}}{10}
+$$ {#eq-lCVRpred}
+
+@eq-lCVRpred turned the expected change across 10&deg;C to 1&deg;C.
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenerios in 2080.
+
+### *Publication Bias*
+
+We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) [@Nakagawa2022-gy].
+Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published.
+To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that accounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
 
@@
 ## **Results**
-
-Using a large database on physiological rates[@Seebacher2015-wi] for marine, freshwater and terrestrial ectotherms we apply new effect size estimates [@Noble2022-ty] that capture changes in mean physiological rates ($lnRR_{Q_{10}}$), and changes in their relative variance ($lnCVR_{Q_{10}}$), standardised to a 10&deg;C temperature difference.
-These standardised effects sizes can be converted to percentage differences to permit comparisons between the relative magnitudes of rate changes resulting from acclimation and relative variance changes at high temperatures.
-Acclimation responses can be determined by comparing acclimation $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acclimation}}}$) to acute $lnRR_{Q_{10}}$ ($lnRR_{Q_{10_{acute}}}$) from ectotherms acclimated to different temperatures.
-The difference in $lnRR_{Q_{10_{acclimation}}}$ compared to $lnRR_{Q_{10_{acute}}}$ measures the extent of acclimation (i.e., plasticity).
 
@@
 
-Using the ERA5 climate model, we extracted a 72-year period (1950-2022) of either surface air temperature (0.01&deg; resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25&deg; resolution).
-We used the historical temperature data for each geographical location to calculate a measure of thermal variability and predcitability (see *Methods*).
 Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
@@
 
-### ***Potential consequences of reduced plasticity and variance in physiological rates across ectotherms***
+### ***Consequences of reduced plasticity and variance in physiological rates across ectotherms***
 
@@
 
-## **Methods & Protocols**
-### *Literature collection*
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated Seebacher *et al.* @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et al.* [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
-We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
-
-Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
-We also cross-checked papers we found in our searches with a recent paper by Havird *et al.* @Havird2020-mj, which also updates the dataset of Seebacher *et al.* @Seebacher2015-wi's.
-We included any papers that were missed between our searches and those of Havird *et al.* @Havird2020-mj.
-Havird *et al.* @Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et al.* @Seebacher2015-wi's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et al.* @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that Seebacher *et al.* @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
-While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by Seebacher *et al.* @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
-
-We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
-To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
-In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
-After title and abstract screening, there was a total of 149 papers for full text screening.
-Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
-We provide a PRISMA flow diagram of our extraction process in the *Supplement* (see @fig-prisma).
-
-### *Data Compilation*
-
-We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
-If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
-We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
-We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
-For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
-If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
-If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
-When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
-
-### *$Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances*
-
-Following Noble *et al.* @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
-Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
-
-#### *Comparing changes in mean physiological rates*
-
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
-
-$$
-  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10}
-
-Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures at which these rates are measured.
-Log transformation of this ratio makes the effect size normally distributed.
-@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
-The sampling variance for @eq-lnq10 can be computed as follows (as described in @Noble2022-ty):
-
-$$
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-Vlnq10}
-
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations and $N_{1}$ and $N_{2}$ are the sample sizes in group 1 and 2, respectively.
-
-#### *Comparing variance in physiological rates*
-Nakagawa *et al.* @Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to Nakagawa *et al.* @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
-
-$$
-lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$${#eq-lnq10VR}
-$$
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slnq10VR}
-
- @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10&deg;C temperature change along with its sampling variance (@eq-slnq10VR).
-While this is a useful metric, as discussed by Nakagawa *et al.* @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
-As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR}
-$$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$. We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-
-#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-Using the mean, standard deviation, and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.
-
-### *Moderator Variables*
-
-We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et al.* @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
-As such, using the detailed information on the trait type, and its associated units from a given study, we categorized each effect size into one of 12 trait categories.
-These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
-Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('mito_leak') and oxidation ('mito_oxidation') as well as antioxidant enzymes ('antiox').
-All other traits not falling within these categories were placed into 'other'.
-
-### *Climate Data*
-
-To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
-It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
-Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
-
-Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01&deg; resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25&deg; resolution) using the *ncdf4* R package [vers.
-`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
-We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
-For terrestrial species we estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
-We fit models using both air and soil temperature and found that the results were qualitatively similar.
-We therefore only present results for air temperature.
-
-Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
-To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
-To estimate thermal predictability, we calculated the auto-regressive time lag across the entire dataset.
-Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticity evolution.
-
-Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability and predictability for the future.
-We used the CanESM2 climate model (2005-2100) under a high emissions scenario (RCP8.5).
-
-### *Meta-Analysis*
-We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
-We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021-ls; @nakagawaorchard].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
-We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian).
-We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
-If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.
-
-#### *Multi-level Meta-analysis (MLMA) Models*
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, and phylogeny as random effects to account for non-independence.
-We also included trait as a random effect to account for trait variation within the data.
-Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
-We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
-`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
-`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
-We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
-`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
-
-#### *Multi-level Meta-regression (MLMR) Models*
-
-After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
-In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`).
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
-To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
-As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).
-
-We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems).
-Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10&deg;C differ depending on whether acute or acclimation responses are measured.
-If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
-Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits.
-Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above).
-Variance in effects within trait categories appeared to vary depending on the trait type in question.
-Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
-To ensure models converged we limited to trait categories for each habitat with six or more effect sizes.
-
-Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type.
-We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g., @moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
-
-#### *Modelling how climate change will impact on opportunity for selection*
-
-To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiological traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude.
-We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
-Our model included random effects of species, trait, phylogeny and study.
-We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
-To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1&deg;C change as opoosed to 10&deg;C as follows:
-
-$$
-lnCVR_{Q_{1}} = \frac{lnCVR_{Q_{10}}}{10}
-$$ {#eq-lCVRpred}
-
-@eq-lCVRpred turned the expected change across 10&deg;C to 1&deg;C.
-We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenerios in 2080.
-
-### *Publication Bias*
-
-We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) [@Nakagawa2022-gy].
-Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published.
-To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that accounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
-
 ## Funding
@@
 
-## Data Availability 
+## Data and code availability 
 All data and code used to reproduce analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis.
+
+## Author contributions
+Conceptualization: DWAN, FK, FS, SN; Methodology: DWAN, AB, FK, FS, SN; Investigation: DWAN, FK, FS, SN; Visualization: DWAN; Supervision: DWAN, SN, FS; Writing—original draft: DWAN; Writing—review & editing: DWAN, AB, FK, FS, SN.
+
+## Conflict of interest
+Authors declare that they have no competing interests.
 

### 2024-03-13 ms.qmd
Update formatting for GCB

@@
 We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated Seebacher *et al.* @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after Seebacher *et al.* [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
@@
 Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
-We also cross-checked papers we found in our searches with a recent paper by Havird *et al.* @Havird2020-mj, which also updates the dataset of Seebacher *et al.* @Seebacher2015-wi's.
-We included any papers that were missed between our searches and those of Havird *et al.* @Havird2020-mj.
-Havird *et al.* @Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to Seebacher *et al.* @Seebacher2015-wi's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the Seebacher *et al.* @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that Seebacher *et al.* @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
+We included any papers that were missed between our searches and those of @Havird2020-mj.
+@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by Seebacher *et al.* @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
 
@@
 
-Following Noble *et al.* @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
 These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
@@
 #### *Comparing variance in physiological rates*
-Nakagawa *et al.* @Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
 *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to Nakagawa *et al.* @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
 
@@
  @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10&deg;C temperature change along with its sampling variance (@eq-slnq10VR).
-While this is a useful metric, as discussed by Nakagawa *et al.* @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
+While this is a useful metric, as discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
 As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
@@
 However, our general meta-analytic findings do not imply that early life stages are not always less plastic, but that such responses are likely context or trait depedent [@carter2020life; @moghadam2019heat].
-For example, Moghadam *et al.* @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-In contrast, Carter *et al.* @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
+In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
 Despite variation in the literature, very few studies measure multiple life-history stages within the same population.
@@
 Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-For example, Kooijman *et al.* @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
 They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
@@
 Randomly fluctuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
-For example, using seed beetles (*Callosobruchus maculatus*), Hallsson *et al.* @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
-Leung *et al.* @Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
+For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
+@Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
 While it is unclear how these findings relate directly to acclimation because they integrate multiple forms of plasticity, they do suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@Leung2020; @hendry2016key].

### 2024-03-14 ms.qmd
Updated GCB. Something weird as Sanderson paper was missed. Made sure it was cited as it's important.

@@
 Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change (i.e., the portfolio effect) [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013].
+Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change (i.e., the portfolio effect) [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013; @Sanderson2023].
 Decreases in phenotypic variance also suggests strong stabilising selection or reflects constraints on performance [@Scheiner2020; @Dewitt1998].
-Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation].
+Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation; @Sanderson2023].
 The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date there are few data testing the importance of variances in this context [@Scheiner2020].
@@
 
-Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can].
+Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023].
 Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
@@
 Variance reductions in metabolism and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
-Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming].
+Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
 More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
@@
 
-Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one].
+Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
 While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.

### 2024-03-20 ms.qmd
Shorten abstract

@@
 Climate change is expected to result in warmer and more variable thermal environments globally.
-Greater thermal variability is expected to result in strong selection pressures leading to genetic adaptation and/or the evolution of adaptive phenotypic plasticity.
-Such responses depend on genetic and phenotypic variability.
-However, most work has focused on changes in mean phenotypic responses to climate warming ignoring how temperature may also change phenotypic variability.
-Phenotypic variability may be particularly important at extreme, high temperatures, which would facilitate selection of resistant individuals or promote plasticity (acclimation) and thereby increase resilience to heat waves.
-Using newly developed effect size estimates and meta-analysis (>1900 effects from 226 species), we show that across habitats relative variance in physiological rates decreased at higher temperatures.
+Maintaining phenotypic variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
+Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
+Using newly developed effect size estimates and meta-analysis (>1900 effects from 226 species), we show that across habitats relative variance in physiological rates decreases at higher temperatures.
 Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
@@
 Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
-Neither life-history stage nor past climate explained effect variability.
-Our results show that beneficial acclimation responses may trade-off with reductions in physiological rate variance.
-This trade-off could constrain evolutionary responses to climate change and reduce the potential benefits of portfolio effects.
-These findings have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+Our results show that beneficial acclimation responses in some ecosystems (marine and freshwater) may trade-off with reductions in physiological rate variance that can have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
 

### 2024-05-17 ms.qmd
Revising intro

@@
 ---
-title: "Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
+title: "Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
 Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
-Using newly developed effect size estimates and meta-analysis (>1900 effects from 226 species), we show that across habitats relative variance in physiological rates decreases at higher temperatures.
+We developed effect size estimates that quantify how physiological variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
+We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures.
 Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
@@
 Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability in the past should result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
-Without plasticity or adaptation, high extinction rates are predicted unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
-Phenotypic plasticity is expected to be the 'first line of defence' against changing climates, thereby buying time for genetic adaptation to take place (i.e., the 'plasticity first hypothesis')[@WestEberhard2003; @Lande2009].
-Phenotypic plasticity is predicted to evolve when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Despite this theoretical expectation, empirical support is scant (but see [@Leung2020]), likely because many organisms can behaviorally adjust micro-habitat selection to offset thermal stress, the costs of plasticity are high [@Chevin2015; @Dewitt1998], or the prediction is only supported for specific life-history stages.
-
-Reversible phenotypic plasticity, such as acclimation, is expected to provide greater potential to buffer populations from climate impacts as responses are relatively rapid and can therefore be fine-tuned to proximate environmental conditions (assuming the costs of plasticity are low) [@Dewitt1998; @Scheiner2020].
-Acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to facilitate a rapid response to the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
-However, the focus up to now has been primarily on mean physiological responses.
-For example, mean thermal tolerances or acclimation capacities in a population are likely to shift in response to thermal environments [@Seebacher2015-wi; @Gunderson2015-hz; @Havird2020-mj; @Pottier2022].
-However, it is possible that intrapopulation variability might also be impacted in addition to the mean.
+Greater thermal variability in the past is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
+
+Phenotypic plasticity is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to proximate environmental conditions making it the first ‘line-of-defense’ against rapid environmental change [@Dewitt1998; @Scheiner2020].
+For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses.
+Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
+Acclimation to higher temperatures does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather rates remain similar to acute responses at high temperatures ('no acclimation') or only partially compensate [@huey1999testing; @Havird2020-mj].
+Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
+However, the focus up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
+
+As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted. NEED MORE ABOUT WHY VARIANCE NOT JUST IMPORTANCE
+
 Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
@@
 Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures at which these rates are measured.
+$R_{1}$ and $R_{2}$ can be taken from samples of organisms measured acutely at two temperatures or after having been acclimated at these same temperatures.
 Log transformation of this ratio makes the effect size normally distributed.
@@
 #### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-Using the mean, standard deviation, and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator.
+As indicated above, $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures.
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
 As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.
@@
 ## Data and code availability 
-All data and code used to reproduce analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis.
+All data and code used to reproduce analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis and is deposited in Zenodo (https://doi.org/10.5281/zenodo.11123600).
 

### 2024-05-17 ms.qmd
Rewording

@@
 Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
-Acclimation to higher temperatures does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather rates remain similar to acute responses at high temperatures ('no acclimation') or only partially compensate [@huey1999testing; @Havird2020-mj].
+Acclimation alters acute thermal sensitivity but does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].

### 2024-05-17 ms.qmd
More wording on acclimdation. Not quite accurate and it was missing an important aspect

@@
 Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
-Acclimation alters acute thermal sensitivity but does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
+Acclimation alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
+Acclimation, however, does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].

### 2024-05-19 ms.qmd
Editing some awkward sentences

@@
 Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability in the past is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Greater thermal variability is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
 Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].

### 2024-06-11 ms.qmd
Daling with another comment
Adding some revisions to supp[lement, but I think I will move to main as it's important.

@@
 In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
+In all cases, frequentist and Bayesian models resulted in the same conclusions.
 For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
@@
 ```
+
+#### Exploring the impact of temperature on $lnRR_{Q_{10}}$ PROBABLY JUST MOVE TO THE MAIN TEXT
+
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates is linear on the log scale.
+While $Q_{10}$ has been used exstensively in the physiological literature, there is a preference for using a Boltzmann – Arrhenius relationship to model temperature effects because it has been suggested to better incorperate the kinetics of chemical reactions [@gillooly2001effects].
+Over biologically realistic temperature ranges the Boltzmann – Arrhenius relationship and van't Hoff approaches can vary by as much as 15%.
+Despite this, @white2012information compared modelling the temperature-dependent effects on metabolic rate using both the Boltzmann – Arrhenius relationship and van't Hoff ($Q_{10}$) relationship, showing that, when prokaryotes are excluded, the van't Hoff equation provides a 5.8 fold better fit to the data than the Boltzmann – Arrhenius relationship.
+Given that we restricted studies only to those that manipulated temperatures within normal operating ranges for a species and we only focus on eukaryotes, $Q_{10}$ should remain an appropriate way to capcture temperature dependent effects.
+However, given that it is not possible to collect full thermal performance curves for species within our data it was not strickly possible to validate this assumption directly.
+As such, we conducted a series of additonal analyses to better understand when the log-linearity assumption may be violated.
+
+First, we took the maximum temperature of the experimental manipulations and include this temperature in the models.
+If log-linearity is a problem, $lnRR_{Q_{10}}$ should be underestimated for studies applying higher temperature treatments because such temperatures are expected to either converge on or cross the thermal optima.
+The benefit of such an approach means that we are able to statistically correct for the potential non-linearity in the data.
+
+Second, we explored the lowest 25% of $lnRR_{Q_{10}}$ values to understand if these studies have high relative tempereatures compared to the Topt for the species or if they have abnormally high temps.
+Lab and wild can be used.
+		3.
+Using wild populations, extract the temperature time series across the year (range, mean, SD) and compare the temperature manipulations done in the study to those in nature.
+Do they fall within the range?
+How far are they from their upper temperatures?
+		4.
+Using the difference between the upper temperatures in nature to the upper temperature of the experiment, include this as a moderator to explore if the deviation from natural conditions covaries with Q10.
+
+```{r, lnrrq10_nonlinear}
+
+# Subset the data
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                     max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor <- vcv(tree_lnrr, cor = TRUE)
+        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
+
+rerun = FALSE
+if(rerun){
+  model1.1_nl <- metafor::rma.mv(effect_size ~ max_temp_c, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes_nl <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + mid_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.1_nl
+  saveRDS(model1.1_nl, file = "./output/models/lnRRQ10_1.1_nl")
+  saveRDS(model1.1_bayes_nl, file = "./output/models/lnRRQ10_1.1_bayes_nl")
+} else{ 
+  model1.1_nl <- readRDS("./output/models/lnRRQ10_1.1_nl")
+model1.1_bayes_nl <- readRDS("./output/models/lnRRQ10_1.1_bayes_nl")
+}
+
+```

### 2024-06-12 R/fig_concept.R
Adding in a conceptual figure which I may add to the methods

@@ -1,0 +1,3 @@
+version https://git-lfs.github.com/spec/v1
+oid sha256:9cd19047e92b1d3169dff953b8b0f72d180ddbd92b7345528558798d99e5bbf5
+size 2758

### 2024-06-12 ms.qmd
Updating models to include temp

--- 2024-05-19 ms.qmd
@@
 lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
 
@@
         A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
-
-# Found some other data entry problems from old dataset.
-Sample sizes are decimals.
-That's not correct.
-It has to be an integer.
-These are not the new data that we entered.
-Data now checked.
-Seemed to have resulted in a 'frame shift' in some data.
-Not sure how that happened, but it's now fixed.
-#hist(lnRRQ10_data$V)
-
-# Studies with big V, why? Check N
-lnRRQ10_data %>% filter(V >= 2)
 
@@
   # More realistic model with 
-  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model1.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 
@@
    # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
-   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+   model1.3_m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
 
-  model1.3_m_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model1.3_m_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
                                             ~1 | trait,
@@
                               R = list(species_full = m_phylo), 
-                              struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_m)
+                              struct = "HCS", rho = 0, phi = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_m, control = list(iter.max=1000, rel.tol=1e-8))
 
@@
   # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 + max_temp_c | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
 
     # More realistic model with traits in freshwater species
-  model1.3_f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model1.3_f <- metafor::rma.mv(effect_size ~  max_temp_c+c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
   # Heteroscedastic variance model for freshwater
-  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model1.3_f_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
   # Run the Bayesian equivalent of the top supported model. 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 + max_temp_c| spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
 
     # More realistic model with traits in terrestrial species
-  model1.3_t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model1.3_t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
   # Heteroscedastic variance model for terrestrial
-  model1.3_t_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model1.3_t_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
   # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 + max_temp_c| spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
 
@@
   # More realistic model with 
-  model1.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model1.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 
@@
   newdata <- data.frame( c_accl_time = 0, 
+                          max_temp_c = 0, 
                                 type = as.factor(rep(c("acute", "acclim"))), 
@@
 # Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
-  X <- model.matrix(~c_accl_time + type*habitat*life.hist, data = newdata)
+  X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = newdata)
 
@@
  if(rerun){ 
-    model1.s1 <- metafor::rma.mv(effect_size ~  c_accl_time + name, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model1.s1 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 ```
+
+#### Exploring the impact of temperature on $lnRR_{Q_{10}}$ PROBABLY JUST MOVE TO THE MAIN TEXT
+
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
+While $Q_{10}$ [@van1884etudes] has been used exstensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi], there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model temperature effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
+Over biologically realistic temperature ranges the BA and $Q_{10}$ approaches can vary at times by as much as 15% [@gillooly2001effects].
+However, debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence and both BA and $Q_{10}$ can exhibit curvilinearity at normal operating temperatures (as discussed in [@michaletz2024hotter]).
+@white2012information also showed that the BA model may not always perform better.
+For example, in eukaryotes the $Q_{10}$ approach provided a 5.8 fold better fit to metabolic rate data than the BA relationship [@white2012information].
+
+Given that we restricted studies only to those that manipulated temperatures within normal operating ranges for a species and we only focus on eukaryotes, $Q_{10}$ should remain an appropriate way to capture temperature-dependent effects [@michaletz2024hotter].
+However, given that it is not possible to collect full thermal performance curves for species within our data we could not validate this assumption directly.
+However, to correct mean effect size in our analysis as temperatures increase we included the maximum temperature of the experimental manipulations in our models.
+If the log-linearity assumption is violated then $lnRR_{Q_{10}}$ should decrease for studies applying higher temperature treatments because such temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
+To improve model interpretation we centred the maximum temperature around the mean temperature of the experimental treatments.
+
+```{r, lnrrq10_nonlinear}
+
+# Subset the data
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                     max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor <- vcv(tree_lnrr, cor = TRUE)
+        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
+
+rerun = FALSE
+if(rerun){
+  model1.1_nl <- metafor::rma.mv(effect_size ~ max_temp_c, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes_nl <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.1_nl
+  saveRDS(model1.1_nl, file = "./output/models/lnRRQ10_1.1_nl")
+  saveRDS(model1.1_bayes_nl, file = "./output/models/lnRRQ10_1.1_bayes_nl")
+} else{ 
+  model1.1_nl <- readRDS("./output/models/lnRRQ10_1.1_nl")
+model1.1_bayes_nl <- readRDS("./output/models/lnRRQ10_1.1_bayes_nl")
+}
+
+```

### 2024-06-12 ms.qmd
Fix models in metafor as double random slopes not possible. Doens't make a difference though to results and we have in Bayesian models anyway

@@
 if(rerun){
-   # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
+   # More realistic model with traits in marine species.
+Remove antioxidants because there are just too few effects.
+Note that, for orchardplot we can only fit one random slope, so we'll just use obs as results are unchanged and Bayesian models have it accounted for
    model1.3_m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
@@
                                             ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
+                                            ~1 | spp,
                                             ~1 | trait,
@@
                                             ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
+                                            ~1 | spp,
                                             ~1 | trait,
@@
                               R = list(species_full = m_phylo), 
-                              struct = "HCS", rho = 0, phi = 0, dfs = "contain", 
+                              struct = "HCS", rho = 0,  dfs = "contain", 
                               test = "t", data = lnRRQ10_data_m, control = list(iter.max=1000, rel.tol=1e-8))

### 2024-06-13 ms.qmd
Updating responses to reviewer comments and changes MS. Make some notes on what to add after rendered to track changes version

@@
 We developed effect size estimates that quantify how physiological variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
-We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures.
+We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures driven by the lower proportional increase in physiological rate variance relative to the mean.
 Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
@@
 Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+Importantly, as done in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
 We provide a PRISMA flow diagram of our extraction process in the *Supplement* (see @fig-prisma).
@@
 For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.
+As such, positive effect sizes suggest that the mean or relative variance is larger at the higher of the two temperatures (numerator) when standardized to 10&deg;C.
+
+#### *Assumptions of $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
+
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
+While this is likely in our data given that we restricted our analysis of $Q_{10}$ to standard operating temperatures for a given species, it may not always be satisfied given the diversity of species in our dataset.
+$Q_{10}$ [@van1884etudes] has been used exstensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi].
+However, there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model thermal effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
+While debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence it is important to recognise that both BA and $Q_{10}$ can exhibit curvilinearity as temperatures increase (as discussed in [@michaletz2024hotter]).
+@white2012information also showed that the BA model may not always perform better.
+For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8 fold better fit to metabolic rate data than the BA relationship [@white2012information].
+Given that studies included in our analysis never measured full performance curves at acute and acclimation temperatures it was not possible for us to compare different models of thermal dependence.
+Nonetheless, $Q_{10}$-based effect sizes remain the most practical effect-size for comparing thermal dependence when using existing empircial data, with the benefit that these effects having convenient properties that make them suitable for meta-analysis.
+Nonetheless, we control for possible violations of the log-linearity assumption in our analyses (see below).
 
@@
 
+In all our models we tested and corrected for the possibility of the log-linearity assumption of our effect sizes being violated.
+We predcited that, if $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we should see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
+To improve model interpretation we centred the maximum temperature around the mean temperature of the experimental treatments.
+
 #### *Modelling how climate change will impact on opportunity for selection*
@@
 
+  # Secondary sensitivity analysis that uses cluster robust variance estimation to deal with unaccounted sources of non-independence.
+Not completely dealing with sharced sampling covariances in data as when collected these data were never indicated in past studies so hard to build full VCV matrix.
+
+   model1.2_rve <- robust(model1.2, cluster = lnRRQ10_data$record_num) # Consistent.
+
+  # Baysian model allows us to propagate error better is should be more robust to non-independence
    model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
@@
 
+  # Robust variance estimator.
+    model1.3_m_rve <- robust(model1.3_m, cluster = lnRRQ10_data_m$record_num) # Mostly Consistent but some changes to p for some traits.
+
+  # Baeysian model
   model1.3_m_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
@@
 Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a decrease with increasing temperature across all habitat types, which was especially pronounced in terrestrial and marine ectotherms.
+Reductions in variance were driven by slower increases in the variance in physiological rates relative to the mean with scaling relationships between log standard deviation and log mean all being smaller than 1 and varying across habitats (See Supplementary Materials).
 Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
@@
 ```
+
+#### Mean-variance relationships justify use of $lnCVR_{Q_{10}}$
+We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
+We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean in physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
+We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
+
+```{r, fig-mv}
+#| label: fig-mv
+#| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
+Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
+
+# Model mean variance relationships to estimate the relationship
+    model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+    model_mv2  <- brm(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+
+mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd))) +
+                geom_point(aes(color = habitat), size = 2.2) + 
+                geom_smooth(method = "lm", se = FALSE) + 
+                labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
+                legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
+
+mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd))) +
+                geom_point(aes(color = habitat), size = 2.2) + 
+                geom_smooth(method = "lm", se = FALSE) + 
+                labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
+                legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
+
+(mv1 / mv2)  + plot_annotation(tag_levels = "A", tag_suffix = ")") + theme(plot.tag = element_text(size = 20, face = "bold"))
+
+```
+
+Overall, we found that the relationship between the mean and SD of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the relative variance in physiological rates does not increase proportionally as the mean increases.
+Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`).
 
@@
 
-$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
-While $Q_{10}$ [@van1884etudes] has been used exstensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi], there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model temperature effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
-Over biologically realistic temperature ranges the BA and $Q_{10}$ approaches can vary at times by as much as 15% [@gillooly2001effects].
-However, debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence and both BA and $Q_{10}$ can exhibit curvilinearity at normal operating temperatures (as discussed in [@michaletz2024hotter]).
-@white2012information also showed that the BA model may not always perform better.
-For example, in eukaryotes the $Q_{10}$ approach provided a 5.8 fold better fit to metabolic rate data than the BA relationship [@white2012information].
-
-Given that we restricted studies only to those that manipulated temperatures within normal operating ranges for a species and we only focus on eukaryotes, $Q_{10}$ should remain an appropriate way to capture temperature-dependent effects [@michaletz2024hotter].
-However, given that it is not possible to collect full thermal performance curves for species within our data we could not validate this assumption directly.
-However, to correct mean effect size in our analysis as temperatures increase we included the maximum temperature of the experimental manipulations in our models.
-If the log-linearity assumption is violated then $lnRR_{Q_{10}}$ should decrease for studies applying higher temperature treatments because such temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
-To improve model interpretation we centred the maximum temperature around the mean temperature of the experimental treatments.
-
 ```{r, lnrrq10_nonlinear}

### 2024-06-13 ms.qmd
More changes

@@
   lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
 
@@
           A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
-
-# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
-  #hist(lnCVRQ10_data$V)
-
-# Studies with big V, why? Check N
-  lnCVRQ10_data %>% filter(V >= 2)
 
@@
   # More realistic model 
-  model2.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
 
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
   # More realistic model 
-  model2.3 <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model2.3 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
 
-   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 
-  model2.3f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model2.3f <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
 
-  model2.3m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model2.3m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
   # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
-  model2.3t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model2.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
   # More realistic model 
-  model2.4 <- metafor::rma.mv(effect_size ~  c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
 
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 

### 2024-06-14 R/fig_concept.R
Update concept code

@@ -1,3 +1,3 @@
 version https://git-lfs.github.com/spec/v1
-oid sha256:9cd19047e92b1d3169dff953b8b0f72d180ddbd92b7345528558798d99e5bbf5
-size 2758
+oid sha256:bc72d3a1204001b6fbb8c5585568ceb09a58557bd11e81922a52d7d24858c8a7
+size 3090

### 2024-06-14 ms.qmd
Updating MS with suggsted changed from reviewers

@@
     reference-doc: ./bib/template.docx
+    output-file: "ms_revised.docx"
 editor_options: 
@@
 Low oxygen availability may be a major factor influencing the vulnerability of aquatic ecosystems, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
-Given that terrestrial ectotherms are expected to be closer to their thermal limits, an increase in temperature may have a stronger impact on variation in physiological rates within populations compared to aquatic ectotherms which may have important cascading effects on energy transfer and productivity across different ecosystems [@seebacher2023can; @barneche2021warming].
+Given the observed variation among terrestrial and aquatic ectotherms in their acclimation capacity and the different challenges associated with living in air versus water, the effect of climate warming on variation in physiological traits may differ among terrestrial and aquatic ecosystems, which may have important cascading effects on energy transfer and productivity between these ecosystems [@seebacher2023can; @barneche2021warming].
 
 Here, we use meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We then developed new effect sizes effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
+We then developed new effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
 2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
@@
 @Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
+Given the physiological traits we included were broader than @Havird2020-mj, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
 More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
@@
 While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used by @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
 
@@
 Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
-Importantly, as done in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
+Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
 We provide a PRISMA flow diagram of our extraction process in the *Supplement* (see @fig-prisma).
@@
 
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$).
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
 These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
 Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+
+```{r, fig-concept}
+#| label: fig-concept
+#| fig-width: 8
+#| fig-height: 12
+#| fig-cap: Calculations of acute and acclimation effect sizes.
+(A) Two idealised thermal performance curves for animals held at 'cold' ('blue') temperatures and warm ('red') temperatures.
+Shaded blue and red areas are the thermal optima of the performance curves.
+Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20$^\circ$C and $T_{2} = $^\circ$C) for both acclimation groups.
+At each temperature a mean physiological rate (R) (points) and it's standard deviation (SD) (error bars) are estimated.
+R1.1 and R1.2 indicated the mean and SD for the cold acclimated animals at temperature 1 and 2, respectively.
+R2.1 and R2.2 indicated the mean and SD for the warm acclimated animals at temperature 1 and 2, respectively.
+An example of how acute and acclimation $lnCVR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right hand side of the figure with reference to each of the four possible groups.
+Note that, two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
+(B) Species are expected, *a priori*, to vary in their thermal performance curves (thin lines) around an average (thick black line).
+We restricted our data to areas of each species' performance curve that fell within the natural thermal range of the species (thick lines on each species-level curve).
+However, given it was not possible to measure the full performance curve for each species some test temperatures within studies may have converged on or moved past the thermal optima.
+In such cases, we expected our $Q_{10}$ effect sizes to be smaller.
+
+fig_concept <- magick::image_read("output/figures/fig1_concept_full.png")
+plot(fig_concept)
+```
 
@@
 
-Where, $R_{1}$ and  $R_{2}$ are mean physiological rates and  $T_{1}$ and  $T_{2}$ are the temperatures at which these rates are measured.
+Where, $R_{1}$ and  $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and  $T_{2}$, respectively.
 $R_{1}$ and $R_{2}$ can be taken from samples of organisms measured acutely at two temperatures or after having been acclimated at these same temperatures.
@@
 
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations and $N_{1}$ and $N_{2}$ are the sample sizes in group 1 and 2, respectively.
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and  $T_{2}$, respectively.
 
@@
 These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that Seebacher *et al.* @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
 Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
@@
 
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 
-We show that acclimation of physiological rates and changes relative variance differ across habitats.
+We show that acclimation of physiological rates and changes in relative variance differ across habitats.
 In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance thereby maintaining the raw material for selection to operate.
-In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance so that the beneficial effects of acclimation trade-off against reduced potential for selection at high temperatures.
-In terrestrial ectotherms, relative variance reductions are particularly pronounced, and this coincides with a general inability to acclimate.
-Terrestrial ectotherms are therefore most vulnerable to climate because both compensations for potentially negative effect of temperature via acclimation, and adaptation to novel conditions are relatively ineffective.
-However, terrestrial species have greater opportunity for behavioural microhabitat selection which will decrease the impacts of climate change at least in complex, thermally heterogeneous environments [@huey2012predicting].
+In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance so that the beneficial effects of acclimation trade off against reduced potential for selection at high temperatures.
+In terrestrial ectotherms, relative variance reductions are particularly pronounced, and this coincides with a general inability to acclimate, which may make them more vulnerable to climate warming compared to aquatic ectotherms.
+However, terrestrial species also have greater opportunity for behavioural microhabitat selection which will decrease the impacts of climate change at least in complex, thermally heterogeneous environments [@huey2012predicting].
 
@@
 
-### ***Plasticity and variance in physiological rates do not differ between life-stages***
+### ***Plasticity and relative variance in physiological rates do not differ between life stages***
 Life-history stages often occupy different ecological niches and exhibit different physiological responses, levels of plasticity, and patterns of mortality in response to temperature.
 As such, it is becoming increasingly important to understand how climate change will impact different life-history stages [@levy2015resolving; @petitgas2013impacts].
-Greater plasticity in early life-stages of development is expected to be important to increase resilience to the effects of climate change because early life-stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
+Greater plasticity in early life stages of development is expected to be important to increase resilience to the effects of climate change because early life stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
 We show that there were generally similar patterns between early and late life stages across a diversity of taxa, both in terms of variance changes and the capacity for plasticity.
 On average, our results show that early life stages are not more vulnerable to the impacts of climate change.
-However, our general meta-analytic findings do not imply that early life stages are not always less plastic, but that such responses are likely context or trait depedent [@carter2020life; @moghadam2019heat].
+However, our general meta-analytic findings do not imply that early life stages are not always less plastic, but that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
 For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-In contrast, @carter2020life showed greater thermal plasticity in metabolism for adults but little in pupae of *Onthophagus taurus*.
+In contrast, @carter2020life showed greater thermal plasticity in metabolic rate for adults but little in pupae of *Onthophagus taurus*.
 Despite variation in the literature, very few studies measure multiple life-history stages within the same population.
@@
 
-### ***Ecological consequences of reduced variation in physiological rates***
-Variance reductions in metabolism and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
+### ***Ecological consequences of reduced relative variation in physiological rates***
+Relative variance reductions in metabolic rates and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
 Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
@@
 Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
-However, we did not find evidence to this effect.
-Our finding is consistent with other meta-analyses [@barley2021limited; @Gunderson2015-hz] with thermal tolerance (which we did not consider here).
+However, we did not find evidence of this effect, which is consistent with other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] (which we did not consider here).
 Modelling correct microenvironments for over 200 species across such diverse habitats is challenging.
-The lack of a relationship between physiological plasticity and environmental variability and predictability could be due the fact that ectotherms simply seek out microhabitats that make their environment quite stable [@huey2012predicting].
+The lack of a relationship between physiological plasticity and environmental variability and predictability could be due to the fact that ectotherms simply seek out microhabitats that make their environment quite stable [@huey2012predicting].
 Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
@@
 Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
-Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across tropic levels within communities?
+Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across trophic levels within communities?
 What are the biochemical, cellular, and physiological mechanisms that underly reduced variance in physiological rates?

### 2024-06-14 ms.qmd
Fixed some code

@@
                               test = "t", data = lnCVRQ10_data)
-
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
   # Save model
   saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
+
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model
   saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")

### 2024-06-14 ms.qmd
Adding in a test for assessing the power function for Grafen branch lengths

@@
 We will explore a few different options with p to determine the best power function
-
+      tree_p0.5 <- compute.brlen(tree, method = "Grafen", power = 0.5) # Probably most sensible power
+      tree_p0.6 <- compute.brlen(tree, method = "Grafen", power = 0.6) # Probably most sensible power
       tree_p0.7 <- compute.brlen(tree, method = "Grafen", power = 0.7) # Probably most sensible power
+      tree_p0.8 <- compute.brlen(tree, method = "Grafen", power = 0.8) # Probably most sensible power
+      tree_p0.9 <- compute.brlen(tree, method = "Grafen", power = 0.9) # Probably most sensible power
+      tree_p1.0 <- compute.brlen(tree, method = "Grafen", power = 1.0) # Probably most sensible power
 
      # Create null nodes 
+      tree_p0.5$node.label <- NULL # We don't use nodes and will cause a warning so create null node names(
+      tree_p0.6$node.label <- NULL # We don't use nodes and will cause a warning so create null node names(
       tree_p0.7$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
+      tree_p0.8$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
+      tree_p0.9$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
+      tree_p1.0$node.label <- NULL # We don't use nodes and will cause a warning so create null node names
 ```
@@
 ##################################################
+# Grafen test
+##################################################
+
+if(rerun){
+           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
+    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
+
+        mod_list <- list()
+
+    for(i in 1:length(list)){
+
+    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
+    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
+      model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+             mod_list[i] <- model1_phylo 
+      names(mod_list)[i] <- names(list)[i]                
+    }
+
+}
+
+##################################################
 # Model 1.1: Intercept only model. 
@@
 lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long))
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long), 
+                              max_temp_c = scale(temp_2, scale = FALSE))
 
@@
   # More realistic model with 
-  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.2          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + type + habitat + type:habitat, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.4          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.5          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.6          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c+ c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.7          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + cv_c + type, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 | spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
   # More realistic model with 
-  model3.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
 
@@
   # More realistic model with 
-  model3.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model3.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
+   model3.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild_acclim)
 
@@
     # Terrestrial Models
-    model3.8_t  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 We want predictability AND variance
-    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.10_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
     # Freshwater Models
-    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-    model3.9_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-     model3.10_f  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+     model3.10_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
     # Marine Models
-      model3.8_m  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+      model3.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-    model3.9_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-    model3.10_m  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+    model3.10_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
                                      c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
-                                     match = interaction(spp, lat, long))
+                                     match = interaction(spp, lat, long),
+                                     max_temp_c = scale(temp_2, scale = FALSE))
 
@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + t2(Longitude, Latitude) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
 
@@
   new_data_t <- data.frame(
+      max_temp_c = 0, 
       c_accl_time = 0,
@@
   new_data_m <- data.frame(
+    max_temp_c = 0, 
       c_accl_time = 0,
@@
   new_data_f <- data.frame(
+    max_temp_c = 0, 
       c_accl_time = 0,
@@
   lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
 
@@
   # More realistic model 
-  model3.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
+  model3.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | trait,
@@
 
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
 

### 2024-06-15 ms.qmd
Fixed up some code. Models running for testing phylogenetic power for branch length

@@
 ##################################################
-# Grafen test
+# Grafen mode comparison test with different power
 ##################################################
 
+rerun = FALSE
 if(rerun){
@@
                               test = "t", data = lnRRQ10_data) 
-             mod_list[i] <- model1_phylo 
+             mod_list[[i]] <- model1_phylo 
         names(mod_list)[i] <- names(list)[i]                
     }
+
+  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
+  saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
+
+} else {
+
+  # Load the model list
+    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+
+  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
+   delta_aic <- order(sapply(mod_list, function(x) AIC(x))) - min(order(sapply(mod_list, function(x) AIC(x))))
 

### 2024-06-15 ms.qmd
Moce code around

@@
 #############
+
+##################################################
+# Grafen mode comparison test with different power
+##################################################
+
+rerun = FALSE
+if(rerun){
+           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
+    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
+
+        mod_list <- list()
+
+    for(i in 1:length(list)){
+
+    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
+    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
+       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+             mod_list[[i]] <- model1_phylo 
+        names(mod_list)[i] <- names(list)[i]                
+    }
+
+  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
+  saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
+
+} else {
+
+  # Load the model list
+    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+
+  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
+   delta_aic <- order(sapply(mod_list, function(x) AIC(x))) - min(order(sapply(mod_list, function(x) AIC(x))))
+
+}
+
 ##################################################
@@
 sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
-
-##################################################
-# Grafen mode comparison test with different power
-##################################################
-
-rerun = FALSE
-if(rerun){
-           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
-    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
-
-        mod_list <- list()
-
-    for(i in 1:length(list)){
-
-    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
-    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
-       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data) 
-             mod_list[[i]] <- model1_phylo 
-        names(mod_list)[i] <- names(list)[i]                
-    }
-
-  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
-  saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
-
-} else {
-
-  # Load the model list
-    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
-
-  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
-   delta_aic <- order(sapply(mod_list, function(x) AIC(x))) - min(order(sapply(mod_list, function(x) AIC(x))))
-
-}
 

### 2024-06-15 ms.qmd
Adding preprint note to keep track of where it's at

@@
         names(mod_list)[i] <- names(list)[i]       
+        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
     }

### 2024-06-15 ms.qmd
Some code annotation

@@
 if(rerun){
+    # Create a list of the distinct trees to loop over
            list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
@@
 
+    # Create an empty list to store the models
         mod_list <- list()

### 2024-06-17 ms.qmd
More revisions for today. Mostly working on figures which are taking ages

@@
 #### *Multi-level Meta-analysis (MLMA) Models*
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, and phylogeny as random effects to account for non-independence.
-We also included trait as a random effect to account for trait variation within the data.
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
@@
 In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`).
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
 Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
@@
 In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10&deg;C differ depending on whether acute or acclimation responses are measured.
-If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
-Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits.
-Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above).
+For both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, if the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
+Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ changed across traits.
+Within each habitat (marine, freshwater, and terrestrial) we fit models that included an interaction between effect type (acute / acclimation) and trait category (as defined above).
 Variance in effects within trait categories appeared to vary depending on the trait type in question.
 Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
-To ensure models converged we limited to trait categories for each habitat with six or more effect sizes.
+To ensure models converged, we did not include trait categories that had less than six effect sizes.
 
@@
 
-We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling variance (or sampling standard error) [@Nakagawa2022-gy].
+We explored the possibility for publication bias graphically using funnel plots, and more formally by including sampling variance (or sampling standard error) in our meta-regression models  [@Nakagawa2022-gy].
 Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published.
@@
 ##################
-col <- c("#0871B9", "#F3B40D", "#1BB908")
+  viridis_cols <- c( "#21908CFF", "#440154FF","#228C22")
 
@@
 
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 8, branch.size = 2) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1, branch.size = 2) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
 
-  scale_fill_manual(values = c(col)) + ylim(-0.8, 2) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.7, size = 5)
+  scale_fill_manual(values = viridis_cols) + ylim(-0.5, 1.5) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.7, size = 5)
 
   p1.2 <- p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
-        axis.text = element_text(size = 15), legend.title = element_text(size = 15),
-                               legend.text = element_text(size = 15),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 24),
+                               legend.text = element_text(size = 24),
                                title = element_text(size = 24))
@@
 
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 8, branch.size = 2, k.pos = "none") +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  viridis_cols <- c( "#21908CFF", "#440154FF","#228C22")
+
+  #sum_data_p2 <- mod_results(model2.2, mod = "habitat", group = "record_num", by = "type", at = list(type = c("acute", "acclim")))
+
+  #ggplot(lnCVRQ10_data, aes(y = effect_size, x = habitat, colour = habitat, shape = type)) + ggbeeswarm::geom_quasirandom( method = "tukey", aes(color = habitat)) + 
+   #scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-1.5, 1.5) + scale_colour_manual(values = viridis_cols) + 
+   # theme_classic() + coord_flip()
+
+  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1, branch.size = 2, k.pos = "none") +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-1.5, 1.5) + scale_fill_manual(values = viridis_cols) +
 
@@
            label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x1-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(f_cvr_mean), digit = 2)), hjust = 0, size = 6) + 
+  annotate("text", x = x1-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 6) + 
   annotate("text", x = x1-0.15, y = 1, 
@@
            label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x2-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(m_cvr_mean), digit = 2)), hjust = 0, size = 6) +
+  annotate("text", x = x2-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 6) +
   annotate("text", x = x2-0.15, y = 1, 
@@
            label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = x3-0.15, y = -1.5, label = paste0("P = ", round(pmcmc(t_cvr_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col)) + ylim(-2, 2) + 
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5)
+    annotate("text", x = x3-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 6) + ylim(-1.5, 1.75) + 
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-2, 2)
 
   p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 15),
-                                       legend.title = element_text(size = 15),
-                               legend.text = element_text(size = 15),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 24),
+                               legend.text = element_text(size = 24),
                                title = element_text(size = 24))
 
-  ggsave(p2, filename = "./output/figures/fig2.png", width = 9.3, height = 8.8)
+  ggsave(p2, filename = "./output/figures/fig2.pdf", width = 9.3, height = 8.8)
 
@@
 Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a decrease with increasing temperature across all habitat types, which was especially pronounced in terrestrial and marine ectotherms.
+There were no differences between $lnCVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$.
 Reductions in variance were driven by slower increases in the variance in physiological rates relative to the mean with scaling relationships between log standard deviation and log mean all being smaller than 1 and varying across habitats (See Supplementary Materials).
-Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
+There was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
 In contrast, freshwater ectotherms exhibited a smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
@@
 
-# Look at the environment details across different habitats. Seems very similar. *** Check with ALEX ***
+# Look at the environment details across different habitats. Seems very similar.
   lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(cv), mean(acf_all))
@@
 
-  # Lets now use the whole posterior distribtion instead. This is a little hacky because the object is complicated
-
-######## *** THE CODE BELOW NEEDS SOME NEW CHECKING AS ABOVE WAS MODIFIED! ****
-
   # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
@@
 Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Across habitat types climate change is predicted to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% change in relative variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
+Climate change is predicted to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% reduction in relative variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
 
@@
 Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
-Predicted change in physiological rate variance (relative variance) for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
+Predicted change in relative physiological rate variance for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
 Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change).
@@
 Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronouced in terrestrial ectotherms (~28%).
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronounced in terrestrial ectotherms (~28%).
 These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
@@
 
-### ***Consequences of reduced plasticity and variance in physiological rates across ectotherms***
+### ***Implications of differing acclimation capacities and decreased relative variability in physiological rates among ectotherms***
 
@@
 #| label: fig-cvrtrait
-#| fig-cap: "Acute and Acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+#| fig-cap: "Acute and acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.

### 2024-06-17 ms.qmd
Moved code around forgot we needed data load first

@@
 #############
-
-##################################################
-# Grafen mode comparison test with different power
-##################################################
-
-rerun = FALSE
-if(rerun){
-    # Create a list of the distinct trees to loop over
-           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
-    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
-
-    # Create an empty list to store the models
-        mod_list <- list()
-
-    for(i in 1:length(list)){
-
-    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
-    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
-       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data) 
-             mod_list[[i]] <- model1_phylo 
-        names(mod_list)[i] <- names(list)[i]       
-        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
-    }
-
-  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
-    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
-
-} else {
-
-  # Load the model list
-    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
-
-  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
-   delta_aic <- order(sapply(mod_list, function(x) AIC(x))) - min(order(sapply(mod_list, function(x) AIC(x))))
-
-}
-
 ##################################################
@@
 sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
+
+##################################################
+# Grafen mode comparison test with different power
+##################################################
+
+rerun = FALSE
+if(rerun){
+    # Create a list of the distinct trees to loop over
+           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
+    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
+
+    # Create an empty list to store the models
+        mod_list <- list()
+
+    for(i in 1:length(list)){
+    i = 5
+    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
+    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
+       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+             mod_list[[i]] <- model1_phylo 
+        names(mod_list)[i] <- names(list)[i]       
+        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
+    }
+
+  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
+    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
+
+} else {
+
+  # Load the model list
+    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+
+  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
+   delta_aic <- order(sapply(mod_list, function(x) AIC(x))) - min(order(sapply(mod_list, function(x) AIC(x))))
+
+}
 

### 2024-06-17 ms.qmd
Mod_list finally done. As expeted. No effects of power

--- 2024-06-17 ms.qmd
@@
 sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
+
+##################################################
+# Grafen mode comparison test with different power
+##################################################
+
+rerun = FALSE
+if(rerun){
+    # Create a list of the distinct trees to loop over
+           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
+    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
+
+    # Create an empty list to store the models
+        mod_list <- list()
+
+    for(i in 1:length(list)){
+
+    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
+    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
+       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+             mod_list[[i]] <- model1_phylo 
+        names(mod_list)[i] <- names(list)[i]       
+        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
+    }
+
+  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
+    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
+
+} else {
+
+  # Load the model list
+    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+
+  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
+   aic <- sapply(mod_list, function(x) AIC(x))
+
+}
 

### 2024-06-18 ms.qmd
More responses and updating figures which are taking ages

@@
 
-### *Terrestrial and aquatic ectotherms differ in their capacity to acclimate but acclimation does not depend on life-history stage*
-
-Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
-
-Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
-
-Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
-Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
-
-```{r, lncvrq10}
-#| label: lncvrq10
+```{r, fig-phylo}
+#| label: fig-phylo
 #| echo: false
-#| warning: false
-#| error: false
-#| include: false
-#| cache: true
-
-#############
-  ## lnCVRQ10
-#############
-##################################################
-  # Organise the data and prune tree
-#################################################
-  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
-                                    max_temp_c = scale(temp_2, scale = FALSE))
-
-# Check and prune tree
-  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
-          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
-
-###################################################
-  # Model 2.1: Intercept only model.
-  # Used for heterogeneity analysis
-###################################################
-rerun = FALSE
-if(rerun){
-  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.1
-  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
-  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
-} else{ 
-        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
-  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
-}
-
-# Heterogeneity analysis
-   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
-  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
-  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
-
-    res_cvr <- posteriors_2.1[,"sigma"]
-   stdy_cvr <- posteriors_2.1[,"record_num"]
-  phylo_cvr <- posteriors_2.1[,"species_full"]
-    spp_cvr <- posteriors_2.1[,"spp"]
-  trait_cvr <- posteriors_2.1[,"trait"]
-  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
-
-  # Calculate I2
-     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
-   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
-     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
-    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
-   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
-     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
-
-  # Table
-     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
-                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
-
-###################################################
-  # Model 2.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
-  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
-
-  } else{
-        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
-  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
-}
-
-######################################################
-  # Bayesian Contrasts
-######################################################
-
-  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
-  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
-  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
-  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
-  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
-  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
-  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
-
-# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
-It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
-  # First get sample sizes
-    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
-
-  # Calculated weighted mean by sample size. 
-    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
-    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
-    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
-
-  # Lets now convert these to a %
-    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
-    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
-    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
-
-###################################################
-  # Model 2.3: Model controlling for acclimation time, 
-  # type and trait category assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.3 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
-  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
-
-  # We can also run subsets for each habitat
-   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-
-   # cor matrices
-   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
-       A_m_cvr <- vcv(tree_m_cvr, corr = FALSE)
-   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
-       A_f_cvr <- vcv(tree_f_cvr, corr = FALSE)
-   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
-       A_t_cvr <- vcv(tree_t_cvr, corr = FALSE)
-
-  model2.3f <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "f"))
-
-  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
-
-  model2.3m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "m"))
-  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
-
-  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
-  model2.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "t"))
-  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
-
-  } else{
-        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
-        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
-        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
-        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
-  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
-}
-
-###################################################
-  # Model 2.4: Model controlling for acclimation time, 
-  # type and life history stage assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-  # Save model
-  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
-
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model
-  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
-
-  } else{
-        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
-  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
-}
-
-```
-
-```{r, fig-1}
-#| label: fig-1
-#| fig-cap: "Taxonomic distribution of acute and acclimation $Q_{10}$ estimates across major habitats.
-**A)** Phylogenetic distribution of taxa contained within the data.
-The total number of acute and acclimation Q10 effect sizes are highlighted as well as whether the taxa are marine, freshwater or terrestrial.
-Silhouettes are representative taxa of major clades within the tree.
-**B)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
-**C)** Mean $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
-Note there were no differences between acute and acclimation $Q_{10}$ types.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI)."
-#| warning: false
-#| echo: false
-
-# Load and plot Figure 1.
-Note that this figure was derived using 3 separate code chunks described below.
-Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
-  fig1 <- image_read("./output/figures/fig1_final.png")
-  fig1
+#| fig-cap: "Phylogenetic distribution of acute and acclimation $Q_{10}$ estimates across major habitats.
+The total number of acute and acclimation $Q_{10}$ effect sizes are highlighted as well as whether the taxa are marine, freshwater or terrestrial.
+Silhouettes are only representative taxa of major clades within the tree.
+
 ##################
-  # Figure 1a plot
+  # Figure 2 plot
+  # Phylogeny
 ##################
@@
       scales1 <- c("#053061", "#D1E5F0", "#67001F")
-      scales2 <- c("#053061", "#E7E0DB", "#67001F")
       p1 <- d + 
@@
                hjust=0, font.size=3, width = 0.35) + 
-                scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
+                scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects") + theme(legend.text =element_text(size = 24),
+                                                                                    legend.title = element_text(size = 30, face = "bold"))
 
@@
 
+# Load and plot Figure 1.
+Note that this figure was derived using 3 separate code chunks described below.
+Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
+  fig1 <- image_read("./output/figures/fig1_final.png")
+  plot(fig1)
+
+```
+
+### *Terrestrial and aquatic ectotherms differ in their capacity to acclimate but acclimation does not depend on life-history stage*
+
+Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
+
+Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+
+Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
+Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+
+```{r, lncvrq10}
+#| label: lncvrq10
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+#| cache: true
+
+#############
+  ## lnCVRQ10
+#############
+##################################################
+  # Organise the data and prune tree
+#################################################
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
+          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
+
+###################################################
+  # Model 2.1: Intercept only model.
+  # Used for heterogeneity analysis
+###################################################
+rerun = FALSE
+if(rerun){
+  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.1
+  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
+  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
+} else{ 
+        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
+  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
+}
+
+# Heterogeneity analysis
+   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
+  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
+  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
+
+    res_cvr <- posteriors_2.1[,"sigma"]
+   stdy_cvr <- posteriors_2.1[,"record_num"]
+  phylo_cvr <- posteriors_2.1[,"species_full"]
+    spp_cvr <- posteriors_2.1[,"spp"]
+  trait_cvr <- posteriors_2.1[,"trait"]
+  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
+
+  # Calculate I2
+     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
+   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
+     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
+    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
+   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
+     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
+
+  # Table
+     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
+                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
+
+###################################################
+  # Model 2.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
+  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
+
+  } else{
+        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
+  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
+}
+
+######################################################
+  # Bayesian Contrasts
+######################################################
+
+  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
+  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
+  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
+  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
+  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
+  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
+  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
+
+# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
+It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
+  # First get sample sizes
+    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
+    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
+    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+
+  # Lets now convert these to a %
+    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
+    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
+    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
+
+###################################################
+  # Model 2.3: Model controlling for acclimation time, 
+  # type and trait category assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.3 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
+  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
+
+  # We can also run subsets for each habitat
+   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
+       A_m_cvr <- vcv(tree_m_cvr, corr = FALSE)
+   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
+       A_f_cvr <- vcv(tree_f_cvr, corr = FALSE)
+   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
+       A_t_cvr <- vcv(tree_t_cvr, corr = FALSE)
+
+  model2.3f <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "f"))
+
+  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
+
+  model2.3m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "m"))
+  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
+
+  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
+  model2.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "t"))
+  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
+
+  } else{
+        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
+        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
+        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
+        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
+  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
+}
+
+###################################################
+  # Model 2.4: Model controlling for acclimation time, 
+  # type and life history stage assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+  # Save model
+  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
+
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model
+  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
+
+  } else{
+        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
+  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
+}
+
+```
+
+```{r, fig-1}
+#| label: fig-1
+#| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
+**C)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
+Note there were no differences between acute and acclimation $Q_{10}$ types.
+For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Sample sizes are the same for panel A and B.
+Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+$\Beta$ values are the contrasts between acute and acclimation means.
+$\mu$ values are the overall mean $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ averaged across acute and acclimdation types within each habitat type.
+In both cases, their 95% CI's are indicated within square brackets.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+#| warning: false
+#| echo: false
+
 ##################
-  # Figure 1b plot
+  # Figure 2a plot
 ##################
-  viridis_cols <- c( "#21908CFF", "#440154FF","#228C22")
-
+
+  cols <- c("#053061","#D1E5F0",  "#67001F")
   k_lnrr <- manual_extract(model1.2, mod = "habitat", group = "record_num", exclude = NULL)
 
-p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1, branch.size = 2) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
   annotate("text", x = 1.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), "[", round(model1.2$ci.lb[3], 2)," to ", round(model1.2$ci.ub[3], 2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.20, y = 1.4, 
-         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-  annotate("text", x = 1.20, y = -0.8, label = "P < 0.001", hjust = 0, size = 6) +
+         label =TeX(paste0("$\\beta = $", round(model1.2$b[4], 2), "[", round(model1.2$ci.lb[4], 2)," to ", round(model1.2$ci.ub[4], 2), "] ", " $p_{MCMC}$ < 0.001")), hjust = 0, size = 8) + 
+  annotate("text", x = 1.20, y = -0.5, 
+         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
 
   annotate("text", x = 2.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-  annotate("text", x = 2.20, y = 1.4, 
-         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 2.20, y = -0.8, label = "P = 0.01", hjust = 0, size = 6) +
+         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ", " $p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
+  annotate("text", x = 2.20, y = -0.5, 
+         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
 
   annotate("text", x = 3.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ")), hjust = 0, size = 6) +
-  annotate("text", x = 3.20, y = 1.4, 
-         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 6) +
-  annotate("text", x = 3.20, y = -0.8, label = "P = 0.36", hjust = 0, size = 6) +
-
-  scale_fill_manual(values = viridis_cols) + ylim(-0.5, 1.5) +  annotate("text", label= paste0("k = ", k_lnrr$k, " (", k_lnrr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.7, size = 5)
+         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ", " $p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
+  annotate("text", x = 3.20, y = -0.5, 
+         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
+
+  scale_fill_manual(values = cols) + scale_color_manual(values = rep("black",3)) + ylim(-0.5, 1.5)
 
@@
                                        axis.text.y = element_text(angle = 45, size = 24),
-                                       legend.title = element_text(size = 24),
+                                       legend.title = element_text(size = 30),
                                legend.text = element_text(size = 24),
-                               title = element_text(size = 24))
-
-  ggsave(p1.2, filename = "./output/figures/fig1.png", width = 9.1, height = 9.2, device = "png")
+                               title = element_text(size = 24), legend.position = "top")
 
@@
 
-  viridis_cols <- c( "#21908CFF", "#440154FF","#228C22")
-
   #sum_data_p2 <- mod_results(model2.2, mod = "habitat", group = "record_num", by = "type", at = list(type = c("acute", "acclim")))
@@
 
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1, branch.size = 2, k.pos = "none") +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-1.5, 1.5) + scale_fill_manual(values = viridis_cols) +
+  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, k.pos = "none") +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-1.5, 1.5) +
+
+  scale_fill_manual(values = cols) + scale_color_manual(values = rep("black",3)) +
 
@@
     annotate("text", x = x3-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 6) + ylim(-1.5, 1.75) + 
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-2, 2)
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)
 
@@
                                        axis.text = element_text(size = 24),
-                                       axis.text.y = element_text(angle = 45, size = 24),
-                                       legend.title = element_text(size = 24),
+                                       axis.text.y = element_blank(),
+                                       legend.title = element_text(size = 30),
                                legend.text = element_text(size = 24),
-                               title = element_text(size = 24))
+                               title = element_text(size = 24), legend.position = "top")
 
@@
 
+  (p1.2 + p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
 ```
 
-### *Reduced variation in physiological rates in terrestrial and marine ectotherms*
+### *Relative variation in physiological rates is reduced in terrestrial and marine ectotherms*
 
@@
                                                           acf_all_c = scale(acf_all))
+
+# Check the environmental variability across habitats. What is the average SD in temps
+
+envi_var <- lnRRQ10_data_wild %>% group_by(habitat) %>% summarise(mean_SD = mean(sd), 
+                                                                  mean_pred = mean(acf_all),
+                                                                  stdy = length(unique(record_num)), 
+                                                                        n = n())
+
+###################################################
+  # model_envi: Check how tempeartures vary by habitat
+  # Expect terrestrial and freshwater systems tp be more variable 
+  # Than marine. Predcition for autocorrelation is less clear
+###################################################
+# Lets have a look at modelling whether the environmental variability and predcitability vary by habitats
+         sd_mod <- bf(log(sd) ~ habitat  + (1|record_num) + (1|spp)) 
+    acf_all_mod <- bf(acf_all ~ habitat  + (1|record_num) + (1|spp))
+
+model_envi <- brms::brm(sd_mod + acf_all_mod + set_rescor(TRUE), family = gaussian(),  control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
 

### 2024-06-18 ms.qmd
Fixing up Life history figure

@@
 These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
-Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('mito_leak') and oxidation ('mito_oxidation') as well as antioxidant enzymes ('antiox').
+Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
 All other traits not falling within these categories were placed into 'other'.
@@
 
-add_theme  <- function(){theme(axis.title  = element_text(size = 24),
-                               axis.text.y = element_text(size = 15),
-                               axis.text.x = element_text(size = 15),
-                              legend.title = element_text(size = 15),
-                               legend.text = element_text(size = 15),
-                               title = element_text(size = 24))}
-branch.size = 2
-trunk.size = 5
-
-p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1, 1.8)
-
-p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45,)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1, 1.8)
-
-p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) +  ylim(-1, 1.8)
-
-p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "top.left", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-2.5, 2.5)
-
-p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
-
-p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-2.5, 2.5)
-
-fig4 <-(p1 | p2 | p3) / (p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+branch.size = 2.8
+trunk.size = 1.8
+
+p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "none", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8)
+
+p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45,)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.8, 1.8)
+
+p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) +  ylim(-0.8, 1.8)
+
+p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "none", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.5)
+
+p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 1.5)
+
+p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.7, 1.5)
+
+fig4 <-(p1 | p2 | p3) / (p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")") + theme(legend.position = "bottom")
 ggsave(fig4, filename = "./output/figures/fig4_lh.pdf", width = 19, height = 12, device = "pdf")
@@
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-The x-axis is truncated for ease of visualisation."
+The x-axis is truncated for ease of visualisation.
+See methods section “Moderator Variables” for a full description of the trait categories.
+"
 #| echo: false

### 2024-06-18 ms.qmd
Adding new figure to suppl for temp

@@
 
-#### Exploring the impact of temperature on $lnRR_{Q_{10}}$ PROBABLY JUST MOVE TO THE MAIN TEXT
-
-```{r, lnrrq10_nonlinear}
-
-# Subset the data
-lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
-                                     max_temp_c = scale(temp_2, scale = FALSE))
-
-# Check and prune tree
-tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor <- vcv(tree_lnrr, cor = TRUE)
-        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
-
-rerun = FALSE
-if(rerun){
-  model1.1_nl <- metafor::rma.mv(effect_size ~ max_temp_c, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-  model1.1_bayes_nl <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.1_nl
-  saveRDS(model1.1_nl, file = "./output/models/lnRRQ10_1.1_nl")
-  saveRDS(model1.1_bayes_nl, file = "./output/models/lnRRQ10_1.1_bayes_nl")
-} else{ 
-  model1.1_nl <- readRDS("./output/models/lnRRQ10_1.1_nl")
-model1.1_bayes_nl <- readRDS("./output/models/lnRRQ10_1.1_bayes_nl")
-}
+#### Exploring the impact of temperature on $lnRR_{Q_{10}}$
+
+```{r, fig-lnrrq10_temp}
+#| label: fig-lnrrq10_temp
+#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and maximum temperature used in treatments within a study. Temperature is centered around the mean temperature in the data."
+
+bubble_plot(model1.2, mod = "max_temp_c", group = "record_num", ylab = TeX("$lnRR_{Q_{10}}"), xlab = TeX("Centered Maximum Temperature ($^{\\circ}$C)"), by = "habitat", condition.nrow = 1)  + theme(axis.title  = element_text(size = 30),
+                        axis.text = element_text(size = 26), 
+                        axis.text.y = element_text(size = 26),
+                        legend.text = element_text(size = 26), 
+                        legend.title = element_text(size = 24))
 

### 2024-06-18 ms.qmd
Few more reviewer comments dealt with

@@
 Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
-Our results show that beneficial acclimation responses in some ecosystems (marine and freshwater) may trade-off with reductions in physiological rate variance that can have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+Our results show that beneficial acclimation responses in some habitats (marine and freshwater) may trade-off with reductions in physiological rate variance that can have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
 
@@
 Periods of past climatic change have had disproportionate impacts on some ecosystems over others raising the question of which ecosystems will be most vulnerable to contemporary climate change.
-Species occupying terrestrial ecosystems are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
+Species occupying terrestrial habitats are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
 However, this conclusion has been questioned given that marine ectotherms have recently been shown to be closer to their upper thermal limits compared to terrestrial species [@Pinsky2019-fn].
-Marine and freshwater ecosystems appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
+Marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
 However, it is unclear if the magnitude of physiological adjustment is sufficient to compensate for potentially negative environmental effects, particularly when temperature interacts with other abiotic changes.
-Low oxygen availability may be a major factor influencing the vulnerability of aquatic ecosystems, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
-Given the observed variation among terrestrial and aquatic ectotherms in their acclimation capacity and the different challenges associated with living in air versus water, the effect of climate warming on variation in physiological traits may differ among terrestrial and aquatic ecosystems, which may have important cascading effects on energy transfer and productivity between these ecosystems [@seebacher2023can; @barneche2021warming].
+Low oxygen availability may be a major factor influencing the vulnerability of aquatic habitats, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
+Given the observed variation among terrestrial and aquatic ectotherms in their acclimation capacity and the different challenges associated with living in air versus water, the effect of climate warming on variation in physiological traits may differ among terrestrial and aquatic habitats, which may have important cascading effects on energy transfer and productivity between these habitats [@seebacher2023can; @barneche2021warming].
 
@@
 Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) has nearly identical AIC.
+As such, we used an intermediate value of p = 0.7.
 We used the R packages *ape* (vers.
@@
 Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$.
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower acclimation $lnRR_{Q_{10}}$.
 To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
@@
 
-We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems).
+We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine).
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
@@
 Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater ecosystems as temperatures increase, with the decrease being particularly pronounced in terrestrial ectotherms (~28%).
+Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater habitats as temperatures increase, with the decrease being particularly pronounced in terrestrial ectotherms (~28%).
 These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
@@
 They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-Our results suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial ecosystems.
+Our results suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial habitats.
 However, data testing the impacts of changes in variance on populations are limited to very few taxa.
@@
 Theoretical evolutionary models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial ecosystems [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
+Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
 However, we did not find evidence of this effect, which is consistent with other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] (which we did not consider here).
@@
 How much of the reduction in variance is driven by lower levels of genetic variance?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major habitats.
 

### 2024-06-18 ms.qmd
Some reworking of figs

@@
 
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-1 A).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-1).
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
 The two acute $lnRR_{Q_{10}}$ effect sizes differed significantly from each other (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), but on average they were in the same direction and only differed by ~10%.
@@
       # Plot the tree
-      scales1 <- c("#053061", "#D1E5F0", "#67001F")
+
+       col <- c("#0871B9", "#F3B40D", "#1BB908")
       p1 <- d + 
             #geom_tiplab(size=2, offset = 10) + 
-            geom_tippoint(aes(color=habitat), size = 2) +
+            geom_tippoint(aes(color=habitat), size = 2.5) +
             labs(color = "Habitat") + 
-            scale_colour_manual(values = scales1)
+            scale_colour_manual(values = col)
 
@@
 
-ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
+  ggsave(filename = "fig2_unedited_18June.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
 
@@
 Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
-  fig1 <- image_read("./output/figures/fig1_final.png")
-  plot(fig1)
+  fig2 <- image_read("./output/figures/Fig2_r1.png")
+  plot(fig2)
 
@@
 Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-1]B) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]B).
 
@@
 
-Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-2).
+Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-S2).
 Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
@@
 
-```{r, fig-1}
-#| label: fig-1
+```{r, fig-3}
+#| label: fig-3
 #| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
@@
 ##################
-  # Figure 2a plot
+  # Figure 3a plot
 ##################
 
-  cols <- c("#053061","#D1E5F0",  "#67001F")
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
   k_lnrr <- manual_extract(model1.2, mod = "habitat", group = "record_num", exclude = NULL)
 
-  p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
 
-  scale_fill_manual(values = cols) + scale_color_manual(values = rep("black",3)) + ylim(-0.5, 1.5)
-
-  p1.2 <- p1.2 + theme_classic() + theme(axis.title  = element_text(size = 24),
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-0.5, 1.5)
+
+  p3a <- p3a + theme_classic() + theme(axis.title  = element_text(size = 24),
                                        axis.text = element_text(size = 24),
@@
 ##################
-  # Figure 1c plot
+  # Figure 3b plot
 ################## 
@@
 
-  #sum_data_p2 <- mod_results(model2.2, mod = "habitat", group = "record_num", by = "type", at = list(type = c("acute", "acclim")))
-
-  #ggplot(lnCVRQ10_data, aes(y = effect_size, x = habitat, colour = habitat, shape = type)) + ggbeeswarm::geom_quasirandom( method = "tukey", aes(color = habitat)) + 
-   #scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-1.5, 1.5) + scale_colour_manual(values = viridis_cols) + 
-   # theme_classic() + coord_flip()
-
-  p2 <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, k.pos = "none") +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-1.5, 1.5) +
-
-  scale_fill_manual(values = cols) + scale_color_manual(values = rep("black",3)) +
-
-  annotate("text", x = x1, y = -2, 
+  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, k.pos = "none") +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) +
+
+  annotate("text", x = x1, y = -1.5, 
            label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
@@
 
-  annotate("text", x = x2, y = -2, 
+  annotate("text", x = x2, y = -1.5, 
            label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
@@
 
-  annotate("text", x = x3, y = -2, 
+  annotate("text", x = x3, y = -1.5, 
            label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
@@
 
-  p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
+  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
                                        axis.text = element_text(size = 24),
@@
 
-  ggsave(p2, filename = "./output/figures/fig2.pdf", width = 9.3, height = 8.8)
-
-  (p1.2 + p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+  fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+   ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 9.3, height = 8.8)
 
@@
 
-```{r, fig-2}
-#| label: fig-2
+```{r, fig-S2}
+#| label: fig-S2
 #| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
@@
 
-bubble_plot(model1.2, mod = "max_temp_c", group = "record_num", ylab = TeX("$lnRR_{Q_{10}}"), xlab = TeX("Centered Maximum Temperature ($^{\\circ}$C)"), by = "habitat", condition.nrow = 1)  + theme(axis.title  = element_text(size = 30),
+mod_table <- mod_results(model1.2, mod = "max_temp_c", group = "record_num", at = list(c_accl_time = 0))$mod_table  %>% mutate(moderator = moderator + mean(lnRRQ10_data$temp_2, na.rm = TRUE))
+
+col <- c("#0871B9", "#F3B40D", "#1BB908")
+ggplot(data = lnRRQ10_data, aes(x = temp_2, y = effect_size)) + 
+geom_point(aes(size = 1/sqrt(V), colour = habitat), alpha = 0.8) +
+labs(x = TeX("Maximum Temperature ($^{\\circ}$C)"), y = TeX("$lnRR_{Q_{10}}"), size = "Precision (1/SE)", color = "Habitat") + 
+ggplot2::geom_smooth(data = mod_table, 
+ggplot2::aes(x = moderator , y = lowerPR), method = "loess", 
+            formula = y ~ x, se = FALSE, lty = "dotted", colour = "black") + 
+ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = upperPR), method = "loess", 
+            formula = y ~ x, se = FALSE, lty = "dotted", colour = "black") + 
+ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = lowerCL), method = "loess", 
+            formula = y ~ x, se = FALSE, lty = "dashed", colour = "black") + 
+ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = upperCL), method = "loess", 
+            formula = y ~ x, se = FALSE, lty = "dashed", colour = "black") + 
+ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = estimate), method = "loess", 
+            formula = y ~ x, se = FALSE, colour = "black") + 
+            scale_colour_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ 
+theme_classic() + theme(axis.title  = element_text(size = 30), 
                         axis.text = element_text(size = 26), 
                         axis.text.y = element_text(size = 26),
-                        legend.text = element_text(size = 26), 
-                        legend.title = element_text(size = 24))
+                        legend.text = element_text(size = 24), 
+                        legend.title = element_text(size = 26))
 

### 2024-06-18 ms.qmd
Updates

@@
 
-  annotate("text", x = x1, y = -1.5, 
+  annotate("text", x = x1, y = -1.3, 
            label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
@@
 
-  annotate("text", x = x2, y = -1.5, 
+  annotate("text", x = x2, y = -1.3, 
            label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
@@
 
-  annotate("text", x = x3, y = -1.5, 
+  annotate("text", x = x3, y = -1, 
            label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 

### 2024-06-19 ms.qmd
New supp code and new models for acute response differences

@@
 Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability and predictability for the future.
-We used the CanESM2 climate model (2005-2100) under a high emissions scenario (RCP8.5).
+We used the CanESM2 climate model (2005-2100) [vers.
+1.2.0; @koen_hufkens_2019_2647541] under a high emissions scenario (RCP8.5).
 
@@
 ####################################################
- # Goal here is to test the assumption that acute Q10's are different or not
+ # Goal here is to test the assumption that acute Q10's are different or not. Note Reviewer wanted more analysis in this space so added additional models
  lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
@@
     saveRDS(model1.s1, file = "./output/models/model1.s1")
+
+    model1.s1_int <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name*habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1_int, file = "./output/models/model1.s1_int")
+
+    # Bayesian model
+    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+
+    saveRDS(model1.s1_bayes, file = "./output/models/model1.s1_bayes")
+
+    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+
+    saveRDS(model1.s1_bayes_int, file = "./output/models/model1.s1_bayes_int")
+
 } else{
             model1.s1 <-  readRDS(file = "./output/models/model1.s1")
+      model1.s1_bayes <- readRDS(file= "./output/models/model1.s1_bayes")
 }
+
+post_acute <- posterior_samples(model1.s1_bayes, pars = "^b")
+  hot_acute <- post_acute[,"b_Intercept"] + post_acute[,"b_namelnRR_Q10_acute_t2"]
+  cold_acute <- post_acute[,"b_Intercept"]
+  change_acute <- post_acute[,"b_namelnRR_Q10_acute_t2"]
+
+n_acutes <- lnRRQ10_data_acute  %>% group_by(name, habitat) %>% summarise(n = n(), stdy = n_distinct(record_num), spp = n_distinct(species_full))  %>% arrange(habitat)
 
@@
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
-The two acute $lnRR_{Q_{10}}$ effect sizes differed significantly from each other (acute responses were greater for animals acclimated to high temperatures -- $\beta$ = `r model1.s1$b[3]`, 95% CI: `r model1.s1$ci.lb[3]` to `r model1.s1$ci.ub[3]`, $p_{MCMC}$ = `r p_value(model1.s1$pval[3])`), but on average they were in the same direction and only differed by ~10%.
+The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures (($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`)) (@fig-Sacute).
+However, on average they were in the same direction and only differed by ~10%.
 As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
@@
 prisma
+```
+
+#### Comparing cool and warm acclimated acute responses
+
+```{r, @fig-Sacute}
+#| label: fig-Sacute
+#| fig.width: 12.7
+#| fig.height: 8.7
+#| fig-cap: "Mean acute $lnRR_{Q_{10}}$ for cool (blue) and warm (red) acclimated populations for terrestrial (dimonds), marine (square) and freshwater (circle) habitats.
+Note that poinst in each category show the full distribution of data irrespective of habitat for simplicity.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Note that means for all three habitats are displayed but there is weak evidence that the means differ between habitats given a model with and without an interaction with habitat are equally supported.
+Note that x-axis is truncated for ease of visualisation.
+Sample sizes for each habitat for acute warm and cold are: marine [warm = (131, 38, 29), cold = (136, 41, 32)], freshwater [warm = (294, 76, 61), cold = (293, 77, 63)], terrestrial [warm = (83, 31, 35), cold = (84, 31, 35)].
+Numbers within brackets are number of effects, number of studies and number of species."
+#| echo: false
+
+col_acute <- c("#3F5FAC", "#EF3D25")
+orchard_plot(model1.s1_int, mod = "name", by = "habitat", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, condition.lab = "Habitat") + scale_x_discrete(labels = c("LnRR_Q10_acute_t2" = "Warm - Acute", "LnRR_Q10_acute_t1" = "Cool - Acute")) + scale_fill_manual(values = col_acute) + scale_colour_manual(values = col_acute) + ylim (-0.5, 2.5) +  theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top") 
+                               #annotate("text", label= paste0("k = ", k_lnrr_acute$k, " (", k_lnrr_acute$sdy, ")"), x = c(1.2, 2.2), y = 2)
 ```

### 2024-06-19 ms.qmd
Finished addressing a bigger comment from R3, added new colours to code to harmonise figure colours across habitats

@@
 
-```{r}
+```{r, setup}
 #| label: setup
@@
 
-```{r data_setup_summary}
-
+```{r, data_setup_summary}
+#| label: data_setup_summary
+#| echo: false
 ##########################
@@
   # Load the model list
-    mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+    #mod_list <- readRDS("./output/models/lnRRQ10_phylo")
 
   # Have a look at the AIC of the various models to compare which power paramater is best, if any.
-   aic <- sapply(mod_list, function(x) AIC(x))
+   #aic <- sapply(mod_list, function(x) AIC(x))
 
@@
 
-    # Bayesian model
+    AIC(model1.s1_int, model1.s1) # AIC basically the same
+
+    # Bayesian models to check its the same result
     model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
@@
             model1.s1 <-  readRDS(file = "./output/models/model1.s1")
+            model1.s1_int <-  readRDS(file = "./output/models/model1.s1_int")
       model1.s1_bayes <- readRDS(file= "./output/models/model1.s1_bayes")
@@
 #| fig.height: 8.7
-#| fig-cap: "Mean acute $lnRR_{Q_{10}}$ for cool (blue) and warm (red) acclimated populations for terrestrial (dimonds), marine (square) and freshwater (circle) habitats.
-Note that poinst in each category show the full distribution of data irrespective of habitat for simplicity.
+#| fig-cap: "Mean acute $lnRR_{Q_{10}}$ for cool (blue) and warm (red) acclimated populations for terrestrial (diamonds), marine (square) and freshwater (circle) habitats.
+Note that points  in each category show the full distribution of data irrespective of habitat for simplicity.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-Note that means for all three habitats are displayed but there is weak evidence that the means differ between habitats given a model with and without an interaction with habitat are equally supported.
+Note that means for all three habitats are displayed but there is weak evidence that the means differ between habitats given models with and without an interaction with habitat are equally supported.
 Note that x-axis is truncated for ease of visualisation.
@@
 Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
-
-# Model mean variance relationships to estimate the relationship
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+# Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
     model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+    saveRDS(model_mv1, file = "./output/models/model_mv1")
+
     model_mv2  <- brm(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
-
-mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd))) +
+    saveRDS(model_mv2, file = "./output/models/model_mv2")
+
+mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd),color = habitat)) +
                 geom_point(aes(color = habitat), size = 2.2) + 
@@
                 labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                scale_colour_manual(values = col) + 
                 facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
@@
 
-mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd))) +
+mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd), color = habitat)) +
                 geom_point(aes(color = habitat), size = 2.2) + 
@@
                 labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                scale_colour_manual(values = col)  +
                 facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 

### 2024-06-19 ms.qmd
Dealing with intro comments and R1 acclimation

@@
 Climate change is expected to result in warmer and more variable thermal environments globally.
-Maintaining phenotypic variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
+Maintaining variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
 Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
@@
 
-Phenotypic plasticity is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
 Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to proximate environmental conditions making it the first ‘line-of-defense’ against rapid environmental change [@Dewitt1998; @Scheiner2020].
-For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses.
+For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
 Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
@@
 Acclimation, however, does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
+
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
@@
 
-Understanding how variability in physiological rates -- traits thought to be closely linked to fitness -- are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change (i.e., the portfolio effect) [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013; @Sanderson2023].
-Decreases in phenotypic variance also suggests strong stabilising selection or reflects constraints on performance [@Scheiner2020; @Dewitt1998].
-Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation; @Sanderson2023].
-The implications of changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date there are few data testing the importance of variances in this context [@Scheiner2020].
-
-Periods of past climatic change have had disproportionate impacts on some ecosystems over others raising the question of which ecosystems will be most vulnerable to contemporary climate change.
-Species occupying terrestrial habitats are thought to be particularly vulnerable given their weak acclimation abilities and greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
+Phenotypic plasticity is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Thermal variation and predictability are known to differ across major habitats (terrestrial, marine and freshwater), and as such, we expect the extent of plasticity to vary.
+Species occupying terrestrial habitats often show weak acclimation abilities and so are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
 However, this conclusion has been questioned given that marine ectotherms have recently been shown to be closer to their upper thermal limits compared to terrestrial species [@Pinsky2019-fn].
@@
 Given the observed variation among terrestrial and aquatic ectotherms in their acclimation capacity and the different challenges associated with living in air versus water, the effect of climate warming on variation in physiological traits may differ among terrestrial and aquatic habitats, which may have important cascading effects on energy transfer and productivity between these habitats [@seebacher2023can; @barneche2021warming].
+
+Understanding how variability in physiological rates are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
+Decreases in phenotypic variance also suggests strong stabilising selection or reflects constraints on performance [@Scheiner2020; @Dewitt1998].
+Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation; @Sanderson2023].
+Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change (i.e., the portfolio effect) [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013; @Sanderson2023].
+Changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date there are few data testing the importance of variances in this context [@Scheiner2020].
 
@@
 We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian).
+We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WAIC) (if Bayesian).
 We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
@@
 Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) has nearly identical AIC.
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) has nearly identical $AIC_{c}$.
 As such, we used an intermediate value of p = 0.7.
@@
 We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
-To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1&deg;C change as opoosed to 10&deg;C as follows:
+To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1&deg;C change as opposed to 10&deg;C as follows:
 
@@
                               test = "t", data = lnRRQ10_data)
+
+  # Additional model fit as a result of reviewer commenting that acclimation time is assumed to be linear.
+So, fit a non-linear parameter to see if it improves fit (even though data doesn't suggest it is the case).
+   model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+    AIC(model1.2_nl, model1.2) # Again, basically the same and go with most parsimonious model
 
@@
 ```
+
+```{r}
+  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + theme_classic() + theme(axis.title  = element_text(size = 30), 
+                        axis.text = element_text(size = 26), 
+                        axis.text.y = element_text(size = 26),
+                        legend.text = element_text(size = 24), 
+                        legend.title = element_text(size = 26))
+```

### 2024-06-19 ms.qmd
code at end

@@
 
-```{r}
-  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + theme_classic() + theme(axis.title  = element_text(size = 30), 
+```{r, fig-accl_time}
+#| label: fig-accl_time
+#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time within a study. Acclimation time is centered around the mean acclimation time in the data."
+
+  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(colour)) +theme_classic() + theme(axis.title  = element_text(size = 30),
                         axis.text = element_text(size = 26), 
@@
                         legend.title = element_text(size = 26))
+
 ```

### 2024-06-19 ms.qmd
Adding in a aclcimation time figure

--- 2024-06-19 ms.qmd
@@
 
-```{r}
-  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + theme_classic() + theme(axis.title  = element_text(size = 30), 
+```{r, fig-accl_time}
+#| label: fig-accl_time
+#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time for terrestrial (green), marine (orange) and freshwater (blue) habitats.
+Acclimation time is centered around the mean acclimation time (37.5 days) in the data.
+Not all studies reported acclimation time hence the total number of effects, k, was 1767."
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, colour = habitat, fill = habitat)) + scale_colour_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
                         axis.text = element_text(size = 26), 

### 2024-06-20 ms.qmd
Fixed up Fig 3 (previous fig 2). There were some mistakes in the objects and life-history means were being named the same, overwriting means for acute and acclim. This is fixed now.

@@
     # Marine 
-         m_acute <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
-        m_acclim <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
+         m_acute_lh <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
+        m_acclim_lh <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
     # Freshwater
             f_ad <- 4
-         f_acute <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
-        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
+         f_acute_lh <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
+        f_acclim_lh <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
     # Terrestrial
             t_ad <- 8
-         t_acute <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
-        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species
+         t_acute_lh <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
+        t_acclim_lh <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species
 
   # Acute differences between a and j across all habitats
-     acute_all <- c(m_acute, f_acute, t_acute); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
-    acclim_all <- c(m_acclim, f_acclim, t_acclim)
+     acute_all_lh <- c(m_acute_lh, f_acute_lh, t_acute_lh); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
+    acclim_all_lh <- c(m_acclim_lh, f_acclim_lh, t_acclim_lh)
 
@@
 
-  ggsave(filename = "fig2_unedited_18June.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
+  #ggsave(filename = "fig2_unedited_18June.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in")
 
@@
 #| include: false
-#| cache: true
+#| cache: false
 
@@
 
-```{r, fig-3}
-#| label: fig-3
-#| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across marine, freshwater, and terrestrial systems.
-**C)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across traits for marine, freshwater and terrestrial systems.
-Note there were no differences between acute and acclimation $Q_{10}$ types.
+```{r, fig-2}
+#| label: fig-2
+#| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
+**B)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
 For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\Beta$ values are the contrasts between acute and acclimation means.
-$\mu$ values are the overall mean $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ averaged across acute and acclimdation types within each habitat type.
+$\Beta$ values are the contrasts between acute and acclimation means within each habitat.
+$\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
 In both cases, their 95% CI's are indicated within square brackets.
-$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+$p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
+For ease of visualisation, all raw data for both acute and acclimation type effect sizes are presented as circles."
 #| warning: false
@@
 
-  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
 
-  annotate("text", x = 1.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(model1.2$b[4], 2), "[", round(model1.2$ci.lb[4], 2)," to ", round(model1.2$ci.ub[4], 2), "] ", " $p_{MCMC}$ < 0.001")), hjust = 0, size = 8) + 
-  annotate("text", x = 1.20, y = -0.5, 
-         label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
-
-  annotate("text", x = 2.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ", " $p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
-  annotate("text", x = 2.20, y = -0.5, 
-         label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = 3.5, y = 0, 
-         label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ", " $p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
-  annotate("text", x = 3.20, y = -0.5, 
-         label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
+  annotate("text", x = 1.5, y = -0.30, label =TeX(paste0("$\\beta = $", round(mean(f_acclim - f_acute), 2), "[", round(quantile(f_acclim - f_acute, 0.025), 2)," to ", round(quantile(f_acclim - f_acute, 0.975), 2), "] ", " $\\,p_{MCMC}$ < 0.001")), hjust = 0, size = 8) +
+  annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+  annotate("text", x = 2.5, y = -0.30, label =TeX(paste0("$\\beta = $", round(mean(m_acclim - m_acute), 2), "[", round(quantile(m_acclim - m_acute, 0.025), 2)," to ", round(quantile(m_acclim - m_acute, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
+  annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = 3.5, y = -0.30, label =TeX(paste0("$\\beta = $", round(mean(t_acclim - t_acute), 2), "[", round(quantile(t_acclim - t_acute, 0.025), 2)," to ", round(quantile(t_acclim - t_acute, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
+  annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
 
@@
 
-  annotate("text", x = x1, y = -1.3, 
-           label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x1-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 6) + 
-  annotate("text", x = x1-0.15, y = 1, 
-           label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
-
-  annotate("text", x = x2, y = -1.3, 
-           label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x2-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 6) +
-  annotate("text", x = x2-0.15, y = 1, 
-           label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) +
-
-  annotate("text", x = x3, y = -1, 
-           label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = x3-0.15, y = 1, 
-           label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = x3-0.15, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 6) + ylim(-1.5, 1.75) + 
+  annotate("text", x = x1, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+         annotate("text", x = x1, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x1-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 8) + 
+  annotate("text", x = x1-0.20, y = 1, label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = x2, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+     annotate("text", x = x2, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x2-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 8) +
+  annotate("text", x = x2-0.20, y = 1, label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = x3+0.10, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+  annotate("text", x = x3+0.10, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x3-0.10, y = 1, label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) + 
+  annotate("text", x = x3-0.10, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 8) +
+
+    labs(shape = "Type") +
     annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)
@@
                                legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top")
+                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")
 
   fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-
-   ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 9.3, height = 8.8)
+  fig3
+  ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 21.88, height = 9)
 
@@
 
+#### How acclimation time is related to $lnRR_{Q_{10}}$ 
 ```{r, fig-accl_time}

### 2024-06-20 ms.qmd
Update to figure captions. Added to moderators section a possible analysis with predcitions. Wait to chat with Shinichi and Frank before I run analysis. Corrected some mistakes in labelling objects on L735

@@
 Shaded blue and red areas are the thermal optima of the performance curves.
-Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20$^\circ$C and $T_{2} = $^\circ$C) for both acclimation groups.
-At each temperature a mean physiological rate (R) (points) and it's standard deviation (SD) (error bars) are estimated.
-R1.1 and R1.2 indicated the mean and SD for the cold acclimated animals at temperature 1 and 2, respectively.
-R2.1 and R2.2 indicated the mean and SD for the warm acclimated animals at temperature 1 and 2, respectively.
+Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20$^\circ$C and $T_{2} = 30$^\circ$C) for both curves.
+At each temperature a mean physiological rate (R) (points) and its standard deviation (SD) (error bars above and below mean) are estimated.
+R1.1 and R1.2 are the rates and associated SD (subscripted) for the cold acclimated animals at temperature 1 and 2, respectively.
+R2.1 and R2.2 are the rates and associated SD (subscripted) for the warm acclimated animals at temperature 1 and 2, respectively.
 An example of how acute and acclimation $lnCVR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right hand side of the figure with reference to each of the four possible groups.
@@
 However, given it was not possible to measure the full performance curve for each species some test temperatures within studies may have converged on or moved past the thermal optima.
-In such cases, we expected our $Q_{10}$ effect sizes to be smaller.
+In such cases, we expected our $Q_{10}$ effect sizes to be smaller as indicated by comparing the black dashed lines to grey dashed lines.
 
@@
 All other traits not falling within these categories were placed into 'other'.
+We also did a coarse-grained analysis of traits by comparing whole-organism measures (i.e., ‘cardiac’, ‘muscle’, ‘sprint’, ‘endurance’, ‘max MR’, ‘rest MR’), which all integrate a diversity of physiological and biochemical processes, with more fine-grained traits on enzymatic reactions (i.e., ‘metabolic enzyme’, ‘ATPase’, 'Proton Leak' and ‘OXPHOS’) which are more individualized biochemical processes.
+We expected that whole-organism traits would be more likely to maintain relative variation in physiological function because they are composed of a greater number of biochemical reactions and would be more likely to acclimate.
 
@@
   # Acute differences between a and j across all habitats
-     acute_all_lh <- c(m_acute_lh, f_acute_lh, t_acute_lh); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
+     acute_all_lh <- c(m_acute_lh, f_acute_lh, t_acute_lh); mean(acute_all_lh); quantile(acute_all_lh, c(0.025, 0.975)); pmcmc(acute_all_lh)
     acclim_all_lh <- c(m_acclim_lh, f_acclim_lh, t_acclim_lh)
@@
 
+### *Data Summary*
 The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
@@
 #| echo: false
-#| fig-cap: "Phylogenetic distribution of acute and acclimation $Q_{10}$ estimates across major habitats.
-The total number of acute and acclimation $Q_{10}$ effect sizes are highlighted as well as whether the taxa are marine, freshwater or terrestrial.
+#| fig-cap: "Phylogenetic distribution of acute and acclimation $lnRR_{Q_{10}}$/$lnCVR_{Q_{10}}$ estimates across major habitats.
+The total number of acute and acclimation  $lnRR_{Q_{10}}$/$lnCVR_{Q_{10}}$ effect sizes are indicated by the coloured bars as well as whether the taxa are marine, freshwater or terrestrial.
 Silhouettes are only representative taxa of major clades within the tree.
@@
 
-Different trait categories showed different acclimation responses across habitat types, however, they mirrored overall patterns (see Supplement; @fig-S2).
-Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all)`; Adult-Juvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all)`).
+Different trait categories showed different acclimation responses across habitat types (see Supplement; @fig-S2).
+Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
 
@@
 Sample sizes are the same for panel A and B.
-Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+In panels A and B, thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
 $\Beta$ values are the contrasts between acute and acclimation means within each habitat.
@@
 $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
-For ease of visualisation, all raw data for both acute and acclimation type effect sizes are presented as circles."
+For ease of visualisation, all teh raw data plotted for both acute and acclimation type effect sizes are presented as circles."
 #| warning: false
@@
 #| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult and juvenile life-history stages for Marine (A & D), Freshwater (B & E) and Terrestrial (C & F) ectotherms.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for marine (A & D), freshwater (B & E) and terrestrial (C & F) ectotherms.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-Raw data for both adult and juvenile life-history stages also presented but points are not distinguished by different symbols for ease of presentation."
+For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
+"
 #| echo: false
@@
                                title = element_text(size = 36))}
+
 branch.size = 2.8
@@
 
-p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "none", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8)
-
-p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45,)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.8, 1.8)
-
-p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) +  ylim(-0.8, 1.8)
-
-p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, legend.pos = "none", angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.5)
-
-p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 1.5)
-
-p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.7, 1.5)
-
-fig4 <-(p1 | p2 | p3) / (p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")") + theme(legend.position = "bottom")
-ggsave(fig4, filename = "./output/figures/fig4_lh.pdf", width = 19, height = 12, device = "pdf")
+n_lnrr_lh  <- lnRRQ10_data  %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+n_lncvr_lh <- lnCVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+
+x.pos = c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+m_r <- n_lnrr_lh %>% filter(habitat == "m")
+f_r <- n_lnrr_lh %>% filter(habitat == "f")
+t_r <- n_lnrr_lh %>% filter(habitat == "t")
+
+p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot)
+
+p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
+
+p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot)
+
+# CVR
+
+m_cv <- n_lncvr_lh %>% filter(habitat == "m")
+f_cv <- n_lncvr_lh %>% filter(habitat == "f")
+t_cv <- n_lncvr_lh %>% filter(habitat == "t")
+
+p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank())
+
+p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
+
+p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none")
+
+fig4 <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")") 
+ggsave(fig4, filename = "./output/figures/fig4_lh_r1.pdf", width = 22, height = 12, device = "pdf")
 
@@
 # Lets have a look at modelling whether the environmental variability and predcitability vary by habitats
+if(rerun){
      sd_mod <- bf(log(sd) ~ habitat  + (1|record_num) + (1|spp)) 
@@
   model_envi <- brms::brm(sd_mod + acf_all_mod + set_rescor(TRUE), family = gaussian(),  control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+  saveRDS(model_envi, file = "./output/models/model_envi")
+} else {
+  model_envi <- readRDS("./output/models/model_envi")
+}
 
@@
 
-Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity or changes in physiological rate variance among terrestrial, marine or freshwater populations (@fig-4; @fig-5).
+Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity (@fig-4) or changes in physiological rate variance (@fig-5) among terrestrial, marine or freshwater populations.
 
@@
 
-#### PRISMA Flow Diagram
+#### *PRISMA flow diagram*
 
@@
 
-#### Comparing cool and warm acclimated acute responses
-
-```{r, @fig-Sacute}
-#| label: fig-Sacute
-#| fig.width: 12.7
-#| fig.height: 8.7
-#| fig-cap: "Mean acute $lnRR_{Q_{10}}$ for cool (blue) and warm (red) acclimated populations for terrestrial (diamonds), marine (square) and freshwater (circle) habitats.
-Note that points  in each category show the full distribution of data irrespective of habitat for simplicity.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-Note that means for all three habitats are displayed but there is weak evidence that the means differ between habitats given models with and without an interaction with habitat are equally supported.
-Note that x-axis is truncated for ease of visualisation.
-Sample sizes for each habitat for acute warm and cold are: marine [warm = (131, 38, 29), cold = (136, 41, 32)], freshwater [warm = (294, 76, 61), cold = (293, 77, 63)], terrestrial [warm = (83, 31, 35), cold = (84, 31, 35)].
-Numbers within brackets are number of effects, number of studies and number of species."
-#| echo: false
-
-col_acute <- c("#3F5FAC", "#EF3D25")
-orchard_plot(model1.s1_int, mod = "name", by = "habitat", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, condition.lab = "Habitat") + scale_x_discrete(labels = c("LnRR_Q10_acute_t2" = "Warm - Acute", "LnRR_Q10_acute_t1" = "Cool - Acute")) + scale_fill_manual(values = col_acute) + scale_colour_manual(values = col_acute) + ylim (-0.5, 2.5) +  theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 24),
-                                       axis.text.y = element_text(angle = 45, size = 24),
-                                       legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top") 
-                               #annotate("text", label= paste0("k = ", k_lnrr_acute$k, " (", k_lnrr_acute$sdy, ")"), x = c(1.2, 2.2), y = 2)
-```
-
-#### Acute and acclimation $lnRR_{Q_{10}}$ for different trait categories across marine, freshwater and terrestrial taxa
-
-```{r, fig-S2}
-#| label: fig-S2
-#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-The x-axis is truncated for ease of visualisation.
-See methods section “Moderator Variables” for a full description of the trait categories.
-"
-#| echo: false
-k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
-k_fresh=manual_extract(model1.3_f_het, mod = "trait_category", group = "record_num")
-k_terrs=manual_extract(model1.3_t_het, mod = "trait_category", group = "record_num")
-
-ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
-                            annotate("text", label= paste0("k = ", k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4) + add_theme()
-#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme() + 
-                              annotate("text", label= paste0("k = ", k_fresh$k, " (", k_fresh$sdy, ")"), x = k_fresh$moderator, y = 2.4) + add_theme()
-#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
-  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")+ annotate("text", label= paste0("k = ", k_terrs$k, " (", k_terrs$sdy, ")"), x = k_terrs$moderator, y = 2.4) + add_theme() + ylim(-1,3)
-#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 14, width = 10)
-
-img_fig2 <- magick::image_read("./output/figures/fig2_trait.png")
-img_fig2
-```
-
-```{r, fig-cvrtrait}
-#| label: fig-cvrtrait
-#| fig-cap: "Acute and acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-The x-axis is truncated for ease of visualisation.
-See methods section “Moderator Variables” for a full description of the trait categories.
-"
-#| echo: false
-
-k_marinecv=manual_extract(model2.3m, mod = "trait_category", group = "record_num", exclude = "Antiox")
-k_freshcv=manual_extract(model2.3f, mod = "trait_category", group = "record_num")
-k_terrscv=manual_extract(model2.3t, mod = "trait_category", group = "record_num")
-
-ptm <- orchard_plot(model2.3m, mod = "trait_category", group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, k.pos = "none", condition.lab = "Type") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + add_theme() + annotate("text", label= paste0("k = ", k_marinecv$k, " (", k_marinecv$sdy, ")"), x = k_marinecv$moderator, y = 2.4) + ylim(-2, 2.6)
-#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptf <- orchard_plot(model2.3f, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type",  k.pos = "none") +
-  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
-                              "Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate",
-                              "Mito_oxidation" = "OXPHOS")) + theme_classic()+ add_theme() + annotate("text", label= paste0("k = ", k_freshcv$k, " (", k_freshcv$sdy, ")"), x = k_freshcv$moderator, y = 2.4) + ylim(-2.5, 2.65)
-#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-ptt <- orchard_plot(model2.3t, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0,  k.pos = "none", condition.lab = "Type") +
-  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
-                              "Rest_MR" = "Resting Metabolic Rate",
-                              "Max_MR" = "Maximum Metabolic Rate")) + theme_classic() +  annotate("text", label= paste0("k = ", k_terrscv$k, " (", k_terrscv$sdy, ")"), x = k_terrscv$moderator, y = 2.4) + labs(legend = "Type")+ add_theme() + ylim(-2, 2.65)
-#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
-
-figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 14, width = 10)
-
-img_figcvrtrait <- magick::image_read("./output/figures/figcvrtrait.png")
-img_figcvrtrait
-```
-
-#### Mean-variance relationships justify use of $lnCVR_{Q_{10}}$
-We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
-We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean in physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
-We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
-
-```{r, fig-mv}
-  #| label: fig-mv
-  #| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
-Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
-    col <- c("#0871B9", "#F3B40D", "#1BB908")
-
-  # Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
-      model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
-      saveRDS(model_mv1, file = "./output/models/model_mv1")
-
-      model_mv2  <- brm(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
-      saveRDS(model_mv2, file = "./output/models/model_mv2")
-
-  mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd),color = habitat)) +
-                  geom_point(aes(color = habitat), size = 2.2) + 
-                  geom_smooth(method = "lm", se = FALSE) + 
-                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
-                  scale_colour_manual(values = col) + 
-                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
-                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
-
-  mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd), color = habitat)) +
-                  geom_point(aes(color = habitat), size = 2.2) + 
-                  geom_smooth(method = "lm", se = FALSE) + 
-                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
-                  scale_colour_manual(values = col)  +
-                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
-                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
-
-  (mv1 / mv2)  + plot_annotation(tag_levels = "A", tag_suffix = ")") + theme(plot.tag = element_text(size = 20, face = "bold"))
-
-```
-
-Overall, we found that the relationship between the mean and SD of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
-Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the relative variance in physiological rates does not increase proportionally as the mean increases.
-Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`).
-
-#### Comparing raw variance changes using $lnVR_{Q_{10}}$
-```{r, lnvrq10}
-#| label: lnvrq10
-#| echo: false
-#| warning: false
-#| error: false
-#| include: false
-#| cache: true
-
-#############
-  ## lnVRQ10
-#############
-##################################################
-  # Organise the data and prune tree
-#################################################
-  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
-                                    max_temp_c = scale(temp_2, scale = FALSE))
-
-# Check and prune tree
-  tree_lnVR <- tree_checks(data = lnVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnVRQ10_data, tree = tree_lnVR, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-  phylo_cor_VR <- vcv(tree_lnVR, cor = TRUE)
-          A_VR <- vcv(tree_lnVR, cor = FALSE) # For bayes, need cov matrix
-
-###################################################
-  # Model 3.1: Intercept only model.
-  # Used for heterogeneity analysis
-###################################################
-rerun = FALSE
-if(rerun){
-  model3.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
-                              test = "t", data = lnVRQ10_data)
-
-  model3.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
-
-  # Save model1.1
-  saveRDS(model3.1, file = "./output/models/lnVRQ10_3.1")
-  saveRDS(model3.1_bayes, file = "./output/models/lnVRQ10_3.1_bayes")
-} else{ 
-        model3.1 <- readRDS("./output/models/lnVRQ10_3.1")
-  model3.1_bayes <- readRDS("./output/models/lnVRQ10_3.1_bayes")
-}
-
-# Heterogeneity analysis
-   w_VR <- with(lnVRQ10_data, 1/V) # weights
-  sv_VR <- sum(w_VR*(dim(lnVRQ10_data)[1]-1)) / (sum(w_VR)^2 + sum(w_VR^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_3.1 <- posterior_samples(model3.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_3.1) <- gsub("__Intercept", "", colnames(posteriors_3.1))
-  colnames(posteriors_3.1) <- gsub("sd_", "", colnames(posteriors_3.1))
-
-    res_VR <- posteriors_3.1[,"sigma"]
-   stdy_VR <- posteriors_3.1[,"record_num"]
-  phylo_VR <- posteriors_3.1[,"species_full"]
-    spp_VR <- posteriors_3.1[,"spp"]
-  trait_VR <- posteriors_3.1[,"trait"]
-  total_VR <- phylo_VR + spp_VR + res_VR + sv_VR + stdy_VR + trait_VR
-
-  # Calculate I2
-     tot_i2_VR <- (sv_VR / total_VR)*100    ; mean(tot_i2_VR)  ; quantile(tot_i2_VR, c(0.025, 0.975))
-   phylo_i2_VR <- (phylo_VR / total_VR)*100 ; mean(phylo_i2_VR); quantile(phylo_i2_VR, c(0.025, 0.975))
-     spp_i2_VR <- (spp_VR / total_VR)*100   ; mean(spp_i2_VR)  ; quantile(spp_i2_VR, c(0.025, 0.975))
-    stdy_i2_VR <- (stdy_VR / total_VR)*100  ; mean(stdy_i2_VR) ; quantile(stdy_i2_VR, c(0.025, 0.975))
-   trait_i2_VR <- (trait_VR / total_VR)*100 ; mean(trait_i2_VR); quantile(trait_i2_VR, c(0.025, 0.975))
-     res_i2_VR <- (res_VR / total_VR)*100   ; mean(res_i2_VR)  ; quantile(res_i2_VR, c(0.025, 0.975))
-
-  # Table
-     i2_lnVR <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2_VR),mean(spp_i2_VR), mean(stdy_i2_VR), mean(trait_i2_VR)),
-                           lci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[1], quantile(spp_i2_VR, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2_VR, c(0.025, 0.975))[1], quantile(trait_i2_VR, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[2], quantile(spp_i2_VR, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2_VR, c(0.025, 0.975))[2], quantile(trait_i2_VR, c(0.025, 0.975))[2]))
-
-###################################################
-  # Model 3.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model3.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
-                              test = "t", data = lnVRQ10_data)
-
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
-  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")
-
-  } else{
-        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
-  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
-}
-
-######################################################
-  # Bayesian Contrasts
-######################################################
-
-  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
-  f_acute_VR  <- posteriors_3.2[,"b_Intercept"]; pmcmc(f_acute_VR)
-  f_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
-  m_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
-  m_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
-  t_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
-  t_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
-
-# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
-It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
-  # First get sample sizes
-    N <- lnVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
-
-  # Calculated weighted mean by sample size. 
-    f_VR_mean <- (f_acute_VR * N[1,"n"][[1]] + f_acclim_VR * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_VR_mean)
-    m_VR_mean <- (m_acute_VR * N[3,"n"][[1]] + m_acclim_VR * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_VR_mean)
-    t_VR_mean <- (t_acute_VR * N[5,"n"][[1]] + t_acclim_VR * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_VR_mean)
-
-  # Lets now convert these to a %
-    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) 
-    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) 
-    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100)
-
-```
-
-Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-s1). @tbl-s1
-
-```{r, fig-s1}
-#| label: fig-s1
-#| fig-align: center
-#| fig-cap: "Estimated mean $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial systems.
-Note there were no differences between acute and acclimation $Q_{10}$ types so they were averaged.
-Thick black bars are 95% confidence intervals (CI's) and thin bars 95% prediction intervals (PI's).
-The percentage change in variance is also back calculated.
-Note that these are raw variances and do not account for changes in mean physiological rates.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species."
-
-##################
-  # Figure S1
-################## 
-  # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
-  col <- c("#0871B9", "#F3B40D", "#1BB908")
-  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 5) +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
-           label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -5, 
-           label =paste0(round(mean(exp(f_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
-  annotate("text", x = 2.3, y = -5.2, 
-           label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -5, 
-           label =paste0(round(mean(exp(m_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
-           label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 3.15, y = -5, 
-           label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = 3.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(t_VR_mean), digit = 3)))), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
-
-  p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
-          axis.text = element_text(size = 15), legend.text = element_text(size = 15),
-          legend.title = element_text(size = 15))
-
-  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
-
-  figs1 <- image_read("./output/figures/figS1.pdf")
-  figs1
-```
-
-```{r, tbl-s1}
-#| label: tbl-s1
-#| echo: false
-#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
-Model estimates are based off 1,253 effect sizes from 139 studies.
-
- # Extract the fixed / population-level effect summaries of the posterior
-    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
-    fixed <- cbind(Parameter = c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
-    rownames(fixed) <- NULL
-
- # Extract the random effect summaries of the posteriors (SDs)
-    random <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x)))
-    random <- cbind(Parameter = c( "Study", "Phylogeny", "Species", "Trait"), random)
-    rownames(random) <- NULL
-
-# Create the table
-    tabs1 <- rbind(fixed, random)
-
-    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
-```
-
-#### Plots of $I^2$ for multi-level models
-```{r, fig-s3}
-#| label: fig-s3
-#| fig-cap: "$I^2$ estimates. A) $lnRR_{Q_{10}}$ B) $lnCVR_{Q_{10}}$ and C) $lnVR_{Q_{10}}$." 
-#| fig-align: center
-
-ps3_1 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2), 2), "%")), size = 10)
-
-ps3_2 <- ggplot(i2_lncvr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_blank(), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 10)
-
-ps3_3 <- ggplot(i2_lnVR, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_blank(), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 10)
-
-figs3 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figs3.png")
-
-figs3 <- image_read("./output/figures/figs3.png")
-figs3
-```
-
-#### Publication Bias Analysis
-
-Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
-
-```{r, pubias}
-#| label: pubias
-#| echo: false
-#| include: false
-rerun = FALSE
-if(rerun){
-  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
-
-  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
-
-  saveRDS(model_full_lnrr_pb, file = "./output/models/lnRRQ10_pubbias")
-  saveRDS(model_full_lncvr_pb, file = "./output/models/lnCVRQ10_pubbias")
-  saveRDS(model_full_lnvr_pb, file = "./output/models/lnVRQ10_pubbias")
-} else {
-   model_full_lnrr_pb <- readRDS(file = "./output/models/lnRRQ10_pubbias")
-  model_full_lncvr_pb <- readRDS(file = "./output/models/lnCVRQ10_pubbias")
-  model_full_lnvr_pb <- readRDS(file = "./output/models/lnVRQ10_pubbias")
-}
-
-```
-
-```{r, fig-s2}
-#| label: fig-s2
-#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
-Both acute ('green') and acclimation ('orange') effect sizes are plotted.
-cols <- c("#303234", "#D3D3D3")
-ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)
-
-ps2_2 <- ggplot(lnCVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnCVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none", axis.title.y = element_blank())+ scale_color_manual(name = "Type", values = cols)
-
-ps2_3 <- ggplot(lnVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15),  axis.title.y = element_blank())+ scale_color_manual(name = "Type", values = cols)
-
-figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS2.png")
-
-figs2 <- image_read("./output/figures/figS2.png")
-figs2
-```
-
-#### Exploring the impact of temperature on $lnRR_{Q_{10}}$
+#### *Exploring the impact of maximum treatment temperature on $lnRR_{Q_{10}}$*
 
@@
 
-#### How acclimation time is related to $lnRR_{Q_{10}}$ 
+#### *How acclimation time is related to $lnRR_{Q_{10}}$* 
 ```{r, fig-accl_time}
@@
 ```
+#### *Comparing cool and warm acclimated acute responses*
+
+```{r, @fig-Sacute}
+#| label: fig-Sacute
+#| fig.width: 12.7
+#| fig.height: 8.7
+#| fig-cap: "Mean acute $lnRR_{Q_{10}}$ for cool (blue) and warm (red) acclimated populations for terrestrial (diamonds), marine (square) and freshwater (circle) habitats.
+Note that points  in each category show the full distribution of data irrespective of habitat for simplicity.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Note that means for all three habitats are displayed but there is weak evidence that the means differ between habitats given models with and without an interaction with habitat are equally supported.
+Note that x-axis is truncated for ease of visualisation.
+Sample sizes for each habitat for acute warm and cold are: marine [warm = (131, 38, 29), cold = (136, 41, 32)], freshwater [warm = (294, 76, 61), cold = (293, 77, 63)], terrestrial [warm = (83, 31, 35), cold = (84, 31, 35)].
+Numbers within brackets are number of effects, number of studies and number of species."
+#| echo: false
+
+col_acute <- c("#3F5FAC", "#EF3D25")
+orchard_plot(model1.s1_int, mod = "name", by = "habitat", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, condition.lab = "Habitat") + scale_x_discrete(labels = c("LnRR_Q10_acute_t2" = "Warm - Acute", "LnRR_Q10_acute_t1" = "Cool - Acute")) + scale_fill_manual(values = col_acute) + scale_colour_manual(values = col_acute) + ylim (-0.5, 2.5) +  theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top") 
+                               #annotate("text", label= paste0("k = ", k_lnrr_acute$k, " (", k_lnrr_acute$sdy, ")"), x = c(1.2, 2.2), y = 2)
+```
+
+#### *Acute and acclimation $lnRR_{Q_{10}}$ for different trait categories across marine, freshwater and terrestrial taxa*
+
+```{r, fig-S2}
+#| label: fig-S2
+#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+The x-axis is truncated for ease of visualisation.
+See methods section “Moderator Variables” for a full description of the trait categories.
+"
+#| echo: false
+k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
+k_fresh=manual_extract(model1.3_f_het, mod = "trait_category", group = "record_num")
+k_terrs=manual_extract(model1.3_t_het, mod = "trait_category", group = "record_num")
+
+ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(axis.text = element_text(size=12)) + ylim(-1.5, 2.5) +
+                            annotate("text", label= paste0("k = ", k_marine$k, " (", k_marine$sdy, ")"), x = k_marine$moderator, y = 2.4) + add_theme()
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme() + 
+                              annotate("text", label= paste0("k = ", k_fresh$k, " (", k_fresh$sdy, ")"), x = k_fresh$moderator, y = 2.4) + add_theme()
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model1.3_t_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop", k.pos = "none",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate")) + theme_classic() + labs(legend = "Type")+ annotate("text", label= paste0("k = ", k_terrs$k, " (", k_terrs$sdy, ")"), x = k_terrs$moderator, y = 2.4) + add_theme() + ylim(-1,3)
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 14, width = 10)
+
+img_fig2 <- magick::image_read("./output/figures/fig2_trait.png")
+img_fig2
+```
+
+```{r, fig-cvrtrait}
+#| label: fig-cvrtrait
+#| fig-cap: "Acute and acclimation $lnCVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+The x-axis is truncated for ease of visualisation.
+See methods section “Moderator Variables” for a full description of the trait categories.
+"
+#| echo: false
+
+k_marinecv=manual_extract(model2.3m, mod = "trait_category", group = "record_num", exclude = "Antiox")
+k_freshcv=manual_extract(model2.3f, mod = "trait_category", group = "record_num")
+k_terrscv=manual_extract(model2.3t, mod = "trait_category", group = "record_num")
+
+ptm <- orchard_plot(model2.3m, mod = "trait_category", group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, k.pos = "none", condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + add_theme() + annotate("text", label= paste0("k = ", k_marinecv$k, " (", k_marinecv$sdy, ")"), x = k_marinecv$moderator, y = 2.4) + ylim(-2, 2.6)
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf <- orchard_plot(model2.3f, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0, condition.lab = "Type",  k.pos = "none") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic()+ add_theme() + annotate("text", label= paste0("k = ", k_freshcv$k, " (", k_freshcv$sdy, ")"), x = k_freshcv$moderator, y = 2.4) + ylim(-2.5, 2.65)
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt <- orchard_plot(model2.3t, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnCVR_{Q_{10}}$"), angle = 0,  k.pos = "none", condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate")) + theme_classic() +  annotate("text", label= paste0("k = ", k_terrscv$k, " (", k_terrscv$sdy, ")"), x = k_terrscv$moderator, y = 2.4) + labs(legend = "Type")+ add_theme() + ylim(-2, 2.65)
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 14, width = 10)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figcvrtrait.png")
+img_figcvrtrait
+```
+
+#### *Mean-variance relationships justify use of $lnCVR_{Q_{10}}$*
+We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
+We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean in physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
+We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
+
+```{r, fig-mv}
+  #| label: fig-mv
+  #| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
+Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
+    col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+  # Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
+      model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+      saveRDS(model_mv1, file = "./output/models/model_mv1")
+
+      model_mv2  <- brm(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+      saveRDS(model_mv2, file = "./output/models/model_mv2")
+
+  mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd),color = habitat)) +
+                  geom_point(aes(color = habitat), size = 2.2) + 
+                  geom_smooth(method = "lm", se = FALSE) + 
+                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                  scale_colour_manual(values = col) + 
+                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
+                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
+
+  mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd), color = habitat)) +
+                  geom_point(aes(color = habitat), size = 2.2) + 
+                  geom_smooth(method = "lm", se = FALSE) + 
+                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                  scale_colour_manual(values = col)  +
+                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
+                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
+
+  (mv1 / mv2)  + plot_annotation(tag_levels = "A", tag_suffix = ")") + theme(plot.tag = element_text(size = 20, face = "bold"))
+
+```
+
+Overall, we found that the relationship between the mean and SD of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the relative variance in physiological rates does not increase proportionally as the mean increases.
+Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`).
+
+#### *Comparing raw variance changes using $lnVR_{Q_{10}}$*
+```{r, lnvrq10}
+#| label: lnvrq10
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+#| cache: true
+
+#############
+  ## lnVRQ10
+#############
+##################################################
+  # Organise the data and prune tree
+#################################################
+  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+  tree_lnVR <- tree_checks(data = lnVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnVRQ10_data, tree = tree_lnVR, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_VR <- vcv(tree_lnVR, cor = TRUE)
+          A_VR <- vcv(tree_lnVR, cor = FALSE) # For bayes, need cov matrix
+
+###################################################
+  # Model 3.1: Intercept only model.
+  # Used for heterogeneity analysis
+###################################################
+rerun = FALSE
+if(rerun){
+  model3.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+  model3.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+
+  # Save model1.1
+  saveRDS(model3.1, file = "./output/models/lnVRQ10_3.1")
+  saveRDS(model3.1_bayes, file = "./output/models/lnVRQ10_3.1_bayes")
+} else{ 
+        model3.1 <- readRDS("./output/models/lnVRQ10_3.1")
+  model3.1_bayes <- readRDS("./output/models/lnVRQ10_3.1_bayes")
+}
+
+# Heterogeneity analysis
+   w_VR <- with(lnVRQ10_data, 1/V) # weights
+  sv_VR <- sum(w_VR*(dim(lnVRQ10_data)[1]-1)) / (sum(w_VR)^2 + sum(w_VR^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_3.1 <- posterior_samples(model3.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_3.1) <- gsub("__Intercept", "", colnames(posteriors_3.1))
+  colnames(posteriors_3.1) <- gsub("sd_", "", colnames(posteriors_3.1))
+
+    res_VR <- posteriors_3.1[,"sigma"]
+   stdy_VR <- posteriors_3.1[,"record_num"]
+  phylo_VR <- posteriors_3.1[,"species_full"]
+    spp_VR <- posteriors_3.1[,"spp"]
+  trait_VR <- posteriors_3.1[,"trait"]
+  total_VR <- phylo_VR + spp_VR + res_VR + sv_VR + stdy_VR + trait_VR
+
+  # Calculate I2
+     tot_i2_VR <- (sv_VR / total_VR)*100    ; mean(tot_i2_VR)  ; quantile(tot_i2_VR, c(0.025, 0.975))
+   phylo_i2_VR <- (phylo_VR / total_VR)*100 ; mean(phylo_i2_VR); quantile(phylo_i2_VR, c(0.025, 0.975))
+     spp_i2_VR <- (spp_VR / total_VR)*100   ; mean(spp_i2_VR)  ; quantile(spp_i2_VR, c(0.025, 0.975))
+    stdy_i2_VR <- (stdy_VR / total_VR)*100  ; mean(stdy_i2_VR) ; quantile(stdy_i2_VR, c(0.025, 0.975))
+   trait_i2_VR <- (trait_VR / total_VR)*100 ; mean(trait_i2_VR); quantile(trait_i2_VR, c(0.025, 0.975))
+     res_i2_VR <- (res_VR / total_VR)*100   ; mean(res_i2_VR)  ; quantile(res_i2_VR, c(0.025, 0.975))
+
+  # Table
+     i2_lnVR <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_VR),mean(spp_i2_VR), mean(stdy_i2_VR), mean(trait_i2_VR)),
+                           lci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[1], quantile(spp_i2_VR, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_VR, c(0.025, 0.975))[1], quantile(trait_i2_VR, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[2], quantile(spp_i2_VR, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_VR, c(0.025, 0.975))[2], quantile(trait_i2_VR, c(0.025, 0.975))[2]))
+
+###################################################
+  # Model 3.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model3.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
+  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")
+
+  } else{
+        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
+  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
+}
+
+######################################################
+  # Bayesian Contrasts
+######################################################
+
+  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
+  f_acute_VR  <- posteriors_3.2[,"b_Intercept"]; pmcmc(f_acute_VR)
+  f_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
+  m_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
+  m_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
+  t_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
+
+# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
+It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
+  # First get sample sizes
+    N <- lnVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_VR_mean <- (f_acute_VR * N[1,"n"][[1]] + f_acclim_VR * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_VR_mean)
+    m_VR_mean <- (m_acute_VR * N[3,"n"][[1]] + m_acclim_VR * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_VR_mean)
+    t_VR_mean <- (t_acute_VR * N[5,"n"][[1]] + t_acclim_VR * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_VR_mean)
+
+  # Lets now convert these to a %
+    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) 
+    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) 
+    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100)
+
+```
+
+Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-s1). @tbl-s1
+
+```{r, fig-s1}
+#| label: fig-s1
+#| fig-align: center
+#| fig-cap: "Estimated mean $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial systems.
+Note there were no differences between acute and acclimation $Q_{10}$ types so they were averaged.
+Thick black bars are 95% confidence intervals (CI's) and thin bars 95% prediction intervals (PI's).
+The percentage change in variance is also back calculated.
+Note that these are raw variances and do not account for changes in mean physiological rates.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species."
+
+##################
+  # Figure S1
+################## 
+  # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
+  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 5) +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
+           label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 1.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
+  annotate("text", x = 1.15, y = -5, 
+           label =paste0(round(mean(exp(f_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
+  annotate("text", x = 2.3, y = -5.2, 
+           label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 2.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
+  annotate("text", x = 2.15, y = -5, 
+           label =paste0(round(mean(exp(m_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
+           label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
+  annotate("text", x = 3.15, y = -5, 
+           label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
+    annotate("text", x = 3.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(t_VR_mean), digit = 3)))), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
+
+  p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
+          axis.text = element_text(size = 15), legend.text = element_text(size = 15),
+          legend.title = element_text(size = 15))
+
+  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
+
+  figs1 <- image_read("./output/figures/figS1.pdf")
+  figs1
+```
+
+```{r, tbl-s1}
+#| label: tbl-s1
+#| echo: false
+#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
+Model estimates are based off 1,253 effect sizes from 139 studies.
+
+ # Extract the fixed / population-level effect summaries of the posterior
+    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
+    fixed <- cbind(Parameter = c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
+    rownames(fixed) <- NULL
+
+ # Extract the random effect summaries of the posteriors (SDs)
+    random <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x)))
+    random <- cbind(Parameter = c( "Study", "Phylogeny", "Species", "Trait"), random)
+    rownames(random) <- NULL
+
+# Create the table
+    tabs1 <- rbind(fixed, random)
+
+    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
+```
+
+#### *Plots of $I^2$ for multi-level models*
+```{r, fig-s3}
+#| label: fig-s3
+#| fig-cap: "$I^2$ estimates. A) $lnRR_{Q_{10}}$ B) $lnCVR_{Q_{10}}$ and C) $lnVR_{Q_{10}}$." 
+#| fig-align: center
+
+ps3_1 <- ggplot(i2_lnrr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_text(size = 20), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2), 2), "%")), size = 10)
+
+ps3_2 <- ggplot(i2_lncvr, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_blank(), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 10)
+
+ps3_3 <- ggplot(i2_lnVR, aes(x = est, y = name)) + xlim(0, 50) + geom_point(size = 5) + geom_errorbar(aes(xmin = lci, xmax = uci), width = 0.15) + theme_bw() + labs(x = "Percentage of Variation (%)") + theme(axis.title.y = element_blank(), axis.text = element_blank(), axis.title = element_text(size = 24)) + geom_text(aes(label = paste0(round(est, 2), "% ", "[", round(lci, 2), " - ", round(uci, 2), "%]")), position = position_nudge(x = 5, y = 0.2)) + annotate("text", x = 30, y = 1.5, label = TeX(paste0("$I^2_{sv}$ = ", round(mean(tot_i2_cvr), 2), "%")), size = 10)
+
+figs3 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figs3.png")
+
+figs3 <- image_read("./output/figures/figs3.png")
+figs3
+```
+
+#### *Publication bias analysis*
+
+Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
+
+```{r, pubias}
+#| label: pubias
+#| echo: false
+#| include: false
+rerun = FALSE
+if(rerun){
+  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+
+  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+
+  saveRDS(model_full_lnrr_pb, file = "./output/models/lnRRQ10_pubbias")
+  saveRDS(model_full_lncvr_pb, file = "./output/models/lnCVRQ10_pubbias")
+  saveRDS(model_full_lnvr_pb, file = "./output/models/lnVRQ10_pubbias")
+} else {
+   model_full_lnrr_pb <- readRDS(file = "./output/models/lnRRQ10_pubbias")
+  model_full_lncvr_pb <- readRDS(file = "./output/models/lnCVRQ10_pubbias")
+  model_full_lnvr_pb <- readRDS(file = "./output/models/lnVRQ10_pubbias")
+}
+
+```
+
+```{r, fig-s2}
+#| label: fig-s2
+#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
+Both acute ('green') and acclimation ('orange') effect sizes are plotted.
+cols <- c("#303234", "#D3D3D3")
+ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)
+
+ps2_2 <- ggplot(lnCVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnCVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none", axis.title.y = element_blank())+ scale_color_manual(name = "Type", values = cols)
+
+ps2_3 <- ggplot(lnVRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnVR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15),  axis.title.y = element_blank())+ scale_color_manual(name = "Type", values = cols)
+
+figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS2.png")
+
+figs2 <- image_read("./output/figures/figS2.png")
+figs2
+```

### 2024-06-21 R/functions.R
fixed function so fig has latex

@@ -439,14 +439,14 @@ manual_extract  <- function(model, mod = "trait_category", group = "record_num",
 #' 
  text <- function(post, b = TRUE){
       if(b){
-        paste0("B = ", round(mean(post), 2))
+        paste0("$\\beta$ = ", round(mean(post), 2))
       } else {
         paste0("95% CI: ", round(quantile(post, c(0.025, 0.975)[1]), 2), " to ", round(quantile(post, c(0.025, 0.975)[2]), 2))
       }
   }
 
 p_text <- function(post){
-   paste0("p = ", round(pmcmc(post), 2))
+   paste0("$p_{MCMC}$ = ", round(pmcmc(post), 2))
 }
 
 

### 2024-06-21 ms.qmd
Cleaning code and moving acf to supplement

@@
 
-  fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+  fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A")
   fig3
@@
 
-fig4 <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A", tag_suffix = ")") 
+fig4 <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
 ggsave(fig4, filename = "./output/figures/fig4_lh_r1.pdf", width = 22, height = 12, device = "pdf")
 
-fig4 <- magick::image_read("./output/figures/fig4_lh.pdf")
+fig4 <- magick::image_read("./output/figures/fig4_lh_r1.pdf")
 fig4
@@
      sd_mod <- bf(log(sd) ~ habitat  + (1|record_num) + (1|spp))
-    acf_all_mod <- bf(acf_all ~ habitat  + (1|record_num) + (1|spp))
-
-  model_envi <- brms::brm(sd_mod + acf_all_mod + set_rescor(TRUE), family = gaussian(),  control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
+
+  model_envi <- brms::brm(sd_mod, family = gaussian(),  control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
   saveRDS(model_envi, file = "./output/models/model_envi")
@@
 }
-
-###################################################
-  # Model 3.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model3.2          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + type + habitat + type:habitat, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.2
-  saveRDS(model3.2, file = "./output/models/lnRRQ10_3.2")
-  saveRDS(model3.2_bayes, file = "./output/models/lnRRQ10_3.2_bayes")
-
-  } else{
-        model3.2 <- readRDS("./output/models/lnRRQ10_3.2")
-  model3.2_bayes <- readRDS("./output/models/lnRRQ10_3.2_bayes")
-}
-
-####################################################
-  ## Model 3.2: Bayesian Contrasts
-###################################################
-  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
-  f_acute_wild  <- posteriors_3.2[,"b_Intercept"]
-  f_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
-  m_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
-  m_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
-  t_acute_wild  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
-  t_acclim_wild <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
-
-# Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10_wild <- exp(f_acute_wild) ; mean(f_acute_Q10_wild)
-  f_acclim_Q10_wild <- exp(f_acclim_wild); mean(f_acclim_Q10_wild)
-   m_acute_Q10_wild <- exp(m_acute_wild) ; mean(f_acute_Q10_wild)
-  m_acclim_Q10_wild <- exp(m_acclim_wild); mean(f_acclim_Q10_wild)
-   t_acute_Q10_wild <- exp(t_acute_wild) ; mean(t_acute_Q10_wild)
-  t_acclim_Q10_wild <- exp(t_acclim_wild); mean(t_acclim_Q10_wild)
-
-# % change in acclimation on log scale; relative to the acute measurements
-  change_f_wild <- ((f_acclim_wild - f_acute_wild) / f_acute_wild) *100; quantile(change_f_wild, c(0.025, 0.975))
-  change_m_wild <- ((m_acclim_wild - m_acute_wild) / m_acute_wild) *100; quantile(change_m_wild, c(0.025, 0.975))
-  change_t_wild <- ((t_acclim_wild - t_acute_wild) / t_acute_wild) *100; quantile(change_t_wild, c(0.025, 0.975))
 
@@
 
-################################################################
-  # Model 3.4: Environmental autocorrelation model by acute/acclim
-################################################################
-if(rerun){
-  # More realistic model with 
-  model3.4          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model3.4, file = "./output/models/lnRRQ10_3.4")
-  saveRDS(model3.4_bayes, file = "./output/models/lnRRQ10_3.4_bayes")
-
-  } else{
-        model3.4 <- readRDS("./output/models/lnRRQ10_3.4")
-  model3.4_bayes <- readRDS("./output/models/lnRRQ10_3.4_bayes")
-}
-
-################################################################
-  # Model 3.5: Environmental variability  model
-################################################################
-if(rerun){
-  # More realistic model with 
-  model3.5          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait) + (1|obs), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.5
-  saveRDS(model3.5, file = "./output/models/lnRRQ10_3.5")
-  saveRDS(model3.5_bayes, file = "./output/models/lnRRQ10_3.5_bayes")
-
-  } else{
-        model3.5 <- readRDS("./output/models/lnRRQ10_3.5")
-  model3.5_bayes <- readRDS("./output/models/lnRRQ10_3.5_bayes")
-}
-
-################################################################
-  # Model 3.6: Environmental autocorrelation model
-################################################################
-if(rerun){
-  # More realistic model with 
-  model3.6          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c+ c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_wild)
-
-  # Save model3.6
-  saveRDS(model3.6, file = "./output/models/lnRRQ10_3.6")
-  saveRDS(model3.6_bayes, file = "./output/models/lnRRQ10_3.6_bayes")
-
-  } else{
-        model3.6 <- readRDS("./output/models/lnRRQ10_3.6")
-  model3.6_bayes <- readRDS("./output/models/lnRRQ10_3.6_bayes")
-}
-
-################################################################
-  # Model 3.7: Environmental variability and autocorrelation model
-################################################################
-
-if(rerun){
-  # More realistic model with 
-  model3.7          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild)
-
-   model3.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
-
-  # Save model3.7
-  saveRDS(model3.7, file = "./output/models/lnRRQ10_3.7")
-  saveRDS(model3.7_bayes, file = "./output/models/lnRRQ10_3.7_bayes")
-
-  } else{
-        model3.7 <- readRDS("./output/models/lnRRQ10_3.7")
-  model3.7_bayes <- readRDS("./output/models/lnRRQ10_3.7_bayes")
-}
-
-############################################################################################
-# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
-# differently in each habitat
-############################################################################################  
-  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-if(rerun){
-  # More realistic model with 
-  model3.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim)
-
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
-  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
-
-  } else{
-        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
-  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 3.8
-#################################################
- posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
-
-    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
-    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
-    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
-
 ############################################################################################
@@
     # Terrestrial Models
-    model3.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-    saveRDS(model3.8_t, "./output/models/model3.8_t")
-
     model3.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
@@
 
-        # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-    model3.10_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_t)
-     saveRDS(model3.10_t, "./output/models/model3.10_t")
     # Freshwater Models
-    model3.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+
+    model3.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
                                        random = list(~1 | record_num,
@@
                               test = "t", data = lnRRQ10_data_wild_acclim_f)
-    saveRDS(model3.8_f, "./output/models/model3.8_f")
-
-    model3.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
 
@@
 
-       # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-
-     model3.10_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_f)
-      saveRDS(model3.10_f, "./output/models/model3.10_f")
     # Marine Models
-      model3.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-        saveRDS(model3.8_m, "./output/models/model3.8_m")
 
@@
     saveRDS(model3.9_m, "./output/models/model3.9_m")
-    # Model just quickly tests if we are missing an important interaction.
-It may not necessarily be just about the variability.
-We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things.
-We want predictability AND variance
-
-    model3.10_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acclim_m)
-    saveRDS(model3.10_m, "./output/models/model3.10_m")
+
   } else {
-     model3.8_t <- readRDS("./output/models/model3.8_t")
      model3.9_t <- readRDS("./output/models/model3.9_t")
-    model3.10_t <- readRDS("./output/models/model3.10_t")
-     model3.8_f <- readRDS("./output/models/model3.8_f")
      model3.9_f <- readRDS("./output/models/model3.9_f")
-    model3.10_f <- readRDS("./output/models/model3.10_f")
      model3.9_m <- readRDS("./output/models/model3.9_m")
-    model3.10_m <- readRDS("./output/models/model3.10_m")
-     model3.8_m <- readRDS("./output/models/model3.8_m")
 }
@@
 
-###################################################
-  # Model 4.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model4.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.2
-  saveRDS(model4.2, file = "./output/models/lnCVRQ10_4.2")
-  saveRDS(model4.2_bayes, file = "./output/models/lnCVRQ10_4.2_bayes")
-
-  } else{
-        model4.2 <- readRDS("./output/models/lnCVRQ10_4.2")
-  model4.2_bayes <- readRDS("./output/models/lnCVRQ10_4.2_bayes")
-}
-
-####################################################
-  ## Model 4.2: Bayesian Contrasts
-###################################################
-  posteriors_4.2 <- posterior_samples(model4.2_bayes, pars = "^b")
-  f_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"]
-  f_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_typeacclim"]
-  m_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"]
-  m_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatm"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatm"]
-  t_acute_wild_cvr  <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"]
-  t_acclim_wild_cvr <- posteriors_4.2[,"b_Intercept"] + posteriors_4.2[,"b_habitatt"] + posteriors_4.2[,"b_typeacclim"] + posteriors_4.2[,"b_typeacclim:habitatt"]
-
-# CVRQ10 values for each category.
-   f_acute_Q10_wild_cvr <- exp(f_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
-  f_acclim_Q10_wild_cvr <- exp(f_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
-   m_acute_Q10_wild_cvr <- exp(m_acute_wild_cvr) ; mean(f_acute_Q10_wild_cvr)
-  m_acclim_Q10_wild_cvr <- exp(m_acclim_wild_cvr); mean(f_acclim_Q10_wild_cvr)
-   t_acute_Q10_wild_cvr <- exp(t_acute_wild_cvr) ; mean(t_acute_Q10_wild_cvr)
-  t_acclim_Q10_wild_cvr <- exp(t_acclim_wild_cvr); mean(t_acclim_Q10_wild_cvr)
-
-# % change in acclimation on log scale
-  change_f_wild_cvr <- ((f_acclim_wild_cvr - f_acute_wild_cvr) / f_acute_wild_cvr)*100; quantile(change_f_wild_cvr, c(0.025, 0.975))
-  change_m_wild_cvr <- ((m_acclim_wild_cvr - m_acute_wild_cvr) /m_acute_wild_cvr)*100; quantile(change_m_wild_cvr, c(0.025, 0.975))
-  change_t_wild_cvr <- ((t_acclim_wild_cvr - t_acute_wild_cvr)/t_acute_wild_cvr)*100; quantile(change_t_wild_cvr, c(0.025, 0.975))
-
 ####################################################
@@
 
-################################################################
-  # Model 4.4: Environmental autocorrelation model by acute/acclim
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
-  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
-
-  } else{
-        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
-  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
-}
-
-################################################################
-  # Model 4.5: Environmental variability
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.5          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.5_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.5
-  saveRDS(model4.5, file = "./output/models/lnCVRQ10_4.5")
-  saveRDS(model4.5_bayes, file = "./output/models/lnCVRQ10_4.5_bayes")
-
-  } else{
-        model4.5 <- readRDS("./output/models/lnCVRQ10_4.5")
-  model4.5_bayes <- readRDS("./output/models/lnCVRQ10_4.5_bayes")
-}
-
-################################################################
-  # Model 4.6: Environmental autocorrelation model 
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.6          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.6_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.6
-  saveRDS(model4.6, file = "./output/models/lnCVRQ10_4.6")
-  saveRDS(model4.6_bayes, file = "./output/models/lnCVRQ10_4.6_bayes")
-
-  } else{
-        model4.6 <- readRDS("./output/models/lnCVRQ10_4.6")
-  model4.6_bayes <- readRDS("./output/models/lnCVRQ10_4.6_bayes")
-}
-
-################################################################
-  # Model 4.7: Environmental autocorrelation and variability
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.7          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + cv_c + type, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.7_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + cv_c + type + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.7
-  saveRDS(model4.7, file = "./output/models/lnCVRQ10_4.7")
-  saveRDS(model4.7_bayes, file = "./output/models/lnCVRQ10_4.7_bayes")
-
-  } else{
-        model4.7 <- readRDS("./output/models/lnCVRQ10_4.7")   ### DIFFERENT 
-  #model4.7_bayes <- readRDS("./output/models/lnCVRQ10_4.7_bayes")
-}
-
-############################################################################################
-  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
-  # differently in each habitat
-############################################################################################  
-  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-if(rerun){
-  # More realistic model with 
-  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model4.8
-  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
-  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
-
-  } else{
-        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
-  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.8
-#################################################
- posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
-
-    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
-    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
-    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
-
 ############################################################################################
@@
 
-```{r, fig-4}
-#| label: fig-4
+```{r, fig-5}
+#| label: fig-5
 #| fig-align: center
-#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
+#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10}_{acclim}}$ (A) and $lnCVR_{Q_{10}_{acclim}}$ (B) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ values for the slopes are shown for each habitat."
 
 size_axis = 18
-# CV
+col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+# lnRR CV
  dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
@@
 
- col <- c("#0871B9", "#F3B40D", "#1BB908")
 p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
@@
 scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
+geom_text(data = dat_text, aes(x = x, y = y, label = TeX(label)), size = 5) + 
 geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y-0.6, label = p), size = 5) +
+geom_text(data = dat_text, aes(x = x, y = y-0.6, label = TeX(p)), size = 5) +
 geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
@@
 
-  # ACF
-dat_text2 <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
-                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
-                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
-                      condition = c("f", "m", "t"),
-                      x = rep(-2.8, 3),
-                      y = rep(-1.2, 3))
-
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y, label =label), size = 5) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
-geom_text(data = dat_text2, aes(x = x+1, y = y-0.65, label = p), size = 5) +
-theme(legend.position = "bottom", 
-      strip.background = element_blank(), 
-      strip.text = element_blank(), 
-      axis.text = element_text(size = size_axis), 
-      axis.title = element_text(size = size_axis),
-      legend.text = element_text(size = 16),
-      legend.title = element_text(size = 16))
-
-p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-
-ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
-
-  p8.1.2 <- image_read("./output/figures/fig8.png")
-  p8.1.2 
-```
-
-```{r, fig-5}
-#| label: fig-5
-#| fig-align: center
-#| fig-cap: "Predicted mean (thick black line) $lnCVR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
-Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
-
-size_axis = 18
-# CV
+# lnCVR CV
+
 dat_text <- data.frame(label = c(text(slope_f_4.9), text(slope_m_4.9), text(slope_t_4.9)),
@@
 
- col <- c("#0871B9", "#F3B40D", "#1BB908")
 p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
@@
 
-  # ACF
-dat_text2 <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
-                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
-                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
-                      condition = c("f", "m", "t"),
-                      x = rep(-2.8, 3),
-                      y = rep(-4, 3))
-
-p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y, label = label), size = 5) + 
-geom_text(data = dat_text2, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
-geom_text(data = dat_text2, aes(x = x+1, y = y-1.2, label = p), size = 5) +
-theme(legend.position = "bottom", 
-      strip.background = element_blank(), 
-      strip.text = element_blank(), 
-      axis.text = element_text(size = size_axis), 
-      axis.title = element_text(size = size_axis),
-      legend.text = element_text(size = 16),
-      legend.title = element_text(size = 16))
-
-p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 20))
 
@@
 
+#### *Environmental predictability*
+
+Theoretical models highlight the importance of environmental predictability in selecting for plastic responses.
+However, capturing environmental predictability is challing given that it is unclear which timescale one should select.
+For example, is it more important to look at correlation between temperatures monthly or seasonally.
+In addition, such temporal resolution will likely depend on the species in question given that for some species fine-grained thermal predictability maybe more important compared to others.
+
+With these limitations in mind, we used our temperature time series to calculate autoregressive correlation in temperaure across the entire time series.
+We then modelled how this measure of thermal predictability was related to plasticity.
+
+```{r}
+
+############################################################################################
+# Model 3.8: Acclimatization lnRRQ10 only. Test if environmental predictability explains 
+# differently in each habitat
+############################################################################################  
+  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+if(rerun){
+  # More realistic model with 
+  model3.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim)
+
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model3.8, file = "./output/models/lnRRQ10_3.8")
+  saveRDS(model3.8_bayes, file = "./output/models/lnRRQ10_3.8_bayes")
+
+  } else{
+        model3.8 <- readRDS("./output/models/lnRRQ10_3.8")
+  model3.8_bayes <- readRDS("./output/models/lnRRQ10_3.8_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 3.8
+#################################################
+ posteriors3.8 <- posterior_samples(model3.8_bayes, "^b")
+
+    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
+    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
+    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
+
+################################################################
+  # Model 4.4: Environmental autocorrelation model by acute/acclim
+################################################################
+if(rerun){
+  # More realistic model with 
+  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model3.3
+  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
+  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
+
+  } else{
+        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
+  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
+}
+
+##################################################
+    # Model 3.8, 3.9 and 3.10 - Habitat subset
+##################################################
+    # Subset data to habitat
+    lnRRQ10_data_wild_acclim_t <- lnRRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnRRQ10_data_wild_acclim_f <- lnRRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnRRQ10_data_wild_acclim_m <- lnRRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+if(rerun){
+    # Terrestrial Models
+    model3.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t)
+    saveRDS(model3.8_t, "./output/models/model3.8_t")
+
+    # Freshwater Models
+    model3.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f)
+    saveRDS(model3.8_f, "./output/models/model3.8_f")
+
+    # Marine Models
+      model3.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m)
+        saveRDS(model3.8_m, "./output/models/model3.8_m")
+
+  } else {
+     model3.8_t <- readRDS("./output/models/model3.8_t")
+     model3.8_f <- readRDS("./output/models/model3.8_f")
+     model3.8_m <- readRDS("./output/models/model3.8_m")
+}
+
+############################################################################################
+  # Model 4.8: Acclimatization lnCVRQ10 only. Test if environmental predictability explains 
+  # differently in each habitat
+############################################################################################  
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+if(rerun){
+  # More realistic model with 
+  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model4.8
+  saveRDS(model4.8, file = "./output/models/lnRRQ10_4.8")
+  saveRDS(model4.8_bayes, file = "./output/models/lnRRQ10_4.8_bayes")
+
+  } else{
+        model4.8 <- readRDS("./output/models/lnRRQ10_4.8")
+  model4.8_bayes <- readRDS("./output/models/lnRRQ10_4.8_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.8
+#################################################
+ posteriors4.8 <- posterior_samples(model4.8_bayes, "^b")
+
+    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
+    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
+    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
+
+```
+
+```{r, fig-4}
+#| label: fig-4
+#| fig-align: center
+#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
+Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
+
+size_axis = 18
+# lnRR ACF
+
+ col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+ dat_text2rr <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
+                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
+                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
+                      condition = c("f", "m", "t"),
+                      x = rep(-2.8, 3),
+                      y = rep(-1.2, 3))
+
+p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text2rr, aes(x = x+1, y = y, label =label), size = 5) + 
+geom_text(data = dat_text2rr, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
+geom_text(data = dat_text2rr, aes(x = x+1, y = y-0.65, label = p), size = 5) +
+theme(legend.position = "bottom", 
+      strip.background = element_blank(), 
+      strip.text = element_blank(), 
+      axis.text = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      legend.text = element_text(size = 16),
+      legend.title = element_text(size = 16))
+
+# lnCVR ACF
+dat_text2cvr <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
+                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
+                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
+                      condition = c("f", "m", "t"),
+                      x = rep(-2.8, 3),
+                      y = rep(-4, 3))
+
+p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
+theme_classic() + 
+scale_fill_manual(values = c(col)) + 
+geom_text(data = dat_text2cvr, aes(x = x+1, y = y, label = label), size = 5) + 
+geom_text(data = dat_text2cvr, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
+geom_text(data = dat_text2cvr, aes(x = x+1, y = y-1.2, label = p), size = 5) +
+theme(legend.position = "bottom", 
+      strip.background = element_blank(), 
+      strip.text = element_blank(), 
+      axis.text = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      legend.text = element_text(size = 16),
+      legend.title = element_text(size = 16))
+
+p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 20))
+
+ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
+
+  p8.1.2 <- image_read("./output/figures/fig8.png")
+  p8.1.2 
+```
 #### *Publication bias analysis*

### 2024-06-21 ms.qmd
Fixed up code for CV figure. Added 3 habitat models of 4.9 Bayes for ease of plotting

@@
 ############################################################################################          
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
 
@@
   # More realistic model with 
-  model4.9  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+  model4.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
 
   # Save model3.8
-  saveRDS(model4.9, file = "./output/models/lnRRQ10_4.9")
-  saveRDS(model4.9_bayes, file = "./output/models/lnRRQ10_4.9_bayes")
+  saveRDS(model4.9, file = "./output/models/lnCVRQ10_4.9")
+  saveRDS(model4.9_bayes, file = "./output/models/lnCVRQ10_4.9_bayes")
 
   } else{
-        model4.9 <- readRDS("./output/models/lnRRQ10_4.9")
-  model4.9_bayes <- readRDS("./output/models/lnRRQ10_4.9_bayes")
+        model4.9 <- readRDS("./output/models/lnCVRQ10_4.9")
+  model4.9_bayes <- readRDS("./output/models/lnCVRQ10_4.9_bayes")
 }
@@
     slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
+
+##################################################
+    # Model 4.8, 4.9 and 4.10 - Habitat subset
+    # Used for making plots
+##################################################
+    # Subset data to habitat
+    lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+if(rerun){
+    # Terrestrial Models
+    model4.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
+    saveRDS(model4.9_t, "./output/models/model4.9_t")
+
+    # Freshwater Models
+
+    model4.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
+
+    saveRDS(model4.9_f, "./output/models/model4.9_f")
+
+    # Marine Models
+
+    model4.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
+    saveRDS(model4.9_m, "./output/models/model4.9_m")
+
+  } else {
+     model4.9_t <- readRDS("./output/models/model4.9_t")
+     model4.9_f <- readRDS("./output/models/model4.9_f")
+     model4.9_m <- readRDS("./output/models/model4.9_m")
+}
 
@@
 
-size_axis = 18
+size_axis = 20
 col <- c("#0871B9", "#F3B40D", "#1BB908")
 
+####################
 # lnRR CV
+####################
  dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
@@
                       condition = c("f", "m", "t"),
-                      x = rep(1.2, 3),
-                      y = rep(-1.2, 3))
-
-p8.1 <- bubble_plot(model3.9, mod = "cv_c", group = "record_num", by = "habitat", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text, aes(x = x, y = y, label = TeX(label)), size = 5) + 
-geom_text(data = dat_text, aes(x = x, y = y-0.3, label = label2), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y-0.6, label = TeX(p)), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y+4, label = title), size = 5) + 
-theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
-
+                      x = rep(0, 3),
+                      y = rep(-1.1, 3))
+y_adj = -3
+# Terrestrial
+  p_t_rr <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[3]) + 
+  scale_fill_manual(values = "black")+ labs(title = dat_text$title[3]) +
+  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
+  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
+  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)
+
+# Marine
+p_m_rr <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[2]) + 
+  scale_fill_manual(values = "black") + labs(title = dat_text$title[2]) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+
+# Freshwater
+p_f_rr <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[1]) + 
+  scale_fill_manual(values = "black") + labs(title = dat_text$title[1]) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+
+####################
 # lnCVR CV
-
-dat_text <- data.frame(label = c(text(slope_f_4.9), text(slope_m_4.9), text(slope_t_4.9)),
-                      label2 = c(text(slope_f_4.9, b = FALSE), text(slope_m_4.9,b = FALSE), text(slope_t_4.9,b = FALSE)),
-                      p = c(p_text(slope_f_4.9), p_text(slope_m_4.9), p_text(slope_t_4.9)),
+####################
+dat_textcvr <- data.frame(label = c(text(slope_f_4.9), 
+                                 text(slope_m_4.9), 
+                                 text(slope_t_4.9)),
+                      label2 = c(text(slope_f_4.9, b = FALSE), 
+                                 text(slope_m_4.9,b = FALSE), 
+                                 text(slope_t_4.9,b = FALSE)),
+                           p = c(p_text(slope_f_4.9), 
+                                 p_text(slope_m_4.9), 
+                                 p_text(slope_t_4.9)),
                        title = c("Freshwater", "Marine", "Terrestrial"), 
                       condition = c("f", "m", "t"),
-                      x = rep(1.2, 3),
+                      x = rep(0, 3),
                       y = rep(-4, 3))
 
-p9.1 <- bubble_plot(model4.9, mod = "cv_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text, aes(x = x, y = y, label = label), size = 5) + 
-geom_text(data = dat_text, aes(x = x, y = y-1, label = label2), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y-2, label = p), size = 5) +
-geom_text(data = dat_text, aes(x = x, y = y+10, label = title, size = 5)) + 
-theme(legend.position = "none", strip.background = element_blank(), strip.text = element_blank(),axis.text = element_text(size = size_axis), axis.title = element_text(size = size_axis))
-
-p9.1.2 <- (p9.1 / p9.2) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 20))
-
-ggsave(p9.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig9.png")
-
-  p9.1.2 <- image_read("./output/figures/fig9.png")
-  p9.1.2 
+# Freshwater
+  yadj2 = -6
+  x_f = 0.6
+  p_f_cv <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
+      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[1]) + 
+    scale_fill_manual(values = "black") + 
+    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
+  theme(axis.text = element_text(size = size_axis), 
+        axis.text.y = element_text(size = size_axis), 
+        axis.title = element_text(size = size_axis), 
+        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
+    ylim(-6, 3.5)
+
+# Marine
+  x_m = -0.4
+  p_m_cv <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
+    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
+                 aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
+                 colour = col[2]) + 
+    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
+    theme(axis.text = element_text(size = size_axis), 
+        axis.text.y = element_text(size = size_axis), 
+        axis.title = element_text(size = size_axis), 
+        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
+    ylim(-6, 3.5)
+
+# Terrestrial
+
+x_t = 0
+p_t_cv <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
+  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
+               aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
+               colour = col[3]) + 
+  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
+  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
+  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
+  theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
+  ylim(-6, 3.5)
+
+####################
+# Full plot
+####################
+
+p_cv <- (p_t_rr + p_m_rr + p_f_rr) / (p_t_cv + p_m_cv + p_f_cv) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
+
+ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig_p_cv_r1.pdf")
+
+  p_cv <- image_read("./output/figures/fig_p_cv_r1.png")
+  p_cv 
 ```
@@
 ############################################################################################
-  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
 

### 2024-06-21 ms.qmd
Figured out why border wasn't drawn. You need to have shape = 21 (a fillable shape). I didn't realise there were different types!

@@
   p_t_rr <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
-    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[3]) + 
-  scale_fill_manual(values = "black")+ labs(title = dat_text$title[3]) +
+    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
   annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
@@
 p_m_rr <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
-    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[2]) + 
-  scale_fill_manual(values = "black") + labs(title = dat_text$title[2]) +
+    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
   annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
@@
 p_f_rr <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
-    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[1]) + 
-  scale_fill_manual(values = "black") + labs(title = dat_text$title[1]) +
+    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
   annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
@@
   p_f_cv <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
-      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[1]) + 
-    scale_fill_manual(values = "black") + 
+      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
     annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
@@
                  aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
-                 colour = col[2]) + 
+                 fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
     annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
@@
                aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
-               colour = col[3]) + 
+               fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
   annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +

### 2024-06-21 ms.qmd
Fix fig caption. Fig 5 is basically done

@@
 #| fig-align: center
-#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10}_{acclim}}$ (A) and $lnCVR_{Q_{10}_{acclim}}$ (B) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
+#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A) and $lnCVR_{Q_{10_{acclim}}}$ (B) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.

### 2024-06-21 ms.qmd
Fixing fill for plots in supp. Adding in shape = 21 and changing to filll from colour

@@
 ggplot(data = lnRRQ10_data, aes(x = temp_2, y = effect_size)) + 
-geom_point(aes(size = 1/sqrt(V), colour = habitat), alpha = 0.8) +
+geom_point(aes(size = 1/sqrt(V), fill = habitat), alpha = 0.8, shape = 21, colour = "black") +
 labs(x = TeX("Maximum Temperature ($^{\\circ}$C)"), y = TeX("$lnRR_{Q_{10}}"), size = "Precision (1/SE)", color = "Habitat") + 
@@
             formula = y ~ x, se = FALSE, colour = "black") + 
-            scale_colour_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ 
+            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ 
 theme_classic() + theme(axis.title  = element_text(size = 30), 
@@
 
-  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, colour = habitat, fill = habitat)) + scale_colour_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
+  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
                         axis.text = element_text(size = 26), 

### 2024-06-21 ms.qmd
Fixed up fig-4 which is now in supp to jive with fig-5 in main MS

@@
 Theoretical models highlight the importance of environmental predictability in selecting for plastic responses.
-However, capturing environmental predictability is challing given that it is unclear which timescale one should select.
+However, capturing environmental predictability is challenging given that it is unclear which timescale one should select.
 For example, is it more important to look at correlation between temperatures monthly or seasonally.
@@
 #| fig-align: center
-#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats.
+#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A) and $lnCVR_{Q_{10_{acclim}}}$ (B) as a function of the Thermal Predictability for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
-Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."
-
-size_axis = 18
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ values for the slopes are shown for each habitat."
+
+size_axis = 20
+col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+####################
 # lnRR ACF
-
- col <- c("#0871B9", "#F3B40D", "#1BB908")
-
- dat_text2rr <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
-                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
-                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
+####################
+ dat_textacf <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
+                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
+                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
+                      title = c("Freshwater", "Marine", "Terrestrial"), 
                       condition = c("f", "m", "t"),
-                      x = rep(-2.8, 3),
-                      y = rep(-1.2, 3))
-
-p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2rr, aes(x = x+1, y = y, label =label), size = 5) + 
-geom_text(data = dat_text2rr, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
-geom_text(data = dat_text2rr, aes(x = x+1, y = y-0.65, label = p), size = 5) +
-theme(legend.position = "bottom", 
-      strip.background = element_blank(), 
-      strip.text = element_blank(), 
-      axis.text = element_text(size = size_axis), 
+                      x = rep(0, 3))
+y_adj = -3
+# Terrestrial
+  p_t_rr_acf <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
+  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
+  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
+  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
       axis.title = element_text(size = size_axis),
-      legend.text = element_text(size = 16),
-      legend.title = element_text(size = 16))
-
-# lnCVR ACF
-dat_text2cvr <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
-                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
-                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)
+
+# Marine
+p_m_rr_acf <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+
+# Freshwater
+p_f_rr_acf <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+
+####################
+# lnCVR CV
+####################
+dat_textcvr_acf <- data.frame(label = c(text(slope_f_4.9), 
+                                 text(slope_m_4.9), 
+                                 text(slope_t_4.9)),
+                      label2 = c(text(slope_f_4.9, b = FALSE), 
+                                 text(slope_m_4.9,b = FALSE), 
+                                 text(slope_t_4.9,b = FALSE)),
+                           p = c(p_text(slope_f_4.9), 
+                                 p_text(slope_m_4.9), 
+                                 p_text(slope_t_4.9)),
+                       title = c("Freshwater", "Marine", "Terrestrial"), 
                       condition = c("f", "m", "t"),
-                      x = rep(-2.8, 3),
+                      x = rep(0, 3),
                       y = rep(-4, 3))
 
-p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
-theme_classic() + 
-scale_fill_manual(values = c(col)) + 
-geom_text(data = dat_text2cvr, aes(x = x+1, y = y, label = label), size = 5) + 
-geom_text(data = dat_text2cvr, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
-geom_text(data = dat_text2cvr, aes(x = x+1, y = y-1.2, label = p), size = 5) +
-theme(legend.position = "bottom", 
-      strip.background = element_blank(), 
-      strip.text = element_blank(), 
-      axis.text = element_text(size = size_axis), 
+# Freshwater
+  yadj2 = -6
+  x_f = 0.6
+  p_f_cv_acf <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
+      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
+    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
+  theme(axis.text = element_text(size = size_axis), 
+        axis.text.y = element_text(size = size_axis), 
         axis.title = element_text(size = size_axis), 
-      legend.text = element_text(size = 16),
-      legend.title = element_text(size = 16))
-
-p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 20))
-
-ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")
-
-  p8.1.2 <- image_read("./output/figures/fig8.png")
-  p8.1.2 
+        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
+    ylim(-6, 3.5)
+
+# Marine
+  x_m = -0.4
+  p_m_cv_acf <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
+    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
+                 aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
+                 fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
+    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
+    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
+    theme(axis.text = element_text(size = size_axis), 
+        axis.text.y = element_text(size = size_axis), 
+        axis.title = element_text(size = size_axis), 
+        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
+    ylim(-6, 3.5)
+
+# Terrestrial
+
+x_t = 0
+p_t_cv_acf <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
+  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
+               aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
+               fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
+  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
+  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
+  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
+  theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
+  ylim(-6, 3.5)
+
+####################
+# Full plot
+####################
+
+p_cv_acf <- (p_t_rr_acf + p_m_rr_acf + p_f_rr_acf) / (p_t_cv_acf + p_m_cv_acf + p_f_cv_acf) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
+
+ggsave(p_cv_acf, width = 18, height = 10, filename = "./output/figures/fig_p_cv_acf_r1.pdf")
+
+  p_cv <- image_read("./output/figures/fig_p_cv_r1.png")
+  p_cv 
 ```

### 2024-06-22 ms.qmd
fixed some fig 4 code, nead to connet all new models for bubble plots

@@
     lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
-                                                        acf_all_c = scale(acf_all))
+                                                        acf_all_c = scale(acf_all),
+                                                        acf_lag1_c = scale(acf_lag1))
 
@@
 ############################################################################################  
-  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
+  lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim") %>% mutate(acf_lag1_c = scale(acf_lag1))
 
@@
   # More realistic model with 
-  model3.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
+  model3.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c, V = V,
                                        random = list(~1 | record_num,
@@
 
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
 
@@
 
-    slope_f_3.8 <- posteriors3.8[,"b_acf_all_c"]; pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
-    slope_m_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatm"]; pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
-    slope_t_3.8 <- posteriors3.8[,"b_acf_all_c"] + posteriors3.8[,"b_acf_all_c:habitatt"]; pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
-
-################################################################
-  # Model 4.4: Environmental autocorrelation model by acute/acclim
-################################################################
-if(rerun){
-  # More realistic model with 
-  model4.4          <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + type + type:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + type + type:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model3.3
-  saveRDS(model4.4, file = "./output/models/lnCVRQ10_4.4")
-  saveRDS(model4.4_bayes, file = "./output/models/lnCVRQ10_4.4_bayes")
-
-  } else{
-        model4.4 <- readRDS("./output/models/lnCVRQ10_4.4")
-  model4.4_bayes <- readRDS("./output/models/lnCVRQ10_4.4_bayes")
-}
+    slope_f_3.8 <- posteriors3.8[,"b_acf_lag1_c"] 
+                    pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
+    slope_m_3.8 <- posteriors3.8[,"b_acf_lag1_c"] + posteriors3.8[,"b_acf_lag1_c:habitatm"] 
+                    pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
+    slope_t_3.8 <- posteriors3.8[,"b_acf_lag1_c"] + posteriors3.8[,"b_acf_lag1_c:habitatt"] 
+                    pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
 
@@
     # Terrestrial Models
-    model3.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+    model3.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                        random = list(~1 | record_num,
@@
     # Freshwater Models
-    model3.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+    model3.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                        random = list(~1 | record_num,
@@
     # Marine Models
-      model3.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_all_c, V = V,
+      model3.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
                                        random = list(~1 | record_num,
@@
   # More realistic model with 
-  model4.8  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c + habitat + habitat:acf_all_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
+  model4.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + acf_all_c + habitat + habitat:acf_all_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
 
@@
 
-    slope_f_4.8 <- posteriors4.8[,"b_acf_all_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
-    slope_m_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
-    slope_t_4.8 <- posteriors4.8[,"b_acf_all_c"] + posteriors4.8[,"b_acf_all_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
+    slope_f_4.8 <- posteriors4.8[,"b_acf_lag1_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
+    slope_m_4.8 <- posteriors4.8[,"b_acf_lag1_c"] + posteriors4.8[,"b_acf_lag1_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
+    slope_t_4.8 <- posteriors4.8[,"b_acf_lag1_c"] + posteriors4.8[,"b_acf_lag1_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
+
+#################################################
+### Same model as above, but seperate for habitat 
+### For plotting, 4.8
+#################################################
+
+if(rerun){
+  # Terrestrial Models
+    model4.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
+    saveRDS(model4.8_t, "./output/models/model4.8_t")
+} else {
+     model4.8_t <- readRDS("./output/models/model4.8_t")
+     model4.8_m <- readRDS("./output/models/model4.8_m")
+     model4.8_f <- readRDS("./output/models/model4.8_f")
+}
 
@@
 ####################
- dat_textacf <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
-                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
-                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
+ dat_textacf <- data.frame(label = c(text(slope_f_3.8), 
+                                     text(slope_m_3.8), 
+                                     text(slope_t_3.8)),
+                          label2 = c(text(slope_f_3.8, b = FALSE), 
+                                     text(slope_m_3.8, b = FALSE), 
+                                     text(slope_t_3.8, b = FALSE)),
+                               p = c(p_text(slope_f_3.8), 
+                                     p_text(slope_m_3.8), 
+                                     p_text(slope_t_3.8)),
                            title = c("Freshwater", "Marine", "Terrestrial"), 
@@
 ####################
-dat_textcvr_acf <- data.frame(label = c(text(slope_f_4.9), 
-                                 text(slope_m_4.9), 
-                                 text(slope_t_4.9)),
-                      label2 = c(text(slope_f_4.9, b = FALSE), 
-                                 text(slope_m_4.9,b = FALSE), 
-                                 text(slope_t_4.9,b = FALSE)),
-                           p = c(p_text(slope_f_4.9), 
-                                 p_text(slope_m_4.9), 
-                                 p_text(slope_t_4.9)),
+dat_textcvr_acf <- data.frame(label = c(text(slope_f_4.8), 
+                                 text(slope_m_4.8), 
+                                 text(slope_t_4.8)),
+                      label2 = c(text(slope_f_4.8, b = FALSE), 
+                                 text(slope_m_4.8,b = FALSE), 
+                                 text(slope_t_4.8,b = FALSE)),
+                           p = c(p_text(slope_f_4.8), 
+                                 p_text(slope_m_4.8), 
+                                 p_text(slope_t_4.8)),
                        title = c("Freshwater", "Marine", "Terrestrial"), 
@@
   x_f = 0.6
-  p_f_cv_acf <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
-      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
-    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
+  p_f_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
+                              xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
+      geom_point(data = lnCVRQ10_data_wild_acclim_f, 
+                 aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
+                 fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
+    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr_acf$p[1]), size = 8) +
+    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[1]), size = 8) +
+    annotate("text", x = dat_textcvr_acf$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[1]), size = 8) +
   theme(axis.text = element_text(size = size_axis), 
@@
   x_m = -0.4
-  p_m_cv_acf <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
+  p_m_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
+                              xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
     geom_point(data = lnCVRQ10_data_wild_acclim_m, 
-                 aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
+                 aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
                  fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
-    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
+    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr_acf$p[2]), size = 8) +
+    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[2]), size = 8) +
+    annotate("text", x = dat_textcvr_acf$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[2]), size = 8) +
     theme(axis.text = element_text(size = size_axis), 
@@
 x_t = 0
-p_t_cv_acf <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
+p_t_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
+                            xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
   geom_point(data = lnCVRQ10_data_wild_acclim_t, 
-               aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
+               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
                fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
-  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
-  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
-  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
+  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr_acf$p[3]), size = 8) +
+  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr_acf$label2[3]), size = 8) +
+  annotate("text", x = dat_textcvr_acf$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr_acf$label[3]), size = 8) +
   theme(axis.text = element_text(size = size_axis), 

### 2024-06-23 ms.qmd
Add in updated figure for supp for predictability. Added some mored for plotting and fixed up Fig S2 legend

@@
 #################################################
+ lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
+ lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
+ lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")
 
 if(rerun){
-  # Terrestrial Models
+  # Terrestrial Model
     model4.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
@@
     saveRDS(model4.8_t, "./output/models/model4.8_t")
+
+  # Freshwater Model
+    model4.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
+    saveRDS(model4.8_f, "./output/models/model4.8_f")
+
+  # Marine Model
+    model4.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
+    saveRDS(model4.8_m, "./output/models/model4.8_m")
 } else {
@@
   y_adj = -3
+#############
 # Terrestrial
-  p_t_rr_acf <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = TRUE) + 
-    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
-  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
-  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
-  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
+#############
+  p_t_rr_acf <-  bubble_plot(model3.8_t, mod = "acf_lag1_c", group = "spp", 
+                             ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), 
+                             xlab = "Thermal Predictability", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_t, 
+               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
+               fill = col[3], colour = "black", stroke = 0.2, shape = 21) + 
+    labs(title = dat_textacf$title[3]) +
+    annotate("text", x = dat_textacf$x[3], y = y_adj, label = TeX(dat_textacf$p[3]), size = 8) +
+    annotate("text", x = dat_textacf$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
+    annotate("text", x = dat_textacf$x[3], y = y_adj + 1, label = TeX(dat_textacf$label[3]), size = 8) +
+    theme( axis.text = element_text(size = size_axis), 
+         axis.text.y = element_text(size = size_axis), 
+          axis.title = element_text(size = size_axis),
+        axis.title.x = element_blank(),
+          plot.title = element_text( size = 36, hjust = 0)) + 
+    ylim(-3,3)
+#############
+# Marine
+#############
+  x_m = -2.5
+p_m_rr_acf <-  bubble_plot(model3.8_m, mod = "acf_lag1_c", group = "spp", 
+                           ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), 
+                           xlab = "Thermal Predictability", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_m, 
+               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
+               fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  
+    labs(title = dat_textacf$title[2]) +
+    annotate("text", x = dat_textacf$x[2]+x_m, y = y_adj,     label = TeX(dat_textacf$p[2]),      size = 8) +
+    annotate("text", x = dat_textacf$x[2]+x_m, y = y_adj+0.5, label = TeX(dat_textacf$label2[2]), size = 8) +
+    annotate("text", x = dat_textacf$x[2]+x_m, y = y_adj+1,   label = TeX(dat_textacf$label[2]),  size = 8) +
     theme(axis.text = element_text(size = size_axis), 
@@
        axis.title.x = element_blank(),
-      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)
-
-# Marine
-p_m_rr_acf <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
-    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
-  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
-  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
-  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
+         plot.title = element_text( size = 36, hjust = 0)) + 
+    ylim(-3, 3)
+
+#############
+# Freshwater
+#############
+x_f = -0.2
+p_f_rr_acf <-  bubble_plot(model3.8_f, mod = "acf_lag1_c", group = "spp", 
+                           ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), 
+                           xlab = "Thermal Predictability", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_f, 
+               aes(x = acf_lag1_c, y = effect_size, size = 1/sqrt(V)), 
+               fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  
+    labs(title = dat_textacf$title[1]) +
+    annotate("text", x = dat_textacf$x[1]+x_f, y = y_adj,     label = TeX(dat_textacf$p[1]),      size = 8) +
+    annotate("text", x = dat_textacf$x[1]+x_f, y = y_adj+0.5, label = TeX(dat_textacf$label2[1]), size = 8) +
+    annotate("text", x = dat_textacf$x[1]+x_f, y = y_adj+ 1,  label = TeX(dat_textacf$label[1]),  size = 8) +
     theme(axis.text = element_text(size = size_axis), 
@@
        axis.title.x = element_blank(),
-      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
-
-# Freshwater
-p_f_rr_acf <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
-    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
-  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
-  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
-  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
-theme(axis.text = element_text(size = size_axis), 
-      axis.text.y = element_text(size = size_axis), 
-      axis.title = element_text(size = size_axis), 
-      axis.title.x = element_blank(),
-      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+         plot.title = element_text( size = 36, hjust = 0)) + 
+    ylim(-3, 3)
 
@@
                       y = rep(-4, 3))
-
+#############
 # Freshwater
+#############
   yadj2 = -6
-  x_f = 0.6
-  p_f_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
+  x_f = -0.2
+  p_f_cv_acf <-  bubble_plot(model4.8_f, mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                               xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
@@
     ylim(-6, 3.5)
-
+#############
 # Marine
-  x_m = -0.4
-  p_m_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
+#############
+  x_m = -2.5
+  p_m_cv_acf <-  bubble_plot(model4.8_m, mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                               xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
@@
     ylim(-6, 3.5)
-
+#############
 # Terrestrial
-
-x_t = 0
-p_t_cv_acf <-  bubble_plot( , mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
+#############
+x_t = -0.2
+p_t_cv_acf <-  bubble_plot(model4.8_t, mod = "acf_lag1_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), 
                             xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
@@
 
-p_cv_acf <- (p_t_rr_acf + p_m_rr_acf + p_f_rr_acf) / (p_t_cv_acf + p_m_cv_acf + p_f_cv_acf) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
-
-ggsave(p_cv_acf, width = 18, height = 10, filename = "./output/figures/fig_p_cv_acf_r1.pdf")
-
-  p_cv <- image_read("./output/figures/fig_p_cv_r1.png")
-  p_cv 
+p_acf <- (p_t_rr_acf + p_m_rr_acf + p_f_rr_acf) / (p_t_cv_acf + p_m_cv_acf + p_f_cv_acf) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
+
+ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/fig_p_acf_r1.pdf")
+
+  p_acf <- image_read("./output/figures/fig_p_acf_r1.png")
+  p_acf 
 ```
@@
 if(rerun){
-  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
-
-  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+
+  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
 
@@
 #| label: fig-s2
-#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
-Both acute ('green') and acclimation ('orange') effect sizes are plotted.
+#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B) log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
+Both acute ('black') and acclimation ('grey') effect sizes are plotted.
 cols <- c("#303234", "#D3D3D3")

### 2024-06-23 ms.qmd
UPdating pub bias. Realise I was missing information about the actual model results

@@
 
-Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
-
 ```{r, pubias}
@@
 
+  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_V")[,1]
+
   model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
 
+  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_V")[,1]
+
   model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+
+  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_V")[,1]
 
@@
 ```
+
+Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
+Meta-regression models including sampling variance as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(model_full_lnvr_pb)`, 95% CI: `r quantile(model_full_lnvr_pb, 0.025)` to `r quantile(model_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(model_full_lnvr_pb))`).

### 2024-06-24 ms.qmd
Updated pub bias. Use of effective sample size, rerun models controlling for max temp, better reporting in supplement and better description in methods

--- 2024-06-23 ms.qmd
@@
 
-We explored the possibility for publication bias graphically using funnel plots, and more formally by including sampling variance (or sampling standard error) in our meta-regression models  [@Nakagawa2022-gy].
-Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published.
-To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that accounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models  [@Nakagawa2022-gy].
+Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
+As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random effects (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+While sampling standard error (or variance) could have been included in our model, @Nakagawa2022-gy suggested instead to use $\sqrt{1/ne}$ (and its square root) to avoid potential problems with using sampling error itself (see @Nakagawa2022-gy for a discussion).
 
@@
 if(rerun){
-  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
-
-  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+
+# USe effective sample size instead because sampling variance estimates could indue a spurious correlation with our effect size
+    lnRRQ10_data <- lnRRQ10_data %>%  
+              mutate(n_ef = ifelse(name == "lnRR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
+                            ifelse(name == "lnRR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
+                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation
+
+    lnCVRQ10_data <- lnCVRQ10_data %>%  
+              mutate(n_ef = ifelse(name == "lnCVR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
+                            ifelse(name == "lnCVR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
+                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation
+
+    lnVRQ10_data <- lnVRQ10_data %>%  
+              mutate(n_ef = ifelse(name == "lnVR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
+                            ifelse(name == "lnVR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
+                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation
+
+  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  #Pull the posterior for the slope with sqrt effective n
+  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_sqrt1Dn_ef")[,1]
+
+  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+
+  #Pull the posterior for the slope with sqrt effective n
+  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_sqrt1Dn_ef")[,1]
+
+  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+
+  #Pull the posterior for the slope with sqrt effective n
+  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_sqrt1Dn_ef")[,1]
 
@@
 ```
+
+Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
+Meta-regression models including sampling standard error as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(model_full_lnvr_pb)`, 95% CI: `r quantile(model_full_lnvr_pb, 0.025)` to `r quantile(model_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(model_full_lnvr_pb))`) was not significant indicating little evidence for publication bias.

### 2024-06-25 ms.qmd
Fixing variance fig in supp

@@
 #| label: fig-2
-#| fig-cap:  **A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
+#| fig-cap:  "**A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
 **B)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
@@
 $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
-For ease of visualisation, all teh raw data plotted for both acute and acclimation type effect sizes are presented as circles."
+For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles."
 #| warning: false
@@
 #| fig-align: center
-#| fig-cap: "Estimated mean $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial systems.
-Note there were no differences between acute and acclimation $Q_{10}$ types so they were averaged.
-Thick black bars are 95% confidence intervals (CI's) and thin bars 95% prediction intervals (PI's).
+#| fig-cap: "Estimated mean acute and acclimation $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial habitats.
 The percentage change in variance is also back calculated.
 Note that these are raw variances and do not account for changes in mean physiological rates.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species."
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+$\Beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying .
+$\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
+In both cases, their 95% CI's are indicated within square brackets.
+$p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
+For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles."
+
+k_vr <- manual_extract(model3.2, mod = "habitat", group = "spp", exclude = NULL)
 
@@
   col <- c("#0871B9", "#F3B40D", "#1BB908")
-  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 5) +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
-           label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
-  annotate("text", x = 1.15, y = -5, 
-           label =paste0(round(mean(exp(f_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
-  annotate("text", x = 2.3, y = -5.2, 
-           label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
-  annotate("text", x = 2.15, y = -5, 
-           label =paste0(round(mean(exp(m_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
-           label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
-  annotate("text", x = 3.15, y = -5, 
-           label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
-    annotate("text", x = 3.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(t_VR_mean), digit = 3)))), hjust = 0, size = 6) + scale_fill_manual(values = c(col))
+  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", by = "type", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1) +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-2,3) +
+
+     annotate("text", x = 1.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+    annotate("text", x = 1.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = 1.20, y = -2, label =paste0(round(mean(f_VR_mean_ef), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+    annotate("text", x = 2.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+    annotate("text", x = 2.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = 2.20, y = -2, label =paste0(round(mean(m_VR_mean_ef), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ =", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+    annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col))
 
@@
 #| echo: false
-#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
-Model estimates are based off 1,253 effect sizes from 139 studies.
+#| tbl-cap: "Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
+Model estimates are based off 1,253 effect sizes from 139 studies."
 
@@
 ```
+
 #### *Publication bias analysis*

### 2024-06-25 ms.qmd
Fig S2 code update

@@
   col <- c("#0871B9", "#F3B40D", "#1BB908")
-  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", by = "type", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1) +
+  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", by = "type", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8) +
               scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-2,3) +
@@
     annotate("text", x = 1.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = 1.20, y = -2, label =paste0(round(mean(f_VR_mean_ef), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+  annotate("text", x = 1.20, y = -2, label =paste0(round(mean(f_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
 
@@
     annotate("text", x = 2.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = 2.20, y = -2, label =paste0(round(mean(m_VR_mean_ef), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+  annotate("text", x = 2.20, y = -2, label =paste0(round(mean(m_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
 
@@
     annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col))
+  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col)) + annotate("text", y = 2.5, x = c(1.3, 2.3, 3.3)+0.1, label = TeX(paste0("\\it{k} = ", k_vr$k, " (", k_vr$sdy, ")")), size = 6)
 
   p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
-          axis.text = element_text(size = 15), legend.text = element_text(size = 15),
-          legend.title = element_text(size = 15))
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top")
 

### 2024-06-25 ms.qmd
Fix some dumb mistakes in code. Now correct.

@@
     lnRRQ10_data <- lnRRQ10_data %>%  
-              mutate(n_ef = ifelse(name == "lnRR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
-                            ifelse(name == "lnRR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
-                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation
+              mutate(n_ef = ifelse(name == "lnRR_Q10_acute_t1", (r1.1_N + r1.2_N) / (r1.1_N*r1.2_N), # acute 1
+                            ifelse(name == "lnRR_Q10_acute_t2", (r2.1_N + r2.2_N) / (r2.1_N*r2.2_N), # acute 2
+                                                                (r1.1_N + r2.2_N) / (r1.1_N*r2.2_N)))) # acclimation
 
     lnCVRQ10_data <- lnCVRQ10_data %>%  
-              mutate(n_ef = ifelse(name == "lnCVR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
-                            ifelse(name == "lnCVR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
-                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation
+               mutate(n_ef = ifelse(name == "lnRR_Q10_acute_t1", (r1.1_N + r1.2_N) / (r1.1_N*r1.2_N), # acute 1
+                            ifelse(name == "lnRR_Q10_acute_t2", (r2.1_N + r2.2_N) / (r2.1_N*r2.2_N), # acute 2
+                                                                (r1.1_N + r2.2_N) / (r1.1_N*r2.2_N))))
 
     lnVRQ10_data <- lnVRQ10_data %>%  
-              mutate(n_ef = ifelse(name == "lnVR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
-                            ifelse(name == "lnVR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
-                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation
-
-  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+              mutate(n_ef = ifelse(name == "lnRR_Q10_acute_t1", (r1.1_N + r1.2_N) / (r1.1_N*r1.2_N), # acute 1
+                            ifelse(name == "lnRR_Q10_acute_t2", (r2.1_N + r2.2_N) / (r2.1_N*r2.2_N), # acute 2
+                                                                (r1.1_N + r2.2_N) / (r1.1_N*r2.2_N))))
+
+  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 
@@
 
-  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
 
@@
 
-  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
 

### 2024-06-25 ms.qmd
ESS too low so increase MCMC samples

@@
 
-  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
 
@@
 
-  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
 

### 2024-06-26 ms.qmd
Re-work some text on mean-variance relationships

@@
 We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
-We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean in physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
+We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
 We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
@@
 
-Overall, we found that the relationship between the mean and SD of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
-Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the relative variance in physiological rates does not increase proportionally as the mean increases.
-Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`).
+Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases.
+Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
 

### 2024-06-26 ms.qmd
Fix posteriors

@@
                             ifelse(name == "lnRR_Q10_acute_t2", (r2.1_N + r2.2_N) / (r2.1_N*r2.2_N), # acute 2
-                                                                (r1.1_N + r2.2_N) / (r1.1_N*r2.2_N))))
+                                                                (r1.1_N + r2.2_N) / (r1.1_N*r2.2_N)))) #acclimation
 
@@
   #Pull the posterior for the slope with sqrt effective n
-  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_sqrt1Dn_ef")[,1]
+  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_sqrtn_ef")[,1]
 
@@
   #Pull the posterior for the slope with sqrt effective n
-  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_sqrt1Dn_ef")[,1]
+  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_sqrtn_ef")[,1]
 
@@
   #Pull the posterior for the slope with sqrt effective n
-  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_sqrt1Dn_ef")[,1]
+  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_sqrtn_ef")[,1]
 

### 2024-06-26 ms.qmd
Fix to fig in S

@@
 
-        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ =", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ = ", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) +
     annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +

### 2024-06-26 ms.qmd
Checking climate projections code chunks and updating objects with the corrected model that includes max temp adjustment to effect size.

@@
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+  climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% 
+                          dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
 
@@
 # Subset the data
-lnCVRQ10_data_wild <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+  lnCVRQ10_data_wild <- data_long2 %>% 
+    filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
                         mutate(spp = species_full, 
@@
 
-# Look at the environment details across different habitats. Seems very similar.
-  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(cv), mean(acf_all))
+# Look at the environment details across different habitats. 
+  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(sd))
 
@@
 
-p_cv <- (p_t_rr + p_m_rr + p_f_rr) / (p_t_cv + p_m_cv + p_f_cv) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
+  p_cv <- (p_t_rr + p_m_rr + p_f_rr) / (p_t_cv + p_m_cv + p_f_cv) + 
+            plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
 
@@
 
-  # Model lat and long. Need to exclude missing acclimdation data. That will make it easier to create predcitions and explore the model fit.
-
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
+  # Model lat and long.
+Need to exclude missing acclimdation data.
+That will make it easier to create predcitions and explore the model fit.
+Include max temp to correct predictions for possible decrease at higher temps.
+
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) +
+                               (1 | record_num) + 
+                               (1 | gr(species_full, cov = A_wild_cvr)) + 
+                               (1 + max_temp_c | spp) + 
+                               (1 | trait) + 
+                               (1 | obs), 
+                      data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), 
+                      prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                      control = list(adapt_delta = 0.99, max_treedepth = 12), 
+                      chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
+                      data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
 
@@
 # Fitted vs actual data
-  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Predicted Effect Size", y = "Observed Effect Size") + theme_classic() + 
+  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size))      + 
+        geom_point() + geom_smooth(method = "lm")                     + 
+        labs(x = "Predicted Effect Size", y = "Observed Effect Size") + 
+        theme_classic()                                               + 
         geom_abline(intercept = 0, slope = 1)
@@
 Lets explore the data for odd ball predictions to see if there are any obvious reasons why.
-T here are very few for the most part but lets see why sign changes occur which are most stricking differences.
+There are very few for the most part but lets see why sign changes occur which are most stricking differences.
 Sign changes indicate the observed data is completely opposite in sign to the predcited data
@@
 
-    mean(r2) # Seems a bit high 0.5
-  quantile(r2, probs = c(0.025, 0.975)); #0.27-0.69
+    mean(r2) # Seems a bit high 0.53
+  quantile(r2, probs = c(0.025, 0.975)); #0.30-0.72
 
@@
 
-  mean(r2_2) #  0.48
-  quantile(r2_2, probs = c(0.025, 0.975)); #0.31-0.60
+  mean(r2_2) #  0.50
+  quantile(r2_2, probs = c(0.025, 0.975)); #0.33-0.62
 
@@
 
-  # Merge with model predcitions.
-This is the predcited lnCVRq10 for 10C change AT the specific latitude and longitude.
-We must assume that there is no plasticity or adaptation at each site to make projections
+  # Merge with model predictions.
+This is the predicted lnCVRQ10 for 10C change AT the specific latitude and longitude.
+We must assume that there is no plasticity or adaptation at each site to make projections.
   all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
@@
 
-  # First, lets merge the climate data with the predcitions, but here predcitions are not summarised. We have the entire posteior
+  # First, lets merge the climate data with the predictions, but here predictions are not summarised. We have the entire posteior
 
@@
 
-  # Second, lets convert each estimate to lncvr 1 degree C instead of 10...
+  # Second, lets convert each estimate to lncvr to 1 degree C instead of 10...
    all_pred2_no_sum2 <- all_pred2_no_sum %>%  
@@
 Effectively pooling across all the iterations for each dataset.
-This gives us an estimation of the mean change in variance across all locations/species., but it gives us 3200 point estimates of this mean.
+This gives us an estimation of the mean change in variance across all locations/species, but it gives us 3200 point estimates of this mean.
 We can then use this to calculate the 95% CI's.
-    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) # Fixed an error here. It was applying the mean across columns, not rows!
+    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) 
     mean(mean_perc)
@@
 
-# Need to take a step back
-  # 1. Why do we have NA in this data set? Thats because some species in the Future projections don't have data!
-  # 2. Why are l95 and u95 for marine not working...Fixed
-  # 3. Apply to the posteriors, rather than summary. Done
-
+# Create a table to summarise everything
 tables_future <- all_pred2 %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
@@
 #| message: false
-#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+#| fig-cap: "Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
 Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
 Predicted change in relative physiological rate variance for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
-Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change).
+Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change)."
 
@@
             formula = y ~ x, se = FALSE, colour = "black") + 
-            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ 
+            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ labs(fill = "Habitat") +
 theme_classic() + theme(axis.title  = element_text(size = 30), 

### 2024-06-26 ms.qmd
Changing title to probably more accurately reflect results

@@
 ---
-title: "Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change"
+title: "Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change"
 bibliography: ./bib/refs.bib

### 2024-06-29 ms.qmd
Fixing up supp figures and figures in text that get squished on render. Also moved text about detailed trait categories to the supple,ent and focus on the broader trait categories.

@@
 #| fig-height: 12
-#| fig-cap: Calculations of acute and acclimation effect sizes.
+#| fig-cap: "Calculations of acute and acclimation effect sizes.
 (A) Two idealised thermal performance curves for animals held at 'cold' ('blue') temperatures and warm ('red') temperatures.
@@
 R2.1 and R2.2 are the rates and associated SD (subscripted) for the warm acclimated animals at temperature 1 and 2, respectively.
-An example of how acute and acclimation $lnCVR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right hand side of the figure with reference to each of the four possible groups.
+An example of how acute and acclimation $lnCVR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right-hand side of the figure with reference to each of the four possible groups.
 Note that, two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
@@
 However, given it was not possible to measure the full performance curve for each species some test temperatures within studies may have converged on or moved past the thermal optima.
-In such cases, we expected our $Q_{10}$ effect sizes to be smaller as indicated by comparing the black dashed lines to grey dashed lines.
+In such cases, we expected our $Q_{10}$ effect sizes to be smaller as indicated by comparing the black dashed lines to grey dashed lines."
 
@@
 @white2012information also showed that the BA model may not always perform better.
-For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8 fold better fit to metabolic rate data than the BA relationship [@white2012information].
+For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better fit to metabolic rate data than the BA relationship [@white2012information].
 Given that studies included in our analysis never measured full performance curves at acute and acclimation temperatures it was not possible for us to compare different models of thermal dependence.
@@
 Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
-As such, using the detailed information on the trait type, and its associated units from a given study, we categorized each effect size into one of 12 trait categories.
-These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
-Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
-All other traits not falling within these categories were placed into 'other'.
-We also did a coarse-grained analysis of traits by comparing whole-organism measures (i.e., ‘cardiac’, ‘muscle’, ‘sprint’, ‘endurance’, ‘max MR’, ‘rest MR’), which all integrate a diversity of physiological and biochemical processes, with more fine-grained traits on enzymatic reactions (i.e., ‘metabolic enzyme’, ‘ATPase’, 'Proton Leak' and ‘OXPHOS’) which are more individualized biochemical processes.
+While we explored differences across more detailed trait categories (see Supplemental Materials),  most traits could be categorised into two broad categories that included whole-organism measures (i.e., ‘cardiac’, ‘muscle’, ‘sprint’, ‘endurance’, ‘max MR’, ‘rest MR’; see Supplemental Materials for details), which all integrate a diversity of physiological and biochemical processes.
+The other major trait category included measures of enzymatic reaction rates (i.e., ‘metabolic enzyme’, ‘ATPase’, 'Proton Leak' and ‘OXPHOS’) which are more individualized biochemical processes.
 We expected that whole-organism traits would be more likely to maintain relative variation in physiological function because they are composed of a greater number of biochemical reactions and would be more likely to acclimate.
+We did not include traits that could not be categories into these two (i.e., ‘Other’).
 
@@
 We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
+We refer to this model structure as “Model 1” throughout where results are provided.
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
@@
 Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show lower acclimation $lnRR_{Q_{10}}$.
+Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show a smaller acclimation $lnRR_{Q_{10}}$.
 To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
-As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).
+
+In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated.
+We predicted that, if $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we should see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
+To improve model interpretation we also mean-centred the maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our models we proceeded to build seperate models that tested our core questions.
+As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` $^\circ C$).
 
 We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine).
-Models included an interaction between effect type (i.e., acute or acclimation) and habitat.
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
 Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
@@
 We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g., @moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
-
-In all our models we tested and corrected for the possibility of the log-linearity assumption of our effect sizes being violated.
-We predcited that, if $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we should see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
-To improve model interpretation we centred the maximum temperature around the mean temperature of the experimental treatments.
 
@@
 ####################################################
+  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
+    lnRRQ10_data <- lnRRQ10_data %>% 
+                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
+                                                "tissue/organism",
+                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
+                                                "biochemical", trait_category)))
+
   # Filter to different habitats
@@
 if(rerun){
+  # Trait model. Subset to only trait categories that are clear. Remove 'other'
+      model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+                                           (1 | record_num) + 
+                                           (1 | gr(species_full, cov = A)) + 
+                                           (1 + max_temp_c | spp) +(1|trait) + 
+                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
+                                         data2 = list(A=A), family = gaussian(), 
+                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnRRQ10_data, trait_broad != "other"))
+
   # More realistic model with traits in marine species.
@@
                                             ~1 | species_full,
-                                            ~1 | spp,
+                                            ~1 + max_temp_c | spp,
                                             ~1 | trait,
@@
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
-The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures (($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`)) (@fig-Sacute).
+The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
 However, on average they were in the same direction and only differed by ~10%.
@@
 The total number of acute and acclimation  $lnRR_{Q_{10}}$/$lnCVR_{Q_{10}}$ effect sizes are indicated by the coloured bars as well as whether the taxa are marine, freshwater or terrestrial.
-Silhouettes are only representative taxa of major clades within the tree.
+Silhouettes are only representative taxa of major clades within the tree."
 
@@
 
+Effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+All results are from Model 1 (see “Meta-Analysis” above).
+
 Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
@@
 In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]B).
-
-Nonetheless, effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+All results are from Model 2 (see “Meta-Analysis” above).
 
@@
 #| label: fig-2
-#| fig-cap:  "**A)** Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
-**B)** Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+#| fig-cap: "A Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
+B Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
 For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 In panels A and B, thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\Beta$ values are the contrasts between acute and acclimation means within each habitat.
-$\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
+$\\Beta$ values are the contrasts between acute and acclimation means within each habitat.
+$\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
 In both cases, their 95% CI's are indicated within square brackets.
@@
   fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A")
+  ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 21.88, height = 9)
+
+  fig3 <- magick::image_read("./output/figures/fig3_r1.pdf")
   fig3
-  ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 21.88, height = 9)
-
 ```
@@
 ############################################################################################          
+lnRRQ10_data_wild_acclim <- lnRRQ10_data_wild %>%  filter(type == "acclim")
 
@@
 
-       r2_t <- r2_ml(model3.9_t)[1]    
 ```
@@
 
-  ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig_p_cv_r1.pdf")
+  ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig_p_cv_r1.png")
 
@@
 
-### Changes in physiological rate variance under climate change
+### *Changes in physiological rate variance under climate change*
 
@@
 
-# Here, we want to make global predcitions, at the lat/long in the data for how the opportunity of selection is expected to change with climate change.
+# Here, we want to make global predictions, at the lat/long in the data for how the opportunity of selection is expected to change with climate change.
 How can we do this?
@@
 Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across trophic levels within communities?
-What are the biochemical, cellular, and physiological mechanisms that underly reduced variance in physiological rates?
+What are the biochemical, cellular, and physiological mechanisms that underlie reduced variance in physiological rates?
 Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?
@@
 col <- c("#0871B9", "#F3B40D", "#1BB908")
-ggplot(data = lnRRQ10_data, aes(x = temp_2, y = effect_size)) + 
+lnrrq10_temp <- ggplot(data = lnRRQ10_data, aes(x = temp_2, y = effect_size)) + 
 geom_point(aes(size = 1/sqrt(V), fill = habitat), alpha = 0.8, shape = 21, colour = "black") +
@@
 
+ggsave(lnrrq10_temp, file = "./output/figures/lnrrq10_temp.png", height = 6, width = 8)
+
+lnrrq10_temp <- magick::image_read("./output/figures/lnrrq10_temp.png")
+lnrrq10_temp
+
 ```
@@
 
-  bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
+  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
                         axis.text = element_text(size = 26), 
@@
 
+  ggsave(accl_time, file = "./output/figures/accl_time.png", height = 6, width = 8.5)
+
+accl_time <- magick::image_read("./output/figures/accl_time.png")
+accl_time
 ```
@@
 
-#### *Acute and acclimation $lnRR_{Q_{10}}$ for different trait categories across marine, freshwater and terrestrial taxa*
+#### *Acute and acclimation $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa*
+
+In addition to the broader trait categories we fit models to understand how acute and acclimation effect sizes varied across trait categories.
+To achieve this, we categorized each effect size into one of 12 trait categories.
+These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
+Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
+All other traits not falling within these categories were placed into 'other'.
+
+@fig-S2; @fig-cvrtrait
 
@@
 #| label: fig-S2
-#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+#| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across detailed trait categories for A) marine, B) freshwater and C) terrestrial systems.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 #| echo: false
+
 k_marine=manual_extract(model1.3_m_het, mod = "trait_category", group = "record_num", exclude = "Antiox")
@@
 
-fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 14, width = 10)
+fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
+ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 20, width = 15)
 
@@
 figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 14, width = 10)
+ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 20, width = 15)
 
@@
 
-#### *Mean-variance relationships justify use of $lnCVR_{Q_{10}}$*
+#### *Mean-variance relationships to understand patterns in $lnCVR_{Q_{10}}$*
 We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
@@
 We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
+
+Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases.
+Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
 
@@
   # Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
+rerun = FALSE
+if(rerun) { 
       model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
@@
       saveRDS(model_mv2, file = "./output/models/model_mv2")
+} else {
+        model_mv1 <- readRDS("./output/models/model_mv1")
+        model_mv2 <- readRDS("./output/models/model_mv2")
+}
 
@@
 
-  (mv1 / mv2)  + plot_annotation(tag_levels = "A", tag_suffix = ")") + theme(plot.tag = element_text(size = 20, face = "bold"))
-
+ p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
+  ggsave(p_mv, file = "./output/figures/plot_mv.png", height = 8, width = 8)
+
+  p_mv <- magick::image_read("./output/figures/plot_mv.png")
+  p_mv
 ```
-
-Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
-Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases.
-Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
 
@@
 Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\Beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying .
-$\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
+$\\Beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying .
+$\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
 In both cases, their 95% CI's are indicated within square brackets.
@@
 
-With these limitations in mind, we used our temperature time series to calculate autoregressive correlation in temperaure across the entire time series.
-We then modelled how this measure of thermal predictability was related to plasticity.
-
-```{r}
-
+With these limitations in mind, we used our temperature time series to calculate auto regressive correlation in temperature across the entire time series.
+We then modeled how this measure of thermal predictability was related to plasticity.
+
+```{r, acf}
+#| label: acf
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+#| cache: true
 ############################################################################################
@@
 
-  p_acf <- image_read("./output/figures/fig_p_acf_r1.png")
+  p_acf <- image_read("./output/figures/fig_p_acf_r1.pdf")
   p_acf 
@@
 if(rerun){
-
-# USe effective sample size instead because sampling variance estimates could indue a spurious correlation with our effect size
+  # Use effective sample size instead because sampling variance estimates could induce a spurious correlation with our effect size
     lnRRQ10_data <- lnRRQ10_data %>%  
@@
 
-  #Pull the posterior for the slope with sqrt effective n
-  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_sqrtn_ef")[,1]
-
     model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
 
-  #Pull the posterior for the slope with sqrt effective n
-  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_sqrtn_ef")[,1]
-
     model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
-
-  #Pull the posterior for the slope with sqrt effective n
-  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_sqrtn_ef")[,1]
 
@@
 
+ #Pull the posterior for the slope with sqrt effective n
+  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_sqrtn_ef")[,1]
+ #Pull the posterior for the slope with sqrt effective n
+  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_sqrtn_ef")[,1]
+ #Pull the posterior for the slope with sqrt effective n
+  post_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_sqrtn_ef")[,1]
 ```
@@
 #| label: fig-s2
-#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B) log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
-Both acute ('black') and acclimation ('grey') effect sizes are plotted.
+#| fig-cap: "Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B) log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$).
+Both acute ('black') and acclimation ('grey') effect sizes are plotted."
 cols <- c("#303234", "#D3D3D3")
@@
 Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
-Meta-regression models including sampling standard error as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(model_full_lnvr_pb)`, 95% CI: `r quantile(model_full_lnvr_pb, 0.025)` to `r quantile(model_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(model_full_lnvr_pb))`) was not significant indicating little evidence for publication bias.
+Meta-regression models including sampling standard error as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(post_full_lnvr_pb)`, 95% CI: `r quantile(post_full_lnvr_pb, 0.025)` to `r quantile(post_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_full_lnvr_pb))`) was not significant indicating little evidence for publication bias.

### 2024-07-01 ms.qmd
Move trait specific models to supplement. Added new "broad trait" models with clearer predcitions about differences we expect. Added a new figure for the traits

@@
   # Filter to different habitats
-   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m") 
-   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f") 
-   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")
-
-  # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
-  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_t <- lnRRQ10_data_t %>% filter(!is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & trait_broad != "other") 
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & trait_broad != "other") 
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & trait_broad != "other")
 
@@
 if(rerun){
-  # Trait model. Subset to only trait categories that are clear. Remove 'other'
+
+#################################
+  # Broad Trait Category Models
+  # Subset to only trait categories 
+  # that are clear. Remove 'other'
+#################################
+  # Full Bayesian model   
    model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
@@
                                          chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnRRQ10_data, trait_broad != "other"))
-
-  # More realistic model with traits in marine species.
-Remove antioxidants because there are just too few effects.
-Note that, for orchardplot we can only fit one random slope, so we'll just use obs as results are unchanged and Bayesian models have it accounted for
-   model1.3_m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
+    saveRDS(model1.3_btrait_bayes, "./output/models/model1.3_btrait_bayes")
+
+  # Metafor models for creating plots. Subset by habitat to make this easier
+      # Marine
+         model1.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
                               R = list(species_full = m_phylo), dfs = "contain", 
-                              test = "t", 
+                              test = "t", struct = c("GEN","HCS"),  phi = 0,
                               data = lnRRQ10_data_m)
-
-  # Robust variance estimator.
-    model1.3_m_rve <- robust(model1.3_m, cluster = lnRRQ10_data_m$record_num) # Mostly Consistent but some changes to p for some traits.
-
-  # Baeysian model
-  model1.3_m_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
-                                            ~1 | trait,
-                                            ~1 + trait_category | obs),
-                              R = list(species_full = m_phylo), 
-                              struct = "HCS", rho = 0,  dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_m, control = list(iter.max=1000, rel.tol=1e-8))
-
-  # Check k is the same for both models (yes) and check which model is best supported
-    AICc1.3_m     <- AIC(model1.3_m) + AICc_correction(model1.3_m)
-    AICc1.3_m_het <- AIC(model1.3_m_het) + AICc_correction(model1.3_m_het)
-  # Clear support for this model. We'll go with this.
-    AICc1.3_m - AICc1.3_m_het
-
-  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 0)
-
-  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 + max_temp_c | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
-
-    # More realistic model with traits in freshwater species
-  model1.3_f <- metafor::rma.mv(effect_size ~  max_temp_c+c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full =f_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_f)
-
-  # Heteroscedastic variance model for freshwater
-  model1.3_f_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
-                                            ~1 | trait,
-                                            ~1 + trait_category | obs),
-                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_f, method = "REML", control=list(iter.max=1000, rel.tol=1e-8))
-
-  ## Check support for two models
-  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het) # Clearly better supported.
-      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
-  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het
-
-  # Run the Bayesian equivalent of the top supported model. 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 + max_temp_c| spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
-
-    # More realistic model with traits in terrestrial species
-  model1.3_t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full =t_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_t)
-
-  # Heteroscedastic variance model for terrestrial
-  model1.3_t_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c | spp,
-                                            ~1 | trait,
-                                            ~1 + trait_category | obs),
-                              R = list(species_full =t_phylo), struct = "HCS", rho = 0, dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_t)
-
-  # Check which model is better
-    AICc_model1.3_t     <- AIC(model1.3_t) + AICc_correction(model1.3_t)
-    AICc_model1.3_t_het <- AIC(model1.3_t_het) + AICc_correction(model1.3_t_het)
-
-  #  Delta
-    AICc_model1.3_t - AICc_model1.3_t_het
-
-  # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 + max_temp_c| spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
-
-    # Save models
-  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
-  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
-  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
-
-  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
-  saveRDS(model1.3_f_het, file = "./output/models/lnRRQ10_1.3f_het")
-  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
-
-  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
-  saveRDS(model1.3_t_het, file = "./output/models/lnRRQ10_1.3t_het")
-  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")
+         saveRDS(model1.3_m_broad, "./output/models/model1.3_m_broad")
+
+      # Freshwater
+         model1.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = f_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = lnRRQ10_data_f)
+          saveRDS(model1.3_f_broad, "output/models/model1.3_f_broad")
+
+      # Terrestrial
+         model1.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = t_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = lnRRQ10_data_t)
+         saveRDS(model1.3_t_broad, "output/models/model1.3_t_broad")
 
   } else{
-        model1.3_m <- readRDS("./output/models/lnRRQ10_1.3m")
-    model1.3_m_het <- readRDS("./output/models/lnRRQ10_1.3m_het")
-  model1.3_m_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_m")
-        model1.3_f <- readRDS("./output/models/lnRRQ10_1.3f")
-    model1.3_f_het <- readRDS("./output/models/lnRRQ10_1.3f_het")
-  model1.3_f_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_f")
-        model1.3_t <- readRDS("./output/models/lnRRQ10_1.3t")
-    model1.3_t_het <- readRDS("./output/models/lnRRQ10_1.3t_het")
-  model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
+    model1.3_btrait_bayes <- readRDS("./output/models/model1.3_btrait_bayes")
+         model1.3_m_broad <- readRDS("./output/models/model1.3_m_broad")
+         model1.3_f_broad <- readRDS("./output/models/model1.3_f_broad")
+         model1.3_t_broad <- readRDS("./output/models/model1.3_t_broad")
 }
@@
 ###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.3 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
-  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
-
+  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
+    lnCVRQ10_data <- lnCVRQ10_data %>% 
+                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
+                                                "tissue/organism",
+                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
+                                                "biochemical", trait_category)))
  # We can also run subsets for each habitat
-   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t"), tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
 
@@
    m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
-       A_m_cvr <- vcv(tree_m_cvr, corr = FALSE)
    f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
-       A_f_cvr <- vcv(tree_f_cvr, corr = FALSE)
    t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
-       A_t_cvr <- vcv(tree_t_cvr, corr = FALSE)
-
-  model2.3f <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+
+if(rerun){
+
+  # Full Bayesian model   
+   model2.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+                                           (1 | record_num) + 
+                                           (1 | gr(species_full, cov = A)) + 
+                                           (1 + max_temp_c | spp) +(1|trait) + 
+                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
+                                         data2 = list(A=A), family = gaussian(), 
+                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnCVRQ10_data, trait_broad != "other"))
+    saveRDS(model2.3_btrait_bayes, "./output/models/model2.3_btrait_bayes")
+
+  # Metafor models for creating plots. Subset by habitat to make this easier
+      # Marine
+         model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | trait,
-                                            ~1 | obs),
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = filter(lnCVRQ10_data, habitat == "m" & trait_broad != "other"))
+         saveRDS(model2.3_m_broad, "output/models/model2.3_m_broad")
+
+      # Freshwater
+         model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
                               R = list(species_full = f_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "f"))
-
-  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
-
-  model2.3m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              test = "t", struct = c("GEN","HCS"),  phi = 0,
+                              data = filter(lnCVRQ10_data, habitat == "f" & trait_broad != "other"))
+          saveRDS(model2.3_f_broad, "output/models/model2.3_f_broad")
+
+      # Terrestrial
+         model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "m"))
-  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
-
-  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
-  model2.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
+                                            ~1 + trait_broad| obs),
                               R = list(species_full = t_phylo_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data  %>% filter(habitat == "t"))
-  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = filter(lnCVRQ10_data, habitat == "t" & trait_broad != "other"))
+         saveRDS(model2.3_t_broad, "output/models/model2.3_t_broad")
 
   } else{
-        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
-        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
-        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
-        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
-  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
+    model2.3_btrait_bayes <- readRDS("./output/models/model2.3_btrait_bayes")
+    model2.3_m_broad <- readRDS("output/models/model2.3_m_broad")
+    model2.3_f_broad <- readRDS("output/models/model2.3_f_broad")
+    model2.3_t_broad <- readRDS("output/models/model2.3_t_broad")
 }
@@
 Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
+
+```{r, fig-btrait}
+#| label: fig-btrait
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across marine (A & D), freshwater (B & E) and terrestrial (C & F) habitats.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
+"
+#| echo: false
+#| warning: false
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lnrr_btrait  <- lnRRQ10_data  %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+n_lncvr_btrait <- lnCVRQ10_data %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+
+       col <- c("#0871B9", "#F3B40D", "#1BB908")
+     x.pos <- c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+############
+# lnRR
+############
+m_r <- n_lnrr_btrait %>% filter(habitat == "m")
+f_r <- n_lnrr_btrait %>% filter(habitat == "f")
+t_r <- n_lnrr_btrait %>% filter(habitat == "t")
+
+p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4))
+
+p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4))
+
+p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4))
+
+############
+# CVR
+############
+m_cv <- n_lncvr_btrait %>% filter(habitat == "m")
+f_cv <- n_lncvr_btrait %>% filter(habitat == "f")
+t_cv <- n_lncvr_btrait %>% filter(habitat == "t")
+
+p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4))
+
+p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4))
+
+p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4))
+
+############
+# Full fig
+############
+figbtrait <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
+ggsave(figbtrait, filename = "./output/figures/fig4_btrait_r1.png", width = 22, height = 12, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/fig4_btrait_r1.png")
+figbtrait
+```
 
@@
 @fig-S2; @fig-cvrtrait
+
+```{r, detail_trait}
+
+## Detailed trait category analyses for lnRR
+rerun = FALSE
+if(rerun){
+#################################
+  # Detailed Trait Categories
+  # For supplement
+#################################
+
+  # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
+  lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat = "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat = "f" & !is.na(c_accl_time))
+  lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat = "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
+
+  # Prune tree
+   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo <- vcv(tree_m, corr = TRUE)
+       A_m <- vcv(tree_m, corr = FALSE)
+   f_phylo <- vcv(tree_f, corr = TRUE)
+       A_f <- vcv(tree_f, corr = FALSE)
+   t_phylo <- vcv(tree_t, corr = TRUE)
+       A_t <- vcv(tree_t, corr = FALSE)
+
+  # More realistic model with traits in marine species.
+Remove antioxidants because there are just too few effects.
+Note that, for orchardplot we can only fit one random slope, so we'll just use obs as results are unchanged and Bayesian models have it accounted for
+   model1.3_m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = m_phylo), dfs = "contain", 
+                              test = "t", 
+                              data = lnRRQ10_data_m)
+
+  # Robust variance estimator.
+    model1.3_m_rve <- robust(model1.3_m, cluster = lnRRQ10_data_m$record_num) # Mostly Consistent but some changes to p for some traits.
+
+  # Baeysian model
+  model1.3_m_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = m_phylo), 
+                              struct = c("GEN", "HCS"),  phi = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_m, control = list(iter.max=1000, rel.tol=1e-8))
+
+  # Check k is the same for both models (yes) and check which model is best supported
+    AICc1.3_m     <- AIC(model1.3_m) + AICc_correction(model1.3_m)
+    AICc1.3_m_het <- AIC(model1.3_m_het) + AICc_correction(model1.3_m_het)
+  # Clear support for this model. We'll go with this.
+    AICc1.3_m - AICc1.3_m_het
+
+  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 0)
+
+  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 + max_temp_c | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
+
+    # More realistic model with traits in freshwater species
+  model1.3_f <- metafor::rma.mv(effect_size ~  max_temp_c+c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full =f_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_f)
+
+  # Heteroscedastic variance model for freshwater
+  model1.3_f_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full =f_phylo), struct = c("GEN", "HCS"), phi = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_f, method = "REML", control=list(iter.max=1000, rel.tol=1e-8))
+
+  ## Check support for two models
+  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het) # Clearly better supported.
+      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
+  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het
+
+  # Run the Bayesian equivalent of the top supported model. 
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 + max_temp_c| spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
+
+    # More realistic model with traits in terrestrial species
+  model1.3_t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full =t_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_t)
+
+  # Heteroscedastic variance model for terrestrial
+  model1.3_t_het <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full =t_phylo), struct = c("GEN", "HCS"),  phi = 0, dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_t)
+
+  # Check which model is better
+    AICc_model1.3_t     <- AIC(model1.3_t) + AICc_correction(model1.3_t)
+    AICc_model1.3_t_het <- AIC(model1.3_t_het) + AICc_correction(model1.3_t_het)
+
+  #  Delta
+    AICc_model1.3_t - AICc_model1.3_t_het
+
+  # Bayesian model
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 + max_temp_c| spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
+
+    # Save models
+  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
+  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
+  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
+
+  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
+  saveRDS(model1.3_f_het, file = "./output/models/lnRRQ10_1.3f_het")
+  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
+
+  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
+  saveRDS(model1.3_t_het, file = "./output/models/lnRRQ10_1.3t_het")
+  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")
+
+  } else{
+        model1.3_m <- readRDS("./output/models/lnRRQ10_1.3m")
+    model1.3_m_het <- readRDS("./output/models/lnRRQ10_1.3m_het")
+  model1.3_m_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_m")
+        model1.3_f <- readRDS("./output/models/lnRRQ10_1.3f")
+    model1.3_f_het <- readRDS("./output/models/lnRRQ10_1.3f_het")
+  model1.3_f_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_f")
+        model1.3_t <- readRDS("./output/models/lnRRQ10_1.3t")
+    model1.3_t_het <- readRDS("./output/models/lnRRQ10_1.3t_het")
+  model1.3_t_bayes <- readRDS("./output/models/lnRRQ10_1.3_bayes_t")
+}
+
+## Detailed trait category analyses for lnCVR
+
+  # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
+  lnCVRQ10_data_m <- lnCVRQ10_data %>% filter(habitat == "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
+  lnCVRQ10_data_f <- lnCVRQ10_data %>% filter(habitat == "f" & !is.na(c_accl_time))
+  lnCVRQ10_data_t <- lnCVRQ10_data %>% filter(habitat == "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
+
+  # Prune tree
+   tree_m_cvr <- tree_checks(lnCVRQ10_data_m, tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data_f, tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data_t, tree = tree_lncvr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
+   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
+   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
+
+if(rerun){
+#########################
+  # Detailed Trait Categories
+  # Models for the supplement
+#########################
+  # More realistic model 
+  model2.3 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.3, file = "./output/models/lnCVRQ10_2.3")
+  saveRDS(model2.3_bayes, file = "./output/models/lnCVRQ10_2.3_bayes")
+
+  model2.3f <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN", "HCS"), phi = 0, data = lnCVRQ10_data_f)
+
+  saveRDS(model2.3f, file = "./output/models/lnCVRQ10_model2.3f")
+
+  model2.3m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category| obs),
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnCVRQ10_data_m))
+  saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
+
+  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
+  model2.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnCVRQ10_data_t)
+  saveRDS(model2.3t, file = "./output/models/lnCVRQ10_model2.3t")
+
+  } else{
+#########################
+  # Detailed Trait Categories
+  # Models for the supplement
+#########################
+        model2.3 <- readRDS("./output/models/lnCVRQ10_2.3")
+        model2.3f <- readRDS("./output/models/lnCVRQ10_model2.3f")
+        model2.3m <- readRDS("./output/models/lnCVRQ10_model2.3m")
+        model2.3t <- readRDS("./output/models/lnCVRQ10_model2.3t")
+  model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
+}
+```
 

### 2024-07-01 ms.qmd
Fix in fig legend. Adding code chunk arguments and just cleaning some code to make it easier to read.

@@
 Shaded blue and red areas are the thermal optima of the performance curves.
-Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20$^\circ$C and $T_{2} = 30$^\circ$C) for both curves.
+Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20$^\\circ$C and $T_{2} = 30$^\\circ$C) for both curves.
 At each temperature a mean physiological rate (R) (points) and its standard deviation (SD) (error bars above and below mean) are estimated.
@@
 
-Different trait categories showed different acclimation responses across habitat types (see Supplement; @fig-S2).
+Different trait categories showed different acclimation responses across habitat types (@fig-btrait and see Supplement; @fig-S2).
 Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
@@
 Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
-Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-cvrtrait).
+Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-btrait).
 
@@
 ```{r, detail_trait}
+#| label: detail_trait
+#| echo: false
+#| include: false
+#| warning: false
 
 ## Detailed trait category analyses for lnRR
-rerun = FALSE
-if(rerun){
-#################################
-  # Detailed Trait Categories
-  # For supplement
-#################################
 
@@
 
+rerun = FALSE
+if(rerun){
+#################################
+  # Detailed Trait Categories
+  # For supplement
+#################################
   # More realistic model with traits in marine species.
@@
 
-  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 0)
-
   # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
-   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 + max_temp_c | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
+   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + 
+                                   (~1 | record_num) + 
+                                   (1 | gr(species_full, cov = A_m)) + 
+                                   (1 + max_temp_c | spp) +(1|trait) + 
+                                   (1 + trait_category |gr(obs, cor = FALSE)),  
+                                 data2 = list(A_m=A_m), family = gaussian(), 
+                                 prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                 control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                 chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)
 
@@
   # Run the Bayesian equivalent of the top supported model. 
-   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 + max_temp_c| spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
+   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + 
+                                   (~1 | record_num) + 
+                                   (1 | gr(species_full, cov = A_f)) + 
+                                   (1 + max_temp_c| spp) + (1|trait) + 
+                                   (1+trait_category|gr(obs, cor = FALSE)), 
+                                 data2 = list(A_f=A_f), family = gaussian(), 
+                                 prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                 control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                 chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
 
@@
   # Bayesian model
-   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 + max_temp_c| spp) + (1 | trait) + (1 + trait_category | gr(obs, cor = FALSE)), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
+   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c + c_accl_time + type + trait_category + type:trait_category + 
+                                   (~1 | record_num) + 
+                                   (1 | gr(species_full, cov = A_t)) + 
+                                   (1 + max_temp_c| spp) + 
+                                   (1 | trait) + 
+                                   (1 + trait_category | gr(obs, cor = FALSE)), 
+                                 data2 = list(A_t=A_t), family = gaussian(), 
+                                 prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                 control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                 chains = 8, thin = 5, iter = 3000, warmup = 1000, cores = 8, data = lnRRQ10_data_t)
 
@@
 
-   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + 
+                                 (~1 | record_num) + 
+                                 (1 | gr(species_full, cov = A_CVR)) + 
+                                 (1 + max_temp_c| spp) + 
+                                 (1|trait), 
+                               data2 = list(A_CVR=A_CVR), family = gaussian(), 
+                               prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                               control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
                               R = list(species_full = m_phylo_cvr), dfs = "contain", 
-                              test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnCVRQ10_data_m))
+                              test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnCVRQ10_data_m)
   saveRDS(model2.3m, file = "./output/models/lnCVRQ10_model2.3m")
 
-  # NOte that we need to drop interaction for terestrial as it's not able to estimate. 
+  # Note that we need to drop interaction for terrestrial as it's not able to estimate. 
   model2.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, V = V, 
@@
 
-#### *Plots of $I^2$ for multi-level models*
+#### *Plots of $I^2$ for multilevel models*
 ```{r, fig-s3}

### 2024-07-01 ms.qmd
Fixing supp figure code chunk name as it shouldn't be double plotting funnel plots.

@@
 
-@fig-S2; @fig-cvrtrait
+@fig-cvrtrait; @fig-cvrtrait
 
@@
   # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
-  lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat = "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
-  lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat = "f" & !is.na(c_accl_time))
-  lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat = "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
+  lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
+  lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & !is.na(c_accl_time))
+  lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
 
@@
 
-```{r, fig-S2}
-#| label: fig-S2
+```{r, fig-lnrrtrait}
+#| label: fig-lnrrtrait
 #| fig-cap: "Acute and Acclimation $lnRR_{Q_{10}}$ across detailed trait categories for A) marine, B) freshwater and C) terrestrial systems.
@@
 #### *Mean-variance relationships to understand patterns in $lnCVR_{Q_{10}}$*
-We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
-We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
-We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
-
-Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
-Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases.
-Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
-
-```{r, fig-mv}
-  #| label: fig-mv
-  #| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
-Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
-    col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+```{r, mc_models}
+#| label: mc_models
+#| echo: false
+#| include: false
 
@@
 }
+
+```
+
+We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
+We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
+We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
+
+Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases.
+Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
+
+```{r, fig-mv}
+  #| label: fig-mv
+  #| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
+Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
+    col <- c("#0871B9", "#F3B40D", "#1BB908")
 

### 2024-07-01 ms.qmd
fixed up supp figs
fix some spelling errors

@@
 #############################
-## Terrestrial Ectotherms
+## Terrestrial ectotherms
 #############################
@@
 
-  # Create new dataframe with only unique values for predcition.
+  # Create new data frame with only unique values for prediction.
   new_data_m  <- cbind(marine_data, new_data_m)
 
-  # We'll now make the predcitions from the model object using the new dataframe
+  # We'll now make the predictions from the model object using the new data frame
   marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
 
-  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
   marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
@@
 
-  # Create new dataframe with only unique values for predcition.
+  # Create new data frame with only unique values for prediction.
   new_data_f  <- cbind(fresh_data, new_data_f)
 
-  # We'll now make the predcitions from the model object using the new dataframe
+  # We'll now make the predictions from the model object using the new data frame
   fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
 
-  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
   fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
@@
 # Now that we have all the predictions we can merge the data together.
-Note that species itself is not really that useful because each prediction at each latitude and longitude should incoperate the species effect.
+Note that species itself is not really that useful because each prediction at each latitude and longitude should incorporate the species effect.
 So we'll remove it.
@@
 Note there are only 134 species because this is subset of the wild data.
-  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)  %>% mutate(uniques = interaction(spp, Latitude, Longitude))
-  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% dplyr::select(-species_full)
+         all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% 
+                     dplyr::select(-species_full)  %>% 
+                     mutate(uniques = interaction(spp, Latitude, Longitude))
+  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% d
+                      plyr::select(-species_full)
         spp_wild  <- length(unique(sub_data$spp))
@@
 
-@fig-cvrtrait; @fig-cvrtrait
+@fig-lnrrtrait; @fig-cvrtrait
 

### 2024-07-02 ms.qmd
Added Bayesian posteriors to trait fig

@@
 ###########################################################
-## Model 1.4 - whether chance between q10 depends on life stage and habita
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       trait_b_data <- data.frame(  type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lnrr_traitb <- fitted(model1.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lnrr_traitb <- cbind(trait_b_data, pred_lnrr_traitb)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lnrr_trait_post <- fitted(model1.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lnrr_trait_post <-  pred_lnrr_trait_post[,c(1,3,5,7,9,11)] - pred_lnrr_trait_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lnrr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lnrr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lnrr_trait_post), function(x) p_value(pmcmc(x))))
+
+###########################################################
+## Model 1.4 - whether chance between q10 depends on life stage and habitat
 ###########################################################
@@
 Different trait categories showed different acclimation responses across habitat types (@fig-btrait and see Supplement; @fig-S2).
+
 Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
@@
 
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       trait_b_data <- data.frame(  type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lncvr_traitb <- fitted(model2.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lncvr_traitb <- cbind(trait_b_data, pred_lncvr_traitb)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lncvr_traitb_post <- fitted(model2.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lncvr_trait_post <-  pred_lncvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lncvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lncvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lncvr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lncvr_trait_post), function(x) p_value(pmcmc(x))))
+
 ###################################################
@@
 
-p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4))
-
-p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4))
-
-p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4))
+t_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+yloc = c(1.5, 2.5)
+
+p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -0.8, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.5, 2) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.25, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8)
 
@@
 
-p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4))
-
-p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4))
-
-p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4))
+t_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
 
@@
 figbtrait <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/fig4_btrait_r1.png", width = 22, height = 12, device = "png")
+ggsave(figbtrait, filename = "./output/figures/fig4_btrait_r1.png", width = 28, height = 14, device = "png")
 
@@
 
-# Lets explore the model and how it's predciting the real data
+# Lets explore the model and how it's predicting the real data
   data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
@@
 
-# Seems to be OK, but over and under-predciting at times.
+# Seems to be OK, but over and under-predicting at times.
 Lets explore the data for odd ball predictions to see if there are any obvious reasons why.
-There are very few for the most part but lets see why sign changes occur which are most stricking differences.
-Sign changes indicate the observed data is completely opposite in sign to the predcited data
+There are very few for the most part but lets see why sign changes occur which are most striking differences.
+Sign changes indicate the observed data is completely opposite in sign to the predicted data
 
@@
 
-  # Create new dataframe with only unique values for predcition.
+  # Create new data frame with only unique values for prediction.
   new_data_t2  <- cbind(terrest_data, new_data_t)
 
-  # We'll now make the predcitions from the model object using the new dataframe
+  # We'll now make the predictions from the model object using the new data frame
   terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
 
-  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
   terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))

### 2024-07-02 ms.qmd
Re-writing sections for traits in results. Updated figure with stats

@@
 
-Different trait categories showed different acclimation responses across habitat types (@fig-btrait and see Supplement; @fig-S2).
+Across habitats the extent to which whole-organism versus biochemical processes acclimated varied (@fig-btrait A-C; and see Supplement [@fig-S2] for more detailed trait analysis).
+Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats (@fig-btrait B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms (@fig-btrait C).
+Unsurprisingly, neither broad trait category showed evidence of acclimation in terrestrial ectotherms (@fig-btrait A).
 
@@
 
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
+                                 (~1 | record_num) + 
+                                 (1 | gr(species_full, cov = A_CVR)) + 
+                                 (1 + max_temp_c| spp) + 
+                                 (1|trait) +
+                                 (1|obs), 
+                               data2 = list(A_CVR=A_CVR), family = gaussian(), 
+                               prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                               control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
 }
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       lh_b_data <- data.frame(     type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                               life.hist = rep(c("j", "a"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lncvr_lh_cvr <- fitted(model2.4_bayes, 
+                                     newdata = lh_b_data, 
+                                     re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lncvr_lh_cvr <- cbind(lh_b_data, pred_lncvr_lh_cvr)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lncvr_lh_post <- fitted(model2.4_bayes, 
+                                     newdata = lh_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lncvr_lh_post <-  pred_lncvr_lh_post[,c(1,3,5,7,9,11)] - pred_lncvr_lh_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lncvr_lh_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lncvr_lh_post), function(x) p_value(pmcmc(x))))
 
@@
 Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a decrease with increasing temperature across all habitat types, which was especially pronounced in terrestrial and marine ectotherms.
-There were no differences between $lnCVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$.
+The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between-study and trait differences (see Supplement;  @fig-s3).
+There were no differences between $lnCVR_{Q_{10_{acute}}}$ and $lnCVR_{Q_{10_{acclimation}}}$.
 Reductions in variance were driven by slower increases in the variance in physiological rates relative to the mean with scaling relationships between log standard deviation and log mean all being smaller than 1 and varying across habitats (See Supplementary Materials).
@@
 
-The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between-study and trait differences (see Supplement;  @fig-s3).
-Each life-history stage exhibited the same pattern of variance change in each of the habitats (@fig-cvrlh).
-Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (@fig-btrait).
+Across habitats whole-organism versus biochemical processes showed a similar decrease in relative variance in physiological rates (@fig-btrait D-F; see Supplement [@fig-S2] for more detailed trait analysis), except for biochemical processes in ectotherms occupying freshwater habitats, which showed small, albeit significant increase in relative variance when acclimated (@fig-btrait F).
+Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (see supplemental @fig-S2).
+Each life-history stage exhibited the same pattern of relative variance change in each of the habitats (@fig-cvrlh).
 
@@
 
+## lnRR Q10
+
 m_r <- n_lnrr_lh %>% filter(habitat == "m")
@@
 
-p1 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot)
-
-p2 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
-
-p3 <- orchard_plot(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot)
+p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot)
+
+p2 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
+
+p3 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
 
@@
 
-p1_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank())
-
-p2_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
-
-p3_cvr <- orchard_plot(model2.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Life Stage", by = "life.hist",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none")
+p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank())
+
+p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
+
+p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
 

### 2024-07-02 ms.qmd
Adding posterior predictions for life history

@@
       # Create new data for predictions
-       lh_b_data <- data.frame(     type = c("acclim", "acute"),
+       lh_b_data <- data.frame(     
                               max_temp_c = 0,
                              c_accl_time = 0,
-                                       V = 0,
+                                    type = c("acclim", "acute"),
                                  habitat = rep(c("t", "m", "f"), each = 4),
@@
             contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
-                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                     trait = rep(c("", ""), each = 1),
                                                     diff = sapply(data.frame(contrast_lncvr_lh_post), mean),

### 2024-07-02 ms.qmd
Updated life history figure with stats. Need to check stats carefully as it required manual caluclation given fitted wasn't working. Did some checks and looks ok, but more warranted. Need to now update stats in results section for LH comparisons pooling, then clean up code

@@
 #######################################################################
- # Create the data we want to make predcitions for. Just more intuitive
+ # Create the data we want to make predictions for. Just more intuitive
   newdata <- data.frame( c_accl_time = 0, 
                           max_temp_c = 0, 
-                                type = as.factor(rep(c("acute", "acclim"))), 
-                             habitat = as.factor(rep(c("m", "f", "t"), each = 4)), 
-                           life.hist = as.factor(c("j", "a", "a", "j")))
-  newdata$type  <- relevel(newdata$type, ref = "acute")
+                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
+                             habitat = rep(c("m", "f", "t"), each = 4), 
+                           life.hist = rep(c("j", "a"), each = 2))
 
@@
   sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
+            p <- apply(pred, 1, function(x) p_value(pmcmc(x)))
 
   # Create a summary dataset. 
-  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95)
+  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95, p = p)
 
 # Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-    # Marine 
+
+    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
+  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+                                                     stage = rep(c("j", "a"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
+
+    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
+          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.
+
+        # Contrast statistics
+            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+                                                     tyoe = rep(c("acute", "acclim"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
+  ######## OLD CODE BELOW>
         m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
         m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
+
     # Freshwater
@@
         f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
+
     # Terrestrial
@@
         m_acclim_lh <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
+
     # Freshwater
@@
         f_acclim_lh <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
+
     # Terrestrial
@@
 
+   # Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
+
 ###################################################
@@
       # Create new data for predictions
-       lh_b_data <- data.frame(     
+       lh_b_data <- data.frame( c_accl_time = 0, 
                           max_temp_c = 0, 
-                             c_accl_time = 0,
-                                    type = c("acclim", "acute"),
-                                 habitat = rep(c("t", "m", "f"), each = 4),
+                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
+                             habitat = rep(c("m", "f", "t"), each = 4), 
                            life.hist = rep(c("j", "a"), each = 2))
 
-       # Predict from model. Note this is the summary.
-         pred_lncvr_lh_cvr <- fitted(model2.4_bayes, 
-                                     newdata = lh_b_data, 
-                                     re_formula = NA,
-                                     summary = TRUE, 
-                                     robust = FALSE)
-         pred_lncvr_lh_cvr <- cbind(lh_b_data, pred_lncvr_lh_cvr)
-
-       # Predict to get the posterior.
+            # I have no idea why the fitted function is not working on this model. We're doing this the old fashioned way
+            X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = lh_b_data)
+
+            # Extract posteriors
+              post_lh <- posterior_samples(model2.4_bayes, pars = "^b")
+
+        # Now we can do all the calculations in one shot.# Predict to get the posterior.
 Note that we have the full posterior distribution here for each of the 12 categories in the new data.
 Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lncvr_lh_post <- fitted(model2.4_bayes, 
-                                     newdata = lh_b_data, re_formula = NA,
-                                     summary = FALSE, 
-                                     robust = FALSE)
-        contrast_lncvr_lh_post <-  pred_lncvr_lh_post[,c(1,3,5,7,9,11)] - pred_lncvr_lh_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+            pred_lh <- apply(t(post_lh),2 , function(x) as.matrix(X)%*%x)
+
+        contrast_lncvr_lh_post <-  pred_lh[c(1,3,5,7,9,11),] - pred_lh[c(2,4,6,8,10,12),] # Acclimation - acute.
 
@@
             contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
-                                                     trait = rep(c("", ""), each = 1),
-                                                    diff = sapply(data.frame(contrast_lncvr_lh_post), mean),
-                                                     l95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.025)),
-                                                     u95 = sapply(data.frame(contrast_lncvr_lh_post), function(x) quantile(x, 0.975)),
-                                                       p = sapply(data.frame(contrast_lncvr_lh_post), function(x) p_value(pmcmc(x))))
-
+                                                     stage = rep(c("j", "a"), each = 1),
+                                                    diff = apply(data.frame(contrast_lncvr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) p_value(pmcmc(x))))
 ```
@@
 
+###############
 ## lnRR Q10
+###############
+
+t_trait_b <- contrast_type_lnrr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b <- contrast_type_lnrr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b <- contrast_type_lnrr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+yloc = c(1.5, 2.5)
 
@@
 
-p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot)
-
-p2 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
-
-p3 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
-
-# CVR
-
+p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.3, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+###############
+# ln CVR
+###############
 m_cv <- n_lncvr_lh %>% filter(habitat == "m")
@@
 
-p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank())
-
-p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical"))
-
-p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+  t_trait_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
 
 fig4 <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(fig4, filename = "./output/figures/fig4_lh_r1.pdf", width = 22, height = 12, device = "pdf")
+ggsave(fig4, filename = "./output/figures/fig4_lh_r1.pdf", width = 28, height = 14, device = "pdf")
 

### 2024-07-02 ms.qmd
Added some more code to pool chains and wrote results on LH for lnRRQ10

@@
 # Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-
+  ############
     # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
+  ############
   contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.
@@
                                                        p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
-
+    ############
     # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
+    ############
           contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.
@@
             contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
-                                                     tyoe = rep(c("acute", "acclim"), each = 1),
+                                                     type = rep(c("acute", "acclim"), each = 1),
                                                     diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
@@
                                                        p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
-  ######## OLD CODE BELOW>
-        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
-        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
-
-    # Freshwater
-        f_ad <- 4
-        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
-        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
-
-    # Terrestrial
-        t_ad <- 8
-        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
-        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species
-
-# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-    # Marine 
-         m_acute_lh <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
-        m_acclim_lh <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
-
-    # Freshwater
-            f_ad <- 4
-         f_acute_lh <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
-        f_acclim_lh <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
-
-    # Terrestrial
-            t_ad <- 8
-         t_acute_lh <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
-        t_acclim_lh <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species
 
   # Acute differences between a and j across all habitats
-     acute_all_lh <- c(m_acute_lh, f_acute_lh, t_acute_lh); mean(acute_all_lh); quantile(acute_all_lh, c(0.025, 0.975)); pmcmc(acute_all_lh)
-    acclim_all_lh <- c(m_acclim_lh, f_acclim_lh, t_acclim_lh)
-
-# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong. These two lines of code should roughly match
-#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
-#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")
+     acute_all_lh <- c(contrast_lnrr_lh_post_type[1,], contrast_lnrr_lh_post_type[3,], contrast_lnrr_lh_post_type[5,]) 
+    acclim_all_lh <- c(contrast_lnrr_lh_post_type[2,], contrast_lnrr_lh_post_type[4,], contrast_lnrr_lh_post_type[6,])
 
@@
 
-Acclimation capacity also did not vary by life-history stage and there were no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (@fig-cvrlh A-C) (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
+Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles (@fig-cvrlh A-C).
+When comparing between acute and acclimation responses between adults and juveniles there were also no differences across habitats (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
 

### 2024-07-02 ms.qmd
Fixed a bug in life history stats fed into figure

@@
         # Contrast statistics
-            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+            contrast_stage_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
                                                      stage = rep(c("j", "a"), each = 1),
@@
 
-t_trait_b <- contrast_type_lnrr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-m_trait_b <- contrast_type_lnrr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-f_trait_b <- contrast_type_lnrr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+t_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
 

### 2024-07-03 ms.qmd
Revising sections of the discussion. Completely re-wrote first section. Needs some mroe explanations for why.

@@
 Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
-We developed effect size estimates that quantify how physiological variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
+We developed effect size estimates that quantify how physiological rate variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
 We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures driven by the lower proportional increase in physiological rate variance relative to the mean.
 Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
-Marine organisms also showed a capacity to acclimate to higher temperatures, but capacity for plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
+Marine organisms also acclimated, but plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
 Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
-Our results show that beneficial acclimation responses in some habitats (marine and freshwater) may trade-off with reductions in physiological rate variance that can have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+Our results show that, while there are weak acclimation responses in some habitats (marine and freshwater), such responses may trade-off with reductions in relative physiological rate variance that may have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
 
@@
 Thermal variation and predictability are known to differ across major habitats (terrestrial, marine and freshwater), and as such, we expect the extent of plasticity to vary.
-Species occupying terrestrial habitats often show weak acclimation abilities and so are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper].
-However, this conclusion has been questioned given that marine ectotherms have recently been shown to be closer to their upper thermal limits compared to terrestrial species [@Pinsky2019-fn].
+Species occupying terrestrial habitats often show weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
 Marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
@@
 We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
-We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
-
-Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
-We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
-We included any papers that were missed between our searches and those of @Havird2020-mj.
-@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader than @Havird2020-mj, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
-While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
-
-We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
-To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
-In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
-After title and abstract screening, there was a total of 149 papers for full text screening.
-Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
-Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
-We provide a PRISMA flow diagram of our extraction process in the *Supplement* (see @fig-prisma).
+For full details on the search protocol see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
 
@@
 We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
-We refer to this model structure as “Model 1” throughout where results are provided.
+We refer to this model structure as “Model 1” in the results.
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
@@
 In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated.
-We predicted that, if $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we should see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high temperatures.
+We predicted that, if $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we would see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
 Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
-To improve model interpretation we also mean-centred the maximum temperature and included it in our models.
-
-With acclimation time and maximum temperature as moderators in all our models we proceeded to build seperate models that tested our core questions.
-As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` $^\circ C$).
-
-We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine).
+To improve model interpretation, we also mean-centered the maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
+All estimates from our models are therefore conditioned on an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23$^\circ C$) across the dataset.
+
+We first tested the degree to which the difference in acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine).
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
@@
 In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10&deg;C differ depending on whether acute or acclimation responses are measured.
-For both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, if the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat.
-Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ changed across traits.
-Within each habitat (marine, freshwater, and terrestrial) we fit models that included an interaction between effect type (acute / acclimation) and trait category (as defined above).
-Variance in effects within trait categories appeared to vary depending on the trait type in question.
-Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
-To ensure models converged, we did not include trait categories that had less than six effect sizes.
-
-Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type.
+
+Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
+We also explored how acute and acclimation effects varied across more detailed trait categories, and these results can be found in the *Supplementary Materials*.
+Given that residual variance appeared to differ across trait categories we fit heteroscedastic residual variance models which were better supported in all cases ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
+
+Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
 We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g., @moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
 
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnCVR_{Q_{10}}$ were predicted by a populations climate variability (CV).
+We only used $lnRR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on the plastic adjustments to physiological rates.
+We used all $lnCVR_{Q_{10}}$ data because there were no differences between $lnCVR_{Q_{10_{acclimation}}}$ and $lnCVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe climate would impact acclimation and acute $lnCVR_{Q_{10}}$ differently.
+To test how climate variability impacted mean effect size in wild populations we fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators while controlling for acclimation time and maximum temperature used in the experiments (referred to as "Model 5").
+We also explored how environmental predictability, as measured by how correlated successive temperatures at a given location were across months, might also explain capacity for acclimation.
+However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
+As such, we report on these results for a single lag (1 month) in the *Supplementary Materials* but note they do not differ from CV analyses.
+
 #### *Modelling how climate change will impact on opportunity for selection*
 
-To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiological traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude.
+To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiological traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
 We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
@@
 @eq-lCVRpred turned the expected change across 10&deg;C to 1&deg;C.
-We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenerios in 2080.
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
 
@@
 Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random effects (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random effects (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
 While sampling standard error (or variance) could have been included in our model, @Nakagawa2022-gy suggested instead to use $\sqrt{1/ne}$ (and its square root) to avoid potential problems with using sampling error itself (see @Nakagawa2022-gy for a discussion).
@@
 
-Across habitats the extent to which whole-organism versus biochemical processes acclimated varied (@fig-btrait A-C; and see Supplement [@fig-S2] for more detailed trait analysis).
+Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; @fig-btrait A-C; and see Supplement [@fig-S2] for more detailed trait analysis).
 Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats (@fig-btrait B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms (@fig-btrait C).
@@
 
-Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles (@fig-cvrlh A-C).
+Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles ("Model 4"; @fig-cvrlh A-C).
 When comparing between acute and acclimation responses between adults and juveniles there were also no differences across habitats (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
@@
 Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a decrease with increasing temperature across all habitat types, which was especially pronounced in terrestrial and marine ectotherms.
-The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between-study and trait differences (see Supplement;  @fig-s3).
+The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between-study and trait differences ("Model 1"; see Supplement  @fig-s3).
 There were no differences between $lnCVR_{Q_{10_{acute}}}$ and $lnCVR_{Q_{10_{acclimation}}}$.
@@
 There was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`).
+In contrast, freshwater ectotherms exhibited a smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`) (results from "Model 2").
 
 Across habitats whole-organism versus biochemical processes showed a similar decrease in relative variance in physiological rates (@fig-btrait D-F; see Supplement [@fig-S2] for more detailed trait analysis), except for biochemical processes in ectotherms occupying freshwater habitats, which showed small, albeit significant increase in relative variance when acclimated (@fig-btrait F).
-Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (see supplemental @fig-S2).
-Each life-history stage exhibited the same pattern of relative variance change in each of the habitats (@fig-cvrlh).
+Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (see supplemental @fig-S2) ("Model 3").
+Each life-history stage exhibited the same pattern of relative variance change in each of the habitats ("Model 4"; @fig-cvrlh).
 
@@
 
-Thermal variability (i.e., $CV$) and predictability experienced by a population in the past did not explain acclimation capacity (@fig-4) or changes in physiological rate variance (@fig-5) among terrestrial, marine or freshwater populations.
+Thermal variability (i.e., $CV$) experienced by a population in the past did not explain acclimation capacity (@fig-5 A) or changes in physiological rate variance (@fig-5 B) among terrestrial, marine or freshwater populations ("Model 5").
 
@@
 So, what we want is to be able to understand how Q10 changes with latitude and longitude.
-Once we know that, we an extarct how temperature is expected to change from our current levels to future levels.
+Once we know that, we an extract how temperature is expected to change from our current levels to future levels.
 This will be in degrees C.
 Then, assuming no plasticity and evolution (big assumption) we can get a baseline change in variance for each site.
-We first need to adjust the predcited Q10 value so that it's at 1C temperaure, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
-This will adjust the predcited Q10 value to the change in 1 degree C.
+We first need to adjust the predicted Q10 value so that it's at 1C temperature, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
+This will adjust the predicted Q10 value to the change in 1 degree C.
 We can then multiply this by the temperature change expected at that location to get the % change in variance or acure/acclim response.
@@
 #############################
-  fresh_data <- sub_data  %>% filter(habitat == "f")%>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+  fresh_data <- sub_data  %>% filter(habitat == "f") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
 
@@
                      mutate(uniques = interaction(spp, Latitude, Longitude))
-  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% d
-                      plyr::select(-species_full)
+  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>%      dplyr::select(-species_full)
         spp_wild  <- length(unique(sub_data$spp))
@@
 Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Climate change is predicted to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% reduction in relative variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenerio.
+Climate change is predicted to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% reduction in relative variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenario.
+All results are taken from "Model 6".
 
@@
 
-Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023].
+Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
 Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater habitats as temperatures increase, with the decrease being particularly pronounced in terrestrial ectotherms (~28%).
 These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results uncover an hitherto unrecognised dynamic where the benefits of acclimation may be counteracted by a decrease in trait variance.
+Our results uncover an hitherto unrecognised dynamic where the benefits of acclimation may be counteracted by a decrease in relative trait variance, which when considered along side acclimation capacity, change our understanding of how ectotherms across different habitats will be able to cope with increased temperatures.
 
@@
 
-Understanding the interplay between plasticity and genetic adaptation has important implications for predicting population resilience to climate change [@urban2023and; @Chevin2010; @hoffmann2011climate; @merila2014climate; @bush2016incorporating; @seebacher2023can; @cooke2021one].
-For example, incorporating phenotypic plasticity and adaptation into species distribution models dampens the predicted contraction of distributions in the face of climate change [e.g., @bush2016incorporating].
-In addition, it may be expected that reductions in variance impact the 'opportunity for selection' by reducing the strength of selection and/or the genetic variance exposed to selection, thereby reducing the capacity to evolve under climate change [@hoffmann2011climate; @urban2023and].
-Quantifying the degree of plasticity and genetic/phenotypic variation in key physiological responses is therefore recognised as being critical to informing projections for organisms threatened by climate change [@cooke2021one].
-
 We show that acclimation of physiological rates and changes in relative variance differ across habitats.
-In freshwater habitats, acclimation responses will likely be beneficial and this coincides with relatively little reduction in the relative variance thereby maintaining the raw material for selection to operate.
-In contrast, acclimation responses of marine organisms are associated with a nearly equal reduction in relative variance so that the beneficial effects of acclimation trade off against reduced potential for selection at high temperatures.
-In terrestrial ectotherms, relative variance reductions are particularly pronounced, and this coincides with a general inability to acclimate, which may make them more vulnerable to climate warming compared to aquatic ectotherms.
-However, terrestrial species also have greater opportunity for behavioural microhabitat selection which will decrease the impacts of climate change at least in complex, thermally heterogeneous environments [@huey2012predicting].
-
-Our findings highlight the potential vulnerability of terrestrial and marine ectotherms to climate change.
-Our meta-analytic results provide percentage changes of relative variances and acclimation responses that can be used to parameterise models (e.g., species distribution models) [@bush2016incorporating; @demarche2019incorporating] to predict species distributions or assess population resilience in the face of climate warming.
-Our results also define the range of biological responses observed across diverse taxa (e.g., through prediction intervals) providing opportunities to incorporate realistic biological variation into the modelling process.
+Our findings confirm previous results that quantify the different capacity of terrestrial, marine and freshwater ectotherms to acclimate [@Seebacher2015-wi; @Gunderson2015-hz; @morley2019physiological].
+Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
+The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms (decrease of 16% versus ~10% in @Seebacher2015-wi), and opposite in terrestrial ectotherms (increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi), possibly due to our use of new $Q_{10}$ based effect sizes that allow us to control for sampling variance.
+
+More importantly, the change in relative variance in physiological rates across habitats is nearly equivalent (marine) or larger (terrestrial) compared to their capacity to acclimate.
+Only in freshwater ectotherms did reductions in physiological rates as a result of acclimation coincide with no major change in relative variation.
+Mechanistically, it is unclear what is contributing to reductions in relative variation in physiological rates at higher temperatures.
+One possible explanation may be that biochemical reactions are operating more efficiently at higher temperatures, or when acclimated, within a species' normal thermal range.
+Increased efficiency may result in fewer physiological processes .....
+Such effects are expected to be amplified across habitats because of different thermal safety margins, with terrestrial ectotherms being closer to their thermal maxima , and this increased efficiency leads reduced constraints on physiological processes.
+Our analysis showing that biochemical traits are better capable   These results further highlight the potential vulnerability of terrestrial ectotherms to climate change, while calling into question if acclimation in marine systems will be able to counteract the potentially negative effects of reductions in relative variance.
+Assuming changes in relative variation in physiological rates are underpinned by genetic variation, and that there is a genetic correlation with fitness, such reductions in physiological variance could limit a populations ability to adapt to future climates [@urban2023and].
+
+While we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited.
+As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized or how behavioural strategies of ectotherms might be able to compensate for the general weak acclimation abilities of many ectotherms.
+For example, terrestrial species have greater opportunity for behavioural microhabitat selection which is expected to decrease the impacts of climate change in thermally heterogeneous environments [@huey2012predicting].
+Future theoretical models, that vary both mean and variance, are needed to better understand the broader evolutionary and ecological implications of our findings.
 
@@
 
-#### *PRISMA flow diagram*
+#### *Literature Search Protocol and PRISMA flow diagram*
+
+More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
+
+Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
+We included any papers that were missed between our searches and those of @Havird2020-mj.
+@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader than @Havird2020-mj, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
+While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
+As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+
+We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
+To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
+In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
+After title and abstract screening, there was a total of 149 papers for full text screening.
+Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
 

### 2024-07-03 ms.qmd
New refs and updated quarto

@@
 The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms (decrease of 16% versus ~10% in @Seebacher2015-wi), and opposite in terrestrial ectotherms (increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi), possibly due to our use of new $Q_{10}$ based effect sizes that allow us to control for sampling variance.
-
-More importantly, the change in relative variance in physiological rates across habitats is nearly equivalent (marine) or larger (terrestrial) compared to their capacity to acclimate.
-Only in freshwater ectotherms did reductions in physiological rates as a result of acclimation coincide with no major change in relative variation.
-Mechanistically, it is unclear what is contributing to reductions in relative variation in physiological rates at higher temperatures.
-One possible explanation may be that biochemical reactions are operating more efficiently at higher temperatures, or when acclimated, within a species' normal thermal range.
-Increased efficiency may result in fewer physiological processes .....
-Such effects are expected to be amplified across habitats because of different thermal safety margins, with terrestrial ectotherms being closer to their thermal maxima , and this increased efficiency leads reduced constraints on physiological processes.
-Our analysis showing that biochemical traits are better capable   These results further highlight the potential vulnerability of terrestrial ectotherms to climate change, while calling into question if acclimation in marine systems will be able to counteract the potentially negative effects of reductions in relative variance.
+Importantly, while marine and freshwater ectotherms were capable of partial acclimation, the effect size was small (amounting to $Q_{10}$ dropping from 1.8 to 1.6), suggesting acclimation will, on average, provide limited capacity to maintain physiological rates in the face of climate change.
+
+Changes in relative variance in physiological rates across habitats was nearly equivalent (marine) or larger (terrestrial) compared to their capacity to acclimate.
+Only in freshwater ectotherms did acclimation in physiological rates coincide with no change in relative variation.
+Mechanistically, it is unclear what is contributing to reduction in relative variation in physiological rates at higher temperatures.
+One possible explanation may be that biochemical reactions are operating more efficiently or are relying on more conformationally stable enzymes at higher temperatures [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins].
+Such a mechanism may also help explain the differences in relative variance across habitat types.
+Terrestrial ectotherms may be relying on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range.
+Needless to say, our results further highlight the potential vulnerability of terrestrial ectotherms to climate change, while calling into question if acclimation in marine systems will be able to counteract the potentially negative effects of reductions in relative variance.
 Assuming changes in relative variation in physiological rates are underpinned by genetic variation, and that there is a genetic correlation with fitness, such reductions in physiological variance could limit a populations ability to adapt to future climates [@urban2023and].
 
-While we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited.
+Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited.
 As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized or how behavioural strategies of ectotherms might be able to compensate for the general weak acclimation abilities of many ectotherms.
@@
 
-### ***Ecological consequences of reduced relative variation in physiological rates***
-Relative variance reductions in metabolic rates and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
-Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
-They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-Our results suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial habitats.
-However, data testing the impacts of changes in variance on populations are limited to very few taxa.
-Future experimentation across a broader range of taxa should manipulate levels of variance to understand its ecological outcomes.
-
 ### ***No signature of past climate on capacity for physiological plasticity***
-
 Theoretical evolutionary models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
@@
 The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
+
+### ***Ecological consequences of reduced relative variation in physiological rates***
+Relative variance reductions in metabolic rates and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
+Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
+For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
+They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
+Our results suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial habitats.
+However, data testing the impacts of changes in variance on populations are limited to very few taxa.
+Future experimentation across a broader range of taxa should manipulate levels of variance to understand its ecological outcomes.
 

### 2024-07-04 ms.qmd
Removing the ecological consequences section from discussion and moving a few sentences to the intro. I think some of these are better placed there anyway.

@@
 
+Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
+
 Phenotypic plasticity is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
@@
 Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
-The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms (decrease of 16% versus ~10% in @Seebacher2015-wi), and opposite in terrestrial ectotherms (increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi), possibly due to our use of new $Q_{10}$ based effect sizes that allow us to control for sampling variance.
-Importantly, while marine and freshwater ectotherms were capable of partial acclimation, the effect size was small (amounting to $Q_{10}$ dropping from 1.8 to 1.6), suggesting acclimation will, on average, provide limited capacity to maintain physiological rates in the face of climate change.
+The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms (decrease of 16% versus ~10% in @Seebacher2015-wi), and opposite in terrestrial ectotherms (increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi), possibly due to the use of new $Q_{10}$ based effect sizes that allow us to control for sampling variance.
+Importantly, while marine and freshwater ectotherms were capable of partial acclimation, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6).
 
@@
 Only in freshwater ectotherms did acclimation in physiological rates coincide with no change in relative variation.
-Mechanistically, it is unclear what is contributing to reduction in relative variation in physiological rates at higher temperatures.
-One possible explanation may be that biochemical reactions are operating more efficiently or are relying on more conformationally stable enzymes at higher temperatures [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins].
+Mechanistically, it is unclear what is contributing to the reduction in relative variation in physiological rates at higher temperatures.
+One possible explanation may be that biochemical reactions are operating more efficiently or are relying on more conformationally stable enzymes at higher temperatures impacting between individual variation [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins].
 Such a mechanism may also help explain the differences in relative variance across habitat types.
-Terrestrial ectotherms may be relying on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range.
-Needless to say, our results further highlight the potential vulnerability of terrestrial ectotherms to climate change, while calling into question if acclimation in marine systems will be able to counteract the potentially negative effects of reductions in relative variance.
-Assuming changes in relative variation in physiological rates are underpinned by genetic variation, and that there is a genetic correlation with fitness, such reductions in physiological variance could limit a populations ability to adapt to future climates [@urban2023and].
-
-Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited.
-As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized or how behavioural strategies of ectotherms might be able to compensate for the general weak acclimation abilities of many ectotherms.
+For example, terrestrial ectotherms may rely on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range necessary to operate in more variable thermal environments [@angilletta2009thermal].
+Acclimation responses in marine and freshwater organisms would also result in the maintenance, or even increase, in variance at higher temperatures due to the expression of alternative enzymes that function more effectively at higher temperatures.
+Given that biochemical traits in marine and freshwater organisms acclimated, and their relative variance increased in freshwater after acclimation, this seems plausible.
+
+Our results further highlight the potential vulnerability of terrestrial ectotherms to climate change, while calling into question if acclimation in marine systems will be able to counteract the potentially negative effects of reductions in relative variance.
+Assuming changes in relative variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, such reductions in physiological variance could limit a populations ability to adapt to future climates [@urban2023and].
+Of course, considering how behavioural modifications buffer organisms from high temperatures is also needed.
 For example, terrestrial species have greater opportunity for behavioural microhabitat selection which is expected to decrease the impacts of climate change in thermally heterogeneous environments [@huey2012predicting].
-Future theoretical models, that vary both mean and variance, are needed to better understand the broader evolutionary and ecological implications of our findings.
+Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited in terrestrial and marine habitats.
+As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized.
+Future theoretical models, that vary both mean and variance, are needed to characterise the interplay between changes in mean and variance.
 
@@
 The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
-
-### ***Ecological consequences of reduced relative variation in physiological rates***
-Relative variance reductions in metabolic rates and performance (e.g., sprint speed) were most strongly impacted by increased temperature.
-Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-For example, @kooijman1989population integrated individual variation in dynamic energy budget (DEB) models developed for *Daphnia magna*.
-They showed that greater between-individual variation in DEB parameters led to less extreme population fluctuations compared to scenarios with no variation [@kooijman1989population].
-Our results suggest that terrestrial ectotherms will likely face greater challenges to adapting to climate change [@hoffmann2013upper; @Gunderson2015-hz; @Pottier2022], leading to greater rates of extinction and reduced productivity in terrestrial habitats.
-However, data testing the impacts of changes in variance on populations are limited to very few taxa.
-Future experimentation across a broader range of taxa should manipulate levels of variance to understand its ecological outcomes.
 

### 2024-07-04 ms.qmd
editing conclusions. New paragrah and some adjustments to sentences

@@
 While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations as evidenced by wide prediction intervals.
-Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced and possibly more realistic predictions about the impacts of climate change on natural populations.
-While we do not yet understand the relative contribution of environmental and genetic factors to variances changes, models could better decouple how different levels of heritability with different total variance impact evolutionary and ecological predictions.
-Our meta-analysis now provides the opportunity to parameterise models and ensure they are better aligned with empirical findings.
-Nonetheless, many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
+Substantial variation in acclimation responses and changes in variance exist among populations, as evidenced by wide prediction intervals.
+Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
+
+While we do not yet understand the relative contribution of environmental and genetic factors to variance changes, models could better decouple how different levels of heritability and total variance impact evolutionary and ecological predictions.
+Our meta-analysis now provides the opportunity to parameterise such models, and ensure they are better aligned with empirical findings.
+Many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
 Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across trophic levels within communities?
@@
 How much of the reduction in variance is driven by lower levels of genetic variance?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major habitats.
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
 

### 2024-07-04 ms.qmd
UPdated and working on LH secin in discussion

@@
 The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms (decrease of 16% versus ~10% in @Seebacher2015-wi), and opposite in terrestrial ectotherms (increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi), possibly due to the use of new $Q_{10}$ based effect sizes that allow us to control for sampling variance.
-Importantly, while marine and freshwater ectotherms were capable of partial acclimation, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6).
+Greater capacity for acclimation in aquatic organisms may be the result of fewer opportunities for behaviuoral thermoregulation in aquatic environments making physiological remodeling important for maintaining homeostasis [@Gunderson2015-hz; @morley2019physiological].
+While marine and freshwater ectotherms were capable of partial acclimation it is still important to recognise that, on average, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6).
 
@@
 Of course, considering how behavioural modifications buffer organisms from high temperatures is also needed.
-For example, terrestrial species have greater opportunity for behavioural microhabitat selection which is expected to decrease the impacts of climate change in thermally heterogeneous environments [@huey2012predicting].
+Terrestrial species likely have greater opportunity for behavioural microhabitat selection in thermally heterogeneous environments which is expected to decrease the impacts of climate change [@huey2012predicting; @sunday2014thermal].
 Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited in terrestrial and marine habitats.
@@
 ### ***Plasticity and relative variance in physiological rates do not differ between life stages***
-Life-history stages often occupy different ecological niches and exhibit different physiological responses, levels of plasticity, and patterns of mortality in response to temperature.
+We show that early (juvenile) and late (adult) life stages exhibited similar acclimation capacities and changes in relative variance across habitats.
+The lack of differences we observed may be due to the fact that both juvenile and adult animals occupy similar ecological niches and thermoregulate in similar ways making physiological responses to temperature similar.
+It is possible that temperatures experienced earlier in development, for example egg or early larval stages, would show different patterns because early developmental constraints are known to affect how physiological systems respond later in life because of programmatic effects [@angilletta2009thermal; @noble2018developmental; @o2019developmental].
+Such effects would manifest in juveniles life-history stages
+
+environments are expected Life-history stages often occupy different ecological niches and exhibit different physiological responses, levels of plasticity, and patterns of mortality in response to temperature.
 As such, it is becoming increasingly important to understand how climate change will impact different life-history stages [@levy2015resolving; @petitgas2013impacts].
 Greater plasticity in early life stages of development is expected to be important to increase resilience to the effects of climate change because early life stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
-We show that there were generally similar patterns between early and late life stages across a diversity of taxa, both in terms of variance changes and the capacity for plasticity.
 On average, our results show that early life stages are not more vulnerable to the impacts of climate change.

### 2024-07-05 ms.qmd
Working on the introduction

@@
 
-Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
-However, the focus up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
-
-As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted. NEED MORE ABOUT WHY VARIANCE NOT JUST IMPORTANCE
-
-Changes in variability of traits governing energy demand could have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-Maintaining intrapopulation variability in physiological rates in a warmer world may therefore be important for population resilience to climate change.
-
 Phenotypic plasticity is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Thermal variation and predictability are known to differ across major habitats (terrestrial, marine and freshwater), and as such, we expect the extent of plasticity to vary.
+Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect the extent of plasticity of organisms within these habitats to vary.
 Species occupying terrestrial habitats often show weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
 Marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
-However, it is unclear if the magnitude of physiological adjustment is sufficient to compensate for potentially negative environmental effects, particularly when temperature interacts with other abiotic changes.
-Low oxygen availability may be a major factor influencing the vulnerability of aquatic habitats, whereas remaining close to thermal limits and greater water loss is expected to be a stronger constraint on physiological processes in terrestrial ectotherms [@Verberk2016].
-Given the observed variation among terrestrial and aquatic ectotherms in their acclimation capacity and the different challenges associated with living in air versus water, the effect of climate warming on variation in physiological traits may differ among terrestrial and aquatic habitats, which may have important cascading effects on energy transfer and productivity between these habitats [@seebacher2023can; @barneche2021warming].
-
-Understanding how variability in physiological rates are affected by climate change is important because lack of physiological variation can limit responses to selection (i.e., the 'opportunity for selection on a trait') [@Pelletier2012].
-Decreases in phenotypic variance also suggests strong stabilising selection or reflects constraints on performance [@Scheiner2020; @Dewitt1998].
-Changes in physiological trait variation may also have important ecological consequences by promoting population productivity and stability [@Agashe2009; @kooijman1989population], species coexistence and ecosystem processes [@imura2003genetic; @Bolnick2011; @hart2016variation; @Sanderson2023].
-Higher physiological variance in a population may also indicate greater niche breadth which can buffer populations against environmental change (i.e., the portfolio effect) [@Bolnick2011; @Schindler2010; @Zheng2023; @Slatyer2013; @Sanderson2023].
-Changes in variance could, therefore, have wide-reaching consequences for understanding the capacity of populations to persist in and adapt to novel environments but to date there are few data testing the importance of variances in this context [@Scheiner2020].
+
+Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
+The focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
+As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted.
+NEED MORE ABOUT WHY VARIANCE NOT JUST IMPORTANCE
+
+Changes in variability of traits governing energy demand are expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+In addition, if phenotypic and genetic variation are correlated and traits are linked to fitness, changes in variation can limit responses to selection impacting a populations capacity to evolve [@Pelletier2012].
+Therefore, maintaining intrapopulation variability in physiological rates in a warmer world may be important for population resilience to climate change.
 
@@
 
-Overall, $lnRR_{Q_{10_{acclimation}}}$ was `r abs(mean(avg_change))`% lower than  $lnRR_{Q_{10_{acute}}}$ across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%).
+Capacity for acclimation depended on the habitat.
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
@@
 
-  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8, alpha = 0.4) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  p3a <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", xlab = TeX("$lnRR_{Q_{10}}$"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
   theme(legend.direction = "vertical") +
@@
 
-  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, k.pos = "none")  +
+  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8,  k.pos = "none")  +
               scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
@@
 Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
-Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater habitats as temperatures increase, with the decrease being particularly pronounced in terrestrial ectotherms (~28%).
+Here, acclimation responses ($lnRR_{Q_{10}}$) varied across habitats while relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater habitats as temperatures increase.
+Decreases in relative variance were particularly pronounced in terrestrial ectotherms (~28%).
 These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
@@
 ### ***Plasticity and relative variance in physiological rates do not differ between life stages***
-We show that early (juvenile) and late (adult) life stages exhibited similar acclimation capacities and changes in relative variance across habitats.
-The lack of differences we observed may be due to the fact that both juvenile and adult animals occupy similar ecological niches and thermoregulate in similar ways making physiological responses to temperature similar.
-It is possible that temperatures experienced earlier in development, for example egg or early larval stages, would show different patterns because early developmental constraints are known to affect how physiological systems respond later in life because of programmatic effects [@angilletta2009thermal; @noble2018developmental; @o2019developmental].
+Differences in plasticity is expected between different life-stages because of distinct patterns of mortality, habitat use and behaviour between early and late life history stages [@martin2015age; @stearns1976life].
+Age has also been shown to reduce the capacity for acclimation [e.g., see @rossi2019ageing].
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults while @rossi2019ageing show that older air-acclimated fish had a diminished scope for gill remodeling relative to younger fish in mangrove rivulus (*Kryptolebias marmoratus*).
+
+Despite these examples, more broadly, we show little difference between early and late life acclimation capacities and changes in relative variance across habitats in our data indicating that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
+The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar ecological niches with similar dispersal and thermoregulatory behaviors making physiological responses to temperature similar.
+It is possible that temperatures experienced earlier in development, for example egg or larval stages, exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
+Early developmental constraints are known to affect how physiological systems respond later in life because of programmatic effects [@angilletta2009thermal; @noble2018developmental; @o2019developmental], and as such, developmental conditions may also cascade to .
 Such effects would manifest in juveniles life-history stages
 
-environments are expected Life-history stages often occupy different ecological niches and exhibit different physiological responses, levels of plasticity, and patterns of mortality in response to temperature.
-As such, it is becoming increasingly important to understand how climate change will impact different life-history stages [@levy2015resolving; @petitgas2013impacts].
-Greater plasticity in early life stages of development is expected to be important to increase resilience to the effects of climate change because early life stages are often particularly vulnerable periods in development [@martin2015age; @stearns1976life].
-On average, our results show that early life stages are not more vulnerable to the impacts of climate change.
-However, our general meta-analytic findings do not imply that early life stages are not always less plastic, but that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-In contrast, @carter2020life showed greater thermal plasticity in metabolic rate for adults but little in pupae of *Onthophagus taurus*.
-Despite variation in the literature, very few studies measure multiple life-history stages within the same population.
-In future research, there needs to be more studies that explicitly compare differences in plasticity among life stages across multiple traits within the same population.
-
 ### ***No signature of past climate on capacity for physiological plasticity***
-Theoretical evolutionary models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] suggests that plasticity should be more likely to evolve in terrestrial environments.
-However, we did not find evidence of this effect, which is consistent with other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] (which we did not consider here).
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might then suggest that plasticity should be more likely to evolve in terrestrial environments.
+However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences].
+The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] (which we did not consider here).
+However, our results do contrast with comparative studies that show partial support for environmental variability being related to acclimation responses in aquatic habitats [@Seebacher2015-wi; ]
+
 Modelling correct microenvironments for over 200 species across such diverse habitats is challenging.
@@
 While it is unclear how these findings relate directly to acclimation because they integrate multiple forms of plasticity, they do suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@Leung2020; @hendry2016key].
-The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity.
+The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity, but it is unclear how this can be measured across diverse taxa at a biologically relevant spatial and temporal scale.
 
@@
 Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
-
 While we do not yet understand the relative contribution of environmental and genetic factors to variance changes, models could better decouple how different levels of heritability and total variance impact evolutionary and ecological predictions.
 Our meta-analysis now provides the opportunity to parameterise such models, and ensure they are better aligned with empirical findings.
+
 Many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
@@
 Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
+
+## Awknowledgements
+We would like to thank Malgorzata Lagisz for helping sort out the phylogeny used in our analysis.
+We are also grateful to three anonymous reviewers who all provided highly constructive feedback that greatly improved the manuscript.
 

### 2024-07-06 ms.qmd
Fixing up discussion of thermal variability and also life stages

@@
 
-Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to proximate environmental conditions making it the first ‘line-of-defense’ against rapid environmental change [@Dewitt1998; @Scheiner2020].
+Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to proximate environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998; @Scheiner2020].
 For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
 Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
+Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
 Acclimation alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
@@
 
-Phenotypic plasticity is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect the extent of plasticity of organisms within these habitats to vary.
-Species occupying terrestrial habitats often show weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
-Marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
-
-Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
-The focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
-As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted.
-NEED MORE ABOUT WHY VARIANCE NOT JUST IMPORTANCE
+Reversible forms of phenotypic plasticity, such as acclimation, are expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect organisms within these habitats to vary in their capacity for plastic adjustments in physiology.
+Species occupying terrestrial habitats have been shown to exhibit weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
+In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
+However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
+
+As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted. NEED MORE ABOUT WHY VARIANCE NOT JUST IMPORTANCE
 
@@
 As such, positive effect sizes suggest that the mean or relative variance is larger at the higher of the two temperatures (numerator) when standardized to 10&deg;C.
-
-#### *Assumptions of $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-
-$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
-While this is likely in our data given that we restricted our analysis of $Q_{10}$ to standard operating temperatures for a given species, it may not always be satisfied given the diversity of species in our dataset.
-$Q_{10}$ [@van1884etudes] has been used exstensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi].
-However, there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model thermal effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
-While debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence it is important to recognise that both BA and $Q_{10}$ can exhibit curvilinearity as temperatures increase (as discussed in [@michaletz2024hotter]).
-@white2012information also showed that the BA model may not always perform better.
-For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better fit to metabolic rate data than the BA relationship [@white2012information].
-Given that studies included in our analysis never measured full performance curves at acute and acclimation temperatures it was not possible for us to compare different models of thermal dependence.
-Nonetheless, $Q_{10}$-based effect sizes remain the most practical effect-size for comparing thermal dependence when using existing empircial data, with the benefit that these effects having convenient properties that make them suitable for meta-analysis.
-Nonetheless, we control for possible violations of the log-linearity assumption in our analyses (see below).
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear (see *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below).
 
@@
 
-In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated.
-We predicted that, if $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we would see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated ([@fig-concept]; and see Supplementary Materials).
+We predicted that, if $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ were not strictly log-linear than we would see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
 The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
@@
 For example, terrestrial ectotherms may rely on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range necessary to operate in more variable thermal environments [@angilletta2009thermal].
-Acclimation responses in marine and freshwater organisms would also result in the maintenance, or even increase, in variance at higher temperatures due to the expression of alternative enzymes that function more effectively at higher temperatures.
+Acclimation responses in marine and freshwater organisms may also themselves buffer / maintain variance in physiological rates at higher temperatures due to the expression of alternative enzymes that function more effectively at higher temperatures.
 Given that biochemical traits in marine and freshwater organisms acclimated, and their relative variance increased in freshwater after acclimation, this seems plausible.
@@
 ### ***Plasticity and relative variance in physiological rates do not differ between life stages***
-Differences in plasticity is expected between different life-stages because of distinct patterns of mortality, habitat use and behaviour between early and late life history stages [@martin2015age; @stearns1976life].
-Age has also been shown to reduce the capacity for acclimation [e.g., see @rossi2019ageing].
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults while @rossi2019ageing show that older air-acclimated fish had a diminished scope for gill remodeling relative to younger fish in mangrove rivulus (*Kryptolebias marmoratus*).
-
-Despite these examples, more broadly, we show little difference between early and late life acclimation capacities and changes in relative variance across habitats in our data indicating that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
-The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar ecological niches with similar dispersal and thermoregulatory behaviors making physiological responses to temperature similar.
-It is possible that temperatures experienced earlier in development, for example egg or larval stages, exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
-Early developmental constraints are known to affect how physiological systems respond later in life because of programmatic effects [@angilletta2009thermal; @noble2018developmental; @o2019developmental], and as such, developmental conditions may also cascade to .
-Such effects would manifest in juveniles life-history stages
+Acclimation capacities are expected to differ between life-stages because of distinct of patterns of dispersal, habitat use and behaviour that force earlier life stages to cope with more variable environmental conditions which can also lead to developmental constraints on how physiological systems respond later in life [@martin2015age; @stearns1976life; @angilletta2009thermal; @noble2018developmental; @o2019developmental; @Pottier2022].
+In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], and such costs can be magnified in late life reducing the capacity for plasticity [e.g., @rossi2019ageing].
+These processes can also result in changes to intrapopulation variation in physiological rates at higher temperatures but the direction of change between early and adult life stages is likely to depend on the costs of adjusting physiological processes, energy reserves at different life stages, and the extent to which early life experiences constraint plasticity.
+
+Despite these expectations, more broadly, we show little difference between early and late life acclimation capacities and little change in the relative variance in physiological rates across habitats.
+This may not be too surprising given that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
+The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar thermal niches with similar dispersal and thermoregulatory behaviors making physiological responses to temperature similar.
+It is possible that temperatures experienced earlier in development (e.g., egg or larval stages) exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
+Some empirical evidence supports this in insects.
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
+To date, however, there are few studies that have focused on how variability in responses change and we would encourage more empirical focus on this questions given the potential ecological and evolutionary implications.
 
@@
 Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might then suggest that plasticity should be more likely to evolve in terrestrial environments.
-However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences].
-The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] (which we did not consider here).
-However, our results do contrast with comparative studies that show partial support for environmental variability being related to acclimation responses in aquatic habitats [@Seebacher2015-wi; ]
-
-Modelling correct microenvironments for over 200 species across such diverse habitats is challenging.
-The lack of a relationship between physiological plasticity and environmental variability and predictability could be due to the fact that ectotherms simply seek out microhabitats that make their environment quite stable [@huey2012predicting].
-Therefore, it is possible that more fine-scale resolution of the habitats that organisms occupy will elucidate expected patterns.
-Randomly fluctuating environments have been suggested to select for reduced plasticity, particularly if plastic responses are costly and this has been demonstrated by a number of empirical studies [@Leung2020; @rescan2022experimental; @leung2023phenotypic].
-For example, using seed beetles (*Callosobruchus maculatus*), @hallsson2012selection showed that experimentally evolving populations under randomly fluctuating thermal conditions did not show any increase in plasticity, but had reduced plasticity.
-@Leung2020 also showed reduced plasticity in morphological traits of experimentally evolving algae populations (*Dunaliella salina*) when environments were less predictable [see also @leung2023phenotypic].
-While it is unclear how these findings relate directly to acclimation because they integrate multiple forms of plasticity, they do suggest that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@Leung2020; @hendry2016key].
-The fact that aquatic ectotherms did show a capacity to acclimate suggests that environmental predictability, which is expected to be higher in aquatic environments, may be more important than environmental variability in driving the evolution of plasticity, but it is unclear how this can be measured across diverse taxa at a biologically relevant spatial and temporal scale.
+Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity should be more likely to evolve in terrestrial environments.
+However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
+The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz].
+
+However, whether a populations capacity for physiological plasticity and the thermal variability (or predictability) it experiences are related has received more mixed results.
+We show no relationship between acclimation capacity and thermal variability in marine, freshwater and terrestrial habitats.
+Our results are consistent with @Gunderson2015-hz who show no relationship between plasticity in heat tolerance and latitude or thermal seasonality.
+However, other analyses on heat tolerance limits have found relationships between latitude (a proxy for seasonality) [@morley2019physiological] or measures of thermal variability [@verberk2024heat].
+@Seebacher2015-wi also found evidence that acclimation capacity is related to a populations thermal variability, however, relationships depended on the habitat and traits in question.
+Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological] or possibly the climate projections/models being used to quantify thermal variability.
+Modelling realistic microenvironments across such diverse taxa is challenging because it is unclear what the most appropriate spatial and temporal scale might be for specific taxa that is of evolutionary relevance.
 
@@
 
-Enhanced knowledge of how variation in physiological rates vary across populations and species and the degree to which they can be adjusted in response to the environment may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
+Enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
 While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations, as evidenced by wide prediction intervals.
-Nonetheless, changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
+Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial species-level and trait-level variance estimates.
+Nonetheless, quantitative measures on the changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
 While we do not yet understand the relative contribution of environmental and genetic factors to variance changes, models could better decouple how different levels of heritability and total variance impact evolutionary and ecological predictions.
@@
 Many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
-Particularly interesting questions include: How does a reduction in physiological rate variance change energy flow across trophic levels within communities?
-What are the biochemical, cellular, and physiological mechanisms that underlie reduced variance in physiological rates?
+Particularly interesting questions include: How do differences in physiological rate variance change energy flow across trophic levels within communities?
+What are the biochemical, cellular, and physiological mechanisms that underlie differences in physiological rate variance across habitats?
 Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?
 How much of the reduction in variance is driven by lower levels of genetic variance?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across all major ecosystems.
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across major ecosystems globally.
 
@@
 ```
+
+#### *Further discussions on the assumptions of $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
+
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
+While this is likely in our data given that we restricted our analysis of $Q_{10}$ to standard operating temperatures for a given species, it may not always be satisfied given the diversity of species in our dataset.
+$Q_{10}$ [@van1884etudes] has been used exstensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi].
+However, there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model thermal effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
+While debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence it is important to recognise that both BA and $Q_{10}$ can exhibit curvilinearity as temperatures increase (as discussed in [@michaletz2024hotter]).
+@white2012information also showed that the BA model may not always perform better.
+For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better fit to metabolic rate data than the BA relationship [@white2012information].
+Given that studies included in our analysis never measured full performance curves at acute and acclimation temperatures it was not possible for us to compare different models of thermal dependence.
+Nonetheless, $Q_{10}$-based effect sizes remain the most practical effect-size for comparing thermal dependence when using existing empircial data, with the benefit that these effects having convenient properties that make them suitable for meta-analysis.
+Nonetheless, we control for possible violations of the log-linearity assumption in our analyses.
 

### 2024-07-06 ms.qmd
Fixing up a few things. 7110 words for main text.

@@
 2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
-3) Are changes in plasticity or variance in physiological rates impacted by past climate history?
-4) How are means and variances in physiological rates expected to change under climate change?
+3) How does acclimation and changes in variance relate to different life-stages and types of traits, and does this depend on habitat?
+4) Are changes in plasticity or variance in physiological rates impacted by past climate history?
+5) How are means and variances in physiological rates expected to change under climate change?
 
@@
 
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and  $T_{2}$, respectively.
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and  $T_{2}$, respectively (@fig-concept A).
 
@@
 #### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-As indicated above, $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures.
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures (@fig-concept A).
 For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
@@
 For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes suggest that the mean or relative variance is larger at the higher of the two temperatures (numerator) when standardized to 10&deg;C.
-$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear (see *Supplementary Materials* for further discussion).
-We test and control for any violations of these assumptions in our analysis (see below).
+As such, positive effect sizes suggest that the mean (i.e., $lnRR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10&deg;C.
+Importantly, $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear (see *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below) (@fig-concept B).
 
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
+This included the duration of acclimation in days given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
@@
 While we explored differences across more detailed trait categories (see Supplemental Materials),  most traits could be categorised into two broad categories that included whole-organism measures (i.e., ‘cardiac’, ‘muscle’, ‘sprint’, ‘endurance’, ‘max MR’, ‘rest MR’; see Supplemental Materials for details), which all integrate a diversity of physiological and biochemical processes.
-The other major trait category included measures of enzymatic reaction rates (i.e., ‘metabolic enzyme’, ‘ATPase’, 'Proton Leak' and ‘OXPHOS’) which are more individualized biochemical processes.
+The other major trait category included measures of enzymatic reaction rates (i.e., ‘metabolic enzyme’, ‘ATPase’, 'Proton Leak' and ‘OXPHOS’) targeting specific biochemical processes.
 We expected that whole-organism traits would be more likely to maintain relative variation in physiological function because they are composed of a greater number of biochemical reactions and would be more likely to acclimate.
-We did not include traits that could not be categories into these two (i.e., ‘Other’).
+We did not include traits that could not be categorised into these two (i.e., ‘Other’).
 
@@
 
-To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
+To understand how climate is related to a species’ physiological acclimation abilities and changes in relative variance we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
 It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
@@
 We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
-For terrestrial species we estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
-We fit models using both air and soil temperature and found that the results were qualitatively similar.
-We therefore only present results for air temperature.
+For terrestrial species we also estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
+However, the results were qualitatively similar so we only present results for air temperature.
 
@@
 To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
-To estimate thermal predictability, we calculated the auto-regressive time lag across the entire dataset.
-Theoretical and empirical studies of plasticity evolution have emphasised the importance of both climate variability and predictability in plasticity evolution.
-
-Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability and predictability for the future.
+We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, we identifying biologically relevant lags for such diverse taxa is challenging.
+As such, we present a coarse analysis using this metric of thermal predictability in the *Supplemental Materials*.
+
+Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability into the future.
 We used the CanESM2 climate model (2005-2100) [vers.
@@
   fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A")
-  ggsave(fig3, filename = "./output/figures/fig3_r1.pdf", width = 21.88, height = 9)
-
-  fig3 <- magick::image_read("./output/figures/fig3_r1.pdf")
+  ggsave(fig3, filename = "./output/figures/fig3_r1.png", width = 21.88, height = 9)
+
+  fig3 <- magick::image_read("./output/figures/fig3_r1.png")
   fig3
@@
 
-Understanding acclimation capacity and how variation in physiological rates changes across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
+Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
 Here, acclimation responses ($lnRR_{Q_{10}}$) varied across habitats while relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater habitats as temperatures increase.
@@
 As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized.
-Future theoretical models, that vary both mean and variance, are needed to characterise the interplay between changes in mean and variance.
+Future theoretical models are needed to better understand the ecological and evolutionary consequences of changes in both mean and variance.
 
@@
 In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], and such costs can be magnified in late life reducing the capacity for plasticity [e.g., @rossi2019ageing].
-These processes can also result in changes to intrapopulation variation in physiological rates at higher temperatures but the direction of change between early and adult life stages is likely to depend on the costs of adjusting physiological processes, energy reserves at different life stages, and the extent to which early life experiences constraint plasticity.
-
+These processes can also result in changes to intrapopulation variation in physiological rates at higher temperatures but the direction of change between early and adult life stages is likely to depend on the costs of adjusting physiological processes, energy reserves at different life stages, and the extent to which early life experiences constrain plasticity.
 Despite these expectations, more broadly, we show little difference between early and late life acclimation capacities and little change in the relative variance in physiological rates across habitats.
 This may not be too surprising given that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
-The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar thermal niches with similar dispersal and thermoregulatory behaviors making physiological responses to temperature similar.
+The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar thermal niches, disperse to a similar extent and exhibit comparable thermoregulatory behaviors making physiological responses to temperature similar.
 It is possible that temperatures experienced earlier in development (e.g., egg or larval stages) exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
@@
 Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity should be more likely to evolve in terrestrial environments.
+Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity is more likely to evolve in terrestrial environments.
 However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
@@
 
-However, whether a populations capacity for physiological plasticity and the thermal variability (or predictability) it experiences are related has received more mixed results.
+Whether a populations capacity for physiological plasticity and the thermal variability (or predictability) it experiences are related has received more mixed results.
 We show no relationship between acclimation capacity and thermal variability in marine, freshwater and terrestrial habitats.
@@
 @Seebacher2015-wi also found evidence that acclimation capacity is related to a populations thermal variability, however, relationships depended on the habitat and traits in question.
-Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological] or possibly the climate projections/models being used to quantify thermal variability.
+Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological], different traits or possibly the fact that different climate projections/models are being used to quantify thermal variability.
 Modelling realistic microenvironments across such diverse taxa is challenging because it is unclear what the most appropriate spatial and temporal scale might be for specific taxa that is of evolutionary relevance.
@@
 While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial species-level and trait-level variance estimates.
+Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial species- and trait-level variance estimates.
 Nonetheless, quantitative measures on the changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
@@
 
-Many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
+Nonetheless, it is clear that many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
 Particularly interesting questions include: How do differences in physiological rate variance change energy flow across trophic levels within communities?
 What are the biochemical, cellular, and physiological mechanisms that underlie differences in physiological rate variance across habitats?
-Are reductions in variance in one trait associated with reductions in correlated traits, or do some traits increase while others decrease?
-How much of the reduction in variance is driven by lower levels of genetic variance?
+Are changes in variance in one trait associated with changes in other traits, or do some traits increase while others decrease?
+Are changes in physiological rate variance correlated with changes in genetic variation?
 Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across major ecosystems globally.

### 2024-07-06 ms.qmd
Extending the mean-variance models to all treatments because we actually need to know the relative scaling in each one to better understand lnCVR acute and acclimation.

@@
 if(rerun) {
+
+      r_11_m <- bf(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+      r_12_m <- bf(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+      r_21_m <- bf(log(r2.1_sd) ~ log(r2.1)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+      r_22_m <- bf(log(r2.2_sd) ~ log(r2.2)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+
+      mv_model_all <- brm(r_11_m + r_12_m + r_21_m + r_22_m + set_rescor(TRUE), 
+                          chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, 
+                          control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+       saveRDS(mv_model_all, file = "./output/models/mv_model_all")
+
       model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)

### 2024-07-07 ms.qmd
Re-render and just read reding

@@
 
-Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to proximate environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998; @Scheiner2020].
+Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998; @Scheiner2020].
 For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
@@
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
-Acclimation alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
+Acclimation therefore alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
 Acclimation, however, does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
@@
 Where, $R_{1}$ and  $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and  $T_{2}$, respectively.
-$R_{1}$ and $R_{2}$ can be taken from samples of organisms measured acutely at two temperatures or after having been acclimated at these same temperatures.
 Log transformation of this ratio makes the effect size normally distributed.
@@
 We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
-For terrestrial species we also estimated soil temperatures as this maybe more representative of microhabitat choice compared to air temperature.
-However, the results were qualitatively similar so we only present results for air temperature.
 
@@
 To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
-We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, we identifying biologically relevant lags for such diverse taxa is challenging.
+We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, identifying biologically relevant lags for such diverse taxa is challenging.
 As such, we present a coarse analysis using this metric of thermal predictability in the *Supplemental Materials*.
@@
 In all cases, frequentist and Bayesian models resulted in the same conclusions.
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
 We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
@@
 Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) has nearly identical $AIC_{c}$.
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
 As such, we used an intermediate value of p = 0.7.
@@
 Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz], which would make it more likely that terrestrial ectotherms would show a smaller acclimation $lnRR_{Q_{10}}$.
-To control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
+However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz].
+Nonetheless, to control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
 
@@
 
-#### *Modelling how climate change will impact on opportunity for selection*
-
-To understand the consequences of human-induced climate change on the potential to impact the opportunity for selection on physiological traits we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
+#### *Modelling how climate change will impact relative variance in physiological rates*
+
+To understand the consequences of human-induced climate change on the potential to impact relative variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
 We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
@@
 Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random effects (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
-While sampling standard error (or variance) could have been included in our model, @Nakagawa2022-gy suggested instead to use $\sqrt{1/ne}$ (and its square root) to avoid potential problems with using sampling error itself (see @Nakagawa2022-gy for a discussion).
+As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
 
@@
 There were no differences between $lnCVR_{Q_{10_{acute}}}$ and $lnCVR_{Q_{10_{acclimation}}}$.
-Reductions in variance were driven by slower increases in the variance in physiological rates relative to the mean with scaling relationships between log standard deviation and log mean all being smaller than 1 and varying across habitats (See Supplementary Materials).
+Reductions in variance were driven by slower increases in the variance in physiological rates as mean physiological rates increased with scaling relationships between log standard deviation and log mean all being smaller than 1 and varying across habitats (see Supplementary Materials; @tbl-slopes & @fig-mv).
 There was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
@@
 These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results uncover an hitherto unrecognised dynamic where the benefits of acclimation may be counteracted by a decrease in relative trait variance, which when considered along side acclimation capacity, change our understanding of how ectotherms across different habitats will be able to cope with increased temperatures.
+Our results uncover an hitherto unrecognised dynamic where the benefits of acclimation may be counteracted by shifts in trait variance impacting how ectotherm populations across different habitats will be able to cope with increased temperatures.
 
@@
 For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-To date, however, there are few studies that have focused on how variability in responses change and we would encourage more empirical focus on this questions given the potential ecological and evolutionary implications.
+A focus on collecting more detailed information on the differences in behaviour, dispersal and thermal environments experienced across different life stages is likely to provide a more complete picture on when plasticity differs across life stages.
+To date, however, there are few studies that have focused on how variability in responses change.
+We would also encourage more empirical focus on this questions given the potential ecological and evolutionary implications.
 
@@
 However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
-The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz].
+The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@hendry2016key; @Leung2020].
 
@@
 Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological], different traits or possibly the fact that different climate projections/models are being used to quantify thermal variability.
-Modelling realistic microenvironments across such diverse taxa is challenging because it is unclear what the most appropriate spatial and temporal scale might be for specific taxa that is of evolutionary relevance.
+Modelling realistic microenvironments across such diverse taxa is also challenging because it is unclear what the most appropriate spatial and temporal scale might be that is of evolutionary relevance.
+As such, it is also likely that historical temperature time series' are not representative of the selective environment a population has experienced making relationships between capacity for acclimation and temperature variability (or predictability) difficult to pin down.
 
@@
 While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial species- and trait-level variance estimates.
+Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial study- and trait-level variance estimates.
 Nonetheless, quantitative measures on the changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
@@
 
-More specifically, we performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
+We performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
 We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
@@
 #| label: fig-lnrrq10_temp
-#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and maximum temperature used in treatments within a study. Temperature is centered around the mean temperature in the data."
+#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and maximum temperature used in treatments within a study."
 
@@
 
-      model_mv1  <- brm(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
-      saveRDS(model_mv1, file = "./output/models/model_mv1")
-
-      model_mv2  <- brm(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait), chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, control = list(adapt_delta = 0.98), data = lnRRQ10_data)
-      saveRDS(model_mv2, file = "./output/models/model_mv2")
 } else {
-        model_mv1 <- readRDS("./output/models/model_mv1")
-        model_mv2 <- readRDS("./output/models/model_mv2")
+        mv_model_all <- readRDS("./output/models/mv_model_all")
 }
 
+# Post processing
+  model_mv1.1 <- posterior_samples(mv_model_all,  pars = "^b_logr11") # Acclimated at 1, measured at 1
+  model_mv1.2 <- posterior_samples(mv_model_all,  pars = "^b_logr12") # Acclimated at 1, measured at 2; Acute
+  model_mv2.2 <- posterior_samples(mv_model_all,  pars = "^b_logr22") # Acclimated at 2, measured at 2
+  model_mv2.1 <- posterior_samples(mv_model_all,  pars = "^b_logr21") # Acclimated at 2, measured at 1; Acute
+
+# Extract slopes
+    slope_extract <- function(x, v){
+        list = list()
+         list[['fresh']] <-  x[,2]  # Slope for freshwater
+        list[['marine']] <-  x[,2] + x[, grepl(":habitatm", colnames(x))] # Slope for marine
+         list[['terrs']] <-  x[,2] + x[, grepl(":habitatt", colnames(x))] # Slope for terrestrial
+         return(list)
+    }
+
+# From each model, lets get the slopes for each habitat
+         r1.1 <-  slope_extract(model_mv1.1)
+         r1.2 <-  slope_extract(model_mv1.2)
+         r2.1 <-  slope_extract(model_mv2.1)
+         r2.2 <-  slope_extract(model_mv2.2)
+
+# Summary
+         table <- data.frame(
+                               mean = do.call("rbind", lapply(r1.1,  mean)),
+                               L = do.call("rbind", lapply(r1.1,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r1.1,  function(x) quantile(x, 0.975))))
+
+         r_1.2 = data.frame( mean = do.call("rbind", lapply(r1.2,  mean)),
+                               L = do.call("rbind", lapply(r1.2,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r1.2,  function(x) quantile(x, 0.975))))
+         r_2.1 = data.frame(mean = do.call("rbind", lapply(r2.1,  mean)),
+                               L = do.call("rbind", lapply(r2.1,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r2.1,  function(x) quantile(x, 0.975))))
+          r_2.2 = data.frame(mean = do.call("rbind", lapply(r2.2,  mean)),
+                               L = do.call("rbind", lapply(r2.2,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r2.2,  function(x) quantile(x, 0.975))))
+
+          table <- rbind(table, r_1.2,  r_2.1, r_2.2)
+          table$habitat <- rep(c("Freshwater", "Marine", "Terrestrial"), 4)
+          table$type <- c(rep("r1.1",3),
+                          rep("r1.2", 3),
+                          rep("r2.1",3),
+                          rep("r2.2", 3))
+          rownames(table) <- NULL
+
+    table <- table %>% dplyr::select(type, habitat, mean, X2.5., X97.5.) %>% rename("2.5%" = X2.5.,
+                                                                                    "97.5%" = X97.5.,
+                                                                                    "Slope" = mean,
+                                                                                    "Treatment" = type,
+                                                                                    "Habitat" = habitat) %>% 
+      mutate(Type = ifelse(Treatment %in% c("r1.1", "r2.2"), "Acclimation", ifelse(Treatment %in% c("r1.2", "r2.1"), "Acute", " "))) %>% relocate(Type, .before = Treatment) %>% dplyr::arrange(Habitat)
 ```
@@
 Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
-Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases.
-Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (@tbl-slopes), however, ectotherms from terrestrial habitats had much shallower slopes than marine and freshwater ectotherms, particularly at higher treatment temperatures, indicating increased mean physiological rates generally do not result in higher between individual variance in physiological rates (@tbl-slopes).
+Interestingly, in marine ectotherms the slope was highest at cooler temperatures, wheeras the slope was suppressed when acclimated and/or measured at higher temperatures (i.e., r.1.
+compared to r1.2, r2.1, r2.2) (@tbl-slopes).
+In freshwater ectotherms, there we some differences in scaling relationships but they were all fairly comparable no matter what acclimatin and test temperature (@tbl-slopes).
 
@@
   p_mv
+```
+
+```{r, tbl-slopes}
+#| label: tbl-slopes
+#| tbl-cap: "Slopes and 95% credible intervals (lower = 2.5% and upper = 97.5%) of log transformed standard deviation (log(SD)) and log transformed mean (log(mean)) for each of the four treatment types (r1.1, r1.2, r2.1, r2.2).
+Note that r1.1 and r2.2 represent measurements of physiological rates of acclimated animals and measured at their respective acclimation temperature.
+In contrast, r1.2 and r2.1 are acute measurements.
+See Figure 1 in main manuscript for full details on treatments."
+
+flextable(table) %>% bold(part = "header") %>% autofit()
 ```

### 2024-07-07 ms.qmd
Re-read and revised a few sections

@@
   tbl-prefix: "Table"
+editor: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-<p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
+<p style="text-align: center;">
+
+Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^, Alex Bush^4^, Frank
+Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$
+
+</p>
 
 ## Affiliations:
-^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
-^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
-^3^ School of Life and Environmental Sciences, University of Sydney, Sydney, NSW 2006, Australia  &NewLine;  
-^4^ Department of Biology, Lancaster University, Liverpool, UK &NewLine;  
-$\dagger$ contributed equally &NewLine;  
-$\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;
+
+^1^ Division of Ecology and Evolution, Research School of Biology, The
+Australian National University, Canberra, ACT 2600, Australia
+\
+^2^ Ecology and Evolution Research Centre, School of Biological, Earth
+and Environmental Sciences, University of New South Wales, Sydney, NSW,
+Australia
+\
+^3^ School of Life and Environmental Sciences, University of Sydney,
+Sydney, NSW 2006, Australia
+\
+^4^ Department of Biology, Lancaster University, Liverpool, UK
+\
+$\dagger$ contributed equally
+\
+$\ddagger$ corresponding author, daniel.noble\@anu.edu.au
 
@@
 
-Climate change is expected to result in warmer and more variable thermal environments globally.
-Maintaining variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
-Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
-We developed effect size estimates that quantify how physiological rate variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
-We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures driven by the lower proportional increase in physiological rate variance relative to the mean.
-Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
-Marine organisms also acclimated, but plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
-Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
-Our results show that, while there are weak acclimation responses in some habitats (marine and freshwater), such responses may trade-off with reductions in relative physiological rate variance that may have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+Climate change is expected to result in warmer and more variable thermal
+environments globally. Maintaining variability in physiological rates
+and adjusting them in response to extreme temperatures (plasticity) is
+essential for allowing populations to adapt to climate change. Yet,
+incorporating both plasticity and changes in phenotypic variation when
+predicting the impacts of climate change on populations is often
+ignored. We developed effect size estimates that quantify how
+physiological rate variance changes relative to the mean as temperature
+increases, which we refer to as 'relative variance'. We show by
+meta-analysing \>1900 effects from 226 species that relative variance in
+physiological rates decreases at higher temperatures driven by the lower
+proportional increase in physiological rate variance relative to the
+mean. Freshwater ectotherms are capable of acclimating and have the
+smallest reductions in relative variance. Marine organisms also
+acclimated, but plasticity traded-off with a reduction in relative
+variance in physiological rates at higher temperatures. Relative
+variance reductions were particularly pronounced for terrestrial
+ectotherms, and this coincided with a lack of capacity for acclimation,
+highlighting the vulnerability of terrestrial ectotherms to climate
+change. Our results show that, while there are weak acclimation
+responses in some habitats (marine and freshwater), such responses may
+trade-off with reductions in relative physiological rate variance that
+may have important evolutionary and ecological ramifications that affect
+our understanding of how climate change will impact populations now and
+in the future.
 
@@
 
-Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
-Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
-
-Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998; @Scheiner2020].
-For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
-Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
-Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
-Acclimation therefore alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
-Acclimation, however, does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
-
-Reversible forms of phenotypic plasticity, such as acclimation, are expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect organisms within these habitats to vary in their capacity for plastic adjustments in physiology.
-Species occupying terrestrial habitats have been shown to exhibit weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
-In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
-However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
-
-As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted. NEED MORE ABOUT WHY VARIANCE NOT JUST IMPORTANCE
-
-Changes in variability of traits governing energy demand are expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-More variable populations, genetically and/or phenotypically, are predicted to be associated with broader niches, reduced intraspecific competition, increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-In addition, if phenotypic and genetic variation are correlated and traits are linked to fitness, changes in variation can limit responses to selection impacting a populations capacity to evolve [@Pelletier2012].
-Therefore, maintaining intrapopulation variability in physiological rates in a warmer world may be important for population resilience to climate change.
-
-Here, we use meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We then developed new effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
-2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
-3) How does acclimation and changes in variance relate to different life-stages and types of traits, and does this depend on habitat?
-4) Are changes in plasticity or variance in physiological rates impacted by past climate history?
-5) How are means and variances in physiological rates expected to change under climate change?
+Climate change is expected to result in warmer but also more variable
+thermal environments globally [@Suarez2023; @Easterling2000;
+@Ummenhofer2017]. Greater thermal variability is predicted to result in
+strong selection pressures that lead to genetic adaptation and/or the
+evolution of adaptive phenotypic plasticity -- both of which are
+considered important for population resilience to contemporary
+human-induced climate change [@Seebacher2015-wi; @Merila2014;
+@Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can;
+@cooke2021one]. Without plasticity or adaptation, high extinction rates
+are expected unless organisms can migrate to track suitable habitats
+[@Cahill2012; @Nunney2016].
+
+Reversible phenotypic plasticity, such as physiological acclimation, is
+relatively rapid and can be fine-tuned to environmental conditions
+making it the first ‘line-of-defense’ against environmental change
+[@Dewitt1998; @Scheiner2020]. For example, physiological rates are known
+to speed up as temperature increases because of the thermodynamic
+effects on chemical reaction rates -- so called 'acute' temperature
+responses (@fig-concept). Acute temperature increases that push
+organisms from their thermal optimum can be mitigated by plastically
+adjusting reaction rates in response to chronic temperatures through
+acclimation [@Seebacher2015-wi; @Havird2020-mj]. Physiological
+acclimation is driven by endocrine and epigenetic processes that change
+the underlying physiology to allow organisms to maintain physiological
+performance around a fitness optimum despite changes in the environment
+[@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
+Acclimation therefore alters acute thermal sensitivity to offset the
+potentially negative effects of acute temperature changes (e.g., higher
+energetic demands). Acclimation, however, does not normally result in
+physiological rates returning to their original state (‘complete’
+compensation - *sensu* @huey1999testing), but rather are only partially
+compensated [@huey1999testing; @Havird2020-mj].
+
+Reversible forms of phenotypic plasticity, such as acclimation, are
+expected to evolve in populations when environmental variability is high
+but predictable and the costs of plasticity are low [@Chevin2017;
+@Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010]. Thermal variation
+and predictability are known to differ across habitats (terrestrial,
+marine and freshwater) [@steele2019comparison], and as such, we expect
+organisms within these habitats to vary in their capacity for plastic
+adjustments in physiology. Species occupying terrestrial habitats have
+been shown to exhibit weak acclimation abilities, and so, are likely to
+be particularly vulnerable to climate change given their greater
+probability of experiencing thermal extremes that overwhelm
+physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz;
+@hoffmann2013upper; @morley2019physiological]. In contrast, marine and
+freshwater habitats appear to have greater physiological acclimation
+capacity [e.g., @Seebacher2015-wi; @Pottier2022]. However, the focus of
+research up to now has been primarily on mean physiological responses
+neglecting how variability in physiological rates might also be impacted
+at higher temperatures.
+
+As mean physiological rates increase with temperature there is reason to
+believe that the intrapopulation variability might also be impacted.
+NEED MORE ABOUT WHY VARIANCE IS EXPECTED TO CHANGE!
+
+Changes in variability of traits governing energy demand are expected to
+have important consequences on the flow of energy within and between
+populations, communities, and ecosystems [@hendry2016key;
+@seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+More variable populations, genetically and/or phenotypically, are
+predicted to be associated with broader niches, reduced intraspecific
+competition, increased growth rate, decreased vulnerability to
+environmental change and lower extinction risk [@forsman2015rethinking;
+@forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+In addition, if phenotypic and genetic variation are correlated and
+traits are linked to fitness, changes in variation can limit responses
+to selection impacting a populations capacity to evolve
+[@Pelletier2012]. Therefore, maintaining intrapopulation variability in
+physiological rates in a warmer world may be important for population
+resilience to climate change.
+
+Here, we use meta-analysis to re-evaluate the degree to which aquatic
+and terrestrial ectotherms are capable of physiological plasticity. We
+then developed new effect sizes to quantify how variance in
+physiological rates change with temperature to ask the following
+questions: 1) How much is variance in physiological rates expected to
+change, if at all, as temperatures rise? 2) Are temperature effects on
+plastic adjustments in physiological rates larger than changes in
+variance across aquatic and terrestrial ectotherms? 3) How does
+acclimation and changes in variance relate to different life-stages and
+types of traits, and does this depend on habitat? 4) Are changes in
+plasticity or variance in physiological rates impacted by past climate
+history? 5) How are means and variances in physiological rates expected
+to change under climate change?
 
 ## **Materials and Methods**
+
 ### *Literature collection*
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-For full details on the search protocol see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
+
+We compiled literature on ectothermic animals that measured
+physiological rates (e.g., metabolic rate) at two or more temperatures
+after having been acclimated (or acclimatized) at these temperatures. We
+used data from a previous meta-analysis [@Seebacher2015-wi] and updated
+@Seebacher2015-wi's data by extracting data from suitable studies from
+our own searches that followed the same search protocol. For full
+details on the search protocol see the *Supplementary Materials*, where
+we also provide a PRISMA flow diagram of our extraction process
+(@fig-prisma).
 
@@
 
-We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
-If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
-We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
-We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
-For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
-If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
-If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
-When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
-
-### *$Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances*
-
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
-Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+We extracted means, standard deviations, and sample sizes for
+physiological rates at the two test temperatures. If there were more
+than two test temperatures, we chose only the test temperatures that
+fell within the most likely natural range of temperatures experienced by
+the species in question. We extracted these data from text, tables or
+figures of a given paper. Data were extracted from figures using the R
+package *metaDigitise* [@Pick2019-mg]. We also recorded the phylum,
+class, order, genus and species, and the latitude and longitude from
+where the experimental animals were sourced. For studies that did not
+provide latitude and longitude for the population, we searched for
+similar studies by the same lab group to identify where the population
+was likely to have been sourced. If the experimental animals were
+derived from the wild, we recorded the nearest latitude and longitude of
+the field collection site. If the animals were sourced from a commercial
+supplier, we took the latitude and longitude of the supplier. When it
+was not possible to find latitude and longitude using these methods, we
+looked up the distribution of the species in question and took the
+latitude and longitude of the centroid of the species' distributional
+range.
+
+### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
+
+Following @Noble2022-ty we calculated a series of temperature-corrected
+effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as
+well as the variability in physiological rates ($lnVR_{Q_{10}}$ and
+$lnCVR_{Q_{10}}$) (@fig-concept). These effect sizes are similar to the
+traditional temperature coefficient ($Q_{10}$), but with formal
+analytical approximations of their sampling variances. Sampling
+variances for effect sizes allowed us to make use of traditional
+meta-analytic modelling approaches.
 
@@
 
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+To compare mean physiological rates, we calculated the log $Q_{10}$
+response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
 
@@
 
-Where, $R_{1}$ and  $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and  $T_{2}$, respectively.
-Log transformation of this ratio makes the effect size normally distributed.
-@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
-The sampling variance for @eq-lnq10 can be computed as follows (as described in @Noble2022-ty):
+Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures
+$T_{1}$ and $T_{2}$, respectively. Log transformation of this ratio
+makes the effect size normally distributed. @eq-lnq10 is essentially a
+temperature corrected equivalent to the log response ratio (lnRR)
+[@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator
+are measured at different temperatures. This allows comparisons of the
+means from two temperature treatments directly regardless of the
+absolute measurement temperatures. The sampling variance for @eq-lnq10
+can be computed as follows (as described in @Noble2022-ty):
 
@@
 
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and  $T_{2}$, respectively (@fig-concept A).
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$
+and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and
+$T_{2}$, respectively (@fig-concept A).
 
 #### *Comparing variance in physiological rates*
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that
+allow for comparisons of changes in variance between two groups, the log
+variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in
+trait variability between two groups. We refer readers to
+@Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but
+these can easily be extended to their $Q_{10}$ analogues (and associated
+sampling variance) as follows:
 
@@
 lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$${#eq-lnq10VR}
-$$
+$$ {#eq-lnq10VR} $$
 s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
@@
 
- @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10&deg;C temperature change along with its sampling variance (@eq-slnq10VR).
-While this is a useful metric, as discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship that needs to be accounted for in analysing changes in variance.
-As such, we calculated the coefficient of variation, which standardizes changes in variance for changes in means as follows:
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate
+variance (@eq-lnq10VR) across a 10°C temperature change along with its
+sampling variance (@eq-slnq10VR). While this is a useful metric, as
+discussed by @Nakagawa2015-fo there is often a strong mean-variance
+relationship that needs to be accounted for in analysing changes in
+variance. As such, we calculated the coefficient of variation, which
+standardizes changes in variance for changes in means as follows:
 
@@
 lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR}
-$$
+$$ {#eq-lnq10CVR} $$
 s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
@@
 
-where $CV$ is the coefficient of variation defined as $SD / R$. We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-
-#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures (@fig-concept A).
-For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
-For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes suggest that the mean (i.e., $lnRR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10&deg;C.
-Importantly, $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear (see *Supplementary Materials* for further discussion).
-We test and control for any violations of these assumptions in our analysis (see below) (@fig-concept B).
+where $CV$ is the coefficient of variation defined as $SD / R$. We refer
+to $lnCVR_{Q_{10}}$ as relative variance because variance changes are
+relative to the mean.
+
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
+
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from
+samples of organisms measured acutely at two temperatures or after
+having been acclimated these same temperatures (@fig-concept A). For
+studies that measure acute and acclimated responses we used the mean,
+standard deviation, and sample size to derive both acute and acclimation
+$lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates. For
+studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$
+acutely we could only calculate acute versions of these effect size
+estimates. For all effect sizes the higher temperature was in the
+numerator and the lower of the two temperatures in the denominator. As
+such, positive effect sizes suggest that the mean (i.e.,
+$lnRR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger
+at the higher of the two temperatures (numerator) when standardized to
+10°C. Importantly, $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and
+$lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the
+effect of temperature on physiological rates (or changes in relative
+variance) is log-linear (see *Supplementary Materials* for further
+discussion). We test and control for any violations of these assumptions
+in our analysis (see below) ([@fig-concept]B).
 
@@
 
-We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-This included the duration of acclimation in days given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
-While we explored differences across more detailed trait categories (see Supplemental Materials),  most traits could be categorised into two broad categories that included whole-organism measures (i.e., ‘cardiac’, ‘muscle’, ‘sprint’, ‘endurance’, ‘max MR’, ‘rest MR’; see Supplemental Materials for details), which all integrate a diversity of physiological and biochemical processes.
-The other major trait category included measures of enzymatic reaction rates (i.e., ‘metabolic enzyme’, ‘ATPase’, 'Proton Leak' and ‘OXPHOS’) targeting specific biochemical processes.
-We expected that whole-organism traits would be more likely to maintain relative variation in physiological function because they are composed of a greater number of biochemical reactions and would be more likely to acclimate.
-We did not include traits that could not be categorised into these two (i.e., ‘Other’).
+We recorded or derived a series of moderator variables from each study
+that are expected to have an impact on our effect size estimates. This
+included the duration of acclimation in days given that acclimation
+responses are expected to depend on how long chronic temperature
+exposure occurs (longer exposure = better acclimation response)
+[@Seebacher2015-wi]. We also recorded if the sample of animals were
+derived from captive or wild stocks, the life-history stage of the
+animals used ("adult" or "juvenile") and the habitat type ("freshwater",
+"marine" or "terrestrial") given that @Seebacher2015-wi show that these
+factors can impact $Q_{10}$ estimates. Physiological rate measures
+varied widely across the studies but could generally be grouped into
+discrete trait categories [@Seebacher2015-wi]. While we explored
+differences across more detailed trait categories (see *Supplemental
+Materials* for details on the types of traits), most traits could be
+categorised into two broad categories that included whole-organism
+measures, which all integrate a diversity of physiological and
+biochemical processes, and biochemical processes (e.g., enzyme reaction
+rates, proton leak). Traits that could not be categorised into these two
+we classified as ‘Other’.
 
@@
 
-To understand how climate is related to a species’ physiological acclimation abilities and changes in relative variance we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
-It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
-Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
-
-Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01&deg; resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25&deg; resolution) using the *ncdf4* R package [vers.
-`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
-We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
-
-Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
-To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
-We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, identifying biologically relevant lags for such diverse taxa is challenging.
-As such, we present a coarse analysis using this metric of thermal predictability in the *Supplemental Materials*.
-
-Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections and calculated thermal variability into the future.
-We used the CanESM2 climate model (2005-2100) [vers.
-1.2.0; @koen_hufkens_2019_2647541] under a high emissions scenario (RCP8.5).
+To understand how climate is related to a species’ physiological
+acclimation abilities and changes in relative variance we used the
+coordinates reported by each study to extract temperature data from
+terrestrial and aquatic environments. It was unclear whether climate at
+the locations of captive reared organisms would be representative of a
+population's climate history - particularly for species reared under
+captive condition for many generations. Given that we were interested in
+understanding climate driven effects on acclimation capacity we only
+used studies on wild populations for climate analyses.
+
+Monthly average temperature data were extracted from the ERA5 climate
+model, available from the Copernicus climate data store
+[@Hersbach2020-hx]. For each population and species in the dataset we
+extracted a 72-year period (1950-2022) of either surface air temperature
+(0.01° resolution) for both terrestrial and freshwater taxa, or sea
+surface temperature for the marine taxa (at 0.25° resolution) using the
+*ncdf4* R package [vers. `r utils::packageVersion("ncdf4")`,
+@Pierce2021-lc]. We chose surface temperature because we believed that
+it was more likely to reflect the micro-thermal environment experienced
+by terrestrial and freshwater ectotherms at those locations.
+
+Using the thermal time-series data for each location we calculated
+metrics of thermal variability across months and years as well as
+estimates of thermal predictability (i.e., autocorrelation). To estimate
+thermal variability, we calculated the coefficient of variation
+($\frac{SD}{M}$, where SD = standard deviation in temperature and M =
+the mean temperature for each year). We also estimated thermal
+predictability, by calculating the auto-regressive time lag across
+months (i.e., a measure of how correlated temperatures were between
+months), however, identifying biologically relevant lags for such
+diverse taxa is challenging. As such, we present a coarse analysis using
+this metric of thermal predictability in the *Supplemental Materials*.
+
+Lastly, to illustrate the effects that climate warming could have on
+physiological rate variance we also extracted climate projections and
+calculated thermal variability into the future. We used the CanESM2
+climate model (2005-2100) [vers. 1.2.0; @koen_hufkens_2019_2647541]
+under a high emissions scenario (RCP8.5).
 
 ### *Meta-Analysis*
-We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
-We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021-ls; @nakagawaorchard].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
-In all cases, frequentist and Bayesian models resulted in the same conclusions.
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
-We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WAIC) (if Bayesian).
-We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
-If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.
+
+We analysed our data using multilevel meta-analytic (MLMA) and
+meta-regression (MLMR) models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms*
+[vers. `r utils::packageVersion("brms")` @Burkner2017-wg;
+@Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn]. We fit both
+Bayesian and frequentist approaches to ensure that our results were
+consistent, and to create orchard plots more easily [vers. 2.0,
+@Nakagawa2021-ls; @nakagawaorchard]. In addition, Bayesian methods
+better protect against type I errors in the presence of complex sources
+of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz]. In
+all cases, frequentist and Bayesian models resulted in the same
+conclusions. For our Bayesian models, we ran 4 MCMC chains, each with a
+warm-up of 1000 followed by 4000 sampling iterations keeping every 5
+iterations for a minimum of 3200 samples from the posterior
+distribution. We used flat Gaussian priors for 'fixed' effects (i.e.,
+$N(0, 10)$) and a student t-distribution for 'random' effects (i.e.,
+$student_{t}(3, 0, 10)$). We checked that all MCMC chains were mixing
+and had converged (i.e., $R_{hat} = 1$). We compared any competing
+models using Akaike's Information Criteria (AIC) (if frequentist) or
+Wantabe Information Criteria (WAIC) (if Bayesian). We deemed models with
+the lowest IC value to be best supported if there was a $\Delta IC$
+between the competing models of 2 or more. If two models were within 2
+$\Delta IC$ units we went with the most parsimonious model.
 
 #### *Multi-level Meta-analysis (MLMA) Models*
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
-We refer to this model structure as “Model 1” in the results.
-Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
-We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
-`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
-`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
-We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
-As such, we used an intermediate value of p = 0.7.
-We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
-`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+
+We first fit multi-level meta-analysis (MLMA) models (i.e.,
+intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$,
+that included study, species, trait type, and phylogeny as random
+effects to account for non-independence and identify sources of
+variability. We refer to this model structure as “Model 1” in the
+results. Our MLMA models allowed us to partition the variation in
+$lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while
+accounting for total sampling variance in each. This allowed us to
+calculate the proportion of total heterogeneity [i.e., $I_{total}^2$;
+*sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$
+metrics describing the proportion of variance explained by each random
+effect level [@Nakagawa2012-oc]. We also present 95% prediction
+intervals which describe the expected distribution of effects from
+future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the
+*rotl* package in R (vers. `r utils::packageVersion("rotl")`)
+[@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj]. We resolved all
+polytomies in the tree. Any missing taxa were replaced with closely
+related species and branch lengths were computed using Grafen's method
+[using power = 0.7, @Grafen1989-pr]. Models fit using correlation
+matrices computed with different power (p) parameters (from 0.5 – 1.0)
+had nearly identical $AIC_{c}$. As such, we used an intermediate value
+of p = 0.7. We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools*
+(vers. `r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune
+the tree for individual analyses and calculate phylogenetic covariance
+(or correlation) matrices used in meta-analytic models.
 
@@
 
-After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
-In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz].
-Nonetheless, to control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models.
-
-In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated ([@fig-concept]; and see Supplementary Materials).
-We predicted that, if $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ were not strictly log-linear than we would see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
-To improve model interpretation, we also mean-centered the maximum temperature and included it in our models.
-
-With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23$^\circ C$) across the dataset.
-
-We first tested the degree to which the difference in acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine).
-Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10&deg;C differ depending on whether acute or acclimation responses are measured.
-
-Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
-We also explored how acute and acclimation effects varied across more detailed trait categories, and these results can be found in the *Supplementary Materials*.
-Given that residual variance appeared to differ across trait categories we fit heteroscedastic residual variance models which were better supported in all cases ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = 12).
-
-Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
-We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g., @moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
-
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnCVR_{Q_{10}}$ were predicted by a populations climate variability (CV).
-We only used $lnRR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on the plastic adjustments to physiological rates.
-We used all $lnCVR_{Q_{10}}$ data because there were no differences between $lnCVR_{Q_{10_{acclimation}}}$ and $lnCVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe climate would impact acclimation and acute $lnCVR_{Q_{10}}$ differently.
-To test how climate variability impacted mean effect size in wild populations we fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators while controlling for acclimation time and maximum temperature used in the experiments (referred to as "Model 5").
-We also explored how environmental predictability, as measured by how correlated successive temperatures at a given location were across months, might also explain capacity for acclimation.
-However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report on these results for a single lag (1 month) in the *Supplementary Materials* but note they do not differ from CV analyses.
+After quantifying levels of heterogeneity, we fit a series of
+multi-level meta-regression (MLMR) models to test our key questions. In
+all models, we included the same random effects as we used in our MLMA
+models. Acclimation time varied from
+`r range(data_wide$acclim_period, na.rm = TRUE)[1]` to
+`r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD
+= `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$
+`r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial
+ectotherms were acclimated for a much shorter duration (mean $\pm$ SD =
+`r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n =
+`r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD =
+`r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n =
+`r acclim_time[1,4]`) and marine species (mean $\pm$ SD =
+`r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n =
+`r acclim_time[2,4]`). However, rates of acclimation have been shown to
+be faster for many terrestrial groups compared to aquatic organisms
+\[e.g., amphibians and reptiles have faster rates of acclimation than
+fishes; See @Einum2023-lz\]. Nonetheless, to control for these possible
+differences, acclimation time was mean-centered (mean = 0) and included
+in all our models, though it was not a strong predictor of effect size
+variation (*Supplementary Materials*, @fig-accl_time).
+
+In addition to acclimation, all our models corrected for the possibility
+of the log-linearity assumption of our effect sizes being violated
+([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp). We
+predicted that, if $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ were not
+strictly log-linear than we would see a decrease in average effect size
+for studies applying higher temperature treatments because these
+temperatures are expected to either converge on or cross the thermal
+optima of the performance curve causing reaction rates to decelerate or
+decrease beyond $T_{op}$ [@michaletz2024hotter]. The benefit of such an
+approach means that we could still take advantage of the excellent
+properties of $Q_{10}$ as an effect size while statistically correcting
+for the potential non-linearity that would be expected in the data at
+high treatment temperatures. Given that our data included a wide range
+of species and habitats, we also included a random slope of maximum
+temperature that varied across species because we, *a priori*, expected
+that each species will vary in their thermal performance curve and the
+chosen temperatures experimentally manipulated along the performance
+curve. To improve model interpretation, we also mean-centered the
+maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our
+models we proceeded to build separate models that tested our core
+questions. All estimates from our models are therefore conditioned on an
+average level of acclimation time (i.e.,
+`r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum
+temperature (i.e., 23$^\circ C$) across the dataset.
+
+We first tested the degree to which the difference in acute and
+acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by
+habitat type (i.e., terrestrial, freshwater, and marine). Models
+included an interaction between effect type (i.e., acute or acclimation)
+and habitat (referred to as “Model 2”). Reduced mean
+$lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$
+indicates that acclimation to thermal environments results in partial
+compensation of physiological rates (i.e., phenotypic plasticity),
+whereas no differences between $lnRR_{Q_{10_{acute}}}$ and
+$lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of
+physiological plasticity [@Havird2020-mj; @Seebacher2015-wi]. In
+contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to
+$lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual
+variation in physiological rates across 10°C differ depending on whether
+acute or acclimation responses are measured.
+
+Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and
+$lnCVR_{Q_{10}}$ differed between whole-organism versus biochemical
+traits across habitats by fitting an model with an interaction between
+type, habitat and trait category (referred to as "Model 3"). We also
+explored how acute and acclimation effects varied across more detailed
+trait categories, and these results can be found in the *Supplementary
+Materials*. Given that residual variance appeared to differ across trait
+categories we fit heteroscedastic residual variance models which were
+better supported in all cases ($\Delta AIC_{c}$; marine = 58, freshwater
+= 120, and terrestrial = 12). We expected that whole-organism traits
+would be more likely to maintain relative variation in physiological
+function and be less likely to acclimate because whole-organism function
+relies on a greater number of biochemical reactions each with different
+thermal sensitivies [@fields2001protein; @angilletta2009thermal].
+
+Third, we tested whether different life-stages were more or less likely
+to acclimate by fitting a model for each habitat type and including an
+interaction between life-stage ('adult' or 'juvenile') and effect type
+(referred to as "Model 4"). We predicted that acclimation responses
+would be more likely early in development compared to later in
+development as this pattern has been shown in previous studies [e.g.,
+@moghadam2019heat], but that this should depend on the habitat type
+given the different constraints faced by different early life stages
+across major habitat types.
+
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$
+and $lnCVR_{Q_{10}}$ were predicted by a populations climate variability
+(CV). We only used $lnRR_{Q_{10_{acclimation}}}$ for these models
+because our predictions were specifically focused on the plastic
+adjustments to physiological rates. We used all $lnCVR_{Q_{10}}$ data
+because there were no differences between $lnCVR_{Q_{10_{acclimation}}}$
+and $lnCVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe
+climate would impact acclimation and acute $lnCVR_{Q_{10}}$ differently.
+To test how climate variability impacted mean effect size in wild
+populations we fit models that included an interaction between habitat
+type and thermal coefficient of variability (CV) as moderators while
+controlling for acclimation time and maximum temperature used in the
+experiments (referred to as "Model 5"). We also explored how
+environmental predictability, as measured by how correlated successive
+temperatures at a given location were across months, might also explain
+capacity for acclimation. However, such analyses are challenging to
+interpret because the temporal scale that is biologically relevant to
+different organisms will be different making the choice of lag to
+estimate the correlation difficult to apply across taxa. As such, we
+report on these results for a single lag (1 month) in the *Supplementary
+Materials* but note they do not differ from CV analyses.
 
@@
 
-To understand the consequences of human-induced climate change on the potential to impact relative variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
-We assumed that any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
-Our model included random effects of species, trait, phylogeny and study.
-We predicted the expected change in $lnCVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
-To do this, we first converted the predicted $lnCVR_{Q_{10}}$ to a 1&deg;C change as opposed to 10&deg;C as follows:
+To understand the consequences of human-induced climate change on the
+potential to impact relative variance in physiological rates we fit a
+model that included an interaction between acclimation type, habitat
+type, latitude and longitude (referred to as "Model 6"). We assumed that
+any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary
+by habitat type (i.e., an interaction between habitat). We used
+non-linear tensors for latitude and longitude as any response could be
+complicated by local factors (e.g., altitude). Our model included random
+effects of species, trait, phylogeny and study. We predicted the
+expected change in $lnCVR_{Q_{10}}$ for each wild population in our
+dataset at the specific populations latitude and longitude. To do this,
+we first converted the predicted $lnCVR_{Q_{10}}$ to a 1°C change as
+opposed to 10°C as follows:
 
@@
 
-@eq-lCVRpred turned the expected change across 10&deg;C to 1&deg;C.
-We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
+@eq-lCVRpred turned the expected change across 10°C to 1°C. We then
+multiplied this predicted change by the change in air and sea surface
+temperatures at the locations of each population (and species) that is
+expected under high emissions scenarios in 2080.
 
@@
 
-We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models  [@Nakagawa2022-gy].
-Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
+We explored the possibility for publication bias graphically using
+funnel plots, and more formally by including the square root of the
+inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression
+models [@Nakagawa2022-gy]. Funnel plot asymmetry may suggest a form of
+publication bias called the 'file-drawer' effect whereby low-powered
+studies are less likely to be published, however, graphical approaches
+do not account for sources of non-independence and high heterogeneity
+which can drive apparent funnel asymmetry [@Nakagawa2022-gy]. As such,
+we included $\sqrt{1/ne}$ as a moderator in a multi-level
+meta-regression model that accounted for all the random (i.e, study,
+species, trait) and fixed effects (acclimation time, type of effect,
+habitat, trait category and the interaction between habitat type and
+trait category) (referred to as "Model 7").
 
@@
 ### *Data Summary*
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
-The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
-However, on average they were in the same direction and only differed by ~10%.
-As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
-
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzyme rates ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+
+The final dataset included a total of
+`r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]`
+freshwater (fishes =
+`r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`,
+molluscs =
+`r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
+amphibians =
+`r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`,
+reptiles =
+`r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`,
+arthropods =
+`r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+and a single crustacean and nematode species),
+`r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]`
+marine (fishes =
+`r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`,
+annelids =
+`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`,
+molluscs =
+`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
+echinoderms =
+`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`,
+reptiles =
+`r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`,
+arthropods =
+`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+and a single crustacean and cnidarian species), and
+`r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]`
+terrestrial species (annelids =
+`r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`,
+molluscs =
+`r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
+arthropods =
+`r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+reptiles =
+`r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`
+and amphibians =
+`r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`
+along with a single tardigrade species) (@fig-phylo). We had more data
+on acute thermal responses (n =
+`r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`)
+compared to thermal responses after an acclimation period (n =
+`r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`)
+because acute responses were reported for each of the two acclimation
+temperatures (@fig-phylo). The two acute $lnRR_{Q_{10}}$ effect sizes
+([@fig-concept]A) differed significantly from each other ($\beta$ =
+`r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to
+`r quantile(change_acute, 0.975)`, $p_{MCMC}$ =
+`r p_value(pmcmc(change_acute))`) with animals acclimated to high
+temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ =
+`r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to
+`r quantile(hot_acute, 0.975)`, $p_{MCMC}$ =
+`r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`)
+compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`,
+95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to
+`r quantile(cold_acute, 0.975)`, $p_{MCMC}$ =
+`r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`)
+(@fig-Sacute). However, on average they were in the same direction and
+only differed by \~10%. As such, we averaged the two acute
+$lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
+
+Most of the effect size estimates came from measurements of metabolic
+rates (both resting and maximal -- $N_{species}$ =
+`r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`,
+$N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation
+effects together), metabolic enzyme rates ($N_{species}$ =
+`r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`,
+$N_{effects}$ =
+`r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`)
+and whole-organism performance traits (i.e., measures of speed and
+endurance -- $N_{species}$ =
+`r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`,
+$N_{effects}$ =
+`r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
 
@@
 
-Effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`% , 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
-All results are from Model 1 (see “Meta-Analysis” above).
-
-Capacity for acclimation depended on the habitat.
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]B).
-All results are from Model 2 (see “Meta-Analysis” above).
-
-Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; @fig-btrait A-C; and see Supplement [@fig-S2] for more detailed trait analysis).
-Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats (@fig-btrait B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms (@fig-btrait C).
-Unsurprisingly, neither broad trait category showed evidence of acclimation in terrestrial ectotherms (@fig-btrait A).
-
-Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles ("Model 4"; @fig-cvrlh A-C).
-When comparing between acute and acclimation responses between adults and juveniles there were also no differences across habitats (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
+Effect heterogeneity was high (only `r mean(tot_i2)`% of the variance
+was the result of sampling variability, 95% CI:
+`r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and
+most variance was explained by the specific study and type of trait
+(Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to
+`r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95%
+CI: `r quantile(trait_i2, 0.025)[1]` to
+`r quantile(trait_i2, 0.975)[1]`%). Evolutionary relationships among
+taxa and species ecology (i.e., species random effect) explained little
+variation in acute and acclimation responses (Species: `r mean(spp_i2)`%
+, 95% CI: `r quantile(spp_i2, 0.025)[1]` to
+`r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95%
+CI: `r quantile(phylo_i2, 0.025)[1]` to
+`r quantile(phylo_i2, 0.975)[1]`%). All results are from Model 1 (see
+“Meta-Analysis” above).
+
+Capacity for acclimation depended on the habitat. Ectotherms in marine
+and freshwater environments showed partial compensation of physiological
+rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of
+`r abs(mean(change_f))`% (95% CI:
+`r quantile(change_f, c(0.025, 0.975))[1]` to
+`r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and
+`r abs(mean(change_m))`% (95% CI:
+`r quantile(change_m, c(0.025, 0.975))[1]` to
+`r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In
+contrast, terrestrial ectotherms showed no acclimation (possibly even
+inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in
+$lnRR_{Q_{10_{acclimation}}}$ (95% CI:
+`r quantile(change_t, c(0.025, 0.975))[1]` to
+`r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]B). All results are
+from Model 2 (see “Meta-Analysis” above).
+
+Across habitats the extent to which whole-organism versus biochemical
+processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see
+Supplement, @fig-S2) for more detailed trait analysis). Biochemical
+processes were more effective at acclimating compared to whole-organism
+traits for ectotherms occupying marine habitats ([@fig-btrait]B),
+whereas both whole-organism and biochemical traits acclimated in
+freshwater ectotherms ([@fig-btrait]C). Unsurprisingly, neither broad
+trait category showed evidence of acclimation in terrestrial ectotherms
+([@fig-btrait]A).
+
+Acclimation capacity did not vary consistently by life-history stage
+with no differences between $lnRR_{Q_{10_{acclimation}}}$ and
+$lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine
+habitats where adults appeared to be able to acclimate to a greater
+extent, although the effect size was small and in the same direction and
+magnitude of juveniles ("Model 4"; [@fig-cvrlh]A-C). When comparing
+between acute and acclimation responses between adults and juveniles
+there were also no differences across habitats (Adult-Juvenile (Acute):
+`r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to
+`r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation):
+`r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]`
+to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(acclim_all_lh)`).
 
@@
 
-Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a decrease with increasing temperature across all habitat types, which was especially pronounced in terrestrial and marine ectotherms.
-The total proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to $lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI: `r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`), with most variation being driven by between-study and trait differences ("Model 1"; see Supplement  @fig-s3).
-There were no differences between $lnCVR_{Q_{10_{acute}}}$ and $lnCVR_{Q_{10_{acclimation}}}$.
-Reductions in variance were driven by slower increases in the variance in physiological rates as mean physiological rates increased with scaling relationships between log standard deviation and log mean all being smaller than 1 and varying across habitats (see Supplementary Materials; @tbl-slopes & @fig-mv).
-There was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(m_cvr_mean)`) reduction in relative variation for marine ectotherms when temperatures increased by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a smaller reduction in relative physiological rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(f_cvr_mean)`) (results from "Model 2").
-
-Across habitats whole-organism versus biochemical processes showed a similar decrease in relative variance in physiological rates (@fig-btrait D-F; see Supplement [@fig-S2] for more detailed trait analysis), except for biochemical processes in ectotherms occupying freshwater habitats, which showed small, albeit significant increase in relative variance when acclimated (@fig-btrait F).
-Reduced relative variance was particularly prominent for resting metabolic rates and sprint speed although traits differed in whether they exhibited a reduction in variation in physiological rates at high temperatures (see supplemental @fig-S2) ("Model 3").
-Each life-history stage exhibited the same pattern of relative variance change in each of the habitats ("Model 4"; @fig-cvrlh).
+Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a
+decrease with increasing temperature across all habitat types, which was
+especially pronounced in terrestrial and marine ectotherms. The total
+proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to
+$lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI:
+`r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`),
+with most variation being driven by between-study and trait differences
+("Model 1"; see Supplement @fig-s3). There were no differences between
+$lnCVR_{Q_{10_{acute}}}$ and $lnCVR_{Q_{10_{acclimation}}}$. Reductions
+in variance were driven by slower increases in the variance in
+physiological rates as mean physiological rates increased with scaling
+relationships between log standard deviation and log mean all being
+smaller than 1 and varying across habitats (see *Supplementary
+Materials*; @tbl-slopes & @fig-mv). There was a `r mean(t_cvr_mean_ef)`%
+(95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to
+`r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance
+for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI:
+`r quantile(m_cvr_mean_ef, 0.025)[1]` to
+`r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(m_cvr_mean)`) reduction in relative variation for marine
+ectotherms when temperatures increased by 10$^\circ$C. In contrast,
+freshwater ectotherms exhibited a smaller reduction in relative
+physiological rate variance at high temperatures
+(`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]`
+to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(f_cvr_mean)`) (results from "Model 2").
+
+Across habitats whole-organism versus biochemical processes showed a
+similar decrease in relative variance in physiological rates
+([@fig-btrait]D-F; see Supplement @fig-S2) for more detailed trait
+analysis), except for biochemical processes in ectotherms occupying
+freshwater habitats, which showed small, albeit significant increase in
+relative variance when acclimated ([@fig-btrait]F). Reduced relative
+variance was particularly prominent for resting metabolic rates and
+sprint speed although traits differed in whether they exhibited a
+reduction in variation in physiological rates at high temperatures (see
+*Supplemental Material*, @fig-S2) ("Model 3"). Each life-history stage
+exhibited the same pattern of relative variance change in each of the
+habitats ("Model 4"; @fig-cvrlh).
 
@@
 
-Thermal variability (i.e., $CV$) experienced by a population in the past did not explain acclimation capacity (@fig-5 A) or changes in physiological rate variance (@fig-5 B) among terrestrial, marine or freshwater populations ("Model 5").
+Thermal variability (i.e., $CV$) experienced by a population in the past
+did not explain acclimation capacity ([@fig-5]A) or changes in
+physiological rate variance ([@fig-5]B) among terrestrial, marine or
+freshwater populations ("Model 5").
 
@@
 
-Measurements of acute and acclimation responses from wild ectotherms were much less common than from captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` wild populations).
-Globally, there was a clear bias towards species in the Northern Hemisphere (@fig-fig6 A-C).
-Projected changes in physiological rate variance were highly variable across the globe, with some regions showing a decrease in physiological rate variance, while others showing an increase (@fig-fig6 D).
-However, out of the `r length(unique(all_pred2$match))` populations, relative variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations.
-
-Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
-Climate change is predicted to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% reduction in relative variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5 climate scenario.
-All results are taken from "Model 6".
+Measurements of acute and acclimation responses from wild ectotherms
+were much less common than from captive populations ($N_{species}$ =
+`r length(unique(all_pred$spp))`, from
+`r length(unique(all_pred$uniques))` wild populations). Globally, there
+was a clear bias towards species in the Northern Hemisphere
+([@fig-fig6]A-C). Projected changes in physiological rate variance were
+highly variable across the globe, with some regions showing a decrease
+in physiological rate variance, while others showing an increase
+([@fig-fig6]D). However, out of the `r length(unique(all_pred2$match))`
+populations, relative variance was predicted to decrease in
+`r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`%
+of the locations.
+
+Using the ERA5 climate model, predictions of current global changes in
+physiological rate variance were generally conservative with our model
+explaining \~ 50% of the variation in the observed data ($R^2$ =
+`r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)`
+to `r round(quantile(r2_2, 0.975)[1], 2)`). Climate change is predicted
+to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% reduction in
+relative variance for freshwater systems (95% CI:
+`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]`
+to
+`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%,
+$p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a
+`r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative
+variance for marine systems (95% CI:
+`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]`
+to
+`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%,
+$p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a
+`r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative
+variance for terrestrial systems (95% CI:
+`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]`
+to
+`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%,
+$p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5
+climate scenario. All results are taken from "Model 6".
 
@@
 
-Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
-Here, acclimation responses ($lnRR_{Q_{10}}$) varied across habitats while relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms decreased across terrestrial, marine and freshwater habitats as temperatures increase.
-Decreases in relative variance were particularly pronounced in terrestrial ectotherms (~28%).
-These effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections.
-Our results uncover an hitherto unrecognised dynamic where the benefits of acclimation may be counteracted by shifts in trait variance impacting how ectotherm populations across different habitats will be able to cope with increased temperatures.
-
-### ***Implications of differing acclimation capacities and decreased relative variability in physiological rates among ectotherms***
-
-We show that acclimation of physiological rates and changes in relative variance differ across habitats.
-Our findings confirm previous results that quantify the different capacity of terrestrial, marine and freshwater ectotherms to acclimate [@Seebacher2015-wi; @Gunderson2015-hz; @morley2019physiological].
-Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
-The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms (decrease of 16% versus ~10% in @Seebacher2015-wi), and opposite in terrestrial ectotherms (increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi), possibly due to the use of new $Q_{10}$ based effect sizes that allow us to control for sampling variance.
-Greater capacity for acclimation in aquatic organisms may be the result of fewer opportunities for behaviuoral thermoregulation in aquatic environments making physiological remodeling important for maintaining homeostasis [@Gunderson2015-hz; @morley2019physiological].
-While marine and freshwater ectotherms were capable of partial acclimation it is still important to recognise that, on average, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6).
-
-Changes in relative variance in physiological rates across habitats was nearly equivalent (marine) or larger (terrestrial) compared to their capacity to acclimate.
-Only in freshwater ectotherms did acclimation in physiological rates coincide with no change in relative variation.
-Mechanistically, it is unclear what is contributing to the reduction in relative variation in physiological rates at higher temperatures.
-One possible explanation may be that biochemical reactions are operating more efficiently or are relying on more conformationally stable enzymes at higher temperatures impacting between individual variation [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins].
-Such a mechanism may also help explain the differences in relative variance across habitat types.
-For example, terrestrial ectotherms may rely on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range necessary to operate in more variable thermal environments [@angilletta2009thermal].
-Acclimation responses in marine and freshwater organisms may also themselves buffer / maintain variance in physiological rates at higher temperatures due to the expression of alternative enzymes that function more effectively at higher temperatures.
-Given that biochemical traits in marine and freshwater organisms acclimated, and their relative variance increased in freshwater after acclimation, this seems plausible.
-
-Our results further highlight the potential vulnerability of terrestrial ectotherms to climate change, while calling into question if acclimation in marine systems will be able to counteract the potentially negative effects of reductions in relative variance.
-Assuming changes in relative variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, such reductions in physiological variance could limit a populations ability to adapt to future climates [@urban2023and].
-Of course, considering how behavioural modifications buffer organisms from high temperatures is also needed.
-Terrestrial species likely have greater opportunity for behavioural microhabitat selection in thermally heterogeneous environments which is expected to decrease the impacts of climate change [@huey2012predicting; @sunday2014thermal].
-Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited in terrestrial and marine habitats.
-As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized.
-Future theoretical models are needed to better understand the ecological and evolutionary consequences of changes in both mean and variance.
+Understanding acclimation capacity and how variation in physiological
+rates change across populations and species is important for predicting
+the ecological and evolutionary consequences of climate change
+[@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating;
+@seebacher2023can; @Sanderson2023; @urban2023and]. Here, acclimation
+responses ($lnRR_{Q_{10}}$) varied across habitats while relative
+variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms
+decreased across terrestrial, marine and freshwater habitats as
+temperatures increase. Decreases in relative variance were particularly
+pronounced in terrestrial ectotherms (\~28%). These effects are expected
+to result in a decrease in the variability in physiological rates for
+marine and terrestrial ectotherms between \~4-13% under future climate
+change projections. Our results uncover an hitherto unrecognised dynamic
+where the benefits of acclimation may be counteracted by shifts in trait
+variance impacting how ectotherm populations across different habitats
+will be able to cope with increased temperatures.
+
+### ***Acclimation capacities and changes in relative variability in physiological rates vary among habitats***
+
+We show that acclimation of physiological rates and changes in relative
+variance differ across habitats. Our findings confirm previous results
+that quantify the different capacity of terrestrial, marine and
+freshwater ectotherms to acclimate [@Seebacher2015-wi;
+@Gunderson2015-hz; @morley2019physiological]. Our analysis generally
+supports that of @Seebacher2015-wi, @Gunderson2015-hz and
+@morley2019physiological that all show a general inability of
+terrestrial ectotherms to physiologically acclimate. The change in
+acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for
+freshwater organisms (\~17%), but higher in marine ectotherms (decrease
+of 16% versus \~10% in @Seebacher2015-wi), and opposite in terrestrial
+ectotherms (increase of \~6% compared to an \~8% decrease in
+@Seebacher2015-wi), possibly due to the use of new $Q_{10}$ based effect
+sizes that allow us to control for sampling variance. Greater capacity
+for acclimation in aquatic organisms may be the result of fewer
+opportunities for behavioural thermoregulation in aquatic environments
+making physiological remodeling important for maintaining homeostasis
+[@Gunderson2015-hz; @morley2019physiological]. While marine and
+freshwater ectotherms were capable of partial acclimation it is still
+important to recognise that, on average, the effect size was small
+(amounting to $Q_{10}$ dropping from \~1.8 to 1.6).
+
+Changes in relative variance in physiological rates across habitats was
+nearly equivalent (marine) or larger (terrestrial) compared to their
+capacity to acclimate. Only in freshwater ectotherms did acclimation in
+physiological rates coincide with no change in relative variation.
+Mechanistically, it is unclear what is contributing to the reduction in
+relative variation in physiological rates at higher temperatures. One
+possible explanation may be that biochemical reactions are operating
+more efficiently or are relying on more conformationally stable enzymes
+at higher temperatures impacting between individual variation
+[@tattersall2012coping; @angilletta2009thermal; @somero1995proteins;
+@fields2001protein]. Such a mechanism may also help explain the
+differences in relative variance across habitat types. For example,
+terrestrial ectotherms may rely on more specialised enzymatic variants
+that operate over a more limited temperature range individually but
+together allow for organisms to function over a wider thermal range
+necessary to operate in more variable thermal environments
+[@angilletta2009thermal].
+
+Interestingly, we show that biochemical traits (i.e., enzymes) were more
+likely to acclimate compared to whole-organisms traits as predicted, but
+only for marine ectotherms. In contrast, both whole-organism and
+biochemical traits were equally likely to acclimate in freshwater
+ectotherms. Unsurprisingly, we observed no distinction between traits in
+terrestrial ectotherms. We also expected relative variance to differ
+between whole-organism and biochemical traits, but we did not find
+strong support for this except for in freshwater ectotherms where
+biochemical traits were more likely to maintain or increase relative
+variance compared with whole-organisms traits. Acclimation responses in
+marine and freshwater organisms may buffer / maintain variance in
+physiological rates at higher temperatures due to the expression of
+alternative enzyme forms or intracellular stabalising compounds/solutes
+that impact enzyme function [@fields2001protein].
+
+Our results further highlight the potential vulnerability of terrestrial
+ectotherms to climate change, while calling into question if acclimation
+in marine systems will be able to counteract the potentially negative
+effects of reductions in relative variance. Assuming changes in relative
+variation in physiological rates are underpinned by genetic variation,
+and there is a genetic correlation with fitness, such reductions in
+physiological variance could limit a populations ability to adapt to
+future climates [@urban2023and]. Of course, considering how behavioural
+modifications buffer organisms from high temperatures is also needed.
+Terrestrial species likely have greater opportunity for behavioural
+microhabitat selection in thermally heterogeneous environments which is
+expected to decrease the impacts of climate change [@huey2012predicting;
+@sunday2014thermal]. Importantly, while we seen a reduction in relative
+variation, absolute variation in physiological rates did increase with
+temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial
+and marine habitats compared to freshwater -- supporting the general
+notion that capacity for adaptation may still be limited in terrestrial
+and marine habitats. As of yet, it is unclear whether a focus on
+relative or absolute variance should be prioritized. Future theoretical
+models are needed to better understand the ecological and evolutionary
+consequences of changes in both mean and variance.
 
 ### ***Plasticity and relative variance in physiological rates do not differ between life stages***
-Acclimation capacities are expected to differ between life-stages because of distinct of patterns of dispersal, habitat use and behaviour that force earlier life stages to cope with more variable environmental conditions which can also lead to developmental constraints on how physiological systems respond later in life [@martin2015age; @stearns1976life; @angilletta2009thermal; @noble2018developmental; @o2019developmental; @Pottier2022].
-In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], and such costs can be magnified in late life reducing the capacity for plasticity [e.g., @rossi2019ageing].
-These processes can also result in changes to intrapopulation variation in physiological rates at higher temperatures but the direction of change between early and adult life stages is likely to depend on the costs of adjusting physiological processes, energy reserves at different life stages, and the extent to which early life experiences constrain plasticity.
-Despite these expectations, more broadly, we show little difference between early and late life acclimation capacities and little change in the relative variance in physiological rates across habitats.
-This may not be too surprising given that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
-The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar thermal niches, disperse to a similar extent and exhibit comparable thermoregulatory behaviors making physiological responses to temperature similar.
-It is possible that temperatures experienced earlier in development (e.g., egg or larval stages) exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
-Some empirical evidence supports this in insects.
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
-A focus on collecting more detailed information on the differences in behaviour, dispersal and thermal environments experienced across different life stages is likely to provide a more complete picture on when plasticity differs across life stages.
-To date, however, there are few studies that have focused on how variability in responses change.
-We would also encourage more empirical focus on this questions given the potential ecological and evolutionary implications.
+
+Acclimation capacities are expected to differ between life-stages
+because of distinct of patterns of dispersal, habitat use and behaviour
+that force earlier life stages to cope with more variable environmental
+conditions which can also lead to developmental constraints on how
+physiological systems respond later in life [@martin2015age;
+@stearns1976life; @angilletta2009thermal; @noble2018developmental;
+@o2019developmental; @Pottier2022]. In addition, plastic responses are
+also expected to be costly [@angilletta2009thermal; @Dewitt1998], and
+such costs can be magnified in late life reducing the capacity for
+plasticity [e.g., @rossi2019ageing]. These processes can also result in
+changes to intrapopulation variation in physiological rates at higher
+temperatures but the direction of change between early and adult life
+stages is likely to depend on the costs of adjusting physiological
+processes, energy reserves at different life stages, and the extent to
+which early life experiences constrain plasticity.
+
+Despite these expectations, more broadly, we show little difference
+between early and late life acclimation capacities and little change in
+the relative variance in physiological rates across habitats. This may
+not be too surprising given that such responses are likely context or
+trait dependent [@carter2020life; @moghadam2019heat]. The lack of
+differences we observed may also be due to the fact that both juvenile
+and adult animals occupy similar thermal niches, disperse to a similar
+extent and exhibit comparable thermoregulatory behaviors making
+physiological responses to temperature similar. It is possible that
+temperatures experienced earlier in development (e.g., egg or larval
+stages) exhibit greater capacity for acclimation because of limited
+dispersal capabilities and very different habitats. Some empirical
+evidence supports this in insects. For example, @moghadam2019heat showed
+that larval *Drosophila* were more plastic in their heat hardening
+responses compared to adults. A focus on collecting more detailed
+information on the differences in behaviour, dispersal and thermal
+environments experienced across different life stages is likely to
+provide a more complete picture on when plasticity differs across life
+stages. To date, however, there are few studies that have focused on how
+variability in responses change. We would also encourage more empirical
+focus on this questions given the potential ecological and evolutionary
+implications.
 
 ### ***No signature of past climate on capacity for physiological plasticity***
-Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity is more likely to evolve in terrestrial environments.
-However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
-The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@hendry2016key; @Leung2020].
-
-Whether a populations capacity for physiological plasticity and the thermal variability (or predictability) it experiences are related has received more mixed results.
-We show no relationship between acclimation capacity and thermal variability in marine, freshwater and terrestrial habitats.
-Our results are consistent with @Gunderson2015-hz who show no relationship between plasticity in heat tolerance and latitude or thermal seasonality.
-However, other analyses on heat tolerance limits have found relationships between latitude (a proxy for seasonality) [@morley2019physiological] or measures of thermal variability [@verberk2024heat].
-@Seebacher2015-wi also found evidence that acclimation capacity is related to a populations thermal variability, however, relationships depended on the habitat and traits in question.
-Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological], different traits or possibly the fact that different climate projections/models are being used to quantify thermal variability.
-Modelling realistic microenvironments across such diverse taxa is also challenging because it is unclear what the most appropriate spatial and temporal scale might be that is of evolutionary relevance.
-As such, it is also likely that historical temperature time series' are not representative of the selective environment a population has experienced making relationships between capacity for acclimation and temperature variability (or predictability) difficult to pin down.
+
+Theoretical models predict that plasticity should evolve in populations
+experiencing greater environmental variability (spatial or temporal),
+particularly when oscillations are predictable over time to make
+environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010;
+@Nunney2016; @Murren2015; @hendry2016key; @Reed2010]. Higher spatial and
+temporal heterogeneity in terrestrial habitats [@steele2019comparison]
+might suggest that plasticity is more likely to evolve in terrestrial
+environments. However, if thermal variability is too high and
+unpredictable, the rates of acclimation slow, and there are costs
+associated with re-modelling physiological processes [which seem likely,
+@angilletta2009thermal] then we would instead expect canalised responses
+[@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences;
+@Leung2020; @rescan2022experimental; @leung2023phenotypic]. The lack of
+acclimation in terrestrial ectotherms we observed is consistent with the
+latter hypothesis, and is supported by other meta-analyses of heat
+tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there
+are costs to being plastic or that the environmental signals are
+insufficient to trigger endocrine and epigenetic mechanisms that lead to
+plasticity when environments are not predictable [@hendry2016key;
+@Leung2020].
+
+Whether a populations capacity for physiological plasticity and the
+thermal variability (or predictability) it experiences are related has
+received more mixed results. We show no relationship between acclimation
+capacity and thermal variability in marine, freshwater and terrestrial
+habitats. Our results are consistent with @Gunderson2015-hz who show no
+relationship between plasticity in heat tolerance and latitude or
+thermal seasonality. However, other analyses on heat tolerance limits
+have found relationships between latitude (a proxy for seasonality)
+[@morley2019physiological] or measures of thermal variability
+[@verberk2024heat]. @Seebacher2015-wi also found evidence that
+acclimation capacity is related to a populations thermal variability,
+however, relationships depended on the habitat and traits in question.
+Discrepancies across studies could be related to the taxa included in
+analyses [e.g., @morley2019physiological], different traits or possibly
+the fact that different climate projections/models are being used to
+quantify thermal variability. Modelling realistic microenvironments
+across such diverse taxa is also challenging because it is unclear what
+the most appropriate spatial and temporal scale might be that is of
+evolutionary relevance. As such, it is also likely that historical
+temperature time series' are not representative of the selective
+environment a population has experienced making relationships between
+capacity for acclimation and temperature variability (or predictability)
+difficult to pin down.
 
@@
 
-Enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
-While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial study- and trait-level variance estimates.
-Nonetheless, quantitative measures on the changes in the relative variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
-While we do not yet understand the relative contribution of environmental and genetic factors to variance changes, models could better decouple how different levels of heritability and total variance impact evolutionary and ecological predictions.
-Our meta-analysis now provides the opportunity to parameterise such models, and ensure they are better aligned with empirical findings.
-
-Nonetheless, it is clear that many fascinating questions remain unanswered that will require greater focus on the consequences of changes in variance (rather than just the mean).
-Particularly interesting questions include: How do differences in physiological rate variance change energy flow across trophic levels within communities?
-What are the biochemical, cellular, and physiological mechanisms that underlie differences in physiological rate variance across habitats?
-Are changes in variance in one trait associated with changes in other traits, or do some traits increase while others decrease?
-Are changes in physiological rate variance correlated with changes in genetic variation?
-Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across major ecosystems globally.
-
-## Awknowledgements
-We would like to thank Malgorzata Lagisz for helping sort out the phylogeny used in our analysis.
-We are also grateful to three anonymous reviewers who all provided highly constructive feedback that greatly improved the manuscript.
+Enhanced knowledge of how variation in physiological rates vary across
+populations and species, and the degree to which they can be adjusted in
+response to the environment, may lead to more informed predictions about
+the ecological and evolutionary dynamics of natural populations
+[@forsman2015rethinking; @seebacher2023can; @cooke2021one;
+@Sanderson2023]. While we show general patterns across taxa and habitats
+it is important to recognise that this does not mean such patterns apply
+to all populations. Substantial variation in acclimation responses and
+changes in variance exist among populations and traits, as evidenced by
+wide prediction intervals and substantial study- and trait-level
+variance estimates. Nonetheless, quantitative measures on the changes in
+the relative variance in physiological rates could be better
+incorporated into physiological and ecological models to provide more
+nuanced, and possibly more realistic, predictions about the impacts of
+climate change on natural populations. While we do not yet understand
+the relative contribution of environmental and genetic factors to
+variance changes, models could better decouple how different levels of
+heritability and total variance impact evolutionary and ecological
+predictions. Our meta-analysis now provides the opportunity to
+parameterise such models, and ensure they are better aligned with
+empirical findings.
+
+Nonetheless, it is clear that many fascinating questions remain
+unanswered that will require greater focus on the consequences of
+changes in variance (rather than just the mean). Particularly
+interesting questions include: How do differences in physiological rate
+variance change energy flow across trophic levels within communities?
+What are the biochemical, cellular, and physiological mechanisms that
+underlie differences in physiological rate variance across habitats? Are
+changes in variance in one trait associated with changes in other
+traits, or do some traits increase while others decrease? Are changes in
+physiological rate variance correlated with changes in genetic
+variation? Answers to these questions will require integrative
+approaches that combine empirical and theoretical work across multiple
+levels of biological organisation but will likely provide useful
+advances in understanding the full consequences that climate change will
+have on ectotherms across major ecosystems globally.
+
+## Acknowledgements
+
+We would like to thank Malgorzata Lagisz for helping sort out the
+phylogeny used in our analysis. We are also grateful to three anonymous
+reviewers who all provided highly constructive feedback that greatly
+improved the manuscript.
 
 ## Funding
-DWAN is supported by an Australian Research Council (ARC) Future Fellowship (FT220100276) and ARC Discovery Project (DP210101152).
-SN is supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
+
+DWAN is supported by an Australian Research Council (ARC) Future
+Fellowship (FT220100276) and ARC Discovery Project (DP210101152). SN is
+supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
 
 ## Data and code availability
-All data and code used to reproduce analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis and is deposited in Zenodo (https://doi.org/10.5281/zenodo.11123600).
+
+All data and code used to reproduce analyses can be found on GitHub at:
+https://github.com/daniel1noble/Q10_meta_analysis and is deposited in
+Zenodo (https://doi.org/10.5281/zenodo.11123600).
 
 ## Author contributions
-Conceptualization: DWAN, FK, FS, SN; Methodology: DWAN, AB, FK, FS, SN; Investigation: DWAN, FK, FS, SN; Visualization: DWAN; Supervision: DWAN, SN, FS; Writing—original draft: DWAN; Writing—review & editing: DWAN, AB, FK, FS, SN.
+
+Conceptualization: DWAN, FK, FS, SN; Methodology: DWAN, AB, FK, FS, SN;
+Investigation: DWAN, FK, FS, SN; Visualization: DWAN; Supervision: DWAN,
+SN, FS; Writing—original draft: DWAN; Writing—review & editing: DWAN,
+AB, FK, FS, SN.
 
 ## Conflict of interest
+
 Authors declare that they have no competing interests.
@@
 <br> 
-<div id="refs"></div>
+<div id ="refs"></div>
 <br>
@@
 
-We performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm* OR temp*) NOT (plant* OR tree* OR forest* OR fung* OR mammal* OR marsup* OR bird* OR human OR exercis* OR train* OR hypoxi*))"*.
-We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
-
-Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
-We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
-We included any papers that were missed between our searches and those of @Havird2020-mj.
-@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader than @Havird2020-mj, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
-More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
-While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
-As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
-
-We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
-To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
-In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
-After title and abstract screening, there was a total of 149 papers for full text screening.
-Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
-Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
+We performed a literature search using the Web of Science database for
+articles or proceedings papers published in English from 2013 to 2017
+(the date after [@Seebacher2015-wi] searches were conducted) using the
+following topic search string: *"(acclimat* AND (therm\* OR temp*) NOT
+(plant* OR tree\* OR forest\* OR fung\* OR mammal\* OR marsup\* OR
+bird\* OR human OR exercis\* OR train\* OR hypoxi*))"*. We further
+limited to the following research areas: Anatomy Morphology;
+Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism;
+Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology;
+Respiratory System, Reproductive Biology, Zoology.
+
+Our search resulted in 1,321 papers for screening in Rayyan
+[@Ouzzani2016-ge]. We also cross-checked papers we found in our searches
+with a recent paper by @Havird2020-mj, which also updates the dataset of
+@Seebacher2015-wi's. We included any papers that were missed between our
+searches and those of @Havird2020-mj. @Havird2020-mj added 7 new studies
+(mainly because they were focused on metabolic rates), and our searches
+differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader than
+@Havird2020-mj, we had a substantial increase in additional papers that
+we added to @Seebacher2015-wi's dataset. More specifically, in addition
+to the `r length(unique(old_papers$record_num))` papers we included from
+the @Seebacher2015-wi dataset, we extracted data from an extra
+`r length(unique(new_papers$record_num))` papers (with a total of
+`r dim(new_papers)[1]` effects; a
+`r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`%
+increase in the number of published articles). Note that
+@Seebacher2015-wi included a total of 205 publications, however, not all
+these contained the necessary statistics we needed to derive effect
+sizes and associated sampling variances (see below). While we may have
+missed papers, our goal was to obtain a large representative (and
+unbiased) sample of acclimation research rather than a comprehensive
+dataset. As such, our database represents the most up-to-date dataset
+used since @Seebacher2015-wi to answer questions on physiological rates
+across ectotherms.
+
+We split the screening of titles and abstracts for the 1,321 papers
+found in our search among DWAN, FK, FS, and SN evenly. To ensure
+consistency among authors in title and abstract inclusion, relevant
+authors went through a randomly selected set of papers together before
+the formal screening to calibrate selection of papers based on our
+inclusion criteria (see below). In cases of disagreement regarding
+inclusion, we conservatively included the paper for full text screening
+and discussed uncertain papers among authors to come to a decision.
+After title and abstract screening, there was a total of 149 papers for
+full text screening. Papers were included only if they: 1) measured a
+physiological rate acutely at two temperatures on a sample of animals
+chronically exposed to the same two temperatures for at least 1 week;
+and 2) where physiological rates measured were burst and sustained
+locomotion, metabolic rates (standard, resting, routine and maximal),
+heart rates, and/or enzyme activities. Importantly, as in
+@Seebacher2015-wi, we only included studies that manipulated
+temperatures within normal thermal ranges for the species.
 
@@
 
-#### *Further discussions on the assumptions of $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-
-$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
-While this is likely in our data given that we restricted our analysis of $Q_{10}$ to standard operating temperatures for a given species, it may not always be satisfied given the diversity of species in our dataset.
-$Q_{10}$ [@van1884etudes] has been used exstensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi].
-However, there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model thermal effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
-While debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence it is important to recognise that both BA and $Q_{10}$ can exhibit curvilinearity as temperatures increase (as discussed in [@michaletz2024hotter]).
-@white2012information also showed that the BA model may not always perform better.
-For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better fit to metabolic rate data than the BA relationship [@white2012information].
-Given that studies included in our analysis never measured full performance curves at acute and acclimation temperatures it was not possible for us to compare different models of thermal dependence.
-Nonetheless, $Q_{10}$-based effect sizes remain the most practical effect-size for comparing thermal dependence when using existing empircial data, with the benefit that these effects having convenient properties that make them suitable for meta-analysis.
-Nonetheless, we control for possible violations of the log-linearity assumption in our analyses.
-
-#### *Exploring the impact of maximum treatment temperature on $lnRR_{Q_{10}}$*
+#### *Further discussions on the assumptions of* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
+
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$
+more generally, all assume that the effect of temperature on
+physiological rates (or changes in relative variance) is log-linear.
+While this is likely in our data given that we restricted our analysis
+of $Q_{10}$ to standard operating temperatures for a given species, it
+may not always be satisfied given the diversity of species in our
+dataset. $Q_{10}$ [@van1884etudes] has been used exstensively in the
+physiological literature to successfully address a multitude of
+questions [e.g., @Havird2020-mj; @Seebacher2015-wi]. However, there is a
+preference for using a Boltzmann – Arrhenius (BA) relationship (or its
+more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal;
+@michaletz2024hotter]) to model thermal effects on physiological rates
+[@gillooly2001effects; @michaletz2024hotter]. While debate still exists
+over the utility of $Q_{10}$ when modelling temperature-dependence it is
+important to recognise that both BA and $Q_{10}$ can exhibit
+curvilinearity as temperatures increase (as discussed in
+[@michaletz2024hotter]). @white2012information also showed that the BA
+model may not always perform better. For example, in eukaryotes,
+modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better
+fit to metabolic rate data than the BA relationship
+[@white2012information]. Given that studies included in our analysis
+never measured full performance curves at acute and acclimation
+temperatures it was not possible for us to compare different models of
+thermal dependence. Nonetheless, $Q_{10}$-based effect sizes remain the
+most practical effect-size for comparing thermal dependence when using
+existing empircial data, with the benefit that these effects having
+convenient properties that make them suitable for meta-analysis.
+Nonetheless, we control for possible violations of the log-linearity
+assumption in our analyses.
+
+#### *Exploring the impact of maximum treatment temperature on* $lnRR_{Q_{10}}$
 
@@
 
-#### *How acclimation time is related to $lnRR_{Q_{10}}$* 
+#### *How acclimation time is related to* $lnRR_{Q_{10}}$
+
 ```{r, fig-accl_time}
@@
 ```
+
 #### *Comparing cool and warm acclimated acute responses*
@@
 
-#### *Acute and acclimation $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa*
-
-In addition to the broader trait categories we fit models to understand how acute and acclimation effect sizes varied across trait categories.
-To achieve this, we categorized each effect size into one of 12 trait categories.
-These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
-Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
-All other traits not falling within these categories were placed into 'other'.
+#### *Acute and acclimation* $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa
+
+In addition to the broader trait categories we fit models to understand
+how acute and acclimation effect sizes varied across trait categories.
+To achieve this, we categorized each effect size into one of 12 trait
+categories. These categories included measures of whole organism
+performance measures including cardiac (i.e., 'cardiac') and muscle
+('muscle') function, sprint speed ('sprint') and endurance ('endurance')
+and metabolic rates (i.e., maximal and resting metabolic rate; max MR',
+'rest MR', respectively). Studies also quantified various enzymatic
+reaction rates, including enzymes involved in general metabolic
+responses (categorized as 'metabolic enzyme'), various parts of the
+electron transport chain, including ATPase activity ('ATPase'),
+mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for
+Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
+All other traits not falling within these categories were placed into
+'other'.
 
@@
 
-#### *Mean-variance relationships to understand patterns in $lnCVR_{Q_{10}}$*
+#### *Mean-variance relationships to understand patterns in* $lnCVR_{Q_{10}}$
 
@@
 
-We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
-We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
-We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
-
-Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
-Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (@tbl-slopes), however, ectotherms from terrestrial habitats had much shallower slopes than marine and freshwater ectotherms, particularly at higher treatment temperatures, indicating increased mean physiological rates generally do not result in higher between individual variance in physiological rates (@tbl-slopes).
-Interestingly, in marine ectotherms the slope was highest at cooler temperatures, wheeras the slope was suppressed when acclimated and/or measured at higher temperatures (i.e., r.1.
-compared to r1.2, r2.1, r2.2) (@tbl-slopes).
-In freshwater ectotherms, there we some differences in scaling relationships but they were all fairly comparable no matter what acclimatin and test temperature (@tbl-slopes).
+We explored mean-variance relationships for the acute and acclimation
+responses across all traits and habitats. We estimated the scaling
+relationship between log standard deviation in physiological rates
+\[log(SD)\] and log mean physiological rates \[log(mean)\], accounting
+for non-independence resulting from effects coming from the same
+species, study and traits (i.e., random effects of species, study and
+trait) as done in our main analyses. We also included an interaction
+between log(mean) and habitat type to better understand how the scaling
+relationship between log(SD) and log(mean) varies across habitats.
+
+Overall, we found that the relationship between log(mean) and log(SD) of
+the acute and acclimation responses was generally linear, suggesting
+that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv). Overall, the
+scaling relationship between log(SD) and log(mean) was sub-linear across
+all habitats (@tbl-slopes), however, ectotherms from terrestrial
+habitats had much shallower slopes than marine and freshwater
+ectotherms, particularly at higher treatment temperatures, indicating
+increased mean physiological rates generally do not result in higher
+between individual variance in physiological rates (@tbl-slopes).
+Interestingly, in marine ectotherms the slope was highest at cooler
+temperatures, wheeras the slope was suppressed when acclimated and/or
+measured at higher temperatures (i.e., r.1. compared to r1.2, r2.1,
+r2.2) (@tbl-slopes). In freshwater ectotherms, there we some differences
+in scaling relationships but they were all fairly comparable no matter
+what acclimatin and test temperature (@tbl-slopes).
 
@@
 
-#### *Comparing raw variance changes using $lnVR_{Q_{10}}$*
+#### *Comparing raw variance changes using* $lnVR_{Q_{10}}$
+
 ```{r, lnvrq10}
@@
 
-Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-s1). @tbl-s1
+Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with
+higher temperatures across all habitat types, with terrestrial
+ectotherms having the smallest increase in variance (@fig-s1 & @tbl-s1).
 
@@
 
-#### *Plots of $I^2$ for multilevel models*
+#### *Plots of* $I^2$ for multilevel models
+
 ```{r, fig-s3}
@@
 
-Theoretical models highlight the importance of environmental predictability in selecting for plastic responses.
-However, capturing environmental predictability is challenging given that it is unclear which timescale one should select.
-For example, is it more important to look at correlation between temperatures monthly or seasonally.
-In addition, such temporal resolution will likely depend on the species in question given that for some species fine-grained thermal predictability maybe more important compared to others.
-
-With these limitations in mind, we used our temperature time series to calculate auto regressive correlation in temperature across the entire time series.
-We then modeled how this measure of thermal predictability was related to plasticity.
+Theoretical models highlight the importance of environmental
+predictability in selecting for plastic responses. However, capturing
+environmental predictability is challenging given that it is unclear
+which timescale one should select. For example, is it more important to
+look at correlation between temperatures monthly or seasonally. In
+addition, such temporal resolution will likely depend on the species in
+question given that for some species fine-grained thermal predictability
+maybe more important compared to others.
+
+With these limitations in mind, we used our temperature time series to
+calculate auto regressive correlation in temperature across the entire
+time series. We then modeled how this measure of thermal predictability
+was related to plasticity.
 
@@
 
-Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
-Meta-regression models including sampling standard error as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(post_full_lnvr_pb)`, 95% CI: `r quantile(post_full_lnvr_pb, 0.025)` to `r quantile(post_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_full_lnvr_pb))`) was not significant indicating little evidence for publication bias.
+Funnel plots did not show any noticeable deviation from the typical
+funnel shape for any of the effect size estimates (@fig-s2).
+Meta-regression models including sampling standard error as a moderator
+also suggested no relationship with effect size for $lnRR_{Q_{10}}$
+($\beta$ = `r mean(post_pb_lnrr)`, 95% CI:
+`r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`,
+$p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$
+($\beta$ = `r mean(post_pb_lncvr)`, 95% CI:
+`r quantile(post_pb_lncvr, 0.025)` to
+`r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ =
+`r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ =
+`r mean(post_full_lnvr_pb)`, 95% CI:
+`r quantile(post_full_lnvr_pb, 0.025)` to
+`r quantile(post_full_lnvr_pb, 0.975)`, $p_{MCMC}$ =
+`r p_value(pmcmc(post_full_lnvr_pb))`) was not significant indicating
+little evidence for publication bias.

### 2024-07-08 ms.qmd
UPdated and re-rendered MS

@@
 ^1^ Division of Ecology and Evolution, Research School of Biology, The
-Australian National University, Canberra, ACT 2600, Australia
-\
+Australian National University, Canberra, ACT 2600, Australia\
 ^2^ Ecology and Evolution Research Centre, School of Biological, Earth
 and Environmental Sciences, University of New South Wales, Sydney, NSW,
-Australia
-\
+Australia\
 ^3^ School of Life and Environmental Sciences, University of Sydney,
-Sydney, NSW 2006, Australia
-\
-^4^ Department of Biology, Lancaster University, Liverpool, UK
-\
-$\dagger$ contributed equally
-\
+Sydney, NSW 2006, Australia\
+^4^ Department of Biology, Lancaster University, Liverpool, UK\
+$\dagger$ contributed equally\
 $\ddagger$ corresponding author, daniel.noble\@anu.edu.au
@@
 @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-More variable populations, genetically and/or phenotypically, are
-predicted to be associated with broader niches, reduced intraspecific
-competition, increased growth rate, decreased vulnerability to
+More variable populations, genetically and/or phenotypically, are also 
+predicted to be associated with broader niches, have increased growth rate, decreased vulnerability to
 environmental change and lower extinction risk [@forsman2015rethinking;
@@
 In addition, if phenotypic and genetic variation are correlated and
-traits are linked to fitness, changes in variation can limit responses
+traits are linked to fitness, changes in variation may limit responses
 to selection impacting a populations capacity to evolve
@@
 Shaded blue and red areas are the thermal optima of the performance curves.
-Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20$^\\circ$C and $T_{2} = 30$^\\circ$C) for both curves.
+Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20°C and $T_{2}$ = 30°C) for both curves.
 At each temperature a mean physiological rate (R) (points) and its standard deviation (SD) (error bars above and below mean) are estimated.
@@
 
-fig_concept <- magick::image_read("output/figures/fig1_concept_full.png")
+fig_concept <- magick::image_read("output/figures/fig1.png")
 plot(fig_concept)
@@
 absolute measurement temperatures. The sampling variance for @eq-lnq10
-can be computed as follows (as described in @Noble2022-ty):
+can be computed as follows [as described in @Noble2022-ty]:
 
@@
 and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and
-$T_{2}$, respectively (@fig-concept A).
+$T_{2}$, respectively ([@fig-concept]A).
 
@@
 samples of organisms measured acutely at two temperatures or after
-having been acclimated these same temperatures (@fig-concept A). For
+having been acclimated these same temperatures ([@fig-concept]A). For
 studies that measure acute and acclimated responses we used the mean,
@@
 effect of temperature on physiological rates (or changes in relative
-variance) is log-linear (see *Supplementary Materials* for further
+variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further
 discussion). We test and control for any violations of these assumptions
-in our analysis (see below) ([@fig-concept]B).
+in our analysis (see below).
 
@@
 Figures were exported, imported into Adobe Illustrator for minor formatting changes and grid organisation.
-  fig2 <- image_read("./output/figures/Fig2_r1.png")
+  fig2 <- image_read("./output/figures/Fig2.png")
   plot(fig2)
@@
 processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see
-Supplement, @fig-S2) for more detailed trait analysis). Biochemical
+*Supplementary Materials*, @fig-lnrrtrait for more detailed trait analysis). Biochemical
 processes were more effective at acclimating compared to whole-organism
@@
 #| label: fig-2
-#| fig-cap: "A Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
-B Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+#| fig-cap: "A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
+B) Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
 For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Sample sizes are the same for panel A and B.
-In panels A and B, thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+Sample sizes are the same for panel A) and B).
+In panels A) and B), thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
 $\\Beta$ values are the contrasts between acute and acclimation means within each habitat.
@@
   fig3 <- (p3a + p3b) + plot_annotation(tag_levels = "A")
-  ggsave(fig3, filename = "./output/figures/fig3_r1.png", width = 21.88, height = 9)
-
-  fig3 <- magick::image_read("./output/figures/fig3_r1.png")
+  ggsave(fig3, filename = "./output/figures/fig3.png", width = 21.88, height = 9)
+
+  fig3 <- magick::image_read("./output/figures/fig3.png")
   fig3
@@
 similar decrease in relative variance in physiological rates
-([@fig-btrait]D-F; see Supplement @fig-S2) for more detailed trait
+([@fig-btrait]D-F; see *Supplementary Materials*, @fig-cvrtrait) for more detailed trait
 analysis), except for biochemical processes in ectotherms occupying
@@
 reduction in variation in physiological rates at high temperatures (see
-*Supplemental Material*, @fig-S2) ("Model 3"). Each life-history stage
+*Supplemental Material*, @fig-cvrtrait) ("Model 3"). Each life-history stage
 exhibited the same pattern of relative variance change in each of the
@@
 figbtrait <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/fig4_btrait_r1.png", width = 28, height = 14, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/fig4_btrait_r1.png")
+ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/fig4.png")
 figbtrait
@@
 fig4 <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(fig4, filename = "./output/figures/fig4_lh_r1.pdf", width = 28, height = 14, device = "pdf")
-
-fig4 <- magick::image_read("./output/figures/fig4_lh_r1.pdf")
+ggsave(fig4, filename = "./output/figures/fig5.pdf", width = 28, height = 14, device = "pdf")
+
+fig4 <- magick::image_read("./output/figures/fig5.pdf")
 fig4
@@
 
-  ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig_p_cv_r1.png")
-
-  p_cv <- image_read("./output/figures/fig_p_cv_r1.png")
+  ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig6.png")
+
+  p_cv <- image_read("./output/figures/fig6.png")
   p_cv 
@@
 
-ggsave(p, filename = "./output/figures/fig-preds.png", width = 7.8, height = 10.1)
-
-image_read("./output/figures/fig-preds.png")
+ggsave(p, filename = "./output/figures/fig7.png", width = 7.8, height = 10.1)
+
+image_read("./output/figures/fig7.png")
 ```
@@
 acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for
-freshwater organisms (\~17%), but higher in marine ectotherms (decrease
-of 16% versus \~10% in @Seebacher2015-wi), and opposite in terrestrial
-ectotherms (increase of \~6% compared to an \~8% decrease in
-@Seebacher2015-wi), possibly due to the use of new $Q_{10}$ based effect
-sizes that allow us to control for sampling variance. Greater capacity
-for acclimation in aquatic organisms may be the result of fewer
-opportunities for behavioural thermoregulation in aquatic environments
-making physiological remodeling important for maintaining homeostasis
-[@Gunderson2015-hz; @morley2019physiological]. While marine and
-freshwater ectotherms were capable of partial acclimation it is still
-important to recognise that, on average, the effect size was small
-(amounting to $Q_{10}$ dropping from \~1.8 to 1.6).
+freshwater organisms (~17%), but higher in marine ectotherms [decrease
+of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial
+ectotherms [increase of ~6% compared to an ~8% decrease in
+@Seebacher2015-wi], possibly due to the use of newly derived
+$Q_{10}$ effect sizes that allow us to control for sampling variance.
+Greater capacity for acclimation in aquatic organisms may be the result
+of fewer opportunities for behavioural thermoregulation in aquatic
+environments making physiological remodeling important for maintaining
+homeostasis [@Gunderson2015-hz; @morley2019physiological].
+Additionally, aquatic and terrestrial environments can vary in
+nutritional resources [e.g., fatty acid content of prey;
+@twining2019aquatic] that can impact physiological rates and their
+variability by affecting performance curves and acclimation responses
+[@hardison2024diet]. While marine and freshwater ectotherms were
+capable of partial acclimation it is still important to recognise that,
+on average, the effect size was small (amounting to $Q_{10}$ dropping
+from ~1.8 to 1.6).
 
@@
 
-Our results further highlight the potential vulnerability of terrestrial
+Our results further highlight the vulnerability of terrestrial
 ectotherms to climate change, while calling into question if acclimation
@@
 <br>
-<div id ="refs"></div>
+
+::: {#refs}
+:::
+
 <br>
 
-## Supplemental Results and Figures
+## Supplemental Materials
 
@@
 
-prisma <- magick::image_read("./output/figures/PRISMA.png")
+prisma <- magick::image_read("./output/figures/figS1.png")
 prisma
@@
 
-ggsave(lnrrq10_temp, file = "./output/figures/lnrrq10_temp.png", height = 6, width = 8)
-
-lnrrq10_temp <- magick::image_read("./output/figures/lnrrq10_temp.png")
+ggsave(lnrrq10_temp, file = "./output/figures/figS2.png", height = 6, width = 8)
+
+lnrrq10_temp <- magick::image_read("./output/figures/figS2.png")
 lnrrq10_temp
@@
 
-  ggsave(accl_time, file = "./output/figures/accl_time.png", height = 6, width = 8.5)
-
-accl_time <- magick::image_read("./output/figures/accl_time.png")
+  ggsave(accl_time, file = "./output/figures/figS3.png", height = 6, width = 8.5)
+
+accl_time <- magick::image_read("./output/figures/figS3.png")
 accl_time
@@
 col_acute <- c("#3F5FAC", "#EF3D25")
-orchard_plot(model1.s1_int, mod = "name", by = "habitat", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, condition.lab = "Habitat") + scale_x_discrete(labels = c("LnRR_Q10_acute_t2" = "Warm - Acute", "LnRR_Q10_acute_t1" = "Cool - Acute")) + scale_fill_manual(values = col_acute) + scale_colour_manual(values = col_acute) + ylim (-0.5, 2.5) +  theme_classic() + theme(axis.title  = element_text(size = 24),
+Sacute <- orchard_plot(model1.s1_int, mod = "name", by = "habitat", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", angle = 45, trunk.size = 1.8, branch.size = 2.8, alpha = 0.4, condition.lab = "Habitat") + scale_x_discrete(labels = c("LnRR_Q10_acute_t2" = "Warm - Acute", "LnRR_Q10_acute_t1" = "Cool - Acute")) + scale_fill_manual(values = col_acute) + scale_colour_manual(values = col_acute) + ylim (-0.5, 2.5) +  theme_classic() + theme(axis.title  = element_text(size = 24),
                                        axis.text = element_text(size = 24),
@@
                                #annotate("text", label= paste0("k = ", k_lnrr_acute$k, " (", k_lnrr_acute$sdy, ")"), x = c(1.2, 2.2), y = 2)
+
+Sacute
+ggsave(Sacute, file = "./output/figures/figS4.png", height = 10, width = 12)
 ```
@@
 
-@fig-lnrrtrait; @fig-cvrtrait
+Acclimation capacity varied across trait categories and habiats with measures of resting metabolic rate, including associated biochemical reactions like oxidative phosphorylation (OXPHOS) and ATPase activity, acclimating in marine and freshwater ectotherms (@fig-lnrrtrait).
+Whether relative variation in physiological rates changes also depended on trait type, with freshwater ectotherms generally maintaining relative variance in physiological rates better than marine and freshwater ectotherms (@fig-cvrtrait).
+We note though that some traits have very small sample sizes on their own and should be interpreted with caution.
 
@@
 fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
-ggsave(fig2, filename = "./output/figures/fig2_trait.png", height = 20, width = 15)
-
-img_fig2 <- magick::image_read("./output/figures/fig2_trait.png")
+ggsave(fig2, filename = "./output/figures/figS5.png", height = 20, width = 15)
+
+img_fig2 <- magick::image_read("./output/figures/figS5.png")
 img_fig2
@@
 figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figcvrtrait.png", height = 20, width = 15)
-
-img_figcvrtrait <- magick::image_read("./output/figures/figcvrtrait.png")
+ggsave(figcvrtrait, filename = "./output/figures/figS6.png", height = 20, width = 15)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figS6.png")
 img_figcvrtrait
@@
 relationship between log standard deviation in physiological rates
-\[log(SD)\] and log mean physiological rates \[log(mean)\], accounting
+[log(SD)] and log mean physiological rates [log(mean)], accounting
 for non-independence resulting from effects coming from the same
@@
 in scaling relationships but they were all fairly comparable no matter
-what acclimatin and test temperature (@tbl-slopes).
+what acclimation and test temperature (@tbl-slopes).
 
@@
  p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
-  ggsave(p_mv, file = "./output/figures/plot_mv.png", height = 8, width = 8)
-
-  p_mv <- magick::image_read("./output/figures/plot_mv.png")
+  ggsave(p_mv, file = "./output/figures/figS7.png", height = 8, width = 8)
+
+  p_mv <- magick::image_read("./output/figures/figS7.png")
   p_mv
@@
 
-  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
-
-  figs1 <- image_read("./output/figures/figS1.pdf")
+  ggsave(p3, filename = "./output/figures/figS8.pdf", width = 11.5, height = 8)
+
+  figs1 <- image_read("./output/figures/figS8.pdf")
   figs1
@@
 figs3 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figs3.png")
-
-figs3 <- image_read("./output/figures/figs3.png")
+ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figS9.png")
+
+figs3 <- image_read("./output/figures/figS9.png")
 figs3
@@
 
-ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/fig_p_acf_r1.pdf")
-
-  p_acf <- image_read("./output/figures/fig_p_acf_r1.pdf")
+ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS10.pdf")
+
+  p_acf <- image_read("./output/figures/figS10.pdf")
   p_acf 
@@
 figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS2.png")
-
-figs2 <- image_read("./output/figures/figS2.png")
+ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS11.png")
+
+figs2 <- image_read("./output/figures/figS11.png")
 figs2

### 2024-07-09 ms.qmd
Fixed supp table lnVR which should now have mx temp and a slope random effect

@@
 
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lnrr_wild_acclim <- tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acclim, tree = tree_lnrr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lnrr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
 if(rerun){
@@
   # More realistic model with 
-  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
+  model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
                                        random = list(~1 | record_num,
@@
                                             ~1 | trait,
-                                            ~1 | spp,
+                                            ~1 + max_temp_c| spp,
                                             ~1 | obs),
@@
 
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
 
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + 
+        (~1 | record_num) + 
+        (1 | gr(species_full, cov = A_VR)) + 
+        (1 + max_temp_c| spp) + 
+        (1|trait), 
+        data2 = list(A_VR=A_VR), family = gaussian(), 
+        prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+        control = list(adapt_delta = 0.98, max_treedepth = 12), 
+        chains = 4, thin = 5, iter = 8000, warmup = 1000, cores = 4, data = lnVRQ10_data)
 
@@
     fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
-    fixed <- cbind(Parameter = c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
+    fixed <- cbind(Parameter = c("Intercept", "Mximum Temperature (centered)", "Acclimation Time (centered)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
     rownames(fixed) <- NULL
@@
  # Extract the random effect summaries of the posteriors (SDs)
-    random <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x)))
-    random <- cbind(Parameter = c( "Study", "Phylogeny", "Species", "Trait"), random)
+    random <- rbind(header = rep(0, 4), do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x))))
+    random <- cbind(Parameter = c(" ", "Study", "Phylogeny", "Species (intercept)", "Species (slope max temp)", "Trait"), random)
     rownames(random) <- NULL
@@
 
-    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
+    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 10)
 ```

### 2024-07-09 ms.qmd
Add Sinclair ref which is important

@@
 variability by affecting performance curves and acclimation responses
-[@hardison2024diet]. While marine and freshwater ectotherms were
+[@hardison2024diet; @sinclair2016can]. While marine and freshwater ectotherms were
 capable of partial acclimation it is still important to recognise that,
@@
 @stearns1976life; @angilletta2009thermal; @noble2018developmental;
-@o2019developmental; @Pottier2022]. In addition, plastic responses are
+@o2019developmental; @Pottier2022; @sinclair2016can]. In addition, plastic responses are
 also expected to be costly [@angilletta2009thermal; @Dewitt1998], and

### 2024-07-11 ms.qmd
UPdated ms with some possible simulations to may be better understand the CVR/VR relationships in context of thermal performance curves

@@
 little evidence for publication bias.
+
+#### *Performance Curve Simulations*
+
+To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance (and relative variance) across temperature we conducted a simple simulation.
+To simulate the performance curves, we used a modified Gaussian function (@eq-sim):
+
+$$
+P_{z} = 2\epsilon^{-\frac{(z-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{z-\delta}{\sigma}\right)
+$$ {#eq-sim}
+
+where $z$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where fitness is maximised), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the fitness function or rate variation.
+We simulated 40 individuals with varying performance breadth, optima and rate variation.
+We then calculated the relative variance in fitness across the temperature gradient as the variance in fitness at each temperature divided by the maximum fitness at that temperature.
+The results are shown in @fig-sim.
+
+```{r, sim}
+#| label: sim
+#| echo: false
+
+# Library
+pacman::p_load(latex2exp, ggplot2, dplyr, tidyr, viridis)
+
+# delta; Optimal environment (the optimal temperature where fitness is maximised)
+# sigma; Niche breadth (this is the variation in the fitness surface)
+# alpha; Skewness of the fitness function
+
+# Environmental Temperature
+  set.seed(23)
+     z = seq(0,45,0.1) # Temperature gradient
+     n = 40            # Number of individuals
+ind_sd = 0.5           # Standard deviation among individuals
+
+# Simulation 1. Assume optimum is rather constant among individuals 
+#parameters
+delta =  35  
+sigma =  9 + rnorm(n, 0, ind_sd)
+alpha = -15 + rnorm(n, 0, ind_sd)
+
+ws1<- list()
+for(i in 1:length(alpha)){
+ws1[[i]] <- 2*exp(-(z-delta)^2/(2*sigma[i]^2))*pnorm(alpha[i]*(z-delta)/sigma)
+}
+
+ws1 <- data.frame(do.call(cbind, ws1)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+# Simulation 2: Assume optimum varies but sigma and alpha the same
+#parameters
+
+delta =  35 + rnorm(n, 0, 1) 
+sigma =  9  
+alpha = -15
+
+ws2<- list()
+for(i in 1:length(delta)){
+ws2[[i]] <- 2*exp(-(z-delta[i])^2/(2*sigma^2))*pnorm(alpha*(z-delta[i])/sigma)
+}
+
+ws2 <- data.frame(do.call(cbind, ws2)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+# Simulation 3: Assume optimum sigma and alpha vary
+#parameters
+
+delta =  35 + rnorm(n, 0, 1) 
+sigma =  9  + rnorm(n, 0, ind_sd) 
+alpha = -15 + rnorm(n, 0, ind_sd)
+
+ws3<- list()
+for(i in 1:length(delta)){
+ws3[[i]] <- 2*exp(-(z-delta[i])^2/(2*sigma[i]^2))*pnorm(alpha[i]*(z-delta[i])/sigma[i])
+}
+
+ws3 <- data.frame(do.call(cbind, ws3)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+# Simulation 4: Assume optimum varies but sigma and alpha the same
+#parameters
+
+delta =  35 
+sigma =  9  + rnorm(n, 0, ind_sd) 
+alpha = -15
+
+ws4<- list()
+for(i in 1:length(sigma)){
+ws4[[i]] <- 2*exp(-(z-delta)^2/(2*sigma[i]^2))*pnorm(alpha*(z-delta)/sigma[i])
+}
+
+ws4 <- data.frame(do.call(cbind, ws4)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+```
+
+```{r, sim2}
+#| label: sim2
+#| echo: false
+#| eval: false
+##### Larger simulation
+
+#parameters
+set.seed(23)
+ delta_ind_sd = seq(0.01, 2, by =0.20)
+ alpha_ind_sd = 0.05
+ sigma_ind_sd = seq(0.01, 2, by =0.20)
+        delta =  35 
+        sigma =  9  
+        alpha = -15
+            n = 1000
+
+# create all combuinations of sd
+sims <- expand.grid(delta_ind_sd, alpha_ind_sd, sigma_ind_sd) %>% 
+  mutate(sim = row_number())  %>% rename(delta = Var1, alpha = Var2, sigma = Var3)
+
+sim_results <- data.frame()
+
+for(i in 1:nrow(sims)){
+      optima_sim <- delta + rnorm(n, 0, sims[i, "delta"])
+       alpha_sim <- alpha + rnorm(n, 0, sims[i, "alpha"])
+       sigma_sim <- sigma + rnorm(n, 0, sims[i, "sigma"])
+
+    ws = list()
+    for(j in 1:length(optima_sim)){
+     ws[[j]] <- 2*exp(-(z-optima_sim[j])^2/(2*sigma_sim[j]^2))*pnorm(alpha_sim[j]*(z-optima_sim[j])/sigma_sim[j])
+    }
+
+    # Aggregate the list
+    data <- data.frame(do.call(cbind, ws)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+    # Summarise data
+    sum_sim <- data %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+    sim_results[i,1:5] <- cbind(delta = sims[i, "delta"], alpha = sims[i, "alpha"], sigma = sims[i, "sigma"], lnCVR = log(sum_sim$cv[2]/sum_sim$cv[1]), lnVR = log(sum_sim$sd[2]/sum_sim$sd[1]))
+    print(paste0("Simulation is ", round(i/nrow(sims)*100, 2), "% complete"))
+}
+
+colnames(sim_results) <- c("delta", "alpha", "sigma", "lnCVR", "lnVR")
+
+# Save simulation so that we don't have to re-run each time
+  saveRDS(sim_results, file = "./output/sim_results")
+
+```
+
+```{r, fig-sim}
+#| label: fig-sim
+#| fig-align: center
+#| fig-cap: "Simulated performance curves for *n* = 40 individuals in four hypothetical scenerios with varying performance breadth ($\\sigma$), optima ($\\delta$) and skewness ($\\alpha$).
+Individual performance curves are different colours.
+$lnCVR_{Q_{10}}$ is calculated as the log transformed ratio of the coefficient of variance (CV) in performance at the higher temperature divided by the CV in performance at that temperature at each point along the curve.
+$lnVR_{Q_{10}}$ is calculated as the log transformed ratio of the standard deviation in performance at the higher temperature divided by the standard deviation in performance at that temperature.
+The dashed red line indicates the higher temperature (28$^\\circ$C) and the dashed blue line indicates the lower temperature (18$^\\circ$C).
+Note that the mean ($\\mu$) and standard deviation ($\\sigma$) of physiological rates are shown for each temperature.
+In all simulations, $\\delta$ = 35, $\\sigma$ = 9 and $\\alpha$ = -15, while between individual variation for $\\sigma_{_b_{\\delta}}$ = 1,  $\\sigma_{_b_{\\sigma}}$ = 0.5 and $\\sigma_{_b_{\\alpha}}$ = 0.5."
+
+my_theme <- function(){
+  theme(
+           axis.title.y = element_text(size = 20), 
+           axis.title.x = element_text(size = 20),
+           axis.text.x = element_text(size = 18),
+            axis.text.y = element_text(size = 18),
+            plot.title = element_text(size = 28))
+}
+
+my_annotate  <- function(data, size_ano){
+  list(annotate("text", x = 18-15, y = 2, label = TeX("18$^\\circ$C"), size = size_ano), 
+  annotate("text", x = 28-15, y =2, label = TeX("28$^\\circ$C"), size = size_ano),
+  annotate("text", x = 28-16, y = 1.8, label = TeX(paste0("$\\sigma = $", round(data$sd[2], 2))), size = size_ano),
+  annotate("text", x = 18-16, y = 1.8, label = TeX(paste0("$\\sigma = $", round(data$sd[1], 2))), size = size_ano),
+  annotate("text", x = 28-16, y = 1.6, label = TeX(paste0("$\\mu = $", round(data$mean[2], 2))), size = size_ano),
+  annotate("text", x = 18-16, y = 1.6, label = TeX(paste0("$\\mu = $", round(data$mean[1], 2))), size = size_ano),
+  annotate("text", x = 8, y = 1, label = TeX(paste0("$lnCVR_{Q_{10}}$ = ", round(log(data$cv[2]/data$cv[1]), 2))), size = size_ano),
+  annotate("text", x = 8, y = 0.8, label = TeX(paste0("$lnVR_{Q_{10}}$ = ", round(log(data$sd[2]/data$sd[1]), 2))), size = size_ano))
+}
+size_ano = 10
+
+# mean, SD and CV
+  sum_sim1 <- ws1 %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+sim1 <- ggplot(ws1, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth & Rate") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") + geom_vline(xintercept = 18, linetype = "dashed", color = "blue") + my_annotate(sum_sim1, size_ano)
+
+# mean, SD and CV
+  sum_sim2 <- ws2 %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+sim2 <- ggplot(ws2, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Optima") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim2, size_ano)
+
+# mean, SD and CV
+  sum_sim3 <- ws3 %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+sim3 <- ggplot(ws3, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth, Optima & Rate") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim3, size_ano)
+
+# mean, SD and CV
+  sum_sim4 <- ws4 %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+sim4 <- ggplot(ws4, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim4, size_ano)
+
+p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
+ggsave(p_sim, width = 18.5, height = 18, filename = "./output/figures/figS12.png")
+
+p_sim
+```
+
+```{r, fig-sim2}
+#| label: fig-sim2
+#| fig-align: center
+#| fig-cap: "Expected $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ when varying $\\sigma_{_b_{\\delta}}$ = {0.01, 2} and  $\\sigma_{_b_{\\sigma}}$ = {0.01, 2} while fixing $\\sigma_{_b_{\\alpha}}$ = 0.05.
+In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$, $\\sigma_{_b_{\\sigma}}$ and $\\sigma_{_b_{\\alpha}}$."
+
+sim_results <- readRDS("./output/sim_results")
+bins_cvr = 20
+bins_vr = 20
+
+lncvr_sim_delta_sigma <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnCVR)) +
+  geom_contour_filled(bins = bins_cvr) +
+  scale_color_viridis(direction = -1) +
+  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
+       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
+       fill = TeX("$lnCVR_{Q_{10}}$")) + theme_classic()+ my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
+
+lnvr_sim_delta_sigma <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
+  geom_contour_filled(bins = bins_vr) +
+  scale_color_viridis() +
+  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
+       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
+       fill = TeX("$lnVR_{Q_{10}}$")) + theme_classic() + my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
+
+p_sim2 <- (lncvr_sim_delta_sigma + lnvr_sim_delta_sigma) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
+p_sim2
+```

### 2024-07-11 ms.qmd
Re-rendered

@@
 To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance (and relative variance) across temperature we conducted a simple simulation.
-To simulate the performance curves, we used a modified Gaussian function (@eq-sim):
+To simulate the performance curves, we used a asymmetrical Gaussian function (@eq-sim):
 
@@
 
-where $z$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where fitness is maximised), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the fitness function or rate variation.
+where $z$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximised), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the performance function or rate variation.
+
+We first explored four hypothetical examples to identify key parameters (@fig-sim).
 We simulated 40 individuals with varying performance breadth, optima and rate variation.
-We then calculated the relative variance in fitness across the temperature gradient as the variance in fitness at each temperature divided by the maximum fitness at that temperature.
-The results are shown in @fig-sim.
+We then calculated the relative variance in performance across the temperature gradient as the variance in performance at each temperature divided by the maximum performance at that temperature.
+
+We then conducted a larger simulaton manipulating the level of between individual variation in the optima and performance breadth while holding constant rate variation because optima and breadth appeared to be most important (@fig-sim).
+We simulated *n* = 1000 individual performance curves and took the mean and standard deviation of the performance at two temperatures 10 degrees apart (18 and 28 degrees) to calculate the log coefficient of variation (CV) and log variance ratio in performance.
+
+Our simulations recovered parameter space for $lnVR_{Q_{10}}$ that matched our empirical results (@fig-sim2).
 

### 2024-07-12 ms.qmd
Testing out rate variation for sims, but don't make a difference

@@
 
-```{r, sim2}
-#| label: sim2
-#| echo: false
-#| eval: false
-##### Larger simulation
-
-#parameters
-set.seed(23)
- delta_ind_sd = seq(0.01, 2, by =0.20)
- alpha_ind_sd = 0.05
- sigma_ind_sd = seq(0.01, 2, by =0.20)
-        delta =  35 
-        sigma =  9  
-        alpha = -15
-            n = 1000
-
-# create all combuinations of sd
-sims <- expand.grid(delta_ind_sd, alpha_ind_sd, sigma_ind_sd) %>% 
-  mutate(sim = row_number())  %>% rename(delta = Var1, alpha = Var2, sigma = Var3)
-
-sim_results <- data.frame()
-
-for(i in 1:nrow(sims)){
-      optima_sim <- delta + rnorm(n, 0, sims[i, "delta"])
-       alpha_sim <- alpha + rnorm(n, 0, sims[i, "alpha"])
-       sigma_sim <- sigma + rnorm(n, 0, sims[i, "sigma"])
-
-    ws = list()
-    for(j in 1:length(optima_sim)){
-     ws[[j]] <- 2*exp(-(z-optima_sim[j])^2/(2*sigma_sim[j]^2))*pnorm(alpha_sim[j]*(z-optima_sim[j])/sigma_sim[j])
-    }
-
-    # Aggregate the list
-    data <- data.frame(do.call(cbind, ws)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
-
-    # Summarise data
-    sum_sim <- data %>% 
-              filter(z %in% c(18, 28)) %>% 
-              group_by(z) %>% 
-              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
-
-    sim_results[i,1:5] <- cbind(delta = sims[i, "delta"], alpha = sims[i, "alpha"], sigma = sims[i, "sigma"], lnCVR = log(sum_sim$cv[2]/sum_sim$cv[1]), lnVR = log(sum_sim$sd[2]/sum_sim$sd[1]))
-    print(paste0("Simulation is ", round(i/nrow(sims)*100, 2), "% complete"))
-}
-
-colnames(sim_results) <- c("delta", "alpha", "sigma", "lnCVR", "lnVR")
-
-# Save simulation so that we don't have to re-run each time
-  saveRDS(sim_results, file = "./output/sim_results")
-
-```
-
 ```{r, fig-sim}
@@
 
+```{r, sim2}
+#| label: sim2
+#| echo: false
+#| eval: false
+##### Larger simulation
+
+#parameters
+  set.seed(23)
+ delta_ind_sd = seq(0.01, 2, by = 0.20)
+ alpha_ind_sd = 0.01
+ sigma_ind_sd = seq(0.01, 2, by = 0.20)
+        delta =  35 
+        sigma =  9  
+        alpha = -15 
+            n = 1000
+            z = seq(0,45,0.1) # Temperature gradient
+
+# create all combinations of sd
+sims <- expand.grid(delta_ind_sd, alpha_ind_sd, sigma_ind_sd) %>% 
+  mutate(sim = row_number())  %>% rename(delta = Var1, alpha = Var2, sigma = Var3)
+
+sim_results <- data.frame()
+
+for(i in 1:nrow(sims)){
+      optima_sim <- delta + rnorm(n, 0, sims[i, "delta"])
+       alpha_sim <- alpha + rnorm(n, 0, sims[i, "alpha"])
+       sigma_sim <- sigma + rnorm(n, 0, sims[i, "sigma"])
+
+    ws = list()
+    for(j in 1:length(optima_sim)){
+     ws[[j]] <- 2*exp(-(z-optima_sim[j])^2/(2*sigma_sim[j]^2))*pnorm(alpha_sim[j]*(z-optima_sim[j])/sigma_sim[j])
+    }
+
+    # Aggregate the list
+    data <- data.frame(do.call(cbind, ws)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+    # Summarise data
+    sum_sim <- data %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+    sim_results[i,1:5] <- cbind(delta = sims[i, "delta"], alpha = sims[i, "alpha"], sigma = sims[i, "sigma"], lnCVR = log(sum_sim$cv[2]/sum_sim$cv[1]), lnVR = log(sum_sim$sd[2]/sum_sim$sd[1]))
+    print(paste0("Simulation is ", round(i/nrow(sims)*100, 2), "% complete"))
+}
+
+colnames(sim_results) <- c("delta", "alpha", "sigma", "lnCVR", "lnVR")
+
+# Save simulation so that we don't have to re-run each time
+  saveRDS(sim_results, file = "./output/sim_results")
+
+```
+
 ```{r, fig-sim2}
@@
 
-lncvr_sim_delta_sigma <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnCVR)) +
+lncvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnCVR)) +
   geom_contour_filled(bins = bins_cvr) +
@@
        y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
-       fill = TeX("$lnCVR_{Q_{10}}$")) + theme_classic()+ my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
-
-lnvr_sim_delta_sigma <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
+       fill = TeX("$lnCVR_{Q_{10}}$"), title = TeX("Variation in Rates ($\\sigma_{\\alpha}$ = 0.01)")) + theme_classic()+ my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
+
+lnvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
   geom_contour_filled(bins = bins_vr) +
@@
 
-p_sim2 <- (lncvr_sim_delta_sigma + lnvr_sim_delta_sigma) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
+p_sim2 <- ((lncvr_sim_delta_sigma1 + lnvr_sim_delta_sigma1)) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
+ggsave(p_sim2, width = 20, height = 10, filename = "./output/figures/figS13_new.pdf")
+
+p_sim2 <- image_read("./output/figures/figS13.pdf")
 p_sim2
 ```
+
+```{r}
+#| label: sim3
+#| echo: false
+#| include: false
+
+# Environmental Temperature
+  set.seed(23)
+     z = seq(0,45,0.1) # Temperature gradient
+     n = 40            # Number of individuals
+ind_sd = 0.5           # Standard deviation among individuals
+
+# Simulation 1. Assume optimum is rather constant among individuals 
+#parameters
+delta =  35 + rnorm(n,0,5) 
+sigma =  20 +rnorm(n,0,0.1)
+alpha = 0.0001 +rnorm(n,0,1)
+
+ws1<- list()
+for(i in 1:length(delta)){
+ws1[[i]] <- 2*exp(-(z-delta[i])^2/(2*sigma[i]^2))*pnorm(alpha[i]*(z-delta[i])/sigma[i])
+}
+
+ws1 <- data.frame(do.call(cbind, ws1)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
+
+# mean, SD and CV
+  sum_sim4 <- ws1 %>% 
+              filter(z %in% c(18, 28)) %>% 
+              group_by(z) %>% 
+              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
+
+ggplot(ws1, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim4, 10)
+
+#---------
+# Parameters
+# temp temperature in degrees centigrade
+# r_tref rate at the standardised temperature, tref
+# e activation energy (eV)
+# el low temperature de-activation energy (eV)
+# tl temperature (ºC) at which enzyme is 1/2 active and 1/2 suppressed due to low temperatures
+# eh high temperature de-activation energy (eV)
+# th temperature (ºC) at which enzyme is 1/2 active and 1/2 suppressed due to high temperatures
+# tref standardisation temperature in degrees centigrade. Temperature at which rates are not inactivated by either high or low temperatures
+
+eh <- 1
+el <- 0.2
+tl <- 5
+th <- 40
+tref <- 20
+r_tref <- 1
+e <- 0.65
+temp <- seq(0, 60, 0.1)
+
+# Sharpe-Schoolfield Arrhenius equation
+sharpeschoolfull_1981 <- function(temp, r_tref, e, el, tl, eh, th, tref){
+  tref <- 273.15 + tref
+  k <- 8.62e-05
+  boltzmann.term <- r_tref*exp(e/k * (1/tref - 1/(temp + 273.15)))
+  inactivation.term <- 1/(1 + exp(-el/k * (1/(tl + 273.15) - 1/(temp + 273.15))) + exp(eh/k * (1/(th + 273.15) - 1/(temp + 273.15))))
+  return(boltzmann.term * inactivation.term)
+}
+
+per <- sharpeschoolfull_1981(temp, r_tref, e, el, tl, eh, th, tref)
+
+# Create a data frame for plotting
+df <- data.frame(Temperature = temp, Rate = per)
+
+ggplot(df, aes(x = Temperature, y = Rate)) +
+  geom_line(color = "blue") +
+  theme_minimal() +
+  labs(title = "Sharpe-Schoolfield Arrhenius Equation",
+       x = "Temperature (K)",
+       y = "Rate")
+
+#------
+
+#T body temp,(Ta)
+#QT, temperature coefficient
+#C, constant in shifts of vertical axis
+#Tth, temperature of thermal threshold
+#d, constant in shifts of horizontal axis
+
+pf <- function(T, Tthres, d, C, QT){
+  therm <- C*exp((T*log10(QT))/10)
+      d <- ifelse(T<Tthres, 1, (1-d*(Tthres - T)^2))
+ return(therm*d)
+}
+
+T = seq(5, 50, 0.1)
+Tthres = 25
+d = 0.01
+C = 0.1
+QT = 4
+
+pf1 <- c()
+for(i in 1:length(T)){
+  pf1[i] <- pf(T[i], Tthres, d, C, QT)
+}
+plot(T, pf1, type = "l", xlab = "Temperature", ylab = "Performance", main = "Performance Curve")
+
+```

### 2024-07-12 ms.qmd
Note, tried to may be model performance curve with different function, but can't get one to work and it's not clear how sharpe-schoolfield related to more general whole-organism function.

@@
 ```
-
-```{r}
-#| label: sim3
-#| echo: false
-#| include: false
-
-# Environmental Temperature
-  set.seed(23)
-     z = seq(0,45,0.1) # Temperature gradient
-     n = 40            # Number of individuals
-ind_sd = 0.5           # Standard deviation among individuals
-
-# Simulation 1. Assume optimum is rather constant among individuals 
-#parameters
-delta =  35 + rnorm(n,0,5) 
-sigma =  20 +rnorm(n,0,0.1)
-alpha = 0.0001 +rnorm(n,0,1)
-
-ws1<- list()
-for(i in 1:length(delta)){
-ws1[[i]] <- 2*exp(-(z-delta[i])^2/(2*sigma[i]^2))*pnorm(alpha[i]*(z-delta[i])/sigma[i])
-}
-
-ws1 <- data.frame(do.call(cbind, ws1)) %>% pivot_longer(everything(), names_to = "run", values_to = "fitness")  %>% mutate(z = rep(z,each = n))
-
-# mean, SD and CV
-  sum_sim4 <- ws1 %>% 
-              filter(z %in% c(18, 28)) %>% 
-              group_by(z) %>% 
-              summarise(mean = mean(fitness), sd = sd(fitness), cv = sd/mean, n = n())
-
-ggplot(ws1, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim4, 10)
-
-#---------
-# Parameters
-# temp temperature in degrees centigrade
-# r_tref rate at the standardised temperature, tref
-# e activation energy (eV)
-# el low temperature de-activation energy (eV)
-# tl temperature (ºC) at which enzyme is 1/2 active and 1/2 suppressed due to low temperatures
-# eh high temperature de-activation energy (eV)
-# th temperature (ºC) at which enzyme is 1/2 active and 1/2 suppressed due to high temperatures
-# tref standardisation temperature in degrees centigrade. Temperature at which rates are not inactivated by either high or low temperatures
-
-eh <- 1
-el <- 0.2
-tl <- 5
-th <- 40
-tref <- 20
-r_tref <- 1
-e <- 0.65
-temp <- seq(0, 60, 0.1)
-
-# Sharpe-Schoolfield Arrhenius equation
-sharpeschoolfull_1981 <- function(temp, r_tref, e, el, tl, eh, th, tref){
-  tref <- 273.15 + tref
-  k <- 8.62e-05
-  boltzmann.term <- r_tref*exp(e/k * (1/tref - 1/(temp + 273.15)))
-  inactivation.term <- 1/(1 + exp(-el/k * (1/(tl + 273.15) - 1/(temp + 273.15))) + exp(eh/k * (1/(th + 273.15) - 1/(temp + 273.15))))
-  return(boltzmann.term * inactivation.term)
-}
-
-per <- sharpeschoolfull_1981(temp, r_tref, e, el, tl, eh, th, tref)
-
-# Create a data frame for plotting
-df <- data.frame(Temperature = temp, Rate = per)
-
-ggplot(df, aes(x = Temperature, y = Rate)) +
-  geom_line(color = "blue") +
-  theme_minimal() +
-  labs(title = "Sharpe-Schoolfield Arrhenius Equation",
-       x = "Temperature (K)",
-       y = "Rate")
-
-#------
-
-#T body temp,(Ta)
-#QT, temperature coefficient
-#C, constant in shifts of vertical axis
-#Tth, temperature of thermal threshold
-#d, constant in shifts of horizontal axis
-
-pf <- function(T, Tthres, d, C, QT){
-  therm <- C*exp((T*log10(QT))/10)
-      d <- ifelse(T<Tthres, 1, (1-d*(Tthres - T)^2))
- return(therm*d)
-}
-
-T = seq(5, 50, 0.1)
-Tthres = 25
-d = 0.01
-C = 0.1
-QT = 4
-
-pf1 <- c()
-for(i in 1:length(T)){
-  pf1[i] <- pf(T[i], Tthres, d, C, QT)
-}
-plot(T, pf1, type = "l", xlab = "Temperature", ylab = "Performance", main = "Performance Curve")
-
-```

### 2024-07-12 ms.qmd
Adding some code to run models for lnVR as simulations show that it's important.

@@
 
+###################################################
+  # Model 3.3: Model controlling for acclimation time, 
+  # type and trait category assuming type can vary by habitat
+###################################################
+  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
+    lnVRQ10_data <- lnVRQ10_data %>% 
+                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
+                                                "tissue/organism",
+                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
+                                                "biochemical", trait_category)))
+ # We can also run subsets for each habitat
+   tree_m_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_f_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_t_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
+
+ # cor matrices
+   m_phylo_vr <- vcv(tree_m_vr, corr = TRUE)
+   f_phylo_vr <- vcv(tree_f_vr, corr = TRUE)
+   t_phylo_vr <- vcv(tree_t_vr, corr = TRUE)
+
+if(rerun){
+
+  # Full Bayesian model   
+   model3.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+                                           (1 | record_num) + 
+                                           (1 | gr(species_full, cov = A_VR)) + 
+                                           (1 + max_temp_c | spp) +(1|trait) + 
+                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
+                                         data2 = list(A_VR=A_VR), family = gaussian(), 
+                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnVRQ10_data, trait_broad != "other"))
+    saveRDS(model3.3_btrait_bayes, "./output/models/model3.3_btrait_bayes")
+
+  # Metafor models for creating plots. Subset by habitat to make this easier
+      # Marine
+         model3.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = m_phylo_vr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = filter(lnVRQ10_data, habitat == "m" & trait_broad != "other"))
+         saveRDS(model3.3_m_broad, "output/models/model3.3_m_broad")
+
+      # Freshwater
+         model3.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = f_phylo_vr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"),  phi = 0,
+                              data = filter(lnVRQ10_data, habitat == "f" & trait_broad != "other"))
+          saveRDS(model3.3_f_broad, "output/models/model3.3_f_broad")
+
+      # Terrestrial
+         model3.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = t_phylo_vr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = filter(lnVRQ10_data, habitat == "t" & trait_broad != "other"))
+         saveRDS(model3.3_t_broad, "output/models/model3.3_t_broad")
+
+  } else{
+    model3.3_btrait_bayes <- readRDS("./output/models/model3.3_btrait_bayes")
+    model3.3_m_broad <- readRDS("output/models/model3.3_m_broad")
+    model3.3_f_broad <- readRDS("output/models/model3.3_f_broad")
+    model3.3_t_broad <- readRDS("output/models/model3.3_t_broad")
+}
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       trait_b_data <- data.frame(  type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lnvr_traitb <- fitted(model3.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lnvr_traitb <- cbind(trait_b_data, pred_lnvr_traitb)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lnvr_traitb_post <- fitted(model3.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lnvr_trait_post <-  pred_lnvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lnvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lnvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lnvr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lnvr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lnvr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lnvr_trait_post), function(x) p_value(pmcmc(x))))
+
+###################################################
+  # Model 3.4: Model controlling for acclimation time, 
+  # type and life history stage assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model3.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+  # Save model
+  saveRDS(model3.4, file = "./output/models/lnVRQ10_3.4")
+
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
+                                 (~1 | record_num) + 
+                                 (1 | gr(species_full, cov = A_VR)) + 
+                                 (1 + max_temp_c| spp) + 
+                                 (1|trait) +
+                                 (1|obs), 
+                               data2 = list(A_VR=A_VR), family = gaussian(), 
+                               prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                               control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model
+  saveRDS(model3.4_bayes, file = "./output/models/lnVRQ10_3.4_bayes")
+
+  } else{
+        model3.4 <- readRDS("./output/models/lnVRQ10_3.4")
+  model3.4_bayes <- readRDS("./output/models/lnVRQ10_3.4_bayes")
+}
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       lh_b_data <- data.frame( c_accl_time = 0, 
+                          max_temp_c = 0, 
+                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
+                             habitat = rep(c("m", "f", "t"), each = 4), 
+                           life.hist = rep(c("j", "a"), each = 2))
+
+            # I have no idea why the fitted function is not working on this model. We're doing this the old fashioned way
+            X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = lh_b_data)
+
+            # Extract posteriors
+              post_lh_vr <- posterior_samples(model3.4_bayes, pars = "^b")
+
+        # Now we can do all the calculations in one shot.# Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lh_vr <- apply(t(post_lh_vr),2 , function(x) as.matrix(X)%*%x)
+
+        contrast_lnvr_lh_post <-  pred_lh_vr[c(1,3,5,7,9,11),] - pred_lh_vr[c(2,4,6,8,10,12),] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lnvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     stage = rep(c("j", "a"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnvr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) p_value(pmcmc(x))))
 ```
@@
 To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance (and relative variance) across temperature we conducted a simple simulation.
-To simulate the performance curves, we used a asymmetrical Gaussian function (@eq-sim):
+To simulate performance curves, we used a asymmetrical Gaussian function (@eq-sim):
 
@@
 
-where $z$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximised), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the performance function or rate variation.
-
-We first explored four hypothetical examples to identify key parameters (@fig-sim).
-We simulated 40 individuals with varying performance breadth, optima and rate variation.
+where $z$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the performance function or rate variation.
+While we could have used other performance curve functions (e.g., Arrhenius), our intentions were not to model the exact curves (which are not know) but rather identify what might vary across the major habitat types that could contribute to the different patterns of variance change at higher temperatures we observed across habitats.
+
+We first explored four hypothetical examples to identify key parameters from this function that appear to impact $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ the most (@fig-sim).
+To achieve this, we simulated 40 individuals with varying amounts of between individual variation in performance breadth, optima and rate variation.
 We then calculated the relative variance in performance across the temperature gradient as the variance in performance at each temperature divided by the maximum performance at that temperature.
-
-We then conducted a larger simulaton manipulating the level of between individual variation in the optima and performance breadth while holding constant rate variation because optima and breadth appeared to be most important (@fig-sim).
+This simple analysis identified thermal optima and breath as being the major factors likely leading to the observed patterns in $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ we identify in our meta-analysis.
+
+We then conducted a larger simulation that expanded the parameter space by manipulating the level of between individual variation in both the thermal optima and performance breadth while holding constant rate variation because optima and breadth appeared to be most important (@fig-sim).
 We simulated *n* = 1000 individual performance curves and took the mean and standard deviation of the performance at two temperatures 10 degrees apart (18 and 28 degrees) to calculate the log coefficient of variation (CV) and log variance ratio in performance.
-
-Our simulations recovered parameter space for $lnVR_{Q_{10}}$ that matched our empirical results (@fig-sim2).
+Our simulations assume that the value of variance does not change depending on the temperatures choose, but given our analysis restricts the data to temperatures within the normal thermal range of each species, standardising a temperature window in this way is likely comparable.
+
+Overall, our simulations recovered plausible parameter space for levels of between individual variation in thermal optima and breath that matched some of our empirical results (@fig-sim2).
+While $lnCVR_{Q_{10}}$ ([@fig-sim2]A) values were overestimated compared to our empirical results, $lnVR_{Q_{10}}$ nicely matched ([@fig-sim2]B).
+Overestimation of $lnCVR_{Q_{10}}$ is likely the result of the rate parameter being too steep in our model (i.e., $Q_{10}$ being too high) compared to what is typical in nature resulting in rates at higher temperatures to be larger than what is expected.
+This would inflate the coefficient of variation because the variance is standardised by the rates at the respective temperatures.
+Using alternative performance functions may correct this deviation, but this question is out of scope here and would require a much larger simulation.
+Regardless, $lnCVR_{Q_{10}}$ largely showed similar patterns to $lnVR_{Q_{10}}$.
+
+Importantly, our $lnVR_{Q_{10}}$ values matched our empirical results quite nicely.
+Interestingly, for a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]B).
+In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2]B).
 
@@
 
-sim1 <- ggplot(ws1, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth & Rate") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") + geom_vline(xintercept = 18, linetype = "dashed", color = "blue") + my_annotate(sum_sim1, size_ano)
+sim1 <- ggplot(ws1, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth & Rate") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") + geom_vline(xintercept = 18, linetype = "dashed", color = "blue") + my_annotate(sum_sim1, size_ano) + theme(legend.position = "none")
 
@@
 
-sim2 <- ggplot(ws2, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Optima") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim2, size_ano)
+sim2 <- ggplot(ws2, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Optima") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim2, size_ano)+ theme(legend.position = "none")
 
@@
 
-sim3 <- ggplot(ws3, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth, Optima & Rate") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim3, size_ano)
+sim3 <- ggplot(ws3, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth, Optima & Rate") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim3, size_ano)+ theme(legend.position = "none")
 
@@
 
-sim4 <- ggplot(ws4, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim4, size_ano)
+sim4 <- ggplot(ws4, aes(x = z, y = fitness, color = run)) + geom_line() + theme_classic() + labs(y = "Physiological Rate", x = TeX("Temperature ($^\\circ$C)"), color = "Individual", title = "Thermal Breadth") + scale_color_viridis_d() + my_theme()+ geom_vline(xintercept = 28, linetype = "dashed", color = "red") +     geom_vline(xintercept = 18, linetype = "dashed", color = "blue")   + my_annotate(sum_sim4, size_ano)+ theme(legend.position = "none")
 
 p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
-ggsave(p_sim, width = 18.5, height = 18, filename = "./output/figures/figS12.png")
+ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS12.png")
 
@@
 #| fig-align: center
-#| fig-cap: "Expected $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$ when varying $\\sigma_{_b_{\\delta}}$ = {0.01, 2} and  $\\sigma_{_b_{\\sigma}}$ = {0.01, 2} while fixing $\\sigma_{_b_{\\alpha}}$ = 0.05.
-In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$, $\\sigma_{_b_{\\sigma}}$ and $\\sigma_{_b_{\\alpha}}$."
+#| fig-cap: "Expected $lnCVR_{Q_{10}}$ (A) and $lnVR_{Q_{10}}$ (B) when varying $\\sigma_{_b_{\\delta}}$ = {0.01, 2} and  $\\sigma_{_b_{\\sigma}}$ = {0.01, 2} while fixing $\\sigma_{_b_{\\alpha}}$ = 0.01.
+In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$, $\\sigma_{_b_{\\sigma}}$ and $\\sigma_{_b_{\\alpha}}$.
+(B) The parameter space that match observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms.
+Dashed lines indicate the relative differences between the three habitat types when holding one parameter constant."
 

### 2024-07-12 ms.qmd
Added new supp plot for lnVR

@@
 For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
-"
+$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
 #| echo: false
@@
     flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 10)
+```
+
+```{r, fig-lnvrlh}
+#| label: fig-lnvrlh
+#| echo: false
+#| fig-cap: "Estimated mean acclimation and acute $lnVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for marine (A), freshwater (B) and terrestrial (C) ectotherms.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
+$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lnvr_lh <- lnVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+
+x.pos = c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+###############
+## lnVR Q10
+###############
+
+t_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+yloc = c(1.5, 2.5)
+
+m_r <- n_lnvr_lh %>% filter(habitat == "m")
+f_r <- n_lnvr_lh %>% filter(habitat == "f")
+t_r <- n_lnvr_lh %>% filter(habitat == "t")
+
+p1_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5,3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+figvr_lh <-(p3_vr | p1_vr | p2_vr) + plot_annotation(tag_levels = "A") 
+ggsave(figvr_lh, filename = "./output/figures/figSlh.pdf", width = 28, height = 10, device = "pdf")
+
+figvr_lh <- magick::image_read("./output/figures/figSlh.pdf")
+figvr_lh
+
 ```

### 2024-07-13 R/functions.R
Updtaed ignore and write new function for pooling acute and acclim trait types for Bayesian posteriors

@@ -466,4 +466,31 @@ post_summary <- function(x){
 #' @description Converts a single estimate of lnCVR10 into a 1 degree Celsius estimate
  lncvr_1c <-  function(x){
         return(x/10)
-  }
+ }
+ 
+ 
+ #' @title get_whole_bio
+ #' @description Takes posterior predictions of acute and acclimation effect sizes across habitats and broad trait categories, pools the acute and acclimation effects and then calculates a contrasts between biochem and whole-orgamism for effects sizes. Returns a data frame.
+ get_whole_bio <- function(post, habitat, trait_b_data){
+   # Find columns that match and subset cols from posterior
+   cols_habit <- as.numeric(rownames(trait_b_data)[trait_b_data$habitat == habitat])
+   
+   hab_type <- post[,cols_habit]
+   
+   # Find cols that match names
+   type1 <- c(hab_type[,1], hab_type[,1])  # Tissue Traits Pooled
+   type2 <- c(hab_type[,3], hab_type[,4])  # Biochem Traits Pooled
+   
+   # Now, find the contrast
+   contrast <-  type2 - type1
+   
+   # Summarise info about contrast
+   data_sum <- data.frame( habitat = habitat,
+                           comparison = paste0("Biochem - Tissue"),
+                           Est. = mean(contrast),
+                           `95% L CI` = quantile(contrast, 0.025),
+                           `95% U CI` = quantile(contrast, 0.975),
+                           `pmcmc` = p_value(pmcmc(contrast)), check.names = FALSE, row.names = NULL)
+   return(data_sum)
+   
+ }

### 2024-07-13 ms.qmd
Updating code and figures to move lnVR in the main MS and lnCVR in supplement as it's jut too difficult to interpret lnCVR and we are alerady analysing lnRR (mean) so better to keep the variance lnVR bedide it so that it's cleaer and connects better to readers. CVR is roughly the same anyway

@@
 ---
-title: "Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change"
+title: "Physiological plasticity and variance in physiological rates vary across ectotherm populations"
 bibliography: ./bib/refs.bib
@@
 
-@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate
+where parameters are defined above. @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate
 variance (@eq-lnq10VR) across a 10°C temperature change along with its
-sampling variance (@eq-slnq10VR). While this is a useful metric, as
+sampling variance (@eq-slnq10VR). As
 discussed by @Nakagawa2015-fo there is often a strong mean-variance
-relationship that needs to be accounted for in analysing changes in
-variance. As such, we calculated the coefficient of variation, which
-standardizes changes in variance for changes in means as follows:
+relationship. As such, the coefficient of variation is often used because it allows one to
+standardize changes in variance as the mean changes as follows:
 
@@
 relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make certain assumptions about mean-variance relationships, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
 
@@
 such, positive effect sizes suggest that the mean (i.e.,
-$lnRR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger
+$lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger
 at the higher of the two temperatures (numerator) when standardized to
-10°C. Importantly, $lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and
-$lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the
-effect of temperature on physiological rates (or changes in relative
+10°C. Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the
+effect of temperature on physiological rates (or changes in
 variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further
@@
 
+  # Calculated weighted mean by sample size. 
+    f_RR_mean <- (f_acute * N[1,"n"][[1]] + f_acclim * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_RR_mean)
+    m_RR_mean <- (m_acute * N[3,"n"][[1]] + m_acclim * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_RR_mean)
+    t_RR_mean <- (t_acute * N[5,"n"][[1]] + t_acclim * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_RR_mean)
+
 ####################################################
@@
                                                        p = sapply(data.frame(contrast_lnrr_trait_post), function(x) p_value(pmcmc(x))))
-
+       # Contrasts for pooled acute and acclimation across trait categories
+
+            contrast_lnrr_trait_cat_stats <- rbind(get_whole_bio(pred_lnrr_trait_post, habitat = "t", trait_b_data),
+                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "m", trait_b_data),
+                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "f", trait_b_data))
 ###########################################################
@@
 
-```{r, lncvrq10}
-#| label: lncvrq10
+```{r, lnvrq10}
+#| label: lnvrq10
 #| echo: false
@@
 #| include: false
-#| cache: false
+#| cache: true
 
 #############
-  ## lnCVRQ10
+  ## lnVRQ10
 #############
@@
 #################################################
-  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
@@
 # Check and prune tree
-  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
+  tree_lnVR <- tree_checks(data = lnVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnVRQ10_data, tree = tree_lnVR, dataCol = "species_full", type = "check") # Good
 
 # Create the phylo correlation matrix
-  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
-          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
+  phylo_cor_VR <- vcv(tree_lnVR, cor = TRUE)
+          A_VR <- vcv(tree_lnVR, cor = FALSE) # For bayes, need cov matrix
 
 ###################################################
-  # Model 2.1: Intercept only model.
+  # Model 3.1: Intercept only model.
   # Used for heterogeneity analysis
@@
 if(rerun){
-  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+  model3.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+  model3.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
 
   # Save model1.1
-  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
-  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
+  saveRDS(model3.1, file = "./output/models/lnVRQ10_3.1")
+  saveRDS(model3.1_bayes, file = "./output/models/lnVRQ10_3.1_bayes")
 } else{ 
-        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
-  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
+        model3.1 <- readRDS("./output/models/lnVRQ10_3.1")
+  model3.1_bayes <- readRDS("./output/models/lnVRQ10_3.1_bayes")
 }
@@
 # Heterogeneity analysis
-   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
-  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
+   w_VR <- with(lnVRQ10_data, 1/V) # weights
+  sv_VR <- sum(w_VR*(dim(lnVRQ10_data)[1]-1)) / (sum(w_VR)^2 + sum(w_VR^2))
 
 # extract posterior sds, but square them to turn to variance
-  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
-  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
-
-    res_cvr <- posteriors_2.1[,"sigma"]
-   stdy_cvr <- posteriors_2.1[,"record_num"]
-  phylo_cvr <- posteriors_2.1[,"species_full"]
-    spp_cvr <- posteriors_2.1[,"spp"]
-  trait_cvr <- posteriors_2.1[,"trait"]
-  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
+  posteriors_3.1 <- posterior_samples(model3.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_3.1) <- gsub("__Intercept", "", colnames(posteriors_3.1))
+  colnames(posteriors_3.1) <- gsub("sd_", "", colnames(posteriors_3.1))
+
+    res_VR <- posteriors_3.1[,"sigma"]
+   stdy_VR <- posteriors_3.1[,"record_num"]
+  phylo_VR <- posteriors_3.1[,"species_full"]
+    spp_VR <- posteriors_3.1[,"spp"]
+  trait_VR <- posteriors_3.1[,"trait"]
+  total_VR <- phylo_VR + spp_VR + res_VR + sv_VR + stdy_VR + trait_VR
 
   # Calculate I2
-     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
-   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
-     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
-    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
-   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
-     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
+     tot_i2_VR <- (sv_VR / total_VR)*100    ; mean(tot_i2_VR)  ; quantile(tot_i2_VR, c(0.025, 0.975))
+   phylo_i2_VR <- (phylo_VR / total_VR)*100 ; mean(phylo_i2_VR); quantile(phylo_i2_VR, c(0.025, 0.975))
+     spp_i2_VR <- (spp_VR / total_VR)*100   ; mean(spp_i2_VR)  ; quantile(spp_i2_VR, c(0.025, 0.975))
+    stdy_i2_VR <- (stdy_VR / total_VR)*100  ; mean(stdy_i2_VR) ; quantile(stdy_i2_VR, c(0.025, 0.975))
+   trait_i2_VR <- (trait_VR / total_VR)*100 ; mean(trait_i2_VR); quantile(trait_i2_VR, c(0.025, 0.975))
+     res_i2_VR <- (res_VR / total_VR)*100   ; mean(res_i2_VR)  ; quantile(res_i2_VR, c(0.025, 0.975))
 
   # Table
-     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
-                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
+     i2_lnVR <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_VR),mean(spp_i2_VR), mean(stdy_i2_VR), mean(trait_i2_VR)),
+                           lci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[1], quantile(spp_i2_VR, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_VR, c(0.025, 0.975))[1], quantile(trait_i2_VR, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[2], quantile(spp_i2_VR, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_VR, c(0.025, 0.975))[2], quantile(trait_i2_VR, c(0.025, 0.975))[2]))
 
 ###################################################
-  # Model 2.2: Model controlling for acclimation time, 
+  # Model 3.2: Model controlling for acclimation time, 
   # type and habitat assuming type can vary by habitat
@@
   # More realistic model 
-  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+  model3.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + 
+        (~1 | record_num) + 
+        (1 | gr(species_full, cov = A_VR)) + 
+        (1 + max_temp_c| spp) + 
+        (1|trait), 
+        data2 = list(A_VR=A_VR), family = gaussian(), 
+        prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+        control = list(adapt_delta = 0.98, max_treedepth = 12), 
+        chains = 4, thin = 5, iter = 8000, warmup = 1000, cores = 4, data = lnVRQ10_data)
 
   # Save model1.2
-  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
-  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
+  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
+  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")
 
   } else{
-        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
-  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
+        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
+  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
 }
@@
 
-  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
-  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
-  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
-  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
-  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
-  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
-  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
+  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
+  f_acute_VR  <- posteriors_3.2[,"b_Intercept"]; pmcmc(f_acute_VR)
+  f_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
+  m_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
+  m_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
+  t_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
+  t_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
 
@@
   # First get sample sizes
-    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+    N <- lnVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
 
   # Calculated weighted mean by sample size. 
-    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
-    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
-    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+    f_VR_mean <- (f_acute_VR * N[1,"n"][[1]] + f_acclim_VR * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_VR_mean)
+    m_VR_mean <- (m_acute_VR * N[3,"n"][[1]] + m_acclim_VR * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_VR_mean)
+    t_VR_mean <- (t_acute_VR * N[5,"n"][[1]] + t_acclim_VR * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_VR_mean)
 
   # Lets now convert these to a %
-    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
-    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
-    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
+    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) 
+    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) 
+    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100)
+
+  # Now, lets get contrasts between habitats averaged over type
+      f_m_c <- f_VR_mean - m_VR_mean   ; pmcmc(f_m_c); mean(f_m_c)
+      f_t_c <- t_VR_mean_ef - f_VR_mean; pmcmc(f_t_c); mean(f_t_c)
+      m_t_c <- t_VR_mean_ef - m_VR_mean; pmcmc(m_t_c); mean(m_t_c)
 
 ###################################################
-  # Model 2.3: Model controlling for acclimation time, 
+  # Model 3.3: Model controlling for acclimation time, 
   # type and trait category assuming type can vary by habitat
@@
   # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
-    lnCVRQ10_data <- lnCVRQ10_data %>% 
+    lnVRQ10_data <- lnVRQ10_data %>% 
                     mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
@@
  # We can also run subsets for each habitat
-   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
-   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
-   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_m_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_f_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_t_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
 
  # cor matrices
-   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
-   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
-   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
+   m_phylo_vr <- vcv(tree_m_vr, corr = TRUE)
+   f_phylo_vr <- vcv(tree_f_vr, corr = TRUE)
+   t_phylo_vr <- vcv(tree_t_vr, corr = TRUE)
 
@@
   # Full Bayesian model   
-   model2.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+   model3.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
                                            (1 | record_num) + 
-                                           (1 | gr(species_full, cov = A)) + 
+                                           (1 | gr(species_full, cov = A_VR)) + 
                                            (1 + max_temp_c | spp) +(1|trait) + 
                                            (1 + trait_broad |gr(obs, cor = FALSE)),  
-                                         data2 = list(A=A), family = gaussian(), 
+                                         data2 = list(A_VR=A_VR), family = gaussian(), 
                                          prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
                                          control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnCVRQ10_data, trait_broad != "other"))
-    saveRDS(model2.3_btrait_bayes, "./output/models/model2.3_btrait_bayes")
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnVRQ10_data, trait_broad != "other"))
+    saveRDS(model3.3_btrait_bayes, "./output/models/model3.3_btrait_bayes")
 
@@
       # Marine
-         model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+         model3.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 + trait_broad| obs),
-                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              R = list(species_full = m_phylo_vr), dfs = "contain", 
                               test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = filter(lnCVRQ10_data, habitat == "m" & trait_broad != "other"))
-         saveRDS(model2.3_m_broad, "output/models/model2.3_m_broad")
+                              data = filter(lnVRQ10_data, habitat == "m" & trait_broad != "other"))
+         saveRDS(model3.3_m_broad, "output/models/model3.3_m_broad")
 
       # Freshwater
-         model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+         model3.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 + trait_broad| obs),
-                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
+                              R = list(species_full = f_phylo_vr), dfs = "contain", 
                               test = "t", struct = c("GEN","HCS"),  phi = 0,
-                              data = filter(lnCVRQ10_data, habitat == "f" & trait_broad != "other"))
-          saveRDS(model2.3_f_broad, "output/models/model2.3_f_broad")
+                              data = filter(lnVRQ10_data, habitat == "f" & trait_broad != "other"))
+          saveRDS(model3.3_f_broad, "output/models/model3.3_f_broad")
 
       # Terrestrial
-         model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+         model3.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 + trait_broad| obs),
-                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
+                              R = list(species_full = t_phylo_vr), dfs = "contain", 
                               test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = filter(lnCVRQ10_data, habitat == "t" & trait_broad != "other"))
-         saveRDS(model2.3_t_broad, "output/models/model2.3_t_broad")
+                              data = filter(lnVRQ10_data, habitat == "t" & trait_broad != "other"))
+         saveRDS(model3.3_t_broad, "output/models/model3.3_t_broad")
 
   } else{
-    model2.3_btrait_bayes <- readRDS("./output/models/model2.3_btrait_bayes")
-    model2.3_m_broad <- readRDS("output/models/model2.3_m_broad")
-    model2.3_f_broad <- readRDS("output/models/model2.3_f_broad")
-    model2.3_t_broad <- readRDS("output/models/model2.3_t_broad")
+    model3.3_btrait_bayes <- readRDS("./output/models/model3.3_btrait_bayes")
+    model3.3_m_broad <- readRDS("output/models/model3.3_m_broad")
+    model3.3_f_broad <- readRDS("output/models/model3.3_f_broad")
+    model3.3_t_broad <- readRDS("output/models/model3.3_t_broad")
 }
@@
        # Predict from model. Note this is the summary.
-         pred_lncvr_traitb <- fitted(model2.3_btrait_bayes, 
+         pred_lnvr_traitb <- fitted(model3.3_btrait_bayes, 
                                      newdata = trait_b_data, re_formula = NA,
@@
                                      robust = FALSE)
-         pred_lncvr_traitb <- cbind(trait_b_data, pred_lncvr_traitb)
+         pred_lnvr_traitb <- cbind(trait_b_data, pred_lnvr_traitb)
 
@@
 Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lncvr_traitb_post <- fitted(model2.3_btrait_bayes, 
+            pred_lnvr_traitb_post <- fitted(model3.3_btrait_bayes, 
                                      newdata = trait_b_data, re_formula = NA,
@@
                                      robust = FALSE)
-        contrast_lncvr_trait_post <-  pred_lncvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lncvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+        contrast_lnvr_trait_post <-  pred_lnvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lnvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
 
         # Contrast statistics
-            contrast_lncvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+            contrast_lnvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
                                                      trait = rep(c("tissue/organism", "biochemical"), each = 1),
-                                                    diff = sapply(data.frame(contrast_lncvr_trait_post), mean),
-                                                     l95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.025)),
-                                                     u95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.975)),
-                                                       p = sapply(data.frame(contrast_lncvr_trait_post), function(x) p_value(pmcmc(x))))
-
-   # Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
+                                                    diff = sapply(data.frame(contrast_lnvr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lnvr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lnvr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lnvr_trait_post), function(x) p_value(pmcmc(x))))
+        # Contrasts for pooled acute and acclimation across trait categories
+
+            contrast_lnvr_trait_cat_stats <- rbind(get_whole_bio(pred_lnvr_traitb_post, habitat = "t", trait_b_data),
+                                                        get_whole_bio(pred_lnvr_traitb_post, habitat = "m", trait_b_data),
+                                                        get_whole_bio(pred_lnvr_traitb_post, habitat = "f", trait_b_data))
 
 ###################################################
-  # Model 2.4: Model controlling for acclimation time, 
+  # Model 3.4: Model controlling for acclimation time, 
   # type and life history stage assuming type can vary by habitat
@@
   # More realistic model 
-  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+  model3.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
   # Save model
-  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
-
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
+  saveRDS(model3.4, file = "./output/models/lnVRQ10_3.4")
+
+   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
                                  (~1 | record_num) + 
-                                 (1 | gr(species_full, cov = A_CVR)) + 
+                                 (1 | gr(species_full, cov = A_VR)) + 
                                  (1 + max_temp_c| spp) + 
@@
                                  (1|obs), 
-                               data2 = list(A_CVR=A_CVR), family = gaussian(), 
+                               data2 = list(A_VR=A_VR), family = gaussian(), 
                                prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
@@
   # Save model
-  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
+  saveRDS(model3.4_bayes, file = "./output/models/lnVRQ10_3.4_bayes")
 
   } else{
-        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
-  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
+        model3.4 <- readRDS("./output/models/lnVRQ10_3.4")
+  model3.4_bayes <- readRDS("./output/models/lnVRQ10_3.4_bayes")
 }
@@
             # Extract posteriors
-              post_lh <- posterior_samples(model2.4_bayes, pars = "^b")
+              post_lh_vr <- posterior_samples(model3.4_bayes, pars = "^b")
 
@@
 Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lh <- apply(t(post_lh),2 , function(x) as.matrix(X)%*%x)
-
-        contrast_lncvr_lh_post <-  pred_lh[c(1,3,5,7,9,11),] - pred_lh[c(2,4,6,8,10,12),] # Acclimation - acute.
+            pred_lh_vr <- apply(t(post_lh_vr),2 , function(x) as.matrix(X)%*%x)
+
+        contrast_lnvr_lh_post <-  pred_lh_vr[c(1,3,5,7,9,11),] - pred_lh_vr[c(2,4,6,8,10,12),] # Acclimation - acute.
 
         # Contrast statistics
-            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+            contrast_lnvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
                                                      stage = rep(c("j", "a"), each = 1),
-                                                    diff = apply(data.frame(contrast_lncvr_lh_post), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) p_value(pmcmc(x))))
+                                                    diff = apply(data.frame(contrast_lnvr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) p_value(pmcmc(x))))
 ```
@@
 #| fig-cap: "A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
-B) Mean acute and acclimation $lnCVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
 For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 ################## 
-  # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
-But, there is a clear reduction in between individual variance for terrestrial species.
-As temperature get hotter then the variance in physiological rates decreases.
-This is not true of aquatic systems.
-
-  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
-
-  x1 = 1.4
-  x2 = 2.4
-  x3 = 3.4
-
-  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8,  k.pos = "none")  +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-
-  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) +
-
-  annotate("text", x = x1, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
-         annotate("text", x = x1, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = x1-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 8) + 
-  annotate("text", x = x1-0.20, y = 1, label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = x2, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
-     annotate("text", x = x2, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = x2-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 8) +
-  annotate("text", x = x2-0.20, y = 1, label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = x3+0.10, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
-  annotate("text", x = x3+0.10, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = x3-0.10, y = 1, label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) + 
-  annotate("text", x = x3-0.10, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 8) +
-
-    labs(shape = "Type") +
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)
+    # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
+  k_vr <- manual_extract(model3.2, mod = "habitat", group = "spp", exclude = NULL)
+
+  p3b <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", by = "type", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8) +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-2,3) +
+
+     annotate("text", x = 1.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+    annotate("text", x = 1.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = 1.20, y = -2, label =paste0(round(mean(f_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+    annotate("text", x = 2.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+    annotate("text", x = 2.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = 2.20, y = -2, label =paste0(round(mean(m_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ = ", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) +
+    annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col)) + annotate("text", y = 2.5, x = c(1.3, 2.3, 3.3)+0.1, label = TeX(paste0("\\it{k} = ", k_vr$k, " (", k_vr$sdy, ")")), size = 6) + scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3))
 
@@
                                        axis.text = element_text(size = 24),
-                                       axis.text.y = element_blank(),
+                                       axis.text.y = element_text(angle = 45, size = 24),
                                        legend.title = element_text(size = 30),
                                legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")
+                               title = element_text(size = 24), legend.position = "top")
 
@@
 
-### *Relative variation in physiological rates is reduced in terrestrial and marine ectotherms*
-
-Relative variance in physiological rates ($lnCVR_{Q_{10}}$) showed a
-decrease with increasing temperature across all habitat types, which was
-especially pronounced in terrestrial and marine ectotherms. The total
-proportion of heterogeneity in $lnCVR_{Q_{10}}$ was lower compared to
-$lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_cvr)`, 95% CI:
-`r quantile(tot_i2_cvr, 0.025)` to `r quantile(tot_i2_cvr, 0.975)`),
+### *Variation in physiological rates increases in aquatic but not terrestrial ectotherms*
+
+Variance in physiological rates ($lnVR_{Q_{10}}$) showed an
+increase with increasing temperature across all habitat types.
+However, physiological rate variance increase significantly more in freshwater (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c)`, 95% CI: `r quantile(f_t_c, 0.025)` to `r quantile(f_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c))`) and marine ectotherms (marine vs terrestrial: $\beta$ = `r mean(m_t_c)`, 95% CI: `r quantile(m_t_c, 0.025)` to `r quantile(m_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c))`) compared to the limited increase in terrestrial ecotherms (@fig-2).
+The total
+proportion of heterogeneity in $lnVR_{Q_{10}}$ was lower compared to
+$lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI:
+`r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`),
 with most variation being driven by between-study and trait differences
-("Model 1"; see Supplement @fig-s3). There were no differences between
-$lnCVR_{Q_{10_{acute}}}$ and $lnCVR_{Q_{10_{acclimation}}}$. Reductions
+("Model 1"; see *Supplementary Materials* @fig-s3). There were no differences between
+$lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$. Reductions
 in variance were driven by slower increases in the variance in
@@
 smaller than 1 and varying across habitats (see *Supplementary
-Materials*; @tbl-slopes & @fig-mv). There was a `r mean(t_cvr_mean_ef)`%
-(95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to
-`r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(t_cvr_mean)`) reduction in relative physiological rate variance
-for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI:
-`r quantile(m_cvr_mean_ef, 0.025)[1]` to
-`r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(m_cvr_mean)`) reduction in relative variation for marine
+Materials*; @tbl-slopes & @fig-mv). There was a `r mean(t_VR_mean_ef)`%
+(95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to
+`r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(t_VR_mean)`) reduction in relative physiological rate variance
+for terrestrial ectotherms and a `r mean(m_VR_mean_ef)`% (95% CI:
+`r quantile(m_VR_mean_ef, 0.025)[1]` to
+`r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(m_VR_mean)`) reduction in relative variation for marine
 ectotherms when temperatures increased by 10$^\circ$C. In contrast,
@@
 physiological rate variance at high temperatures
-(`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]`
-to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(f_cvr_mean)`) (results from "Model 2").
+(`r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]`
+to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
+`r pmcmc(f_VR_mean)`) (results from "Model 2"). The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
 
 Across habitats whole-organism versus biochemical processes showed a
-similar decrease in relative variance in physiological rates
+similar change in variance in physiological rates
 ([@fig-btrait]D-F; see *Supplementary Materials*, @fig-cvrtrait) for more detailed trait
@@
 #| label: fig-btrait
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across marine (A & D), freshwater (B & E) and terrestrial (C & F) habitats.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across marine (A & D), freshwater (B & E) and terrestrial (C & F) habitats.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
               group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
-n_lncvr_btrait <- lnCVRQ10_data %>% filter(trait_broad != "other") %>% 
+n_lnvr_btrait <- lnVRQ10_data %>% filter(trait_broad != "other") %>% 
               group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
@@
 ############
-# CVR
+# lnVR
 ############
-m_cv <- n_lncvr_btrait %>% filter(habitat == "m")
-f_cv <- n_lncvr_btrait %>% filter(habitat == "f")
-t_cv <- n_lncvr_btrait %>% filter(habitat == "t")
-
-t_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-m_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-f_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-
-p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
+m_r_vr <- n_lnvr_btrait %>% filter(habitat == "m")
+f_r_vr <- n_lnvr_btrait %>% filter(habitat == "f")
+t_r_vr <- n_lnvr_btrait %>% filter(habitat == "t")
+
+t_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+yloc = c(1.5, 2.5)
+
+p1_vr_trait <- orchard_plot(model3.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r_vr$k, " (", m_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b_vr$diff, " [", m_trait_b_vr$l95, " to ", m_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_vr$p)), hjust = 0, size = 8)
+
+p2_vr_trait <- orchard_plot(model3.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r_vr$k, " (", f_r_vr$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b_vr$diff, " [", f_trait_b_vr$l95, " to ", f_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_vr$p)), hjust = 0, size = 8)
+
+p3_vr_trait <- orchard_plot(model3.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5, 3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r_vr$k, " (", t_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b_vr$diff, " [", t_trait_b_vr$l95, " to ", t_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_vr$p)), hjust = 0, size = 8)
 
@@
 ############
-figbtrait <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
+figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
 ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
@@
 #| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnCVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for marine (A & D), freshwater (B & E) and terrestrial (C & F) ectotherms.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for marine (A & D), freshwater (B & E) and terrestrial (C & F) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 n_lnrr_lh  <- lnRRQ10_data  %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
-n_lncvr_lh <- lnCVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+n_lnvr_lh <- lnVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
 
@@
 ###############
-# ln CVR
+## lnVR Q10
 ###############
-m_cv <- n_lncvr_lh %>% filter(habitat == "m")
-f_cv <- n_lncvr_lh %>% filter(habitat == "f")
-t_cv <- n_lncvr_lh %>% filter(habitat == "t")
-
-  t_trait_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-m_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-f_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-
-p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
-
-fig4 <-(p3 | p1 | p2) / (p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
+
+t_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+yloc = c(1.5, 2.5)
+
+m_r <- n_lnvr_lh %>% filter(habitat == "m")
+f_r <- n_lnvr_lh %>% filter(habitat == "f")
+t_r <- n_lnvr_lh %>% filter(habitat == "t")
+
+p1_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5,3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+fig4 <-(p3 | p1 | p2) / (p3_vr | p1_vr | p2_vr) + plot_annotation(tag_levels = "A") 
 ggsave(fig4, filename = "./output/figures/fig5.pdf", width = 28, height = 14, device = "pdf")
@@
 
-```{r wildlncvr}
-#| label: wildlncvr
+```{r wildlnvr}
+#| label: wildlnvr
 #| cache: true
@@
 # Subset the data
-  lnCVRQ10_data_wild <- data_long2 %>% 
-    filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+  lnVRQ10_data_wild <- data_long2 %>% 
+    filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
                         mutate(spp = species_full, 
@@
 # Now, join climate data to full data. This will give us all the climate variability data for each site across time
-  lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
+  lnVRQ10_data_wild <- left_join(lnVRQ10_data_wild, climate2, by = "match")
 
@@
 # Check and prune tree
-  tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
+  tree_lnvr_wild <- tree_checks(data = lnVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnVRQ10_data_wild, tree = tree_lnvr_wild, dataCol = "species_full", type = "check") # Good
 
 # Create the phylo correlation matrix
-  phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
-          A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
+  phylo_cor_wild_vr <- vcv(tree_lnvr_wild, cor = TRUE)
+          A_wild_vr <- vcv(tree_lnvr_wild, cor = FALSE) # For bayes, need cov matrix
 
 # Scale environment variables
-    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
+    lnVRQ10_data_wild <- lnVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
                                                         acf_all_c = scale(acf_all),
@@
 ####################################################
-  # Model 4.3: Model environmental variability by acute/acclim
+  # Model 5.3: Model environmental variability by acute/acclim
 ####################################################
@@
   # More realistic model with 
-  model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
+  model5.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
                                        random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.3
-  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
-  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
+                              R = list(species_full = phylo_cor_wild_vr), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data_wild)
+
+   model5.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_vr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_vr=A_wild_vr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data_wild)
+
+  # Save model5.3
+  saveRDS(model5.3, file = "./output/models/lnVRQ10_5.3")
+  saveRDS(model5.3_bayes, file = "./output/models/lnVRQ10_5.3_bayes")
 
   } else{
-        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
-  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
+        model5.3 <- readRDS("./output/models/lnVRQ10_5.3")
+  model5.3_bayes <- readRDS("./output/models/lnVRQ10_5.3_bayes")
 }
@@
 
-#### *Acute and acclimation* $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa
+#### *Acute and acclimation* $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa (REMOVE)
 
@@
 
-#### *Comparing raw variance changes using* $lnVR_{Q_{10}}$
-
-```{r, lnvrq10}
-#| label: lnvrq10
+#### *Comparing relative variance changes using* $lnCVR_{Q_{10}}$
+
+```{r, lncvrq10}
+#| label: lncvrq10
 #| echo: false
@@
 #| include: false
-#| cache: true
+#| cache: false
 
 #############
-  ## lnVRQ10
+  ## lnCVRQ10
 #############
@@
 #################################################
-  lnVRQ10_data <- data_long2 %>% filter(grepl("lnVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                               mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
@@
 # Check and prune tree
-  tree_lnVR <- tree_checks(data = lnVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnVRQ10_data, tree = tree_lnVR, dataCol = "species_full", type = "check") # Good
+  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
 
 # Create the phylo correlation matrix
-  phylo_cor_VR <- vcv(tree_lnVR, cor = TRUE)
-          A_VR <- vcv(tree_lnVR, cor = FALSE) # For bayes, need cov matrix
+  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
+          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
 
 ###################################################
-  # Model 3.1: Intercept only model.
+  # Model 2.1: Intercept only model.
   # Used for heterogeneity analysis
@@
 if(rerun){
-  model3.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
-                              test = "t", data = lnVRQ10_data)
-
-  model3.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
   # Save model1.1
-  saveRDS(model3.1, file = "./output/models/lnVRQ10_3.1")
-  saveRDS(model3.1_bayes, file = "./output/models/lnVRQ10_3.1_bayes")
+  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
+  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
 } else{ 
-        model3.1 <- readRDS("./output/models/lnVRQ10_3.1")
-  model3.1_bayes <- readRDS("./output/models/lnVRQ10_3.1_bayes")
+        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
+  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
 }
@@
 # Heterogeneity analysis
-   w_VR <- with(lnVRQ10_data, 1/V) # weights
-  sv_VR <- sum(w_VR*(dim(lnVRQ10_data)[1]-1)) / (sum(w_VR)^2 + sum(w_VR^2))
+   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
+  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
 
 # extract posterior sds, but square them to turn to variance
-  posteriors_3.1 <- posterior_samples(model3.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_3.1) <- gsub("__Intercept", "", colnames(posteriors_3.1))
-  colnames(posteriors_3.1) <- gsub("sd_", "", colnames(posteriors_3.1))
-
-    res_VR <- posteriors_3.1[,"sigma"]
-   stdy_VR <- posteriors_3.1[,"record_num"]
-  phylo_VR <- posteriors_3.1[,"species_full"]
-    spp_VR <- posteriors_3.1[,"spp"]
-  trait_VR <- posteriors_3.1[,"trait"]
-  total_VR <- phylo_VR + spp_VR + res_VR + sv_VR + stdy_VR + trait_VR
+  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
+  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
+
+    res_cvr <- posteriors_2.1[,"sigma"]
+   stdy_cvr <- posteriors_2.1[,"record_num"]
+  phylo_cvr <- posteriors_2.1[,"species_full"]
+    spp_cvr <- posteriors_2.1[,"spp"]
+  trait_cvr <- posteriors_2.1[,"trait"]
+  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
 
   # Calculate I2
-     tot_i2_VR <- (sv_VR / total_VR)*100    ; mean(tot_i2_VR)  ; quantile(tot_i2_VR, c(0.025, 0.975))
-   phylo_i2_VR <- (phylo_VR / total_VR)*100 ; mean(phylo_i2_VR); quantile(phylo_i2_VR, c(0.025, 0.975))
-     spp_i2_VR <- (spp_VR / total_VR)*100   ; mean(spp_i2_VR)  ; quantile(spp_i2_VR, c(0.025, 0.975))
-    stdy_i2_VR <- (stdy_VR / total_VR)*100  ; mean(stdy_i2_VR) ; quantile(stdy_i2_VR, c(0.025, 0.975))
-   trait_i2_VR <- (trait_VR / total_VR)*100 ; mean(trait_i2_VR); quantile(trait_i2_VR, c(0.025, 0.975))
-     res_i2_VR <- (res_VR / total_VR)*100   ; mean(res_i2_VR)  ; quantile(res_i2_VR, c(0.025, 0.975))
+     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
+   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
+     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
+    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
+   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
+     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
 
   # Table
-     i2_lnVR <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2_VR),mean(spp_i2_VR), mean(stdy_i2_VR), mean(trait_i2_VR)),
-                           lci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[1], quantile(spp_i2_VR, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2_VR, c(0.025, 0.975))[1], quantile(trait_i2_VR, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2_VR, c(0.025, 0.975))[2], quantile(spp_i2_VR, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2_VR, c(0.025, 0.975))[2], quantile(trait_i2_VR, c(0.025, 0.975))[2]))
+     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
+                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
 
 ###################################################
-  # Model 3.2: Model controlling for acclimation time, 
+  # Model 2.2: Model controlling for acclimation time, 
   # type and habitat assuming type can vary by habitat
@@
   # More realistic model 
-  model3.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
-                              test = "t", data = lnVRQ10_data)
-
-   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + 
-        (~1 | record_num) + 
-        (1 | gr(species_full, cov = A_VR)) + 
-        (1 + max_temp_c| spp) + 
-        (1|trait), 
-        data2 = list(A_VR=A_VR), family = gaussian(), 
-        prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-        control = list(adapt_delta = 0.98, max_treedepth = 12), 
-        chains = 4, thin = 5, iter = 8000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
   # Save model1.2
-  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
-  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")
+  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
+  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
 
   } else{
-        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
-  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
+        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
+  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
 }
@@
 
-  posteriors_3.2 <- posterior_samples(model3.2_bayes, pars = "^b")
-  f_acute_VR  <- posteriors_3.2[,"b_Intercept"]; pmcmc(f_acute_VR)
-  f_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_typeacclim"]
-  m_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"]
-  m_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatm"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatm"]
-  t_acute_VR  <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"]
-  t_acclim_VR <- posteriors_3.2[,"b_Intercept"] + posteriors_3.2[,"b_habitatt"] + posteriors_3.2[,"b_typeacclim"] + posteriors_3.2[,"b_typeacclim:habitatt"]
+  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
+  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
+  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
+  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
+  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
+  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
+  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
 
@@
   # First get sample sizes
-    N <- lnVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
 
   # Calculated weighted mean by sample size. 
-    f_VR_mean <- (f_acute_VR * N[1,"n"][[1]] + f_acclim_VR * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_VR_mean)
-    m_VR_mean <- (m_acute_VR * N[3,"n"][[1]] + m_acclim_VR * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_VR_mean)
-    t_VR_mean <- (t_acute_VR * N[5,"n"][[1]] + t_acclim_VR * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_VR_mean)
+    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
+    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
+    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
 
   # Lets now convert these to a %
-    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) 
-    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) 
-    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100)
+    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
+    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
+    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
 
 ###################################################
-  # Model 3.3: Model controlling for acclimation time, 
+  # Model 2.3: Model controlling for acclimation time, 
   # type and trait category assuming type can vary by habitat
@@
   # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
-    lnVRQ10_data <- lnVRQ10_data %>% 
+    lnCVRQ10_data <- lnCVRQ10_data %>% 
                     mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
@@
  # We can also run subsets for each habitat
-   tree_m_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
-   tree_f_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
-   tree_t_vr <- tree_checks(lnVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
 
  # cor matrices
-   m_phylo_vr <- vcv(tree_m_vr, corr = TRUE)
-   f_phylo_vr <- vcv(tree_f_vr, corr = TRUE)
-   t_phylo_vr <- vcv(tree_t_vr, corr = TRUE)
+   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
+   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
+   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
 
@@
   # Full Bayesian model   
-   model3.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+   model2.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
                                            (1 | record_num) + 
-                                           (1 | gr(species_full, cov = A_VR)) + 
+                                           (1 | gr(species_full, cov = A)) + 
                                            (1 + max_temp_c | spp) +(1|trait) + 
                                            (1 + trait_broad |gr(obs, cor = FALSE)),  
-                                         data2 = list(A_VR=A_VR), family = gaussian(), 
+                                         data2 = list(A=A), family = gaussian(), 
                                          prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
                                          control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnVRQ10_data, trait_broad != "other"))
-    saveRDS(model3.3_btrait_bayes, "./output/models/model3.3_btrait_bayes")
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnCVRQ10_data, trait_broad != "other"))
+    saveRDS(model2.3_btrait_bayes, "./output/models/model2.3_btrait_bayes")
 
@@
       # Marine
-         model3.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+         model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 + trait_broad| obs),
-                              R = list(species_full = m_phylo_vr), dfs = "contain", 
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
                               test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = filter(lnVRQ10_data, habitat == "m" & trait_broad != "other"))
-         saveRDS(model3.3_m_broad, "output/models/model3.3_m_broad")
+                              data = filter(lnCVRQ10_data, habitat == "m" & trait_broad != "other"))
+         saveRDS(model2.3_m_broad, "output/models/model2.3_m_broad")
 
       # Freshwater
-         model3.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+         model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 + trait_broad| obs),
-                              R = list(species_full = f_phylo_vr), dfs = "contain", 
+                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
                               test = "t", struct = c("GEN","HCS"),  phi = 0,
-                              data = filter(lnVRQ10_data, habitat == "f" & trait_broad != "other"))
-          saveRDS(model3.3_f_broad, "output/models/model3.3_f_broad")
+                              data = filter(lnCVRQ10_data, habitat == "f" & trait_broad != "other"))
+          saveRDS(model2.3_f_broad, "output/models/model2.3_f_broad")
 
       # Terrestrial
-         model3.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+         model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 + trait_broad| obs),
-                              R = list(species_full = t_phylo_vr), dfs = "contain", 
+                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
                               test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = filter(lnVRQ10_data, habitat == "t" & trait_broad != "other"))
-         saveRDS(model3.3_t_broad, "output/models/model3.3_t_broad")
+                              data = filter(lnCVRQ10_data, habitat == "t" & trait_broad != "other"))
+         saveRDS(model2.3_t_broad, "output/models/model2.3_t_broad")
 
   } else{
-    model3.3_btrait_bayes <- readRDS("./output/models/model3.3_btrait_bayes")
-    model3.3_m_broad <- readRDS("output/models/model3.3_m_broad")
-    model3.3_f_broad <- readRDS("output/models/model3.3_f_broad")
-    model3.3_t_broad <- readRDS("output/models/model3.3_t_broad")
+    model2.3_btrait_bayes <- readRDS("./output/models/model2.3_btrait_bayes")
+    model2.3_m_broad <- readRDS("output/models/model2.3_m_broad")
+    model2.3_f_broad <- readRDS("output/models/model2.3_f_broad")
+    model2.3_t_broad <- readRDS("output/models/model2.3_t_broad")
 }
@@
        # Predict from model. Note this is the summary.
-         pred_lnvr_traitb <- fitted(model3.3_btrait_bayes, 
+         pred_lncvr_traitb <- fitted(model2.3_btrait_bayes, 
                                      newdata = trait_b_data, re_formula = NA,
@@
                                      robust = FALSE)
-         pred_lnvr_traitb <- cbind(trait_b_data, pred_lnvr_traitb)
+         pred_lncvr_traitb <- cbind(trait_b_data, pred_lncvr_traitb)
 
@@
 Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lnvr_traitb_post <- fitted(model3.3_btrait_bayes, 
+            pred_lncvr_traitb_post <- fitted(model2.3_btrait_bayes, 
                                      newdata = trait_b_data, re_formula = NA,
@@
                                      robust = FALSE)
-        contrast_lnvr_trait_post <-  pred_lnvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lnvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+        contrast_lncvr_trait_post <-  pred_lncvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lncvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
 
         # Contrast statistics
-            contrast_lnvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+            contrast_lncvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
                                                      trait = rep(c("tissue/organism", "biochemical"), each = 1),
-                                                    diff = sapply(data.frame(contrast_lnvr_trait_post), mean),
-                                                     l95 = sapply(data.frame(contrast_lnvr_trait_post), function(x) quantile(x, 0.025)),
-                                                     u95 = sapply(data.frame(contrast_lnvr_trait_post), function(x) quantile(x, 0.975)),
-                                                       p = sapply(data.frame(contrast_lnvr_trait_post), function(x) p_value(pmcmc(x))))
+                                                    diff = sapply(data.frame(contrast_lncvr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lncvr_trait_post), function(x) p_value(pmcmc(x))))
+
+   # Contrasts for pooled acute and acclimation across trait categories
+
+            contrast_lncvr_trait_cat_stats <- rbind(get_whole_bio(pred_lncvr_traitb_post, habitat = "t", trait_b_data),
+                                                        get_whole_bio(pred_lncvr_traitb_post, habitat = "m", trait_b_data),
+                                                        get_whole_bio(pred_lncvr_traitb_post, habitat = "f", trait_b_data))
 
 ###################################################
-  # Model 3.4: Model controlling for acclimation time, 
+  # Model 2.4: Model controlling for acclimation time, 
   # type and life history stage assuming type can vary by habitat
@@
   # More realistic model 
-  model3.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
                               random = list(~1 | record_num,
@@
                                             ~1 | obs),
-                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
-                              test = "t", data = lnVRQ10_data)
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
   # Save model
-  saveRDS(model3.4, file = "./output/models/lnVRQ10_3.4")
-
-   model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
+  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
+
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
                                  (~1 | record_num) + 
-                                 (1 | gr(species_full, cov = A_VR)) + 
+                                 (1 | gr(species_full, cov = A_CVR)) + 
                                  (1 + max_temp_c| spp) + 
@@
                                  (1|obs), 
-                               data2 = list(A_VR=A_VR), family = gaussian(), 
+                               data2 = list(A_CVR=A_CVR), family = gaussian(), 
                                prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
@@
   # Save model
-  saveRDS(model3.4_bayes, file = "./output/models/lnVRQ10_3.4_bayes")
+  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
 
   } else{
-        model3.4 <- readRDS("./output/models/lnVRQ10_3.4")
-  model3.4_bayes <- readRDS("./output/models/lnVRQ10_3.4_bayes")
+        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
+  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
 }
@@
             # Extract posteriors
-              post_lh_vr <- posterior_samples(model3.4_bayes, pars = "^b")
+              post_lh <- posterior_samples(model2.4_bayes, pars = "^b")
 
@@
 Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lh_vr <- apply(t(post_lh_vr),2 , function(x) as.matrix(X)%*%x)
-
-        contrast_lnvr_lh_post <-  pred_lh_vr[c(1,3,5,7,9,11),] - pred_lh_vr[c(2,4,6,8,10,12),] # Acclimation - acute.
+            pred_lh <- apply(t(post_lh),2 , function(x) as.matrix(X)%*%x)
+
+        contrast_lncvr_lh_post <-  pred_lh[c(1,3,5,7,9,11),] - pred_lh[c(2,4,6,8,10,12),] # Acclimation - acute.
 
         # Contrast statistics
-            contrast_lnvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
                                                      stage = rep(c("j", "a"), each = 1),
-                                                    diff = apply(data.frame(contrast_lnvr_lh_post), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) p_value(pmcmc(x))))
+                                                    diff = apply(data.frame(contrast_lncvr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) p_value(pmcmc(x))))
 ```
 
-Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with
+Overall, analyses with $lnCVR_{Q_{10}}$ showed similar patterns to those with $lnVR_{Q_{10}}$, except that, because of rates being taken into consideration and there is a strong mean-variance relationship, the patterns were generally opposite in direction.
+Either way, the relative differences are quite similar.
+Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with
 higher temperatures across all habitat types, with terrestrial
-ectotherms having the smallest increase in variance (@fig-s1 & @tbl-s1).
+ectotherms having the largest decrease in relative variance (@fig-s1).
+There were also no major differences in the relative differences among broad trait categories (@fig-cvrbtrait) or life-history stages (@fig-lncvrlh).
 
@@
 
-k_vr <- manual_extract(model3.2, mod = "habitat", group = "spp", exclude = NULL)
+#################
+# Fig S CVR
+##################
+  # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
+But, there is a clear reduction in between individual variance for terrestrial species.
+As temperature get hotter then the variance in physiological rates decreases.
+This is not true of aquatic systems.
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
+  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
+
+  x1 = 1.4
+  x2 = 2.4
+  x3 = 3.4
+
+  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8,  k.pos = "none")  +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) +
+
+  annotate("text", x = x1, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+         annotate("text", x = x1, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x1-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 8) + 
+  annotate("text", x = x1-0.20, y = 1, label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = x2, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+     annotate("text", x = x2, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x2-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 8) +
+  annotate("text", x = x2-0.20, y = 1, label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = x3+0.10, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+  annotate("text", x = x3+0.10, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x3-0.10, y = 1, label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) + 
+  annotate("text", x = x3-0.10, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 8) +
+
+    labs(shape = "Type") +
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)
+
+  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_blank(),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")
+
+########
 
@@
 ##################
-  # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
-  col <- c("#0871B9", "#F3B40D", "#1BB908")
-  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", by = "type", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8) +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + ylim(-2,3) +
-
-     annotate("text", x = 1.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 8) +
-    annotate("text", x = 1.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = 1.20, y = -2, label =paste0(round(mean(f_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
-
-    annotate("text", x = 2.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 8) +
-    annotate("text", x = 2.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = 2.20, y = -2, label =paste0(round(mean(m_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
-
-        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ = ", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) +
-    annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col)) + annotate("text", y = 2.5, x = c(1.3, 2.3, 3.3)+0.1, label = TeX(paste0("\\it{k} = ", k_vr$k, " (", k_vr$sdy, ")")), size = 6)
-
-  p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 24),
-                                       axis.text.y = element_text(angle = 45, size = 24),
-                                       legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top")
 
@@
 
-```{r, tbl-s1}
-#| label: tbl-s1
-#| echo: false
-#| tbl-cap: "Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types.
-Model estimates are based off 1,253 effect sizes from 139 studies."
-
- # Extract the fixed / population-level effect summaries of the posterior
-    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
-    fixed <- cbind(Parameter = c("Intercept", "Mximum Temperature (centered)", "Acclimation Time (centered)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
-    rownames(fixed) <- NULL
-
- # Extract the random effect summaries of the posteriors (SDs)
-    random <- rbind(header = rep(0, 4), do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x))))
-    random <- cbind(Parameter = c(" ", "Study", "Phylogeny", "Species (intercept)", "Species (slope max temp)", "Trait"), random)
-    rownames(random) <- NULL
-
-# Create the table
-    tabs1 <- rbind(fixed, random)
-
-    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 10)
-```
-
-```{r, fig-lnvrlh}
-#| label: fig-lnvrlh
-#| echo: false
-#| fig-cap: "Estimated mean acclimation and acute $lnVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for marine (A), freshwater (B) and terrestrial (C) ectotherms.
+```{r, fig-cvrbtrait}
+#| label: fig-btrait
+#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for tissue/whole-orgamism traits and biochemical traits across marine (A), freshwater (B) and terrestrial (C) habitats.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
+For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
 $\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
 $p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+#| echo: false
+#| warning: false
 
@@
 
-n_lnvr_lh <- lnVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+n_lncvr_btrait  <- lnCVRQ10_data  %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+
+       col <- c("#0871B9", "#F3B40D", "#1BB908")
+     x.pos <- c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+############
+# CVR
+############
+m_cv <- n_lncvr_btrait %>% filter(habitat == "m")
+f_cv <- n_lncvr_btrait %>% filter(habitat == "f")
+t_cv <- n_lncvr_btrait %>% filter(habitat == "t")
+
+t_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
+
+############
+# Full fig
+############
+figbtrait_vr <-(p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A") 
+ggsave(figbtrait_vr, filename = "./output/figures/figStrait_cvr.png", width = 28, height = 8, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figStrait_cvr.png")
+figbtrait
+```
+
+```{r, fig-lncvrlh}
+#| label: fig-lnvrlh
+#| echo: false
+#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for marine (A), freshwater (B) and terrestrial (C) ectotherms.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
+$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lncvr_lh <- lnCVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
 
@@
 ###############
-## lnVR Q10
+# ln CVR
 ###############
-
-t_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-m_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-f_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-
-yloc = c(1.5, 2.5)
-
-m_r <- n_lnvr_lh %>% filter(habitat == "m")
-f_r <- n_lnvr_lh %>% filter(habitat == "f")
-t_r <- n_lnvr_lh %>% filter(habitat == "t")
-
-p1_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
-
-p2_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
-
-p3_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5,3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
-
-figvr_lh <-(p3_vr | p1_vr | p2_vr) + plot_annotation(tag_levels = "A") 
-ggsave(figvr_lh, filename = "./output/figures/figSlh.pdf", width = 28, height = 10, device = "pdf")
-
-figvr_lh <- magick::image_read("./output/figures/figSlh.pdf")
-figvr_lh
+m_cv <- n_lncvr_lh %>% filter(habitat == "m")
+f_cv <- n_lncvr_lh %>% filter(habitat == "f")
+t_cv <- n_lncvr_lh %>% filter(habitat == "t")
+
+  t_trait_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+figvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
+ggsave(figcvr_lh, filename = "./output/figures/figSlh.pdf", width = 28, height = 10, device = "pdf")
+
+figcvr_lh <- magick::image_read("./output/figures/figSlh.pdf")
+figcvr_lh
+
+```
+
+```{r wildlncvr}
+#| label: wildlncvr
+#| cache: true
+#| include: false
+#| echo: false
+#| warning: false
+#| 
+#######################################
+  ## lnCVRQ10 from Wild Populations ##
+#######################################
+##################################################
+  # Organise the data and prune tree
+##################################################
+
+# Bring in  historial climate data
+  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+# Create a match column.
+  climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% 
+                          dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+
+# Populations and species?
+  pop_spp_w <- climate2[complete.cases(climate2),]
+
+# Subset the data
+  lnCVRQ10_data_wild <- data_long2 %>% 
+    filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+                        mutate(spp = species_full, 
+                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
+                                     match = interaction(spp, lat, long),
+                                     max_temp_c = scale(temp_2, scale = FALSE))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+  lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
+
+# Look at the environment details across different habitats. 
+  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(sd))
+
+# Check and prune tree
+  tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
+          A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale environment variables
+    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
+                                                        acf_all_c = scale(acf_all),
+                                                        acf_lag1_c = scale(acf_lag1))
+
+####################################################
+  # Model 4.3: Model environmental variability by acute/acclim
+####################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.3
+  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
+  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
+
+  } else{
+        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
+  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
+}
+
+############################################################################################
+# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################          
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+if(rerun){
+  # More realistic model with 
+  model4.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model4.9, file = "./output/models/lnCVRQ10_4.9")
+  saveRDS(model4.9_bayes, file = "./output/models/lnCVRQ10_4.9_bayes")
+
+  } else{
+        model4.9 <- readRDS("./output/models/lnCVRQ10_4.9")
+  model4.9_bayes <- readRDS("./output/models/lnCVRQ10_4.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.9
+#################################################
+ posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
+
+    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
+    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
+    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
+
+##################################################
+    # Model 4.8, 4.9 and 4.10 - Habitat subset
+    # Used for making plots
+##################################################
+    # Subset data to habitat
+    lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+if(rerun){
+    # Terrestrial Models
+    model4.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
+    saveRDS(model4.9_t, "./output/models/model4.9_t")
+
+    # Freshwater Models
+
+    model4.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
+
+    saveRDS(model4.9_f, "./output/models/model4.9_f")
+
+    # Marine Models
+
+    model4.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
+    saveRDS(model4.9_m, "./output/models/model4.9_m")
+
+  } else {
+     model4.9_t <- readRDS("./output/models/model4.9_t")
+     model4.9_f <- readRDS("./output/models/model4.9_f")
+     model4.9_m <- readRDS("./output/models/model4.9_m")
+}
 

### 2024-07-13 ms.qmd
huge overhaul and re-organisation of code. bring lnVR to main MS. Re-rendered after a few failures as there were code bugs. Need to fix results sections now, mainly re-write and add a fe wmore overall comparisons across habiats

@@
   avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
+
+  # First get sample sizes
+    N <- lnRRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
 
@@
 
+# First get sample sizes
+    N <- lnVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
 ###################################################
@@
 
-# Bring in  historial climate data
+# Bring in  historical climate data
   climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
@@
   lnVRQ10_data_wild <- left_join(lnVRQ10_data_wild, climate2, by = "match")
-
-# Look at the environment details across different habitats. 
-  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(sd))
 
@@
 ############################################################################################
-# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
+# Model 5.9: Acclimatization lnVRQ10 only. Test if environmental variance explains 
 # differently in each habitat
 ############################################################################################          
-  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+  lnVRQ10_data_wild_acclim <- lnVRQ10_data_wild %>%  filter(type == "acclim")
 
@@
   # Check and prune tree
-tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+tree_lnvr_wild_acclim <- tree_checks(data = lnVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnVRQ10_data_wild_acclim, tree = tree_lnvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lnvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lnvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
 
@@
   # More realistic model with 
-  model4.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model4.9, file = "./output/models/lnCVRQ10_4.9")
-  saveRDS(model4.9_bayes, file = "./output/models/lnCVRQ10_4.9_bayes")
-
-  } else{
-        model4.9 <- readRDS("./output/models/lnCVRQ10_4.9")
-  model4.9_bayes <- readRDS("./output/models/lnCVRQ10_4.9_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.9
-#################################################
- posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
-
-    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
-    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
-    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
-
-##################################################
-    # Model 4.8, 4.9 and 4.10 - Habitat subset
-    # Used for making plots
-##################################################
-    # Subset data to habitat
-    lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
-    lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")
-    lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
-
-if(rerun){
-    # Terrestrial Models
-    model4.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+  model5.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
                                        random = list(~1 | record_num,
@@
                               R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
-    saveRDS(model4.9_t, "./output/models/model4.9_t")
-
-    # Freshwater Models
-
-    model4.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                              test = "t", data = lnVRQ10_data_wild_acclim)
+
+   model5.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data_wild_acclim)
+
+  # Save models
+  saveRDS(model5.9, file = "./output/models/lnVRQ10_5.9")
+  saveRDS(model5.9_bayes, file = "./output/models/lnVRQ10_5.9_bayes")
+
+  } else{
+        model5.9 <- readRDS("./output/models/lnVRQ10_5.9")
+  model5.9_bayes <- readRDS("./output/models/lnVRQ10_5.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 5.9
+#################################################
+ posteriors5.9 <- posterior_samples(model5.9_bayes, "^b")
+
+    slope_f_5.9 <- posteriors5.9[,"b_cv_c"]
+    slope_m_5.9 <- posteriors5.9[,"b_cv_c"] + posteriors5.9[,"b_cv_c:habitatm"]
+    slope_t_5.9 <- posteriors5.9[,"b_cv_c"] + posteriors5.9[,"b_cv_c:habitatt"]
+
+##################################################
+    # Model 5.8, 5.9 and 5.10 - Habitat subset
+    # Used for making plots
+##################################################
+    # Subset data to habitat
+    lnVRQ10_data_wild_acclim_t <- lnVRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnVRQ10_data_wild_acclim_f <- lnVRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnVRQ10_data_wild_acclim_m <- lnVRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+if(rerun){
+    # Terrestrial Models
+    model5.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
                                        random = list(~1 | record_num,
@@
                               R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
-
-    saveRDS(model4.9_f, "./output/models/model4.9_f")
-
-    # Marine Models
-
-    model4.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                              test = "t", data = lnVRQ10_data_wild_acclim_t, control=list(iter.max=1000, rel.tol=1e-8))
+    saveRDS(model5.9_t, "./output/models/model5.9_t")
+
+    # Freshwater Models
+
+    model5.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
                                        random = list(~1 | record_num,
@@
                               R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
-    saveRDS(model4.9_m, "./output/models/model4.9_m")
+                              test = "t", data = lnVRQ10_data_wild_acclim_f)
+
+    saveRDS(model5.9_f, "./output/models/model5.9_f")
+
+    # Marine Models
+
+    model5.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data_wild_acclim_m)
+    saveRDS(model5.9_m, "./output/models/model5.9_m")
 
   } else {
-     model4.9_t <- readRDS("./output/models/model4.9_t")
-     model4.9_f <- readRDS("./output/models/model4.9_f")
-     model4.9_m <- readRDS("./output/models/model4.9_m")
+     model5.9_t <- readRDS("./output/models/model5.9_t")
+     model5.9_f <- readRDS("./output/models/model5.9_f")
+     model5.9_m <- readRDS("./output/models/model5.9_m")
 }
@@
 ####################
-# lnCVR CV
+# lnVR CV
 ####################
-dat_textcvr <- data.frame(label = c(text(slope_f_4.9), 
-                                 text(slope_m_4.9), 
-                                 text(slope_t_4.9)),
-                      label2 = c(text(slope_f_4.9, b = FALSE), 
-                                 text(slope_m_4.9,b = FALSE), 
-                                 text(slope_t_4.9,b = FALSE)),
-                           p = c(p_text(slope_f_4.9), 
-                                 p_text(slope_m_4.9), 
-                                 p_text(slope_t_4.9)),
+dat_textvr <- data.frame(label = c(text(slope_f_5.9), 
+                                 text(slope_m_5.9), 
+                                 text(slope_t_5.9)),
+                      label2 = c(text(slope_f_5.9, b = FALSE), 
+                                 text(slope_m_5.9,b = FALSE), 
+                                 text(slope_t_5.9,b = FALSE)),
+                           p = c(p_text(slope_f_5.9), 
+                                 p_text(slope_m_5.9), 
+                                 p_text(slope_t_5.9)),
                        title = c("Freshwater", "Marine", "Terrestrial"), 
@@
   x_f = 0.6
-  p_f_cv <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
-      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
-    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
+  p_f_vr <-  bubble_plot(model5.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
+      geom_point(data = lnVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
+    annotate("text", x = dat_textvr$x[1]+x_f, y = yadj2, label = TeX(dat_textvr$p[1]), size = 8) +
+    annotate("text", x = dat_textvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textvr$label2[1]), size = 8) +
+    annotate("text", x = dat_textvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textvr$label[1]), size = 8) +
   theme(axis.text = element_text(size = size_axis), 
@@
   x_m = -0.4
-  p_m_cv <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
-    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
+  p_m_vr <-  bubble_plot(model5.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
+    geom_point(data = lnVRQ10_data_wild_acclim_m, 
                  aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
                  fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
-    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
-    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
+    annotate("text", x = dat_textvr$x[1]+x_m, y = yadj2, label = TeX(dat_textvr$p[2]), size = 8) +
+    annotate("text", x = dat_textvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textvr$label2[2]), size = 8) +
+    annotate("text", x = dat_textvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textvr$label[2]), size = 8) +
     theme(axis.text = element_text(size = size_axis), 
@@
 x_t = 0
-p_t_cv <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
-  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
+p_t_vr <-  bubble_plot(model5.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
+  geom_point(data = lnVRQ10_data_wild_acclim_t, 
                aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
                fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
-  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
-  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
-  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
+  annotate("text", x = dat_textvr$x[3]+x_t, y = yadj2, label = TeX(dat_textvr$p[3]), size = 8) +
+  annotate("text", x = dat_textvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textvr$label2[3]), size = 8) +
+  annotate("text", x = dat_textvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textvr$label[3]), size = 8) +
   theme(axis.text = element_text(size = size_axis), 
@@
 
-  p_cv <- (p_t_rr + p_m_rr + p_f_rr) / (p_t_cv + p_m_cv + p_f_cv) + 
+  p_cv <- (p_t_rr + p_m_rr + p_f_rr) / (p_t_vr + p_m_vr + p_f_vr) + 
             plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
@@
 
-```{r, global}
+```{r, globalvr}
 #| label: global
@@
 
-   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) +
+   model6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) +
                                (1 | record_num) + 
-                               (1 | gr(species_full, cov = A_wild_cvr)) + 
+                               (1 | gr(species_full, cov = A_wild_vr)) + 
                                (1 + max_temp_c | spp) + 
@@
                                (1 | obs), 
-                      data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), 
+                      data2 = list(A_wild_vr=A_wild_vr), family = gaussian(), 
                       prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
@@
                       chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
-                      data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
-
-  saveRDS(model5_bayes, file = "./output/models/lnCVRQ10_5_bayes")
+                      data = lnVRQ10_data_wild[complete.cases(lnVRQ10_data_wild$c_accl_time),])
+
+  saveRDS(model6_bayes, file = "./output/models/lnVRQ10_6_bayes")
 
   } else{
-  model5_bayes <- readRDS("./output/models/lnCVRQ10_5_bayes")
+  model6_bayes <- readRDS("./output/models/lnVRQ10_6_bayes")
 }
@@
 # Lets explore the model and how it's predicting the real data
-  data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+  data_w_vr <- lnVRQ10_data_wild[complete.cases(lnVRQ10_data_wild$c_accl_time),]
 
 # combine with predictions
-  data_w_pred <- cbind(data_w, predict(model5_bayes))
+  data_w_pred_vr <- cbind(data_w_vr, predict(model6_bayes))
 
 # Fitted vs actual data
-  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size))      + 
+  ggplot(data = data_w_pred_vr, aes(x = Estimate, y = effect_size))      + 
         geom_point() + geom_smooth(method = "lm")                     + 
@@
 We expect the rows of raw data for acute and acclim to be repeated even though these data are NOT all used to make the calculation.
-  sign_change_dat <- data_w_pred  %>% filter(sign(Estimate) != sign(effect_size))
+  sign_change_dat_vr <- data_w_pred_vr  %>% filter(sign(Estimate) != sign(effect_size))
   #View(sign_change_dat)
@@
 # Fitted by Lat/long Longitude, Latitude
-  ggplot(data = data_w_pred, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+  ggplot(data = data_w_pred_vr, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred_vr, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
 
 # Observed by Lat/long
-  ggplot(data = data_w_pred, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
+  ggplot(data = data_w_pred_vr, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred_vr, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
 
 # How much variation does this model explain.
-Need to do this manually because function doesn't seme to work on the model object.
-We need to remember that predcit will include random effect variances so we may need to exclude this
-  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
-  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)
+Need to do this manually because function doesn't seem to work on the model object.
+Note that this is just for fixed effects, re_formula = NA ignore the random effects.
+  re_post_vr <- posterior_samples(model6_bayes, pars = "^sd_")
+    v_fix_vr <- apply(predict(model6_bayes, summary = FALSE, re_formula = NA), 1, function(x) var(x))
 
 # sigma2_v = typical sampling error variance
-sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
-  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
-              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))
-
-# Now check that var fix from raw data and remove sampling variance. 
-  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
+  sub_data_vr <- lnVRQ10_data_wild[complete.cases(lnVRQ10_data_wild$c_accl_time),]
+  sigma2_v_vr <- sum(1 / sub_data_vr$V) * (dim(sub_data_vr)[1] - 1) /
+                 (sum(1 / sub_data_vr$V)^2 - sum((1 / sub_data_vr$V)^2))
 
 # Extract the random effect variances
-  v_trait <- re_post$sd_trait__Intercept^2
-    v_spp <- re_post$sd_spp__Intercept^2
-    v_phy <- re_post$sd_species_full__Intercept^2
-    v_std <- re_post$sd_record_num__Intercept^2
-      v_r <- re_post$sd_obs__Intercept^2
-
-# Lets get the total variance for the random effects only
-  tot_re <- v_trait + v_spp + v_phy + v_std + v_r
-
-# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
-    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too
-
-    mean(r2) # Seems a bit high 0.53
-  quantile(r2, probs = c(0.025, 0.975)); #0.30-0.72
-
-# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
-  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2
-
-  mean(r2_2) #  0.50
-  quantile(r2_2, probs = c(0.025, 0.975)); #0.33-0.62
+  v_trait_vr <- re_post_vr$sd_trait__Intercept^2
+    v_spp_vr <- re_post_vr$sd_spp__Intercept^2
+    v_phy_vr <- re_post_vr$sd_species_full__Intercept^2
+    v_std_vr <- re_post_vr$sd_record_num__Intercept^2
+      v_r_vr <- re_post_vr$sd_obs__Intercept^2
+
+# Lets get the total variance for the random effects
+  tot_re_vr <- v_trait_vr + v_spp_vr + v_phy_vr + v_std_vr + v_r_vr
+
+# Now, calculate r2. Note that this isn't perfect and should be under estimated because we are ignoring random slope
+         r2 <- (v_fix_vr) / (v_fix_vr + tot_re_vr)
+
+    mean(r2) #  0.43
+    quantile(r2, probs = c(0.025, 0.975)); #0.33-0.51
 
@@
 ######################################################################
-# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
+# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different.
 
@@
 
-  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+  terrest_data_vr <- sub_data_vr  %>% 
+                  filter(habitat == "t")  %>% 
+                  distinct(spp, species_full, habitat, type, Latitude, Longitude)
+
   new_data_t <- data.frame(
@@
   # Create new data frame with only unique values for prediction.
-  new_data_t2  <- cbind(terrest_data, new_data_t)
+  new_data_t2_vr  <- cbind(terrest_data_vr, new_data_t)
 
   # We'll now make the predictions from the model object using the new data frame
-  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+  terre_pred_vr <- predict(model6_bayes, newdata = new_data_t2_vr, 
+                        summary = TRUE, re_formula = NA, 
+                        robust = FALSE, intervals = "confidence")
 
   # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
-  terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+  terre_pred_no_sum_vr <- cbind(new_data_t2_vr, 
+                                t(predict(model6_bayes, newdata = new_data_t2_vr, re_formula = NA, summary = FALSE)))
 
   # Lets merge predictions with the original data
-  terrest_data <- cbind(terrest_data, terre_pred)
+  terrest_data_vr <- cbind(terrest_data_vr, terre_pred_vr)
 
@@
 Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE .
-These are extremely close, and I suspect are only different because sample_new_levels is sampling differently each time predict is run, so will be slightly different from run-to-run
-  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
+These are identical.
+  terre_pred2 <- predict(model6_bayes, newdata = new_data_t2_vr, summary = FALSE, re_formula = NA)
   plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
@@
 #############################
-  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+  marine_data_vr <- sub_data_vr  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
 
@@
   # Create new data frame with only unique values for prediction.
-  new_data_m  <- cbind(marine_data, new_data_m)
+  new_data_m_vr  <- cbind(marine_data_vr, new_data_m)
 
   # We'll now make the predictions from the model object using the new data frame
-  marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+  marine_pred_vr <- predict(model6_bayes, newdata = new_data_m_vr, summary = TRUE, 
+                            re_formula = NA, intervals = "confidence")
 
   # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
-  marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+  marine_pred_no_sum_vr <- cbind(new_data_m_vr, t(predict(model6_bayes, newdata = new_data_m_vr, 
+                                                          summary = FALSE, re_formula = NA)))
 
   # Lets merge predictions with the original data
-  marine_data <- cbind(marine_data, marine_pred)
+  marine_data_vr <- cbind(marine_data_vr, marine_pred_vr)
 
@@
 #############################
-  fresh_data <- sub_data  %>% filter(habitat == "f") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+  fresh_data_vr <- sub_data_vr  %>% 
+                  filter(habitat == "f") %>% 
+                  distinct(spp, species_full, habitat, type, Latitude, Longitude)
 
@@
                                     obs = 0, 
-       record_num = 0
-    )
+                             record_num = 0)
 
   # Create new data frame with only unique values for prediction.
-  new_data_f  <- cbind(fresh_data, new_data_f)
+  new_data_f_vr  <- cbind(fresh_data_vr, new_data_f)
 
   # We'll now make the predictions from the model object using the new data frame
-  fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+  fresh_pred_vr <- predict(model6_bayes, newdata = new_data_f_vr, summary = TRUE, 
+                           re_formula = NA, intervals = "confidence")
 
   # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
-  fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+  fresh_pred_non_sum_vr <- cbind(new_data_f_vr, t(predict(model6_bayes, newdata = new_data_f_vr,
+                                                          summary = FALSE, re_formula = NA)))
 
   # Lets merge predictions with the original data
-  fresh_data <- cbind(fresh_data, fresh_pred)
+  fresh_data_vr <- cbind(fresh_data_vr, fresh_pred_vr)
 
@@
 Note there are only 134 species because this is subset of the wild data.
-         all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% 
+         all_pred_vr <- rbind(terrest_data_vr, marine_data_vr, fresh_data_vr) %>% 
                         dplyr::select(-species_full)  %>% 
-                     mutate(uniques = interaction(spp, Latitude, Longitude))
-  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>%      dplyr::select(-species_full)
-        spp_wild  <- length(unique(sub_data$spp))
+                        mutate(uniques = as.character(interaction(spp, Latitude, Longitude)))
+  all_pred_no_sum_vr <- rbind(terre_pred_no_sum_vr, marine_pred_no_sum_vr, fresh_pred_non_sum_vr) %>%      
+                        dplyr::select(-species_full)
+           spp_wild  <- length(unique(sub_data_vr$spp))
 ```
 
-```{r, future_clim}
+```{r, future_climvr}
 #| label: future_clim
@@
 # Now, lets summarise the mean for the current temps (i.e., 2018-2022)
-current_temps <-   future_temp  %>% 
-                   dplyr::select(Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(future_temp)))  %>% 
-                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15, match = interaction(Species, Latitude, Longitude))
+current_temps <-   future_temp  %>% dplyr::select(Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(future_temp)))  %>% mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15, match = interaction(Species, Latitude, Longitude))
 
 # Lets clean this data up.
-We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins.
+We only need the mean temperature here, but this needs to be converted to Celsius as right now it's in Kelvins.
 We'll now take the last 5 years of the future temperature 2096-2100
-  future_temps  <- future_temp  %>% 
-                  dplyr::select(Species, Latitude, Longitude,  grep("X2096|X2097|X2098|X2099|X2100", colnames(future_temp)))  %>% 
-                  mutate(mean = apply(.[, grep("X2096|X2097|X2098|X2099|X2100", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_future = mean - 273.15,  match = interaction(Species, Latitude, Longitude))
-
-# Now we can merge the climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
-
-  climate_data <- left_join(current_temps, future_temps, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
+  future_temps  <- future_temp  %>% dplyr::select(Species, Latitude, Longitude,  grep("X2096|X2097|X2098|X2099|X2100", colnames(future_temp)))  %>% mutate(mean = apply(.[, grep("X2096|X2097|X2098|X2099|X2100", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_future = mean - 273.15,  match = interaction(Species, Latitude, Longitude))
+
+# Now we can merge the climate data sets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
+
+  climate_data <- left_join(current_temps, future_temps, by = "match")  %>% 
+                  dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% 
+                  mutate(T_change = Celc_future - Celc_curr)  %>% 
+                  rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
 
@@
 
-# Lets have a global plot of temperature changes to see it sptially
+# Lets have a global plot of temperature changes to see it spatially
 
@@
 
-# Now lets merge all_pred with the climate projections
+# Now lets merge all_pred_vr with the climate projections
   # Simplify columns 
@@
   # Merge with model predictions.
-This is the predicted lnCVRQ10 for 10C change AT the specific latitude and longitude.
+This is the predicted lnVRQ10 for 10C change AT the specific latitude and longitude.
 We must assume that there is no plasticity or adaptation at each site to make projections.
-  all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
+  all_pred2_vr <- all_pred_vr %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
               left_join(., climate_data_new, by = "match")  %>% 
-              mutate(lnCVR_future = (Estimate / 10) * T_change,
-                      lnCVR_F_l95 = (Q2.5 / 10) * T_change,
-                      lnCVR_F_u95 = (Q97.5 / 10) * T_change, 
-                      per_change = (exp(lnCVR_future) - 1) * 100,
-                      per_change_l95 = (exp(lnCVR_F_l95) - 1) * 100,
-                      per_change_u95 = (exp(lnCVR_F_u95) - 1) * 100)
-
-  # First, lets merge the climate data with the predictions, but here predictions are not summarised. We have the entire posteior
-
-    all_pred2_no_sum <-  all_pred_no_sum %>% 
+              mutate(lnVR_future = (Estimate / 10) * T_change,
+                      lnVR_F_l95 = (Q2.5 / 10) * T_change,
+                      lnVR_F_u95 = (Q97.5 / 10) * T_change, 
+                      per_change = (exp(lnVR_future) - 1) * 100,
+                      per_change_l95 = (exp(lnVR_F_l95) - 1) * 100,
+                      per_change_u95 = (exp(lnVR_F_u95) - 1) * 100,
+                     match = as.character(match),
+                     uniques = as.character(uniques))
+
+  # First, lets merge the climate data with the predictions, but here predictions are not summarized. We have the entire posterior
+
+    all_pred2_no_sum_vr <-  all_pred_no_sum_vr %>% 
                         mutate(match = interaction(spp, Latitude, Longitude))  %>% 
@@
 
-  # Second, lets convert each estimate to lncvr to 1 degree C instead of 10...
-   all_pred2_no_sum2 <- all_pred2_no_sum %>%  
-                        mutate_if(colnames(.) %in% c(1:3200), lncvr_1c)
+  # Second, lets convert each estimate to lnvr to 1 degree C instead of 10...
+   all_pred2_no_sum2_vr <- all_pred2_no_sum_vr %>%  
+                        mutate_if(colnames(.) %in% c(1:3200), lncvr_1c) # Note, names lncvr_1c but will work for any effect
 
   # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
-    all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]  <- all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)] * all_pred2_no_sum2$T_change
+    all_pred2_no_sum2_vr[,colnames(all_pred2_no_sum2_vr) %in% c(1:3200)]  <- all_pred2_no_sum2_vr[,colnames(all_pred2_no_sum2_vr) %in% c(1:3200)] * all_pred2_no_sum2_vr$T_change
 
   # Fourth, we can calculate the percentage change on the posterior
-    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]) - 1)*100
+    all_pred2_no_sum2_vr[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2_vr[,colnames(all_pred2_no_sum2_vr) %in% c(1:3200)]) - 1)*100
 
@@
 We can then use this to calculate the 95% CI's.
-    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) 
+    mean_perc <-  apply(all_pred2_no_sum2_vr[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) 
     mean(mean_perc)
@@
   # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
-  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE))
-  lapply(mean_perc_habitat, mean)
-  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
-  #lapply(mean_perc_habitat, hist)
+  mean_perc_habitat_vr <-  lapply(split(all_pred2_no_sum2_vr,  all_pred2_no_sum2_vr$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE))
+  lapply(mean_perc_habitat_vr, mean)
+  lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))
 
 # Create a table to summarise everything
-tables_future <- all_pred2 %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
+tables_future <- all_pred2_vr %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
                                                                 l95 = mean(per_change_l95, na.rm = TRUE), 
@@
 
-# Check on how many to decrease
-  decreases <- all_pred2 %>% group_by(match)  %>% summarise(n = if_else(any(per_change < 0), 1, 0))
+# Check on how many to increase
+  increases <- all_pred2_vr %>% group_by(match)  %>% summarise(n = if_else(any(per_change > 0), 1, 0))
 
@@
 were much less common than from captive populations ($N_{species}$ =
-`r length(unique(all_pred$spp))`, from
-`r length(unique(all_pred$uniques))` wild populations). Globally, there
+`r length(unique(all_pred2_vr$spp))`, from
+`r length(unique(all_pred2_vr$uniques))` wild populations). Globally, there
 was a clear bias towards species in the Northern Hemisphere
@@
 in physiological rate variance, while others showing an increase
-([@fig-fig6]D). However, out of the `r length(unique(all_pred2$match))`
-populations, relative variance was predicted to decrease in
-`r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`%
+([@fig-fig6]D). However, out of the `r length(unique(all_pred2_vr$match))`
+populations, variance was predicted to increase to some extent at
+`r (sum(increases$n, na.rm = TRUE) / length(increases$n[complete.cases(increases$n)]))*100`%
 of the locations.
@@
 physiological rate variance were generally conservative with our model
-explaining \~ 50% of the variation in the observed data ($R^2$ =
-`r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)`
-to `r round(quantile(r2_2, 0.975)[1], 2)`). Climate change is predicted
-to result in a `r abs(lapply(mean_perc_habitat, mean)$f)`% reduction in
+explaining ~ 43% of the variation in the observed data ($R^2$ =
+`r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)`
+to `r round(quantile(r2, 0.975)[1], 2)`). Climate change is predicted
+to result in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% reduction in
 relative variance for freshwater systems (95% CI:
-`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]`
+`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]`
 to
-`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%,
-$p_{MCMC}$ = `r pmcmc(mean_perc_habitat$f)`), a
-`r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in relative
+`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%,
+$p_{MCMC}$ = `r pmcmc(mean_perc_habitat_vr$f)`), a
+`r abs(lapply(mean_perc_habitat_vr, mean)$m)`% reduction in relative
 variance for marine systems (95% CI:
-`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]`
+`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]`
 to
-`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%,
-$p_{MCMC}$ = `r pmcmc(mean_perc_habitat$m)`), and a
-`r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in relative
+`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%,
+$p_{MCMC}$ = `r pmcmc(mean_perc_habitat_vr$m)`), and a
+`r abs(lapply(mean_perc_habitat_vr, mean)$t)`% reduction in relative
 variance for terrestrial systems (95% CI:
-`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]`
+`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]`
 to
-`r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%,
-$p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat$t))`) under a RCP8.5
+`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%,
+$p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5
 climate scenario. All results are taken from "Model 6".
@@
 #| message: false
-#| fig-cap: "Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+#| fig-cap: "Model predictions for the expected change in acclimation $lnVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
 Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
@@
   geom_point(
-    data = all_pred  %>% filter(type == "acclim"),
+    data = all_pred_vr  %>% filter(type == "acclim"),
     aes(Longitude, Latitude, color = Estimate),
     alpha = 0.7, size = 5
-  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$"), title = "Current (2018-2022)") + scale_color_viridis() + theme_map(base_size = 22) +  theme(plot.title = element_text(hjust = 0.5))
+  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnVR_{Q_{10}}$"), title = "Current (2018-2022)") + scale_color_viridis() + theme_map(base_size = 22) +  theme(plot.title = element_text(hjust = 0.5))
 
@@
     geom_point(
-      data = all_pred2[complete.cases(all_pred2$per_change),],
+      data = all_pred2_vr[complete.cases(all_pred2_vr$per_change),],
       aes(Longitude, Latitude, color = per_change),
@@
 
+#### *Mean-variance relationships to understand patterns in* $lnCVR_{Q_{10}}$
+
+```{r, mc_models}
+#| label: mc_models
+#| echo: false
+#| include: false
+
+ # Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
+rerun = FALSE
+if(rerun) {
+
+      r_11_m <- bf(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+      r_12_m <- bf(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+      r_21_m <- bf(log(r2.1_sd) ~ log(r2.1)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+      r_22_m <- bf(log(r2.2_sd) ~ log(r2.2)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
+
+      mv_model_all <- brm(r_11_m + r_12_m + r_21_m + r_22_m + set_rescor(TRUE), 
+                          chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, 
+                          control = list(adapt_delta = 0.98), data = lnRRQ10_data)
+       saveRDS(mv_model_all, file = "./output/models/mv_model_all")
+
+} else {
+        mv_model_all <- readRDS("./output/models/mv_model_all")
+}
+
+# Post processing
+  model_mv1.1 <- posterior_samples(mv_model_all,  pars = "^b_logr11") # Acclimated at 1, measured at 1
+  model_mv1.2 <- posterior_samples(mv_model_all,  pars = "^b_logr12") # Acclimated at 1, measured at 2; Acute
+  model_mv2.2 <- posterior_samples(mv_model_all,  pars = "^b_logr22") # Acclimated at 2, measured at 2
+  model_mv2.1 <- posterior_samples(mv_model_all,  pars = "^b_logr21") # Acclimated at 2, measured at 1; Acute
+
+# Extract slopes
+    slope_extract <- function(x, v){
+        list = list()
+         list[['fresh']] <-  x[,2]  # Slope for freshwater
+        list[['marine']] <-  x[,2] + x[, grepl(":habitatm", colnames(x))] # Slope for marine
+         list[['terrs']] <-  x[,2] + x[, grepl(":habitatt", colnames(x))] # Slope for terrestrial
+         return(list)
+    }
+
+# From each model, lets get the slopes for each habitat
+         r1.1 <-  slope_extract(model_mv1.1)
+         r1.2 <-  slope_extract(model_mv1.2)
+         r2.1 <-  slope_extract(model_mv2.1)
+         r2.2 <-  slope_extract(model_mv2.2)
+
+# Summary
+         table <- data.frame(
+                               mean = do.call("rbind", lapply(r1.1,  mean)),
+                               L = do.call("rbind", lapply(r1.1,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r1.1,  function(x) quantile(x, 0.975))))
+
+         r_1.2 = data.frame( mean = do.call("rbind", lapply(r1.2,  mean)),
+                               L = do.call("rbind", lapply(r1.2,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r1.2,  function(x) quantile(x, 0.975))))
+         r_2.1 = data.frame(mean = do.call("rbind", lapply(r2.1,  mean)),
+                               L = do.call("rbind", lapply(r2.1,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r2.1,  function(x) quantile(x, 0.975))))
+          r_2.2 = data.frame(mean = do.call("rbind", lapply(r2.2,  mean)),
+                               L = do.call("rbind", lapply(r2.2,  function(x) quantile(x, 0.025))),
+                               U = do.call("rbind", lapply(r2.2,  function(x) quantile(x, 0.975))))
+
+          table <- rbind(table, r_1.2,  r_2.1, r_2.2)
+          table$habitat <- rep(c("Freshwater", "Marine", "Terrestrial"), 4)
+          table$type <- c(rep("r1.1",3),
+                          rep("r1.2", 3),
+                          rep("r2.1",3),
+                          rep("r2.2", 3))
+          rownames(table) <- NULL
+
+    table <- table %>% dplyr::select(type, habitat, mean, X2.5., X97.5.) %>% rename("2.5%" = X2.5.,
+                                                                                    "97.5%" = X97.5.,
+                                                                                    "Slope" = mean,
+                                                                                    "Treatment" = type,
+                                                                                    "Habitat" = habitat) %>% 
+      mutate(Type = ifelse(Treatment %in% c("r1.1", "r2.2"), "Acclimation", ifelse(Treatment %in% c("r1.2", "r2.1"), "Acute", " "))) %>% relocate(Type, .before = Treatment) %>% dplyr::arrange(Habitat)
+```
+
+We explored mean-variance relationships for the acute and acclimation
+responses across all traits and habitats. We estimated the scaling
+relationship between log standard deviation in physiological rates
+[log(SD)] and log mean physiological rates [log(mean)], accounting
+for non-independence resulting from effects coming from the same
+species, study and traits (i.e., random effects of species, study and
+trait) as done in our main analyses. We also included an interaction
+between log(mean) and habitat type to better understand how the scaling
+relationship between log(SD) and log(mean) varies across habitats.
+
+Overall, we found that the relationship between log(mean) and log(SD) of
+the acute and acclimation responses was generally linear, suggesting
+that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv). Overall, the
+scaling relationship between log(SD) and log(mean) was sub-linear across
+all habitats (@tbl-slopes), however, ectotherms from terrestrial
+habitats had much shallower slopes than marine and freshwater
+ectotherms, particularly at higher treatment temperatures, indicating
+increased mean physiological rates generally do not result in higher
+between individual variance in physiological rates (@tbl-slopes).
+Interestingly, in marine ectotherms the slope was highest at cooler
+temperatures, wheeras the slope was suppressed when acclimated and/or
+measured at higher temperatures (i.e., r.1. compared to r1.2, r2.1,
+r2.2) (@tbl-slopes). In freshwater ectotherms, there we some differences
+in scaling relationships but they were all fairly comparable no matter
+what acclimation and test temperature (@tbl-slopes).
+
+```{r, fig-mv}
+#| label: fig-mv
+#| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
+Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
+    col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+  mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd),color = habitat)) +
+                  geom_point(aes(color = habitat), size = 2.2) + 
+                  geom_smooth(method = "lm", se = FALSE) + 
+                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                  scale_colour_manual(values = col) + 
+                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
+                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
+
+  mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd), color = habitat)) +
+                  geom_point(aes(color = habitat), size = 2.2) + 
+                  geom_smooth(method = "lm", se = FALSE) + 
+                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
+                  scale_colour_manual(values = col)  +
+                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
+                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
+
+ p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
+  ggsave(p_mv, file = "./output/figures/figS7.png", height = 8, width = 8)
+
+  p_mv <- magick::image_read("./output/figures/figS7.png")
+  p_mv
+```
+
+```{r, tbl-slopes}
+#| label: tbl-slopes
+#| tbl-cap: "Slopes and 95% credible intervals (lower = 2.5% and upper = 97.5%) of log transformed standard deviation (log(SD)) and log transformed mean (log(mean)) for each of the four treatment types (r1.1, r1.2, r2.1, r2.2).
+Note that r1.1 and r2.2 represent measurements of physiological rates of acclimated animals and measured at their respective acclimation temperature.
+In contrast, r1.2 and r2.1 are acute measurements.
+See Figure 1 in main manuscript for full details on treatments."
+
+flextable(table) %>% bold(part = "header") %>% autofit()
+```
+
+#### *Comparing relative variance changes using* $lnCVR_{Q_{10}}$
+
+```{r, lncvrq10}
+#| label: lncvrq10
+#| echo: false
+#| warning: false
+#| error: false
+#| include: false
+#| cache: false
+
+#############
+  ## lnCVRQ10
+#############
+##################################################
+  # Organise the data and prune tree
+#################################################
+  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
+          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
+
+###################################################
+  # Model 2.1: Intercept only model.
+  # Used for heterogeneity analysis
+###################################################
+rerun = FALSE
+if(rerun){
+  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.1
+  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
+  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
+} else{ 
+        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
+  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
+}
+
+# Heterogeneity analysis
+   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
+  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
+  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
+
+    res_cvr <- posteriors_2.1[,"sigma"]
+   stdy_cvr <- posteriors_2.1[,"record_num"]
+  phylo_cvr <- posteriors_2.1[,"species_full"]
+    spp_cvr <- posteriors_2.1[,"spp"]
+  trait_cvr <- posteriors_2.1[,"trait"]
+  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
+
+  # Calculate I2
+     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
+   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
+     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
+    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
+   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
+     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
+
+  # Table
+     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
+                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
+
+###################################################
+  # Model 2.2: Model controlling for acclimation time, 
+  # type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model1.2
+  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
+  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
+
+  } else{
+        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
+  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
+}
+
+######################################################
+  # Bayesian Contrasts
+######################################################
+
+  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
+  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
+  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
+  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
+  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
+  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
+  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
+
+# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
+It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
+  # First get sample sizes
+    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
+    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
+    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
+
+  # Lets now convert these to a %
+    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
+    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
+    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
+
+###################################################
+  # Model 2.3: Model controlling for acclimation time, 
+  # type and trait category assuming type can vary by habitat
+###################################################
+  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
+    lnCVRQ10_data <- lnCVRQ10_data %>% 
+                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
+                                                "tissue/organism",
+                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
+                                                "biochemical", trait_category)))
+ # We can also run subsets for each habitat
+   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
+
+ # cor matrices
+   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
+   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
+   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
+
+if(rerun){
+
+  # Full Bayesian model   
+   model2.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+                                           (1 | record_num) + 
+                                           (1 | gr(species_full, cov = A)) + 
+                                           (1 + max_temp_c | spp) +(1|trait) + 
+                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
+                                         data2 = list(A=A), family = gaussian(), 
+                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnCVRQ10_data, trait_broad != "other"))
+    saveRDS(model2.3_btrait_bayes, "./output/models/model2.3_btrait_bayes")
+
+  # Metafor models for creating plots. Subset by habitat to make this easier
+      # Marine
+         model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = filter(lnCVRQ10_data, habitat == "m" & trait_broad != "other"))
+         saveRDS(model2.3_m_broad, "output/models/model2.3_m_broad")
+
+      # Freshwater
+         model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"),  phi = 0,
+                              data = filter(lnCVRQ10_data, habitat == "f" & trait_broad != "other"))
+          saveRDS(model2.3_f_broad, "output/models/model2.3_f_broad")
+
+      # Terrestrial
+         model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = filter(lnCVRQ10_data, habitat == "t" & trait_broad != "other"))
+         saveRDS(model2.3_t_broad, "output/models/model2.3_t_broad")
+
+  } else{
+    model2.3_btrait_bayes <- readRDS("./output/models/model2.3_btrait_bayes")
+    model2.3_m_broad <- readRDS("output/models/model2.3_m_broad")
+    model2.3_f_broad <- readRDS("output/models/model2.3_f_broad")
+    model2.3_t_broad <- readRDS("output/models/model2.3_t_broad")
+}
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       trait_b_data <- data.frame(  type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lncvr_traitb <- fitted(model2.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lncvr_traitb <- cbind(trait_b_data, pred_lncvr_traitb)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lncvr_traitb_post <- fitted(model2.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lncvr_trait_post <-  pred_lncvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lncvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lncvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lncvr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lncvr_trait_post), function(x) p_value(pmcmc(x))))
+
+   # Contrasts for pooled acute and acclimation across trait categories
+
+            contrast_lncvr_trait_cat_stats <- rbind(get_whole_bio(pred_lncvr_traitb_post, habitat = "t", trait_b_data),
+                                                        get_whole_bio(pred_lncvr_traitb_post, habitat = "m", trait_b_data),
+                                                        get_whole_bio(pred_lncvr_traitb_post, habitat = "f", trait_b_data))
+
+###################################################
+  # Model 2.4: Model controlling for acclimation time, 
+  # type and life history stage assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model 
+  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data)
+  # Save model
+  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
+
+   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
+                                 (~1 | record_num) + 
+                                 (1 | gr(species_full, cov = A_CVR)) + 
+                                 (1 + max_temp_c| spp) + 
+                                 (1|trait) +
+                                 (1|obs), 
+                               data2 = list(A_CVR=A_CVR), family = gaussian(), 
+                               prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                               control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+
+  # Save model
+  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
+
+  } else{
+        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
+  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
+}
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       lh_b_data <- data.frame( c_accl_time = 0, 
+                          max_temp_c = 0, 
+                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
+                             habitat = rep(c("m", "f", "t"), each = 4), 
+                           life.hist = rep(c("j", "a"), each = 2))
+
+            # I have no idea why the fitted function is not working on this model. We're doing this the old fashioned way
+            X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = lh_b_data)
+
+            # Extract posteriors
+              post_lh <- posterior_samples(model2.4_bayes, pars = "^b")
+
+        # Now we can do all the calculations in one shot.# Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lh <- apply(t(post_lh),2 , function(x) as.matrix(X)%*%x)
+
+        contrast_lncvr_lh_post <-  pred_lh[c(1,3,5,7,9,11),] - pred_lh[c(2,4,6,8,10,12),] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     stage = rep(c("j", "a"), each = 1),
+                                                    diff = apply(data.frame(contrast_lncvr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) p_value(pmcmc(x))))
+```
+
+Overall, analyses with $lnCVR_{Q_{10}}$ showed similar patterns to those with $lnVR_{Q_{10}}$, except that, because of rates being taken into consideration and there is a strong mean-variance relationship, the patterns were generally opposite in direction.
+Either way, the relative differences are quite similar.
+Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with
+higher temperatures across all habitat types, with terrestrial
+ectotherms having the largest decrease in relative variance (@fig-s1).
+There were also no major differences in the relative differences among broad trait categories (@fig-cvrbtrait) or life-history stages (@fig-lncvrlh).
+
+```{r, fig-s1}
+#| label: fig-s1
+#| fig-align: center
+#| fig-cap: "Estimated mean acute and acclimation $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial habitats.
+The percentage change in variance is also back calculated.
+Note that these are raw variances and do not account for changes in mean physiological rates.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+$\\Beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying .
+$\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
+In both cases, their 95% CI's are indicated within square brackets.
+$p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
+For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles."
+
+#################
+# Fig S CVR
+##################
+  # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
+But, there is a clear reduction in between individual variance for terrestrial species.
+As temperature get hotter then the variance in physiological rates decreases.
+This is not true of aquatic systems.
+  col <- c("#0871B9", "#F3B40D", "#1BB908")
+  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
+
+  x1 = 1.4
+  x2 = 2.4
+  x3 = 3.4
+
+  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8,  k.pos = "none")  +
+              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) +
+
+  annotate("text", x = x1, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+         annotate("text", x = x1, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x1-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 8) + 
+  annotate("text", x = x1-0.20, y = 1, label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = x2, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+     annotate("text", x = x2, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x2-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 8) +
+  annotate("text", x = x2-0.20, y = 1, label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = x3+0.10, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
+  annotate("text", x = x3+0.10, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
+  annotate("text", x = x3-0.10, y = 1, label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) + 
+  annotate("text", x = x3-0.10, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 8) +
+
+    labs(shape = "Type") +
+    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)
+
+  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_blank(),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")
+
+########
+
+##################
+  # Figure S1
+##################
+
+  ggsave(p3, filename = "./output/figures/figS8.pdf", width = 11.5, height = 8)
+
+  figs1 <- image_read("./output/figures/figS8.pdf")
+  figs1
+```
+
+```{r, fig-cvrbtrait}
+#| label: fig-cvrbtrait
+#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for tissue/whole-orgamism traits and biochemical traits across marine (A), freshwater (B) and terrestrial (C) habitats.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
+$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+#| echo: false
+#| warning: false
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lncvr_btrait  <- lnCVRQ10_data  %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+
+       col <- c("#0871B9", "#F3B40D", "#1BB908")
+     x.pos <- c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+############
+# CVR
+############
+m_cv <- n_lncvr_btrait %>% filter(habitat == "m")
+f_cv <- n_lncvr_btrait %>% filter(habitat == "f")
+t_cv <- n_lncvr_btrait %>% filter(habitat == "t")
+
+t_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
+
+############
+# Full fig
+############
+figbtrait_vr <-(p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A") 
+ggsave(figbtrait_vr, filename = "./output/figures/figStrait_cvr.png", width = 28, height = 8, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figStrait_cvr.png")
+figbtrait
+```
+
+```{r, fig-lncvrlh}
+#| label: fig-lncvrlh
+#| echo: false
+#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for marine (A), freshwater (B) and terrestrial (C) ectotherms.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
+$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lncvr_lh <- lnCVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+
+x.pos = c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+###############
+# ln CVR
+###############
+m_cv <- n_lncvr_lh %>% filter(habitat == "m")
+f_cv <- n_lncvr_lh %>% filter(habitat == "f")
+t_cv <- n_lncvr_lh %>% filter(habitat == "t")
+
+  t_trait_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
+ggsave(figcvr_lh, filename = "./output/figures/figSlh.pdf", width = 28, height = 10, device = "pdf")
+
+figcvr_lh <- magick::image_read("./output/figures/figSlh.pdf")
+figcvr_lh
+
+```
+
+```{r wildlncvr}
+#| label: wildlncvr
+#| cache: true
+#| include: false
+#| echo: false
+#| warning: false
+#| 
+#######################################
+  ## lnCVRQ10 from Wild Populations ##
+#######################################
+##################################################
+  # Organise the data and prune tree
+##################################################
+
+# Bring in  historial climate data
+  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+# Create a match column.
+  climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% 
+                          dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+
+# Populations and species?
+  pop_spp_w <- climate2[complete.cases(climate2),]
+
+# Subset the data
+  lnCVRQ10_data_wild <- data_long2 %>% 
+    filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+                        mutate(spp = species_full, 
+                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
+                                     match = interaction(spp, lat, long),
+                                     max_temp_c = scale(temp_2, scale = FALSE))
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+  lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
+
+# Look at the environment details across different habitats. 
+  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(sd))
+
+# Check and prune tree
+  tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+  tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+  phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
+          A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale environment variables
+    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
+                                                        acf_all_c = scale(acf_all),
+                                                        acf_lag1_c = scale(acf_lag1))
+
+####################################################
+  # Model 4.3: Model environmental variability by acute/acclim
+####################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild)
+
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+
+  # Save model4.3
+  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
+  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
+
+  } else{
+        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
+  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
+}
+
+############################################################################################
+# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
+# differently in each habitat
+############################################################################################          
+  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
+
+  # Create the phylo correlation matrix
+
+  # Check and prune tree
+tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
+
+phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
+        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
+
+if(rerun){
+  # More realistic model with 
+  model4.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim)
+
+   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
+
+  # Save model3.8
+  saveRDS(model4.9, file = "./output/models/lnCVRQ10_4.9")
+  saveRDS(model4.9_bayes, file = "./output/models/lnCVRQ10_4.9_bayes")
+
+  } else{
+        model4.9 <- readRDS("./output/models/lnCVRQ10_4.9")
+  model4.9_bayes <- readRDS("./output/models/lnCVRQ10_4.9_bayes")
+}
+
+#################################################
+### Bayesian Slopes from Model 4.9
+#################################################
+ posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
+
+    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
+    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
+    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
+
+##################################################
+    # Model 4.8, 4.9 and 4.10 - Habitat subset
+    # Used for making plots
+##################################################
+    # Subset data to habitat
+    lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
+    lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")
+    lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
+
+if(rerun){
+    # Terrestrial Models
+    model4.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
+    saveRDS(model4.9_t, "./output/models/model4.9_t")
+
+    # Freshwater Models
+
+    model4.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
+
+    saveRDS(model4.9_f, "./output/models/model4.9_f")
+
+    # Marine Models
+
+    model4.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
+                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
+    saveRDS(model4.9_m, "./output/models/model4.9_m")
+
+  } else {
+     model4.9_t <- readRDS("./output/models/model4.9_t")
+     model4.9_f <- readRDS("./output/models/model4.9_f")
+     model4.9_m <- readRDS("./output/models/model4.9_m")
+}
+
+```
+
+```{r, globallncvr}
+#| label: globallncvr
+#| echo: false
+#| include: false
+
+# Here, we want to make global predictions, at the lat/long in the data for how the opportunity of selection is expected to change with climate change.
+How can we do this?
+Q10 effects already have temperature controls within the effect size.
+So, what we want is to be able to understand how Q10 changes with latitude and longitude.
+Once we know that, we an extract how temperature is expected to change from our current levels to future levels.
+This will be in degrees C.
+Then, assuming no plasticity and evolution (big assumption) we can get a baseline change in variance for each site.
+We first need to adjust the predicted Q10 value so that it's at 1C temperature, not 10, we can do this through this formula Qt = (Q10 / 10)*T, where T is the temperature change in C.
+This will adjust the predicted Q10 value to the change in 1 degree C.
+We can then multiply this by the temperature change expected at that location to get the % change in variance or acure/acclim response.
+We can then plot these globally.
+
+#############################
+rerun = FALSE
+if(rerun){
+
+  # Model lat and long.
+Need to exclude missing acclimdation data.
+That will make it easier to create predcitions and explore the model fit.
+Include max temp to correct predictions for possible decrease at higher temps.
+
+   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) +
+                               (1 | record_num) + 
+                               (1 | gr(species_full, cov = A_wild_cvr)) + 
+                               (1 + max_temp_c | spp) + 
+                               (1 | trait) + 
+                               (1 | obs), 
+                      data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), 
+                      prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                      control = list(adapt_delta = 0.99, max_treedepth = 12), 
+                      chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
+                      data = lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),])
+
+  saveRDS(model5_bayes, file = "./output/models/lnCVRQ10_5_bayes")
+
+  } else{
+  model5_bayes <- readRDS("./output/models/lnCVRQ10_5_bayes")
+}
+
+# Lets explore the model and how it's predicting the real data
+  data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+
+# combine with predictions
+  data_w_pred <- cbind(data_w, predict(model5_bayes))
+
+# Fitted vs actual data
+  ggplot(data = data_w_pred, aes(x = Estimate, y = effect_size))      + 
+        geom_point() + geom_smooth(method = "lm")                     + 
+        labs(x = "Predicted Effect Size", y = "Observed Effect Size") + 
+        theme_classic()                                               + 
+        geom_abline(intercept = 0, slope = 1)
+
+# Seems to be OK, but over and under-predicting at times.
+Lets explore the data for odd ball predictions to see if there are any obvious reasons why.
+There are very few for the most part but lets see why sign changes occur which are most striking differences.
+Sign changes indicate the observed data is completely opposite in sign to the predicted data
+
+#  Spot check of a bunch of studies doesn't show any obvious issues with the data.
+Note that data is repeated because acute and acclimated rates are calculated.
+We expect the rows of raw data for acute and acclim to be repeated even though these data are NOT all used to make the calculation.
+  sign_change_dat <- data_w_pred  %>% filter(sign(Estimate) != sign(effect_size))
+  #View(sign_change_dat)
+
+# Fitted by Lat/long Longitude, Latitude
+  ggplot(data = data_w_pred, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
+
+# Observed by Lat/long
+  ggplot(data = data_w_pred, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
+
+  ggplot(data = data_w_pred, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
+
+# How much variation does this model explain.
+Need to do this manually because function doesn't seme to work on the model object.
+We need to remember that predcit will include random effect variances so we may need to exclude this
+  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
+  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)
+
+# sigma2_v = typical sampling error variance
+sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
+  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
+              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))
+
+# Now check that var fix from raw data and remove sampling variance. 
+  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
+
+# Extract the random effect variances
+  v_trait <- re_post$sd_trait__Intercept^2
+    v_spp <- re_post$sd_spp__Intercept^2
+    v_phy <- re_post$sd_species_full__Intercept^2
+    v_std <- re_post$sd_record_num__Intercept^2
+      v_r <- re_post$sd_obs__Intercept^2
+
+# Lets get the total variance for the random effects only
+  tot_re <- v_trait + v_spp + v_phy + v_std + v_r
+
+# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
+    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too
+
+    mean(r2) # Seems a bit high 0.53
+  quantile(r2, probs = c(0.025, 0.975)); #0.30-0.72
+
+# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
+  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2
+
+  mean(r2_2) #  0.50
+  quantile(r2_2, probs = c(0.025, 0.975)); #0.33-0.62
+
+######################################################################
+# Model predictions for terrestrial, marine and freshwater ectotherms
+######################################################################
+# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
+
+#############################
+## Terrestrial ectotherms
+#############################
+
+  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+  new_data_t <- data.frame(
+      max_temp_c = 0, 
+      c_accl_time = 0,
+      V = 0,
+      trait = 0,
+      obs = 0, 
+      record_num = 0
+    )
+
+  # Create new data frame with only unique values for prediction.
+  new_data_t2  <- cbind(terrest_data, new_data_t)
+
+  # We'll now make the predictions from the model object using the new data frame
+  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
+  # Lets merge predictions with the original data
+  terrest_data <- cbind(terrest_data, terre_pred)
+
+  # Test manual calculations.
+We can also set summary = FALSE and then do the calculations ourselves.
+Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE .
+These are extremely close, and I suspect are only different because sample_new_levels is sampling differently each time predict is run, so will be slightly different from run-to-run
+  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
+  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
+
+#############################
+## Marine ectotherms  
+#############################
+  marine_data <- sub_data  %>% filter(habitat == "m") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+
+  new_data_m <- data.frame(
+       max_temp_c = 0, 
+      c_accl_time = 0,
+                V = 0,
+            trait = 0,
+              obs = 0, 
+       record_num = 0
+    )
+
+  # Create new data frame with only unique values for prediction.
+  new_data_m  <- cbind(marine_data, new_data_m)
+
+  # We'll now make the predictions from the model object using the new data frame
+  marine_pred <- predict(model5_bayes, newdata = new_data_m, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
+  # Lets merge predictions with the original data
+  marine_data <- cbind(marine_data, marine_pred)
+
+#############################
+## Freshwater ectotherms
+#############################
+  fresh_data <- sub_data  %>% filter(habitat == "f") %>% distinct(spp, species_full, habitat, type, Latitude, Longitude)
+
+  new_data_f <- data.frame(
+       max_temp_c = 0, 
+      c_accl_time = 0,
+                V = 0,
+            trait = 0,
+              obs = 0, 
+       record_num = 0
+    )
+
+  # Create new data frame with only unique values for prediction.
+  new_data_f  <- cbind(fresh_data, new_data_f)
+
+  # We'll now make the predictions from the model object using the new data frame
+  fresh_pred <- predict(model5_bayes, newdata = new_data_f, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")
+
+  # We'll also keep the whole posterior which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
+  fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))
+
+  # Lets merge predictions with the original data
+  fresh_data <- cbind(fresh_data, fresh_pred)
+
+# Now that we have all the predictions we can merge the data together.
+Note that species itself is not really that useful because each prediction at each latitude and longitude should incorporate the species effect.
+So we'll remove it.
+While I retain spp, it's still not totally specific to the species, but left it there so it's clear how these data match with the wild data.
+Note there are only 134 species because this is subset of the wild data.
+         all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% 
+                     dplyr::select(-species_full)  %>% 
+                     mutate(uniques = interaction(spp, Latitude, Longitude))
+  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>%      dplyr::select(-species_full)
+        spp_wild  <- length(unique(sub_data$spp))
+```
+
+```{r, future_climlncvr}
+#| label: future_climlncvr
+#| echo: false
+#| warning: false
+#| include: false
+
+# Now we want to take the predictions from `global` and use this for future climate sceneios.
+We have the future temperatures expected for each location.
+We can then use the predicted Q10 values to calculate the expected change in variance.
+We can then plot these globally.
+
+# First, lets get the current and future temperature data for 2081-2085. We'll use the mean. 
+  future_temp <- read.csv("./output/climate_data/CanESM2_air_and_SST_timeseries.csv")
+
+# Now, lets summarise the mean for the current temps (i.e., 2018-2022)
+current_temps <-   future_temp  %>% 
+                   dplyr::select(Species, Latitude, Longitude, grep("X2018|X2019|X2020|X2021|X2022", colnames(future_temp)))  %>% 
+                                mutate(mean = apply(.[, grep("X2018|X2019|X2020|X2021|X2022", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_curr = mean - 273.15, match = interaction(Species, Latitude, Longitude))
+
+# Lets clean this data up.
+We only need the mean temperature here, but this needs to be converted to Celcius as right now it's in Kelvins.
+We'll now take the last 5 years of the future temperature 2096-2100
+  future_temps  <- future_temp  %>% 
+                  dplyr::select(Species, Latitude, Longitude,  grep("X2096|X2097|X2098|X2099|X2100", colnames(future_temp)))  %>% 
+                  mutate(mean = apply(.[, grep("X2096|X2097|X2098|X2099|X2100", colnames(.))], 1, function(x) mean(x, na.rm = TRUE)), Celc_future = mean - 273.15,  match = interaction(Species, Latitude, Longitude))
+
+# Now we can merge the climate datasets together so that we have the species, lat and long, current and future climate. Then we can calculate the expected 'increase' in T into the future
+
+  climate_data <- left_join(current_temps, future_temps, by = "match")  %>% dplyr::select(match, Latitude.x, Longitude.x, Species.x, Celc_curr, Celc_future)  %>% mutate(T_change = Celc_future - Celc_curr)  %>% rename(Species = Species.x, Latitude = Latitude.x, Longitude = Longitude.x)
+
+# Lets look at future and current. Most, I would expect, should be above the line indicating higher future temperatures.
+  ggplot(data = climate_data, aes(x = Celc_curr, y = Celc_future)) + geom_point() + geom_smooth(method = "lm") + labs(x = "Current Temperature (C)", y = "Future Temperature (C)") + theme_classic() + geom_abline(intercept = 0, slope = 1)
+
+# Lets have a global plot of temperature changes to see it sptially
+
+world_map = map_data("world") %>% 
+  filter(! long > 180)
+
+  map2_temp_proj <- ggplot() +
+    geom_map(
+      data = world_map, map = world_map,
+      aes(long, lat, map_id = region),
+      color = "black", fill = "lightgray") +
+    expand_limits(x = world_map$long, y = world_map$lat) +
+    coord_map("moll") +
+    geom_point(
+      data = climate_data[complete.cases(climate_data$T_change),],
+      aes(Longitude, Latitude, color = T_change),
+      alpha = 0.7, size = 5
+    ) + labs(x = "Longitude", y = "Latitude", color = TeX("$\\Delta$ Temp.
+($^\\circ$C)"), title = "Current (2018-2022) vs Future (2096-2100)") + scale_colour_gradient2(trans = "reverse") + theme_map(base_size = 22) + theme(plot.title = element_text(hjust = 0.5))
+
+# Now lets merge all_pred with the climate projections
+  # Simplify columns 
+  climate_data_new <- climate_data  %>% dplyr::select(-Latitude, -Longitude)
+
+  # Merge with model predictions.
+This is the predicted lnCVRQ10 for 10C change AT the specific latitude and longitude.
+We must assume that there is no plasticity or adaptation at each site to make projections.
+  all_pred2 <- all_pred %>% mutate(match = interaction(spp, Latitude, Longitude)) %>% 
+              left_join(., climate_data_new, by = "match")  %>% 
+              mutate(lnCVR_future = (Estimate / 10) * T_change,
+                      lnCVR_F_l95 = (Q2.5 / 10) * T_change,
+                      lnCVR_F_u95 = (Q97.5 / 10) * T_change, 
+                      per_change = (exp(lnCVR_future) - 1) * 100,
+                      per_change_l95 = (exp(lnCVR_F_l95) - 1) * 100,
+                      per_change_u95 = (exp(lnCVR_F_u95) - 1) * 100)
+
+  # First, lets merge the climate data with the predictions, but here predictions are not summarised. We have the entire posteior
+
+    all_pred2_no_sum <-  all_pred_no_sum %>% 
+                        mutate(match = interaction(spp, Latitude, Longitude))  %>% 
+                        left_join(., climate_data_new, by = "match")
+
+  # Second, lets convert each estimate to lncvr to 1 degree C instead of 10...
+   all_pred2_no_sum2 <- all_pred2_no_sum %>%  
+                        mutate_if(colnames(.) %in% c(1:3200), lncvr_1c)
+
+  # Third, lets multiply each estimate by the temperature change at that location. I've checked 4 different cells and they are calculated correctly.
+    all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]  <- all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)] * all_pred2_no_sum2$T_change
+
+  # Fourth, we can calculate the percentage change on the posterior
+    all_pred2_no_sum2[,paste0("perc", c(1:3200))]  <- (exp(all_pred2_no_sum2[,colnames(all_pred2_no_sum2) %in% c(1:3200)]) - 1)*100
+
+  # Now we can summarise each.
+Here, what we are doing is taking the mean for each column.
+Effectively pooling across all the iterations for each dataset.
+This gives us an estimation of the mean change in variance across all locations/species, but it gives us 3200 point estimates of this mean.
+We can then use this to calculate the 95% CI's.
+    mean_perc <-  apply(all_pred2_no_sum2[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE) 
+    mean(mean_perc)
+    quantile(mean_perc, 0.025)
+    quantile(mean_perc, 0.975)
+    hist(mean_perc)
+
+  # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
+  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 1, mean, na.rm = TRUE))
+  lapply(mean_perc_habitat, mean)
+  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
+  #lapply(mean_perc_habitat, hist)
+
+# Create a table to summarise everything
+tables_future <- all_pred2 %>% group_by(habitat) %>% summarise(mean = mean(per_change, na.rm = TRUE), 
+                                                                l95 = mean(per_change_l95, na.rm = TRUE), 
+                                                                u95 = mean(per_change_u95, na.rm = TRUE))
+
+# Check on how many to decrease
+  decreases <- all_pred2 %>% group_by(match)  %>% summarise(n = if_else(any(per_change < 0), 1, 0))
+
+```
+
 #### *Acute and acclimation* $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa (REMOVE)
@@
 
-#### *Mean-variance relationships to understand patterns in* $lnCVR_{Q_{10}}$
-
-```{r, mc_models}
-#| label: mc_models
-#| echo: false
-#| include: false
-
- # Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
-rerun = FALSE
-if(rerun) {
-
-      r_11_m <- bf(log(r1.1_sd) ~ log(r1.1)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
-      r_12_m <- bf(log(r1.2_sd) ~ log(r1.2)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
-      r_21_m <- bf(log(r2.1_sd) ~ log(r2.1)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
-      r_22_m <- bf(log(r2.2_sd) ~ log(r2.2)*habitat + (1|record_num) + (1|spp) + (1|trait)) + gaussian()
-
-      mv_model_all <- brm(r_11_m + r_12_m + r_21_m + r_22_m + set_rescor(TRUE), 
-                          chains = 4, cores = 4, iter = 4000, warmup = 1000, thin = 1, 
-                          control = list(adapt_delta = 0.98), data = lnRRQ10_data)
-       saveRDS(mv_model_all, file = "./output/models/mv_model_all")
-
-} else {
-        mv_model_all <- readRDS("./output/models/mv_model_all")
-}
-
-# Post processing
-  model_mv1.1 <- posterior_samples(mv_model_all,  pars = "^b_logr11") # Acclimated at 1, measured at 1
-  model_mv1.2 <- posterior_samples(mv_model_all,  pars = "^b_logr12") # Acclimated at 1, measured at 2; Acute
-  model_mv2.2 <- posterior_samples(mv_model_all,  pars = "^b_logr22") # Acclimated at 2, measured at 2
-  model_mv2.1 <- posterior_samples(mv_model_all,  pars = "^b_logr21") # Acclimated at 2, measured at 1; Acute
-
-# Extract slopes
-    slope_extract <- function(x, v){
-        list = list()
-         list[['fresh']] <-  x[,2]  # Slope for freshwater
-        list[['marine']] <-  x[,2] + x[, grepl(":habitatm", colnames(x))] # Slope for marine
-         list[['terrs']] <-  x[,2] + x[, grepl(":habitatt", colnames(x))] # Slope for terrestrial
-         return(list)
-    }
-
-# From each model, lets get the slopes for each habitat
-         r1.1 <-  slope_extract(model_mv1.1)
-         r1.2 <-  slope_extract(model_mv1.2)
-         r2.1 <-  slope_extract(model_mv2.1)
-         r2.2 <-  slope_extract(model_mv2.2)
-
-# Summary
-         table <- data.frame(
-                               mean = do.call("rbind", lapply(r1.1,  mean)),
-                               L = do.call("rbind", lapply(r1.1,  function(x) quantile(x, 0.025))),
-                               U = do.call("rbind", lapply(r1.1,  function(x) quantile(x, 0.975))))
-
-         r_1.2 = data.frame( mean = do.call("rbind", lapply(r1.2,  mean)),
-                               L = do.call("rbind", lapply(r1.2,  function(x) quantile(x, 0.025))),
-                               U = do.call("rbind", lapply(r1.2,  function(x) quantile(x, 0.975))))
-         r_2.1 = data.frame(mean = do.call("rbind", lapply(r2.1,  mean)),
-                               L = do.call("rbind", lapply(r2.1,  function(x) quantile(x, 0.025))),
-                               U = do.call("rbind", lapply(r2.1,  function(x) quantile(x, 0.975))))
-          r_2.2 = data.frame(mean = do.call("rbind", lapply(r2.2,  mean)),
-                               L = do.call("rbind", lapply(r2.2,  function(x) quantile(x, 0.025))),
-                               U = do.call("rbind", lapply(r2.2,  function(x) quantile(x, 0.975))))
-
-          table <- rbind(table, r_1.2,  r_2.1, r_2.2)
-          table$habitat <- rep(c("Freshwater", "Marine", "Terrestrial"), 4)
-          table$type <- c(rep("r1.1",3),
-                          rep("r1.2", 3),
-                          rep("r2.1",3),
-                          rep("r2.2", 3))
-          rownames(table) <- NULL
-
-    table <- table %>% dplyr::select(type, habitat, mean, X2.5., X97.5.) %>% rename("2.5%" = X2.5.,
-                                                                                    "97.5%" = X97.5.,
-                                                                                    "Slope" = mean,
-                                                                                    "Treatment" = type,
-                                                                                    "Habitat" = habitat) %>% 
-      mutate(Type = ifelse(Treatment %in% c("r1.1", "r2.2"), "Acclimation", ifelse(Treatment %in% c("r1.2", "r2.1"), "Acute", " "))) %>% relocate(Type, .before = Treatment) %>% dplyr::arrange(Habitat)
-```
-
-We explored mean-variance relationships for the acute and acclimation
-responses across all traits and habitats. We estimated the scaling
-relationship between log standard deviation in physiological rates
-[log(SD)] and log mean physiological rates [log(mean)], accounting
-for non-independence resulting from effects coming from the same
-species, study and traits (i.e., random effects of species, study and
-trait) as done in our main analyses. We also included an interaction
-between log(mean) and habitat type to better understand how the scaling
-relationship between log(SD) and log(mean) varies across habitats.
-
-Overall, we found that the relationship between log(mean) and log(SD) of
-the acute and acclimation responses was generally linear, suggesting
-that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv). Overall, the
-scaling relationship between log(SD) and log(mean) was sub-linear across
-all habitats (@tbl-slopes), however, ectotherms from terrestrial
-habitats had much shallower slopes than marine and freshwater
-ectotherms, particularly at higher treatment temperatures, indicating
-increased mean physiological rates generally do not result in higher
-between individual variance in physiological rates (@tbl-slopes).
-Interestingly, in marine ectotherms the slope was highest at cooler
-temperatures, wheeras the slope was suppressed when acclimated and/or
-measured at higher temperatures (i.e., r.1. compared to r1.2, r2.1,
-r2.2) (@tbl-slopes). In freshwater ectotherms, there we some differences
-in scaling relationships but they were all fairly comparable no matter
-what acclimation and test temperature (@tbl-slopes).
-
-```{r, fig-mv}
-#| label: fig-mv
-#| fig-cap: "Mean-standard deviation relationships for the acute and acclimation responses across all habitats.
-Relationships are depicted for the low temperature treatment of the study (A) and high temperature treatment (B)."
-    col <- c("#0871B9", "#F3B40D", "#1BB908")
-
-  mv1 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.1), y = log(r1.1_sd),color = habitat)) +
-                  geom_point(aes(color = habitat), size = 2.2) + 
-                  geom_smooth(method = "lm", se = FALSE) + 
-                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
-                  scale_colour_manual(values = col) + 
-                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
-                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
-
-  mv2 <- ggplot2::ggplot(lnRRQ10_data, aes(x = log(r1.2), y = log(r1.2_sd), color = habitat)) +
-                  geom_point(aes(color = habitat), size = 2.2) + 
-                  geom_smooth(method = "lm", se = FALSE) + 
-                  labs(x = "log (Mean)", y = "log (SD)", color = "Habitat") + 
-                  scale_colour_manual(values = col)  +
-                  facet_wrap(~type) + theme_classic() + theme(axis.text = element_text(size=14), axis.title = element_text(size = 16), 
-                  legend.text = element_text(size = 14), legend.title = element_text(size = 16), strip.text = element_text(size = 16))
-
- p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
-  ggsave(p_mv, file = "./output/figures/figS7.png", height = 8, width = 8)
-
-  p_mv <- magick::image_read("./output/figures/figS7.png")
-  p_mv
-```
-
-```{r, tbl-slopes}
-#| label: tbl-slopes
-#| tbl-cap: "Slopes and 95% credible intervals (lower = 2.5% and upper = 97.5%) of log transformed standard deviation (log(SD)) and log transformed mean (log(mean)) for each of the four treatment types (r1.1, r1.2, r2.1, r2.2).
-Note that r1.1 and r2.2 represent measurements of physiological rates of acclimated animals and measured at their respective acclimation temperature.
-In contrast, r1.2 and r2.1 are acute measurements.
-See Figure 1 in main manuscript for full details on treatments."
-
-flextable(table) %>% bold(part = "header") %>% autofit()
-```
-
-#### *Comparing relative variance changes using* $lnCVR_{Q_{10}}$
-
-```{r, lncvrq10}
-#| label: lncvrq10
-#| echo: false
-#| warning: false
-#| error: false
-#| include: false
-#| cache: false
-
-#############
-  ## lnCVRQ10
-#############
-##################################################
-  # Organise the data and prune tree
-#################################################
-  lnCVRQ10_data <- data_long2 %>% filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
-                                    max_temp_c = scale(temp_2, scale = FALSE))
-
-# Check and prune tree
-  tree_lncvr <- tree_checks(data = lnCVRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnCVRQ10_data, tree = tree_lncvr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-  phylo_cor_CVR <- vcv(tree_lncvr, cor = TRUE)
-          A_CVR <- vcv(tree_lncvr, cor = FALSE) # For bayes, need cov matrix
-
-###################################################
-  # Model 2.1: Intercept only model.
-  # Used for heterogeneity analysis
-###################################################
-rerun = FALSE
-if(rerun){
-  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.1
-  saveRDS(model2.1, file = "./output/models/lnCVRQ10_2.1")
-  saveRDS(model2.1_bayes, file = "./output/models/lnCVRQ10_2.1_bayes")
-} else{ 
-        model2.1 <- readRDS("./output/models/lnCVRQ10_2.1")
-  model2.1_bayes <- readRDS("./output/models/lnCVRQ10_2.1_bayes")
-}
-
-# Heterogeneity analysis
-   w_cvr <- with(lnCVRQ10_data, 1/V) # weights
-  sv_cvr <- sum(w_cvr*(dim(lnCVRQ10_data)[1]-1)) / (sum(w_cvr)^2 + sum(w_cvr^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_2.1 <- posterior_samples(model2.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_2.1) <- gsub("__Intercept", "", colnames(posteriors_2.1))
-  colnames(posteriors_2.1) <- gsub("sd_", "", colnames(posteriors_2.1))
-
-    res_cvr <- posteriors_2.1[,"sigma"]
-   stdy_cvr <- posteriors_2.1[,"record_num"]
-  phylo_cvr <- posteriors_2.1[,"species_full"]
-    spp_cvr <- posteriors_2.1[,"spp"]
-  trait_cvr <- posteriors_2.1[,"trait"]
-  total_cvr <- phylo_cvr + spp_cvr + res_cvr + sv_cvr + stdy_cvr + trait_cvr
-
-  # Calculate I2
-     tot_i2_cvr <- (sv_cvr / total_cvr)*100    ; mean(tot_i2_cvr)  ; quantile(tot_i2_cvr, c(0.025, 0.975))
-   phylo_i2_cvr <- (phylo_cvr / total_cvr)*100 ; mean(phylo_i2_cvr); quantile(phylo_i2_cvr, c(0.025, 0.975))
-     spp_i2_cvr <- (spp_cvr / total_cvr)*100   ; mean(spp_i2_cvr)  ; quantile(spp_i2_cvr, c(0.025, 0.975))
-    stdy_i2_cvr <- (stdy_cvr / total_cvr)*100  ; mean(stdy_i2_cvr) ; quantile(stdy_i2_cvr, c(0.025, 0.975))
-   trait_i2_cvr <- (trait_cvr / total_cvr)*100 ; mean(trait_i2_cvr); quantile(trait_i2_cvr, c(0.025, 0.975))
-     res_i2_cvr <- (res_cvr / total_cvr)*100   ; mean(res_i2_cvr)  ; quantile(res_i2_cvr, c(0.025, 0.975))
-
-  # Table
-     i2_lncvr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2_cvr),mean(spp_i2_cvr), mean(stdy_i2_cvr), mean(trait_i2_cvr)),
-                           lci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[1], quantile(spp_i2_cvr, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[1], quantile(trait_i2_cvr, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2_cvr, c(0.025, 0.975))[2], quantile(spp_i2_cvr, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2_cvr, c(0.025, 0.975))[2], quantile(trait_i2_cvr, c(0.025, 0.975))[2]))
-
-###################################################
-  # Model 2.2: Model controlling for acclimation time, 
-  # type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model1.2
-  saveRDS(model2.2, file = "./output/models/lnCVRQ10_2.2")
-  saveRDS(model2.2_bayes, file = "./output/models/lnCVRQ10_2.2_bayes")
-
-  } else{
-        model2.2 <- readRDS("./output/models/lnCVRQ10_2.2")
-  model2.2_bayes <- readRDS("./output/models/lnCVRQ10_2.2_bayes")
-}
-
-######################################################
-  # Bayesian Contrasts
-######################################################
-
-  posteriors_2.2 <- posterior_samples(model2.2_bayes, pars = "^b")
-  f_acute_cvr  <- posteriors_2.2[,"b_Intercept"]; pmcmc(f_acute_cvr)
-  f_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_typeacclim"]
-  m_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"]
-  m_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatm"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatm"]
-  t_acute_cvr  <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"]
-  t_acclim_cvr <- posteriors_2.2[,"b_Intercept"] + posteriors_2.2[,"b_habitatt"] + posteriors_2.2[,"b_typeacclim"] + posteriors_2.2[,"b_typeacclim:habitatt"]
-
-# We'll take the marginalised mean for each type as there is no difference between acclimation and acute really except for in freshwater, but this effect size is so tiny.
-It's a 10% reduction at high temps and acclim is only a 2% reduction in variance at high temps.
-  # First get sample sizes
-    N <- lnCVRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
-
-  # Calculated weighted mean by sample size. 
-    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
-    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
-    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)
-
-  # Lets now convert these to a %
-    f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
-    m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
-    t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction
-
-###################################################
-  # Model 2.3: Model controlling for acclimation time, 
-  # type and trait category assuming type can vary by habitat
-###################################################
-  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
-    lnCVRQ10_data <- lnCVRQ10_data %>% 
-                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
-                                                "tissue/organism",
-                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
-                                                "biochemical", trait_category)))
- # We can also run subsets for each habitat
-   tree_m_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "m" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
-   tree_f_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "f" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
-   tree_t_cvr <- tree_checks(lnCVRQ10_data %>% filter(habitat == "t" & trait_broad != "other"), tree = tree_lncvr, dataCol = "species_full", type = "prune")
-
- # cor matrices
-   m_phylo_cvr <- vcv(tree_m_cvr, corr = TRUE)
-   f_phylo_cvr <- vcv(tree_f_cvr, corr = TRUE)
-   t_phylo_cvr <- vcv(tree_t_cvr, corr = TRUE)
-
-if(rerun){
-
-  # Full Bayesian model   
-   model2.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
-                                           (1 | record_num) + 
-                                           (1 | gr(species_full, cov = A)) + 
-                                           (1 + max_temp_c | spp) +(1|trait) + 
-                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
-                                         data2 = list(A=A), family = gaussian(), 
-                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnCVRQ10_data, trait_broad != "other"))
-    saveRDS(model2.3_btrait_bayes, "./output/models/model2.3_btrait_bayes")
-
-  # Metafor models for creating plots. Subset by habitat to make this easier
-      # Marine
-         model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = m_phylo_cvr), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = filter(lnCVRQ10_data, habitat == "m" & trait_broad != "other"))
-         saveRDS(model2.3_m_broad, "output/models/model2.3_m_broad")
-
-      # Freshwater
-         model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = f_phylo_cvr), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"),  phi = 0,
-                              data = filter(lnCVRQ10_data, habitat == "f" & trait_broad != "other"))
-          saveRDS(model2.3_f_broad, "output/models/model2.3_f_broad")
-
-      # Terrestrial
-         model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = t_phylo_cvr), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = filter(lnCVRQ10_data, habitat == "t" & trait_broad != "other"))
-         saveRDS(model2.3_t_broad, "output/models/model2.3_t_broad")
-
-  } else{
-    model2.3_btrait_bayes <- readRDS("./output/models/model2.3_btrait_bayes")
-    model2.3_m_broad <- readRDS("output/models/model2.3_m_broad")
-    model2.3_f_broad <- readRDS("output/models/model2.3_f_broad")
-    model2.3_t_broad <- readRDS("output/models/model2.3_t_broad")
-}
-
-###########################################################
-  # Processing Bayesian Posteriors
-###########################################################
-      # Create new data for predictions
-       trait_b_data <- data.frame(  type = c("acclim", "acute"),
-                              max_temp_c = 0,
-                             c_accl_time = 0,
-                                       V = 0,
-                                 habitat = rep(c("t", "m", "f"), each = 4),
-                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
-
-       # Predict from model. Note this is the summary.
-         pred_lncvr_traitb <- fitted(model2.3_btrait_bayes, 
-                                     newdata = trait_b_data, re_formula = NA,
-                                     summary = TRUE, 
-                                     robust = FALSE)
-         pred_lncvr_traitb <- cbind(trait_b_data, pred_lncvr_traitb)
-
-       # Predict to get the posterior.
-Note that we have the full posterior distribution here for each of the 12 categories in the new data.
-Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lncvr_traitb_post <- fitted(model2.3_btrait_bayes, 
-                                     newdata = trait_b_data, re_formula = NA,
-                                     summary = FALSE, 
-                                     robust = FALSE)
-        contrast_lncvr_trait_post <-  pred_lncvr_traitb_post[,c(1,3,5,7,9,11)] - pred_lncvr_traitb_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
-
-        # Contrast statistics
-            contrast_lncvr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
-                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
-                                                    diff = sapply(data.frame(contrast_lncvr_trait_post), mean),
-                                                     l95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.025)),
-                                                     u95 = sapply(data.frame(contrast_lncvr_trait_post), function(x) quantile(x, 0.975)),
-                                                       p = sapply(data.frame(contrast_lncvr_trait_post), function(x) p_value(pmcmc(x))))
-
-   # Contrasts for pooled acute and acclimation across trait categories
-
-            contrast_lncvr_trait_cat_stats <- rbind(get_whole_bio(pred_lncvr_traitb_post, habitat = "t", trait_b_data),
-                                                        get_whole_bio(pred_lncvr_traitb_post, habitat = "m", trait_b_data),
-                                                        get_whole_bio(pred_lncvr_traitb_post, habitat = "f", trait_b_data))
-
-###################################################
-  # Model 2.4: Model controlling for acclimation time, 
-  # type and life history stage assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model 
-  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data)
-  # Save model
-  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
-
-   model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
-                                 (~1 | record_num) + 
-                                 (1 | gr(species_full, cov = A_CVR)) + 
-                                 (1 + max_temp_c| spp) + 
-                                 (1|trait) +
-                                 (1|obs), 
-                               data2 = list(A_CVR=A_CVR), family = gaussian(), 
-                               prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-                               control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
-
-  # Save model
-  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
-
-  } else{
-        model2.4 <- readRDS("./output/models/lnCVRQ10_2.4")
-  model2.4_bayes <- readRDS("./output/models/lnCVRQ10_2.4_bayes")
-}
-
-###########################################################
-  # Processing Bayesian Posteriors
-###########################################################
-      # Create new data for predictions
-       lh_b_data <- data.frame( c_accl_time = 0, 
-                          max_temp_c = 0, 
-                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
-                             habitat = rep(c("m", "f", "t"), each = 4), 
-                           life.hist = rep(c("j", "a"), each = 2))
-
-            # I have no idea why the fitted function is not working on this model. We're doing this the old fashioned way
-            X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = lh_b_data)
-
-            # Extract posteriors
-              post_lh <- posterior_samples(model2.4_bayes, pars = "^b")
-
-        # Now we can do all the calculations in one shot.# Predict to get the posterior.
-Note that we have the full posterior distribution here for each of the 12 categories in the new data.
-Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lh <- apply(t(post_lh),2 , function(x) as.matrix(X)%*%x)
-
-        contrast_lncvr_lh_post <-  pred_lh[c(1,3,5,7,9,11),] - pred_lh[c(2,4,6,8,10,12),] # Acclimation - acute.
-
-        # Contrast statistics
-            contrast_lncvr_lh_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
-                                                     stage = rep(c("j", "a"), each = 1),
-                                                    diff = apply(data.frame(contrast_lncvr_lh_post), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lncvr_lh_post), 1, function(x) p_value(pmcmc(x))))
-```
-
-Overall, analyses with $lnCVR_{Q_{10}}$ showed similar patterns to those with $lnVR_{Q_{10}}$, except that, because of rates being taken into consideration and there is a strong mean-variance relationship, the patterns were generally opposite in direction.
-Either way, the relative differences are quite similar.
-Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with
-higher temperatures across all habitat types, with terrestrial
-ectotherms having the largest decrease in relative variance (@fig-s1).
-There were also no major differences in the relative differences among broad trait categories (@fig-cvrbtrait) or life-history stages (@fig-lncvrlh).
-
-```{r, fig-s1}
-#| label: fig-s1
-#| fig-align: center
-#| fig-cap: "Estimated mean acute and acclimation $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial habitats.
-The percentage change in variance is also back calculated.
-Note that these are raw variances and do not account for changes in mean physiological rates.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\\Beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying .
-$\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
-In both cases, their 95% CI's are indicated within square brackets.
-$p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
-For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles."
-
-#################
-# Fig S CVR
-##################
-  # Clear from the model that there really is no difference between the change in variance for acute or acclimation CVR.
-But, there is a clear reduction in between individual variance for terrestrial species.
-As temperature get hotter then the variance in physiological rates decreases.
-This is not true of aquatic systems.
-  col <- c("#0871B9", "#F3B40D", "#1BB908")
-  k_cvr <- manual_extract(model2.2, mod = "habitat", group = "record_num", exclude = NULL)
-
-  x1 = 1.4
-  x2 = 2.4
-  x3 = 3.4
-
-  p3b <- orchard_plot(model2.2, xlab = TeX("$lnCVR_{Q_{10}}$"), by = "type", at = list(type = c("acute", "acclim")), mod = "habitat", group  = "record_num", weights = "prop", angle = 45, trunk.size = 1.8, branch.size = 2.8,  k.pos = "none")  +
-              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-
-  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) +
-
-  annotate("text", x = x1, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(f_cvr_mean), 3), "[", round(quantile(f_cvr_mean, 0.025), 2)," to ", round(quantile(f_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
-         annotate("text", x = x1, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = x1-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(f_cvr_mean), digit = 2))), hjust = 0, size = 8) + 
-  annotate("text", x = x1-0.20, y = 1, label =paste0(round(mean(exp(f_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = x2, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(m_cvr_mean), 3), "[", round(quantile(m_cvr_mean, 0.025), 2)," to ", round(quantile(m_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
-     annotate("text", x = x2, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = x2-0.20, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(m_cvr_mean), digit = 2))), hjust = 0, size = 8) +
-  annotate("text", x = x2-0.20, y = 1, label =paste0(round(mean(exp(m_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = x3+0.10, y = -1.5, label =TeX(paste0("$\\mu = $", round(mean(t_cvr_mean), 3), "[", round(quantile(t_cvr_mean, 0.025), 2)," to ", round(quantile(t_cvr_mean, 0.975),2), "] ")), hjust = 0, size = 8) +
-  annotate("text", x = x3+0.10, y = 0.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
-  annotate("text", x = x3-0.10, y = 1, label =paste0(round(mean(exp(t_cvr_mean)-1)*100, 2), "%"), hjust = 0, size = 8) + 
-  annotate("text", x = x3-0.10, y = -1.5, label = TeX(paste0("$p_{MCMC} = $", round(pmcmc(t_cvr_mean), digit = 3))), hjust = 0, size = 8) +
-
-    labs(shape = "Type") +
-    annotate("text", label= paste0("k = ", k_cvr$k, " (", k_cvr$sdy, ")"), x = c(0.8, 1.8, 2.8), y = 1.3, size = 5) + ylim (-1.5, 1.5)
-
-  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 24),
-                                       axis.text.y = element_blank(),
-                                       legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")
-
-########
-
-##################
-  # Figure S1
-##################
-
-  ggsave(p3, filename = "./output/figures/figS8.pdf", width = 11.5, height = 8)
-
-  figs1 <- image_read("./output/figures/figS8.pdf")
-  figs1
-```
-
-```{r, fig-cvrbtrait}
-#| label: fig-btrait
-#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for tissue/whole-orgamism traits and biochemical traits across marine (A), freshwater (B) and terrestrial (C) habitats.
-Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
-$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
-$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
-#| echo: false
-#| warning: false
-
-add_theme  <- function(){theme(axis.title  = element_text(size = 30),
-                               axis.text.y = element_text(size = 30),
-                               axis.text.x = element_text(size = 30),
-                              legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 36))}
-
-branch.size = 2.8
-trunk.size = 1.8
-
-n_lncvr_btrait  <- lnCVRQ10_data  %>% filter(trait_broad != "other") %>% 
-              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
-
-       col <- c("#0871B9", "#F3B40D", "#1BB908")
-     x.pos <- c(0.7, 1.30, 1.70, 2.30)
-size_annot <- 5.5
-
-############
-# CVR
-############
-m_cv <- n_lncvr_btrait %>% filter(habitat == "m")
-f_cv <- n_lncvr_btrait %>% filter(habitat == "f")
-t_cv <- n_lncvr_btrait %>% filter(habitat == "t")
-
-t_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-m_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-f_trait_b_cvr <- contrast_lncvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-
-p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
-
-############
-# Full fig
-############
-figbtrait_vr <-(p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait_vr, filename = "./output/figures/figStrait_cvr.png", width = 28, height = 8, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/figStrait_cvr.png")
-figbtrait
-```
-
-```{r, fig-lncvrlh}
-#| label: fig-lnvrlh
-#| echo: false
-#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for marine (A), freshwater (B) and terrestrial (C) ectotherms.
-Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
-$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
-$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
-
-add_theme  <- function(){theme(axis.title  = element_text(size = 30),
-                               axis.text.y = element_text(size = 30),
-                               axis.text.x = element_text(size = 30),
-                              legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 36))}
-
-branch.size = 2.8
-trunk.size = 1.8
-
-n_lncvr_lh <- lnCVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
-
-x.pos = c(0.7, 1.30, 1.70, 2.30)
-size_annot <- 5.5
-
-###############
-# ln CVR
-###############
-m_cv <- n_lncvr_lh %>% filter(habitat == "m")
-f_cv <- n_lncvr_lh %>% filter(habitat == "f")
-t_cv <- n_lncvr_lh %>% filter(habitat == "t")
-
-  t_trait_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-m_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-f_trait_b_cvr <- contrast_lncvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-
-p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
-
-figvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figcvr_lh, filename = "./output/figures/figSlh.pdf", width = 28, height = 10, device = "pdf")
-
-figcvr_lh <- magick::image_read("./output/figures/figSlh.pdf")
-figcvr_lh
-
-```
-
-```{r wildlncvr}
-#| label: wildlncvr
-#| cache: true
-#| include: false
-#| echo: false
-#| warning: false
-#| 
-#######################################
-  ## lnCVRQ10 from Wild Populations ##
-#######################################
-##################################################
-  # Organise the data and prune tree
-##################################################
-
-# Bring in  historial climate data
-  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
-
-# Create a match column.
-  climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% 
-                          dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
-
-# Populations and species?
-  pop_spp_w <- climate2[complete.cases(climate2),]
-
-# Subset the data
-  lnCVRQ10_data_wild <- data_long2 %>% 
-    filter(grepl("lnCVR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
-                        mutate(spp = species_full, 
-                                     c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), 
-                                     match = interaction(spp, lat, long),
-                                     max_temp_c = scale(temp_2, scale = FALSE))
-
-# Now, join climate data to full data. This will give us all the climate variability data for each site across time
-  lnCVRQ10_data_wild <- left_join(lnCVRQ10_data_wild, climate2, by = "match")
-
-# Look at the environment details across different habitats. 
-  lnCVRQ10_data_wild  %>% group_by(habitat) %>% summarise(mean(sd))
-
-# Check and prune tree
-  tree_lncvr_wild <- tree_checks(data = lnCVRQ10_data_wild, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-  tree_checks(data = lnCVRQ10_data_wild, tree = tree_lncvr_wild, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-  phylo_cor_wild_cvr <- vcv(tree_lncvr_wild, cor = TRUE)
-          A_wild_cvr <- vcv(tree_lncvr_wild, cor = FALSE) # For bayes, need cov matrix
-
-# Scale environment variables
-    lnCVRQ10_data_wild <- lnCVRQ10_data_wild %>% mutate(     cv_c = scale(cv),
-                                                        acf_all_c = scale(acf_all),
-                                                        acf_lag1_c = scale(acf_lag1))
-
-####################################################
-  # Model 4.3: Model environmental variability by acute/acclim
-####################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild)
-
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
-
-  # Save model4.3
-  saveRDS(model4.3, file = "./output/models/lnCVRQ10_4.3")
-  saveRDS(model4.3_bayes, file = "./output/models/lnCVRQ10_4.3_bayes")
-
-  } else{
-        model4.3 <- readRDS("./output/models/lnCVRQ10_4.3")
-  model4.3_bayes <- readRDS("./output/models/lnCVRQ10_4.3_bayes")
-}
-
-############################################################################################
-# Model 4.9: Acclimatization lnCVRQ10 only. Test if environmental variance explains 
-# differently in each habitat
-############################################################################################          
-  lnCVRQ10_data_wild_acclim <- lnCVRQ10_data_wild %>%  filter(type == "acclim")
-
-  # Create the phylo correlation matrix
-
-  # Check and prune tree
-tree_lncvr_wild_acclim <- tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnCVRQ10_data_wild_acclim, tree = tree_lncvr_wild_acclim, dataCol = "species_full", type = "check")
-
-phylo_cor_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = TRUE)
-        A_wild_acclim <- vcv(tree_lncvr_wild_acclim, cor = FALSE) # For bayes, need cov matrix
-
-if(rerun){
-  # More realistic model with 
-  model4.9  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim)
-
-   model4.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 | spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild_acclim)
-
-  # Save model3.8
-  saveRDS(model4.9, file = "./output/models/lnCVRQ10_4.9")
-  saveRDS(model4.9_bayes, file = "./output/models/lnCVRQ10_4.9_bayes")
-
-  } else{
-        model4.9 <- readRDS("./output/models/lnCVRQ10_4.9")
-  model4.9_bayes <- readRDS("./output/models/lnCVRQ10_4.9_bayes")
-}
-
-#################################################
-### Bayesian Slopes from Model 4.9
-#################################################
- posteriors4.9 <- posterior_samples(model4.9_bayes, "^b")
-
-    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
-    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
-    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
-
-##################################################
-    # Model 4.8, 4.9 and 4.10 - Habitat subset
-    # Used for making plots
-##################################################
-    # Subset data to habitat
-    lnCVRQ10_data_wild_acclim_t <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "t")
-    lnCVRQ10_data_wild_acclim_f <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "f")
-    lnCVRQ10_data_wild_acclim_m <- lnCVRQ10_data_wild_acclim %>% filter(habitat == "m")
-
-if(rerun){
-    # Terrestrial Models
-    model4.9_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim_t)
-    saveRDS(model4.9_t, "./output/models/model4.9_t")
-
-    # Freshwater Models
-
-    model4.9_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim_f)
-
-    saveRDS(model4.9_f, "./output/models/model4.9_f")
-
-    # Marine Models
-
-    model4.9_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c, V = V,
-                                       random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
-                              test = "t", data = lnCVRQ10_data_wild_acclim_m)
-    saveRDS(model4.9_m, "./output/models/model4.9_m")
-
-  } else {
-     model4.9_t <- readRDS("./output/models/model4.9_t")
-     model4.9_f <- readRDS("./output/models/model4.9_f")
-     model4.9_m <- readRDS("./output/models/model4.9_m")
-}
-
-```
-
 #### *Plots of* $I^2$ for multilevel models
@@
     slope_f_3.8 <- posteriors3.8[,"b_acf_lag1_c"] 
-                    pmcmc(slope_f_3.8); quantile(slope_f_3.8, c(0.025, 0.975))
     slope_m_3.8 <- posteriors3.8[,"b_acf_lag1_c"] + posteriors3.8[,"b_acf_lag1_c:habitatm"] 
-                    pmcmc(slope_m_3.8); quantile(slope_m_3.8, c(0.025, 0.975))
     slope_t_3.8 <- posteriors3.8[,"b_acf_lag1_c"] + posteriors3.8[,"b_acf_lag1_c:habitatt"]
-                    pmcmc(slope_t_3.8); quantile(slope_t_3.8, c(0.025, 0.975))
 
@@
 
-    slope_f_4.8 <- posteriors4.8[,"b_acf_lag1_c"]; mean(slope_f_4.8); pmcmc(slope_f_4.8); quantile(slope_f_4.8, c(0.025, 0.975))
-    slope_m_4.8 <- posteriors4.8[,"b_acf_lag1_c"] + posteriors4.8[,"b_acf_lag1_c:habitatm"]; mean(slope_m_4.8); pmcmc(slope_m_4.8); quantile(slope_m_4.8, c(0.025, 0.975))
-    slope_t_4.8 <- posteriors4.8[,"b_acf_lag1_c"] + posteriors4.8[,"b_acf_lag1_c:habitatt"]; mean(slope_t_4.8); pmcmc(slope_t_4.8); quantile(slope_t_4.8, c(0.025, 0.975))
+    slope_f_4.8 <- posteriors4.8[,"b_acf_lag1_c"]; mean(slope_f_4.8)
+    slope_m_4.8 <- posteriors4.8[,"b_acf_lag1_c"] + posteriors4.8[,"b_acf_lag1_c:habitatm"]
+    slope_t_4.8 <- posteriors4.8[,"b_acf_lag1_c"] + posteriors4.8[,"b_acf_lag1_c:habitatt"]
 
 #################################################
-### Same model as above, but seperate for habitat 
+### Same model as above, but separate for habitat 
 ### For plotting, 4.8

### 2024-07-13 ms.qmd
Added in detailed trait anlaysis for lnVR given we are focusing more on this for easier interpretation

@@
 ---
-title: "Physiological plasticity and variance in physiological rates vary across ectotherm populations"
+title: "Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change"
 bibliography: ./bib/refs.bib
@@
 
-## Detailed trait category analyses for lnRR
-
+##########################################
+## lnRR - Detailed trait category analyses 
+##########################################
   # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
@@
 
-## Detailed trait category analyses for lnCVR
+##########################################
+# lnCVR - Detailed trait analysis
+##########################################
 
@@
   model2.3_bayes <- readRDS("./output/models/lnCVRQ10_2.3_bayes")
+  }
+
+##########################################
+## lnVR - Detailed trait category analyses
+##########################################
+  # Filter out antioxidant and NAs. For terrestrial, need to filter out endurance and max_MR because only 3 effect sizes
+  lnVRQ10_data_m <- lnVRQ10_data %>% filter(habitat == "m" & !trait_category =="antiox") %>% filter(!is.na(c_accl_time))
+  lnVRQ10_data_f <- lnVRQ10_data %>% filter(habitat == "f" & !is.na(c_accl_time))
+  lnVRQ10_data_t <- lnVRQ10_data %>% filter(habitat == "t" & !is.na(c_accl_time)) %>% filter(!trait_category %in% c("endurance", "max_MR", "other"))
+
+  # Prune tree
+   tree_m_VR <- tree_checks(lnVRQ10_data_m, tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_f_VR <- tree_checks(lnVRQ10_data_f, tree = tree_lnVR, dataCol = "species_full", type = "prune")
+   tree_t_VR <- tree_checks(lnVRQ10_data_t, tree = tree_lnVR, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo_VR <- vcv(tree_m_VR, corr = TRUE)
+   f_phylo_VR <- vcv(tree_f_VR, corr = TRUE)
+   t_phylo_VR <- vcv(tree_t_VR, corr = TRUE)
+
+if(rerun){
+#########################
+  # Detailed Trait Categories
+  # Models for the supplement
+#########################
+  # More realistic model 
+  model3.3 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, 
+                                   V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_VR), dfs = "contain", 
+                              test = "t", data = lnVRQ10_data)
+
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category + 
+                                 (~1 | record_num) + 
+                                 (1 | gr(species_full, cov = A_VR)) + 
+                                 (1 + max_temp_c| spp) + 
+                                 (1|trait), 
+                               data2 = list(A_VR=A_VR), family = gaussian(), 
+                               prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                               control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
+
+  # Save models
+  saveRDS(model3.3, file = "./output/models/lnVRQ10_3.3")
+  saveRDS(model3.3_bayes, file = "./output/models/lnVRQ10_3.3_bayes")
+
+  # Models for plotting
+
+  model3.3f <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, 
+                                  V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = f_phylo_vr), dfs = "contain", 
+                              test = "t", struct = c("GEN", "HCS"), phi = 0, data = lnVRQ10_data_f)
+
+  saveRDS(model3.3f, file = "./output/models/lnVRQ10_model3.3f")
+
+  model3.3m <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category + type:trait_category, 
+                                   V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category| obs),
+                              R = list(species_full = m_phylo_vr), dfs = "contain", 
+                              test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnVRQ10_data_m)
+  saveRDS(model3.3m, file = "./output/models/lnVRQ10_model3.3m")
+
+  # Note that we need to drop interaction for terrestrial as it's not able to estimate. 
+  model3.3t <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_category, 
+                                   V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c | spp,
+                                            ~1 | trait,
+                                            ~1 + trait_category | obs),
+                              R = list(species_full = t_phylo_vr), dfs = "contain", 
+                              test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnVRQ10_data_t)
+  saveRDS(model3.3t, file = "./output/models/lnVRQ10_model3.3t")
+
+  } else{
+#########################
+  # Detailed Trait Categories
+  # Models for the supplement
+#########################
+        model3.3 <- readRDS("./output/models/lnCVRQ10_3.3")
+        model3.3f <- readRDS("./output/models/lnCVRQ10_model3.3f")
+        model3.3m <- readRDS("./output/models/lnCVRQ10_model3.3m")
+        model3.3t <- readRDS("./output/models/lnCVRQ10_model3.3t")
+  model3.3_bayes <- readRDS("./output/models/lnCVRQ10_3.3_bayes")
 }

### 2024-07-13 ms.qmd
Moved simulations to main MS. Trimed supplement.

@@
   options(digits = 2, scipen = 3)
+
+my_theme <- function(){
+  theme(
+           axis.title.y = element_text(size = 20), 
+           axis.title.x = element_text(size = 20),
+           axis.text.x = element_text(size = 18),
+            axis.text.y = element_text(size = 18),
+            plot.title = element_text(size = 28))
+}
 ```
@@
 ```
+
+### *Performance Curve Simulation*
+To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance across temperature we conducted a simple simulation.
+To simulate performance curves, we used a asymmetrical Gaussian function (@eq-sim):
+
+$$
+P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
+$$ {#eq-sim}
+
+where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see *Supplementary Materials* showing curves).
+While we could have used other performance curve functions (e.g., Arrhenius), our intentions were not to model the exact curves (which are not know) but rather identify what might vary across the major habitat types that could contribute to the different patterns of variance change at higher temperatures we observed across habitats.
+
+We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$, $\alpha$) in all possible combinations from 0.01 to 2.
+We then took the mean and standard deviation of the performance at two temperatures 10 degrees apart (18 and 28 degrees) to calculate the log variance ratio $lnVR_{Q_{10}}$.
+Our simulations assume that the value of variance does not change depending on the temperatures choosen, but given our analysis restricts the data to temperatures within the normal thermal range of each species we do not envisage this being problematic.
 
@@
 Variance in physiological rates ($lnVR_{Q_{10}}$) showed an
-increase with increasing temperature across all habitat types.
-However, physiological rate variance increase significantly more in freshwater (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c)`, 95% CI: `r quantile(f_t_c, 0.025)` to `r quantile(f_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c))`) and marine ectotherms (marine vs terrestrial: $\beta$ = `r mean(m_t_c)`, 95% CI: `r quantile(m_t_c, 0.025)` to `r quantile(m_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c))`) compared to the limited increase in terrestrial ecotherms (@fig-2).
-The total
-proportion of heterogeneity in $lnVR_{Q_{10}}$ was lower compared to
-$lnRR_{Q_{10}}$ ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI:
-`r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`),
-with most variation being driven by between-study and trait differences
-("Model 1"; see *Supplementary Materials* @fig-s3). There were no differences between
-$lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$. Reductions
-in variance were driven by slower increases in the variance in
-physiological rates as mean physiological rates increased with scaling
-relationships between log standard deviation and log mean all being
-smaller than 1 and varying across habitats (see *Supplementary
+increase with increasing temperature across all habitat types with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI:
+`r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`; "Model 1"; see *Supplementary Materials* @fig-s3).
+However, physiological rate variance increased significantly more in freshwater (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c)`, 95% CI: `r quantile(f_t_c, 0.025)` to `r quantile(f_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c))`) and marine ectotherms (marine vs terrestrial: $\beta$ = `r mean(m_t_c)`, 95% CI: `r quantile(m_t_c, 0.025)` to `r quantile(m_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c))`) compared to the limited increase in terrestrial ecotherms (@fig-2).
+There were no differences between
+$lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$. Differences
+in variance between habitats were driven by different scaling relationships between mean and variance across habitats (see *Supplementary
 Materials*; @tbl-slopes & @fig-mv). There was a `r mean(t_VR_mean_ef)`%
@@
 `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(t_VR_mean)`) reduction in relative physiological rate variance
+`r pmcmc(t_VR_mean)`) increase in physiological rate variance
 for terrestrial ectotherms and a `r mean(m_VR_mean_ef)`% (95% CI:
@@
 `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(m_VR_mean)`) reduction in relative variation for marine
+`r pmcmc(m_VR_mean)`) increase in variation for marine
 ectotherms when temperatures increased by 10$^\circ$C. In contrast,
-freshwater ectotherms exhibited a smaller reduction in relative
-physiological rate variance at high temperatures
-(`r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]`
+freshwater ectotherms exhibited a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]`
 to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(f_VR_mean)`) (results from "Model 2"). The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
+`r pmcmc(f_VR_mean)` increase in variance at high temperatures
+(@fig-2). (results from "Model 2"). The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
+
+$lnVR_{Q_{10}}$ values from our simulations matched our empirical results quite nicely in key areas of parameter space (@fig-sim2).
+Interestingly, for a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
+In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2])
+
+```{r, fig-sim2}
+#| label: fig-sim2
+#| fig-align: center
+#| fig-cap: "Expected $lnVR_{Q_{10}}$ when varying $\\sigma_{_b_{\\delta}}$ = {0.01, 2} and  $\\sigma_{_b_{\\sigma}}$ = {0.01, 2} while fixing $\\sigma_{_b_{\\alpha}}$ = 0.01.
+In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$, $\\sigma_{_b_{\\sigma}}$.
+The parameter space that match observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms.
+Dashed lines indicate the relative differences between the three habitat types when holding one parameter constant."
+
+sim_results <- readRDS("./output/sim_results")
+bins_vr = 20
+
+lnvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
+  geom_contour_filled(bins = bins_vr) +
+  scale_color_viridis() +
+  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
+       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
+       fill = TeX("$lnVR_{Q_{10}}$")) + theme_classic() + my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
+
+#ggsave(lnvr_sim_delta_sigma1, width = 9.5, height = 8, filename = "./output/figures/figsim_new2.pdf")
+
+p_sim2 <- image_read("./output/figures/figsim_new.pdf")
+p_sim2
+```
 
@@
 similar change in variance in physiological rates
-([@fig-btrait]D-F; see *Supplementary Materials*, @fig-cvrtrait) for more detailed trait
+([@fig-btrait]D-F; see *Supplementary Materials*, @fig-vrtrait) for more detailed trait
 analysis), except for biochemical processes in ectotherms occupying
@@
 reduction in variation in physiological rates at high temperatures (see
-*Supplemental Material*, @fig-cvrtrait) ("Model 3"). Each life-history stage
+*Supplemental Material*, @fig-vrtrait) ("Model 3"). Each life-history stage
 exhibited the same pattern of relative variance change in each of the
@@
 $$
-P_{z} = 2\epsilon^{-\frac{(z-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{z-\delta}{\sigma}\right)
+P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
 $$ {#eq-sim}
 
-where $z$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the performance function or rate variation.
-While we could have used other performance curve functions (e.g., Arrhenius), our intentions were not to model the exact curves (which are not know) but rather identify what might vary across the major habitat types that could contribute to the different patterns of variance change at higher temperatures we observed across habitats.
-
-We first explored four hypothetical examples to identify key parameters from this function that appear to impact $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ the most (@fig-sim).
-To achieve this, we simulated 40 individuals with varying amounts of between individual variation in performance breadth, optima and rate variation.
+where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the performance function or rate variation.
+To understand how each parameter impacts the shape of performance curces, we simulated 40 individuals with varying amounts of between individual variation in performance breadth, optima and rate variation.
 We then calculated the relative variance in performance across the temperature gradient as the variance in performance at each temperature divided by the maximum performance at that temperature.
-This simple analysis identified thermal optima and breath as being the major factors likely leading to the observed patterns in $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ we identify in our meta-analysis.
-
-We then conducted a larger simulation that expanded the parameter space by manipulating the level of between individual variation in both the thermal optima and performance breadth while holding constant rate variation because optima and breadth appeared to be most important (@fig-sim).
-We simulated *n* = 1000 individual performance curves and took the mean and standard deviation of the performance at two temperatures 10 degrees apart (18 and 28 degrees) to calculate the log coefficient of variation (CV) and log variance ratio in performance.
-Our simulations assume that the value of variance does not change depending on the temperatures choose, but given our analysis restricts the data to temperatures within the normal thermal range of each species, standardising a temperature window in this way is likely comparable.
-
-Overall, our simulations recovered plausible parameter space for levels of between individual variation in thermal optima and breath that matched some of our empirical results (@fig-sim2).
-While $lnCVR_{Q_{10}}$ ([@fig-sim2]A) values were overestimated compared to our empirical results, $lnVR_{Q_{10}}$ nicely matched ([@fig-sim2]B).
-Overestimation of $lnCVR_{Q_{10}}$ is likely the result of the rate parameter being too steep in our model (i.e., $Q_{10}$ being too high) compared to what is typical in nature resulting in rates at higher temperatures to be larger than what is expected.
-This would inflate the coefficient of variation because the variance is standardised by the rates at the respective temperatures.
-Using alternative performance functions may correct this deviation, but this question is out of scope here and would require a much larger simulation.
-Regardless, $lnCVR_{Q_{10}}$ largely showed similar patterns to $lnVR_{Q_{10}}$.
-
-Importantly, our $lnVR_{Q_{10}}$ values matched our empirical results quite nicely.
-Interestingly, for a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]B).
-In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2]B).
+This simple analysis identified thermal optima and breath as being the major factors likely leading to the observed patterns in $lnVR_{Q_{10}}$ we identify in our meta-analysis.
 
@@
 In all simulations, $\\delta$ = 35, $\\sigma$ = 9 and $\\alpha$ = -15, while between individual variation for $\\sigma_{_b_{\\delta}}$ = 1,  $\\sigma_{_b_{\\sigma}}$ = 0.5 and $\\sigma_{_b_{\\alpha}}$ = 0.5."
-
-my_theme <- function(){
-  theme(
-           axis.title.y = element_text(size = 20), 
-           axis.title.x = element_text(size = 20),
-           axis.text.x = element_text(size = 18),
-            axis.text.y = element_text(size = 18),
-            plot.title = element_text(size = 28))
-}
 
@@
 ```
-
-```{r, fig-sim2}
-#| label: fig-sim2
-#| fig-align: center
-#| fig-cap: "Expected $lnCVR_{Q_{10}}$ (A) and $lnVR_{Q_{10}}$ (B) when varying $\\sigma_{_b_{\\delta}}$ = {0.01, 2} and  $\\sigma_{_b_{\\sigma}}$ = {0.01, 2} while fixing $\\sigma_{_b_{\\alpha}}$ = 0.01.
-In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$, $\\sigma_{_b_{\\sigma}}$ and $\\sigma_{_b_{\\alpha}}$.
-(B) The parameter space that match observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms.
-Dashed lines indicate the relative differences between the three habitat types when holding one parameter constant."
-
-sim_results <- readRDS("./output/sim_results")
-bins_cvr = 20
-bins_vr = 20
-
-lncvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnCVR)) +
-  geom_contour_filled(bins = bins_cvr) +
-  scale_color_viridis(direction = -1) +
-  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
-       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
-       fill = TeX("$lnCVR_{Q_{10}}$"), title = TeX("Variation in Rates ($\\sigma_{\\alpha}$ = 0.01)")) + theme_classic()+ my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
-
-lnvr_sim_delta_sigma1 <- ggplot(sim_results, aes(x = delta, y = sigma, z = lnVR)) +
-  geom_contour_filled(bins = bins_vr) +
-  scale_color_viridis() +
-  labs(x = TeX("Variation in Thermal Optima ($\\sigma_{\\delta}$)"),
-       y = TeX("Variation in Thermal Breadth ($\\sigma_{\\sigma}$)"),
-       fill = TeX("$lnVR_{Q_{10}}$")) + theme_classic() + my_theme() + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 12))
-
-p_sim2 <- ((lncvr_sim_delta_sigma1 + lnvr_sim_delta_sigma1)) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
-ggsave(p_sim2, width = 20, height = 10, filename = "./output/figures/figS13_new.pdf")
-
-p_sim2 <- image_read("./output/figures/figS13.pdf")
-p_sim2
-```

### 2024-07-14 ms.qmd
Adding some general comparisons across major category types, written lnVR results, adding to lnRR and fixed a bug in the get_lifestage function. Need to remember that we're using a different methods to caluclate predictions and this results in posterior being in columns not rows, so flipped this around.

@@
 @Seebacher2015-wi's data by extracting data from suitable studies from
-our own searches that followed the same search protocol. For full
+our own searches that followed the same search protocol. We extracted data from an extra
+`r length(unique(new_papers$record_num))` papers (with a total of
+`r dim(new_papers)[1]` effects; a
+`r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`%
+increase in the number of published articles). For full
 details on the search protocol see the *Supplementary Materials*, where
@@
 we classified as ‘Other’.
-
-### *Climate Data*
-
-To understand how climate is related to a species’ physiological
-acclimation abilities and changes in relative variance we used the
-coordinates reported by each study to extract temperature data from
-terrestrial and aquatic environments. It was unclear whether climate at
-the locations of captive reared organisms would be representative of a
-population's climate history - particularly for species reared under
-captive condition for many generations. Given that we were interested in
-understanding climate driven effects on acclimation capacity we only
-used studies on wild populations for climate analyses.
-
-Monthly average temperature data were extracted from the ERA5 climate
-model, available from the Copernicus climate data store
-[@Hersbach2020-hx]. For each population and species in the dataset we
-extracted a 72-year period (1950-2022) of either surface air temperature
-(0.01° resolution) for both terrestrial and freshwater taxa, or sea
-surface temperature for the marine taxa (at 0.25° resolution) using the
-*ncdf4* R package [vers. `r utils::packageVersion("ncdf4")`,
-@Pierce2021-lc]. We chose surface temperature because we believed that
-it was more likely to reflect the micro-thermal environment experienced
-by terrestrial and freshwater ectotherms at those locations.
-
-Using the thermal time-series data for each location we calculated
-metrics of thermal variability across months and years as well as
-estimates of thermal predictability (i.e., autocorrelation). To estimate
-thermal variability, we calculated the coefficient of variation
-($\frac{SD}{M}$, where SD = standard deviation in temperature and M =
-the mean temperature for each year). We also estimated thermal
-predictability, by calculating the auto-regressive time lag across
-months (i.e., a measure of how correlated temperatures were between
-months), however, identifying biologically relevant lags for such
-diverse taxa is challenging. As such, we present a coarse analysis using
-this metric of thermal predictability in the *Supplemental Materials*.
-
-Lastly, to illustrate the effects that climate warming could have on
-physiological rate variance we also extracted climate projections and
-calculated thermal variability into the future. We used the CanESM2
-climate model (2005-2100) [vers. 1.2.0; @koen_hufkens_2019_2647541]
-under a high emissions scenario (RCP8.5).
 
@@
 ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp). We
-predicted that, if $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ were not
+predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not
 strictly log-linear than we would see a decrease in average effect size
@@
 We first tested the degree to which the difference in acute and
-acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by
+acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effects varied by
 habitat type (i.e., terrestrial, freshwater, and marine). Models
@@
 contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to
-$lnCVR_{Q_{10_{acute}}}$ would imply that changes in between individual
+$lnVR_{Q_{10_{acute}}}$ would imply that changes in between individual
 variation in physiological rates across 10°C differ depending on whether
@@
 Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and
-$lnCVR_{Q_{10}}$ differed between whole-organism versus biochemical
+$lnVR_{Q_{10}}$ differed between whole-organism versus biochemical
 traits across habitats by fitting an model with an interaction between
@@
 Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$
-and $lnCVR_{Q_{10}}$ were predicted by a populations climate variability
+and $lnVR_{Q_{10}}$ were predicted by a populations climate variability
 (CV). We only used $lnRR_{Q_{10_{acclimation}}}$ for these models
 because our predictions were specifically focused on the plastic
-adjustments to physiological rates. We used all $lnCVR_{Q_{10}}$ data
-because there were no differences between $lnCVR_{Q_{10_{acclimation}}}$
-and $lnCVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe
-climate would impact acclimation and acute $lnCVR_{Q_{10}}$ differently.
+adjustments to physiological rates. We used all $lnVR_{Q_{10}}$ data
+because there were no differences between $lnVR_{Q_{10_{acclimation}}}$
+and $lnVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe
+climate would impact acclimation and acute $lnVR_{Q_{10}}$ differently.
 To test how climate variability impacted mean effect size in wild
@@
 type, latitude and longitude (referred to as "Model 6"). We assumed that
-any change in $lnCVR_{Q_{10}}$ across latitude and longitude could vary
+any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary
 by habitat type (i.e., an interaction between habitat). We used
@@
 effects of species, trait, phylogeny and study. We predicted the
-expected change in $lnCVR_{Q_{10}}$ for each wild population in our
+expected change in $lnVR_{Q_{10}}$ for each wild population in our
 dataset at the specific populations latitude and longitude. To do this,
-we first converted the predicted $lnCVR_{Q_{10}}$ to a 1°C change as
+we first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as
 opposed to 10°C as follows:
@@
 
+  # Contrats adult vs juv across habitats regardless of the acute/acclim
+               contrast_lnrr_lh_cat_stats <- rbind(get_lifestage(pred, habitat = "t", newdata),
+                                                   get_lifestage(pred, habitat = "m", newdata),
+                                                   get_lifestage(pred, habitat = "f", newdata))
+
 ####################################################
@@
 To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance across temperature we conducted a simple simulation.
-To simulate performance curves, we used a asymmetrical Gaussian function (@eq-sim):
+To simulate performance curves, we used an asymmetrical Gaussian function:
 
@@
 
-where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see *Supplementary Materials* showing curves).
-While we could have used other performance curve functions (e.g., Arrhenius), our intentions were not to model the exact curves (which are not know) but rather identify what might vary across the major habitat types that could contribute to the different patterns of variance change at higher temperatures we observed across habitats.
+where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see @fig-sim in *Supplementary Materials* for example curves).
+While we could have modelled performance curves differently than @eq-sim (e.g., Arrhenius), our intentions were not to model the exact curves (which are not know) but rather identify what might vary across the major habitat types that could contribute to the different patterns of variance change at higher temperatures we observed across habitats.
 
@@
 `r quantile(change_t, c(0.025, 0.975))[1]` to
-`r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]B). All results are
+`r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A). All results are
 from Model 2 (see “Meta-Analysis” above).
@@
 whereas both whole-organism and biochemical traits acclimated in
-freshwater ectotherms ([@fig-btrait]C). Unsurprisingly, neither broad
+freshwater ectotherms ([@fig-btrait]C). Unsurprisingly, neither
 trait category showed evidence of acclimation in terrestrial ectotherms
@@
 
-  # Now, lets get contrasts between habitats averaged over type
-      f_m_c <- f_VR_mean - m_VR_mean   ; pmcmc(f_m_c); mean(f_m_c)
-      f_t_c <- t_VR_mean_ef - f_VR_mean; pmcmc(f_t_c); mean(f_t_c)
-      m_t_c <- t_VR_mean_ef - m_VR_mean; pmcmc(m_t_c); mean(m_t_c)
+  # Now, lets get contrasts between habitats for acute and acclimation. Keep seperate because the challenge is the rates acclimate so adds quite a bif of variability
+      f_m_c_a <- f_acute_VR - m_acute_VR; pmcmc(f_m_c_a); mean(f_m_c_a)
+      f_t_c_a <- f_acute_VR - t_acute_VR; pmcmc(f_t_c_a); mean(f_t_c_a)
+      m_t_c_a <- m_acute_VR - t_acute_VR; pmcmc(m_t_c_a); mean(m_t_c_a)
+
+      f_m_c_aclim <- f_acclim_VR - m_acclim_VR; pmcmc(f_m_c_aclim); mean(f_m_c_aclim)
+      f_t_c_aclim <- f_acclim_VR - t_acclim_VR; pmcmc(f_t_c_aclim); mean(f_t_c_aclim)
+      m_t_c_aclim <- m_acclim_VR - t_acclim_VR; pmcmc(m_t_c_aclim); mean(m_t_c_aclim)
 
@@
                                                        p = apply(data.frame(contrast_lnvr_lh_post), 1, function(x) p_value(pmcmc(x))))
+
+        # Contrasts for pooled acute and acclimation across life stage categories. Checked freshwater and looks correct.
+            contrast_lnvr_lh_cat_stats <- rbind(get_lifestage(pred_lh_vr, habitat = "t", lh_b_data),
+                                                get_lifestage(pred_lh_vr, habitat = "m", lh_b_data),
+                                                get_lifestage(pred_lh_vr, habitat = "f", lh_b_data))
 ```
@@
 #| label: fig-2
-#| fig-cap: "A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
-B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+#| fig-cap: "(A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
+(B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
 For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Sample sizes are the same for panel A) and B).
-In panels A) and B), thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+Sample sizes are the same for panel A and B.
+In both panels, thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
 $\\Beta$ values are the contrasts between acute and acclimation means within each habitat.
@@
 
-### *Variation in physiological rates increases in aquatic but not terrestrial ectotherms*
+```{r, fig-btrait}
+#| label: fig-btrait
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across marine (A & D), freshwater (B & E) and terrestrial (C & F) habitats.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
+"
+#| echo: false
+#| warning: false
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lnrr_btrait  <- lnRRQ10_data  %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+n_lnvr_btrait <- lnVRQ10_data %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+
+       col <- c("#0871B9", "#F3B40D", "#1BB908")
+     x.pos <- c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+############
+# lnRR
+############
+m_r <- n_lnrr_btrait %>% filter(habitat == "m")
+f_r <- n_lnrr_btrait %>% filter(habitat == "f")
+t_r <- n_lnrr_btrait %>% filter(habitat == "t")
+
+t_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+yloc = c(1.5, 2.5)
+
+p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -0.8, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.5, 2) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.25, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8)
+
+############
+# lnVR
+############
+m_r_vr <- n_lnvr_btrait %>% filter(habitat == "m")
+f_r_vr <- n_lnvr_btrait %>% filter(habitat == "f")
+t_r_vr <- n_lnvr_btrait %>% filter(habitat == "t")
+
+t_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+yloc = c(1.5, 2.5)
+
+p1_vr_trait <- orchard_plot(model3.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r_vr$k, " (", m_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b_vr$diff, " [", m_trait_b_vr$l95, " to ", m_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_vr$p)), hjust = 0, size = 8)
+
+p2_vr_trait <- orchard_plot(model3.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r_vr$k, " (", f_r_vr$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b_vr$diff, " [", f_trait_b_vr$l95, " to ", f_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_vr$p)), hjust = 0, size = 8)
+
+p3_vr_trait <- orchard_plot(model3.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5, 3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r_vr$k, " (", t_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b_vr$diff, " [", t_trait_b_vr$l95, " to ", t_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_vr$p)), hjust = 0, size = 8)
+
+############
+# Full fig
+############
+figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
+ggsave(figbtrait, filename = "./output/figures/fig5.png", width = 28, height = 14, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/fig5.png")
+figbtrait
+```
+
+```{r, fig-cvrlh}
+#| label: fig-cvrlh
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for marine (A & D), freshwater (B & E) and terrestrial (C & F) ectotherms.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
+$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
+#| echo: false
+#| warning: false
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lnrr_lh  <- lnRRQ10_data  %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+n_lnvr_lh <- lnVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
+
+x.pos = c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+###############
+## lnRR Q10
+###############
+
+t_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+yloc = c(1.5, 2.5)
+
+m_r <- n_lnrr_lh %>% filter(habitat == "m")
+f_r <- n_lnrr_lh %>% filter(habitat == "f")
+t_r <- n_lnrr_lh %>% filter(habitat == "t")
+
+p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.3, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+###############
+## lnVR Q10
+###############
+
+t_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+m_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+f_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
+
+yloc = c(1.5, 2.5)
+
+m_r <- n_lnvr_lh %>% filter(habitat == "m")
+f_r <- n_lnvr_lh %>% filter(habitat == "f")
+t_r <- n_lnvr_lh %>% filter(habitat == "t")
+
+p1_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5,3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+
+fig4 <-(p3 | p1 | p2) / (p3_vr | p1_vr | p2_vr) + plot_annotation(tag_levels = "A") 
+ggsave(fig4, filename = "./output/figures/fig6.pdf", width = 28, height = 14, device = "pdf")
+
+fig4 <- magick::image_read("./output/figures/fig6.pdf")
+fig4
+```
+
+### *Variation in physiological rates increases but to a greater extent in aquatic compared terrestrial ectotherms*
 
 Variance in physiological rates ($lnVR_{Q_{10}}$) showed an
-increase with increasing temperature across all habitat types with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI:
+increase with increasing temperature across all habitat types ([@fig-2]B) with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI:
 `r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`; "Model 1"; see *Supplementary Materials* @fig-s3).
-However, physiological rate variance increased significantly more in freshwater (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c)`, 95% CI: `r quantile(f_t_c, 0.025)` to `r quantile(f_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c))`) and marine ectotherms (marine vs terrestrial: $\beta$ = `r mean(m_t_c)`, 95% CI: `r quantile(m_t_c, 0.025)` to `r quantile(m_t_c, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c))`) compared to the limited increase in terrestrial ecotherms (@fig-2).
+However, physiological rate variance increased significantly more in freshwater for acute resposnes (freshwater vs terrestrial: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`), but not for acclimation responses because increases in rates were dampended by acclimation resulting in smaller increases in variance (freshwater vs terrestrial: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
+While marine ectotherms had larger increases in physiological rate variance compared to terrestrial ectoterms these were not signigicant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
+Marine and freshwater did not differ in how much variance changed at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
 There were no differences between
-$lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$. Differences
-in variance between habitats were driven by different scaling relationships between mean and variance across habitats (see *Supplementary
-Materials*; @tbl-slopes & @fig-mv). There was a `r mean(t_VR_mean_ef)`%
+$lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ in any habitat ([@fig-2]B). Differences
+in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary
+Materials* analyses with $lnCVR_{Q_{10}}$; @tbl-slopes & @fig-mv).
+
+Overall, there was a `r mean(t_VR_mean_ef)`%
 (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to
@@
 #| fig-align: center
-#| fig-cap: "Expected $lnVR_{Q_{10}}$ when varying $\\sigma_{_b_{\\delta}}$ = {0.01, 2} and  $\\sigma_{_b_{\\sigma}}$ = {0.01, 2} while fixing $\\sigma_{_b_{\\alpha}}$ = 0.01.
-In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$, $\\sigma_{_b_{\\sigma}}$.
-The parameter space that match observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms.
-Dashed lines indicate the relative differences between the three habitat types when holding one parameter constant."
+#| fig-cap: "Expected $lnVR_{Q_{10}}$ when varying individual variation in thermal breadth($\\sigma_{_b_{\\delta}}$ = {0.01, 2}) and  thermal optima ($\\sigma_{_b_{\\sigma}}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{_b_{\\alpha}}$ = 0.01).
+In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$ and $\\sigma_{_b_{\\sigma}}$.
+The parameter space that matches the observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is also shown.
+Dashed lines indicate the relative differences between the three habitat types when holding one variance parameter constant."
 
@@
 
-#ggsave(lnvr_sim_delta_sigma1, width = 9.5, height = 8, filename = "./output/figures/figsim_new2.pdf")
-
-p_sim2 <- image_read("./output/figures/figsim_new.pdf")
+#ggsave(lnvr_sim_delta_sigma1, width = 9.5, height = 8, filename = "./output/figures/fig4.pdf")
+
+p_sim2 <- image_read("./output/figures/fig4_new.pdf")
 p_sim2
@@
 
-Across habitats whole-organism versus biochemical processes showed a
-similar change in variance in physiological rates
-([@fig-btrait]D-F; see *Supplementary Materials*, @fig-vrtrait) for more detailed trait
-analysis), except for biochemical processes in ectotherms occupying
-freshwater habitats, which showed small, albeit significant increase in
-relative variance when acclimated ([@fig-btrait]F). Reduced relative
-variance was particularly prominent for resting metabolic rates and
-sprint speed although traits differed in whether they exhibited a
-reduction in variation in physiological rates at high temperatures (see
-*Supplemental Material*, @fig-vrtrait) ("Model 3"). Each life-history stage
-exhibited the same pattern of relative variance change in each of the
-habitats ("Model 4"; @fig-cvrlh).
-
-```{r, fig-btrait}
-#| label: fig-btrait
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across marine (A & D), freshwater (B & E) and terrestrial (C & F) habitats.
-Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
-"
-#| echo: false
-#| warning: false
-
-add_theme  <- function(){theme(axis.title  = element_text(size = 30),
-                               axis.text.y = element_text(size = 30),
-                               axis.text.x = element_text(size = 30),
-                              legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 36))}
-
-branch.size = 2.8
-trunk.size = 1.8
-
-n_lnrr_btrait  <- lnRRQ10_data  %>% filter(trait_broad != "other") %>% 
-              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
-n_lnvr_btrait <- lnVRQ10_data %>% filter(trait_broad != "other") %>% 
-              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
-
-       col <- c("#0871B9", "#F3B40D", "#1BB908")
-     x.pos <- c(0.7, 1.30, 1.70, 2.30)
-size_annot <- 5.5
-
-############
-# lnRR
-############
-m_r <- n_lnrr_btrait %>% filter(habitat == "m")
-f_r <- n_lnrr_btrait %>% filter(habitat == "f")
-t_r <- n_lnrr_btrait %>% filter(habitat == "t")
-
-t_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-m_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-f_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-
-yloc = c(1.5, 2.5)
-
-p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -0.8, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
-
-p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.5, 2) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
-
-p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.25, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8)
-
-############
-# lnVR
-############
-m_r_vr <- n_lnvr_btrait %>% filter(habitat == "m")
-f_r_vr <- n_lnvr_btrait %>% filter(habitat == "f")
-t_r_vr <- n_lnvr_btrait %>% filter(habitat == "t")
-
-t_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-m_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-f_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-
-yloc = c(1.5, 2.5)
-
-p1_vr_trait <- orchard_plot(model3.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r_vr$k, " (", m_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b_vr$diff, " [", m_trait_b_vr$l95, " to ", m_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_vr$p)), hjust = 0, size = 8)
-
-p2_vr_trait <- orchard_plot(model3.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r_vr$k, " (", f_r_vr$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b_vr$diff, " [", f_trait_b_vr$l95, " to ", f_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_vr$p)), hjust = 0, size = 8)
-
-p3_vr_trait <- orchard_plot(model3.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5, 3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r_vr$k, " (", t_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b_vr$diff, " [", t_trait_b_vr$l95, " to ", t_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_vr$p)), hjust = 0, size = 8)
-
-############
-# Full fig
-############
-figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/fig4.png")
-figbtrait
-```
-
-```{r, fig-cvrlh}
-#| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for marine (A & D), freshwater (B & E) and terrestrial (C & F) ectotherms.
-Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
-$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
-$p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
-#| echo: false
-#| warning: false
-
-add_theme  <- function(){theme(axis.title  = element_text(size = 30),
-                               axis.text.y = element_text(size = 30),
-                               axis.text.x = element_text(size = 30),
-                              legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 36))}
-
-branch.size = 2.8
-trunk.size = 1.8
-
-n_lnrr_lh  <- lnRRQ10_data  %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
-n_lnvr_lh <- lnVRQ10_data %>% group_by(habitat, life.hist, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(type, life.hist, habitat)
-
-x.pos = c(0.7, 1.30, 1.70, 2.30)
-size_annot <- 5.5
-
-###############
-## lnRR Q10
-###############
-
-t_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-m_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-f_trait_b <- contrast_stage_lnrr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-
-yloc = c(1.5, 2.5)
-
-m_r <- n_lnrr_lh %>% filter(habitat == "m")
-f_r <- n_lnrr_lh %>% filter(habitat == "f")
-t_r <- n_lnrr_lh %>% filter(habitat == "t")
-
-p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
-
-p2 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.4, 1.5) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
-
-p3 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.3, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
-
-###############
-## lnVR Q10
-###############
-
-t_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-m_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-f_trait_b <- contrast_lnvr_lh_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(stage)
-
-yloc = c(1.5, 2.5)
-
-m_r <- n_lnvr_lh %>% filter(habitat == "m")
-f_r <- n_lnvr_lh %>% filter(habitat == "f")
-t_r <- n_lnvr_lh %>% filter(habitat == "t")
-
-p1_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
-
-p2_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
-
-p3_vr <- orchard_plot(model3.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5,3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8) +scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
-
-fig4 <-(p3 | p1 | p2) / (p3_vr | p1_vr | p2_vr) + plot_annotation(tag_levels = "A") 
-ggsave(fig4, filename = "./output/figures/fig5.pdf", width = 28, height = 14, device = "pdf")
-
-fig4 <- magick::image_read("./output/figures/fig5.pdf")
-fig4
-```
+Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`)
+([@fig-btrait]D-F; see also  *Supplementary Materials*, @fig-vrtrait for more detailed trait
+analysis)("Model 3"). Interestingly, variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
+
+Each life-history stage exhibited the same pattern of variance change in each of the
+habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
 
@@
 #| fig-align: center
-#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A) and $lnCVR_{Q_{10_{acclim}}}$ (B) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
+#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A-C) and $lnVR_{Q_{10_{acclim}}}$ (E-G) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
@@
 
-  ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig6.png")
-
-  p_cv <- image_read("./output/figures/fig6.png")
+  ggsave(p_cv, width = 18, height = 10, filename = "./output/figures/fig7.png")
+
+  p_cv <- image_read("./output/figures/fig7.png")
   p_cv 
@@
 #| message: false
-#| fig-cap: "Model predictions for the expected change in acclimation $lnVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
-Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
-Predicted change in relative physiological rate variance for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
-Future climate predictions are the reduction in relative variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change)."
+#| fig-cap: "Model predictions for the expected change in $lnVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+Predicted change in physiological rate variance for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
+Future climate predictions are the reduction in variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change)."
 
@@
 
-ggsave(p, filename = "./output/figures/fig7.png", width = 7.8, height = 10.1)
-
-image_read("./output/figures/fig7.png")
+ggsave(p, filename = "./output/figures/fig8.png", width = 7.8, height = 10.1)
+
+image_read("./output/figures/fig8.png")
 ```
@@
 @seebacher2023can; @Sanderson2023; @urban2023and]. Here, acclimation
-responses ($lnRR_{Q_{10}}$) varied across habitats while relative
-variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms
-decreased across terrestrial, marine and freshwater habitats as
-temperatures increase. Decreases in relative variance were particularly
-pronounced in terrestrial ectotherms (\~28%). These effects are expected
-to result in a decrease in the variability in physiological rates for
-marine and terrestrial ectotherms between \~4-13% under future climate
-change projections. Our results uncover an hitherto unrecognised dynamic
-where the benefits of acclimation may be counteracted by shifts in trait
-variance impacting how ectotherm populations across different habitats
-will be able to cope with increased temperatures.
-
-### ***Acclimation capacities and changes in relative variability in physiological rates vary among habitats***
-
-We show that acclimation of physiological rates and changes in relative
+responses ($lnRR_{Q_{10}}$) varied across habitats while
+variance ($lnVR_{Q_{10}}$) in physiological rates of ectotherms
+increased, with the extent of this increase varying across habitats. Our results uncover an hitherto unrecognised dynamic
+where the limited benefits of acclimation are offset by increases in trait
+variance that may have impacts on how ectotherm populations across these different habitats
+will be able to adapt to increased temperatures.
+
+### ***Acclimation capacities vary among habitats but are often still limited***
+
+We show that acclimation of physiological rates and changes in their
 variance differ across habitats. Our findings confirm previous results
@@
 environments making physiological remodeling important for maintaining
-homeostasis [@Gunderson2015-hz; @morley2019physiological].
-Additionally, aquatic and terrestrial environments can vary in
-nutritional resources [e.g., fatty acid content of prey;
-@twining2019aquatic] that can impact physiological rates and their
-variability by affecting performance curves and acclimation responses
-[@hardison2024diet; @sinclair2016can]. While marine and freshwater ectotherms were
-capable of partial acclimation it is still important to recognise that,
-on average, the effect size was small (amounting to $Q_{10}$ dropping
-from ~1.8 to 1.6).
-
-Changes in relative variance in physiological rates across habitats was
-nearly equivalent (marine) or larger (terrestrial) compared to their
-capacity to acclimate. Only in freshwater ectotherms did acclimation in
+homeostasis [@Gunderson2015-hz; @morley2019physiological]. Importantly, even though marine and freshwater ectotherms were
+capable of partial acclimation on average, the effect size was small (amounting to $Q_{10}$ dropping
+from ~1.8 to 1.6), suggesting acclimation will still provide limited opportunity for aquatic ectotherms when coping with higher temperatures.
+
+Interestingly, we show that biochemical traits (i.e., enzymes) were more
+likely to acclimate compared to whole-organisms traits as predicted, but
+only for marine ectotherms. In contrast, both whole-organism and
+biochemical traits were equally likely to acclimate in freshwater
+ectotherms. Unsurprisingly, we observed no distinction between traits in
+terrestrial ectotherms.
+
+### ***Increased variability in physiological rates across habitats: insights into the adaptive potential of physiological processes in the face of climate change?***
+In contrast to acclimation capacity, variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation.
+Mechanistically, it is unclear what is contributing to the increased variation in physiological rates at higher temperatures, but it could be the result of increased among-individual variability in how biochemical, cellular and physiologcial processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins;
+@fields2001protein]. Higher temperatures increase membrane fluidity affecting electrochemical gradients and impact protein structure and function [@somero1995proteins;
+@fields2001protein; @tattersall2012coping].
+Such challenges (among others) may increase existing variation among indiviudals within a population.
+Some support for these mechanisms exist given that variation in biochemical traits did show larger increases in variability at high teperatures compared to whole-organism traits, although this was only significant for marine organisms.
+Increases in variance are probably dependent on the type of biochemical reaction being measured, and so, the differences across habitats could be attributable to the types of traits being measured.
+
+Importantly, increased variance in physiological rates was not equal among ectotherms accupying terrestrial, marine and freshwater habitats. For example, increases in variance were particularly
+pronounced in freshwater ectotherms (~60% increase over 10 degrees Celsius) compared to terrestrial ectotherms (~36% increase over 10 degrees Celcius).
+The changes in variability we observed across habiats can be explained by differences in among individual variation in thermal breath and optima of individual performance curves between habitats.
+Consistent differences in thermal performance curves across these major habitat types have never been formally compared, probably because of the challeges in measuring full performance curves across taxa.
+However, a multitude of studies support the general notion that species occupying different habiats (terrestrial vs aquatic) should differ.
+@p
+
+Understanding the relative role that plasticity and genetic adaptation will play in response to future climates has attracted considerable attention [@urban2023and].
+If the increased variability we observed in our study is underpinned by genetic variation then our results suggest evolutionary adaptation will be more important than acclimation as populations experience future climates.
+Increased expression of genetic variation in response to novel environments has been shown by numerous studies but primarily for morphological and life-history traits [noble rowinsku rogel, ].
+Our results further highlight the vulnerability of terrestrial
+ectotherms to climate change. Assuming changes in
+variation in physiological rates are underpinned by genetic variation,
+and there is a genetic correlation with fitness, such reductions in
+physiological variance could limit adaptation in terrestrial habitats more than aquatic habiats in the 
+future [@urban2023and].
+For example, under climate we expect an increase of only ~13% in terrestrial habitats whereas for freshwater habiats we expect variation in physiological rates to increase by 29%.
+
+------
+Only in freshwater ectotherms did acclimation in
 physiological rates coincide with no change in relative variation.
-Mechanistically, it is unclear what is contributing to the reduction in
-relative variation in physiological rates at higher temperatures. One
-possible explanation may be that biochemical reactions are operating
-more efficiently or are relying on more conformationally stable enzymes
-at higher temperatures impacting between individual variation
-[@tattersall2012coping; @angilletta2009thermal; @somero1995proteins;
-@fields2001protein]. Such a mechanism may also help explain the
+Such a mechanism may also help explain the
 differences in relative variance across habitat types. For example,
@@
 
-Interestingly, we show that biochemical traits (i.e., enzymes) were more
-likely to acclimate compared to whole-organisms traits as predicted, but
-only for marine ectotherms. In contrast, both whole-organism and
-biochemical traits were equally likely to acclimate in freshwater
-ectotherms. Unsurprisingly, we observed no distinction between traits in
-terrestrial ectotherms. We also expected relative variance to differ
+ We also expected relative variance to differ
 between whole-organism and biochemical traits, but we did not find
@@
 
-Our results further highlight the vulnerability of terrestrial
-ectotherms to climate change, while calling into question if acclimation
-in marine systems will be able to counteract the potentially negative
-effects of reductions in relative variance. Assuming changes in relative
-variation in physiological rates are underpinned by genetic variation,
-and there is a genetic correlation with fitness, such reductions in
-physiological variance could limit a populations ability to adapt to
-future climates [@urban2023and]. Of course, considering how behavioural
+ Of course, considering how behavioural
 modifications buffer organisms from high temperatures is also needed.
@@
 wide prediction intervals and substantial study- and trait-level
-variance estimates. Nonetheless, quantitative measures on the changes in
-the relative variance in physiological rates could be better
+variance estimates. Nonetheless, quantitative measures on the changes in variance in physiological rates could be better
 incorporated into physiological and ecological models to provide more
@@
 
-Nonetheless, it is clear that many fascinating questions remain
+It is clear that many fascinating questions remain
 unanswered that will require greater focus on the consequences of
@@
 
+### *Climate data*
+
+To understand how climate is related to a species’ physiological
+acclimation abilities and changes in relative variance we used the
+coordinates reported by each study to extract temperature data from
+terrestrial and aquatic environments. It was unclear whether climate at
+the locations of captive reared organisms would be representative of a
+population's climate history - particularly for species reared under
+captive condition for many generations. Given that we were interested in
+understanding climate driven effects on acclimation capacity we only
+used studies on wild populations for climate analyses.
+
+Monthly average temperature data were extracted from the ERA5 climate
+model, available from the Copernicus climate data store
+[@Hersbach2020-hx]. For each population and species in the dataset we
+extracted a 72-year period (1950-2022) of either surface air temperature
+(0.01° resolution) for both terrestrial and freshwater taxa, or sea
+surface temperature for the marine taxa (at 0.25° resolution) using the
+*ncdf4* R package [vers. `r utils::packageVersion("ncdf4")`,
+@Pierce2021-lc]. We chose surface temperature because we believed that
+it was more likely to reflect the micro-thermal environment experienced
+by terrestrial and freshwater ectotherms at those locations.
+
+Using the thermal time-series data for each location we calculated
+metrics of thermal variability across months and years as well as
+estimates of thermal predictability (i.e., autocorrelation). To estimate
+thermal variability, we calculated the coefficient of variation
+($\frac{SD}{M}$, where SD = standard deviation in temperature and M =
+the mean temperature for each year). We also estimated thermal
+predictability, by calculating the auto-regressive time lag across
+months (i.e., a measure of how correlated temperatures were between
+months), however, identifying biologically relevant lags for such
+diverse taxa is challenging. As such, we present a coarse analysis using
+this metric of thermal predictability in the *Supplemental Materials* below.
+
+Lastly, to illustrate the effects that climate warming could have on
+physiological rate variance we also extracted climate projections and
+calculated thermal variability into the future. We used the CanESM2
+climate model (2005-2100) [vers. 1.2.0; @koen_hufkens_2019_2647541]
+under a high emissions scenario (RCP8.5).
+
 #### *Mean-variance relationships to understand patterns in* $lnCVR_{Q_{10}}$
@@
  p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
-  ggsave(p_mv, file = "./output/figures/figS7.png", height = 8, width = 8)
-
-  p_mv <- magick::image_read("./output/figures/figS7.png")
+  ggsave(p_mv, file = "./output/figures/figS5.png", height = 8, width = 8)
+
+  p_mv <- magick::image_read("./output/figures/figS5.png")
   p_mv
@@
 
-########
-
 ##################
-  # Figure S1
+  # Figure 
 ##################
 
-  ggsave(p3, filename = "./output/figures/figS8.pdf", width = 11.5, height = 8)
-
-  figs1 <- image_read("./output/figures/figS8.pdf")
+  ggsave(p3, filename = "./output/figures/figS6.pdf", width = 11.5, height = 8)
+
+  figs1 <- image_read("./output/figures/figS6.pdf")
   figs1
@@
 ############
-figbtrait_vr <-(p1_cvr | p2_cvr | p3_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait_vr, filename = "./output/figures/figStrait_cvr.png", width = 28, height = 8, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/figStrait_cvr.png")
+figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
+ggsave(figbtrait_vr, filename = "./output/figures/figS7.png", width = 28, height = 8, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figS7.png")
 figbtrait
@@
 figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figcvr_lh, filename = "./output/figures/figSlh.pdf", width = 28, height = 10, device = "pdf")
-
-figcvr_lh <- magick::image_read("./output/figures/figSlh.pdf")
+ggsave(figcvr_lh, filename = "./output/figures/figS8.pdf", width = 28, height = 10, device = "pdf")
+
+figcvr_lh <- magick::image_read("./output/figures/figS8.pdf")
 figcvr_lh
@@
 
-#### *Acute and acclimation* $lnRR_{Q_{10}}$ for detailed trait categories across marine, freshwater and terrestrial taxa (REMOVE)
+#### *Acute and acclimation* for detailed trait categories across marine, freshwater and terrestrial taxa
 
@@
 
-Acclimation capacity varied across trait categories and habiats with measures of resting metabolic rate, including associated biochemical reactions like oxidative phosphorylation (OXPHOS) and ATPase activity, acclimating in marine and freshwater ectotherms (@fig-lnrrtrait).
-Whether relative variation in physiological rates changes also depended on trait type, with freshwater ectotherms generally maintaining relative variance in physiological rates better than marine and freshwater ectotherms (@fig-cvrtrait).
+Acclimation capacity varied across trait categories and habitat with measures of resting metabolic rate, including associated biochemical reactions like oxidative phosphorylation (OXPHOS) and ATPase activity, acclimating in marine and freshwater ectotherms (@fig-lnrrtrait).
+Whether relative variation in physiological rates changes also depended on trait type, with freshwater ectotherms generally maintaining variance in physiological rates better than marine and freshwater ectotherms (@fig-vrtrait & @fig-cvrtrait).
 We note though that some traits have very small sample sizes on their own and should be interpreted with caution.
@@
                                             ~1 + trait_category | obs),
-                              R = list(species_full = f_phylo_vr), dfs = "contain", 
+                              R = list(species_full = f_phylo_VR), dfs = "contain", 
                               test = "t", struct = c("GEN", "HCS"), phi = 0, data = lnVRQ10_data_f)
@@
                                             ~1 + trait_category| obs),
-                              R = list(species_full = m_phylo_vr), dfs = "contain", 
+                              R = list(species_full = m_phylo_VR), dfs = "contain", 
                               test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnVRQ10_data_m)
@@
                                             ~1 + trait_category | obs),
-                              R = list(species_full = t_phylo_vr), dfs = "contain", 
+                              R = list(species_full = t_phylo_VR), dfs = "contain", 
                               test = "t", struct = c("GEN", "HCS"),  phi = 0, data = lnVRQ10_data_t)
@@
 #########################
-        model3.3 <- readRDS("./output/models/lnCVRQ10_3.3")
-        model3.3f <- readRDS("./output/models/lnCVRQ10_model3.3f")
-        model3.3m <- readRDS("./output/models/lnCVRQ10_model3.3m")
-        model3.3t <- readRDS("./output/models/lnCVRQ10_model3.3t")
-  model3.3_bayes <- readRDS("./output/models/lnCVRQ10_3.3_bayes")
+        model3.3 <- readRDS("./output/models/lnVRQ10_3.3")
+        model3.3f <- readRDS("./output/models/lnVRQ10_model3.3f")
+        model3.3m <- readRDS("./output/models/lnVRQ10_model3.3m")
+        model3.3t <- readRDS("./output/models/lnVRQ10_model3.3t")
+  model3.3_bayes <- readRDS("./output/models/lnVRQ10_3.3_bayes")
 }
@@
 fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
-ggsave(fig2, filename = "./output/figures/figS5.png", height = 20, width = 15)
-
-img_fig2 <- magick::image_read("./output/figures/figS5.png")
+ggsave(fig2, filename = "./output/figures/figS9.png", height = 20, width = 15)
+
+img_fig2 <- magick::image_read("./output/figures/figS9.png")
 img_fig2
+```
+
+```{r, fig-vrtrait}
+#| label: fig-vrtrait
+#| fig-cap: "Acute and acclimation $lnVR_{Q_{10}}$ across traits for A) marine, B) freshwater and C) terrestrial systems.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+The x-axis is truncated for ease of visualisation.
+See methods section “Moderator Variables” for a full description of the trait categories.
+"
+#| echo: false
+
+k_marinevr=manual_extract(model3.3m, mod = "trait_category", group = "record_num", exclude = "Antiox")
+ k_freshvr=manual_extract(model3.3f, mod = "trait_category", group = "record_num")
+ k_terrsvr=manual_extract(model3.3t, mod = "trait_category", group = "record_num")
+
+ptm_vr <- orchard_plot(model3.3m, mod = "trait_category", group = "record_num", weights = "prop",  xlab = TeX("$lnVR_{Q_{10}}$"), angle = 0, k.pos = "none", condition.lab = "Type") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + add_theme() + annotate("text", label= paste0("k = ", k_marinevr$k, " (", k_marinevr$sdy, ")"), x = k_marinevr$moderator, y = 2.4) + ylim(-2, 2.6)
+#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptf_vr <- orchard_plot(model3.3f, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnVR_{Q_{10}}$"), angle = 0, condition.lab = "Type",  k.pos = "none") +
+  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
+                              "Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate",
+                              "Mito_oxidation" = "OXPHOS")) + theme_classic()+ add_theme() + annotate("text", label= paste0("k = ", k_freshvr$k, " (", k_freshvr$sdy, ")"), x = k_freshvr$moderator, y = 2.4) + ylim(-2.5, 2.65)
+#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+ptt_vr <- orchard_plot(model3.3t, mod = "trait_category",  group = "record_num", weights = "prop",  xlab = TeX("$lnVR_{Q_{10}}$"), angle = 0,  k.pos = "none", condition.lab = "Type") +
+  scale_x_discrete(labels = c("Metabolic_enzyme" = "Metabolic Enzymes",
+                              "Rest_MR" = "Resting Metabolic Rate",
+                              "Max_MR" = "Maximum Metabolic Rate")) + theme_classic() +  annotate("text", label= paste0("k = ", k_terrsvr$k, " (", k_terrsvr$sdy, ")"), x = k_terrsvr$moderator, y = 2.4) + labs(legend = "Type")+ add_theme() + ylim(-2, 2.65)
+#ptt$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
+
+figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+ggsave(figvrtrait, filename = "./output/figures/figS10.png", height = 20, width = 15)
+
+img_figvrtrait <- magick::image_read("./output/figures/figS10.png")
+img_figvrtrait
 ```
@@
 figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figS6.png", height = 20, width = 15)
-
-img_figcvrtrait <- magick::image_read("./output/figures/figS6.png")
+ggsave(figcvrtrait, filename = "./output/figures/figS11.png", height = 20, width = 15)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figS11.png")
 img_figcvrtrait
@@
 figs3 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figS9.png")
-
-figs3 <- image_read("./output/figures/figS9.png")
+ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figS12.png")
+
+figs3 <- image_read("./output/figures/figS12.png")
 figs3
@@
 
-ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS10.pdf")
-
-  p_acf <- image_read("./output/figures/figS10.pdf")
+ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS13.pdf")
+
+  p_acf <- image_read("./output/figures/figS13.pdf")
   p_acf 
@@
 figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS11.png")
-
-figs2 <- image_read("./output/figures/figS11.png")
+ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS14.png")
+
+figs2 <- image_read("./output/figures/figS14.png")
 figs2
@@
 p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
-ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS12.png")
-
+ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS15.png")
+
+p_sim <- image_read("./output/figures/figS15.png")
 p_sim

### 2024-07-14 R/functions.R

@@ -478,7 +478,7 @@ post_summary <- function(x){
    hab_type <- post[,cols_habit]
    
    # Find cols that match names
-   type1 <- c(hab_type[,1], hab_type[,1])  # Tissue Traits Pooled
+   type1 <- c(hab_type[,1], hab_type[,2])  # Tissue Traits Pooled
    type2 <- c(hab_type[,3], hab_type[,4])  # Biochem Traits Pooled
    
    # Now, find the contrast
@@ -494,3 +494,31 @@ post_summary <- function(x){
    return(data_sum)
    
  }
+ 
+ 
+ #' @title get_lifestage
+ #' @description Takes posterior predictions of acute and acclimation effect sizes across habitats and life stages, pools the acute and acclimation effects and then calculates a contrasts between adult and jeuv for effects sizes. Returns a data frame.
+ get_lifestage <- function(post, habitat, lh_b_data){
+   # Find columns that match and subset cols from posterior
+   cols_habit <- as.numeric(rownames(lh_b_data)[lh_b_data$habitat == habitat])
+   
+   lh_type <- post[cols_habit,]
+   
+   # Find cols that match names
+   type1 <- c(lh_type[1,], lh_type[2,])  # J Pooled
+   type2 <- c(lh_type[3,], lh_type[4,])  # A Pooled
+   
+   # Now, find the contrast
+   contrast <-  type2 - type1
+   
+   # Summarise info about contrast
+   data_sum <- data.frame( habitat = habitat,
+                           comparison = paste0("Adult - Juv"),
+                           Est. = mean(contrast),
+                           `95% L CI` = quantile(contrast, 0.025),
+                           `95% U CI` = quantile(contrast, 0.975),
+                           `pmcmc` = p_value(pmcmc(contrast)), check.names = FALSE, row.names = NULL)
+   return(data_sum)
+   
+ }
+ 

### 2024-07-14 ms.qmd
delet spaces

@@
                                                 get_lifestage(pred_lh_vr, habitat = "f", lh_b_data))
+
 ```

### 2024-07-14 ms.qmd
Fix line ending drivig me nuts and rerender

@@
 
-Climate change is expected to result in warmer and more variable thermal
-environments globally. Maintaining variability in physiological rates
-and adjusting them in response to extreme temperatures (plasticity) is
-essential for allowing populations to adapt to climate change. Yet,
-incorporating both plasticity and changes in phenotypic variation when
-predicting the impacts of climate change on populations is often
-ignored. We developed effect size estimates that quantify how
-physiological rate variance changes relative to the mean as temperature
-increases, which we refer to as 'relative variance'. We show by
-meta-analysing \>1900 effects from 226 species that relative variance in
-physiological rates decreases at higher temperatures driven by the lower
-proportional increase in physiological rate variance relative to the
-mean. Freshwater ectotherms are capable of acclimating and have the
-smallest reductions in relative variance. Marine organisms also
-acclimated, but plasticity traded-off with a reduction in relative
-variance in physiological rates at higher temperatures. Relative
-variance reductions were particularly pronounced for terrestrial
-ectotherms, and this coincided with a lack of capacity for acclimation,
-highlighting the vulnerability of terrestrial ectotherms to climate
-change. Our results show that, while there are weak acclimation
-responses in some habitats (marine and freshwater), such responses may
-trade-off with reductions in relative physiological rate variance that
-may have important evolutionary and ecological ramifications that affect
-our understanding of how climate change will impact populations now and
-in the future.
+Climate change is expected to result in warmer and more variable thermal environments globally.
+Maintaining variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
+Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
+We developed effect size estimates that quantify how physiological rate variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
+We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures driven by the lower proportional increase in physiological rate variance relative to the mean.
+Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
+Marine organisms also acclimated, but plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
+Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
+Our results show that, while there are weak acclimation responses in some habitats (marine and freshwater), such responses may trade-off with reductions in relative physiological rate variance that may have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
 
@@
 
-Climate change is expected to result in warmer but also more variable
-thermal environments globally [@Suarez2023; @Easterling2000;
-@Ummenhofer2017]. Greater thermal variability is predicted to result in
-strong selection pressures that lead to genetic adaptation and/or the
-evolution of adaptive phenotypic plasticity -- both of which are
-considered important for population resilience to contemporary
-human-induced climate change [@Seebacher2015-wi; @Merila2014;
-@Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can;
-@cooke2021one]. Without plasticity or adaptation, high extinction rates
-are expected unless organisms can migrate to track suitable habitats
-[@Cahill2012; @Nunney2016].
-
-Reversible phenotypic plasticity, such as physiological acclimation, is
-relatively rapid and can be fine-tuned to environmental conditions
-making it the first ‘line-of-defense’ against environmental change
-[@Dewitt1998; @Scheiner2020]. For example, physiological rates are known
-to speed up as temperature increases because of the thermodynamic
-effects on chemical reaction rates -- so called 'acute' temperature
-responses (@fig-concept). Acute temperature increases that push
-organisms from their thermal optimum can be mitigated by plastically
-adjusting reaction rates in response to chronic temperatures through
-acclimation [@Seebacher2015-wi; @Havird2020-mj]. Physiological
-acclimation is driven by endocrine and epigenetic processes that change
-the underlying physiology to allow organisms to maintain physiological
-performance around a fitness optimum despite changes in the environment
-[@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
-Acclimation therefore alters acute thermal sensitivity to offset the
-potentially negative effects of acute temperature changes (e.g., higher
-energetic demands). Acclimation, however, does not normally result in
-physiological rates returning to their original state (‘complete’
-compensation - *sensu* @huey1999testing), but rather are only partially
-compensated [@huey1999testing; @Havird2020-mj].
-
-Reversible forms of phenotypic plasticity, such as acclimation, are
-expected to evolve in populations when environmental variability is high
-but predictable and the costs of plasticity are low [@Chevin2017;
-@Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010]. Thermal variation
-and predictability are known to differ across habitats (terrestrial,
-marine and freshwater) [@steele2019comparison], and as such, we expect
-organisms within these habitats to vary in their capacity for plastic
-adjustments in physiology. Species occupying terrestrial habitats have
-been shown to exhibit weak acclimation abilities, and so, are likely to
-be particularly vulnerable to climate change given their greater
-probability of experiencing thermal extremes that overwhelm
-physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz;
-@hoffmann2013upper; @morley2019physiological]. In contrast, marine and
-freshwater habitats appear to have greater physiological acclimation
-capacity [e.g., @Seebacher2015-wi; @Pottier2022]. However, the focus of
-research up to now has been primarily on mean physiological responses
-neglecting how variability in physiological rates might also be impacted
+Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000;
+@Ummenhofer2017].
+Greater thermal variability is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
+
+Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998; @Scheiner2020].
+For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
+Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
+Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
+Acclimation therefore alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
+Acclimation, however, does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
+
+Reversible forms of phenotypic plasticity, such as acclimation, are expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect organisms within these habitats to vary in their capacity for plastic adjustments in physiology.
+Species occupying terrestrial habitats have been shown to exhibit weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
+In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
+However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted
 at higher temperatures.
 
-As mean physiological rates increase with temperature there is reason to
-believe that the intrapopulation variability might also be impacted.
-NEED MORE ABOUT WHY VARIANCE IS EXPECTED TO CHANGE!
-
-Changes in variability of traits governing energy demand are expected to
-have important consequences on the flow of energy within and between
-populations, communities, and ecosystems [@hendry2016key;
-@seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-More variable populations, genetically and/or phenotypically, are also 
-predicted to be associated with broader niches, have increased growth rate, decreased vulnerability to
-environmental change and lower extinction risk [@forsman2015rethinking;
+As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted. NEED MORE ABOUT WHY VARIANCE IS EXPECTED TO CHANGE!
+
+Changes in variability of traits governing energy demand are expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+More variable populations, genetically and/or phenotypically, are also  predicted to be associated with broader niches, have increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking;
 @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
-In addition, if phenotypic and genetic variation are correlated and
-traits are linked to fitness, changes in variation may limit responses
-to selection impacting a populations capacity to evolve
-[@Pelletier2012]. Therefore, maintaining intrapopulation variability in
-physiological rates in a warmer world may be important for population
-resilience to climate change.
-
-Here, we use meta-analysis to re-evaluate the degree to which aquatic
-and terrestrial ectotherms are capable of physiological plasticity. We
-then developed new effect sizes to quantify how variance in
-physiological rates change with temperature to ask the following
-questions: 1) How much is variance in physiological rates expected to
-change, if at all, as temperatures rise? 2) Are temperature effects on
-plastic adjustments in physiological rates larger than changes in
-variance across aquatic and terrestrial ectotherms? 3) How does
-acclimation and changes in variance relate to different life-stages and
-types of traits, and does this depend on habitat? 4) Are changes in
-plasticity or variance in physiological rates impacted by past climate
-history? 5) How are means and variances in physiological rates expected
-to change under climate change?
+In addition, if phenotypic and genetic variation are correlated and traits are linked to fitness, changes in variation may limit responses to selection impacting a populations capacity to evolve [@Pelletier2012].
+Therefore, maintaining intrapopulation variability in physiological rates in a warmer world may be important for population resilience to climate change.
+
+Here, we use meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
+We then developed new effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
+2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
+3) How does acclimation and changes in variance relate to different life-stages and types of traits, and does this depend on habitat?
+4) Are changes in plasticity or variance in physiological rates impacted by past climate history?
+5) How are means and variances in physiological rates expected to change under climate change?
 
@@
 
-We compiled literature on ectothermic animals that measured
-physiological rates (e.g., metabolic rate) at two or more temperatures
-after having been acclimated (or acclimatized) at these temperatures. We
-used data from a previous meta-analysis [@Seebacher2015-wi] and updated
-@Seebacher2015-wi's data by extracting data from suitable studies from
-our own searches that followed the same search protocol. We extracted data from an extra
-`r length(unique(new_papers$record_num))` papers (with a total of
-`r dim(new_papers)[1]` effects; a
-`r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`%
-increase in the number of published articles). For full
-details on the search protocol see the *Supplementary Materials*, where
-we also provide a PRISMA flow diagram of our extraction process
-(@fig-prisma).
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures
+after having been acclimated (or acclimatized) at these temperatures.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+For full details on the search protocol see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
 
@@
 
-We extracted means, standard deviations, and sample sizes for
-physiological rates at the two test temperatures. If there were more
-than two test temperatures, we chose only the test temperatures that
-fell within the most likely natural range of temperatures experienced by
-the species in question. We extracted these data from text, tables or
-figures of a given paper. Data were extracted from figures using the R
-package *metaDigitise* [@Pick2019-mg]. We also recorded the phylum,
-class, order, genus and species, and the latitude and longitude from
-where the experimental animals were sourced. For studies that did not
-provide latitude and longitude for the population, we searched for
-similar studies by the same lab group to identify where the population
-was likely to have been sourced. If the experimental animals were
-derived from the wild, we recorded the nearest latitude and longitude of
-the field collection site. If the animals were sourced from a commercial
-supplier, we took the latitude and longitude of the supplier. When it
-was not possible to find latitude and longitude using these methods, we
-looked up the distribution of the species in question and took the
-latitude and longitude of the centroid of the species' distributional
-range.
+We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
+If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
+We extracted these data from text, tables or figures of a given paper.
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
+We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
+If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
+If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
+When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
 
@@
 
-Following @Noble2022-ty we calculated a series of temperature-corrected
-effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as
-well as the variability in physiological rates ($lnVR_{Q_{10}}$ and
-$lnCVR_{Q_{10}}$) (@fig-concept). These effect sizes are similar to the
-traditional temperature coefficient ($Q_{10}$), but with formal
-analytical approximations of their sampling variances. Sampling
-variances for effect sizes allowed us to make use of traditional
-meta-analytic modelling approaches.
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
 
@@
 
-To compare mean physiological rates, we calculated the log $Q_{10}$
-response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
 
@@
 
-Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures
-$T_{1}$ and $T_{2}$, respectively. Log transformation of this ratio
-makes the effect size normally distributed. @eq-lnq10 is essentially a
-temperature corrected equivalent to the log response ratio (lnRR)
-[@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator
-are measured at different temperatures. This allows comparisons of the
-means from two temperature treatments directly regardless of the
-absolute measurement temperatures. The sampling variance for @eq-lnq10
-can be computed as follows [as described in @Noble2022-ty]:
+Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
+Log transformation of this ratio makes the effect size normally distributed.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
+The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
 
@@
 
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$
-and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and
-$T_{2}$, respectively ([@fig-concept]A).
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
 
@@
 
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that
-allow for comparisons of changes in variance between two groups, the log
-variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in
-trait variability between two groups. We refer readers to
-@Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but
-these can easily be extended to their $Q_{10}$ analogues (and associated
-sampling variance) as follows:
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
 
@@
 
-where parameters are defined above. @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate
-variance (@eq-lnq10VR) across a 10°C temperature change along with its
-sampling variance (@eq-slnq10VR). As
-discussed by @Nakagawa2015-fo there is often a strong mean-variance
-relationship. As such, the coefficient of variation is often used because it allows one to
-standardize changes in variance as the mean changes as follows:
+where parameters are defined above.
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it allows one to standardize changes in variance as the mean changes as follows:
 
@@
 
-where $CV$ is the coefficient of variation defined as $SD / R$. We refer
-to $lnCVR_{Q_{10}}$ as relative variance because variance changes are
-relative to the mean.
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
 While we analyse $lnCVR_{Q_{10}}$ it does make certain assumptions about mean-variance relationships, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
@@
 
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from
-samples of organisms measured acutely at two temperatures or after
-having been acclimated these same temperatures ([@fig-concept]A). For
-studies that measure acute and acclimated responses we used the mean,
-standard deviation, and sample size to derive both acute and acclimation
-$lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates. For
-studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$
-acutely we could only calculate acute versions of these effect size
-estimates. For all effect sizes the higher temperature was in the
-numerator and the lower of the two temperatures in the denominator. As
-such, positive effect sizes suggest that the mean (i.e.,
-$lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger
-at the higher of the two temperatures (numerator) when standardized to
-10°C. Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the
-effect of temperature on physiological rates (or changes in
-variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further
-discussion). We test and control for any violations of these assumptions
-in our analysis (see below).
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after
+having been acclimated these same temperatures ([@fig-concept]A).
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes suggest that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in
+variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion). We test and control for any violations of these assumptions in our analysis (see below).
 
@@
 
-We recorded or derived a series of moderator variables from each study
-that are expected to have an impact on our effect size estimates. This
-included the duration of acclimation in days given that acclimation
-responses are expected to depend on how long chronic temperature
-exposure occurs (longer exposure = better acclimation response)
-[@Seebacher2015-wi]. We also recorded if the sample of animals were
-derived from captive or wild stocks, the life-history stage of the
-animals used ("adult" or "juvenile") and the habitat type ("freshwater",
-"marine" or "terrestrial") given that @Seebacher2015-wi show that these
-factors can impact $Q_{10}$ estimates. Physiological rate measures
-varied widely across the studies but could generally be grouped into
-discrete trait categories [@Seebacher2015-wi]. While we explored
-differences across more detailed trait categories (see *Supplemental
-Materials* for details on the types of traits), most traits could be
-categorised into two broad categories that included whole-organism
-measures, which all integrate a diversity of physiological and
-biochemical processes, and biochemical processes (e.g., enzyme reaction
-rates, proton leak). Traits that could not be categorised into these two
-we classified as ‘Other’.
+We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
+This included the duration of acclimation in days given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
+While we explored differences across more detailed trait categories (see *Supplemental
+Materials* for details on the types of traits), most traits could be categorised into two broad categories that included whole-organism
+measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction
+rates, proton leak). Traits that could not be categorised into these two we classified as ‘Other’.
 
@@
 
-We analysed our data using multilevel meta-analytic (MLMA) and
-meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms*
-[vers. `r utils::packageVersion("brms")` @Burkner2017-wg;
+We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2017-wg;
 @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010-fn]. We fit both
-Bayesian and frequentist approaches to ensure that our results were
-consistent, and to create orchard plots more easily [vers. 2.0,
-@Nakagawa2021-ls; @nakagawaorchard]. In addition, Bayesian methods
-better protect against type I errors in the presence of complex sources
-of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz]. In
-all cases, frequentist and Bayesian models resulted in the same
-conclusions. For our Bayesian models, we ran 4 MCMC chains, each with a
-warm-up of 1000 followed by 4000 sampling iterations keeping every 5
-iterations for a minimum of 3200 samples from the posterior
-distribution. We used flat Gaussian priors for 'fixed' effects (i.e.,
-$N(0, 10)$) and a student t-distribution for 'random' effects (i.e.,
-$student_{t}(3, 0, 10)$). We checked that all MCMC chains were mixing
-and had converged (i.e., $R_{hat} = 1$). We compared any competing
-models using Akaike's Information Criteria (AIC) (if frequentist) or
-Wantabe Information Criteria (WAIC) (if Bayesian). We deemed models with
-the lowest IC value to be best supported if there was a $\Delta IC$
-between the competing models of 2 or more. If two models were within 2
-$\Delta IC$ units we went with the most parsimonious model.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
+2.0,
+@Nakagawa2021-ls; @nakagawaorchard].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
+In all cases, frequentist and Bayesian models resulted in the same conclusions.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
+We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WAIC) (if Bayesian).
+We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
+If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.
 
@@
 
-We first fit multi-level meta-analysis (MLMA) models (i.e.,
-intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$,
-that included study, species, trait type, and phylogeny as random
-effects to account for non-independence and identify sources of
-variability. We refer to this model structure as “Model 1” in the
-results. Our MLMA models allowed us to partition the variation in
-$lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while
-accounting for total sampling variance in each. This allowed us to
-calculate the proportion of total heterogeneity [i.e., $I_{total}^2$;
-*sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$
-metrics describing the proportion of variance explained by each random
-effect level [@Nakagawa2012-oc]. We also present 95% prediction
-intervals which describe the expected distribution of effects from
-future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the
-*rotl* package in R (vers. `r utils::packageVersion("rotl")`)
-[@Michonneau2016-if], and plotted using *ggtree* (vers.
-`r utils::packageVersion("ggtree")`) [@Yu2017-wj]. We resolved all
-polytomies in the tree. Any missing taxa were replaced with closely
-related species and branch lengths were computed using Grafen's method
-[using power = 0.7, @Grafen1989-pr]. Models fit using correlation
-matrices computed with different power (p) parameters (from 0.5 – 1.0)
-had nearly identical $AIC_{c}$. As such, we used an intermediate value
-of p = 0.7. We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools*
-(vers. `r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune
-the tree for individual analyses and calculate phylogenetic covariance
-(or correlation) matrices used in meta-analytic models.
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of
+variability.
+We refer to this model structure as “Model 1” in the results.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+This allowed us to
+calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$
+metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc]. We also present 95% prediction
+intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers. `r utils::packageVersion("rotl")`)
+[@Michonneau2016-if], and plotted using *ggtree* (vers. `r utils::packageVersion("ggtree")`) [@Yu2017-wj]. We resolved all
+polytomies in the tree.
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
+As such, we used an intermediate value of p = 0.7.
+We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
 
@@
 
-After quantifying levels of heterogeneity, we fit a series of
-multi-level meta-regression (MLMR) models to test our key questions. In
-all models, we included the same random effects as we used in our MLMA
-models. Acclimation time varied from
-`r range(data_wide$acclim_period, na.rm = TRUE)[1]` to
-`r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD
-= `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$
-`r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial
-ectotherms were acclimated for a much shorter duration (mean $\pm$ SD =
-`r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n =
-`r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD =
-`r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n =
-`r acclim_time[1,4]`) and marine species (mean $\pm$ SD =
-`r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n =
-`r acclim_time[2,4]`). However, rates of acclimation have been shown to
-be faster for many terrestrial groups compared to aquatic organisms
-\[e.g., amphibians and reptiles have faster rates of acclimation than
-fishes; See @Einum2023-lz\]. Nonetheless, to control for these possible
-differences, acclimation time was mean-centered (mean = 0) and included
-in all our models, though it was not a strong predictor of effect size
-variation (*Supplementary Materials*, @fig-accl_time).
-
-In addition to acclimation, all our models corrected for the possibility
-of the log-linearity assumption of our effect sizes being violated
-([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp). We
-predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not
-strictly log-linear than we would see a decrease in average effect size
-for studies applying higher temperature treatments because these
-temperatures are expected to either converge on or cross the thermal
-optima of the performance curve causing reaction rates to decelerate or
-decrease beyond $T_{op}$ [@michaletz2024hotter]. The benefit of such an
-approach means that we could still take advantage of the excellent
-properties of $Q_{10}$ as an effect size while statistically correcting
-for the potential non-linearity that would be expected in the data at
-high treatment temperatures. Given that our data included a wide range
-of species and habitats, we also included a random slope of maximum
-temperature that varied across species because we, *a priori*, expected
-that each species will vary in their thermal performance curve and the
-chosen temperatures experimentally manipulated along the performance
-curve. To improve model interpretation, we also mean-centered the
-maximum temperature and included it in our models.
-
-With acclimation time and maximum temperature as moderators in all our
-models we proceeded to build separate models that tested our core
-questions. All estimates from our models are therefore conditioned on an
-average level of acclimation time (i.e.,
-`r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum
-temperature (i.e., 23$^\circ C$) across the dataset.
-
-We first tested the degree to which the difference in acute and
-acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effects varied by
-habitat type (i.e., terrestrial, freshwater, and marine). Models
-included an interaction between effect type (i.e., acute or acclimation)
-and habitat (referred to as “Model 2”). Reduced mean
-$lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$
-indicates that acclimation to thermal environments results in partial
-compensation of physiological rates (i.e., phenotypic plasticity),
-whereas no differences between $lnRR_{Q_{10_{acute}}}$ and
-$lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of
-physiological plasticity [@Havird2020-mj; @Seebacher2015-wi]. In
-contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to
-$lnVR_{Q_{10_{acute}}}$ would imply that changes in between individual
-variation in physiological rates across 10°C differ depending on whether
-acute or acclimation responses are measured.
-
-Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and
-$lnVR_{Q_{10}}$ differed between whole-organism versus biochemical
-traits across habitats by fitting an model with an interaction between
-type, habitat and trait category (referred to as "Model 3"). We also
-explored how acute and acclimation effects varied across more detailed
-trait categories, and these results can be found in the *Supplementary
-Materials*. Given that residual variance appeared to differ across trait
-categories we fit heteroscedastic residual variance models which were
-better supported in all cases ($\Delta AIC_{c}$; marine = 58, freshwater
-= 120, and terrestrial = 12). We expected that whole-organism traits
-would be more likely to maintain relative variation in physiological
-function and be less likely to acclimate because whole-organism function
-relies on a greater number of biochemical reactions each with different
-thermal sensitivies [@fields2001protein; @angilletta2009thermal].
-
-Third, we tested whether different life-stages were more or less likely
-to acclimate by fitting a model for each habitat type and including an
-interaction between life-stage ('adult' or 'juvenile') and effect type
-(referred to as "Model 4"). We predicted that acclimation responses
-would be more likely early in development compared to later in
-development as this pattern has been shown in previous studies [e.g.,
-@moghadam2019heat], but that this should depend on the habitat type
-given the different constraints faced by different early life stages
-across major habitat types.
-
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$
-and $lnVR_{Q_{10}}$ were predicted by a populations climate variability
-(CV). We only used $lnRR_{Q_{10_{acclimation}}}$ for these models
-because our predictions were specifically focused on the plastic
-adjustments to physiological rates. We used all $lnVR_{Q_{10}}$ data
-because there were no differences between $lnVR_{Q_{10_{acclimation}}}$
-and $lnVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe
-climate would impact acclimation and acute $lnVR_{Q_{10}}$ differently.
-To test how climate variability impacted mean effect size in wild
-populations we fit models that included an interaction between habitat
-type and thermal coefficient of variability (CV) as moderators while
-controlling for acclimation time and maximum temperature used in the
-experiments (referred to as "Model 5"). We also explored how
-environmental predictability, as measured by how correlated successive
-temperatures at a given location were across months, might also explain
-capacity for acclimation. However, such analyses are challenging to
-interpret because the temporal scale that is biologically relevant to
-different organisms will be different making the choice of lag to
-estimate the correlation difficult to apply across taxa. As such, we
-report on these results for a single lag (1 month) in the *Supplementary
-Materials* but note they do not differ from CV analyses.
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions. In
+all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD
+= `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial
+ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n =
+`r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n =
+`r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n =
+`r acclim_time[2,4]`).
+However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz].
+Nonetheless, to control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models, though it was not a strong predictor of effect size variation (*Supplementary Materials*, @fig-accl_time).
+
+In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
+We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we would see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
+To improve model interpretation, we also mean-centered the maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
+All estimates from our models are therefore conditioned on an average level of acclimation time (i.e.,
+`r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23$^\circ C$) across the dataset.
+
+We first tested the degree to which the difference in acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effects varied by
+habitat type (i.e., terrestrial, freshwater, and marine).
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$
+indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
+In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10°C differ depending on whether acute or acclimation responses are measured.
+
+Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
+We also explored how acute and acclimation effects varied across more detailed trait categories, and these results can be found in the *Supplementary Materials*.
+Given that residual variance appeared to differ across trait categories we fit heteroscedastic residual variance models.
+We expected that whole-organism traits would be more likely to maintain relative variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivies [@fields2001protein; @angilletta2009thermal].
+
+Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
+We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by a populations climate variability (CV).
+We only used $lnRR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on the plastic adjustments to physiological rates.
+We used all $lnVR_{Q_{10}}$ data because there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe climate would impact acclimation and acute $lnVR_{Q_{10}}$ differently.
+To test how climate variability impacted mean effect size in wild populations we fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators while controlling for acclimation time and maximum temperature used in the experiments (referred to as "Model 5").
+We also explored how environmental predictability, as measured by how correlated successive temperatures at a given location were across months, might also explain capacity for acclimation.
+However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
+As such, we report on these results for a single lag (1 month) in the *Supplementary Materials* but note they do not differ from CV analyses.
 
@@
 
-To understand the consequences of human-induced climate change on the
-potential to impact relative variance in physiological rates we fit a
-model that included an interaction between acclimation type, habitat
-type, latitude and longitude (referred to as "Model 6"). We assumed that
-any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary
-by habitat type (i.e., an interaction between habitat). We used
-non-linear tensors for latitude and longitude as any response could be
-complicated by local factors (e.g., altitude). Our model included random
-effects of species, trait, phylogeny and study. We predicted the
-expected change in $lnVR_{Q_{10}}$ for each wild population in our
-dataset at the specific populations latitude and longitude. To do this,
-we first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as
-opposed to 10°C as follows:
+To understand the consequences of human-induced climate change on the potential to impact relative variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
+We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
+Our model included random effects of species, trait, phylogeny and study.
+We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
+To do this, we first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C as follows:
 
@@
 
-@eq-lCVRpred turned the expected change across 10°C to 1°C. We then
-multiplied this predicted change by the change in air and sea surface
-temperatures at the locations of each population (and species) that is
-expected under high emissions scenarios in 2080.
+@eq-lCVRpred turned the expected change across 10°C to 1°C.
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
 
@@
 
-We explored the possibility for publication bias graphically using
-funnel plots, and more formally by including the square root of the
-inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression
-models [@Nakagawa2022-gy]. Funnel plot asymmetry may suggest a form of
-publication bias called the 'file-drawer' effect whereby low-powered
-studies are less likely to be published, however, graphical approaches
-do not account for sources of non-independence and high heterogeneity
-which can drive apparent funnel asymmetry [@Nakagawa2022-gy]. As such,
-we included $\sqrt{1/ne}$ as a moderator in a multi-level
-meta-regression model that accounted for all the random (i.e, study,
-species, trait) and fixed effects (acclimation time, type of effect,
-habitat, trait category and the interaction between habitat type and
-trait category) (referred to as "Model 7").
+We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
+Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
+As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
 
@@
 
-### *Performance Curve Simulation*
+### *Simulating among-individual variance in performance curves*
 To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance across temperature we conducted a simple simulation.
@@
 
-The final dataset included a total of
-`r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]`
-freshwater (fishes =
-`r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`,
-molluscs =
-`r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
-amphibians =
-`r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`,
-reptiles =
-`r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`,
-arthropods =
-`r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-and a single crustacean and nematode species),
-`r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]`
-marine (fishes =
-`r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`,
-annelids =
-`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`,
-molluscs =
-`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
-echinoderms =
-`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`,
-reptiles =
-`r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`,
-arthropods =
-`r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-and a single crustacean and cnidarian species), and
-`r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]`
-terrestrial species (annelids =
-`r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`,
-molluscs =
-`r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
-arthropods =
-`r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-reptiles =
-`r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`
-and amphibians =
-`r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`
-along with a single tardigrade species) (@fig-phylo). We had more data
-on acute thermal responses (n =
-`r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`)
-compared to thermal responses after an acclimation period (n =
-`r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`)
-because acute responses were reported for each of the two acclimation
-temperatures (@fig-phylo). The two acute $lnRR_{Q_{10}}$ effect sizes
-([@fig-concept]A) differed significantly from each other ($\beta$ =
-`r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to
-`r quantile(change_acute, 0.975)`, $p_{MCMC}$ =
-`r p_value(pmcmc(change_acute))`) with animals acclimated to high
-temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ =
-`r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to
-`r quantile(hot_acute, 0.975)`, $p_{MCMC}$ =
-`r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`)
-compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`,
-95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to
-`r quantile(cold_acute, 0.975)`, $p_{MCMC}$ =
-`r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`)
-(@fig-Sacute). However, on average they were in the same direction and
-only differed by \~10%. As such, we averaged the two acute
-$lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
-
-Most of the effect size estimates came from measurements of metabolic
-rates (both resting and maximal -- $N_{species}$ =
-`r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`,
-$N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation
-effects together), metabolic enzyme rates ($N_{species}$ =
-`r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`,
-$N_{effects}$ =
-`r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`)
-and whole-organism performance traits (i.e., measures of speed and
-endurance -- $N_{species}$ =
-`r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`,
-$N_{effects}$ =
-`r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
+amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`,
+reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`,
+arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians =
+`r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
+The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to
+`r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
+However, on average they were in the same direction and only differed by ~10%.
+As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
+
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzyme rates ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
 
@@
 
-Effect heterogeneity was high (only `r mean(tot_i2)`% of the variance
-was the result of sampling variability, 95% CI:
-`r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and
-most variance was explained by the specific study and type of trait
-(Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to
-`r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95%
-CI: `r quantile(trait_i2, 0.025)[1]` to
-`r quantile(trait_i2, 0.975)[1]`%). Evolutionary relationships among
-taxa and species ecology (i.e., species random effect) explained little
-variation in acute and acclimation responses (Species: `r mean(spp_i2)`%
-, 95% CI: `r quantile(spp_i2, 0.025)[1]` to
-`r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95%
-CI: `r quantile(phylo_i2, 0.025)[1]` to
-`r quantile(phylo_i2, 0.975)[1]`%). All results are from Model 1 (see
-“Meta-Analysis” above).
-
-Capacity for acclimation depended on the habitat. Ectotherms in marine
-and freshwater environments showed partial compensation of physiological
-rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of
-`r abs(mean(change_f))`% (95% CI:
-`r quantile(change_f, c(0.025, 0.975))[1]` to
-`r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and
-`r abs(mean(change_m))`% (95% CI:
-`r quantile(change_m, c(0.025, 0.975))[1]` to
-`r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In
-contrast, terrestrial ectotherms showed no acclimation (possibly even
-inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in
-$lnRR_{Q_{10_{acclimation}}}$ (95% CI:
-`r quantile(change_t, c(0.025, 0.975))[1]` to
-`r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A). All results are
-from Model 2 (see “Meta-Analysis” above).
-
-Across habitats the extent to which whole-organism versus biochemical
-processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see
-*Supplementary Materials*, @fig-lnrrtrait for more detailed trait analysis). Biochemical
-processes were more effective at acclimating compared to whole-organism
-traits for ectotherms occupying marine habitats ([@fig-btrait]B),
-whereas both whole-organism and biochemical traits acclimated in
-freshwater ectotherms ([@fig-btrait]C). Unsurprisingly, neither
-trait category showed evidence of acclimation in terrestrial ectotherms
-([@fig-btrait]A).
-
-Acclimation capacity did not vary consistently by life-history stage
-with no differences between $lnRR_{Q_{10_{acclimation}}}$ and
-$lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine
-habitats where adults appeared to be able to acclimate to a greater
-extent, although the effect size was small and in the same direction and
-magnitude of juveniles ("Model 4"; [@fig-cvrlh]A-C). When comparing
-between acute and acclimation responses between adults and juveniles
-there were also no differences across habitats (Adult-Juvenile (Acute):
-`r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to
-`r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation):
-`r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]`
-to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(acclim_all_lh)`).
+Effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`%, 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95%
+CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%). All results are from Model 1 (see “Meta-Analysis” above).
+
+Capacity for acclimation depended on the habitat.
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
+All results are from Model 2 (see “Meta-Analysis” above).
+
+Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see
+*Supplementary Materials*, @fig-lnrrtrait for more detailed trait analysis).
+Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms ([@fig-btrait]C).
+Unsurprisingly, neither trait category showed evidence of acclimation in terrestrial ectotherms ([@fig-btrait]A).
+
+Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles ("Model 4"; [@fig-cvrlh]A-C).
+When comparing between acute and acclimation responses between adults and juveniles there were also no differences across habitats (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
 
@@
 In both panels, thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\\Beta$ values are the contrasts between acute and acclimation means within each habitat.
+$\\beta$ values are the contrasts between acute and acclimation means within each habitat.
 $\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
@@
 #| label: fig-btrait
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across marine (A & D), freshwater (B & E) and terrestrial (C & F) habitats.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 #| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for marine (A & D), freshwater (B & E) and terrestrial (C & F) ectotherms.
+#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
-$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$\\beta$ values are the contrasts between acute and acclimation means within each life stage.
 $p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
@@
 
-Variance in physiological rates ($lnVR_{Q_{10}}$) showed an
-increase with increasing temperature across all habitat types ([@fig-2]B) with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI:
-`r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`; "Model 1"; see *Supplementary Materials* @fig-s3).
-However, physiological rate variance increased significantly more in freshwater for acute resposnes (freshwater vs terrestrial: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`), but not for acclimation responses because increases in rates were dampended by acclimation resulting in smaller increases in variance (freshwater vs terrestrial: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
-While marine ectotherms had larger increases in physiological rate variance compared to terrestrial ectoterms these were not signigicant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
+Variance in physiological rates ($lnVR_{Q_{10}}$) showed an increase with increasing temperature across all habitat types ([@fig-2]B) with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI: `r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`; "Model 1"; see *Supplementary Materials* @fig-s3).
+However, physiological rate variance increased significantly more in freshwater for acute responses (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c_a)`, 95% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c_aclim)`, 95% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`).
+While marine ectotherms had larger increases in physiological rate variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
 Marine and freshwater did not differ in how much variance changed at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
-There were no differences between
-$lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ in any habitat ([@fig-2]B). Differences
-in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary
-Materials* analyses with $lnCVR_{Q_{10}}$; @tbl-slopes & @fig-mv).
-
-Overall, there was a `r mean(t_VR_mean_ef)`%
-(95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to
-`r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(t_VR_mean)`) increase in physiological rate variance
-for terrestrial ectotherms and a `r mean(m_VR_mean_ef)`% (95% CI:
-`r quantile(m_VR_mean_ef, 0.025)[1]` to
-`r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(m_VR_mean)`) increase in variation for marine
-ectotherms when temperatures increased by 10$^\circ$C. In contrast,
-freshwater ectotherms exhibited a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]`
-to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ =
-`r pmcmc(f_VR_mean)` increase in variance at high temperatures
-(@fig-2). (results from "Model 2"). The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
+There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ in any habitat ([@fig-2]B).
+Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* analyses with $lnCVR_{Q_{10}}$; @tbl-slopes & @fig-mv).
+
+Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms and a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms when temperatures increased by 10$^\circ$C.
+In contrast, freshwater ectotherms exhibited a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))` increase in variance at high temperatures (@fig-2; results from "Model 2").
+The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
 
@@
 #| fig-align: center
-#| fig-cap: "Expected $lnVR_{Q_{10}}$ when varying individual variation in thermal breadth($\\sigma_{_b_{\\delta}}$ = {0.01, 2}) and  thermal optima ($\\sigma_{_b_{\\sigma}}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{_b_{\\alpha}}$ = 0.01).
-In all simulations, $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{_b_{\\delta}}$ and $\\sigma_{_b_{\\sigma}}$.
-The parameter space that matches the observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is also shown.
+#| fig-cap: "Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying individual variation in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal optima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
+In all simulations, population parameters were $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{\\delta}$ and $\\sigma_{\\sigma}$.
+The parameter space that matches the observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is highlighted.
 Dashed lines indicate the relative differences between the three habitat types when holding one variance parameter constant."
@@
 
-Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`)
-([@fig-btrait]D-F; see also  *Supplementary Materials*, @fig-vrtrait for more detailed trait
-analysis)("Model 3"). Interestingly, variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
-
-Each life-history stage exhibited the same pattern of variance change in each of the
-habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
+Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; see also  *Supplementary Materials*, @fig-vrtrait for more detailed trait analysis)("Model 3").
+Interestingly, variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
+
+Each life-history stage exhibited the same pattern of variance change in each of the habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
 
@@
 
-Thermal variability (i.e., $CV$) experienced by a population in the past
-did not explain acclimation capacity ([@fig-5]A) or changes in
-physiological rate variance ([@fig-5]B) among terrestrial, marine or
-freshwater populations ("Model 5").
+Thermal variability (i.e., $CV$) experienced by a population in the past did not explain acclimation capacity ([@fig-5]A--C) or changes in physiological rate variance ([@fig-5]D--F) among terrestrial, marine or freshwater populations ("Model 5").
 
@@
                        title = c("Freshwater", "Marine", "Terrestrial"), 
-                      condition = c("f", "m", "t"),
+                      condition = c("f", "m"
+                                    , "t"),
                       x = rep(0, 3),
@@
 
-Measurements of acute and acclimation responses from wild ectotherms
-were much less common than from captive populations ($N_{species}$ =
-`r length(unique(all_pred2_vr$spp))`, from
-`r length(unique(all_pred2_vr$uniques))` wild populations). Globally, there
-was a clear bias towards species in the Northern Hemisphere
-([@fig-fig6]A-C). Projected changes in physiological rate variance were
-highly variable across the globe, with some regions showing a decrease
-in physiological rate variance, while others showing an increase
-([@fig-fig6]D). However, out of the `r length(unique(all_pred2_vr$match))`
-populations, variance was predicted to increase to some extent at
-`r (sum(increases$n, na.rm = TRUE) / length(increases$n[complete.cases(increases$n)]))*100`%
-of the locations.
-
-Using the ERA5 climate model, predictions of current global changes in
-physiological rate variance were generally conservative with our model
-explaining ~ 43% of the variation in the observed data ($R^2$ =
-`r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)`
-to `r round(quantile(r2, 0.975)[1], 2)`). Climate change is predicted
-to result in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% reduction in
-relative variance for freshwater systems (95% CI:
-`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]`
-to
-`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%,
-$p_{MCMC}$ = `r pmcmc(mean_perc_habitat_vr$f)`), a
-`r abs(lapply(mean_perc_habitat_vr, mean)$m)`% reduction in relative
-variance for marine systems (95% CI:
-`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]`
-to
-`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%,
-$p_{MCMC}$ = `r pmcmc(mean_perc_habitat_vr$m)`), and a
-`r abs(lapply(mean_perc_habitat_vr, mean)$t)`% reduction in relative
-variance for terrestrial systems (95% CI:
-`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]`
-to
-`r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%,
-$p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5
-climate scenario. All results are taken from "Model 6".
+Measurements of acute and acclimation responses from wild ectotherms were much less common than from captive populations ($N_{species}$ = `r length(unique(all_pred2_vr$spp))`, from `r length(unique(all_pred2_vr$uniques))` wild populations).
+Globally, there was a clear bias towards species in the Northern Hemisphere ([@fig-fig6]A-C).
+Projected changes in physiological rate variance were highly variable across the globe, however, variance was predicted to increase to some extent at `r (sum(increases$n, na.rm = TRUE) / length(increases$n[complete.cases(increases$n)]))*100`% of the locations.
+
+Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 43% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
+Climate change is predicted to result, on average, in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% increase in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$f))`), a `r abs(lapply(mean_perc_habitat_vr, mean)$m)`% increase in marine systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$m))`), and a `r abs(lapply(mean_perc_habitat_vr, mean)$t)`%  increase in terrestrial systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5 climate scenario ([@fig-fig6]D).
+All results are taken from "Model 6".
 
@@
 
-Understanding acclimation capacity and how variation in physiological
-rates change across populations and species is important for predicting
-the ecological and evolutionary consequences of climate change
-[@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating;
-@seebacher2023can; @Sanderson2023; @urban2023and]. Here, acclimation
-responses ($lnRR_{Q_{10}}$) varied across habitats while
-variance ($lnVR_{Q_{10}}$) in physiological rates of ectotherms
-increased, with the extent of this increase varying across habitats. Our results uncover an hitherto unrecognised dynamic
-where the limited benefits of acclimation are offset by increases in trait
-variance that may have impacts on how ectotherm populations across these different habitats
+Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
+Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance ($lnVR_{Q_{10}}$) of ectotherms varied habitats.
+Our results uncover an hitherto unrecognised dynamic where the limited benefits of acclimation are compensated for by increases in trait variance that may have impacts on how ectotherm populations across these different habitats
 will be able to adapt to increased temperatures.
@@
 
-We show that acclimation of physiological rates and changes in their
-variance differ across habitats. Our findings confirm previous results
-that quantify the different capacity of terrestrial, marine and
-freshwater ectotherms to acclimate [@Seebacher2015-wi;
-@Gunderson2015-hz; @morley2019physiological]. Our analysis generally
-supports that of @Seebacher2015-wi, @Gunderson2015-hz and
-@morley2019physiological that all show a general inability of
-terrestrial ectotherms to physiologically acclimate. The change in
-acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for
-freshwater organisms (~17%), but higher in marine ectotherms [decrease
-of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial
-ectotherms [increase of ~6% compared to an ~8% decrease in
-@Seebacher2015-wi], possibly due to the use of newly derived
-$Q_{10}$ effect sizes that allow us to control for sampling variance.
-Greater capacity for acclimation in aquatic organisms may be the result
-of fewer opportunities for behavioural thermoregulation in aquatic
-environments making physiological remodeling important for maintaining
-homeostasis [@Gunderson2015-hz; @morley2019physiological]. Importantly, even though marine and freshwater ectotherms were
-capable of partial acclimation on average, the effect size was small (amounting to $Q_{10}$ dropping
-from ~1.8 to 1.6), suggesting acclimation will still provide limited opportunity for aquatic ectotherms when coping with higher temperatures.
-
-Interestingly, we show that biochemical traits (i.e., enzymes) were more
-likely to acclimate compared to whole-organisms traits as predicted, but
-only for marine ectotherms. In contrast, both whole-organism and
-biochemical traits were equally likely to acclimate in freshwater
-ectotherms. Unsurprisingly, we observed no distinction between traits in
-terrestrial ectotherms.
+We show that the capacity for acclimation of physiological rates differs across habitats.
+Our findings confirm previous results that quantify the different capacity of terrestrial, marine and freshwater ectotherms to acclimate [@Seebacher2015-wi;
+@Gunderson2015-hz; @morley2019physiological]. Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and
+@morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
+The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi], possibly due to the use of newly derived $Q_{10}$ effect sizes that allow us to control for sampling variance.
+Greater capacity for acclimation in aquatic organisms may be the result of fewer opportunities for behavioural thermoregulation in aquatic environments making physiological remodeling important for maintaining homeostasis [@Gunderson2015-hz; @morley2019physiological].
+Importantly, even though marine and freshwater ectotherms were capable of partial acclimation, on average, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6), suggesting acclimation will provide limited scope for aquatic ectotherms to adjust their physiology to higher temperatures.
+
+Interestingly, we show that biochemical traits (i.e., enzymes) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
+In contrast, both whole-organism and biochemical traits were equally likely to acclimate in freshwater ectotherms.
+Unsurprisingly, we observed no distinction between traits in terrestrial ectotherms.
 
@@
 In contrast to acclimation capacity, variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation.
-Mechanistically, it is unclear what is contributing to the increased variation in physiological rates at higher temperatures, but it could be the result of increased among-individual variability in how biochemical, cellular and physiologcial processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins;
-@fields2001protein]. Higher temperatures increase membrane fluidity affecting electrochemical gradients and impact protein structure and function [@somero1995proteins;
-@fields2001protein; @tattersall2012coping].
-Such challenges (among others) may increase existing variation among indiviudals within a population.
-Some support for these mechanisms exist given that variation in biochemical traits did show larger increases in variability at high teperatures compared to whole-organism traits, although this was only significant for marine organisms.
-Increases in variance are probably dependent on the type of biochemical reaction being measured, and so, the differences across habitats could be attributable to the types of traits being measured.
-
-Importantly, increased variance in physiological rates was not equal among ectotherms accupying terrestrial, marine and freshwater habitats. For example, increases in variance were particularly
-pronounced in freshwater ectotherms (~60% increase over 10 degrees Celsius) compared to terrestrial ectotherms (~36% increase over 10 degrees Celcius).
-The changes in variability we observed across habiats can be explained by differences in among individual variation in thermal breath and optima of individual performance curves between habitats.
-Consistent differences in thermal performance curves across these major habitat types have never been formally compared, probably because of the challeges in measuring full performance curves across taxa.
-However, a multitude of studies support the general notion that species occupying different habiats (terrestrial vs aquatic) should differ.
+Mechanistically, it is unclear what is contributing to the increased variation in physiological rates at higher temperatures, but it could be the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein].
+Higher temperatures increase membrane fluidity affecting electrochemical gradients and impacting protein structure and function [@somero1995proteins; @fields2001protein; @tattersall2012coping].
+Such challenges (among others) may expose among-individual variation within a population.
+Some support for these mechanisms exist given that variation in biochemical traits did show larger increases in variability at high temperatures compared to whole-organism traits, although this was only significant for marine organisms.
+Increases in variance are probably dependent on the type of biochemical reaction being measured, and so, the differences across habitats could be attributable to the types of traits typically measured on these organisms.
+
+Importantly, increased variance in physiological rates was not equal among ectotherms occupying terrestrial, marine and freshwater habitats.
+Increases in variance were particularly pronounced in freshwater ectotherms (~60% increase over 10 degrees Celsius) compared to terrestrial ectotherms (~36% increase over 10 degrees Celsius).
+The changes in variability we observed across habitats can be explained by differences in among individual variation in thermal breath and optima of individual performance curves between habitats.
+Consistent differences in thermal performance curves across these major habitat types have never been formally compared, probably because of the challenges in measuring full performance curves across taxa.
+However, a multitude of studies support the general notion that species occupying different habitats (terrestrial vs aquatic) should differ.
 @p
@@
 Our results further highlight the vulnerability of terrestrial
-ectotherms to climate change. Assuming changes in
-variation in physiological rates are underpinned by genetic variation,
-and there is a genetic correlation with fitness, such reductions in
-physiological variance could limit adaptation in terrestrial habitats more than aquatic habiats in the 
-future [@urban2023and].
-For example, under climate we expect an increase of only ~13% in terrestrial habitats whereas for freshwater habiats we expect variation in physiological rates to increase by 29%.
+ectotherms to climate change. Assuming changes in variation in physiological rates are underpinned by genetic variation,
+and there is a genetic correlation with fitness, such reductions in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and].
+For example, under climate we expect an increase of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by 29%.
 
 ------
-Only in freshwater ectotherms did acclimation in
-physiological rates coincide with no change in relative variation.
-Such a mechanism may also help explain the
-differences in relative variance across habitat types. For example,
-terrestrial ectotherms may rely on more specialised enzymatic variants
-that operate over a more limited temperature range individually but
-together allow for organisms to function over a wider thermal range
-necessary to operate in more variable thermal environments
-[@angilletta2009thermal].
-
- We also expected relative variance to differ
-between whole-organism and biochemical traits, but we did not find
-strong support for this except for in freshwater ectotherms where
-biochemical traits were more likely to maintain or increase relative
-variance compared with whole-organisms traits. Acclimation responses in
-marine and freshwater organisms may buffer / maintain variance in
-physiological rates at higher temperatures due to the expression of
-alternative enzyme forms or intracellular stabalising compounds/solutes
-that impact enzyme function [@fields2001protein].
-
- Of course, considering how behavioural
-modifications buffer organisms from high temperatures is also needed.
-Terrestrial species likely have greater opportunity for behavioural
-microhabitat selection in thermally heterogeneous environments which is
-expected to decrease the impacts of climate change [@huey2012predicting;
-@sunday2014thermal]. Importantly, while we seen a reduction in relative
-variation, absolute variation in physiological rates did increase with
-temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial
-and marine habitats compared to freshwater -- supporting the general
-notion that capacity for adaptation may still be limited in terrestrial
-and marine habitats. As of yet, it is unclear whether a focus on
-relative or absolute variance should be prioritized. Future theoretical
-models are needed to better understand the ecological and evolutionary
-consequences of changes in both mean and variance.
+Only in freshwater ectotherms did acclimation in physiological rates coincide with no change in relative variation.
+Such a mechanism may also help explain the differences in relative variance across habitat types.
+For example, terrestrial ectotherms may rely on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range necessary to operate in more variable thermal environments [@angilletta2009thermal].
+
+ We also expected relative variance to differ between whole-organism and biochemical traits, but we did not find strong support for this except for in freshwater ectotherms where biochemical traits were more likely to maintain or increase relative variance compared with whole-organisms traits.
+Acclimation responses in marine and freshwater organisms may buffer / maintain variance in physiological rates at higher temperatures due to the expression of alternative enzyme forms or intracellular stabalising compounds/solutes that impact enzyme function [@fields2001protein].
+
+ Of course, considering how behavioural modifications buffer organisms from high temperatures is also needed.
+Terrestrial species likely have greater opportunity for behavioural microhabitat selection in thermally heterogeneous environments which is expected to decrease the impacts of climate change [@huey2012predicting; @sunday2014thermal].
+Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited in terrestrial and marine habitats.
+As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized.
+Future theoretical models are needed to better understand the ecological and evolutionary consequences of changes in both mean and variance.
 
@@
 
-Acclimation capacities are expected to differ between life-stages
-because of distinct of patterns of dispersal, habitat use and behaviour
-that force earlier life stages to cope with more variable environmental
-conditions which can also lead to developmental constraints on how
-physiological systems respond later in life [@martin2015age;
-@stearns1976life; @angilletta2009thermal; @noble2018developmental;
-@o2019developmental; @Pottier2022; @sinclair2016can]. In addition, plastic responses are
-also expected to be costly [@angilletta2009thermal; @Dewitt1998], and
-such costs can be magnified in late life reducing the capacity for
-plasticity [e.g., @rossi2019ageing]. These processes can also result in
-changes to intrapopulation variation in physiological rates at higher
-temperatures but the direction of change between early and adult life
-stages is likely to depend on the costs of adjusting physiological
-processes, energy reserves at different life stages, and the extent to
-which early life experiences constrain plasticity.
-
-Despite these expectations, more broadly, we show little difference
-between early and late life acclimation capacities and little change in
-the relative variance in physiological rates across habitats. This may
-not be too surprising given that such responses are likely context or
-trait dependent [@carter2020life; @moghadam2019heat]. The lack of
-differences we observed may also be due to the fact that both juvenile
-and adult animals occupy similar thermal niches, disperse to a similar
-extent and exhibit comparable thermoregulatory behaviors making
-physiological responses to temperature similar. It is possible that
-temperatures experienced earlier in development (e.g., egg or larval
-stages) exhibit greater capacity for acclimation because of limited
-dispersal capabilities and very different habitats. Some empirical
-evidence supports this in insects. For example, @moghadam2019heat showed
-that larval *Drosophila* were more plastic in their heat hardening
-responses compared to adults. A focus on collecting more detailed
-information on the differences in behaviour, dispersal and thermal
-environments experienced across different life stages is likely to
-provide a more complete picture on when plasticity differs across life
-stages. To date, however, there are few studies that have focused on how
-variability in responses change. We would also encourage more empirical
-focus on this questions given the potential ecological and evolutionary
-implications.
+Acclimation capacities are expected to differ between life-stages because of distinct of patterns of dispersal, habitat use and behaviour that force earlier life stages to cope with more variable environmental conditions which can also lead to developmental constraints on how physiological systems respond later in life [@martin2015age; @stearns1976life; @angilletta2009thermal; @noble2018developmental; @o2019developmental; @Pottier2022; @sinclair2016can].
+In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], and such costs can be magnified in late life reducing the capacity for plasticity [e.g., @rossi2019ageing].
+These processes can also result in changes to intrapopulation variation in physiological rates at higher temperatures but the direction of change between early and adult life stages is likely to depend on the costs of adjusting physiological processes, energy reserves at different life stages, and the extent to which early life experiences constrain plasticity.
+
+Despite these expectations, more broadly, we show little difference between early and late life acclimation capacities and little change in the variance in physiological rates across habitats.
+This may not be too surprising given that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
+The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar thermal niches, disperse to a similar extent and exhibit comparable thermoregulatory behaviors making physiological responses to temperature similar.
+It is possible that temperatures experienced earlier in development (e.g., egg or larval stages) exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
+Some empirical evidence supports this in insects.
+For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
+A focus on collecting more detailed information on behaviour, dispersal and thermal environments experienced by different life stages is likely to provide a more complete picture on when plasticity differs.
+To date, however, there are few studies that have focused on how variability in responses change.
+We would also encourage more empirical focus on this questions given the potential ecological and evolutionary implications.
 
@@
 
-Theoretical models predict that plasticity should evolve in populations
-experiencing greater environmental variability (spatial or temporal),
-particularly when oscillations are predictable over time to make
-environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010;
-@Nunney2016; @Murren2015; @hendry2016key; @Reed2010]. Higher spatial and
-temporal heterogeneity in terrestrial habitats [@steele2019comparison]
-might suggest that plasticity is more likely to evolve in terrestrial
-environments. However, if thermal variability is too high and
-unpredictable, the rates of acclimation slow, and there are costs
-associated with re-modelling physiological processes [which seem likely,
-@angilletta2009thermal] then we would instead expect canalised responses
-[@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences;
-@Leung2020; @rescan2022experimental; @leung2023phenotypic]. The lack of
-acclimation in terrestrial ectotherms we observed is consistent with the
-latter hypothesis, and is supported by other meta-analyses of heat
-tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there
-are costs to being plastic or that the environmental signals are
-insufficient to trigger endocrine and epigenetic mechanisms that lead to
-plasticity when environments are not predictable [@hendry2016key;
-@Leung2020].
-
-Whether a populations capacity for physiological plasticity and the
-thermal variability (or predictability) it experiences are related has
-received more mixed results. We show no relationship between acclimation
-capacity and thermal variability in marine, freshwater and terrestrial
-habitats. Our results are consistent with @Gunderson2015-hz who show no
-relationship between plasticity in heat tolerance and latitude or
-thermal seasonality. However, other analyses on heat tolerance limits
-have found relationships between latitude (a proxy for seasonality)
-[@morley2019physiological] or measures of thermal variability
-[@verberk2024heat]. @Seebacher2015-wi also found evidence that
-acclimation capacity is related to a populations thermal variability,
-however, relationships depended on the habitat and traits in question.
-Discrepancies across studies could be related to the taxa included in
-analyses [e.g., @morley2019physiological], different traits or possibly
-the fact that different climate projections/models are being used to
-quantify thermal variability. Modelling realistic microenvironments
-across such diverse taxa is also challenging because it is unclear what
-the most appropriate spatial and temporal scale might be that is of
-evolutionary relevance. As such, it is also likely that historical
-temperature time series' are not representative of the selective
-environment a population has experienced making relationships between
-capacity for acclimation and temperature variability (or predictability)
-difficult to pin down.
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity is more likely to evolve in terrestrial environments.
+However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
+The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@hendry2016key; @Leung2020].
+
+Whether a populations capacity for physiological plasticity and the thermal variability (or predictability) it experiences are related has received more mixed results.
+We show no relationship between acclimation capacity and thermal variability in marine, freshwater and terrestrial habitats.
+Our results are consistent with @Gunderson2015-hz who show no relationship between plasticity in heat tolerance and latitude or thermal seasonality.
+However, other analyses on heat tolerance limits have found relationships between latitude (a proxy for seasonality) [@morley2019physiological] or even direct measures of thermal variability [@verberk2024heat].
+@Seebacher2015-wi also found evidence that acclimation capacity was related to a populations thermal variability, however, relationships depended on the habitat and traits in question.
+Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological], different traits or possibly the fact that different climate projections/models are being used to quantify thermal variability.
+Modelling realistic microenvironments across such diverse taxa is also challenging because it is unclear what the most appropriate spatial and temporal scale might be that is of evolutionary relevance.
+Historical temperature time series' may not be representative of the selective environment a population has experienced making relationships between capacity for acclimation and temperature variability (or predictability) difficult to pin down.
 
@@
 
-Enhanced knowledge of how variation in physiological rates vary across
-populations and species, and the degree to which they can be adjusted in
-response to the environment, may lead to more informed predictions about
-the ecological and evolutionary dynamics of natural populations
-[@forsman2015rethinking; @seebacher2023can; @cooke2021one;
-@Sanderson2023]. While we show general patterns across taxa and habitats
-it is important to recognise that this does not mean such patterns apply
-to all populations. Substantial variation in acclimation responses and
-changes in variance exist among populations and traits, as evidenced by
-wide prediction intervals and substantial study- and trait-level
-variance estimates. Nonetheless, quantitative measures on the changes in variance in physiological rates could be better
-incorporated into physiological and ecological models to provide more
-nuanced, and possibly more realistic, predictions about the impacts of
-climate change on natural populations. While we do not yet understand
-the relative contribution of environmental and genetic factors to
-variance changes, models could better decouple how different levels of
-heritability and total variance impact evolutionary and ecological
-predictions. Our meta-analysis now provides the opportunity to
-parameterise such models, and ensure they are better aligned with
-empirical findings.
-
-It is clear that many fascinating questions remain
-unanswered that will require greater focus on the consequences of
-changes in variance (rather than just the mean). Particularly
-interesting questions include: How do differences in physiological rate
+Enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
+While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
+Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial study- and trait-level variance estimates.
+Nonetheless, quantitative measures on the changes in variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
+While we do not yet understand the relative contribution of environmental and genetic factors to variance changes, models could better decouple how different levels of heritability and total variance impact evolutionary and ecological predictions.
+Our meta-analysis now provides the opportunity to parameterise such models, and ensure they are better aligned with empirical findings.
+
+It is clear that many fascinating questions remain unanswered that will require greater focus on the consequences of
+changes in variance (rather than just the mean). Particularly interesting questions include: How do differences in physiological rate
 variance change energy flow across trophic levels within communities?
-What are the biochemical, cellular, and physiological mechanisms that
-underlie differences in physiological rate variance across habitats? Are
-changes in variance in one trait associated with changes in other
-traits, or do some traits increase while others decrease? Are changes in
-physiological rate variance correlated with changes in genetic
-variation? Answers to these questions will require integrative
-approaches that combine empirical and theoretical work across multiple
-levels of biological organisation but will likely provide useful
-advances in understanding the full consequences that climate change will
-have on ectotherms across major ecosystems globally.
+What are the biochemical, cellular, and physiological mechanisms that underlie differences in physiological rate variance across habitats?
+Are changes in variance in one trait associated with changes in other traits, or do some traits increase while others decrease?
+Are changes in physiological rate variance correlated with changes in genetic variation?
+Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across major ecosystems globally.
 
@@
 
-We would like to thank Malgorzata Lagisz for helping sort out the
-phylogeny used in our analysis. We are also grateful to three anonymous
-reviewers who all provided highly constructive feedback that greatly
-improved the manuscript.
+We would like to thank Malgorzata Lagisz for helping sort out the phylogeny used in our analysis and Enrico Rezende for discussions around the implementation of thermal performance curves.
+We are also grateful to three anonymous reviewers who all provided highly constructive feedback that greatly improved the manuscript.
 
@@
 
-DWAN is supported by an Australian Research Council (ARC) Future
-Fellowship (FT220100276) and ARC Discovery Project (DP210101152). SN is
-supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
+DWAN is supported by an Australian Research Council (ARC) Future Fellowship (FT220100276) and ARC Discovery Project (DP210101152).
+SN is supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
 
@@
 
-All data and code used to reproduce analyses can be found on GitHub at:
-https://github.com/daniel1noble/Q10_meta_analysis and is deposited in
-Zenodo (https://doi.org/10.5281/zenodo.11123600).
+All data and code used to reproduce analyses can be found on GitHub at: https://github.com/daniel1noble/Q10_meta_analysis and is deposited in Zenodo (https://doi.org/10.5281/zenodo.11123600).
 
@@
 
-Conceptualization: DWAN, FK, FS, SN; Methodology: DWAN, AB, FK, FS, SN;
-Investigation: DWAN, FK, FS, SN; Visualization: DWAN; Supervision: DWAN,
-SN, FS; Writing—original draft: DWAN; Writing—review & editing: DWAN,
-AB, FK, FS, SN.
+Conceptualization: DWAN, FK, FS, SN; Methodology: DWAN, AB, FK, FS, SN; Investigation: DWAN, FK, FS, SN; Visualization: DWAN; Supervision: DWAN, SN, FS; Writing—original draft: DWAN; Writing—review & editing: DWAN, AB, FK, FS, SN.
 
@@
 
-#### *Literature Search Protocol and PRISMA flow diagram*
-
-We performed a literature search using the Web of Science database for
-articles or proceedings papers published in English from 2013 to 2017
-(the date after [@Seebacher2015-wi] searches were conducted) using the
-following topic search string: *"(acclimat* AND (therm\* OR temp*) NOT
-(plant* OR tree\* OR forest\* OR fung\* OR mammal\* OR marsup\* OR
-bird\* OR human OR exercis\* OR train\* OR hypoxi*))"*. We further
-limited to the following research areas: Anatomy Morphology;
-Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism;
-Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology;
-Respiratory System, Reproductive Biology, Zoology.
-
-Our search resulted in 1,321 papers for screening in Rayyan
-[@Ouzzani2016-ge]. We also cross-checked papers we found in our searches
-with a recent paper by @Havird2020-mj, which also updates the dataset of
-@Seebacher2015-wi's. We included any papers that were missed between our
-searches and those of @Havird2020-mj. @Havird2020-mj added 7 new studies
-(mainly because they were focused on metabolic rates), and our searches
-differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
-Given the physiological traits we included were broader than
-@Havird2020-mj, we had a substantial increase in additional papers that
-we added to @Seebacher2015-wi's dataset. More specifically, in addition
-to the `r length(unique(old_papers$record_num))` papers we included from
-the @Seebacher2015-wi dataset, we extracted data from an extra
-`r length(unique(new_papers$record_num))` papers (with a total of
-`r dim(new_papers)[1]` effects; a
-`r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`%
-increase in the number of published articles). Note that
-@Seebacher2015-wi included a total of 205 publications, however, not all
-these contained the necessary statistics we needed to derive effect
-sizes and associated sampling variances (see below). While we may have
-missed papers, our goal was to obtain a large representative (and
-unbiased) sample of acclimation research rather than a comprehensive
-dataset. As such, our database represents the most up-to-date dataset
-used since @Seebacher2015-wi to answer questions on physiological rates
-across ectotherms.
-
-We split the screening of titles and abstracts for the 1,321 papers
-found in our search among DWAN, FK, FS, and SN evenly. To ensure
-consistency among authors in title and abstract inclusion, relevant
-authors went through a randomly selected set of papers together before
-the formal screening to calibrate selection of papers based on our
-inclusion criteria (see below). In cases of disagreement regarding
-inclusion, we conservatively included the paper for full text screening
-and discussed uncertain papers among authors to come to a decision.
-After title and abstract screening, there was a total of 149 papers for
-full text screening. Papers were included only if they: 1) measured a
-physiological rate acutely at two temperatures on a sample of animals
-chronically exposed to the same two temperatures for at least 1 week;
-and 2) where physiological rates measured were burst and sustained
-locomotion, metabolic rates (standard, resting, routine and maximal),
-heart rates, and/or enzyme activities. Importantly, as in
-@Seebacher2015-wi, we only included studies that manipulated
-temperatures within normal thermal ranges for the species.
+#### **Literature Search Protocol and PRISMA flow diagram**
+
+We performed a literature search using the Web of Science database for articles or proceedings papers published in English from 2013 to 2017 (the date after [@Seebacher2015-wi] searches were conducted) using the following topic search string: *"(acclimat* AND (therm\* OR temp*) NOT (plant* OR tree\* OR forest\* OR fung\* OR mammal\* OR marsup\* OR bird\* OR human OR exercis\* OR train\* OR hypoxi*))"*.
+We further limited to the following research areas: Anatomy Morphology; Biodiversity Conservation; Biology; Ecology; Endocrinology Metabolism; Entomology; Evolutionary Biology; Marine Freshwater Biology; Physiology; Respiratory System, Reproductive Biology, Zoology.
+
+Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge]. We also cross-checked papers we found in our searches
+with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
+We included any papers that were missed between our searches and those of @Havird2020-mj.
+@Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].
+Given the physiological traits we included were broader than @Havird2020-mj, we had a substantial increase in additional papers that we added to @Seebacher2015-wi's dataset.
+More specifically, in addition to the `r length(unique(old_papers$record_num))` papers we included from the @Seebacher2015-wi dataset, we extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
+While we may have
+missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive
+dataset. As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+
+We split the screening of titles and abstracts for the 1,321 papers found in our search among DWAN, FK, FS, and SN evenly.
+To ensure consistency among authors in title and abstract inclusion, relevant authors went through a randomly selected set of papers together before the formal screening to calibrate selection of papers based on our inclusion criteria (see below).
+In cases of disagreement regarding inclusion, we conservatively included the paper for full text screening and discussed uncertain papers among authors to come to a decision.
+After title and abstract screening, there was a total of 149 papers for full text screening.
+Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
 
@@
 
-#### *Further discussions on the assumptions of* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
-
-$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$
-more generally, all assume that the effect of temperature on
+#### **Further discussions on the assumptions of $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates**
+
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on
 physiological rates (or changes in relative variance) is log-linear.
-While this is likely in our data given that we restricted our analysis
-of $Q_{10}$ to standard operating temperatures for a given species, it
-may not always be satisfied given the diversity of species in our
-dataset. $Q_{10}$ [@van1884etudes] has been used exstensively in the
-physiological literature to successfully address a multitude of
-questions [e.g., @Havird2020-mj; @Seebacher2015-wi]. However, there is a
-preference for using a Boltzmann – Arrhenius (BA) relationship (or its
-more recent extension, the Sharpe-Schoolfield model [@molnar2017thermal;
-@michaletz2024hotter]) to model thermal effects on physiological rates
-[@gillooly2001effects; @michaletz2024hotter]. While debate still exists
-over the utility of $Q_{10}$ when modelling temperature-dependence it is
-important to recognise that both BA and $Q_{10}$ can exhibit
-curvilinearity as temperatures increase (as discussed in
-[@michaletz2024hotter]). @white2012information also showed that the BA
-model may not always perform better. For example, in eukaryotes,
-modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better
-fit to metabolic rate data than the BA relationship
-[@white2012information]. Given that studies included in our analysis
-never measured full performance curves at acute and acclimation
-temperatures it was not possible for us to compare different models of
-thermal dependence. Nonetheless, $Q_{10}$-based effect sizes remain the
-most practical effect-size for comparing thermal dependence when using
-existing empircial data, with the benefit that these effects having
-convenient properties that make them suitable for meta-analysis.
-Nonetheless, we control for possible violations of the log-linearity
-assumption in our analyses.
-
-#### *Exploring the impact of maximum treatment temperature on* $lnRR_{Q_{10}}$
+While this is likely in our data given that we restricted our analysis of $Q_{10}$ to standard operating temperatures for a given species, it may not always be satisfied given the diversity of species in our dataset.
+$Q_{10}$ [@van1884etudes] has been used extensively in the physiological literature to successfully address a multitude of questions [e.g., @Havird2020-mj; @Seebacher2015-wi].
+However, there is a preference for using a Boltzmann – Arrhenius (BA) relationship (or its extension, the Sharpe-Schoolfield model [@molnar2017thermal; @michaletz2024hotter]) to model thermal effects on physiological rates [@gillooly2001effects; @michaletz2024hotter].
+While debate still exists over the utility of $Q_{10}$ when modelling temperature-dependence it is important to recognise that both BA and $Q_{10}$ can exhibit curvilinearity as temperatures increase (as discussed in [@michaletz2024hotter]).
+@white2012information also showed that the BA model may not always perform better.
+For example, in eukaryotes, modelling thermal dependence using $Q_{10}$ provided a 5.8-fold better fit to metabolic rate data than the BA relationship [@white2012information].
+Given that studies included in our analysis never measured full performance curves at acute and acclimation temperatures it was not possible for us to compare different models of thermal dependence.
+Nonetheless, $Q_{10}$-based effect sizes remain the most practical effect-size for comparing thermal dependence when using existing empircial data, with the benefit that these effects having convenient properties that make them suitable for meta-analysis.
+Nonetheless, we control for possible violations of the log-linearity assumption in our analyses.
+
+#### **Exploring the impact of maximum treatment temperature on $lnRR_{Q_{10}}$**
 
@@
 
-#### *How acclimation time is related to* $lnRR_{Q_{10}}$
+#### **How acclimation time is related to $lnRR_{Q_{10}}$**
 
@@
 Acclimation time is centered around the mean acclimation time (37.5 days) in the data.
-Not all studies reported acclimation time hence the total number of effects, k, was 1767."
+Not all studies reported acclimation time hence the total number of effects, *k*, was 1767."
   col <- c("#0871B9", "#F3B40D", "#1BB908")
@@
 
-#### *Comparing cool and warm acclimated acute responses*
+#### **Comparing cool and warm acclimated acute responses**
 
@@
 Note that points in each category show the full distribution of data irrespective of habitat for simplicity.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+*k* = total number of effect size estimates while the numbers in brackets indicate the number of species.
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 
-### *Climate data*
-
-To understand how climate is related to a species’ physiological
-acclimation abilities and changes in relative variance we used the
-coordinates reported by each study to extract temperature data from
-terrestrial and aquatic environments. It was unclear whether climate at
-the locations of captive reared organisms would be representative of a
-population's climate history - particularly for species reared under
-captive condition for many generations. Given that we were interested in
-understanding climate driven effects on acclimation capacity we only
-used studies on wild populations for climate analyses.
-
-Monthly average temperature data were extracted from the ERA5 climate
-model, available from the Copernicus climate data store
-[@Hersbach2020-hx]. For each population and species in the dataset we
-extracted a 72-year period (1950-2022) of either surface air temperature
-(0.01° resolution) for both terrestrial and freshwater taxa, or sea
-surface temperature for the marine taxa (at 0.25° resolution) using the
-*ncdf4* R package [vers. `r utils::packageVersion("ncdf4")`,
-@Pierce2021-lc]. We chose surface temperature because we believed that
-it was more likely to reflect the micro-thermal environment experienced
-by terrestrial and freshwater ectotherms at those locations.
-
-Using the thermal time-series data for each location we calculated
-metrics of thermal variability across months and years as well as
-estimates of thermal predictability (i.e., autocorrelation). To estimate
-thermal variability, we calculated the coefficient of variation
-($\frac{SD}{M}$, where SD = standard deviation in temperature and M =
-the mean temperature for each year). We also estimated thermal
-predictability, by calculating the auto-regressive time lag across
-months (i.e., a measure of how correlated temperatures were between
-months), however, identifying biologically relevant lags for such
-diverse taxa is challenging. As such, we present a coarse analysis using
-this metric of thermal predictability in the *Supplemental Materials* below.
-
-Lastly, to illustrate the effects that climate warming could have on
-physiological rate variance we also extracted climate projections and
-calculated thermal variability into the future. We used the CanESM2
-climate model (2005-2100) [vers. 1.2.0; @koen_hufkens_2019_2647541]
-under a high emissions scenario (RCP8.5).
-
-#### *Mean-variance relationships to understand patterns in* $lnCVR_{Q_{10}}$
+#### **Climate data**
+
+To understand how climate is related to a species’ physiological acclimation abilities and changes in variance we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
+It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
+Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
+
+Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01° resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25° resolution) using the *ncdf4* R package [vers.
+`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
+We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+
+Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as
+estimates of thermal predictability (i.e., autocorrelation).
+To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
+We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, identifying biologically relevant lags for such diverse taxa is challenging.
+As such, we present a coarse analysis using this metric of thermal predictability in the *Supplemental Materials* below.
+
+Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections into the future.
+We used the CanESM2 climate model (2005-2100) [vers.
+1.2.0; @koen_hufkens_2019_2647541] under a high emissions scenario (RCP8.5).
+
+#### **Mean-variance relationships to understand patterns in $lnCVR_{Q_{10}}$**
 
@@
 
- # Model mean variance relationships to estimate the relationship. Two additonal models to address reviewer comments about what exactly is changing in the effect size
+ # Model mean variance relationships to estimate the relationship. Two additional models to address reviewer comments about what exactly is changing in the effect size
 rerun = FALSE
@@
 
-We explored mean-variance relationships for the acute and acclimation
-responses across all traits and habitats. We estimated the scaling
-relationship between log standard deviation in physiological rates
-[log(SD)] and log mean physiological rates [log(mean)], accounting
-for non-independence resulting from effects coming from the same
-species, study and traits (i.e., random effects of species, study and
-trait) as done in our main analyses. We also included an interaction
-between log(mean) and habitat type to better understand how the scaling
-relationship between log(SD) and log(mean) varies across habitats.
-
-Overall, we found that the relationship between log(mean) and log(SD) of
-the acute and acclimation responses was generally linear, suggesting
-that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv). Overall, the
-scaling relationship between log(SD) and log(mean) was sub-linear across
-all habitats (@tbl-slopes), however, ectotherms from terrestrial
-habitats had much shallower slopes than marine and freshwater
-ectotherms, particularly at higher treatment temperatures, indicating
-increased mean physiological rates generally do not result in higher
-between individual variance in physiological rates (@tbl-slopes).
-Interestingly, in marine ectotherms the slope was highest at cooler
-temperatures, wheeras the slope was suppressed when acclimated and/or
-measured at higher temperatures (i.e., r.1. compared to r1.2, r2.1,
-r2.2) (@tbl-slopes). In freshwater ectotherms, there we some differences
-in scaling relationships but they were all fairly comparable no matter
-what acclimation and test temperature (@tbl-slopes).
+We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats.
+We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses.
+We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.
+
+Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (@tbl-slopes), however, ectotherms from terrestrial habitats had much shallower slopes than marine and freshwater ectotherms, particularly at higher treatment temperatures, indicating increased mean physiological rates generally do not result in higher between individual variance in physiological rates (@tbl-slopes).
+Interestingly, in marine ectotherms the slope was highest at cooler temperatures, whereas the slope was suppressed when acclimated and/or measured at higher temperatures (i.e., r.1.
+compared to r1.2, r2.1, r2.2) (@tbl-slopes).
+In freshwater ectotherms, there we some differences in scaling relationships but they were all fairly comparable no matter what acclimation and test temperature (@tbl-slopes).
 
@@
 
-#### *Comparing relative variance changes using* $lnCVR_{Q_{10}}$
+#### **Comparing relative variance changes using $lnCVR_{Q_{10}}$**
 
@@
 
-Overall, analyses with $lnCVR_{Q_{10}}$ showed similar patterns to those with $lnVR_{Q_{10}}$, except that, because of rates being taken into consideration and there is a strong mean-variance relationship, the patterns were generally opposite in direction.
+Overall, analyses with $lnCVR_{Q_{10}}$ showed similar patterns to those with $lnVR_{Q_{10}}$, except that, because of rates being taken into consideration and there being strong mean-variance relationships, the patterns were generally opposite in direction.
 Either way, the relative differences are quite similar.
 Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with
-higher temperatures across all habitat types, with terrestrial
-ectotherms having the largest decrease in relative variance (@fig-s1).
+higher temperatures across all habitat types, with terrestrial ectotherms having the largest decrease in relative variance (@fig-s1).
 There were also no major differences in the relative differences among broad trait categories (@fig-cvrbtrait) or life-history stages (@fig-lncvrlh).
@@
 #| fig-align: center
-#| fig-cap: "Estimated mean acute and acclimation $lnVR_{Q_{10}}$ for marine, freshwater and terrestrial habitats.
+#| fig-cap: "Estimated mean acute and acclimation $lnCVR_{Q_{10}}$ for marine, freshwater and terrestrial habitats.
 The percentage change in variance is also back calculated.
@@
 Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\\Beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying .
+$\\beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying no significant differences.
 $\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
@@
 #| label: fig-cvrbtrait
-#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for tissue/whole-orgamism traits and biochemical traits across marine (A), freshwater (B) and terrestrial (C) habitats.
+#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for tissue/whole-orgamism traits and biochemical traits across  terrestrial (A), marine (B) and freshwater (C) habitats.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+*k* = total number of effect size estimates while the numbers in brackets indicate the number of species.
 For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
-$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$\\beta$ values are the contrasts between acute and acclimation means within each life stage.
 $p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
@@
 #| echo: false
-#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for marine (A), freshwater (B) and terrestrial (C) ectotherms.
+#| fig-cap: "Estimated mean acclimation and acute $lnCVR_{Q_{10}}$ for adult (a) and juvenile (j) life-history stages for terrestrial (A), marine (B) and freshwater (C) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+*k* = total number of effect size estimates while the numbers in brackets indicate the number of species.
 For ease of visualisation, raw data for both adult and juvenile life-history stages are presented but points are not distinguished by different symbols.
-$\\Beta$ values are the contrasts between acute and acclimation means within each life stage.
+$\\beta$ values are the contrasts between acute and acclimation means within each life stage.
 $p_{MCMC}$ values are the posterior probability of the contrast being different from zero."
@@
 #| include: false
+#| eval: false
 
@@
   sign_change_dat <- data_w_pred  %>% filter(sign(Estimate) != sign(effect_size))
-  #View(sign_change_dat)
-
-# Fitted by Lat/long Longitude, Latitude
-  ggplot(data = data_w_pred, aes(y = Estimate, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Predicted Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = Estimate, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Predicted Effect Size") + theme_classic()
-
-# Observed by Lat/long
-  ggplot(data = data_w_pred, aes(y = effect_size, x = Latitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Latitude", y = "Observed Effect Size") + theme_classic()
-
-  ggplot(data = data_w_pred, aes(y = effect_size, x = Longitude)) + geom_point() + geom_smooth(method = "loess") + labs(x = "Longitude", y = "Observed Effect Size") + theme_classic()
-
-# How much variation does this model explain.
-Need to do this manually because function doesn't seme to work on the model object.
-We need to remember that predcit will include random effect variances so we may need to exclude this
-  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
-  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)
-
-# sigma2_v = typical sampling error variance
-sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
-  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
-              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))
-
-# Now check that var fix from raw data and remove sampling variance. 
-  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58
-
-# Extract the random effect variances
-  v_trait <- re_post$sd_trait__Intercept^2
-    v_spp <- re_post$sd_spp__Intercept^2
-    v_phy <- re_post$sd_species_full__Intercept^2
-    v_std <- re_post$sd_record_num__Intercept^2
-      v_r <- re_post$sd_obs__Intercept^2
-
-# Lets get the total variance for the random effects only
-  tot_re <- v_trait + v_spp + v_phy + v_std + v_r
-
-# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
-    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too
-
-    mean(r2) # Seems a bit high 0.53
-  quantile(r2, probs = c(0.025, 0.975)); #0.30-0.72
-
-# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
-  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2
-
-  mean(r2_2) #  0.50
-  quantile(r2_2, probs = c(0.025, 0.975)); #0.33-0.62
 
@@
 
-#### *Acute and acclimation* for detailed trait categories across marine, freshwater and terrestrial taxa
-
-In addition to the broader trait categories we fit models to understand
-how acute and acclimation effect sizes varied across trait categories.
-To achieve this, we categorized each effect size into one of 12 trait
-categories. These categories included measures of whole organism
-performance measures including cardiac (i.e., 'cardiac') and muscle
-('muscle') function, sprint speed ('sprint') and endurance ('endurance')
-and metabolic rates (i.e., maximal and resting metabolic rate; max MR',
-'rest MR', respectively). Studies also quantified various enzymatic
-reaction rates, including enzymes involved in general metabolic
-responses (categorized as 'metabolic enzyme'), various parts of the
-electron transport chain, including ATPase activity ('ATPase'),
-mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for
-Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
-All other traits not falling within these categories were placed into
-'other'.
+#### **Acute and acclimation* for detailed trait categories across marine, freshwater and terrestrial taxa**
+
+In addition to the broader trait categories we fit models to understand how acute and acclimation effect sizes varied across more detailed trait categories.
+To achieve this, we categorized each effect size into one of 12 trait categories.
+These categories included measures of whole organism performance measures including cardiac (i.e., 'cardiac') and muscle ('muscle') function, sprint speed ('sprint') and endurance ('endurance') and metabolic rates (i.e., maximal and resting metabolic rate; max MR', 'rest MR', respectively).
+Studies also quantified various enzymatic reaction rates, including enzymes involved in general metabolic responses (categorized as 'metabolic enzyme'), various parts of the electron transport chain, including ATPase activity ('ATPase'), mitochondrial leak ('Proton Leak') and oxidation ('OXPHOS', short for Oxidative Phosphorylation), as well as antioxidant enzymes ('antiox').
+All other traits not falling within these categories were placed into 'other'.
 
 Acclimation capacity varied across trait categories and habitat with measures of resting metabolic rate, including associated biochemical reactions like oxidative phosphorylation (OXPHOS) and ATPase activity, acclimating in marine and freshwater ectotherms (@fig-lnrrtrait).
-Whether relative variation in physiological rates changes also depended on trait type, with freshwater ectotherms generally maintaining variance in physiological rates better than marine and freshwater ectotherms (@fig-vrtrait & @fig-cvrtrait).
+Whether variation in physiological rates changes also depended on trait type, with freshwater ectotherms generally maintaining variance in physiological rates better than marine and freshwater ectotherms (@fig-vrtrait & @fig-cvrtrait).
 We note though that some traits have very small sample sizes on their own and should be interpreted with caution.
@@
 
-#### *Plots of* $I^2$ for multilevel models
+#### **Plots of $I^2$ for multilevel models**
 
@@
 
-#### *Environmental predictability*
-
-Theoretical models highlight the importance of environmental
-predictability in selecting for plastic responses. However, capturing
-environmental predictability is challenging given that it is unclear
-which timescale one should select. For example, is it more important to
-look at correlation between temperatures monthly or seasonally. In
-addition, such temporal resolution will likely depend on the species in
-question given that for some species fine-grained thermal predictability
-maybe more important compared to others.
-
-With these limitations in mind, we used our temperature time series to
-calculate auto regressive correlation in temperature across the entire
-time series. We then modeled how this measure of thermal predictability
-was related to plasticity.
+#### **Environmental predictability**
+
+Theoretical models highlight the importance of environmental predictability in selecting for plastic responses.
+However, capturing environmental predictability is challenging given that it is unclear which timescale one should select.
+For example, is it more important to look at correlation between temperatures monthly or seasonally.
+In addition, such temporal resolution will likely depend on the species in question given that for some species fine-grained thermal predictability maybe more important compared to others.
+
+With these limitations in mind, we used our temperature time series to calculate auto regressive correlation in temperature across the entire time series.
+We then modeled how this measure of thermal predictability was related to plasticity.
 
@@
 #| fig-align: center
-#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A) and $lnCVR_{Q_{10_{acclim}}}$ (B) as a function of the Thermal Predictability for wild populations across marine, freshwater and terrestrial habitats.
+#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A) and $lnCVR_{Q_{10_{acclim}}}$ (B) as a function of the thermal predictability for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
@@
 
-#### *Publication bias analysis*
+#### **Publication bias analysis**
 
@@
 
-Funnel plots did not show any noticeable deviation from the typical
-funnel shape for any of the effect size estimates (@fig-s2).
-Meta-regression models including sampling standard error as a moderator
-also suggested no relationship with effect size for $lnRR_{Q_{10}}$
-($\beta$ = `r mean(post_pb_lnrr)`, 95% CI:
-`r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`,
-$p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$
-($\beta$ = `r mean(post_pb_lncvr)`, 95% CI:
-`r quantile(post_pb_lncvr, 0.025)` to
-`r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ =
-`r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ =
-`r mean(post_full_lnvr_pb)`, 95% CI:
-`r quantile(post_full_lnvr_pb, 0.025)` to
-`r quantile(post_full_lnvr_pb, 0.975)`, $p_{MCMC}$ =
-`r p_value(pmcmc(post_full_lnvr_pb))`) was not significant indicating
-little evidence for publication bias.
-
-#### *Performance Curve Simulations*
+Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).
+Meta-regression models including sampling standard error as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(post_full_lnvr_pb)`, 95% CI: `r quantile(post_full_lnvr_pb, 0.025)` to `r quantile(post_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_full_lnvr_pb))`) was not significant indicating little evidence for publication bias.
+
+#### **Performance Curve Simulations**
 

### 2024-07-15 ms.qmd
New abstract merging ideas with Franks suggestions

@@
 
-Climate change is expected to result in warmer and more variable thermal environments globally.
-Maintaining variability in physiological rates and adjusting them in response to extreme temperatures (plasticity) is essential for allowing populations to adapt to climate change.
-Yet, incorporating both plasticity and changes in phenotypic variation when predicting the impacts of climate change on populations is often ignored.
-We developed effect size estimates that quantify how physiological rate variance changes relative to the mean as temperature increases, which we refer to as 'relative variance'.
-We show by meta-analysing >1900 effects from 226 species that relative variance in physiological rates decreases at higher temperatures driven by the lower proportional increase in physiological rate variance relative to the mean.
-Freshwater ectotherms are capable of acclimating and have the smallest reductions in relative variance.
-Marine organisms also acclimated, but plasticity traded-off with a reduction in relative variance in physiological rates at higher temperatures.
-Relative variance reductions were particularly pronounced for terrestrial ectotherms, and this coincided with a lack of capacity for acclimation, highlighting the vulnerability of terrestrial ectotherms to climate change.
-Our results show that, while there are weak acclimation responses in some habitats (marine and freshwater), such responses may trade-off with reductions in relative physiological rate variance that may have important evolutionary and ecological ramifications that affect our understanding of how climate change will impact populations now and in the future.
+Climate change will result in warmer and more variable temperatures globally impacting physiological rates and function in ectothermic animals.
+Acclimation of physiological rates can help maintain function, however, how variance in physiological rates change with temperature has been ignored despite its potential ecological and evolutionary importance.
+We apply new effect sizes that quantify the extent to which both mean and variance in physiological rates change as temperature increases.
+Meta-analysing >1900 effects from 226 species, we show that variance in physiological rates increases at higher temperatures, but that the magnitude of change depends on habitat.
+Freshwater and marine ectotherms are capable of acclimation and have the greatest increase in physiological rate variance.
+In contrast, terrestrial ectotherms lack a capacity for acclimation and have a smaller increase in variance.
+Simulations suggest fundamental differences in among-individual variation in thermal breadth and optima of performance curves across habitats that contribute to these differences.
+Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in physiological rates will provide less raw material for evolutionary adaptation.
+Considering both acclimation capacity and variance in physiological rates side-by-side is therefore important for understanding how climate change will impact populations.
 
@@
 
-Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000;
-@Ummenhofer2017].
+Climate change is expected to result in warmer and more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
 Greater thermal variability is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].

### 2024-07-15 ms.qmd
Fixing up some comments from Franka dn Shinichi throughout, add new affiliation for Shin, wording changes

@@
 Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^, Alex Bush^4^, Frank
-Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$
+Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2,5^ $\dagger$
 
@@
 ^4^ Department of Biology, Lancaster University, Liverpool, UK\
+^5^ Department of Biological Sciences, University of Alberta, CW 405, Biological Sciences Building, Edmonton, AB T6G 2E9, Canada\
 $\dagger$ contributed equally\
@@
 
-**Running head**: Reduced physiological rate variation in ectotherms
+**Running head**: Physiological rate variation in ectotherms
 
@@
 Climate change is expected to result in warmer and more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Greater thermal variability is predicted to pose strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
 Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
@@
 For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
-Acute temperature increases that push organisms from their thermal optimum can be mitigated by plastically adjusting reaction rates in response to chronic temperatures through acclimation [@Seebacher2015-wi; @Havird2020-mj].
+However, longer-lasting (days-weeks) temperature increases move environmental conditions away from thermal optima of physiological rate functions (i.e., thermal performance curves) can be mitigated by acclimation, which adjust reaction rates [@Seebacher2015-wi; @Havird2020-mj].
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
@@
 
-Reversible forms of phenotypic plasticity, such as acclimation, are expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Acclimation is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
 Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect organisms within these habitats to vary in their capacity for plastic adjustments in physiology.
@@
 In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
-However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted
-at higher temperatures.
-
-As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted. NEED MORE ABOUT WHY VARIANCE IS EXPECTED TO CHANGE!
-
-Changes in variability of traits governing energy demand are expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-More variable populations, genetically and/or phenotypically, are also  predicted to be associated with broader niches, have increased growth rate, decreased vulnerability to environmental change and lower extinction risk [@forsman2015rethinking;
-@forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation].
+However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
+
+As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted.
+Positive mean-variance relationships are common across biology suggesting that, as rates increase, so to should variation in rates (i.e., Taylor's Law; []).
+
+Changes in physiological rate variability is expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+Generally, more variable populations are predicted to be associated with broader niches, have increased growth rate, and decreased vulnerability to environmental change lowering extinction risk (i.e., "portfolio effects", [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010].
 In addition, if phenotypic and genetic variation are correlated and traits are linked to fitness, changes in variation may limit responses to selection impacting a populations capacity to evolve [@Pelletier2012].
@@
 
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after
-having been acclimated these same temperatures ([@fig-concept]A).
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
 For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
@@
 As such, positive effect sizes suggest that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
-Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in
-variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion). We test and control for any violations of these assumptions in our analysis (see below).
+Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below).
 
@@
 Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
-While we explored differences across more detailed trait categories (see *Supplemental
-Materials* for details on the types of traits), most traits could be categorised into two broad categories that included whole-organism
-measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction
-rates, proton leak). Traits that could not be categorised into these two we classified as ‘Other’.
+While we explored differences across more detailed trait categories (see *Supplemental Materials* for details on the types of traits), most traits could be categorised into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak).
+Traits that could not be categorised into these two we classified as ‘Other’.
 
@@
 We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2017-wg;
-@Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
+`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
 `r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
 We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0,
-@Nakagawa2021-ls; @nakagawaorchard].
+2.0, @Nakagawa2021-ls; @nakagawaorchard].
 In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
@@
 
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of
-variability.
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
 We refer to this model structure as “Model 1” in the results.
 Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to
-calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$
-metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc]. We also present 95% prediction
-intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers. `r utils::packageVersion("rotl")`)
-[@Michonneau2016-if], and plotted using *ggtree* (vers. `r utils::packageVersion("ggtree")`) [@Yu2017-wj]. We resolved all
-polytomies in the tree.
+This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
+`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
+We resolved all polytomies in the tree.
 Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
@@
 
-After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions. In
-all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD
-= `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial
-ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n =
-`r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n =
-`r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n =
-`r acclim_time[2,4]`).
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
+In all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
 However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz].
@@
 As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
+
+### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
+To better understand the characteristics of performance curves among individuals in a sample that would lead to observed changes in variance across temperature we conducted a simple simulation.
+To simulate performance curves, we used an asymmetrical Gaussian function (@angilletta2009thermal):
+
+$$
+P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
+$$ {#eq-sim}
+
+where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see @fig-sim in *Supplementary Materials* for example curves).
+We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$, $\alpha$) in all possible combinations from 0.01 to 2.
+We then took the standard deviation of the performance at two temperatures 10°C apart (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify parameter space that matches observed patterns in our empirical data.
 
@@
 
-  # Contrats adult vs juv across habitats regardless of the acute/acclim
+  # Contrast adult vs juv across habitats regardless of the acute/acclim
                contrast_lnrr_lh_cat_stats <- rbind(get_lifestage(pred, habitat = "t", newdata),
@@
 
-### *Simulating among-individual variance in performance curves*
-To better understand the characteristics of the performance curves in a sample that would lead to observed changes in variance across temperature we conducted a simple simulation.
-To simulate performance curves, we used an asymmetrical Gaussian function:
-
-$$
-P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
-$$ {#eq-sim}
-
-where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see @fig-sim in *Supplementary Materials* for example curves).
-While we could have modelled performance curves differently than @eq-sim (e.g., Arrhenius), our intentions were not to model the exact curves (which are not know) but rather identify what might vary across the major habitat types that could contribute to the different patterns of variance change at higher temperatures we observed across habitats.
-
-We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$, $\alpha$) in all possible combinations from 0.01 to 2.
-We then took the mean and standard deviation of the performance at two temperatures 10 degrees apart (18 and 28 degrees) to calculate the log variance ratio $lnVR_{Q_{10}}$.
-Our simulations assume that the value of variance does not change depending on the temperatures choosen, but given our analysis restricts the data to temperatures within the normal thermal range of each species we do not envisage this being problematic.
-
 ## **Results**
@@
 
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`,
-amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`,
-reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`,
-arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians =
-`r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
+and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
@@
 #| echo: false
-#| fig-cap: "Phylogenetic distribution of acute and acclimation $lnRR_{Q_{10}}$/$lnCVR_{Q_{10}}$ estimates across major habitats.
-The total number of acute and acclimation  $lnRR_{Q_{10}}$/$lnCVR_{Q_{10}}$ effect sizes are indicated by the coloured bars as well as whether the taxa are marine, freshwater or terrestrial.
+#| fig-cap: "Phylogenetic distribution of acute and acclimation $lnRR_{Q_{10}}$/$lnVR_{Q_{10}}$ estimates across major habitats.
+The total number of acute and acclimation  $lnRR_{Q_{10}}$/$lnVR_{Q_{10}}$ effect sizes are indicated by the coloured bars as well as whether the taxa are marine, freshwater or terrestrial.
 Silhouettes are only representative taxa of major clades within the tree."
@@
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
+In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
 All results are from Model 2 (see “Meta-Analysis” above).
 
-Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see
-*Supplementary Materials*, @fig-lnrrtrait for more detailed trait analysis).
+Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see *Supplementary Materials*, @fig-lnrrtrait for more detailed trait analysis).
 Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms ([@fig-btrait]C).
@@
 
-Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent, although the effect size was small and in the same direction and magnitude of juveniles ("Model 4"; [@fig-cvrlh]A-C).
-When comparing between acute and acclimation responses between adults and juveniles there were also no differences across habitats (Adult-Juvenile (Acute): `r mean(acute_all_lh)`, 95% CI: `r quantile(acute_all_lh, 0.025)[1]` to `r quantile(acute_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acute_all_lh)`; Adult-Juvenile (Acclimation): `r mean(acclim_all_lh)`, 95% CI: `r quantile(acclim_all_lh, 0.025)[1]` to `r quantile(acclim_all_lh, 0.975)[1]`, $p_{MCMC}$ = `r pmcmc(acclim_all_lh)`).
+Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
+When comparing between acute and acclimation responses between adults and juveniles irrespective of effect type there were also no differences across habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
 
@@
 figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/fig5.png", width = 28, height = 14, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/fig5.png")
+ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/fig4.png")
 figbtrait
@@
 fig4 <-(p3 | p1 | p2) / (p3_vr | p1_vr | p2_vr) + plot_annotation(tag_levels = "A") 
-ggsave(fig4, filename = "./output/figures/fig6.pdf", width = 28, height = 14, device = "pdf")
-
-fig4 <- magick::image_read("./output/figures/fig6.pdf")
+ggsave(fig4, filename = "./output/figures/fig5.pdf", width = 28, height = 14, device = "pdf")
+
+fig4 <- magick::image_read("./output/figures/fig5.pdf")
 fig4
@@
 Variance in physiological rates ($lnVR_{Q_{10}}$) showed an increase with increasing temperature across all habitat types ([@fig-2]B) with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI: `r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`; "Model 1"; see *Supplementary Materials* @fig-s3).
-However, physiological rate variance increased significantly more in freshwater for acute responses (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c_a)`, 95% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance (freshwater vs terrestrial: $\beta$ = `r mean(f_t_c_aclim)`, 95% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`).
+Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))` increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
+The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
+
+Physiological rate variance increased significantly more in freshwater compared to terrestrial ectotherms for acute responses ($\beta$ = `r mean(f_t_c_a)`, 95% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance ($\beta$ = `r mean(f_t_c_aclim)`, 95% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`).
 While marine ectotherms had larger increases in physiological rate variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
@@
 
-Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms and a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms when temperatures increased by 10$^\circ$C.
-In contrast, freshwater ectotherms exhibited a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))` increase in variance at high temperatures (@fig-2; results from "Model 2").
-The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
-
-$lnVR_{Q_{10}}$ values from our simulations matched our empirical results quite nicely in key areas of parameter space (@fig-sim2).
-Interestingly, for a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
+$lnVR_{Q_{10}}$ values from our simulations matched our empirical results in particular areas of parameter space (@fig-sim2).
+For a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
 In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2])
@@
 
-#ggsave(lnvr_sim_delta_sigma1, width = 9.5, height = 8, filename = "./output/figures/fig4.pdf")
-
-p_sim2 <- image_read("./output/figures/fig4_new.pdf")
+#ggsave(lnvr_sim_delta_sigma1, width = 9.5, height = 8, filename = "./output/figures/fig6.pdf")
+
+p_sim2 <- image_read("./output/figures/fig6_new.pdf")
 p_sim2
@@
 We show that the capacity for acclimation of physiological rates differs across habitats.
-Our findings confirm previous results that quantify the different capacity of terrestrial, marine and freshwater ectotherms to acclimate [@Seebacher2015-wi;
-@Gunderson2015-hz; @morley2019physiological]. Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and
-@morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
+Our findings confirm previous results that quantify the different capacity of terrestrial, marine and freshwater ectotherms to acclimate [@Seebacher2015-wi; @Gunderson2015-hz; @morley2019physiological].
+Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
 The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi], possibly due to the use of newly derived $Q_{10}$ effect sizes that allow us to control for sampling variance.
@@
 
-Interestingly, we show that biochemical traits (i.e., enzymes) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
+We show that biochemical traits (e.g., enzymes) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
 In contrast, both whole-organism and biochemical traits were equally likely to acclimate in freshwater ectotherms.
-Unsurprisingly, we observed no distinction between traits in terrestrial ectotherms.
+Unsurprisingly, we observed no distinction between traits in terrestrial ectotherms......FRANK?
 
 ### ***Increased variability in physiological rates across habitats: insights into the adaptive potential of physiological processes in the face of climate change?***
+
 In contrast to acclimation capacity, variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation.
 Mechanistically, it is unclear what is contributing to the increased variation in physiological rates at higher temperatures, but it could be the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein].
-Higher temperatures increase membrane fluidity affecting electrochemical gradients and impacting protein structure and function [@somero1995proteins; @fields2001protein; @tattersall2012coping].
+Higher temperatures increase membrane fluidity affecting  gradients and impacting protein structure and function [@somero1995proteins; @fields2001protein; @tattersall2012coping].
 Such challenges (among others) may expose among-individual variation within a population.
-Some support for these mechanisms exist given that variation in biochemical traits did show larger increases in variability at high temperatures compared to whole-organism traits, although this was only significant for marine organisms.
-Increases in variance are probably dependent on the type of biochemical reaction being measured, and so, the differences across habitats could be attributable to the types of traits typically measured on these organisms.
-
-Importantly, increased variance in physiological rates was not equal among ectotherms occupying terrestrial, marine and freshwater habitats.
-Increases in variance were particularly pronounced in freshwater ectotherms (~60% increase over 10 degrees Celsius) compared to terrestrial ectotherms (~36% increase over 10 degrees Celsius).
-The changes in variability we observed across habitats can be explained by differences in among individual variation in thermal breath and optima of individual performance curves between habitats.
-Consistent differences in thermal performance curves across these major habitat types have never been formally compared, probably because of the challenges in measuring full performance curves across taxa.
-However, a multitude of studies support the general notion that species occupying different habitats (terrestrial vs aquatic) should differ.
-@p
-
-Understanding the relative role that plasticity and genetic adaptation will play in response to future climates has attracted considerable attention [@urban2023and].
-If the increased variability we observed in our study is underpinned by genetic variation then our results suggest evolutionary adaptation will be more important than acclimation as populations experience future climates.
-Increased expression of genetic variation in response to novel environments has been shown by numerous studies but primarily for morphological and life-history traits [noble rowinsku rogel, ].
-Our results further highlight the vulnerability of terrestrial
-ectotherms to climate change. Assuming changes in variation in physiological rates are underpinned by genetic variation,
-and there is a genetic correlation with fitness, such reductions in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and].
-For example, under climate we expect an increase of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by 29%.
-
-------
-Only in freshwater ectotherms did acclimation in physiological rates coincide with no change in relative variation.
-Such a mechanism may also help explain the differences in relative variance across habitat types.
-For example, terrestrial ectotherms may rely on more specialised enzymatic variants that operate over a more limited temperature range individually but together allow for organisms to function over a wider thermal range necessary to operate in more variable thermal environments [@angilletta2009thermal].
-
- We also expected relative variance to differ between whole-organism and biochemical traits, but we did not find strong support for this except for in freshwater ectotherms where biochemical traits were more likely to maintain or increase relative variance compared with whole-organisms traits.
-Acclimation responses in marine and freshwater organisms may buffer / maintain variance in physiological rates at higher temperatures due to the expression of alternative enzyme forms or intracellular stabalising compounds/solutes that impact enzyme function [@fields2001protein].
-
- Of course, considering how behavioural modifications buffer organisms from high temperatures is also needed.
-Terrestrial species likely have greater opportunity for behavioural microhabitat selection in thermally heterogeneous environments which is expected to decrease the impacts of climate change [@huey2012predicting; @sunday2014thermal].
-Importantly, while we seen a reduction in relative variation, absolute variation in physiological rates did increase with temperature (@fig-s1) -- albeit to a much lesser extent in terrestrial and marine habitats compared to freshwater -- supporting the general notion that capacity for adaptation may still be limited in terrestrial and marine habitats.
-As of yet, it is unclear whether a focus on relative or absolute variance should be prioritized.
-Future theoretical models are needed to better understand the ecological and evolutionary consequences of changes in both mean and variance.
+Indeed, even acclimation itself can impact among-individual variation [REF FRANK?], and we find evidence to that effect given that biochemical processes in marine organisms were both more likely to acclimate and have reduced variance increases compared to acute responses.
+However, this was not a general phenomena given that freshwater ectotherms were able to maintain high variance despite strong acclimation responses.
+
+Importantly, increased variance in physiological rates was not equal among ectotherms occupying terrestrial, marine and freshwater habitats, with increases in variance being higher in freshwater ectotherms (~60% increase / 10°C) compared to terrestrial ectotherms (~36% increase / 10°C).
+One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ [@angilletta2009thermal; @huey1989evolution].
+Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal optima and breadth making this hypothesis plausible.
+Such patterns across habitats are expected given that terrestrial ectotherms should be adapted warmer and more variable environments.
+Theoretical models also suggest that populations with greater temporal environmental variation exhibit greater thermal breadth [@lynch1987environmental].
+While we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected, such analyses will depend on an appropriate measure of temporal variation in temperature that is biologically relevant - a challenging feat across diverse taxa but worthy of future investigation.
+
+Our results further highlight the potential vulnerability of terrestrial ectotherms to climate change.
+Assuming changes in variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, such reductions in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and].
+For example, under climate change we expect an increase in variance in physiological rates of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30%.
+Importantly, there will be limits to variance increases, and we predict that organisms closer to their upper thermal limits ($CT_{max}$) will have lower $lnVR_{Q_{10}}$ values compared to those farther away from $CT_{max}$.
+Some evidence points to possible differences across habitats in upper thermal limits already [@Gunderson2015-hz; @Pinsky2019-fn] making this a fruitful future question to ask.
 
@@
 
-Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when oscillations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when fluctuations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
 Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity is more likely to evolve in terrestrial environments.
@@
 
-Whether a populations capacity for physiological plasticity and the thermal variability (or predictability) it experiences are related has received more mixed results.
+Whether population capacity for acclimation is related to the thermal variability (or predictability) it experiences is equivocal.
 We show no relationship between acclimation capacity and thermal variability in marine, freshwater and terrestrial habitats.
@@
 
-  ggsave(p3, filename = "./output/figures/figS6.pdf", width = 11.5, height = 8)
+  ggsave(p3b, filename = "./output/figures/figS6.pdf", width = 11.5, height = 8)
 

### 2024-07-15 ms.qmd
Fixing up responses! I nee dto add line numbers at the end which I think will be easy.Added a few more refs and also re-rendered for another read!

@@
 Climate change is expected to result in warmer and more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability is predicted to pose strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Greater thermal variability is predicted to pose a strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
 Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
@@
 For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
-However, longer-lasting (days-weeks) temperature increases move environmental conditions away from thermal optima of physiological rate functions (i.e., thermal performance curves) can be mitigated by acclimation, which adjust reaction rates [@Seebacher2015-wi; @Havird2020-mj].
+However, longer-lasting (days-weeks) temperature increases that move environmental conditions away from thermal optima of physiological rate functions (i.e., thermal performance curves) can be mitigated by acclimation, which adjust reaction rates [@Seebacher2015-wi; @Havird2020-mj].
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
@@
 In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
-However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological rates might also be impacted at higher temperatures.
-
-As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability might also be impacted.
-Positive mean-variance relationships are common across biology suggesting that, as rates increase, so to should variation in rates (i.e., Taylor's Law; []).
+However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological processes might also be impacted by higher temperatures.
+
+As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability will also be impacted.
+Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so to should variation (i.e., Taylor's Law; [@giometto2015sample]).
+As biochemical reaction rates increase with temperatures
 
@@
 
-We show that biochemical traits (e.g., enzymes) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
+We show that biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
 In contrast, both whole-organism and biochemical traits were equally likely to acclimate in freshwater ectotherms.
@@
 This may not be too surprising given that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
-The lack of differences we observed may also be due to the fact that both juvenile and adult animals occupy similar thermal niches, disperse to a similar extent and exhibit comparable thermoregulatory behaviors making physiological responses to temperature similar.
+The lack of differences we observed may be because both juvenile and adult animals occupy similar thermal niches, disperse to a similar extent and exhibit comparable thermoregulatory behaviors making physiological responses to temperature similar.
 It is possible that temperatures experienced earlier in development (e.g., egg or larval stages) exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
@@
 
-Enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment, may lead to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
-While we show general patterns across taxa and habitats it is important to recognise that this does not mean such patterns apply to all populations.
+Enhanced knowledge of how variation in physiological rates vary across populations and species, and the degree to which they can be adjusted in response to the environment leads to more informed predictions about the ecological and evolutionary dynamics of natural populations [@forsman2015rethinking; @seebacher2023can; @cooke2021one; @Sanderson2023].
+We show general patterns across taxa and habitats that provide a foundation to understand the relationship between plasticity and trait variance, as well as particular trade-offs that could impact the benefits (or lack thereof) of acclimation.
+It is important to recognise, however, that these patterns do not necessarily apply to all populations.
 Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial study- and trait-level variance estimates.
-Nonetheless, quantitative measures on the changes in variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
+Conservation efforts are often targeted at particular populations or species, and taxonomic differences are important in this context.
+Regardless, quantitative measures of the changes in variance in physiological rates could be better incorporated into physiological and ecological models to provide more nuanced, and possibly more realistic, predictions about the impacts of climate change on natural populations.
 While we do not yet understand the relative contribution of environmental and genetic factors to variance changes, models could better decouple how different levels of heritability and total variance impact evolutionary and ecological predictions.

### 2024-07-15 ms.qmd
A nice final evening read of the full paper. Corrected a bunch of things and it's getting much closer now!

@@
 
-Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^, Alex Bush^4^, Frank
-Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2,5^ $\dagger$
+Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^, Alex Bush^3^, Frank
+Seebacher^4^ $\dagger$, & Shinichi Nakagawa^2,5^ $\dagger$
 
@@
 Australia\
-^3^ School of Life and Environmental Sciences, University of Sydney,
+^3^ Department of Biology, Lancaster University, Liverpool, UK\
+^4^ School of Life and Environmental Sciences, University of Sydney,
 Sydney, NSW 2006, Australia\
-^4^ Department of Biology, Lancaster University, Liverpool, UK\
 ^5^ Department of Biological Sciences, University of Alberta, CW 405, Biological Sciences Building, Edmonton, AB T6G 2E9, Canada\
@@
 Climate change is expected to result in warmer and more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability is predicted to pose a strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
+Greater thermal variability is predicted to pose strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
 Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
@@
 Acclimation therefore alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
-Acclimation, however, does not normally result in physiological rates returning to their original state (‘complete’ compensation - *sensu* @huey1999testing), but rather are only partially compensated [@huey1999testing; @Havird2020-mj].
+Acclimation, however, does not normally result in physiological rates returning to their original state [‘complete’ compensation - *sensu* @huey1999testing].
+Rather, increased physiological rates are only partially compensated [@huey1999testing; @Havird2020-mj].
 
@@
 As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability will also be impacted.
-Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so to should variation (i.e., Taylor's Law; [@giometto2015sample]).
+Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so to should variation [i.e., Taylor's Law; @giometto2015sample].
 As biochemical reaction rates increase with temperatures
@@
 Changes in physiological rate variability is expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-Generally, more variable populations are predicted to be associated with broader niches, have increased growth rate, and decreased vulnerability to environmental change lowering extinction risk (i.e., "portfolio effects", [@forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010].
+Generally, more variable populations are predicted to be associated with broader niches, have increased growth rate, and decreased vulnerability to environmental change lowering extinction risk [i.e., "portfolio effects", @forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010].
 In addition, if phenotypic and genetic variation are correlated and traits are linked to fitness, changes in variation may limit responses to selection impacting a populations capacity to evolve [@Pelletier2012].
@@
 An example of how acute and acclimation $lnCVR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right-hand side of the figure with reference to each of the four possible groups.
-Note that, two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
+Note that we use $lnCVR_{Q_{10}}$ because it makes use of all avilable data.
+Two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
 (B) Species are expected, *a priori*, to vary in their thermal performance curves (thin lines) around an average (thick black line).
@@
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015-wi].
-While we explored differences across more detailed trait categories (see *Supplemental Materials* for details on the types of traits), most traits could be categorised into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak).
+Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi].
+We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
 Traits that could not be categorised into these two we classified as ‘Other’.
@@
 We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WAIC) (if Bayesian).
-We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more.
-If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.
 
@@
 
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
 We refer to this model structure as “Model 1” in the results.
-Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
 This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
@@
 However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz].
-Nonetheless, to control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models, though it was not a strong predictor of effect size variation (*Supplementary Materials*, @fig-accl_time).
+Nonetheless, to control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models, though it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
 
@@
 All estimates from our models are therefore conditioned on an average level of acclimation time (i.e.,
-`r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23$^\circ C$) across the dataset.
+`r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23°C) across the dataset.
 
@@
 indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnCVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10°C differ depending on whether acute or acclimation responses are measured.
+In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10°C differ depending on whether acute or acclimation responses are measured.
 
 Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
-We also explored how acute and acclimation effects varied across more detailed trait categories, and these results can be found in the *Supplementary Materials*.
-Given that residual variance appeared to differ across trait categories we fit heteroscedastic residual variance models.
-We expected that whole-organism traits would be more likely to maintain relative variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivies [@fields2001protein; @angilletta2009thermal].
+We expected that whole-organism traits would be more likely to maintain relative variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
 
@@
 We used all $lnVR_{Q_{10}}$ data because there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe climate would impact acclimation and acute $lnVR_{Q_{10}}$ differently.
-To test how climate variability impacted mean effect size in wild populations we fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators while controlling for acclimation time and maximum temperature used in the experiments (referred to as "Model 5").
+We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
 We also explored how environmental predictability, as measured by how correlated successive temperatures at a given location were across months, might also explain capacity for acclimation.
 However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report on these results for a single lag (1 month) in the *Supplementary Materials* but note they do not differ from CV analyses.
+As such, we report on these results for a single lag (1 month) in the *Supplementary Materials* but note they do not differ from our CV analysis.
 
@@
 
-To understand the consequences of human-induced climate change on the potential to impact relative variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
+To understand the consequences of human-induced climate change on the potential to impact variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
 We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
@@
 Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category) (referred to as "Model 7").
+As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+Given that their was no evidence for publication bias results are presented in the *Supplementary Materials*.
 
 ### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
-To better understand the characteristics of performance curves among individuals in a sample that would lead to observed changes in variance across temperature we conducted a simple simulation.
-To simulate performance curves, we used an asymmetrical Gaussian function (@angilletta2009thermal):
+To better understand the characteristics of performance curves of a population that would lead to our observed changes in variance across temperature we conducted a simple simulation that varied among-individual variation in performance curve parameters.
+To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
 
@@
 where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see @fig-sim in *Supplementary Materials* for example curves).
-We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$, $\alpha$) in all possible combinations from 0.01 to 2.
-We then took the standard deviation of the performance at two temperatures 10°C apart (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify parameter space that matches observed patterns in our empirical data.
+We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
+We also varied $\alpha$, but this did not impact our conclusions and so we keep among-individual variation fixed.
+From the population of performance curves, we took the standard deviation at two temperatures 10°C apart (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify parameter space that matched observed patterns in our empirical data.
 
@@
 Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`%, 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95%
-CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%). All results are from Model 1 (see “Meta-Analysis” above).
+CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
+These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
+All results are from Model 1 (see “Meta-Analysis” above).
 
@@
 
-Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; [@fig-btrait]A-C; and see *Supplementary Materials*, @fig-lnrrtrait for more detailed trait analysis).
+Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; [@fig-btrait]A-C).
 Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms ([@fig-btrait]C).
@@
 Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
-When comparing between acute and acclimation responses between adults and juveniles irrespective of effect type there were also no differences across habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
+When comparing between acute and acclimation responses between adults and juveniles irrespective of effect type there were also no differences within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
 
@@
 
-Variance in physiological rates ($lnVR_{Q_{10}}$) showed an increase with increasing temperature across all habitat types ([@fig-2]B) with less heterogeneity overall ($I^2_{sv}$ = `r mean(tot_i2_VR)`, 95% CI: `r quantile(tot_i2_VR, 0.025)` to `r quantile(tot_i2_VR, 0.975)`; "Model 1"; see *Supplementary Materials* @fig-s3).
+Variance in physiological rates ($lnVR_{Q_{10}}$) showed an increase with increasing temperature across all habitat types ([@fig-2]B).
 Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))` increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
@@
 Marine and freshwater did not differ in how much variance changed at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
-There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ in any habitat ([@fig-2]B).
-Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* analyses with $lnCVR_{Q_{10}}$; @tbl-slopes & @fig-mv).
+There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B).
+Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* scaling analyses, @tbl-slopes & @fig-mv, and analyses with $lnCVR_{Q_{10}}$, @fig-s1).
 
@@
 For a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
-In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2])
+In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2]).
 
@@
 
-Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; see also  *Supplementary Materials*, @fig-vrtrait for more detailed trait analysis)("Model 3").
+Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
 Interestingly, variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
@@
 
-Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 43% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
+Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 46% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
 Climate change is predicted to result, on average, in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% increase in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$f))`), a `r abs(lapply(mean_perc_habitat_vr, mean)$m)`% increase in marine systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$m))`), and a `r abs(lapply(mean_perc_habitat_vr, mean)$t)`%  increase in terrestrial systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5 climate scenario ([@fig-fig6]D).
@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
-Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance ($lnVR_{Q_{10}}$) of ectotherms varied habitats.
-Our results uncover an hitherto unrecognised dynamic where the limited benefits of acclimation are compensated for by increases in trait variance that may have impacts on how ectotherm populations across these different habitats
-will be able to adapt to increased temperatures.
+Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
+Our results uncover an hitherto unrecognised dynamic where the limited benefits of acclimation are potentially compensated for by increases in trait variance that may have impacts on how ectotherm populations across these different habitats will be able to adapt to increased temperatures.
 
@@
 Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
-The change in acclimation $Q_{10}$ we found was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi], possibly due to the use of newly derived $Q_{10}$ effect sizes that allow us to control for sampling variance.
+These consistent results are surprising given the different physiological traits measured (i.e., thermal limits versus physiological rates).
+The change in acclimation $Q_{10}$ we found with our expanded dataset (34% increase in effects) was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi], possibly due to the use of newly derived $Q_{10}$ effect sizes that allow us to control for sampling variance.
 Greater capacity for acclimation in aquatic organisms may be the result of fewer opportunities for behavioural thermoregulation in aquatic environments making physiological remodeling important for maintaining homeostasis [@Gunderson2015-hz; @morley2019physiological].
@@
 
-We show that biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
+Biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
 In contrast, both whole-organism and biochemical traits were equally likely to acclimate in freshwater ectotherms.
@@
 
-In contrast to acclimation capacity, variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation.
+Contrary to acclimation capacity variance in physiological rates increased across habitats with effect sizes being 3-5x larger than those observed for acclimation.
 Mechanistically, it is unclear what is contributing to the increased variation in physiological rates at higher temperatures, but it could be the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein].
-Higher temperatures increase membrane fluidity affecting  gradients and impacting protein structure and function [@somero1995proteins; @fields2001protein; @tattersall2012coping].
+Higher temperatures increase membrane fluidity affecting electrochemical gradients and impacting protein structure and function [@somero1995proteins; @fields2001protein; @tattersall2012coping].
 Such challenges (among others) may expose among-individual variation within a population.
 Indeed, even acclimation itself can impact among-individual variation [REF FRANK?], and we find evidence to that effect given that biochemical processes in marine organisms were both more likely to acclimate and have reduced variance increases compared to acute responses.
-However, this was not a general phenomena given that freshwater ectotherms were able to maintain high variance despite strong acclimation responses.
+However, this was not a general phenomena given that freshwater ectotherms were able to maintain high variance despite being able to acclimate.
 
@@
 Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal optima and breadth making this hypothesis plausible.
-Such patterns across habitats are expected given that terrestrial ectotherms should be adapted warmer and more variable environments.
-Theoretical models also suggest that populations with greater temporal environmental variation exhibit greater thermal breadth [@lynch1987environmental].
-While we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected, such analyses will depend on an appropriate measure of temporal variation in temperature that is biologically relevant - a challenging feat across diverse taxa but worthy of future investigation.
+Such patterns across habitats are expected given that terrestrial ectotherms should be adapted to warmer and more variable environments.
+Theoretical models also suggest that populations with greater temporal environmental variability exhibit greater thermal breadth [@lynch1987environmental].
+While we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected, such analyses will depend on an appropriate measure of temporal variation in temperature that is biologically relevant -- a challenging feat across diverse taxa but worthy of future investigation.
 
 Our results further highlight the potential vulnerability of terrestrial ectotherms to climate change.
-Assuming changes in variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, such reductions in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and].
+Assuming changes in variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, smaller increases in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and].
 For example, under climate change we expect an increase in variance in physiological rates of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30%.
-Importantly, there will be limits to variance increases, and we predict that organisms closer to their upper thermal limits ($CT_{max}$) will have lower $lnVR_{Q_{10}}$ values compared to those farther away from $CT_{max}$.
+There will obviously be limits to variance increases, and we predict that organisms closer to their upper thermal limits ($CT_{max}$) will have lower $lnVR_{Q_{10}}$ values compared to those farther away from $CT_{max}$.
 Some evidence points to possible differences across habitats in upper thermal limits already [@Gunderson2015-hz; @Pinsky2019-fn] making this a fruitful future question to ask.
 
-### ***Plasticity and relative variance in physiological rates do not differ between life stages***
+### ***Plasticity and variance in physiological rates do not differ between life stages***
 
@@
 
-### ***No signature of past climate on capacity for physiological plasticity***
+### ***No signature of past climate on capacity for physiological plasticity or changes in variance***
 
@@
 where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ is the performance breadth, and $\alpha$ is the skewness of the performance function or rate variation.
-To understand how each parameter impacts the shape of performance curces, we simulated 40 individuals with varying amounts of between individual variation in performance breadth, optima and rate variation.
+To understand how each parameter impacts the shape of performance curves, we simulated 40 individuals with varying amounts of between individual variation in performance breadth, optima and rate variation.
 We then calculated the relative variance in performance across the temperature gradient as the variance in performance at each temperature divided by the maximum performance at that temperature.
@@
 $lnVR_{Q_{10}}$ is calculated as the log transformed ratio of the standard deviation in performance at the higher temperature divided by the standard deviation in performance at that temperature.
-The dashed red line indicates the higher temperature (28$^\\circ$C) and the dashed blue line indicates the lower temperature (18$^\\circ$C).
+The dashed red line indicates the higher temperature (28°C) and the dashed blue line indicates the lower temperature (18°C).
 Note that the mean ($\\mu$) and standard deviation ($\\sigma$) of physiological rates are shown for each temperature.
-In all simulations, $\\delta$ = 35, $\\sigma$ = 9 and $\\alpha$ = -15, while between individual variation for $\\sigma_{_b_{\\delta}}$ = 1,  $\\sigma_{_b_{\\sigma}}$ = 0.5 and $\\sigma_{_b_{\\alpha}}$ = 0.5."
+In all simulations, $\\delta$ = 35, $\\sigma$ = 9 and $\\alpha$ = -15, while between individual variation for $\\sigma_{\\delta}$ = 1,  $\\sigma_{\\sigma}$ = 0.5 and $\\sigma_{\\alpha}$ = 0.5."
 

### 2024-07-16 ms.qmd
Intro paragraph on why variance written, fixed a few things throughout, finished off discussion, mostly, just a few senetences need in one paragraph

@@
 In contrast, terrestrial ectotherms lack a capacity for acclimation and have a smaller increase in variance.
-Simulations suggest fundamental differences in among-individual variation in thermal breadth and optima of performance curves across habitats that contribute to these differences.
-Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in physiological rates will provide less raw material for evolutionary adaptation.
+Simulations suggest fundamental differences in among-individual variation in thermal breadth and optima of performance curves across habitats that may contribute to these differences.
+Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in physiological rates may provide less raw material for evolutionary adaptation.
 Considering both acclimation capacity and variance in physiological rates side-by-side is therefore important for understanding how climate change will impact populations.
@@
 Acclimation, however, does not normally result in physiological rates returning to their original state [‘complete’ compensation - *sensu* @huey1999testing].
-Rather, increased physiological rates are only partially compensated [@huey1999testing; @Havird2020-mj].
+Rather, increased physiological rates are usually only partially compensated [@huey1999testing; @Havird2020-mj].
 
@@
 Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect organisms within these habitats to vary in their capacity for plastic adjustments in physiology.
-Species occupying terrestrial habitats have been shown to exhibit weak acclimation abilities, and so, are likely to be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
+@rohr2018complex show relationships between acclimation capacity, latitude and body size suggesting climate could be an important driver of acclimation responses.
+In addition, species occupying terrestrial habitats have been shown to exhibit weaker acclimation abilities, and so, may be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
 In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
@@
 
-As mean physiological rates increase with temperature there is reason to believe that the intrapopulation variability will also be impacted.
+As mean physiological rates increase with temperature there is reason to believe that intrapopulation variability will also be impacted.
 Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so to should variation [i.e., Taylor's Law; @giometto2015sample].
-As biochemical reaction rates increase with temperatures
-
-Changes in physiological rate variability is expected to have important consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-Generally, more variable populations are predicted to be associated with broader niches, have increased growth rate, and decreased vulnerability to environmental change lowering extinction risk [i.e., "portfolio effects", @forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010].
-In addition, if phenotypic and genetic variation are correlated and traits are linked to fitness, changes in variation may limit responses to selection impacting a populations capacity to evolve [@Pelletier2012].
+Differences in the shape of thermal performance curves (thermal breadth, maximal performance and thermal optima) can exacerbate among-individual variability at higher temperatures, which can also depend on different levels of biological organisation, environmental conditions and acclimation responses [@rezende2019thermal; @tattersall2012coping; @schulte2011thermal; @angilletta2009thermal].
+Presumably, increases in underlying variation in physiological rates should be related to varying robustness among individuals in how biochemical and physiological networks are affected by temperature [@schulte2011thermal].
+A focus on quantifying the shape of performance curves has often taken precedence over quantifying levels of among-individual variation in curves which has limited our understanding of their capacity to evolve.
+
+Importantly, changes in physiological rate variability is expected to have consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+Generally, more variable populations are predicted to be associated with broader niches, have increased growth rate, and decreased vulnerability to environmental change lowering extinction risk [i.e., "portfolio effects",@Schindler2010] [see also, @forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010; @portner2021climate].
+In addition, if phenotypic and genetic variation in physiological rates are correlated rates and linked to fitness, changes in variation may limit responses to selection impacting a populations capacity to evolve [@Pelletier2012; @hoffmann2011climate].
 Therefore, maintaining intrapopulation variability in physiological rates in a warmer world may be important for population resilience to climate change.
@@
 4) Are changes in plasticity or variance in physiological rates impacted by past climate history?
-5) How are means and variances in physiological rates expected to change under climate change?
+5) How are variances in physiological rates expected to change under climate change?
 
@@
 
-We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures.
-If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question.
+We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures ([@fig-concept]A).
+If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
 We extracted these data from text, tables or figures of a given paper.
@@
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi].
+Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
 We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
@@
 $$
-lnCVR_{Q_{1}} = \frac{lnCVR_{Q_{10}}}{10}
+lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
 $$ {#eq-lCVRpred}
@@
 Variance in physiological rates ($lnVR_{Q_{10}}$) showed an increase with increasing temperature across all habitat types ([@fig-2]B).
-Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`%, 95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))` increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
-The relative differences between habitats were similar when considering $lnCVR_{Q_{10}}$ (See *Supplementary Materials*).
+Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`% (95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))`) increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
+The relative differences between habitats were even larger when considering $lnCVR_{Q_{10}}$, which controls for changes in mean rates (See *Supplementary Materials*).
 
@@
 Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
-Interestingly, variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
+Variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
 
@@
 Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
-These consistent results are surprising given the different physiological traits measured (i.e., thermal limits versus physiological rates).
+These consistent results are interesting given the different physiological traits measured in these meta-analyses (i.e., thermal limits versus physiological rates).
+
 The change in acclimation $Q_{10}$ we found with our expanded dataset (34% increase in effects) was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi], possibly due to the use of newly derived $Q_{10}$ effect sizes that allow us to control for sampling variance.
@@
 
-Biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms.
-In contrast, both whole-organism and biochemical traits were equally likely to acclimate in freshwater ectotherms.
-Unsurprisingly, we observed no distinction between traits in terrestrial ectotherms......FRANK?
+Biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms, presumably because of the less complicated physiological networks that underlie specific biochemical processes [@schulte2011thermal].
+However, this prediction did not hold up generally with both whole-organism and biochemical traits being equally likely to acclimate in freshwater ectotherms, which may be due to the different types of biochemical processes measured in the two habitats.
 
@@
 Contrary to acclimation capacity variance in physiological rates increased across habitats with effect sizes being 3-5x larger than those observed for acclimation.
-Mechanistically, it is unclear what is contributing to the increased variation in physiological rates at higher temperatures, but it could be the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein].
+Mechanistically, it is unclear what exactly is contributing to the increased variation in physiological rates at higher temperatures, but it is likely the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein; @schulte2011thermal].
 Higher temperatures increase membrane fluidity affecting electrochemical gradients and impacting protein structure and function [@somero1995proteins; @fields2001protein; @tattersall2012coping].
 Such challenges (among others) may expose among-individual variation within a population.
-Indeed, even acclimation itself can impact among-individual variation [REF FRANK?], and we find evidence to that effect given that biochemical processes in marine organisms were both more likely to acclimate and have reduced variance increases compared to acute responses.
+Indeed, even acclimation itself can impact among-individual variation, possibly through changes in individual performance curves [@schulte2011thermal].
+Indeed, we find evidence to that effect given that biochemical processes in marine organisms were both more likely to acclimate and have reduced variance increases compared to acute responses.
 However, this was not a general phenomena given that freshwater ectotherms were able to maintain high variance despite being able to acclimate.
 
-Importantly, increased variance in physiological rates was not equal among ectotherms occupying terrestrial, marine and freshwater habitats, with increases in variance being higher in freshwater ectotherms (~60% increase / 10°C) compared to terrestrial ectotherms (~36% increase / 10°C).
-One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ [@angilletta2009thermal; @huey1989evolution].
-Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal optima and breadth making this hypothesis plausible.
+Importantly, increased variance in physiological rates was not equal among terrestrial, marine and freshwater ectotherms, with increases in variance being higher in freshwater ectotherms (~60% increase / 10°C) compared to terrestrial ectotherms (~36% increase / 10°C).
+One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ [@angilletta2009thermal; @huey1989evolution; @tattersall2012coping; @rezende2019thermal].
+Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal optima and breadth across habitats making this hypothesis plausible.
 Such patterns across habitats are expected given that terrestrial ectotherms should be adapted to warmer and more variable environments.
 Theoretical models also suggest that populations with greater temporal environmental variability exhibit greater thermal breadth [@lynch1987environmental].
-While we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected, such analyses will depend on an appropriate measure of temporal variation in temperature that is biologically relevant -- a challenging feat across diverse taxa but worthy of future investigation.
+While we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected, such analyses will depend on an appropriate measure of temporal variation in temperature that is biologically relevant -- a challenging feat across diverse taxa, but worthy of future investigation.
 
 Our results further highlight the potential vulnerability of terrestrial ectotherms to climate change.
-Assuming changes in variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, smaller increases in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and].
+Assuming changes in variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, smaller increases in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and; @hoffmann2011climate].
 For example, under climate change we expect an increase in variance in physiological rates of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30%.
 There will obviously be limits to variance increases, and we predict that organisms closer to their upper thermal limits ($CT_{max}$) will have lower $lnVR_{Q_{10}}$ values compared to those farther away from $CT_{max}$.
-Some evidence points to possible differences across habitats in upper thermal limits already [@Gunderson2015-hz; @Pinsky2019-fn] making this a fruitful future question to ask.
+Some evidence points to possible differences across habitats in upper thermal limits already [@Gunderson2015-hz; @Pinsky2019-fn] making this a fruitful future question to explore.
 
@@
 
-Acclimation capacities are expected to differ between life-stages because of distinct of patterns of dispersal, habitat use and behaviour that force earlier life stages to cope with more variable environmental conditions which can also lead to developmental constraints on how physiological systems respond later in life [@martin2015age; @stearns1976life; @angilletta2009thermal; @noble2018developmental; @o2019developmental; @Pottier2022; @sinclair2016can].
+Acclimation capacities are expected to differ between life-stages because of distinct patterns of dispersal, habitat use and behaviour that force earlier life stages to cope with more variable environmental conditions which can also lead to developmental constraints on how physiological systems respond later in life [@martin2015age; @stearns1976life; @angilletta2009thermal; @noble2018developmental; @o2019developmental; @Pottier2022; @sinclair2016can].
 In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], and such costs can be magnified in late life reducing the capacity for plasticity [e.g., @rossi2019ageing].
@@
 To date, however, there are few studies that have focused on how variability in responses change.
-We would also encourage more empirical focus on this questions given the potential ecological and evolutionary implications.
+We would also encourage more empirical focus on this question given its potential ecological and evolutionary implications.
 
@@
 It is important to recognise, however, that these patterns do not necessarily apply to all populations.
-Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial study- and trait-level variance estimates.
+Substantial variation in acclimation responses and changes in variance exist among populations and traits, as evidenced by wide prediction intervals and substantial study- and trait-level variance estimates, which is consistent with our understanding of factors influencing variation in performance curves across taxa [@rezende2019thermal; @tattersall2012coping].
 Conservation efforts are often targeted at particular populations or species, and taxonomic differences are important in this context.
@@
 
-We would like to thank Malgorzata Lagisz for helping sort out the phylogeny used in our analysis and Enrico Rezende for discussions around the implementation of thermal performance curves.
-We are also grateful to three anonymous reviewers who all provided highly constructive feedback that greatly improved the manuscript.
+We would like to thank Malgorzata Lagisz for helping sort out the phylogeny used in our analysis and Enrico Rezende for discussions around alternative implementations of thermal performance curves.
+We are also grateful to three anonymous reviewers who all provided extremely constructive feedback that greatly improved the manuscript.
 
@@
 
-figs3 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs3, width = 16, height = 5.7, filename = "./output/figures/figS12.png")
-
-figs3 <- image_read("./output/figures/figS12.png")
-figs3
+figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
+ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS12.png")
+
+figS12 <- image_read("./output/figures/figS12.png")
+figS12
 ```

### 2024-07-17 ms.qmd
Adding note about how to also modify individual variation in performance (i.e height of curves)

@@
 alpha = -15 + rnorm(n, 0, ind_sd)
+# k=2 # note that, if we want to control the between individual differences in performance we can multiply curve by constant.
+Can do that and add variation and then all aspects of the curve can be modified.
 

### 2024-07-21 ms.qmd
Integrated all comments from Frank and Shin up to discussion

@@
 
-Climate change will result in warmer and more variable temperatures globally impacting physiological rates and function in ectothermic animals.
-Acclimation of physiological rates can help maintain function, however, how variance in physiological rates change with temperature has been ignored despite its potential ecological and evolutionary importance.
-We apply new effect sizes that quantify the extent to which both mean and variance in physiological rates change as temperature increases.
-Meta-analysing >1900 effects from 226 species, we show that variance in physiological rates increases at higher temperatures, but that the magnitude of change depends on habitat.
-Freshwater and marine ectotherms are capable of acclimation and have the greatest increase in physiological rate variance.
-In contrast, terrestrial ectotherms lack a capacity for acclimation and have a smaller increase in variance.
-Simulations suggest fundamental differences in among-individual variation in thermal breadth and optima of performance curves across habitats that may contribute to these differences.
-Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in physiological rates may provide less raw material for evolutionary adaptation.
+Climate change causes warmer and more variable temperatures globally, impacting physiological rates and function in ectothermic animals.
+Acclimation of physiological rates can help maintain function.
+However, it is unresolved how variance in physiological rates changes with temperature despite its potential ecological and evolutionary importance.
+We tested whether thermal variation affects physiological traits in ectotherms by conducting a meta-analysis (>1900 effects from 226 species), and applying new effect sizes that quantify how trait mean and variance change as temperature increases.
+We show that variance in physiological rates increases at higher temperatures, but that the magnitude of change depends on habitat.
+Freshwater and marine ectotherms are capable of acclimation and have the greatest increase in variance.
+In contrast, terrestrial ectotherms lack the capacity for acclimation and have smaller increases in variance.
+Simulations suggest that these patterns may result from differences in among-individual variation in thermal breadth and optima of performance curves across habitats.
+Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in variance may provide less raw material for evolutionary adaptation.
 Considering both acclimation capacity and variance in physiological rates side-by-side is therefore important for understanding how climate change will impact populations.
@@
 Acclimation therefore alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
-Acclimation, however, does not normally result in physiological rates returning to their original state [‘complete’ compensation - *sensu* @huey1999testing].
-Rather, increased physiological rates are usually only partially compensated [@huey1999testing; @Havird2020-mj].
-
-Acclimation is expected to evolve in populations when environmental variability is high but predictable and the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
-Thermal variation and predictability are known to differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and as such, we expect organisms within these habitats to vary in their capacity for plastic adjustments in physiology.
+Acclimation, however, does not necessarily result in complete compensation in response to environmental change [ *sensu* @huey1999testing].
+Rather, increased physiological rates are often only partially compensated [@huey1999testing; @Havird2020-mj].
+
+Acclimation is expected to evolve in populations experiencing high but predictable environmental variability, and when the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Thermal variation and predictability differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and it may be expected that organisms within these habitats vary in their capacity for acclimation.
 @rohr2018complex show relationships between acclimation capacity, latitude and body size suggesting climate could be an important driver of acclimation responses.
-In addition, species occupying terrestrial habitats have been shown to exhibit weaker acclimation abilities, and so, may be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
-In contrast, marine and freshwater habitats appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
+In addition, species occupying terrestrial habitats exhibit weaker acclimation capacities and, therefore may be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
+In contrast, marine and freshwater organisms appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
 However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological processes might also be impacted by higher temperatures.
 
-As mean physiological rates increase with temperature there is reason to believe that intrapopulation variability will also be impacted.
-Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so to should variation [i.e., Taylor's Law; @giometto2015sample].
-Differences in the shape of thermal performance curves (thermal breadth, maximal performance and thermal optima) can exacerbate among-individual variability at higher temperatures, which can also depend on different levels of biological organisation, environmental conditions and acclimation responses [@rezende2019thermal; @tattersall2012coping; @schulte2011thermal; @angilletta2009thermal].
-Presumably, increases in underlying variation in physiological rates should be related to varying robustness among individuals in how biochemical and physiological networks are affected by temperature [@schulte2011thermal].
-A focus on quantifying the shape of performance curves has often taken precedence over quantifying levels of among-individual variation in curves which has limited our understanding of their capacity to evolve.
-
-Importantly, changes in physiological rate variability is expected to have consequences on the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-Generally, more variable populations are predicted to be associated with broader niches, have increased growth rate, and decreased vulnerability to environmental change lowering extinction risk [i.e., "portfolio effects",@Schindler2010] [see also, @forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010; @portner2021climate].
-In addition, if phenotypic and genetic variation in physiological rates are correlated rates and linked to fitness, changes in variation may limit responses to selection impacting a populations capacity to evolve [@Pelletier2012; @hoffmann2011climate].
+As mean physiological rates increase with temperature it is likely that intrapopulation variability will also be impacted.
+Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so too should variability [i.e., Taylor's Law; @giometto2015sample].
+Differences in the shape of thermal performance curves (thermal breadth, maximal performance and thermal optima) can reflect among-individual variability at higher temperatures, which can also differ between different levels of biological organisation, environmental conditions, and acclimation responses [@rezende2019thermal; @tattersall2012coping; @schulte2011thermal; @angilletta2009thermal].
+Presumably, increases in variation in physiological rates reflects environment-mediated changes to underlying regulatory networks, which can lead to an increased variation in phenotypic outcomes [@costanzo2021environmental; @matthey2020plasticity; ].
+Quantifying levels of among-individual variation in thermal performance curves is important to understand their capacity to evolve, as well as the resilience of populations to environmental change [@careau2014individual].
+
+Importantly, changes in physiological rate variability are expected to have consequences for the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+Generally, more variable populations are predicted to be associated with broader niches, have increased growth rates, and decreased vulnerability to environmental change, lowering extinction risk [i.e., "portfolio effects",@Schindler2010] [see also, @forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010; @portner2021climate].
+In addition, if phenotypic and genetic variation in physiological rates are correlated and linked to fitness, reduced phenotypic variation may limit responses to selection and reduce the capacity of populations to evolve [@Pelletier2012; @hoffmann2011climate].
 Therefore, maintaining intrapopulation variability in physiological rates in a warmer world may be important for population resilience to climate change.
 
-Here, we use meta-analysis to re-evaluate the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We then developed new effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions: 1) How much is variance in physiological rates expected to change, if at all, as temperatures rise?
-2) Are temperature effects on plastic adjustments in physiological rates larger than changes in variance across aquatic and terrestrial ectotherms?
-3) How does acclimation and changes in variance relate to different life-stages and types of traits, and does this depend on habitat?
-4) Are changes in plasticity or variance in physiological rates impacted by past climate history?
+Here, we use meta-analysis to establish the current state-of-knowledge of the extent to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
+We then developed new effect sizes to quantify how variance in physiological rates changes with temperature to ask the following questions regarding acclimation-induced changes in trait means and variances: 1) Does variance in physiological rates change as temperatures rise?
+2) Are temperature effects on means of physiological rates greater than changes in variance across aquatic and terrestrial ectotherms?
+3) How do changes in trait mean and variance relate to different life-stages, traits, and habitats?
+4) Are changes in mean and variance of physiological rates impacted by past climate history?
 5) How are variances in physiological rates expected to change under climate change?
@@
 
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures
-after having been acclimated (or acclimatized) at these temperatures.
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
 We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
 We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-For full details on the search protocol see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
+For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
 
@@
 
-We extracted means, standard deviations, and sample sizes for physiological rates at the two test temperatures ([@fig-concept]A).
-If there were more than two test temperatures, we chose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
+We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
+If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
 We extracted these data from text, tables or figures of a given paper.
@@
 #| fig-height: 12
-#| fig-cap: "Calculations of acute and acclimation effect sizes.
+#| fig-cap: "Calculations of acute and acclimation $lnVR_{Q_{10}}$ and $lnRR_{Q_{10}}$.
 (A) Two idealised thermal performance curves for animals held at 'cold' ('blue') temperatures and warm ('red') temperatures.
@@
 R2.1 and R2.2 are the rates and associated SD (subscripted) for the warm acclimated animals at temperature 1 and 2, respectively.
-An example of how acute and acclimation $lnCVR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right-hand side of the figure with reference to each of the four possible groups.
-Note that we use $lnCVR_{Q_{10}}$ because it makes use of all avilable data.
+An example of how acute and acclimation $lnVR_{Q_{10}}$ and $lnRR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right-hand side of the figure with reference to each of the four possible groups.
 Two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
@@
 
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes, of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
 
@@
 where parameters are defined above.
-@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) across a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
 As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it allows one to standardize changes in variance as the mean changes as follows:
+As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
 
@@
 We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make certain assumptions about mean-variance relationships, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
 
@@
 For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes suggest that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
 Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
@@
 We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-This included the duration of acclimation in days given that acclimation responses are expected to depend on how long chronic temperature exposure occurs (longer exposure = better acclimation response) [@Seebacher2015-wi].
+This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
 We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
@@
 This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
-We also present 95% prediction intervals which describe the expected distribution of effects from future studies [@Nakagawa2021-ls; @Noble2022-ty].
+We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
 
@@
 In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than both freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-However, rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have faster rates of acclimation than fishes; See @Einum2023-lz].
-Nonetheless, to control for these possible differences, acclimation time was mean-centered (mean = 0) and included in all our models, though it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
-
-In addition to acclimation, all our models corrected for the possibility of the log-linearity assumption of our effect sizes being violated ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
-We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear than we would see a decrease in average effect size for studies applying higher temperature treatments because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of such an approach means that we could still take advantage of the excellent properties of $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we, *a priori*, expected that each species will vary in their thermal performance curve and the chosen temperatures experimentally manipulated along the performance curve.
-To improve model interpretation, we also mean-centered the maximum temperature and included it in our models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
+To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
+
+In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
+We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
+We mean-centered the maximum temperature and included it in our models.
 
 With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average level of acclimation time (i.e.,
+All estimates from our models are therefore conditioned on an average acclimation time (i.e.,
 `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23°C) across the dataset.
 
-We first tested the degree to which the difference in acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effects varied by
-habitat type (i.e., terrestrial, freshwater, and marine).
+We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$
-indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ suggests organisms are not capable of physiological plasticity [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would imply that changes in between individual variation in physiological rates across 10°C differ depending on whether acute or acclimation responses are measured.
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
+In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
 
 Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
-We expected that whole-organism traits would be more likely to maintain relative variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
+We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
 
@@
 
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by a populations climate variability (CV).
-We only used $lnRR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on the plastic adjustments to physiological rates.
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV).
+We only used $lnRR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses.
 We used all $lnVR_{Q_{10}}$ data because there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe climate would impact acclimation and acute $lnVR_{Q_{10}}$ differently.
 We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
-We also explored how environmental predictability, as measured by how correlated successive temperatures at a given location were across months, might also explain capacity for acclimation.
+We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
 However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report on these results for a single lag (1 month) in the *Supplementary Materials* but note they do not differ from our CV analysis.
-
-#### *Modelling how climate change will impact relative variance in physiological rates*
-
-To understand the consequences of human-induced climate change on the potential to impact variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as "Model 6").
+As such, we report a simple analysis in the *Supplementary Materials* but note they do not differ from our CV analysis.
+
+#### *Modelling how climate change can impact relative variance in physiological rates*
+
+To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
 We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
@@
 Our model included random effects of species, trait, phylogeny and study.
-We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at the specific populations latitude and longitude.
-To do this, we first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C as follows:
+We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
+We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
 
@@
 
-@eq-lCVRpred turned the expected change across 10°C to 1°C.
 We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
@@
 We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
-Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
+Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
+However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
 As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
-Given that their was no evidence for publication bias results are presented in the *Supplementary Materials*.
+There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
 
 ### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
-To better understand the characteristics of performance curves of a population that would lead to our observed changes in variance across temperature we conducted a simple simulation that varied among-individual variation in performance curve parameters.
+
+We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures.
+The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
 To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
@@
 
-where $T$ is the temperature gradient, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the performance function or rate variation (see @fig-sim in *Supplementary Materials* for example curves).
+where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
 We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
-We also varied $\alpha$, but this did not impact our conclusions and so we keep among-individual variation fixed.
-From the population of performance curves, we took the standard deviation at two temperatures 10°C apart (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify parameter space that matched observed patterns in our empirical data.
+We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
+From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
 
@@
     t_RR_mean <- (t_acute * N[5,"n"][[1]] + t_acclim * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_RR_mean)
+
+  # Rates differ?
+    t_f_rates <- (t_RR_mean - f_RR_mean)
+    t_m_rates <- (t_RR_mean - m_RR_mean)
 
@@
 and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
-We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
+We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to acclimation responses (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
 The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to
@@
 However, on average they were in the same direction and only differed by ~10%.
-As such, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
-
-Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzyme rates ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
+Hence, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
+
+Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`), metabolic enzyme rates ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of locomotor speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
 
@@
 #| echo: false
-#| fig-cap: "Phylogenetic distribution of acute and acclimation $lnRR_{Q_{10}}$/$lnVR_{Q_{10}}$ estimates across major habitats.
-The total number of acute and acclimation  $lnRR_{Q_{10}}$/$lnVR_{Q_{10}}$ effect sizes are indicated by the coloured bars as well as whether the taxa are marine, freshwater or terrestrial.
+#| fig-cap: "Phylogenetic distribution of acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ estimates across major habitats.
+The total number of acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes are indicated by the coloured bars, and the colouring at the tips of the phylogeny indicates marine, freshwater, and terrestrial habitats.
 Silhouettes are only representative taxa of major clades within the tree."
@@
 
-Effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
+Results from "Model 1" (see “Meta-Analysis” above) show that effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
 Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`%, 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95%
-CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%).
-These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
-All results are from Model 1 (see “Meta-Analysis” above).
-
-Capacity for acclimation depended on the habitat.
+CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%). These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
+
+Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)` 95%CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)` 95%CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)` 95%CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)` 95%CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)` 95%CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `p_value(pmcmc(t_f_rates))`) ("Model 2").
+However, capacity for acclimation depended on the habitat.
 Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
 In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
-All results are from Model 2 (see “Meta-Analysis” above).
-
-Across habitats the extent to which whole-organism versus biochemical processes acclimated varied ("Model 3"; [@fig-btrait]A-C).
-Biochemical processes were more effective at acclimating compared to whole-organism traits for ectotherms occupying marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated in freshwater ectotherms ([@fig-btrait]C).
-Unsurprisingly, neither trait category showed evidence of acclimation in terrestrial ectotherms ([@fig-btrait]A).
-
-Acclimation capacity did not vary consistently by life-history stage with no differences between $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults appeared to be able to acclimate to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
-When comparing between acute and acclimation responses between adults and juveniles irrespective of effect type there were also no differences within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
+
+Across habitats, the extent to which whole-organism versus biochemical traits acclimated varied ("Model 3"; [@fig-btrait]A-C).
+Biochemical traits acclimated to a greater extent compared to whole-organism traits in marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated similarly in freshwater ectotherms ([@fig-btrait]C).
+Neither trait category acclimated in terrestrial ectotherms ([@fig-btrait]A).
+
+Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
+Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
 
@@
 #| label: fig-2
-#| fig-cap: "(A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
-(B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
-For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-Sample sizes are the same for panel A and B.
+#| fig-cap: "Meta-analysis results for different habitats.
 In both panels, thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
@@
 $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
-For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles."
+(A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
+Overall mean physiological rates ($\\mu$) across the habitats are provided in the results for simplicity and only contrasts between acute and acclimation $lnRR_{Q_{10}}$ are shown (B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+Sample sizes are the same for panel A and B.
+For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles.
+"
 #| warning: false
@@
 #| label: fig-btrait
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
+#| fig-cap: "Meta-analysis results for organismal and biochemical trait categories.
+Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 #| label: fig-cvrlh
-#| fig-cap: "Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
+#| fig-cap: "Meta-analysis results for different life stages.
+Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`% (95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))`) increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
-The relative differences between habitats were even larger when considering $lnCVR_{Q_{10}}$, which controls for changes in mean rates (See *Supplementary Materials*).
+Analysis of $lnCVR_{Q_{10}}$, which accounts for changes in mean physiological rates, also showed that the relative variance for terrestrial ectotherms decreased compared to marine and freshwater ectotherms, suggesting that increases in variance are less than expected for ectotherms occupying terrestrial habitats (See *Supplementary Materials*).
 
 Physiological rate variance increased significantly more in freshwater compared to terrestrial ectotherms for acute responses ($\beta$ = `r mean(f_t_c_a)`, 95% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance ($\beta$ = `r mean(f_t_c_aclim)`, 95% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`).
-While marine ectotherms had larger increases in physiological rate variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
-Marine and freshwater did not differ in how much variance changed at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
+While marine ectotherms had larger increases in variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
+Marine and freshwater habitats did not differ in the extent of variance increases at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
 There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B).
@@
 $lnVR_{Q_{10}}$ values from our simulations matched our empirical results in particular areas of parameter space (@fig-sim2).
-For a given between individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower levels of between individual variation in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
-In contrast, terrestrial ectotherms are expected to have higher levels of between individual variation in thermal breadth when controlling for between individual variation in thermal optima ([@fig-sim2]).
+For a given among-individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower among-individual variance in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
+In contrast, terrestrial ectotherms are expected to have higher levels of among-individual variance in thermal breadth when controlling for among-individual variance in thermal optima ([@fig-sim2]).
 
@@
 #| fig-align: center
-#| fig-cap: "Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying individual variation in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal optima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
+#| fig-cap: "Results from sensitivity analysis.
+Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal optima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
 In all simulations, population parameters were $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{\\delta}$ and $\\sigma_{\\sigma}$.
@@
 Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
-Variance increases for biochemical traits is reduced during acclimation in marine ectotherms ([@fig-btrait]E).
+Variance increases for biochemical traits was reduced during acclimation in marine ectotherms ([@fig-btrait]E).
 
@@
 #| fig-align: center
-#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A-C) and $lnVR_{Q_{10_{acclim}}}$ (E-G) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
+#| fig-cap: "Past climate variability did not predict acclimation responses.
+Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A-C) and $lnVR_{Q_{10_{acclim}}}$ (E-G) as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
@@
 Globally, there was a clear bias towards species in the Northern Hemisphere ([@fig-fig6]A-C).
-Projected changes in physiological rate variance were highly variable across the globe, however, variance was predicted to increase to some extent at `r (sum(increases$n, na.rm = TRUE) / length(increases$n[complete.cases(increases$n)]))*100`% of the locations.
-
-Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 46% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
+Projected changes in physiological rate variance were highly variable across the globe, however, variance was predicted to increase at all locations.
+
+Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explained ~ 46% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
 Climate change is predicted to result, on average, in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% increase in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$f))`), a `r abs(lapply(mean_perc_habitat_vr, mean)$m)`% increase in marine systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$m))`), and a `r abs(lapply(mean_perc_habitat_vr, mean)$t)`%  increase in terrestrial systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5 climate scenario ([@fig-fig6]D).
@@
 #| message: false
-#| fig-cap: "Model predictions for the expected change in $lnVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
+#| fig-cap: "Potential effects of climate change on trait variance.
+Model predictions for the expected change in $lnVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms.
 Predicted change in physiological rate variance for each population based on current temperatures (average from 2018-2022; A-C) as well as the expected change from current temperatures based on future temperature predictions (average from 2096-2100, D).
-Future climate predictions are the reduction in variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change)."
+Future climate predictions are the increase in variance expected under a RCP8.5 climate scenario relative to current climate conditions (% change)."
 

### 2024-07-21 ms.qmd
Fixed up some text

@@
 With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average acclimation time (i.e.,
-`r mean(data_wide$acclim_period, na.rm = TRUE)` days) and maximum temperature (i.e., 23°C) across the dataset.
+All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
 
@@
 
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV).
-We only used $lnRR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses.
-We used all $lnVR_{Q_{10}}$ data because there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$ and we had no *a priori* reason to believe climate would impact acclimation and acute $lnVR_{Q_{10}}$ differently.
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
+We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
 We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
@@
 However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report a simple analysis in the *Supplementary Materials* but note they do not differ from our CV analysis.
+As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
 
@@
 
-We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures.
+We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
 The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
@@
 
-Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)` 95%CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)` 95%CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)` 95%CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)` 95%CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)` 95%CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `p_value(pmcmc(t_f_rates))`) ("Model 2").
+Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
 However, capacity for acclimation depended on the habitat.
@@
 Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`% (95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))`) increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
-Analysis of $lnCVR_{Q_{10}}$, which accounts for changes in mean physiological rates, also showed that the relative variance for terrestrial ectotherms decreased compared to marine and freshwater ectotherms, suggesting that increases in variance are less than expected for ectotherms occupying terrestrial habitats (See *Supplementary Materials*).
+Analysis of $lnCVR_{Q_{10}}$, which accounts for changes in mean physiological rates, also showed that the relative variance for terrestrial ectotherms decreased compared to marine and freshwater ectotherms, suggesting that increases in variance are less than expected for ectotherms occupying terrestrial habitats (See *Supplementary Materials*, @fig-s1).
 
@@
 There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B).
-Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* scaling analyses, @tbl-slopes & @fig-mv, and analyses with $lnCVR_{Q_{10}}$, @fig-s1).
+Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* scaling analyses, @tbl-slopes & @fig-mv).
 
@@
 Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
-Our results uncover an hitherto unrecognised dynamic where the limited benefits of acclimation are potentially compensated for by increases in trait variance that may have impacts on how ectotherm populations across these different habitats will be able to adapt to increased temperatures.
+Our results uncover an hitherto unrecognised dynamic where the benefits of partial acclimation are paralleled by increases in trait variance that may have impacts on how ectotherm populations across different habitats will be able to adapt to increased temperatures.
 
@@
 Our findings confirm previous results that quantify the different capacity of terrestrial, marine and freshwater ectotherms to acclimate [@Seebacher2015-wi; @Gunderson2015-hz; @morley2019physiological].
-Our analysis generally supports that of @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
+Our analysis confirms findings by @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
 These consistent results are interesting given the different physiological traits measured in these meta-analyses (i.e., thermal limits versus physiological rates).
 
-The change in acclimation $Q_{10}$ we found with our expanded dataset (34% increase in effects) was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi], possibly due to the use of newly derived $Q_{10}$ effect sizes that allow us to control for sampling variance.
+The change in acclimation $Q_{10}$ we found in our expanded dataset was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi].
+The difference observed in terrestrial ectotherms between studies may be due to additional data from terrestrial species added in our analysis, and to the use of newly derived $Q_{10}$ effect sizes that allowed us to control for sampling variance.
 Greater capacity for acclimation in aquatic organisms may be the result of fewer opportunities for behavioural thermoregulation in aquatic environments making physiological remodeling important for maintaining homeostasis [@Gunderson2015-hz; @morley2019physiological].
-Importantly, even though marine and freshwater ectotherms were capable of partial acclimation, on average, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6), suggesting acclimation will provide limited scope for aquatic ectotherms to adjust their physiology to higher temperatures.
-
-Biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organisms traits as predicted, but only for marine ectotherms, presumably because of the less complicated physiological networks that underlie specific biochemical processes [@schulte2011thermal].
-However, this prediction did not hold up generally with both whole-organism and biochemical traits being equally likely to acclimate in freshwater ectotherms, which may be due to the different types of biochemical processes measured in the two habitats.
-
-### ***Increased variability in physiological rates across habitats: insights into the adaptive potential of physiological processes in the face of climate change?***
-
-Contrary to acclimation capacity variance in physiological rates increased across habitats with effect sizes being 3-5x larger than those observed for acclimation.
+Importantly, even though marine and freshwater ectotherms were capable of partial acclimation, on average, the effect size was small (amounting to $Q_{10}$ dropping from ~1.8 to 1.6), suggesting that acclimation provides limited scope for aquatic ectotherms to adjust their physiology to higher temperatures.
+
+Biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organism traits as predicted, but only for marine ectotherms, presumably because of the less complicated physiological networks that underlie specific biochemical processes [@schulte2011thermal].
+However, whole-organism and biochemical traits acclimated to the same extent in freshwater ectotherms.
+Differences between marine and freshwater ectotherms do not appear to be related to the types of traits measured across the habitats but rather that the traits responded differently.
+However, it is important to note that whole-organism traits in marine ectotherms did respond in the same direction and of a similar magnitude to freshwater ectotherms, so it is possible the difference in marine habitats is simply a sampling artefact.
+
+### ***Increased variability in physiological rates across habitats: adaptive potential of physiological processes in the face of climate change?***
+
+Contrary to acclimation capacity variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation of mean trait values.
 Mechanistically, it is unclear what exactly is contributing to the increased variation in physiological rates at higher temperatures, but it is likely the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein; @schulte2011thermal].
@@
 Such challenges (among others) may expose among-individual variation within a population.
-Indeed, even acclimation itself can impact among-individual variation, possibly through changes in individual performance curves [@schulte2011thermal].
-Indeed, we find evidence to that effect given that biochemical processes in marine organisms were both more likely to acclimate and have reduced variance increases compared to acute responses.
-However, this was not a general phenomena given that freshwater ectotherms were able to maintain high variance despite being able to acclimate.
+Indeed, there is considerable variation in acclimation capacity among individuals which would increase variance in thermal performance curves within populations [@loughland2020differences; @schulte2011thermal].
 
 Importantly, increased variance in physiological rates was not equal among terrestrial, marine and freshwater ectotherms, with increases in variance being higher in freshwater ectotherms (~60% increase / 10°C) compared to terrestrial ectotherms (~36% increase / 10°C).
-One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ [@angilletta2009thermal; @huey1989evolution; @tattersall2012coping; @rezende2019thermal].
+One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ between habitats [@angilletta2009thermal; @huey1989evolution; @tattersall2012coping; @rezende2019thermal].
 Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal optima and breadth across habitats making this hypothesis plausible.
-Such patterns across habitats are expected given that terrestrial ectotherms should be adapted to warmer and more variable environments.
+Such patterns across habitats are expected given that terrestrial ectotherms should be adapted to more extreme and variable thermal environments.
 Theoretical models also suggest that populations with greater temporal environmental variability exhibit greater thermal breadth [@lynch1987environmental].
-While we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected, such analyses will depend on an appropriate measure of temporal variation in temperature that is biologically relevant -- a challenging feat across diverse taxa, but worthy of future investigation.
+However, we did not find support that thermal variation co-varied with $lnVR_{Q_{10}}$ (see below), as would be expected.
+The relevance of analyses of thermal variability will depend on temporal variation in temperature that is biologically relevant – a challenging feat across diverse taxa, but worthy of future investigation.
 
 Our results further highlight the potential vulnerability of terrestrial ectotherms to climate change.
-Assuming changes in variation in physiological rates are underpinned by genetic variation, and there is a genetic correlation with fitness, smaller increases in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and; @hoffmann2011climate].
+Assuming that changes in variation in physiological rates are underpinned by genetic variation, and that there is a genetic correlation with fitness, smaller increases in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and; @hoffmann2011climate].
 For example, under climate change we expect an increase in variance in physiological rates of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30%.
 There will obviously be limits to variance increases, and we predict that organisms closer to their upper thermal limits ($CT_{max}$) will have lower $lnVR_{Q_{10}}$ values compared to those farther away from $CT_{max}$.
-Some evidence points to possible differences across habitats in upper thermal limits already [@Gunderson2015-hz; @Pinsky2019-fn] making this a fruitful future question to explore.
+Some evidence points to possible differences across habitats in upper thermal limits already [@Gunderson2015-hz; @Pinsky2019-fn], making this a fruitful future question to explore.
 
@@
 Acclimation capacities are expected to differ between life-stages because of distinct patterns of dispersal, habitat use and behaviour that force earlier life stages to cope with more variable environmental conditions which can also lead to developmental constraints on how physiological systems respond later in life [@martin2015age; @stearns1976life; @angilletta2009thermal; @noble2018developmental; @o2019developmental; @Pottier2022; @sinclair2016can].
-In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], and such costs can be magnified in late life reducing the capacity for plasticity [e.g., @rossi2019ageing].
+In addition, plastic responses are also expected to be costly [@angilletta2009thermal; @Dewitt1998], such costs can be magnified in later life reducing the capacity for plasticity [e.g., @rossi2019ageing].
 These processes can also result in changes to intrapopulation variation in physiological rates at higher temperatures but the direction of change between early and adult life stages is likely to depend on the costs of adjusting physiological processes, energy reserves at different life stages, and the extent to which early life experiences constrain plasticity.
 
-Despite these expectations, more broadly, we show little difference between early and late life acclimation capacities and little change in the variance in physiological rates across habitats.
-This may not be too surprising given that such responses are likely context or trait dependent [@carter2020life; @moghadam2019heat].
+Despite these expectations, our analysis does not show any significant differences between early and late life acclimation capacities and little change in the variance in physiological rates across habitats.
+This may not be too surprising given that such responses are likely context or trait-dependent [@carter2020life; @moghadam2019heat].
 The lack of differences we observed may be because both juvenile and adult animals occupy similar thermal niches, disperse to a similar extent and exhibit comparable thermoregulatory behaviors making physiological responses to temperature similar.
-It is possible that temperatures experienced earlier in development (e.g., egg or larval stages) exhibit greater capacity for acclimation because of limited dispersal capabilities and very different habitats.
-Some empirical evidence supports this in insects.
-For example, @moghadam2019heat showed that larval *Drosophila* were more plastic in their heat hardening responses compared to adults.
 A focus on collecting more detailed information on behaviour, dispersal and thermal environments experienced by different life stages is likely to provide a more complete picture on when plasticity differs.
-To date, however, there are few studies that have focused on how variability in responses change.
-We would also encourage more empirical focus on this question given its potential ecological and evolutionary implications.
-
-### ***No signature of past climate on capacity for physiological plasticity or changes in variance***
-
-Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when fluctuations are predictable over time to make environmental cues more reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
-Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] might suggest that plasticity is more likely to evolve in terrestrial environments.
-However, if thermal variability is too high and unpredictable, the rates of acclimation slow, and there are costs associated with re-modelling physiological processes [which seem likely, @angilletta2009thermal] then we would instead expect canalised responses [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
+We would also encourage more empirical focus on this question and its potential ecological and evolutionary implications.
+
+### ***Past climate does not influence capacity for physiological acclimation or changes in variance***
+
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when fluctuations are predictable over time to make environmental cues reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] therefore suggest that plasticity is more likely to evolve in terrestrial environments.
+However, if thermal variability is too high and unpredictable, the rates of acclimation decrease and there are increased costs associated with re-modelling physiological processes [@angilletta2009thermal] it would instead be expected that phenotypes are canalised during development [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
 The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@hendry2016key; @Leung2020].
@@
 However, other analyses on heat tolerance limits have found relationships between latitude (a proxy for seasonality) [@morley2019physiological] or even direct measures of thermal variability [@verberk2024heat].
-@Seebacher2015-wi also found evidence that acclimation capacity was related to a populations thermal variability, however, relationships depended on the habitat and traits in question.
+@Seebacher2015-wi also found that acclimation capacity was related to a populations thermal variability, however, relationships depended on the habitat and traits in question, and tropical animals showed greater acclimation capacity.
 Discrepancies across studies could be related to the taxa included in analyses [e.g., @morley2019physiological], different traits or possibly the fact that different climate projections/models are being used to quantify thermal variability.
-Modelling realistic microenvironments across such diverse taxa is also challenging because it is unclear what the most appropriate spatial and temporal scale might be that is of evolutionary relevance.
+Latitude covaries with a diversity of different ecological attributes aside from temperature [@louthan2021climate], which means it may be capturing other aspects of the environment that affect acclimation capacity.
+In addition, modelling realistic microenvironments across such diverse taxa is also challenging because it is unclear what the most appropriate spatial and temporal scale might be that is of evolutionary relevance.
 Historical temperature time series' may not be representative of the selective environment a population has experienced making relationships between capacity for acclimation and temperature variability (or predictability) difficult to pin down.
@@
 
-It is clear that many fascinating questions remain unanswered that will require greater focus on the consequences of
-changes in variance (rather than just the mean). Particularly interesting questions include: How do differences in physiological rate
-variance change energy flow across trophic levels within communities?
+Many fascinating questions remain unanswered that will require greater focus on the consequences of
+changes in variance (rather than just the mean).
+Particularly interesting questions include: How do differences in physiological rate variance change energy flow across trophic levels within communities?
 What are the biochemical, cellular, and physiological mechanisms that underlie differences in physiological rate variance across habitats?
@@
 
-DWAN is supported by an Australian Research Council (ARC) Future Fellowship (FT220100276) and ARC Discovery Project (DP210101152).
-SN is supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
+DWAN is supported by an Australian Research Council (ARC) Future Fellowship (FT220100276) and ARC Discovery Project DP210101152.
+SN is supported by ARC Discovery Project Grants DP210100812 and DP230101248.
+FS is supported by ARC Discovery Project Grant DP220101342.
 
@@
 
-Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge]. We also cross-checked papers we found in our searches
-with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
+Our search resulted in 1,321 papers for screening in Rayyan [@Ouzzani2016-ge].
+We also cross-checked papers we found in our searches with a recent paper by @Havird2020-mj, which also updates the dataset of @Seebacher2015-wi's.
 We included any papers that were missed between our searches and those of @Havird2020-mj.
@@
 Note that @Seebacher2015-wi included a total of 205 publications, however, not all these contained the necessary statistics we needed to derive effect sizes and associated sampling variances (see below).
-While we may have
-missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive
-dataset. As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
+While we may have missed papers, our goal was to obtain a large representative (and unbiased) sample of acclimation research rather than a comprehensive dataset.
+As such, our database represents the most up-to-date dataset used since @Seebacher2015-wi to answer questions on physiological rates across ectotherms.
 
@@
 
-$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on
-physiological rates (or changes in relative variance) is log-linear.
+$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in relative variance) is log-linear.
 While this is likely in our data given that we restricted our analysis of $Q_{10}$ to standard operating temperatures for a given species, it may not always be satisfied given the diversity of species in our dataset.
@@
 
-Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as
-estimates of thermal predictability (i.e., autocorrelation).
+Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
 To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
@@
 
-Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv).
+Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear (@fig-mv).
 Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (@tbl-slopes), however, ectotherms from terrestrial habitats had much shallower slopes than marine and freshwater ectotherms, particularly at higher treatment temperatures, indicating increased mean physiological rates generally do not result in higher between individual variance in physiological rates (@tbl-slopes).
@@
 Either way, the relative differences are quite similar.
-Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with
-higher temperatures across all habitat types, with terrestrial ectotherms having the largest decrease in relative variance (@fig-s1).
+Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with higher temperatures across all habitat types, with terrestrial ectotherms having the largest decrease in relative variance (@fig-s1).
 There were also no major differences in the relative differences among broad trait categories (@fig-cvrbtrait) or life-history stages (@fig-lncvrlh).
@@
 We then modeled how this measure of thermal predictability was related to plasticity.
+We found no relationship between our estimate of environmental predictability and effect sizes (@fig-4).
 

### 2024-07-23 ms.qmd
Few updated sentences
Fixed sentence

@@
 Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
-Our results uncover an hitherto unrecognised dynamic where the benefits of partial acclimation are paralleled by increases in trait variance that may have impacts on how ectotherm populations across different habitats will be able to adapt to increased temperatures.
+Our results uncover an hitherto unrecognised dynamic where the benefits of partial acclimation are paralleled by increases in trait variance that depend on habitat in ways that may have impacts on how ectotherm populations will be able to adapt to increased temperatures.
 
@@
 For example, under climate change we expect an increase in variance in physiological rates of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30%.
+Importantly, responses to selection will also depend on the magnitude and direction of genetic covariances with other traits, which need consideration.
 There will obviously be limits to variance increases, and we predict that organisms closer to their upper thermal limits ($CT_{max}$) will have lower $lnVR_{Q_{10}}$ values compared to those farther away from $CT_{max}$.

### 2024-09-03 ms.qmd
Updated with plos format

@@
 bibliography: ./bib/refs.bib
-csl: ./bib/ecology-letters.csl
+csl: ./bib/plos.csl
 format:
@@
     reference-doc: ./bib/template.docx
-    output-file: "ms_revised.docx"
+    output-file: "ms_plos.docx"
 editor_options: 

### 2024-09-11 ms.qmd
Update MS with slightly new format. Need to fix formatting some more
Incorporated suggestions from R2

@@
 For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
-However, longer-lasting (days-weeks) temperature increases that move environmental conditions away from thermal optima of physiological rate functions (i.e., thermal performance curves) can be mitigated by acclimation, which adjust reaction rates [@Seebacher2015-wi; @Havird2020-mj].
+However, longer-lasting (days-weeks) temperature increases that move environmental conditions away from thermal maxima of physiological rate functions (i.e., thermal performance curves) can be mitigated by acclimation, which adjust reaction rates [@Seebacher2015-wi; @Havird2020-mj].
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
@@
 Acclimation, however, does not necessarily result in complete compensation in response to environmental change [ *sensu* @huey1999testing].
-Rather, increased physiological rates are often only partially compensated [@huey1999testing; @Havird2020-mj].
+Rather, increased physiological rates are often only partially compensated such that ectotherms acclimated to, and measured at, warmer temperatures (R2.2 in @fig-concept) have higher physiological rates than those acclimated to, and measured at, cooler temperatures (R1.1 in @fig-concept) [@huey1999testing; @Havird2020-mj].
 
@@
 Positive mean-variance relationships are common across biology suggesting that, as physiological rates increase with temperature, so too should variability [i.e., Taylor's Law; @giometto2015sample].
-Differences in the shape of thermal performance curves (thermal breadth, maximal performance and thermal optima) can reflect among-individual variability at higher temperatures, which can also differ between different levels of biological organisation, environmental conditions, and acclimation responses [@rezende2019thermal; @tattersall2012coping; @schulte2011thermal; @angilletta2009thermal].
+Differences in the shape of thermal performance curves (thermal breadth, maximal performance and thermal maxima) can reflect among-individual variability at higher temperatures, which can also differ between different levels of biological organisation, environmental conditions, and acclimation responses [@rezende2019thermal; @tattersall2012coping; @schulte2011thermal; @angilletta2009thermal].
 Presumably, increases in variation in physiological rates reflects environment-mediated changes to underlying regulatory networks, which can lead to an increased variation in phenotypic outcomes [@costanzo2021environmental; @matthey2020plasticity; ].
@@
 5) How are variances in physiological rates expected to change under climate change?
-
-## **Materials and Methods**
-
-### *Literature collection*
-
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
-
-### *Data Compilation*
-
-We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
-If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
-We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
-We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
-For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
-If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
-If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
-When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
-
-### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
-
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
-Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
-
-```{r, fig-concept}
-#| label: fig-concept
-#| fig-width: 8
-#| fig-height: 12
-#| fig-cap: "Calculations of acute and acclimation $lnVR_{Q_{10}}$ and $lnRR_{Q_{10}}$.
-(A) Two idealised thermal performance curves for animals held at 'cold' ('blue') temperatures and warm ('red') temperatures.
-Shaded blue and red areas are the thermal optima of the performance curves.
-Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20°C and $T_{2}$ = 30°C) for both curves.
-At each temperature a mean physiological rate (R) (points) and its standard deviation (SD) (error bars above and below mean) are estimated.
-R1.1 and R1.2 are the rates and associated SD (subscripted) for the cold acclimated animals at temperature 1 and 2, respectively.
-R2.1 and R2.2 are the rates and associated SD (subscripted) for the warm acclimated animals at temperature 1 and 2, respectively.
-An example of how acute and acclimation $lnVR_{Q_{10}}$ and $lnRR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right-hand side of the figure with reference to each of the four possible groups.
-Two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
-(B) Species are expected, *a priori*, to vary in their thermal performance curves (thin lines) around an average (thick black line).
-We restricted our data to areas of each species' performance curve that fell within the natural thermal range of the species (thick lines on each species-level curve).
-However, given it was not possible to measure the full performance curve for each species some test temperatures within studies may have converged on or moved past the thermal optima.
-In such cases, we expected our $Q_{10}$ effect sizes to be smaller as indicated by comparing the black dashed lines to grey dashed lines."
-
-fig_concept <- magick::image_read("output/figures/fig1.png")
-plot(fig_concept)
-```
-
-#### *Comparing changes in mean physiological rates*
-
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
-
-$$
-  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10}
-
-Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
-Log transformation of this ratio makes the effect size normally distributed.
-@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
-The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
-
-$$
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-Vlnq10}
-
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
-
-#### *Comparing variance in physiological rates*
-
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
-
-$$
-lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10VR} $$
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slnq10VR}
-
-where parameters are defined above.
-@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
-As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR} $$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$.
-We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
-
-#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
-
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
-For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
-For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
-Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
-We test and control for any violations of these assumptions in our analysis (see below).
-
-### *Moderator Variables*
-
-We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
-We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
-Traits that could not be categorised into these two we classified as ‘Other’.
-
-### *Meta-Analysis*
-
-We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
-We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021-ls; @nakagawaorchard].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
-In all cases, frequentist and Bayesian models resulted in the same conclusions.
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
-We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-
-#### *Multi-level Meta-analysis (MLMA) Models*
-
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
-We refer to this model structure as “Model 1” in the results.
-Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
-We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
-`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
-`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
-We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
-As such, we used an intermediate value of p = 0.7.
-We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
-`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
-
-#### *Multi-level Meta-regression (MLMR) Models*
-
-After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
-In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
-
-In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
-We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal optima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
-We mean-centered the maximum temperature and included it in our models.
-
-With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
-
-We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
-Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
-
-Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
-We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
-
-Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
-We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
-
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
-We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
-We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
-We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
-However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
-
-#### *Modelling how climate change can impact relative variance in physiological rates*
-
-To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
-We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
-Our model included random effects of species, trait, phylogeny and study.
-We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
-We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
-
-$$
-lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
-$$ {#eq-lCVRpred}
-
-We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
-
-### *Publication Bias*
-
-We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
-Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
-However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
-There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
-
-### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
-
-We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
-The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
-To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
-
-$$
-P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
-$$ {#eq-sim}
-
-where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
-We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
-We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
-From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
 
@@
 
+```{r, fig-concept}
+#| label: fig-concept
+#| fig-width: 8
+#| fig-height: 12
+#| fig-cap: "Calculations of acute and acclimation $lnVR_{Q_{10}}$ and $lnRR_{Q_{10}}$.
+(A) Two idealised thermal performance curves for animals acclimated at 'cold' ('blue') temperatures and warm ('red') temperatures.
+Shaded blue and red areas are the thermal maxima of the performance curves.
+Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20°C and $T_{2}$ = 30°C) for both curves.
+At each temperature a mean physiological rate (R) (points) and its standard deviation (SD) (error bars above and below mean) are estimated.
+R1.1 and R1.2 are the rates and associated SD (subscripted) for the cold acclimated animals at temperature 1 and 2, respectively.
+R2.1 and R2.2 are the rates and associated SD (subscripted) for the warm acclimated animals at temperature 1 and 2, respectively.
+An example of how acute and acclimation $lnVR_{Q_{10}}$ and $lnRR_{Q_{10}}$ are calculated from the treatments within the study is provided on the right-hand side of the figure with reference to each of the four possible groups.
+Two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
+(B) Species are expected, *a priori*, to vary in their thermal performance curves (thin lines) around an average (thick black line).
+We restricted our data to areas of each species' performance curve that fell within the natural thermal range of the species (thick lines on each species-level curve).
+However, given it was not possible to measure the full performance curve for each species some test temperatures within studies may have converged on or moved past the thermal maxima.
+In such cases, we expected our $Q_{10}$ effect sizes to be smaller as indicated by comparing the black dashed lines to grey dashed lines."
+
+fig_concept <- magick::image_read("output/figures/fig1.png")
+plot(fig_concept)
+```
+
 ## **Results**
@@
 $lnVR_{Q_{10}}$ values from our simulations matched our empirical results in particular areas of parameter space (@fig-sim2).
-For a given among-individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower among-individual variance in thermal optima compared to marine and freshwater ectotherms ([@fig-sim2]).
-In contrast, terrestrial ectotherms are expected to have higher levels of among-individual variance in thermal breadth when controlling for among-individual variance in thermal optima ([@fig-sim2]).
+For a given among-individual variance in thermal breadth, terrestrial ectotherms are predicted to have lower among-individual variance in thermal maxima compared to marine and freshwater ectotherms ([@fig-sim2]).
+In contrast, terrestrial ectotherms are expected to have higher levels of among-individual variance in thermal breadth when controlling for among-individual variance in thermal maxima ([@fig-sim2]).
 
@@
 #| fig-cap: "Results from sensitivity analysis.
-Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal optima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
+Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal maxima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
 In all simulations, population parameters were $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{\\delta}$ and $\\sigma_{\\sigma}$.
@@
 
-Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explained ~ 46% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
+Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 46% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
 Climate change is predicted to result, on average, in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% increase in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$f))`), a `r abs(lapply(mean_perc_habitat_vr, mean)$m)`% increase in marine systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$m))`), and a `r abs(lapply(mean_perc_habitat_vr, mean)$t)`%  increase in terrestrial systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5 climate scenario ([@fig-fig6]D).
@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
-Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
+Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance at warmer temperatures ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
 Our results uncover an hitherto unrecognised dynamic where the benefits of partial acclimation are paralleled by increases in trait variance that depend on habitat in ways that may have impacts on how ectotherm populations will be able to adapt to increased temperatures.
@@
 Our analysis confirms findings by @Seebacher2015-wi, @Gunderson2015-hz and @morley2019physiological that all show a general inability of terrestrial ectotherms to physiologically acclimate.
-These consistent results are interesting given the different physiological traits measured in these meta-analyses (i.e., thermal limits versus physiological rates).
+These consistent results are interesting given the different physiological traits measured in these meta-analyses (e.g., thermal limits versus physiological rates).
 
@@
 One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ between habitats [@angilletta2009thermal; @huey1989evolution; @tattersall2012coping; @rezende2019thermal].
-Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal optima and breadth across habitats making this hypothesis plausible.
+Our simulations suggest that theoretical and observed $lnVR_{Q_{10}}$ match when thermal performance curves have different among-individual variance in thermal maxima and breadth across habitats making this hypothesis plausible.
 Such patterns across habitats are expected given that terrestrial ectotherms should be adapted to more extreme and variable thermal environments.
@@
 Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across major ecosystems globally.
+
+## **Materials and Methods**
+
+### *Literature collection*
+
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
+
+### *Data Compilation*
+
+We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
+If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
+We extracted these data from text, tables or figures of a given paper.
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
+We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
+If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
+If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
+When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
+
+### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
+
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+
+#### *Comparing changes in mean physiological rates*
+
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+
+$$
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10}
+
+Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
+Log transformation of this ratio makes the effect size normally distributed.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
+The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
+
+$$
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-Vlnq10}
+
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
+
+#### *Comparing variance in physiological rates*
+
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
+$$
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10VR} $$
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slnq10VR}
+
+where parameters are defined above.
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR} $$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
+
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
+
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below).
+
+### *Moderator Variables*
+
+We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
+This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
+We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
+Traits that could not be categorised into these two we classified as ‘Other’.
+
+### *Meta-Analysis*
+
+We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
+`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
+2.0, @Nakagawa2021-ls; @nakagawaorchard].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
+In all cases, frequentist and Bayesian models resulted in the same conclusions.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
+We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+
+#### *Multi-level Meta-analysis (MLMA) Models*
+
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
+We refer to this model structure as “Model 1” in the results.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
+`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
+We resolved all polytomies in the tree.
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
+As such, we used an intermediate value of p = 0.7.
+We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+
+#### *Multi-level Meta-regression (MLMR) Models*
+
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
+In all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
+To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
+
+In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
+We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
+We mean-centered the maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
+All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
+
+We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
+In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
+
+Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
+We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
+
+Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
+We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
+We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
+We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
+We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
+However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
+As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
+
+#### *Modelling how climate change can impact relative variance in physiological rates*
+
+To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
+We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
+Our model included random effects of species, trait, phylogeny and study.
+We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
+We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
+
+$$
+lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
+$$ {#eq-lCVRpred}
+
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
+
+### *Publication Bias*
+
+We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
+Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
+However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
+As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
+
+### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
+
+We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
+The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
+To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
+
+$$
+P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
+$$ {#eq-sim}
+
+where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
+We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
+We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
+From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
 
@@
 We then calculated the relative variance in performance across the temperature gradient as the variance in performance at each temperature divided by the maximum performance at that temperature.
-This simple analysis identified thermal optima and breath as being the major factors likely leading to the observed patterns in $lnVR_{Q_{10}}$ we identify in our meta-analysis.
+This simple analysis identified thermal maxima and breath as being the major factors likely leading to the observed patterns in $lnVR_{Q_{10}}$ we identify in our meta-analysis.
 

### 2024-09-12 ms.qmd
Reformat for PLoS

@@
 Here, we use meta-analysis to establish the current state-of-knowledge of the extent to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We then developed new effect sizes to quantify how variance in physiological rates changes with temperature to ask the following questions regarding acclimation-induced changes in trait means and variances: 1) Does variance in physiological rates change as temperatures rise?
+We developed new effect sizes ([@fig-concept]A)to quantify how variance in physiological rates change with temperature to ask the following questions regarding acclimation-induced changes in trait means and variances: 1) Does variance in physiological rates change as temperatures rise?
 2) Are temperature effects on means of physiological rates greater than changes in variance across aquatic and terrestrial ectotherms?
@@
 5) How are variances in physiological rates expected to change under climate change?
+Importantly, unlike past analyses, our analysis corrects for changes in $Q_10$ that may vary across thermal performance curves across diverse taxa ([@fig-concept]B).
 

### 2024-09-18 ms.qmd
Re-organising paper. Need to cut text a bit

@@
 bibliography: ./bib/refs.bib
-csl: ./bib/plos.csl
+csl: ./bib/functional-ecology.csl
 format:
@@
 
-```{r lnrrq10}
-#| label: lnrrq10
-#| echo: false
-#| cache: true
-#| message: false
-#| warning: false
-#| include: false
-
-#############
-## lnRRQ10 ##
-#############
-##################################################
-# Organise the data and prune tree
-##################################################
-# Subset the data
-lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
-                                    max_temp_c = scale(temp_2, scale = FALSE))
-
-# Check and prune tree
-tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor <- vcv(tree_lnrr, cor = TRUE)
-        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
-
-# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
-sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
-
-##################################################
-# Grafen mode comparison test with different power
-##################################################
-
-rerun = FALSE
-if(rerun){
-    # Create a list of the distinct trees to loop over
-           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
-    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
-
-    # Create an empty list to store the models
-        mod_list <- list()
-
-    for(i in 1:length(list)){
-
-    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
-    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
-       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data) 
-             mod_list[[i]] <- model1_phylo 
-        names(mod_list)[i] <- names(list)[i]       
-        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
-    }
-
-  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
-    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
-
-} else {
-
-  # Load the model list
-    #mod_list <- readRDS("./output/models/lnRRQ10_phylo")
-
-  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
-   #aic <- sapply(mod_list, function(x) AIC(x))
-
-}
-
-##################################################
-# Model 1.1: Intercept only model. 
-##################################################
-rerun = FALSE
-if(rerun){
-  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.1
-  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
-  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
-} else{ 
-  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
-model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
-}
-
-# Heterogeneity analysis
-   w <- with(lnRRQ10_data, 1/V) # weights
-  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
-  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
-
-    res <- posteriors_1.1[,"sigma"]
-   stdy <- posteriors_1.1[,"record_num"]
-  phylo <- posteriors_1.1[,"species_full"]
-    spp <- posteriors_1.1[,"spp"]
-  trait <- posteriors_1.1[,"trait"]
-  total <- phylo + spp + res + sv + stdy + trait
-
-  # Calculate I2
-     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
-   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
-     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
-    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
-   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
-     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
-
-  # Table
-     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
-                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
-
-###################################################
-# Model 1.2: Model controlling for acclimation time, 
-# type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model with 
-  model1.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-  # Additional model fit as a result of reviewer commenting that acclimation time is assumed to be linear.
-So, fit a non-linear parameter to see if it improves fit (even though data doesn't suggest it is the case).
-   model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-    AIC(model1.2_nl, model1.2) # Again, basically the same and go with most parsimonious model
-
-  # Secondary sensitivity analysis that uses cluster robust variance estimation to deal with unaccounted sources of non-independence.
-Not completely dealing with sharced sampling covariances in data as when collected these data were never indicated in past studies so hard to build full VCV matrix.
-
-   model1.2_rve <- robust(model1.2, cluster = lnRRQ10_data$record_num) # Consistent.
-
-  # Baysian model allows us to propagate error better is should be more robust to non-independence
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.2
-  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
-  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
-
-  } else{
-        model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
-  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
-}
-
-####################################################
-## Model 1.2: Bayesian Contrasts
-###################################################
-  posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
-  f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
-  f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
-  m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
-  m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
-  t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
-  t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
-
-# Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
-  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
-   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
-  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
-   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
-  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
-
-# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
-  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
-  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
-  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
-  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
-  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
-
-  # First get sample sizes
-    N <- lnRRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
-
-  # Calculated weighted mean by sample size. 
-    f_RR_mean <- (f_acute * N[1,"n"][[1]] + f_acclim * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_RR_mean)
-    m_RR_mean <- (m_acute * N[3,"n"][[1]] + m_acclim * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_RR_mean)
-    t_RR_mean <- (t_acute * N[5,"n"][[1]] + t_acclim * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_RR_mean)
-
-  # Rates differ?
-    t_f_rates <- (t_RR_mean - f_RR_mean)
-    t_m_rates <- (t_RR_mean - m_RR_mean)
-
-####################################################
-# Model 1.3's: Trait type varied by acclimation type
-# but data is separated by habitat to simplify
-####################################################
-  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
-    lnRRQ10_data <- lnRRQ10_data %>% 
-                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
-                                                "tissue/organism",
-                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
-                                                "biochemical", trait_category)))
-
-  # Filter to different habitats
-   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & trait_broad != "other") 
-   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & trait_broad != "other") 
-   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & trait_broad != "other")
-
-  # Prune tree
-   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-
-   # cor matrices
-   m_phylo <- vcv(tree_m, corr = TRUE)
-       A_m <- vcv(tree_m, corr = FALSE)
-   f_phylo <- vcv(tree_f, corr = TRUE)
-       A_f <- vcv(tree_f, corr = FALSE)
-   t_phylo <- vcv(tree_t, corr = TRUE)
-       A_t <- vcv(tree_t, corr = FALSE)
-
-if(rerun){
-
-#################################
-  # Broad Trait Category Models
-  # Subset to only trait categories 
-  # that are clear. Remove 'other'
-#################################
-  # Full Bayesian model   
-   model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
-                                           (1 | record_num) + 
-                                           (1 | gr(species_full, cov = A)) + 
-                                           (1 + max_temp_c | spp) +(1|trait) + 
-                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
-                                         data2 = list(A=A), family = gaussian(), 
-                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnRRQ10_data, trait_broad != "other"))
-    saveRDS(model1.3_btrait_bayes, "./output/models/model1.3_btrait_bayes")
-
-  # Metafor models for creating plots. Subset by habitat to make this easier
-      # Marine
-         model1.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = m_phylo), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"),  phi = 0,
-                              data = lnRRQ10_data_m)
-         saveRDS(model1.3_m_broad, "./output/models/model1.3_m_broad")
-
-      # Freshwater
-         model1.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = f_phylo), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = lnRRQ10_data_f)
-          saveRDS(model1.3_f_broad, "output/models/model1.3_f_broad")
-
-      # Terrestrial
-         model1.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = t_phylo), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = lnRRQ10_data_t)
-         saveRDS(model1.3_t_broad, "output/models/model1.3_t_broad")
-
-  } else{
-    model1.3_btrait_bayes <- readRDS("./output/models/model1.3_btrait_bayes")
-         model1.3_m_broad <- readRDS("./output/models/model1.3_m_broad")
-         model1.3_f_broad <- readRDS("./output/models/model1.3_f_broad")
-         model1.3_t_broad <- readRDS("./output/models/model1.3_t_broad")
-}
-
-###########################################################
-  # Processing Bayesian Posteriors
-###########################################################
-      # Create new data for predictions
-       trait_b_data <- data.frame(  type = c("acclim", "acute"),
-                              max_temp_c = 0,
-                             c_accl_time = 0,
-                                       V = 0,
-                                 habitat = rep(c("t", "m", "f"), each = 4),
-                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
-
-       # Predict from model. Note this is the summary.
-         pred_lnrr_traitb <- fitted(model1.3_btrait_bayes, 
-                                     newdata = trait_b_data, re_formula = NA,
-                                     summary = TRUE, 
-                                     robust = FALSE)
-         pred_lnrr_traitb <- cbind(trait_b_data, pred_lnrr_traitb)
-
-       # Predict to get the posterior.
-Note that we have the full posterior distribution here for each of the 12 categories in the new data.
-Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lnrr_trait_post <- fitted(model1.3_btrait_bayes, 
-                                     newdata = trait_b_data, re_formula = NA,
-                                     summary = FALSE, 
-                                     robust = FALSE)
-        contrast_lnrr_trait_post <-  pred_lnrr_trait_post[,c(1,3,5,7,9,11)] - pred_lnrr_trait_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
-
-        # Contrast statistics
-            contrast_lnrr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
-                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
-                                                    diff = sapply(data.frame(contrast_lnrr_trait_post), mean),
-                                                     l95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.025)),
-                                                     u95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.975)),
-                                                       p = sapply(data.frame(contrast_lnrr_trait_post), function(x) p_value(pmcmc(x))))
-       # Contrasts for pooled acute and acclimation across trait categories
-
-            contrast_lnrr_trait_cat_stats <- rbind(get_whole_bio(pred_lnrr_trait_post, habitat = "t", trait_b_data),
-                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "m", trait_b_data),
-                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "f", trait_b_data))
-###########################################################
-## Model 1.4 - whether chance between q10 depends on life stage and habitat
-###########################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model1.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.4
-  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
-  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
-
-  } else{
-        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
-  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
-}
-
-#######################################################################
-# Bayesian posteriors from model 1.4
-#######################################################################
- # Create the data we want to make predictions for. Just more intuitive
-  newdata <- data.frame( c_accl_time = 0, 
-                          max_temp_c = 0, 
-                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
-                             habitat = rep(c("m", "f", "t"), each = 4), 
-                           life.hist = rep(c("j", "a"), each = 2))
-
-# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
-  X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = newdata)
-
-# Extract posteriors
-  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
-
-# Now we can do all the calculations in one shot.
-         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
-     sum_pred <- apply(pred, 1, function(x) mean(x))
-  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
-  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
-            p <- apply(pred, 1, function(x) p_value(pmcmc(x)))
-
-  # Create a summary dataset. 
-  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95, p = p)
-
-# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-############
-    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
-############
-  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.
-
-        # Contrast statistics
-            contrast_stage_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
-                                                     stage = rep(c("j", "a"), each = 1),
-                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
-############
-    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
-############
-          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.
-
-        # Contrast statistics
-            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
-                                                     type = rep(c("acute", "acclim"), each = 1),
-                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
-
-  # Acute differences between a and j across all habitats
-     acute_all_lh <- c(contrast_lnrr_lh_post_type[1,], contrast_lnrr_lh_post_type[3,], contrast_lnrr_lh_post_type[5,]) 
-    acclim_all_lh <- c(contrast_lnrr_lh_post_type[2,], contrast_lnrr_lh_post_type[4,], contrast_lnrr_lh_post_type[6,])
-
-  # Contrast adult vs juv across habitats regardless of the acute/acclim
-               contrast_lnrr_lh_cat_stats <- rbind(get_lifestage(pred, habitat = "t", newdata),
-                                                   get_lifestage(pred, habitat = "m", newdata),
-                                                   get_lifestage(pred, habitat = "f", newdata))
-
-####################################################
-# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
-####################################################
- # Goal here is to test the assumption that acute Q10's are different or not. Note Reviewer wanted more analysis in this space so added additional models
- lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
-
- if(rerun){ 
-    model1.s1 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
-    saveRDS(model1.s1, file = "./output/models/model1.s1")
-
-    model1.s1_int <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name*habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
-    saveRDS(model1.s1_int, file = "./output/models/model1.s1_int")
-
-    AIC(model1.s1_int, model1.s1) # AIC basically the same
-
-    # Bayesian models to check its the same result
-    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
-
-    saveRDS(model1.s1_bayes, file = "./output/models/model1.s1_bayes")
-
-    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
-
-    saveRDS(model1.s1_bayes_int, file = "./output/models/model1.s1_bayes_int")
-
-} else{
-            model1.s1 <-  readRDS(file = "./output/models/model1.s1")
-            model1.s1_int <-  readRDS(file = "./output/models/model1.s1_int")
-      model1.s1_bayes <- readRDS(file= "./output/models/model1.s1_bayes")
-}
-
-post_acute <- posterior_samples(model1.s1_bayes, pars = "^b")
-  hot_acute <- post_acute[,"b_Intercept"] + post_acute[,"b_namelnRR_Q10_acute_t2"]
-  cold_acute <- post_acute[,"b_Intercept"]
-  change_acute <- post_acute[,"b_namelnRR_Q10_acute_t2"]
-
-n_acutes <- lnRRQ10_data_acute  %>% group_by(name, habitat) %>% summarise(n = n(), stdy = n_distinct(record_num), spp = n_distinct(species_full))  %>% arrange(habitat)
-
-```
-
 ```{r, fig-concept}
@@
 
+## **Materials and Methods**
+
+### *Literature collection*
+
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
+
+### *Data Compilation*
+
+We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
+If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
+We extracted these data from text, tables or figures of a given paper.
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
+We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
+If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
+If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
+When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
+
+### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
+
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+
+#### *Comparing changes in mean physiological rates*
+
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+
+$$
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10}
+
+Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
+Log transformation of this ratio makes the effect size normally distributed.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
+The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
+
+$$
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-Vlnq10}
+
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
+
+#### *Comparing variance in physiological rates*
+
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
+$$
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10VR} $$
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slnq10VR}
+
+where parameters are defined above.
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR} $$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
+
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
+
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below).
+
+### *Moderator Variables*
+
+We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
+This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
+We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
+Traits that could not be categorised into these two we classified as ‘Other’.
+
+### *Meta-Analysis*
+
+We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
+`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
+2.0, @Nakagawa2021-ls; @nakagawaorchard].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
+In all cases, frequentist and Bayesian models resulted in the same conclusions.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
+We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+
+#### *Multi-level Meta-analysis (MLMA) Models*
+
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
+We refer to this model structure as “Model 1” in the results.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
+`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
+We resolved all polytomies in the tree.
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
+As such, we used an intermediate value of p = 0.7.
+We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+
+#### *Multi-level Meta-regression (MLMR) Models*
+
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
+In all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
+To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
+
+In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
+We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
+We mean-centered the maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
+All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
+
+We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
+In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
+
+Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
+We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
+
+Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
+We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
+We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
+We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
+We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
+However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
+As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
+
+#### *Modelling how climate change can impact relative variance in physiological rates*
+
+To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
+We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
+Our model included random effects of species, trait, phylogeny and study.
+We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
+We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
+
+$$
+lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
+$$ {#eq-lCVRpred}
+
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
+
+### *Publication Bias*
+
+We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
+Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
+However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
+As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
+
+### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
+
+We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
+The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
+To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
+
+$$
+P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
+$$ {#eq-sim}
+
+where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
+We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
+We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
+From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
+
+```{r lnrrq10}
+#| label: lnrrq10
+#| echo: false
+#| cache: true
+#| message: false
+#| warning: false
+#| include: false
+
+#############
+## lnRRQ10 ##
+#############
+##################################################
+# Organise the data and prune tree
+##################################################
+# Subset the data
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor <- vcv(tree_lnrr, cor = TRUE)
+        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
+
+# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
+sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
+
+##################################################
+# Grafen mode comparison test with different power
+##################################################
+
+rerun = FALSE
+if(rerun){
+    # Create a list of the distinct trees to loop over
+           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
+    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
+
+    # Create an empty list to store the models
+        mod_list <- list()
+
+    for(i in 1:length(list)){
+
+    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
+    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
+       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+             mod_list[[i]] <- model1_phylo 
+        names(mod_list)[i] <- names(list)[i]       
+        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
+    }
+
+  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
+    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
+
+} else {
+
+  # Load the model list
+    #mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+
+  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
+   #aic <- sapply(mod_list, function(x) AIC(x))
+
+}
+
+##################################################
+# Model 1.1: Intercept only model. 
+##################################################
+rerun = FALSE
+if(rerun){
+  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.1
+  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
+  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
+} else{ 
+  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
+model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
+}
+
+# Heterogeneity analysis
+   w <- with(lnRRQ10_data, 1/V) # weights
+  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
+  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
+
+    res <- posteriors_1.1[,"sigma"]
+   stdy <- posteriors_1.1[,"record_num"]
+  phylo <- posteriors_1.1[,"species_full"]
+    spp <- posteriors_1.1[,"spp"]
+  trait <- posteriors_1.1[,"trait"]
+  total <- phylo + spp + res + sv + stdy + trait
+
+  # Calculate I2
+     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
+   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
+     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
+    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
+   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
+     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
+
+  # Table
+     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
+                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
+
+###################################################
+# Model 1.2: Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model with 
+  model1.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  # Additional model fit as a result of reviewer commenting that acclimation time is assumed to be linear.
+So, fit a non-linear parameter to see if it improves fit (even though data doesn't suggest it is the case).
+   model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+    AIC(model1.2_nl, model1.2) # Again, basically the same and go with most parsimonious model
+
+  # Secondary sensitivity analysis that uses cluster robust variance estimation to deal with unaccounted sources of non-independence.
+Not completely dealing with sharced sampling covariances in data as when collected these data were never indicated in past studies so hard to build full VCV matrix.
+
+   model1.2_rve <- robust(model1.2, cluster = lnRRQ10_data$record_num) # Consistent.
+
+  # Baysian model allows us to propagate error better is should be more robust to non-independence
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.2
+  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
+  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
+
+  } else{
+        model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
+  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
+}
+
+####################################################
+## Model 1.2: Bayesian Contrasts
+###################################################
+  posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
+  f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
+  f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
+  m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
+  m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
+  t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
+  t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
+
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
+  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
+   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
+  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
+   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
+  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
+
+# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
+  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
+  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
+  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
+  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
+  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
+
+  # First get sample sizes
+    N <- lnRRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_RR_mean <- (f_acute * N[1,"n"][[1]] + f_acclim * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_RR_mean)
+    m_RR_mean <- (m_acute * N[3,"n"][[1]] + m_acclim * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_RR_mean)
+    t_RR_mean <- (t_acute * N[5,"n"][[1]] + t_acclim * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_RR_mean)
+
+  # Rates differ?
+    t_f_rates <- (t_RR_mean - f_RR_mean)
+    t_m_rates <- (t_RR_mean - m_RR_mean)
+
+####################################################
+# Model 1.3's: Trait type varied by acclimation type
+# but data is separated by habitat to simplify
+####################################################
+  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
+    lnRRQ10_data <- lnRRQ10_data %>% 
+                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
+                                                "tissue/organism",
+                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
+                                                "biochemical", trait_category)))
+
+  # Filter to different habitats
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & trait_broad != "other") 
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & trait_broad != "other") 
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & trait_broad != "other")
+
+  # Prune tree
+   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo <- vcv(tree_m, corr = TRUE)
+       A_m <- vcv(tree_m, corr = FALSE)
+   f_phylo <- vcv(tree_f, corr = TRUE)
+       A_f <- vcv(tree_f, corr = FALSE)
+   t_phylo <- vcv(tree_t, corr = TRUE)
+       A_t <- vcv(tree_t, corr = FALSE)
+
+if(rerun){
+
+#################################
+  # Broad Trait Category Models
+  # Subset to only trait categories 
+  # that are clear. Remove 'other'
+#################################
+  # Full Bayesian model   
+   model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+                                           (1 | record_num) + 
+                                           (1 | gr(species_full, cov = A)) + 
+                                           (1 + max_temp_c | spp) +(1|trait) + 
+                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
+                                         data2 = list(A=A), family = gaussian(), 
+                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnRRQ10_data, trait_broad != "other"))
+    saveRDS(model1.3_btrait_bayes, "./output/models/model1.3_btrait_bayes")
+
+  # Metafor models for creating plots. Subset by habitat to make this easier
+      # Marine
+         model1.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = m_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"),  phi = 0,
+                              data = lnRRQ10_data_m)
+         saveRDS(model1.3_m_broad, "./output/models/model1.3_m_broad")
+
+      # Freshwater
+         model1.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = f_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = lnRRQ10_data_f)
+          saveRDS(model1.3_f_broad, "output/models/model1.3_f_broad")
+
+      # Terrestrial
+         model1.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = t_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = lnRRQ10_data_t)
+         saveRDS(model1.3_t_broad, "output/models/model1.3_t_broad")
+
+  } else{
+    model1.3_btrait_bayes <- readRDS("./output/models/model1.3_btrait_bayes")
+         model1.3_m_broad <- readRDS("./output/models/model1.3_m_broad")
+         model1.3_f_broad <- readRDS("./output/models/model1.3_f_broad")
+         model1.3_t_broad <- readRDS("./output/models/model1.3_t_broad")
+}
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       trait_b_data <- data.frame(  type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lnrr_traitb <- fitted(model1.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lnrr_traitb <- cbind(trait_b_data, pred_lnrr_traitb)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lnrr_trait_post <- fitted(model1.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lnrr_trait_post <-  pred_lnrr_trait_post[,c(1,3,5,7,9,11)] - pred_lnrr_trait_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lnrr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lnrr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lnrr_trait_post), function(x) p_value(pmcmc(x))))
+       # Contrasts for pooled acute and acclimation across trait categories
+
+            contrast_lnrr_trait_cat_stats <- rbind(get_whole_bio(pred_lnrr_trait_post, habitat = "t", trait_b_data),
+                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "m", trait_b_data),
+                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "f", trait_b_data))
+###########################################################
+## Model 1.4 - whether chance between q10 depends on life stage and habitat
+###########################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model1.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.4
+  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
+  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
+
+  } else{
+        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
+  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
+}
+
+#######################################################################
+# Bayesian posteriors from model 1.4
+#######################################################################
+ # Create the data we want to make predictions for. Just more intuitive
+  newdata <- data.frame( c_accl_time = 0, 
+                          max_temp_c = 0, 
+                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
+                             habitat = rep(c("m", "f", "t"), each = 4), 
+                           life.hist = rep(c("j", "a"), each = 2))
+
+# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
+  X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = newdata)
+
+# Extract posteriors
+  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
+
+# Now we can do all the calculations in one shot.
+         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
+     sum_pred <- apply(pred, 1, function(x) mean(x))
+  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
+  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
+            p <- apply(pred, 1, function(x) p_value(pmcmc(x)))
+
+  # Create a summary dataset. 
+  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95, p = p)
+
+# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
+############
+    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
+############
+  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_stage_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+                                                     stage = rep(c("j", "a"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
+############
+    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
+############
+          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.
+
+        # Contrast statistics
+            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+                                                     type = rep(c("acute", "acclim"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
+
+  # Acute differences between a and j across all habitats
+     acute_all_lh <- c(contrast_lnrr_lh_post_type[1,], contrast_lnrr_lh_post_type[3,], contrast_lnrr_lh_post_type[5,]) 
+    acclim_all_lh <- c(contrast_lnrr_lh_post_type[2,], contrast_lnrr_lh_post_type[4,], contrast_lnrr_lh_post_type[6,])
+
+  # Contrast adult vs juv across habitats regardless of the acute/acclim
+               contrast_lnrr_lh_cat_stats <- rbind(get_lifestage(pred, habitat = "t", newdata),
+                                                   get_lifestage(pred, habitat = "m", newdata),
+                                                   get_lifestage(pred, habitat = "f", newdata))
+
+####################################################
+# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
+####################################################
+ # Goal here is to test the assumption that acute Q10's are different or not. Note Reviewer wanted more analysis in this space so added additional models
+ lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
+
+ if(rerun){ 
+    model1.s1 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1, file = "./output/models/model1.s1")
+
+    model1.s1_int <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name*habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1_int, file = "./output/models/model1.s1_int")
+
+    AIC(model1.s1_int, model1.s1) # AIC basically the same
+
+    # Bayesian models to check its the same result
+    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+
+    saveRDS(model1.s1_bayes, file = "./output/models/model1.s1_bayes")
+
+    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+
+    saveRDS(model1.s1_bayes_int, file = "./output/models/model1.s1_bayes_int")
+
+} else{
+            model1.s1 <-  readRDS(file = "./output/models/model1.s1")
+            model1.s1_int <-  readRDS(file = "./output/models/model1.s1_int")
+      model1.s1_bayes <- readRDS(file= "./output/models/model1.s1_bayes")
+}
+
+post_acute <- posterior_samples(model1.s1_bayes, pars = "^b")
+  hot_acute <- post_acute[,"b_Intercept"] + post_acute[,"b_namelnRR_Q10_acute_t2"]
+  cold_acute <- post_acute[,"b_Intercept"]
+  change_acute <- post_acute[,"b_namelnRR_Q10_acute_t2"]
+
+n_acutes <- lnRRQ10_data_acute  %>% group_by(name, habitat) %>% summarise(n = n(), stdy = n_distinct(record_num), spp = n_distinct(species_full))  %>% arrange(habitat)
+
+```
+
 ## **Results**
@@
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to acclimation responses (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
-The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to
-`r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
+The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
 However, on average they were in the same direction and only differed by ~10%.
@@
 Answers to these questions will require integrative approaches that combine empirical and theoretical work across multiple levels of biological organisation but will likely provide useful advances in understanding the full consequences that climate change will have on ectotherms across major ecosystems globally.
-
-## **Materials and Methods**
-
-### *Literature collection*
-
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
-
-### *Data Compilation*
-
-We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
-If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
-We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
-We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
-For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
-If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
-If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
-When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
-
-### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
-
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
-Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
-
-#### *Comparing changes in mean physiological rates*
-
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
-
-$$
-  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10}
-
-Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
-Log transformation of this ratio makes the effect size normally distributed.
-@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
-The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
-
-$$
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-Vlnq10}
-
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
-
-#### *Comparing variance in physiological rates*
-
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
-
-$$
-lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10VR} $$
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slnq10VR}
-
-where parameters are defined above.
-@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
-As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR} $$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$.
-We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
-
-#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
-
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
-For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
-For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
-Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
-We test and control for any violations of these assumptions in our analysis (see below).
-
-### *Moderator Variables*
-
-We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
-We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
-Traits that could not be categorised into these two we classified as ‘Other’.
-
-### *Meta-Analysis*
-
-We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
-We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021-ls; @nakagawaorchard].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
-In all cases, frequentist and Bayesian models resulted in the same conclusions.
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
-We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-
-#### *Multi-level Meta-analysis (MLMA) Models*
-
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
-We refer to this model structure as “Model 1” in the results.
-Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
-We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
-`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
-`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
-We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
-As such, we used an intermediate value of p = 0.7.
-We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
-`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
-
-#### *Multi-level Meta-regression (MLMR) Models*
-
-After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
-In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
-
-In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
-We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
-We mean-centered the maximum temperature and included it in our models.
-
-With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
-
-We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
-Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
-
-Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
-We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
-
-Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
-We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
-
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
-We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
-We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
-We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
-However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
-
-#### *Modelling how climate change can impact relative variance in physiological rates*
-
-To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
-We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
-Our model included random effects of species, trait, phylogeny and study.
-We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
-We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
-
-$$
-lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
-$$ {#eq-lCVRpred}
-
-We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
-
-### *Publication Bias*
-
-We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
-Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
-However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
-There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
-
-### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
-
-We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
-The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
-To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
-
-$$
-P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
-$$ {#eq-sim}
-
-where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
-We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
-We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
-From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
 

### 2024-09-19 ms.qmd
Having to trim references as paper is too long

--- 2024-09-12 ms.qmd
@@
     reference-doc: ./bib/template.docx
-    output-file: "ms_plos.docx"
+    output-file: "ms_fe.docx"
 editor_options: 
@@
 However, it is unresolved how variance in physiological rates changes with temperature despite its potential ecological and evolutionary importance.
-We tested whether thermal variation affects physiological traits in ectotherms by conducting a meta-analysis (>1900 effects from 226 species), and applying new effect sizes that quantify how trait mean and variance change as temperature increases.
+We tested the extent to which thermal variation affects variation physiological rates and their capacity to acclimate in ectotherms by conducting a meta-analysis (>1900 effects from 226 species) and applying new effect sizes that quantify how trait mean and variance change as temperature increases.
+Comparing both the magnitude of acclimation and changes in variation side-by-side provides unique opportunities for evaluating the importance of plasticity or selection under climate change.
 We show that variance in physiological rates increases at higher temperatures, but that the magnitude of change depends on habitat.
@@
 
-Climate change is expected to result in warmer and more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017].
-Greater thermal variability is predicted to pose strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one].
-Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
-
-Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998; @Scheiner2020].
+Climate change is expected to result in warmer and more variable thermal environments globally [@Suarez2023; @Ummenhofer2017].
+Greater thermal variability is predicted to pose strong selection pressure that leads to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to human-induced climate change [@Seebacher2015-wi; @Chevin2015; @Chevin2017; @Chevin2010; @seebacher2023can; @cooke2021one].
+Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012].
+
+Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998].
 For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
@@
 
-Acclimation is expected to evolve in populations experiencing high but predictable environmental variability, and when the costs of plasticity are low [@Chevin2017; @Scheiner2020; @Nunney2016; @Dewitt1998; @Reed2010].
+Acclimation is expected to evolve in populations experiencing high but predictable environmental variability, and when the costs of plasticity are low [@Chevin2017; @Dewitt1998; @Reed2010].
 Thermal variation and predictability differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and it may be expected that organisms within these habitats vary in their capacity for acclimation.
@@
 Differences in the shape of thermal performance curves (thermal breadth, maximal performance and thermal maxima) can reflect among-individual variability at higher temperatures, which can also differ between different levels of biological organisation, environmental conditions, and acclimation responses [@rezende2019thermal; @tattersall2012coping; @schulte2011thermal; @angilletta2009thermal].
-Presumably, increases in variation in physiological rates reflects environment-mediated changes to underlying regulatory networks, which can lead to an increased variation in phenotypic outcomes [@costanzo2021environmental; @matthey2020plasticity; ].
+Presumably, increases in variation in physiological rates reflects environment-mediated changes to underlying regulatory networks, which can lead to an increased variation in phenotypic outcomes [@costanzo2021environmental; @matthey2020plasticity].
 Quantifying levels of among-individual variation in thermal performance curves is important to understand their capacity to evolve, as well as the resilience of populations to environmental change [@careau2014individual].
 
-Importantly, changes in physiological rate variability are expected to have consequences for the flow of energy within and between populations, communities, and ecosystems [@hendry2016key; @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
-Generally, more variable populations are predicted to be associated with broader niches, have increased growth rates, and decreased vulnerability to environmental change, lowering extinction risk [i.e., "portfolio effects",@Schindler2010] [see also, @forsman2015rethinking; @forsman2014effects; @Bolnick2011; @hendry2016key; @hart2016variation; @Schindler2010; @portner2021climate].
+Changes in physiological rate variability is expected to have consequences for the flow of energy within and between populations, communities, and ecosystems [ @seebacher2023can; @barneche2021warming; @Sanderson2023; @Bolnick2011].
+Generally, more variable populations are predicted to be associated with broader niches, have increased growth rates, and decreased vulnerability to environmental change, lowering extinction risk [i.e., "portfolio effects",@Schindler2010] [see also, @forsman2015rethinking; @forsman2014effects; @Bolnick2011;  @hart2016variation; @Schindler2010; @portner2021climate].
 In addition, if phenotypic and genetic variation in physiological rates are correlated and linked to fitness, reduced phenotypic variation may limit responses to selection and reduce the capacity of populations to evolve [@Pelletier2012; @hoffmann2011climate].
@@
 5) How are variances in physiological rates expected to change under climate change?
-Importantly, unlike past analyses, our analysis corrects for changes in $Q_10$ that may vary across thermal performance curves across diverse taxa ([@fig-concept]B).
-
-```{r lnrrq10}
-#| label: lnrrq10
-#| echo: false
-#| cache: true
-#| message: false
-#| warning: false
-#| include: false
-
-#############
-## lnRRQ10 ##
-#############
-##################################################
-# Organise the data and prune tree
-##################################################
-# Subset the data
-lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
-                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
-                                    max_temp_c = scale(temp_2, scale = FALSE))
-
-# Check and prune tree
-tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor <- vcv(tree_lnrr, cor = TRUE)
-        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
-
-# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
-sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
-
-##################################################
-# Grafen mode comparison test with different power
-##################################################
-
-rerun = FALSE
-if(rerun){
-    # Create a list of the distinct trees to loop over
-           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
-    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
-
-    # Create an empty list to store the models
-        mod_list <- list()
-
-    for(i in 1:length(list)){
-
-    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
-    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
-       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data) 
-             mod_list[[i]] <- model1_phylo 
-        names(mod_list)[i] <- names(list)[i]       
-        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
-    }
-
-  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
-    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
-
-} else {
-
-  # Load the model list
-    #mod_list <- readRDS("./output/models/lnRRQ10_phylo")
-
-  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
-   #aic <- sapply(mod_list, function(x) AIC(x))
-
-}
-
-##################################################
-# Model 1.1: Intercept only model. 
-##################################################
-rerun = FALSE
-if(rerun){
-  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 | spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.1
-  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
-  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
-} else{ 
-  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
-model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
-}
-
-# Heterogeneity analysis
-   w <- with(lnRRQ10_data, 1/V) # weights
-  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
-
-# extract posterior sds, but square them to turn to variance
-  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
-  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
-  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
-
-    res <- posteriors_1.1[,"sigma"]
-   stdy <- posteriors_1.1[,"record_num"]
-  phylo <- posteriors_1.1[,"species_full"]
-    spp <- posteriors_1.1[,"spp"]
-  trait <- posteriors_1.1[,"trait"]
-  total <- phylo + spp + res + sv + stdy + trait
-
-  # Calculate I2
-     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
-   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
-     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
-    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
-   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
-     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
-
-  # Table
-     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
-                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
-                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
-                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
-                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
-                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
-
-###################################################
-# Model 1.2: Model controlling for acclimation time, 
-# type and habitat assuming type can vary by habitat
-###################################################
-
-if(rerun){
-  # More realistic model with 
-  model1.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-  # Additional model fit as a result of reviewer commenting that acclimation time is assumed to be linear.
-So, fit a non-linear parameter to see if it improves fit (even though data doesn't suggest it is the case).
-   model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-    AIC(model1.2_nl, model1.2) # Again, basically the same and go with most parsimonious model
-
-  # Secondary sensitivity analysis that uses cluster robust variance estimation to deal with unaccounted sources of non-independence.
-Not completely dealing with sharced sampling covariances in data as when collected these data were never indicated in past studies so hard to build full VCV matrix.
-
-   model1.2_rve <- robust(model1.2, cluster = lnRRQ10_data$record_num) # Consistent.
-
-  # Baysian model allows us to propagate error better is should be more robust to non-independence
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.2
-  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
-  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
-
-  } else{
-        model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
-  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
-}
-
-####################################################
-## Model 1.2: Bayesian Contrasts
-###################################################
-  posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
-  f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
-  f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
-  m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
-  m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
-  t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
-  t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
-
-# Q10 values for each category. Effect sizes are quite small really
-   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
-  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
-   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
-  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
-   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
-  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
-
-# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
-  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
-  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
-  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
-  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
-  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
-
-  # First get sample sizes
-    N <- lnRRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
-
-  # Calculated weighted mean by sample size. 
-    f_RR_mean <- (f_acute * N[1,"n"][[1]] + f_acclim * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_RR_mean)
-    m_RR_mean <- (m_acute * N[3,"n"][[1]] + m_acclim * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_RR_mean)
-    t_RR_mean <- (t_acute * N[5,"n"][[1]] + t_acclim * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_RR_mean)
-
-  # Rates differ?
-    t_f_rates <- (t_RR_mean - f_RR_mean)
-    t_m_rates <- (t_RR_mean - m_RR_mean)
-
-####################################################
-# Model 1.3's: Trait type varied by acclimation type
-# but data is separated by habitat to simplify
-####################################################
-  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
-    lnRRQ10_data <- lnRRQ10_data %>% 
-                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
-                                                "tissue/organism",
-                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
-                                                "biochemical", trait_category)))
-
-  # Filter to different habitats
-   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & trait_broad != "other") 
-   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & trait_broad != "other") 
-   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & trait_broad != "other")
-
-  # Prune tree
-   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
-
-   # cor matrices
-   m_phylo <- vcv(tree_m, corr = TRUE)
-       A_m <- vcv(tree_m, corr = FALSE)
-   f_phylo <- vcv(tree_f, corr = TRUE)
-       A_f <- vcv(tree_f, corr = FALSE)
-   t_phylo <- vcv(tree_t, corr = TRUE)
-       A_t <- vcv(tree_t, corr = FALSE)
-
-if(rerun){
-
-#################################
-  # Broad Trait Category Models
-  # Subset to only trait categories 
-  # that are clear. Remove 'other'
-#################################
-  # Full Bayesian model   
-   model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
-                                           (1 | record_num) + 
-                                           (1 | gr(species_full, cov = A)) + 
-                                           (1 + max_temp_c | spp) +(1|trait) + 
-                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
-                                         data2 = list(A=A), family = gaussian(), 
-                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnRRQ10_data, trait_broad != "other"))
-    saveRDS(model1.3_btrait_bayes, "./output/models/model1.3_btrait_bayes")
-
-  # Metafor models for creating plots. Subset by habitat to make this easier
-      # Marine
-         model1.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = m_phylo), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"),  phi = 0,
-                              data = lnRRQ10_data_m)
-         saveRDS(model1.3_m_broad, "./output/models/model1.3_m_broad")
-
-      # Freshwater
-         model1.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = f_phylo), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = lnRRQ10_data_f)
-          saveRDS(model1.3_f_broad, "output/models/model1.3_f_broad")
-
-      # Terrestrial
-         model1.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | trait,
-                                            ~1 + trait_broad| obs),
-                              R = list(species_full = t_phylo), dfs = "contain", 
-                              test = "t", struct = c("GEN","HCS"), phi = 0,
-                              data = lnRRQ10_data_t)
-         saveRDS(model1.3_t_broad, "output/models/model1.3_t_broad")
-
-  } else{
-    model1.3_btrait_bayes <- readRDS("./output/models/model1.3_btrait_bayes")
-         model1.3_m_broad <- readRDS("./output/models/model1.3_m_broad")
-         model1.3_f_broad <- readRDS("./output/models/model1.3_f_broad")
-         model1.3_t_broad <- readRDS("./output/models/model1.3_t_broad")
-}
-
-###########################################################
-  # Processing Bayesian Posteriors
-###########################################################
-      # Create new data for predictions
-       trait_b_data <- data.frame(  type = c("acclim", "acute"),
-                              max_temp_c = 0,
-                             c_accl_time = 0,
-                                       V = 0,
-                                 habitat = rep(c("t", "m", "f"), each = 4),
-                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
-
-       # Predict from model. Note this is the summary.
-         pred_lnrr_traitb <- fitted(model1.3_btrait_bayes, 
-                                     newdata = trait_b_data, re_formula = NA,
-                                     summary = TRUE, 
-                                     robust = FALSE)
-         pred_lnrr_traitb <- cbind(trait_b_data, pred_lnrr_traitb)
-
-       # Predict to get the posterior.
-Note that we have the full posterior distribution here for each of the 12 categories in the new data.
-Here, we want to look at the difference between acute and acclimation within each of the categories.
-            pred_lnrr_trait_post <- fitted(model1.3_btrait_bayes, 
-                                     newdata = trait_b_data, re_formula = NA,
-                                     summary = FALSE, 
-                                     robust = FALSE)
-        contrast_lnrr_trait_post <-  pred_lnrr_trait_post[,c(1,3,5,7,9,11)] - pred_lnrr_trait_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
-
-        # Contrast statistics
-            contrast_lnrr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
-                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
-                                                    diff = sapply(data.frame(contrast_lnrr_trait_post), mean),
-                                                     l95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.025)),
-                                                     u95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.975)),
-                                                       p = sapply(data.frame(contrast_lnrr_trait_post), function(x) p_value(pmcmc(x))))
-       # Contrasts for pooled acute and acclimation across trait categories
-
-            contrast_lnrr_trait_cat_stats <- rbind(get_whole_bio(pred_lnrr_trait_post, habitat = "t", trait_b_data),
-                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "m", trait_b_data),
-                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "f", trait_b_data))
-###########################################################
-## Model 1.4 - whether chance between q10 depends on life stage and habitat
-###########################################################
-rerun = FALSE
-if(rerun){
-  # More realistic model with 
-  model1.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
-
-   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-  # Save model1.4
-  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
-  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
-
-  } else{
-        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
-  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
-}
-
-#######################################################################
-# Bayesian posteriors from model 1.4
-#######################################################################
- # Create the data we want to make predictions for. Just more intuitive
-  newdata <- data.frame( c_accl_time = 0, 
-                          max_temp_c = 0, 
-                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
-                             habitat = rep(c("m", "f", "t"), each = 4), 
-                           life.hist = rep(c("j", "a"), each = 2))
-
-# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
-  X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = newdata)
-
-# Extract posteriors
-  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
-
-# Now we can do all the calculations in one shot.
-         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
-     sum_pred <- apply(pred, 1, function(x) mean(x))
-  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
-  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
-            p <- apply(pred, 1, function(x) p_value(pmcmc(x)))
-
-  # Create a summary dataset. 
-  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95, p = p)
-
-# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
-############
-    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
-############
-  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.
-
-        # Contrast statistics
-            contrast_stage_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
-                                                     stage = rep(c("j", "a"), each = 1),
-                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
-############
-    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
-############
-          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.
-
-        # Contrast statistics
-            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
-                                                     type = rep(c("acute", "acclim"), each = 1),
-                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
-                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
-                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
-                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
-
-  # Acute differences between a and j across all habitats
-     acute_all_lh <- c(contrast_lnrr_lh_post_type[1,], contrast_lnrr_lh_post_type[3,], contrast_lnrr_lh_post_type[5,]) 
-    acclim_all_lh <- c(contrast_lnrr_lh_post_type[2,], contrast_lnrr_lh_post_type[4,], contrast_lnrr_lh_post_type[6,])
-
-  # Contrast adult vs juv across habitats regardless of the acute/acclim
-               contrast_lnrr_lh_cat_stats <- rbind(get_lifestage(pred, habitat = "t", newdata),
-                                                   get_lifestage(pred, habitat = "m", newdata),
-                                                   get_lifestage(pred, habitat = "f", newdata))
-
-####################################################
-# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
-####################################################
- # Goal here is to test the assumption that acute Q10's are different or not. Note Reviewer wanted more analysis in this space so added additional models
- lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
-
- if(rerun){ 
-    model1.s1 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
-    saveRDS(model1.s1, file = "./output/models/model1.s1")
-
-    model1.s1_int <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name*habitat, V = V, 
-                              random = list(~1 | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
-    saveRDS(model1.s1_int, file = "./output/models/model1.s1_int")
-
-    AIC(model1.s1_int, model1.s1) # AIC basically the same
-
-    # Bayesian models to check its the same result
-    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
-
-    saveRDS(model1.s1_bayes, file = "./output/models/model1.s1_bayes")
-
-    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
-
-    saveRDS(model1.s1_bayes_int, file = "./output/models/model1.s1_bayes_int")
-
-} else{
-            model1.s1 <-  readRDS(file = "./output/models/model1.s1")
-            model1.s1_int <-  readRDS(file = "./output/models/model1.s1_int")
-      model1.s1_bayes <- readRDS(file= "./output/models/model1.s1_bayes")
-}
-
-post_acute <- posterior_samples(model1.s1_bayes, pars = "^b")
-  hot_acute <- post_acute[,"b_Intercept"] + post_acute[,"b_namelnRR_Q10_acute_t2"]
-  cold_acute <- post_acute[,"b_Intercept"]
-  change_acute <- post_acute[,"b_namelnRR_Q10_acute_t2"]
-
-n_acutes <- lnRRQ10_data_acute  %>% group_by(name, habitat) %>% summarise(n = n(), stdy = n_distinct(record_num), spp = n_distinct(species_full))  %>% arrange(habitat)
-
-```
 
@@
 
+## **Materials and Methods**
+
+### *Literature collection*
+
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
+We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
+We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
+For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
+
+### *Data Compilation*
+
+We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
+If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
+We extracted these data from text, tables or figures of a given paper.
+Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
+We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
+For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
+If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
+If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
+When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
+
+### *Moderator Variables*
+
+We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
+This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
+We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
+Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
+We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
+Traits that could not be categorised into these two we classified as ‘Other’.
+
+### *Meta-Analysis*
+
+We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
+`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
+`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
+2.0, @Nakagawa2021-ls; @nakagawaorchard].
+In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
+In all cases, frequentist and Bayesian models resulted in the same conclusions.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
+We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+We also explored the potential for publication bias in our dataset but there was no evidence it existed (details in *Supplementary Materials*).
+
+#### *Multi-level Meta-analysis (MLMA) Models*
+
+We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
+We refer to this model structure as “Model 1” in the results.
+Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
+This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
+We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
+
+A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
+`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
+`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
+We resolved all polytomies in the tree.
+Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
+Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
+As such, we used an intermediate value of p = 0.7.
+We used the R packages *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
+
+#### *Multi-level Meta-regression (MLMR) Models*
+
+After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
+In all models, we included the same random effects as we used in our MLMA models.
+Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
+To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
+
+In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
+We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
+The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
+Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
+We mean-centered the maximum temperature and included it in our models.
+
+With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
+All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
+
+We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
+Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
+Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
+In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
+
+Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
+We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
+
+Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
+We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
+
+Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
+We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
+We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
+We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
+However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
+As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
+
+#### *Modelling how climate change can impact relative variance in physiological rates*
+
+To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
+We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
+We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
+Our model included random effects of species, trait, phylogeny and study.
+We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
+We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
+
+$$
+lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
+$$ {#eq-lCVRpred}
+
+We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
+
+### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
+
+We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
+The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
+To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
+
+$$
+P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
+$$ {#eq-sim}
+
+where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
+We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
+We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
+From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
+
+```{r lnrrq10}
+#| label: lnrrq10
+#| echo: false
+#| cache: true
+#| message: false
+#| warning: false
+#| include: false
+
+#############
+## lnRRQ10 ##
+#############
+##################################################
+# Organise the data and prune tree
+##################################################
+# Subset the data
+lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
+                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
+                                    max_temp_c = scale(temp_2, scale = FALSE))
+
+# Check and prune tree
+tree_lnrr <- tree_checks(data = lnRRQ10_data, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor <- vcv(tree_lnrr, cor = TRUE)
+        A <- vcv(tree_lnrr, cor = FALSE) # For bayes, need cov matrix
+
+# have a quick look on habitat, development and type. Mostly looks sensible but there is not too much data in terrestrial realm.
+sum_life <- lnRRQ10_data %>% group_by(life.hist, type, habitat) %>% summarise(n=n()) %>% arrange(habitat)
+
+##################################################
+# Grafen mode comparison test with different power
+##################################################
+
+rerun = FALSE
+if(rerun){
+    # Create a list of the distinct trees to loop over
+           list  <- list(tree_p0.5, tree_p0.6, tree_p0.7, tree_p0.8, tree_p0.9, tree_p1.0)
+    names(list)  <- c("tree_p0.5", "tree_p0.6", "tree_p0.7", "tree_p0.8", "tree_p0.9", "tree_p1.0")
+
+    # Create an empty list to store the models
+        mod_list <- list()
+
+    for(i in 1:length(list)){
+
+    tree_lnrr_phylo <- tree_checks(data = lnRRQ10_data, tree = list[[i]], dataCol = "species_full", type = "prune")
+    phylo_cor_phylo <- vcv(tree_lnrr_phylo, cor = TRUE)
+       model1_phylo <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_phylo), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data) 
+             mod_list[[i]] <- model1_phylo 
+        names(mod_list)[i] <- names(list)[i]       
+        print(paste0("Model using ", names(mod_list)[i], " is finished with ", length(list)-i, " left to run"))
+    }
+
+  # Save the model list so that it doesn't need to be re-run again. It takes a LONG time otherwise.
+    saveRDS(mod_list, file = "./output/models/lnRRQ10_phylo")
+
+} else {
+
+  # Load the model list
+    #mod_list <- readRDS("./output/models/lnRRQ10_phylo")
+
+  # Have a look at the AIC of the various models to compare which power paramater is best, if any.
+   #aic <- sapply(mod_list, function(x) AIC(x))
+
+}
+
+##################################################
+# Model 1.1: Intercept only model. 
+##################################################
+rerun = FALSE
+if(rerun){
+  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.1
+  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
+  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
+} else{ 
+  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
+model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")
+}
+
+# Heterogeneity analysis
+   w <- with(lnRRQ10_data, 1/V) # weights
+  sv <- sum(w*(dim(lnRRQ10_data)[1]-1)) / (sum(w)^2 + sum(w^2))
+
+# extract posterior sds, but square them to turn to variance
+  posteriors_1.1 <- posterior_samples(model1.1_bayes, pars = c("^sd", "sigma"))^2
+  colnames(posteriors_1.1) <- gsub("__Intercept", "", colnames(posteriors_1.1))
+  colnames(posteriors_1.1) <- gsub("sd_", "", colnames(posteriors_1.1))
+
+    res <- posteriors_1.1[,"sigma"]
+   stdy <- posteriors_1.1[,"record_num"]
+  phylo <- posteriors_1.1[,"species_full"]
+    spp <- posteriors_1.1[,"spp"]
+  trait <- posteriors_1.1[,"trait"]
+  total <- phylo + spp + res + sv + stdy + trait
+
+  # Calculate I2
+     tot_i2 <- (sv / total)*100    ; mean(tot_i2)  ; quantile(tot_i2, c(0.025, 0.975))
+   phylo_i2 <- (phylo / total)*100 ; mean(phylo_i2); quantile(phylo_i2, c(0.025, 0.975))
+     spp_i2 <- (spp / total)*100   ; mean(spp_i2)  ; quantile(spp_i2, c(0.025, 0.975))
+    stdy_i2 <- (stdy / total)*100  ; mean(stdy_i2) ; quantile(stdy_i2, c(0.025, 0.975))
+   trait_i2 <- (trait / total)*100 ; mean(trait_i2); quantile(trait_i2, c(0.025, 0.975))
+     res_i2 <- (res / total)*100   ; mean(res_i2)  ; quantile(res_i2, c(0.025, 0.975))
+
+  # Table
+     i2_lnrr <- data.frame(name = c("Phylogeny", "Species", "Study", "Trait"),
+                           est = c(mean(phylo_i2),mean(spp_i2), mean(stdy_i2), mean(trait_i2)),
+                           lci = c(quantile(phylo_i2, c(0.025, 0.975))[1], quantile(spp_i2, c(0.025, 0.975))[1],
+                                   quantile(stdy_i2, c(0.025, 0.975))[1], quantile(trait_i2, c(0.025, 0.975))[1]),
+                           uci = c(quantile(phylo_i2, c(0.025, 0.975))[2], quantile(spp_i2, c(0.025, 0.975))[2],
+                                   quantile(stdy_i2, c(0.025, 0.975))[2], quantile(trait_i2, c(0.025, 0.975))[2]))
+
+###################################################
+# Model 1.2: Model controlling for acclimation time, 
+# type and habitat assuming type can vary by habitat
+###################################################
+
+if(rerun){
+  # More realistic model with 
+  model1.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+  # Additional model fit as a result of reviewer commenting that acclimation time is assumed to be linear.
+So, fit a non-linear parameter to see if it improves fit (even though data doesn't suggest it is the case).
+   model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+    AIC(model1.2_nl, model1.2) # Again, basically the same and go with most parsimonious model
+
+  # Secondary sensitivity analysis that uses cluster robust variance estimation to deal with unaccounted sources of non-independence.
+Not completely dealing with sharced sampling covariances in data as when collected these data were never indicated in past studies so hard to build full VCV matrix.
+
+   model1.2_rve <- robust(model1.2, cluster = lnRRQ10_data$record_num) # Consistent.
+
+  # Baysian model allows us to propagate error better is should be more robust to non-independence
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.2
+  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
+  saveRDS(model1.2_bayes, file = "./output/models/lnRRQ10_1.2_bayes")
+
+  } else{
+        model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
+  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
+}
+
+####################################################
+## Model 1.2: Bayesian Contrasts
+###################################################
+  posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
+  f_acute  <- posteriors_1.2[,"b_Intercept"]; pmcmc(f_acute)
+  f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
+  m_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"]
+  m_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatm"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatm"]
+  t_acute  <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"]
+  t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
+
+# Q10 values for each category. Effect sizes are quite small really
+   f_acute_Q10 <- exp(f_acute) ; mean(f_acute_Q10); quantile(f_acute_Q10, c(0.025, 0.975))
+  f_acclim_Q10 <- exp(f_acclim); mean(f_acclim_Q10); quantile(f_acclim_Q10, c(0.025, 0.975))
+   m_acute_Q10 <- exp(m_acute) ; mean(m_acute_Q10); quantile(m_acute_Q10, c(0.025, 0.975))
+  m_acclim_Q10 <- exp(m_acclim); mean(m_acclim_Q10); quantile(m_acclim_Q10, c(0.025, 0.975))
+   t_acute_Q10 <- exp(t_acute) ; mean(t_acute_Q10); quantile(t_acute_Q10, c(0.025, 0.975))
+  t_acclim_Q10 <- exp(t_acclim); mean(t_acclim_Q10); quantile(t_acclim_Q10, c(0.025, 0.975))
+
+# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
+  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
+  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
+  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
+  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
+  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.
+
+  # First get sample sizes
+    N <- lnRRQ10_data %>% group_by(habitat, type) %>% summarise(n=n())
+
+  # Calculated weighted mean by sample size. 
+    f_RR_mean <- (f_acute * N[1,"n"][[1]] + f_acclim * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_RR_mean)
+    m_RR_mean <- (m_acute * N[3,"n"][[1]] + m_acclim * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_RR_mean)
+    t_RR_mean <- (t_acute * N[5,"n"][[1]] + t_acclim * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_RR_mean)
+
+  # Rates differ?
+    t_f_rates <- (t_RR_mean - f_RR_mean)
+    t_m_rates <- (t_RR_mean - m_RR_mean)
+
+####################################################
+# Model 1.3's: Trait type varied by acclimation type
+# but data is separated by habitat to simplify
+####################################################
+  # Add two general trait categories to test for trait differences (whole-organism vs biochemical)
+    lnRRQ10_data <- lnRRQ10_data %>% 
+                    mutate(trait_broad = ifelse(trait_category %in% c("cardiac", "rest_MR", "sprint", "muscle", "endurance", "max_MR"), 
+                                                "tissue/organism",
+                                         ifelse(trait_category %in% c("ATPase", "metabolic_enzyme", "antiox", "mito_oxidation", "mito_leak"), 
+                                                "biochemical", trait_category)))
+
+  # Filter to different habitats
+   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m" & trait_broad != "other") 
+   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f" & trait_broad != "other") 
+   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t" & trait_broad != "other")
+
+  # Prune tree
+   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")
+
+   # cor matrices
+   m_phylo <- vcv(tree_m, corr = TRUE)
+       A_m <- vcv(tree_m, corr = FALSE)
+   f_phylo <- vcv(tree_f, corr = TRUE)
+       A_f <- vcv(tree_f, corr = FALSE)
+   t_phylo <- vcv(tree_t, corr = TRUE)
+       A_t <- vcv(tree_t, corr = FALSE)
+
+if(rerun){
+
+#################################
+  # Broad Trait Category Models
+  # Subset to only trait categories 
+  # that are clear. Remove 'other'
+#################################
+  # Full Bayesian model   
+   model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
+                                           (1 | record_num) + 
+                                           (1 | gr(species_full, cov = A)) + 
+                                           (1 + max_temp_c | spp) +(1|trait) + 
+                                           (1 + trait_broad |gr(obs, cor = FALSE)),  
+                                         data2 = list(A=A), family = gaussian(), 
+                                         prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                         control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                         chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = filter(lnRRQ10_data, trait_broad != "other"))
+    saveRDS(model1.3_btrait_bayes, "./output/models/model1.3_btrait_bayes")
+
+  # Metafor models for creating plots. Subset by habitat to make this easier
+      # Marine
+         model1.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = m_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"),  phi = 0,
+                              data = lnRRQ10_data_m)
+         saveRDS(model1.3_m_broad, "./output/models/model1.3_m_broad")
+
+      # Freshwater
+         model1.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = f_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = lnRRQ10_data_f)
+          saveRDS(model1.3_f_broad, "output/models/model1.3_f_broad")
+
+      # Terrestrial
+         model1.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | trait,
+                                            ~1 + trait_broad| obs),
+                              R = list(species_full = t_phylo), dfs = "contain", 
+                              test = "t", struct = c("GEN","HCS"), phi = 0,
+                              data = lnRRQ10_data_t)
+         saveRDS(model1.3_t_broad, "output/models/model1.3_t_broad")
+
+  } else{
+    model1.3_btrait_bayes <- readRDS("./output/models/model1.3_btrait_bayes")
+         model1.3_m_broad <- readRDS("./output/models/model1.3_m_broad")
+         model1.3_f_broad <- readRDS("./output/models/model1.3_f_broad")
+         model1.3_t_broad <- readRDS("./output/models/model1.3_t_broad")
+}
+
+###########################################################
+  # Processing Bayesian Posteriors
+###########################################################
+      # Create new data for predictions
+       trait_b_data <- data.frame(  type = c("acclim", "acute"),
+                              max_temp_c = 0,
+                             c_accl_time = 0,
+                                       V = 0,
+                                 habitat = rep(c("t", "m", "f"), each = 4),
+                             trait_broad = rep(c("tissue/organism", "biochemical"), each = 2))
+
+       # Predict from model. Note this is the summary.
+         pred_lnrr_traitb <- fitted(model1.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = TRUE, 
+                                     robust = FALSE)
+         pred_lnrr_traitb <- cbind(trait_b_data, pred_lnrr_traitb)
+
+       # Predict to get the posterior.
+Note that we have the full posterior distribution here for each of the 12 categories in the new data.
+Here, we want to look at the difference between acute and acclimation within each of the categories.
+            pred_lnrr_trait_post <- fitted(model1.3_btrait_bayes, 
+                                     newdata = trait_b_data, re_formula = NA,
+                                     summary = FALSE, 
+                                     robust = FALSE)
+        contrast_lnrr_trait_post <-  pred_lnrr_trait_post[,c(1,3,5,7,9,11)] - pred_lnrr_trait_post[,c(2,4,6,8,10,12)] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_lnrr_trait_stats <- data.frame( habitat = rep(c("t", "m", "f"), each = 2),
+                                                     trait = rep(c("tissue/organism", "biochemical"), each = 1),
+                                                    diff = sapply(data.frame(contrast_lnrr_trait_post), mean),
+                                                     l95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.025)),
+                                                     u95 = sapply(data.frame(contrast_lnrr_trait_post), function(x) quantile(x, 0.975)),
+                                                       p = sapply(data.frame(contrast_lnrr_trait_post), function(x) p_value(pmcmc(x))))
+       # Contrasts for pooled acute and acclimation across trait categories
+
+            contrast_lnrr_trait_cat_stats <- rbind(get_whole_bio(pred_lnrr_trait_post, habitat = "t", trait_b_data),
+                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "m", trait_b_data),
+                                                        get_whole_bio(pred_lnrr_trait_post, habitat = "f", trait_b_data))
+###########################################################
+## Model 1.4 - whether chance between q10 depends on life stage and habitat
+###########################################################
+rerun = FALSE
+if(rerun){
+  # More realistic model with 
+  model1.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data)
+
+   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+  # Save model1.4
+  saveRDS(model1.4, file = "./output/models/lnRRQ10_1.4")
+  saveRDS(model1.4_bayes, file = "./output/models/lnRRQ10_1.4_bayes")
+
+  } else{
+        model1.4 <- readRDS("./output/models/lnRRQ10_1.4")
+  model1.4_bayes <- readRDS("./output/models/lnRRQ10_1.4_bayes")
+}
+
+#######################################################################
+# Bayesian posteriors from model 1.4
+#######################################################################
+ # Create the data we want to make predictions for. Just more intuitive
+  newdata <- data.frame( c_accl_time = 0, 
+                          max_temp_c = 0, 
+                                type = relevel(factor(c("acclim", "acute")), ref = "acute"), 
+                             habitat = rep(c("m", "f", "t"), each = 4), 
+                           life.hist = rep(c("j", "a"), each = 2))
+
+# Calculate the design matrix using this new data. Need to be careful here to check that the levels are set up the same as the posterior.
+  X <- model.matrix(~max_temp_c + c_accl_time + type*habitat*life.hist, data = newdata)
+
+# Extract posteriors
+  posteriors_1_4 <- posterior_samples(model1.4_bayes, pars = "^b")
+
+# Now we can do all the calculations in one shot.
+         pred <- apply(t(posteriors_1_4), 2, function(x) as.matrix(X)%*%x)
+     sum_pred <- apply(pred, 1, function(x) mean(x))
+  sum_predL95 <- apply(pred, 1, function(x) quantile(x, 0.025))
+  sum_predU95 <- apply(pred, 1, function(x) quantile(x, 0.975))
+            p <- apply(pred, 1, function(x) p_value(pmcmc(x)))
+
+  # Create a summary dataset. 
+  newdata <- cbind(newdata, est = sum_pred, L = sum_predL95, u = sum_predU95, p = p)
+
+# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
+############
+    # Contrast between Acclimation and Acute WITHIN each life-history stage. Double checked a bunch of calculations to make sure the right contrasts were being done. 
+############
+  contrast_lnrr_lh_post <-  pred[c(1,3,5,7,9,11),] - pred[c(2,4,6,8,10,12),] # Acclimation - acute.
+
+        # Contrast statistics
+            contrast_stage_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+                                                     stage = rep(c("j", "a"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnrr_lh_post), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnrr_lh_post), 1, function(x) p_value(pmcmc(x))))
+############
+    # Contrast between Acclimation and Acute ACROSS each life-history stage. Double checked a bunch of comparisons.
+############
+          contrast_lnrr_lh_post_type <-  pred[c(4,3,8,7,12,11),] - pred[c(2,1,6,5,10,9),] # Adult - Jeu.
+
+        # Contrast statistics
+            contrast_type_lnrr_lh_stats <- data.frame( habitat = rep(c("m", "f", "t"), each = 2),
+                                                     type = rep(c("acute", "acclim"), each = 1),
+                                                    diff = apply(data.frame(contrast_lnrr_lh_post_type), 1, mean),
+                                                     l95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.025)),
+                                                     u95 = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) quantile(x, 0.975)),
+                                                       p = apply(data.frame(contrast_lnrr_lh_post_type), 1, function(x) p_value(pmcmc(x))))
+
+  # Acute differences between a and j across all habitats
+     acute_all_lh <- c(contrast_lnrr_lh_post_type[1,], contrast_lnrr_lh_post_type[3,], contrast_lnrr_lh_post_type[5,]) 
+    acclim_all_lh <- c(contrast_lnrr_lh_post_type[2,], contrast_lnrr_lh_post_type[4,], contrast_lnrr_lh_post_type[6,])
+
+  # Contrast adult vs juv across habitats regardless of the acute/acclim
+               contrast_lnrr_lh_cat_stats <- rbind(get_lifestage(pred, habitat = "t", newdata),
+                                                   get_lifestage(pred, habitat = "m", newdata),
+                                                   get_lifestage(pred, habitat = "f", newdata))
+
+####################################################
+# Sensitivity analysis -- Do Acute Q10's (hot / cold) differ?
+####################################################
+ # Goal here is to test the assumption that acute Q10's are different or not. Note Reviewer wanted more analysis in this space so added additional models
+ lnRRQ10_data_acute <-  lnRRQ10_data %>% filter(grepl("acute", name))
+
+ if(rerun){ 
+    model1.s1 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1, file = "./output/models/model1.s1")
+
+    model1.s1_int <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name*habitat, V = V, 
+                              random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_acute)
+    saveRDS(model1.s1_int, file = "./output/models/model1.s1_int")
+
+    AIC(model1.s1_int, model1.s1) # AIC basically the same
+
+    # Bayesian models to check its the same result
+    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+
+    saveRDS(model1.s1_bayes, file = "./output/models/model1.s1_bayes")
+
+    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+
+    saveRDS(model1.s1_bayes_int, file = "./output/models/model1.s1_bayes_int")
+
+} else{
+            model1.s1 <-  readRDS(file = "./output/models/model1.s1")
+            model1.s1_int <-  readRDS(file = "./output/models/model1.s1_int")
+      model1.s1_bayes <- readRDS(file= "./output/models/model1.s1_bayes")
+}
+
+post_acute <- posterior_samples(model1.s1_bayes, pars = "^b")
+  hot_acute <- post_acute[,"b_Intercept"] + post_acute[,"b_namelnRR_Q10_acute_t2"]
+  cold_acute <- post_acute[,"b_Intercept"]
+  change_acute <- post_acute[,"b_namelnRR_Q10_acute_t2"]
+
+n_acutes <- lnRRQ10_data_acute  %>% group_by(name, habitat) %>% summarise(n = n(), stdy = n_distinct(record_num), spp = n_distinct(species_full))  %>% arrange(habitat)
+
+```
+
 ## **Results**
@@
 In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
-
-Across habitats, the extent to which whole-organism versus biochemical traits acclimated varied ("Model 3"; [@fig-btrait]A-C).
-Biochemical traits acclimated to a greater extent compared to whole-organism traits in marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated similarly in freshwater ectotherms ([@fig-btrait]C).
-Neither trait category acclimated in terrestrial ectotherms ([@fig-btrait]A).
 
@@
 
-```{r, fig-btrait}
-#| label: fig-btrait
-#| fig-cap: "Meta-analysis results for organismal and biochemical trait categories.
-Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
-Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
-"
-#| echo: false
-#| warning: false
-
-add_theme  <- function(){theme(axis.title  = element_text(size = 30),
-                               axis.text.y = element_text(size = 30),
-                               axis.text.x = element_text(size = 30),
-                              legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 36))}
-
-branch.size = 2.8
-trunk.size = 1.8
-
-n_lnrr_btrait  <- lnRRQ10_data  %>% filter(trait_broad != "other") %>% 
-              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
-n_lnvr_btrait <- lnVRQ10_data %>% filter(trait_broad != "other") %>% 
-              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
-
-       col <- c("#0871B9", "#F3B40D", "#1BB908")
-     x.pos <- c(0.7, 1.30, 1.70, 2.30)
-size_annot <- 5.5
-
-############
-# lnRR
-############
-m_r <- n_lnrr_btrait %>% filter(habitat == "m")
-f_r <- n_lnrr_btrait %>% filter(habitat == "f")
-t_r <- n_lnrr_btrait %>% filter(habitat == "t")
-
-t_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-m_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-f_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-
-yloc = c(1.5, 2.5)
-
-p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -0.8, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
-
-p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.5, 2) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
-
-p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.25, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8)
-
-############
-# lnVR
-############
-m_r_vr <- n_lnvr_btrait %>% filter(habitat == "m")
-f_r_vr <- n_lnvr_btrait %>% filter(habitat == "f")
-t_r_vr <- n_lnvr_btrait %>% filter(habitat == "t")
-
-t_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-m_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-f_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
-
-yloc = c(1.5, 2.5)
-
-p1_vr_trait <- orchard_plot(model3.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r_vr$k, " (", m_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b_vr$diff, " [", m_trait_b_vr$l95, " to ", m_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_vr$p)), hjust = 0, size = 8)
-
-p2_vr_trait <- orchard_plot(model3.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r_vr$k, " (", f_r_vr$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b_vr$diff, " [", f_trait_b_vr$l95, " to ", f_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_vr$p)), hjust = 0, size = 8)
-
-p3_vr_trait <- orchard_plot(model3.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5, 3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r_vr$k, " (", t_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b_vr$diff, " [", t_trait_b_vr$l95, " to ", t_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_vr$p)), hjust = 0, size = 8)
-
-############
-# Full fig
-############
-figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/fig4.png")
-figbtrait
-```
-
 ```{r, fig-cvrlh}
@@
 ```
-
-Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
-Variance increases for biochemical traits was reduced during acclimation in marine ectotherms ([@fig-btrait]E).
 
@@
 
-Biochemical traits (e.g., enzyme activities) were more likely to acclimate compared to whole-organism traits as predicted, but only for marine ectotherms, presumably because of the less complicated physiological networks that underlie specific biochemical processes [@schulte2011thermal].
-However, whole-organism and biochemical traits acclimated to the same extent in freshwater ectotherms.
-Differences between marine and freshwater ectotherms do not appear to be related to the types of traits measured across the habitats but rather that the traits responded differently.
-However, it is important to note that whole-organism traits in marine ectotherms did respond in the same direction and of a similar magnitude to freshwater ectotherms, so it is possible the difference in marine habitats is simply a sampling artefact.
-
 ### ***Increased variability in physiological rates across habitats: adaptive potential of physiological processes in the face of climate change?***
@@
 
-Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when fluctuations are predictable over time to make environmental cues reliable [@Chevin2017; @Lande2009; @Chevin2010; @Nunney2016; @Murren2015; @hendry2016key; @Reed2010].
+Theoretical models predict that plasticity should evolve in populations experiencing greater environmental variability (spatial or temporal), particularly when fluctuations are predictable over time to make environmental cues reliable [@Chevin2017; @Lande2009; @Chevin2010; @Murren2015;  @Reed2010].
 Higher spatial and temporal heterogeneity in terrestrial habitats [@steele2019comparison] therefore suggest that plasticity is more likely to evolve in terrestrial environments.
 However, if thermal variability is too high and unpredictable, the rates of acclimation decrease and there are increased costs associated with re-modelling physiological processes [@angilletta2009thermal] it would instead be expected that phenotypes are canalised during development [@angilletta2009thermal; @Seebacher2015-wi; @loughland2020differences; @Leung2020; @rescan2022experimental; @leung2023phenotypic].
-The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [@hendry2016key; @Leung2020].
+The lack of acclimation in terrestrial ectotherms we observed is consistent with the latter hypothesis, and is supported by other meta-analyses of heat tolerance [@barley2021limited; @Gunderson2015-hz] suggesting that there are costs to being plastic or that the environmental signals are insufficient to trigger endocrine and epigenetic mechanisms that lead to plasticity when environments are not predictable [ @Leung2020].
 
@@
 
-## **Materials and Methods**
-
-### *Literature collection*
-
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
-We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
-We extracted data from an extra `r length(unique(new_papers$record_num))` papers (with a total of `r dim(new_papers)[1]` effects; a `r  (length(unique(new_papers$record_num)) / length(unique(old_papers$record_num)))*100`% increase in the number of published articles).
-For full details on the search protocol, see the *Supplementary Materials*, where we also provide a PRISMA flow diagram of our extraction process (@fig-prisma).
-
-### *Data Compilation*
-
-We extracted means, standard deviations, and sample sizes for physiological rates measured at the two test temperatures that coincided with acclimation temperatures ([@fig-concept]A).
-If there were more than two temperatures, we chose only the temperatures that fell within the most likely natural range of temperatures experienced by the species in question (@fig-concept).
-We extracted these data from text, tables or figures of a given paper.
-Data were extracted from figures using the R package *metaDigitise* [@Pick2019-mg].
-We also recorded the phylum, class, order, genus and species, and the latitude and longitude from where the experimental animals were sourced.
-For studies that did not provide latitude and longitude for the population, we searched for similar studies by the same lab group to identify where the population was likely to have been sourced.
-If the experimental animals were derived from the wild, we recorded the nearest latitude and longitude of the field collection site.
-If the animals were sourced from a commercial supplier, we took the latitude and longitude of the supplier.
-When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.
-
-### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
-
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
-Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
-
-#### *Comparing changes in mean physiological rates*
-
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
-
-$$
-  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10}
-
-Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
-Log transformation of this ratio makes the effect size normally distributed.
-@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
-The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
-
-$$
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-Vlnq10}
-
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
-
-#### *Comparing variance in physiological rates*
-
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
-
-$$
-lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10VR} $$
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slnq10VR}
-
-where parameters are defined above.
-@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
-As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR} $$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$.
-We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
-
-#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
-
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
-For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
-For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
-Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
-We test and control for any violations of these assumptions in our analysis (see below).
-
-### *Moderator Variables*
-
-We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates.
-This included the duration of acclimation in days given that acclimation responses may depend on how long chronic temperature exposure occurs.
-We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015-wi show that these factors can impact $Q_{10}$ estimates.
-Physiological rate measures varied widely across the studies but could generally be grouped into two broad categories that included whole-organism measures, which all integrate a diversity of physiological and biochemical processes, and biochemical processes (e.g., enzyme reaction rates, proton leak) [@Seebacher2015-wi; @rezende2019thermal].
-We explore differences across more detailed trait categories in *Supplemental Materials*, but note sample sizes are limited for many traits.
-Traits that could not be categorised into these two we classified as ‘Other’.
-
-### *Meta-Analysis*
-
-We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
-`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers.
-`r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers.
-`r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
-We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
-2.0, @Nakagawa2021-ls; @nakagawaorchard].
-In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].
-In all cases, frequentist and Bayesian models resulted in the same conclusions.
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
-We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
-
-#### *Multi-level Meta-analysis (MLMA) Models*
-
-We first fit multi-level meta-analysis (MLMA) models (i.e., intercept-only models) for both $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$, that included study, species, trait type, and phylogeny as random effects to account for non-independence and identify sources of variability.
-We refer to this model structure as “Model 1” in the results.
-Our MLMA models allowed us to partition the variation in $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ among these key sources while accounting for total sampling variance in each.
-This allowed us to calculate the proportion of total heterogeneity [i.e., $I_{total}^2$; *sensu* @Nakagawa2012-oc; @Noble2022-ty] along with various $I^2$ metrics describing the proportion of variance explained by each random effect level [@Nakagawa2012-oc].
-We also present 95% prediction intervals which describe the expected distribution of effects for future studies [@Nakagawa2021-ls; @Noble2022-ty].
-
-A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers.
-`r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers.
-`r utils::packageVersion("ggtree")`) [@Yu2017-wj].
-We resolved all polytomies in the tree.
-Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
-Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$.
-As such, we used an intermediate value of p = 0.7.
-We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
-`r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
-
-#### *Multi-level Meta-regression (MLMR) Models*
-
-After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions.
-In all models, we included the same random effects as we used in our MLMA models.
-Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean $\pm$ SD = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean $\pm$ SD = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]` days, n = `r acclim_time[3,4]`) than freshwater (mean $\pm$ SD = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]` days, n = `r acclim_time[1,4]`) and marine species (mean $\pm$ SD = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]` days, n = `r acclim_time[2,4]`).
-To control for these differences, acclimation time was mean-centered (mean = 0) and included in all our models, although it was not a strong predictor of effect size variation in any of our models (*Supplementary Materials*, @fig-accl_time).
-
-In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
-We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
-Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
-We mean-centered the maximum temperature and included it in our models.
-
-With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
-
-We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
-Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
-Reduced mean $lnRR_{Q_{10_{acclimation}}}$ relative to $lnRR_{Q_{10_{acute}}}$ indicates that acclimation to thermal environments results in (partial) compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ indicates that organisms did not acclimate [@Havird2020-mj; @Seebacher2015-wi].
-In contrast, a difference in $lnVR_{Q_{10_{acclimation}}}$ relative to $lnVR_{Q_{10_{acute}}}$ would show that changes in between-individual variation differ between acute responses and acclimation responses.
-
-Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
-We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
-
-Third, we tested whether different life-stages were more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type (referred to as "Model 4").
-We predicted that acclimation responses would be more likely early in development compared to later in development as this pattern has been shown in previous studies [e.g.,@moghadam2019heat], but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.
-
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
-We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
-We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").
-We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location.
-However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa.
-As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
-
-#### *Modelling how climate change can impact relative variance in physiological rates*
-
-To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
-We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
-We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
-Our model included random effects of species, trait, phylogeny and study.
-We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
-We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
-
-$$
-lnVR_{Q_{1}} = \frac{lnVR_{Q_{10}}}{10}
-$$ {#eq-lCVRpred}
-
-We then multiplied this predicted change by the change in air and sea surface temperatures at the locations of each population (and species) that is expected under high emissions scenarios in 2080.
-
-### *Publication Bias*
-
-We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
-Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
-However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
-As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
-There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
-
-### *Identifying patterns of among-individual variance in performance curves contributing to variance increases*
-
-We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
-The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.
-To simulate performance curves, we used an asymmetrical Gaussian function [@angilletta2009thermal]:
-
-$$
-P_{T} = 2\epsilon^{-\frac{(T-\delta)^2}{2\sigma^2}}\Phi\left(\alpha\frac{T-\delta}{\sigma}\right)
-$$ {#eq-sim}
-
-where $T$ is temperature, $\delta$ is the optimal temperature (the temperature where performance is maximized), $\sigma$ the performance breadth, and $\alpha$ the skewness of the curve (see @fig-sim in *Supplementary Materials* for example curves).
-We simulated *n* = 1000 individual performance curves by varying the amount of between individual variance on each of the key parameters ($\delta$, $\sigma$) in all possible combinations from 0.01 to 2.
-We also varied $\alpha$, but this did not impact our conclusions and so we kept among-individual variation fixed for each simulation (at 0.01).
-From the population of performance curves, we took the standard deviation at two temperatures (18 and 28°C) to calculate $lnVR_{Q_{10}}$ and identify potential parameter spaces that could produce observed patterns in our empirical data.
-
 ## Acknowledgements
@@
 ```
+
+### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
+
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+
+#### *Comparing changes in mean physiological rates*
+
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+
+$$
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10}
+
+Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
+Log transformation of this ratio makes the effect size normally distributed.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
+The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
+
+$$
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-Vlnq10}
+
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
+
+#### *Comparing variance in physiological rates*
+
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
+$$
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10VR} $$
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slnq10VR}
+
+where parameters are defined above.
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR} $$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
+
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
+
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below).
 
@@
 #### **Acute and acclimation* for detailed trait categories across marine, freshwater and terrestrial taxa**
+
+Across habitats, the extent to which whole-organism versus biochemical traits acclimated varied ("Model 3"; [@fig-btrait]A-C).
+Biochemical traits acclimated to a greater extent compared to whole-organism traits in marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated similarly in freshwater ectotherms ([@fig-btrait]C).
+Neither trait category acclimated in terrestrial ectotherms ([@fig-btrait]A).
+
+Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
+Variance increases for biochemical traits was reduced during acclimation in marine ectotherms ([@fig-btrait]E).
+
+```{r, fig-btrait}
+#| label: fig-btrait
+#| fig-cap: "Meta-analysis results for organismal and biochemical trait categories.
+Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) effect sizes for tissue/whole-orgamism traits and biochemical traits across terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
+Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, raw data for both trait categories are presented but points are not distinguished by different symbols.
+"
+#| echo: false
+#| warning: false
+
+add_theme  <- function(){theme(axis.title  = element_text(size = 30),
+                               axis.text.y = element_text(size = 30),
+                               axis.text.x = element_text(size = 30),
+                              legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 36))}
+
+branch.size = 2.8
+trunk.size = 1.8
+
+n_lnrr_btrait  <- lnRRQ10_data  %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+n_lnvr_btrait <- lnVRQ10_data %>% filter(trait_broad != "other") %>% 
+              group_by(habitat, trait_broad, type) %>% summarise(k = n(), spp = length(unique(spp))) %>% arrange(trait_broad, type, habitat)
+
+       col <- c("#0871B9", "#F3B40D", "#1BB908")
+     x.pos <- c(0.7, 1.30, 1.70, 2.30)
+size_annot <- 5.5
+
+############
+# lnRR
+############
+m_r <- n_lnrr_btrait %>% filter(habitat == "m")
+f_r <- n_lnrr_btrait %>% filter(habitat == "f")
+t_r <- n_lnrr_btrait %>% filter(habitat == "t")
+
+t_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b <- contrast_lnrr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+yloc = c(1.5, 2.5)
+
+p1 <- orchard_plot(model1.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.8, 1.8) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -0.8, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+
+p2 <- orchard_plot(model1.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-0.5, 2) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", f_r$k, " (", f_r$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.5, label = TeX(paste0("$\\beta$ = ", f_trait_b$diff, " [", f_trait_b$l95, " to ", f_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b$p)), hjust = 0, size = 8)
+
+p3 <- orchard_plot(model1.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-0.3, 1.8) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_r$k, " (", t_r$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -0.25, label = TeX(paste0("$\\beta$ = ", t_trait_b$diff, " [", t_trait_b$l95, " to ", t_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b$p)), hjust = 0, size = 8)
+
+############
+# lnVR
+############
+m_r_vr <- n_lnvr_btrait %>% filter(habitat == "m")
+f_r_vr <- n_lnvr_btrait %>% filter(habitat == "f")
+t_r_vr <- n_lnvr_btrait %>% filter(habitat == "t")
+
+t_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "t") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+m_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "m") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+f_trait_b_vr <- contrast_lnvr_trait_stats %>% filter(habitat == "f") %>% purrr::modify_if(~is.numeric(.), ~round(., 2)) %>% arrange(trait)
+
+yloc = c(1.5, 2.5)
+
+p1_vr_trait <- orchard_plot(model3.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-1.5, 3) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", m_r_vr$k, " (", m_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black",4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", m_trait_b_vr$diff, " [", m_trait_b_vr$l95, " to ", m_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_vr$p)), hjust = 0, size = 8)
+
+p2_vr_trait <- orchard_plot(model3.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Freshwater")  + add_theme() + theme(legend.position = "none", axis.text.y = element_blank()) + ylim(-1.5, 3) + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", f_r_vr$k, " (", f_r_vr$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1)) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", f_trait_b_vr$diff, " [", f_trait_b_vr$l95, " to ", f_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_vr$p)), hjust = 0, size = 8)
+
+p3_vr_trait <- orchard_plot(model3.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t", legend.pos = "none"), group = "record_num", xlab = TeX("$lnVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size, angle = 45)+ labs(title = "Terrestrial") + add_theme()  +  ylim(-1.5, 3) + theme(legend.position = "none") + annotate("text", x = x.pos, y = 2.5, label = TeX(paste0("\\it{k} = ", t_r_vr$k, " (", t_r_vr$spp, ")")), size = size_annot) + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.5, label = TeX(paste0("$\\beta$ = ", t_trait_b_vr$diff, " [", t_trait_b_vr$l95, " to ", t_trait_b_vr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_vr$p)), hjust = 0, size = 8)
+
+############
+# Full fig
+############
+figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
+ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/fig4.png")
+figbtrait
+```
 
@@
 #### **Publication bias analysis**
+### *Publication Bias*
+
+We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models [@Nakagawa2022-gy].
+Funnel plot asymmetry indicates a form of publication bias called the ‘file-drawer’ effect whereby low-powered studies are less likely to be published.
+However, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy].
+As such, we included $\sqrt{1/ne}$ as a moderator in a multilevel meta-regression model that accounted for all the random (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).
+There was no evidence for publication bias, and results are presented in the *Supplementary Materials* (see @fig-s2).
 

### 2024-12-11 ms.qmd
Running models with slope for type

@@
 if(rerun){
-  # More realistic model with 
+  # More realistic model with.
+*** Reviewers want to control for the fact that we want to estimate the difference in effect sizes between acclimation and acute responses at the level of each effect size within each study.
+We can do this using random slope and will deal with studies where only acclimation is estimated better without loosing power.***
   model1.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
 
-  # Baysian model allows us to propagate error better is should be more robust to non-independence
-   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+  # Baysian model allows us to propagate error better is should be more robust to non-independence.
+*** Reviewers want to control for the fact that we want to estimate the difference in effect sizes between acclimation and acute responses at the level of each effect size within each study.
+We can do this using random slope and will deal with studies where only acclimation is estimated better without loosing power.***
+   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 + type| record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 

### 2024-12-12 ms.qmd
Added abstract and adjusting models to include random slope. The climate analysis needs some thought because its true this one will need to use a sub-sample of data and compare acute AND aclcimation difference to climate. An interaction model will only ask if the effect of climate variability itself differs in its relationship for acute and acclimation effects

@@
 **Running head**: Physiological rate variation in ectotherms
-
+Havird 
 ## **Abstract**
 
-Climate change causes warmer and more variable temperatures globally, impacting physiological rates and function in ectothermic animals.
+1.	Climate change causes warmer and more variable temperatures globally, impacting physiological rates and function in ectothermic animals.
 Acclimation of physiological rates can help maintain function.
 However, it is unresolved how variance in physiological rates changes with temperature despite its potential ecological and evolutionary importance.
-We tested the extent to which thermal variation affects variation physiological rates and their capacity to acclimate in ectotherms by conducting a meta-analysis (>1900 effects from 226 species) and applying new effect sizes that quantify how trait mean and variance change as temperature increases.
-Comparing both the magnitude of acclimation and changes in variation side-by-side provides unique opportunities for evaluating the importance of plasticity or selection under climate change.
-We show that variance in physiological rates increases at higher temperatures, but that the magnitude of change depends on habitat.
+2.	2.	We developed new effect sizes that capture how both the mean and variation in physiological rates change across temperature (based on the temperature coefficient, $Q_{10}$), and used them to test how acclimation and acute thermal responses vary across aquatic and terrestrial ectotherms using meta-analysis (>1900 effects from 226 species).
+Comparing both the magnitude of acclimation and changes in variation side-by-side provides unique opportunities for evaluating the importance of plasticity and selection under climate change.
+3.	We show that variance in physiological rates increases at higher temperatures, but that the magnitude of change depends on habitat.
 Freshwater and marine ectotherms are capable of acclimation and have the greatest increase in variance.
@@
 Simulations suggest that these patterns may result from differences in among-individual variation in thermal breadth and optima of performance curves across habitats.
-Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in variance may provide less raw material for evolutionary adaptation.
+4.	Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in variance may provide less raw material for evolutionary adaptation.
 Considering both acclimation capacity and variance in physiological rates side-by-side is therefore important for understanding how climate change will impact populations.
@@
    model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
                               R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data)
+                              test = "t", data = lnRRQ10_data, control = list(optimizer = "bobyqa", rel.tol=1e-8, maxeval=1000)) #‘bobyqa’
 
@@
   model3.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
    model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + 
-        (~1 | record_num) + 
+        (~1 + type| record_num) + 
         (1 | gr(species_full, cov = A_VR)) + 
@@
    model3.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
-                                           (1 | record_num) + 
+                                           (1 + type | record_num) + 
                                            (1 | gr(species_full, cov = A_VR)) + 
@@
          model3.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
          model3.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
          model3.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
   model3.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type| record_num,
                                             ~1 | species_full,
@@
    model3.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
-                                 (~1 | record_num) + 
+                                 (1 + type | record_num) + 
                                  (1 | gr(species_full, cov = A_VR)) + 
@@
   model3.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
 
-   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
+   model3.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c + (1 + type | record_num) + (1 | gr(species_full, cov = A_wild)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild=A_wild), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild)
 
@@
 #######################################
-  ## lnCVRQ10 from Wild Populations ##
+  ## lnVRQ10 from Wild Populations ##
 #######################################
@@
   model5.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
 
-   model5.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_vr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_vr=A_wild_vr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data_wild)
+   model5.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (1 + type| record_num) + (1 | gr(species_full, cov = A_wild_vr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_vr=A_wild_vr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data_wild)
 
@@
 
-   model5.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data_wild_acclim)
+   model5.9_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c + (1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data_wild_acclim)
 
@@
    model6_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) +
-                               (1 | record_num) + 
+                               (1 + type | record_num) + 
                                (1 | gr(species_full, cov = A_wild_vr)) + 
@@
 
-#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
 
@@
 compared to r1.2, r2.1, r2.2) (@tbl-slopes).
-In freshwater ectotherms, there we some differences in scaling relationships but they were all fairly comparable no matter what acclimation and test temperature (@tbl-slopes).
+In freshwater ectotherms, there were some differences in scaling relationships but they were all fairly comparable no matter what acclimation and test temperature (@tbl-slopes).
 
@@
   model2.2 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + habitat + type:habitat, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
 
-   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (1 + type | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
 
@@
    model2.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
-                                           (1 | record_num) + 
+                                           (1 + type | record_num) + 
                                            (1 | gr(species_full, cov = A)) + 
@@
          model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type| record_num,
                                             ~1 | species_full,
@@
          model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type| record_num,
                                             ~1 | species_full,
@@
          model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
   model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
    model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
-                                 (~1 | record_num) + 
+                                 (~1 + type| record_num) + 
                                  (1 | gr(species_full, cov = A_CVR)) + 
@@
   model3.8  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type| record_num,
                                             ~1 | species_full,
@@
 
-   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
+   model3.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c + (1 + type | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acclim)
 
@@
     model3.8_t  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type| record_num,
                                             ~1 | species_full,
@@
     model3.8_f  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
       model3.8_m  <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + acf_lag1_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
 
-   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
+   model4.8_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + acf_lag1_c + habitat + habitat:acf_lag1_c + (1 | record_num) + (1 | gr(species_full, cov = A_wild_acclim)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_acclim=A_wild_acclim), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data_wild_acclim)
 
@@
 #### **Publication bias analysis**
-### *Publication Bias*
 
@@
 
-    model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
-
-    model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
-
-    model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
+    model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 + type | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+
+    model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 + type | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)
+
+    model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(n_ef) + habitat*life.hist*type + trait_category + (~1 + type| record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 1, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)
 

### 2024-12-13 ms.qmd
Updates to models

@@
 
+### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
+
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
+These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
+Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
+
+#### *Comparing changes in mean physiological rates*
+
+To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
+
+$$
+  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10}
+
+Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
+Log transformation of this ratio makes the effect size normally distributed.
+@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
+This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
+The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
+
+$$
+  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-Vlnq10}
+
+Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
+
+#### *Comparing variance in physiological rates*
+
+@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
+*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
+We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+
+$$
+lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10VR} $$
+s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slnq10VR}
+
+where parameters are defined above.
+@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR} $$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
+
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
+
+$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
+As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
+We test and control for any violations of these assumptions in our analysis (see below).
+
 ### *Moderator Variables*
@@
 
-  # Additional model fit as a result of reviewer commenting that acclimation time is assumed to be linear.
-So, fit a non-linear parameter to see if it improves fit (even though data doesn't suggest it is the case).
-   model1.2_nl <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + I(c_accl_time^2) + type + habitat + type:habitat, V = V, 
-                              random = list(~1 + type | record_num,
-                                            ~1 | species_full,
-                                            ~1 | trait,
-                                            ~1 + max_temp_c| spp,
-                                            ~1 | obs),
-                              R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data, control = list(optimizer = "bobyqa", rel.tol=1e-8, maxeval=1000)) #‘bobyqa’
-
-    AIC(model1.2_nl, model1.2) # Again, basically the same and go with most parsimonious model
-
   # Secondary sensitivity analysis that uses cluster robust variance estimation to deal with unaccounted sources of non-independence.
@@
    model1.3_btrait_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*trait_broad*habitat + 
-                                           (1 | record_num) + 
+                                           (1 + type | record_num) + 
                                            (1 | gr(species_full, cov = A)) + 
@@
 
-  # Metafor models for creating plots. Subset by habitat to make this easier
+  # Metafor models for creating plots.
+Subset by habitat to make this easier.
+**NOTE: For these models we are only able to include two random slopes.
+Metafor does not allow additional terms.
+Given that trait type slope is in Bayeisan model and it doesn't generally impact things much we will not include it here givem these models just make it more convient to plot.
       # Marine
@@
   model1.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + type | record_num,
                                             ~1 | species_full,
@@
 
-   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
+   model1.4_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type*habitat*life.hist + (1 + type| record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
 
@@
     model1.s1 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + name | record_num,
                                             ~1 | species_full,
@@
                               R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
+                              test = "t", data = lnRRQ10_data_acute, control = list(optimizer = "bobyqa"))
     saveRDS(model1.s1, file = "./output/models/model1.s1")
@@
     model1.s1_int <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + name*habitat, V = V, 
-                              random = list(~1 | record_num,
+                              random = list(~1 + name | record_num,
                                             ~1 | species_full,
@@
                               R = list(species_full = phylo_cor), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_acute)
+                              test = "t", data = lnRRQ10_data_acute, control = list(optimizer = "bobyqa"))
     saveRDS(model1.s1_int, file = "./output/models/model1.s1_int")
 
-    AIC(model1.s1_int, model1.s1) # AIC basically the same
+    AIC(model1.s1_int, model1.s1) # AIC better for non-interaction model
 
     # Bayesian models to check its the same result
-    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+    model1.s1_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name + (~1 + name| record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
 
@@
 
-    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
+    model1.s1_bayes_int <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + name*habitat + (~1 + name | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_acute)
 
@@
    model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + 
-        (~1 + type| record_num) + 
+        (1 + type| record_num) + 
         (1 | gr(species_full, cov = A_VR)) + 
@@
 
-  # Metafor models for creating plots. Subset by habitat to make this easier
+  # Metafor models for creating plots. Subset by habitat to make this easier. Again, only able to fit two 'random slopes' so need to keep them simplier but still only for plotting.
       # Marine
          model3.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 + type | record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,
@@
          model3.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 + type | record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,
@@
          model3.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 + type | record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,
@@
                                control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
+                               chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
 
@@
 ```
-
-### $Q_{10}$ Based Effect Sizes and Sampling Variances for Means and Variances
-
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
-These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
-Sampling variances for effect sizes allowed us to make use of traditional meta-analytic modelling approaches.
-
-#### *Comparing changes in mean physiological rates*
-
-To compare mean physiological rates, we calculated the log $Q_{10}$ response ratio, $lnRR_{Q_{10}}$ [@Noble2022-ty] as follows:
-
-$$
-  lnRR_{Q_{10}} = ln\left( \frac{R_{2}}{R_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10}
-
-Where, $R_{1}$ and $R_{2}$ are mean physiological rates at temperatures $T_{1}$ and $T_{2}$, respectively.
-Log transformation of this ratio makes the effect size normally distributed.
-@eq-lnq10 is essentially a temperature corrected equivalent to the log response ratio (lnRR) [@Hedges1999-de; @Lajeunesse2011-fq] when the numerator and denominator are measured at different temperatures.
-This allows comparisons of the means from two temperature treatments directly regardless of the absolute measurement temperatures.
-The sampling variance for @eq-lnq10 can be computed as follows [as described in @Noble2022-ty]:
-
-$$
-  s_{lnRR_{Q_{10}}} = \left( \frac{SD_{2}^2}{R^2_{2}N_{2}} + \frac{SD_{1}^2}{R^2_{1}N_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-Vlnq10}
-
-Here, $SD_{1}^2$ and $SD_{2}^2$ are the standard deviations, and $N_{1}$ and $N_{2}$ are the sample sizes of the groups measured at $T_{1}$ and $T_{2}$, respectively ([@fig-concept]A).
-
-#### *Comparing variance in physiological rates*
-
-@Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
-
-$$
-lnVR_{Q_{10}} = ln\left( \frac{SD_{2}}{SD_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10VR} $$
-s_{lnVR_{Q_{10}}} = \left( \frac{1}{2\left( N_{2}-1 \right)} + \frac{1}{2\left(N_{1} - 1\right)} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slnq10VR}
-
-where parameters are defined above.
-@eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
-As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR} $$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$.
-We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
-
-#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
-
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
-For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
-For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
-For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
-Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
-We test and control for any violations of these assumptions in our analysis (see below).
 

### 2024-12-13 ms.qmd
Models

@@
 #| warning: false
-#| 
+
 #######################################
@@
 # Create a match column.
-climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+climate2 <- climate %>% 
+            mutate(match = interaction(Species, Latitude, Longitude)) %>% 
+            dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
 
 # Subset the data
-lnRRQ10_data_wild <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
+lnRRQ10_data_wild <- data_long2 %>% 
+                    filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period) & source == "w") %>% 
                       mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE), match = interaction(spp, lat, long), 
@@
                                            (1 + trait_broad |gr(obs, cor = FALSE)),  
-                                         data2 = list(A=A), family = gaussian(), 
+                                         data2 = list(A=A_CVR), family = gaussian(), 
                                          prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
@@
          model2.3_m_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 + type| record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,
@@
          model2.3_f_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 + type| record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,
@@
          model2.3_t_broad <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type + trait_broad + type:trait_broad, V = V, 
-                              random = list(~1 + type | record_num,
+                              random = list(~1 | record_num,
                                             ~1 | species_full,

### 2024-12-13 ms.qmd
Notes

@@
 
-  # Metafor models for creating plots. Subset by habitat to make this easier
+  # Metafor models for creating plots. Subset by habitat to make this easier. Again, cannot include random slope here because it's not possible to do this in metafor.
       # Marine
@@
    model2.4_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat*life.hist + 
-                                 (~1 + type| record_num) + 
+                                 (1 + type| record_num) + 
                                  (1 | gr(species_full, cov = A_CVR)) + 
@@
   model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
-                                       random = list(~1 | record_num,
+                                       random = list(~1 + type| record_num,
                                             ~1 | species_full,
@@
 
-   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
+   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 + type| record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
 
@@
    model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + t2(Longitude, Latitude) +
-                               (1 | record_num) + 
+                               (1 + type | record_num) + 
                                (1 | gr(species_full, cov = A_wild_cvr)) + 

### 2024-12-16 ms.qmd
Chanegs reflected in new quarto doc

@@
 
-Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$) (@fig-concept).
+Following @Noble2022-ty we calculated a series of temperature-corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$) (@fig-concept).
 These effect sizes are similar to the traditional temperature coefficient ($Q_{10}$), but with formal analytical approximations of their sampling variances.
@@
 @Nakagawa2015-fo proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*).
-*lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups.
-We refer readers to @Nakagawa2015-fo for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:
+Here, we focus on *lnVR* but derivations for *lnCVR*, along with re-analyses with lnCVR, are presented in the *Supplementary Materials*.
+In short, *lnVR* is a ratio that describes the difference in trait variability between two groups.
+Like *lnRR*, *lnVR* can also easily be extended to its $Q_{10}$ analogue (and associated sampling variance) as follows:
 
@@
 @eq-lnq10VR and @eq-slnq10VR describe the change in physiological rate variance (@eq-lnq10VR) normalised to a 10°C temperature change along with its sampling variance (@eq-slnq10VR).
-As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR} $$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$.
-We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
-
-#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
+
+#### *Calculating acute and acclimation* $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ estimates*
 
 $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
-For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates.
+For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ estimates.
 For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
 For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
-As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$), variance ($lnVR_{Q_{10}}$) or relative variance (i.e., $lnCVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$) or variance ($lnVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
 Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
@@
 ```
+
+### *Comparing relative variance changes: the *lnCVR* ratio*
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR} $$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
 

### 2024-12-17 R/functions.R
New functions for averaging

@@ -522,3 +522,17 @@ post_summary <- function(x){
    
  }
  
+#' @title weighted_avg_effects
+#' @description Calculates the weighted average effect for two effect sizes and their sampling variances. This is used to average the two acute effects for the climate analysis.
+ weighted_avg_effects <- function(ef1, ef2, sv1, sv2){
+      w1 = 1/sv1
+      w2 = 1/sv2
+      return((ef1*w1 + ef2*w2)/(w1 + w2))
+  }
+#' @title weighted_avg_sv
+#' @description Calculates the sampling variance for teh weighted average effect size. This is used to average the two acute effects for the climate analysis.
+  weighted_avg_sv <- function(sv1, sv2){
+      w1 = 1/sv1
+      w2 = 1/sv2
+      return(1/(w1 + w2))
+  }

### 2024-12-17 R/functions.R
Update notes for functions

@@ -523,14 +523,14 @@ post_summary <- function(x){
  }
  
 #' @title weighted_avg_effects
-#' @description Calculates the weighted average effect for two effect sizes and their sampling variances. This is used to average the two acute effects for the climate analysis.
+#' @description Calculates the weighted average effect for two effect sizes and their sampling variances. This is used to average the two acute effects for the climate analysis. Note that because we want to give greater weight to the effect sizes with the smaller sampling variance, we take the inverse of the sampling variance. This means that the effect size is weighted more in the average.
  weighted_avg_effects <- function(ef1, ef2, sv1, sv2){
       w1 = 1/sv1
       w2 = 1/sv2
       return((ef1*w1 + ef2*w2)/(w1 + w2))
   }
 #' @title weighted_avg_sv
-#' @description Calculates the sampling variance for teh weighted average effect size. This is used to average the two acute effects for the climate analysis.
+#' @description Calculates the sampling variance for teh weighted average effect size. This is used to average the two acute effects for the climate analysis. Note that, we use the precision here because the combined sampling variance needs to also account for the precision of the sampling variances. This is done by taking the inverse of the sum of the precisions.
   weighted_avg_sv <- function(sv1, sv2){
       w1 = 1/sv1
       w2 = 1/sv2

### 2024-12-17 ms.qmd
Data now should be organised for new analysis but secies names are off because used wide dtaa and probably we only cleaned up species names in wide data. S=Need to fix this for phylogenetic tree

@@
 }
+
+```
+
+```{r, wildlnRR_acutevsacclim}
+#| label: wildlnRR_acutevsacclim
+#| echo: false
+#| include: false
+
+###---------------------------------------###
+# Analysis that calculates the plastic adjustment, acclimation - acute within a study and trait to look at whether plasticity is correlated with climate.
+A good point raised by Reviewer 1 that we should test.
+###---------------------------------------###
+
+###---------------------------------------###
+# Data
+###---------------------------------------###
+
+  # Bring in Climate data
+  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+  # Create a match column.
+  climate2 <- climate %>% 
+              mutate(match = paste(Species, Latitude, Longitude, sep =".")) %>% 
+              dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+
+  # Subset the data and do some new calculations
+    # Steps:
+    # 1. Suse wide data
+    # 2. Drop out lnVR and lnCVR
+    # 3.  Exclude effects where we don't have BOTH acute and acclimation. We need both to subtract from each other
+    # 4. Calculate the weighted average of the effects and its associated sampleing variance so we have only a single acute
+    # 5. Clean up by removing old acute columns
+    # 6. Calculate the difference between acclimation and acute and it's associated associated sampling variance
+    # 7. Clean up by removing old acclimation and acute columns as well as all 'r' columns
+    # 8. Add a match column for joining climate data
+
+                          drop <- colnames(data_wide)[grep("ln[CV]", colnames(data_wide))]
+
+  lnRRQ10_data_acc_minus_aclim <- data_wide %>%        
+                  dplyr::select(!all_of(drop)) %>%  
+                  filter(!is.na(lnRR_Q10_acute_t1) | !is.na(lnRR_Q10_acute_t2)) %>% 
+                  mutate(lnRR_acute = weighted_avg_effects(lnRR_Q10_acute_t1, lnRR_Q10_acute_t2, V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2),
+                      lnRR_acute_SV = weighted_avg_sv(V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2))   %>% 
+                  dplyr::select(-lnRR_Q10_acute_t1, -lnRR_Q10_acute_t2, -V_lnRR_Q10_acute_t1, -V_lnRR_Q10_acute_t2)  %>% 
+                  mutate(lnRRQ10_ac_acclimate = lnRR_acute - lnRR_Q10_acclim, 
+                         lnRRQ10_ac_acclimate_SV = lnRR_acute_SV + V_lnRR_Q10_acclim) %>%
+                  dplyr::select(-lnRR_Q10_acclim, -V_lnRR_Q10_acclim, -lnRR_acute_SV, -lnRR_acute, -grep("r", colnames(.)))  %>% 
+                  mutate(match = paste(gsub("_", "", species_full), lat, long, sep = "."), 
+                    max_temp_c = scale(temp_2, scale = FALSE))
+
+# Now that we have the data calcualted as the difference between acute and acclimation for each effect we want to know of this difference, i.e., the direction and magnitude of plasticity is associated with climate.
+We do not need to pivot longer because the response is simply the difference now so we are ready for anlaysis
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnRRQ10_data_wild_acute_vs_acclim <- left_join(lnRRQ10_data_acc_minus_aclim, climate2, by = "match")
+
+# Check and prune tree
+tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
+        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale data
+        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
+                                                          acf_all_c = scale(acf_all))
 

### 2024-12-18 ms.qmd
Fixed tree issue. Was just using wrong tree object

@@
 tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
+tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr_wild, dataCol = "species_full", type = "check") # Good
 

### 2024-12-18 ms.qmd
Added models for acute-acclim effect size for overall habitat differences and to test climate variability hypotheses

@@
                          lnRRQ10_ac_acclimate_SV = lnRR_acute_SV + V_lnRR_Q10_acclim) %>%
-                  dplyr::select(-lnRR_Q10_acclim, -V_lnRR_Q10_acclim, -lnRR_acute_SV, -lnRR_acute, -grep("r", colnames(.)))  %>% 
+                  dplyr::select(-lnRR_Q10_acclim, -V_lnRR_Q10_acclim, -lnRR_acute_SV, -lnRR_acute, -grep("r[12]", colnames(.)))  %>% 
                   mutate(match = paste(gsub("_", "", species_full), lat, long, sep = "."), 
-                    max_temp_c = scale(temp_2, scale = FALSE))
+                    max_temp_c = scale(temp_2, scale = FALSE),
+                           spp = species_full)
 
@@
 # Create the phylo correlation matrix
-phylo_cor_wild <- vcv(tree_lnrr_wild, cor = TRUE)
-        A_wild <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
+phylo_cor_wild_ac_acclim <- vcv(tree_lnrr_wild, cor = TRUE)
+        A_wild_ac_acclim <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
 
 # Scale data
-        lnRRQ10_data_wild <- lnRRQ10_data_wild %>% mutate(cv_c = scale(cv),
-                                                          acf_all_c = scale(acf_all))
+        lnRRQ10_data_wild_acute_vs_acclim <- lnRRQ10_data_wild_acute_vs_acclim %>% 
+                                                        mutate(cv_c = scale(cv),
+                                                          acf_all_c = scale(acf_all),
+                                                          c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# How much data? Quite a bit with both acute and acclimation, which is good.
+        lnRRQ10_data_wild_acute_vs_acclim %>% group_by(habitat) %>% summarise(n = n(), stdy = length(unique(record_num)))
+
+# Plot the effects with climate variation and predcitabiliy
+
+  lnRRQ10_data_wild_acute_vs_acclim  %>% 
+    ggplot(aes(x = acf_all, y = lnRRQ10_ac_acclimate, color = habitat)) + geom_point() + facet_wrap(~habitat) + theme_classic() + my_theme() + labs(x = "Autocorrelation", y = "Acute - Acclimation", color = "Habitat") + geom_smooth(method = "lm", se = FALSE) + geom_smooth(method = "lm", se = FALSE, aes(group = habitat), linetype = "dashed") + theme(legend.position = "none")
+
+  lnRRQ10_data_wild_acute_vs_acclim  %>% 
+    ggplot(aes(x = cv, y = lnRRQ10_ac_acclimate, color = habitat)) + geom_point() + facet_wrap(~habitat) + theme_classic() + my_theme() + labs(x = "Coefficient of Variation (CV)", y = "Acute - Acclimation", color = "Habitat") + geom_smooth(method = "lm", se = FALSE) + geom_smooth(method = "lm", se = FALSE, aes(group = habitat), linetype = "dashed") + theme(legend.position = "none")
+
+# How much missing data in acclimation time?
+  lnRRQ10_data_wild_acute_vs_acclim %>% filter(is.na(acclim_period)) %>% group_by(habitat) %>% summarise(n = n(), stdy = length(unique(record_num)))
+
+####################################################
+  # Model3_new: Model environmental variability by acute/acclim
+####################################################
+  rerun = FALSE
+
+# Ok, now that we have it we may as well just rerun the model using the effect size Reviewer 1 is talking about to show that it is nearly the same (rememnber, we lose power here).
+Also remoember that positive effect sizes show acclimation because it implies the acute slope is larger than the acclimation slope.
+Sp, we expect freshwater and marine to have positive overall effect sizes.
+
+if(rerun){
+model3_new_overall  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + habitat, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                                     ~1 | species_full,
+                                                     ~1 | trait,
+                                                     ~1 + max_temp_c| spp,
+                                                     ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
+  save(model3_new_overall, file = "./output/models/lnRRQ10_3_new_overall")
+} else{
+  model3_new_overall <- readRDS("./output/models/lnRRQ10_3_new_overall")
+}
+
+if(rerun){
+  # More realistic model with 
+  model3_new  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                                     ~1 | species_full,
+                                                     ~1 | trait,
+                                                     ~1 + max_temp_c| spp,
+                                                     ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
+
+    model3_new_bayes <- brms::brm(lnRRQ10_ac_acclimate | se(sqrt(lnRRQ10_ac_acclimate_SV), sigma = TRUE) ~ max_temp_c + c_accl_time + cv_c + 
+                                  habitat + habitat:cv_c + 
+                                  (1 | record_num) + 
+                                  (1 | gr(species_full, cov = A_wild_ac_acclim)) + 
+                                  (1 + max_temp_c| spp) + 
+                                  (1|trait), data2 = list(A_wild_ac_acclim = A_wild_ac_acclim), 
+                                  family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                  control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                  chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acute_vs_acclim)
+
+  # Save model3_new
+    saveRDS(model3_new, file = "./output/models/lnRRQ10_3_new")
+    saveRDS(model3_new_bayes, file = "./output/models/lnRRQ10_3_new_bayes")
+
+  } else{
+        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
+  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
+}
+
+# Orchard plot model3_new
+  orchaRd:orchard_plot(model3_new, )
 

### 2024-12-19 ms.qmd
Extract posteriros and added plot

@@
   save(model3_new_overall, file = "./output/models/lnRRQ10_3_new_overall")
+
+  model3_new_overall_bayes <- brms::brm(lnRRQ10_ac_acclimate | se(sqrt(lnRRQ10_ac_acclimate_SV), sigma = TRUE) ~ 
+                                max_temp_c + c_accl_time + habitat + (1 | record_num) + 
+                              (1 | gr(species_full, cov = A_wild_ac_acclim)) + 
+                              (1 + max_temp_c| spp) + 
+                              (1|trait), 
+                              data2 = list(A_wild_ac_acclim = A_wild_ac_acclim), 
+                              family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                              control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                              chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
+                              data = lnRRQ10_data_wild_acute_vs_acclim)
+save(model3_new_overall_bayes, file = "./output/models/lnRRQ10_3_new_overall_bayes")
+
 } else{
   model3_new_overall <- readRDS("./output/models/lnRRQ10_3_new_overall")
+  model3_new_overall_bayes <- readRDS("./output/models/lnRRQ10_3_new_overall_bayes")
 }
+
+####################################################
+  # Get contrasts from overall model
+####################################################
+
+  # Extract posteriors
+  posteriors_3_overall <- posterior_samples(model3_new_overall_bayes, "^b")
+
+  # Freshwater
+    f_ac_acclim  <- posteriors_3_overall[,"b_Intercept"]; pmcmc(f_ac_acclim); mean(f_ac_acclim); quantile(f_ac_acclim, c(0.025, 0.975))
+  # Marine
+    m_ac_acclim  <- f_ac_acclim + posteriors_3_overall[,"b_habitatm"]; pmcmc(m_ac_acclim); mean(m_ac_acclim); quantile(m_ac_acclim, c(0.025, 0.975))
+  # Terrestrial
+    t_ac_acclim  <- f_ac_acclim + posteriors_3_overall[,"b_habitatt"]; pmcmc(t_ac_acclim); mean(t_ac_acclim); quantile(t_ac_acclim, c(0.025, 0.975))
+
+     col <- c("#0871B9", "#F3B40D", "#1BB908")
+  k_lnrr_ac_acl <- manual_extract(model3_new_overall, mod = "habitat", group = "record_num", exclude = NULL)
+
+  p3_ac_aclim <- orchaRd::orchard_plot(model3_new_overall, mod = "habitat", group  = "record_num", weights = "prop", xlab = TeX("\\Delta $lnRR_{Q_{10}}$ (Acute - Acclimation)"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical") +
+
+  annotate("text", x = 1.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(f_ac_acclim), 2), "[", round(quantile(f_ac_acclim, 0.025), 2)," to ", round(quantile(f_ac_acclim, 0.975), 2), "] ", " $\\,p_{MCMC}$ = 0.03")), hjust = 0, size = 8) +
+  #annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+  annotate("text", x = 2.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(m_ac_acclim), 2), "[", round(quantile(m_ac_acclim, 0.025), 2)," to ", round(quantile(m_ac_acclim, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
+  #annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = 3.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(t_ac_acclim), 2), "[", round(quantile(t_ac_acclim, 0.025), 2)," to ", round(quantile(t_ac_acclim, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
+  #annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
+
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 1.2)
+
+  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top")
 

### 2024-12-20 ms.qmd
Fixed the figure
Added changes to the qmd

@@
 As such, positive effect sizes indicate that the mean (i.e., $lnRR_{Q_{10}}$) or variance ($lnVR_{Q_{10}}$) is larger at the higher of the two temperatures (numerator) when standardized to 10°C.
+When measuring plasticity, it is the difference between $lnRR_{Q_{10}}$ acute (denoted, $lnRR_{Q_{10_{acute}}}$) and acclimation (denoted, $lnRR_{Q_{10_{acclimation}}}$) that captures the degree to which organisms plastically adjust (or acclimate).
 Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).
@@
 
-In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see Supplementary Materials @fig-lnrrq10_temp).
+In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see *Supplementary Materials* @fig-lnrrq10_temp).
 We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
@@
 
-With acclimation time and maximum temperature as moderators in all our models we proceeded to build separate models that tested our core questions.
+Lastly, all models included a random slope of effect type (acute vs acclimation) to estimate the variance in  the magnitude of plastic changes (acute vs acclimation) across studies.
+Such an analysis is similar to analyses using an effect size that is a contrast between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ but is more powerful because it allows studies without acute responses to be included (see *Supplementary Materials*).
+With acclimation time and maximum temperature as moderators in all our models.
+Accounting for these in our meta-regression models, we proceeded to build separate models that tested our core questions.
 All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
@@
 
-  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 1.2)
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 2)
 
@@
 ```
+
+#### **Interaction-based effect sizes**
+
+When measuring plasticity, what is reletavent is the difference between  lnRR_(Q_10 )acute and acclimation that captures the degree to which organisms plastically adjust (or acclimate).
 

### 2024-12-20 ms.qmd
Adding new analysis to the supplement

@@
 
-     col <- c("#0871B9", "#F3B40D", "#1BB908")
-  k_lnrr_ac_acl <- manual_extract(model3_new_overall, mod = "habitat", group = "record_num", exclude = NULL)
-
-  p3_ac_aclim <- orchaRd::orchard_plot(model3_new_overall, mod = "habitat", group  = "record_num", weights = "prop", xlab = TeX("\\Delta $lnRR_{Q_{10}}$ (Acute - Acclimation)"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-  theme(legend.direction = "vertical") +
-
-  annotate("text", x = 1.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(f_ac_acclim), 2), "[", round(quantile(f_ac_acclim, 0.025), 2)," to ", round(quantile(f_ac_acclim, 0.975), 2), "] ", " $\\,p_{MCMC}$ = 0.03")), hjust = 0, size = 8) +
-  #annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
-
-  annotate("text", x = 2.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(m_ac_acclim), 2), "[", round(quantile(m_ac_acclim, 0.025), 2)," to ", round(quantile(m_ac_acclim, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
-  #annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = 3.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(t_ac_acclim), 2), "[", round(quantile(t_ac_acclim, 0.025), 2)," to ", round(quantile(t_ac_acclim, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
-  #annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
-
-  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 2)
-
-  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 24),
-                                       axis.text.y = element_text(angle = 45, size = 24),
-                                       legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top")
-
 if(rerun){
@@
 
-#### **Interaction-based effect sizes**
-
-When measuring plasticity, what is reletavent is the difference between  lnRR_(Q_10 )acute and acclimation that captures the degree to which organisms plastically adjust (or acclimate).
+#### **Interaction-based effect sizes to compare acute and acclimation $lnRR_{Q_{10}}$ within studies**
+
+When measuring plasticity, what is reletavent is the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ because this captures the degree to which organisms plastically adjust (or acclimate).
+Variation in the magnitude of plasticity across studies is captured in our random slope models and is more powerful given that even studies without acute responses measured can be included.
+We can then estimate the mean difference between acute and acclimation in our meta-regression models while accounting for variation in responses within studies with our random slope.
+This analysis is the same as if we were to model the difference in acute and acclimation effect sizes within studies instead of each seperately.
+
+We can validate that our main analysis is similar to an analysis that only includes studies with both acute and acclimation responses.
+To achive this, we need to derive a new effect size that contrasts the difference between acute and acclimation responses within a given study and trait using the following equation:
+
+$$
+  \Delta lnRR_{Q_{10}} = lnRR_{Q_{10_{acute}}} - lnRR_{Q_{10_{acclimation}}}
+$$ {#eq-lnq10_diff}
+
+where, $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ are defined as in @eq-lnq10 in the main manuscript.
+We can calculate the combined sampling variance of the difference in effect sizes using the following equation:
+
+$$
+  s_{\Delta lnRR_{Q_{10}}} = s_{lnRR_{Q_{10_{acute}}}} + s_{lnRR_{Q_{10_{acclimation}}}}
+$$ {#eq-Vlnq10_diff}
+
+where, s_{lnRR_{Q_{10_{acute}}}} and s_{lnRR_{Q_{10_{acclimation}}}} is the sampling variance for the acute and acclimation effect sizes, respectively.
+Again, all notation is defined in @eq-Vlnq10 in the main manuscript.
+
+It is noteworthy here that our analysis using @eq-lnq10_diff as our mani effect size means that we are now interested in the overall meta-analytic mean estimates, not the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ as in our main analyses.
+Positive $\Delta lnRR_{Q_{10}}$ values indicate that acute responses are higher than acclimated responses, while negative values indicate the opposite.
+Positive values indicate that organisms are able to plastically adjust their physiological rates to acute temperature changes, while negative values indicate that organisms are not able to plastically adjust their physiological rates.
+
+Using $\Delta lnRR_{Q_{10}}$ for each trait within a study we fit a model that estimated the meta-anlaytic mean effect size for each habitat (freshwater, marine and terrestrial) accounting for acclimation time and maximum temperature as in our main analysis, along with random effects of study, species, phylogeny, and trait.
+Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta.
+
+```{r, fig-delta}
+#| label: fig-delta
+#| fig-cap: "Analysis with $\Delta lnRR_{Q_{10}}$ "
+
+     col <- c("#0871B9", "#F3B40D", "#1BB908")
+  k_lnrr_ac_acl <- manual_extract(model3_new_overall, mod = "habitat", group = "record_num", exclude = NULL)
+
+  p3_ac_aclim <- orchaRd::orchard_plot(model3_new_overall, mod = "habitat", group  = "record_num", weights = "prop", xlab = TeX("\\Delta $lnRR_{Q_{10}}$ (Acute - Acclimation)"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical") +
+
+  annotate("text", x = 1.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(f_ac_acclim), 2), "[", round(quantile(f_ac_acclim, 0.025), 2)," to ", round(quantile(f_ac_acclim, 0.975), 2), "] ", " $\\,p_{MCMC}$ = 0.03")), hjust = 0, size = 8) +
+  #annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+  annotate("text", x = 2.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(m_ac_acclim), 2), "[", round(quantile(m_ac_acclim, 0.025), 2)," to ", round(quantile(m_ac_acclim, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
+  #annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = 3.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(t_ac_acclim), 2), "[", round(quantile(t_ac_acclim, 0.025), 2)," to ", round(quantile(t_ac_acclim, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
+  #annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
+
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 2)
+
+  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top") 
+p3_ac_aclim
+```
 

### 2024-12-21 ms.qmd
Adjust MS to C4 for reviewer

@@
 When measuring plasticity, it is the difference between $lnRR_{Q_{10}}$ acute (denoted, $lnRR_{Q_{10_{acute}}}$) and acclimation (denoted, $lnRR_{Q_{10_{acclimation}}}$) that captures the degree to which organisms plastically adjust (or acclimate).
+As done by @Seebacher2015-wi, we consider acute $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ as animals measured acutely at both temperatures even though one of the acute measurements is also the acclimation temperature.
+A better measure of "acute" responses would be to calculate $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ on two completely new temperatures but this was not often done in studies.
 Importantly, our effect sizes, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates (or changes in variance) is log-linear (see [@fig-concept]B & *Supplementary Materials* for further discussion).

### 2024-12-22 ms.qmd
Added new code and 'burn-in"

@@
 However, it is unresolved how variance in physiological rates changes with temperature despite its potential ecological and evolutionary importance.
-2.	2.	We developed new effect sizes that capture how both the mean and variation in physiological rates change across temperature (based on the temperature coefficient, $Q_{10}$), and used them to test how acclimation and acute thermal responses vary across aquatic and terrestrial ectotherms using meta-analysis (>1900 effects from 226 species).
+2.	We developed new effect sizes that capture how both the mean and variation in physiological rates change across temperature (based on the temperature coefficient, $Q_{10}$), and used them to test how acclimation and acute thermal responses vary across aquatic and terrestrial ectotherms using meta-analysis (>1900 effects from 226 species).
 Comparing both the magnitude of acclimation and changes in variation side-by-side provides unique opportunities for evaluating the importance of plasticity and selection under climate change.
@@
 In all cases, frequentist and Bayesian models resulted in the same conclusions.
-For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
+For our Bayesian models, we ran 4 MCMC chains, each with a warm-up (burn-in) of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
 We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
@@
 
-Results from "Model 1" (see “Meta-Analysis” above) show that effect heterogeneity was high (only `r mean(tot_i2)`% of the variance was the result of sampling variability, 95% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`% , 95% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`%; Trait Type: `r mean(trait_i2)`% , 95% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`%, 95% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`%; Phylogeny: `r mean(phylo_i2)`% , 95%
-CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`%). These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
-
-Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
+Results from "Model 1" (see “Meta-Analysis” above) show that effect heterogeneity was high (only `r mean(tot_i2)`\% of the variance was the result of sampling variability, 95\% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`\%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`\% , 95\% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`\%; Trait Type: `r mean(trait_i2)`\% , 95\% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`\%).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`\%, 95\% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`\%; Phylogeny: `r mean(phylo_i2)`\% , 95\%
+CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`\%). These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
+
+Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
 However, capacity for acclimation depended on the habitat.
-Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
-In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`% increase in $lnRR_{Q_{10_{acclimation}}}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
+Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`\% (95\% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`\% (95\% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments.
+In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`\% increase in $lnRR_{Q_{10_{acclimation}}}$ (95\% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).
 
 Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
-Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
+Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
 
@@
 Variance in physiological rates ($lnVR_{Q_{10}}$) showed an increase with increasing temperature across all habitat types ([@fig-2]B).
-Overall, there was a `r mean(t_VR_mean_ef)`% (95% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`% (95% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`% (95% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))`) increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
+Overall, there was a `r mean(t_VR_mean_ef)`\% (95\% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`\% (95\% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`\% (95\% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))`) increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
 Analysis of $lnCVR_{Q_{10}}$, which accounts for changes in mean physiological rates, also showed that the relative variance for terrestrial ectotherms decreased compared to marine and freshwater ectotherms, suggesting that increases in variance are less than expected for ectotherms occupying terrestrial habitats (See *Supplementary Materials*, @fig-s1).
 
-Physiological rate variance increased significantly more in freshwater compared to terrestrial ectotherms for acute responses ($\beta$ = `r mean(f_t_c_a)`, 95% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance ($\beta$ = `r mean(f_t_c_aclim)`, 95% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`).
-While marine ectotherms had larger increases in variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
-Marine and freshwater habitats did not differ in the extent of variance increases at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
+Physiological rate variance increased significantly more in freshwater compared to terrestrial ectotherms for acute responses ($\beta$ = `r mean(f_t_c_a)`, 95\% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance ($\beta$ = `r mean(f_t_c_aclim)`, 95\% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`).
+While marine ectotherms had larger increases in variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95\% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95\% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B).
+Marine and freshwater habitats did not differ in the extent of variance increases at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95\% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95\% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`).
 There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B).
@@
 
-Each life-history stage exhibited the same pattern of variance change in each of the habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
+Each life-history stage exhibited the same pattern of variance change in each of the habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
 
@@
                               test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
-  save(model3_new_overall, file = "./output/models/lnRRQ10_3_new_overall")
+  saveRDS(model3_new_overall, file = "./output/models/lnRRQ10_3_new_overall")
 
@@
                               data = lnRRQ10_data_wild_acute_vs_acclim)
-save(model3_new_overall_bayes, file = "./output/models/lnRRQ10_3_new_overall_bayes")
+saveRDS(model3_new_overall_bayes, file = "./output/models/lnRRQ10_3_new_overall_bayes")
 
@@
   posteriors_3_overall <- posterior_samples(model3_new_overall_bayes, "^b")
+
+  # Check acclimation time if it explains variation in new effect?
+  b_c_accl_time_slope <- posteriors_3_overall[,"b_c_accl_time"]; pmcmc(b_c_accl_time_slope); mean(b_c_accl_time_slope); quantile(b_c_accl_time_slope, c(0.025, 0.975))
 
@@
 
-Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 46% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
-Climate change is predicted to result, on average, in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`% increase in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$f))`), a `r abs(lapply(mean_perc_habitat_vr, mean)$m)`% increase in marine systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$m))`), and a `r abs(lapply(mean_perc_habitat_vr, mean)$t)`%  increase in terrestrial systems (95% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5 climate scenario ([@fig-fig6]D).
+Using the ERA5 climate model, predictions of current global changes in physiological rate variance were generally conservative with our model explaining ~ 46\% of the variation in the observed data ($R^2$ = `r round(mean(r2), 2)`, 95\% CI: `r round(quantile(r2, 0.025)[1], 2)` to `r round(quantile(r2, 0.975)[1], 2)`).
+Climate change is predicted to result, on average, in a `r abs(lapply(mean_perc_habitat_vr, mean)$f)`\% increase in variance for freshwater systems (95\% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$f[2]`\%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$f))`), a `r abs(lapply(mean_perc_habitat_vr, mean)$m)`\% increase in marine systems (95\% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$m[2]`\%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$m))`), and a `r abs(lapply(mean_perc_habitat_vr, mean)$t)`\%  increase in terrestrial systems (95\% CI: `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat_vr, function(x) quantile(x, c(0.025, 0.975)))$t[2]`\%, $p_{MCMC}$ = `r p_value(pmcmc(mean_perc_habitat_vr$t))`) under a RCP8.5 climate scenario ([@fig-fig6]D).
 All results are taken from "Model 6".
@@
 
-The change in acclimation $Q_{10}$ we found in our expanded dataset was similar to @Seebacher2015-wi for freshwater organisms (~17%), but higher in marine ectotherms [decrease of 16% versus ~10% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6% compared to an ~8% decrease in @Seebacher2015-wi].
+The change in acclimation $Q_{10}$ we found in our expanded dataset was similar to @Seebacher2015-wi for freshwater organisms (~17\%), but higher in marine ectotherms [decrease of 16\% versus ~10\% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6\% compared to an ~8\% decrease in @Seebacher2015-wi].
 The difference observed in terrestrial ectotherms between studies may be due to additional data from terrestrial species added in our analysis, and to the use of newly derived $Q_{10}$ effect sizes that allowed us to control for sampling variance.
@@
 
-Importantly, increased variance in physiological rates was not equal among terrestrial, marine and freshwater ectotherms, with increases in variance being higher in freshwater ectotherms (~60% increase / 10°C) compared to terrestrial ectotherms (~36% increase / 10°C).
+Importantly, increased variance in physiological rates was not equal among terrestrial, marine and freshwater ectotherms, with increases in variance being higher in freshwater ectotherms (~60\% increase / 10°C) compared to terrestrial ectotherms (~36\% increase / 10°C).
 One possible hypothesis for the differences in variability we observed across habitats could be that among-individual variation in key parameters affecting the shape of thermal performance curves differ between habitats [@angilletta2009thermal; @huey1989evolution; @tattersall2012coping; @rezende2019thermal].
@@
 Assuming that changes in variation in physiological rates are underpinned by genetic variation, and that there is a genetic correlation with fitness, smaller increases in physiological variance could limit adaptation in terrestrial habitats more than aquatic habitats in the future [@urban2023and; @hoffmann2011climate].
-For example, under climate change we expect an increase in variance in physiological rates of only ~13% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30%.
+For example, under climate change we expect an increase in variance in physiological rates of only ~13\% in terrestrial habitats whereas for freshwater habitats we expect variation in physiological rates to increase by ~30\%.
 Importantly, responses to selection will also depend on the magnitude and direction of genetic covariances with other traits, which need consideration.
@@
 Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta.
+Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c_slope)`, 95\% CI: `r quantile(b_max_temp_c_slope, c(0.025, 0.975))`).
 

### 2024-12-22 ms.qmd
Trying to fix symbols so changes all %

@@
 For our Bayesian models, we ran 4 MCMC chains, each with a warm-up (burn-in) of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution.
-We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$).
-We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).
+We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}$(3, 0, 10)).
+We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat}$ = 1).
 We also explored the potential for publication bias in our dataset but there was no evidence it existed (details in *Supplementary Materials*).

### 2024-12-25 ms.qmd
Adjusting text in qmd too

@@
 With acclimation time and maximum temperature as moderators in all our models.
+
 Accounting for these in our meta-regression models, we proceeded to build separate models that tested our core questions.
-All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.
-
-We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
+All estimates from our models are therefore conditioned on an average acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days) and an average maximum temperature (i.e., 23°C) across the dataset.We first tested the extent to which acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ effect sizes varied between habitat types (i.e., terrestrial, freshwater, and marine).
 Models included an interaction between effect type (i.e., acute or acclimation) and habitat (referred to as “Model 2”).
@@
 Second, we tested whether acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ differed between whole-organism versus biochemical traits across habitats by fitting an model with an interaction between type, habitat and trait category (referred to as "Model 3").
+A more detailed trait analysis is presented in the *Supplementary Materials*.
 We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
@@
 
-#### **Acute and acclimation* for detailed trait categories across marine, freshwater and terrestrial taxa**
+#### **Acute and acclimation for detailed trait categories across marine, freshwater and terrestrial taxa**
 

### 2024-12-26 ms.qmd
Adjusting text in qmd

@@
 Results from "Model 1" (see “Meta-Analysis” above) show that effect heterogeneity was high (only `r mean(tot_i2)`\% of the variance was the result of sampling variability, 95\% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`\%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`\% , 95\% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`\%; Trait Type: `r mean(trait_i2)`\% , 95\% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`\%).
-Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`\%, 95\% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`\%; Phylogeny: `r mean(phylo_i2)`\% , 95\%
-CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`\%). These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
+Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`\%, 95\% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`\%; Phylogeny: `r mean(phylo_i2)`\% , 95\% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`\%).
+These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
 
@@
 $\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
-In both cases, their 95% CI's are indicated within square brackets.
+In both cases, their 95% CI's are indicated within square brackets and raw effects are weighted by their precision (inverse sampling variance).
 $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
@@
 Sample sizes are the same for panel A and B.
-For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles.
-"
+For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles."
 #| warning: false
@@
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Raw effects are weighted by their precision (inverse sampling variance).
 k = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 Overall, there was a `r mean(t_VR_mean_ef)`\% (95\% CI: `r quantile(t_VR_mean_ef, 0.025)[1]` to `r quantile(t_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(t_VR_mean))`) increase in physiological rate variance for terrestrial ectotherms,  a `r mean(m_VR_mean_ef)`\% (95\% CI:`r quantile(m_VR_mean_ef, 0.025)[1]` to `r quantile(m_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(m_VR_mean))`) increase in variation for marine ectotherms and a `r mean(f_VR_mean_ef)`\% (95\% CI: `r quantile(f_VR_mean_ef, 0.025)[1]` to `r quantile(f_VR_mean_ef, 0.975)[1]`, $p_{MCMC}$ = `r p_value(pmcmc(f_VR_mean))`) increase in variance for freshwater ectotherms across 10°C (@fig-2; results from "Model 2").
-Analysis of $lnCVR_{Q_{10}}$, which accounts for changes in mean physiological rates, also showed that the relative variance for terrestrial ectotherms decreased compared to marine and freshwater ectotherms, suggesting that increases in variance are less than expected for ectotherms occupying terrestrial habitats (See *Supplementary Materials*, @fig-s1).
 
@@
 Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Raw effects are weighted by their precision (inverse sampling variance).
 Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ values for the slopes are shown for each habitat."
@@
 #| label: fig-lnrrq10_temp
-#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and maximum temperature used in treatments within a study."
+#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and maximum temperature used in treatments within a study.
+Raw effects are weighted by their precision (inverse sampling variance)."
 
@@
 Acclimation time is centered around the mean acclimation time (37.5 days) in the data.
-Not all studies reported acclimation time hence the total number of effects, *k*, was 1767."
+Not all studies reported acclimation time hence the total number of effects, *k*, was 1767.
+Raw effects are weighted by their precision (inverse sampling variance)."
   col <- c("#0871B9", "#F3B40D", "#1BB908")
@@
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Raw effects are weighted by their precision (inverse sampling variance).
 Note that means for all three habitats are displayed but there is weak evidence that the means differ between habitats given models with and without an interaction with habitat are equally supported.
@@
 #| label: fig-delta
-#| fig-cap: "Analysis with $\Delta lnRR_{Q_{10}}$ "
+#| fig-cap: "Analysis with $\Delta lnRR_{Q_{10}}$. Raw effects are weighted by their precision (inverse sampling variance). "
 
@@
 
-Overall, analyses with $lnCVR_{Q_{10}}$ showed similar patterns to those with $lnVR_{Q_{10}}$, except that, because of rates being taken into consideration and there being strong mean-variance relationships, the patterns were generally opposite in direction.
-Either way, the relative differences are quite similar.
+Analysis of $lnCVR_{Q_{10}}$, which accounts for changes in mean physiological rates, also showed that the relative variance for terrestrial ectotherms decreased compared to marine and freshwater ectotherms, suggesting that increases in variance are less than expected for ectotherms occupying terrestrial habitats (@fig-s1).
+Generally, these results are consistent with those using $lnVR_{Q_{10}}$.
+
 Overall, analysis of $lnCVR_{Q_{10}}$ suggested that relative variance decreased with higher temperatures across all habitat types, with terrestrial ectotherms having the largest decrease in relative variance (@fig-s1).
@@
 Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+Raw effects are weighted by their precision (inverse sampling variance).
 $\\beta$ values are the contrasts between acute and acclimation means within each habitat with 'NS' signifiying no significant differences.
@@
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Raw effects are weighted by their precision (inverse sampling variance).
 *k* = total number of effect size estimates while the numbers in brackets indicate the number of species.
@@
 Thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
+Raw effects are weighted by their precision (inverse sampling variance).
 The x-axis is truncated for ease of visualisation.

### 2024-12-27 ms.qmd
Added details on simulation justification

@@
 
-We conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
+Changes in $lnVR_{Q_{10}}$ are expected to depend on differences in the among-individual variation in the thermal performance curves across species [@angilletta2009thermal].
+In other words, we expect performance curves to vary among individuals within a population and this variation is expected to co-vary with habitats [@angilletta2009thermal].
+To understand how differences in thermal performance curve variation correlate with the empirical patterns of variance change we observe, we conducted a simple simulation as a sensitivity analysis to better understand the characteristics of performance curves that could lead to our observed changes in variance across temperatures and habitats.
 The simulation varied among-individual variation in performance curves to identify the parameters that could produce the results we observed.

### 2024-12-27 ms.qmd
Adjusting legends and text to deal with R2 comments

@@
 Two acute effect sizes can be calculated, one for the cold acclimated animals and one for the warm acclimated animals.
-(B) Species are expected, *a priori*, to vary in their thermal performance curves (thin lines) around an average (thick black line).
+Acute effects quantify the thermodynamic impacts of temperature on reaction rates whereas acclimated reaction rates measure how much (if at all) these rates are suppressed from having experienced the temperatures chronically (B) Species are expected, *a priori*, to vary in their thermal performance curves (thin lines) around an average (thick black line).
 We restricted our data to areas of each species' performance curve that fell within the natural thermal range of the species (thick lines on each species-level curve).
@@
 
-We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rate) at two or more temperatures after having been acclimated (or acclimatized) at these temperatures.
+We compiled literature on ectothermic animals that measured physiological rates (e.g., metabolic rates, heart rates, enzyme reaction rates) at two or more temperatures after having been acclimated at these temperatures for at least 1 week.
 We used data from a previous meta-analysis [@Seebacher2015-wi] and updated @Seebacher2015-wi's data by extracting data from suitable studies from our own searches that followed the same search protocol.
@@
 
-$R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ can all be taken from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
+Effect sizes can be calculated from samples of organisms measured acutely at two temperatures or after having been acclimated these same temperatures ([@fig-concept]A).
 For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ estimates.
@@
 We predicted the expected change in $lnVR_{Q_{10}}$ for each wild population in our dataset at its specific populations latitude and longitude.
-We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C:
+We first converted the predicted $lnVR_{Q_{10}}$ to a 1°C change as opposed to 10°C to better map to relevant changes in temperature coinciding with climate change:
 

### 2024-12-28 ms.qmd
Response about figures, and predcition intervals

@@
 `r utils::packageVersion("metafor")` @Viechtbauer2010-fn].
-We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers.
+We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots that more easily convey heterogeneity in effects with prediction intervals [vers.
 2.0, @Nakagawa2021-ls; @nakagawaorchard].
+Prediction intervals can be interpreted as the range of expected effects from future studies [@Noble2022-ty].
 In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz].

### 2024-12-28 ms.qmd
Few more comments. Will render and finish off a few more while also check render

@@
 Simulations suggest that these patterns may result from differences in among-individual variation in thermal breadth and optima of performance curves across habitats.
-4.	Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because limited increases in variance may provide less raw material for evolutionary adaptation.
+4.	Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because of both a lack of acclimation capacity and a limited increases in variance that may provide less raw material for evolutionary adaptation.
 Considering both acclimation capacity and variance in physiological rates side-by-side is therefore important for understanding how climate change will impact populations.
@@
 We also explored the potential for publication bias in our dataset but there was no evidence it existed (details in *Supplementary Materials*).
+We report overall meta-analytic means (denoted by $\mu$) and contrasts between meta-analytic means (denoted by $\beta$) throughout.
 
@@
 }
-
-# Orchard plot model3_new
-  orchaRd:orchard_plot(model3_new, )
 
@@
 #| label: fig-delta
-#| fig-cap: "Analysis with $\Delta lnRR_{Q_{10}}$. Raw effects are weighted by their precision (inverse sampling variance). "
+#| fig-cap: "Analysis with $\\Delta lnRR_{Q_{10}}$. Raw effects are weighted by their precision (inverse sampling variance). "
 

### 2024-12-29 ms.qmd
Re-render

@@
 **Running head**: Physiological rate variation in ectotherms
-Havird 
+
 ## **Abstract**
@@
 We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter].
-The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures.
 Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments.
@@
 
-The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`,
-and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
+The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single crustacean and cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single tardigrade species) (@fig-phylo).
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to acclimation responses (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
@@
 Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`\%, 95\% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`\%; Phylogeny: `r mean(phylo_i2)`\% , 95\% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`\%).
-These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).
-
-Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
+These patterns were similar for $lnVR_{Q_{10}}$ (see *Supplementary Materials*, @fig-s3).
+
+Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly between aquatic and terrestrial habitats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
 However, capacity for acclimation depended on the habitat.
@@
 
-p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
+p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.5, 1.6) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)
 
@@
   b_c_accl_time_slope <- posteriors_3_overall[,"b_c_accl_time"]; pmcmc(b_c_accl_time_slope); mean(b_c_accl_time_slope); quantile(b_c_accl_time_slope, c(0.025, 0.975))
+
+  # Check slope
+   b_max_temp_c <- posteriors_3_overall[,"b_max_temp_c"]; pmcmc(b_max_temp_c); mean(b_max_temp_c); quantile(b_max_temp_c, c(0.025, 0.975))
 
@@
 
-### *Comparing relative variance changes: the *lnCVR* ratio*
-As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
-As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:
-
-$$
-lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
-$$ {#eq-lnq10CVR} $$
-s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
-$$ {#eq-slncvr}
-
-where $CV$ is the coefficient of variation defined as $SD / R$.
-We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
-While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
+#### **Climate data**
+
+To understand how climate is related to a species’ physiological acclimation abilities and changes in variance we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
+It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
+Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
+
+Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
+For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01° resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25° resolution) using the *ncdf4* R package [vers.
+`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
+We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
+
+Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
+To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
+We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, identifying biologically relevant lags for such diverse taxa is challenging.
+As such, we present a coarse analysis using this metric of thermal predictability in the *Supplemental Materials* below.
+
+Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections into the future.
+We used the CanESM2 climate model (2005-2100) [vers.
+1.2.0; @koen_hufkens_2019_2647541] under a high emissions scenario (RCP8.5).
 
@@
 
-#### **Climate data**
-
-To understand how climate is related to a species’ physiological acclimation abilities and changes in variance we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments.
-It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations.
-Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations for climate analyses.
-
-Monthly average temperature data were extracted from the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx].
-For each population and species in the dataset we extracted a 72-year period (1950-2022) of either surface air temperature (0.01° resolution) for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa (at 0.25° resolution) using the *ncdf4* R package [vers.
-`r utils::packageVersion("ncdf4")`, @Pierce2021-lc].
-We chose surface temperature because we believed that it was more likely to reflect the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.
-
-Using the thermal time-series data for each location we calculated metrics of thermal variability across months and years as well as estimates of thermal predictability (i.e., autocorrelation).
-To estimate thermal variability, we calculated the coefficient of variation ($\frac{SD}{M}$, where SD = standard deviation in temperature and M = the mean temperature for each year).
-We also estimated thermal predictability, by calculating the auto-regressive time lag across months (i.e., a measure of how correlated temperatures were between months), however, identifying biologically relevant lags for such diverse taxa is challenging.
-As such, we present a coarse analysis using this metric of thermal predictability in the *Supplemental Materials* below.
-
-Lastly, to illustrate the effects that climate warming could have on physiological rate variance we also extracted climate projections into the future.
-We used the CanESM2 climate model (2005-2100) [vers.
-1.2.0; @koen_hufkens_2019_2647541] under a high emissions scenario (RCP8.5).
+#### **Interaction-based effect sizes to compare acute and acclimation $lnRR_{Q_{10}}$ within studies**
+
+When measuring plasticity, what is relevant is the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ because this captures the degree to which organisms plastically adjust (or acclimate).
+Variation in the magnitude of plasticity across studies is captured in our random slope models and is more powerful given that even studies without acute responses measured can be included.
+We can then estimate the mean difference between acute and acclimation in our meta-regression models while accounting for variation in responses within studies with our random slope.
+This analysis is the same as if we were to model the difference in acute and acclimation effect sizes within studies instead of each separately.
+
+We can validate that our main analysis is similar to an analysis that only includes studies with both acute and acclimation responses.
+To achieve this, we need to derive a new effect size that contrasts the difference between acute and acclimation responses within a given study and trait using the following equation:
+
+$$
+  \Delta lnRR_{Q_{10}} = lnRR_{Q_{10_{acute}}} - lnRR_{Q_{10_{acclimation}}}
+$$ {#eq-lnq10_diff}
+
+where, $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ are defined as in @eq-lnq10 in the main manuscript.
+We can calculate the combined sampling variance of the difference in effect sizes using the following equation:
+
+$$
+  s_{\Delta lnRR_{Q_{10}}} = s_{lnRR_{Q_{10_{acute}}}} + s_{lnRR_{Q_{10_{acclimation}}}}
+$$ {#eq-Vlnq10_diff}
+
+where, $s_{lnRR_{Q_{10_{acute}}}}$ and $s_{lnRR_{Q_{10_{acclimation}}}}$ is the sampling variance for the acute and acclimation effect sizes, respectively.
+Again, all notation is defined in @eq-Vlnq10 in the main manuscript.
+
+It is noteworthy here that our analysis using @eq-lnq10_diff as our mani effect size means that we are now interested in the overall meta-analytic mean estimates, not the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ as in our main analyses.
+Positive $\Delta lnRR_{Q_{10}}$ values indicate that acute responses are higher than acclimated responses, while negative values indicate the opposite.
+Positive values indicate that organisms are able to plastically adjust their physiological rates to acute temperature changes, while negative values indicate that organisms are not able to plastically adjust their physiological rates.
+
+Using $\Delta lnRR_{Q_{10}}$ for each trait within a study we fit a model that estimated the meta-anlaytic mean effect size for each habitat (freshwater, marine and terrestrial) accounting for acclimation time and maximum temperature as in our main analysis, along with random effects of study, species, phylogeny, and trait.
+Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta.
+Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c)`, 95\% CI: `r quantile(b_max_temp_c, c(0.025, 0.975))`, p = `r pmcmc(b_max_temp_c)`).
+
+```{r, fig-delta}
+#| label: fig-delta
+#| fig-cap: "Meta-analysis results for $\\Delta lnRR_{Q_{10}}$ across different habitats.
+Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
+$\\beta$ values are the contrasts between acute and acclimation means within each habitat.
+$\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
+95% CI's are indicated within square brackets and raw effects are weighted by their precision (inverse sampling variance).
+$p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
+k = total number of effect size estimates while the numbers in brackets indicate the number of species.
+For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles.
+Raw effects are weighted by their precision (inverse sampling variance).
+"
+
+     col <- c("#0871B9", "#F3B40D", "#1BB908")
+  k_lnrr_ac_acl <- manual_extract(model3_new_overall, mod = "habitat", group = "record_num", exclude = NULL)
+
+  p3_ac_aclim <- orchaRd::orchard_plot(model3_new_overall, mod = "habitat", group  = "record_num", weights = "prop", xlab = TeX("\\Delta $lnRR_{Q_{10}}$ (Acute - Acclimation)"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
+  theme(legend.direction = "vertical") +
+
+  annotate("text", x = 1.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(f_ac_acclim), 2), "[", round(quantile(f_ac_acclim, 0.025), 2)," to ", round(quantile(f_ac_acclim, 0.975), 2), "] ", " $\\,p_{MCMC}$ = 0.03")), hjust = 0, size = 8) +
+  #annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
+
+  annotate("text", x = 2.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(m_ac_acclim), 2), "[", round(quantile(m_ac_acclim, 0.025), 2)," to ", round(quantile(m_ac_acclim, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
+  #annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
+
+  annotate("text", x = 3.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(t_ac_acclim), 2), "[", round(quantile(t_ac_acclim, 0.025), 2)," to ", round(quantile(t_ac_acclim, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
+  #annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
+
+  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 2)
+
+  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
+                                       axis.text = element_text(size = 24),
+                                       axis.text.y = element_text(angle = 45, size = 24),
+                                       legend.title = element_text(size = 30),
+                               legend.text = element_text(size = 24),
+                               title = element_text(size = 24), legend.position = "top")
+
+  ggsave(p3_ac_aclim, filename = "./output/figures/figS5.pdf", width = 11.5, height = 8)
+
+  p3_ac_aclim <- image_read("./output/figures/figS5.pdf")
+  p3_ac_aclim
+
+```
+
+#### **Comparing relative variance changes: the *lnCVR* ratio**
+As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship.
+As such, the coefficient of variation is often used because it permits standardization of changes in variance as mean trait values change:
+
+$$
+lnCVR_{Q_{10}} = ln\left( \frac{\text{CV}_{2}}{\text{CV}_{1}} \right){ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }
+$$ {#eq-lnq10CVR} $$
+s_{lnCVR_{Q_{10}}} = \left[ \frac{(\text{SD}_{1})^2}{N_{1}({R}_{1})^2} + \frac{(\text{SD}_{2})^2}{N_{2} ({R}_{2})^2} + \frac{1}{2\left( N_{1}-1 \right)} + \frac{1}{2\left(N_{2} - 1\right)} \right]{ \left(\ \frac{10^{\circ}C}{T_{2}-T_{1}} \right) }^2
+$$ {#eq-slncvr}
+
+where $CV$ is the coefficient of variation defined as $SD / R$.
+We refer to $lnCVR_{Q_{10}}$ as relative variance because variance changes are relative to the mean.
+While we analyse $lnCVR_{Q_{10}}$ it does make the assumption that SD is directly proportional to the mean, and given that we are analysing the mean alongside the variance we present results on $lnCVR_{Q_{10}}$ in the supplement.
 
@@
  p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
-  ggsave(p_mv, file = "./output/figures/figS5.png", height = 8, width = 8)
-
-  p_mv <- magick::image_read("./output/figures/figS5.png")
+  ggsave(p_mv, file = "./output/figures/figS6.png", height = 8, width = 8)
+
+  p_mv <- magick::image_read("./output/figures/figS6.png")
   p_mv
@@
 flextable(table) %>% bold(part = "header") %>% autofit()
-```
-
-#### **Interaction-based effect sizes to compare acute and acclimation $lnRR_{Q_{10}}$ within studies**
-
-When measuring plasticity, what is reletavent is the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ because this captures the degree to which organisms plastically adjust (or acclimate).
-Variation in the magnitude of plasticity across studies is captured in our random slope models and is more powerful given that even studies without acute responses measured can be included.
-We can then estimate the mean difference between acute and acclimation in our meta-regression models while accounting for variation in responses within studies with our random slope.
-This analysis is the same as if we were to model the difference in acute and acclimation effect sizes within studies instead of each seperately.
-
-We can validate that our main analysis is similar to an analysis that only includes studies with both acute and acclimation responses.
-To achive this, we need to derive a new effect size that contrasts the difference between acute and acclimation responses within a given study and trait using the following equation:
-
-$$
-  \Delta lnRR_{Q_{10}} = lnRR_{Q_{10_{acute}}} - lnRR_{Q_{10_{acclimation}}}
-$$ {#eq-lnq10_diff}
-
-where, $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ are defined as in @eq-lnq10 in the main manuscript.
-We can calculate the combined sampling variance of the difference in effect sizes using the following equation:
-
-$$
-  s_{\Delta lnRR_{Q_{10}}} = s_{lnRR_{Q_{10_{acute}}}} + s_{lnRR_{Q_{10_{acclimation}}}}
-$$ {#eq-Vlnq10_diff}
-
-where, s_{lnRR_{Q_{10_{acute}}}} and s_{lnRR_{Q_{10_{acclimation}}}} is the sampling variance for the acute and acclimation effect sizes, respectively.
-Again, all notation is defined in @eq-Vlnq10 in the main manuscript.
-
-It is noteworthy here that our analysis using @eq-lnq10_diff as our mani effect size means that we are now interested in the overall meta-analytic mean estimates, not the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ as in our main analyses.
-Positive $\Delta lnRR_{Q_{10}}$ values indicate that acute responses are higher than acclimated responses, while negative values indicate the opposite.
-Positive values indicate that organisms are able to plastically adjust their physiological rates to acute temperature changes, while negative values indicate that organisms are not able to plastically adjust their physiological rates.
-
-Using $\Delta lnRR_{Q_{10}}$ for each trait within a study we fit a model that estimated the meta-anlaytic mean effect size for each habitat (freshwater, marine and terrestrial) accounting for acclimation time and maximum temperature as in our main analysis, along with random effects of study, species, phylogeny, and trait.
-Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta.
-Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c_slope)`, 95\% CI: `r quantile(b_max_temp_c_slope, c(0.025, 0.975))`).
-
-```{r, fig-delta}
-#| label: fig-delta
-#| fig-cap: "Analysis with $\\Delta lnRR_{Q_{10}}$. Raw effects are weighted by their precision (inverse sampling variance). "
-
-     col <- c("#0871B9", "#F3B40D", "#1BB908")
-  k_lnrr_ac_acl <- manual_extract(model3_new_overall, mod = "habitat", group = "record_num", exclude = NULL)
-
-  p3_ac_aclim <- orchaRd::orchard_plot(model3_new_overall, mod = "habitat", group  = "record_num", weights = "prop", xlab = TeX("\\Delta $lnRR_{Q_{10}}$ (Acute - Acclimation)"), angle = 20, legend.pos = "top.left", trunk.size = 1.8, branch.size = 2.8) + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
-  theme(legend.direction = "vertical") +
-
-  annotate("text", x = 1.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(f_ac_acclim), 2), "[", round(quantile(f_ac_acclim, 0.025), 2)," to ", round(quantile(f_ac_acclim, 0.975), 2), "] ", " $\\,p_{MCMC}$ = 0.03")), hjust = 0, size = 8) +
-  #annotate("text", x = 1.20, y = -0.5, label =paste0(round(mean(change_f), 3), "%"), hjust = 0, size = 8) + labs(shape = "Type") +
-
-  annotate("text", x = 2.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(m_ac_acclim), 2), "[", round(quantile(m_ac_acclim, 0.025), 2)," to ", round(quantile(m_ac_acclim, 0.975),2), "] ", " $\\,p_{MCMC}$ = 0.01")), hjust = 0, size = 8) +
-  #annotate("text", x = 2.20, y = -0.5, label =paste0(round(mean(change_m), 3), "%"), hjust = 0, size = 8) +
-
-  annotate("text", x = 3.5, y = -1, label =TeX(paste0("$\\mu = $", round(mean(t_ac_acclim), 2), "[", round(quantile(t_ac_acclim, 0.025), 2)," to ", round(quantile(t_ac_acclim, 0.975),2), "] ", "$\\,p_{MCMC}$ = 0.36")), hjust = 0, size = 8) +
-  #annotate("text", x = 3.20, y = -0.5, label =paste0(round(mean(change_t), 3), "%"), hjust = 0, size = 8) +
-
-  scale_fill_manual(values = col) + scale_color_manual(values = rep("black",3)) + ylim(-1.2, 2)
-
-  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
-                                       axis.text = element_text(size = 24),
-                                       axis.text.y = element_text(angle = 45, size = 24),
-                                       legend.title = element_text(size = 30),
-                               legend.text = element_text(size = 24),
-                               title = element_text(size = 24), legend.position = "top") 
-p3_ac_aclim
 ```
@@
                                        axis.text = element_text(size = 24),
-                                       axis.text.y = element_blank(),
                                        legend.title = element_text(size = 30),
@@
 
-  ggsave(p3b, filename = "./output/figures/figS6.pdf", width = 11.5, height = 8)
-
-  figs1 <- image_read("./output/figures/figS6.pdf")
+  ggsave(p3b, filename = "./output/figures/figS7.pdf", width = 11.5, height = 8)
+
+  figs1 <- image_read("./output/figures/figS7.pdf")
   figs1
@@
 figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait_vr, filename = "./output/figures/figS7.png", width = 28, height = 8, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/figS7.png")
+ggsave(figbtrait_vr, filename = "./output/figures/figS8.png", width = 28, height = 8, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figS8.png")
 figbtrait
@@
 figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figcvr_lh, filename = "./output/figures/figS8.pdf", width = 28, height = 10, device = "pdf")
-
-figcvr_lh <- magick::image_read("./output/figures/figS8.pdf")
+ggsave(figcvr_lh, filename = "./output/figures/figS9.pdf", width = 28, height = 10, device = "pdf")
+
+figcvr_lh <- magick::image_read("./output/figures/figS9.pdf")
 figcvr_lh
@@
 figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/fig4.png")
+ggsave(figbtrait, filename = "./output/figures/figS10.png", width = 28, height = 14, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figS10.png")
 figbtrait
@@
 fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
-ggsave(fig2, filename = "./output/figures/figS9.png", height = 20, width = 15)
-
-img_fig2 <- magick::image_read("./output/figures/figS9.png")
+ggsave(fig2, filename = "./output/figures/figS11.png", height = 20, width = 15)
+
+img_fig2 <- magick::image_read("./output/figures/figS11.png")
 img_fig2
@@
 figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figvrtrait, filename = "./output/figures/figS10.png", height = 20, width = 15)
-
-img_figvrtrait <- magick::image_read("./output/figures/figS10.png")
+ggsave(figvrtrait, filename = "./output/figures/figS12.png", height = 20, width = 15)
+
+img_figvrtrait <- magick::image_read("./output/figures/figS12.png")
 img_figvrtrait
@@
 figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figS11.png", height = 20, width = 15)
-
-img_figcvrtrait <- magick::image_read("./output/figures/figS11.png")
+ggsave(figcvrtrait, filename = "./output/figures/figS13.png", height = 20, width = 15)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figS13.png")
 img_figcvrtrait
@@
 figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS12.png")
-
-figS12 <- image_read("./output/figures/figS12.png")
+ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS14.png")
+
+figS12 <- image_read("./output/figures/figS14.png")
 figS12
@@
 
-ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS13.pdf")
-
-  p_acf <- image_read("./output/figures/figS13.pdf")
+ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS15.pdf")
+
+  p_acf <- image_read("./output/figures/figS15.pdf")
   p_acf 
@@
 figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS14.png")
-
-figs2 <- image_read("./output/figures/figS14.png")
+ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS16.png")
+
+figs2 <- image_read("./output/figures/figS16.png")
 figs2
@@
 
-#### **Performance Curve Simulations**
+#### **Performance curve simulations**
 
@@
 p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
-ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS15.png")
-
-p_sim <- image_read("./output/figures/figS15.png")
+ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS17.png")
+
+p_sim <- image_read("./output/figures/figS17.png")
 p_sim

### 2024-12-29 ms.qmd
Addressed a few more comments

@@
 
-It is noteworthy here that our analysis using @eq-lnq10_diff as our mani effect size means that we are now interested in the overall meta-analytic mean estimates, not the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ as in our main analyses.
+It is noteworthy here that our analysis using @eq-lnq10_diff as our main effect size means that we are now interested in the overall meta-analytic mean estimates, not the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ as in our main analyses.
 Positive $\Delta lnRR_{Q_{10}}$ values indicate that acute responses are higher than acclimated responses, while negative values indicate the opposite.
-Positive values indicate that organisms are able to plastically adjust their physiological rates to acute temperature changes, while negative values indicate that organisms are not able to plastically adjust their physiological rates.
+Positive values indicate that organisms can plastically adjust their physiological rates to acute temperature changes, while negative values indicate that organisms are not able to plastically adjust their physiological rates.
 
@@
 
-p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
+p1_cvr <- orchard_plot(model2.3_m_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.7, 1.6)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + scale_fill_manual(values = rep(col[2],4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.7, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.3_f_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + labs(title = "Freshwater") + add_theme() + ylim(-1.6, 1.3) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + scale_fill_manual(values = rep(col[1], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -1.6, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.3_t_broad, mod = "trait_broad", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ labs(title = "Terrestrial") + add_theme()  + ylim(-2, 2) + annotate("text", x = x.pos, y = 1.5, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + scale_fill_manual(values = rep(col[3], 4)) + scale_color_manual(values = rep("black", 4)) + annotate("text", x = yloc, y = -2, label = TeX(paste0("$\\beta$ = ", t_trait_b_cvr$diff, " [", t_trait_b_cvr$l95, " to ", t_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_b_cvr$p)), hjust = 0, size = 8)
 
@@
 
-p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
-
-p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
+p1_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + ylim(c(-2, 2.2)) + labs(title = "Marine") + add_theme() + ylim(-1.5, 1.1)  + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", m_cv$k, " (", m_cv$spp, ")")), size = size_annot) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", m_trait_b_cvr$diff, " [", m_trait_b_cvr$l95, " to ", m_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p2_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "f"), group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type", angle = 45, g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)  + labs(title = "Freshwater") + add_theme() + ylim(-1.3, 1.1) + annotate("text", x = x.pos, y = 0.8, label = TeX(paste0("\\it{k} = ", f_cv$k, " (", f_cv$spp, ")")), size = size_annot) + theme(legend.position = "right", legend.justification = c(1, 1), axis.text.y = element_blank()) + guides(shape = guide_legend(direction = "vertical"), size = guide_legend(direction = "vertical")) + annotate("text", x = yloc, y = -1.3, label = TeX(paste0("$\\beta$ = ", f_trait_b_cvr$diff, " [", f_trait_b_cvr$l95, " to ", f_trait_b_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", f_trait_b_cvr$p)), hjust = 0, size = 8)
+
+p3_cvr <- orchard_plot(model2.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "t"), angle = 45, group = "record_num", xlab = TeX("$lnCVR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, branch.size = branch.size, trunk.size = trunk.size)+ labs(title = "Terrestrial") + add_theme()  + ylim(-1.55, 1.1) + annotate("text", x = x.pos, y = 0.6, label = TeX(paste0("\\it{k} = ", t_cv$k, " (", t_cv$spp, ")")), size = size_annot) +  theme(legend.position = "none") + annotate("text", x = yloc, y = -1.55, label = TeX(paste0("$\\beta$ = ", t_trait_cvr$diff, " [", t_trait_cvr$l95, " to ", t_trait_cvr$u95, "] ", "$\\,p_{MCMC}$ = ", t_trait_cvr$p)), hjust = 0, size = 8) + scale_x_discrete(labels = c("A" = "Adult","J" = "Juvenile"))
 

### 2024-12-30 ms.qmd
Adding a bunch of new code to do climate analysis with interaction-based lnRRQ10 and also add these results and figures in. Updated supp figs as order changes

@@
   # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
-  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
-  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
+  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reduction in lnRRQ10
+  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reduction in lnRRQ10
   change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
@@
 There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B).
-Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* scaling analyses, @tbl-slopes & @fig-mv).
 
@@
      model3.9_m <- readRDS("./output/models/model3.9_m")
-}
-
-```
-
-```{r, wildlnRR_acutevsacclim}
-#| label: wildlnRR_acutevsacclim
-#| echo: false
-#| include: false
-
-###---------------------------------------###
-# Analysis that calculates the plastic adjustment, acclimation - acute within a study and trait to look at whether plasticity is correlated with climate.
-A good point raised by Reviewer 1 that we should test.
-###---------------------------------------###
-
-###---------------------------------------###
-# Data
-###---------------------------------------###
-
-  # Bring in Climate data
-  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
-
-  # Create a match column.
-  climate2 <- climate %>% 
-              mutate(match = paste(Species, Latitude, Longitude, sep =".")) %>% 
-              dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
-
-  # Subset the data and do some new calculations
-    # Steps:
-    # 1. Suse wide data
-    # 2. Drop out lnVR and lnCVR
-    # 3.  Exclude effects where we don't have BOTH acute and acclimation. We need both to subtract from each other
-    # 4. Calculate the weighted average of the effects and its associated sampleing variance so we have only a single acute
-    # 5. Clean up by removing old acute columns
-    # 6. Calculate the difference between acclimation and acute and it's associated associated sampling variance
-    # 7. Clean up by removing old acclimation and acute columns as well as all 'r' columns
-    # 8. Add a match column for joining climate data
-
-                          drop <- colnames(data_wide)[grep("ln[CV]", colnames(data_wide))]
-
-  lnRRQ10_data_acc_minus_aclim <- data_wide %>%        
-                  dplyr::select(!all_of(drop)) %>%  
-                  filter(!is.na(lnRR_Q10_acute_t1) | !is.na(lnRR_Q10_acute_t2)) %>% 
-                  mutate(lnRR_acute = weighted_avg_effects(lnRR_Q10_acute_t1, lnRR_Q10_acute_t2, V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2),
-                      lnRR_acute_SV = weighted_avg_sv(V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2))   %>% 
-                  dplyr::select(-lnRR_Q10_acute_t1, -lnRR_Q10_acute_t2, -V_lnRR_Q10_acute_t1, -V_lnRR_Q10_acute_t2)  %>% 
-                  mutate(lnRRQ10_ac_acclimate = lnRR_acute - lnRR_Q10_acclim, 
-                         lnRRQ10_ac_acclimate_SV = lnRR_acute_SV + V_lnRR_Q10_acclim) %>%
-                  dplyr::select(-lnRR_Q10_acclim, -V_lnRR_Q10_acclim, -lnRR_acute_SV, -lnRR_acute, -grep("r[12]", colnames(.)))  %>% 
-                  mutate(match = paste(gsub("_", "", species_full), lat, long, sep = "."), 
-                    max_temp_c = scale(temp_2, scale = FALSE),
-                           spp = species_full)
-
-# Now that we have the data calcualted as the difference between acute and acclimation for each effect we want to know of this difference, i.e., the direction and magnitude of plasticity is associated with climate.
-We do not need to pivot longer because the response is simply the difference now so we are ready for anlaysis
-
-# Now, join climate data to full data. This will give us all the climate variability data for each site across time
-lnRRQ10_data_wild_acute_vs_acclim <- left_join(lnRRQ10_data_acc_minus_aclim, climate2, by = "match")
-
-# Check and prune tree
-tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
-tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr_wild, dataCol = "species_full", type = "check") # Good
-
-# Create the phylo correlation matrix
-phylo_cor_wild_ac_acclim <- vcv(tree_lnrr_wild, cor = TRUE)
-        A_wild_ac_acclim <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
-
-# Scale data
-        lnRRQ10_data_wild_acute_vs_acclim <- lnRRQ10_data_wild_acute_vs_acclim %>% 
-                                                        mutate(cv_c = scale(cv),
-                                                          acf_all_c = scale(acf_all),
-                                                          c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
-
-# How much data? Quite a bit with both acute and acclimation, which is good.
-        lnRRQ10_data_wild_acute_vs_acclim %>% group_by(habitat) %>% summarise(n = n(), stdy = length(unique(record_num)))
-
-# Plot the effects with climate variation and predcitabiliy
-
-  lnRRQ10_data_wild_acute_vs_acclim  %>% 
-    ggplot(aes(x = acf_all, y = lnRRQ10_ac_acclimate, color = habitat)) + geom_point() + facet_wrap(~habitat) + theme_classic() + my_theme() + labs(x = "Autocorrelation", y = "Acute - Acclimation", color = "Habitat") + geom_smooth(method = "lm", se = FALSE) + geom_smooth(method = "lm", se = FALSE, aes(group = habitat), linetype = "dashed") + theme(legend.position = "none")
-
-  lnRRQ10_data_wild_acute_vs_acclim  %>% 
-    ggplot(aes(x = cv, y = lnRRQ10_ac_acclimate, color = habitat)) + geom_point() + facet_wrap(~habitat) + theme_classic() + my_theme() + labs(x = "Coefficient of Variation (CV)", y = "Acute - Acclimation", color = "Habitat") + geom_smooth(method = "lm", se = FALSE) + geom_smooth(method = "lm", se = FALSE, aes(group = habitat), linetype = "dashed") + theme(legend.position = "none")
-
-# How much missing data in acclimation time?
-  lnRRQ10_data_wild_acute_vs_acclim %>% filter(is.na(acclim_period)) %>% group_by(habitat) %>% summarise(n = n(), stdy = length(unique(record_num)))
-
-####################################################
-  # Model3_new: Model environmental variability by acute/acclim
-####################################################
-  rerun = FALSE
-
-# Ok, now that we have it we may as well just rerun the model using the effect size Reviewer 1 is talking about to show that it is nearly the same (rememnber, we lose power here).
-Also remoember that positive effect sizes show acclimation because it implies the acute slope is larger than the acclimation slope.
-Sp, we expect freshwater and marine to have positive overall effect sizes.
-
-if(rerun){
-  model3_new_overall  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + habitat, V = lnRRQ10_ac_acclimate_SV,
-                                       random = list(~1 | record_num,
-                                                     ~1 | species_full,
-                                                     ~1 | trait,
-                                                     ~1 + max_temp_c| spp,
-                                                     ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_ac_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
-  saveRDS(model3_new_overall, file = "./output/models/lnRRQ10_3_new_overall")
-
-  model3_new_overall_bayes <- brms::brm(lnRRQ10_ac_acclimate | se(sqrt(lnRRQ10_ac_acclimate_SV), sigma = TRUE) ~ 
-                                max_temp_c + c_accl_time + habitat + (1 | record_num) + 
-                              (1 | gr(species_full, cov = A_wild_ac_acclim)) + 
-                              (1 + max_temp_c| spp) + 
-                              (1|trait), 
-                              data2 = list(A_wild_ac_acclim = A_wild_ac_acclim), 
-                              family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-                              control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                              chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
-                              data = lnRRQ10_data_wild_acute_vs_acclim)
-saveRDS(model3_new_overall_bayes, file = "./output/models/lnRRQ10_3_new_overall_bayes")
-
-} else{
-  model3_new_overall <- readRDS("./output/models/lnRRQ10_3_new_overall")
-  model3_new_overall_bayes <- readRDS("./output/models/lnRRQ10_3_new_overall_bayes")
-}
-
-####################################################
-  # Get contrasts from overall model
-####################################################
-
-  # Extract posteriors
-  posteriors_3_overall <- posterior_samples(model3_new_overall_bayes, "^b")
-
-  # Check acclimation time if it explains variation in new effect?
-  b_c_accl_time_slope <- posteriors_3_overall[,"b_c_accl_time"]; pmcmc(b_c_accl_time_slope); mean(b_c_accl_time_slope); quantile(b_c_accl_time_slope, c(0.025, 0.975))
-
-  # Check slope
-   b_max_temp_c <- posteriors_3_overall[,"b_max_temp_c"]; pmcmc(b_max_temp_c); mean(b_max_temp_c); quantile(b_max_temp_c, c(0.025, 0.975))
-
-  # Freshwater
-    f_ac_acclim  <- posteriors_3_overall[,"b_Intercept"]; pmcmc(f_ac_acclim); mean(f_ac_acclim); quantile(f_ac_acclim, c(0.025, 0.975))
-  # Marine
-    m_ac_acclim  <- f_ac_acclim + posteriors_3_overall[,"b_habitatm"]; pmcmc(m_ac_acclim); mean(m_ac_acclim); quantile(m_ac_acclim, c(0.025, 0.975))
-  # Terrestrial
-    t_ac_acclim  <- f_ac_acclim + posteriors_3_overall[,"b_habitatt"]; pmcmc(t_ac_acclim); mean(t_ac_acclim); quantile(t_ac_acclim, c(0.025, 0.975))
-
-if(rerun){
-  # More realistic model with 
-  model3_new  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = lnRRQ10_ac_acclimate_SV,
-                                       random = list(~1 | record_num,
-                                                     ~1 | species_full,
-                                                     ~1 | trait,
-                                                     ~1 + max_temp_c| spp,
-                                                     ~1 | obs),
-                              R = list(species_full = phylo_cor_wild_ac_acclim), dfs = "contain", 
-                              test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
-
-    model3_new_bayes <- brms::brm(lnRRQ10_ac_acclimate | se(sqrt(lnRRQ10_ac_acclimate_SV), sigma = TRUE) ~ max_temp_c + c_accl_time + cv_c + 
-                                  habitat + habitat:cv_c + 
-                                  (1 | record_num) + 
-                                  (1 | gr(species_full, cov = A_wild_ac_acclim)) + 
-                                  (1 + max_temp_c| spp) + 
-                                  (1|trait), data2 = list(A_wild_ac_acclim = A_wild_ac_acclim), 
-                                  family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
-                                  control = list(adapt_delta = 0.98, max_treedepth = 12), 
-                                  chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acute_vs_acclim)
-
-  # Save model3_new
-    saveRDS(model3_new, file = "./output/models/lnRRQ10_3_new")
-    saveRDS(model3_new_bayes, file = "./output/models/lnRRQ10_3_new_bayes")
-
-  } else{
-        model3.3 <- readRDS("./output/models/lnRRQ10_3.3")
-  model3.3_bayes <- readRDS("./output/models/lnRRQ10_3.3_bayes")
 }
@@
             formula = y ~ x, se = FALSE, colour = "black") + 
-            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ labs(fill = "Habitat") +
+            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ labs(fill = "Habitat") + facet_wrap(~type)+
 theme_classic() + theme(axis.title  = element_text(size = 30), 
@@
 Raw effects are weighted by their precision (inverse sampling variance)."
-  col <- c("#0871B9", "#F3B40D", "#1BB908")
-
-  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
+  col <- rep(c("#0871B9", "#F3B40D", "#1BB908"), 2)
+
+  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)", at = list(type = c("acclim", "acute")), condition.nrow = 1, by = "type", k = FALSE) + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
                         axis.text = element_text(size = 26), 
@@
 
+```{r, wildlnRR_acutevsacclim}
+#| label: wildlnRR_acutevsacclim
+#| echo: false
+#| include: false
+
+###---------------------------------------###
+# Analysis that calculates the plastic adjustment, acclimation - acute within a study and trait to look at whether plasticity is correlated with climate.
+A good point raised by Reviewer 1 that we should test.
+###---------------------------------------###
+
+###---------------------------------------###
+# Data
+###---------------------------------------###
+
+  # Bring in Climate data
+  climate <- read.csv("./output/climate_data/ERA5_air_and_SST_timeseries.csv")
+
+  # Create a match column.
+  climate2 <- climate %>% 
+              mutate(match = paste(Species, Latitude, Longitude, sep =".")) %>% 
+              dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
+
+  # Subset the data and do some new calculations
+    # Steps:
+    # 1. Suse wide data
+    # 2. Drop out lnVR and lnCVR
+    # 3.  Exclude effects where we don't have BOTH acute and acclimation. We need both to subtract from each other
+    # 4. Calculate the weighted average of the effects and its associated sampleing variance so we have only a single acute
+    # 5. Clean up by removing old acute columns
+    # 6. Calculate the difference between acclimation and acute and it's associated associated sampling variance
+    # 7. Clean up by removing old acclimation and acute columns as well as all 'r' columns
+    # 8. Add a match column for joining climate data
+
+                          drop <- colnames(data_wide)[grep("ln[CV]", colnames(data_wide))]
+
+  lnRRQ10_data_acc_minus_aclim <- data_wide %>%        
+                  dplyr::select(!all_of(drop)) %>%  
+                  filter(!is.na(lnRR_Q10_acute_t1) | !is.na(lnRR_Q10_acute_t2)) %>% 
+                  mutate(lnRR_acute = weighted_avg_effects(lnRR_Q10_acute_t1, lnRR_Q10_acute_t2, V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2),
+                      lnRR_acute_SV = weighted_avg_sv(V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2))   %>% 
+                  dplyr::select(-lnRR_Q10_acute_t1, -lnRR_Q10_acute_t2, -V_lnRR_Q10_acute_t1, -V_lnRR_Q10_acute_t2)  %>% 
+                  mutate(lnRRQ10_ac_acclimate = lnRR_acute - lnRR_Q10_acclim, 
+                         lnRRQ10_ac_acclimate_SV = lnRR_acute_SV + V_lnRR_Q10_acclim) %>% 
+                  dplyr::select(-lnRR_Q10_acclim, -V_lnRR_Q10_acclim, -lnRR_acute_SV, -lnRR_acute, -grep("r[12]", colnames(.)))  %>% 
+                  mutate(match = paste(gsub("_", "", species_full), lat, long, sep = "."), 
+                    max_temp_c = scale(temp_2, scale = FALSE),
+                           spp = species_full)
+
+# Now that we have the data calcualted as the difference between acute and acclimation for each effect we want to know of this difference, i.e., the direction and magnitude of plasticity is associated with climate.
+We do not need to pivot longer because the response is simply the difference now so we are ready for anlaysis
+
+# Now, join climate data to full data. This will give us all the climate variability data for each site across time
+lnRRQ10_data_wild_acute_vs_acclim <- left_join(lnRRQ10_data_acc_minus_aclim, climate2, by = "match")
+
+# Check and prune tree
+tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr_wild, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild_ac_acclim <- vcv(tree_lnrr_wild, cor = TRUE)
+        A_wild_ac_acclim <- vcv(tree_lnrr_wild, cor = FALSE) # For bayes, need cov matrix
+
+# Scale data
+        lnRRQ10_data_wild_acute_vs_acclim <- lnRRQ10_data_wild_acute_vs_acclim %>% 
+                                                        mutate(cv_c = scale(cv),
+                                                          acf_all_c = scale(acf_all),
+                                                          c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))
+
+# How much data? Quite a bit with both acute and acclimation, which is good.
+        lnRRQ10_data_wild_acute_vs_acclim %>% group_by(habitat) %>% summarise(n = n(), stdy = length(unique(record_num)))
+
+# How much missing data in acclimation time?
+  lnRRQ10_data_wild_acute_vs_acclim %>% filter(is.na(acclim_period)) %>% group_by(habitat) %>% summarise(n = n(), stdy = length(unique(record_num)))
+
+####################################################
+  # Model3_new: Model environmental variability by acute/acclim
+####################################################
+  rerun = FALSE
+
+# Ok, now that we have it we may as well just rerun the model using the effect size Reviewer 1 is talking about to show that it is nearly the same (rememnber, we lose power here).
+Also remoember that positive effect sizes show acclimation because it implies the acute slope is larger than the acclimation slope.
+Sp, we expect freshwater and marine to have positive overall effect sizes.
+
+if(rerun){
+  model3_new_overall  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + habitat, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                                     ~1 | species_full,
+                                                     ~1 | trait,
+                                                     ~1 + max_temp_c| spp,
+                                                     ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
+  saveRDS(model3_new_overall, file = "./output/models/lnRRQ10_3_new_overall")
+
+  model3_new_overall_bayes <- brms::brm(lnRRQ10_ac_acclimate | se(sqrt(lnRRQ10_ac_acclimate_SV), sigma = TRUE) ~ 
+                                max_temp_c + c_accl_time + habitat + (1 | record_num) + 
+                              (1 | gr(species_full, cov = A_wild_ac_acclim)) + 
+                              (1 + max_temp_c| spp) + 
+                              (1|trait), 
+                              data2 = list(A_wild_ac_acclim = A_wild_ac_acclim), 
+                              family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                              control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                              chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
+                              data = lnRRQ10_data_wild_acute_vs_acclim)
+saveRDS(model3_new_overall_bayes, file = "./output/models/lnRRQ10_3_new_overall_bayes")
+
+} else{
+  model3_new_overall <- readRDS("./output/models/lnRRQ10_3_new_overall")
+  model3_new_overall_bayes <- readRDS("./output/models/lnRRQ10_3_new_overall_bayes")
+}
+
+####################################################
+  # Get contrasts from overall model
+####################################################
+
+  # Extract posteriors
+  posteriors_3_overall <- posterior_samples(model3_new_overall_bayes, "^b")
+
+  # Check acclimation time if it explains variation in new effect?
+  b_c_accl_time_slope <- posteriors_3_overall[,"b_c_accl_time"]; pmcmc(b_c_accl_time_slope); mean(b_c_accl_time_slope); quantile(b_c_accl_time_slope, c(0.025, 0.975))
+
+  # Check slope
+   b_max_temp_c <- posteriors_3_overall[,"b_max_temp_c"]; pmcmc(b_max_temp_c); mean(b_max_temp_c); quantile(b_max_temp_c, c(0.025, 0.975))
+
+  # Freshwater
+    f_ac_acclim  <- posteriors_3_overall[,"b_Intercept"]; pmcmc(f_ac_acclim); mean(f_ac_acclim); quantile(f_ac_acclim, c(0.025, 0.975))
+  # Marine
+    m_ac_acclim  <- f_ac_acclim + posteriors_3_overall[,"b_habitatm"]; pmcmc(m_ac_acclim); mean(m_ac_acclim); quantile(m_ac_acclim, c(0.025, 0.975))
+  # Terrestrial
+    t_ac_acclim  <- f_ac_acclim + posteriors_3_overall[,"b_habitatt"]; pmcmc(t_ac_acclim); mean(t_ac_acclim); quantile(t_ac_acclim, c(0.025, 0.975))
+
+if(rerun){
+  # More realistic model with 
+  model3_new  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c + habitat + habitat:cv_c, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                                     ~1 | species_full,
+                                                     ~1 | trait,
+                                                     ~1 + max_temp_c| spp,
+                                                     ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acute_vs_acclim)
+
+    model3_new_bayes <- brms::brm(lnRRQ10_ac_acclimate | se(sqrt(lnRRQ10_ac_acclimate_SV), sigma = TRUE) ~ max_temp_c + c_accl_time + cv_c + 
+                                  habitat + habitat:cv_c + 
+                                  (1 | record_num) + 
+                                  (1 | gr(species_full, cov = A_wild_ac_acclim)) + 
+                                  (1 + max_temp_c| spp) + 
+                                  (1|trait), data2 = list(A_wild_ac_acclim = A_wild_ac_acclim), 
+                                  family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                                  control = list(adapt_delta = 0.98, max_treedepth = 12), 
+                                  chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_wild_acute_vs_acclim)
+
+  # Save model3_new
+    saveRDS(model3_new, file = "./output/models/model3_new")
+    saveRDS(model3_new_bayes, file = "./output/models/model3_new_bayes")
+
+  } else{
+        model3_new <- readRDS("./output/models/model3_new")
+  model3_new_bayes <- readRDS("./output/models/model3_new_bayes")
+}
+
+#################################################
+### Bayesian Slopes from model3_new_bayes
+#################################################
+ posteriors_model3_new_bayes <- posterior_samples(model3_new_bayes, "^b")
+
+    slope_f_new_delta <- posteriors_model3_new_bayes[,"b_cv_c"]
+    slope_m_new_delta <- posteriors_model3_new_bayes[,"b_cv_c"] + posteriors_model3_new_bayes[,"b_cv_c:habitatm"]
+    slope_t_new_delta <- posteriors_model3_new_bayes[,"b_cv_c"] + posteriors_model3_new_bayes[,"b_cv_c:habitatt"]
+
+##################################################
+    # Models - Habitat subset
+    # Used for making plots
+##################################################
+    # Subset data to habitat
+
+    lnRRQ10_data_wild_acclim_t_delta <- lnRRQ10_data_wild_acute_vs_acclim %>% filter(habitat == "t") %>% filter(!is.na(cv_c)) %>% filter(!is.na(c_accl_time))
+    lnRRQ10_data_wild_acclim_f_delta <- lnRRQ10_data_wild_acute_vs_acclim %>% filter(habitat == "f") %>% filter(!is.na(cv_c)) %>% filter(!is.na(c_accl_time))
+    lnRRQ10_data_wild_acclim_m_delta <- lnRRQ10_data_wild_acute_vs_acclim %>% filter(habitat == "m") %>% filter(!is.na(cv_c)) %>% filter(!is.na(c_accl_time))
+
+  # Check and prune tree
+
+    # Terrestrial. 
+        tree_lnrr_delta_wild_t <- tree_checks(data = lnRRQ10_data_wild_acclim_t_delta, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+    tree_checks(data = lnRRQ10_data_wild_acclim_t_delta, tree = tree_lnrr_delta_wild_t, dataCol = "species_full", type = "check") # Good
+
+  # Marine
+    tree_lnrr_delta_wild_m <- tree_checks(data = lnRRQ10_data_wild_acclim_m_delta, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+    tree_checks(data = lnRRQ10_data_wild_acclim_m_delta, tree = tree_lnrr_delta_wild_m, dataCol = "species_full", type = "check") # Good
+
+  # Freshwater
+    tree_lnrr_delta_wild_f <- tree_checks(data = lnRRQ10_data_wild_acclim_f_delta, tree = tree_p0.7, dataCol = "species_full", type = "prune")
+    tree_checks(data = lnRRQ10_data_wild_acclim_f_delta, tree = tree_lnrr_delta_wild_f, dataCol = "species_full", type = "check") # Good
+
+# Create the phylo correlation matrix
+phylo_cor_wild_ac_acclim_t <- vcv(tree_lnrr_delta_wild_t, cor = TRUE)
+phylo_cor_wild_ac_acclim_m <- vcv(tree_lnrr_delta_wild_m, cor = TRUE)
+phylo_cor_wild_ac_acclim_f <- vcv(tree_lnrr_delta_wild_f, cor = TRUE)
+
+if(rerun){
+
+  # Terrestrial Models: # Note that convergence issues with this model now given data drops too few for a random slope of max temp so need to drop from model.
+Removed max temp slope.
+Note some effects are not defined (missing SD for one group etc) so are dropped from model
+    model_delta_t  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 | spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim_t), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_t_delta, control=list(iter.max=1000, rel.tol=1e-8))
+    saveRDS(model_delta_t, "./output/models/model_delta_t")
+
+    # Freshwater Models. Note some effects are not defined (missing SD for one group etc) so are dropped from model
+
+    model_delta_f  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim_f), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_f_delta)
+
+    saveRDS(model_delta_f, "./output/models/model_delta_f")
+
+    # Marine Models. Note some effects are not defined (missing SD for one group etc) so are dropped from model
+
+    model_delta_m  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c, V = lnRRQ10_ac_acclimate_SV,
+                                       random = list(~1 | record_num,
+                                            ~1 | species_full,
+                                            ~1 | trait,
+                                            ~1 + max_temp_c| spp,
+                                            ~1 | obs),
+                              R = list(species_full = phylo_cor_wild_ac_acclim_m), dfs = "contain", 
+                              test = "t", data = lnRRQ10_data_wild_acclim_m_delta)
+    saveRDS(model_delta_m, "./output/models/model_delta_m")
+
+  } else {
+     model_delta_t <- readRDS("./output/models/model_delta_t")
+     model_delta_f <- readRDS("./output/models/model_delta_f")
+     model_delta_m <- readRDS("./output/models/model_delta_m")
+}
+
+```
+
 When measuring plasticity, what is relevant is the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ because this captures the degree to which organisms plastically adjust (or acclimate).
@@
 Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c)`, 95\% CI: `r quantile(b_max_temp_c, c(0.025, 0.975))`, p = `r pmcmc(b_max_temp_c)`).
+
+Like our analysis with $lnRR_{Q_{10_{acclimation}}}$, $\Delta lnRR_{Q_{10}}$ was also not related to climate variability that a given population experienced @fig-delta-climate.
 
@@
 
+```{r, fig-delta-climate}
+#| label: fig-delta-climate
+#| fig-cap: "Past climate variability did not predict acclimation responses as measured by $\\Delta lnRR_{Q_{10}}$.
+Predicted mean acclimation (thick black line) $\\Delta lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats.
+Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals.
+Raw effects are weighted by their precision (inverse sampling variance).
+Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ values for the slopes are shown for each habitat."
+
+size_axis = 20
+col <- c("#0871B9", "#F3B40D", "#1BB908")
+
+####################
+# lnVR_Delta CV
+####################
+ dat_text <- data.frame(label = c(text(slope_f_new_delta), text(slope_m_new_delta), text(slope_t_new_delta)),
+                       label2 = c(text(slope_f_new_delta, b = FALSE), text(slope_m_new_delta,b = FALSE), text(slope_t_new_delta,b = FALSE)),
+                            p = c(p_text(slope_f_new_delta), p_text(slope_m_new_delta), p_text(slope_t_new_delta)),
+                        title = c("Freshwater", "Marine", "Terrestrial"), 
+                    condition = c("f", "m", "t"),
+                            x = rep(0, 3),
+                            y = rep(-1.1, 3))
+y_adj = -3
+size_axis =14
+
+# Terrestrial
+  p_t_rr <-  bubble_plot(model_delta_t, mod = "cv_c", group = "spp", ylab = TeX("$\\Delta lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_t_delta, aes(x = cv_c, y = lnRRQ10_ac_acclimate, size = 1/sqrt(lnRRQ10_ac_acclimate_SV)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
+  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
+  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
+  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis),
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,2)
+
+# Marine
+p_m_rr <-  bubble_plot(model_delta_m, mod = "cv_c", group = "spp", ylab = TeX("$\\Delta lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_m_delta, aes(x = cv_c, y = lnRRQ10_ac_acclimate, size = 1/sqrt(lnRRQ10_ac_acclimate_SV)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
+  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+
+# Freshwater
+p_f_rr <-  bubble_plot(model_delta_f, mod = "cv_c", group = "spp", ylab = TeX("$\\Delta lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+    geom_point(data = lnRRQ10_data_wild_acclim_f_delta, aes(x = cv_c, y = lnRRQ10_ac_acclimate, size = 1/sqrt(lnRRQ10_ac_acclimate_SV)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
+  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
+theme(axis.text = element_text(size = size_axis), 
+      axis.text.y = element_text(size = size_axis), 
+      axis.title = element_text(size = size_axis), 
+      axis.title.x = element_blank(),
+      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)
+
+  p_cv_delta <- (p_t_rr + p_m_rr + p_f_rr) +
+            plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))
+
+  ggsave(p_cv_delta, width = 18, height = 10, filename = "./output/figures/figS6.png")
+
+  p_cv_delta <- image_read("./output/figures/figS6.png")
+  p_cv_delta
+
+```
+
 #### **Comparing relative variance changes: the *lnCVR* ratio**
@@
  p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
-  ggsave(p_mv, file = "./output/figures/figS6.png", height = 8, width = 8)
-
-  p_mv <- magick::image_read("./output/figures/figS6.png")
+  ggsave(p_mv, file = "./output/figures/figS7.png", height = 8, width = 8)
+
+  p_mv <- magick::image_read("./output/figures/figS7.png")
   p_mv
@@
 
-  ggsave(p3b, filename = "./output/figures/figS7.pdf", width = 11.5, height = 8)
-
-  figs1 <- image_read("./output/figures/figS7.pdf")
+  ggsave(p3b, filename = "./output/figures/figS8.pdf", width = 11.5, height = 8)
+
+  figs1 <- image_read("./output/figures/figS8.pdf")
   figs1
@@
 figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait_vr, filename = "./output/figures/figS8.png", width = 28, height = 8, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/figS8.png")
+ggsave(figbtrait_vr, filename = "./output/figures/figS9.png", width = 28, height = 8, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figS9.png")
 figbtrait
@@
 figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
-ggsave(figcvr_lh, filename = "./output/figures/figS9.pdf", width = 28, height = 10, device = "pdf")
-
-figcvr_lh <- magick::image_read("./output/figures/figS9.pdf")
+ggsave(figcvr_lh, filename = "./output/figures/figS10.pdf", width = 28, height = 10, device = "pdf")
+
+figcvr_lh <- magick::image_read("./output/figures/figS10.pdf")
 figcvr_lh
@@
 figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
-ggsave(figbtrait, filename = "./output/figures/figS10.png", width = 28, height = 14, device = "png")
-
-figbtrait <- magick::image_read("./output/figures/figS10.png")
+ggsave(figbtrait, filename = "./output/figures/figS11.png", width = 28, height = 14, device = "png")
+
+figbtrait <- magick::image_read("./output/figures/figS11.png")
 figbtrait
@@
 fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
-ggsave(fig2, filename = "./output/figures/figS11.png", height = 20, width = 15)
-
-img_fig2 <- magick::image_read("./output/figures/figS11.png")
+ggsave(fig2, filename = "./output/figures/figS12.png", height = 20, width = 15)
+
+img_fig2 <- magick::image_read("./output/figures/figS12.png")
 img_fig2
@@
 figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figvrtrait, filename = "./output/figures/figS12.png", height = 20, width = 15)
-
-img_figvrtrait <- magick::image_read("./output/figures/figS12.png")
+ggsave(figvrtrait, filename = "./output/figures/figS13.png", height = 20, width = 15)
+
+img_figvrtrait <- magick::image_read("./output/figures/figS13.png")
 img_figvrtrait
@@
 figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-ggsave(figcvrtrait, filename = "./output/figures/figS13.png", height = 20, width = 15)
-
-img_figcvrtrait <- magick::image_read("./output/figures/figS13.png")
+ggsave(figcvrtrait, filename = "./output/figures/figS14.png", height = 20, width = 15)
+
+img_figcvrtrait <- magick::image_read("./output/figures/figS14.png")
 img_figcvrtrait
@@
 figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS14.png")
-
-figS12 <- image_read("./output/figures/figS14.png")
+ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS15.png")
+
+figS12 <- image_read("./output/figures/figS15.png")
 figS12
@@
 
-ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS15.pdf")
-
-  p_acf <- image_read("./output/figures/figS15.pdf")
+ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS16.pdf")
+
+  p_acf <- image_read("./output/figures/figS16.pdf")
   p_acf 
@@
 figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
-ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS16.png")
-
-figs2 <- image_read("./output/figures/figS16.png")
+ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS17.png")
+
+figs2 <- image_read("./output/figures/figS17.png")
 figs2
@@
 p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
-ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS17.png")
-
-p_sim <- image_read("./output/figures/figS17.png")
+ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS18.png")
+
+p_sim <- image_read("./output/figures/figS18.png")
 p_sim

### 2024-12-30 ms.qmd
Adding k into fig. 2x acute because we have cold and hot but only 1 acclimation

@@
             formula = y ~ x, se = FALSE, colour = "black") + 
-            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ labs(fill = "Habitat") + facet_wrap(~type)+
+            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + labs(fill = "Habitat") + facet_wrap(~type) +
 theme_classic() + theme(axis.title  = element_text(size = 30), 
@@
 
-  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)", at = list(type = c("acclim", "acute")), condition.nrow = 1, by = "type", k = FALSE) + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
+  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)", at = list(type = c("acclim", "acute")), condition.nrow = 1, by = "type") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30),
                         axis.text = element_text(size = 26), 

### 2024-12-30 ms.qmd
Few of R2 comments dealt with

@@
 `r utils::packageVersion("ggtree")`) [@Yu2017-wj].
-We resolved all polytomies in the tree.
+We resolved all polytomies in the tree randomly using using the *multi2di* function in *ape* (vers.
+`r utils::packageVersion("ape")`) [@Paradis2019-gx].
 Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr].
@@
 As such, we used an intermediate value of p = 0.7.
-We used the R packages *ape* (vers.
-`r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers.
+We used the R packages *ape*  and *phytools* (vers.
 `r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.
@@
 
-Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*).
-We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$.
+Finally, we used the ERA5 climate model [@Hersbach2020-hx] to test whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (see further details in the *Supplementary Materials*).
+We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses.
 We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5").

### 2024-12-30 ms.qmd
Added in new ref

@@
 A more detailed trait analysis is presented in the *Supplementary Materials*.
-We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal].
+We expected that whole-organism traits would be more likely to maintain variation in physiological function and be less likely to acclimate because whole-organism function relies on a greater number of biochemical reactions each with different thermal sensitivities [@fields2001protein; @angilletta2009thermal; @iverson2020thermal].
 

### 2025-01-01 ms.qmd
Dealt with R1 and R2 comments in introduction and fig 1.

@@
 Reversible phenotypic plasticity, such as physiological acclimation, is relatively rapid and can be fine-tuned to environmental conditions making it the first ‘line-of-defense’ against environmental change [@Dewitt1998].
-For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses (@fig-concept).
-However, longer-lasting (days-weeks) temperature increases that move environmental conditions away from thermal maxima of physiological rate functions (i.e., thermal performance curves) can be mitigated by acclimation, which adjust reaction rates [@Seebacher2015-wi; @Havird2020-mj].
+For example, physiological rates are known to speed up as temperature increases because of the thermodynamic effects on chemical reaction rates -- so called 'acute' temperature responses.
+However, longer-lasting (days-weeks) temperature increases that move environmental conditions away from thermal optima can be mitigated by acclimation, which adjust reaction rates or the thermal optima itself [@Seebacher2015-wi; @Havird2020-mj].
 Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
@@
 Acclimation, however, does not necessarily result in complete compensation in response to environmental change [ *sensu* @huey1999testing].
-Rather, increased physiological rates are often only partially compensated such that ectotherms acclimated to, and measured at, warmer temperatures (R2.2 in @fig-concept) have higher physiological rates than those acclimated to, and measured at, cooler temperatures (R1.1 in @fig-concept) [@huey1999testing; @Havird2020-mj].
+Rather, increased physiological rates are often only partially compensated such that ectotherms acclimated to, and measured at, warmer temperatures have higher physiological rates than those acclimated to, and measured at, cooler temperatures [@huey1999testing; @Havird2020-mj].
 

### 2025-01-01 ms.qmd
Update supp with R1 comments

@@
 
+# Look at life stages and trait type distribution
+#life_trait <- lnRRQ10_data %>% group_by(life.hist, trait_broad, habitat) %>% summarise(n=n()) %>% arrange(habitat)
+#colnames(life_trait) <- c("Life Stage", "Trait Category", "Habitat", "# of Effects")
+#flextable(life_trait) %>% save_as_docx(path = "./output/tables/table.docx")
+
 ##################################################
@@
   t_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_habitatt"] + posteriors_1.2[,"b_typeacclim"] + posteriors_1.2[,"b_typeacclim:habitatt"]
+
+# Slopes for max temp and acclimation time
+  acc_time_slope_model1.2 <- posteriors_1.2[,"b_c_accl_time"]
+  max_temp_slope_model1.2 <- posteriors_1.2[,"b_max_temp_c"]
 
@@
 After title and abstract screening, there was a total of 149 papers for full text screening.
-Papers were included only if they: 1) measured a physiological rate acutely at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
-Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species.
+Papers were included only if they: 1) measured a physiological rate at two temperatures on a sample of animals chronically exposed to the same two temperatures for at least 1 week.
+Studies had to measure, following acclimation, physiological rates at acute temperatures that at least matched acclimation temperatures, but often measurements were fully factorial allowing for both acclimated and acute measurements to be extracted; and 2) where physiological rates measured were burst and sustained locomotion, metabolic rates (standard, resting, routine and maximal), heart rates, and/or enzyme activities.
+Importantly, as in @Seebacher2015-wi, we only included studies that manipulated temperatures within normal thermal ranges for the species because we expected stressful temperatures would impact physiological rates.
+We determined which temperatures coincided with normal thermal ranges using information within the study (i.e., self-reported) or, when not provided, information from the internet on typical activity temperatures (e.g., Wikipedia or Google searches).
+This criterion meant that we often only had a single data set (1 acclimated and 2 acute measurements) for each paper.
 
@@
 #### **Exploring the impact of maximum treatment temperature on $lnRR_{Q_{10}}$**
+
+As predicted, we did find evidence that $lnRR_{Q_{10}}$ was impacted by the maximum temperature used within a study, but this effect was small (Slope from "Model 2": `r mean (max_temp_slope_model1.2)`, 95% CI: `r quantile(max_temp_slope_model1.2, 0.025)` to `r quantile(max_temp_slope_model1.2, 0.975)`, $p_{MCMC}$ = `r round(pmcmc(max_temp_slope_model1.2), digit = 4)`, @fig-lnrrq10_temp).
+Regardless, we control for maximum temperature in all our models.
 
@@
 
+While we control for acclimation time in all our models, it did not impact $lnRR_{Q_{10}}$ (Slope from "Model 2": `r mean (acc_time_slope_model1.2)`, 95% CI: `r quantile(acc_time_slope_model1.2, 0.025)` to `r quantile(acc_time_slope_model1.2, 0.975)`, $p_{MCMC}$ = `r round(pmcmc(acc_time_slope_model1.2), digit = 4)`, @fig-accl_time)
+
 ```{r, fig-accl_time}
@@
 
-  ggsave(accl_time, file = "./output/figures/figS3.png", height = 6, width = 8.5)
+  ggsave(accl_time, file = "./output/figures/figS3.png", height = 6, width = 12)
 
@@
 
-#### **Acute and acclimation for detailed trait categories across marine, freshwater and terrestrial taxa**
+#### **Acute and acclimation for trait categories across marine, freshwater and terrestrial taxa**
 
@@
 Neither trait category acclimated in terrestrial ectotherms ([@fig-btrait]A).
+However, there were no biochemical traits measured for juveniles in terrestrial species confounding life stage and trat category – though there were no differences between adult and juveniles in any case (see results in main manuscript).
 

### 2025-01-02 ms.qmd
Adjusted qmd

@@
 
-To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included an interaction between acclimation type, habitat type, latitude and longitude (referred to as “Model 6”).
+To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included a non-linear smoother between latitude and longitude and an interaction between effect type and habitat type while correcting for acclimation time and maximum temperature (referred to as “Model 6”).
 We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
@@
 (A) Mean acute and acclimation $lnRR_{Q_{10}}$ across ectotherms in marine, freshwater, and terrestrial habitats.
-Overall mean physiological rates ($\\mu$) across the habitats are provided in the results for simplicity and only contrasts between acute and acclimation $lnRR_{Q_{10}}$ are shown (B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+Overall mean physiological rates ($\\mu$) across the habitats are provided in the results for simplicity and only contrasts between acute and acclimation $lnRR_{Q_{10}}$ are shown.
+Percentages refer to the percentage change in physiological rates between acclimation and acute $lnRR_{Q_{10}}$ (B) Mean acute and acclimation $lnVR_{Q_{10}}$ across ectotherms in marine, freshwater and terrestrial habitats.
+Percentages refer to the percentage change in physiological rate variance for a 10°C temperature change.
 For both plots, k = total number of effect size estimates while the numbers in brackets indicate the number of species.

### 2025-01-03 ms.qmd
dealt with the last of R2 comments and only one more R1 comment to deal with that involves a figure adjustment.

@@
 However, longer-lasting (days-weeks) temperature increases that move environmental conditions away from thermal optima can be mitigated by acclimation, which adjust reaction rates or the thermal optima itself [@Seebacher2015-wi; @Havird2020-mj].
-Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance around a fitness optimum despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
+Physiological acclimation is driven by endocrine and epigenetic processes that change the underlying physiology to allow organisms to maintain physiological performance despite changes in the environment [@seebacher2019histone; @little2013thyroid; @taff2016endocrine].
 Acclimation therefore alters acute thermal sensitivity to offset the potentially negative effects of acute temperature changes (e.g., higher energetic demands).
@@
 
-Acclimation is expected to evolve in populations experiencing high but predictable environmental variability, and when the costs of plasticity are low [@Chevin2017; @Dewitt1998; @Reed2010].
-Thermal variation and predictability differ across habitats (terrestrial, marine and freshwater) [@steele2019comparison], and it may be expected that organisms within these habitats vary in their capacity for acclimation.
+Acclimation is expected to evolve in populations experiencing high but predictable environmental variability, and when the fitness costs of plasticity are low [@Chevin2017; @Dewitt1998; @Reed2010].
 @rohr2018complex show relationships between acclimation capacity, latitude and body size suggesting climate could be an important driver of acclimation responses.
-In addition, species occupying terrestrial habitats exhibit weaker acclimation capacities and, therefore may be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
-In contrast, marine and freshwater organisms appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022].
+In addition, distinct patterns of dispersal, habitat use, and costs of plasticity may result in life-history stages diverging in their capacity for acclimation [@rossi2019ageing].
+Species occupying terrestrial habitats exhibit weaker acclimation capacities and, therefore may be particularly vulnerable to climate change given their greater probability of experiencing thermal extremes that overwhelm physiological homeostasis [@Seebacher2015-wi; @Gunderson2015-hz; @hoffmann2013upper; @morley2019physiological].
+In contrast, marine and freshwater organisms appear to have greater physiological acclimation capacity [e.g., @Seebacher2015-wi; @Pottier2022], possibly because of differences in thermal variability in these environments [e.g., @steele2019comparison] that selects for differences in plasticity.
 However, the focus of research up to now has been primarily on mean physiological responses neglecting how variability in physiological processes might also be impacted by higher temperatures.
@@
 Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011; @bush2016incorporating; @seebacher2023can; @Sanderson2023; @urban2023and].
-Here we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance at warmer temperatures ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
+While most of our data are from vertebrates and fish, we show that both acclimation responses ($lnRR_{Q_{10}}$) and increases in physiological rate variance at warmer temperatures ($lnVR_{Q_{10}}$) of ectotherms varied across habitats.
 Our results uncover an hitherto unrecognised dynamic where the benefits of partial acclimation are paralleled by increases in trait variance that depend on habitat in ways that may have impacts on how ectotherm populations will be able to adapt to increased temperatures.
@@
 We included any papers that were missed between our searches and those of @Havird2020-mj.
+Although the goals and search queries differed between @Havird2020-mj and our meta-analysis both meta-analyses make use of data for metabolic rate using similar experimental designs.
 @Havird2020-mj added 7 new studies (mainly because they were focused on metabolic rates), and our searches differed from theirs by only a single paper [i.e., @Bulgarella2015-yl].

### 2025-01-03 ms.qmd
Few corrections. Still deciding on what to do with sim fig

@@
 #| fig-align: center
-#| fig-cap: "Simulated performance curves for *n* = 40 individuals in four hypothetical scenerios with varying performance breadth ($\\sigma$), optima ($\\delta$) and skewness ($\\alpha$).
+#| fig-cap: "Simulated performance curves for *n* = 40 individuals in four hypothetical scenarios with varying performance breadth ($\\sigma$), optima ($\\delta$) and skewness ($\\alpha$).
 Individual performance curves are different colours.

### 2025-01-03 ms.qmd
Finsihed dealing with figure comment for R1

@@
 #| fig-align: center
-#| fig-cap: "Results from sensitivity analysis.
-Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal maxima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
+#| fig-cap: "Performance curve simulations for the expected $lnVR_{Q_{10}}$ when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal maxima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01).
 In all simulations, population parameters were $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{\\delta}$ and $\\sigma_{\\sigma}$.
-The parameter space that matches the observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is highlighted.
+The parameter space that matches the observed mean $lnVR_{Q_{10}}$ from our meta-analysis for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is labelled and highlighted.
 Dashed lines indicate the relative differences between the three habitat types when holding one variance parameter constant."

### 2025-01-06 ms.qmd
realise I did not properly deal with R1 comment on aoverall so did that now

@@
                                                         get_whole_bio(pred_lnrr_trait_post, habitat = "f", trait_b_data))
+
+#######------------------------------------------------------------#########
+# Add overall trait R1
+#######------------------------------------------------------------#########
+  # Tissue/whole-organism acute and acclimation RR
+    pred_lnrr_post_overall_acute_tissue = c(pred_lnrr_trait_post[,2], pred_lnrr_trait_post[,6], pred_lnrr_trait_post[,10])
+    pred_lnrr_post_overall_aclim_tissue = c(pred_lnrr_trait_post[,1], pred_lnrr_trait_post[,5], pred_lnrr_trait_post[,9])
+     contrast_lnrr_tissue <- pred_lnrr_post_overall_aclim_tissue - pred_lnrr_post_overall_acute_tissue
+
+      # Biochemical acute and acclimation RR
+    pred_lnrr_post_overall_acute_biochem = c(pred_lnrr_trait_post[,4], pred_lnrr_trait_post[,8], pred_lnrr_trait_post[,12])
+    pred_lnrr_post_overall_aclim_biochem = c(pred_lnrr_trait_post[,3], pred_lnrr_trait_post[,7], pred_lnrr_trait_post[,11])
+        contrast_lnrr_biochem <- pred_lnrr_post_overall_aclim_biochem - pred_lnrr_post_overall_acute_biochem
+
+#######------------------------------------------------------------#########
+
 ###########################################################
@@
 
+#######------------------------------------------------------------#########  
+# Add overall trait R1 - pool habitats
+#######------------------------------------------------------------#########
+
+ # Adult acute and acclimation RR - Note here we use rows because it's a different matrix calculation
+    pred_lnrr_post_overall_acute_adult <- c(pred[4,], pred[8,], pred[12,]);
+    pred_lnrr_post_overall_aclim_adult <- c(pred[3,], pred[7,], pred[11,])
+                contrast_lnrr_adult_lh <- pred_lnrr_post_overall_aclim_adult - pred_lnrr_post_overall_acute_adult
+
+  # Juvenile acute and acclimation RR - Note here we use rows because it's a different matrix calculation
+    pred_lnrr_post_overall_acute_jeu <-  c(pred[2,], pred[6,], pred[10,])
+    pred_lnrr_post_overall_aclim_jeu <- c(pred[1,], pred[5,], pred[9,])
+                contrast_lnrr_jeu_lh <- pred_lnrr_post_overall_aclim_jeu - pred_lnrr_post_overall_acute_jeu
+
 ####################################################
@@
 
-Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles, except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
+Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`), except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
 Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
@@
 
+#######------------------------------------------------------------#########
+         # Add overall trait R1
+#######------------------------------------------------------------#########
+      # Tissue/whole-organism acute and acclimation VR
+    pred_lnvr_post_overall_acute_tissue = c(pred_lnvr_traitb_post[,2], pred_lnvr_traitb_post[,6], pred_lnvr_traitb_post[,10])
+    pred_lnvr_post_overall_aclim_tissue = c(pred_lnvr_traitb_post[,1], pred_lnvr_traitb_post[,5], pred_lnvr_traitb_post[,9])
+      pooled_tissue = c(pred_lnvr_post_overall_acute_tissue, pred_lnvr_post_overall_aclim_tissue)
+
+      # Biochemical acute and acclimation VR
+    pred_lnvr_post_overall_acute_biochem = c(pred_lnvr_traitb_post[,4], pred_lnvr_traitb_post[,8], pred_lnvr_traitb_post[,12])
+    pred_lnvr_post_overall_aclim_biochem = c(pred_lnvr_traitb_post[,3], pred_lnvr_traitb_post[,7], pred_lnvr_traitb_post[,11])
+      pooled_biochem = c(pred_lnvr_post_overall_acute_biochem, pred_lnvr_post_overall_aclim_biochem)
+#######------------------------------------------------------------#########
+
 ###################################################
@@
                                                 get_lifestage(pred_lh_vr, habitat = "f", lh_b_data))
+
+#######------------------------------------------------------------#########
+# Add overall trait R1
+#######------------------------------------------------------------#########
+  # Adult acute and acclimation VR
+    pred_lnvr_post_overall_acute_adult = c(pred_lh_vr[4,], pred_lh_vr[8,], pred_lh_vr[12,])
+    pred_lnvr_post_overall_aclim_adult = c(pred_lh_vr[3,], pred_lh_vr[7,], pred_lh_vr[11,])
+      pooled_adult = c(pred_lnvr_post_overall_aclim_adult, pred_lnvr_post_overall_acute_adult)
+
+  # Juvenile acute and acclimation VR
+    pred_lnvr_post_overall_acute_jeu = c(pred_lh_vr[2,], pred_lh_vr[6,], pred_lh_vr[10,]); 
+    pred_lnvr_post_overall_aclim_jeu = c(pred_lh_vr[1,], pred_lh_vr[5,], pred_lh_vr[9,]); 
+      pooled_juev = c(pred_lnvr_post_overall_acute_jeu, pred_lnvr_post_overall_aclim_jeu)
 
@@
 
-Each life-history stage exhibited the same pattern of variance change in each of the habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
+Each life-history stage exhibited the same pattern of variance change in each of the habitats (Adult-Juvenile contrasts: Marine: $\beta$ = `r contrast_lnvr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[2,4]` to `r contrast_lnvr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[3,4]` to `r contrast_lnvr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnvr_lh_cat_stats[1,4]` to `r contrast_lnvr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_lh_cat_stats[1,6]`, overall across habitats: $\beta$ = `r mean(pooled_adult - pooled_juev)`, 95\% CI: `r quantile(pooled_adult - pooled_juev, 0.025)` to `r quantile(pooled_adult - pooled_juev, 0.975)`, $p_{MCMC}$ = `r pmcmc(pooled_adult - pooled_juev)`), with no differences between acute and acclimation effect types ("Model 4"; @fig-cvrlh).
 
@@
 Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI).
-$\\beta$ values are the contrasts between acute and acclimation means within each habitat.
 $\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type.
@@
 Across habitats, the extent to which whole-organism versus biochemical traits acclimated varied ("Model 3"; [@fig-btrait]A-C).
+Overall, there was no difference between the capacity for biochemical and tissue/whole-organism traits to plastically adjust (overall difference between acclimation and acute $lnRR_{Q_{10}}$ across habitats: `r mean(c(contrast_lnrr_tissue, contrast_lnrr_biochem))`, 95% CI: `r quantile(c(contrast_lnrr_tissue, contrast_lnrr_biochem), 0.025)` to `r quantile(c(contrast_lnrr_tissue, contrast_lnrr_biochem), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_tissue, contrast_lnrr_biochem))`).
 Biochemical traits acclimated to a greater extent compared to whole-organism traits in marine habitats ([@fig-btrait]B), whereas both whole-organism and biochemical traits acclimated similarly in freshwater ectotherms ([@fig-btrait]C).
@@
 
-Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but this was only significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
+Across habitats biochemical processes tended to result in greater increases in variance at higher temperatures, but not significantly so (overall contrast: `r mean(pooled_biochem - pooled_tissue)`, 95% CI:`r quantile(pooled_biochem - pooled_tissue, 0.025)` to `r quantile(pooled_biochem - pooled_tissue, 0.975)`,  $p_{MCMC}$ = `r pmcmc(pooled_biochem - pooled_tissue)`).
+However, within habitats there was a significant for marine ectotherms (biochemical/whole-organism contrasts: Marine: $\beta$ = `r contrast_lnvr_trait_cat_stats[2,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[2,4]` to `r contrast_lnvr_trait_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[2,6]`; Freshwater: $\beta$ = `r contrast_lnvr_trait_cat_stats[3,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[3,4]` to `r contrast_lnvr_trait_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[3,6]`; Terrestrial: $\beta$ = `r contrast_lnvr_trait_cat_stats[1,3]`, 95% CI: `r contrast_lnvr_trait_cat_stats[1,4]` to `r contrast_lnvr_trait_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnvr_trait_cat_stats[1,6]`) ([@fig-btrait]D-F; "Model 3").
 Variance increases for biochemical traits was reduced during acclimation in marine ectotherms ([@fig-btrait]E).

### 2025-01-06 ms.qmd
Added in new code to add the overall estimates for traits and life stage category analysis. Added in a sentence for R1

@@
 
-Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`), except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
+Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `r mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`), except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
 Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).

### 2025-01-06 ms.qmd
Some important additions from Shinichi

@@
 Simulations suggest that these patterns may result from differences in among-individual variation in thermal breadth and optima of performance curves across habitats.
-4.	Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because of both a lack of acclimation capacity and a limited increases in variance that may provide less raw material for evolutionary adaptation.
+4.	Our results highlight the greater vulnerability of terrestrial ectotherms to climate change because of both a lack of acclimation capacity and a limited increase in variance that may provide less raw material for evolutionary adaptation.
 Considering both acclimation capacity and variance in physiological rates side-by-side is therefore important for understanding how climate change will impact populations.
@@
 
-where, $s_{lnRR_{Q_{10_{acute}}}}$ and $s_{lnRR_{Q_{10_{acclimation}}}}$ is the sampling variance for the acute and acclimation effect sizes, respectively.
+where, $s_{lnRR_{Q_{10_{acute}}}}$ and $s_{lnRR_{Q_{10_{acclimation}}}}$ is the sampling variance for the acute and acclimation effect sizes, respectively (note that we assume the independence of ‘acute’ and ‘acclimation’ groups).
 Again, all notation is defined in @eq-Vlnq10 in the main manuscript.
@@
 $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero.
-k = total number of effect size estimates while the numbers in brackets indicate the number of species.
-For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles.
+k = total number of effect size estimates, while the numbers in brackets indicate the number of species.
+For ease of visualisation, all the raw data plotted for both acute and acclimation-type effect sizes are presented as circles.
 Raw effects are weighted by their precision (inverse sampling variance).

### 2025-01-07 ms.qmd
Small adjustments and re-render of doc. Renames it. Added awknowledgements

@@
     reference-doc: ./bib/template.docx
-    output-file: "ms_fe.docx"
+    output-file: "ms_fe_r1_clean.docx"
 editor_options: 
@@
 We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to acclimation responses (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because acute responses were reported for each of the two acclimation temperatures (@fig-phylo).
-The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
-However, on average they were in the same direction and only differed by ~10%.
-Hence, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in subsequent analyses.
 
@@
 
-Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly between aquatic and terrestrial habitats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
+Physiological rates increased more with temperature in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly between aquatic and terrestrial habitats (differences between average $lnRR_{Q_{10}}$; Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2").
 However, capacity for acclimation depended on the habitat.
@@
 We would like to thank Malgorzata Lagisz for helping sort out the phylogeny used in our analysis and Enrico Rezende for discussions around alternative implementations of thermal performance curves.
-We are also grateful to three anonymous reviewers who all provided extremely constructive feedback that greatly improved the manuscript.
+We are also grateful to four anonymous reviewers and Justin Havird who all provided extremely constructive feedback that greatly improved the manuscript.
 
@@
 #### **Comparing cool and warm acclimated acute responses**
+
+The two acute $lnRR_{Q_{10}}$ effect sizes ([@fig-concept]A) differed significantly from each other ($\beta$ = `r mean(change_acute)`, 95% CI: `r quantile(change_acute, 0.025)` to `r quantile(change_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(change_acute))`) with animals acclimated to high temperatures having slightly higher average $lnRR_{Q_{10}}$ ($\mu$ = `r mean(hot_acute)`, 95% CI: 95% CI: `r quantile(hot_acute, 0.025)` to `r quantile(hot_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(hot_acute))`, $Q_{10}$ = `r mean(exp(hot_acute))`) compared to animals at lower temperatures ($\mu$ = `r mean(cold_acute)`, 95% CI: 95% CI: `r quantile(cold_acute, 0.025)` to `r quantile(cold_acute, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(cold_acute))`, $Q_{10}$ = `r mean(exp(cold_acute))`) (@fig-Sacute).
+However, on average they were in the same direction and only differed by ~10%.
+Hence, we averaged the two acute $lnRR_{Q_{10}}$ effect sizes in all our analyses.
 

### 2025-01-08 ms.qmd
Fxiing and cleaning the paper. Also seperate out supp and main ms

@@
 Freshwater and marine ectotherms are capable of acclimation and have the greatest increase in variance.
-In contrast, terrestrial ectotherms lack the capacity for acclimation and have smaller increases in variance.
+In contrast, terrestrial ectotherms have reduced acclimation abilities and smaller increases in physiological rate.
 Simulations suggest that these patterns may result from differences in among-individual variation in thermal breadth and optima of performance curves across habitats.
@@
 Here, we use meta-analysis to establish the current state-of-knowledge of the extent to which aquatic and terrestrial ectotherms are capable of physiological plasticity.
-We developed new effect sizes ([@fig-concept]A)to quantify how variance in physiological rates change with temperature to ask the following questions regarding acclimation-induced changes in trait means and variances: 1) Does variance in physiological rates change as temperatures rise?
+We then developed new effect sizes to quantify how variance in physiological rates change with temperature to ask the following questions regarding acclimation-induced changes in trait means and variances: 1) Does variance in physiological rates change as temperatures rise?
 2) Are temperature effects on means of physiological rates greater than changes in variance across aquatic and terrestrial ectotherms?
@@
 (A) Two idealised thermal performance curves for animals acclimated at 'cold' ('blue') temperatures and warm ('red') temperatures.
-Shaded blue and red areas are the thermal maxima of the performance curves.
 Physiological rates are measured for a sample of ectotherms at two different temperatures along the thermal performance curves ($T_{1}$ = 20°C and $T_{2}$ = 30°C) for both curves.
@@
 For studies that measure acute and acclimated responses we used the mean, standard deviation, and sample size to derive both acute and acclimation $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ estimates.
-For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ acutely we could only calculate acute versions of these effect size estimates.
+For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ after acclimation we could only calculate acclimation versions of these effect size estimates.
 For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
@@
 
-#### *Multi-level Meta-regression (MLMR) Models*
+#### *Multi-level Meta-Regression (MLMR) Models*
 
@@
 Such an analysis is similar to analyses using an effect size that is a contrast between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ but is more powerful because it allows studies without acute responses to be included (see *Supplementary Materials*).
-With acclimation time and maximum temperature as moderators in all our models.
 
@@
 
-Finally, we used the ERA5 climate model [@Hersbach2020-hx] to test whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (see further details in the *Supplementary Materials*).
+Finally, we used the ERA5 climate model [@Hersbach2020-hx] to test whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ were predicted by climate variability (CV) (see further details in the *Supplementary Materials*).
 We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses.
@@
 
-#### *Modelling how climate change can impact relative variance in physiological rates*
+#### *Modelling how climate change can impact variance in physiological rates*
 
 To explore the potential consequences of the impacts that human-induced climate change may have on variance in physiological rates we fit a model that included a non-linear smoother between latitude and longitude and an interaction between effect type and habitat type while correcting for acclimation time and maximum temperature (referred to as “Model 6”).
-We assumed that any change in $lnVR_{Q_{10}}$ across latitude and longitude could vary by habitat type (i.e., an interaction between habitat).
 We used non-linear tensors for latitude and longitude as any response could be complicated by local factors (e.g., altitude).
@@
 
-Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `r mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`), except for marine habitats where adults acclimated to a greater extent ("Model 4"; [@fig-cvrlh]A-C).
-Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`).
+Acclimation capacity did not vary consistently by life-history stage with no differences in $lnRR_{Q_{10_{acclimation}}}$ and $lnRR_{Q_{10_{acute}}}$ between adult and juveniles (overall contrast: `r mean(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))` 95\% CI: `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.025)` to `r quantile(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh), 0.975)`, $p_{MCMC}$ = `r pmcmc(c(contrast_lnrr_adult_lh,contrast_lnrr_jeu_lh))`).
+Averaging over acute and acclimation effects there were also no differences between adults and juveniles within habitats (Adult-Juvenile: Terrestrial: `r contrast_lnrr_lh_cat_stats[1,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[1,4]` to `r contrast_lnrr_lh_cat_stats[1,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[1,6]`; Marine: `r contrast_lnrr_lh_cat_stats[2,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[2,4]` to `r contrast_lnrr_lh_cat_stats[2,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[2,6]`; Freshwater: `r contrast_lnrr_lh_cat_stats[3,3]`, 95\% CI: `r contrast_lnrr_lh_cat_stats[3,4]` to `r contrast_lnrr_lh_cat_stats[3,5]`, $p_{MCMC}$ = `r contrast_lnrr_lh_cat_stats[3,6]`; "Model 4"; [@fig-cvrlh]A-C).
 
@@
 #| fig-cap: "Meta-analysis results for different life stages.
-Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult (a) and juvenile (j) life-history stages for terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
+Estimated mean acclimation and acute $lnRR_{Q_{10}}$ (A-C) and $lnVR_{Q_{10}}$ (D-F) for adult and juvenile life-history stages for terrestrial (A & D), marine (B & E) and freshwater (C & F) ectotherms.
 Across all plots, thick bars indicate 95% confidence intervals and thin bars indicate 95% prediction intervals.
@@
 # Terrestrial
-  p_t_rr <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+  p_t_rr <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclimation}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
     geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
@@
 # Marine
-p_m_rr <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+p_m_rr <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclimation}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
     geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
@@
 # Freshwater
-p_f_rr <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
+p_f_rr <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclimation}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
     geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
@@
   x_f = 0.6
-  p_f_vr <-  bubble_plot(model5.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
+  p_f_vr <-  bubble_plot(model5.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclimation}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
       geom_point(data = lnVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
@@
   x_m = -0.4
-  p_m_vr <-  bubble_plot(model5.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
+  p_m_vr <-  bubble_plot(model5.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclimation}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
     geom_point(data = lnVRQ10_data_wild_acclim_m, 
@@
 x_t = 0
-p_t_vr <-  bubble_plot(model5.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
+p_t_vr <-  bubble_plot(model5.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnVR_{Q_{10_{acclimation}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
   geom_point(data = lnVRQ10_data_wild_acclim_t, 
@@
 
-The change in acclimation $Q_{10}$ we found in our expanded dataset was similar to @Seebacher2015-wi for freshwater organisms (~17\%), but higher in marine ectotherms [decrease of 16\% versus ~10\% in @Seebacher2015-wi], and opposite in terrestrial ectotherms [increase of ~6\% compared to an ~8\% decrease in @Seebacher2015-wi].
+The change in acclimation $Q_{10}$ we found in our expanded dataset was similar to @Seebacher2015-wi for freshwater organisms (~17\%), but higher in marine ectotherms [decrease of 16\% versus ~10\% in @Seebacher2015-wi], and lower in terrestrial ectotherms [increase of ~6\% compared to an ~8\% decrease in @Seebacher2015-wi].
 The difference observed in terrestrial ectotherms between studies may be due to additional data from terrestrial species added in our analysis, and to the use of newly derived $Q_{10}$ effect sizes that allowed us to control for sampling variance.

### 2025-02-17 ms.qmd
Fixing up requested changes

@@
 
-Contrary to acclimation capacity variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation of mean trait values.
+Contrary to acclimation capacity, variance in physiological rates increased across habitats with effect sizes being 3-5 times larger than those observed for acclimation of mean trait values.
 Mechanistically, it is unclear what exactly is contributing to the increased variation in physiological rates at higher temperatures, but it is likely the result of increased among-individual variability in how biochemical, cellular and physiological processes function at higher temperatures to maintain homeostasis [@tattersall2012coping; @angilletta2009thermal; @somero1995proteins; @fields2001protein; @schulte2011thermal].
@@
 Using $\Delta lnRR_{Q_{10}}$ for each trait within a study we fit a model that estimated the meta-anlaytic mean effect size for each habitat (freshwater, marine and terrestrial) accounting for acclimation time and maximum temperature as in our main analysis, along with random effects of study, species, phylogeny, and trait.
-Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta.
+Our analyses give quantitatively and qualitatively similar results to our main analysis (@fig-delta).
 Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c)`, 95\% CI: `r quantile(b_max_temp_c, c(0.025, 0.975))`, p = `r pmcmc(b_max_temp_c)`).

### 2025-02-17 ms.qmd
Dealt with all reviewer responses and responded to them all.

@@
 For studies that only measured $R_{1}$, $R_{2}$, $SD_{1}^2$ and $SD_{2}^2$ after acclimation we could only calculate acclimation versions of these effect size estimates.
+Ideally, all studies would have a fully factorial design but this was not always the case making it challenging to compare acute and acclimated responses within studies.
+Nonetheless, our analytical models are suitable for dealing with missing within-study acute effects (see below).
+In addition, analysis of a subset of the data where acute and acclimation effects could be compared within studies yields the same conclusion (See *Supplementary Materials*).
 For all effect sizes the higher temperature was in the numerator and the lower of the two temperatures in the denominator.
@@
 
+# Model only used for model comparison
+model6_bayes_nonsmooth <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + type*habitat + Longitude + Latitude +
+                               (1 + type | record_num) + 
+                               (1 | gr(species_full, cov = A_wild_vr)) + 
+                               (1 + max_temp_c | spp) + 
+                               (1 | trait) + 
+                               (1 | obs), 
+                      data2 = list(A_wild_vr=A_wild_vr), family = gaussian(), 
+                      prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
+                      control = list(adapt_delta = 0.99, max_treedepth = 12), 
+                      chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, 
+                      data = lnVRQ10_data_wild[complete.cases(lnVRQ10_data_wild$c_accl_time),])
+
   saveRDS(model6_bayes, file = "./output/models/lnVRQ10_6_bayes")
+  saveRDS(model6_bayes_nonsmooth, file = "./output/models/lnVRQ10_6_bayes_nonsmooth")
 
@@
 Projected changes in physiological rate variance were highly variable across the globe, however, variance was predicted to increase at all locations.
+Latitude and longitude explained variation in these responses with models containing smoothers being supported over models with just main effects of latitude and longitude ($\Delat$ wAIC = 2.9).
 
